### 2015-08-17 code/01_generate_networks.Rmd
initial R matching

---
title: "Generate Networks"
author: "Fernando Cagua"
date: "17 August 2015"
output: html_document
---

```{r, echo = FALSE, message=FALSE, warning=FALSE}
library(dplyr)
library(magrittr)
library(knitr)

opts_knit$set (root.dir=normalizePath('../'))
opts_chunk$set (fig.path = "./figures/01/")
opts_chunk$set (cache.path = "./cache/02/")
opts_chunk$set (fig.width = 11, 
                fig.height = 9,
                out.width = "858px")
```

First I read the data. Here I'm assuming that the different sites are independent, that the `Round` column corresponds to different samplings days and that it's OK to estimate the total weight by adding `Number_of_visits_per6min` across `Round`

```{r}
data <- read.csv("./data/network_data/Bartomeus_Ntw_nceas.txt",sep="\t") %>%
	tbl_df() %T>% print(width = Inf)

ntw <- data %>%
	dplyr::mutate(pla = paste0("p_", Plant_id),
								pol = paste0("i_", Insect_id)) %>%
	dplyr::group_by(Site, pla, pol) %>%
	dplyr::summarise(weight = sum(Number_of_visits_per6min)) %>%
	dplyr::group_by() %T>%
	print()
```

Now let's convert it to an `igraph` network and calculate a bipartite maximal matching.

```{r}
m_match <- plyr::dlply(ntw, "Site", function(x){
	edg <- x %>% 
		dplyr::select(-Site)
	ver <- edg %>%
		dplyr::select(-weight) %>%
		tidyr::gather(type, name, pla, pol) %>%
		dplyr::distinct() %>%
		dplyr::select(name, type)

	net <- igraph::graph.data.frame(edg, directed = F, vertices = ver)
	list(net = net,
			 match = igraph::maximum.bipartite.matching(net))
})
```

Now let's have a look at the matching results

```{r}
plyr::ldply(m_match, function(x){
	data.frame(matching_size = x$match$matching_size,
						 n_pla = table(igraph::V(x$net)$type)["pla"],
						 n_pol = table(igraph::V(x$net)$type)["pol"],
						 n_int = length(igraph::E(x$net)$weight),
						 matching_weight = x$match$matching_weight,
						 sum_weight = sum(igraph::E(x$net)$weight))
}) %>% kable
```

### 2015-08-23 code/01_generate_networks.Rmd
find matching size R

@@
 opts_chunk$set (fig.path = "./figures/01/")
-opts_chunk$set (cache.path = "./cache/02/")
+opts_chunk$set (cache.path = "./cache/01/")
 opts_chunk$set (fig.width = 11, 
@@
 						 sum_weight = sum(igraph::E(x$net)$weight))
-}) %>% kable
+}) %>% 
+	dplyr::mutate(n_comb = choose(n_int, matching_size)) %>%
+	kable
 ```
+
+The matching size and number of interactions doesn't coincide with the ones previously used for the bipartite matching.

### 2015-09-02 paper/manuscript.tex
start manuscript. add acknowledgement to takeuki

\documentclass{article}

\begin{document}

\section{Acknowledgmenets}

Takeuki Uno for the insight provided to find the set of all maximum matching algorithms.

\end{document}

### 2015-09-02 code/02_example_maximum_matching.Rmd
explore the algorithm to calculate all maximum matchings in a bipartite network

---
title: "Calculating all possible maximum matchings"
author: "Fernando Cagua"
date: "2 September 2015"
output: html_document
---

```{r, echo = FALSE, message=FALSE, warning=FALSE}
library(dplyr)
library(magrittr)
library(igraph)
library(ggplot2)
library(knitr)

opts_knit$set (root.dir=normalizePath('../'))
opts_chunk$set (fig.path = "./figures/02/")
opts_chunk$set (cache.path = "./cache/02/")
opts_chunk$set (fig.width = 11, 
                fig.height = 6,
                out.width = "858px")
```

```{r, echo = FALSE, results = "hide", message=FALSE, warning=FALSE}
list.files("./code/functions", full.names = TRUE) %>% lapply(source)
```

Here I show how to calculate the bipartite maximum matchings of an arbitrary bipartite graph.

### 1. Create the graph

```{r, warning = FALSE}
g <- graph_from_literal( a-b-c-d-e-f-a, a-d, g-f, h, i-f, j-k-h)
V(g)$type <- c(FALSE,TRUE)
g %>%	add_layout_(as_bipartite()) %>%	plot()
```

### 2. Calculate a maximum bipartite matching

```{r}
match <- max_bipartite_match(g) 
print(match)
```

This give use the size of the matching, this is how many nodes can be matched on each side.

### 3. Make the line graph of the bipartite network

Which is the an alternative representation in which edges become nodes and there is a link between them if they share a node in the original network

```{r}
h <- g %>% igraph::make_line_graph() %T>% plot
```

### 4. Get the complementer graph of the line graph

Which is equivalent of changing all 0s for 1s and all 1s for 0s in the adjacency matrix

```{r}
h <- h %>% igraph::complementer() %T>% plot
```

### 5. Find all the cliques that have the same size as the maximum matching found before

```{r}
cli <- h %>% igraph::max_cliques(min = match$matching_size)
cli <- unlist(cli) %>% matrix(ncol = match$matching_size, byrow = TRUE)
print(cli)
```

### 6. Let's have a look!!!

At five of them...

```{r, fig.height= 5}
matchings <- apply(cli, 1, function(x) {
	y <- rep(1, length(E(g)))
	y[x] <- 2
	y
})

plyr::a_ply(matchings[, round(seq(1,20, length.out = 5))], 2, function(x){
	p <- g %>%	add_layout_(as_bipartite()) %>%	plot.igraph(edge.color = x)
})
```

### 7. Let's see the proportion of unmatched

On posibility is to rank nodes by how many times they act as driver nodes in all maximum matchings in the network. Here we assume that we only want to match the nodes on "top"

```{r}
get_matched_vertex(g, choosen_type = FALSE, 
									 matchings = cli, output = "data.frame") %>%
	dplyr::filter(matched == FALSE) %>%
	ggplot() +
	geom_histogram(aes(x = v)) +
	xlab("vertex") +
	ylab("frequency of acting as a driver node") +
	theme_minimal()
```

### 2015-09-02 code/02_example_maximum_matching.Rmd
analise nodes and links from the critical/redundant perspective

@@
 
+I'm interested in investingating the relative importance of different nodes (and edges) for the controlability of bipartite networks.
+
+# 1. All maximum matchings
+
+One option is to see how many times the node is selected as a driver node based on all the possible maximum matchings on a bipartite network
+
+## Find them first
+
 Here I show how to calculate the bipartite maximum matchings of an arbitrary bipartite graph.
 
-### 1. Create the graph
+### Create the graph
 
@@
 
-### 2. Calculate a maximum bipartite matching
+### Calculate a maximum bipartite matching
 
@@
 
-### 3. Make the line graph of the bipartite network
+### Make the line graph of the bipartite network
 
@@
 
-### 4. Get the complementer graph of the line graph
+### Get the complementer graph of the line graph
 
@@
 
-### 5. Find all the cliques that have the same size as the maximum matching found before
+### Find all the cliques that have the same size as the maximum matching found before
 
@@
 
-### 6. Let's have a look!!!
+Let's have a look!!!
 
@@
 
-### 7. Let's see the proportion of unmatched
+## Analyse importance
 
@@
 ```{r}
-get_matched_vertex(g, choosen_type = FALSE, 
+node_relev_m <- get_matched_vertex(g, choosen_type = FALSE, 
 									 matchings = cli, output = "data.frame") %>%
-	dplyr::filter(matched == FALSE) %>%
+	dplyr::group_by(v) %>%
+	dplyr::summarise(freq = sum(!matched))
+
+node_relev_m %>%
 	ggplot() +
-	geom_histogram(aes(x = v)) +
+	geom_point(aes(x = v, y = freq), shape = 21, size = 4) +
 	xlab("vertex") +
 	ylab("frequency of acting as a driver node") +
-	theme_minimal()
+	theme_bw()
 ```
+
+# 2. By removing links/nodes
+
+Another alternative to determine the relative importance of each node (but also links) is to remove it and see how it affects the matching.
+Following Liu, Slotine and Barabasi 2011, for links we have the following definitions:
+
+1. **Critical** if in it's absense we need to increase the number of driver nodes to maintain full control of the system
+2. **Redundant** if it can be removed without affecting the current set of driver nodes
+3. **Ordinary** if it's neither critical nor redundant, i.e., its removal can eliminate some control configurations, but the network can still be controlable in its absense
+
+for nodes we have the following definitions
+
+1. **Critical** if in it's absense we need to increase the number of driver nodes to maintain full control of the system
+2. **Redundant** if it after removal the current set of driver nodes decreasses
+3. **Ordinary** if after removal the number of driver nodes is maintained
+
+We wan't to see if these definitions (particularly for the nodes) agree with the measssures given by the maxumum matchings.
+
+Let's use the same dummy network as before.
+
+```{r, warning = FALSE}
+g %>%	add_layout_(as_bipartite()) %>%	plot()
+```
+
+### Calculate a maximum bipartite matching
+
+```{r}
+match <- max_bipartite_match(g) 
+this_side_nodes <- length(V(g)[type == F])
+min_drivers <- this_side_nodes - match$matching_size
+print(match)
+```
+
+## Importance for links
+
+```{r}
+plyr::ldply(E(g), function(x){
+	matching_size <- g %>% delete_edges(x) %>%
+		max_bipartite_match() %$%
+		matching_size
+	data.frame(e = x, matching_size = matching_size)
+}) %>%
+	dplyr::mutate(delta_drivers = this_side_nodes - matching_size - min_drivers,
+								categ = categ_link(delta_drivers))
+```
+
+Well this is boring. All edges are redundant
+
+## Importance for nodes
+
+```{r}
+node_relev_c <- plyr::ldply(V(g), function(x){
+	matching_size <- g %>% delete_vertices(x) %>%
+		max_bipartite_match() %$%
+		matching_size
+	data.frame(v = x, matching_size = matching_size)
+}) %>%
+	dplyr::mutate(delta_drivers = this_side_nodes - matching_size - min_drivers,
+								categ = categ_node(delta_drivers)) %T>% print
+```
+
+This not as boring :) We can see that some are redundant ordinary and some are critical (there is no redundant one).
+
+# Compare
+
+```{r}
+dplyr::inner_join(node_relev_m, node_relev_c, by = c("v" = ".id")) %>%
+	ggplot() +
+	geom_point(aes(x = v, y = freq, fill = categ), shape = 21, size = 4) +
+	xlab("vertex") +
+	ylab("frequency of acting as a driver node") +
+	theme_bw()
+```
+
+Well now I realise this network was a crappy example.
+Obviously removing R decreasses the matching...
+But I don't think that'll happen using the proper bipartite matching (this is having head vertices in one side and tail vertices in the other).
+Especially because f, d, and b were also critical.
+
+Still this is a good proof of concept of what will come for the other networks

### 2015-09-08 code/01_generate_networks.Rmd
modify code to comply better with igraph 1.0
update script to match new data structure

@@
 ```{r}
-data <- read.csv("./data/network_data/Bartomeus_Ntw_nceas.txt",sep="\t") %>%
+data <- read.csv("./data/bartomeus/Bartomeus_Ntw_nceas.txt",sep="\t") %>%
 	tbl_df() %T>% print(width = Inf)
@@
 
-	net <- igraph::graph.data.frame(edg, directed = F, vertices = ver)
+	net <- igraph::graph_from_data_frame(edg, directed = F, vertices = ver)
 	list(net = net,

### 2015-09-08 code/01_generate_networks.Rmd
save networks as an igraph object

@@
 The matching size and number of interactions doesn't coincide with the ones previously used for the bipartite matching.
+
+## Save networks for later use
+
+```{r}
+networks <- plyr::dlply(ntw, "Site", function(x){
+	edg <- x %>% 
+		dplyr::select(-Site)
+	ver <- edg %>%
+		dplyr::select(-weight) %>%
+		tidyr::gather(type, name, pla, pol) %>%
+		dplyr::distinct() %>%
+		dplyr::select(name, type)
+
+	igraph::graph_from_data_frame(edg, directed = F, vertices = ver)
+})
+
+saveRDS(networks, "./data/bartomeus/networks.dat", ascii = TRUE, compress = FALSE)
+```

### 2015-09-08 code/03_ntw_maximum_matchings.R
scripts to calculate all possible maximum matchings in the networks

@@ -1,0 +1,38 @@
+# This script calculates all the possible maximum matchings for each of the
+# networks. It is designed to run in the cluster
+setwd("~/github/controlling-pollination-networks/")
+
+# which network
+i <- as.integer(commandArgs(trailingOnly = TRUE)[1])
+i <- 3
+# load libraries
+library(magrittr)
+# load functions
+list.files("./code/functions", full.names = TRUE) %>% lapply(source)
+# load networksnano
+net <- readRDS("./data/bartomeus/networks.dat")
+# generate parameter space
+space <- expand.grid(type = c("bi", "weight", "AB", "BA"), 
+										 net = 1:length(net)) %>%
+	dplyr::inner_join(data.frame(type = c("bi", "AB", "BA", "weight", "weight"),
+															 keep = c("all", "A", "B", "A", "B")))
+# select the corresponding one for this computation
+p <- space[i,]
+# transform the network into the bipartite format we need
+m_net <- net[[p$net]] %>%
+	bipartite_digraph(type = p$type, keep = p$keep) %>%
+	digraph_bipartite() %>%
+	igraph::add_layout_(igraph::as_bipartite())
+# calculate a maximum matching (so we know the size)
+matching <- igraph::max_bipartite_match(m_net)
+
+# set the filename where the matchings will be saved
+filename <- paste(names(net)[p$net], p$type, p$keep, sep = "_")
+filename <- paste0("./data/bartomeus/maximum_matchings/", filename, ".dat")
+
+# actually calculate all the maximum matchings for the network
+igraph::make_line_graph(m_net) %>%
+	igraph::complementer() %>% 
+	igraph::max_cliques(min = matching$matching_size, 
+											max = matching$matching_size, 
+											file = filename)

### 2015-09-08 code/_03_ntw_maximum_matchings.sh

@@ -1,0 +1,13 @@
+#!/bin/bash
+
+#$ -V
+#$ -cwd
+#$ -j y
+#$ -S /bin/bash
+#$ -t 1-60
+#$ -m a
+#$ -M efc29@uclive.ac.nz
+#$ -r yes
+
+Rscript --no-save --no-restore 03_ntw_maximum_matchings.R $SGE_TASK_ID 
+exit 0

### 2015-09-16 code/01_generate_networks.Rmd
scripts to calculate all possible maximum matchings in the networks
change data saving structure

@@
 ```{r}
-data <- read.csv("./data/bartomeus/Bartomeus_Ntw_nceas.txt",sep="\t") %>%
+data <- read.csv("./data/Bartomeus_Ntw_nceas.txt",sep="\t") %>%
 	tbl_df() %T>% print(width = Inf)
@@
 
-saveRDS(networks, "./data/bartomeus/networks.dat", ascii = TRUE, compress = FALSE)
+for(i in 1:length(networks)){
+	saveRDS(networks[[i]],
+					paste0("./data/networks/", names(networks)[i], ".dat"),
+					ascii = TRUE, compress = FALSE)
+}
+
 ```

### 2015-09-18 code/05_read_redundancy.Rmd
read node redundancy results

---
title: "Read redundancies"
author: "Fernando Cagua"
date: "12 September 2015"
output: html_document
---

```{r, echo = FALSE, message=FALSE, warning=FALSE}
library(dplyr)
library(magrittr)
library(knitr)
library(ggplot2)
library(ggtern)

opts_knit$set (root.dir=normalizePath('../'))
opts_chunk$set (fig.path = "./figures/05/")
opts_chunk$set (cache.path = "./cache/05/")
opts_chunk$set (fig.width = 11, 
                fig.height = 9,
                out.width = "858px")
```

```{r}
# load utility functions
nn <- list.files("./code/functions", full.names = TRUE) %>% lapply(source)
# load netw
net <- list.files("./data/networks/", full.names = TRUE) %>%
	lapply(readRDS)
names(net) <- list.files("./data/networks/", full.names = FALSE) %>%
	stringr::str_split("\\.") %>% lapply(`[`, 1) %>% unlist ()
```

Let's have a look at the diferences in number of driver nodes of the different methods.

```{r, warning = FALSE}
# generate parameter space
space <- expand.grid(type = c("bi", "weight", "AB", "BA"), 
										 net = 1:length(net)) %>%
	dplyr::inner_join(data.frame(type = c("bi", "AB", "BA", "weight", "weight"),
															 keep = c("all", "A", "B", "A", "B")))
# select the corresponding one for this computation

driver_nodes <- 1:nrow(space) %>%
	plyr::laply(function(i){
		p <- space[i,]
		net[[p$net]] %>%
			keep_largest_component() %>%
			bipartite_digraph(type = p$type, keep = p$keep) %>%
			n_unmatched_vertex()
	})

space %<>%
	dplyr::mutate(n_driver = driver_nodes,
								type = interaction(type, keep))

net_names <- plyr::ldply(net, function(x){
	length(igraph::V(x))
}) %>%
	dplyr::mutate(net = 1:nrow(.)) %>%
	dplyr::rename(n_species = V1,
								net_name = `.id`)

space <- dplyr::inner_join(space, net_names) %>%
	dplyr::mutate(n_no_driver = n_species - n_driver)

glm(cbind(n_driver, n_no_driver) ~ type,  data = space, family = "binomial") %>% summary

```

This means,

 * ~ 52% of the species for Pla-Pol or Pol-Pla 
 * ~ 43% of the species for weighted (regardless of priority)
 * ~ 15% of the species for bi-directional

Which is quite an improvement.

# Node redundancy

Now let's have a look at the proportion of critical, redundant and ordinary nodes in each class.

```{r, warning = FALSE}
folder <- "./data/redundancy/node/"

node_redundancy <- list.files(folder, full.names = TRUE) %>%
	plyr::ldply(function(x, name){
		y <- read.csv(x) 
		info <- basename(x) %>% 
			stringr::str_sub(end = -5) %>% 
			stringr::str_split("_") %>% 
			unlist()
		y %>%
			dplyr::mutate(net = info[[1]],
										type = info[2],
										keep = info[3])
	})

ggplot(node_redundancy) +
	geom_bar(aes(x = interaction(type, keep), fill = robustness)) +
	facet_wrap(~ net, scales = "free", nrow = 2) +
	scale_fill_brewer(palette = "Set1")

node_redundancy %>%
	dplyr::mutate(type = interaction(type, keep)) %>%
	dplyr::group_by(net, type, robustness) %>%
	dplyr::summarise(n = n()) %>%
	tidyr::spread(robustness, n) %>%
	dplyr::mutate(critical = replace(critical, is.na(critical), 0)) %>%
	ggplot(aes(x = ordinary, z = redundant, y = critical)) +
	geom_point(aes(fill = type), shape = 21, size = 5, alpha = 0.7) + 
	facet_wrap(~ net) +
	coord_tern() + 
	scale_fill_brewer(palette = "Set1")

```

In both  representations we can see that there is little variation among configurations with the same phylosophy.

* For pla-pol or pol-pla all species are either redundant or ordinary
* There are some critical species in the weight configuration but most of them are redundant and ordinary to a lesser degree
* The bidirectional configuration makes a larger proportion of species critical species critical and almost all the other are redundant

# Save results

```{r}
write.csv(node_redundancy, file = "./data/node_redundancy.dat", row.names = F)
```

### 2015-10-07 code/03_ntw_maximum_matchings.R
fixing wrong maximum matchings that igraph didn't detect

@@ -40,16 +40,26 @@ m_net <- net[[as.numeric(p$net)]] %>%
 	igraph::add_layout_(igraph::as_bipartite())
 # calculate a maximum matching (so we know the size)
 matching <- igraph::max_bipartite_match(m_net)
+# this igraph function is wrong
 
 # set the filename where the matchings will be saved
 filename <- paste(names(net)[as.numeric(p$net)], p$type, p$keep, sep = "_")
 filename <- paste0("./data/maximum_matchings/", filename, ".dat")
 
-# actually calculate all the maximum matchings for the network
-igraph::make_line_graph(m_net) %>%
-	igraph::complementer() %>% 
-# 	igraph::count_max_cliques(min = matching$matching_size, 
-# 														max = matching$matching_size) %>%
-	igraph::max_cliques(min = matching$matching_size, 
-											max = matching$matching_size, 
-											file = filename)
+# actually calculate all the maximum matchings for the network, but because we don't really know the size of the maximum matching, we'll loop over and see if the cliques algorithm can find more
+for (j in (matching$matching_size + 10):matching$matching_size){
+	
+	igraph::make_line_graph(m_net) %>%
+		igraph::complementer() %>% 
+		# 	igraph::count_max_cliques(min = matching$matching_size, 
+		# 														max = matching$matching_size) %>%
+		igraph::max_cliques(min = j, 
+												max = j, 
+												file = filename)
+	
+	if (length(scan(filename, nmax = 1)) != 0){
+		if (j == matching$matching_size + 10) waring("matching size is the top")
+		break
+	}
+	
+}

### 2015-10-07 code/05_read_redundancy.Rmd
change bi to z-bi

@@
 # generate parameter space
-space <- expand.grid(type = c("bi", "weight", "AB", "BA"), 
+space <- expand.grid(type = c("z-bi", "weight", "AB", "BA"), 
 										 net = 1:length(net)) %>%
-	dplyr::inner_join(data.frame(type = c("bi", "AB", "BA", "weight", "weight"),
+	dplyr::inner_join(data.frame(type = c("z-bi", "AB", "BA", "weight", "weight"),
 															 keep = c("all", "A", "B", "A", "B")))

### 2015-10-08 code/07_max-match_vs_redundancy.Rmd
alles

---
title: "redundancy vs maximum matchings"
author: "Fernando Cagua"
date: "5 October 2015"
output: html_document
---

```{r, echo = FALSE, message=FALSE, warning=FALSE}
library(dplyr)
library(magrittr)
library(knitr)
library(ggplot2)
library(ggtern)

opts_knit$set (root.dir=normalizePath('../'))
opts_chunk$set (fig.path = "./figures/07/")
opts_chunk$set (cache.path = "./cache/07/")
opts_chunk$set (fig.width = 11, 
                fig.height = 9,
                out.width = "858px")
```

```{r}
# load utility functions
nn <- list.files("./code/functions", full.names = TRUE) %>% lapply(source)
# load netw
net <- list.files("./data/networks/", full.names = TRUE) %>%
    lapply(readRDS)
names(net) <- list.files("./data/networks/", full.names = FALSE) %>%
    stringr::str_split("\\.") %>% lapply(`[`, 1) %>% unlist ()
```

Let's check if the redundancy matches the maximum matching results.

## Read redundancy

```{r}
node_redundancy <- read.csv(file = "./data/node_redundancy.dat")

node_re <- node_redundancy %>% 
	plyr::ddply("net", function(x){
		this_net <- net[[first(x$net)]] %>%
	# select only the largest connected component of the network
			keep_largest_component()
		nodes <- igraph::V(this_net)[x$n]$name
		x %>%
			dplyr::mutate(node = nodes)
	}) %>% dplyr::tbl_df()
```

## Read maximum matchings

```{r}
folder <- "./data/maximum_matchings_summary/" 
files <- list.files(folder)
node_mm <- plyr::adply(files, 1, function(x){
	read.csv(file.path(folder, x)) %>%
		dplyr::mutate(net = unlist(stringr::str_split(x, "_"))[1],
									type = unlist(stringr::str_split(x, "_"))[2], 
									keep = unlist(stringr::str_split(x, "_"))[3],
									batch = unlist(stringr::str_split(x, "_"))[4])
}) %>%
	dplyr::select(-X1) %>%
	dplyr::group_by(net, type, keep, node) %>%
	dplyr::summarise(freq = sum(freq))

```

## Join them

```{r}
dplyr::full_join(node_mm, node_re) %>%
	dplyr::filter(!is.na(freq)) %>%
	dplyr::group_by(net, type, keep) %>%
	dplyr::mutate(r = rank(freq, ties.method = "first"),
								f_f = freq/max(freq)) %>%

	ggplot() +
	geom_point(aes(x = r, y = f_f, fill = robustness), shape = 21) +
	facet_wrap(type ~ net, scales = "free")
```

### 2015-10-08 code/08_invaded_vs_non-invaded.Rmd
alles

---
title: "Invaded vs non invaded"
author: "Fernando Cagua"
date: "5 October 2015"
output: html_document
---

```{r, echo = FALSE, message=FALSE, warning=FALSE}
library(dplyr)
library(magrittr)
library(knitr)
library(ggplot2)
library(ggtern)

opts_knit$set (root.dir=normalizePath('../'))
opts_chunk$set (fig.path = "./figures/08/")
opts_chunk$set (cache.path = "./cache/08/")
opts_chunk$set (fig.width = 11, 
                fig.height = 9,
                out.width = "858px")
```

```{r}
# load utility functions
nn <- list.files("./code/functions", full.names = TRUE) %>% lapply(source)
# load netw
net <- list.files("./data/networks/", full.names = TRUE) %>%
    lapply(readRDS)
names(net) <- list.files("./data/networks/", full.names = FALSE) %>%
    stringr::str_split("\\.") %>% lapply(`[`, 1) %>% unlist ()
```

With the redundancy. What are the differences between the invaded and the non-invaded sites?

Base data frame

```{r}
node_redundancy <- read.csv(file = "./data/node_redundancy.dat")

inv <- dplyr::data_frame(net_name = unique(node_redundancy$net) %>% as.character(),
												 inv = grepl("2", net_name) | grepl("4", net_name)) %>% 
	dplyr::mutate(site = rep(c("BAT", "FRA", "MED", "FAR", "MIQ", "SEL"), each =2),
								invader = rep(c("car", "op", "car", "op"),  c(2, 2, 4, 4)))
```

```{r}
# generate parameter space
space <- expand.grid(type = c("bi", "weight", "AB", "BA"), 
                                         net = 1:length(net)) %>%
    dplyr::inner_join(data.frame(type = c("bi", "AB", "BA", "weight", "weight"),
                                                             keep = c("all", "A", "B", "A", "B")))

# select the corresponding one for this computation

driver_nodes <- 1:nrow(space) %>%
    plyr::laply(function(i){
        p <- space[i,]
        net[[p$net]] %>%
            keep_largest_component() %>%
            bipartite_digraph(type = p$type, keep = p$keep) %>%
            n_unmatched_vertex()
    })

space %<>%
    dplyr::mutate(n_driver = driver_nodes,
                                type = interaction(type, keep))

net_names <- plyr::ldply(net, function(x){
    length(igraph::V(x))
}) %>%
    dplyr::mutate(net = 1:nrow(.)) %>%
    dplyr::rename(n_species = V1,
                                net_name = `.id`)

space <- dplyr::inner_join(space, net_names) %>%
    dplyr::mutate(n_no_driver = n_species - n_driver)
```

Let's see if there is a difference in the proportion of needed species by invasion type

```{r}
space %<>%
	dplyr::mutate(prop_driver = n_driver/n_species) %>%
	dplyr::inner_join(inv)
```

```{r}
space %>%
	ggplot() +
	geom_boxplot(aes(y = prop_driver, x = type, fill = inv))

lme4::glmer(cbind(n_driver, n_no_driver) ~ inv + (1|type) , data = space, family = "binomial") %>%
	summary()
```

Let's try again

```{r}
s_diff <- space %>% 
	arrange(inv) %>%
	group_by(site, type) %>%
	summarise(dif = diff(qlogis(prop_driver)), 
						invader = unique(invader))

s_diff %>%
	ggplot(aes(x = dif)) +
	geom_density()

lme4::lmer(dif ~ invader + (1|type) , data = s_diff) %>%
	summary()
```

No. No differences on the proportion of driver nodes between invaded and un-invaded systems, though almost... The proportion is a bit higher for the invaded system, but we don't have enough replicates to see if it's significant or not.

## Composition differences

Let's look at the number of

### 2015-10-08 code/functions/bipartite_digraph.R

@@ -10,7 +10,7 @@
 #' 
 #' @examples
 bipartite_digraph <- function(net,
-											type = c("bi", "weight", "AB", "BA"),
+											type = c("z-bi", "weight", "AB", "BA"),
 											keep = c("all", "A", "B", "random")){
 	
 	# sanity checks
@@ -22,7 +22,7 @@ bipartite_digraph <- function(net,
 	)
 	
 	# if its bidirectional just make an easy convertion
-	if (type[1] == "bi") y <- igraph::as.directed(net)
+	if (type[1] == "z-bi") y <- igraph::as.directed(net)
 	
 	# if it's by weight
 	else if (type[1] == "weight") {

### 2015-10-08 code/tinkering.R

@@ -1,0 +1,64 @@
+netBIt <- net[[1]] %>%
+	keep_largest_component() %>%
+	bipartite_digraph(type = "z-bi", keep = "all")
+
+netBI <- net[[1]] %>%
+	keep_largest_component() %>%
+	bipartite_digraph(type = "z-bi", keep = "all") %>%
+	igraph::delete_vertices("p_1")
+
+netABt <- net[[1]] %>%
+	keep_largest_component() %>%
+	bipartite_digraph(type = "AB", keep = "A")
+
+netAB <- net[[1]] %>%
+	keep_largest_component() %>%
+	bipartite_digraph(type = "AB", keep = "A") %>%
+	igraph::delete_vertices("p_1")
+
+netBAt <- net[[1]] %>%
+	keep_largest_component() %>%
+	bipartite_digraph(type = "BA", keep = "B") 
+
+netBA <- net[[1]] %>%
+	keep_largest_component() %>%
+	bipartite_digraph(type = "BA", keep = "B") %>%
+	igraph::delete_vertices("p_1")
+
+a <- . %T>% igraph::plot.igraph(vertex.size = 10, edge.arrow.size = 0.2, vertex.color = V(.)$type == "pla") %>% igraph::add_layout_(igraph::as_bipartite(V(.)$type == "pla")) %T>%
+	igraph::plot.igraph(vertex.size = 10, edge.arrow.size = 0.2) %>% digraph_bipartite() %T>% igraph::plot.igraph(vertex.size = 10, edge.arrow.size = 0.2)   %>%
+	igraph::add_layout_(igraph::as_bipartite()) %>%
+	igraph::max_bipartite_match()
+
+35-a(netBIt)$matching_size
+35-a(netABt)$matching_size
+a(netBA)$matching_size
+
+# calculate a maximum matching (so we know the size)
+matching$matching[is.na(matching$matching) 
+									& grepl("to", names(matching$matching))] %>%
+	length()
+
+library(igraph)
+net[[1]] %>%
+	add_layout_(as_bipartite(V(.)$type=="pla")) %>% plot.igraph()
+
+matching <- igraph::max_bipartite_match(m_net)
+
+# actually calculate all the maximum matchings for the network
+netABtb <- netABt %>% digraph_bipartite()
+netBAtb <- netBAt %>% digraph_bipartite() 
+netBItb <- netBIt %>% digraph_bipartite() 
+
+b <- netBItb %>%
[…]

### 2015-10-19 code/05_read_redundancy.Rmd
correct redundancy

@@
 	tidyr::spread(robustness, n) %>%
-	dplyr::mutate(critical = replace(critical, is.na(critical), 0)) %>%
+	dplyr::mutate(critical = replace(critical, is.na(critical), 0),
+								ordinary = replace(ordinary, is.na(ordinary), 0)) %>%
 	ggplot(aes(x = ordinary, z = redundant, y = critical)) +

### 2015-10-19 code/04_critical_elements.R

@@ -35,6 +35,7 @@ message("Critical Elements Index ", i, " Working on net ", p$net, "; type ", p$t
 m_net <- net[[p$net]] %>%
 	keep_largest_component() %>%
 	bipartite_digraph(type = p$type, keep = p$keep)
+igraph::E(m_net)$weight <- 1
 
 # get baseline number of unmatched vertices
 base_n_unm <- n_unmatched_vertex(m_net)

### 2015-10-20 code/08_invaded_vs_non-invaded.Rmd
comparing invaded vs non invaded ecosystems

@@
 # generate parameter space
-space <- expand.grid(type = c("bi", "weight", "AB", "BA"), 
+space <- expand.grid(type = c("z-bi", "weight", "AB", "BA"), 
                                          net = 1:length(net)) %>%
-    dplyr::inner_join(data.frame(type = c("bi", "AB", "BA", "weight", "weight"),
+    dplyr::inner_join(data.frame(type = c("z-bi", "AB", "BA", "weight", "weight"),
                                                              keep = c("all", "A", "B", "A", "B")))
@@
 		p <- space[i,]
-        net[[p$net]] %>%
+		n <- net[[p$net]] %>%
 			keep_largest_component() %>%
-            bipartite_digraph(type = p$type, keep = p$keep) %>%
+			bipartite_digraph(type = p$type, keep = p$keep)
+		igraph::E(n)$weight <- 1
+		n %>%
 			n_unmatched_vertex()
@@
 
-Let's look at the number of
+Let's look at the number of critical/redundant species
+
+```{r}
+node_redundancy %>%
+	dplyr::mutate(type = paste(type, keep, sep = ".")) %>%
+	dplyr::rename(net_name = net) %>%
+	dplyr::group_by(net_name, type, robustness) %>%
+	dplyr::summarise(n = n()) %>%
+	dplyr::group_by() %>%
+	dplyr::left_join(space)
+
+```

### 2015-10-20 code/05_read_redundancy.Rmd
update redundancy results

@@
 		p <- space[i,]
-		net[[p$net]] %>%
+		n <- net[[p$net]] %>%
 			keep_largest_component() %>%
-			bipartite_digraph(type = p$type, keep = p$keep) %>%
+			bipartite_digraph(type = p$type, keep = p$keep)
+		igraph::E(n)$weight <- 1
+		n %>%
 			n_unmatched_vertex()
@@
 
- * ~ 52% of the species for Pla-Pol or Pol-Pla 
- * ~ 43% of the species for weighted (regardless of priority)
- * ~ 15% of the species for bi-directional
+ * ~ 74% of the species for Pla-Pol or Pol-Pla 
+ * ~ 67% of the species for weighted (regardless of priority)
+ * ~ 50% of the species for bi-directional
 

### 2015-12-01 code/05_read_redundancy.Rmd
presentation figures

@@
 
+inv <- dplyr::data_frame(net = unique(node_redundancy$net) %>% as.character(),
+												 inv = grepl("2", net) | grepl("4", net)) %>% 
+	dplyr::mutate(site = rep(c("BAT", "FRA", "MED", "FAR", "MIQ", "SEL"), each =2),
+								invader = rep(c("car", "op", "car", "op"),  c(2, 2, 4, 4)))
+
+nr <- node_redundancy %>%
+	dplyr::mutate(type = interaction(type, keep)) %>%
+	dplyr::group_by(net, type, robustness) %>%
+	dplyr::summarise(n = n()) %>%
+	tidyr::spread(robustness, n) %>%
+	dplyr::mutate(critical = replace(critical, is.na(critical), 0),
+								ordinary = replace(ordinary, is.na(ordinary), 0)) %>%
+	dplyr::filter(type == "weight.A") %>%
+	dplyr::inner_join(inv)
+
+points <- 
+	rbind(c(1, 0, 0, 100), 
+				c(2, 100, 0, 0),
+				c(3, 0, 100, 0),
+				c(4, 100/3, 100/3, 100/3),
+				c(5, 50, 0, 50), 
+				c(6, 0, 50, 50),
+				c(7, 50, 50, 0)) %>%
+	data.frame() %>%
+	`colnames<-`(c("id", "o", "c", "r")) %T>% {
+		ggtern(data = ., aes(o, c, r)) +
+			geom_text(aes(label = id))
+	}
+
+polygons <- 
+	rbind(c(1, 1),
+				c(1, 5),
+				c(1, 4),
+				c(1, 6),
+				c(2, 2),
+				c(2, 7),
+				c(2, 4),
+				c(2, 5),
+				c(3, 3),
+				c(3, 6),
+				c(3, 4),
+				c(3, 7)) %>%
+	data.frame() %>%
+	`colnames<-`(c("lab", "id")) %>%
+	inner_join(points)
+
+pdf("./presentation_figures/tern_net_poster.pdf", width = 14.5, height = 5.5)
+ggplot() + 
+		geom_polygon(data = polygons, aes(x = o, y = c, z = r,  fill = as.factor(lab)), colour = "black", size = 1) +
+	geom_point(data = nr, aes(x = ordinary, z = redundant, y = critical), size = 8, shape = 21, fill = "white") +
+	coord_tern()	 + scale_fill_manual(values = c("#4daf4a", "#377eb8", "#e41a1c")) +
+	theme(text = element_blank())
+dev.off()
+
+pdf("./presentation_figures/tern_net_pres.pdf", width = 8, height = 5.5)
+ggplot() + 
+		geom_polygon(data = polygons, aes(x = o, z = c, y = r,  fill = as.factor(lab)), colour = "black", size = 1) +
+	geom_point(data = nr, aes(x = ordinary, y = redundant, z = critical), size = 5, shape = 21, fill = "white", alpha = 0.9) +
+	coord_tern()	 + scale_fill_manual(values = c("#4daf4a", "#377eb8", "#e41a1c")) +
+	theme(text = element_blank())
+dev.off()
 ```
@@
 ```
+
+# Link redundancy
+
+```{r}
+folder <- "./data/redundancy/edge/"
+
+link_redundancy <- list.files(folder, full.names = TRUE) %>%
+	plyr::ldply(function(x, name){
+		y <- read.csv(x) 
+		info <- basename(x) %>% 
+			stringr::str_sub(end = -5) %>% 
+			stringr::str_split("_") %>% 
+			unlist()
+		y %>%
+			dplyr::mutate(net = info[[1]],
+										type = info[2],
+										keep = info[3])
+	})
+
+link_redundancy %>%
+	dplyr::mutate(type = interaction(type, keep)) %>%
+	dplyr::group_by(net, type, robustness) %>%
+	dplyr::summarise(n = n()) %>%
+	tidyr::spread(robustness, n) %>%
+	dplyr::mutate(critical = replace(critical, is.na(critical), 0),
+								ordinary = replace(ordinary, is.na(ordinary), 0)) %>%
+	dplyr::filter(type == "AB.A") %>%
+	dplyr::inner_join(inv) %>%
+	ggplot(aes(x = ordinary, z = redundant, y = critical)) +
+	geom_point(aes(fill = inv), shape = 21, size = 5, alpha = 0.7) + 
+	coord_tern() + 
+	scale_fill_brewer(palette = "Set1")
+```

### 2015-12-01 presentation_figures/triad.R

@@ -1,6 +1,7 @@
 library(ggplot2)
 library(ggtern)
 library(magrittr)
+library(dplyr)
 
 points <- 
 	rbind(c(1, 0, 0, 100), 
@@ -33,10 +34,10 @@ polygons <-
 	`colnames<-`(c("lab", "id")) %>%
 	inner_join(points)
 
+pdf("./presentation_figures/tern_empty.pdf", width = 8, height = 5.5)
 ggtern(polygons,aes(o,r,c)) +
-	geom_polygon(aes(fill = as.factor(lab)), colour = "black", size = 2) +
+	geom_polygon(aes(fill = as.factor(lab)), colour = "black", size = 1) +
 	scale_fill_manual(values = c("#4daf4a", "#377eb8", "#e41a1c")) +
 	theme(text = element_blank(), 
-				line = element_blank(), 
-				legend.position = "top")
-
+				line = element_blank())
+dev.off()

### 2015-12-01 paper/manuscript.Rnw
manuscript and other minor changes

\input{preamble} % See preamble.tex to edit the overall layout

\begin{document}
\SweaveOpts{concordance=TRUE,prefix.string=figures/fig-}
\setkeys{Gin}{width=1\textwidth}

% title
\input{title_authors}
\maketitle

\begin{abstract}
\noindent Si sabemos que el disfrute exige lentitud, y que---mas en general---la felicidad se asocia con el ir despacio, por que corremos tanto? El arte de comer estriba en saborear cada bocado sin pensar en el siguiente, sin apresurar el siguiente. El arte de leer, en demorarse en cada palabra como si el sentido del escrito entero estuviera contenido en ella. El arte de amar, en vivir cada momento de la relacion con la persona amada como si fuese el destino de toda la historia del mundo, desde la aparicion del primer organismo unicelular hasta hoy. Y asi podemos generalizar a las demas actividades, creo, hasta obtener un arte de vivir. Para mi se resume en la palabra ahi. --- Jorge Riechmann
\end{abstract}

\keywords{Control theory}

% line numbers
\linenumbers
\setlength\linenumbersep{15pt}
\renewcommand\linenumberfont{\normalfont\footnotesize\sffamily\color{gray}}

\onehalfspacing

<<libraries and preparatory stuff, echo = FALSE>>=
library(ggplot2)
library(magrittr)
@

% Main Text
\section*{Introduction}

Ecological communities are formed by the interconnection of several species. Therefore, changes in the abundances of one species can potentially alter the abundances of the species they interact with. For instance, in a classic example of ecosystem cascades, a reduction on the abundance of sea otters, an important predator or sea urchins, can drive a dramatic reduction on kelp abundances because the sea urchins that consume kelp are released from predation. It has been long established that some species, like the sea otter, have a disproportionate large effect in their environment relative to their abundance.

In several ecosystems the relative importance of species have been identified based on empirical observations of long term dynamics. However, in less studied, highly diverse, or where the "keystone" role is shared by several species, it can be challenging to determine which is the set of species that influence the most the ecosystem dynamics. Alternative approaches that recognize a continuum of importance and that are less dependent on empirical observations have also been developed. Some of them are based on metrics that evaluate their position in the food web or on mass balance models of functional groups. Nevertheless, these approaches are conceptually limited to throphic interactions and in general ignore the structural mechanisms that allow or prevent the spread of perturbations in the ecosystem.

From a systems perspective, perturbations like over-exploitation, eutrophication or global warming are equivalent to management actions like culling, no-take areas or captive rearing in the sense that they have the potential to modify the abundances of one or several species in the ecosystem. Therefore identifying these key species is crucial not only to predict how these perturbations will spread trough the community but also to guide effective conservation efforts.

Recent work on the control of complex systems suggest that in principle it is possible to alter any ecological community's composition, by modifying the abundances of just some key species. Here, we apply these theories to estimate the controllability of different ecological communities and to find the species, that due to the structural characteristics of their interactions are more likely to drive the dynamics of the community.

\section*{Methods \& Results}

Using six paired plant pollinator communities we explored the concepts of control theory. This is the initial data set things will be tested. If more data is considered necessary we'll see that later.

\subsection*{Controllability of ecological communities}

\subsubsection*{Minimum set of species }

Using maximum matching to control all species in the network. We found that depending on the scheme around of the species are needed to have a grasp at the whole community (\autoref{fig:n_species}). However, the relative ranking of networks remains relatively unchanged across schemes. So rather than focusing on the differences across schemes perhaps it would be interesting to see what characteristics make a network to require more or less driver nodes to be completely controled. Alternatively it would be interesting to see if there are systemic differences between different types of networks. An initial step would be to stay with bipartite networks of the mutualistic type (plant/frugivores) or the the consumer-resource type (host/paraiste or predator/prey). Perhaps some model networks of varying parameters?

\begin{figure}
\centering
<<fig = T, echo = F, width = 6, height = 3>>=
n_driver <- read.csv("../data/n_driver_species.dat")

ggplot(n_driver, aes(x = type, y = n_driver/n_species)) +
	geom_violin(colour = "grey") +
	geom_line(aes(colour = as.factor(net),group = as.factor(net))) +
	geom_point(aes(fill = as.factor(net)), shape = 21) +
	xlab("link structure scheme") + ylab("proportion of driver species") + 
	theme_classic() + theme(legend.position = "none", text = element_text(family = "Times"), axis.title.x = element_text(vjust = -0.7), axis.title.y = element_text(vjust = 1.5)) 
@
\caption{\label{fig:n_species} Proportion of species that needs to be controled for all twelve networks under different link assumptions. AB indicates that the links go from plants to pollinators; BA that the links go from pollinator to plants; ``weight'' that the direction of control is chosen by dependency (ties are resolved by giving priority to plants in weight.A and to pollinators in weight.B); z-bi indicates that the links go in both directions}
\end{figure}

\subsubsection*{Profiles of critical and redundant species}

Dividing the nodes and links among critical, ordinary and redundant we can have an idea of ``control profiles'' of the networks.

\subsubsection*{Profiles of internal/external dilation}

\subsection*{Ranking species}

By frequency in control sets

Strongly interacting species (interaction heterogeneity)

\section*{Discussion}

 For instance, restoration projects that aim to drive an invasive species out of the community, to reestablish a particular ecosystem service or in general modify the ecosystem state have had a limited amount of success. We argue that quantifying the relative dynamic importance of species the set of key species is the first step to evaluate current management efforts as well as to design targeted and informed

 Dynamic system approach

\section*{Acknowledgmenets}

Takeuki Uno for the insight provided to find the set of all maximum matching algorithms.

\end{document}

### 2015-12-01 code/03_ntw_maximum_matchings.R

@@ -1,6 +1,6 @@
 # This script calculates all the possible maximum matchings for each of the
 # networks. It is designed to run in the cluster
-setwd("~/github/controlling-pollination-networks/")
+setwd("~/github/driver-species/")
 
 # which network
 i <- as.integer(commandArgs(trailingOnly = TRUE)[1])

### 2015-12-01 code/04_critical_elements.R

@@ -1,6 +1,6 @@
 # This script detects which nodes and which links are critical or redundant for
 # controling the whole network dynamics
-setwd("~/github/controlling-pollination-networks/")
+setwd("~/github/driver-species/")
 
 # which network
 i <- as.integer(commandArgs(trailingOnly = TRUE)[1])

### 2015-12-01 code/06_read_max_match.R

@@ -1,4 +1,4 @@
-setwd("~/github/controlling-pollination-networks/")
+setwd("~/github/driver-species/")
 library(magrittr)
 
 i <- as.integer(commandArgs(trailingOnly = T)[1])

### 2015-12-01 code/07_max-match_vs_redundancy.Rmd

@@
 library(ggplot2)
-library(ggtern)
 
@@
 ```{r}
-dplyr::full_join(node_mm, node_re) %>%
-	dplyr::filter(!is.na(freq)) %>%
+ranked_mm <- dplyr::full_join(node_mm, node_re) %>%
+	dplyr::filter(!is.na(freq),
+								type == "weight") %>%
 	dplyr::group_by(net, type, keep) %>%
-	dplyr::mutate(r = rank(freq, ties.method = "first"),
-								f_f = freq/max(freq)) %>%
+	dplyr::mutate(r = rank(freq, ties.method = "min"),
+								f_f = freq/max(freq))
 
-	ggplot() +
+	ggplot(ranked_mm) +
 	geom_point(aes(x = r, y = f_f, fill = robustness), shape = 21) +
@@
 ```
+
+## Role of invasive species
+
+```{r}
+	library(scales)
+inv <- dplyr::data_frame(net = unique(node_redundancy$net) %>% as.character(),
+												 inv = grepl("2", net) | grepl("4", net)) %>% 
+	dplyr::mutate(site = rep(c("BAT", "FRA", "MED", "FAR", "MIQ", "SEL"), each =2),
+								invader = rep(c("car", "op", "car", "op"),  c(2, 2, 4, 4)))
+
+invasive_sp <- data.frame(node = c("p_4", "p_25"), invs.species = TRUE)
+
+ranked_with_inv <- 
+	ranked_mm %>% filter(keep == "A") %>% full_join(invasive_sp) %>% full_join(inv)
+
+pdf("./presentation_figures/bp_prop_mm.pdf", width = 8, height = 5.5)
+ggplot(ranked_with_inv,aes(y = f_f, x = site, fill = inv)) +
+	geom_boxplot(size = 1) +
+	theme_minimal() + 
+	theme(legend.position = "none",
+				axis.title = element_blank(), 
+				axis.text = element_text(size = 16)) +
+	scale_x_discrete(labels= c("site 1", "site 2", "site 3", "site 4", "site 5", "site 6")) +
+	scale_y_continuous(labels = percent) +
+	scale_fill_manual(values = c("#a6cee3", "#fb9a99"))
+dev.off()
+
+pdf("./presentation_figures/bp_prop_mm_inv.pdf", width = 8, height = 5.5)
+ggplot(ranked_with_inv %>% filter(inv == T),aes(y = f_f, x = site, fill = inv)) +
+	geom_boxplot(size = 1) +
+	theme_minimal() + 
+	theme(legend.position = "none",
+				axis.title = element_blank(), 
+				axis.text = element_text(size = 16)) +
+	scale_x_discrete(labels= c("site 1", "site 2", "site 3", "site 4", "site 5", "site 6")) +
+	scale_y_continuous(labels = percent) +
+	scale_fill_manual(values = c("#fb9a99", "white"))
+dev.off()
+
+mm_prop_invasive <- ranked_with_inv %>% filter(invs.species)
+
+pdf("./presentation_figures/bp_prop_mm_inv_species.pdf", width = 8, height = 5.5)
+ggplot(ranked_with_inv %>% filter(inv == T),aes(y = f_f, x = site, fill = inv)) +
+	geom_boxplot(size = 1) +
+	geom_point(data = mm_prop_invasive, aes(x = site, y = f_f), shape = 21, size = 4, fill = "#e41a1c") + 
+	theme_minimal() + 
+	theme(legend.position = "none",
+				axis.title = element_blank(), 
+				axis.text = element_text(size = 16)) +
+	scale_x_discrete(labels= c("site 1", "site 2", "site 3", "site 4", "site 5", "site 6")) +
+	scale_y_continuous(labels = percent) +
+	scale_fill_manual(values = c("#fb9a99", "white"))
+dev.off()
+
+neigh <- plyr::ldply(net, function(x){
+	plyr::ddply(invasive_sp, "node", function(y){
+		node <- which(V(x)$name == y$node)
+		if (length(node) == 0){
+			return(NULL)
+		} else {
+			data.frame(neighbors = neighbors(x, node)$name)
+		}
+	})
+}) %>%
+	dplyr::select(-node) %>%
+	dplyr::rename_("net" = ".id", 
+								 "node" = "neighbors") %>%
+	dplyr::mutate(neigh = T)
+
+neigh <- ranked_with_inv %>% filter(inv == T) %>% left_join(neigh) %>% filter(neigh)
+
+pdf("./presentation_figures/bp_prop_mm_inv_species_poster.pdf", width = 14.5, height = 5.5)
+ggplot(ranked_with_inv %>% filter(inv == T),aes(y = f_f, x = site, fill = inv)) +
+	geom_boxplot(size = 1, fill = "white") +
+	geom_point(data = mm_prop_invasive, aes(x = site, y = f_f), shape = 22, size = 8, fill = "#e41a1c", alpha = 0.75) + 
+	# geom_jitter(data = neigh, aes(x = site, y = f_f), shape = 21, size =3,  fill = "#377eb8", position = position_jitter(width = 0.25, height = 0)) + 
+		ylab("species relevance\nfor management\n") +
+	theme_minimal() + 
+	theme(legend.position = "none",
+				axis.title.x = element_blank(), 
+				axis.text = element_text(size = 44),
+				axis.title.y = element_text(size = 44)) +
+	scale_x_discrete(labels= c("site 1", "site 2", "site 3", "site 4", "site 5", "site 6")) +
+	scale_y_continuous(labels = percent) +
+	scale_fill_manual(values = c("#fb9a99", "white"))
+dev.off()
+```

### 2015-12-01 code/08_invaded_vs_non-invaded.Rmd

@@
 library(ggplot2)
-library(ggtern)
+library(igraph)
 
@@
 ```{r}
+library(scales)
+
+pdf("./presentation_figures/bp_n_drivers.pdf", width = 8, height = 5.5)
 space %>%
+	dplyr::filter(type == "weight.A") %>%
 	ggplot() +
-	geom_boxplot(aes(y = prop_driver, x = type, fill = inv))
+	geom_boxplot(aes(y = prop_driver, x = inv, fill = inv), size = 1, width = 1) +
+	theme_minimal() + 
+	theme(legend.position = "none",
+				axis.title = element_blank(), 
+				axis.text = element_text(size = 16)) +
+	scale_x_discrete(labels= c("uninvaded", "invaded")) +
+	scale_y_continuous(labels = percent) +
+	scale_fill_manual(values = c("#377eb8", "#e41a1c"))
+dev.off()
+
+pdf("./presentation_figures/bp_n_drivers_poster.pdf", width = 14.5, height = 5.5)
+space %>%
+	dplyr::filter(type == "weight.A") %>%
+	ggplot() +
+	geom_boxplot(aes(y = prop_driver, x = inv, fill = inv), size = 1, width = 1, alpha = 0.75) +
+	ylab("prop. management \ntarget species\n ") +
+	theme_minimal() + 
+	theme(legend.position = "none",
+				axis.title.x = element_blank(), 
+				axis.text = element_text(size = 44),
+				axis.title.y = element_text(size = 44)) +
+	scale_x_discrete(labels= c("uninvaded", "invaded")) +
+	scale_y_continuous(labels = percent) +
+	scale_fill_manual(values = c("#377eb8", "#e41a1c"))
+dev.off()
 

### 2015-12-01 paper/manuscript.tex
updated redundancy script

@@
-\documentclass{article}
+\input{preamble} % See preamble.tex to edit the overall layout
 
+\usepackage{Sweave}
 \begin{document}
+\input{figures/fig--concordance}
+\setkeys{Gin}{width=1\textwidth}
 
-\section{Acknowledgmenets}
+% title
+\input{title_authors}
+\maketitle
+
+\begin{abstract}
+\noindent Si sabemos que el disfrute exige lentitud, y que---mas en general---la felicidad se asocia con el ir despacio, por que corremos tanto?
+El arte de comer estriba en saborear cada bocado sin pensar en el siguiente, sin apresurar el siguiente.
+El arte de leer, en demorarse en cada palabra como si el sentido del escrito entero estuviera contenido en ella.
+El arte de amar, en vivir cada momento de la relacion con la persona amada como si fuese el destino de toda la historia del mundo, desde la aparicion del primer organismo unicelular hasta hoy.
+Y asi podemos generalizar a las demas actividades, creo, hasta obtener un arte de vivir.
+Para mi se resume en la palabra ahi.
+--- Jorge Riechmann
+\end{abstract}
+
+\keywords{Control theory}
+
+% line numbers
+\linenumbers
+\setlength\linenumbersep{15pt}
+\renewcommand\linenumberfont{\normalfont\footnotesize\sffamily\color{gray}}
+
+\onehalfspacing
+
+% Main Text
+\section*{Introduction}
+
+Ecological communities are formed by the interconnection of several species.
+Therefore, changes in the abundances of one species can potentially alter the abundances of the species they interact with.
+For instance, in a classic example of ecosystem cascades, a reduction on the abundance of sea otters, an important predator or sea urchins, can drive a dramatic reduction on kelp abundances because the sea urchins that consume kelp are released from predation.
+It has been long established that some species, like the sea otter, have a disproportionate large effect in their environment relative to their abundance.
+
+In several ecosystems the relative importance of species have been identified based on empirical observations of long term dynamics.
+However, in less studied, highly diverse, or where the "keystone" role is shared by several species, it can be challenging to determine which is the set of species that influence the most the ecosystem dynamics.
+Alternative approaches that recognize a continuum of importance and that are less dependent on empirical observations have also been developed.
+Some of them are based on metrics that evaluate their position in the food web or on mass balance models of functional groups.
+Nevertheless, these approaches are conceptually limited to throphic interactions and in general ignore the structural mechanisms that allow or prevent the spread of perturbations in the ecosystem.
+
+From a systems perspective, perturbations like over-exploitation, eutrophication or global warming are equivalent to management actions like culling, no-take areas or captive rearing in the sense that they have the potential to modify the abundances of one or several species in the ecosystem.
+Therefore identifying these key species is crucial not only to predict how these perturbations will spread trough the community but also to guide effective conservation efforts.
+
+Recent work on the control of complex systems suggest that in principle it is possible to alter any ecological community's composition, by modifying the abundances of just some key species.
+Here, we apply these theories to estimate the controllability of different ecological communities and to find the species, that due to the structural characteristics of their interactions are more likely to drive the dynamics of the community.
+
+\section*{Methods \& Results}
+
+Using six paired plant pollinator communities we explored the concepts of control theory. This is the initial data set things will be tested. If more data is considered necessary we'll see that later.
+
+\subsection*{Controllability of ecological communities}
+
+\subsubsection*{Minimum set of species }
+
+Using maximum matching to control all species in the network.
+We found that depending on the scheme around of the species are needed to have a grasp at the whole community (\autoref{fig:n_species}).
+However, the relative ranking of networks remains relatively unchanged across schemes.
+So rather than focusing on the differences across schemes perhaps it would be interesting to see what characteristics make a network to require more or less driver nodes to be completely controled.
+Alternatively it would be interesting to see if there are systemic differences between different types of networks.
+An initial step would be to stay with bipartite networks of the mutualistic type (plant/frugivores) or the the consumer-resource type (host/paraiste or predator/prey).
+Perhaps some model networks of varying parameters?
+
+\begin{figure}
+\centering
+\includegraphics{figures/fig--002}
+\caption{\label{fig:n_species} Proportion of species that needs to be controled for all twelve networks under different link assumptions.
+AB indicates that the links go from plants to pollinators; BA that the links go from pollinator to plants; ``weight'' that the direction of control is chosen by dependency (ties are resolved by giving priority to plants in weight.A and to pollinators in weight.B); z-bi indicates that the links go in both directions}
+\end{figure}
+
+\subsubsection*{Profiles of critical and redundant species}
+
+Dividing the nodes and links among critical, ordinary and redundant we can have an idea of ``control profiles'' of the networks.
+
+\subsubsection*{Profiles of internal/external dilation}
+
+\subsection*{Ranking species}
+
+By frequency in control sets
+
+Strongly interacting species (interaction heterogeneity)
+
+\section*{Discussion}
+
+ For instance, restoration projects that aim to drive an invasive species out of the community, to reestablish a particular ecosystem service or in general modify the ecosystem state have had a limited amount of success.
+We argue that quantifying the relative dynamic importance of species the set of key species is the first step to evaluate current management efforts as well as to design targeted and informed
+
+ Dynamic system approach
+
+\section*{Acknowledgmenets}
 

### 2015-12-01 paper/manuscript.Rnw
akwnoledgements
minor details

@@
 
-Takeuki Uno for the insight provided to find the set of all maximum matching algorithms.
+The authors thank Takeuki Uno for the insight provided to find the set of all maximum matching algorithms.
+EFC acknowledges the support from the University of Canterbury Doctoral Scholarship, the UC Meadow Mushroooms Postgraduate Scholarship, a travel grant from the European Space Agency and a Rutherford Discovery Fellowship (to DBS).
+DBS ackloledges the support of a Rutherford Discovery Scholarship, administered by the Royal Society of New Zealand.
 

### 2015-12-01 paper/manuscript.Rnw
second graph initial commit

--- 2015-12-01 paper/manuscript.Rnw
@@
 
+<<>>=
+folder <- "../data/redundancy/node/"
+node_redundancy <- list.files(folder, full.names = TRUE) %>%
+    plyr::ldply(function(x, name){
+        y <- read.csv(x) 
+        info <- basename(x) %>% 
+            stringr::str_sub(end = -5) %>% 
+            stringr::str_split("_") %>% 
+            unlist()
+        y %>%
+            dplyr::mutate(net = info[[1]],
+                                        type = info[2],
+                                        keep = info[3])
+    })
+
+g
+@
+
 \subsubsection*{Profiles of internal/external dilation}

### 2015-12-03 paper/manuscript.Rnw
redundancy analysis

--- 2015-12-01 paper/manuscript.Rnw
@@
 library(magrittr)
+
+my_theme <- theme_classic() + theme(legend.position = "none", text = element_text(family = "Times"), axis.title.x = element_text(vjust = -0.7), axis.title.y = element_text(vjust = 1.5)) 
 @
@@
 	xlab("link structure scheme") + ylab("proportion of driver species") +
-	theme_classic() + theme(legend.position = "none", text = element_text(family = "Times"), axis.title.x = element_text(vjust = -0.7), axis.title.y = element_text(vjust = 1.5)) 
+	my_theme
 @
-\caption{\label{fig:n_species} Proportion of species that needs to be controled for all twelve networks under different link assumptions.
+\caption{
+\label{fig:n_species} 
+Proportion of species that needs to be controled for all twelve networks under different link assumptions.
 AB indicates that the links go from plants to pollinators; BA that the links go from pollinator to plants; ``weight'' that the direction of control is chosen by dependency (ties are resolved by giving priority to plants in weight.A and to pollinators in weight.B); z-bi indicates that the links go in both directions}
 \end{figure}
+
+There is no significant difference between the number of species needed to control the system in an invaded and an uninvaded ecosystem.
 
@@
 Dividing the nodes and links among critical, ordinary and redundant we can have an idea of ``control profiles'' of the networks.
+Both species and interactions can be classified as redundant, ordinary and critical depending on the number of species that need to be controled to gain full control over the network once the species has been removed (\autoref{fig:s_crit_prop} and \ref{fig:i_crit_prop}).
+
+\begin{figure}[tp]
+\centering
+<<fig = T, echo = F, width = 6, height = 2.5>>=
+folder <- "../data/redundancy/node/"
+node_redundancy <- list.files(folder, full.names = TRUE) %>%
+    plyr::ldply(function(x, name){
+        y <- read.csv(x) 
+        info <- basename(x) %>% 
+            stringr::str_sub(end = -5) %>% 
+            stringr::str_split("_") %>% 
+            unlist()
+        y %>%
+            dplyr::mutate(net = info[[1]],
+                                        type = info[2],
+                                        keep = info[3])
+    })
+
+nr_sum <- node_redundancy %>%
+	dplyr::mutate(type = interaction(type, keep)) %>%
+	dplyr::group_by(net, type, robustness) %>%
+	dplyr::summarise(freq = n()) %>%
+	dplyr::group_by(net, type) %>%
+	dplyr::mutate(n_species = sum (freq)) %>%
+	dplyr::group_by() %>%
+	dplyr::mutate(prop = freq / n_species, 
+								type = as.character(type), 
+								robustness = as.character(robustness))
+
+ggplot(nr_sum) +
+	geom_boxplot(aes(x = type, y = prop, fill = robustness)) +
+	geom_vline(xintercept = seq(1.5, 5.5), linetype = 2) +
+	xlab("link structure scheme") +
+	ylab("species proportion") +
+	my_theme + theme(legend.position = "right")
+@
+\caption{\label{fig:s_crit_prop} Proportion of species that are ordinary (when removed the number of species needed to control the network doesn't change), redundant (when removed less species are needed) and critical (when removed the number of species needed to control the network increasses).
+Schemes same as in \autoref{fig:n_species}}
+\end{figure}
+
+\begin{figure}[tp]
+\centering
+<<fig = T, echo = F, width = 6, height = 2.5>>=
+folder <- "../data/redundancy/edge/"
+link_redundancy <- list.files(folder, full.names = TRUE) %>%
+    plyr::ldply(function(x, name){
+        y <- read.csv(x) 
+        info <- basename(x) %>% 
+            stringr::str_sub(end = -5) %>% 
+            stringr::str_split("_") %>% 
+            unlist()
+        y %>%
+            dplyr::mutate(net = info[[1]],
+                                        type = info[2],
+                                        keep = info[3])
+    })
+
+lr_sum <- link_redundancy %>%
+	dplyr::mutate(type = interaction(type, keep)) %>%
+	dplyr::group_by(net, type, robustness) %>%
+	dplyr::summarise(freq = n()) %>%
+	dplyr::group_by(net, type) %>%
+	dplyr::mutate(n_species = sum (freq)) %>%
+	dplyr::group_by() %>%
+	dplyr::mutate(prop = freq / n_species, 
+								type = as.character(type), 
+								robustness = as.character(robustness))
+
+ggplot(lr_sum) +
+	geom_boxplot(aes(x = type, y = prop, fill = robustness)) +
+	geom_vline(xintercept = seq(1.5, 5.5), linetype = 2) +
+	xlab("link structure scheme") +
+	ylab("interactions proportion") +
+	my_theme + theme(legend.position = "right")
+@
+\caption{\label{fig:i_crit_prop} Proportion of interactions that are ordinary (when removed the number of species needed to control is reduced), redundant (when removed the number of species needed to control doesn't change) and critical (when removed the number of species needed to control the network increasses).
+Schemes same as in \autoref{fig:n_species}}
+\end{figure}
+
+On the species redundancy profile (\autoref{fig:s_crit_prop}), the profiles are also highly dependent on the chosen directionality scheme.
+For instance, in the case in which species have links in both directions there are not ordinary species and the number of critical species is relatively high, this is not surprising because under this scheme, there is a much smaller set of species that needs to be controled and therefore removing one of these can increase the minimum set of species needed to control the network.
+
+However, there appears to be a relatively small variability between networks analysed using this approach.
+Again, as in the previous section, I think there is little that can be understood by using just this data-set.
+Again I think it would be most interesting to see if there are systemic differences between different types of networks where a larger variation in the profiles is expected.
+
+On the interaction redundancy profile (\autoref{fig:i_crit_prop}) things seem a bit more interesting because the variation across networks and across link directionality schemes is pretty small.
+For instance for the bidirectional scheme, although the total number of links is doubled, the relative proportion of links that are critical and redundant is mantained.
 
@@
 
+\citet{Ruths2014} proposed another clever way to characterise the control profile of a network by charactering the number of nodes that need to be controled among the ``mechanism'' that originates it.
+
+\begin{figure}
+\centering
+<<fig = T, echo = F, width = 6, height = 3>>=
+library(ggtern)
+dilation <- read.csv(file = "../data/dilation_profiles.dat")
+
+ggplot(dilation, aes(x = eta_s, z = eta_e, y = eta_i)) +
+	geom_point(aes(fill = type.keep), shape = 21, size = 5, alpha = 0.7) +
+	coord_tern() + theme_classic() + theme(text =  element_text(family = "Times"))
+
+detach("package:ggtern", unload = TRUE)
+@
+\caption{\label{fig:dilation} Control profiles of pollination networks.
+Control nodes are split among nodes that need to be controled because they are a source node, some that are control nodes because they respond to internal dilations (cycles) and some that are control nodes because they repsond to external dilations (sink nodes not matched)}
+\end{figure}
+
 \subsection*{Ranking species}
 
-By frequency in control sets
+\subsubsection*{By frequency in control sets}
 
-Strongly interacting species (interaction heterogeneity)
+\subsubsection*{By redundancy}
+
+\subsubsection*{Strongly interacting species (interaction heterogeneity)}
 
@@
 
+The authors thank Dr.
 Takeuki Uno for the insight provided to find the set of all maximum matching algorithms.
+EFC acknowledges the support from the University of Canterbury Doctoral Scholarship, the University of Canterbury Meadow Mushroooms Postgraduate Scholarship, a travel grant from the European Space Agency and a Rutherford Discovery Fellowship (to DBS).
+DBS ackloledges the support of a Rutherford Discovery Scholarship, administered by the Royal Society of New Zealand.
 
+\bibliography{references}
 \end{document}

### 2015-12-03 code/09_dilation profiles.Rmd
dilation profiles

--- 2015-10-20 code/08_invaded_vs_non-invaded.Rmd
@@
 ---
-title: "Invaded vs non invaded"
+title: "Dilation profile"
 author: "Fernando Cagua"
-date: "5 October 2015"
+date: "3 December 2015"
 output: html_document
@@
 opts_knit$set (root.dir=normalizePath('../'))
-opts_chunk$set (fig.path = "./figures/08/")
-opts_chunk$set (cache.path = "./cache/08/")
+opts_chunk$set (fig.path = "./figures/09/")
+opts_chunk$set (cache.path = "./cache/09/")
 opts_chunk$set (fig.width = 11, 
@@
 
-With the redundancy. What are the differences between the invaded and the non-invaded sites?
-
-Base data frame
-
-```{r}
-node_redundancy <- read.csv(file = "./data/node_redundancy.dat")
-
-inv <- dplyr::data_frame(net_name = unique(node_redundancy$net) %>% as.character(),
-												 inv = grepl("2", net_name) | grepl("4", net_name)) %>% 
-	dplyr::mutate(site = rep(c("BAT", "FRA", "MED", "FAR", "MIQ", "SEL"), each =2),
-								invader = rep(c("car", "op", "car", "op"),  c(2, 2, 4, 4)))
-```
+Calculate the number of control
 
@@
     dplyr::mutate(n_driver = driver_nodes,
-                                type = interaction(type, keep))
+                                type.keep = interaction(type, keep))
 
@@
 
-Let's see if there is a difference in the proportion of needed species by invasion type
+Get number of source nodes
 
 ```{r}
-space %<>%
-	dplyr::mutate(prop_driver = n_driver/n_species) %>%
-	dplyr::inner_join(inv)
+dilation <- 1:nrow(space) %>%
+	plyr::ldply(function(i){
+		p <- space[i,]
+		n <- net[[p$net]] %>%
+			keep_largest_component() %>%
+			bipartite_digraph(type = p$type, keep = p$keep)
+		igraph::E(n)$weight <- 1
+		out_degree <- igraph::degree(n, mode = "out")
+		in_degree <- igraph::degree(n, mode = "in")
+		n_sources <- sum(out_degree > 0 & in_degree == 0)
+		n_sinks <- sum(out_degree == 0 & in_degree > 0)
+		n_ext_dil <- max(0,n_sinks - n_sources)
+		data.frame(type = p$type, net = p$net, keep = p$keep, 
+							 n_sources = n_sources, n_sinks = n_sinks, 
+							 n_ext_dil = n_ext_dil)
+	})
+
+dilation <- inner_join(space, dilation) %>%
+	dplyr::mutate(eta_s = n_sources / n_driver, 
+								eta_e = n_ext_dil / n_driver, 
+								eta_i = 1 - eta_s - eta_e)
 ```
 
+Let's have a look
+
 ```{r}
-space %>%
-	ggplot() +
-	geom_boxplot(aes(y = prop_driver, x = type, fill = inv))
+library(ggtern)
 
-lme4::glmer(cbind(n_driver, n_no_driver) ~ inv + (1|type) , data = space, family = "binomial") %>%
-	summary()
+ggplot(dilation, aes(x = eta_s, z = eta_e, y = eta_i)) +
+	geom_point(aes(fill = type.keep), shape = 21, size = 5, alpha = 0.7) +
+	coord_tern() 
 ```
 
-Let's try again
+Save the data
 
 ```{r}
-s_diff <- space %>% 
-	arrange(inv) %>%
-	group_by(site, type) %>%
-	summarise(dif = diff(qlogis(prop_driver)), 
-						invader = unique(invader))
-
-s_diff %>%
-	ggplot(aes(x = dif)) +
-	geom_density()
-
-lme4::lmer(dif ~ invader + (1|type) , data = s_diff) %>%
-	summary()
+write.csv(dilation, file = "./data/dilation_profiles.dat", row.names = F)
 ```
-
-No.
-No differences on the proportion of driver nodes between invaded and un-invaded systems, though almost...
-The proportion is a bit higher for the invaded system, but we don't have enough replicates to see if it's significant or not.
-
-## Composition differences
-
-Let's look at the number of critical/redundant species
-
-```{r}
-node_redundancy %>%
-	dplyr::mutate(type = paste(type, keep, sep = ".")) %>%
-	dplyr::rename(net_name = net) %>%
-	dplyr::group_by(net_name, type, robustness) %>%
-	dplyr::summarise(n = n()) %>%
-	dplyr::group_by() %>%
-	dplyr::left_join(space)
-
-```

### 2015-12-05 code/08_invaded_vs_non-invaded.Rmd
save info about the networks

@@
 								invader = rep(c("car", "op", "car", "op"),  c(2, 2, 4, 4)))
+
+inv <- plyr::ldply(net, function(x){
+	data.frame(n_pla = sum(igraph::V(x)$type == "pla"),
+						 n_pol = sum(igraph::V(x)$type == "pol"))
+}) %>% dplyr::add_rownames() %>%
+	dplyr::rename(net = rowname, 
+								net_name = .id) %>% dplyr::full_join(inv)
+```
+
+Save ntw metadata
+```{r}
+write.csv(inv, "./data/ntw_info.csv", row.names = F)
 ```

### 2015-12-05 code/11_compare_n-drivers_random.Rmd
analise networks versus randomisations for n control nodes

---
title: "Comparing n_drivers with random networks"
author: "Fernando Cagua"
date: "3 December 2015"
output: html_document
---

```{r, echo = FALSE, message=FALSE, warning=FALSE}
library(dplyr)
library(magrittr)
library(knitr)
library(ggplot2)
library(ggtern)

opts_knit$set (root.dir=normalizePath('../'))
opts_chunk$set (fig.path = "./figures/10/")
opts_chunk$set (cache.path = "./cache/10/")
opts_chunk$set (fig.width = 11, 
                fig.height = 9,
                out.width = "858px")
```

```{r}
# load utility functions
nn <- list.files("./code/functions", full.names = TRUE) %>% lapply(source)
# load netw
net <- list.files("./data/networks/", full.names = TRUE) %>%
	lapply(readRDS)
names(net) <- list.files("./data/networks/", full.names = FALSE) %>%
	stringr::str_split("\\.") %>% lapply(`[`, 1) %>% unlist ()
```

Get number of controls

```{r}
# generate parameter space
space <- expand.grid(type = c("z-bi", "weight", "AB", "BA"), 
                                         net = 1:length(net)) %>%
    dplyr::inner_join(data.frame(type = c("z-bi", "AB", "BA", "weight", "weight"),
                                                             keep = c("all", "A", "B", "A", "B")))

# select the corresponding one for this computation

driver_nodes <- 1:nrow(space) %>%
	plyr::laply(function(i){
		p <- space[i,]
		n <- net[[p$net]] %>%
			keep_largest_component() %>%
			bipartite_digraph(type = p$type, keep = p$keep)
		igraph::E(n)$weight <- 1
		n %>%
			n_unmatched_vertex()
	})

space %<>%
    dplyr::mutate(n_driver = driver_nodes,
                                type.keep = interaction(type, keep))

net_names <- plyr::ldply(net, function(x){
    length(igraph::V(x))
}) %>%
    dplyr::mutate(net = 1:nrow(.)) %>%
    dplyr::rename(n_species = V1,
                                net_name = `.id`)

n_control <- dplyr::inner_join(space, net_names) %>%
    dplyr::mutate(n_no_driver = n_species - n_driver)
```

Generate a random network and calculate the number of no drivers

```{r}
library(foreach)
library(doMC)
registerDoMC(cores = 4)

# generate parameter space
space <- expand.grid(type = c("z-bi", "weight", "AB", "BA"), 
										 net = 1:length(net), 
										 method = c("r0", "c0", "quasiswap")) %>%
	dplyr::inner_join(data.frame(type = c("z-bi", "AB", "BA", "weight", "weight"),
															 keep = c("all", "A", "B", "A", "B")))

# number of desired permutations
nperm <- 999

random_n <- space %>%
	# for each network and randomisation type
	plyr::ddply(c("net", "method"), function(p){
		nn <- net[[p$net[1]]] %>%
			keep_largest_component() %>%
			bipartite_digraph(type = p$type, keep = p$keep)
		igraph::E(nn)$weight <- 1

		# generate a set of random networks
		random_net <- get_random_net(nn, as.character(p$method[1]), nperm)

		# for each of the networks
		plyr::ldply(random_net, function(x){
			1:nrow(p) %>%
				# for each of the directionality schemes
				plyr::ldply(function(i){
					p <- p[i,]
					# calculate number of control nodes
					x %<>% keep_largest_component() %>%
						bipartite_digraph(p$type, p$keep)
					data.frame(type = p$type, keep = p$keep, 
										 n_driver = x %>%
										 	n_unmatched_vertex())
				})
			# make it pararell
		}, .parallel = T)
	}, .progress = "text")

```

let's have a quick view

```{r}
ggplot(random_n) + 
	geom_boxplot(aes(x = as.character(interaction(type, keep)), y = n_driver, fill = method), colour = "grey10") + 
	geom_point(data = n_control, 
						 aes(x = interaction(type, keep), y = n_driver), colour = "red") +
	facet_wrap(~ net, scales = "free") +
	theme_classic()
```

Save the resulys
```{r}
write.csv(random_n, "./data/random_n_driver.csv", row.names = FALSE)
```

Calculate z scores

```{r}
random_n_z <- random_n %>% 
	dplyr::group_by(net, type, keep, method) %>%
	dplyr::summarise(n_driver_u = mean(n_driver, na.rm = T),
									 n_driver_sd = sd(n_driver, na.rm = T)) %>%
	dplyr::full_join(n_control) %>% 
	dplyr::group_by() %>%
	dplyr::mutate(n_driver_z_score = (n_driver - n_driver_u)/n_driver_sd)

random_n_z %>% 
	ggplot(aes(x  = type, y = n_driver_z_score)) +
	geom_hline(yintercept = c(-2, 2), linetype = 2) +
	geom_boxplot(aes(fill = method)) +
	theme_classic()
```

Diversity ratio and z scores

```{r}
net_info <- read.csv("./data/ntw_info.csv")

net_info %<>%
	dplyr::mutate(ratio_pol_pla = n_pol/n_pla)

random_n_z %>%
	dplyr::full_join(net_info) %>%
	dplyr::filter(method == "c0") %>%
	ggplot(aes(x = n_driver_z_score, y = ratio_pol_pla, colour = as.character(interaction(type, keep)))) +
	geom_point() +
	geom_smooth(method = "lm")

```

### 2015-12-05 code/functions/get_random_net.R

@@ -1,0 +1,25 @@
+#' Title
+#'
+#' @param net 
+#' @param method
+#' @param nperm
+#' @param type 
+#' @param keep
+#' 
+#'  Assumes that the network has cateories "pla" and "pol 
+#'
+#' @return
+#' @export
+#'
+#' @examples
+#' 
+# function to obtain the number of control nodes for a particular randomisation scheme
+get_random_net <- function (net, method, nperm) {
+	
+	random_mat <- igraph::as_incidence_matrix(net, types = igraph::V(net)$type == "pla") %>%
+		vegan::nullmodel(method) %>%
+		stats::simulate(nperm)
+	
+	plyr::alply(random_mat, 3, igraph::graph_from_incidence_matrix, weighted = TRUE)
+
+}

### 2015-12-05 paper/manuscript.Rnw
update manuscript and remove tex files

@@
-\input{preamble} % See preamble.tex to edit the overall layout
+\documentclass[a4paper,10pt]{article}
+% abstract + title + authors
+\usepackage{abstract}
+\renewcommand{\abstractnamefont}{\normalfont\bfseries}
+\renewcommand{\abstracttextfont}{\normalfont\small\itshape} 
+\usepackage{titlesec}
+\usepackage{authblk}
+\usepackage{datetime}
+\newdateformat{usvardate}{
+\monthname[\THEMONTH] \ordinal{DAY}, \THEYEAR}
 
+% keywords
+\providecommand{\keywords}[1]{\textbf{\textit{Keywords---}} #1}
+
+% math
+\usepackage{amssymb}
+\usepackage{newtxmath}
+
+% manuscript looking document
+\usepackage{setspace}
+\usepackage{lineno,xcolor}
+\setlength{\parskip}{0.5em}
+
+% comments
+
+% graphics
+\usepackage{graphicx}
+\usepackage{float}
+
+% references & links
+\usepackage[
+backend=biber,
+style= authoryear,
+citestyle = authoryear,
+url=false,
+doi=true,
+isbn=false
+]{biblatex}
+\addbibresource{references.bib}
+
+\usepackage{hyperref}
+\hypersetup{
+    colorlinks=true,
+    citecolor=magenta,
+    linkcolor=magenta
+}
+\usepackage{doi}
 \begin{document}
@@
 % title
-\input{title_authors}
+% Article title
+  \title{\fontsize{16pt}{10pt}\selectfont\textbf{Structural controlability of pollination networks}}
+
+% Authors and Affiliations
+  \author[1]{\large E. Fernando Cagua}
+  \author[1]{\large Daniel B. Stouffer}
+  \affil[1]{\normalsize Center of Integrative Ecology, School of Biological Sciences, University of Canterbury}
+
+ \date{\small\usvardate\today}
+
 \maketitle
@@
 
-There is no significant difference between the number of species needed to control the system in an invaded and an uninvaded ecosystem.
+There was no significant difference between the number of species needed to control the system in an invaded and an uninvaded ecosystem.
+
+When comparing the number of control nodes of the observed networks to their random counterparts an interesting pattern emegerges (\autoref{fig:random_n_species}).
+The number of control nodes is significantly larger than randomisations that mantain the degree distribution of the plants.
+However there is no significant difference when the randomisations mantain the degree of pollinators (or both plants and pollinators).
+This pattern is consistent across all schemes of link directionality.
+This suggest that the patterns of pollinator visitations are the structural characteristic that determines the controlability of the network.
+We probably should analyse other pollination networks to see if this pattern hold.
+We also should think about the implications of this finding.
+
+\begin{figure}
+\centering
+<<fig = T, echo = F, width = 6, height = 3.5>>=
+random_n <- read.csv("../data/random_n_driver.csv")
+n_control <- n_driver %>%
+	dplyr::select(-keep) %>%
+	tidyr::separate(type, c("type", "keep"), "\\.", remove = T)
+
+random_n_z <- random_n %>% 
+	dplyr::group_by(net, type, keep, method) %>%
+	dplyr::summarise(n_driver_u = mean(n_driver, na.rm = T),
+									 n_driver_sd = sd(n_driver, na.rm = T)) %>%
+	dplyr::full_join(n_control) %>% 
+	dplyr::group_by() %>%
+	dplyr::mutate(n_driver_z_score = (n_driver - n_driver_u)/n_driver_sd)
+
+random_n_z %>% 
+	ggplot(aes(x  = as.character(interaction(type, keep)), y = n_driver_z_score)) +
+	geom_rect(ymin = -2, ymax = 2, xmin = -1, xmax = 10, fill = "grey90") +
+	geom_hline(yintercept = 0, size = 0.4) +
+	geom_vline(xintercept = seq(1.5, 5.5), linetype = 2) +
+	geom_boxplot(aes(fill = method)) +
+	scale_fill_discrete(name = "randomisations\nmantain\ndegree of", labels= c("plants", "pollinators", "both")) + 
+	my_theme + 
+	xlab("link structure scheme") +
+	ylab("standard score") +
+	theme(legend.position = "right",
+				axis.line.x = element_blank(), axis.ticks.x = element_blank())
+@
+\caption{
+\label{fig:random_n_species} 
+Difference between the number of control nodes in the analysed networks versus randomisations of the same networks.
+Unshaded areas suggest a significant difference.
+Schemes same as in \autoref{fig:n_species}}
+\end{figure}
+
+It occured to me that it is possible that the patterns (and perhaps others observed like more phylogenetic signal in polinators than in plants) are a consequence of a greater diversity of pollinators in the interaction networks.
+More pollinators relative to plants imply that randomisations that mantain the degree distribution of pollinators are more constrained than those that only mantain the degree distribution of plants.
+It also means that statistical tests on that group have a more observations and therefore rendering significant results for smaller effect sizes.
+I cheked that with the 12 pollination networks of the study and there seems to be some evidence for that (\autoref{fig:zscore_ratio}).
+Perhaps it would be good to check with other networks to see if it holds.
+
+\begin{figure}[h]
+\centering
+<<fig = T, echo = F, width = 6, height = 3.5>>=
+net_info <- read.csv("../data/ntw_info.csv")
+
+net_info %<>%
+	dplyr::mutate(ratio_pol_pla = n_pol/n_pla)
+
+random_n_z %>%
+	dplyr::full_join(net_info) %>%
+	dplyr::mutate(t = as.character(interaction(type, keep))) %>% 
+	dplyr::filter(method == "c0", t != "BA.B") %>%
+	ggplot(aes(x = ratio_pol_pla, y = n_driver_z_score)) +
+	geom_point() +
+	geom_smooth(method = "lm", alpha = 0.1, colour = "grey10") +
+	xlab("ratio of number of pollinators to plants") +
+	ylab("standard score") +
+	my_theme + 
+	facet_wrap(~t, scales = "free") + 
+	theme(strip.background = element_blank())
+@
+\caption{
+\label{fig:zscore_ratio} 
+When considering only randomisations that mantain the degree distribution of plants, there seems to be a possitive relationship between the ratio of pollinators to plants and the Z-score of randomisations.
+The pattern is, however, not significant for the weighted schemes.
+The z-scores are identical for the AB.A and the BA.B schemes.
+Schemes same as in \autoref{fig:n_species}}
+\end{figure}
 
@@
 	ylab("species proportion") +
-	my_theme + theme(legend.position = "right")
+	scale_fill_discrete(name = "nodes") +
+	my_theme + 
+	theme(legend.position = "right", 
+				axis.line.x = element_blank(), 
+				axis.ticks.x = element_blank())
 @
@@
 	geom_vline(xintercept = seq(1.5, 5.5), linetype = 2) +
+	scale_fill_discrete(name = "links") +
 	xlab("link structure scheme") +
@@
 
-\citet{Ruths2014} proposed another clever way to characterise the control profile of a network by charactering the number of nodes that need to be controled among the ``mechanism'' that originates it.
+\textcite{Ruths2014} proposed another clever way to characterise the control profile of a network by charactering the number of nodes that need to be controled among the ``mechanism'' that originates it.
+Similar as the maximum matching algorith, the idea comes from the concept that in the absense of cycles one node can at most control another one.
+Then the origin of control nodes can be splitted between nodes that need to be controled because they are a ``source node'' those that have only out links, control nodes associated to ``external dilations'' and those associated to ``internal dilations''.
+
+It could be interesting to compare different networks using this framework.
+They argue that source dominated networks should be relatively easy to control in a top-down fashion.
+On the other hand internal dilation dominated networks represent the signature of a network that self-regulates and is not meant to be controled in that it's not designed to visit every possible state.
+
+However as we can see here this framework is pretty useless when the direction of control is not perfectly known (as in most real wolrd networks really...).
+For instance when applying it to the data-set (\autoref{fig:dilation}), we see that when the control flows from pollinators to plants (AB.A) the network is source dominated simply because the pollinator diversity is greater than the plant's.
+When we asume that each guild can control each other (z-bi.all) the networks are internal dilation dominated because it's purely composed of cycles.
+However the weighted version might offer a meaningful possibility to develop the analysis.
 
@@
 
-\bibliography{references}
+% \bibliography{references}
+\printbibliography
 \end{document}

### 2015-12-07 code/07_max-match_vs_redundancy.Rmd
update manuscript

@@
 ranked_mm <- dplyr::full_join(node_mm, node_re) %>%
-	dplyr::filter(!is.na(freq),
-								type == "weight") %>%
+	dplyr::filter(!is.na(freq)) %>%
 	dplyr::group_by(net, type, keep) %>%
-	dplyr::mutate(r = rank(freq, ties.method = "min"),
+	dplyr::mutate(r = rank(freq, ties.method = "random"),
 								f_f = freq/max(freq))
 
-	ggplot(ranked_mm) +
-	geom_point(aes(x = r, y = f_f, fill = robustness), shape = 21) +
+ranked_mm %>%
+	dplyr::filter(type == "weight") %>%
+	ggplot() +
+	geom_line(aes(x = r, y = f_f, linetype = keep)) +
+
+	geom_point(aes(x = r, y = f_f, fill = robustness), shape = 21, size = 3.5) +
 	facet_wrap(type ~ net, scales = "free")
+
+ranked_mm %>%
+	dplyr::filter(net == "MED3CA") %>%
+	ggplot(aes(x = r, y = f_f)) +
+	geom_line(aes(group = keep), linetype = 2) +
+	geom_point(aes(fill = robustness), shape = 21, size = 3.5) +
+	facet_wrap(~type)
+
 ```

### 2015-12-07 paper/manuscript.Rnw
update manuscript

@@
 % comments
+\usepackage[draft]{todonotes}
 
@@
 \section*{Introduction}
+
+\todo[inline]{This intro was written when I though that the paper was mainly gonna be about the relative importance of species and how invasives fit there.
+Read with caution as I don't think that's the case anymore}
 
@@
 
-detach("package:ggtern", unload = TRUE)
+detach("package:ggtern", unload = TRUE, character.only = TRUE)
+detach("package:ggplot2", unload = TRUE, character.only = TRUE)
+library(ggplot2)
 @
@@
 \subsubsection*{By frequency in control sets}
+
+There are multiple sets of species with which is structurally possible to control network dynamics.
+An initial posibility os to relate the importance of a species for network dynamics to the frequency at which a species is present in the control sets.
+
+Turns out unsurprisingly that the importance of particular species and its distribution over a networks dependends on the scheme chosen for the directionality of the links (\autoref{fig:n_control_dist}).
+When pollinators control plants (AB) no plant must be controled and most pollinators have an importance close to one. 
+On the other hand when plants control pollinators (BA) presumably because the pollinator diversity is larger than the plant diversity, the pattern is less "bimodal" and intermediate levels of importance are allowed.
+
+\begin{figure}
+\centering
+<<echo = F, cache = T>>=
+folder <- "../data/maximum_matchings_summary/" 
+files <- list.files(folder)
+node_mm <- plyr::adply(files, 1, function(x){
+	read.csv(file.path(folder, x)) %>%
+		dplyr::mutate(net = unlist(stringr::str_split(x, "_"))[1],
+									type = unlist(stringr::str_split(x, "_"))[2], 
+									keep = unlist(stringr::str_split(x, "_"))[3],
+									batch = unlist(stringr::str_split(x, "_"))[4])
+}) %>%
+	dplyr::select(-X1) %>%
+	dplyr::group_by(net, type, keep, node) %>%
+	dplyr::summarise(freq = sum(freq))
+@
+
+<<fig = T, echo = F, width = 6, height = 4>>=
+ranked_mm <- node_mm %>%
+	dplyr::filter(!is.na(freq)) %>%
+	dplyr::group_by(net, type, keep) %>%
+	dplyr::mutate(r = rank(freq, ties.method = "random"),
+								f_f = freq/max(freq), 
+								type.keep = as.character(interaction(type, keep)))  %>%
+	dplyr::rename(net_name = net)
+
+invasive_sp <- data.frame(node = c("p_4", "p_25"), invs.species = TRUE)
+
+ranked_with_inv <- 
+	ranked_mm %>% 
+	dplyr::group_by() %>%
+	dplyr::full_join(invasive_sp) %>% 
+	dplyr::full_join(net_info)
+
+ggplot(ranked_with_inv, aes(x = f_f, fill = net_name)) +
+	geom_density(alpha = 0.025, adjust = 1, colour = "grey20") +
+	geom_point(data = ranked_with_inv %>%
+						 	dplyr::filter(invs.species), aes(y = scale(net) + 2),
+						 shape = 21, fill = "grey") +
+	facet_wrap(~type, ncol = 2) +
+	my_theme +	
+	xlab("species frequency in control sets") +
+	theme(strip.background = element_blank(),
+				axis.text.x = element_text(angle = 90))
+@
+\caption{\label{fig:n_control_dist} Distribution of the relative frequency a species is present in the set of control species among the networks.
+The frequency of invasive species in each of the six invaded networks is denoted with a circle.
+Results for the bidirectional liks (z-bi) were obatined only for the nine smallest networks, which included 3 invaded ecosystems}
+\end{figure}
+
+Among the weighted versions there was little difference if dependency ties were resolved for plants of for pollinators (\autoref{fig:n_control_dist_ntw}), again there are more species with intermediate levels of importance.
+Even more spread out are things when we consider bidirectional links.
+I imagine that this pattern is partly because there are many many more ways to control the network in the bidirectional scheme than in the others.
+
+In both AB and BA the relative importance of different species is almost fully constrained by the scheme.
+In the weighted scheme, invasive species are in all cases among the most important ones.
+Interestingly the pattern is opposite for when the direction can go both ways.
+It would be good to see then whether these patterns are a reflection of the fact that invasive species are actually dominant or an artifact arising from the fact that all invasive species are plants and that all networks are dominated by pollinators.
+An initial inspection on the distributrion of plants and pollinators per network for these schemes suggest that that might be the case for the bidirectional scheme but not for the weighted one (\autoref{fig:n_control_dist_guild} and \ref{fig:n_control_dist_per_net}).
+
+\begin{figure}
+\centering
+<<fig = T, echo = F, width = 6, height = 4>>=
+ranked_with_inv %>%
+	tidyr::separate(node, into = c("categ", "number"), sep = "_", remove = F) %>%
+	ggplot(aes(x = f_f)) + 
+	geom_density(aes(fill = categ), 
+							 alpha = 0.5, adjust = 0.5, colour = "grey20") +
+	geom_point(data = ranked_with_inv %>%
+						 	dplyr::filter(invs.species), aes(y = scale(net) + 2), 
+						 shape = 21, fill = "red") +
+	facet_wrap(~type, ncol = 2) +
+	scale_fill_grey(name = "", labels = c("pollinators", "plants")) +
+	my_theme +	
+	xlab("species frequency in control sets") +
+	theme(strip.background = element_blank(),
+				axis.text.x = element_text(angle = 90), legend.position = "right")
+@
+\caption{\label{fig:n_control_dist_guild} Distribution of the relative frequency a species is present in the set of control species by guild.}
+\end{figure}
+
+We explored that option by
+
+<<>>=
+ranked_with_inv  %>%
+	tidyr::separate(node, into = c("categ", "number"), sep = "_", remove = F) %>%
+	dplyr::group_by(net, type.keep, categ) %>%
+	dplyr::summarise(f_f = median(f_f), 
+									 ratio_pol_pla = mean(ratio_pol_pla)) %>%
+	dplyr::group_by(net, type.keep) %>%
+	dplyr::mutate(f_sum = f_f - lead(f_f)) %>%
+	ggplot(aes(x = ratio_pol_pla, y = f_sum)) +
+	geom_point() +
+	geom_smooth(method = "lm")+ 
+	facet_wrap(~type.keep)
+@
 
@@
 \printbibliography
+
+\newpage
+\section*{Supplementary Information}
+\makeatletter 
+\renewcommand{\thefigure}{S\@arabic\c@figure}
+\makeatother
+\setcounter{figure}{0}
+
+\begin{figure}[h!]
+\centering
+<<fig = T, echo = F, width = 6, height = 4>>=
+ggplot(ranked_mm, aes(x = net_name, y = f_f, fill = type.keep)) +
+	geom_boxplot()+
+# 	geom_jitter(shape = 21, 
+# 							position = position_jitter(height = 0), 
+# 							alpha = 0.2, size = 1) +
+	facet_wrap(~type) +
+	my_theme +	
+	theme(strip.background = element_blank(),
+				axis.text.x = element_text(angle = 90))
+@
+\caption{\label{fig:n_control_dist_ntw} Distribution of the relative frequency a species is present in the set of control species among by network}
+\end{figure}
+
+\begin{figure}[h!]
+\centering
+<<fig = T, echo = F, width = 6, height = 9.5>>=
+bb <- ranked_with_inv %>%
+	tidyr::separate(node, into = c("categ", "number"), sep = "_", remove = F) %>%
+	dplyr::filter(type == "weight" | type == "z-bi")
+
+bb %>%
+	ggplot(aes(x = f_f)) + 
+	geom_density(aes(fill = categ), 
+							 alpha = 0.5, adjust = 0.5, colour = "grey20") +
+	geom_point(data = bb %>%
+						 	dplyr::filter(invs.species), aes(y = scale(net) + 2), 
+						 shape = 21, fill = "red") +
+	facet_grid(net_name ~ type.keep, scales = "free_y") +
+	scale_fill_grey(name = "", labels = c("pollinators", "plants")) +
+	my_theme +	
+	xlab("species frequency in control sets") +
+	theme(strip.background = element_blank(),
+				axis.text.x = element_text(angle = 90), legend.position = "top")
+@
+\caption{\label{fig:n_control_dist_per_net} Distribution of the relative frequency a species is present in the set of control species among by network partitioned by plant or pollinators.
+Invasive species is depicted with a red dot.}
+\end{figure}
 \end{document}

### 2015-12-08 paper/manuscript.Rnw
update manuscript with redundancy vs frequency

@@
 library(magrittr)
+# load utility functions
+nn <- list.files("../code/functions", full.names = TRUE) %>% lapply(source)
 
@@
 
-We explored that option by
+We explored that option by comparing the relationship between the ratio of pollinator to plant diversity and the difference between mean imporance of pollinators and the mean importance of plants (\autoref{fig:ratio_pla_pol_importance}).
+Although there was a positive relationship it doesn't seem to be significative.
+However when removing one of the uninvaded networks in which plants were in average more important than the pollinators for the bidirectional scheme (MED4CA, \autoref{fig:n_control_dist_per_net}) the relationship between the ratio an the relative importance of pollinators and plants becomes significant in the bidirectional scheme.
 
-<<>>=
+\begin{figure}
+\centering
+<<fig = T, echo = F, width = 6, height = 2>>=
 ranked_with_inv  %>%
@@
 	geom_point() +
-	geom_smooth(method = "lm")+ 
-	facet_wrap(~type.keep)
+	geom_smooth(method = "lm", colour = "grey10")+ 
+	facet_wrap(~type.keep, ncol = 5, scales = "free_y") + 
+	xlab("ratio of number of pollinators to plants") +
+	ylab("difference between mean\nimportance of pollinators\nand plants") +
+	my_theme +
+	theme(strip.background = element_blank())
 @
+\caption{\label{fig:ratio_pla_pol_importance} Distribution of the relative frequency a species is present in the set of control species by guild.}
+\end{figure}
 
@@
 
+To understand what the redundancy characterisation (splitting nodes and links between critical, ordinary and redundant) means an initial step would be to relate it to the importance given by their frequency on the control sets.
+However this comparison can only be done among nodes, not links.
+
+Because I think there is enough indication that the unidirectional schemes are crap, we'll focus on the weighted and the bidirectional schemes.
+There doesn't seem to be a direct relationship between the frequency of a species as a control node and it's characterisation as critical, ordinary or redundant for the weighted scheme (\autoref{fig:redundancy_n_control_weight}).
+However critical species in the bidirectional scheme tend to cluster towards the bottom of the frequency (\autoref{fig:redundancy_n_control_bi}).
+
+Given that as we saw in \autoref{fig:ratio_pla_pol_importance} plants tend to cluster as well in the bottom of the frequency scale, it's conceivable to think that there is a difference between the profiles of plants and polinators.
+We explored that difference (\autoref{fig:redundancy_pol_pla}) and indeed there there are marked differences bewteeen plants an pollinators.
+
+In the bidirectional scheme, most polinators are redundant, which means that removing that species from the system reduces the number of control nodes.
+Which could be explained if we take into account that there are more pollinators than plants.
+In the weighted scheme things are a bit more interesting, most plants are ordinary in the sense that removing them doesn't change the number of nodes that has to be controled.
+Wile some are critical in the sense that removing them means that one needs one more node to control the network.
+All invasive species were categorised as ordinary.
+
+\begin{figure}
+\centering
+<<echo = F>>=
+net <- list.files("../data/networks/", full.names = TRUE) %>%
+    lapply(readRDS)
+names(net) <- list.files("../data/networks/", full.names = FALSE) %>%
+    stringr::str_split("\\.") %>% lapply(`[`, 1) %>% unlist ()
+
+node_redundancy %<>% 
+	plyr::ddply("net", function(x){
+		this_net <- net[[dplyr::first(x$net)]] %>%
+	# select only the largest connected component of the network
+			keep_largest_component()
+		nodes <- igraph::V(this_net)[x$n]$name
+		x %>%
+			dplyr::mutate(node = nodes)
+	}) %>% dplyr::tbl_df()
+@
+
+<<fig = T, echo = F, width = 6, height = 2.5>>=
+node_redundancy %>%
+	tidyr::separate(node, c("categ", "number")) %>%
+	dplyr::rename(net_name = net) %>%
+	dplyr::mutate(type.keep = as.character(interaction(type, keep))) %>%
+	dplyr::group_by(type.keep, robustness, categ) %>%
+	dplyr::summarise(n_sp = n()) %>%
+	ggplot() +
+	geom_bar(aes(x = categ, y = n_sp, fill = robustness), 
+					 stat = "identity", 
+					 position = "fill",
+					 colour = "grey10") +
+	facet_grid(~type.keep) +
+	scale_fill_discrete(name = "species") + 
+	scale_x_discrete(labels = c("pollinators", "plants")) +
+	xlab("") +
+	ylab("proportion") +
+	my_theme +
+	theme(legend.position = "right", 
+				strip.background = element_blank(), 
+				axis.text.x = element_text(angle = 45))
+@
+\caption{\label{fig:redundancy_pol_pla} Proportion of pollinators and plants that are ordinary, redundant or critical among different schemes.
+See \autoref{fig:s_crit_prop} for details about this characterisation.}
+\end{figure}
 \subsubsection*{Strongly interacting species (interaction heterogeneity)}
@@
 \end{figure}
+
+\begin{figure}[h!]
+\centering
+<<fig = T, echo = F, width = 6, height = 9.5>>=
+node_redundancy %>%
+	dplyr::rename(net_name = net) %>%
+	dplyr::full_join(ranked_with_inv) %>%
+	dplyr::filter(type == "weight", !is.na(f_f)) %>%
+	dplyr::mutate(net_name = as.character(net_name)) %>%
+	ggplot() +
+	geom_line(aes(x = r, y = f_f, linetype = keep)) +
+	geom_point(aes(x = r, y = f_f, fill = robustness), shape = 21, size = 2) +
+	facet_wrap( ~ net_name, scales = "free", ncol = 3) +
+	ylab("species frequency in control sets") +
+	xlab("rank") +
+	my_theme +
+	theme(legend.position = "top", strip.background = element_blank())
+@
+\caption{\label{fig:redundancy_n_control_weight} Relationship between species' frequency in the control sets and the redundancy categories for the weighted scheme.}
+\end{figure}
+
+\begin{figure}[h!]
+\centering
+<<fig = T, echo = F, width = 6, height = 7>>=
+node_redundancy %>%
+	dplyr::rename(net_name = net) %>%
+	dplyr::full_join(ranked_with_inv) %>%
+	dplyr::filter(type == "z-bi", !is.na(f_f)) %>%
+	dplyr::mutate(net_name = as.character(net_name)) %>%
+	ggplot() +
+	geom_line(aes(x = r, y = f_f, linetype = keep)) +
+	geom_point(aes(x = r, y = f_f, fill = robustness), shape = 21, size = 2) +
+	facet_wrap( ~ net_name, scales = "free") +
+	ylab("species frequency in control sets") + 
+	xlab("rank") +
+	my_theme +
+	theme(legend.position = "top", strip.background = element_blank())
+@
+\caption{\label{fig:redundancy_n_control_bi} Relationship between species' frequency in the control sets and the redundancy categories for the bidirectional scheme.}
+\end{figure}
+
 \end{document}

### 2015-12-10 paper/manuscript.Rnw
draft results manuscript almost done

@@
 Schemes same as in \autoref{fig:n_species}}
+\end{figure}
+
+To understand the effects of the directionality imposed by the dependencies (only for the weighted method), I randomised the direction of the links.
+I compared the number on control species in the weighted scheme with a randomisation that mantain the interacting species but randomise the direction of dependency (\autoref{fig:zscore_dir_ratio}).
+In pretty much all cases, the number of control nodes is significantly larger in the observed networks.
+
+\begin{figure}[h]
+\centering
+<<fig = T, echo = F, width = 6, height = 2.5>>=
+random_dir_n <- read.csv("../data/random_dir_n_driver.csv")
+
+random_dir_n %>% 
+	dplyr::mutate(type = "weight") %>%
+	dplyr::group_by(net, type, keep) %>%
+	dplyr::summarise(n_driver_u = mean(n_driver, na.rm = T),
+									 n_driver_sd = sd(n_driver, na.rm = T)) %>%
+	dplyr::inner_join(n_control) %>% 
+	dplyr::group_by() %>%
+	dplyr::mutate(n_driver_z_score = (n_driver - n_driver_u)/n_driver_sd) %>% 
+	ggplot(aes(x  = as.character(interaction(type, keep)), y = n_driver_z_score)) +
+	geom_rect(ymin = -2, ymax = 2, xmin = -1, xmax = 10, fill = "grey90") +
+	geom_hline(yintercept = 0, size = 0.4) +
+	geom_vline(xintercept = seq(1.5, 2.5), linetype = 2) +
+	geom_jitter(position = position_jitter(height = 0), shape = 21) +
+	geom_boxplot(fill = "white", alpha = 0.5) +
+	scale_fill_discrete(name = "randomisations\nmantain\ndegree of", labels= c("plants", "pollinators", "both")) + 
+	my_theme + 
+	xlab("link structure scheme") +
+	ylab("standard score") +
+	theme(legend.position = "right",
+				axis.line.x = element_blank(), axis.ticks.x = element_blank())
+
+@
+\caption{
+\label{fig:zscore_dir_ratio} 
+In the weighted case, we compared randomisations that maintain the network structure but shuffle the directionality of the dependency.
+Observed networks need a significanly larger number of control nodes than randomisations.
+The difference is more marked when there is a preference to assign dependency from plants to pollinators when dependency is equal in both directions.
+Z scores are based on 999 network randomisations.}
 \end{figure}
@@
 
-In the bidirectional scheme, most polinators are redundant, which means that removing that species from the system reduces the number of control nodes.
-Which could be explained if we take into account that there are more pollinators than plants.
-In the weighted scheme things are a bit more interesting, most plants are ordinary in the sense that removing them doesn't change the number of nodes that has to be controled.
-Wile some are critical in the sense that removing them means that one needs one more node to control the network.
-All invasive species were categorised as ordinary.
-
 \begin{figure}
@@
 \end{figure}
-\subsubsection*{Strongly interacting species (interaction heterogeneity)}
+
+In the bidirectional scheme, most polinators are redundant, which means that removing that species from the system reduces the number of control nodes.
+Which could be explained if we take into account that there are more pollinators than plants.
+In the weighted scheme things are a bit more interesting, most plants are ordinary in the sense that removing them doesn't change the number of nodes that has to be controled.
+Wile some are critical in the sense that removing them means that one needs one more node to control the network.
+All invasive species were categorised as ordinary.
+
+The redundancy is capturing different variability than the frequency in the control sets. However they also show a clear distiction between the role of plants and pollinators.
+
+\subsubsection*{Interaction heterogeneity}
+
+\textcite{Liu2011} suggest that the controlability of a network and specifically the number of control nodes is strongly correlated to the degree distribution of the network, it is not unreasonable to think then that species with a high degree would play a special role.
+More recently \textcite{Gibson} showed that what really matters is the interaction strength of the species and that strongly interacting species (those that influence other the most), and not necessarely the most abbundant, are the ones that can drive the community from one state into another.
+Here we explore the relationship betweeen the two metrics of species controlability, the degree and the mean interaction strength of species.
+
+First we start by recognising that mean interaction strength is correlated with the degree of a species in a network (\autoref{fig:degree_strength}).
+The effect is not terribly strong, particularly for pollinators, but suggest that species that interact with lots of species also tend to visit them a lot.
+Sadly there is no data on relative abbundances to investigate if both degree but particularly interaction strength (as infered from visitation frequency) is a consequence of mass action.
+
+\begin{figure}
+\centering
+<<fig = T, echo = F, width = 6, height = 2.5, cache = TRUE>>=
+
+deg_strength <- plyr::ldply(net,function(x){
+	degree <- igraph::degree(x)
+	m <- igraph::as_adjacency_matrix(x, attr = "weight", sparse = F)
+	m[m == 0] <- NA 
+	m_int_strength <- apply(m, 1, mean, na.rm = T)
+	s_int_strength <- apply(m, 1, sum, na.rm = T)
+	ncont <- igraph::as_incidence_matrix(x, 
+														types = igraph::V(x)$type == "pla") %>%
+		nestedcontribution() %>% dplyr::add_rownames("node")
+	data.frame(node = names(degree), 
+						 degree = degree, 
+						 m_int_strength = m_int_strength,
+						 s_int_strength = s_int_strength) %>%
+		dplyr::full_join(ncont)
+}) %>% dplyr::rename_("net_name" = ".id")
+
+imp <- ranked_with_inv %>%
+	dplyr::full_join(deg_strength) %>%
+	dplyr::filter(!is.na(type.keep), 
+								type == "weight",
+								keep == "A" | keep == "all") %>%
+	tidyr::separate(node, into = c("categ", "number"), sep = "_", remove = F)
+
+inv <- imp %>% dplyr::filter(!is.na(invs.species))
+
+imp %>%
+	ggplot(aes(y = degree, x = m_int_strength, fill = categ)) + 
+	geom_jitter(position = position_jitter(height = 0.25, width = 0.5),
+							shape = 21, alpha = 0.5) +
+	geom_smooth(method = "gam", colour = "grey10") +
+	xlab("mean interaction strength (visitation frequency)") +
+	scale_fill_discrete(name = "", labels = c("pollinators", "plants")) +
+	geom_point(data = inv, fill = "red", size = 2.5, shape = 21) +
+	my_theme +
+	theme(legend.position = "right")
+@
+\caption{\label{fig:degree_strength} Relationship between the mean visitation frequency per species (as a surrogate of interaction strength) and its degree in a particular network.
+Invasive plants are depicted with a red circle.}
+\end{figure}
+
+Here we only look at the effect on the weighted scheme.
+We can see in \autoref{fig:degree_strength_importance} that the patterns are different for plants and polinators.
+For plants importancy in controling the network is positively related to both the mean interaction strengt and the degree of the species.
+However for pollinators that's not the case: the relationship between importance and mean interaction strengt is pretty weak, but there is a significant negative relationship between the degree and the importancy.
+
+\begin{figure}
+\centering
+<<fig = T, echo = F, width = 6, height = 7>>=
+library(grid)
+library(gridExtra)
+
+p1 <- imp %>%
+	ggplot(aes(x = m_int_strength, y = f_f)) +
+	geom_point(aes(fill = categ),
+						 shape = 21, 
+						 alpha = 0.5) +
+	scale_shape_manual(values = c(21, 22)) +
+	facet_wrap(~type) +
+	geom_smooth(aes(colour = categ, fill = categ), 
+							family = "binomial", method = "gam", colour = "grey10") +
+	geom_point(data = inv, fill = "red", size = 2.5, shape = 21) +
+	my_theme +
+	xlab("mean interaction strength") +
+	ylab("species frequency\nin control sets") +
+	scale_color_discrete(name = "", labels = c("pollinators", "plants")) +
+	scale_fill_discrete(name = "", labels = c("pollinators", "plants")) +
+	theme(legend.position = "right", strip.background = element_blank())
+
+p2 <- imp %>%
+	ggplot(aes(x = degree, y = f_f)) +
+	geom_point(aes(fill = categ),
+						 shape = 21, 
+						 alpha = 0.5) +
+	scale_shape_manual(values = c(21, 22)) +
+	facet_wrap(~type) +
+	geom_smooth(aes(colour = categ, fill = categ), 
+							family = "binomial", method = "gam", colour = "grey10") +
+	geom_point(data = inv, fill = "red", size = 2.5, shape = 21) +
+	my_theme +
+	xlab("degree") +
+	ylab("species frequency\nin control sets") +
+	scale_color_discrete(name = "", labels = c("pollinators", "plants")) +
+	scale_fill_discrete(name = "", labels = c("pollinators", "plants")) +
+	theme(legend.position = "right", strip.background = element_blank())
+
+p3 <- imp %>%
+	ggplot(aes(x = nestedcontribution, y = f_f)) +
+	geom_point(aes(fill = categ),
+						 shape = 21, 
+						 alpha = 0.5) +
+	scale_shape_manual(values = c(21, 22)) +
+	facet_wrap(~type) +
+	geom_smooth(aes(colour = categ, fill = categ), 
+							family = "binomial", method = "gam", colour = "grey10") +
+	geom_point(data = inv, fill = "red", size = 2.5, shape = 21) +
+	my_theme +
+	xlab("contribution to nestedness") +
+	ylab("species frequency\nin control sets") +
+	scale_color_discrete(name = "", labels = c("pollinators", "plants")) +
+	scale_fill_discrete(name = "", labels = c("pollinators", "plants")) +
+	theme(legend.position = "right", strip.background = element_blank())
+
+grid.arrange(p1, p2, p3, ncol = 1)
+@
+\caption{\label{fig:degree_strength_importance} Relationship between the mean visitation frequency per species (as a surrogate of interaction strength) and its degree in a particular network with its presence in the control sets.
+Invasive plants are depicted with a red circle.
+Contribution to nestedness were calculated using 99 network randomisations.}
+\end{figure}
+
+As expected plants tend to have a larger degree than polinators.
+But regardless of the guild one would expect that as the degree of a species increases so does the likelyhood of it being less dependent than its counterpart and hence have more outer links, which in theory should increase its importance as driver node.
+The fact that this happens with plants but doesn't happen with pollinators is another part of how plants and pollinators play a distinct role in teh controlability of the networks.
+This might happen in part because of the nested structure of the mutualistic networks.
+A generalist polinator will still be "nested" within a set of generalist plants, in other words a generalist plant will have more partners than a generalist polinator which drives the arrows from plants to polinators anyways.
+(yeah fer this doesn't make sense...)
+
+We therefore explored the posibility that the importance is related to the contribution to nestedness.
+Voila!
+In this case both plants and polinators have a clear positive relationship (\autoref{fig:degree_strength_importance}c)!
+That's pretty cool but I don't know how to interpret this.
+Daniel help please!
+
+Because the profiling of nodes proposed by \textcite{Guimera2005} captures a lot of the connectivity of nodes we explore the relationship with the roles as well.
+
+\subsection*{Link redundancy and species}
+
+We got some links that are redundant and other that are critical from the control point of view.
+I wanted to have a look at what drives that.
+I haven't done the formal analysis yet but a visual inspection of the network is reveals a pretty strong pattern.
+
+Critical links tend to occur predominantly when control direction goes from pollinators to plants, this is when the plant is more dependent in the pollinator than the pollinator is on the plant (which is much less common than the other way around), and generaly involve specialist plants (\autoref{fig:link_n_example}).
+
+\begin{figure}
+\centering
+<<fig = T, echo = F, width = 6, height = 6>>=
+mnet <- "MED1CA"
+mtype <- "weight"
+mkeep <- "A"
+
+rob <- link_redundancy %>%
+	dplyr::filter(net == mnet, type == mtype , keep == mkeep) %$%
+	robustness
+
+m_net <- net[[mnet]] %>%
+	# select only the largest connected component of the network
+	keep_largest_component() %>%
+	# transform the network into the bipartite format we need
+	bipartite_digraph(type = mtype , keep = mkeep)
+
+igraph::plot.igraph(m_net, edge.arrow.size = .4, edge.color = as.integer(rob) +6, vertex.size = 10, vertex.color = as.integer(as.factor(igraph::V(m_net)$type)) -1, vertex.label = NA)
+
+@
+\caption{\label{fig:link_n_example} Example network.
+Plants and polinators are shown as white and yellow circles respectively.
+Redundant links are shown on grey and critical links are shown on purple.}
+\end{figure}
 
@@
 
-Dynamic system approach
-
 \section*{Acknowledgmenets}
@@
 The authors thank Dr.
-Takeuki Uno for the insight provided to find the set of all maximum matching algorithms.
+Takeuki Uno for the insight provided to find the set of all maximum matching algorithms, and Bernat Bramon and Marilia Gaiarsa for feedback in early stages of the project.
 EFC acknowledges the support from the University of Canterbury Doctoral Scholarship, the University of Canterbury Meadow Mushroooms Postgraduate Scholarship, a travel grant from the European Space Agency and a Rutherford Discovery Fellowship (to DBS).

### 2015-12-10 code/12_n-drivers_random_direction.R

@@ -1,0 +1,40 @@
+library(ggplot2)
+library(magrittr)
+# load utility functions
+nn <- list.files("./code/functions", full.names = TRUE) %>% lapply(source)
+
+net <- list.files("./data/networks/", full.names = TRUE) %>%
+	lapply(readRDS)
+names(net) <- list.files("./data/networks/", full.names = FALSE) %>%
+	stringr::str_split("\\.") %>% lapply(`[`, 1) %>% unlist ()
+
+space <- expand.grid(net = 1:length(net),
+										 keep = c("A", "B"),
+										 perm = 1:999)
+
+rand_directions <- plyr::ddply(space, c("net", "keep", "perm"), function(x){
+	
+	m_net <- net[[x$net]] %>%
+		# select only the largest connected component of the network
+		keep_largest_component() %>%
+		# transform the network into the bipartite format we need
+		bipartite_digraph(type = "weight", keep = x$keep)
+	
+	n <- igraph::tail_of(m_net, igraph::E(m_net)) %>% names() %>%
+		cbind(igraph::head_of(m_net, igraph::E(m_net)) %>% names())
+	
+	nr <- n %>%
+		apply(1, sample) %>% c()
+
+	rn <- igraph::make_directed_graph(nr)
+	
+	igraph::E(rn)$weight <- 1
+	igraph::V(rn)$type <- grepl("i", names(igraph::V(rn)))
+	igraph::V(rn)$type <- plyr::mapvalues(igraph::V(rn)$type, 
+																			 c(TRUE, FALSE), c("pol", "pla"))
+	
+	data.frame(overlap = sum(c(t(n)) == nr)/ 2 / nrow(n),
+						 n_driver = rn %>% n_unmatched_vertex())
+}, .progress = "text")
+
+write.csv(rand_directions, "./data/random_dir_n_driver.csv", row.names = FALSE)

### 2015-12-10 code/13_understanding_link_redundancy.R

@@ -1,0 +1,37 @@
+folder <- "./data/redundancy/edge/"
+
+link_redundancy <- list.files(folder, full.names = TRUE) %>%
+	plyr::ldply(function(x, name){
+		y <- read.csv(x) 
+		info <- basename(x) %>% 
+			stringr::str_sub(end = -5) %>% 
+			stringr::str_split("_") %>% 
+			unlist()
+		y %>%
+			dplyr::mutate(net = info[[1]],
+										type = info[2],
+										keep = info[3])
+	}) 
+
+net <- list.files("./data/networks/", full.names = TRUE) %>%
+	lapply(readRDS)
+names(net) <- list.files("./data/networks/", full.names = FALSE) %>%
+	stringr::str_split("\\.") %>% lapply(`[`, 1) %>% unlist ()
+
+
+mnet <- "MIQ1OP"
+mtype <- "weight"
+mkeep <- "A"
+
+rob <- link_redundancy %>%
+	dplyr::filter(net == mnet, type == mtype , keep == mkeep) %$%
+	robustness
+
+m_net <- net[[mnet]] %>%
+	# select only the largest connected component of the network
+	keep_largest_component() %>%
+	# transform the network into the bipartite format we need
+	bipartite_digraph(type = mtype , keep = mkeep)
+
+igraph::plot.igraph(m_net, edge.arrow.size = .2, edge.color = as.integer(rob), vertex.size = 10)
+

### 2015-12-10 code/functions/nestedcontribution.R

@@ -1,0 +1,60 @@
+nestedcontribution <- function(web, nsimul = 99){
+	# following Saavedra et al. 2011
+	# returns a list of species' contributions to nestedness
+	
+	# create a binary matrix
+	web <- ifelse(web>0,1,0)
+	
+	# if the web has no names (e.g. null models), give them names:
+	if (is.null(rownames(web))) rownames(web) <- paste0("L", seq.int(nrow(web)))
+	if (is.null(colnames(web))) colnames(web) <- paste0("H", seq.int(ncol(web)))
+	
+	# build containers for the different contribution values
+	lower.out <- data.frame(row.names=rownames(web))
+	lower.out$nestedcontribution <- NA
+	
+	higher.out <- data.frame(row.names=colnames(web))
+	higher.out$nestedcontribution <- NA
+	
+	if (any(dim(web) < 2)){
+		warning("Your web is too small for a meaningful computation of nestedcontrrank (and probably other indices)!")
+	}else{
+		# compute the original nestedness
+		nested.orig <- vegan::nestednodf(web)$statistic["NODF"]
+		
+		# compute the nestedness contribution of each row
+		for(i in rownames(web)){
+			# determine the probability of each interaction according to Bascompte et al. 2003
+			probs <- (rowSums(web)[i] / ncol(web) + colSums(web) / nrow(web)) / 2.
+			
+			# calculate the nestedness for an ensemble of networks with row i's interactions drawn at random
+			nested.null <- sapply(1:nsimul, function(x) {web.null <- web; web.null[i,] <- rbinom(ncol(web),1,probs); vegan::nestednodf(web.null)$statistic["NODF"]})
+			
+			# the below is the swap model
+			#nested.null <- sapply(1:nsimul, function(x) {web.null <- web; web.null[i,] <- sample(web[i,]); vegan::nestednodf(web.null)$statistic["NODF"]})
+			
+			lower.out[i,"nestedcontribution"] <- (nested.orig - mean(nested.null))/sd(nested.null)
+		}
+		
+		# compute the nestedness contribution of each column
+		for(i in colnames(web)){
+			# determine the probability of each interaction according to Bascompte et al. 2003
+			probs <- (rowSums(web) / ncol(web) + colSums(web)[i] / nrow(web)) / 2.
+			
+			# calculate the nestedness for an ensemble of networks with row i's interactions drawn at random
[…]

### 2015-12-22 paper/manuscript.Rmd
new Rmd manuscript

--- 2015-12-07 paper/manuscript.Rnw
@@
-\documentclass[a4paper,10pt]{article}
-% abstract + title + authors
-\usepackage{abstract}
-\renewcommand{\abstractnamefont}{\normalfont\bfseries}
-\renewcommand{\abstracttextfont}{\normalfont\small\itshape} 
-\usepackage{titlesec}
-\usepackage{authblk}
-\usepackage{datetime}
-\newdateformat{usvardate}{
-\monthname[\THEMONTH] \ordinal{DAY}, \THEYEAR}
+---
+title: "driver species paper"
+output: pdf_document
+---
 
-% keywords
-\providecommand{\keywords}[1]{\textbf{\textit{Keywords---}} #1}
+**how is the control species number influenced by network structure?**
 
-% math
-\usepackage{amssymb}
-\usepackage{newtxmath}
-
-% manuscript looking document
-\usepackage{setspace}
-\usepackage{lineno,xcolor}
-\setlength{\parskip}{0.5em}
-
-% comments
-\usepackage[draft]{todonotes}
-
-% graphics
-\usepackage{graphicx}
-\usepackage{float}
-
-% references & links
-\usepackage[
-backend=biber,
-style= authoryear,
-citestyle = authoryear,
-url=false,
-doi=true,
-isbn=false
-]{biblatex}
-\addbibresource{references.bib}
-
-\usepackage{hyperref}
-\hypersetup{
-    colorlinks=true,
-    citecolor=magenta,
-    linkcolor=magenta
-}
-\usepackage{doi}
-\begin{document}
-\SweaveOpts{concordance=TRUE,prefix.string=figures/fig-}
-\setkeys{Gin}{width=1\textwidth}
-
-% title
-% Article title
-  \title{\fontsize{16pt}{10pt}\selectfont\textbf{Structural controlability of pollination networks}}
-
-% Authors and Affiliations
-  \author[1]{\large E. Fernando Cagua}
-  \author[1]{\large Daniel B. Stouffer}
-  \affil[1]{\normalsize Center of Integrative Ecology, School of Biological Sciences, University of Canterbury}
-
- \date{\small\usvardate\today}
-
-\maketitle
-
-\begin{abstract}
-\noindent Si sabemos que el disfrute exige lentitud, y que---mas en general---la felicidad se asocia con el ir despacio, por que corremos tanto?
-El arte de comer estriba en saborear cada bocado sin pensar en el siguiente, sin apresurar el siguiente.
-El arte de leer, en demorarse en cada palabra como si el sentido del escrito entero estuviera contenido en ella.
-El arte de amar, en vivir cada momento de la relacion con la persona amada como si fuese el destino de toda la historia del mundo, desde la aparicion del primer organismo unicelular hasta hoy.
-Y asi podemos generalizar a las demas actividades, creo, hasta obtener un arte de vivir.
-Para mi se resume en la palabra ahi.
---- Jorge Riechmann
-\end{abstract}
-
-\keywords{Control theory}
-
-% line numbers
-\linenumbers
-\setlength\linenumbersep{15pt}
-\renewcommand\linenumberfont{\normalfont\footnotesize\sffamily\color{gray}}
-
-\onehalfspacing
-
-<<libraries and preparatory stuff, echo = FALSE>>=
+Using both Bartomeus and Lopezaraiza dataset
+```{r, echo=FALSE}
 library(ggplot2)
 library(magrittr)
+# load utility functions
+nn <- list.files("../code/functions", full.names = TRUE) %>% lapply(source)
 
 my_theme <- theme_classic() + theme(legend.position = "none", text = element_text(family = "Times"), axis.title.x = element_text(vjust = -0.7), axis.title.y = element_text(vjust = 1.5)) 
-@
+```
 
-% Main Text
-\section*{Introduction}
+```{r, echo=FALSE, warning=FALSE, message=FALSE}
+n_driver <- read.csv("../data/n_driver_species.dat")
+random_n <- read.csv("../data/random_n_driver.csv")
 
-\todo[inline]{This intro was written when I though that the paper was mainly gonna be about the relative importance of species and how invasives fit there.
-Read with caution as I don't think that's the case anymore}
-
-Ecological communities are formed by the interconnection of several species.
-Therefore, changes in the abundances of one species can potentially alter the abundances of the species they interact with.
-For instance, in a classic example of ecosystem cascades, a reduction on the abundance of sea otters, an important predator or sea urchins, can drive a dramatic reduction on kelp abundances because the sea urchins that consume kelp are released from predation.
-It has been long established that some species, like the sea otter, have a disproportionate large effect in their environment relative to their abundance.
-
-In several ecosystems the relative importance of species have been identified based on empirical observations of long term dynamics.
-However, in less studied, highly diverse, or where the "keystone" role is shared by several species, it can be challenging to determine which is the set of species that influence the most the ecosystem dynamics.
-Alternative approaches that recognize a continuum of importance and that are less dependent on empirical observations have also been developed.
-Some of them are based on metrics that evaluate their position in the food web or on mass balance models of functional groups.
-Nevertheless, these approaches are conceptually limited to throphic interactions and in general ignore the structural mechanisms that allow or prevent the spread of perturbations in the ecosystem.
-
-From a systems perspective, perturbations like over-exploitation, eutrophication or global warming are equivalent to management actions like culling, no-take areas or captive rearing in the sense that they have the potential to modify the abundances of one or several species in the ecosystem.
-Therefore identifying these key species is crucial not only to predict how these perturbations will spread trough the community but also to guide effective conservation efforts.
-
-Recent work on the control of complex systems suggest that in principle it is possible to alter any ecological community's composition, by modifying the abundances of just some key species.
-Here, we apply these theories to estimate the controllability of different ecological communities and to find the species, that due to the structural characteristics of their interactions are more likely to drive the dynamics of the community.
-
-\section*{Methods \& Results}
-
-Using six paired plant pollinator communities we explored the concepts of control theory. This is the initial data set things will be tested. If more data is considered necessary we'll see that later.
-
-\subsection*{Controllability of ecological communities}
-
-\subsubsection*{Minimum set of species }
-
-Using maximum matching to control all species in the network.
-We found that depending on the scheme around of the species are needed to have a grasp at the whole community (\autoref{fig:n_species}).
-However, the relative ranking of networks remains relatively unchanged across schemes.
-So rather than focusing on the differences across schemes perhaps it would be interesting to see what characteristics make a network to require more or less driver nodes to be completely controled.
-Alternatively it would be interesting to see if there are systemic differences between different types of networks.
-An initial step would be to stay with bipartite networks of the mutualistic type (plant/frugivores) or the the consumer-resource type (host/paraiste or predator/prey).
-Perhaps some model networks of varying parameters?
-
-\begin{figure}
-\centering
-<<fig = T, echo = F, width = 6, height = 3>>=
-n_driver <- read.csv("../data/n_driver_species.dat")
-
-ggplot(n_driver, aes(x = type, y = n_driver/n_species)) +
-	geom_violin(colour = "grey") +
-	geom_line(aes(colour = as.factor(net),group = as.factor(net))) +
-	geom_point(aes(fill = as.factor(net)), shape = 21) +
-	xlab("link structure scheme") + ylab("proportion of driver species") +
-	my_theme
-@
-\caption{
-\label{fig:n_species} 
-Proportion of species that needs to be controled for all twelve networks under different link assumptions.
-AB indicates that the links go from plants to pollinators; BA that the links go from pollinator to plants; ``weight'' that the direction of control is chosen by dependency (ties are resolved by giving priority to plants in weight.A and to pollinators in weight.B); z-bi indicates that the links go in both directions}
-\end{figure}
-
-There was no significant difference between the number of species needed to control the system in an invaded and an uninvaded ecosystem.
-
-When comparing the number of control nodes of the observed networks to their random counterparts an interesting pattern emegerges (\autoref{fig:random_n_species}).
-The number of control nodes is significantly larger than randomisations that mantain the degree distribution of the plants.
-However there is no significant difference when the randomisations mantain the degree of pollinators (or both plants and pollinators).
-This pattern is consistent across all schemes of link directionality.
-This suggest that the patterns of pollinator visitations are the structural characteristic that determines the controlability of the network.
-We probably should analyse other pollination networks to see if this pattern hold.
-We also should think about the implications of this finding.
-
-\begin{figure}
-\centering
-<<fig = T, echo = F, width = 6, height = 3.5>>=
-random_n <- read.csv("../data/random_n_driver.csv")
 n_control <- n_driver %>%
@@
 				axis.line.x = element_blank(), axis.ticks.x = element_blank())
-@
-\caption{
-\label{fig:random_n_species} 
-Difference between the number of control nodes in the analysed networks versus randomisations of the same networks.
-Unshaded areas suggest a significant difference.
-Schemes same as in \autoref{fig:n_species}}
-\end{figure}
+```
 
-It occured to me that it is possible that the patterns (and perhaps others observed like more phylogenetic signal in polinators than in plants) are a consequence of a greater diversity of pollinators in the interaction networks.
-More pollinators relative to plants imply that randomisations that mantain the degree distribution of pollinators are more constrained than those that only mantain the degree distribution of plants.
-It also means that statistical tests on that group have a more observations and therefore rendering significant results for smaller effect sizes.
-I cheked that with the 12 pollination networks of the study and there seems to be some evidence for that (\autoref{fig:zscore_ratio}).
-Perhaps it would be good to check with other networks to see if it holds.
+\newpage
 
-\begin{figure}[h]
-\centering
-<<fig = T, echo = F, width = 6, height = 3.5>>=
-net_info <- read.csv("../data/ntw_info.csv")
+**what's the role of the dependency?**
 
-net_info %<>%
-	dplyr::mutate(ratio_pol_pla = n_pol/n_pla)
+Using dataset by Ballantune to demonstrate congruency between visitation and effective pollination dependency.
 
-random_n_z %>%
-	dplyr::full_join(net_info) %>%
-	dplyr::mutate(t = as.character(interaction(type, keep))) %>% 
-	dplyr::filter(method == "c0", t != "BA.B") %>%
-	ggplot(aes(x = ratio_pol_pla, y = n_driver_z_score)) +
-	geom_point() +
-	geom_smooth(method = "lm", alpha = 0.1, colour = "grey10") +
-	xlab("ratio of number of pollinators to plants") +
+```{r, echo=FALSE, warning=FALSE, message=FALSE}
+random_dir_n <- read.csv("../data/random_dir_n_driver.csv")
+
+random_dir_n %>% 
+	dplyr::mutate(type = "weight") %>%
+	dplyr::group_by(net, type, keep) %>%
+	dplyr::summarise(n_driver_u = mean(n_driver, na.rm = T),
+									 n_driver_sd = sd(n_driver, na.rm = T)) %>%
+	dplyr::inner_join(n_control) %>% 
+	dplyr::group_by() %>%
+	dplyr::mutate(n_driver_z_score = (n_driver - n_driver_u)/n_driver_sd) %>% 
+	ggplot(aes(x  = as.character(interaction(type, keep)), y = n_driver_z_score)) +
+	geom_rect(ymin = -2, ymax = 2, xmin = -1, xmax = 10, fill = "grey90") +
+	geom_hline(yintercept = 0, size = 0.4) +
+	geom_vline(xintercept = seq(1.5, 2.5), linetype = 2) +
+	geom_jitter(position = position_jitter(height = 0), shape = 21) +
+	geom_boxplot(fill = "white", alpha = 0.5) +
+	scale_fill_discrete(name = "randomisations\nmantain\ndegree of", labels= c("plants", "pollinators", "both")) + 
+	my_theme + 
+	xlab("link structure scheme") +
 	ylab("standard score") +
-	my_theme + 
-	facet_wrap(~t, scales = "free") + 
-	theme(strip.background = element_blank())
-@
-\caption{
-\label{fig:zscore_ratio} 
-When considering only randomisations that mantain the degree distribution of plants, there seems to be a possitive relationship between the ratio of pollinators to plants and the Z-score of randomisations.
-The pattern is, however, not significant for the weighted schemes.
-The z-scores are identical for the AB.A and the BA.B schemes.
-Schemes same as in \autoref{fig:n_species}}
-\end{figure}
+	theme(legend.position = "right",
+				axis.line.x = element_blank(), axis.ticks.x = element_blank())
+```
 
-\subsubsection*{Profiles of critical and redundant species}
+\newpage
 
-Dividing the nodes and links among critical, ordinary and redundant we can have an idea of ``control profiles'' of the networks.
-Both species and interactions can be classified as redundant, ordinary and critical depending on the number of species that need to be controled to gain full control over the network once the species has been removed (\autoref{fig:s_crit_prop} and \ref{fig:i_crit_prop}).
+**finally what makes a species relevant from management, and how invasive species fit there**?
 
-\begin{figure}[tp]
-\centering
-<<fig = T, echo = F, width = 6, height = 2.5>>=
+exploring these and other factors related to especialization
+
+```{r, echo=FALSE, warning=FALSE, message=FALSE, cache=TRUE}
+library(grid)
+library(gridExtra)
+
 folder <- "../data/redundancy/node/"
@@
 
-ggplot(nr_sum) +
-	geom_boxplot(aes(x = type, y = prop, fill = robustness)) +
-	geom_vline(xintercept = seq(1.5, 5.5), linetype = 2) +
-	xlab("link structure scheme") +
-	ylab("species proportion") +
-	scale_fill_discrete(name = "nodes") +
-	my_theme + 
-	theme(legend.position = "right", 
-				axis.line.x = element_blank(), 
-				axis.ticks.x = element_blank())
-@
-\caption{\label{fig:s_crit_prop} Proportion of species that are ordinary (when removed the number of species needed to control the network doesn't change), redundant (when removed less species are needed) and critical (when removed the number of species needed to control the network increasses).
-Schemes same as in \autoref{fig:n_species}}
-\end{figure}
+net <- list.files("../data/networks/", full.names = TRUE) %>%
+    lapply(readRDS)
+names(net) <- list.files("../data/networks/", full.names = FALSE) %>%
+    stringr::str_split("\\.") %>% lapply(`[`, 1) %>% unlist ()
 
-\begin{figure}[tp]
-\centering
-<<fig = T, echo = F, width = 6, height = 2.5>>=
-folder <- "../data/redundancy/edge/"
-link_redundancy <- list.files(folder, full.names = TRUE) %>%
-    plyr::ldply(function(x, name){
-        y <- read.csv(x) 
-        info <- basename(x) %>% 
-            stringr::str_sub(end = -5) %>% 
-            stringr::str_split("_") %>% 
-            unlist()
-        y %>%
-            dplyr::mutate(net = info[[1]],
-                                        type = info[2],
-                                        keep = info[3])
-    })
+node_redundancy %<>% 
+	plyr::ddply("net", function(x){
+		this_net <- net[[dplyr::first(x$net)]] %>%
+	# select only the largest connected component of the network
+			keep_largest_component()
+		nodes <- igraph::V(this_net)[x$n]$name
+		x %>%
+			dplyr::mutate(node = nodes)
+	}) %>% dplyr::tbl_df()
 
-lr_sum <- link_redundancy %>%
-	dplyr::mutate(type = interaction(type, keep)) %>%
-	dplyr::group_by(net, type, robustness) %>%
-	dplyr::summarise(freq = n()) %>%
-	dplyr::group_by(net, type) %>%
-	dplyr::mutate(n_species = sum (freq)) %>%
-	dplyr::group_by() %>%
-	dplyr::mutate(prop = freq / n_species, 
-								type = as.character(type), 
-								robustness = as.character(robustness))
+deg_strength <- plyr::ldply(net,function(x){
+	degree <- igraph::degree(x)
+	m <- igraph::as_adjacency_matrix(x, attr = "weight", sparse = F)
+	m[m == 0] <- NA 
+	m_int_strength <- apply(m, 1, mean, na.rm = T)
+	s_int_strength <- apply(m, 1, sum, na.rm = T)
+	ncont <- igraph::as_incidence_matrix(x, 
+														types = igraph::V(x)$type == "pla") %>%
+		nestedcontribution() %>% dplyr::add_rownames("node")
+	data.frame(node = names(degree), 
+						 degree = degree, 
+						 m_int_strength = m_int_strength,
+						 s_int_strength = s_int_strength) %>%
+		dplyr::full_join(ncont)
+}) %>% dplyr::rename_("net_name" = ".id")
 
-ggplot(lr_sum) +
-	geom_boxplot(aes(x = type, y = prop, fill = robustness)) +
-	geom_vline(xintercept = seq(1.5, 5.5), linetype = 2) +
-	scale_fill_discrete(name = "links") +
-	xlab("link structure scheme") +
-	ylab("interactions proportion") +
-	my_theme + theme(legend.position = "right")
-@
-\caption{\label{fig:i_crit_prop} Proportion of interactions that are ordinary (when removed the number of species needed to control is reduced), redundant (when removed the number of species needed to control doesn't change) and critical (when removed the number of species needed to control the network increasses).
-Schemes same as in \autoref{fig:n_species}}
-\end{figure}
+net_info <- read.csv("../data/ntw_info.csv")
 
-On the species redundancy profile (\autoref{fig:s_crit_prop}), the profiles are also highly dependent on the chosen directionality scheme.
-For instance, in the case in which species have links in both directions there are not ordinary species and the number of critical species is relatively high, this is not surprising because under this scheme, there is a much smaller set of species that needs to be controled and therefore removing one of these can increase the minimum set of species needed to control the network.
+net_info %<>%
+	dplyr::mutate(ratio_pol_pla = n_pol/n_pla)
 
-However, there appears to be a relatively small variability between networks analysed using this approach.
-Again, as in the previous section, I think there is little that can be understood by using just this data-set.
-Again I think it would be most interesting to see if there are systemic differences between different types of networks where a larger variation in the profiles is expected.
-
-On the interaction redundancy profile (\autoref{fig:i_crit_prop}) things seem a bit more interesting because the variation across networks and across link directionality schemes is pretty small.
-For instance for the bidirectional scheme, although the total number of links is doubled, the relative proportion of links that are critical and redundant is mantained.
-
-\subsubsection*{Profiles of internal/external dilation}
-
-\textcite{Ruths2014} proposed another clever way to characterise the control profile of a network by charactering the number of nodes that need to be controled among the ``mechanism'' that originates it.
-Similar as the maximum matching algorith, the idea comes from the concept that in the absense of cycles one node can at most control another one.
-Then the origin of control nodes can be splitted between nodes that need to be controled because they are a ``source node'' those that have only out links, control nodes associated to ``external dilations'' and those associated to ``internal dilations''.
-
-It could be interesting to compare different networks using this framework.
-They argue that source dominated networks should be relatively easy to control in a top-down fashion.
-On the other hand internal dilation dominated networks represent the signature of a network that self-regulates and is not meant to be controled in that it's not designed to visit every possible state.
-
-However as we can see here this framework is pretty useless when the direction of control is not perfectly known (as in most real wolrd networks really...).
-For instance when applying it to the data-set (\autoref{fig:dilation}), we see that when the control flows from pollinators to plants (AB.A) the network is source dominated simply because the pollinator diversity is greater than the plant's.
-When we asume that each guild can control each other (z-bi.all) the networks are internal dilation dominated because it's purely composed of cycles.
-However the weighted version might offer a meaningful possibility to develop the analysis.
-
-\begin{figure}
-\centering
-<<fig = T, echo = F, width = 6, height = 3>>=
-library(ggtern)
-dilation <- read.csv(file = "../data/dilation_profiles.dat")
-
-ggplot(dilation, aes(x = eta_s, z = eta_e, y = eta_i)) +
-	geom_point(aes(fill = type.keep), shape = 21, size = 5, alpha = 0.7) +
-	coord_tern() + theme_classic() + theme(text =  element_text(family = "Times"))
-
-detach("package:ggtern", unload = TRUE, character.only = TRUE)
-detach("package:ggplot2", unload = TRUE, character.only = TRUE)
-library(ggplot2)
-@
-\caption{\label{fig:dilation} Control profiles of pollination networks.
-Control nodes are split among nodes that need to be controled because they are a source node, some that are control nodes because they respond to internal dilations (cycles) and some that are control nodes because they repsond to external dilations (sink nodes not matched)}
-\end{figure}
-
-\subsection*{Ranking species}
-
-\subsubsection*{By frequency in control sets}
-
-There are multiple sets of species with which is structurally possible to control network dynamics.
-An initial posibility os to relate the importance of a species for network dynamics to the frequency at which a species is present in the control sets.
-
-Turns out unsurprisingly that the importance of particular species and its distribution over a networks dependends on the scheme chosen for the directionality of the links (\autoref{fig:n_control_dist}).
-When pollinators control plants (AB) no plant must be controled and most pollinators have an importance close to one. 
-On the other hand when plants control pollinators (BA) presumably because the pollinator diversity is larger than the plant diversity, the pattern is less "bimodal" and intermediate levels of importance are allowed.
-
-\begin{figure}
-\centering
-<<echo = F, cache = T>>=
 folder <- "../data/maximum_matchings_summary/" 
@@
 	dplyr::summarise(freq = sum(freq))
-@
 
-<<fig = T, echo = F, width = 6, height = 4>>=
 ranked_mm <- node_mm %>%
@@
 
-ggplot(ranked_with_inv, aes(x = f_f, fill = net_name)) +
-	geom_density(alpha = 0.025, adjust = 1, colour = "grey20") +
-	geom_point(data = ranked_with_inv %>%
-						 	dplyr::filter(invs.species), aes(y = scale(net) + 2),
-						 shape = 21, fill = "grey") +
-	facet_wrap(~type, ncol = 2) +
+imp <- ranked_with_inv %>%
+	dplyr::full_join(deg_strength) %>%
+	dplyr::filter(!is.na(type.keep), 
+								type == "weight",
+								keep == "A" | keep == "all") %>%
+	tidyr::separate(node, into = c("categ", "number"), sep = "_", remove = F)
+
+inv <- imp %>% dplyr::filter(!is.na(invs.species))
+
+p1 <- imp %>%
+	ggplot(aes(x = m_int_strength, y = f_f)) +
+	geom_point(aes(fill = categ),
+						 shape = 21, 
+						 alpha = 0.5) +
+	scale_shape_manual(values = c(21, 22)) +
+	facet_wrap(~type) +
+	geom_smooth(aes(colour = categ, fill = categ), 
+							family = "binomial", method = "gam", colour = "grey10") +
+	geom_point(data = inv, fill = "red", size = 2.5, shape = 21) +
 	my_theme +
-	xlab("species frequency in control sets") +
-	theme(strip.background = element_blank(),
-				axis.text.x = element_text(angle = 90))
-@
-\caption{\label{fig:n_control_dist} Distribution of the relative frequency a species is present in the set of control species among the networks.
-The frequency of invasive species in each of the six invaded networks is denoted with a circle.
-Results for the bidirectional liks (z-bi) were obatined only for the nine smallest networks, which included 3 invaded ecosystems}
-\end{figure}
+	xlab("mean interaction strength") +
+	ylab("species frequency\nin control sets") +
+	scale_color_discrete(name = "", labels = c("pollinators", "plants")) +
+	scale_fill_discrete(name = "", labels = c("pollinators", "plants")) +
+	theme(legend.position = "right", strip.background = element_blank())
 
-Among the weighted versions there was little difference if dependency ties were resolved for plants of for pollinators (\autoref{fig:n_control_dist_ntw}), again there are more species with intermediate levels of importance.
-Even more spread out are things when we consider bidirectional links.
-I imagine that this pattern is partly because there are many many more ways to control the network in the bidirectional scheme than in the others.
+p2 <- imp %>%
+	ggplot(aes(x = degree, y = f_f)) +
+	geom_point(aes(fill = categ),
+						 shape = 21, 
+						 alpha = 0.5) +
+	scale_shape_manual(values = c(21, 22)) +
+	facet_wrap(~type) +
+	geom_smooth(aes(colour = categ, fill = categ), 
+							family = "binomial", method = "gam", colour = "grey10") +
+	geom_point(data = inv, fill = "red", size = 2.5, shape = 21) +
+	my_theme +
+	xlab("degree") +
+	ylab("species frequency\nin control sets") +
+	scale_color_discrete(name = "", labels = c("pollinators", "plants")) +
+	scale_fill_discrete(name = "", labels = c("pollinators", "plants")) +
+	theme(legend.position = "right", strip.background = element_blank())
 
-In both AB and BA the relative importance of different species is almost fully constrained by the scheme.
-In the weighted scheme, invasive species are in all cases among the most important ones.
-Interestingly the pattern is opposite for when the direction can go both ways.
-It would be good to see then whether these patterns are a reflection of the fact that invasive species are actually dominant or an artifact arising from the fact that all invasive species are plants and that all networks are dominated by pollinators.
-An initial inspection on the distributrion of plants and pollinators per network for these schemes suggest that that might be the case for the bidirectional scheme but not for the weighted one (\autoref{fig:n_control_dist_guild} and \ref{fig:n_control_dist_per_net}).
+p3 <- imp %>%
+	ggplot(aes(x = nestedcontribution, y = f_f)) +
+	geom_point(aes(fill = categ),
+						 shape = 21, 
+						 alpha = 0.5) +
+	scale_shape_manual(values = c(21, 22)) +
+	facet_wrap(~type) +
+	geom_smooth(aes(colour = categ, fill = categ), 
+							family = "binomial", method = "gam", colour = "grey10") +
+	geom_point(data = inv, fill = "red", size = 2.5, shape = 21) +
+	my_theme +
+	xlab("contribution to nestedness") +
+	ylab("species frequency\nin control sets") +
+	scale_color_discrete(name = "", labels = c("pollinators", "plants")) +
+	scale_fill_discrete(name = "", labels = c("pollinators", "plants")) +
+	theme(legend.position = "right", strip.background = element_blank())
 
-\begin{figure}
-\centering
-<<fig = T, echo = F, width = 6, height = 4>>=
-ranked_with_inv %>%
-	tidyr::separate(node, into = c("categ", "number"), sep = "_", remove = F) %>%
-	ggplot(aes(x = f_f)) + 
-	geom_density(aes(fill = categ), 
-							 alpha = 0.5, adjust = 0.5, colour = "grey20") +
-	geom_point(data = ranked_with_inv %>%
-						 	dplyr::filter(invs.species), aes(y = scale(net) + 2), 
-						 shape = 21, fill = "red") +
-	facet_wrap(~type, ncol = 2) +
-	scale_fill_grey(name = "", labels = c("pollinators", "plants")) +
-	my_theme +	
-	xlab("species frequency in control sets") +
-	theme(strip.background = element_blank(),
-				axis.text.x = element_text(angle = 90), legend.position = "right")
-@
-\caption{\label{fig:n_control_dist_guild} Distribution of the relative frequency a species is present in the set of control species by guild.}
-\end{figure}
-
-We explored that option by
-
-<<>>=
-ranked_with_inv  %>%
-	tidyr::separate(node, into = c("categ", "number"), sep = "_", remove = F) %>%
-	dplyr::group_by(net, type.keep, categ) %>%
-	dplyr::summarise(f_f = median(f_f), 
-									 ratio_pol_pla = mean(ratio_pol_pla)) %>%
-	dplyr::group_by(net, type.keep) %>%
-	dplyr::mutate(f_sum = f_f - lead(f_f)) %>%
-	ggplot(aes(x = ratio_pol_pla, y = f_sum)) +
-	geom_point() +
-	geom_smooth(method = "lm")+ 
-	facet_wrap(~type.keep)
-@
-
-\subsubsection*{By redundancy}
-
-\subsubsection*{Strongly interacting species (interaction heterogeneity)}
-
-\section*{Discussion}
-
-For instance, restoration projects that aim to drive an invasive species out of the community, to reestablish a particular ecosystem service or in general modify the ecosystem state have had a limited amount of success.
-We argue that quantifying the relative dynamic importance of species the set of key species is the first step to evaluate current management efforts as well as to design targeted and informed
-
-Dynamic system approach
-
-\section*{Acknowledgmenets}
-
-The authors thank Dr.
-Takeuki Uno for the insight provided to find the set of all maximum matching algorithms.
-EFC acknowledges the support from the University of Canterbury Doctoral Scholarship, the University of Canterbury Meadow Mushroooms Postgraduate Scholarship, a travel grant from the European Space Agency and a Rutherford Discovery Fellowship (to DBS).
-DBS ackloledges the support of a Rutherford Discovery Scholarship, administered by the Royal Society of New Zealand.
-
-% \bibliography{references}
-\printbibliography
-
-\newpage
-\section*{Supplementary Information}
-\makeatletter 
-\renewcommand{\thefigure}{S\@arabic\c@figure}
-\makeatother
-\setcounter{figure}{0}
-
-\begin{figure}[h!]
-\centering
-<<fig = T, echo = F, width = 6, height = 4>>=
-ggplot(ranked_mm, aes(x = net_name, y = f_f, fill = type.keep)) +
-	geom_boxplot()+
-# 	geom_jitter(shape = 21, 
-# 							position = position_jitter(height = 0), 
-# 							alpha = 0.2, size = 1) +
-	facet_wrap(~type) +
-	my_theme +	
-	theme(strip.background = element_blank(),
-				axis.text.x = element_text(angle = 90))
-@
-\caption{\label{fig:n_control_dist_ntw} Distribution of the relative frequency a species is present in the set of control species among by network}
-\end{figure}
-
-\begin{figure}[h!]
-\centering
-<<fig = T, echo = F, width = 6, height = 9.5>>=
-bb <- ranked_with_inv %>%
-	tidyr::separate(node, into = c("categ", "number"), sep = "_", remove = F) %>%
-	dplyr::filter(type == "weight" | type == "z-bi")
-
-bb %>%
-	ggplot(aes(x = f_f)) + 
-	geom_density(aes(fill = categ), 
-							 alpha = 0.5, adjust = 0.5, colour = "grey20") +
-	geom_point(data = bb %>%
-						 	dplyr::filter(invs.species), aes(y = scale(net) + 2), 
-						 shape = 21, fill = "red") +
-	facet_grid(net_name ~ type.keep, scales = "free_y") +
-	scale_fill_grey(name = "", labels = c("pollinators", "plants")) +
-	my_theme +	
-	xlab("species frequency in control sets") +
-	theme(strip.background = element_blank(),
-				axis.text.x = element_text(angle = 90), legend.position = "top")
-@
-\caption{\label{fig:n_control_dist_per_net} Distribution of the relative frequency a species is present in the set of control species among by network partitioned by plant or pollinators.
-Invasive species is depicted with a red dot.}
-\end{figure}
-\end{document}
+grid.arrange(p1, p2, p3, ncol = 1)
+```

### 2016-02-02 paper/supp_info.Rmd
visitation vs deposition analysis

---
title: "Supplementary Information"
classoption: a4paper
output:
  pdf_document:
    fig_caption: yes
    fig_crop: no
    number_sections: yes
bibliography: references.bib
---

```{r libraries, echo = FALSE, warning = F, message = F}
library(magrittr)
library(knitr)
library(ggplot2)
opts_knit$set (root.dir=normalizePath('../'))
```

```{r auxiliary functions, echo = FALSE, warning = F, message = F}
"./code/V2.0/functions" %>% 
	list.files(full.names = T) %>%
	plyr::l_ply(source)

# figure counter
fig_count <- dplyr::data_frame(ref = "NA", count = 0)
fig_n <- function(ref) {
  fig_count <<- rbind(fig_count,
                      dplyr::data_frame(ref = ref,
                                        count = dplyr::last(fig_count$count) + 1))
  return(dplyr::last(fig_count$count))
}
fig_r <- function(ref) fig_count$count[fig_count$ref == ref]

# table counter
tbl_count <- dplyr::data_frame(ref = "NA", count = 0)
tbl_n <- function(ref) {
  tbl_count <<- rbind(tbl_count,
                      dplyr::data_frame(ref = ref,
                                        count = dplyr::last(tbl_count$count) + 1))
  return(dplyr::last(tbl_count$count))
}
tbl_r <- function(ref) tbl_count$count[tbl_count$ref == ref]
```

```{r plot theme, echo = FALSE, warning = F, message = F}
fer_theme <- theme_bw() +
	theme(text = element_text(family = "Times"),
	      title = element_text(size = 7.5, hjust = 0),
	      legend.title = element_text(size = 9),
	      legend.text = element_text(size = 8),
				axis.text = element_text(size = 8),
				axis.title = element_text(size = 9, hjust = 0.5), 
				strip.text = element_text(size = 9, hjust = 0), 
				strip.background = element_blank(),
				plot.margin = grid::unit(c(5, 0, 2, 0), "mm"))
```

```{r read data and results, echo = FALSE, warning = F, message = F}
net <- "./data/V2.0/networks" %>%
	read_networks()
meta <- readr::read_csv("data/ntw_info.csv") %>% dplyr::tbl_df() %>%
	dplyr::rename(count = method)
n_matched <- readRDS("./data/V2.0/n_matched.rds")
m_f <- readRDS("./data/V2.0/matching_frequency.rds")
```

# Visitation frequency vs. pollen deposition

The number of driver species in a pollination community and the relative importance of each species depend both of the strength of mutual dependencies between plant pollinators and the structure of the pollination network. Traditionally pollination networks have been represented using visitation frequency, but a flower visitor is not necessarely a pollinator. It has been shown that wether pollination networks are represented using visitation or actual pollen deposition can have effects on the network structure and presumably on the strength of mutuial dependency.

We investigated the effects of using visitation, pollen deposition (effective pollination) and pollinator importance (the product of visitation frequency and effective single visit pollen deposition). We used available data collected by @Ballantyne2015 from a low diversity pollination community at a dry lowland heathland in Dorset, UK (50° 43.7'N 2° 07.2'W).

Deposition networks, a proxy pollinator efficiency, were quantified using the mean Single Visit Deposition---the number of conspecific pollen grains effectively deposited on a virgin stigma during a single visit by a particular animal [@NeEman2010; @King2013; @Ballantyne2015]. Visitation networks were constructed counting the visits to flowers during Single Visit Depositions. Pollinator importance networks were consrtucted as the product of pollinator efficiency and visit frequency.

```{r matrix representation, echo = FALSE, warning = F, message = F, fig.height=5.5}
# get network weights 
p <- net[meta$net_name[meta$study == "ballantyne" & meta$count != "binary"]] %>%
	plyr::ldply(function(x) {
		data.frame(vname = igraph::E(net[[1]]) %>% attr("vnames"), 
							weight = igraph::E(x)$weight)
	}) %>%
	dplyr::rename_("net_name" = ".id") %>%
	dplyr::mutate(net_name_f = factor(net_name,  
																		levels = c( 'bal_eff','bal_vis','bal_imp'),
																		labels = c("a) Deposition", "b) Visitation", "c) Importance")), 
	              pla = stringr::str_split_fixed(vname, "\\|", 2)[, 1],
	              pol = stringr::str_split_fixed(vname, "\\|", 2)[, 2]) %>%
  plyr::dlply("net_name_f", function(x){
    p1 <- x %>%
      ggplot(aes(x = pol, y = pla)) +
      geom_tile(aes(fill = weight, width = 0.9, height = 0.9)) + 
      coord_fixed() +
      scale_fill_gradient(low = "#f0f0f0", high = "#525252") +
      ylab("plants") +
      xlab("pollinators") + 
      fer_theme +
      theme(axis.text = element_blank(), 
            axis.ticks = element_blank(), 
            legend.position = "right", 
            legend.title = element_blank(), 
            plot.margin = grid::unit(c(6,0,2,5), "mm"),
            panel.grid = element_blank(),
            legend.key.width = grid::unit(4, "mm"),
            legend.key.height = grid::unit(4, "mm"))
    p2 <- x %>% ggplot(aes(x = weight)) +
      scale_x_log10() +
      stat_density(aes(y =..density..), geom = "line") +
      xlab("link weight") + 
      ylab("density") +
      ggtitle(x$net_name_f[1]) +
      fer_theme +
      theme(plot.margin = grid::unit(c(2,2,0,0), "mm"))
    list(p1, p2)
  })

multiplot(p[[1]][[2]], p[[1]][[1]], p[[2]][[2]], p[[2]][[1]], p[[3]][[2]], p[[3]][[1]], layout = matrix(c(1,2,2,3,4,4,5,6,6), ncol = 3, byrow = T))  
``` 
*__Figure S`r fig_n("ballantyne_ntw")`:__ distribution of interaction weights for the pollen deposition, visitation and pollinator importance networks. Note that the _x_ axis in the density plots have been log-transformed.*

```{r, echo = FALSE, warning = F, message = F}
n_driver <- meta %>%
  dplyr::inner_join(n_matched) %>% 
  dplyr::mutate(n_driver = 1 - n_matched / (n_pla + n_pol))
```

We first investigated the effects at a network scale. Despite marked differences in the distribution of weights of the three networks (Figure S`r fig_r("ballantyne_ntw")`), the minimum number of driver species to control the whole community was consistent among the three different approaches (`r round(n_driver$n_driver[n_driver$net_name == "bal_eff"]*100)`% for deposition, `r round(n_driver$n_driver[n_driver$net_name == "bal_vis"]*100)`% for the visitation, and `r round(n_driver$n_driver[n_driver$net_name == "bal_imp"]*100)`% for the pollinator importance network).

*__Table S`r tbl_n("corr_weights")`:__ spearman correlation coefficients (with p-value) of the relative importance of species and the percentage of interactions that share the direction of dependency obtained using the three weighting schemes and an unweighted scheme. Significant correlations are highlighted in bold.*
```{r, echo = FALSE, warning = F, message = F}
drivers_b <- m_f[meta$net_name[meta$study == "ballantyne"]] %>%
	plyr::ldply(function(x){
	  dplyr::data_frame(species = names(x),
	                    d_freq = attr(x, "n_matchings") - x,
	                    d_reim = 1 - x / attr(x, "n_matchings"),
	                    d_rank = rank(d_reim, ties.method = "average"))
	}) %>%
	dplyr::rename_("net_name" = ".id")

correlations <- drivers_b %>%
  dplyr::select(net_name, species, d_freq) %>%
  tidyr::spread(net_name, d_freq) %>%
  dplyr::select(-species) %>%
  as.matrix() %>%
  Hmisc::rcorr(type = "spearman")

my_paste <- function(x, y){
  if(is.na(y)) return ("-")
  b <- ""
  if(y < 0.05) b <- "**"
  paste0(b, round(x, digits = 2), " (", round(y, digits = 4), ")", b)
}

dir_net_b <- net[meta$net_name[meta$study == "ballantyne"]] %>%
  lapply(function(x){
    x %>% 
      bipartite_digraph(type = "weight", keep = "all") %>%
      igraph::ends(igraph::E(.)) %>% 
      apply(1, function(y) paste(y[1], y[2]))
  })

# same order as the correlations
dir_net_b <- dir_net_b[colnames(correlations$P)]

lt <- combn(length(dir_net_b), 2) %>%
  apply(2, function(x){
    length(intersect(dir_net_b[[x[1]]], dir_net_b[[x[2]]])) /
      length(igraph::E(net[[1]]))
  }) %>%
  magrittr::multiply_by(100) %>% round() %>% paste0("%")

nam <- c("unweighted","deposition", "importance", "visitation")

mapply(my_paste, correlations$r, correlations$P) %>%
  matrix(ncol = length(dir_net_b)) %>% magrittr::set_colnames(nam) %>%
  magrittr::set_rownames(nam) %>% `[<-`(lower.tri(.), lt) %>% kable(align = "c")
```

The choice of weighting used can also have an impact on the realtive importance of species. Therefore we calculated the frequency that each species is present in the possible sets of driver species under the three schemes. Although visitation and deposition produce strikingly different results, we found a very strong agreement between the order produced by visitation and importance (Table S`r tbl_r("corr_weights")`). Arguably, visitation best reflects the dependency of animals to plants, as usually animals forage for pollen or nectar regardless of wether effective pollination occurs or not. Contrastingly, importance, the product between visit frequency and pollinator effectiveness, best relefect the dependency of plants to animals.

Finally, we investigated whether the asymmetry of mutual dependency, which defines the direction of control, was consistent among the three posible weighting schemes. We found again that the direction of the dominant dependency was mantained was consistent for 95% of the interactions weighted by visitation or importance (Table S`r tbl_r("corr_weights")`), the two most appropriate metrics for pollinator and plant dependency.

All together, evidence supports the idea that visitation is a suitable metric to estimate the mutual dependency of species pairs. First it is directly related to pollinator foraging. Second it produces results consistent, at least within our controllability framework, with plant reproductive success (as estimated by the importance metric).

# Supplementary References

### 2016-03-02 paper/manuscript.Rnw
change structure of the paper files

--- 2015-12-07 paper/manuscript.Rnw
@@
 \documentclass[a4paper,10pt]{article}
+\usepackage[margin=22.5mm]{geometry}
+
 % abstract + title + authors
@@
 \usepackage{float}
+\usepackage{sidecap}
+\sidecaptionvpos{figure}{t}
+\usepackage[font=small]{caption}
+\usepackage{subfig}
+\usepackage{caption}
+
+% table
+\usepackage{booktabs}
 
@@
 \usepackage[
-backend=biber,
+backend=bibtex,
 style= authoryear,
@@
 \begin{document}
-\SweaveOpts{concordance=TRUE,prefix.string=figures/fig-}
-\setkeys{Gin}{width=1\textwidth}
 
@@
 % Article title
-  \title{\fontsize{16pt}{10pt}\selectfont\textbf{Structural controlability of pollination networks}}
+  \title{{\LARGE \textsc{Structural controlability of pollination networks}}}
 
 % Authors and Affiliations
-  \author[1]{\large E. Fernando Cagua}
-  \author[1]{\large Daniel B. Stouffer}
-  \affil[1]{\normalsize Center of Integrative Ecology, School of Biological Sciences, University of Canterbury}
-
- \date{\small\usvardate\today}
+  \author{\large E. Fernando Cagua}
+  \author{\large Kate Wooton}
+  \author{\large Johanna Voinopol-Sassu}
+  \author{\large Daniel B. Stouffer}
+  \affil{\normalsize Center of Integrative Ecology, School of Biological Sciences, University of Canterbury}
+ \date{}
 
@@
 
-<<libraries and preparatory stuff, echo = FALSE>>=
+<<libraries, echo = FALSE, warning = F, message = F>>=
+library(magrittr)
+library(knitr)
 library(ggplot2)
-library(magrittr)
-
-my_theme <- theme_classic() + theme(legend.position = "none", text = element_text(family = "Times"), axis.title.x = element_text(vjust = -0.7), axis.title.y = element_text(vjust = 1.5)) 
+library(glmulti)
+opts_knit$set (root.dir=normalizePath('../'))
 @
 
-% Main Text
+<<auxiliary functions, echo = FALSE, warning = F, message = F>>=
+"./code/V2.0/functions" %>% 
+	list.files(full.names = T) %>%
+	plyr::l_ply(source)
+
+# figure counter
+fig_count <- dplyr::data_frame(ref = "NA", count = 0)
+fig_n <- function(ref) {
+  fig_count <<- rbind(fig_count,
+                      dplyr::data_frame(ref = ref,
+                                        count = dplyr::last(fig_count$count) + 1))
+  return(dplyr::last(fig_count$count))
+}
+fig_r <- function(ref) fig_count$count[fig_count$ref == ref]
+
+# table counter
+tbl_count <- dplyr::data_frame(ref = "NA", count = 0)
+tbl_n <- function(ref) {
+  tbl_count <<- rbind(tbl_count,
+                      dplyr::data_frame(ref = ref,
+                                        count = dplyr::last(tbl_count$count) + 1))
+  return(dplyr::last(tbl_count$count))
+}
+tbl_r <- function(ref) tbl_count$count[tbl_count$ref == ref]
+@
+
+<<plot theme, echo = FALSE, warning = F, message = F>>=
+fer_theme <- theme_bw() +
+	theme(text = element_text(family = "Times"),
+	      title = element_text(size = 7.5, hjust = 0),
+	      legend.title = element_text(size = 9),
+	      legend.text = element_text(size = 8),
+				axis.text = element_text(size = 8),
+				axis.title = element_text(size = 9, hjust = 0.5), 
+				strip.text = element_text(size = 9, hjust = 0), 
+				strip.background = element_blank(),
+				plot.margin = grid::unit(c(5, 0, 2, 0), "mm"))
+@
+
+<<read data and results, echo = FALSE, warning = F, message = F>>=
+net <- "./data/V2.0/networks" %>%
+	read_networks()
+meta <- readr::read_csv("data/ntw_info.csv") %>% dplyr::tbl_df() %>%
+	dplyr::rename(count = method)
+n_matched <- readRDS("./data/V2.0/n_matched.rds")
+m_f <- readRDS("./data/V2.0/matching_frequency.rds")
+r_w <- readRDS("./data/V2.0/random_weights.rds") %>% dplyr::tbl_df() %>%
+  dplyr::rename_("net_name" = ".id")
+r_d <- readRDS("./data/V2.0/random_directions.rds") %>% dplyr::tbl_df() %>%
+  dplyr::rename_("net_name" = ".id")
+s_p <- readRDS("./data/V2.0/species_properties.rds") %>% dplyr::tbl_df()
+mod <- readRDS("./data/V2.0/species_models.rds")
+@
+
 \section*{Introduction}
-
-\todo[inline]{This intro was written when I though that the paper was mainly gonna be about the relative importance of species and how invasives fit there.
-Read with caution as I don't think that's the case anymore}
 
@@
 
-Recent work on the control of complex systems suggest that in principle it is possible to alter any ecological community's composition, by modifying the abundances of just some key species.
-Here, we apply these theories to estimate the controllability of different ecological communities and to find the species, that due to the structural characteristics of their interactions are more likely to drive the dynamics of the community.
+Recent work on the control of complex systems suggest that in principle it is possible to alter any ecological community's composition, by modifying the abundances of just some key species \autocite{Isbell2013, Cornelius2013}.
+Here, we apply these theories to estimate the controllability of different ecological communities and to find driver species: species, that due to the structural characteristics of their interactions are more likely to drive the dynamics of the community.
 
-\section*{Methods \& Results}
+Invasive species have been shown to have a disproportionate effect on the structure of pollination communities.
+Influencing for example the strength of species interactions, and the degree of network nestedness and connectivity \autocite{Olesen2002, Aizen2008, Bartomeus2008, Vila2009, Traveset2013}.
+However whether this influence is translated into a driver role has not been tested.
+Here we use plant pollinator communities to investigate the number of species that should be managed to control population dynamics of the whole community, the characteristics that determine whether a species should be managed or not and how invasive species fit.
 
-Using six paired plant pollinator communities we explored the concepts of control theory. This is the initial data set things will be tested. If more data is considered necessary we'll see that later.
+\section*{Methods}
 
-\subsection*{Controllability of ecological communities}
+To investigate the dynamic controllability of pollination networks, we used ten paired plants-pollinator communities.
+Each par was composed by a community invaded by a plant and a community free of the invasive species.
+Weighted visitation networks were constructed from previously published visitation data collected from pollination communities in Bristol, Great Britain \autocite{Lopezaraiza-Mikel2007} and the National Cap de Creus in Northeastern Spain \autocite{Bartomeus2008}.
+The four British uninvaded communities the non-invaded plots were obtained by experimentally removing the invasive species \textit{Impatients grandulifera}.
+Contrastingly, Spanish uninvaded communities were obtained from plots that were not been colonised by the invasive species \textit{Carpobrotus affine acinaciformis} or \textit{Opuntia stricta}.
+In each of the networks we calculated the minimum number of driver species---species that need to be managed in order to gain full control of the community.
 
-\subsubsection*{Minimum set of species }
+We first assigned a direction to each link between plants and pollinators given by the direction of dependency.
+For each link between a plant and its pollinator we quantified the level of dependency of the plant on the pollinator and vice versa \autocite{Bascompte2006}.
+The link points to the plant if the its dependency on the pollinator is larger than the pollinator's dependency on the plant.
+The dependency of plant $i$ on pollinator $j$ is the ratio between the visits coming from pollinator $j$ and all pollinator visits to plant $i$.
+The dependency of pollinator $j$ on plant $i$ is the ratio of the visits by pollinator $j$ to plant $i$ and all visits of pollinator $j$.
 
-Using maximum matching to control all species in the network.
-We found that depending on the scheme around of the species are needed to have a grasp at the whole community (\autoref{fig:n_species}).
-However, the relative ranking of networks remains relatively unchanged across schemes.
-So rather than focusing on the differences across schemes perhaps it would be interesting to see what characteristics make a network to require more or less driver nodes to be completely controled.
-Alternatively it would be interesting to see if there are systemic differences between different types of networks.
-An initial step would be to stay with bipartite networks of the mutualistic type (plant/frugivores) or the the consumer-resource type (host/paraiste or predator/prey).
-Perhaps some model networks of varying parameters?
+In a directed network, a matching is a subset of links in which no two links share a common starting species or a common ending species.
+A species is matched if it is an ending node of an link in the matching.
+Otherwise, it is unmatched.
+It has been shown that the number of driver species can be calculated by counting the number of unmatched nodes in the directed graph representation of the pollination network \autocite{Liu2011}.
+We then found a maximum in the an alternative bipartite representation of the pollination network \autocite{Csardi2006}.
+
+We calculated dependencies based on visitation frequency, which has been shown to be an appropriate surrogate of the inter-specific effects \autocite{Bascompte2006, Vazquez2005}.
+However, because the degree distribution, and ultimately the number of driver species, can be affected by the sampling method \autocite{Bluthgen2010} we compared the number of driver species in a pollination community in which both visitation frequency and effectiveness were measured \autocite{Ballantyne2015}.
+
+To quantify to what extent the number of driver species is characteristic of the structure of pollination networks we compared them a suit of random null-models.
+A set of null models were based on network randomisations that maintained the degree of plants, pollinators, and both plants and pollinators.
+To analyse the effects of the chosen directionality, we devised a null model in which we randomised the visitation patterns and re-calculated the new dependencies.
+In all cases we computed 999 randomisations.
+
+We quantified the relative importance of each species for network dynamics.
+To do this, we counted the number of times a particular species was a driver species across all possible maximum matchings in the pollination network.
+The number of maximum matchings were found by generating the line graph of the alternative bipartite network representation, and then enumerating the maximal cliques in the complement of the line graph \autocite{Csardi2006}.
+
+Finally, we tackled the question whether some structural properties can predict the relative importance of driver species.
+Here, we regressed the importance of each species against measures of centrality (degree, betweenness), measures related to network robustness (contribution to nestedness) and measures of strength of association (visitation levels).
+
+\section*{Results}
+
+<<n_driver, echo = FALSE, warning = F, message = F>>=
+# find n_driver
+n_driver <- n_matched %>%
+  dplyr::inner_join(meta) %>%
+  dplyr::filter(!is.na(inv)) %>%
+  dplyr::mutate(n_dr = n_pla + n_pol - n_matched,
+                n_dr_p = 1 - n_matched / (n_pla + n_pol))
+
+# Wilcoxon signed rank test
+wt <- n_driver %>%
+  dplyr::select(site, inv, n_dr_p) %>%
+  dplyr::mutate(n_dr_p = qlogis(n_dr_p)) %>%
+  tidyr::spread(inv, n_dr_p) %>%
+  dplyr::select(-site) %>%
+  as.matrix() %>% {
+      wilcox.test(x = `[`(.,1), y = `[`(.,2), paired = T)
+  }
+@
+
+We found that if we were to control the dynamics of the whole community, we would need to control between \Sexpr{round(min(n_driver$n_dr_p)*100)} and \Sexpr{round(max(n_driver$n_dr_p)*100)}\% (mean \Sexpr{round(min(n_driver$n_dr_p)*100)}\%) of the species in the community.
+The relative number of driver species did not change if the dependencies were assumed to be bidirectional, from plant to pollinators or from pollinators to plants (Supp.
+Information).
+However, the proportion of driver species did was not significantly different between invaded and uninvaded ecosystems (Wilcoxon signed-rank sum test, $p = \Sexpr{wt$p.value}$).
+
+We examined the role that the asimmetry of the dependencies which defines the direction of control has a central role in structuring the controlability of polination networks.
+We found that empirical networks have a much larger  the importance of dependency
 
@@
 \centering
-<<fig = T, echo = F, width = 6, height = 3>>=
-n_driver <- read.csv("../data/n_driver_species.dat")
+<<fig randomisations, echo = FALSE, warning = F, message = F, fig.height=2.2, fig.width=3.1>>=
+r <- r_w %>%
+  dplyr::bind_rows(r_d) %>%
+  dplyr::inner_join(meta) %>%
+  dplyr::filter(!is.na(inv)) %>%
+  dplyr::mutate(n_dr = n_pla + n_pol - n_matched)
 
-ggplot(n_driver, aes(x = type, y = n_driver/n_species)) +
-	geom_violin(colour = "grey") +
-	geom_line(aes(colour = as.factor(net),group = as.factor(net))) +
-	geom_point(aes(fill = as.factor(net)), shape = 21) +
-	xlab("link structure scheme") + ylab("proportion of driver species") +
-	my_theme
+# non-parametric
+# z_scores <- r$method %>%
+#   unique() %>%
+#   plyr::ldply(function(x){
+#     n_driver %>%
+#       dplyr::mutate(method = x)
+#   }) %>%
+#   dplyr::bind_rows(r) %>%
+#   dplyr::group_by(net_name, method) %>%
+#   dplyr::mutate(z_r = rank(n_dr, na.last = NA, ties.method = "average"),
+#                 z_s = qlogis(z_r/n()),
+#                 z_s = replace(z_s, is.infinite(z_s) & z_s > 0, qlogis(0.9999)),
+#                 z_s = replace(z_s, is.infinite(z_s) & z_s < 0, qlogis(0.0001))) %>%
+#   dplyr::filter(is.na(sim))
+
+z_scores <- r %>%
+  dplyr::group_by(net_name, method) %>%
+  dplyr::summarise(mu = mean(n_dr, na.rm = T),
+                   sigma = sd(n_dr, na.rm = T)) %>%
+  dplyr::inner_join(n_driver) %>%
+  dplyr::group_by() %>%
+  dplyr::mutate(z_s = (n_dr - mu)/sigma)
+
+z_scores %<>%
+  plyr::ddply("method", function(x){
+    x %>%
+      dplyr::mutate(sign = t.test(z_s)$p.value)
+  }) %>% 
+  dplyr::group_by(method) %>%
+  dplyr::mutate(m_z = median(z_s)) %>%
+  dplyr::group_by() %>%
+  dplyr::arrange(m_z)  %>%
+  dplyr::filter(method %in% c("swsh_both", 
+                              "quasiswap_count", 
+                              # "r00_both", 
+                              # "r0_both", 
+                              # "c0_both", 
+                              "r0"))
+
+z_scores_method_order <- unique(z_scores$method)
+
+z_scores %>%
+  dplyr::mutate(method = factor(method, levels = z_scores_method_order),
+                m_n = as.numeric(method),
+                m_n = replace(m_n, m_n == 3, 3.5)) %>%
+  ggplot(aes(x = m_n, y = z_s)) +
+  # geom_hline(yintercept = c(-0), linetype = 2, alpha = 0.7, size = 0.25) + 
+  geom_vline(xintercept = c(2.75), alpha = 0.7, size = 0.25) +
+  geom_hline(yintercept = 0, size = 0.25, linetype = 2, colour = "grey30") +
+  geom_boxplot(aes(group = method), size = 0.25, colour = "grey10",
+							 outlier.shape = 21, outlier.size = 1) +
+  geom_point(aes(y = 12, colour = sign <= 0.05), shape = 8, size = 1) +
+  coord_flip() +
+  scale_colour_manual(values = c(NA, "black")) +
+  scale_x_continuous(breaks = c(1, 2, 3.5), labels = rev(c("dependency", "strength", "degree"))) + 
+  xlab("") +
+  ylab("number of driver species (z-score)") + 
+  fer_theme +
+  theme(axis.text.x = element_text(angle = 90), 
+        legend.position = "none",
+				plot.margin = grid::unit(c(2, 1, 2, 0), "mm"), 
+				# panel.grid.minor.x = element_blank(),
+				panel.grid.minor.y = element_blank())
+
 @
-\caption{
-\label{fig:n_species} 
-Proportion of species that needs to be controled for all twelve networks under different link assumptions.
-AB indicates that the links go from plants to pollinators; BA that the links go from pollinator to plants; ``weight'' that the direction of control is chosen by dependency (ties are resolved by giving priority to plants in weight.A and to pollinators in weight.B); z-bi indicates that the links go in both directions}
+\caption{\label{fig:randomisations} The (\textasteriskcentered indicates a significant difference)}
 \end{figure}
 
-There was no significant difference between the number of species needed to control the system in an invaded and an uninvaded ecosystem.
+<<importance, echo = FALSE, warning = F, message = F>>=
+imp <- mod %>% 
+  lapply(function(x){
+    coef.glmulti(x, select = 0.95) %>%
+      as.data.frame() %>%
+      dplyr::add_rownames("factor") %>%
+      dplyr::arrange(-Importance, factor)
+  })
 
-When comparing the number of control nodes of the observed networks to their random counterparts an interesting pattern emegerges (\autoref{fig:random_n_species}).
-The number of control nodes is significantly larger than randomisations that mantain the degree distribution of the plants.
-However there is no significant difference when the randomisations mantain the degree of pollinators (or both plants and pollinators).
-This pattern is consistent across all schemes of link directionality.
-This suggest that the patterns of pollinator visitations are the structural characteristic that determines the controlability of the network.
-We probably should analyse other pollination networks to see if this pattern hold.
-We also should think about the implications of this finding.
+print_table <- . %>%
+  dplyr::mutate(factor = paste0("$", factor, "$")) %>%
+  magrittr::set_names(c("factor", "est.", "var", "No. mod.", "imp.", "C.I.")) %>% 
+  dplyr::select(-var) %>%
+  kable(format = "latex", align = "c", booktabs = T, digits = 2, escape = F, linesep = "") 
+@
+
+\begin{table}
+\centering
+\small
+\subfloat[pollinators]{
+<<table importance 1, echo = FALSE, warning = F, message = F, results = "asis">>=
+print_table(imp[[1]])
+@
+}
+\subfloat[plants]{
+<<table importance 2, echo = FALSE, warning = F, message = F, results = "asis">>=
+print_table(imp[[2]])
+@
+}
+\caption{\label{table:sd} Minimum number and proportion of driver species necessary to control the full pollination network}
+\end{table}
 
@@
 \centering
-<<fig = T, echo = F, width = 6, height = 3.5>>=
-random_n <- read.csv("../data/random_n_driver.csv")
-n_control <- n_driver %>%
-	dplyr::select(-keep) %>%
-	tidyr::separate(type, c("type", "keep"), "\\.", remove = T)
+<<fig species, echo = FALSE, warning = F, message = F, fig.height=2.2, fig.width=3.1>>=
+data_pol <- mod[[1]]@objects[[1]]$data
+data_pla <- mod[[2]]@objects[[1]]$data
 
-random_n_z <- random_n %>% 
-	dplyr::group_by(net, type, keep, method) %>%
-	dplyr::summarise(n_driver_u = mean(n_driver, na.rm = T),
-									 n_driver_sd = sd(n_driver, na.rm = T)) %>%
-	dplyr::full_join(n_control) %>% 
-	dplyr::group_by() %>%
-	dplyr::mutate(n_driver_z_score = (n_driver - n_driver_u)/n_driver_sd)
-
-random_n_z %>% 
-	ggplot(aes(x  = as.character(interaction(type, keep)), y = n_driver_z_score)) +
-	geom_rect(ymin = -2, ymax = 2, xmin = -1, xmax = 10, fill = "grey90") +
-	geom_hline(yintercept = 0, size = 0.4) +
-	geom_vline(xintercept = seq(1.5, 5.5), linetype = 2) +
-	geom_boxplot(aes(fill = method)) +
-	scale_fill_discrete(name = "randomisations\nmantain\ndegree of", labels= c("plants", "pollinators", "both")) + 
-	my_theme + 
-	xlab("link structure scheme") +
-	ylab("standard score") +
-	theme(legend.position = "right",
-				axis.line.x = element_blank(), axis.ticks.x = element_blank())
+expand.grid(d = seq(min(data_pla$d), max(data_pla$d), by = 1),
+            S_d = seq(min(data_pla$S_d), max(data_pla$S_d), length = 20), 
+            n = mean(data_pla$n, na.rm = T), 
+            S_v = mean(data_pla$S_v)) %>%
+  dplyr::mutate(q = predict.glmulti(mod[[2]], 
+                                    select = 0.95, 
+                                    newdata = .)$averages %>%
+                  as.vector(), 
+                p = plogis(q)) %>%
+  ggplot(aes(x = d, y = S_d, z = p)) +
+  geom_tile(aes(alpha = p), fill = "#0e324b") +
+  # scale_fill_gradient(name = "relative\nimportance", high = "#f0f0f0", low = "#525252") +
+  scale_x_continuous(expand = c(0,0)) +
+  scale_y_continuous(expand = c(0,0)) +
+  xlab("degree") +
+  ylab("strength of dependencies") +
+  stat_contour(colour = "black", size = 0.75) +
+  fer_theme + theme(panel.grid = element_blank())
 @
-\caption{
-\label{fig:random_n_species} 
-Difference between the number of control nodes in the analysed networks versus randomisations of the same networks.
-Unshaded areas suggest a significant difference.
-Schemes same as in \autoref{fig:n_species}}
+\caption{\label{fig:prediction} aSS }
 \end{figure}
 
-It occured to me that it is possible that the patterns (and perhaps others observed like more phylogenetic signal in polinators than in plants) are a consequence of a greater diversity of pollinators in the interaction networks.
-More pollinators relative to plants imply that randomisations that mantain the degree distribution of pollinators are more constrained than those that only mantain the degree distribution of plants.
-It also means that statistical tests on that group have a more observations and therefore rendering significant results for smaller effect sizes.
-I cheked that with the 12 pollination networks of the study and there seems to be some evidence for that (\autoref{fig:zscore_ratio}).
-Perhaps it would be good to check with other networks to see if it holds.
-
-\begin{figure}[h]
-\centering
-<<fig = T, echo = F, width = 6, height = 3.5>>=
-net_info <- read.csv("../data/ntw_info.csv")
-
-net_info %<>%
-	dplyr::mutate(ratio_pol_pla = n_pol/n_pla)
-
-random_n_z %>%
-	dplyr::full_join(net_info) %>%
-	dplyr::mutate(t = as.character(interaction(type, keep))) %>% 
-	dplyr::filter(method == "c0", t != "BA.B") %>%
-	ggplot(aes(x = ratio_pol_pla, y = n_driver_z_score)) +
-	geom_point() +
-	geom_smooth(method = "lm", alpha = 0.1, colour = "grey10") +
-	xlab("ratio of number of pollinators to plants") +
-	ylab("standard score") +
-	my_theme + 
-	facet_wrap(~t, scales = "free") + 
-	theme(strip.background = element_blank())
-@
-\caption{
-\label{fig:zscore_ratio} 
-When considering only randomisations that mantain the degree distribution of plants, there seems to be a possitive relationship between the ratio of pollinators to plants and the Z-score of randomisations.
-The pattern is, however, not significant for the weighted schemes.
-The z-scores are identical for the AB.A and the BA.B schemes.
-Schemes same as in \autoref{fig:n_species}}
-\end{figure}
-
-\subsubsection*{Profiles of critical and redundant species}
-
-Dividing the nodes and links among critical, ordinary and redundant we can have an idea of ``control profiles'' of the networks.
-Both species and interactions can be classified as redundant, ordinary and critical depending on the number of species that need to be controled to gain full control over the network once the species has been removed (\autoref{fig:s_crit_prop} and \ref{fig:i_crit_prop}).
-
-\begin{figure}[tp]
-\centering
-<<fig = T, echo = F, width = 6, height = 2.5>>=
-folder <- "../data/redundancy/node/"
-node_redundancy <- list.files(folder, full.names = TRUE) %>%
-    plyr::ldply(function(x, name){
-        y <- read.csv(x) 
-        info <- basename(x) %>% 
-            stringr::str_sub(end = -5) %>% 
-            stringr::str_split("_") %>% 
-            unlist()
-        y %>%
-            dplyr::mutate(net = info[[1]],
-                                        type = info[2],
-                                        keep = info[3])
-    })
-
-nr_sum <- node_redundancy %>%
-	dplyr::mutate(type = interaction(type, keep)) %>%
-	dplyr::group_by(net, type, robustness) %>%
-	dplyr::summarise(freq = n()) %>%
-	dplyr::group_by(net, type) %>%
-	dplyr::mutate(n_species = sum (freq)) %>%
-	dplyr::group_by() %>%
-	dplyr::mutate(prop = freq / n_species, 
-								type = as.character(type), 
-								robustness = as.character(robustness))
-
-ggplot(nr_sum) +
-	geom_boxplot(aes(x = type, y = prop, fill = robustness)) +
-	geom_vline(xintercept = seq(1.5, 5.5), linetype = 2) +
-	xlab("link structure scheme") +
-	ylab("species proportion") +
-	scale_fill_discrete(name = "nodes") +
-	my_theme + 
-	theme(legend.position = "right", 
-				axis.line.x = element_blank(), 
-				axis.ticks.x = element_blank())
-@
-\caption{\label{fig:s_crit_prop} Proportion of species that are ordinary (when removed the number of species needed to control the network doesn't change), redundant (when removed less species are needed) and critical (when removed the number of species needed to control the network increasses).
-Schemes same as in \autoref{fig:n_species}}
-\end{figure}
-
-\begin{figure}[tp]
-\centering
-<<fig = T, echo = F, width = 6, height = 2.5>>=
-folder <- "../data/redundancy/edge/"
-link_redundancy <- list.files(folder, full.names = TRUE) %>%
-    plyr::ldply(function(x, name){
-        y <- read.csv(x) 
-        info <- basename(x) %>% 
-            stringr::str_sub(end = -5) %>% 
-            stringr::str_split("_") %>% 
-            unlist()
-        y %>%
-            dplyr::mutate(net = info[[1]],
-                                        type = info[2],
-                                        keep = info[3])
-    })
-
-lr_sum <- link_redundancy %>%
-	dplyr::mutate(type = interaction(type, keep)) %>%
-	dplyr::group_by(net, type, robustness) %>%
-	dplyr::summarise(freq = n()) %>%
-	dplyr::group_by(net, type) %>%
-	dplyr::mutate(n_species = sum (freq)) %>%
-	dplyr::group_by() %>%
-	dplyr::mutate(prop = freq / n_species, 
-								type = as.character(type), 
-								robustness = as.character(robustness))
-
-ggplot(lr_sum) +
-	geom_boxplot(aes(x = type, y = prop, fill = robustness)) +
-	geom_vline(xintercept = seq(1.5, 5.5), linetype = 2) +
-	scale_fill_discrete(name = "links") +
-	xlab("link structure scheme") +
-	ylab("interactions proportion") +
-	my_theme + theme(legend.position = "right")
-@
-\caption{\label{fig:i_crit_prop} Proportion of interactions that are ordinary (when removed the number of species needed to control is reduced), redundant (when removed the number of species needed to control doesn't change) and critical (when removed the number of species needed to control the network increasses).
-Schemes same as in \autoref{fig:n_species}}
-\end{figure}
-
-On the species redundancy profile (\autoref{fig:s_crit_prop}), the profiles are also highly dependent on the chosen directionality scheme.
-For instance, in the case in which species have links in both directions there are not ordinary species and the number of critical species is relatively high, this is not surprising because under this scheme, there is a much smaller set of species that needs to be controled and therefore removing one of these can increase the minimum set of species needed to control the network.
-
-However, there appears to be a relatively small variability between networks analysed using this approach.
-Again, as in the previous section, I think there is little that can be understood by using just this data-set.
-Again I think it would be most interesting to see if there are systemic differences between different types of networks where a larger variation in the profiles is expected.
-
-On the interaction redundancy profile (\autoref{fig:i_crit_prop}) things seem a bit more interesting because the variation across networks and across link directionality schemes is pretty small.
-For instance for the bidirectional scheme, although the total number of links is doubled, the relative proportion of links that are critical and redundant is mantained.
-
-\subsubsection*{Profiles of internal/external dilation}
-
-\textcite{Ruths2014} proposed another clever way to characterise the control profile of a network by charactering the number of nodes that need to be controled among the ``mechanism'' that originates it.
-Similar as the maximum matching algorith, the idea comes from the concept that in the absense of cycles one node can at most control another one.
-Then the origin of control nodes can be splitted between nodes that need to be controled because they are a ``source node'' those that have only out links, control nodes associated to ``external dilations'' and those associated to ``internal dilations''.
-
-It could be interesting to compare different networks using this framework.
-They argue that source dominated networks should be relatively easy to control in a top-down fashion.
-On the other hand internal dilation dominated networks represent the signature of a network that self-regulates and is not meant to be controled in that it's not designed to visit every possible state.
-
-However as we can see here this framework is pretty useless when the direction of control is not perfectly known (as in most real wolrd networks really...).
-For instance when applying it to the data-set (\autoref{fig:dilation}), we see that when the control flows from pollinators to plants (AB.A) the network is source dominated simply because the pollinator diversity is greater than the plant's.
-When we asume that each guild can control each other (z-bi.all) the networks are internal dilation dominated because it's purely composed of cycles.
-However the weighted version might offer a meaningful possibility to develop the analysis.
-
-\begin{figure}
-\centering
-<<fig = T, echo = F, width = 6, height = 3>>=
-library(ggtern)
-dilation <- read.csv(file = "../data/dilation_profiles.dat")
-
-ggplot(dilation, aes(x = eta_s, z = eta_e, y = eta_i)) +
-	geom_point(aes(fill = type.keep), shape = 21, size = 5, alpha = 0.7) +
-	coord_tern() + theme_classic() + theme(text =  element_text(family = "Times"))
-
-detach("package:ggtern", unload = TRUE, character.only = TRUE)
-detach("package:ggplot2", unload = TRUE, character.only = TRUE)
-library(ggplot2)
-@
-\caption{\label{fig:dilation} Control profiles of pollination networks.
-Control nodes are split among nodes that need to be controled because they are a source node, some that are control nodes because they respond to internal dilations (cycles) and some that are control nodes because they repsond to external dilations (sink nodes not matched)}
-\end{figure}
-
-\subsection*{Ranking species}
-
-\subsubsection*{By frequency in control sets}
-
-There are multiple sets of species with which is structurally possible to control network dynamics.
-An initial posibility os to relate the importance of a species for network dynamics to the frequency at which a species is present in the control sets.
-
-Turns out unsurprisingly that the importance of particular species and its distribution over a networks dependends on the scheme chosen for the directionality of the links (\autoref{fig:n_control_dist}).
-When pollinators control plants (AB) no plant must be controled and most pollinators have an importance close to one. 
-On the other hand when plants control pollinators (BA) presumably because the pollinator diversity is larger than the plant diversity, the pattern is less "bimodal" and intermediate levels of importance are allowed.
-
-\begin{figure}
-\centering
-<<echo = F, cache = T>>=
-folder <- "../data/maximum_matchings_summary/" 
-files <- list.files(folder)
-node_mm <- plyr::adply(files, 1, function(x){
-	read.csv(file.path(folder, x)) %>%
-		dplyr::mutate(net = unlist(stringr::str_split(x, "_"))[1],
-									type = unlist(stringr::str_split(x, "_"))[2], 
-									keep = unlist(stringr::str_split(x, "_"))[3],
-									batch = unlist(stringr::str_split(x, "_"))[4])
-}) %>%
-	dplyr::select(-X1) %>%
-	dplyr::group_by(net, type, keep, node) %>%
-	dplyr::summarise(freq = sum(freq))
-@
-
-<<fig = T, echo = F, width = 6, height = 4>>=
-ranked_mm <- node_mm %>%
-	dplyr::filter(!is.na(freq)) %>%
-	dplyr::group_by(net, type, keep) %>%
-	dplyr::mutate(r = rank(freq, ties.method = "random"),
-								f_f = freq/max(freq), 
-								type.keep = as.character(interaction(type, keep)))  %>%
-	dplyr::rename(net_name = net)
-
-invasive_sp <- data.frame(node = c("p_4", "p_25"), invs.species = TRUE)
-
-ranked_with_inv <- 
-	ranked_mm %>% 
-	dplyr::group_by() %>%
-	dplyr::full_join(invasive_sp) %>% 
-	dplyr::full_join(net_info)
-
-ggplot(ranked_with_inv, aes(x = f_f, fill = net_name)) +
-	geom_density(alpha = 0.025, adjust = 1, colour = "grey20") +
-	geom_point(data = ranked_with_inv %>%
-						 	dplyr::filter(invs.species), aes(y = scale(net) + 2),
-						 shape = 21, fill = "grey") +
-	facet_wrap(~type, ncol = 2) +
-	my_theme +	
-	xlab("species frequency in control sets") +
-	theme(strip.background = element_blank(),
-				axis.text.x = element_text(angle = 90))
-@
-\caption{\label{fig:n_control_dist} Distribution of the relative frequency a species is present in the set of control species among the networks.
-The frequency of invasive species in each of the six invaded networks is denoted with a circle.
-Results for the bidirectional liks (z-bi) were obatined only for the nine smallest networks, which included 3 invaded ecosystems}
-\end{figure}
-
-Among the weighted versions there was little difference if dependency ties were resolved for plants of for pollinators (\autoref{fig:n_control_dist_ntw}), again there are more species with intermediate levels of importance.
-Even more spread out are things when we consider bidirectional links.
-I imagine that this pattern is partly because there are many many more ways to control the network in the bidirectional scheme than in the others.
-
-In both AB and BA the relative importance of different species is almost fully constrained by the scheme.
-In the weighted scheme, invasive species are in all cases among the most important ones.
-Interestingly the pattern is opposite for when the direction can go both ways.
-It would be good to see then whether these patterns are a reflection of the fact that invasive species are actually dominant or an artifact arising from the fact that all invasive species are plants and that all networks are dominated by pollinators.
-An initial inspection on the distributrion of plants and pollinators per network for these schemes suggest that that might be the case for the bidirectional scheme but not for the weighted one (\autoref{fig:n_control_dist_guild} and \ref{fig:n_control_dist_per_net}).
-
-\begin{figure}
-\centering
-<<fig = T, echo = F, width = 6, height = 4>>=
-ranked_with_inv %>%
-	tidyr::separate(node, into = c("categ", "number"), sep = "_", remove = F) %>%
-	ggplot(aes(x = f_f)) + 
-	geom_density(aes(fill = categ), 
-							 alpha = 0.5, adjust = 0.5, colour = "grey20") +
-	geom_point(data = ranked_with_inv %>%
-						 	dplyr::filter(invs.species), aes(y = scale(net) + 2), 
-						 shape = 21, fill = "red") +
-	facet_wrap(~type, ncol = 2) +
-	scale_fill_grey(name = "", labels = c("pollinators", "plants")) +
-	my_theme +	
-	xlab("species frequency in control sets") +
-	theme(strip.background = element_blank(),
-				axis.text.x = element_text(angle = 90), legend.position = "right")
-@
-\caption{\label{fig:n_control_dist_guild} Distribution of the relative frequency a species is present in the set of control species by guild.}
-\end{figure}
-
-We explored that option by
-
-<<>>=
-ranked_with_inv  %>%
-	tidyr::separate(node, into = c("categ", "number"), sep = "_", remove = F) %>%
-	dplyr::group_by(net, type.keep, categ) %>%
-	dplyr::summarise(f_f = median(f_f), 
-									 ratio_pol_pla = mean(ratio_pol_pla)) %>%
-	dplyr::group_by(net, type.keep) %>%
-	dplyr::mutate(f_sum = f_f - lead(f_f)) %>%
-	ggplot(aes(x = ratio_pol_pla, y = f_sum)) +
-	geom_point() +
-	geom_smooth(method = "lm")+ 
-	facet_wrap(~type.keep)
-@
-
-\subsubsection*{By redundancy}
-
-\subsubsection*{Strongly interacting species (interaction heterogeneity)}
-
-\section*{Discussion}
-
-For instance, restoration projects that aim to drive an invasive species out of the community, to reestablish a particular ecosystem service or in general modify the ecosystem state have had a limited amount of success.
-We argue that quantifying the relative dynamic importance of species the set of key species is the first step to evaluate current management efforts as well as to design targeted and informed
-
-Dynamic system approach
-
-\section*{Acknowledgmenets}
-
-The authors thank Dr.
-Takeuki Uno for the insight provided to find the set of all maximum matching algorithms.
-EFC acknowledges the support from the University of Canterbury Doctoral Scholarship, the University of Canterbury Meadow Mushroooms Postgraduate Scholarship, a travel grant from the European Space Agency and a Rutherford Discovery Fellowship (to DBS).
-DBS ackloledges the support of a Rutherford Discovery Scholarship, administered by the Royal Society of New Zealand.
-
-% \bibliography{references}
 \printbibliography
 
-\newpage
-\section*{Supplementary Information}
-\makeatletter 
-\renewcommand{\thefigure}{S\@arabic\c@figure}
-\makeatother
-\setcounter{figure}{0}
-
-\begin{figure}[h!]
-\centering
-<<fig = T, echo = F, width = 6, height = 4>>=
-ggplot(ranked_mm, aes(x = net_name, y = f_f, fill = type.keep)) +
-	geom_boxplot()+
-# 	geom_jitter(shape = 21, 
-# 							position = position_jitter(height = 0), 
-# 							alpha = 0.2, size = 1) +
-	facet_wrap(~type) +
-	my_theme +	
-	theme(strip.background = element_blank(),
-				axis.text.x = element_text(angle = 90))
-@
-\caption{\label{fig:n_control_dist_ntw} Distribution of the relative frequency a species is present in the set of control species among by network}
-\end{figure}
-
-\begin{figure}[h!]
-\centering
-<<fig = T, echo = F, width = 6, height = 9.5>>=
-bb <- ranked_with_inv %>%
-	tidyr::separate(node, into = c("categ", "number"), sep = "_", remove = F) %>%
-	dplyr::filter(type == "weight" | type == "z-bi")
-
-bb %>%
-	ggplot(aes(x = f_f)) + 
-	geom_density(aes(fill = categ), 
-							 alpha = 0.5, adjust = 0.5, colour = "grey20") +
-	geom_point(data = bb %>%
-						 	dplyr::filter(invs.species), aes(y = scale(net) + 2), 
-						 shape = 21, fill = "red") +
-	facet_grid(net_name ~ type.keep, scales = "free_y") +
-	scale_fill_grey(name = "", labels = c("pollinators", "plants")) +
-	my_theme +	
-	xlab("species frequency in control sets") +
-	theme(strip.background = element_blank(),
-				axis.text.x = element_text(angle = 90), legend.position = "top")
-@
-\caption{\label{fig:n_control_dist_per_net} Distribution of the relative frequency a species is present in the set of control species among by network partitioned by plant or pollinators.
-Invasive species is depicted with a red dot.}
-\end{figure}
 \end{document}

### 2016-03-02 paper/supp_info.Rnw
change structure of the paper files

\documentclass[a4paper,10pt]{article}
\usepackage[margin=22.5mm]{geometry}
\usepackage{titlesec}

% abstract + title + authors
\usepackage{abstract}
\renewcommand{\abstractnamefont}{\normalfont\bfseries}
\renewcommand{\abstracttextfont}{\normalfont\small\itshape} 
\usepackage{titlesec}
\usepackage{authblk}
\usepackage{datetime}
\newdateformat{usvardate}{
\monthname[\THEMONTH] \ordinal{DAY}, \THEYEAR}

% math
\usepackage{amssymb}
\usepackage{newtxmath}

% manuscript looking document
\usepackage{setspace}
\usepackage{lineno,xcolor}
\setlength{\parskip}{0.5em}

% comments
\usepackage[draft]{todonotes}

% colorbox
\usepackage{tcolorbox}

% graphics
\usepackage{graphicx}
\usepackage{float}
\usepackage{sidecap}
\sidecaptionvpos{figure}{t}
\usepackage[font=small]{caption}

% table
\usepackage{booktabs}

% references & links
\usepackage[
backend=bibtex,
style= authoryear,
citestyle = authoryear,
url=false,
doi=true,
isbn=false
]{biblatex}
\addbibresource{references.bib}
\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    citecolor=magenta,
    linkcolor=magenta
}
\usepackage{doi}

\begin{document}

<<libraries, echo = FALSE, warning = F, message = F>>=
library(magrittr)
library(knitr)
library(ggplot2)
library(glmulti)
opts_knit$set (root.dir=normalizePath('../'))
@

<<auxiliary functions, echo = FALSE, warning = F, message = F>>=
"./code/V2.0/functions" %>% 
	list.files(full.names = T) %>%
	plyr::l_ply(source)

# figure counter
fig_count <- dplyr::data_frame(ref = "NA", count = 0)
fig_n <- function(ref) {
  fig_count <<- rbind(fig_count,
                      dplyr::data_frame(ref = ref,
                                        count = dplyr::last(fig_count$count) + 1))
  return(dplyr::last(fig_count$count))
}
fig_r <- function(ref) fig_count$count[fig_count$ref == ref]

# table counter
tbl_count <- dplyr::data_frame(ref = "NA", count = 0)
tbl_n <- function(ref) {
  tbl_count <<- rbind(tbl_count,
                      dplyr::data_frame(ref = ref,
                                        count = dplyr::last(tbl_count$count) + 1))
  return(dplyr::last(tbl_count$count))
}
tbl_r <- function(ref) tbl_count$count[tbl_count$ref == ref]
@

<<plot theme, echo = FALSE, warning = F, message = F>>=
fer_theme <- theme_bw() +
	theme(text = element_text(family = "Times"),
	      title = element_text(size = 7.5, hjust = 0),
	      legend.title = element_text(size = 9),
	      legend.text = element_text(size = 8),
				axis.text = element_text(size = 8),
				axis.title = element_text(size = 9, hjust = 0.5), 
				strip.text = element_text(size = 9, hjust = 0), 
				strip.background = element_blank(),
				plot.margin = grid::unit(c(5, 0, 2, 0), "mm"))
@

<<read data and results, echo = FALSE, warning = F, message = F>>=
net <- "./data/V2.0/networks" %>%
	read_networks()
meta <- readr::read_csv("data/ntw_info.csv") %>% dplyr::tbl_df() %>%
	dplyr::rename(count = method)
n_matched <- readRDS("./data/V2.0/n_matched.rds")
m_f <- readRDS("./data/V2.0/matching_frequency.rds")
a_m <- readRDS("./data/V2.0/n_matched_all_types.rds")
s_p <- readRDS("./data/V2.0/species_properties.rds") %>% dplyr::tbl_df()
mod <- readRDS("./data/V2.0/species_models.rds")

@

% title
\title{
	{\LARGE \textsc{Structural controlability of pollination networks}}\\
	{\normalsize Supplementary Information} }
	% Authors and Affiliations
  \author{\large E. Fernando Cagua}
  \author{\large Kate Wooton}
  \author{\large Johanna Voinopol-Sassu}
  \author{\large Daniel B. Stouffer}
  \affil{\normalsize Center of Integrative Ecology, School of Biological Sciences, University of Canterbury}
\date{}
\maketitle

\renewcommand{\thefigure}{S\arabic{figure}}
\renewcommand{\thetable}{S\arabic{table}}

\onehalfspacing

\section{Number of driver species}

We calculated the number of driver species neccessary to control the whole community under the assumption that a species that depends more strongly on an interaction partner is controlled by the partner (\autoref{table:n_driver}). We tested the robustness of this assumption by comparing the relative number of driver species assuming that a) the dependency assymetry does not imply an unidirectional control direction, rather a species could control all its interaction partners and viceversa, b) that plants depend on pollinators and c) that pollinators depend on plants. Our results using the direction of the largest dependency are consistent with the proposed alternatives: although we obtained different absolute numbers of driver species (\autoref{fig:alternative_assumptions}),  their relative numbers are maintained (\autoref{table:corr_driver}).

\begin{table}[h]
\centering
\small
<<table n_driver, echo = FALSE, warning = F, message = F, results = "asis">>=
# find n_driver
n_driver <- n_matched %>%
  dplyr::inner_join(meta) %>%
  dplyr::filter(!is.na(inv)) %>%
  dplyr::mutate(n_dr = n_pla + n_pol - n_matched,
                n_dr_p = 1 - n_matched / (n_pla + n_pol))

n_driver %>%
  dplyr::select(site, inv, n_pla, n_pol, n_dr, n_dr_p) %>%
  dplyr::mutate(site = as.numeric(as.factor(site)),
                inv = plyr::mapvalues(inv, c(TRUE, FALSE), c("yes", "no")),
                n_dr_p = paste0(round(n_dr_p * 100), "%")) %>%
  dplyr::rename_("invaded" = "inv",
                 "No. plants" = "n_pla",
                 "No. polinators" = "n_pol",
                 "No. driver spp." = "n_dr",
                 "prop. driver spp." = "n_dr_p") %>%
  dplyr::arrange(site) %>%
  kable(align = "c", booktabs = T, 
        linesep = c("", "\\addlinespace"))
@
\caption{\label{table:n_driver} Minimum number and proportion of driver species necessary to control the full pollination network}
\end{table}

\begin{figure}[h]
\centering
<<fig alternative assumptions, echo = FALSE, warning = F, message = F, fig.height=1.5, fig.width=4.3>>=
a_m_driver <- a_m %>% 
  dplyr::full_join(meta) %>%
  dplyr::filter(study != "ballantyne") %>% 
  dplyr::mutate(type = factor(type, 
                              levels =  c("AB", "BA", "weight", "z-bi"),
                              labels = c("pla. to pol.", "pol. to pla.", "dependency", "bidirectional")),
                type_l  = as.character(type)) %>%
  dplyr::mutate(n_driver = n_pla + n_pol - n_matched, 
                n_driver_rel = 1 - n_matched / (n_pla + n_pol))

type_l <- unique(a_m_driver$type_l)

a_m_driver %>%
  ggplot(aes(x = type, y = n_driver_rel), parse = T) +
  geom_boxplot(size = 0.25, colour = "grey10",
							 outlier.shape = 21, outlier.size = 1) +
  coord_flip() + 
  xlab("") +
  ylab("proportion of driver species") + 
  fer_theme + 
  theme(plot.margin = grid::unit(c(0,1,2,0), "mm"))

@
\caption{\label{fig:alternative_assumptions} Proportion of driver species necessary to control the full pollination network under four different assumptions of the direction of control}
\end{figure}

\begin{table}[h]
\centering
\small
<<table alternative assumptions, echo = FALSE, warning = F, message = F, results = "asis">>=

corr_matrix <- a_m_driver %>%
  dplyr::select(net_name, type, n_driver) %>%
  tidyr::spread(type, n_driver) %>%
  dplyr::select(-net_name) %>%
  as.matrix() %>%
  cor(method = "spearman") %>%
  round(digits = 2)

corr_matrix[lower.tri(corr_matrix, diag = T)] <- ""
corr_matrix <- corr_matrix[, -1]
corr_matrix <- corr_matrix[-(nrow(corr_matrix)), ]
kable(corr_matrix, align = "c", format = "latex", booktabs = T)

@
\caption{\label{table:corr_driver} Spearman correlation coefficients of the number of driver species necessary to control the full pollination network.}
\end{table}

\section{Visitation frequency vs. pollen deposition}

The number of driver species in a pollination community and the relative importance of each species depend both of the strength of mutual dependencies between plant pollinators and the structure of the pollination network. Traditionally pollination networks have been represented using visitation frequency, but a flower visitor is not necessarely a pollinator. It has been shown that wether pollination networks are represented using visitation or actual pollen deposition can have effects on the network structure and presumably on the strength of mutuial dependency.

We investigated the effects of using visitation, pollen deposition (effective pollination) and pollinator importance (the product of visitation frequency and effective single visit pollen deposition). We used available data collected by \textcite{Ballantyne2015} from a low diversity pollination community at a dry lowland heathland in Dorset, UK (50° 43.7'N 2° 07.2'W).

Deposition networks, a proxy pollinator efficiency, were quantified using the mean Single Visit Deposition---the number of conspecific pollen grains effectively deposited on a virgin stigma during a single visit by a particular animal \autocite{NeEman2010,King2013,Ballantyne2015}. Visitation networks were constructed counting the visits to flowers during Single Visit Depositions. Pollinator importance networks were consrtucted as the product of pollinator efficiency and visit frequency.

<<get n_driver, echo = FALSE, warning = F, message = F>>=
n_driver <- meta %>%
  dplyr::inner_join(n_matched) %>% 
  dplyr::mutate(n_driver = 1 - n_matched / (n_pla + n_pol))
@

We first investigated the effects at a network scale. Despite marked differences in the distribution of weights of the three networks (\autoref{fig:ballantyne-ntw}), the minimum number of driver species to control the whole community was consistent among the three different approaches \Sexpr{round(n_driver$n_driver[n_driver$net_name == "bal_eff"]*100)}\% for deposition, \Sexpr{round(n_driver$n_driver[n_driver$net_name == "bal_vis"]*100)}\% for the visitation, and \Sexpr{round(n_driver$n_driver[n_driver$net_name == "bal_imp"]*100)}\% for the pollinator importance network).

The choice of weighting used can also have an impact on the realtive importance of species. Therefore we calculated the frequency that each species is present in the possible sets of driver species under the three schemes. Although visitation and deposition produce strikingly different results, we found a very strong agreement between the order produced by visitation and importance (\autoref{table:corr_weights}). Arguably, visitation best reflects the dependency of animals to plants, as usually animals forage for pollen or nectar regardless of wether effective pollination occurs or not. Contrastingly, importance, the product between visit frequency and pollinator effectiveness, best relefect the dependency of plants to animals.

Finally, we investigated whether the asymmetry of mutual dependency, which defines the direction of control, was consistent among the three posible weighting schemes. We found again that the direction of the dominant dependency was mantained was consistent for 95\% of the interactions weighted by visitation or importance (\autoref{table:corr_weights}), the two most appropriate metrics for pollinator and plant dependency.

All together, evidence supports the idea that visitation is a suitable metric to estimate the mutual dependency of species pairs. First it is directly related to pollinator foraging. Second it produces results consistent, at least within our controllability framework, with plant reproductive success (as estimated by the importance metric).

\begin{figure}[h]
\centering
<<matrix representation, echo = FALSE, warning = F, message = F, fig.height=4, fig.width=5.5>>=
p <- net[meta$net_name[meta$study == "ballantyne" & meta$count != "binary"]] %>%
	plyr::ldply(function(x) {
		data.frame(vname = igraph::E(net[[1]]) %>% attr("vnames"), 
							weight = igraph::E(x)$weight)
	}) %>%
	dplyr::rename_("net_name" = ".id") %>%
	dplyr::mutate(net_name_f = factor(net_name,  
																		levels = c( 'bal_eff','bal_vis','bal_imp'),
																		labels = c("a) Deposition", "b) Visitation", "c) Importance")), 
	              pla = stringr::str_split_fixed(vname, "\\|", 2)[, 1],
	              pol = stringr::str_split_fixed(vname, "\\|", 2)[, 2]) %>%
  plyr::dlply("net_name_f", function(x){
    p1 <- x %>%
      ggplot(aes(x = pol, y = pla)) +
      geom_tile(aes(fill = weight, width = 0.9, height = 0.9)) + 
      coord_fixed() +
      scale_fill_gradient(low = "#f0f0f0", high = "#525252") +
      ylab("plants") +
      xlab("pollinators") + 
      fer_theme +
      theme(axis.text = element_blank(), 
            axis.ticks = element_blank(), 
            legend.position = "right", 
            legend.title = element_blank(), 
            plot.margin = grid::unit(c(6,0,2,5), "mm"),
            panel.grid = element_blank(),
            legend.key.width = grid::unit(4, "mm"),
            legend.key.height = grid::unit(4, "mm"))
    p2 <- x %>% ggplot(aes(x = weight)) +
      scale_x_log10() +
      stat_density(aes(y =..density..), geom = "line") +
      xlab("link weight") + 
      ylab("density") +
      ggtitle(x$net_name_f[1]) +
      fer_theme +
      theme(plot.margin = grid::unit(c(2,2,0,0), "mm"))
    list(p1, p2)
  })

multiplot(p[[1]][[2]], p[[1]][[1]], p[[2]][[2]], p[[2]][[1]], p[[3]][[2]], p[[3]][[1]], layout = matrix(c(1,2,2,3,4,4,5,6,6), ncol = 3, byrow = T))  
@
\caption{\label{fig:ballantyne-ntw} Distribution of interaction weights for the pollen deposition, visitation and pollinator importance networks. Note that the \textit{x} axis in the density plots have been log-transformed}
\end{figure}

\begin{table}[h]
\centering
\small
<<table correlations, echo = FALSE, warning = F, message = F, results = "asis">>=
drivers_b <- m_f[meta$net_name[meta$study == "ballantyne"]] %>%
	plyr::ldply(function(x){
	  dplyr::data_frame(species = names(x),
	                    d_freq = attr(x, "n_matchings") - x,
	                    d_reim = 1 - x / attr(x, "n_matchings"),
	                    d_rank = rank(d_reim, ties.method = "average"))
	}) %>%
	dplyr::rename_("net_name" = ".id")

correlations <- drivers_b %>%
  dplyr::select(net_name, species, d_freq) %>%
  tidyr::spread(net_name, d_freq) %>%
  dplyr::select(-species) %>%
  as.matrix() %>%
  Hmisc::rcorr(type = "spearman")

my_paste <- function(x, y){
  if(is.na(y)) return ("-")
  b <- ""
  if(y < 0.05) b <- ""
  paste0(b, round(x, digits = 2), " (", round(y, digits = 4), ")", b)
}

dir_net_b <- net[meta$net_name[meta$study == "ballantyne"]] %>%
  lapply(function(x){
    x %>% 
      bipartite_digraph(type = "weight", keep = "all") %>%
      igraph::ends(igraph::E(.)) %>% 
      apply(1, function(y) paste(y[1], y[2]))
  })

# same order as the correlations 
dir_net_b <- dir_net_b[colnames(correlations$P)]

lt <- combn(length(dir_net_b), 2) %>%
  apply(2, function(x){
    length(intersect(dir_net_b[[x[1]]], dir_net_b[[x[2]]])) /
      length(igraph::E(net[[1]]))
  }) %>%
  magrittr::multiply_by(100) %>% round() %>% paste0("%")

nam <- c("unweighted","deposition", "importance", "visitation")

mapply(my_paste, correlations$r, correlations$P) %>%
  matrix(ncol = length(dir_net_b)) %>% magrittr::set_colnames(nam) %>%
  magrittr::set_rownames(nam) %>% `[<-`(lower.tri(.), lt) %>% 
  kable(align = "c", format = "latex", booktabs = T)
@
\caption{\label{table:corr_weights} Spearman correlation coefficients (with p-value) of the relative importance of species and the percentage of interactions that share the direction of dependency obtained using the three weighting schemes and an unweighted scheme. Significant correlations are highlighted in bold.}
\end{table}

\begin{figure}[h]
\centering
<<fig species, echo = FALSE, warning = F, message = F, fig.height=2.2, fig.width=6.49>>=
data_pol <- mod[[1]]@objects[[1]]$data
data_pla <- mod[[2]]@objects[[1]]$data

expand.grid(d = seq(min(data_pol$d), max(data_pol$d), by = 1),
            S_d = seq(min(data_pol$S_d), max(data_pol$S_d), length = 20), 
            n = seq(min(data_pol$n), max(data_pol$n), length = 3), 
            S_v = mean(data_pol$S_v)) %>%
  dplyr::mutate(q = predict.glmulti(mod[[1]], 
                                    select = 0.95, 
                                    newdata = .)$averages %>%
                  as.vector(), 
                p = plogis(q)) %>%
  dplyr::mutate(n = factor(n, 
                           levels = seq(min(data_pol$n), max(data_pol$n), length = 3),
                           labels = c("low", "mean", "high"))) %>%
  ggplot(aes(x = d, y = S_d, z = p)) +
  geom_tile(aes(fill = p)) +
  scale_fill_gradient(name = "relative\nimportance", high = "#f0f0f0", low = "#525252") +
  scale_x_continuous(expand = c(0,0)) +
  scale_y_continuous(expand = c(0,0)) +
  facet_wrap(~n) +
  xlab("degree") +
  ylab("strength of dependencies") +
  stat_contour(colour = "black", size = 0.25) +
  fer_theme

@
\caption{\label{fig:prediction} aSS }
\end{figure}

\section{Relative importance of species}

First we assessed the impotance of each explanatory variable individually. We included the most relevant subset into a more detailed analysis that included first order interactions between them.

\printbibliography

\end{document}

### 2016-03-08 paper/manuscript.Rnw
complete methods and update some results

@@
 % comments
-\usepackage[draft]{todonotes}
+\usepackage[draft, textsize = scriptsize]{todonotes}
 
@@
 \usepackage{booktabs}
+
+% box
+\usepackage{tcolorbox}
 
@@
 \begin{document}
+\renewcommand*{\bibfont}{\small}
+% line numbers
+\linenumbers
+\setlength\linenumbersep{15pt}
+\renewcommand\linenumberfont{\normalfont\footnotesize\sffamily\color{gray}}
+
+\onehalfspacing
 
@@
   \author{\large E. Fernando Cagua}
-  \author{\large Kate Wooton}
+  \author{\large Kate L. Wootton}
   \author{\large Johanna Voinopol-Sassu}
@@
 
-\keywords{Control theory}
-
-% line numbers
-\linenumbers
-\setlength\linenumbersep{15pt}
-\renewcommand\linenumberfont{\normalfont\footnotesize\sffamily\color{gray}}
-
-\onehalfspacing
+\keywords{Control theory, box in the article}
 
@@
 library(glmulti)
+library(Hmisc)
 opts_knit$set (root.dir=normalizePath('../'))
@@
 
-To investigate the dynamic controllability of pollination networks, we used ten paired plants-pollinator communities.
-Each par was composed by a community invaded by a plant and a community free of the invasive species.
-Weighted visitation networks were constructed from previously published visitation data collected from pollination communities in Bristol, Great Britain \autocite{Lopezaraiza-Mikel2007} and the National Cap de Creus in Northeastern Spain \autocite{Bartomeus2008}.
-The four British uninvaded communities the non-invaded plots were obtained by experimentally removing the invasive species \textit{Impatients grandulifera}.
-Contrastingly, Spanish uninvaded communities were obtained from plots that were not been colonised by the invasive species \textit{Carpobrotus affine acinaciformis} or \textit{Opuntia stricta}.
-In each of the networks we calculated the minimum number of driver species---species that need to be managed in order to gain full control of the community.
+To investigate the dynamic controllability of pollination networks, we used data from ten paired plant-pollinator communities.
+Each pair was composed by a community invaded by a plant and a community effectively free of the invasive species (Table S1).
+The networks were constructed from previously published pollination visitation data collected from pollination communities in Bristol, UK \autocite{Lopezaraiza-Mikel2007} and Cap de Creus National Park, Spain \autocite{Bartomeus2008}.
+In the four British uninvaded communities the non-invaded plots were obtained by experimentally removing all the flowers of invasive species \textit{Impatients grandulifera}.
+In contrast, the Spanish uninvaded communities were obtained from plots that had not yet been colonised by the invasive species \textit{Carpobrotus affine acinaciformis} or \textit{Opuntia stricta}.
 
-We first assigned a direction to each link between plants and pollinators given by the direction of dependency.
-For each link between a plant and its pollinator we quantified the level of dependency of the plant on the pollinator and vice versa \autocite{Bascompte2006}.
-The link points to the plant if the its dependency on the pollinator is larger than the pollinator's dependency on the plant.
-The dependency of plant $i$ on pollinator $j$ is the ratio between the visits coming from pollinator $j$ and all pollinator visits to plant $i$.
-The dependency of pollinator $j$ on plant $i$ is the ratio of the visits by pollinator $j$ to plant $i$ and all visits of pollinator $j$.
+All analysis were performed in R 3.2.2 using bipartite 2.05, igraph 1.0.1, lme4 1.0-6, MuMIn 1.15.6, and vegan 2.3-3 \autocite{RCoreTeam2015, Dormann2008, Csardi2006a, Bates2014, Barton2016, Oksansen2016}.
 
-In a directed network, a matching is a subset of links in which no two links share a common starting species or a common ending species.
-A species is matched if it is an ending node of an link in the matching.
-Otherwise, it is unmatched.
-It has been shown that the number of driver species can be calculated by counting the number of unmatched nodes in the directed graph representation of the pollination network \autocite{Liu2011}.
-We then found a maximum in the an alternative bipartite representation of the pollination network \autocite{Csardi2006}.
+\subsection*{Manageability}
 
-We calculated dependencies based on visitation frequency, which has been shown to be an appropriate surrogate of the inter-specific effects \autocite{Bascompte2006, Vazquez2005}.
-However, because the degree distribution, and ultimately the number of driver species, can be affected by the sampling method \autocite{Bluthgen2010} we compared the number of driver species in a pollination community in which both visitation frequency and effectiveness were measured \autocite{Ballantyne2015}.
+Changes on the abbundances of a species can modify the abbundances of those species it interacts with.
+We exploit this concept to quantify the \textit{manageability} of an ecological community (\autoref{eq:m}).
+\todo{need ecological justification; why is $n_d$ a good metric?} Manageability is directly related to the minimum number of species on which we would need to apply management interventions if we were to gain full control of the abbundances of all species in the ecological community, $n_d$.
+We calculated $n_d$ by finding the maximum matching of the pollination network in each community (Box 1).
 
-To quantify to what extent the number of driver species is characteristic of the structure of pollination networks we compared them a suit of random null-models.
-A set of null models were based on network randomisations that maintained the degree of plants, pollinators, and both plants and pollinators.
-To analyse the effects of the chosen directionality, we devised a null model in which we randomised the visitation patterns and re-calculated the new dependencies.
-In all cases we computed 999 randomisations.
+\begin{equation} \label{eq:m}
+m = 1- \frac{n_d}{n}
+\end{equation}
 
-We quantified the relative importance of each species for network dynamics.
-To do this, we counted the number of times a particular species was a driver species across all possible maximum matchings in the pollination network.
-The number of maximum matchings were found by generating the line graph of the alternative bipartite network representation, and then enumerating the maximal cliques in the complement of the line graph \autocite{Csardi2006}.
+\begin{tcolorbox}[float, title= Box 1: Maximum matching,colback=white,fontupper=\small]
+\parskip=0.5em
 
-Finally, we tackled the question whether some structural properties can predict the relative importance of driver species.
-Here, we regressed the importance of each species against measures of centrality (degree, betweenness), measures related to network robustness (contribution to nestedness) and measures of strength of association (visitation levels).
+It has been shown that the number of nodes (here species) necessary to fully control a complex network, can be calculated by counting the number of unmatched nodes \autocite{Liu2011}.
+In a directed network, like the simple pollination network shown on the left, a matching is a subset of links in which no two links share a common starting species or a common ending species---dark grey links---and a node is matched if it is the ending node of one of the links in the matching---dark grey nodes \autocite{West2001}.
+
+<<fig explain matching, echo = FALSE, warning = F, message = F, results = "asis", fig.height=1.4, fig.width=5.75>>=
+my_theme <- theme_bw() +
+	#scale_color_brewer(palette = "Paired") +
+	theme(legend.position = "none",
+				text = element_text(family = "Times"),
+				plot.margin=unit(c(4,0,-4,0),"mm"),
+				panel.margin=unit(c(0,0,0,0),"mm"),
+				# panel.border = element_rect(colour = "grey10", size = 0.5),
+				panel.border = element_blank(),
+				axis.text = element_blank(),
+				axis.ticks.x = element_blank(),
+				axis.ticks.y = element_blank(),
+				axis.title = element_text(size = 9),
+				plot.title = element_text(hjust = 0.05, vjust = -1.5, size = 9),
+				panel.grid = element_blank())
+
+# Function to generate paths between each connected node
+edgeMaker <- function(whichRow, len = 100, curved = TRUE){
+	fromC <- layoutCoordinates[adj_list[whichRow, 1], ]  # Origin
+	toC <- layoutCoordinates[adj_list[whichRow, 2], ]  # Terminus
+
+	# Add curve:
+	graphCenter <- colMeans(layoutCoordinates)  # Center of the overall graph
+	bezierMid <- c(fromC[1], toC[2])  # A midpoint, for bended edges
+	distance1 <- sum((graphCenter - bezierMid)^2)
+	if(distance1 < sum((graphCenter - c(toC[1], fromC[2]))^2)){
+		bezierMid <- c(toC[1], fromC[2])
+	}  # To select the best Bezier midpoint
+	bezierMid <- (fromC + toC + bezierMid) / 3  # Moderate the Bezier midpoint
+	if(curved == FALSE){bezierMid <- (fromC + toC) / 2}  # Remove the curve
+
+	edge <- data.frame(bezier(c(fromC[1], bezierMid[1], toC[1]),  # Generate
+														c(fromC[2], bezierMid[2], toC[2]),  # X & y
+														evaluation = len))  # Bezier path coordinates
+	edge$Sequence <- 1:len  # For size and colour weighting in plot
+	edge$Group <- paste(adj_list[whichRow, 1:2], collapse = ">")
+	return(edge)
+}
+
+sp_names <- c("a[1]", "a[2]", "a[3]", "p[1]", "p[2]")
+
+adj_matrix <- c(0,0,0,1,0,
+								0,0,0,1,1,
+								0,0,0,0,0,
+								0,0,1,0,0,
+								0,0,1,0,0) %>%
+	matrix(nrow = 5, byrow = T) %>%
+	`rownames<-`(sp_names) %>%
+	`colnames<-`(sp_names)
+
+net <- adj_matrix %>% 
+	igraph::graph_from_adjacency_matrix(mode = "directed") 
+igraph::V(net)$type <- c(F, F, F, T, T)
+igraph::E(net)$weight <- 1
+
+layoutCoordinates <- cbind(c(0,1,2,0.5,1.5), 
+													 c(1,1,1,0,0)) %>%
+	`colnames<-`(c("x", "y"))
+
+adj_list <- adj_matrix %>% 
+	reshape2::melt() %>% 
+	dplyr::filter(value > 0)
+
+# Generate an edge path for each pair of connected nodes
+n <- 17
+allEdges <- lapply(1:nrow(adj_list), edgeMaker, len = n, curved = FALSE)
+allEdges <- do.call(rbind, allEdges) %>%
+	dplyr::filter(Sequence != n) %>%
+	dplyr::mutate(Group = factor(Group),
+				 type = Group)
+
+new_lev <- c("m", "u", "m", "m", "u")
+levels(allEdges$type) <- new_lev
+
+nodes <- data.frame(layoutCoordinates) %>%
+	dplyr::mutate(spe = sp_names,
+								spe_c = c("u", "u", "m", "m", "m"), 
+								pos = rep(c(0.25, -0.25), c(3,2)))
+
+p1 <- ggplot(allEdges) +  # Pretty simple plot code
+	geom_path(aes(x = x, y = y, group = Group, colour = type, size = type), 
+						arrow = arrow(type = "closed", angle = 15, length = grid::unit(0.1, "inches"))) + # and taper
+	geom_point(data = nodes,  # Add nodes
+						 aes(x = x, y = y , fill = spe_c), size = 5, pch = 21,
+						 colour = "black") + 
+	geom_text(data = nodes, aes(x = x, y = y + pos, label = spe), size = 3, parse = T) +
+	scale_fill_manual(values = c("#636363", "white")) + 
+	scale_colour_manual(values = c("#636363", "#bdbdbd")) +
+	my_theme + xlab("") + ylab("") + ylim(c(-0.27, 1.26)) +
+ theme(plot.margin=unit(c(4,4,-4,-4),"mm")) +
+	scale_size_manual(values = c(0.5, 0.5))
+
+net <- digraph_bipartite(net)
+adj_matrix <- net %>% igraph::as_adjacency_matrix(sparse = F, type = "upper")
+layoutCoordinates <- cbind(rep(0:4, 2), rep(c(1,0), each = 5)) %>%
+	`colnames<-`(c("x", "y"))
+
+adj_list <- adj_matrix %>% 
+	reshape2::melt() %>% 
+	dplyr::filter(value > 0)
+
+# Generate an edge path for each pair of connected nodes
+n <- 100
+allEdges <- lapply(1:nrow(adj_list), edgeMaker, len = n, curved = FALSE)
+allEdges <- do.call(rbind, allEdges) %>%
+	dplyr::filter(Sequence != n,
+								Sequence != 1) %>%
+	dplyr::mutate(Group = factor(Group),
+				 type = Group)
+
+new_lev <- c("m", "m", "u", "m", "u")
+levels(allEdges$type) <- new_lev
+
+nodes <- data.frame(layoutCoordinates) %>%
+	dplyr::mutate(spe = rep(sp_names, 2),
+								spe_l = c(paste0(sp_names, " %->% phantom(0)"), paste0(sp_names, " %<-% phantom(0)")),
+								spe_c = c(rep("u",5), c("u", "u", "m", "m", "m")), 
+								pos = rep(c(0.25, -0.25), each = 5))
+
+p2 <- ggplot(allEdges) +  # Pretty simple plot code
+	geom_path(aes(x = x, y = y, group = Group, colour = type, size = type)) + # and taper
+	geom_point(data = nodes,  # Add nodes
+						 aes(x = x, y = y, fill = spe_c), size = 5, pch = 21,
+						 colour = "black") + 
+	geom_text(data = nodes, aes(x = x + 0.08, y = y + pos, label = spe_l), parse = T, size = 3) +
+	# coord_flip()  + scale_x_reverse() + scale_y_reverse() +
+	scale_fill_manual(values = c("#636363", "white")) + 
+	scale_colour_manual(values = c("#636363", "#bdbdbd")) +
+	xlim(c(-0.12, 4.12)) + ylim(c(-0.27, 1.26)) +
+	my_theme + xlab("") + ylab("") +
+	scale_size_manual(values = c(0.5, 0.5))
+
+multiplot(p1, p2, layout = matrix(nrow = 1, c(1,1,1,2,2,2,2,2)))
+@
+
+To find the maximum matching we used a bipartite representation of the network, like the one on the right, in which the levels indicate the outgoing and incoming links to each node.
+Finding a matching here is equivalent to finding the links such that each node on the top is matched to at most one node on the bottom and vice versa \autocite{West2001}.
+The maximum matching is the one in which the matched links have the largest possible weight among all possible matchings.
+
+The use of a maximum matching has also an intuitive explanation.
+In control theory lingo, a network is fully controlable when each node in the network has a "superior" or input that drives its dynamics.
+Matched nodes can be controled within the network by the node pointing to it---its superior.
+However, unmatched nodes have no superior in the network and must be directly controlled by external inputs---what we refer to as management interventions \autocite{Liu2011}.
+
+The size of the maximum matching is therefore directly related to its \textit{manageability} because systems that require a large number of inputs are more difficult to control.
+The manageability of the shown network is $m = 0.6$ because in theory, it is possible to guide the community to a desired state by applying management interventions to two of the five species in the community ($n_d = 2$; $a_1$ and $a_2$ in the depicted maximum matching).
+
+\end{tcolorbox}
+
+We assumed that for a pair of interacting species the direction of control is inverse to the direction of dependency.
+If, for instance, a plant species depends more on a pollinator species than the pollinator depends on the plant, we expect the plant abbundances to be more sensitive to changes in the pollinator abbundance than vice versa.
+Violation of this assumption, however, renders qualitatively consistent results (Figure S1; Table S2).
+Therefore, we first assigned a single direction to each link between plants and pollinators based on the direction the assymetries in dependencies based on visitation frequencies following \textcite{Bascompte2006}.
+The dependency of plant $i$ on pollinator $j$ is the proportion of the visits comming from pollinator $j$ compared to all pollinator visits to plant $i$.
+Likewise, the dependency of pollinator $j$ on plant $i$ is the ratio of the visits by pollinator $j$ to plant $i$ and all visits of pollinator $j$.
+
+\todo{really?
+maybe Jason can help with a citation?
+or is there a better justification?}Intuitively, there is a relationship between diversity and manageability.
+We therefore used a set of generalised linear models to investigate the relatioship between community manageability and (i) the total number of species, (ii) plant richness, (iii) polinators richness, and (iv) the ratio of plants to pollinators richness.
+Because both invaded and British communities tend to be more diverse, we also assesed whether observed differences in manageability were due to these two factors.
+
+To quantify the extent to which the manageability of a pollination community is characteristic of the network structure, we compared it to a suite of random null-models.
+An initial set of null models was based on network randomisations that maintained the species degree (the number of interactions), or that mantained the species strength (total sum of interaction weights).
+Subsequently we calculated the dependencies followed by the manageability of the randomised networks.
+A second set of null models was based on randomisations that mantained the structure of the empirical network but randomised the direction of dependencies between species.
+In all cases we calculated a Z-score between the manageability of each empirical network and the corresponding manageability of 999 randomisations.
+
+\subsection*{Driver species}
+
+The manageability of a community, $m$, provides an indication of the magnitude of $n_d$ but not the identity of the species that can compose this set.
+In fact maximum matchings are not unsually unique in ecological networks and different sets of species of size $n_d$ could be used to control the network \autocite{Liu2011}.
+Nevertheless, species vary on the frequency at which they are part of this set; an indication of their relative importance to drive the state of the ecosystem.
+
+We therefore call \textit{driver species} those that are identified as needing directed interventions in the majority of maximum matchings, and therefore likely to have a disproportionate effect on the abbundances of other species in the community.
+We identified the driver species in each of the communities by computing all possible maximum matchings in the network.
+To do so, we first generated the network's line graph---an alternative representation in which nodes are the interactions of the original network and links represent common ending points.
+We then calculated the complement of the line graph---a graph in which nodes are adjecent if and only if they are not adjancent in the line graph.
+All possible maximum matchings can be found by enumerating all cliques of size $1-n_d$ in the complement graph \autocite{West2001}.
+
+We then tackled the question whether some species level structural properties can predict the relative importance of driver species.
+Here, we evaluated the effect on the species' relative importance of measures of centrality (degree, betweenness, and overlap), measures related to network robustness (contribution to nestedness), and measures of strength of association (visitation levels).
+Candidate models were compared using AIC and the relative importance of the explanatory variables was evaluated using the sum of Akaike weights over all candidate models \autocite{Burnham2003}.
+
+\subsection*{Visitation as proxy for species interdependence}
+
+Visitation frequency has been shown to be an appropriate surrogate for inter-specific effects in pollination networks \autocite{, Vazquez2005, Bascompte2006}.
+Arguably, visitation reflects adequately the dependency of animals to plants, as usually during a visit animals forage for pollen or nectar regardless of wether effective pollination occurs\todo{any citation Daniel?}.
+Nevertheless visitation is not equivalent to pollen deposition and might be insufficient to reflect the dependencies of plants on animals \autocite{Alarcon2010, King2013}.
+We therefore investigated the effect of calculating the dependencies using pollination effectiveness and importance---two metrics more proximate to plant reproductive sucess.
+
+Pollinator efficiency is measured as ``the number of conspecific pollen grains deposited on a virgin stigma during a single visit by a particular animal'' \autocite{NeEman2010}.
+Pollinator importance on the other hand is defined as the product between visitation frequency and pollinator efficency \autocite{Ballantyne2015}.
+We used data collected by \textcite{Ballantyne2015} from a low diversity pollination community at a dry lowland heathland in Dorset, UK.
+We assessed the differences between visitation, pollinator effectiveness, and pollinator importance by comparing (i) the manageability of the community, (ii) the percentage of interactions that mantained the direction of dependency, and (iii) the Spearman correlation of the relative importance of the species in the community.
 
@@
   dplyr::inner_join(meta) %>%
-  dplyr::filter(!is.na(inv)) %>%
-  dplyr::mutate(n_dr = n_pla + n_pol - n_matched,
-                n_dr_p = 1 - n_matched / (n_pla + n_pol))
+  dplyr::filter(count == "visitation") %>%
+  dplyr::mutate(n_sp = n_pla + n_pol, 
+                n_dr = n_sp - n_matched,
+                n_dr_p = n_dr / n_sp)
 
-# Wilcoxon signed rank test
+# Wilcoxon signed rank test invasive vs non invasive
 wt <- n_driver %>%
   dplyr::select(site, inv, n_dr_p) %>%
+  dplyr::filter(!is.na(inv)) %>%
   dplyr::mutate(n_dr_p = qlogis(n_dr_p)) %>%
@@
   dplyr::select(-site) %>%
-  as.matrix() %>% {
-      wilcox.test(x = `[`(.,1), y = `[`(.,2), paired = T)
-  }
+  as.matrix()
+
+n_driver %<>%
+  dplyr::filter(!is.na(inv))
+
+wt <-  wilcox.test(x = wt[, 1], y = wt[, 2], paired = T)
+
+m0 <- glm(cbind(n_dr, n_sp) ~ n_pla * n_pol, 
+          data = n_driver, 
+          family = "binomial")
+m_nr <- glm(cbind(n_dr, n_matched) ~ I(n_pla/n_pol) + study, 
+          data = n_driver, 
+          family = "binomial")
+m1 <- glm(cbind(n_dr, n_matched) ~ I(n_pla/n_pol), 
+          data = n_driver, 
+          family = "binomial")
+m2 <- glm(cbind(n_dr, n_matched) ~ study, 
+          data = n_driver, 
+          family = "binomial")
 @
 
-We found that if we were to control the dynamics of the whole community, we would need to control between \Sexpr{round(min(n_driver$n_dr_p)*100)} and \Sexpr{round(max(n_driver$n_dr_p)*100)}\% (mean \Sexpr{round(min(n_driver$n_dr_p)*100)}\%) of the species in the community.
-The relative number of driver species did not change if the dependencies were assumed to be bidirectional, from plant to pollinators or from pollinators to plants (Supp.
-Information).
-However, the proportion of driver species did was not significantly different between invaded and uninvaded ecosystems (Wilcoxon signed-rank sum test, $p = \Sexpr{wt$p.value}$).
+We found that if we were to control the dynamics of the whole community, we would need to control between \Sexpr{round(min(n_driver$n_dr_p)*100)} and \Sexpr{round(max(n_driver$n_dr_p)*100)}\% (mean \Sexpr{round(mean(n_driver$n_dr_p)*100)}\%) of the species in the community.
+The relative number of driver species did not change if the dependencies were assumed to be bidirectional, or exclusively from plant to pollinators or from pollinators to plants (Figure S1; Table S2).
+In addition we did not detect any significant differences between the proportion of driver species in invaded or uninvaded ecosystems (Wilcoxon signed-rank sum test, $p = \Sexpr{round(wt$p.value, digits = 3)}$) nor between study sites (likelyhood ratio test, $Pr(>\chi^2) = \Sexpr{round(anova(m1, m_nr, test = "LRT")$`Pr(>Chi)`[2], digits = 3)}$; Table S3).
+Nevertheless we found that the ratio of plant to pollinator species richness had an important neggative effect on the proportion of driver species ($Pr(>\chi^2) = \Sexpr{round(anova(m2, m_nr, test = "LRT")$`Pr(>Chi)`[2], digits = 3)}$; \autoref{fig:n_driver_explanatory}, Table S3).
+
+\begin{figure}
+\centering
+<<fig explaining n_driver, echo = FALSE, warning = F, message = F, results = "asis", fig.height=2.2, fig.width=3.245>>=
+p <- predict(m1, type = "response", se.fit = T)
+
+ggplot(data = n_driver,
+       aes(x = n_pla/n_pol, y = 1-n_dr_p)) +
+  geom_ribbon(aes(ymax = 1- (p$fit + 1.96 * p$se.fit), ymin = 1- (p$fit - 1.96 * p$se.fit)),
+              fill = "#f0f0f0") +
+  geom_line(aes(y = 1- p$fit)) +
+  geom_point(aes(fill = study), shape = 21) +
+  ylab("manegeability") +
+  xlab("plant / pollinator richness") +
+  scale_fill_manual(values = c("#ffffff", "#bdbdbd"), 
+                    name = "", labels = c("Lopezaraiza-Mikel et al. (2007)",
+                                          "Bartomeus et al. (2008)")) +
+  fer_theme +
+  theme(plot.margin = grid::unit(c(5, 1, 2, 0), "mm"), 
+        legend.key = element_blank(), 
+        legend.position = "none")
+@
+\caption{\label{fig:n_driver_explanatory} The proportion of species needed to control the network is largely influenced by the ratio of plant to pollinator species richness  but not the location of the community.
+White dots correspond to communities investigated by \textcite{Bartomeus2008}; grey dots correspond to communities investigated by \textcite{Lopezaraiza-Mikel2007}.}
+\end{figure}
 
@@
   dplyr::inner_join(meta) %>%
-  dplyr::filter(!is.na(inv)) %>%
+  dplyr::filter(count == "visitation") %>%
   dplyr::mutate(n_dr = n_pla + n_pol - n_matched)
@@
 # non-parametric
-# z_scores <- r$method %>%
-#   unique() %>%
-#   plyr::ldply(function(x){
-#     n_driver %>%
-#       dplyr::mutate(method = x)
-#   }) %>%
-#   dplyr::bind_rows(r) %>%
+z_scores <- r$method %>%
+  unique() %>%
+  plyr::ldply(function(x){
+    n_driver %>%
+      dplyr::mutate(method = x)
+  }) %>%
+  dplyr::bind_rows(r) %>%
+  dplyr::group_by(net_name, method) %>%
+  dplyr::mutate(z_r = rank(n_dr, na.last = NA),
+                z_s = qlogis(z_r/n()),
+                z_s = replace(z_s, is.infinite(z_s) & z_s > 0, qlogis(0.999)),
+                z_s = replace(z_s, is.infinite(z_s) & z_s < 0, qlogis(0.001))) %>%
+  dplyr::filter(is.na(sim))
+
+# z_scores <- r %>%
 #   dplyr::group_by(net_name, method) %>%
-#   dplyr::mutate(z_r = rank(n_dr, na.last = NA, ties.method = "average"),
-#                 z_s = qlogis(z_r/n()),
-#                 z_s = replace(z_s, is.infinite(z_s) & z_s > 0, qlogis(0.9999)),
-#                 z_s = replace(z_s, is.infinite(z_s) & z_s < 0, qlogis(0.0001))) %>%
-#   dplyr::filter(is.na(sim))
-
-z_scores <- r %>%
-  dplyr::group_by(net_name, method) %>%
-  dplyr::summarise(mu = mean(n_dr, na.rm = T),
-                   sigma = sd(n_dr, na.rm = T)) %>%
-  dplyr::inner_join(n_driver) %>%
-  dplyr::group_by() %>%
-  dplyr::mutate(z_s = (n_dr - mu)/sigma)
+#   dplyr::summarise(mu = mean(n_dr, na.rm = T),
+#                    sigma = sd(n_dr, na.rm = T)) %>%
+#   dplyr::inner_join(n_driver) %>%
+#   dplyr::group_by() %>%
+#   dplyr::mutate(z_s = (n_dr - mu)/sigma)
 
@@
       dplyr::mutate(sign = t.test(z_s)$p.value)
-  }) %>% 
+  }, .inform = T) %>% 
   dplyr::group_by(method) %>%
@@
 							 outlier.shape = 21, outlier.size = 1) +
-  geom_point(aes(y = 12, colour = sign <= 0.05), shape = 8, size = 1) +
+  geom_point(aes(y = 9, colour = sign <= 0.05), shape = 8, size = 1) +
   coord_flip() +
@@
 
+\section*{Acknoledgements}
+
+The authors thank Dr.
+Takeuki Uno for the insight provided to find the set of all maximum matching algorithms, and Bernat Bramon and Marilia Gaiarsa for feedback in early stages of the project.
+EFC acknowledges the support from the University of Canterbury Doctoral Scholarship, the University of Canterbury Meadow Mushroooms Postgraduate Scholarship, a travel grant from the European Space Agency and a Rutherford Discovery Fellowship (to DBS).
+DBS ackloledges the support of a Rutherford Discovery Scholarship, administered by the Royal Society of New Zealand.
+
+\section*{Author contributions}
+
 \printbibliography

### 2016-03-08 paper/supp_info.Rnw
complete methods and update some results

@@
 n_driver <- n_matched %>%
-  dplyr::inner_join(meta) %>%
+  dplyr::full_join(meta) %>% 
   dplyr::filter(!is.na(inv)) %>%
@@
 n_driver %>%
-  dplyr::select(site, inv, n_pla, n_pol, n_dr, n_dr_p) %>%
-  dplyr::mutate(site = as.numeric(as.factor(site)),
+  dplyr::select(site, inv, n_pla, n_pol, n_dr, n_dr_p, study) %>%
+  dplyr::arrange(study, site) %>%
+  dplyr::mutate(site = rep(1:dplyr::n_distinct(site), each = 2),
                 inv = plyr::mapvalues(inv, c(TRUE, FALSE), c("yes", "no")),
-                n_dr_p = paste0(round(n_dr_p * 100), "%")) %>%
+                n_dr_p = paste0(round(n_dr_p * 100), "%"),
+                study = plyr::mapvalues(study, 
+                                        c("bartomeus", "lopezaraiza"),
+                                        c("Bartomeus et al. (2008)",
+                                          "Lopezaraiza-Mikel et al. (2007)"))) %>%
   dplyr::rename_("invaded" = "inv",
-                 "No. plants" = "n_pla",
-                 "No. polinators" = "n_pol",
+                 "No. pla." = "n_pla",
+                 "No. pol." = "n_pol",
                  "No. driver spp." = "n_dr",
-                 "prop. driver spp." = "n_dr_p") %>%
-  dplyr::arrange(site) %>%
+                 "prop. driver spp." = "n_dr_p",
+                 "source" = "study") %>%
   kable(align = "c", booktabs = T, 
@@
 @
-\caption{\label{table:n_driver} Minimum number and proportion of driver species necessary to control the full pollination network}
+\caption{\label{table:n_driver} Properties of the analysed plant-pollinator communities.}
 \end{table}
@@
 @
-\caption{\label{table:corr_driver} Spearman correlation coefficients of the number of driver species necessary to control the full pollination network.}
+\caption{\label{table:corr_driver} Spearman correlation coefficients of the number of driver species necessary to control the full pollination network under the four different assumptions of the direction of control.}
+\end{table}
+
+We built a set of three generalised linear models with a logistic error structure to investigate the variables that influence the set of driver species.
+We found that the proportion of driver species is largely independent of the study site but highly dependent on the ratio of plant to pollinator diveristy (\autoref{table:n_driver_explanatory}).
+
+\begin{table}[h]
+\centering
+\small
+<<table explaining n_driver, echo = FALSE, warning = F, message = F, results = "asis">>=
+
+m_nr <- glm(cbind(n_dr, n_matched) ~ I(n_pla/n_pol) + study, 
+          data = n_driver, 
+          family = "binomial")
+m1 <- glm(cbind(n_dr, n_matched) ~ I(n_pla/n_pol), 
+          data = n_driver, 
+          family = "binomial")
+m2 <- glm(cbind(n_dr, n_matched) ~ study, 
+          data = n_driver, 
+          family = "binomial")
+
+ms <- MuMIn::model.sel(m_nr, m1, m2)
+
+i <- 1:3 # indices of columns with model terms
+response <- "p_d"
+
+res <- as.data.frame(ms)
+v <- names(ms)[i]
+v[v == "(Intercept)"] <- 1
+
+# create formula-like model names:
+mnames <- apply(res[, i], 1, function(x) 
+     deparse(MuMIn::simplify.formula(reformulate(v[!is.na(x)], response = response)))) %>%
+  sub("study", "s", .) %>%
+  sub("I(n_pla/n_pol)", "r_{p/a}", ., fixed = T) %>%
+  sub("~", '\\\\sim', .) %>%
+  paste0("$", ., "$")
+
+res <- dplyr::rename_(res, "$\\Delta$AIC" = "delta")
+
+cbind(model = mnames, res[, -i]) %>%
+  knitr::kable(align = "c", booktabs = T, digits = 2, escape = F, row.names = F, linesep = "")
+@
+\caption{\label{table:n_driver_explanatory} The proportion of species needed to control the network ($p_d$) is largaly influenced by the ratio of plant to pollinator species richness ($r_{p/a}$) but not the location of the community ($s$).}
 \end{table}
@@
 	plyr::ldply(function(x) {
-		data.frame(vname = igraph::E(net[[1]]) %>% attr("vnames"), 
+		data.frame(vname = igraph::E(x) %>% attr("vnames"), 
 							weight = igraph::E(x)$weight)
-	}) %>%
+	}, .inform = T) %>%
 	dplyr::rename_("net_name" = ".id") %>%

### 2016-03-10 paper/manuscript.Rnw
add some more results

@@
 If, for instance, a plant species depends more on a pollinator species than the pollinator depends on the plant, we expect the plant abbundances to be more sensitive to changes in the pollinator abbundance than vice versa.
-Violation of this assumption, however, renders qualitatively consistent results (Figure S1; Table S2).
+However, our results are robust to this assumption as its violation renders qualitatively consistent results (Figure S1 and S2; Table S2).
 Therefore, we first assigned a single direction to each link between plants and pollinators based on the direction the assymetries in dependencies based on visitation frequencies following \textcite{Bascompte2006}.
@@
 
-\subsection*{Visitation as proxy for species interdependence}
+\subsection*{Visitation as a proxy for species interdependence}
 
@@
 \section*{Results}
+
+\subsection*{Manageability}
 
@@
 wt <-  wilcox.test(x = wt[, 1], y = wt[, 2], paired = T)
-
-m0 <- glm(cbind(n_dr, n_sp) ~ n_pla * n_pol, 
+m0 <- glm(cbind(n_dr, n_matched) ~ n_pla * n_pol + study + inv, 
           data = n_driver, 
           family = "binomial")
-m_nr <- glm(cbind(n_dr, n_matched) ~ I(n_pla/n_pol) + study, 
+m_nr <- glm(cbind(n_dr, n_matched) ~ I(n_pla/n_pol) + study + inv, 
+          data = n_driver, 
+          family = "binomial")
+m8 <- glm(cbind(n_dr, n_matched) ~ I(n_pla/n_pol) + inv, 
+          data = n_driver, 
+          family = "binomial")
+m9 <- glm(cbind(n_dr, n_matched) ~ I(n_pla/n_pol) + study, 
           data = n_driver, 
@@
           family = "binomial")
+m3 <- glm(cbind(n_dr, n_matched) ~ I(n_pla + n_pol), 
+          data = n_driver, 
+          family = "binomial")
+m4 <- glm(cbind(n_dr, n_matched) ~ n_pla, 
+          data = n_driver, 
+          family = "binomial")
+m5 <- glm(cbind(n_dr, n_matched) ~ n_pol, 
+          data = n_driver, 
+          family = "binomial")
+m6 <- glm(cbind(n_dr, n_matched) ~ inv, 
+          data = n_driver, 
+          family = "binomial")
+m7 <- glm(cbind(n_dr, n_matched) ~ study + inv, 
+          data = n_driver, 
+          family = "binomial")
 @
 
-We found that if we were to control the dynamics of the whole community, we would need to control between \Sexpr{round(min(n_driver$n_dr_p)*100)} and \Sexpr{round(max(n_driver$n_dr_p)*100)}\% (mean \Sexpr{round(mean(n_driver$n_dr_p)*100)}\%) of the species in the community.
-The relative number of driver species did not change if the dependencies were assumed to be bidirectional, or exclusively from plant to pollinators or from pollinators to plants (Figure S1; Table S2).
-In addition we did not detect any significant differences between the proportion of driver species in invaded or uninvaded ecosystems (Wilcoxon signed-rank sum test, $p = \Sexpr{round(wt$p.value, digits = 3)}$) nor between study sites (likelyhood ratio test, $Pr(>\chi^2) = \Sexpr{round(anova(m1, m_nr, test = "LRT")$`Pr(>Chi)`[2], digits = 3)}$; Table S3).
-Nevertheless we found that the ratio of plant to pollinator species richness had an important neggative effect on the proportion of driver species ($Pr(>\chi^2) = \Sexpr{round(anova(m2, m_nr, test = "LRT")$`Pr(>Chi)`[2], digits = 3)}$; \autoref{fig:n_driver_explanatory}, Table S3).
+We found that if we were to control the dynamics of the whole community, we would need to control between \Sexpr{round(min(n_driver$n_dr_p)*100)} and \Sexpr{round(max(n_driver$n_dr_p)*100)}\% (mean \Sexpr{round(mean(n_driver$n_dr_p)*100)}\%) of the species in the community---which corresponds to manageabilities of \Sexpr{round(min(1-n_driver$n_dr_p), digits = 2)} to \Sexpr{round(max(1-n_driver$n_dr_p), digits = 2)} (Table S1).
+In addition we found that the ratio of plant to pollinator species richness had an important possitive effect on the community manageability ($Pr(>\chi^2) = \Sexpr{round(anova(m2, m_nr, test = "LRT")$`Pr(>Chi)`[2], digits = 3)}$).
+Constrastingly measures of biodiversity (like plant or pollinator richness) or factors such as the status of invasion, or the location of the study did not have a significant effect on the manageability (\autoref{fig:n_driver_explanatory}, Table S3).
 
@@
 
-We examined the role that the asimmetry of the dependencies which defines the direction of control has a central role in structuring the controlability of polination networks.
-We found that empirical networks have a much larger  the importance of dependency
-
-\begin{figure}
-\centering
-<<fig randomisations, echo = FALSE, warning = F, message = F, fig.height=2.2, fig.width=3.1>>=
+<<randomisations z_scores, echo = FALSE, warning= FALSE, message = FALSE>>=
 r <- r_w %>%
@@
 
-# z_scores <- r %>%
-#   dplyr::group_by(net_name, method) %>%
-#   dplyr::summarise(mu = mean(n_dr, na.rm = T),
-#                    sigma = sd(n_dr, na.rm = T)) %>%
-#   dplyr::inner_join(n_driver) %>%
-#   dplyr::group_by() %>%
-#   dplyr::mutate(z_s = (n_dr - mu)/sigma)
-
 z_scores %<>%
@@
 
+@
+
+We found that the manageability of empirical networks is not significantly different to that of network randomisations that maintained the species strength but different to those that maintained species degree (two tailed t-test, $p = \Sexpr{round(unique(dplyr::filter(z_scores, method == "quasiswap_count")$sign), digits = 3)}$ and \Sexpr{round(unique(dplyr::filter(z_scores, method == "swsh_both")$sign), digits = 3)} respectively; \autoref{fig:randomisations}).
+This result was also robust to the assumption that bidirectional shit (FIgure Sx)\todo{finish those analysis}.
+
+found that species strength and not degree structures the manageability of empirical networks (). 
+We examined the role that the asimmetry of the dependencies which defines the direction of control has a central role in structuring the controlability of polination networks.
+We found that empirical networks have a much larger  the importance of dependency
+
+\begin{figure}
+\centering
+<<fig randomisations, echo = FALSE, warning = F, message = F, fig.height=2.2, fig.width=3.1>>=
+
+# z_scores <- r %>%
+#   dplyr::group_by(net_name, method) %>%
+#   dplyr::summarise(mu = mean(n_dr, na.rm = T),
+#                    sigma = sd(n_dr, na.rm = T)) %>%
+#   dplyr::inner_join(n_driver) %>%
+#   dplyr::group_by() %>%
+#   dplyr::mutate(z_s = (n_dr - mu)/sigma)
+
 z_scores_method_order <- unique(z_scores$method)
@@
                 m_n = replace(m_n, m_n == 3, 3.5)) %>%
-  ggplot(aes(x = m_n, y = z_s)) +
+  ggplot(aes(x = m_n, y = -1 * z_s)) +
   # geom_hline(yintercept = c(-0), linetype = 2, alpha = 0.7, size = 0.25) + 
-  geom_vline(xintercept = c(2.75), alpha = 0.7, size = 0.25) +
+  geom_vline(xintercept = c(2.75), alpha = 0.6, size = 0.25) +
   geom_hline(yintercept = 0, size = 0.25, linetype = 2, colour = "grey30") +
-  geom_boxplot(aes(group = method), size = 0.25, colour = "grey10",
+  geom_boxplot(aes(group = method, fill = sign <= 0.05), size = 0.25, colour = "grey10",
 							 outlier.shape = 21, outlier.size = 1) +
-  geom_point(aes(y = 9, colour = sign <= 0.05), shape = 8, size = 1) +
+  # geom_point(aes(y = 9, colour = sign <= 0.05), shape = 8, size = 1) +
   coord_flip() +
-  scale_colour_manual(values = c(NA, "black")) +
-  scale_x_continuous(breaks = c(1, 2, 3.5), labels = rev(c("dependency", "strength", "degree"))) + 
+  scale_fill_manual(values = c("white", "#bdbdbd")) +
+  scale_x_continuous(breaks = c(1, 2, 3.5), labels = rev(c("random\ndependency", "maintain strength\nrandomise degree", "maintain degree\nrandomise strength"))) + 
   xlab("") +
-  ylab("number of driver species (z-score)") + 
+  ylab("Z-score of emp. manageability") + 
   fer_theme +
@@
 \end{figure}
+
+<<eval = F, echo = F>>=
+z_scores %>%
+  dplyr::filter(method == "r0") %>%
+  dplyr::inner_join(n_driver) %>%
+  ggplot(aes(x = n_pla/n_pol, y = z_s)) +
+  geom_point()
+
+r %>%
+  dplyr::filter(method == "r0")  %>%
+  dplyr::inner_join(n_driver, by = "net_name") %>%
+  ggplot(aes(x = n_pla.y/n_pol.y, y = n_matched.x / (n_pla.y + n_pol.y))) +
+  geom_point() +
+  geom_smooth(method = "glm")
+@
+
+\subsection*{Driver species}
 
@@
 The authors thank Dr.
-Takeuki Uno for the insight provided to find the set of all maximum matching algorithms, and Bernat Bramon and Marilia Gaiarsa for feedback in early stages of the project.
+Takeuki Uno for the insight provided to find the set of all maximum matching algorithms, and Bernat Bramon, Matthew Hutchinson and Marilia Gaiarsa for feedback in early stages of the project.
 EFC acknowledges the support from the University of Canterbury Doctoral Scholarship, the University of Canterbury Meadow Mushroooms Postgraduate Scholarship, a travel grant from the European Space Agency and a Rutherford Discovery Fellowship (to DBS).

### 2016-03-10 paper/supp_info.Rnw
add some more results

@@
 \usepackage[font=small]{caption}
+\usepackage{subcaption}
 
@@
 mod <- readRDS("./data/V2.0/species_models.rds")
-
+# r_w <- readRDS("./data/V2.0/random_weights.rds") %>% dplyr::tbl_df() %>%
+#   dplyr::rename_("net_name" = ".id")
+r_w_bi <- readRDS("./data/V2.0/random_weights_bi.rds") %>% dplyr::tbl_df() %>%
+  dplyr::rename_("net_name" = ".id")
 @
@@
   \author{\large E. Fernando Cagua}
-  \author{\large Kate Wooton}
+  \author{\large Kate Wootton}
   \author{\large Johanna Voinopol-Sassu}
@@
 
-\section{Number of driver species}
+\section{Manageability}
 
 We calculated the number of driver species neccessary to control the whole community under the assumption that a species that depends more strongly on an interaction partner is controlled by the partner (\autoref{table:n_driver}).
-We tested the robustness of this assumption by comparing the relative number of driver species assuming that a) the dependency assymetry does not imply an unidirectional control direction, rather a species could control all its interaction partners and viceversa, b) that plants depend on pollinators and c) that pollinators depend on plants.
-Our results using the direction of the largest dependency are consistent with the proposed alternatives: although we obtained different absolute numbers of driver species (\autoref{fig:alternative_assumptions}),  their relative numbers are maintained (\autoref{table:corr_driver}).
+We tested the robustness of this assumption by comparing the relative number of driver species assuming that a) the dependency assymetry does not imply an unidirectional control direction, rather a species could control all its interaction partners and vice versa, b) that plants depend on pollinators and c) that pollinators depend on plants (\autoref{fig:alternative_matchings}).
+Our results using the direction of the largest dependency are consistent with the proposed alternatives: although we obtained different absolute numbers of driver species (\autoref{fig:alternative_assumptions}),  their relative numbers are not statistically distinguishable (\autoref{table:corr_driver}).
 
-\begin{table}[h]
+\begin{table}
 \centering
@@
   dplyr::mutate(n_dr = n_pla + n_pol - n_matched,
-                n_dr_p = 1 - n_matched / (n_pla + n_pol))
+                n_dr_p = n_matched / (n_pla + n_pol))
 
@@
   dplyr::select(site, inv, n_pla, n_pol, n_dr, n_dr_p, study) %>%
-  dplyr::arrange(study, site) %>%
+  dplyr::arrange(study, site, inv) %>%
   dplyr::mutate(site = rep(1:dplyr::n_distinct(site), each = 2),
                 inv = plyr::mapvalues(inv, c(TRUE, FALSE), c("yes", "no")),
-                n_dr_p = paste0(round(n_dr_p * 100), "%"),
+                n_dr_p = round(n_dr_p, digits = 2),
                 study = plyr::mapvalues(study, 
                                         c("bartomeus", "lopezaraiza"),
-                                        c("Bartomeus et al. (2008)",
-                                          "Lopezaraiza-Mikel et al. (2007)"))) %>%
+                                        c("Cap de Creus, Spain",
+                                          "Bristol, United Kingdom"))) %>%
   dplyr::rename_("invaded" = "inv",
@@
                  "No. pol." = "n_pol",
-                 "No. driver spp." = "n_dr",
-                 "prop. driver spp." = "n_dr_p",
+                 "$n_d$" = "n_dr",
+                 "manageability" = "n_dr_p",
                  "source" = "study") %>%
   kable(align = "c", booktabs = T, 
-        linesep = c("", "\\addlinespace"))
+        linesep = c("", "\\addlinespace"), escape = F)
 @
-\caption{\label{table:n_driver} Properties of the analysed plant-pollinator communities.}
+\caption{\label{table:n_driver} Properties of the analysed plant-pollinator communities.
+British networks were assembled by \textcite{Lopezaraiza-Mikel2007}, Spanish networks assembled by \textcite{Bartomeus2008}.}
 \end{table}
 
-\begin{figure}[h]
+\begin{figure}
+\centering
+\begin{subfigure}[c]{0.8\textwidth}
+\centering
+<<fig explain matching pla-pol, echo = FALSE, warning = F, message = F, results = "asis", fig.height=1.4, fig.width=5.75>>=
+my_theme <- theme_bw() +
+	#scale_color_brewer(palette = "Paired") +
+	theme(legend.position = "none",
+				text = element_text(family = "Times"),
+				plot.margin=unit(c(4,0,-4,0),"mm"),
+				panel.margin=unit(c(0,0,0,0),"mm"),
+				# panel.border = element_rect(colour = "grey10", size = 0.5),
+				panel.border = element_blank(),
+				axis.text = element_blank(),
+				axis.ticks.x = element_blank(),
+				axis.ticks.y = element_blank(),
+				axis.title = element_text(size = 9),
+				plot.title = element_text(hjust = 0.05, vjust = -1.5, size = 9),
+				panel.grid = element_blank())
+
+# Function to generate paths between each connected node
+edgeMaker <- function(whichRow, len = 100, curved = TRUE){
+	fromC <- layoutCoordinates[adj_list[whichRow, 1], ]  # Origin
+	toC <- layoutCoordinates[adj_list[whichRow, 2], ]  # Terminus
+
+	# Add curve:
+	graphCenter <- colMeans(layoutCoordinates)  # Center of the overall graph
+	bezierMid <- c(fromC[1], toC[2])  # A midpoint, for bended edges
+	distance1 <- sum((graphCenter - bezierMid)^2)
+	if(distance1 < sum((graphCenter - c(toC[1], fromC[2]))^2)){
+		bezierMid <- c(toC[1], fromC[2])
+	}  # To select the best Bezier midpoint
+	bezierMid <- (fromC + toC + bezierMid) / 3  # Moderate the Bezier midpoint
+	if(curved == FALSE){bezierMid <- (fromC + toC) / 2}  # Remove the curve
+
+	edge <- data.frame(bezier(c(fromC[1], bezierMid[1], toC[1]),  # Generate
+														c(fromC[2], bezierMid[2], toC[2]),  # X & y
+														evaluation = len))  # Bezier path coordinates
+	edge$Sequence <- 1:len  # For size and colour weighting in plot
+	edge$Group <- paste(adj_list[whichRow, 1:2], collapse = ">")
+	return(edge)
+}
+
+sp_names <- c("a[1]", "a[2]", "a[3]", "p[1]", "p[2]")
+
+adj_matrix <- c(0,0,0,0,0,
+								0,0,0,0,0,
+								0,0,0,0,0,
+								1,1,1,0,0,
+								0,1,1,0,0) %>%
+	matrix(nrow = 5, byrow = T) %>%
+	`rownames<-`(sp_names) %>%
+	`colnames<-`(sp_names)
+
+net_exp <- adj_matrix %>% 
+	igraph::graph_from_adjacency_matrix(mode = "directed") 
+igraph::V(net_exp)$type <- c(F, F, F, T, T)
+igraph::E(net_exp)$weight <- 1
+
+layoutCoordinates <- cbind(c(0,1,2,0.5,1.5), 
+													 c(1,1,1,0,0)) %>%
+	`colnames<-`(c("x", "y"))
+
+adj_list <- adj_matrix %>% 
+	reshape2::melt() %>% 
+	dplyr::filter(value > 0)
+
+# Generate an edge path for each pair of connected nodes
+n <- 17
+allEdges <- lapply(1:nrow(adj_list), edgeMaker, len = n, curved = FALSE)
+allEdges <- do.call(rbind, allEdges) %>%
+	dplyr::filter(Sequence != n) %>%
+	dplyr::mutate(Group = factor(Group),
+				 type = Group)
+
+new_lev <- c("m", "u", "u", "m", "u")
+levels(allEdges$type) <- new_lev
+
+nodes <- data.frame(layoutCoordinates) %>%
+	dplyr::mutate(spe = sp_names,
+								spe_c = c("m", "m", "u", "u", "u"), 
+								pos = rep(c(0.25, -0.25), c(3,2)))
+
+p1 <- ggplot(allEdges) +  # Pretty simple plot code
+	geom_path(aes(x = x, y = y, group = Group, colour = type, size = type), 
+						arrow = arrow(type = "closed", angle = 15, length = grid::unit(0.1, "inches"))) + # and taper
+	geom_point(data = nodes,  # Add nodes
+						 aes(x = x, y = y , fill = spe_c), size = 5, pch = 21,
+						 colour = "black") + 
+	geom_text(data = nodes, aes(x = x, y = y + pos, label = spe), size = 3, parse = T) +
+	scale_fill_manual(values = c("#636363", "white")) + 
+	scale_colour_manual(values = c("#636363", "#bdbdbd")) +
+	my_theme + xlab("") + ylab("") + ylim(c(-0.27, 1.26)) +
+ theme(plot.margin=unit(c(4,4,-4,-4),"mm")) +
+	scale_size_manual(values = c(0.5, 0.5))
+
+net_exp <- digraph_bipartite(net_exp)
+adj_matrix <- net_exp %>% igraph::as_adjacency_matrix(sparse = F, type = "upper")
+layoutCoordinates <- cbind(rep(0:4, 2), rep(c(1,0), each = 5)) %>%
+	`colnames<-`(c("x", "y"))
+
+adj_list <- adj_matrix %>% 
+	reshape2::melt() %>% 
+	dplyr::filter(value > 0)
+
+# Generate an edge path for each pair of connected nodes
+n <- 100
+allEdges <- lapply(1:nrow(adj_list), edgeMaker, len = n, curved = FALSE)
+allEdges <- do.call(rbind, allEdges) %>%
+	dplyr::filter(Sequence != n,
+								Sequence != 1) %>%
+	dplyr::mutate(Group = factor(Group),
+				 type = Group)
+
+new_lev <- c("m", "u", "u", "m", "u")
+levels(allEdges$type) <- new_lev
+
+nodes <- data.frame(layoutCoordinates) %>%
+	dplyr::mutate(spe = rep(sp_names, 2),
+								spe_l = c(paste0(sp_names, " %->% phantom(0)"), paste0(sp_names, " %<-% phantom(0)")),
+								spe_c = c(rep("u",5), c("m", "m", "u", "u", "u")), 
+								pos = rep(c(0.25, -0.25), each = 5))
+
+p2 <- ggplot(allEdges) +  # Pretty simple plot code
+	geom_path(aes(x = x, y = y, group = Group, colour = type, size = type)) + # and taper
+	geom_point(data = nodes,  # Add nodes
+						 aes(x = x, y = y, fill = spe_c), size = 5, pch = 21,
+						 colour = "black") + 
+	geom_text(data = nodes, aes(x = x + 0.08, y = y + pos, label = spe_l), parse = T, size = 3) +
+	# coord_flip()  + scale_x_reverse() + scale_y_reverse() +
+	scale_fill_manual(values = c("#636363", "white")) + 
+	scale_colour_manual(values = c("#636363", "#bdbdbd")) +
+	xlim(c(-0.12, 4.12)) + ylim(c(-0.27, 1.26)) +
+	my_theme + xlab("") + ylab("") +
+	scale_size_manual(values = c(0.5, 0.5))
+
+multiplot(p1, p2, layout = matrix(nrow = 1, c(1,1,1,2,2,2,2,2)))
+@
+\caption{plants can drive the abbundance of pollinators but not otherwise}
+\end{subfigure}
+
+\begin{subfigure}[c]{0.8\textwidth}
+\centering
+<<fig explain matching pol-pla, echo = FALSE, warning = F, message = F, results = "asis", fig.height=1.4, fig.width=5.75>>=
+
+sp_names <- c("a[1]", "a[2]", "a[3]", "p[1]", "p[2]")
+
+adj_matrix <- c(0,0,0,1,0,
+								0,0,0,1,1,
+								0,0,0,1,1,
+								0,0,0,0,0,
+								0,0,0,0,0) %>%
+	matrix(nrow = 5, byrow = T) %>%
+	`rownames<-`(sp_names) %>%
+	`colnames<-`(sp_names)
+
+net_exp <- adj_matrix %>% 
+	igraph::graph_from_adjacency_matrix(mode = "directed") 
+igraph::V(net_exp)$type <- c(F, F, F, T, T)
+igraph::E(net_exp)$weight <- 1
+
+layoutCoordinates <- cbind(c(0,1,2,0.5,1.5), 
+													 c(1,1,1,0,0)) %>%
+	`colnames<-`(c("x", "y"))
+
+adj_list <- adj_matrix %>% 
+	reshape2::melt() %>% 
+	dplyr::filter(value > 0)
+
+# Generate an edge path for each pair of connected nodes
+n <- 17
+allEdges <- lapply(1:nrow(adj_list), edgeMaker, len = n, curved = FALSE)
+allEdges <- do.call(rbind, allEdges) %>%
+	dplyr::filter(Sequence != n) %>%
+	dplyr::mutate(Group = factor(Group),
+				 type = Group)
+
+new_lev <- c("m", "u", "m", "u", "u")
+levels(allEdges$type) <- new_lev
+
+nodes <- data.frame(layoutCoordinates) %>%
+	dplyr::mutate(spe = sp_names,
+								spe_c = c("u", "u", "u", "m", "m"), 
+								pos = rep(c(0.25, -0.25), c(3,2)))
+
+p1 <- ggplot(allEdges) +  # Pretty simple plot code
+	geom_path(aes(x = x, y = y, group = Group, colour = type, size = type), 
+						arrow = arrow(type = "closed", angle = 15, length = grid::unit(0.1, "inches"))) + # and taper
+	geom_point(data = nodes,  # Add nodes
+						 aes(x = x, y = y , fill = spe_c), size = 5, pch = 21,
+						 colour = "black") + 
+	geom_text(data = nodes, aes(x = x, y = y + pos, label = spe), size = 3, parse = T) +
+	scale_fill_manual(values = c("#636363", "white")) + 
+	scale_colour_manual(values = c("#636363", "#bdbdbd")) +
+	my_theme + xlab("") + ylab("") + ylim(c(-0.27, 1.26)) +
+ theme(plot.margin=unit(c(4,4,-4,-4),"mm")) +
+	scale_size_manual(values = c(0.5, 0.5))
+
+net_exp <- digraph_bipartite(net_exp)
+adj_matrix <- net_exp %>% igraph::as_adjacency_matrix(sparse = F, type = "upper")
+layoutCoordinates <- cbind(rep(0:4, 2), rep(c(1,0), each = 5)) %>%
+	`colnames<-`(c("x", "y"))
+
+adj_list <- adj_matrix %>% 
+	reshape2::melt() %>% 
+	dplyr::filter(value > 0)
+
+# Generate an edge path for each pair of connected nodes
+n <- 100
+allEdges <- lapply(1:nrow(adj_list), edgeMaker, len = n, curved = FALSE)
+allEdges <- do.call(rbind, allEdges) %>%
+	dplyr::filter(Sequence != n,
+								Sequence != 1) %>%
+	dplyr::mutate(Group = factor(Group),
+				 type = Group)
+
+new_lev <- c("m", "m", "u", "u", "u")
+levels(allEdges$type) <- new_lev
+
+nodes <- data.frame(layoutCoordinates) %>%
+	dplyr::mutate(spe = rep(sp_names, 2),
+								spe_l = c(paste0(sp_names, " %->% phantom(0)"), paste0(sp_names, " %<-% phantom(0)")),
+								spe_c = c(rep("u",5), c("u", "u", "u", "m", "m")), 
+								pos = rep(c(0.25, -0.25), each = 5))
+
+p2 <- ggplot(allEdges) +  # Pretty simple plot code
+	geom_path(aes(x = x, y = y, group = Group, colour = type, size = type)) + # and taper
+	geom_point(data = nodes,  # Add nodes
+						 aes(x = x, y = y, fill = spe_c), size = 5, pch = 21,
+						 colour = "black") + 
+	geom_text(data = nodes, aes(x = x + 0.08, y = y + pos, label = spe_l), parse = T, size = 3) +
+	# coord_flip()  + scale_x_reverse() + scale_y_reverse() +
+	scale_fill_manual(values = c("#636363", "white")) + 
+	scale_colour_manual(values = c("#636363", "#bdbdbd")) +
+	xlim(c(-0.12, 4.12)) + ylim(c(-0.27, 1.26)) +
+	my_theme + xlab("") + ylab("") +
+	scale_size_manual(values = c(0.5, 0.5))
+
+multiplot(p1, p2, layout = matrix(nrow = 1, c(1,1,1,2,2,2,2,2)))
+@
+\caption{pollinators can drive the abbundance of plants but not otherwise}
+\end{subfigure}
+
+\begin{subfigure}[c]{0.8\textwidth}
+\centering
+<<fig explain matching both, echo = FALSE, warning = F, message = F, results = "asis", fig.height=1.4, fig.width=5.75>>=
+
+sp_names <- c("a[1]", "a[2]", "a[3]", "p[1]", "p[2]")
+
+adj_matrix <- c(0,0,0,1,0,
+								0,0,0,1,1,
+								0,0,0,1,1,
+								1,1,1,0,0,
+								0,1,1,0,0) %>%
+	matrix(nrow = 5, byrow = T) %>%
+	`rownames<-`(sp_names) %>%
+	`colnames<-`(sp_names)
+
+net_exp <- adj_matrix %>% 
+	igraph::graph_from_adjacency_matrix(mode = "directed") 
+igraph::V(net_exp)$type <- c(F, F, F, T, T)
+igraph::E(net_exp)$weight <- 1
+
+layoutCoordinates <- cbind(c(0,1,2,0.5,1.5), 
+													 c(1,1,1,0,0)) %>%
+	`colnames<-`(c("x", "y"))
+
+adj_list <- adj_matrix %>% 
+	reshape2::melt() %>% 
+	dplyr::filter(value > 0)
+
+# Generate an edge path for each pair of connected nodes
+n <- 17
+allEdges <- lapply(1:nrow(adj_list), edgeMaker, len = n, curved = FALSE)
+allEdges <- do.call(rbind, allEdges) %>%
+	dplyr::filter(Sequence != n) %>%
+	dplyr::mutate(Group = factor(Group),
+				 type = Group)
+
+new_lev <- c("m", "u", "m", "u", "u", "u", "m", "u", "u", "m")
+dir <- c("m", "m", "m", "m", "m", "u", "u", "u", "u", "u")
+dir2 <- c("m", "u", "m", "u", "u", "u", "m", "m", "u", "m")
+id <- 1:10
+allEdges %<>% dplyr::mutate(dir = type,
+                            dir2 = dir)
+levels(allEdges$type) <- new_lev
+levels(allEdges$dir) <- dir
+levels(allEdges$dir2) <- dir2
+allEdges %<>% 
+  dplyr::mutate(dir = as.numeric(dir),
+                dir2 = as.numeric(dir2),
+                dir = plyr::mapvalues(dir, c(1,2), c(0.03, -0.03)),
+                dir2 = plyr::mapvalues(dir2, c(1,2), c(0.03, -0.03)))
+
+nodes <- data.frame(layoutCoordinates) %>%
+	dplyr::mutate(spe = sp_names,
+								spe_c = c("u", "m", "m", "m", "m"), 
+								pos = rep(c(0.25, -0.25), c(3,2)))
+
+# ggplot(allEdges) +  # Pretty simple plot code
+# 	geom_path(aes(x = x + dir, y = y + dir2, group = Group, colour = type, size = type), 
+# 						arrow = arrow(type = "closed", angle = 15, length = grid::unit(0.1, "inches")))
+
+p1 <- ggplot(allEdges) +  # Pretty simple plot code
+	geom_path(aes(x = x + dir, y = y + dir2, group = Group, colour = type, size = type), 
+						arrow = arrow(type = "closed", angle = 15, length = grid::unit(0.1, "inches"))) + # and taper
+	geom_point(data = nodes,  # Add nodes
+						 aes(x = x, y = y , fill = spe_c), size = 5, pch = 21,
+						 colour = "black") + 
+	geom_text(data = nodes, aes(x = x, y = y + pos, label = spe), size = 3, parse = T) +
+	scale_fill_manual(values = c("#636363", "white")) + 
+	scale_colour_manual(values = c("#636363", "#bdbdbd")) +
+	my_theme + xlab("") + ylab("") + ylim(c(-0.27, 1.26)) +
+ theme(plot.margin=unit(c(4,4,-4,-4),"mm")) +
+	scale_size_manual(values = c(0.5, 0.5))
+
+net_exp <- digraph_bipartite(net_exp)
+adj_matrix <- net_exp %>% igraph::as_adjacency_matrix(sparse = F, type = "upper")
+layoutCoordinates <- cbind(rep(0:4, 2), rep(c(1,0), each = 5)) %>%
+	`colnames<-`(c("x", "y"))
+
+adj_list <- adj_matrix %>% 
+	reshape2::melt() %>% 
+	dplyr::filter(value > 0)
+
+# Generate an edge path for each pair of connected nodes
+n <- 100
+allEdges <- lapply(1:nrow(adj_list), edgeMaker, len = n, curved = FALSE)
+allEdges <- do.call(rbind, allEdges) %>%
+	dplyr::filter(Sequence != n,
+								Sequence != 1) %>%
+	dplyr::mutate(Group = factor(Group),
+				 type = Group)
+
+new_lev <- c("m", "m", "u", "u", "u", "u", "m", "u", "u", "m")
+levels(allEdges$type) <- new_lev
+
+nodes <- data.frame(layoutCoordinates) %>%
+	dplyr::mutate(spe = rep(sp_names, 2),
+								spe_l = c(paste0(sp_names, " %->% phantom(0)"), paste0(sp_names, " %<-% phantom(0)")),
+								spe_c = c(rep("u",5), c("u", "m", "m", "m", "m")), 
+								pos = rep(c(0.25, -0.25), each = 5))
+
+p2 <- ggplot(allEdges) +  # Pretty simple plot code
+	geom_path(aes(x = x, y = y, group = Group, colour = type, size = type)) + # and taper
+	geom_point(data = nodes,  # Add nodes
+						 aes(x = x, y = y, fill = spe_c), size = 5, pch = 21,
+						 colour = "black") + 
+	geom_text(data = nodes, aes(x = x + 0.08, y = y + pos, label = spe_l), parse = T, size = 3) +
+	# coord_flip()  + scale_x_reverse() + scale_y_reverse() +
+	scale_fill_manual(values = c("#636363", "white")) + 
+	scale_colour_manual(values = c("#636363", "#bdbdbd")) +
+	xlim(c(-0.12, 4.12)) + ylim(c(-0.27, 1.26)) +
+	my_theme + xlab("") + ylab("") +
+	scale_size_manual(values = c(0.5, 0.5))
+
+multiplot(p1, p2, layout = matrix(nrow = 1, c(1,1,1,2,2,2,2,2)))
+@
+\caption{plants can drive the abbundance of pollinators with the same likelyhood than pollinators can modify the abbundance of plants}
+\end{subfigure}
+\caption{\label{fig:alternative_matchings} Here we show one of the possible maximum matching for each of the direction of control assumptions in the same simple plant pollinator network. }
+\end{figure}
+
+\begin{figure}
 \centering
@@
 a_m_driver %>%
-  ggplot(aes(x = type, y = n_driver_rel), parse = T) +
+  ggplot(aes(x = type, y = 1 - n_driver_rel), parse = T) +
   geom_boxplot(size = 0.25, colour = "grey10",
@@
   xlab("") +
-  ylab("proportion of driver species") + 
+  ylab("manageability") + 
   fer_theme + 
@@
 
-\begin{table}[h]
+\begin{table}
 \centering
@@
 
-m_nr <- glm(cbind(n_dr, n_matched) ~ I(n_pla/n_pol) + study, 
+m0 <- glm(cbind(n_dr, n_matched) ~ n_pla * n_pol + study + inv, 
+          data = n_driver, 
+          family = "binomial")
+m_nr <- glm(cbind(n_dr, n_matched) ~ I(n_pla/n_pol) + study + inv, 
+          data = n_driver, 
+          family = "binomial")
+m8 <- glm(cbind(n_dr, n_matched) ~ I(n_pla/n_pol) + inv, 
+          data = n_driver, 
+          family = "binomial")
+m9 <- glm(cbind(n_dr, n_matched) ~ I(n_pla/n_pol) + study, 
           data = n_driver, 
@@
           family = "binomial")
+m3 <- glm(cbind(n_dr, n_matched) ~ I(n_pla + n_pol), 
+          data = n_driver, 
+          family = "binomial")
+m4 <- glm(cbind(n_dr, n_matched) ~ n_pla, 
+          data = n_driver, 
+          family = "binomial")
+m5 <- glm(cbind(n_dr, n_matched) ~ n_pol, 
+          data = n_driver, 
+          family = "binomial")
+m6 <- glm(cbind(n_dr, n_matched) ~ inv, 
+          data = n_driver, 
+          family = "binomial")
+m7 <- glm(cbind(n_dr, n_matched) ~ study + inv, 
+          data = n_driver, 
+          family = "binomial")
 
-ms <- MuMIn::model.sel(m_nr, m1, m2)
+ms <- MuMIn::model.sel(m_nr, m1, m2, m0, m3, m4, m5, m6, m7, m8, m9)
 
-i <- 1:3 # indices of columns with model terms
-response <- "p_d"
+i <- 1:8 # indices of columns with model terms
+response <- "m"
 
@@
   sub("I(n_pla/n_pol)", "r_{p/a}", ., fixed = T) %>%
+  sub("I(n_pla + n_pol)", "n", ., fixed = T) %>%
+  sub("n_pla * n_pol", "n_p + n_a + n_p:n_a", ., fixed = T) %>%
+  sub("n_pla", "n_p", .) %>%
+  sub("inv", "i", .) %>%
+  sub("n_pol", "n_a", .) %>%
   sub("~", '\\\\sim', .) %>%
@@
 @
-\caption{\label{table:n_driver_explanatory} The proportion of species needed to control the network ($p_d$) is largaly influenced by the ratio of plant to pollinator species richness ($r_{p/a}$) but not the location of the community ($s$).}
+\caption{\label{table:n_driver_explanatory} The manageability ($m$) is largaly influenced by the ratio of plant to pollinator species richness ($r_{p/a}$) but not the location of the community ($s$), the plant richness ($n_p$), the pollinator richness ($n_a$), or the total number of species in the community ($n$).
+NOTE: In reality the response variable was cbind($n_d$, $1-n_d$), what's the convention to specify such a model?}
 \end{table}
 
-\section{Visitation frequency vs. pollen deposition}
+\begin{figure}
+\centering
+<<fig randomisations bi, echo = FALSE, warning = F, message = F, fig.height=1.46, fig.width=3.1>>=
+r_bi <- r_w_bi %>%
+  dplyr::inner_join(meta) %>%
+  dplyr::filter(count == "visitation") %>%
+  dplyr::mutate(n_dr = n_pla + n_pol - n_matched)
+
+# non-parametric
+z_scores_bi <- r_bi$method %>%
+  unique() %>%
+  plyr::ldply(function(x){
+    a_m %>%
+      dplyr::filter(type == "z-bi") %>%
+      dplyr::inner_join(meta) %>%
+      dplyr::filter(count == "visitation") %>%
+      dplyr::mutate(n_dr = n_pla + n_pol - n_matched) %>%
+      dplyr::mutate(method = x)
+  }) %>% 
+  dplyr::bind_rows(r_bi) %>%
+  dplyr::group_by(net_name, method) %>%
+  dplyr::mutate(z_r = rank(n_dr, na.last = NA),
+                z_s = qlogis(z_r/n()),
+                z_s = replace(z_s, is.infinite(z_s) & z_s > 0, qlogis(0.999)),
+                z_s = replace(z_s, is.infinite(z_s) & z_s < 0, qlogis(0.001))) %>%
+  dplyr::filter(is.na(sim))
+
+z_scores_bi %<>%
+  plyr::ddply("method", function(x){
+    x %>%
+      dplyr::mutate(sign = t.test(z_s)$p.value)
+  }, .inform = T) %>% 
+  dplyr::group_by(method) %>%
+  dplyr::mutate(m_z = median(z_s)) %>%
+  dplyr::group_by() %>%
+  dplyr::arrange(m_z) %>%
+  dplyr::filter(method %in% c("swsh_both", 
+                              "quasiswap_count"
+                              # "r00_both", 
+                              # "r0_both", 
+                              # "c0_both", 
+                              ))
+
+z_scores_method_order <- unique(z_scores_bi$method)
+
+z_scores_bi %>%
+  dplyr::mutate(method = factor(method, levels = z_scores_method_order),
+                m_n = as.numeric(method),
+                m_n = replace(m_n, m_n == 3, 3.5)) %>%
+  ggplot(aes(x = m_n, y = -1 * z_s)) +
+  # geom_hline(yintercept = c(-0), linetype = 2, alpha = 0.7, size = 0.25) + 
+  # geom_vline(xintercept = c(2.75), alpha = 0.6, size = 0.25) +
+  geom_hline(yintercept = 0, size = 0.25, linetype = 2, colour = "grey30") +
+  geom_boxplot(aes(group = method), size = 0.25, colour = "grey10",
+							 outlier.shape = 21, outlier.size = 1) +
+  # geom_point(aes(y = 9, colour = sign <= 0.05), shape = 8, size = 1) +
+  coord_flip() +
+  # scale_fill_manual(values = c("white", "#bdbdbd")) +
+  scale_x_continuous(breaks = c(1, 2, 3.5), labels = rev(c("random\ndependency", "maintain strength\nrandomise degree", "maintain degree\nrandomise strength"))) +
+  xlab("") +
+  ylab("Z-score of emp. manageability") + 
+  fer_theme +
+  theme(axis.text.x = element_text(angle = 90), 
+        legend.position = "none",
+				plot.margin = grid::unit(c(2, 1, 2, 0), "mm"), 
+				# panel.grid.minor.x = element_blank(),
+				panel.grid.minor.y = element_blank())
+
+z_scores_bi %>%
+  ggplot(aes(x = n_pla/n_pol, y = -1 * z_s)) + 
+  geom_point()
+@
+\caption{\label{fig:randomisations_bi} xxx}
+\end{figure}
+
+\section{Driver species}
+
+First we assessed the impotance of each explanatory variable individually. We included the most relevant subset into a more detailed analysis that included first order interactions between them.
+
+\begin{figure}
+\centering
+<<fig species, echo = FALSE, warning = F, message = F, fig.height=2.2, fig.width=6.49>>=
+data_pol <- mod[[1]]@objects[[1]]$data
+data_pla <- mod[[2]]@objects[[1]]$data
+
+expand.grid(d = seq(min(data_pol$d), max(data_pol$d), by = 1),
+            S_d = seq(min(data_pol$S_d), max(data_pol$S_d), length = 20), 
+            n = seq(min(data_pol$n), max(data_pol$n), length = 3), 
+            S_v = mean(data_pol$S_v)) %>%
+  dplyr::mutate(q = predict.glmulti(mod[[1]], 
+                                    select = 0.95, 
+                                    newdata = .)$averages %>%
+                  as.vector(), 
+                p = plogis(q)) %>%
+  dplyr::mutate(n = factor(n, 
+                           levels = seq(min(data_pol$n), max(data_pol$n), length = 3),
+                           labels = c("low", "mean", "high"))) %>%
+  ggplot(aes(x = d, y = S_d, z = p)) +
+  geom_tile(aes(fill = p)) +
+  scale_fill_gradient(name = "relative\nimportance", high = "#f0f0f0", low = "#525252") +
+  scale_x_continuous(expand = c(0,0)) +
+  scale_y_continuous(expand = c(0,0)) +
+  facet_wrap(~n) +
+  xlab("degree") +
+  ylab("strength of dependencies") +
+  stat_contour(colour = "black", size = 0.25) +
+  fer_theme
+
+@
+\caption{\label{fig:prediction} aSS }
+\end{figure}
+
+\section{Visitation as a proxy for species interdependence}
 
 The number of driver species in a pollination community and the relative importance of each species depend both of the strength of mutual dependencies between plant pollinators and the structure of the pollination network.
-Traditionally pollination networks have been represented using visitation frequency, but a flower visitor is not necessarely a pollinator.
-It has been shown that wether pollination networks are represented using visitation or actual pollen deposition can have effects on the network structure and presumably on the strength of mutuial dependency.
+Traditionally pollination networks have been constructed on the basis of visitation frequency, but not all flower visitor are necessarily a pollinator.
+It has been shown that whether or not pollination networks are represented using visitation or actual pollen deposition can have effects on the network structure and presumably on the strength of mutuial dependency \autocite{Alarcon2010}.
 
@@
 
-Deposition networks, a proxy pollinator efficiency, were quantified using the mean Single Visit Deposition---the number of conspecific pollen grains effectively deposited on a virgin stigma during a single visit by a particular animal \autocite{NeEman2010,King2013,Ballantyne2015}.
+Deposition networks were quantified using the mean Single Visit Deposition---the number of conspecific pollen grains effectively deposited on a virgin stigma during a single visit by a particular animal \autocite{NeEman2010,King2013,Ballantyne2015}.
 Visitation networks were constructed counting the visits to flowers during Single Visit Depositions.
@@
 We first investigated the effects at a network scale.
-Despite marked differences in the distribution of weights of the three networks (\autoref{fig:ballantyne-ntw}), the minimum number of driver species to control the whole community was consistent among the three different approaches \Sexpr{round(n_driver$n_driver[n_driver$net_name == "bal_eff"]*100)}\% for deposition, \Sexpr{round(n_driver$n_driver[n_driver$net_name == "bal_vis"]*100)}\% for the visitation, and \Sexpr{round(n_driver$n_driver[n_driver$net_name == "bal_imp"]*100)}\% for the pollinator importance network).
+Despite marked differences in the distribution of weights of the three networks (\autoref{fig:ballantyne-ntw}), the minimum number of driver species to control the whole community was consistent among the three different approaches (\Sexpr{1-round(n_driver$n_driver[n_driver$net_name == "bal_eff"], digits = 2)} for deposition, \Sexpr{1-round(n_driver$n_driver[n_driver$net_name == "bal_vis"], digits = 2)} for the visitation, and \Sexpr{1-round(n_driver$n_driver[n_driver$net_name == "bal_imp"], digits = 2)} for the pollinator importance network).
 
-The choice of weighting used can also have an impact on the realtive importance of species.
-Therefore we calculated the frequency that each species is present in the possible sets of driver species under the three schemes.
-Although visitation and deposition produce strikingly different results, we found a very strong agreement between the order produced by visitation and importance (\autoref{table:corr_weights}).
-Arguably, visitation best reflects the dependency of animals to plants, as usually animals forage for pollen or nectar regardless of wether effective pollination occurs or not.
-Contrastingly, importance, the product between visit frequency and pollinator effectiveness, best relefect the dependency of plants to animals.
-
-Finally, we investigated whether the asymmetry of mutual dependency, which defines the direction of control, was consistent among the three posible weighting schemes.
-We found again that the direction of the dominant dependency was mantained was consistent for 95\% of the interactions weighted by visitation or importance (\autoref{table:corr_weights}), the two most appropriate metrics for pollinator and plant dependency.
-
-All together, evidence supports the idea that visitation is a suitable metric to estimate the mutual dependency of species pairs.
-First it is directly related to pollinator foraging.
-Second it produces results consistent, at least within our controllability framework, with plant reproductive success (as estimated by the importance metric).
-
-\begin{figure}[h]
+\begin{figure}
 \centering
@@
 
-\begin{table}[h]
+The choice of weighting used can also have an impact on the realtive importance of species.
+Therefore we calculated the frequency that each species is present in the possible sets of driver species under the three schemes.
+Although visitation and deposition produce strikingly different results, we found a very strong agreement between the order produced by visitation and importance (\autoref{table:corr_weights}).
+Arguably, visitation best reflects the dependency of animals to plants, as usually animals forage for pollen or nectar regardless of wether effective pollination occurs or not.
+Contrastingly, importance, the product between visit frequency and pollinator effectiveness, best relefect the dependency of plants to animals.
+
+\begin{table}
 \centering
@@
 
-\begin{figure}[h]
-\centering
-<<fig species, echo = FALSE, warning = F, message = F, fig.height=2.2, fig.width=6.49>>=
-data_pol <- mod[[1]]@objects[[1]]$data
-data_pla <- mod[[2]]@objects[[1]]$data
+Finally, we investigated whether the asymmetry of mutual dependency, which defines the direction of control, was consistent among the three posible weighting schemes.
+We found again that the direction of the dominant dependency was mantained was consistent for 95\% of the interactions weighted by visitation or importance (\autoref{table:corr_weights}), the two most appropriate metrics for pollinator and plant dependency.
 
-expand.grid(d = seq(min(data_pol$d), max(data_pol$d), by = 1),
-            S_d = seq(min(data_pol$S_d), max(data_pol$S_d), length = 20), 
-            n = seq(min(data_pol$n), max(data_pol$n), length = 3), 
-            S_v = mean(data_pol$S_v)) %>%
-  dplyr::mutate(q = predict.glmulti(mod[[1]], 
-                                    select = 0.95, 
-                                    newdata = .)$averages %>%
-                  as.vector(), 
-                p = plogis(q)) %>%
-  dplyr::mutate(n = factor(n, 
-                           levels = seq(min(data_pol$n), max(data_pol$n), length = 3),
-                           labels = c("low", "mean", "high"))) %>%
-  ggplot(aes(x = d, y = S_d, z = p)) +
-  geom_tile(aes(fill = p)) +
-  scale_fill_gradient(name = "relative\nimportance", high = "#f0f0f0", low = "#525252") +
-  scale_x_continuous(expand = c(0,0)) +
-  scale_y_continuous(expand = c(0,0)) +
-  facet_wrap(~n) +
-  xlab("degree") +
-  ylab("strength of dependencies") +
-  stat_contour(colour = "black", size = 0.25) +
-  fer_theme
-
-@
-\caption{\label{fig:prediction} aSS }
-\end{figure}
-
-\section{Relative importance of species}
-
-First we assessed the impotance of each explanatory variable individually. We included the most relevant subset into a more detailed analysis that included first order interactions between them.
+All together, evidence supports the idea that visitation is a suitable metric to estimate the mutual dependency of species pairs.
+First it is directly related to pollinator foraging.
+Second it produces results consistent, at least within our controllability framework, with plant reproductive success (as estimated by the importance metric).
 

### 2016-03-13 paper/manuscript.Rnw
recalculate species properties

@@
 
-We found that the manageability of empirical networks is not significantly different to that of network randomisations that maintained the species strength but different to those that maintained species degree (two tailed t-test, $p = \Sexpr{round(unique(dplyr::filter(z_scores, method == "quasiswap_count")$sign), digits = 3)}$ and \Sexpr{round(unique(dplyr::filter(z_scores, method == "swsh_both")$sign), digits = 3)} respectively; \autoref{fig:randomisations}).
-This result was also robust to the assumption that bidirectional shit (FIgure Sx)\todo{finish those analysis}.
-
-found that species strength and not degree structures the manageability of empirical networks (). 
-We examined the role that the asimmetry of the dependencies which defines the direction of control has a central role in structuring the controlability of polination networks.
-We found that empirical networks have a much larger  the importance of dependency
+We found that the manageability of empirical networks varied little when compared to network randomisations that maintained the species strength or species degree (two tailed t-test, $p = \Sexpr{round(unique(dplyr::filter(z_scores, method == "quasiswap_count")$sign), digits = 3)}$ and \Sexpr{round(unique(dplyr::filter(z_scores, method == "swsh_both")$sign), digits = 3)} respectively; \autoref{fig:randomisations}).
+This results were also broadly consistent with those obtained including both dependencies (Figure S3).
+Contrastingly, empirical networks have are much harder to manage than network randomisations in which the direction of the dependencies is altered but the structure is maintained.
 
@@
 @
-\caption{\label{fig:randomisations} The (\textasteriskcentered indicates a significant difference)}
+\caption{\label{fig:randomisations} The manageability of empirical networks is much smaller than those of network randomisations in which the direction of dependencies has been randomised.
+In contrast the manageability of network randomisations that mantain the strength or the degree of species.
+The grey filling indicates that the Z-score is significantly different from zero (t-test, $p < 0.05$).}
 \end{figure}

### 2016-03-13 paper/supp_info.Rnw
recalculate species properties

@@
 library(Hmisc)
+library(MuMIn)
 opts_knit$set (root.dir=normalizePath('../'))

### 2016-03-13 code/V2.0/08-species_properties.R

@@ -47,7 +47,7 @@ plyr::ldply(net, function(n){
     plyr::ldply(function(x) dplyr::add_rownames(as.data.frame(x))) %>%
     dplyr::select_("rowname", "nestedcontribution") %>% 
     dplyr::rename(species = rowname)
-  
+   
   dplyr::inner_join(d1, d2)
 }, .parallel = TRUE) %>%
   dplyr::rename_("net_name" = ".id") %>%

### 2016-04-22 paper/manuscript.Rnw
update manuscript

--- 2016-03-08 paper/manuscript.Rnw
@@
 \usepackage{newtxmath}
+\usepackage{xfrac}
 
@@
 
-\onehalfspacing
+\doublespacing
 
@@
 \maketitle
+
+\iffalse
 
@@
 library(Hmisc)
+library(lme4)
 opts_knit$set (root.dir=normalizePath('../'))
@@
 	plyr::l_ply(source)
-
-# figure counter
-fig_count <- dplyr::data_frame(ref = "NA", count = 0)
-fig_n <- function(ref) {
-  fig_count <<- rbind(fig_count,
-                      dplyr::data_frame(ref = ref,
-                                        count = dplyr::last(fig_count$count) + 1))
-  return(dplyr::last(fig_count$count))
-}
-fig_r <- function(ref) fig_count$count[fig_count$ref == ref]
-
-# table counter
-tbl_count <- dplyr::data_frame(ref = "NA", count = 0)
-tbl_n <- function(ref) {
-  tbl_count <<- rbind(tbl_count,
-                      dplyr::data_frame(ref = ref,
-                                        count = dplyr::last(tbl_count$count) + 1))
-  return(dplyr::last(tbl_count$count))
-}
-tbl_r <- function(ref) tbl_count$count[tbl_count$ref == ref]
 @
@@
 n_matched <- readRDS("./data/V2.0/n_matched.rds")
-m_f <- readRDS("./data/V2.0/matching_frequency.rds")
+a_m <- readRDS("./data/V2.0/n_matched_all_types.rds") 
 r_w <- readRDS("./data/V2.0/random_weights.rds") %>% dplyr::tbl_df() %>%
@@
 s_p <- readRDS("./data/V2.0/species_properties.rds") %>% dplyr::tbl_df()
-mod <- readRDS("./data/V2.0/species_models.rds")
+# mod <- readRDS("./data/V2.0/species_models.rds")
+driver <- c("./data/V2.0/matching_frequency") %>% 
+  list.files(full.names = T) %>%
+  lapply(list.files, full.names = T) %>% 
+  unlist() %>% 
+  lapply(read_allRDS)
+prop <- expand.grid(c("asymmetry", "max_dep"), 
+                    c("scaled_FALSE", "scaled_TRUE")) %>% plyr::alply(1)
+driver <- mapply(function(x, y){
+  attr(x, "type") <- as.character(y[,1])
+  attr(x, "scaled") <- stringr::str_split(as.character(y[,2]), "_") %>% unlist() %>% extract(2) %>% as.logical()
+  return(x)
+}, driver, prop)
+driver_bi <- "./data/V2.0/matching_frequency_bi" %>% 
+  read_allRDS()
+mod <- readRDS("./data/V2.0/detailed_species_models.rds")
+mo <- readRDS("./data/V2.0/detailed_species_models_data.rds")
 @
@@
 However whether this influence is translated into a driver role has not been tested.
+
+\fi
+
+\section*{Introduction}
 Here we use plant pollinator communities to investigate the number of species that should be managed to control population dynamics of the whole community, the characteristics that determine whether a species should be managed or not and how invasive species fit.
@@
 
-To investigate the dynamic controllability of pollination networks, we used data from ten paired plant-pollinator communities.
-Each pair was composed by a community invaded by a plant and a community effectively free of the invasive species (Table S1).
-The networks were constructed from previously published pollination visitation data collected from pollination communities in Bristol, UK \autocite{Lopezaraiza-Mikel2007} and Cap de Creus National Park, Spain \autocite{Bartomeus2008}.
-In the four British uninvaded communities the non-invaded plots were obtained by experimentally removing all the flowers of invasive species \textit{Impatients grandulifera}.
-In contrast, the Spanish uninvaded communities were obtained from plots that had not yet been colonised by the invasive species \textit{Carpobrotus affine acinaciformis} or \textit{Opuntia stricta}.
+\subsection*{Maximum matching}
 
-All analysis were performed in R 3.2.2 using bipartite 2.05, igraph 1.0.1, lme4 1.0-6, MuMIn 1.15.6, and vegan 2.3-3 \autocite{RCoreTeam2015, Dormann2008, Csardi2006a, Bates2014, Barton2016, Oksansen2016}.
+The number of nodes necessary to fully control a complex network can be calculated by counting the number of unmatched nodes in the network's maximum matching \autocite{Liu2011}.
+In a directed network a matching is a subset of links in which no two links share a common starting node or a common ending node and node is matched if it is the ending node of one of the links in the matching (\autoref{fig:explain_mm}a).
+A matching is  maximum if the number of matched liks (matching size) is maximal, and the sum of the weights of the matched links (matching weight) is the largest possible among all possible matchings \autocite{West2001}.
 
-\subsection*{Manageability}
-
-Changes on the abbundances of a species can modify the abbundances of those species it interacts with.
-We exploit this concept to quantify the \textit{manageability} of an ecological community (\autoref{eq:m}).
-\todo{need ecological justification; why is $n_d$ a good metric?} Manageability is directly related to the minimum number of species on which we would need to apply management interventions if we were to gain full control of the abbundances of all species in the ecological community, $n_d$.
-We calculated $n_d$ by finding the maximum matching of the pollination network in each community (Box 1).
-
-\begin{equation} \label{eq:m}
-m = 1- \frac{n_d}{n}
-\end{equation}
-
-\begin{tcolorbox}[float, title= Box 1: Maximum matching,colback=white,fontupper=\small]
-\parskip=0.5em
-
-It has been shown that the number of nodes (here species) necessary to fully control a complex network, can be calculated by counting the number of unmatched nodes \autocite{Liu2011}.
-In a directed network, like the simple pollination network shown on the left, a matching is a subset of links in which no two links share a common starting species or a common ending species---dark grey links---and a node is matched if it is the ending node of one of the links in the matching---dark grey nodes \autocite{West2001}.
-
-<<fig explain matching, echo = FALSE, warning = F, message = F, results = "asis", fig.height=1.4, fig.width=5.75>>=
-my_theme <- theme_bw() +
-	#scale_color_brewer(palette = "Paired") +
-	theme(legend.position = "none",
-				text = element_text(family = "Times"),
-				plot.margin=unit(c(4,0,-4,0),"mm"),
-				panel.margin=unit(c(0,0,0,0),"mm"),
-				# panel.border = element_rect(colour = "grey10", size = 0.5),
-				panel.border = element_blank(),
-				axis.text = element_blank(),
-				axis.ticks.x = element_blank(),
-				axis.ticks.y = element_blank(),
-				axis.title = element_text(size = 9),
-				plot.title = element_text(hjust = 0.05, vjust = -1.5, size = 9),
-				panel.grid = element_blank())
-
-# Function to generate paths between each connected node
-edgeMaker <- function(whichRow, len = 100, curved = TRUE){
-	fromC <- layoutCoordinates[adj_list[whichRow, 1], ]  # Origin
-	toC <- layoutCoordinates[adj_list[whichRow, 2], ]  # Terminus
-
-	# Add curve:
-	graphCenter <- colMeans(layoutCoordinates)  # Center of the overall graph
-	bezierMid <- c(fromC[1], toC[2])  # A midpoint, for bended edges
-	distance1 <- sum((graphCenter - bezierMid)^2)
-	if(distance1 < sum((graphCenter - c(toC[1], fromC[2]))^2)){
-		bezierMid <- c(toC[1], fromC[2])
-	}  # To select the best Bezier midpoint
-	bezierMid <- (fromC + toC + bezierMid) / 3  # Moderate the Bezier midpoint
-	if(curved == FALSE){bezierMid <- (fromC + toC) / 2}  # Remove the curve
-
-	edge <- data.frame(bezier(c(fromC[1], bezierMid[1], toC[1]),  # Generate
-														c(fromC[2], bezierMid[2], toC[2]),  # X & y
-														evaluation = len))  # Bezier path coordinates
-	edge$Sequence <- 1:len  # For size and colour weighting in plot
-	edge$Group <- paste(adj_list[whichRow, 1:2], collapse = ">")
-	return(edge)
-}
+\begin{figure}
+\centering
+<<fig explain mm, echo = FALSE, warning = F, message = F, results = "asis", fig.height=1.6, fig.width=6.2>>=
 
@@
 	dplyr::mutate(spe = sp_names,
-								spe_c = c("u", "u", "m", "m", "m"), 
-								pos = rep(c(0.25, -0.25), c(3,2)))
+								spe_c = c("m", "m", "u", "m", "u"), 
+								pos = rep(c(0.3, -0.3), c(3,2)))
 
@@
 						 colour = "black") + 
-	geom_text(data = nodes, aes(x = x, y = y + pos, label = spe), size = 3, parse = T) +
+	geom_text(data = nodes, aes(x = x, y = y + pos, label = spe), size = 3, parse = T, family = "Times") +
 	scale_fill_manual(values = c("#636363", "white")) + 
 	scale_colour_manual(values = c("#636363", "#bdbdbd")) +
-	my_theme + xlab("") + ylab("") + ylim(c(-0.27, 1.26)) +
+	my_theme + xlab("") + ylab("") + 
+  	xlim(c(-0.09, 2.09)) + ylim(c(-0.48, 1.48)) +
  theme(plot.margin=unit(c(4,4,-4,-4),"mm")) +
-	scale_size_manual(values = c(0.5, 0.5))
+	scale_size_manual(values = c(0.5, 0.5)) +
+  ggtitle("a) directed network")
 
@@
 								spe_l = c(paste0(sp_names, " %->% phantom(0)"), paste0(sp_names, " %<-% phantom(0)")),
-								spe_c = c(rep("u",5), c("u", "u", "m", "m", "m")), 
-								pos = rep(c(0.25, -0.25), each = 5))
+								spe_c = c(c("m", "m", "u", "m", "u"), rep("u",5)), 
+								pos = rep(c(0.3, -0.3), each = 5))
 
@@
 						 colour = "black") + 
-	geom_text(data = nodes, aes(x = x + 0.08, y = y + pos, label = spe_l), parse = T, size = 3) +
+	geom_text(data = nodes, aes(x = x + 0.08, y = y + pos, label = spe_l), parse = T, size = 3, family = "Times") +
 	# coord_flip()  + scale_x_reverse() + scale_y_reverse() +
@@
 	scale_colour_manual(values = c("#636363", "#bdbdbd")) +
-	xlim(c(-0.12, 4.12)) + ylim(c(-0.27, 1.26)) +
+	xlim(c(-0.12, 4.12)) + ylim(c(-0.48, 1.48)) +
 	my_theme + xlab("") + ylab("") +
-	scale_size_manual(values = c(0.5, 0.5))
+	scale_size_manual(values = c(0.5, 0.5)) +
+  ggtitle("b) alternative bipartite representation")
 
@@
 @
+\caption{\label{fig:explain_mm}  One of the possible maximum matchings of a network (dark grey links) defines a set matched ($p_1$, $p_2$, and $a_3$) and unmatched nodes ($a_1$ and $a_2$).
+The minimum number of species neccessary to control this network equates to the number of unmatched nodes $n_d = 2$.
+Superior nodes (dark grey circles) drive the dynamics of other species and are therefore important for the controlability of the network because they either require external input or because the are part of the chain that transmit the external imputs to other species.}
+\end{figure}
 
-To find the maximum matching we used a bipartite representation of the network, like the one on the right, in which the levels indicate the outgoing and incoming links to each node.
-Finding a matching here is equivalent to finding the links such that each node on the top is matched to at most one node on the bottom and vice versa \autocite{West2001}.
-The maximum matching is the one in which the matched links have the largest possible weight among all possible matchings.
+To find the maximum matching in a pollination network we used an alternative bipartite representation of the network (\autoref{fig:explain_mm}b) in which the levels indicate the outgoing and incoming links to each node.
+Finding a matching in this alternative representation is equivalent to finding the set of links such that each node on the top level is matched to at most one node on the bottom level and vice versa \autocite{West2001, Csardi2006a}.
 
-The use of a maximum matching has also an intuitive explanation.
-In control theory lingo, a network is fully controlable when each node in the network has a "superior" or input that drives its dynamics.
+The link between network controllability and the maximum matching also has an intuitive basis.
+In control theory, a network is fully controlable when each node in the network has a "superior", or input that drives its dynamics.
 Matched nodes can be controled within the network by the node pointing to it---its superior.
-However, unmatched nodes have no superior in the network and must be directly controlled by external inputs---what we refer to as management interventions \autocite{Liu2011}.
+However, unmatched nodes have no superior in the network and must be directly controlled by external inputs \autocite{Liu2011}, what we refer to as management interventions .
 
-The size of the maximum matching is therefore directly related to its \textit{manageability} because systems that require a large number of inputs are more difficult to control.
-The manageability of the shown network is $m = 0.6$ because in theory, it is possible to guide the community to a desired state by applying management interventions to two of the five species in the community ($n_d = 2$; $a_1$ and $a_2$ in the depicted maximum matching).
+\subsection*{Manageability}
 
-\end{tcolorbox}
+Systems that require a large number of inputs are more difficult to control.
+The \textit{manageability} of a community is therefore determined by the minimum number of species on which we would need to apply management interventions if we were to gain full control of the abbundances of all species in the ecological community ($n_d$, \autoref{eq:m}).
 
-We assumed that for a pair of interacting species the direction of control is inverse to the direction of dependency.
-If, for instance, a plant species depends more on a pollinator species than the pollinator depends on the plant, we expect the plant abbundances to be more sensitive to changes in the pollinator abbundance than vice versa.
-Violation of this assumption, however, renders qualitatively consistent results (Figure S1; Table S2).
-Therefore, we first assigned a single direction to each link between plants and pollinators based on the direction the assymetries in dependencies based on visitation frequencies following \textcite{Bascompte2006}.
-The dependency of plant $i$ on pollinator $j$ is the proportion of the visits comming from pollinator $j$ compared to all pollinator visits to plant $i$.
-Likewise, the dependency of pollinator $j$ on plant $i$ is the ratio of the visits by pollinator $j$ to plant $i$ and all visits of pollinator $j$.
+\begin{equation} \label{eq:m}
+m = 1- \frac{n_d}{s}
+\end{equation}
 
-\todo{really?
-maybe Jason can help with a citation?
-or is there a better justification?}Intuitively, there is a relationship between diversity and manageability.
+We quantified the manageability of ten paired plant-pollinator communities.
+Each pair was composed by a community invaded by a plant and a community effectively free of the invasive species (Table S1).
+The networks were constructed from previously published visitation data collected from pollination communities in Bristol, UK \autocite{Lopezaraiza-Mikel2007} and Cap de Creus National Park, Spain \autocite{Bartomeus2008}.
+In the four British uninvaded communities the non-invaded plots were obtained by experimentally removing all the flowers of invasive species \textit{Impatients grandulifera}.
+In contrast, the Spanish uninvaded communities were obtained from plots that had not yet been colonised by the invasive species \textit{Carpobrotus affine acinaciformis} or \textit{Opuntia stricta}.
+
+The analysed networks were quantified using visitation frequency, which has been shown to be an appropriate surrogate for inter-specific effects in pollination networks \autocite{Vazquez2005, Bascompte2006}.
+Nevertheless we evaluated the effect of using pollinator efficiency or importance as measures of species interactions \autocite{NeEman2010, Ballantyne2015} and found consistent results (see Supplementary Information).
+
+\subsubsection*{Interspecific effects}
+
+Our maximum matching algotithm requires a directed network in which a link between species $i$ and $j$ pointing to species $j$ indicates that the abundance of species $j$ can be affected by the abundance of species $i$.
+The extent to which a pair of interacting species affect each other---the mutualism strengtht---can be quantified by the magnitude of the mutual dependence \autocite{Bascompte2006}.
+Therefore, we initially assumed that a pair of interacting species can affect each other abundances.
+The effect on each other being inverselly proportional to the magnitude of the dependencies.
+This assumption renders a bipartite network in which interacting pairs are connected by two directed links (\autoref{fig:explain_cd}b).
+
+\begin{figure}
+\centering
+<<fig explain control direction, echo = FALSE, warning = F, message = F, results = "asis", fig.height=1.5, fig.width=6.2>>=
+sp_names <- c("a[1]", "a[2]", "a[3]", "p[1]", "p[2]")
+
+adj_matrix <- c(0,0,0,0,0,
+								0,0,0,0,1,
+								0,0,0,0,0,
+								1,1,1,0,0, 
+								0,0,1,0,0) %>%
+	matrix(nrow = 5, byrow = T) %>%
+	`rownames<-`(sp_names) %>%
+	`colnames<-`(sp_names)
+
+net <- adj_matrix %>% 
+	igraph::graph_from_adjacency_matrix(mode = "directed") 
+igraph::V(net)$type <- c(F, F, F, T, T)
+igraph::E(net)$weight <- 1
+
+layoutCoordinates <- cbind(c(0,1,2,0.5,1.5), 
+													 c(1,1,1,0,0)) %>%
+	`colnames<-`(c("x", "y"))
+
+adj_list <- adj_matrix %>% 
+	reshape2::melt() %>% 
+	dplyr::filter(value > 0)
+
+# Generate an edge path for each pair of connected nodes
+n <- 17
+allEdges <- lapply(1:nrow(adj_list), edgeMaker, len = n, curved = FALSE)
+allEdges <- do.call(rbind, allEdges) %>%
+	dplyr::filter(Sequence != n) %>%
+	dplyr::mutate(Group = factor(Group),
+				 type = Group)
+
+new_lev <- c("m", "u", "m", "m", "u")
+levels(allEdges$type) <- new_lev
+
+nodes <- data.frame(layoutCoordinates) %>%
+	dplyr::mutate(spe = sp_names,
+								spe_c = c("m", "m", "u", "m", "u"), 
+								pos = rep(c(0.3, -0.3), c(3,2)))
+
+weights <- allEdges %>%
+  dplyr::filter(Sequence == 12) %>%
+  dplyr::mutate(weight = c(1, 2, 1, 1, 2))
+
+p1 <- ggplot(allEdges) +  # Pretty simple plot code
+	geom_path(aes(x = x, y = y, group = Group, size = type), colour = "#bdbdbd") + # and taper
+	geom_point(data = nodes,  # Add nodes
+						 aes(x = x, y = y ), size = 5, pch = 21,
+						 colour = "black", fill = "white") + 
+	# geom_text(data = nodes, aes(x = x, y = y + pos, label = spe), size = 3, parse = T, family = "Times") +
+  geom_point(data = weights, aes(x = x, y= y), size = 2.5, alpha = 0.25, colour = "white") +
+  geom_text(data = weights, aes(x = x, y= y, label = weight), size = 2.5, family = "Times") +
+	scale_fill_manual(values = c("#636363", "white")) + 
+	scale_colour_manual(values = c("#636363", "#bdbdbd")) +
+	my_theme + xlab("") + ylab("") + 
+  	xlim(c(-0.09, 2.09)) + ylim(c(-0.15, 1.15)) +
+ theme(plot.margin=unit(c(4,4,-4,-4),"mm")) +
+	scale_size_manual(values = c(0.5, 0.5)) +
+  ggtitle("a) visitation frequency")
+
+############################
+sp_names <- c("a[1]", "a[2]", "a[3]", "p[1]", "p[2]")
+
+adj_matrix <- c(0,0,0,1,0,
+								0,0,0,1,1,
+								0,0,0,1,1,
+								1,1,1,0,0,
+								0,1,1,0,0) %>%
+	matrix(nrow = 5, byrow = T) %>%
+	`rownames<-`(sp_names) %>%
+	`colnames<-`(sp_names)
+
+net_exp <- adj_matrix %>% 
+	igraph::graph_from_adjacency_matrix(mode = "directed") 
+igraph::V(net_exp)$type <- c(F, F, F, T, T)
+igraph::E(net_exp)$weight <- 1
+
+layoutCoordinates <- cbind(c(0,1,2,0.5,1.5), 
+													 c(1,1,1,0,0)) %>%
+	`colnames<-`(c("x", "y"))
+
+adj_list <- adj_matrix %>% 
+	reshape2::melt() %>% 
+	dplyr::filter(value > 0)
+
+# Generate an edge path for each pair of connected nodes
+n <- 17
+allEdges <- lapply(1:nrow(adj_list), edgeMaker, len = n, curved = FALSE)
+allEdges <- do.call(rbind, allEdges) %>%
+	dplyr::filter(Sequence != n) %>%
+	dplyr::mutate(Group = factor(Group),
+				 type = Group)
+
+new_lev <- c("m", "u", "m", "u", "u", "u", "m", "u", "u", "m")
+dir <- c("m", "m", "m", "m", "m", "u", "u", "u", "u", "u")
+dir2 <- c("m", "u", "m", "u", "u", "u", "m", "m", "u", "m")
+id <- 1:10
+allEdges %<>% dplyr::mutate(dir = type,
+                            dir2 = dir)
+levels(allEdges$type) <- new_lev
+levels(allEdges$dir) <- dir
+levels(allEdges$dir2) <- dir2
+allEdges %<>% 
+  dplyr::mutate(dir = as.numeric(dir),
+                dir2 = as.numeric(dir2),
+                dir = plyr::mapvalues(dir, c(1,2), c(0.03, -0.03)),
+                dir2 = plyr::mapvalues(dir2, c(1,2), c(0.03, -0.03)))
+
+nodes <- data.frame(layoutCoordinates) %>%
+	dplyr::mutate(spe = sp_names,
+								spe_c = c("u", "m", "m", "m", "m"), 
+								pos = rep(c(0.3, -0.3), c(3,2)))
+
+# ggplot(allEdges) +  # Pretty simple plot code
+# 	geom_path(aes(x = x + dir, y = y + dir2, group = Group, colour = type, size = type), 
+# 						arrow = arrow(type = "closed", angle = 15, length = grid::unit(0.1, "inches")))
+
+weights <- allEdges %>%
+  dplyr::filter(Sequence == 12) %>%
+  dplyr::mutate(weight = c("1", "0.5", "0.5", "0.5", "0.5", "0.25", "0.5", "0.25", "0.66", "0.33"))
+
+p2 <- ggplot(allEdges) +  # Pretty simple plot code
+	geom_path(aes(x = x + dir, y = y + dir2, group = Group, size = type), 
+						arrow = arrow(type = "closed", angle = 15, length = grid::unit(0.1, "inches")), colour = "#bdbdbd") + # and taper
+	geom_point(data = nodes,  # Add nodes
+						 aes(x = x, y = y ), size = 5, pch = 21,
+						 colour = "black", fill = "white") +  
+	# geom_text(data = nodes, aes(x = x, y = y + pos, label = spe), size = 3, parse = T, family = "Times") +
+  geom_point(data = weights, aes(x = x + dir*3, y= y), size = 2.5, alpha = 0.25, colour = "white") +
+  geom_text(data = weights, aes(x = x + dir*3, y= y, label = weight), size = 2.5, family = "Times", parse = T) +
+	scale_fill_manual(values = c("#636363", "white")) + 
+	scale_colour_manual(values = c("#636363", "#bdbdbd")) +
+	my_theme + xlab("") + ylab("") + 
+  xlim(c(-0.09, 2.09)) + ylim(c(-0.15, 1.15)) +
+ theme(plot.margin=unit(c(4,4,-4,-4),"mm")) +
+	scale_size_manual(values = c(0.5, 0.5)) +
+  ggtitle("b) mutual dependence")
+
+####################################
+
+sp_names <- c("a[1]", "a[2]", "a[3]", "p[1]", "p[2]")
+
+adj_matrix <- c(0,0,0,0,0,
+								0,0,0,1,1,
+								0,0,0,0,0,
+								1,1,1,0,0,
+								0,0,1,0,0) %>%
+	matrix(nrow = 5, byrow = T) %>%
+	`rownames<-`(sp_names) %>%
+	`colnames<-`(sp_names)
+
+net <- adj_matrix %>% 
+	igraph::graph_from_adjacency_matrix(mode = "directed") 
+igraph::V(net)$type <- c(F, F, F, T, T)
+igraph::E(net)$weight <- 1
+
+layoutCoordinates <- cbind(c(0,1,2,0.5,1.5), 
+													 c(1,1,1,0,0)) %>%
+	`colnames<-`(c("x", "y"))
+
+adj_list <- adj_matrix %>% 
+	reshape2::melt() %>% 
+	dplyr::filter(value > 0)
+
+# Generate an edge path for each pair of connected nodes
+n <- 17
+allEdges <- lapply(1:nrow(adj_list), edgeMaker, len = n, curved = FALSE)
+allEdges <- do.call(rbind, allEdges) %>%
+	dplyr::filter(Sequence != n) %>%
+	dplyr::mutate(Group = factor(Group),
+				 type = Group)
+
+# new_lev <- c("m", "u", "m", "m", "u")
+# levels(allEdges$type) <- new_lev
+
+nodes <- data.frame(layoutCoordinates) %>%
+	dplyr::mutate(spe = sp_names,
+								# spe_c = c("m", "m", "u", "m", "u"), 
+								pos = rep(c(0.3, -0.3), c(3,2)))
+
+weights <- allEdges %>%
+  dplyr::filter(Sequence == 12) %>%
+  dplyr::mutate(weight = c(0.75, 1, 0.5, 0.6, 1, 0.16))
+
+p3 <- ggplot(allEdges) +  # Pretty simple plot code
+	geom_path(aes(x = x, y = y, group = Group), size = 0.5,
+						arrow = arrow(type = "closed", angle = 15, length = grid::unit(0.1, "inches")), colour = "#bdbdbd") + # and taper
+	geom_point(data = nodes,  # Add nodes
+						 aes(x = x, y = y ), size = 5, pch = 21,
+						 colour = "black", fill = "white") + 
+	# geom_text(data = nodes, aes(x = x, y = y + pos, label = spe), size = 3, parse = T, family = "Times") +
+   geom_point(data = weights, aes(x = x, y= y), size = 2.5, alpha = 0.25, colour = "white") +
+  geom_text(data = weights, aes(x = x, y= y, label = weight), size = 2.5, family = "Times") +
+	scale_fill_manual(values = c("#636363", "white")) + 
+	scale_colour_manual(values = c("#636363", "#bdbdbd")) +
+	my_theme + xlab("") + ylab("") + 
+  	xlim(c(-0.09, 2.09)) + ylim(c(-0.15, 1.15)) +
+ theme(plot.margin=unit(c(4,4,-4,-4),"mm")) +
+	# scale_size_manual(values = c(0.5, 0.5)) +
+  ggtitle("c) interaction asymmetry")
+
+###########################
+
+multiplot(p1, p2, p3, cols = 3)
+
+@
+\caption{\label{fig:explain_cd} Mutualistic networks are usually described quantitatively by the relative number of visits between each plant and animal species (a).
+The mutual dependencies between interacting species (b) depend directly on the relative visitation frequency.
+The dependency of plant $i$ on pollinator $j$, $d_{ij}$, is the proportion of the visits coming from pollinator $j$ compared to all pollinator visits to plant $i$.
+Likewise, the dependency of pollinator $j$ on plant $i$, $d_{ji}$, is the ratio of the visits by pollinator $j$ to plant $i$ and all visits of pollinator $j$.
+Nevertheless, mutual dependencies in pollination networks tend to be highly assymetric.
+The relative differences of dependencies (c) then is a good indicator  }
+\end{figure}
+
+Nevertheless, mutual dependencies have been shown to be highly assymetric in natural communities \autocite{Bascompte2006}.
+In other words, if a plant species is largely dependent on a pollinator species, then the pollinator tends to depend only very weakly on the plant.
+This suggest that it may be possible to relax our initial assumption and simplify the network such that interacting species are connected by one directed link when mutual dependencies are assymetric.
+The direction of this link being consistent with the dominant direction of control in the bidirectional case (\autoref{fig:explain_cd}c).
+The extent to which a species $i$ affects species $j$ relative to the extent to which species $j$ affects species $i$ can then be summarised by the interaction asymmetry (\autoref{eq:a}).
+
+\begin{equation} \label{eq:a}
+a(i,j) = \frac{\left | d_{ij}-d_{ji} \right |}{\textup{max}\left ( d_{ij}, d_{ji} \right )}
+\end{equation}
+
+We quantified the manageability of the analysed pollination communities by finding the maximum matching of the corresponding pollination network following the method previously explained.
+If a network had more than one component (two species are in different components if there exist no path between them) we analysed the largest one.
+We then performed a paired Spearman correlation test to compare the manageability obtained when including bidirectional effects between interacting species, and when simplyfing the network to include only the dominant direction of the asymmetry.
+
+Naively one might expect to see a negative relationship between diversity and manageability \autocite{Menge1995}.
 We therefore used a set of generalised linear models to investigate the relatioship between community manageability and (i) the total number of species, (ii) plant richness, (iii) polinators richness, and (iv) the ratio of plants to pollinators richness.
-Because both invaded and British communities tend to be more diverse, we also assesed whether observed differences in manageability were due to these two factors.
+Because both invaded and British communities tended to be more diverse, we also assesed whether observed differences in manageability were due to these two factors.
+Competing models were assessed by comparing the Akaike Information Criterion corrected for small sample sizes (AICc).
 
-To quantify the extent to which the manageability of a pollination community is characteristic of the network structure, we compared it to a suite of random null-models.
-An initial set of null models was based on network randomisations that maintained the species degree (the number of interactions), or that mantained the species strength (total sum of interaction weights).
-Subsequently we calculated the dependencies followed by the manageability of the randomised networks.
-A second set of null models was based on randomisations that mantained the structure of the empirical network but randomised the direction of dependencies between species.
-In all cases we calculated a Z-score between the manageability of each empirical network and the corresponding manageability of 999 randomisations.
+To quantify the extent to which manageability is characteristic of the network structure\todo{failed to come up with a better wording}, we compared the manageability of empirical networks to networks generated by two null models of visitation.
+One set of random visitation networks was generated by maintaining the species degree (the number of interactions per species) while varying the number of visits per species.
+A second set of random network mantained the species strength (total sum of visits) while varying the degree of species \autocite{Oksansen2016}.
+We then calculated the mutual dependences and interaction asymmetries of the random networks and calculated the p-value of the manageability of each empirical network and the corresponding manageability of 999 randomisations.
+
+We also quantified the extent to which the relative manageability of a pollination community is given by the dominant direction of control, we mantained the structure of network but randomised the direction of the interaction asymmetries.
+This is, we first calculated the assymetries for each community and then shuffled the direction of the link between species.
+Similar as in previouls null models, we calculated the p-value of the empirical manageability and that of the randomisations.
 
@@
 
-The manageability of a community, $m$, provides an indication of the magnitude of $n_d$ but not the identity of the species that can compose this set.
-In fact maximum matchings are not unsually unique in ecological networks and different sets of species of size $n_d$ could be used to control the network \autocite{Liu2011}.
-Nevertheless, species vary on the frequency at which they are part of this set; an indication of their relative importance to drive the state of the ecosystem.
+The manageability of a community $m$ provides an indication of the magnitude of $n_d$ but not the identity of the species that can compose this set.
+In fact, maximum matchings are often not unique in ecological networks and different sets of species of size $n_d$ could be used to control the network \autocite{Liu2011}.
+Nevertheless, species vary in terms of the frequency with which they are classified as superior nodes (\autoref{fig:explain_mm}).
+This frequency provides an indication of their relative importance to drive the state of the community.
+We therefore call \textit{driver species} those that are identified as needing directed interventions in all possible matchings\todo{elaborate concept}, and consequently likely to have a disproportionate effect on the abbundances of other species in the community.
 
-We therefore call \textit{driver species} those that are identified as needing directed interventions in the majority of maximum matchings, and therefore likely to have a disproportionate effect on the abbundances of other species in the community.
-We identified the driver species in each of the communities by computing all possible maximum matchings in the network.
+Unlike unweighted networks, where a maximum matching is defined by its size (the number of matched edges), in weighted networks, a maximum matching is one whose edges have the largest possible total weight among all possible matchings.
+This means that in weighted networks there is a number of matchings that have maximal size, but are not maximum matchings because its total weight is not maximal too.
+However the weight of species dependencies is unexact, a reflection of the fact that interaction strengths and sampling methods themselves are stochastic to some extent.
+
+We therefore identified the driver species in each of the networks by computing all possible matchings in the network that have the same size and have a weight above a cut-off of 0.5 times the weight of the maximum matching\todo{justify}.
 To do so, we first generated the network's line graph---an alternative representation in which nodes are the interactions of the original network and links represent common ending points.
 We then calculated the complement of the line graph---a graph in which nodes are adjecent if and only if they are not adjancent in the line graph.
-All possible maximum matchings can be found by enumerating all cliques of size $1-n_d$ in the complement graph \autocite{West2001}.
+All possible maximum matchings can be found by enumerating all cliques of size $1-n_d$ in the complement graph \autocite{West2001, Csardi2006a}.
+Because of the number of matchings depends on the cut-off and the weighting of the links, we evaluated the effects of i) using a different cut-offs value between 0 and 1 and ii) weighting the links by the number of visits.
+
+Similar as when we compared the manageability obtained when assuming bidirectional links or single links determined by the asymmetry (\autoref{fig:explain_cd}), we compared the realtive importance of species under these two assumptions by calculating a paired Spearman correlation test between species' relative importance.
+Nevertheless because we are more interested on the agreement between highly ranked species we also calculated a weighted correlation coefficient $r_{w2}$ which gives more weight to higer ranks (\autoref{PintoDaCosta2015}), and the Jaccard similarity of the driver species identified by both methods.
 
 We then tackled the question whether some species level structural properties can predict the relative importance of driver species.
-Here, we evaluated the effect on the species' relative importance of measures of centrality (degree, betweenness, and overlap), measures related to network robustness (contribution to nestedness), and measures of strength of association (visitation levels).
-Candidate models were compared using AIC and the relative importance of the explanatory variables was evaluated using the sum of Akaike weights over all candidate models \autocite{Burnham2003}.
+Here, we used a Generalised Linear Mixed-Effects model (\autoref{Bates2015}) to evaluate the effect on the species' relative importance of measures of centrality (degree, betweenness, and overlap), measures related to network robustness (contribution to nestedness), and measures of strength of association and depedency (visitation and dependency strength) \autocite{Dormann2008}.
+The community was included as a random effect.
+Candidate models were compared using AIC and the relative importance of the explanatory variables was evaluated using the sum of Akaike weights over candidate models that accounted for 95\% of the evidence \autocite{Burnham2003, Bates2014, Barton2016}.
 
-\subsection*{Visitation as proxy for species interdependence}
-
-Visitation frequency has been shown to be an appropriate surrogate for inter-specific effects in pollination networks \autocite{, Vazquez2005, Bascompte2006}.
-Arguably, visitation reflects adequately the dependency of animals to plants, as usually during a visit animals forage for pollen or nectar regardless of wether effective pollination occurs\todo{any citation Daniel?}.
-Nevertheless visitation is not equivalent to pollen deposition and might be insufficient to reflect the dependencies of plants on animals \autocite{Alarcon2010, King2013}.
-We therefore investigated the effect of calculating the dependencies using pollination effectiveness and importance---two metrics more proximate to plant reproductive sucess.
-
-Pollinator efficiency is measured as ``the number of conspecific pollen grains deposited on a virgin stigma during a single visit by a particular animal'' \autocite{NeEman2010}.
-Pollinator importance on the other hand is defined as the product between visitation frequency and pollinator efficency \autocite{Ballantyne2015}.
-We used data collected by \textcite{Ballantyne2015} from a low diversity pollination community at a dry lowland heathland in Dorset, UK.
-We assessed the differences between visitation, pollinator effectiveness, and pollinator importance by comparing (i) the manageability of the community, (ii) the percentage of interactions that mantained the direction of dependency, and (iii) the Spearman correlation of the relative importance of the species in the community.
+All analysis were performed in R 3.2.2 \autocite{RCoreTeam2015}.
 
@@
 
+\subsection*{Manageability}
+
 <<n_driver, echo = FALSE, warning = F, message = F>>=
 # find n_driver
-n_driver <- n_matched %>%
+n_driver <- a_m %>%
   dplyr::inner_join(meta) %>%
@@
 
-# Wilcoxon signed rank test invasive vs non invasive
-wt <- n_driver %>%
-  dplyr::select(site, inv, n_dr_p) %>%
-  dplyr::filter(!is.na(inv)) %>%
-  dplyr::mutate(n_dr_p = qlogis(n_dr_p)) %>%
-  tidyr::spread(inv, n_dr_p) %>%
-  dplyr::select(-site) %>%
-  as.matrix()
+src_bi_w <- n_driver %>%
+  dplyr::filter(type == "z-bi" | type == "weight",
+                study != "ballantyne") %>%
+  dplyr::select(net_name, type, n_dr_p) %>%
+  tidyr::spread(type, n_dr_p) %$%
+  cor.test(weight, `z-bi`, method = "spearman")
 
+# # Wilcoxon signed rank test invasive vs non invasive
+# wt <- n_driver %>%
+#   dplyr::select(site, inv, n_dr_p) %>%
+#   dplyr::filter(!is.na(inv)) %>%
+#   dplyr::mutate(n_dr_p = qlogis(n_dr_p)) %>%
+#   tidyr::spread(inv, n_dr_p) %>%
+#   dplyr::select(-site) %>%
+#   as.matrix()
 n_driver %<>%
   dplyr::filter(!is.na(inv))
+# wt <-  wilcox.test(x = wt[, 1], y = wt[, 2], paired = T)
 
-wt <-  wilcox.test(x = wt[, 1], y = wt[, 2], paired = T)
+n_driver_wb <- dplyr::filter(n_driver, 
+                             type == "z-bi" | type == "weight")
 
-m0 <- glm(cbind(n_dr, n_sp) ~ n_pla * n_pol, 
-          data = n_driver, 
+# Models
+m0 <- glm(cbind(n_dr, n_matched) ~ n_pla * n_pol + study + inv + type,
+          data = n_driver_wb,
           family = "binomial")
-m_nr <- glm(cbind(n_dr, n_matched) ~ I(n_pla/n_pol) + study, 
-          data = n_driver, 
+m_nr <- glm(cbind(n_dr, n_matched) ~ I(n_pla/n_pol) + study + inv + type,
+          data = n_driver_wb,
           family = "binomial")
-m1 <- glm(cbind(n_dr, n_matched) ~ I(n_pla/n_pol), 
-          data = n_driver, 
+m8 <- glm(cbind(n_dr, n_matched) ~ I(n_pla/n_pol) + inv + type,
+          data = n_driver_wb,
           family = "binomial")
-m2 <- glm(cbind(n_dr, n_matched) ~ study, 
-          data = n_driver, 
+m9 <- glm(cbind(n_dr, n_matched) ~ I(n_pla/n_pol) + study + type,
+          data = n_driver_wb,
+          family = "binomial")
+m1 <- glm(cbind(n_dr, n_matched) ~ I(n_pla/n_pol) + type,
+          data = n_driver_wb,
+          family = "binomial")
+m2 <- glm(cbind(n_dr, n_matched) ~ study + type,
+          data = n_driver_wb,
+          family = "binomial")
+m3 <- glm(cbind(n_dr, n_matched) ~ I(n_pla + n_pol) + type,
+          data = n_driver_wb,
+          family = "binomial")
+m4 <- glm(cbind(n_dr, n_matched) ~ n_pla + type,
+          data = n_driver_wb,
+          family = "binomial")
+m5 <- glm(cbind(n_dr, n_matched) ~ n_pol + type,
+          data = n_driver_wb,
+          family = "binomial")
+m6 <- glm(cbind(n_dr, n_matched) ~ inv + type,
+          data = n_driver_wb,
+          family = "binomial")
+m7 <- glm(cbind(n_dr, n_matched) ~ study + inv + type,
+          data = n_driver_wb,
           family = "binomial")
@@
 
-We found that if we were to control the dynamics of the whole community, we would need to control between \Sexpr{round(min(n_driver$n_dr_p)*100)} and \Sexpr{round(max(n_driver$n_dr_p)*100)}\% (mean \Sexpr{round(mean(n_driver$n_dr_p)*100)}\%) of the species in the community.
-The relative number of driver species did not change if the dependencies were assumed to be bidirectional, or exclusively from plant to pollinators or from pollinators to plants (Figure S1; Table S2).
-In addition we did not detect any significant differences between the proportion of driver species in invaded or uninvaded ecosystems (Wilcoxon signed-rank sum test, $p = \Sexpr{round(wt$p.value, digits = 3)}$) nor between study sites (likelyhood ratio test, $Pr(>\chi^2) = \Sexpr{round(anova(m1, m_nr, test = "LRT")$`Pr(>Chi)`[2], digits = 3)}$; Table S3).
-Nevertheless we found that the ratio of plant to pollinator species richness had an important neggative effect on the proportion of driver species ($Pr(>\chi^2) = \Sexpr{round(anova(m2, m_nr, test = "LRT")$`Pr(>Chi)`[2], digits = 3)}$; \autoref{fig:n_driver_explanatory}, Table S3).
+We found that if we were to control the dynamics of the whole community, we would need to control between \Sexpr{round(min(dplyr::filter(n_driver, type == "z-bi")$n_dr_p)*100)} and \Sexpr{round(max(dplyr::filter(n_driver, type == "z-bi")$n_dr_p)*100)}\% (mean \Sexpr{round(mean(dplyr::filter(n_driver, type == "z-bi")$n_dr_p)*100)}\%) of the species in the community if we were to harness bidirectional links between species, and between \Sexpr{round(min(dplyr::filter(n_driver, type == "weight")$n_dr_p)*100)} and \Sexpr{round(max(dplyr::filter(n_driver, type == "weight")$n_dr_p)*100)}\% (mean \Sexpr{round(mean(dplyr::filter(n_driver, type == "weight")$n_dr_p)*100)}\%) if we only take into account the strongest dependence.
+This corresponds to manageabilities between \Sexpr{round(min(1-dplyr::filter(n_driver, type == "z-bi")$n_dr_p), digits = 2)} to \Sexpr{round(max(1-dplyr::filter(n_driver, type == "z-bi")$n_dr_p), digits = 2)} and \Sexpr{round(min(1-dplyr::filter(n_driver, type == "weight")$n_dr_p), digits = 2)} to \Sexpr{round(max(1-dplyr::filter(n_driver, type == "weight")$n_dr_p), digits = 2)} respectively (Table S1).
+Despite different absolute values of manageability between these assuptions, the relative manageability of different communities was mantained (Spearman rank correlation \Sexpr{round(src_bi_w$estimate, digits = 2)}, $p = \Sexpr{as.numeric(format(src_bi_w$p.value, digits = 2))}$).
+In addition, the ratio of plant to pollinator species richness is positively correlated with manageability ($Pr(>\chi^2) = \Sexpr{as.numeric(format(anova(m8, m6, test = "LRT")$`Pr(>Chi)`[2], digits = 2))}$).
+Similarly, invaded communities tend to be more difficult to manage than uninvaded ones ($Pr(>\chi^2) = \Sexpr{as.numeric(format(anova(m8, m1, test = "LRT")$`Pr(>Chi)`[2], digits = 2))}$).
+In constrast, measures of biodiversity (like plant or pollinator richness) or the location of the study did not have a significant effect on the manageability (\autoref{fig:n_driver_explanatory}, Table S3).
 
@@
 <<fig explaining n_driver, echo = FALSE, warning = F, message = F, results = "asis", fig.height=2.2, fig.width=3.245>>=
-p <- predict(m1, type = "response", se.fit = T)
+p <- predict(m8, type = "response", se.fit = F)
 
-ggplot(data = n_driver,
-       aes(x = n_pla/n_pol, y = 1-n_dr_p)) +
-  geom_ribbon(aes(ymax = 1- (p$fit + 1.96 * p$se.fit), ymin = 1- (p$fit - 1.96 * p$se.fit)),
-              fill = "#f0f0f0") +
-  geom_line(aes(y = 1- p$fit)) +
-  geom_point(aes(fill = study), shape = 21) +
+n_driver_wb %>%
+  dplyr::mutate(fit = predict(m8, type = "response", se.fit = T)$fit,
+                se =  predict(m8, type = "response", se.fit = T)$se) %>%
+  dplyr::filter(type == "z-bi" | type == "weight") %>% 
+  ggplot(aes(x = n_pla/n_pol, y = 1-n_dr_p)) +
+  geom_line(aes(y = 1-fit, colour = type, linetype = inv), size = 0.5) + 
+  geom_point(aes(fill = type, shape = inv), show.legend = T, size = 1.25) +
   ylab("manegeability") + 
@@
   scale_fill_manual(values = c("#ffffff", "#bdbdbd"),
-                    name = "", labels = c("Lopezaraiza-Mikel et al. (2007)",
-                                          "Bartomeus et al. (2008)")) +
+                      name = "direction of control", 
+                      labels = c("asymmetry", "mutual dependence")) +
+  scale_colour_manual(values = c("black", "#bdbdbd"),
+                      name = "direction of control", 
+                      labels = c("asymmetry", "mutual dependence")) + 
+  scale_shape_manual(values = c(21, 23), 
+                     name = "invasion status", 
+                     labels = c("invaded", "non invaded")) +
+  scale_linetype_manual(values = c(1, 12), 
+                        name = "invasion status", 
+                        labels = c("invaded", "non invaded")) +
   fer_theme +
   theme(plot.margin = grid::unit(c(5, 1, 2, 0), "mm"), 
-        legend.key = element_blank(), 
-        legend.position = "none")
+        legend.position = "none", 
+        # legend.title = element_blank(),
+        legend.key = element_rect(fill = "white", 
+                                  colour = "white"),
+        legend.key.size = grid::unit(4, "mm"),
+        legend.background = element_rect(colour = "black", size = 0.2),
+        legend.box = "horizontal",
+        legend.direction = "vertical") 
 @
-\caption{\label{fig:n_driver_explanatory} The proportion of species needed to control the network is largely influenced by the ratio of plant to pollinator species richness  but not the location of the community.
-White dots correspond to communities investigated by \textcite{Bartomeus2008}; grey dots correspond to communities investigated by \textcite{Lopezaraiza-Mikel2007}.}
+\caption{\label{fig:n_driver_explanatory} The relative manageability of a plant-pollinator community is largely influenced by the ratio of plant to pollinator species richness and to a smaller extent to the status of invasion.
+Invaded communities (circles, dashed lines) having larger levels of manageability.
+White and grey points correspond to manageabilities calculated using mutual dependences and interaction asymmetry respectively.}
 \end{figure}
 
-We examined the role that the asimmetry of the dependencies which defines the direction of control has a central role in structuring the controlability of polination networks.
-We found that empirical networks have a much larger  the importance of dependency
-
-\begin{figure}
-\centering
-<<fig randomisations, echo = FALSE, warning = F, message = F, fig.height=2.2, fig.width=3.1>>=
+<<randomisations z_scores, echo = FALSE, warning= FALSE, message = FALSE>>=
 r <- r_w %>%
-  dplyr::bind_rows(r_d) %>%
+  dplyr::bind_rows(dplyr::mutate(r_d, type = "weight")) %>%
   dplyr::inner_join(meta) %>%
-  dplyr::filter(count == "visitation") %>%
+  dplyr::filter(study != "ballantyne") %>%
   dplyr::mutate(n_dr = n_pla + n_pol - n_matched)
@@
     n_driver %>%
+      dplyr::mutate(type = stringr::str_replace(type, "-", "_")) %>%
+      dplyr::filter(type == "weight" | type == "z_bi") %>%
       dplyr::mutate(method = x)
@@
   dplyr::bind_rows(r) %>%
-  dplyr::group_by(net_name, method) %>%
+  dplyr::filter(!(type == "z_bi" & method == "r0")) %>%
+  dplyr::group_by(net_name, method, type) %>%
   dplyr::mutate(z_r = rank(n_dr, na.last = NA),
-                z_s = qlogis(z_r/n()),
-                z_s = replace(z_s, is.infinite(z_s) & z_s > 0, qlogis(0.999)),
+                z_r = z_r/n(),
+                z_s = qlogis(z_r),
+                z_s = replace(z_s, (is.infinite(z_s) & z_s > 0) | z_s > qlogis(0.999), qlogis(0.999)),
                 z_s = replace(z_s, is.infinite(z_s) & z_s < 0, qlogis(0.001))) %>%
   dplyr::filter(is.na(sim))
+
+@
+
+The manageability of empirical networks varied little when compared to network randomisations that maintained the species strength or species degree.
+This result is consistent regardless of whether we consider mutual dependences or the interaction asymmetry.
+Contrastingly, empirical networks have smaller manageabilities than network randomisations in which the direction of the dependencies is altered but the structure is maintained.
+
+\begin{figure}
+\centering
+<<fig randomisations, echo = FALSE, warning = F, message = F, fig.height=2.2, fig.width=3.245>>=
 
@@
 
-z_scores %<>%
-  plyr::ddply("method", function(x){
-    x %>%
-      dplyr::mutate(sign = t.test(z_s)$p.value)
-  }, .inform = T) %>% 
-  dplyr::group_by(method) %>%
-  dplyr::mutate(m_z = median(z_s)) %>%
-  dplyr::group_by() %>%
-  dplyr::arrange(m_z) %>%
-  dplyr::filter(method %in% c("swsh_both", 
-                              "quasiswap_count", 
-                              # "r00_both", 
-                              # "r0_both", 
-                              # "c0_both", 
-                              "r0"))
-
 z_scores_method_order <- unique(z_scores$method)
@@
 z_scores %>%
+  dplyr::group_by() %>%
   dplyr::mutate(method = factor(method, levels = z_scores_method_order),
@@
                 m_n = replace(m_n, m_n == 3, 3.5)) %>%
-  ggplot(aes(x = m_n, y = z_s)) +
+  ggplot(aes(x = method, y = -1 * z_s)) +
+  geom_rect(aes(xmin = 0.5, xmax = 3.5, ymin = -Inf, ymax = qlogis(0.025)), fill = "#f0f0f0") +
+  geom_rect(aes(xmin = 0.5, xmax = 3.5, ymin = Inf, ymax = qlogis(0.975)), fill = "#f0f0f0") +
+
   # geom_hline(yintercept = c(-0), linetype = 2, alpha = 0.7, size = 0.25) + 
-  geom_vline(xintercept = c(2.75), alpha = 0.7, size = 0.25) +
+  geom_vline(aes(xintercept = 2.5), alpha = 0.6, size = 0.25) +
    geom_hline(yintercept = 0, size = 0.25, linetype = 2, colour = "grey30") +
-  geom_boxplot(aes(group = method), size = 0.25, colour = "grey10",
-							 outlier.shape = 21, outlier.size = 1) +
-  geom_point(aes(y = 9, colour = sign <= 0.05), shape = 8, size = 1) +
+  geom_boxplot(aes(fill = type), size = 0.3,
+               colour = "grey10", outlier.shape = 21, outlier.size = 1) +
+  # geom_point(aes(y = 9, colour = sign <= 0.05), shape = 8, size = 1) +
+  scale_fill_manual(values = c("white", "#bdbdbd")) +
+  scale_x_discrete(labels = rev(c("random\nassymetry", "maintain vis. strength\nrandomise degree", "maintain vis. degree\nrandomise strength")), expand = c(0,0)) + 
+  scale_y_continuous(breaks = qlogis(c(0.001, 0.025, 0.5, 0.975,0.999)), 
+                     labels = plogis(qlogis(c(0.001, 0.025, 0.5, 0.975,0.999)))) + 
+  xlab("") +
     coord_flip() +
-  scale_colour_manual(values = c(NA, "black")) +
-  scale_x_continuous(breaks = c(1, 2, 3.5), labels = rev(c("dependency", "strength", "degree"))) + 
-  xlab("") +
-  ylab("number of driver species (z-score)") + 
+  ylab("rank of empirical manageability") + 
   fer_theme +
-  theme(axis.text.x = element_text(angle = 90), 
+  theme(
         legend.position = "none",
@@
 @
-\caption{\label{fig:randomisations} The (\textasteriskcentered indicates a significant difference)}
+\caption{\label{fig:randomisations} The manageability of empirical networks was compared to network randomisations using a normalised rank.
+The shaded areas in light grey ($< 0.025$ and $> 0.975$) suggest a significant difference between the empirical network and its randomisations.
+The empirical manageability is much smaller than those of randomisations in which the direction of assymmetries has been randomised.
+In contrast the manageability of network in which the visitation strength or degree was mantained was not different to the manageability of the empirical networks.
+Dark grey and white boxplots represent manageabilities obtained using mutual dependencies and asymmetries respectively.}
 \end{figure}
 
-<<importance, echo = FALSE, warning = F, message = F>>=
+\subsection*{Driver species}
+
+<<rel importance, echo = FALSE, warning = F, message = F>>=
+d_sp <- driver %>%
+  plyr::ldply(function(x) {
+    get_frequencies(x) %>%
+      dplyr::mutate(type = attr(x, "type"),
+                    scaled = attr(x, "scaled"))
+  })
+
+d_sp_bi <- driver_bi %>%
+  get_frequencies() %>%
+      dplyr::mutate(type = "z_bi",
+                    scaled = FALSE)
+
+d_sp <- dplyr::bind_rows(d_sp, d_sp_bi) %>%
+  dplyr::inner_join(meta)
+# d freq is the best proxy seems to be consistent with the invasive species being at the top rank for the bidirectional links
+# d_sp %>%
+#   dplyr::filter(inv, type == "z_bi") %>%
+#   dplyr::group_by(net_name, threshold) %>% 
+#   dplyr::mutate(d_freq_rank = rank(-d_freq, ties.method = "min")) %>%
+#   dplyr::filter(species %in% c("p_4", "p_25"))
+#
+
+correlations <- expand.grid(type = c("asymmetry", "max_dep"),
+            scaled = c(TRUE, FALSE)) %>%
+  plyr::ddply(c("type", "scaled"), function(x){
+    d_sp %>%
+      dplyr::filter(count == "visitation", 
+                    study != "ballantyne") %>% 
+      plyr::ddply(c("net_name", "threshold"), function(y){
+        u <- y %>% 
+          dplyr::filter(type == "z_bi" | 
+                          (type == x$type & scaled == x$scaled)) %>%
+          dplyr::group_by(type) %>%
+          dplyr::mutate(d_freq_rank = rank(-d_reim)) %>%
+          dplyr::select(species, type, d_freq_rank) %>%
+          tidyr::spread(type, d_freq_rank) %>%
+          `class<-`("data.frame")
+
+        if(ncol(u) == 3) {
+          a <- sets::as.set(u[u[, 2] == min(u[, 2]), 1])
+          b <- sets::as.set(u[u[, 3] == min(u[, 3]), 1])
+          c(rw2(u[,2], u[,3]), rw2(rank(-u[,2]), rank(-u[,3])), cor(u[,2], u[,3], method = "spearman"), sets::set_similarity(a, b))
+        } 
+        else c(NA, NA, NA, NA)
+
+      })
+  })
+
+corr_imp <- expand.grid(type = c("asymmetry", "max_dep"),
+            scaled = c(TRUE, FALSE)) %>%
+  plyr::ddply(c("type", "scaled"), function(x){
+    d_sp %>%
+      dplyr::filter(study == "ballantyne") %>% 
+      plyr::ddply(c("threshold"), function(y){
+        u <- y %>% 
+          dplyr::filter((type == "z_bi" & count == "importance") |
+                          (type == x$type & scaled == x$scaled & count == "visitation")) %>%
+          dplyr::group_by(type) %>%
+          dplyr::mutate(d_freq_rank = rank(-d_reim)) %>%
+          dplyr::select(species, type, d_freq_rank) %>%
+          tidyr::spread(type, d_freq_rank) %>%
+          `class<-`("data.frame")
+
+        if(ncol(u) == 3) rw2(u[,2], u[,3])
+        else NA
+
+      })
+  })
+
+# correlations %>%
+#   ggplot(aes(x = threshold, y = V1, colour = interaction(type, scaled))) +
+#   geom_line(aes(linetype = net_name)) +
+#   geom_smooth(se = F)
+
+# 
+# corr_imp %>%
+#   ggplot(aes(x = threshold, y = V1, colour = interaction(type, scaled))) +
+#   geom_line()
+
+# d_sp %>%
+#   dplyr::group_by(net_name, type, scaled) %>%
+#   dplyr::mutate(importance = rank(-d_reim, ties.method = "min"),
+#                 importance = importance / max(importance)) %>%
+#   dplyr::filter(type == "z_bi" |
+#                   (type == "asymmetry" & scaled == F)) %>%
+#   ggplot(aes(x = net_name, y = importance)) +
+#   geom_boxplot(aes(fill = interaction(type, scaled)))
+
+@
+
+Species vary widely on the degree of their importance for network manageability.
+Our method to calculate the relative importance of species relies on calculating all possible maximum matchings.
+The number of matchings increasses exponentially with the number of links and nodes in a network.
+When we use mutual dependecies, there are two links between each interacting species, and we were only able to find the importance of different species in the eleven smallest networks.
+For the remaining nine networks, the number of maximum matchings is much larger than $4\times 10^{10}$ and the computation of the species relative importance became unfeasible.
+
+Nevertheless, we were able to find the relative importance of species in the single link version of the networks where links were weighted by the assymetry.
+For the networks in which we were able to calculate the importance using mutual dependencies, we found a strong correlation between both approaches (Spearman's rank correlation ranged between $\rho = [\Sexpr{round(min(dplyr::filter(correlations, threshold == 0.5, type == "asymmetry", scaled == T)$V3, na.rm = T), digits = 2)}, \Sexpr{round(max(dplyr::filter(correlations, threshold == 0.5, type == "asymmetry", scaled == T)$V3, na.rm = T), digits = 2)}]$, median $\tilde{\rho} = \Sexpr{round(median(dplyr::filter(correlations, threshold == 0.5, type == "asymmetry", scaled == T)$V3, na.rm = T), digits = 2)})$.
+Indeed, when using the weighted rank correlation coefficient $r_{w2}$, we found that the agreement was stronger for highly ranked species than for lowly ranked species ($\tilde{r_{w2}} = \Sexpr{round(median(dplyr::filter(correlations, threshold == 0.5, type == "asymmetry", scaled == T)$V1, na.rm = T), digits = 2)}$ versus $\tilde{r_{w2}} = \Sexpr{round(median(dplyr::filter(correlations, threshold == 0.5, type == "asymmetry", scaled == T)$V2, na.rm = T), digits = 2)}$).
+Moreover both approaches identified a highly similar set of driver species (Jaccard similarity $J = [\Sexpr{round(min(dplyr::filter(correlations, threshold == 0.5, type == "asymmetry", scaled == T)$V4, na.rm = T), digits = 2)}, \Sexpr{round(max(dplyr::filter(correlations, threshold == 0.5, type == "asymmetry", scaled == T)$V4, na.rm = T), digits = 2)}]$, $\tilde{J} = \Sexpr{round(median(dplyr::filter(correlations, threshold == 0.5, type == "asymmetry", scaled == T)$V4, na.rm = T), digits = 2)})$
+
+<<importance, echo = FALSE, warning = F, message = F, results = "hide">>=
+glmer.glmulti<-function(formula,data,random="",...){
+  glmer(paste(deparse(formula, width.cutoff = 500),random),data=data,...)
+}
+
+setMethod('getfit', 'glmerMod', function(object, ...) {
+  summ <- coef(summary(object))
+  summ1 <- summ[,1:2,drop=FALSE]
+  ## if (length(dimnames(summ)[[1]])==1) {
+  ##     summ1 <- matrix(summ1, nr=1,
+  ##                     dimnames=list(c("(Intercept)"),
+  ##                     c("Estimate","Std. Error")))
+  ## }
+  cbind(summ1, df=rep(times =10000,length(fixef(object))))
+})
+
 imp <- mod %>% 
-  lapply(function(x){
-    coef.glmulti(x, select = 0.95) %>%
+  coef.glmulti(select = 0.95) %>%
   as.data.frame() %>%
   dplyr::add_rownames("factor") %>%
-      dplyr::arrange(-Importance, factor)
-  })
+  dplyr::mutate(pare = grepl("(", factor, fixed =T),
+                factor = plyr::mapvalues(factor, 
+                                         c("de", "n", "vi", "eig_cen", 
+                                           "guildpol"),
+                                         c("dependency strength", 
+                                           "contribution to nestedness",
+                                           "visitation strength",
+                                           "eigen-centrality", 
+                                           "guild (pollinator)"))) %>% 
+  dplyr::arrange(-pare, -Importance, -Estimate, factor) %>% 
+  dplyr::select(-pare)
 
 print_table <- . %>%
-  dplyr::mutate(factor = paste0("$", factor, "$")) %>%
+  # dplyr::mutate(factor = paste0("$", factor, "$")) %>%
   magrittr::set_names(c("factor", "est.", "var", "No. mod.", "imp.", "C.I.")) %>% 
@@
 
+<<species, echo = FALSE, warning = F, message = F, fig.height=4.4, fig.width=3.1>>=
+data <- mo
+net <- "./data/V2.0/networks" %>%
+	read_networks()
+# pred <- expand.grid(de = c(seq(min(data$de), max(data$de), length = 20000), mean(data$de)),
+#             n = c(seq(min(data$n), max(data$n), length = 2), mean(data$n)),
+#             vi = c(seq(min(data$vi), max(data$vi), length = 2), mean(data$vi)), 
+#             eig_cen = mean(data$eig_cen, na.rm = T), 
+#             guild = "pla") %>%
+#   dplyr::mutate(q = predict.glmulti(mod, 
+#                                     select = 0.95, 
+#                                     newdata = ., 
+#                                     re.form = NA)$averages %>%
+#                   as.vector(), 
+#                 p = plogis(q)) %>%
+#   dplyr::mutate(de = de * attr(data$de, "scaled:scale") + attr(data$de, "scaled:center"),
+#                 vi = vi * attr(data$vi, "scaled:scale") + attr(data$vi, "scaled:center"),
+#                 n = n * attr(data$n, "scaled:scale") + attr(data$n, "scaled:center"))
+#   # dplyr::filter(de == mean(data$de)) %>%
+#   
+# p1 <- pred %>%
+#   dplyr::filter(vi == unique(vi)[3]) %>%
+#   ggplot(aes(x = de, y = p)) +
+#   geom_line(aes(colour = as.factor(n), group = as.factor(n)), size = 1) +
+#   scale_colour_manual(name = "contribution to nestedness",
+#                       labels = c("max.", "mean", "min"),
+#                       values = c("#cccccc", "#969696", "#525252")) +
+#   # scale_x_continuous(expand = c(0,0)) +
+#   scale_y_continuous(limits = c(0,1)) +
+#   scale_x_log10() + 
+#   # xlab("degree") +
+#   # ylab("strength of dependencies") +
+#   stat_contour(colour = "black", size = 0.75) +
+#   fer_theme + theme(panel.grid = element_blank(), legend.position = "top") 
+# 
+# p2 <- pred %>%
+#   dplyr::filter(n == unique(n)[3]) %>%
+#   ggplot(aes(x = de, y = p)) +
+#   geom_line(aes(colour = as.factor(vi), group = as.factor(vi)), size = 1) +
+#   # scale_fill_gradient(name = "relative\nimportance", high = "#f0f0f0", low = "#525252") +
+#   # scale_x_continuous(expand = c(0,0)) +
+#   scale_y_continuous(limits = c(0,1)) +
+#   scale_x_log10() + 
+#   # xlab("degree") +
+#   # ylab("strength of dependencies") +
+#   stat_contour(colour = "black", size = 0.75) +
+#   fer_theme + theme(panel.grid = element_blank(), legend.position = "top")
+#
+
+guild <- c("pla", "pol") %>%
+  plyr::ldply(function(y){
+    o <- lapply(net, function(x) igraph::V(x)[igraph::V(x)$type == y]$name) %>%
+      unlist() %>% unique()
+    data.frame(guild = y, species = o)
+  })
+
+invasive_sp <- dplyr::filter(meta, inv) %>%
+  dplyr::mutate(species = plyr::mapvalues(invader, 
+                                          c("car", "op", "imp"),
+                                          c("p_4", "p_25", "Impatiens glandulifera")), 
+                invasive = T) %>%
+  dplyr::select(net_name, species, invasive)
+
+connected_sp <- data %>% dplyr::select(net_name, species) %>% 
+  dplyr::mutate(connected = T)
+
+s_p_s <- s_p %>%
+  dplyr::full_join(invasive_sp) %>% 
+  dplyr::mutate(invasive = replace(invasive, is.na(invasive), FALSE)) %>% 
+  dplyr::inner_join(guild) %>%
+  dplyr::inner_join(meta) %>%
+  dplyr::filter(study != "ballantyne") %>%
+  dplyr::inner_join(connected_sp)
+
+dd <- data %>% lapply(as.vector) %>% as.data.frame()
+dd <- s_p_s %>%
+  dplyr::select(net_name, species, invasive, connected) %>%
+  dplyr::inner_join(dd) %>%
+  dplyr::mutate(pp = predict(mod, select = 0.95, newdata = ., re.form = NA)$averages,
+                pp = as.vector(pp),
+                pp = plogis(pp),
+                de2 = de * attr(data$de, "scaled:scale") + attr(data$de, "scaled:center"))
+
+# 
+# d <- s_p_s %>%
+#   dplyr::rename(n = nestedcontribution, 
+#                 de = d_strength, 
+#                 vi = v_strength) %>%
+#   dplyr::select(de, n, vi, eig_cen, guild)
+# 
+# d %>% s_p_s %>%
+#   dplyr::select(guild)
+# 
+# pp <-  predict(mod, newdata = d, select = 0.95, re.form = NA)$averages
+# 
+# species <- s_p_s %>%
+#   dplyr::mutate(pp = plogis(as.vector(pp)))
+
+trans <- function(x, orig){
+  x * attr(orig, "scaled:scale") + attr(orig, "scaled:center")
+}
+
+b_trans <- function(x, orig){
+  (x - attr(orig, "scaled:center")) / attr(orig, "scaled:scale")
+}
+
+# juju <- function(x) 10^x
+
+# 
+# pred2 <- expand.grid(de = b_trans(exp(c(seq(log(trans(min(data$de), data$de)),
+#                                 log(trans(max(data$de), data$de)), 
+#                                 length = 500))), data$de),
+#             n = c(seq(min(data$n), max(data$n), length = 500)),
+#             vi = mean(data$vi), 
+#             eig_cen = mean(data$eig_cen, na.rm = T), 
+#             guild = "pla") %>%
+#   dplyr::mutate(q = predict.glmulti(mod, 
+#                                     select = 0.95, 
+#                                     newdata = ., 
+#                                     re.form = NA)$averages %>%
+#                   as.vector(), 
+#                 p = plogis(q)) %>%
+#   dplyr::mutate(de = de * attr(data$de, "scaled:scale") + attr(data$de, "scaled:center"),
+#                 vi = vi * attr(data$vi, "scaled:scale") + attr(data$vi, "scaled:center"),
+#                 n = n * attr(data$n, "scaled:scale") + attr(data$n, "scaled:center"))
+# 
+# p3 <- pred2 %>%
+#   ggplot() +
+#   geom_tile(aes(fill = p, x = de, y = n, z = p)) + 
+#   scale_x_log10(expand = c(0,0)) +
+#   scale_y_continuous(expand = c(0,0)) +
+#   scale_fill_continuous(limits = c(0,1), low = "#ffffff", high = "#636363") +
+#  
+#   geom_point(data = s_p_s, aes(x = d_strength, y = nestedcontribution, shape = guild, colour = invasive), size = 1) +
+#    # stat_contour(aes(x = de, y = n, z = p), 
+#                # colour = "black", size = 0.5, bins = 5) +
+#   fer_theme + 
+#   scale_shape_manual(values = c(21, 22)) +
+#   scale_color_manual(values = c("#525252","#e41a1c")) + 
+#   theme(panel.grid = element_blank(), legend.position = "none",
+# 				plot.margin = grid::unit(c(0, 0, 2, 0), "mm")) +
+#   xlab("dependency strength") +
+#   ylab("contribution to nestedness")
+# 
+# 
+# pred3 <- expand.grid(de = b_trans(exp(c(seq(log(trans(min(data$de), data$de)),
+#                                 log(trans(max(data$de), data$de)), 
+#                                 length = 500))), data$de),
+#             n = c(mean(data$n)),
+#             vi = b_trans(exp(c(seq(log(trans(min(data$vi), data$vi)),
+#                                 log(trans(max(data$vi), data$vi)),
+#                                 length = 500))), data$vi),
+#             # vi = seq(min(data$vi), max(data$vi), length.out = 500),
+#             eig_cen = mean(data$eig_cen, na.rm = T), 
+#             guild = "pla") %>%
+#   dplyr::mutate(q = predict.glmulti(mod, 
+#                                     select = 0.95, 
+#                                     newdata = ., 
+#                                     re.form = NA)$averages %>%
+#                   as.vector(), 
+#                 p = plogis(q)) %>%
+#   dplyr::mutate(de = de * attr(data$de, "scaled:scale") + attr(data$de, "scaled:center"),
+#                 vi = vi * attr(data$vi, "scaled:scale") + attr(data$vi, "scaled:center"),
+#                 n = n * attr(data$n, "scaled:scale") + attr(data$n, "scaled:center"))
+# 
+# p4 <- pred3 %>%
+#   ggplot() +
+#   geom_tile(aes(x = de, y = vi, z = p, fill = p)) + 
+#   scale_x_log10(expand = c(0,0)) +
+#   scale_y_log10(expand = c(0,0)) +
+#   scale_fill_continuous(limits = c(0,1), low = "#ffffff", high = "#636363", name = "") +
+#   geom_point(data = s_p_s, aes(x = d_strength, y = v_strength, shape = guild, colour = invasive), size = 1, show.legend = F) +
+#   # geom_contour(aes(x = de, y = vi, z = p), colour = "black", size = 0.5, bins = 5) +
+#   fer_theme + theme(panel.grid = element_blank(), legend.position = "top",
+# 				plot.margin = grid::unit(c(5, 0, -2, 0), "mm"),
+# 				legend.key.height = grid::unit(3, "mm"),
+# 				legend.key.width = grid::unit(6, "mm")) +
+#   scale_shape_manual(values = c(21, 22)) +
+#   scale_color_manual(values = c("#525252","#e41a1c")) + 
+#   xlab("") +
+#   ylab("visitation strength")
+# 
+# ratio <- function(x){
+#   o <- round(x * 1000)
+#   rep(c(1,2), times = c(o, 1000-o)) %>%
+#     matrix(ncol = 1)
+# }
+
+# 
+# pred4 <- expand.grid(de = b_trans(exp(c(seq(log(trans(min(data$de), data$de)),
+#                                 log(trans(max(data$de), data$de)), 
+#                                 length = 500))), data$de),
+#             n = mean(data$n),
+#             vi = c(-1, 0, 1),
+#             # vi = seq(min(data$vi), max(data$vi), length.out = 500),
+#             eig_cen = mean(data$eig_cen, na.rm = T), 
+#             guild = "pla") %>%
+#   dplyr::filter(!(n == max(data$n) & vi == min(data$vi)),
+#                 !(n == min(data$n) & vi == max(data$vi))) %>%
+#   dplyr::mutate(q = predict.glmulti(mod, 
+#                                     select = 0.95, 
+#                                     newdata = ., 
+#                                     re.form = NA)$averages %>%
+#                   as.vector(), 
+#                 p = plogis(q)) %>%
+#   dplyr::mutate(de = de * attr(data$de, "scaled:scale") + attr(data$de, "scaled:center"),
+#                 vi = vi * attr(data$vi, "scaled:scale") + attr(data$vi, "scaled:center"),
+#                 n = n * attr(data$n, "scaled:scale") + attr(data$n, "scaled:center"))
+# 
+# pred4 %>%
+#   ggplot(aes(x = de, y = p)) +
+#   geom_line(aes(colour = as.factor(n), linetype = as.factor(vi))) + 
+#   scale_x_log10(expand = c(0,0)) +
+#   fer_theme
+# 
+#
+
+pred4 <- data.frame(de = rep(b_trans(exp(c(seq(log(trans(min(data$de), data$de)),
+                                log(trans(max(data$de), data$de)),
+                                length = 500))), data$de),3),
+            n = rep(c(-1,0,1), each = 500),
+            vi = rep(c(-1,0,1), each = 500),
+            type = rep(c("exp", "mean", "exp"), each = 500),
+            # vi = seq(min(data$vi), max(data$vi), length.out = 500),
+            eig_cen = mean(data$eig_cen, na.rm = T),
+            guild = "pla") %>%
+  dplyr::filter(!(n == 2 & vi == -2),
+                !(n == -2 & vi == 2)) %>%
+  dplyr::mutate(q = predict.glmulti(mod,
+                                    select = 0.95,
+                                    newdata = .,
+                                    re.form = NA)$averages %>%
+                  as.vector(),
+                p = plogis(q)) %>%
+  dplyr::mutate(de = de * attr(data$de, "scaled:scale") + attr(data$de, "scaled:center"),
+                vi = vi * attr(data$vi, "scaled:scale") + attr(data$vi, "scaled:center"),
+                n = n * attr(data$n, "scaled:scale") + attr(data$n, "scaled:center"))
+
+# multiplot(p4, p3, layout = ratio(0.57))
+
+@
+
+Although plants showed significantly higher levels of importance for network control than pollinators (Mann-Withney-Wilcoxon test, $p \Sexpr{fix_small_pvalue(wilcox.test(pp ~ guild, data = dd, alternative = "greater")$p.value)}$), this difference can be largely explained by the strength of dependency of the species (the sum of the dependencies for a given species).
+Indeed, when averaging over the set of GLMMs that accounted at least 95\% of the evidencee based on AICc, we found that the strength of dependency  is the single most important factor determining the relative importance of species for network control (\autoref{table:driver_model}\todo{consider moving the table to thes supplementary}, \autoref{fig:driver_model_alt}).
+Contrastingly, the number of visits a species receives (or performs) and its contribution to nestedness have only a marginal effect on its relative importance for network control.
+In addition, in the ten communities that were invaded, invasive species were invariably classified as a driver species.
+
 \begin{table}
@@
 \small
-\subfloat[pollinators]{
 <<table importance 1, echo = FALSE, warning = F, message = F, results = "asis">>=
-print_table(imp[[1]])
+print_table(imp)
 @
-}
-\subfloat[plants]{
-<<table importance 2, echo = FALSE, warning = F, message = F, results = "asis">>=
-print_table(imp[[2]])
-@
-}
-\caption{\label{table:sd} Minimum number and proportion of driver species necessary to control the full pollination network}
+\caption{\label{table:driver_model} The strength of dependency, contribution to nestedness and visitation strength had a significative effect on all the models that accounted for 95\% of the evidence based on AICc.
+Coeficient estimates were avaraged following \textcite{Buckland1997a}; confidence intervals were calculated following \textcite{Lukacs2010}.}
 \end{table}
@@
 \centering
-<<fig species, echo = FALSE, warning = F, message = F, fig.height=2.2, fig.width=3.1>>=
-data_pol <- mod[[1]]@objects[[1]]$data
-data_pla <- mod[[2]]@objects[[1]]$data
-
-expand.grid(d = seq(min(data_pla$d), max(data_pla$d), by = 1),
-            S_d = seq(min(data_pla$S_d), max(data_pla$S_d), length = 20), 
-            n = mean(data_pla$n, na.rm = T), 
-            S_v = mean(data_pla$S_v)) %>%
-  dplyr::mutate(q = predict.glmulti(mod[[2]], 
-                                    select = 0.95, 
-                                    newdata = .)$averages %>%
-                  as.vector(), 
-                p = plogis(q)) %>%
-  ggplot(aes(x = d, y = S_d, z = p)) +
-  geom_tile(aes(alpha = p), fill = "#0e324b") +
-  # scale_fill_gradient(name = "relative\nimportance", high = "#f0f0f0", low = "#525252") +
-  scale_x_continuous(expand = c(0,0)) +
-  scale_y_continuous(expand = c(0,0)) +
-  xlab("degree") +
-  ylab("strength of dependencies") +
-  stat_contour(colour = "black", size = 0.75) +
-  fer_theme + theme(panel.grid = element_blank())
+<<fig species alt, echo = FALSE, warning = F, message = F, fig.height=2.2, fig.width=3.1>>=
+pred4 %>%
+  ggplot() +
+  geom_line(aes(x = de, y = p, linetype = type, colour = type, group = interaction(n, vi)), show.legend = F, size = 0.5) +
+  scale_x_log10(expand = c(0,0)) +
+   geom_point(data = dplyr::arrange(dd, invasive), aes(x = de2, y = pp, fill = invasive, shape = guild, size = invasive), show.legend = F) +
+    scale_shape_manual(values = c(21, 23)) +
+  scale_size_manual(values = c(1,1.5)) +
+  scale_fill_manual(values = c("white","#e41a1c")) + 
+  scale_color_manual(values = c("#525252", "black")) +
+  scale_linetype_manual(values = c(2, 1)) +
+  xlab("dependency strength") +
+  ylab("relative importance") +
+  fer_theme
 @
-\caption{\label{fig:prediction} aSS }
+\caption{\label{fig:driver_model_alt} Dependency strength is the single most important factor explaining the importance of species for network control.
+Visitation levels and contribution to nestedness had a significant albeit small effect on the importance (dashed lines correspond to \textpm one standard deviation on these factors).
+Invasive species (red) were invariably classified as driver species (those having the maximum importance for network control.}
 \end{figure}
@@
 The authors thank Dr.
-Takeuki Uno for the insight provided to find the set of all maximum matching algorithms, and Bernat Bramon and Marilia Gaiarsa for feedback in early stages of the project.
+Takeuki Uno for the insight provided to find the set of all maximum matching algorithms, and Bernat Bramon, Matthew Hutchinson and Marilia Gaiarsa for feedback in early stages of the project.
 EFC acknowledges the support from the University of Canterbury Doctoral Scholarship, the University of Canterbury Meadow Mushroooms Postgraduate Scholarship, a travel grant from the European Space Agency and a Rutherford Discovery Fellowship (to DBS).
 DBS ackloledges the support of a Rutherford Discovery Scholarship, administered by the Royal Society of New Zealand.
-
-\section*{Author contributions}
 

### 2016-04-22 paper/supp_info.Rnw
update manuscript

@@
 n_matched <- readRDS("./data/V2.0/n_matched.rds")
-m_f <- readRDS("./data/V2.0/matching_frequency.rds")
+m_f <- read_allRDS("./data/V2.0/matching_frequency")
+m_f_b <- read_allRDS("./data/V2.0/matching_frequency_bi/")
 a_m <- readRDS("./data/V2.0/n_matched_all_types.rds") 
@@
 
-z_scores_bi %>%
-  ggplot(aes(x = n_pla/n_pol, y = -1 * z_s)) + 
+@
+\caption{\label{fig:randomisations_bi} The manageability of network randomisations that mantain the strength or the degree of species is not different from the empirical manageability using bidirectional links.}
+\end{figure}
+
+\section{Driver species}
+
+<<driver species dependency, echo = FALSE, warning = F, message = F>>=
+
+get_frequencies <- . %>%
+  plyr::ldply(function(x){
+    plyr::ldply(x, function(y){
+      matched <- y$matched %>%
+        dplyr::rename(species = ve,
+                      m_freq = ma, 
+                      m_weight = we)
+      driver <- y$driver %>%
+        dplyr::rename(species = vs,
+                      d_freq = ma, 
+                      d_weight = we)
+      dplyr::inner_join(matched, driver, by = "species") %>%
+        dplyr::mutate(n_matchings = attr(y, "n_matchings"))
+    }, .id = "threshold") 
+	}, .id = "net_name") %>% 
+  dplyr::mutate(threshold = as.numeric(as.character(threshold))) %>%
+  dplyr::filter(threshold %in% c(0, 0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8, 0.9, 1)) %>%
+  dplyr::mutate(m_reim = m_freq/n_matchings,
+                d_reim = d_freq/n_matchings,
+                d_weight = d_weight/n_matchings)
+
+drivers_b <- get_frequencies(m_f_b) %>% 
+  dplyr::mutate(type = "z-bi")
+
+drivers <- get_frequencies(m_f) %>% 
+  dplyr::mutate(type = "weight") %>%
+  dplyr::bind_rows(drivers_b)
+
+driver_sp <- drivers %>%
+  dplyr::filter(threshold == 1) %>%
+  dplyr::group_by(net_name, species, type) %>%
+  dplyr::summarise(imp = d_weight != 1,
+                   d_reim_0 = d_weight,
+                   sp_imp = paste(d_weight, species))
+
+drivers %<>%
+  dplyr::inner_join(driver_sp) %>%
+  dplyr::inner_join(meta)
+
+n_matchings <- drivers %>%
+  dplyr::filter(threshold == 1, count != "binary") %>%
+  dplyr::group_by(net_name, type) %>%
+  dplyr::summarise(n_matchings = mean(n_matchings))
+
+p_weights <- drivers %>%
+  dplyr::group_by(net_name, type, threshold) %>%
+  dplyr::summarise(n_matchings = mean(n_matchings)) %>% 
+  dplyr::mutate(new_m = n_matchings - lead(n_matchings),
+                new_m = replace(new_m, is.na(new_m), last(n_matchings))) %>%
+  dplyr::select(-n_matchings)
+
+drivers <- drivers %>%
+  dplyr::inner_join(p_weights) %>%
+  dplyr::group_by(net_name, type, species) %>%
+  dplyr::mutate(d_weight_mean = weighted.mean(d_weight, new_m))
+@
+
+Unlike unweighted networks, where a maximum matching is defined by its size (the number of matched edges), in weighted networks, a maximum matching is one whose edges have the largest possible total weight among all possible matchings.
+This means that in weighted networks there is a number of matchings that have maximal size, but are not maximum matchings because its total weight is not maximal too.
+Therefore, for weighted networks the number of possible maximum matchings, even for lage networks, can be small (in the studied networks this number ranged from \Sexpr{min(n_matchings$n_matchings)} to \Sexpr{max(n_matchings$n_matchings)}, $\bar{\mu} = \Sexpr{mean(n_matchings$n_matchings)}$).
+
+However the weight of species dependencies is unexact, a reflection of the fact that interaction strengths and sampling methods themselves are stochastic to some extent.
+This means that certain level of tolerance must be introduced so that we accept some matchings that have the same size but only a proportion of the maximum matching weight.
+As this proportion decreasses we accept a markedly larger number of matchings (\autoref{fig:threshold_n_matchings}).
+
+\begin{figure}
+\centering
+<<fig threshold matching, echo = FALSE, warning = F, message = F, fig.height=2.19, fig.width=3.1>>=
+
+drivers %>%
+  dplyr::filter(count != "binary") %>%
+  dplyr::group_by(net_name, threshold, type) %>%
+  dplyr::summarise(n_matchings = mean(m_freq + d_freq), 
+                   n_sp = mean(n_pla + n_pol)) %>%
+  dplyr::group_by(net_name) %>%
+  dplyr::mutate(n_matchings_rel = n_matchings / max(n_matchings)) %>%
+  ggplot(aes(x = threshold, y = n_matchings)) +
+  # geom_point(aes(colour = type), size = 1) +
+  geom_line(aes(group = interaction(type, net_name),
+                colour = type)) +
+  scale_color_manual(values = c("#252525", "#636363")) + 
+  scale_y_log10() +
+  xlab("proportion of maximum matching weight (threshold)") +
+  ylab("number of accepted matchings") +
+  fer_theme +
+  theme(legend.position = "none")
+@
+\caption{\label{fig:threshold_n_matchings} The number of accepted matchings increasses as the proportion of maximum matching weight decreasses. Each line correspond to one studied network.}
+\end{figure}
+
+<<>>=
+
+get_correlations <- function(y, limit = 5, var = "d_reim", by = c("net_name", "threshold")){
+  y %>%
+  dplyr::filter(count == "visitation") %>%
+  plyr::ddply(by, function(x){
+    c <- x %>% 
+      dplyr::select_("species", var, "type") %>%
+      tidyr::spread_("type", var) %>%
+      dplyr::arrange(species)
+
+    names(c)<- make.names(names(c))
+
+    if(ncol(c) == 2) return(NULL)
+
+    c %<>%
+      dplyr::mutate(w_r = rank(-weight, ties.method = "average"),
+                    b_r = rank(-z.bi, ties.method = "average"),
+                    weight = replace(weight, w_r > limit & b_r > limit, NA),
+                    z.bi = replace(z.bi, w_r > limit & b_r > limit, NA))
+
+    if(nrow(dplyr::filter(c, !is.na(weight))) <= 1) return(NULL)
+
+    c <- cor.test(c$weight, c$z.bi, method = "spearman", exact = F)
+
+    data.frame(statistic = c$statistic,
+               p_value = c$p.value,
+               estimate = c$estimate)
+  }, .inform = T)
+}
+
+correlations <- get_correlations(drivers, limit = 5, "d_weight")
+
+correlations %>%
+  ggplot(aes(x = threshold, y = estimate)) +
+  geom_line(aes(colour = net_name)) +
+  geom_point(aes(fill = p_value < 0.05), shape = 21) +
+  geom_smooth()
+
+drivers %>%
+  dplyr::filter(threshold == 0) %>%
+  get_correlations(limit= 5, "d_weight_mean", by = "net_name") %>%
+  dplyr::inner_join(meta) %>%
+  ggplot(aes(x = n_pla + n_pol, y = estimate)) +
   geom_point()
-@
-\caption{\label{fig:randomisations_bi} xxx}
-\end{figure}
-
-\section{Driver species}
+
+drivers %>%
+  dplyr::filter(threshold == 1) %>%
+  dplyr::group_by(net_name, type) %>%
+  dplyr::mutate(ranked = rank(-d_weight_mean, ties.method = "min")) %>%
+  dplyr::filter(ranked == 1 | ranked == 2) %>% 
+  dplyr::select(net_name, type, species, ranked) %>%
+  dplyr::arrange(net_name, type, species) %>% View
+
+@
+
+<<fig comparing thresholds, echo = FALSE, warning = F, message = F, fig.height=2.19, fig.width=6.2>>=
+
+# ggplot(drivers, aes(x = threshold, y = d_reim - d_reim_0, colour = d_reim_0, group = species)) +
+#   geom_hline(yintercept = c(-0.5, 0.5), linetype = 2) +
+#   geom_point() +
+#   geom_line() +
+#   facet_wrap(~ net_name + type) +
+#   scale_alpha_manual(values = c(1, 0.3)) +
+#   ylim(c(-1, 1)) +
+#     scale_color_gradient2(low = "#377eb8",
+#                          high = "#e41a1c",
+#                          mid = "grey80", midpoint = 0.5) +
+#   fer_theme
+# 
+# drivers %>%
+#   dplyr::filter(study == "ballantyne") %>%
+#   ggplot(aes(x = threshold, y = d_reim - d_reim_0, colour = d_reim_0, group = species)) +
+#   geom_hline(yintercept = c(-0.5, 0.5), linetype = 2) +
+#   geom_point() +
+#   geom_line() +
+#   facet_grid(net_name + type ~ species) +
+#   scale_color_gradient2(low = "#377eb8",
+#                          high = "#e41a1c",
+#                          mid = "grey80", midpoint = 0.5) +
+#   ylim(c(-1, 1)) +
+#   fer_theme
+
+# p1 <-
+  d %>%
+  dplyr::filter(study == "ballantyne", 
+                count == "importance" | count == "visitation") %>%
+  ggplot(aes(x = threshold, y = d_weight, group = species)) +
+  # geom_hline(yintercept = c(-0.5, 0.5), linetype = 2) +
+  geom_line(aes(colour = d_weight_mean)) +
+  geom_hline(aes(yintercept = d_weight_mean, colour = d_weight_mean)) +
+  geom_point(aes(colour = d_weight_mean), size = 1) +
+  facet_wrap(type ~ net_name) +
+  scale_color_gradient2(low = "#377eb8", 
+                         high = "#e41a1c", 
+                         mid = "grey80", midpoint = 0.5) +
+  scale_fill_gradient2(low = "#377eb8", 
+                         high = "#e41a1c", 
+                         mid = "grey80", midpoint = 0.5) +
+  # ylim(c(-1, 1)) +
+  fer_theme +
+  theme(legend.position = "none", 
+        plot.margin = grid::unit(c(5,2,2,0), "mm"))
+
+ball_correllations <- function(drivers, var){
+  drivers %>%
+  dplyr::filter(study == "ballantyne",
+                count == "visitation" | count == "importance") %>% 
+  plyr::ddply(c("threshold"), function(x){
+    c <- x %>% 
+      dplyr::mutate(type_count = interaction(type, count)) %>%
+      dplyr::select_("species", var, "type_count") %>%
+      dplyr::arrange(species) %>%
+      tidyr::spread_("type_count", var) %>%
+      dplyr::select(-species) %>%
+      as.matrix() %>%
+      cor(method = "spearman")
+
+    c[lower.tri(c, diag = T)] <- NA
+
+      c %>%
+        as.data.frame.table() %>%
+        dplyr::filter(!is.na(Freq)) %>%
+        tidyr::separate(Var1, c("type1", "count1"), 
+                        sep = "\\.", remove = F) %>%
+        tidyr::separate(Var2, c("type2", "count2"), 
+                        sep = "\\.", remove = F) %>%
+        dplyr::mutate(comp = paste(Var1, Var2, sep = "_"))
+  })
+}
+
+correlations <- ball_correllations(drivers, "d_reim")
+
+# p2 <- 
+  correlations %>% 
+  # dplyr::filter(type1 != type2) %>%
+  ggplot(aes(x = threshold, y = Freq)) +
+  geom_point(size = 1) +
+  geom_line(aes(colour = comp)) +
+  fer_theme +
+  theme(plot.margin = grid::unit(c(11.2,1,2,0), "mm")) +
+  geom_smooth()
+
+multiplot(p1, p2, layout = matrix(c(1, 1, 2), ncol = 3))
+
+@
 
@@
 \section{Visitation as a proxy for species interdependence}
+
+\subsubsection*{Visitation as a proxy for species interdependence}
+
+Visitation frequency has been shown to be an appropriate surrogate for inter-specific effects in pollination networks \autocite{Vazquez2005, Bascompte2006}.
+Arguably, visitation reflects adequately the dependency of animals to plants, as usually during a visit animals forage for pollen or nectar regardless of wether effective pollination occurs\todo{any citation Daniel?}.
+Nevertheless visitation is not equivalent to pollen deposition and might be insufficient to reflect the dependencies of plants on animals \autocite{Alarcon2010, King2013}.
+We therefore investigated the effect of calculating the dependencies using pollination effectiveness and importance---two metrics more proximate to plant reproductive sucess.
+
+Pollinator efficiency is measured as ``the number of conspecific pollen grains deposited on a virgin stigma during a single visit by a particular animal'' \autocite{NeEman2010}.
+Pollinator importance on the other hand is defined as the product between visitation frequency and pollinator efficency \autocite{Ballantyne2015}.
+We used data collected by \textcite{Ballantyne2015} from a low diversity pollination community at a dry lowland heathland in Dorset, UK.
+We assessed the differences between visitation, pollinator effectiveness, and pollinator importance by comparing (i) the manageability of the community and (ii) the percentage of interactions that mantained the direction of dependency.
 

### 2016-04-28 paper/manuscript.Rnw
first draft of introduction

@@
 % comments
-\usepackage[draft, textsize = scriptsize]{todonotes}
+\usepackage[draft, textsize = scriptsize, color = gray]{todonotes}
 
@@
 
-\doublespacing
+%\doublespacing
+\onehalfspacing
 
@@
 \maketitle
-
-\iffalse
-
-\begin{abstract}
-\noindent Si sabemos que el disfrute exige lentitud, y que---mas en general---la felicidad se asocia con el ir despacio, por que corremos tanto?
-El arte de comer estriba en saborear cada bocado sin pensar en el siguiente, sin apresurar el siguiente.
-El arte de leer, en demorarse en cada palabra como si el sentido del escrito entero estuviera contenido en ella.
-El arte de amar, en vivir cada momento de la relacion con la persona amada como si fuese el destino de toda la historia del mundo, desde la aparicion del primer organismo unicelular hasta hoy.
-Y asi podemos generalizar a las demas actividades, creo, hasta obtener un arte de vivir.
-Para mi se resume en la palabra ahi.
---- Jorge Riechmann
-\end{abstract}
-
-\keywords{Control theory, box in the article}
 
@@
 
+\todo[inline]{I really need some help with specific ideas for the first paragraph. Everything I come up with is shit}
+
+Seminal work on control theory has established a strong link between the structure of complex networks and its controlability \autocite{Liu2011}, and that in principle it is possible to alter any ecological community's composition, by modifying the abundances of just some key species \autocite{Cornelius2013}.
+Based on this work and using a small number of binary (only presence or absence of interactions) food-webs, it has been suggested that the degree distribution of ecological networks makes them inherently difficult to control \autocite{Liu2011, Ruths2014}.
+This theoretical result is in agreement with many cases in which the management of ecological communities is more challenging than aticipated.
+In contrast with other types of complex systems like neural, intra-organizational, or trust neworks, which in comparison have a hierarchical or distributed structure, ecological networks tend to be closed systems in which resources recirculate.
+As such, ecosystems cointain multiple feedbacks that allow them to self-regulate and therefore function relatively independent from external stimulation\todo{add ref}.
+Although these conceptual advances on control theory provided an initial link between the structure of ecological communities and our ability to manage them this relationship is still ambiguous.
+Ultimately, ecological networks can vary widely on their structure and are often comprised by interactions whose strengths can vary by several orders of magnitude\todo{add ref}.
+
+For instance, biotic invasions, as other major drivers of global change, can induce dramatic changes on the patterns of interactions that determine the structure of ecological networks \autocite{Baxter2004, Tylianakis2008, Ehrenfeld2010a}.
+These changes can be particularly pronounced in mutualistic networks of plants and pollinators where biotic invasions have been shown to modify the strength of species interactions and the degree of network nestedness and connectivity \autocite{Olesen2002, Aizen2008, Bartomeus2008, Vila2009, Traveset2013}.
+Moreover, as evidenced by the limited amount of success of restoration projects \autocite{Smith2016}, returning invaded communities to a predisturbance state is quite a difficult endeavour \autocite{Suding2004, Rodewald2015}.
+Understanding how differences in network structure caused by invasions are reflected on our ability to manage them can provide useful lessons to conservation science.
+What is more, it can also provide ecological insights: by explicitly taking into account the extent to wh ich changes in the abbundances of one species may ripple trough the community, applying control theory to ecological networks can provide an indication which species are important from a dynamic perspective and therefore crucial when attempting to alter (or maintain) the ecosystem state.
+
+\textcite{Isbell2013} used a control theoretic approach to find the minimum subset of species neccessary to maintain network structure in six marine food webs.
+They found that humans affect a larger proportion of this subset of species than, for instance, apex predators.
+They argue that this disproportionate influence could translate into unintentional restructuring of food webs.
+Although insightful, \textcite{Isbell2013} had a number of shortcommings that limited the scope and applicability of their results.
+First, they disregard the fact that the minimum set of species is not unique and thus not all species within this set are equally important for the community population dynamics.
+Second, their methods were naive to differences on the strength of interspecific effects.
+And third, their approach was conceptually limited to trophic interactions\todo{is this too harsh?}.
+
+Here, we expand previous theory of the control of complex systems and use a set of paired invaded and uninvaded plant-pollinator communities to investigate \textit{i)} the link between network structure and our ability to manage them, \textit{ii)} whether biotic invasions as drivers of structure change can modify this manageability, and \textit{iii)} the relative importance of species at driving the population dynamics of other species in the community.
+Plant pollinator networks provide an ideal framework to answer these questions.
+On one hand the role of asymmetric species interdependence has been heavily studied and as species are mutually interdependent, it may allow some top-down bottom-up simplifications regarding the direction of control.
+quantitative Our objective is
+
+As this influence is often unregulated for instance but some limitations...
+
+Here we use a suite of plant-pollinator communities
+
+We want to know if ecological communities are difficult to control, and this is modified by the invasion status, and which species are more important for driving the community
+
+Here we use plant pollinator communities to investigate the number of species that should be managed to control population dynamics of the whole community, the characteristics that determine whether a species should be managed or not and how invasive species fit.
+
+\iffalse
+
 Ecological communities are formed by the interconnection of several species.
@@
 \fi
-
-\section*{Introduction}
-Here we use plant pollinator communities to investigate the number of species that should be managed to control population dynamics of the whole community, the characteristics that determine whether a species should be managed or not and how invasive species fit.
 
@@
 
+\section*{Discussion}
+
+Therefore, full controlability of ecological networks---being able to steer the ecosystem into any desired ecosystem state---would require a  This characteristics render ecological networks unlikely to be able to visist every possible system state   other closed systems, ecological networks
+
+The controllability of ecological networks is not a concept limited to control theory.
+Controllability in the ecological context can be seen as a direct meassure of the mimimum number of species whose abbundance would need to be directly regulated to achieve full network control.
+While we are far away from
+
 \section*{Acknoledgements}

### 2016-05-02 paper/manuscript.Rnw
update introduction and half way trough tge methods

--- 2016-04-22 paper/manuscript.Rnw
@@
 \doublespacing
+%\onehalfspacing
 
@@
   \author{\large Kate L. Wootton}
-  \author{\large Johanna Voinopol-Sassu}
   \author{\large Daniel B. Stouffer}
@@
 
-Ecological communities are formed by the interconnection of several species.
-Therefore, changes in the abundances of one species can potentially alter the abundances of the species they interact with.
-For instance, in a classic example of ecosystem cascades, a reduction on the abundance of sea otters, an important predator or sea urchins, can drive a dramatic reduction on kelp abundances because the sea urchins that consume kelp are released from predation.
-It has been long established that some species, like the sea otter, have a disproportionate large effect in their environment relative to their abundance.
-
-In several ecosystems the relative importance of species have been identified based on empirical observations of long term dynamics.
-However, in less studied, highly diverse, or where the "keystone" role is shared by several species, it can be challenging to determine which is the set of species that influence the most the ecosystem dynamics.
-Alternative approaches that recognize a continuum of importance and that are less dependent on empirical observations have also been developed.
-Some of them are based on metrics that evaluate their position in the food web or on mass balance models of functional groups.
-Nevertheless, these approaches are conceptually limited to throphic interactions and in general ignore the structural mechanisms that allow or prevent the spread of perturbations in the ecosystem.
-
-From a systems perspective, perturbations like over-exploitation, eutrophication or global warming are equivalent to management actions like culling, no-take areas or captive rearing in the sense that they have the potential to modify the abundances of one or several species in the ecosystem.
-Therefore identifying these key species is crucial not only to predict how these perturbations will spread trough the community but also to guide effective conservation efforts.
-
-Recent work on the control of complex systems suggest that in principle it is possible to alter any ecological community's composition, by modifying the abundances of just some key species \autocite{Isbell2013, Cornelius2013}.
-Here, we apply these theories to estimate the controllability of different ecological communities and to find driver species: species, that due to the structural characteristics of their interactions are more likely to drive the dynamics of the community.
-
-Invasive species have been shown to have a disproportionate effect on the structure of pollination communities.
-Influencing for example the strength of species interactions, and the degree of network nestedness and connectivity \autocite{Olesen2002, Aizen2008, Bartomeus2008, Vila2009, Traveset2013}.
-However whether this influence is translated into a driver role has not been tested.
-
-\fi
-
-\section*{Introduction}
-Here we use plant pollinator communities to investigate the number of species that should be managed to control population dynamics of the whole community, the characteristics that determine whether a species should be managed or not and how invasive species fit.
+\textit{Tentative spiel for the first paragraph:} We need to manage ecological communities because of ecosystem services and biodiversity maintenance.
+We would like to control communities in the sense of conserving and restoring them.
+However to control them (in that sense) we need to understand how species affect each other and potentially the whole system when they are faced by perturbations or management interventions.
+But we cannot do that yet because we lack a theoretical framework that link the dynamics of the community to management.
+Control theory might provide this link.
+
+Seminal work on control theory has established a strong link between the structure of complex networks and its controlability and that in principle it is possible to alter any ecological community's composition, by modifying the abundances of just some key species \autocite{Liu2011, Cornelius2013}.
+Based on this work and using a small number of binary food-webs (only presence or absence of interactions), it has been suggested that the degree distribution of ecological networks makes them inherently difficult to control \autocite{Liu2011, Ruths2014}.
+This theoretical result is in agreement with many cases in which the management of ecological communities is more challenging than aticipated.
+In contrast with other types of complex systems like neural, intra-organizational, or trust neworks, ecological networks do not have a hierarchical or distributed structuretend but rather tend to be closed systems in which resources recirculate.
+As such, ecosystems contain multiple feedbacks that allow them to self-regulate and, therefore, function relatively independent from external stimulation\todo{add ref}.
+Although these conceptual advances on control theory have provided an initial link between the structure of ecological communities and our ability to manage them, this relationship is still ambiguous.
+Ultimately, the challenge of ecological networks is represented by the variablity of their structure and interaction strengths---which can vary by several orders of mangitude\todo{add ref}.
+
+For instance, biotic invasions, as other major drivers of global change, can induce dramatic changes on the patterns of interactions that determine the structure of ecological networks \autocite{Baxter2004, Tylianakis2008, Ehrenfeld2010a}.
+These changes can be particularly pronounced in mutualistic networks of plants and pollinators where biotic invasions have been shown to modify the strength of species interactions and the degree of network nestedness and connectivity \autocite{Olesen2002, Aizen2008, Bartomeus2008, Vila2009, Traveset2013}.
+Moreover, as evidenced by the limited amount of success of restoration projects \autocite{Smith2016}, returning invaded communities to a predisturbance state is quite a difficult endeavour \autocite{Suding2004, Rodewald2015}.
+Understanding how invasion-induced differences in network structure impact our ability to manage them, can provide useful lessons to conservation science.
+What is more, there are also ecological insights to be had: by explicitly taking into account the extent to which changes in the abbundances of one species may ripple trough the community, applying control theory to ecological networks can provide an indication of which species are important from a dynamic perspective, and therefore crucial when attempting to alter (or maintain) the ecosystem state.
+
+\textcite{Isbell2013} used a control theoretic approach to find the minimum subset of species neccessary to maintain network structure in six marine food webs.
+They found that humans affect a larger proportion of this subset of species than, for instance, apex predators.
+They argue that this disproportionate influence could translate into unintentional restructuring of food webs.
+Although insightful, the scope and applicability of \textcite{Isbell2013} can be extended in numerous ways.
+First, although they find the size of this minimum set, they disregard the fact that the set species composition is not unique and thus not all species that might be included are equally important for the community population dynamics.
+Second, their methods were naive to differences on the strength of interspecific effects.
+And third, their approach was conceptually limited to trophic interactions\todo{is this too harsh?}.
+
+Here, we expand previous theory of the control of complex systems and use a set of paired invaded and uninvaded plant-pollinator communities to investigate the link between network structure and our ability to manage them.
+Plant-pollinator networks provide an ideal framework to answer these questions.
+On one hand, community networks that quantify relative levels of interaction are readily available.
+On the other, the bipartite nature of pollination networks makes it is possible to simplify assumptions of how these interactions translate into interspecific effects.
+Our theoretical extension of network control, allow us to ask the question of whether biotic invasions as drivers of change in network structure increasses or decreasses the manageability of communities as well as the relative importance of species at driving the population dynamics of other species in the community.
+\todo{punchy line to finish here?}.
 
@@
 
-\subsection*{Maximum matching}
+\subsection*{Theory of network manageability}
+
+\subsubsection*{Maximum matching}
 
 The number of nodes necessary to fully control a complex network can be calculated by counting the number of unmatched nodes in the network's maximum matching \autocite{Liu2011}.
-In a directed network a matching is a subset of links in which no two links share a common starting node or a common ending node and node is matched if it is the ending node of one of the links in the matching (\autoref{fig:explain_mm}a).
-A matching is  maximum if the number of matched liks (matching size) is maximal, and the sum of the weights of the matched links (matching weight) is the largest possible among all possible matchings \autocite{West2001}.
+In a directed network a matching is a subset of links in which no two links share a common starting node or a common ending node; a node is matched if it is the ending node of one of the links in the matching (\autoref{fig:explain_mm}a).
+A matching is then maximum if \textit{(i)} the number of matched liks---also known as matching size---is maximal and \textit{(ii)} the sum of the weights of the matched links---known as matching weight---is the largest possible among all possible matchings \autocite{West2001}.
+To find the maximum matching we used an alternative bipartite representation of the network in which the two levels indicate the outgoing and incoming links to each node (\autoref{fig:explain_mm}b).
+Finding a matching in this alternative representation is equivalent to finding the set of links such that each node on the top level is matched to at most one node on the bottom level, and vice versa \autocite{West2001, Csardi2006a}.
 
@@
 
+\section*{Discussion}
+
+We found that
+
+Therefore, full controlability of ecological networks---being able to steer the ecosystem into any desired ecosystem state---would require a  This characteristics render ecological networks unlikely to be able to visist every possible system state   other closed systems, ecological networks
+
+The controllability of ecological networks is not a concept limited to control theory.
+Controllability in the ecological context can be seen as a direct meassure of the mimimum number of species whose abbundance would need to be directly regulated to achieve full network control.
+While we are far away from
+
 \section*{Acknoledgements}

### 2016-05-02 paper/manuscript.Rnw
update methods

@@
 
-To find the maximum matching in a pollination network we used an alternative bipartite representation of the network (\autoref{fig:explain_mm}b) in which the levels indicate the outgoing and incoming links to each node.
-Finding a matching in this alternative representation is equivalent to finding the set of links such that each node on the top level is matched to at most one node on the bottom level and vice versa \autocite{West2001, Csardi2006a}.
-
-The link between network controllability and the maximum matching also has an intuitive basis.
-In control theory, a network is fully controlable when each node in the network has a "superior", or input that drives its dynamics.
-Matched nodes can be controled within the network by the node pointing to it---its superior.
-However, unmatched nodes have no superior in the network and must be directly controlled by external inputs \autocite{Liu2011}, what we refer to as management interventions .
-
-\subsection*{Manageability}
-
-Systems that require a large number of inputs are more difficult to control.
-The \textit{manageability} of a community is therefore determined by the minimum number of species on which we would need to apply management interventions if we were to gain full control of the abbundances of all species in the ecological community ($n_d$, \autoref{eq:m}).
-
-\begin{equation} \label{eq:m}
-m = 1- \frac{n_d}{s}
-\end{equation}
-
-We quantified the manageability of ten paired plant-pollinator communities.
-Each pair was composed by a community invaded by a plant and a community effectively free of the invasive species (Table S1).
-The networks were constructed from previously published visitation data collected from pollination communities in Bristol, UK \autocite{Lopezaraiza-Mikel2007} and Cap de Creus National Park, Spain \autocite{Bartomeus2008}.
-In the four British uninvaded communities the non-invaded plots were obtained by experimentally removing all the flowers of invasive species \textit{Impatients grandulifera}.
-In contrast, the Spanish uninvaded communities were obtained from plots that had not yet been colonised by the invasive species \textit{Carpobrotus affine acinaciformis} or \textit{Opuntia stricta}.
-
-The analysed networks were quantified using visitation frequency, which has been shown to be an appropriate surrogate for inter-specific effects in pollination networks \autocite{Vazquez2005, Bascompte2006}.
-Nevertheless we evaluated the effect of using pollinator efficiency or importance as measures of species interactions \autocite{NeEman2010, Ballantyne2015} and found consistent results (see Supplementary Information).
-
-\subsubsection*{Interspecific effects}
-
-Our maximum matching algotithm requires a directed network in which a link between species $i$ and $j$ pointing to species $j$ indicates that the abundance of species $j$ can be affected by the abundance of species $i$.
-The extent to which a pair of interacting species affect each other---the mutualism strengtht---can be quantified by the magnitude of the mutual dependence \autocite{Bascompte2006}.
-Therefore, we initially assumed that a pair of interacting species can affect each other abundances.
-The effect on each other being inverselly proportional to the magnitude of the dependencies.
-This assumption renders a bipartite network in which interacting pairs are connected by two directed links (\autoref{fig:explain_cd}b).
+Given a maximum matching, the link to network controllability has a relatively straightforward and intuitive basis.
+In control theory, a network is fully controlable when each node has a "superior", this is, an input that drives its dynamics.
+Matched nodes can thus be controled by the node pointing to it---its superior.
+Unmatched nodes on the other hand, have no superior in the network and must be directly controlled by external inputs \autocite{Liu2011}.
+In an ecological context, this is what we refer to as management interventions.
+
+Systems that require a large number of external inputs are more difficult or costly to control.
+The \textit{manageability} of a community $m$ is therefore determined by the proportion $n_d$ of species on which we would need to apply management interventions in order to gain full control of the abundances of all species in the ecological community, $$m = 1- \frac{n_d}{s},$$ where $s$ is the total number of species in the community.
+
+\subsubsection*{Weighting links}
+
+Recall that our maximum matching algorithm requires a directed network in which a link between species $i$ and $j$ pointing to species $j$ indicates that the abundance of $j$ can be affected by the abundance of $i$.
+In ecological networks, establishing a directionality for the links between species is relatively straightforward when they represent resources or energy flow, however, interspecific effects---particularly in pollination networks---are not strictly directed.
+Nevertheless, the extent to which a pair of interacting species affect each other can be quantified by the magnitude of the mutual dependence \autocite{Bascompte2006}.
+As the dependencies are bidirectional, this assumption renders a bipartite network in which interacting pairs are connected by two directed links (\autoref{fig:explain_cd}b).
 
@@
 In other words, if a plant species is largely dependent on a pollinator species, then the pollinator tends to depend only very weakly on the plant.
-This suggest that it may be possible to relax our initial assumption and simplify the network such that interacting species are connected by one directed link when mutual dependencies are assymetric.
-The direction of this link being consistent with the dominant direction of control in the bidirectional case (\autoref{fig:explain_cd}c).
-The extent to which a species $i$ affects species $j$ relative to the extent to which species $j$ affects species $i$ can then be summarised by the interaction asymmetry (\autoref{eq:a}).
-
-\begin{equation} \label{eq:a}
-a(i,j) = \frac{\left | d_{ij}-d_{ji} \right |}{\textup{max}\left ( d_{ij}, d_{ji} \right )}
-\end{equation}
-
-We quantified the manageability of the analysed pollination communities by finding the maximum matching of the corresponding pollination network following the method previously explained.
+This suggest that it may be possible to relax our initial assumption and simplify the network such that interacting species are connected by one directed link when mutual dependencies are highly assymetric (\autoref{fig:explain_cd}c).
+The extent to which a species $i$ affects species $j$ relative to the extent to which species $j$ affects species $i$ can then be summarised by the interaction asymmetry.
+
+$$a(i,j) = \frac{\left | d_{ij}-d_{ji} \right |}{\textup{max}\left ( d_{ij}, d_{ji} \right )}$$
+
+\subsubsection*{Relative species importance}
+
+\todo[inline]{insert ecological motivation}
+
+The manageability of a community $m$ provides an indication of the magnitude of $n_d$ but not the identity of the species that compose this set.
+Moreover, maximum matchings are often not unique in for a given network and different sets of species of size $n_d$ could be used to control the network \autocite{Liu2011}.
+Species vary in terms of the frequency with which they are classified as superior nodes (\autoref{fig:explain_mm}), and this frequency provides an indication of their relative importance in driving the state of the community.
+
+We therefore call \textit{driver species} those that are identified as being a superior node in all\todo{check} possible matchings\todo{elaborate concept}, and consequently likely to have a disproportionate effect on the abbundances of other species in the community.
+Unlike unweighted networks, where a maximum matching is defined by its matching size (the number of matching links), a maximum matching in a weighted network is one whose links have the largest possible total weight among all possible matchings.
+This means that in weighted networks there is a number of matchings that have maximal size, but are not maximum matchings because their total weight is not maximal.
+
+We therefore identified the driver species in each of the networks by computing all possible matchings in the network that have the same maximal size while allowing for some tolerance regarding the weight.
+We relax the matching weight requirement because empirical intreaction strengths, from which we calculate dependencies, are stochastic to some extent and depend on the sampling method and intensity.
+To compute all the maximal matchings, we first generated the network's line graph---an alternative representation in which nodes are the interactions of the original network and links represent common ending points.
+We then calculated the complement of the line graph---a graph in which nodes are adjacent if and only if they are not adjacent in the line graph.
+All possible maximum matchings can be found by enumerating all cliques of size $1-n_d$ in this complement graph \autocite{West2001, Csardi2006a}.
+
+\subsection*{Empirical Data}
+
+In the last section we outlined the theoretical and computational underpinings of our approach.
+Now we illustrate its empirical application using ten pairs of plant-pollinator communities for which we calculated their manageability and the relative importance of species.
+Each network pair was composed by a community invaded by a plant and a community effectively free of the invasive species (Table S1).
+The networks were constructed from previously published visitation data collected from pollination communities in Bristol, UK \autocite{Lopezaraiza-Mikel2007} and in Cap de Creus National Park, Spain \autocite{Bartomeus2008}.
+In the four British uninvaded communities, the non-invaded plots were obtained by experimentally removing all the flowers of the invasive species \textit{Impatients grandulifera}.
+In contrast, the Spanish uninvaded communities were obtained from plots that had not yet been colonised by either of the invasive species \textit{Carpobrotus affine acinaciformis} or \textit{Opuntia stricta}.
+
+The structure of these networks was determined using visitation frequency which has been shown to be an appropriate surrogate for inter-specific effects in pollination networks \autocite{Vazquez2005, Bascompte2006}.
+To examine the importance of this decision, we also evaluated the effect of using pollinator efficiency or importance as alternative measures of species interactions \autocite{NeEman2010, Ballantyne2015}, and we found consistent results for all of these options(see Supplementary Information).
+
+We started by quantifying the manageability of the analysed pollination communities.
+To do that, we calculated the maximum matching of the corresponding pollination network, and estimated the minimum number of species that need directed intervecntions to fully control the species abbundances in the community.
 If a network had more than one component (two species are in different components if there exist no path between them) we analysed the largest one.
+In order to check that
+
 We then performed a paired Spearman correlation test to compare the manageability obtained when including bidirectional effects between interacting species, and when simplyfing the network to include only the dominant direction of the asymmetry.
@@
 
-The manageability of a community $m$ provides an indication of the magnitude of $n_d$ but not the identity of the species that can compose this set.
-In fact, maximum matchings are often not unique in ecological networks and different sets of species of size $n_d$ could be used to control the network \autocite{Liu2011}.
-Nevertheless, species vary in terms of the frequency with which they are classified as superior nodes (\autoref{fig:explain_mm}).
-This frequency provides an indication of their relative importance to drive the state of the community.
-We therefore call \textit{driver species} those that are identified as needing directed interventions in all possible matchings\todo{elaborate concept}, and consequently likely to have a disproportionate effect on the abbundances of other species in the community.
-
-Unlike unweighted networks, where a maximum matching is defined by its size (the number of matched edges), in weighted networks, a maximum matching is one whose edges have the largest possible total weight among all possible matchings.
-This means that in weighted networks there is a number of matchings that have maximal size, but are not maximum matchings because its total weight is not maximal too.
  However the weight of species dependencies is unexact, a reflection of the fact that interaction strengths and sampling methods themselves are stochastic to some extent.
@@
 We therefore identified the driver species in each of the networks by computing all possible matchings in the network that have the same size and have a weight above a cut-off of 0.5 times the weight of the maximum matching\todo{justify}.
-To do so, we first generated the network's line graph---an alternative representation in which nodes are the interactions of the original network and links represent common ending points.
-We then calculated the complement of the line graph---a graph in which nodes are adjecent if and only if they are not adjancent in the line graph.
-All possible maximum matchings can be found by enumerating all cliques of size $1-n_d$ in the complement graph \autocite{West2001, Csardi2006a}.
+
 Because of the number of matchings depends on the cut-off and the weighting of the links, we evaluated the effects of i) using a different cut-offs value between 0 and 1 and ii) weighting the links by the number of visits.

### 2016-05-03 paper/manuscript.Rnw
update methods

@@
 
-\section*{Methods}
-
-\subsection*{Theory of network manageability}
-
-\subsubsection*{Maximum matching}
+\section*{Theory of community manageability}
+
+\subsection*{Maximum matching}
 
@@
 
-\subsubsection*{Weighting links}
+\subsection*{Weighting links}
 
@@
 
-\subsubsection*{Relative species importance}
-
-\todo[inline]{insert ecological motivation}
+\subsection*{Relative species importance}
+
+\todo[inline]{insert ecological motivation?}
 
@@
 
-We therefore call \textit{driver species} those that are identified as being a superior node in all\todo{check} possible matchings\todo{elaborate concept}, and consequently likely to have a disproportionate effect on the abbundances of other species in the community.
+We therefore call \textit{driver species} those that are identified as being a superior node in all\todo{check}  possible matchings, and consequently likely to have a disproportionate effect on the abbundances of other species in the community.
 Unlike unweighted networks, where a maximum matching is defined by its matching size (the number of matching links), a maximum matching in a weighted network is one whose links have the largest possible total weight among all possible matchings.
@@
 
-We therefore identified the driver species in each of the networks by computing all possible matchings in the network that have the same maximal size while allowing for some tolerance regarding the weight.
+Consequently, we identified the driver species in each of the networks by computing all possible matchings in the network that have the same maximal size while allowing for some tolerance regarding the weight.
 We relax the matching weight requirement because empirical intreaction strengths, from which we calculate dependencies, are stochastic to some extent and depend on the sampling method and intensity.
-To compute all the maximal matchings, we first generated the network's line graph---an alternative representation in which nodes are the interactions of the original network and links represent common ending points.
+To compute all the matchings with maximal size, we first generated the network's line graph---an alternative representation in which nodes are the interactions of the original network and links represent common ending points.
 We then calculated the complement of the line graph---a graph in which nodes are adjacent if and only if they are not adjacent in the line graph.
@@
 
-\subsection*{Empirical Data}
+\section*{Methods}
 
@@
 In contrast, the Spanish uninvaded communities were obtained from plots that had not yet been colonised by either of the invasive species \textit{Carpobrotus affine acinaciformis} or \textit{Opuntia stricta}.
-
 The structure of these networks was determined using visitation frequency which has been shown to be an appropriate surrogate for inter-specific effects in pollination networks \autocite{Vazquez2005, Bascompte2006}.
 To examine the importance of this decision, we also evaluated the effect of using pollinator efficiency or importance as alternative measures of species interactions \autocite{NeEman2010, Ballantyne2015}, and we found consistent results for all of these options(see Supplementary Information).
+
+\subsection*{Community manageability}
 
@@
 If a network had more than one component (two species are in different components if there exist no path between them) we analysed the largest one.
-In order to check that
-
-We then performed a paired Spearman correlation test to compare the manageability obtained when including bidirectional effects between interacting species, and when simplyfing the network to include only the dominant direction of the asymmetry.
-
-Naively one might expect to see a negative relationship between diversity and manageability \autocite{Menge1995}.
-We therefore used a set of generalised linear models to investigate the relatioship between community manageability and (i) the total number of species, (ii) plant richness, (iii) polinators richness, and (iv) the ratio of plants to pollinators richness.
-Because both invaded and British communities tended to be more diverse, we also assesed whether observed differences in manageability were due to these two factors.
+Although understanding the distribution of manageability across ecological networks is an useful result in itself, we wanted to test wheter perturbations, like invasion status, have an impact on manageability values.
+As, naively one might expect to see a negative relationship between diversity and manageability \autocite{Menge1995}, we used a set of generalised linear models to investigate the effect of invasion status while controling for \textit{(i)} the total number of species, \textit{(ii)} plant richness, \textit{(iii)} polinators richness, \textit{(iv)} the ratio of plants to pollinators richness, and \textit{(v)} the study site.
 Competing models were assessed by comparing the Akaike Information Criterion corrected for small sample sizes (AICc).
 
-To quantify the extent to which manageability is characteristic of the network structure\todo{failed to come up with a better wording}, we compared the manageability of empirical networks to networks generated by two null models of visitation.
-One set of random visitation networks was generated by maintaining the species degree (the number of interactions per species) while varying the number of visits per species.
-A second set of random network mantained the species strength (total sum of visits) while varying the degree of species \autocite{Oksansen2016}.
-We then calculated the mutual dependences and interaction asymmetries of the random networks and calculated the p-value of the manageability of each empirical network and the corresponding manageability of 999 randomisations.
-
-We also quantified the extent to which the relative manageability of a pollination community is given by the dominant direction of control, we mantained the structure of network but randomised the direction of the interaction asymmetries.
+Subsequently we explored the extent to which structural factors in the empirical networks influence their manageability.
+Previous studies found a direct link between a network's degree distribution and the number of nodes necessary to fully control it \autocite{Liu2011}, but this relationship has not been explored in weighted ecological networks.
+We therefore compared the manageability of the empirical networks to networks generated by three null models.
+One set of random visitation networks was generated by maintaining each species' degree (its number of interactions) while varying the number of visits per species.
+A second set of random networks mantained the species' strength (its total sum of visits) while varying their degrees.
+Randomisations were generated using vegan 2.3-3 \autocite{Oksansen2016}.
+Finally a three set of fully random networks maintained only the connectivity of the empirical network, but both degree and weight were allowed to vary.
+We then calculated the mutual dependences and interaction asymmetries of the random networks and calculated their manageability using the maximum matching algorithm.
+Finally we calculated the p-value of the manageability of each empirical network and the corresponding manageability of 999 randomisations.
+
+The dependency asymetry plays a fundamental role in determining the direction of control in a two species interaction and therefore has the potential to structure the network matching.
+We therefore performed an additional randomisation in which we mantained the structure of network but randomised the direction of the interaction asymmetries.
 This is, we first calculated the assymetries for each community and then shuffled the direction of the link between species.
-Similar as in previouls null models, we calculated the p-value of the empirical manageability and that of the randomisations.
-
-\subsection*{Driver species}
-
- However the weight of species dependencies is unexact, a reflection of the fact that interaction strengths and sampling methods themselves are stochastic to some extent.
-
-We therefore identified the driver species in each of the networks by computing all possible matchings in the network that have the same size and have a weight above a cut-off of 0.5 times the weight of the maximum matching\todo{justify}.
-
-Because of the number of matchings depends on the cut-off and the weighting of the links, we evaluated the effects of i) using a different cut-offs value between 0 and 1 and ii) weighting the links by the number of visits.
-
-Similar as when we compared the manageability obtained when assuming bidirectional links or single links determined by the asymmetry (\autoref{fig:explain_cd}), we compared the realtive importance of species under these two assumptions by calculating a paired Spearman correlation test between species' relative importance.
-Nevertheless because we are more interested on the agreement between highly ranked species we also calculated a weighted correlation coefficient $r_{w2}$ which gives more weight to higer ranks (\autoref{PintoDaCosta2015}), and the Jaccard similarity of the driver species identified by both methods.
-
-We then tackled the question whether some species level structural properties can predict the relative importance of driver species.
-Here, we used a Generalised Linear Mixed-Effects model (\autoref{Bates2015}) to evaluate the effect on the species' relative importance of measures of centrality (degree, betweenness, and overlap), measures related to network robustness (contribution to nestedness), and measures of strength of association and depedency (visitation and dependency strength) \autocite{Dormann2008}.
-The community was included as a random effect.
+Similar as in previouls null models, we calculated the p-value of the empirical manageability compared to that of the randomisations.
+
+\subsection*{Relative importance of species}
+
+Our third question is related to how different species differ on their importance for the population dynamics of the community.
+To quantify this importance we computed all possible matchings that have the same size as the maximum matchings and in each network.
+We then calculated the frequency to which each species is deemed to be a superior node in matchings with a weight equal or larger to 0.5 times the weight of the maximum matchings.
+We choose this threshold as it provided a high agreement between the relative importance of species calculated by weighting interactions with the mutial dependencies or the depndence asymmetry as well as between the network is quantified by visitation or pollination efficiency.
+Nevertheless, the choice of the threshold only had a negligible impact on the results (Supplementary information).
+
+The number of maximal matchings increasses exponentially with the number of links and nodes in a network.
+When we use mutual dependecies, the large number of links in the most diverse communities renders the computation unfeasible.
+Taking this limitation into account we compared the relative network manageability obtained when using assimetries or when using mutual dependencies for eleven networks---for which the number of matchings was smaller than $4\times 10^{10}$.
+Results from a paired Spearman correlation test, the weighted correlation coefficient $r_{w2}$---which gives more weight to higer ranks \autocite{PintoDaCosta2015}, and the Jaccard similarity of the driver species in both approaches, suggested a high similarity in relative ranks.
+Therefore, we used the results from the assymetries, rather than mutiual dependences, to further investigate the factors that determine species' relative importance.
+
+We then asked the question of whether some species-level structural properties can predict the relative importance of species.
+Here, we used a Generalised Linear Mixed-Effects model to evaluate the effect on the species' relative importance of a suite of structural measures.
+We included measures of centrality (degree and eigen-centrality) which have been found to be strong predictors of importance in a coextintion context\todo{add ref}; measures related to network robustness (contribution to nestedness) as nestedness has been proposed as one of the key properties that promote stability in mutualistic networks \autocite{Saavedra2011}; and measures of strength of association and depedency (visitation and dependency strength) as their skewed distribution is characteristic of plant-pollinator networks and determine the extent of interspecific effects.
+All metrics were calculated using bipartite 2.06 \autocite{Dormann2008}.
+To allow for variation among different ecological communities, this factor was included as a random effect \autocite{Bates2015a}.
 Candidate models were compared using AIC and the relative importance of the explanatory variables was evaluated using the sum of Akaike weights over candidate models that accounted for 95\% of the evidence \autocite{Burnham2003, Bates2014, Barton2016}.
+
+Invasive species have been shown to have disproportionate effects on the communities they invade.
+So we examined the extent to which invasive species tend to be driver species---species whith the maximum importance.
+As our invasive species were plants, we compared the relative importance of invasive species to those of other plants in the community and to which degree they differ when accounting for the structural factors that determine their importance\todo{needs to be developed once the results section is rewritten}.
 

### 2016-05-04 paper/manuscript.Rnw
update partially results change code for randomisations

@@
 % Article title
-  \title{{\LARGE \textsc{Structural controlability of pollination networks}}}
+  \title{
+  {\LARGE \textsc{Structural controlability of pollination networks}}\\
+  {\LARGE \textsc{Structural controlability of ecological networks}}\\
+  {\LARGE \textsc{Network manageability in the context of species invasion}}\\
+  {\LARGE \textsc{Biotic invasions reduce manageability of ecological networks}}\\
+  {\LARGE \textsc{Identifying the ``driver species'' of an ecosystem}}}
 
@@
 Although understanding the distribution of manageability across ecological networks is an useful result in itself, we wanted to test wheter perturbations, like invasion status, have an impact on manageability values.
-As, naively one might expect to see a negative relationship between diversity and manageability \autocite{Menge1995}, we used a set of generalised linear models to investigate the effect of invasion status while controling for \textit{(i)} the total number of species, \textit{(ii)} plant richness, \textit{(iii)} polinators richness, \textit{(iv)} the ratio of plants to pollinators richness, and \textit{(v)} the study site.
+As, naively one might expect to see a negative relationship between diversity and manageability \autocite{Menge1995}, we used a set of generalised linear models (with binomial error structure) to investigate the effect of invasion status while controling for \textit{(i)} the total number of species, \textit{(ii)} plant richness, \textit{(iii)} polinators richness, \textit{(iv)} the ratio of plants to pollinators richness, and \textit{(v)} the study site.
 Competing models were assessed by comparing the Akaike Information Criterion corrected for small sample sizes (AICc).
@@
 
-\subsection*{Manageability}
+\subsection*{Community manageability}
 
@@
 
-We found that if we were to control the dynamics of the whole community, we would need to control between \Sexpr{round(min(dplyr::filter(n_driver, type == "z-bi")$n_dr_p)*100)} and \Sexpr{round(max(dplyr::filter(n_driver, type == "z-bi")$n_dr_p)*100)}\% (mean \Sexpr{round(mean(dplyr::filter(n_driver, type == "z-bi")$n_dr_p)*100)}\%) of the species in the community if we were to harness bidirectional links between species, and between \Sexpr{round(min(dplyr::filter(n_driver, type == "weight")$n_dr_p)*100)} and \Sexpr{round(max(dplyr::filter(n_driver, type == "weight")$n_dr_p)*100)}\% (mean \Sexpr{round(mean(dplyr::filter(n_driver, type == "weight")$n_dr_p)*100)}\%) if we only take into account the strongest dependence.
-This corresponds to manageabilities between \Sexpr{round(min(1-dplyr::filter(n_driver, type == "z-bi")$n_dr_p), digits = 2)} to \Sexpr{round(max(1-dplyr::filter(n_driver, type == "z-bi")$n_dr_p), digits = 2)} and \Sexpr{round(min(1-dplyr::filter(n_driver, type == "weight")$n_dr_p), digits = 2)} to \Sexpr{round(max(1-dplyr::filter(n_driver, type == "weight")$n_dr_p), digits = 2)} respectively (Table S1).
-Despite different absolute values of manageability between these assuptions, the relative manageability of different communities was mantained (Spearman rank correlation \Sexpr{round(src_bi_w$estimate, digits = 2)}, $p = \Sexpr{as.numeric(format(src_bi_w$p.value, digits = 2))}$).
-In addition, the ratio of plant to pollinator species richness is positively correlated with manageability ($Pr(>\chi^2) = \Sexpr{as.numeric(format(anova(m8, m6, test = "LRT")$`Pr(>Chi)`[2], digits = 2))}$).
-Similarly, invaded communities tend to be more difficult to manage than uninvaded ones ($Pr(>\chi^2) = \Sexpr{as.numeric(format(anova(m8, m1, test = "LRT")$`Pr(>Chi)`[2], digits = 2))}$).
-In constrast, measures of biodiversity (like plant or pollinator richness) or the location of the study did not have a significant effect on the manageability (\autoref{fig:n_driver_explanatory}, Table S3).
+The studyed networks had levels of manageability between \Sexpr{round(min(1-dplyr::filter(n_driver, type == "z-bi")$n_dr_p), digits = 2)} and \Sexpr{round(max(1-dplyr::filter(n_driver, type == "z-bi")$n_dr_p), digits = 2)} (mean \Sexpr{round(mean(1-dplyr::filter(n_driver, type == "z-bi")$n_dr_p), digits = 2)}) when we considered bidirectional links weighted by the mutual dependences.
+This was in strong agreement  to the results obtained using the dependence asymmetry in which manageability ranged between \Sexpr{round(min(1-dplyr::filter(n_driver, type == "weight")$n_dr_p), digits = 2)} and \Sexpr{round(max(1-dplyr::filter(n_driver, type == "weight")$n_dr_p), digits = 2)} (Spearman rank correlation \Sexpr{round(src_bi_w$estimate, digits = 2)}, $p = \Sexpr{as.numeric(format(src_bi_w$p.value, digits = 2))}$).
+In addition we found that even when controling for diversity, invaded communities had were more difficult to manage than uninvaded ones.
+Out of the explored factors---total number of species, plant richness, pollinator richness and the ratio of plant to pollinator richness---only the ratio of plants to pollinator was retained in the final model (as determined by the AICc; \autoref{fig:n_driver_explanatory}, Table S3).
 
@@
 \centering
-<<fig explaining n_driver, echo = FALSE, warning = F, message = F, results = "asis", fig.height=2.2, fig.width=3.245>>=
-p <- predict(m8, type = "response", se.fit = F)
-
-n_driver_wb %>%
-  dplyr::mutate(fit = predict(m8, type = "response", se.fit = T)$fit,
-                se =  predict(m8, type = "response", se.fit = T)$se) %>%
-  dplyr::filter(type == "z-bi" | type == "weight") %>% 
-  ggplot(aes(x = n_pla/n_pol, y = 1-n_dr_p)) +
-  geom_line(aes(y = 1-fit, colour = type, linetype = inv), size = 0.5) + 
-  geom_point(aes(fill = type, shape = inv), show.legend = T, size = 1.25) +
-  ylab("manegeability") + 
-  xlab("plant / pollinator richness") +
-  scale_fill_manual(values = c("#ffffff", "#bdbdbd"),
-                      name = "direction of control", 
-                      labels = c("asymmetry", "mutual dependence")) +
-  scale_colour_manual(values = c("black", "#bdbdbd"),
-                      name = "direction of control", 
-                      labels = c("asymmetry", "mutual dependence")) + 
-  scale_shape_manual(values = c(21, 23), 
-                     name = "invasion status", 
-                     labels = c("invaded", "non invaded")) +
-  scale_linetype_manual(values = c(1, 12), 
-                        name = "invasion status", 
-                        labels = c("invaded", "non invaded")) +
+<<fig explaining n_driver, echo = FALSE, warning = F, message = F, results = "asis", fig.height=1.7, fig.width=3.245>>=
+
+par_res <- as.data.frame(residuals(m8, "partial"))
+names(par_res) <- paste0(make.names(names(par_res)), "_res")
+par_res %<>%
+  dplyr::bind_cols(m8$data) %>%
+  dplyr::mutate(res_res = residuals(m8, "response"), 
+                res_wor = residuals(m8, "working"))
+
+par_res %>%
+  ggplot(aes(x = inv, y = inv_res)) +
+  # facet_wrap(~type) +
+  geom_boxplot(size = 0.3,
+               colour = "grey10", outlier.shape = 21, outlier.size = 1) +
   fer_theme +
-  theme(plot.margin = grid::unit(c(5, 1, 2, 0), "mm"), 
+  scale_x_discrete(labels = c("un-invaded", "invaded"), name = "") +
+  ylab("adjusted manageability") +
+  coord_flip() +
+  theme(
         legend.position = "none",
-        # legend.title = element_blank(),
-        legend.key = element_rect(fill = "white", 
-                                  colour = "white"),
-        legend.key.size = grid::unit(4, "mm"),
-        legend.background = element_rect(colour = "black", size = 0.2),
-        legend.box = "horizontal",
-        legend.direction = "vertical") 
-@
-\caption{\label{fig:n_driver_explanatory} The relative manageability of a plant-pollinator community is largely influenced by the ratio of plant to pollinator species richness and to a smaller extent to the status of invasion.
-Invaded communities (circles, dashed lines) having larger levels of manageability.
-White and grey points correspond to manageabilities calculated using mutual dependences and interaction asymmetry respectively.}
+				plot.margin = grid::unit(c(2, 1, 2, 0), "mm"), 
+				# panel.grid.minor.x = element_blank(),
+				panel.grid.minor.y = element_blank())
+
+# p <- predict(m8, type = "response", se.fit = F)
+# 
+# n_driver_wb %>%
+#   dplyr::mutate(fit = predict(m8, type = "response", se.fit = T)$fit,
+#                 se =  predict(m8, type = "response", se.fit = T)$se) %>%
+#   dplyr::filter(type == "z-bi" | type == "weight") %>% 
+#   ggplot(aes(x = n_pla/n_pol, y = 1-n_dr_p)) +
+#   geom_line(aes(y = 1-fit, colour = type, linetype = inv), size = 0.5) + 
+#   geom_point(aes(fill = type, shape = inv), show.legend = T, size = 1.25) +
+#   ylab("manegeability") + 
+#   xlab("plant / pollinator richness") +
+#   scale_fill_manual(values = c("#ffffff", "#bdbdbd"),
+#                       name = "direction of control", 
+#                       labels = c("asymmetry", "mutual dependence")) +
+#   scale_colour_manual(values = c("black", "#bdbdbd"),
+#                       name = "direction of control", 
+#                       labels = c("asymmetry", "mutual dependence")) + 
+#   scale_shape_manual(values = c(21, 23), 
+#                      name = "invasion status", 
+#                      labels = c("invaded", "non invaded")) +
+#   scale_linetype_manual(values = c(1, 12), 
+#                         name = "invasion status", 
+#                         labels = c("invaded", "non invaded")) +
+#   fer_theme +
+#   theme(plot.margin = grid::unit(c(5, 1, 2, 0), "mm"), 
+#         legend.position = "none", 
+#         # legend.title = element_blank(),
+#         legend.key = element_rect(fill = "white", 
+#                                   colour = "white"),
+#         legend.key.size = grid::unit(4, "mm"),
+#         legend.background = element_rect(colour = "black", size = 0.2),
+#         legend.box = "horizontal",
+#         legend.direction = "vertical") 
+@
+\caption{\label{fig:n_driver_explanatory} Invaded communities have lower levels of manageability than uninvaded communities even when controling for the ratio of plant to pollinator richness.
+Adjusted manageability corrsponds to the partial working residuals of the invasion status.}
 \end{figure}
@@
 
-\subsection*{Driver species}
+\subsection*{Relative importance of species}
 
@@
 
-Species vary widely on the degree of their importance for network manageability.
-Our method to calculate the relative importance of species relies on calculating all possible maximum matchings.
-The number of matchings increasses exponentially with the number of links and nodes in a network.
-When we use mutual dependecies, there are two links between each interacting species, and we were only able to find the importance of different species in the eleven smallest networks.
-For the remaining nine networks, the number of maximum matchings is much larger than $4\times 10^{10}$ and the computation of the species relative importance became unfeasible.
-
-Nevertheless, we were able to find the relative importance of species in the single link version of the networks where links were weighted by the assymetry.
-For the networks in which we were able to calculate the importance using mutual dependencies, we found a strong correlation between both approaches (Spearman's rank correlation ranged between $\rho = [\Sexpr{round(min(dplyr::filter(correlations, threshold == 0.5, type == "asymmetry", scaled == T)$V3, na.rm = T), digits = 2)}, \Sexpr{round(max(dplyr::filter(correlations, threshold == 0.5, type == "asymmetry", scaled == T)$V3, na.rm = T), digits = 2)}]$, median $\tilde{\rho} = \Sexpr{round(median(dplyr::filter(correlations, threshold == 0.5, type == "asymmetry", scaled == T)$V3, na.rm = T), digits = 2)})$.
+We found a strong agreement between relative species' importance in the 11 networks for which we were able to calulate it using both mutual dependencies and asymmetries (Spearman's rank correlation ranged between $\rho = [\Sexpr{round(min(dplyr::filter(correlations, threshold == 0.5, type == "asymmetry", scaled == T)$V3, na.rm = T), digits = 2)}, \Sexpr{round(max(dplyr::filter(correlations, threshold == 0.5, type == "asymmetry", scaled == T)$V3, na.rm = T), digits = 2)}]$, median $\tilde{\rho} = \Sexpr{round(median(dplyr::filter(correlations, threshold == 0.5, type == "asymmetry", scaled == T)$V3, na.rm = T), digits = 2)})$.
 Indeed, when using the weighted rank correlation coefficient $r_{w2}$, we found that the agreement was stronger for highly ranked species than for lowly ranked species ($\tilde{r_{w2}} = \Sexpr{round(median(dplyr::filter(correlations, threshold == 0.5, type == "asymmetry", scaled == T)$V1, na.rm = T), digits = 2)}$ versus $\tilde{r_{w2}} = \Sexpr{round(median(dplyr::filter(correlations, threshold == 0.5, type == "asymmetry", scaled == T)$V2, na.rm = T), digits = 2)}$).
-Moreover both approaches identified a highly similar set of driver species (Jaccard similarity $J = [\Sexpr{round(min(dplyr::filter(correlations, threshold == 0.5, type == "asymmetry", scaled == T)$V4, na.rm = T), digits = 2)}, \Sexpr{round(max(dplyr::filter(correlations, threshold == 0.5, type == "asymmetry", scaled == T)$V4, na.rm = T), digits = 2)}]$, $\tilde{J} = \Sexpr{round(median(dplyr::filter(correlations, threshold == 0.5, type == "asymmetry", scaled == T)$V4, na.rm = T), digits = 2)})$
+Moreover both approaches identified a highly similar set of driver species (Jaccard similarity $J = [\Sexpr{round(min(dplyr::filter(correlations, threshold == 0.5, type == "asymmetry", scaled == T)$V4, na.rm = T), digits = 2)}, \Sexpr{round(max(dplyr::filter(correlations, threshold == 0.5, type == "asymmetry", scaled == T)$V4, na.rm = T), digits = 2)}]$, $\tilde{J} = \Sexpr{round(median(dplyr::filter(correlations, threshold == 0.5, type == "asymmetry", scaled == T)$V4, na.rm = T), digits = 2)})$.
+Therefore we employed the relative rankings obtained using asymmetries in the following analyses.
 
@@
 
-Although plants showed significantly higher levels of importance for network control than pollinators (Mann-Withney-Wilcoxon test, $p \Sexpr{fix_small_pvalue(wilcox.test(pp ~ guild, data = dd, alternative = "greater")$p.value)}$), this difference can be largely explained by the strength of dependency of the species (the sum of the dependencies for a given species).
+Although plants showed significantly higher levels of importance than pollinators (Mann-Withney-Wilcoxon test, $p \Sexpr{fix_small_pvalue(wilcox.test(pp ~ guild, data = dd, alternative = "greater")$p.value)}$), this difference can be largely explained by the strength of dependency of the species (the sum of the dependencies for a given species).
 Indeed, when averaging over the set of GLMMs that accounted at least 95\% of the evidencee based on AICc, we found that the strength of dependency  is the single most important factor determining the relative importance of species for network control (\autoref{table:driver_model}\todo{consider moving the table to thes supplementary}, \autoref{fig:driver_model_alt}).
-Contrastingly, the number of visits a species receives (or performs) and its contribution to nestedness have only a marginal effect on its relative importance for network control.
+In contrast, the number of visits a species makes (or receives) and its contribution to nestedness have only a marginal effect on its relative importance.
+
 In addition, in the ten communities that were invaded, invasive species were invariably classified as a driver species.
@@
 EFC acknowledges the support from the University of Canterbury Doctoral Scholarship, the University of Canterbury Meadow Mushroooms Postgraduate Scholarship, a travel grant from the European Space Agency and a Rutherford Discovery Fellowship (to DBS).
-DBS ackloledges the support of a Rutherford Discovery Scholarship, administered by the Royal Society of New Zealand.
+DBS ackloledges the support of a Rutherford Discovery Fellowship, administered by the Royal Society of New Zealand.
 

### 2016-05-04 code/V2.0/05-random_weights.R

@@ -26,16 +26,16 @@ null_methods <- c(
 	# "swsh_samp",
 	# "swsh_samp_r",
 	# "swsh_samp_c",
-	"swsh_both"
+	"swsh_both",
 	# "swsh_both_r",
 	# "swsh_both_c",
-	# "r00_ind",
+	"r00_ind",
 	# "r0_ind",
 	# "c0_ind",
-	# "r00_samp",
+	"r00_samp",
 	# "r0_samp",
 	# "c0_samp",
-	# "r00_both",
+	"r00_both"
 	# "r0_both",
 	# "c0_both"
 ) 

### 2016-05-04 code/V2.0/tinkering/understand_randomisations.R

@@ -8,7 +8,7 @@ m[sample(length(m), round(size/10 * 6))] <- 0
 m %<>% matrix(ncol = sqrt(size))
 
 # random models
-simul <- vegan::nullmodel(m, "r00_ind") %>%
+simul <- vegan::nullmodel(m, "r00_both") %>%
 	simulate(3)
 
 # marginal sums

### 2016-05-05 paper/manuscript.Rnw
results updated

@@
   \title{
-  {\LARGE \textsc{Structural controlability of pollination networks}}\\
-  {\LARGE \textsc{Structural controlability of ecological networks}}\\
-  {\LARGE \textsc{Network manageability in the context of species invasion}}\\
-  {\LARGE \textsc{Biotic invasions reduce manageability of ecological networks}}\\
-  {\LARGE \textsc{Identifying the ``driver species'' of an ecosystem}}}
+  {\LARGE \textsc{Structural controlability of pollination networks}}}
 
@@
 \maketitle
+
+Alternative titles:
+
+\textsc{Structural controlability of ecological networks}
+
+\textsc{Network manageability in the context of species invasion}
+
+\textsc{Biotic invasions reduce manageability of ecological networks}
+
+\textsc{Identifying the ``driver species'' of an ecosystem}
 
@@
 
-\subsection*{Relative species importance}
+\subsection*{Relative importance}
 
@@
 
-The manageability of empirical networks varied little when compared to network randomisations that maintained the species strength or species degree.
-This result is consistent regardless of whether we consider mutual dependences or the interaction asymmetry.
-Contrastingly, empirical networks have smaller manageabilities than network randomisations in which the direction of the dependencies is altered but the structure is maintained.
+The manageability of empirical networks was, in general, not significantly different to the manageability of network randomisations that maintain the degree or the strength of individual species (\autoref{fig:randomisations}).
+However when comparing the empirical network to less constrained randomisations that maintained the original connectance but in which species had different degrees and strengths, we found that empirical networks tend to have smaller values of manageability.
+This pattern is even more marked when we maintained the network structure but randomised only the direction of the asymmetries (\autoref{fig:randomisations}).
 
@@
 \centering
-<<fig randomisations, echo = FALSE, warning = F, message = F, fig.height=2.2, fig.width=3.245>>=
+<<fig randomisations, echo = FALSE, warning = F, message = F, fig.height=2.7, fig.width=3.245>>=
 
@@
                 m_n = replace(m_n, m_n == 3, 3.5)) %>%
+  dplyr::filter(!method %in% c("r00_both", "r00_ind")) %>%
   ggplot(aes(x = method, y = -1 * z_s)) +
-  geom_rect(aes(xmin = 0.5, xmax = 3.5, ymin = -Inf, ymax = qlogis(0.025)), fill = "#f0f0f0") +
-  geom_rect(aes(xmin = 0.5, xmax = 3.5, ymin = Inf, ymax = qlogis(0.975)), fill = "#f0f0f0") +
+  geom_rect(aes(xmin = 0.5, xmax = 4.5, ymin = -Inf, ymax = qlogis(0.025)), fill = "#f0f0f0") +
+  geom_rect(aes(xmin = 0.5, xmax = 4.5, ymin = Inf, ymax = qlogis(0.975)), fill = "#f0f0f0") +
 
   # geom_hline(yintercept = c(-0), linetype = 2, alpha = 0.7, size = 0.25) + 
-  geom_vline(aes(xintercept = 2.5), alpha = 0.6, size = 0.25) +
+  geom_vline(aes(xintercept = 3.5), alpha = 0.6, size = 0.25) +
    geom_hline(yintercept = 0, size = 0.25, linetype = 2, colour = "grey30") +
@@
   scale_fill_manual(values = c("white", "#bdbdbd")) +
-  scale_x_discrete(labels = rev(c("random\nassymetry", "maintain vis. strength\nrandomise degree", "maintain vis. degree\nrandomise strength")), expand = c(0,0)) + 
+  scale_x_discrete(
+    labels = rev(c("random\nassymetry", "maintain\nconnectance", "maintain vis. strength\nrandomise degree", "maintain vis. degree\nrandomise strength")),
+    expand = c(0,0)) +
   scale_y_continuous(breaks = qlogis(c(0.001, 0.025, 0.5, 0.975,0.999)), 
@@
 
+<<invasive species differ?, echo = FALSE, warning = F, message = F, results = "hide">>=
+for_invasive <- dd %>%
+  dplyr::mutate(prediction = as.vector(predict.glmulti(mod, select = 0.95, newdata = .)$averages), 
+                predictionp = plogis(prediction), 
+                res = d_reim - predictionp) %>%
+  dplyr::filter(guild == "pla")
+
+inv_test <- wilcox.test(d_reim ~ invasive, data = for_invasive, alternative = "less")
+t.test(dplyr::filter(for_invasive, invasive)$res)
+@
+
 In addition, in the ten communities that were invaded, invasive species were invariably classified as a driver species.
+In general, the relative importance of invasive species was significantly larger than those of the other plants in the studied communities(Mann-Whitney U Test, $p =  \Sexpr{fix_small_pvalue(inv_test$p.value)}$).
+However this difference can be fully explained by the explanatory variables in our model as all the residuals for the invasive species were virtually zero.
 

### 2016-05-06 paper/manuscript.Rnw
revised methods and results

@@
 The number of nodes necessary to fully control a complex network can be calculated by counting the number of unmatched nodes in the network's maximum matching \autocite{Liu2011}.
-In a directed network a matching is a subset of links in which no two links share a common starting node or a common ending node; a node is matched if it is the ending node of one of the links in the matching (\autoref{fig:explain_mm}a).
-A matching is then maximum if \textit{(i)} the number of matched liks---also known as matching size---is maximal and \textit{(ii)} the sum of the weights of the matched links---known as matching weight---is the largest possible among all possible matchings \autocite{West2001}.
-To find the maximum matching we used an alternative bipartite representation of the network in which the two levels indicate the outgoing and incoming links to each node (\autoref{fig:explain_mm}b).
-Finding a matching in this alternative representation is equivalent to finding the set of links such that each node on the top level is matched to at most one node on the bottom level, and vice versa \autocite{West2001, Csardi2006a}.
+In a directed network, a given matching is a subset of links in which no two links share a common starting node or a common ending node; a node is matched if it is the ending node of one of the links in the matching (\autoref{fig:explain_mm}a).
+A matching is then maximum if bith \textit{(i)} the number of matched links---known as matching size---is maximal and \textit{(ii)} the sum of the weights of the matched links---known as matching weight---is the largest possible among all possible matchings of that size \autocite{West2001}.
+To find the maximum matching, we used an alternative bipartite representation of the network in which the two levels indicate the outgoing and incoming links to each node (\autoref{fig:explain_mm}b).
+Finding a matching in this alternative representation is equivalent to finding a set of links such that each node on the top level is matched to at most one node on the bottom level, and vice versa \autocite{West2001, Csardi2006a}.
 
@@
 @
-\caption{\label{fig:explain_mm}  One of the possible maximum matchings of a network (dark grey links) defines a set matched ($p_1$, $p_2$, and $a_3$) and unmatched nodes ($a_1$ and $a_2$).
+\caption{\label{fig:explain_mm} Finding a maximum matching in a complex network.
+a) We start with a directed network  in which the direction of the link represent the direction of control.
+This is, a link from $a_1$ to $p_1$ indicates that the state of $p_1$ (density/abbundances in an ecological context) are influenced by the state of $a_1$.
+b) To facilitate the computation of the maximum matching, we used an alternative undirected bipartite representation of the directed network in which each node in (a) is represented by two nodes that indicate the outgoing and incoming links.
+One of the possible maximum matchings of a network (dark grey links) defines a set matched ($p_1$, $p_2$, and $a_3$) and unmatched nodes ($a_1$ and $a_2$).
 The minimum number of species neccessary to control this network equates to the number of unmatched nodes $n_d = 2$.
@@
 Given a maximum matching, the link to network controllability has a relatively straightforward and intuitive basis.
-In control theory, a network is fully controlable when each node has a "superior", this is, an input that drives its dynamics.
-Matched nodes can thus be controled by the node pointing to it---its superior.
-Unmatched nodes on the other hand, have no superior in the network and must be directly controlled by external inputs \autocite{Liu2011}.
+In control theory, a network is fully controlable when each node has a ``superior'', that is, an input that drives its dynamics.
+Matched nodes can thus be controled by the node pointing to it.
+Unmatched nodes, on the other hand, have no superior in the network and must be directly controlled by external inputs \autocite{Liu2011}.
 In an ecological context, this is what we refer to as management interventions.
@@
 Systems that require a large number of external inputs are more difficult or costly to control.
-The \textit{manageability} of a community $m$ is therefore determined by the proportion $n_d$ of species on which we would need to apply management interventions in order to gain full control of the abundances of all species in the ecological community, $$m = 1- \frac{n_d}{s},$$ where $s$ is the total number of species in the community.
-
-\subsection*{Weighting links}
+Therefore, the manageability $m$ of a community can be approximated by the proportion of species on which we would need to apply management interventions in order to gain full control of the abundances of \textit{all} species in the ecological community, $$m = 1- \frac{n_d}{s},$$ where $n_d$ is the proportion of species needed to gain full control and $s$ is the total number of species in the community.
+
+\subsection*{Weighting \& directing links}
 
 Recall that our maximum matching algorithm requires a directed network in which a link between species $i$ and $j$ pointing to species $j$ indicates that the abundance of $j$ can be affected by the abundance of $i$.
-In ecological networks, establishing a directionality for the links between species is relatively straightforward when they represent resources or energy flow, however, interspecific effects---particularly in pollination networks---are not strictly directed.
+This implies that we need first to establish a directionality for the links between species that in consistent with the dynamics of the comunity.
+In some ecological networks, establishing a directionality is relatively straightforward when they represent resources or energy flow.
+Interspecific effects in pollination networks, however, are not strictly directed.
 Nevertheless, the extent to which a pair of interacting species affect each other can be quantified by the magnitude of the mutual dependence \autocite{Bascompte2006}.
-As the dependencies are bidirectional, this assumption renders a bipartite network in which interacting pairs are connected by two directed links (\autoref{fig:explain_cd}b).
+
+The dependency of plant $i$ on pollinator $j$, $d_{ij}$, is the proportion of the visits coming from pollinator $j$ compared to all pollinator visits to plant $i$.
+Likewise, the dependency of pollinator $j$ on plant $i$, $d_{ji}$, is the ratio of the visits by pollinator $j$ to plant $i$ and all visits of pollinator $j$.
+As the dependencies are bidirectional, adopting this assumption generates a weighted bipartite network in which interacting pairs are connected by two directed links (\autoref{fig:explain_cd}b).
+
+Mutual dependencies have been shown to be highly assymetric in natural communities \autocite{Bascompte2006}.
+In other words, if a plant species is largely dependent on a pollinator species, then the pollinator tends to depend only very weakly on the plant.
+This suggest that it may be possible to relax this initial assumption and simplify the network further such that interacting species are only connected by one directed link when mutual dependencies are assymetric (\autoref{fig:explain_cd}c).
+The extent to which a species $i$ affects species $j$ relative to the extent to which species $j$ affects species $i$ can then be summarised by the interaction asymmetry $$a(i,j) = \frac{\left | d_{ij}-d_{ji} \right |}{\textup{max}\left ( d_{ij}, d_{ji} \right )}$$
+
+Employing an unidrectional interaction asymmetry, as a surrogate of bidirectional mutual dependences, dramatically reduces the number of links in the network.
+Which damatically simplifies the computation of of all posible maximum matchings in a network.
 
@@
   dplyr::filter(Sequence == 12) %>%
-  dplyr::mutate(weight = c(0.75, 1, 0.5, 0.6, 1, 0.16))
+  dplyr::mutate(weight = c(0.75, 0.5, 0.5, 0.6, 0.5, 0.16))
 
@@
 @
-\caption{\label{fig:explain_cd} Mutualistic networks are usually described quantitatively by the relative number of visits between each plant and animal species (a).
-The mutual dependencies between interacting species (b) depend directly on the relative visitation frequency.
-The dependency of plant $i$ on pollinator $j$, $d_{ij}$, is the proportion of the visits coming from pollinator $j$ compared to all pollinator visits to plant $i$.
-Likewise, the dependency of pollinator $j$ on plant $i$, $d_{ji}$, is the ratio of the visits by pollinator $j$ to plant $i$ and all visits of pollinator $j$.
-Nevertheless, mutual dependencies in pollination networks tend to be highly assymetric.
-The relative differences of dependencies (c) then is a good indicator  }
+\caption{\label{fig:explain_cd} Different ways to depict quantitative mutualistic networks.
+a) Pollination networks are usually described by the number of visits between each plant and animal species.
+b) Given visitation data the mutual dependencies between interacting species depend directly on the relative visitation frequency.
+c) The relative differences of dependencies---the interaction asymmetry---then provides a mean to simplify the interspecific effects.}
 \end{figure}
 
-Nevertheless, mutual dependencies have been shown to be highly assymetric in natural communities \autocite{Bascompte2006}.
-In other words, if a plant species is largely dependent on a pollinator species, then the pollinator tends to depend only very weakly on the plant.
-This suggest that it may be possible to relax our initial assumption and simplify the network such that interacting species are connected by one directed link when mutual dependencies are highly assymetric (\autoref{fig:explain_cd}c).
-The extent to which a species $i$ affects species $j$ relative to the extent to which species $j$ affects species $i$ can then be summarised by the interaction asymmetry.
-
-$$a(i,j) = \frac{\left | d_{ij}-d_{ji} \right |}{\textup{max}\left ( d_{ij}, d_{ji} \right )}$$
-
 \subsection*{Relative importance}
-
-\todo[inline]{insert ecological motivation?}
 
@@
 Species vary in terms of the frequency with which they are classified as superior nodes (\autoref{fig:explain_mm}), and this frequency provides an indication of their relative importance in driving the state of the community.
-
-We therefore call \textit{driver species} those that are identified as being a superior node in all\todo{check}  possible matchings, and consequently likely to have a disproportionate effect on the abbundances of other species in the community.
-Unlike unweighted networks, where a maximum matching is defined by its matching size (the number of matching links), a maximum matching in a weighted network is one whose links have the largest possible total weight among all possible matchings.
+Ecologically, these distinctions are crucial because resources are limited and therefore ecological inteventions should be focused on species that might provide the largest impact.
+We therefore call \textit{driver species} those that are identified as being a superior node in all possible matchings, and consequently likely to have the most disproportionate effect on the abundances of other species in their community.
+
+As previously described, unlike unweighted networks, where a maximum matching is defined solely by its matching size, a maximum matching in a weighted network is one whose links have the largest possible total weight among all possible matchings.
 This means that in weighted networks there is a number of matchings that have maximal size, but are not maximum matchings because their total weight is not maximal.
-
-Consequently, we identified the driver species in each of the networks by computing all possible matchings in the network that have the same maximal size while allowing for some tolerance regarding the weight.
-We relax the matching weight requirement because empirical intreaction strengths, from which we calculate dependencies, are stochastic to some extent and depend on the sampling method and intensity.
-To compute all the matchings with maximal size, we first generated the network's line graph---an alternative representation in which nodes are the interactions of the original network and links represent common ending points.
-We then calculated the complement of the line graph---a graph in which nodes are adjacent if and only if they are not adjacent in the line graph.
-All possible maximum matchings can be found by enumerating all cliques of size $1-n_d$ in this complement graph \autocite{West2001, Csardi2006a}.
+One alternative to calculate the species importance, and identify the driver species, would be to consider only maximum matchings.
+However empirical intreaction strengths, from which we calculate dependencies, are to some extent stochastic and depend on the sampling method and intensity.
+We therefore relaxed the matching weight requirement computed all possible matchings in the network that have the same maximal size while allowing for some tolerance regarding the weight.
+To compute all the matchings with maximal size, we first generated the network's line graph---an alternative representation in which nodes are the links of the original network and links represent common ending points\todo{add ref}.
+We then calculated the complement of the line graph: a graph in which nodes are connected if and only if they are not connected in the line graph.
+All possible matchings of maximal size can be found by enumerating all cliques of size $1-n_d$ in this complement graph \autocite{West2001, Csardi2006a}.
 
@@
 In the last section we outlined the theoretical and computational underpinings of our approach.
-Now we illustrate its empirical application using ten pairs of plant-pollinator communities for which we calculated their manageability and the relative importance of species.
-Each network pair was composed by a community invaded by a plant and a community effectively free of the invasive species (Table S1).
+Now we illustrate its empirical application using ten pairs of plant-pollinator communities for which we explored their manageability and the relative importance of their constituent species.
 The networks were constructed from previously published visitation data collected from pollination communities in Bristol, UK \autocite{Lopezaraiza-Mikel2007} and in Cap de Creus National Park, Spain \autocite{Bartomeus2008}.
+Notably, each network pair was composed of a community invaded by a plant and a community ``free'' of the invasive species (Table S1).
 In the four British uninvaded communities, the non-invaded plots were obtained by experimentally removing all the flowers of the invasive species \textit{Impatients grandulifera}.
 In contrast, the Spanish uninvaded communities were obtained from plots that had not yet been colonised by either of the invasive species \textit{Carpobrotus affine acinaciformis} or \textit{Opuntia stricta}.
-The structure of these networks was determined using visitation frequency which has been shown to be an appropriate surrogate for inter-specific effects in pollination networks \autocite{Vazquez2005, Bascompte2006}.
-To examine the importance of this decision, we also evaluated the effect of using pollinator efficiency or importance as alternative measures of species interactions \autocite{NeEman2010, Ballantyne2015}, and we found consistent results for all of these options(see Supplementary Information).
+The structure of these networks was determined using visitation frequency which has been shown to be an appropriate surrogate for interspecific effects in pollination networks \autocite{Vazquez2005, Bascompte2006}.
+To examine whether this decision would influence our results, we also evaluated the effect of using pollinator efficiency or importance as alternative measures of species interactions \autocite{NeEman2010, Ballantyne2015}, and we found quantitatively results for all of these options(see Supplementary Information).
+
+All analysis were performed in R 3.2.2 \autocite{RCoreTeam2015}.
 
@@
 
-We started by quantifying the manageability of the analysed pollination communities.
+Given the different networks, we started by quantifying their manageability.
 To do that, we calculated the maximum matching of the corresponding pollination network, and estimated the minimum number of species that need directed intervecntions to fully control the species abbundances in the community.
-If a network had more than one component (two species are in different components if there exist no path between them) we analysed the largest one.
-Although understanding the distribution of manageability across ecological networks is an useful result in itself, we wanted to test wheter perturbations, like invasion status, have an impact on manageability values.
-As, naively one might expect to see a negative relationship between diversity and manageability \autocite{Menge1995}, we used a set of generalised linear models (with binomial error structure) to investigate the effect of invasion status while controling for \textit{(i)} the total number of species, \textit{(ii)} plant richness, \textit{(iii)} polinators richness, \textit{(iv)} the ratio of plants to pollinators richness, and \textit{(v)} the study site.
-Competing models were assessed by comparing the Akaike Information Criterion corrected for small sample sizes (AICc).
-
-Subsequently we explored the extent to which structural factors in the empirical networks influence their manageability.
-Previous studies found a direct link between a network's degree distribution and the number of nodes necessary to fully control it \autocite{Liu2011}, but this relationship has not been explored in weighted ecological networks.
-We therefore compared the manageability of the empirical networks to networks generated by three null models.
-One set of random visitation networks was generated by maintaining each species' degree (its number of interactions) while varying the number of visits per species.
-A second set of random networks mantained the species' strength (its total sum of visits) while varying their degrees.
+If a network had more than one component (two species are in different components if there exists no path between them), we only analysed the largest one.
+Although understanding the variability of manageability across ecological networks is an useful result itself, we also wanted to test whether perturbations, like invasion status, have an impact on manageability values.
+We therefore used a set of generalised linear models (with binomial error structure) to investigate the effect of invasion status while controling for factors related to species richness---as naively one might expect to see a negative relationship between diversity and manageability \autocite{Menge1995}.
+Coovariates inlcuded the total number of species, plant richness, polinators richness, the ratio of plants to pollinators richness, and the study site.
+We assessed competing models by comparing the Akaike Information Criterion corrected for small sample sizes (AICc).
+
+We next explored the extent to which structural properties of the empirical networks influence their manageability.
+Previous research indicates a direct link between a network's degree distribution and the number of nodes necessary to fully control it \autocite{Liu2011}, but the strength and applicability of this relationship has not been tested for in weighted ecological networks.
+We therefore compared the manageability of the empirical networks to networks generated by three null models which varied in terms of the constraints they impose.
+The first set of random visitation networks maintain the connectivity of the empirical network, but both degree and weight were allowed to vary.
+A second set set was generated by maintaining each species' degree (its number of interactions) while varying the number of visits per species.
+Finally a third set of random networks mantained the species' strength (its total sum of visits) while varying their degrees.
 Randomisations were generated using vegan 2.3-3 \autocite{Oksansen2016}.
-Finally a three set of fully random networks maintained only the connectivity of the empirical network, but both degree and weight were allowed to vary.
-We then calculated the mutual dependences and interaction asymmetries of the random networks and calculated their manageability using the maximum matching algorithm.
+After generating the randomized networks under these three schemes, we then calculated the mutual dependences and interaction asymmetries and determined their manageability using the maximum matching algorithm.
 Finally we calculated the p-value of the manageability of each empirical network and the corresponding manageability of 999 randomisations.
@@
 
-Our third question is related to how different species differ on their importance for the population dynamics of the community.
-To quantify this importance we computed all possible matchings that have the same size as the maximum matchings and in each network.
-We then calculated the frequency to which each species is deemed to be a superior node in matchings with a weight equal or larger to 0.5 times the weight of the maximum matchings.
-We choose this threshold as it provided a high agreement between the relative importance of species calculated by weighting interactions with the mutial dependencies or the depndence asymmetry as well as between the network is quantified by visitation or pollination efficiency.
-Nevertheless, the choice of the threshold only had a negligible impact on the results (Supplementary information).
-
-The number of maximal matchings increasses exponentially with the number of links and nodes in a network.
-When we use mutual dependecies, the large number of links in the most diverse communities renders the computation unfeasible.
-Taking this limitation into account we compared the relative network manageability obtained when using assimetries or when using mutual dependencies for eleven networks---for which the number of matchings was smaller than $4\times 10^{10}$.
-Results from a paired Spearman correlation test, the weighted correlation coefficient $r_{w2}$---which gives more weight to higer ranks \autocite{PintoDaCosta2015}, and the Jaccard similarity of the driver species in both approaches, suggested a high similarity in relative ranks.
-Therefore, we used the results from the assymetries, rather than mutiual dependences, to further investigate the factors that determine species' relative importance.
-
-We then asked the question of whether some species-level structural properties can predict the relative importance of species.
-Here, we used a Generalised Linear Mixed-Effects model to evaluate the effect on the species' relative importance of a suite of structural measures.
-We included measures of centrality (degree and eigen-centrality) which have been found to be strong predictors of importance in a coextintion context\todo{add ref}; measures related to network robustness (contribution to nestedness) as nestedness has been proposed as one of the key properties that promote stability in mutualistic networks \autocite{Saavedra2011}; and measures of strength of association and depedency (visitation and dependency strength) as their skewed distribution is characteristic of plant-pollinator networks and determine the extent of interspecific effects.
-All metrics were calculated using bipartite 2.06 \autocite{Dormann2008}.
-To allow for variation among different ecological communities, this factor was included as a random effect \autocite{Bates2015a}.
-Candidate models were compared using AIC and the relative importance of the explanatory variables was evaluated using the sum of Akaike weights over candidate models that accounted for 95\% of the evidence \autocite{Burnham2003, Bates2014, Barton2016}.
-
-Invasive species have been shown to have disproportionate effects on the communities they invade.
-So we examined the extent to which invasive species tend to be driver species---species whith the maximum importance.
-As our invasive species were plants, we compared the relative importance of invasive species to those of other plants in the community and to which degree they differ when accounting for the structural factors that determine their importance\todo{needs to be developed once the results section is rewritten}.
-
-All analysis were performed in R 3.2.2 \autocite{RCoreTeam2015}.
+Our second key question is related to how different species differ in their importance for the population dynamics of the community.
+To quantify this importance in each network, we computed all possible matchings that have the same size as the networks' maximum matching.
+We then calculated the frequency to which each species is deemed to be a superior node in matchings with a weight greater or equal to 0.5 times the weight of the maximum matching.
+We choosed this threshold as it provided a high agreement between networks quantified by visitation and pollination efficiency as well as between our weighting/directionality assumptions (mutual dependences and inetraction asymmetries).
+Note that the choice of this threshold had a negligible impact on the results (Supplementary information).
+
+We observed that the number of maximal matchings increasses exponentially with the number of links and nodes in a network.
+Unfortunately, this implies that the large number of links in the most diverse communities renders the computation unfeasible when we use mutual dependecies.
+Taking this limitation into account, we compared the relative network manageability obtained when using assimetries or when using mutual dependencies for eleven of the twenty networks---for which the number of matchings was smaller than $4\times 10^{10}$.
+The comparison was performed using paired Spearman correlation test, a weighted correlation coefficient $r_{w2}$---which gives more weight to higer ranks \autocite{PintoDaCosta2015}, and a Jaccard similarity of the driver species in both approaches.
+All three approaches suggested a high similarity in relative ranks.
+Therefore, we used the results from the assymetries, rather than mutual dependences, to further investigate the factors that determine species' relative importance.
+
+Given the species frequency obtained using the interaction asymmetries, we then asked the question of whether some species-level structural properties can predict the relative importance of species.
+To do so, we used a generalised linear mixed-effects model (GLMM) to evaluate the relationship between the species' relative importance and a suite of structural measures.
+We specifically included measures of centrality (degree and eigen-centrality) which have been found to be strong predictors of importance in a coextintion context\todo{add ref}; measures related to network robustness (contribution to nestedness) as nestedness has been proposed as one of the key properties that promote stability in mutualistic networks \autocite{Saavedra2011}; and measures of strength of association and depedence (visitation and dependency strength), as their skewed distribution is characteristic of plant-pollinator networks and determine the extent of interspecific effects.
+All metrics were calculated using the R package bipartite 2.06 \autocite{Dormann2008}.
+We allowed for variation among different communities by including the network identity as a random effect \autocite{Bates2015a}.
+Candidate models were compared using AICc and the relative importance of the explanatory variables was evaluated using the sum of Akaike weights over candidate models that accounted for 95\% of the evidence \autocite{Burnham2003, Bates2014, Barton2016}.
+
+Invasive species have been shown to have disproportionate effects on the communities they invade\todo{add ref}.
+So we lastly examined the extent to which invasive species tend to be driver species---species whith the maximum importance---and to which extent their importance could be explained by the factors previously described.
+To do so, as our invasive species were plants, we first used a Mann-Withney U test to compare the relative importance of invasive species to those of other plants in the community.
+We then examined the residuals of the GLMM to investigate if invasive species' importance is larger or smaller than expected given their network structural properies.
 

### 2016-05-06 paper/manuscript.Rnw
update agradecimientos

@@
 Takeuki Uno for the insight provided to find the set of all maximum matching algorithms, and Bernat Bramon, Matthew Hutchinson and Marilia Gaiarsa for feedback in early stages of the project.
-EFC acknowledges the support from the University of Canterbury Doctoral Scholarship, the University of Canterbury Meadow Mushroooms Postgraduate Scholarship, a travel grant from the European Space Agency and a Rutherford Discovery Fellowship (to DBS).
+EFC acknowledges the support from the University of Canterbury Doctoral Scholarship, the University of Canterbury Meadow Mushroooms Postgraduate Scholarship, a New Zealand International Doctoral Research Scholarship, and a travel grant from the European Space Agency.
 DBS ackloledges the support of a Rutherford Discovery Fellowship, administered by the Royal Society of New Zealand.

### 2016-05-11 paper/manuscript.Rnw
get discussion done

@@
   \title{
-  {\LARGE \textsc{Structural controlability of pollination networks}}}
+  {\LARGE \textsc{Biotic invasions reduce the manageability of mutualistic networks}}}
 
@@
 
-\textsc{Structural controlability of ecological networks}
-
 \textsc{Network manageability in the context of species invasion}
-
-\textsc{Biotic invasions reduce manageability of ecological networks}
-
-\textsc{Identifying the ``driver species'' of an ecosystem}
 
@@
 
-Seminal work on control theory has established a strong link between the structure of complex networks and its controlability and that in principle it is possible to alter any ecological community's composition, by modifying the abundances of just some key species \autocite{Liu2011, Cornelius2013}.
+In contrast with other types of complex systems like neural, intra-organizational, or trust neworks, ecological networks do not have a hierarchical or distributed structure but rather tend to be closed systems in which resources recirculate\todo{add ref}.
+As such, ecosystems contain multiple feedbacks that allow them to self-regulate and, therefore, function relatively independent from external stimulation\todo{add ref}.
+
+Research stemming from control theory has established a strong link between the structure of complex networks and their controlability and that, in principle it is possible to alter a ecological community's composition by modifying the abundances of only a few species \autocite{Liu2011, Cornelius2013}.
 Based on this work and using a small number of binary food-webs (only presence or absence of interactions), it has been suggested that the degree distribution of ecological networks makes them inherently difficult to control \autocite{Liu2011, Ruths2014}.
 This theoretical result is in agreement with many cases in which the management of ecological communities is more challenging than aticipated.
-In contrast with other types of complex systems like neural, intra-organizational, or trust neworks, ecological networks do not have a hierarchical or distributed structuretend but rather tend to be closed systems in which resources recirculate.
-As such, ecosystems contain multiple feedbacks that allow them to self-regulate and, therefore, function relatively independent from external stimulation\todo{add ref}.
 Although these conceptual advances on control theory have provided an initial link between the structure of ecological communities and our ability to manage them, this relationship is still ambiguous.
@@
 In addition, in the ten communities that were invaded, invasive species were invariably classified as a driver species.
-In general, the relative importance of invasive species was significantly larger than those of the other plants in the studied communities(Mann-Whitney U Test, $p =  \Sexpr{fix_small_pvalue(inv_test$p.value)}$).
+In general, the relative importance of invasive species was significantly larger than those of the other plants in the studied communities (Mann-Whitney U Test, $p =  \Sexpr{fix_small_pvalue(inv_test$p.value)}$).
 However this difference can be fully explained by the explanatory variables in our model as all the residuals for the invasive species were virtually zero.
@@
 
+<<interact with invasive , echo = FALSE, warning = F, message = F, results = "asis">>=
+
+dd_inv <- dd %>%
+  dplyr::filter(net_name %in% invasive_sp$net_name) %>%
+  plyr::ddply("net_name", function(x){
+    inv <- invasive_sp$species[invasive_sp$net_name == x$net_name[1]]
+    if(length(inv) == 0){
+      x %>% 
+      dplyr::mutate(int_inv = "none")
+    } else{
+      interacting <- igraph::adjacent_vertices(net[[x$net_name[1]]], inv)[[1]] %>% names
+      x %>% 
+        dplyr::mutate(int_inv = species %in% interacting)
+    }
+  })
+
+# dd_inv %>%
+#   # dplyr::group_by(net_name, int_inv) %>%
+#   # dplyr::summarise(int_inv_d_reim_mean = mean(d_reim)) %>%
+#     ggplot(aes(x = int_inv, y = d_reim)) +
+#   geom_boxplot()
+
+dd_inv_t <- dd_inv %>%
+  dplyr::group_by(net_name, int_inv) %>%
+  dplyr::summarise(int_inv_d_reim_mean = mean(d_reim)) %>%
+  tidyr::spread(int_inv, int_inv_d_reim_mean)
+
+dd_inv_test <- wilcox.test(dd_inv_t[, 3][[1]], dd_inv_t[, 2][[1]], paired = F)
+
+@
+
+No significant difference on importance between pollinators interacting with invasive species or not.
+
 \section*{Discussion}
 
-We found that
-
-Therefore, full controlability of ecological networks---being able to steer the ecosystem into any desired ecosystem state---would require a  This characteristics render ecological networks unlikely to be able to visist every possible system state   other closed systems, ecological networks
-
-The controllability of ecological networks is not a concept limited to control theory.
-Controllability in the ecological context can be seen as a direct meassure of the mimimum number of species whose abbundance would need to be directly regulated to achieve full network control.
-While we are far away from
+Our results reveal that invasive mutualists are driver species in the communities they invade.
+As driver species, they occupy a dominant role in which changes on their abbundance have the potential to cascade trough the community and in turn affect the abbundances of several other species in the community.
+They achieve that by alterning the distribution of the strength of mutual dependencies and the interaction asymmetries---which constitute the foundations of the structure of mutualistic networks \autocite{Vazquez2004, Bascompte2006}.
+Furthermore, these structural differences caused by invasive species at a community level are reflected in a potential decrease in our ability to alter the state of the community.
+
+We confirm previous studies that suggested that in contrast with other kind of complex networks, the structure of ecological networks renders them remarkably difficult to control \autocite{Liu2011, Ruths2014}.
+In a hypothetical situation in which the goal were to regulate the abbundances of all species in a pollination community, our results suggest that we would need to directly intervene the abbundances of at least 40-90\% of those species.
+Fully controling an ecological community is out of the question, as designing and implementating the management interventions needed is currently impractical.
+Nevertheless, the ``manageability'' of an ecological community, which is related to the number of species that would require a directed intervention, can provide a simple, straightforward, and theoretically-informed indication of the degree to which the community is self-regulated and therefore how difficult it might be to modify its state.
+
+Asymmertic depedences have previously found to be related to the stability and persistence of pollination networks \autocite{Memmott2004, Vazquez2004, Lever2014, Astegiano2015}.
+Here, we demonstrate that the manageability of mutualistic networks is also governed by the asymetric nature of mutual dependeces.
+Indeed, our empirical networks have markedly lower levels of manageability compared to randomisations in which the visitation network was unchanged, but the patterns of dependence were broken by randomising the direction of the asymmetries.
+However, consistent with previous results \autocite{Liu2011}, we show that the manageability of empirical networks was indistinguishable from that of networks with a random structure (in terms of modularity and nestedness for example) but that maintained the degree or strength of each species in the community.
+This suggest that the asymmetries at the species (specialization-generalization asymmetries) and the link level (interaction's dependence asymmetries) appear to be sufficiently defined by the distribution of species degree and strength \autocite{Melian2002}.
+Furthermore, we found that invasive species, by altering the patterns of assymetry, reduce the manageability of their communities.
+This result is in agreement with previous studies that suggest that invasors erode native pollination webs by ursurpating interactions and exarcerbate the asymmerties in the network, which in turn might increasse the stability of the community \autocite{Aizen2008, Bartomeus2008}.
+
+The changes on the asymmetries found in the invaded networks are not only reflected in the manageability at a community level: invaders were found to be driver species in every single community in which they were present.
+Invasive plants have usually been found to be super-generalists thus playing a central role in their networks \autocite{Vila2009, Palacio2016}.
+Nevertheless, we found that dependence strength, rather than generalism or other metrics of centrality, explains best the importance of species for the community dynamics.
+Specifically, driver species tend to be those whose interaction partners are collectively more dependent on them than the other way arround.
+However, the influence of dependence strength was held regardless of wheter the species was invasive or not, which corroborates previous observations that suggest that exotic species, although having different traits\todo{add cite}, are not inherently different to their native counterparts, but are rather governed by the same rules of niche and competition that determine species coexistence \autocite{Stouffer2014}.
+Invasive species have been shown to have the ability to transform the structure of ecological communities \autocite{Aizen2008, Albrecht2014}, our results suggest that they also may have the ability to heavily influence the abbundances of other species in the ecosystem.
+
+Because of their effects on other species in the community, driver species might be natural candidates for management interventions.
+For instance, despite inconsistent outcomes, our results suggest that current restoration approaches that focus on direct eradication of invasive species might indeed be an effective way to modify ecosystem state.
+Nevertheless, our results also indicate that removals must be executed with caution as invaded commmunities tend to be dependent on them and therefore vulnerable to their erradication \autocite{Traveset2013, Albrecht2014}.
+Although useful for identifying conservation priorities, our approach is different to previous attempts to quantify species importance that concentrate on measures of centrality, position, coextintion or uniqueness \autocite{Jordan2006,Jordan2009, Lai2012, McDonald-Madden2016}.
+Instead the concept of driver species is more akin to the original concept of keystone species, which illustrated how changes on the abbundance of a key species in turn affect the abbundances of other members of the community \autocite{Paine1969, Paine1995}.
+However, while the keystone species were traditionally identified by infering the effects of a perturbation on a community's population dynamics \autocite{Mills1993}, the driver species concept operates the other way round, and uses the communuty dynamics, underpinned by the interspecific effects, to infer the effects of a perturbation.
+While it is challenging to quantify the dependence of species in an ecological community, an experimental approach to identofy dynamically important species might be even more difficult\todo{add cite}.
+
+Here we ilustrate how a control theoretic approach can be used to study the effect on mutualistic communities of a major driver of global change, however it can be easily extended to understand the structural effects of other kind of preturbations and species interactions.
+Moreover, we see great potential by explicitly integrating control theory with dynamics models of species densities \autocite{Cornelius2013, Gibson2016}.
+From an ecological perspective, it can provide key insight on determining the relationship between controlability and species coexistence, as well as determining the trade-offs between persistence at the species and the community level.
+From a conservation perspective, a combined approach can be useful, not only to idetify ideal targets for management interventions, but also to design informed, rather than hopeful, interventions that achieve restoration goals.
 
@@
 The authors thank Dr.
-Takeuki Uno for the insight provided to find the set of all maximum matching algorithms, and Bernat Bramon, Matthew Hutchinson and Marilia Gaiarsa for feedback in early stages of the project.
+Takeuki Uno for the insight provided to find the set of all maximum matching algorithms, and Jason Tylianakis, Bernat Bramon, Matthew Hutchinson, and Marilia Gaiarsa for feedback in early stages of the project.
 EFC acknowledges the support from the University of Canterbury Doctoral Scholarship, the University of Canterbury Meadow Mushroooms Postgraduate Scholarship, a New Zealand International Doctoral Research Scholarship, and a travel grant from the European Space Agency.
-DBS ackloledges the support of a Rutherford Discovery Fellowship, administered by the Royal Society of New Zealand.
+DBS ackloledges the support of a Marsden Fast-Start grant and a Rutherford Discovery Fellowship, administered by the Royal Society of New Zealand.
 

### 2016-05-11 paper/manuscript.Rnw
start working on the introduction

@@
 We would like to control communities in the sense of conserving and restoring them.
+
 However to control them (in that sense) we need to understand how species affect each other and potentially the whole system when they are faced by perturbations or management interventions.
-But we cannot do that yet because we lack a theoretical framework that link the dynamics of the community to management.
+
+But we cannot do that yet because we lack a theoretical framework that link the dynamics of the community to management. Control theory might provide this link.
+
+ This idea hasboth helped and hindered the search for solutions to many problems facing said communities today.
+On the positive side, for example, it has led to the development of a rich suite of analytical and simulation tools with which to blah blah, even though ecology has not historically been a highly quantitative field.
+On the negative side, this complexity is often thought to be so rampant that attempts to explain, predict, or manage community dynamics will always fall short of the mark.
+Blah, blah, blah....
+
+Complex systems, like ecological communities, are characterised by non-linear relationships in which the whole is greater than the sum of its parts \todo{add refs}.
+This complex systems approach has helped the search for solutions to problems that these communinities face at the same time it has led to the development of a rich suite of analytical and simulation tools with which to understand the role of species when embedded in an intricate network of interactions\todo{add refs}.
+However, in contrast with other types of complex systems like neural, intra-organizational, or trust neworks, ecological networks do not have a hierarchical or distributed structure but rather tend to be closed systems in which resources recirculate\todo{add ref}.
+As such, ecosystems contain multiple feedbacks that allow them to self-regulate and, therefore, function relatively independent from external stimulation\todo{add ref}.
+This property has hindered our ability to effectively explain, predict, or manage the dynamics of ecological communities, particularly when they are faced by perturbations.
+In part this is because...
+we lack a theoretical framework that link the dynamics of the community to management.
 Control theory might provide this link.
 
-In contrast with other types of complex systems like neural, intra-organizational, or trust neworks, ecological networks do not have a hierarchical or distributed structure but rather tend to be closed systems in which resources recirculate\todo{add ref}.
-As such, ecosystems contain multiple feedbacks that allow them to self-regulate and, therefore, function relatively independent from external stimulation\todo{add ref}.
-
-Research stemming from control theory has established a strong link between the structure of complex networks and their controlability and that, in principle it is possible to alter a ecological community's composition by modifying the abundances of only a few species \autocite{Liu2011, Cornelius2013}.
-Based on this work and using a small number of binary food-webs (only presence or absence of interactions), it has been suggested that the degree distribution of ecological networks makes them inherently difficult to control \autocite{Liu2011, Ruths2014}.
+because we are still not able to explain, predict how species affect each other and potentially the whole system when they are faced by perturbations.
+
+Research stemming from control theory has established a strong link between the structure of complex networks and their controlability, and that, in principle, it is possible to alter a ecological community's composition by modifying the abundances of only a few species \autocite{Liu2011, Cornelius2013}.
+Based on this work, it has been suggested that the degree distribution of ecological networks makes them inherently difficult to control \autocite{Liu2011, Ruths2014}.
 This theoretical result is in agreement with many cases in which the management of ecological communities is more challenging than aticipated.
+
 Although these conceptual advances on control theory have provided an initial link between the structure of ecological communities and our ability to manage them, this relationship is still ambiguous.

### 2016-05-12 paper/manuscript.Rnw
edit introduction

--- 2016-05-11 paper/manuscript.Rnw
@@
 
-Alternative titles:
+Alternative title:
 
@@
 
-\textit{Tentative spiel for the first paragraph:} We need to manage ecological communities because of ecosystem services and biodiversity maintenance.
-We would like to control communities in the sense of conserving and restoring them.
-However to control them (in that sense) we need to understand how species affect each other and potentially the whole system when they are faced by perturbations or management interventions.
-But we cannot do that yet because we lack a theoretical framework that link the dynamics of the community to management.
-Control theory might provide this link.
-
-In contrast with other types of complex systems like neural, intra-organizational, or trust neworks, ecological networks do not have a hierarchical or distributed structure but rather tend to be closed systems in which resources recirculate\todo{add ref}.
+Complex systems, such as ecological communities, are characterised by non-linear relationships in which the whole is greater than the sum of its parts \todo{add refs}.
+This complex systems approach has led to the development of a rich suite of analytical and simulation tools with which to understand the role of species when embedded in an intricate network of interactions\todo{add refs}.
+However, in contrast to other types of complex systems like neural, intra-organizational, or trust neworks, ecological networks do not have a hierarchical or distributed structure but rather tend to be closed systems in which resources recirculate\todo{add ref}.
 As such, ecosystems contain multiple feedbacks that allow them to self-regulate and, therefore, function relatively independent from external stimulation\todo{add ref}.
-
-Research stemming from control theory has established a strong link between the structure of complex networks and their controlability and that, in principle it is possible to alter a ecological community's composition by modifying the abundances of only a few species \autocite{Liu2011, Cornelius2013}.
-Based on this work and using a small number of binary food-webs (only presence or absence of interactions), it has been suggested that the degree distribution of ecological networks makes them inherently difficult to control \autocite{Liu2011, Ruths2014}.
-This theoretical result is in agreement with many cases in which the management of ecological communities is more challenging than aticipated.
-Although these conceptual advances on control theory have provided an initial link between the structure of ecological communities and our ability to manage them, this relationship is still ambiguous.
-Ultimately, the challenge of ecological networks is represented by the variablity of their structure and interaction strengths---which can vary by several orders of mangitude\todo{add ref}.
-
-For instance, biotic invasions, as other major drivers of global change, can induce dramatic changes on the patterns of interactions that determine the structure of ecological networks \autocite{Baxter2004, Tylianakis2008, Ehrenfeld2010a}.
+This complex propertes have hindered, or at least complicated, our ability to find management solutions to the many problems ecological communities face.
+A framework that allow us to explain, predict, and manage ecological communities, particularly when they are faced with perturbations, needs to be able to account for their complex structure, and the dynamics that determine the state of each species---and the community as a whole.
+Control theory might be a good candidate framework as it is designed to deal with determining and supervising the behavior of a dynamical system and is well equiped to deal with the many feedbacks presents in ecological communities\todo{add ref}.
+
+Research stemming from control theory has established a strong link between the structure of complex networks and their controlability, and that, in principle, it is possible to alter a ecological community's composition by modifying the abundances of only a few species \autocite{Liu2011, Cornelius2013}.
+Based on this work, it has been suggested that the degree distribution of ecological networks makes them inherently difficult to control \autocite{Liu2011, Ruths2014}.
+This theoretical result is in agreement with many examples in which the management and restoration of ecological communities is more challenging than aticipated.
+For instance, biotic invasions, as a major drivers of global change, can induce dramatic changes on the patterns of interactions that determine the structure of ecological networks \autocite{Baxter2004, Tylianakis2008, Ehrenfeld2010a}.
+The difficulties of returning invaded communities to a predisturbance state can be evidenced by the limited amount of success of restoration projects \autocite{Suding2004, Rodewald2015, Smith2016}.
+Although it is a double challenge, understanding how differences in network structure before and after the invasion impact our ability to manage them is a first step towards an informed recovery.
+
+A control theoretical approach not only might provide insight to conservation but also for ecological science: by explicitly taking into account the extent to which changes in the abbundances of one species may ripple trough the community, applying control theory to ecological networks can provide an indication of which species are important from a dynamic perspective, and therefore crucial when attempting to alter (or maintain) the ecosystem state.
+Nevertheless, although it has been prevoiously used to highlight the disproportionate influence that humans have on marine food-webs \autocite{Isbell2013}, control theory has has rarely been aplied in an ecological context.
+One reason might be that the control of complex networks is still a young field and the tools necessary to account for variation on the strength of interspecific effects, which are characteristic of ecological networks, are not there.
+
+Here, we expand previous theory of the control of complex systems and use a set of ten paired invaded and uninvaded plant-pollinator communities to investigate the link between network structure and our ability to manage them.
+We focus on biotic invasions because they can produce tractable changes in the structure of ecological networks.
 These changes can be particularly pronounced in mutualistic networks of plants and pollinators where biotic invasions have been shown to modify the strength of species interactions and the degree of network nestedness and connectivity \autocite{Olesen2002, Aizen2008, Bartomeus2008, Vila2009, Traveset2013}.
-Moreover, as evidenced by the limited amount of success of restoration projects \autocite{Smith2016}, returning invaded communities to a predisturbance state is quite a difficult endeavour \autocite{Suding2004, Rodewald2015}.
-Understanding how invasion-induced differences in network structure impact our ability to manage them, can provide useful lessons to conservation science.
-What is more, there are also ecological insights to be had: by explicitly taking into account the extent to which changes in the abbundances of one species may ripple trough the community, applying control theory to ecological networks can provide an indication of which species are important from a dynamic perspective, and therefore crucial when attempting to alter (or maintain) the ecosystem state.
-
-\textcite{Isbell2013} used a control theoretic approach to find the minimum subset of species neccessary to maintain network structure in six marine food webs.
-They found that humans affect a larger proportion of this subset of species than, for instance, apex predators.
-They argue that this disproportionate influence could translate into unintentional restructuring of food webs.
-Although insightful, the scope and applicability of \textcite{Isbell2013} can be extended in numerous ways.
-First, although they find the size of this minimum set, they disregard the fact that the set species composition is not unique and thus not all species that might be included are equally important for the community population dynamics.
-Second, their methods were naive to differences on the strength of interspecific effects.
-And third, their approach was conceptually limited to trophic interactions\todo{is this too harsh?}.
-
-Here, we expand previous theory of the control of complex systems and use a set of paired invaded and uninvaded plant-pollinator communities to investigate the link between network structure and our ability to manage them.
-Plant-pollinator networks provide an ideal framework to answer these questions.
+In addition plant-pollinator networks provide an ideal framework to answer these questions.
 On one hand, community networks that quantify relative levels of interaction are readily available.
 On the other, the bipartite nature of pollination networks makes it is possible to simplify assumptions of how these interactions translate into interspecific effects.
-Our theoretical extension of network control, allow us to ask the question of whether biotic invasions as drivers of change in network structure increasses or decreasses the manageability of communities as well as the relative importance of species at driving the population dynamics of other species in the community.
-\todo{punchy line to finish here?}.
+Specifically we ask two key questions framed in the context of a plant invasion.
+First, we quantify the manageability of pollination communities.
+Second, we ask whether some species are more important than others at driving the population dynamics of the community and which factors determine this importance.
+
+\iffalse
 
@@
 
+\fi
+
 \section*{Discussion}

### 2016-05-12 paper/manuscript.Rnw
updating methods (still needs details regarding importance model)

@@
 
-\iffalse
-
 \section*{Theory of community manageability}
@@
 The number of nodes necessary to fully control a complex network can be calculated by counting the number of unmatched nodes in the network's maximum matching \autocite{Liu2011}.
-In a directed network, a given matching is a subset of links in which no two links share a common starting node or a common ending node; a node is matched if it is the ending node of one of the links in the matching (\autoref{fig:explain_mm}a).
-A matching is then maximum if bith \textit{(i)} the number of matched links---known as matching size---is maximal and \textit{(ii)} the sum of the weights of the matched links---known as matching weight---is the largest possible among all possible matchings of that size \autocite{West2001}.
-To find the maximum matching, we used an alternative bipartite representation of the network in which the two levels indicate the outgoing and incoming links to each node (\autoref{fig:explain_mm}b).
+In a directed network, a given matching is a subset of links in which no two links share a common starting node or a common ending node; a node is then matched if it is the ending node of one of the links in the matching and unmatched otherwise(\autoref{fig:explain_mm}a).
+A given matching is then maximum if both \textit{(i)} the number of matched links---known as matching size---is maximal and \textit{(ii)} the sum of the weights of the matched links---known as matching weight---is the largest possible among all possible matchings of that size \autocite{West2001}.
+To find the maximum matching, we it is useful to adopt an alternative bipartite representation of the network in which the two levels indicate the outgoing and incoming links to each node (\autoref{fig:explain_mm}b).
 Finding a matching in this alternative representation is equivalent to finding a set of links such that each node on the top level is matched to at most one node on the bottom level, and vice versa \autocite{West2001, Csardi2006a}.
@@
 a) We start with a directed network  in which the direction of the link represent the direction of control.
-This is, a link from $a_1$ to $p_1$ indicates that the state of $p_1$ (density/abbundances in an ecological context) are influenced by the state of $a_1$.
-b) To facilitate the computation of the maximum matching, we used an alternative undirected bipartite representation of the directed network in which each node in (a) is represented by two nodes that indicate the outgoing and incoming links.
-One of the possible maximum matchings of a network (dark grey links) defines a set matched ($p_1$, $p_2$, and $a_3$) and unmatched nodes ($a_1$ and $a_2$).
-The minimum number of species neccessary to control this network equates to the number of unmatched nodes $n_d = 2$.
-Superior nodes (dark grey circles) drive the dynamics of other species and are therefore important for the controlability of the network because they either require external input or because the are part of the chain that transmit the external imputs to other species.}
+This is, a link from $a_1$ to $p_1$ indicates that the state of $p_1$ (density/abundances in an ecological context) are influenced by the state of $a_1$.
+b) To facilitate the computation of the maximum matching, we can use an alternative representation of the directed network in which each node in (a) is represented by two nodes that indicate their outgoing and incoming links.
+In both (a) and (b) we show one of the possible maximum matchings of a network (dark grey links) that defines a set of matched ($p_1$, $p_2$, and $a_3$), unmatched ($a_1$ and $a_2$) and superior nodes ($a_1$, $a_2$, and $p_1$; dark grey circles).
+The minimum number of species neccessary to control this network equates to the number of unmatched nodes $n_d = 2$, which gives a manageability of $m = 0.8$.}
 \end{figure}
 
-Given a maximum matching, the link to network controllability has a relatively straightforward and intuitive basis.
+Given a maximum matching, the link to network controllability has an intuitive basis.
 In control theory, a network is fully controlable when each node has a ``superior'', that is, an input that drives its dynamics.
-Matched nodes can thus be controled by the node pointing to it.
+Consequently, each matched nodes can be controled by the node pointing to it.
 Unmatched nodes, on the other hand, have no superior in the network and must be directly controlled by external inputs \autocite{Liu2011}.
 In an ecological context, this is what we refer to as management interventions.
-
-Systems that require a large number of external inputs are more difficult or costly to control.
-Therefore, the manageability $m$ of a community can be approximated by the proportion of species on which we would need to apply management interventions in order to gain full control of the abundances of \textit{all} species in the ecological community, $$m = 1- \frac{n_d}{s},$$ where $n_d$ is the proportion of species needed to gain full control and $s$ is the total number of species in the community.
+Building on this, systems that require a large number of external inputs are more difficult or costly to control.
+Therefore, the manageability $m$ of a community can be approximated by the proportion of species on which we would need to apply management interventions in order to gain full control of the abundances of \textit{all} species in the ecological community $$m = 1- \frac{n_d}{s},$$ where $m$ ranges between zero and one, $n_d$ is the number of species needed to gain full control and $s$ is the total number of species in the community.
+
+\subsection*{Relative importance}
+
+The manageability of a community $m$ provides an indication of the magnitude of $n_d$ but not the identity of the species that compose this set.
+This is rather important since maximum matchings are often not unique in for a given network and different sets of species of size $n_d$ could potentially be used to control the network \autocite{Liu2011}.
+Species vary in terms of the frequency with which they are classified as superior nodes (\autoref{fig:explain_mm}), and this frequency provides an indication of their relative importance in driving the state of the community.
+Ecologically, these distinctions are crucial because resources are limited and therefore ecological inteventions should be focused on species that might provide the largest impact.
+As superior nodes \autoref{fig:explain_mm} drive the dynamics of other species and are therefore important for the controlability of the network because they either require external input or because the are part of the chain that transmit the external imputs to other species, we therefore call \textit{driver species} those that are identified as being a superior node in all possible matchings, and hence those most likely to have a disproportionate effect on the abundances of other species in their community.
+
+As previously described, a maximum matching in a weighted network is one whose links have the largest possible total weight among all possible matchings.
+One way to calculate the species importance, and identify the driver species, would be to consider only maximum matchings.
+However empirical intraction strengths are to some extent stochastic and depend on proximate factors such as sampling method and intensity \autocite{Rezende2007}.
+This means that in weighted networks there is a number of matchings that have maximal size, but are not maximum matchings because their total weight is not maximal.
+We therefore relaxed the matching weight requirement and computed all possible matchings in the network that have the same maximal size while allowing for some tolerance regarding the weight.
+To compute all the matchings with maximal size, we first generated the network's line graph---another representation in which nodes are the links of the original network and links represent common ending points\todo{West2001}.
+We then calculated the complement of the line graph: a graph in which nodes are connected if and only if they are not connected in the line graph.
+All possible matchings of maximal size can be found by enumerating all cliques (subgraphs in which every node is linked to every other) of maximum size, which equates to $1-n_d$m in this complement graph \autocite{Csardi2006a, Gutin2013}.
+
+\section*{Methods}
+
+In the last section, we outlined the theoretical and computational underpinings of our approach.
+Now we illustrate its empirical application using ten pairs of plant-pollinator communities for which we explored their manageability and the relative importance of their constituent species.
+The networks were constructed from previously published visitation data collected from pollination communities in Bristol, UK \autocite{Lopezaraiza-Mikel2007} and in Cap de Creus National Park, Spain \autocite{Bartomeus2008}.
+Notably, each network pair was composed of a community invaded by a plant and a community ``free'' of the invasive species (Table S1).
+In the four British uninvaded communities, the non-invaded plots were obtained by experimentally removing all the flowers of the invasive species \textit{Impatients grandulifera}.
+In contrast, the Spanish uninvaded communities were obtained from plots that had not yet been colonised by either of the invasive species \textit{Carpobrotus affine acinaciformis} or \textit{Opuntia stricta}.
+The structure of these networks was determined using visitation frequency which has been shown to be an appropriate surrogate for interspecific effects in pollination networks \autocite{Vazquez2005, Bascompte2006}.
+To examine whether this decision would influence our results, we also evaluated the effect of using pollinator efficiency or importance as alternative measures of species interactions in a different dataset \autocite{NeEman2010, Ballantyne2015}, and we found quantitatively results for all of these options (see Supplementary Information).
 
@@
 
-Recall that our maximum matching algorithm requires a directed network in which a link between species $i$ and $j$ pointing to species $j$ indicates that the abundance of $j$ can be affected by the abundance of $i$.
-This implies that we need first to establish a directionality for the links between species that in consistent with the dynamics of the comunity.
-In some ecological networks, establishing a directionality is relatively straightforward when they represent resources or energy flow.
-Interspecific effects in pollination networks, however, are not strictly directed.
-Nevertheless, the extent to which a pair of interacting species affect each other can be quantified by the magnitude of the mutual dependence \autocite{Bascompte2006}.
-
+Recall that the aforementioned maximum matching algorithm requires a directed network in which a link between species $i$ and $j$ pointing to species $j$ indicates that the abundance of $j$ can be affected by the abundance of $i$.
+This implies that we need first to identify a directionality for the links between species that in consistent with the dynamics of the comunity.
+In some ecological networks, establishing a directionality is relatively straightforward, for example when links represent biomass transfer or energy flow.
+Interspecific effects in pollination networks, however, are not strictly directed since the benefit is mutual between interacting species.
+Nevertheless, the relative extent to which a given pair of interacting species affect each other can be quantified by the magnitude of the mutual dependence \autocite{Bascompte2006}.
 The dependency of plant $i$ on pollinator $j$, $d_{ij}$, is the proportion of the visits coming from pollinator $j$ compared to all pollinator visits to plant $i$.
@@
 
-Mutual dependencies have been shown to be highly assymetric in natural communities \autocite{Bascompte2006}.
-In other words, if a plant species is largely dependent on a pollinator species, then the pollinator tends to depend only very weakly on the plant.
-This suggest that it may be possible to relax this initial assumption and simplify the network further such that interacting species are only connected by one directed link when mutual dependencies are assymetric (\autoref{fig:explain_cd}c).
-The extent to which a species $i$ affects species $j$ relative to the extent to which species $j$ affects species $i$ can then be summarised by the interaction asymmetry $$a(i,j) = \frac{\left | d_{ij}-d_{ji} \right |}{\textup{max}\left ( d_{ij}, d_{ji} \right )}$$
-
-Employing an unidrectional interaction asymmetry, as a surrogate of bidirectional mutual dependences, dramatically reduces the number of links in the network.
-Which damatically simplifies the computation of of all posible maximum matchings in a network.
+Mutual dependencies have been shown to be highly assymetric in natural communities \autocite{Bascompte2006}; in other words, if a plant species is largely dependent on a pollinator species, then that pollinator tends to depend rather weakly on the plant.
+This suggests that it may be possible to relax the assumption of bidirectional dependences and simplify the network further such that interacting species are only connected by one directed link when mutual dependencies are assymetric (\autoref{fig:explain_cd}c).
+The extent to which a species $i$ affects species $j$ relative to the extent to which species $j$ affects species $i$ can be summarised by the interaction asymmetry given by $$a(i,j) = \frac{\left | d_{ij}-d_{ji} \right |}{\textup{max}\left ( d_{ij}, d_{ji} \right )}.$$
+
+Employing an unidrectional interaction asymmetry, as a surrogate of bidirectional mutual dependences, dramatically reduces the number of links in the network, which provides substantial reduction of the time and memory required for the computation of of all posible maximum matchings in a network, particularly for large networks (see ``relative importance of species'' subsection below).
 
@@
 
-\subsection*{Relative importance}
-
-The manageability of a community $m$ provides an indication of the magnitude of $n_d$ but not the identity of the species that compose this set.
-Moreover, maximum matchings are often not unique in for a given network and different sets of species of size $n_d$ could be used to control the network \autocite{Liu2011}.
-Species vary in terms of the frequency with which they are classified as superior nodes (\autoref{fig:explain_mm}), and this frequency provides an indication of their relative importance in driving the state of the community.
-Ecologically, these distinctions are crucial because resources are limited and therefore ecological inteventions should be focused on species that might provide the largest impact.
-We therefore call \textit{driver species} those that are identified as being a superior node in all possible matchings, and consequently likely to have the most disproportionate effect on the abundances of other species in their community.
-
-As previously described, unlike unweighted networks, where a maximum matching is defined solely by its matching size, a maximum matching in a weighted network is one whose links have the largest possible total weight among all possible matchings.
-This means that in weighted networks there is a number of matchings that have maximal size, but are not maximum matchings because their total weight is not maximal.
-One alternative to calculate the species importance, and identify the driver species, would be to consider only maximum matchings.
-However empirical intreaction strengths, from which we calculate dependencies, are to some extent stochastic and depend on the sampling method and intensity.
-We therefore relaxed the matching weight requirement computed all possible matchings in the network that have the same maximal size while allowing for some tolerance regarding the weight.
-To compute all the matchings with maximal size, we first generated the network's line graph---an alternative representation in which nodes are the links of the original network and links represent common ending points\todo{add ref}.
-We then calculated the complement of the line graph: a graph in which nodes are connected if and only if they are not connected in the line graph.
-All possible matchings of maximal size can be found by enumerating all cliques of size $1-n_d$ in this complement graph \autocite{West2001, Csardi2006a}.
-
-\section*{Methods}
-
-In the last section we outlined the theoretical and computational underpinings of our approach.
-Now we illustrate its empirical application using ten pairs of plant-pollinator communities for which we explored their manageability and the relative importance of their constituent species.
-The networks were constructed from previously published visitation data collected from pollination communities in Bristol, UK \autocite{Lopezaraiza-Mikel2007} and in Cap de Creus National Park, Spain \autocite{Bartomeus2008}.
-Notably, each network pair was composed of a community invaded by a plant and a community ``free'' of the invasive species (Table S1).
-In the four British uninvaded communities, the non-invaded plots were obtained by experimentally removing all the flowers of the invasive species \textit{Impatients grandulifera}.
-In contrast, the Spanish uninvaded communities were obtained from plots that had not yet been colonised by either of the invasive species \textit{Carpobrotus affine acinaciformis} or \textit{Opuntia stricta}.
-The structure of these networks was determined using visitation frequency which has been shown to be an appropriate surrogate for interspecific effects in pollination networks \autocite{Vazquez2005, Bascompte2006}.
-To examine whether this decision would influence our results, we also evaluated the effect of using pollinator efficiency or importance as alternative measures of species interactions \autocite{NeEman2010, Ballantyne2015}, and we found quantitatively results for all of these options(see Supplementary Information).
-
-All analysis were performed in R 3.2.2 \autocite{RCoreTeam2015}.
-
 \subsection*{Community manageability}
@@
 Given the different networks, we started by quantifying their manageability.
-To do that, we calculated the maximum matching of the corresponding pollination network, and estimated the minimum number of species that need directed intervecntions to fully control the species abbundances in the community.
+To do so, we calculated the maximum matching of the corresponding pollination network, and estimated the minimum number of species that need directed intervecntions to fully control the species abbundances in the community.
 If a network had more than one component (two species are in different components if there exists no path between them), we only analysed the largest one.
-Although understanding the variability of manageability across ecological networks is an useful result itself, we also wanted to test whether perturbations, like invasion status, have an impact on manageability values.
-We therefore used a set of generalised linear models (with binomial error structure) to investigate the effect of invasion status while controling for factors related to species richness---as naively one might expect to see a negative relationship between diversity and manageability \autocite{Menge1995}.
-Coovariates inlcuded the total number of species, plant richness, polinators richness, the ratio of plants to pollinators richness, and the study site.
-We assessed competing models by comparing the Akaike Information Criterion corrected for small sample sizes (AICc).
+Although understanding the variability of manageability across ecological networks is an useful result itself, we also wanted to test whether network attributes, like invasion status, have an impact on the observed manageability values.
+We therefore used a set of generalised linear models (with binomial error structure) to investigate the effect of invasion status while controling for factors related to species richness, since one might naively expect to see a negative relationship between diversity and manageability \autocite{Menge1995}.
+These covariates inlcuded the total number of species, plant richness, polinators richness, the ratio of plants to pollinators richness, and the study site.
+We assessed competing models by comparing the Akaike Information Criterion corrected for small sample sizes (AICc), and report results for the most parsimonious one.
 
@@
 We therefore compared the manageability of the empirical networks to networks generated by three null models which varied in terms of the constraints they impose.
-The first set of random visitation networks maintain the connectivity of the empirical network, but both degree and weight were allowed to vary.
-A second set set was generated by maintaining each species' degree (its number of interactions) while varying the number of visits per species.
-Finally a third set of random networks mantained the species' strength (its total sum of visits) while varying their degrees.
+The first set of random visitation networks maintain the connectivity of the empirical network, but both degree (its number of interactions) and strength (its total sum of visits) were allowed to vary.
+A second set set was generated by maintaining each species' degree while varying the number of visits per species.
+Finally a third set of random networks mantained the species' strength while varying their degrees.
 Randomisations were generated using vegan 2.3-3 \autocite{Oksansen2016}.
-After generating the randomized networks under these three schemes, we then calculated the mutual dependences and interaction asymmetries and determined their manageability using the maximum matching algorithm.
-Finally we calculated the p-value of the manageability of each empirical network and the corresponding manageability of 999 randomisations.
-
-The dependency asymetry plays a fundamental role in determining the direction of control in a two species interaction and therefore has the potential to structure the network matching.
-We therefore performed an additional randomisation in which we mantained the structure of network but randomised the direction of the interaction asymmetries.
-This is, we first calculated the assymetries for each community and then shuffled the direction of the link between species.
-Similar as in previouls null models, we calculated the p-value of the empirical manageability compared to that of the randomisations.
+After generating the randomized networks under these three schemes, we then calculated the mutual dependences and interaction asymmetries of each and determined their manageability using the maximum matching algorithm.
+Finally we calculated the average rank (akin to a p-value) of the manageability of each empirical network compared to the corresponding manageabilites of each set of 999 randomisations.
+
+The dependency asymmetry plays a fundamental role in determining the direction of control in each two-species interaction and therefore has the potential to influence the network manageability results above.
+We therefore performed an additional randomisation in which we kept the structure of network consistent but randomised the direction of the interaction asymmetries.
+That is, we first calculated the assymetries for each community and then shuffled the direction of the link between species.
+Similar as in previous null models, we calculated the average rank of the empirical manageability as compared to those of the randomisations.
 
@@
 To quantify this importance in each network, we computed all possible matchings that have the same size as the networks' maximum matching.
-We then calculated the frequency to which each species is deemed to be a superior node in matchings with a weight greater or equal to 0.5 times the weight of the maximum matching.
-We choosed this threshold as it provided a high agreement between networks quantified by visitation and pollination efficiency as well as between our weighting/directionality assumptions (mutual dependences and inetraction asymmetries).
-Note that the choice of this threshold had a negligible impact on the results (Supplementary information).
-
-We observed that the number of maximal matchings increasses exponentially with the number of links and nodes in a network.
-Unfortunately, this implies that the large number of links in the most diverse communities renders the computation unfeasible when we use mutual dependecies.
-Taking this limitation into account, we compared the relative network manageability obtained when using assimetries or when using mutual dependencies for eleven of the twenty networks---for which the number of matchings was smaller than $4\times 10^{10}$.
-The comparison was performed using paired Spearman correlation test, a weighted correlation coefficient $r_{w2}$---which gives more weight to higer ranks \autocite{PintoDaCosta2015}, and a Jaccard similarity of the driver species in both approaches.
-All three approaches suggested a high similarity in relative ranks.
-Therefore, we used the results from the assymetries, rather than mutual dependences, to further investigate the factors that determine species' relative importance.
-
-Given the species frequency obtained using the interaction asymmetries, we then asked the question of whether some species-level structural properties can predict the relative importance of species.
-To do so, we used a generalised linear mixed-effects model (GLMM) to evaluate the relationship between the species' relative importance and a suite of structural measures.
-We specifically included measures of centrality (degree and eigen-centrality) which have been found to be strong predictors of importance in a coextintion context\todo{add ref}; measures related to network robustness (contribution to nestedness) as nestedness has been proposed as one of the key properties that promote stability in mutualistic networks \autocite{Saavedra2011}; and measures of strength of association and depedence (visitation and dependency strength), as their skewed distribution is characteristic of plant-pollinator networks and determine the extent of interspecific effects.
+We then calculated the frequency with which each species is deemed to be a superior node in the set of matchings that had a total weight greater or equal to 0.5 times the weight of the maximum matching.
+We selected this threshold as it provided a high agreement between networks quantified by visitation and pollination efficiency as well as between our weighting/directionality assumptions (mutual dependences and inetraction asymmetries); however the choice of this threshold had a negligible impact on the results (Supplementary Information).
+
+Even in sparse networks, like these studied here, the number of maximal matchings increasses exponentially with the number of links and nodes in a network.
+Unfortunately, this means that the large number of links in the most diverse communities rendered the computation unfeasible when we used mutual dependecies.
+Taking this limitation into account, we compared the relative network manageability obtained when using asymmetries to those found when using mutual dependencies for eleven of the twenty networks (those for which the number of matchings was smaller than $4\times 10^{10}$).
+The comparison was performed using a paired Spearman correlation test, a weighted correlation coefficient $r_{w2}$ (which gives more weight to higer ranks; \cite{PintoDaCosta2015}), and a Jaccard similarity of the driver species in both approaches.
+All three approaches identified a high similarity in relative ranks.
+Therefore, we used the results from the assymetries, rather than mutual dependences, to further investigate the factors that determine species' relative importance since this also allows us to obtain results for all networks.
+
+Given the species importance obtained using the interaction asymmetries, we then asked the question of whether some species-level structural properties can predict the relative importance of species.
+To do so, we used a generalised linear mixed-effects model (GLMM) with a logistic link function to evaluate the relationship between the species' relative importance and a suite of structural measures.
+As predictors in this model, we specifically included measures of centrality (degree and eigen-centrality), which have been found to be strong predictors of importance in a coextintion context \autocite{Memmott2004}; a measure related to network robustness (contribution to nestedness), as nestedness has been proposed as one of the key properties that promote stability in mutualistic networks \autocite{Saavedra2011}; and measures of strength of association and dependence (visitation and dependency strength), as their distribution determine the extent of interspecific effects.
 All metrics were calculated using the R package bipartite 2.06 \autocite{Dormann2008}.
-We allowed for variation among different communities by including the network identity as a random effect \autocite{Bates2015a}.
+We allowed for variation between different communities by including the network identity as a random effect \autocite{Bates2015a}.
 Candidate models were compared using AICc and the relative importance of the explanatory variables was evaluated using the sum of Akaike weights over candidate models that accounted for 95\% of the evidence \autocite{Burnham2003, Bates2014, Barton2016}.
 
-Invasive species have been shown to have disproportionate effects on the communities they invade\todo{add ref}.
-So we lastly examined the extent to which invasive species tend to be driver species---species whith the maximum importance---and to which extent their importance could be explained by the factors previously described.
+Invasive species in particular have been shown to have disproportionate effects on the communities they invade (\cite{Bartomeus2008, Gilberto2012}; but see \cite{Vila2009}).
+So we lastly examined the extent to which invasive species tend to be driver species---species whith the maximum importance---and whether their importance could be explained by the factors previously described.
 To do so, as our invasive species were plants, we first used a Mann-Withney U test to compare the relative importance of invasive species to those of other plants in the community.
-We then examined the residuals of the GLMM to investigate if invasive species' importance is larger or smaller than expected given their network structural properies.
 
@@
 
-\fi
-
 \section*{Discussion}
@@
 This suggest that the asymmetries at the species (specialization-generalization asymmetries) and the link level (interaction's dependence asymmetries) appear to be sufficiently defined by the distribution of species degree and strength \autocite{Melian2002}.
-Furthermore, we found that invasive species, by altering the patterns of assymetry, reduce the manageability of their communities.
+Furthermore, we found that invasive species, by altering the patterns of assymetry, reduce the manageability of their communities \autocite{Henriksson2016}.
 This result is in agreement with previous studies that suggest that invasors erode native pollination webs by ursurpating interactions and exarcerbate the asymmerties in the network, which in turn might increasse the stability of the community \autocite{Aizen2008, Bartomeus2008}.

### 2016-05-13 paper/manuscript.Rnw
change models, delete plants test, update figures and a bit results

@@
 We therefore relaxed the matching weight requirement and computed all possible matchings in the network that have the same maximal size while allowing for some tolerance regarding the weight.
-To compute all the matchings with maximal size, we first generated the network's line graph---another representation in which nodes are the links of the original network and links represent common ending points\todo{West2001}.
+To compute all the matchings with maximal size, we first generated the network's line graph---another representation in which nodes are the links of the original network and links represent common ending points \autocite{West2001}.
 We then calculated the complement of the line graph: a graph in which nodes are connected if and only if they are not connected in the line graph.
@@
   dplyr::filter(Sequence == 12) %>%
-  dplyr::mutate(weight = c(0.75, 0.5, 0.5, 0.6, 0.5, 0.16))
+  dplyr::mutate(weight = c("0.75", " ", "0.5", "0.33", " ", "0.25"))
 
@@
 To do so, we used a generalised linear mixed-effects model (GLMM) with a logistic link function to evaluate the relationship between the species' relative importance and a suite of structural measures.
-As predictors in this model, we specifically included measures of centrality (degree and eigen-centrality), which have been found to be strong predictors of importance in a coextintion context \autocite{Memmott2004}; a measure related to network robustness (contribution to nestedness), as nestedness has been proposed as one of the key properties that promote stability in mutualistic networks \autocite{Saavedra2011}; and measures of strength of association and dependence (visitation and dependency strength), as their distribution determine the extent of interspecific effects.
+As predictors in this model, we specifically included measures of centrality (degree and eigen-centrality), which have been found to be strong predictors of importance in a coextintion context \autocite{Memmott2004}; a measure related to network robustness (contribution to nestedness), as nestedness has been proposed as one of the key properties that promote stability in mutualistic networks \autocite{Saavedra2011}; and measures of strength of association and dependence (visitation and dependency strength), as their distribution determine the extent of interspecific effects; and whether the species was invasive or not.
+In addition we also included guild and invasive status as fixed effects; although the importance of plants and pollinators or invasive and non-invasive species could respond differently to our structural metrics, our dataset did not contain enough variation to include the corresponding interactions terms.
 All metrics were calculated using the R package bipartite 2.06 \autocite{Dormann2008}.
@@
 Candidate models were compared using AICc and the relative importance of the explanatory variables was evaluated using the sum of Akaike weights over candidate models that accounted for 95\% of the evidence \autocite{Burnham2003, Bates2014, Barton2016}.
-
-Invasive species in particular have been shown to have disproportionate effects on the communities they invade (\cite{Bartomeus2008, Gilberto2012}; but see \cite{Vila2009}).
-So we lastly examined the extent to which invasive species tend to be driver species---species whith the maximum importance---and whether their importance could be explained by the factors previously described.
-To do so, as our invasive species were plants, we first used a Mann-Withney U test to compare the relative importance of invasive species to those of other plants in the community.
 
@@
 \caption{\label{fig:n_driver_explanatory} Invaded communities have lower levels of manageability than uninvaded communities even when controling for the ratio of plant to pollinator richness.
-Adjusted manageability corrsponds to the partial working residuals of the invasion status.}
+Adjusted manageability corrsponds to the partial working residuals of the invasion status.
+The box covers the 25th–75th percentiles, the middle line marks the median, and the maximum length of the whiskers is 1.5 times the interquartile range.
+Points outside this range show up as outliers.}
 \end{figure}
@@
 
-z_scores_method_order <- unique(z_scores$method)
+z_scores_method_order <- c("r0","swsh_both", "quasiswap_count","r00_ind", "r00_samp", "r00_both")
 
@@
   # geom_hline(yintercept = c(-0), linetype = 2, alpha = 0.7, size = 0.25) + 
-  geom_vline(aes(xintercept = 3.5), alpha = 0.6, size = 0.25) +
+  geom_vline(aes(xintercept = 1.5), alpha = 0.6, size = 0.25) +
    geom_hline(yintercept = 0, size = 0.25, linetype = 2, colour = "grey30") +
@@
   scale_x_discrete(
-    labels = rev(c("random\nassymetry", "maintain\nconnectance", "maintain vis. strength\nrandomise degree", "maintain vis. degree\nrandomise strength")),
+    labels = rev(c("only maintain\nconnectance", "maintain strength\nrandomise degree", "maintain degree\nrandomise strength", "random\nassymetry")),
+    # breaks = c("r00_samp", "swsh_both", "quasiswap_count", "r0"),
     expand = c(0,0)) +
@@
     coord_flip() +
-  ylab("rank of empirical manageability") + 
+  ylab("mean rank of empirical manageability") + 
   fer_theme +
@@
 In contrast the manageability of network in which the visitation strength or degree was mantained was not different to the manageability of the empirical networks.
-Dark grey and white boxplots represent manageabilities obtained using mutual dependencies and asymmetries respectively.}
+Dark grey and white boxplots represent manageabilities obtained using mutual dependencies and asymmetries respectively.
+All boxes are as in \autoref{fig:n_driver_explanatory}.}
 \end{figure}
@@
                                          c("de", "n", "vi", "eig_cen", 
-                                           "guildpol"),
+                                           "guildpol", "d", "invasiveTRUE"),
                                          c("dependency strength", 
@@
                                            "eigen-centrality", 
-                                           "guild (pollinator)"))) %>% 
+                                           "guild (pollinator)", "degree", "invasive sp."))) %>% 
   dplyr::arrange(-pare, -Importance, -Estimate, factor) %>% 
@@
   dplyr::inner_join(dd) %>%
-  dplyr::mutate(pp = predict(mod, select = 0.95, newdata = ., re.form = NA)$averages,
+  dplyr::mutate(pp = predict.glmulti(mod, select = 0.2, newdata = ., re.form = NA),
                 pp = as.vector(pp),
@@
             eig_cen = mean(data$eig_cen, na.rm = T),
+            d = mean(data$d, na.rm = T),
             guild = "pla") %>%
@@
   dplyr::mutate(q = predict.glmulti(mod,
-                                    select = 0.95,
+                                    select = 2 %>% `class<-`("integer"),
                                     newdata = .,
@@
   dplyr::mutate(de = de * attr(data$de, "scaled:scale") + attr(data$de, "scaled:center"),
-                vi = vi * attr(data$vi, "scaled:scale") + attr(data$vi, "scaled:center"),
-                n = n * attr(data$n, "scaled:scale") + attr(data$n, "scaled:center"))
+                vi = vi * attr(data$vi, "scaled:scale") + attr(data$vi, "scaled:center"))
 
@@
 Although plants showed significantly higher levels of importance than pollinators (Mann-Withney-Wilcoxon test, $p \Sexpr{fix_small_pvalue(wilcox.test(pp ~ guild, data = dd, alternative = "greater")$p.value)}$), this difference can be largely explained by the strength of dependency of the species (the sum of the dependencies for a given species).
-Indeed, when averaging over the set of GLMMs that accounted at least 95\% of the evidencee based on AICc, we found that the strength of dependency  is the single most important factor determining the relative importance of species for network control (\autoref{table:driver_model}\todo{consider moving the table to thes supplementary}, \autoref{fig:driver_model_alt}).
+Indeed, when averaging over the set of GLMMs that accounted at least 95\% of the evidencee based on AICc, we found that the strength of dependency  is the single most important factor determining the relative importance of species for network control (\autoref{table:driver_model}, \autoref{fig:driver_model_alt}).
 In contrast, the number of visits a species makes (or receives) and its contribution to nestedness have only a marginal effect on its relative importance.
-
-<<invasive species differ?, echo = FALSE, warning = F, message = F, results = "hide">>=
-for_invasive <- dd %>%
-  dplyr::mutate(prediction = as.vector(predict.glmulti(mod, select = 0.95, newdata = .)$averages), 
-                predictionp = plogis(prediction), 
-                res = d_reim - predictionp) %>%
-  dplyr::filter(guild == "pla")
-
-inv_test <- wilcox.test(d_reim ~ invasive, data = for_invasive, alternative = "less")
-t.test(dplyr::filter(for_invasive, invasive)$res)
-@
-
-In addition, in the ten communities that were invaded, invasive species were invariably classified as a driver species.
-In general, the relative importance of invasive species was significantly larger than those of the other plants in the studied communities (Mann-Whitney U Test, $p =  \Sexpr{fix_small_pvalue(inv_test$p.value)}$).
-However this difference can be fully explained by the explanatory variables in our model as all the residuals for the invasive species were virtually zero.
-
 \begin{table}
@@
 <<fig species alt, echo = FALSE, warning = F, message = F, fig.height=2.2, fig.width=3.1>>=
+
+data_pp <- data
+data_pp$pred_ri <- plogis(predict.glmulti(mod, select = as.integer(1), re.form = NA))
+data_pp$de_s <- data$de * attr(data$de, "scaled:scale") + attr(data$de, "scaled:center")
+data_pp <- lapply(data_pp, as.vector) %>% as.data.frame
+
 pred4 %>%
@@
   scale_x_log10(expand = c(0,0)) +
-   geom_point(data = dplyr::arrange(dd, invasive), aes(x = de2, y = pp, fill = invasive, shape = guild, size = invasive), show.legend = F) +
+   geom_point(data = dplyr::arrange(data_pp, invasive), aes(x = de_s, y = pred_ri, fill = invasive, shape = guild, size = invasive), show.legend = F) +
     scale_shape_manual(values = c(21, 23)) +
@@
 
-<<interact with invasive , echo = FALSE, warning = F, message = F, results = "asis">>=
-
-dd_inv <- dd %>%
-  dplyr::filter(net_name %in% invasive_sp$net_name) %>%
-  plyr::ddply("net_name", function(x){
-    inv <- invasive_sp$species[invasive_sp$net_name == x$net_name[1]]
-    if(length(inv) == 0){
-      x %>% 
-      dplyr::mutate(int_inv = "none")
-    } else{
-      interacting <- igraph::adjacent_vertices(net[[x$net_name[1]]], inv)[[1]] %>% names
-      x %>% 
-        dplyr::mutate(int_inv = species %in% interacting)
-    }
-  })
-
-# dd_inv %>%
-#   # dplyr::group_by(net_name, int_inv) %>%
-#   # dplyr::summarise(int_inv_d_reim_mean = mean(d_reim)) %>%
-#     ggplot(aes(x = int_inv, y = d_reim)) +
-#   geom_boxplot()
-
-dd_inv_t <- dd_inv %>%
-  dplyr::group_by(net_name, int_inv) %>%
-  dplyr::summarise(int_inv_d_reim_mean = mean(d_reim)) %>%
-  tidyr::spread(int_inv, int_inv_d_reim_mean)
-
-dd_inv_test <- wilcox.test(dd_inv_t[, 3][[1]], dd_inv_t[, 2][[1]], paired = F)
-
-@
-
-No significant difference on importance between pollinators interacting with invasive species or not.
-
 \section*{Discussion}

### 2016-05-13 code/V2.0/10-species_models.R

@@ -93,6 +93,13 @@ glm.redefined = function(formula, data, always="", ...) {
   glm(as.formula(paste(deparse(formula, width.cutoff = 500), always)), data=data, ...)
 }
 
+invasive_sp <- dplyr::filter(meta, inv) %>%
+  dplyr::mutate(species = plyr::mapvalues(invader, 
+                                          c("car", "op", "imp"),
+                                          c("p_4", "p_25", "Impatiens glandulifera")), 
+                invasive = T) %>%
+  dplyr::select(net_name, species, invasive)
+
 # calculate a lot of models
 mo <- drivers %>%
   dplyr::filter(threshold == 0.5,
@@ -105,7 +112,9 @@ mo <- drivers %>%
                  "d" = "degree", 
                  "de" = "d_strength",
                  "vi" = "v_strength")  %>%
-  dplyr::mutate(n = scale(n),
+  dplyr::full_join(invasive_sp) %>% 
+  dplyr::mutate(invasive = replace(invasive, is.na(invasive), FALSE)) %>%
+  dplyr::mutate(n = scale(n)[,1],
                 S_d = scale(S_d),
                 S_v = scale(S_v),
                 d = scale(d),
@@ -113,18 +122,21 @@ mo <- drivers %>%
                 de = scale(de),
                 vi = scale(vi))
 
-to_exclude <- c("de", "eig_cen", "n", "vi") %>% 
-  combn(2) %>% 
-  apply(2, function(x) paste(x[1], x[2], sep = ":"))
 
-mod <- glmulti("d_reim", c("de", "guild", "eig_cen","n", "vi"),
+
+
+to_exclude <- c("de", "eig_cen", "n", "vi", "invasive") %>% 
+  combn(2) %>% 
+  apply(2, function(x) paste(x[1], x[2], sep = ":")) 
+
+mod <- glmulti("d_reim", c("d", "de", "guild", "eig_cen","n", "vi", "invasive"),
              # exclude = to_exclude, 
              data = mo,
              family = "binomial",
              fitfunction = glmer.glmulti, 
              level = 1,
              crit = "aic", 
-             method = "h", 
+             method = "g", 
              marginality = T,
              includeobjects = F, 
              random = " + (1 | net_name)")

### 2016-05-16 paper/manuscript.Rnw
edit results, finally a complete version of the paper

@@
 
-\subsection*{Weighting \& directing links}
+\subsection*{Community manageability}
+
+Given the different networks, we started by quantifying their manageability.
+To do so, we calculated the maximum matching of the corresponding pollination network, and estimated the minimum number of species that need directed intervecntions to fully control the species abbundances in the community.
+If a network had more than one component (two species are in different components if there exists no path between them), we only analysed the largest one.
+
+\subsubsection*{Weighting \& directing links}
 
@@
 
-\subsection*{Community manageability}
-
-Given the different networks, we started by quantifying their manageability.
-To do so, we calculated the maximum matching of the corresponding pollination network, and estimated the minimum number of species that need directed intervecntions to fully control the species abbundances in the community.
-If a network had more than one component (two species are in different components if there exists no path between them), we only analysed the largest one.
+\subsubsection*{Data analysis}
+
 Although understanding the variability of manageability across ecological networks is an useful result itself, we also wanted to test whether network attributes, like invasion status, have an impact on the observed manageability values.
@@
 All three approaches identified a high similarity in relative ranks.
-Therefore, we used the results from the assymetries, rather than mutual dependences, to further investigate the factors that determine species' relative importance since this also allows us to obtain results for all networks.
+Therefore, we focused on the results from the assymetries, rather than mutual dependences, to further investigate the factors that determine species' relative importance since this also allows us to obtain results for all networks.
 
@@
 
-The studyed networks had levels of manageability between \Sexpr{round(min(1-dplyr::filter(n_driver, type == "z-bi")$n_dr_p), digits = 2)} and \Sexpr{round(max(1-dplyr::filter(n_driver, type == "z-bi")$n_dr_p), digits = 2)} (mean \Sexpr{round(mean(1-dplyr::filter(n_driver, type == "z-bi")$n_dr_p), digits = 2)}) when we considered bidirectional links weighted by the mutual dependences.
-This was in strong agreement  to the results obtained using the dependence asymmetry in which manageability ranged between \Sexpr{round(min(1-dplyr::filter(n_driver, type == "weight")$n_dr_p), digits = 2)} and \Sexpr{round(max(1-dplyr::filter(n_driver, type == "weight")$n_dr_p), digits = 2)} (Spearman rank correlation \Sexpr{round(src_bi_w$estimate, digits = 2)}, $p = \Sexpr{as.numeric(format(src_bi_w$p.value, digits = 2))}$).
-In addition we found that even when controling for diversity, invaded communities had were more difficult to manage than uninvaded ones.
-Out of the explored factors---total number of species, plant richness, pollinator richness and the ratio of plant to pollinator richness---only the ratio of plants to pollinator was retained in the final model (as determined by the AICc; \autoref{fig:n_driver_explanatory}, Table S3).
+The networks studied here had levels of manageability between \Sexpr{round(min(1-dplyr::filter(n_driver, type == "z-bi")$n_dr_p), digits = 2)} and \Sexpr{round(max(1-dplyr::filter(n_driver, type == "z-bi")$n_dr_p), digits = 2)} (mean \Sexpr{round(mean(1-dplyr::filter(n_driver, type == "z-bi")$n_dr_p), digits = 2)}) when we considered bidirectional links weighted by the mutual dependences.
+This was in strong agreement  to the results obtained using the dependence asymmetry in which manageability ranged between \Sexpr{round(min(1-dplyr::filter(n_driver, type == "weight")$n_dr_p), digits = 2)} and \Sexpr{round(max(1-dplyr::filter(n_driver, type == "weight")$n_dr_p), digits = 2)} (\Sexpr{round(mean(1-dplyr::filter(n_driver, type == "weight")$n_dr_p), digits = 2)}; Spearman rank correlation \Sexpr{round(src_bi_w$estimate, digits = 2)}, $p = \Sexpr{as.numeric(format(src_bi_w$p.value, digits = 2))}$).
+In addition we found that invaded communities were significanlty more difficult to manage than uninvaded ones even when controling for diversity.
+Out of the explored factors---total number of species, plant richness, pollinator richness, and the ratio of plant to pollinator richness---only the ratio of plant to pollinator richness was retained in the final model as determined by the AICc (\autoref{fig:n_driver_explanatory}, Table S3).
 
@@
 
-The manageability of empirical networks was, in general, not significantly different to the manageability of network randomisations that maintain the degree or the strength of individual species (\autoref{fig:randomisations}).
-However when comparing the empirical network to less constrained randomisations that maintained the original connectance but in which species had different degrees and strengths, we found that empirical networks tend to have smaller values of manageability.
+The manageability of empirical networks was, in general, not significantly different to the manageability of network randomisations that maintained the degree or the strength of individual species (\autoref{fig:randomisations}).
+However, when comparing the empirical network to less constrained randomisations that only maintained the original connectance but in which species had different degrees and strengths, we found that empirical networks tended to have smaller values of manageability.
 This pattern is even more marked when we maintained the network structure but randomised only the direction of the asymmetries (\autoref{fig:randomisations}).
@@
 @
-\caption{\label{fig:randomisations} The manageability of empirical networks was compared to network randomisations using a normalised rank.
-The shaded areas in light grey ($< 0.025$ and $> 0.975$) suggest a significant difference between the empirical network and its randomisations.
+\caption{\label{fig:randomisations} The manageability of empirical networks compared to network randomisations.
+For each of four randomisation approaches, we shouw that---akin to a p-value---an scaled mean rank $< 0.025$ or $> 0.975$ (shaded areas in light grey) suggest a significant difference between the empirical network and its randomisations.
 The empirical manageability is much smaller than those of randomisations in which the direction of assymmetries has been randomised.
-In contrast the manageability of network in which the visitation strength or degree was mantained was not different to the manageability of the empirical networks.
+In contrast the manageability of network in which the visitation strength or degree was mantained was not significantly different to the manageability of the empirical networks.
 Dark grey and white boxplots represent manageabilities obtained using mutual dependencies and asymmetries respectively.
@@
 
-We found a strong agreement between relative species' importance in the 11 networks for which we were able to calulate it using both mutual dependencies and asymmetries (Spearman's rank correlation ranged between $\rho = [\Sexpr{round(min(dplyr::filter(correlations, threshold == 0.5, type == "asymmetry", scaled == T)$V3, na.rm = T), digits = 2)}, \Sexpr{round(max(dplyr::filter(correlations, threshold == 0.5, type == "asymmetry", scaled == T)$V3, na.rm = T), digits = 2)}]$, median $\tilde{\rho} = \Sexpr{round(median(dplyr::filter(correlations, threshold == 0.5, type == "asymmetry", scaled == T)$V3, na.rm = T), digits = 2)})$.
-Indeed, when using the weighted rank correlation coefficient $r_{w2}$, we found that the agreement was stronger for highly ranked species than for lowly ranked species ($\tilde{r_{w2}} = \Sexpr{round(median(dplyr::filter(correlations, threshold == 0.5, type == "asymmetry", scaled == T)$V1, na.rm = T), digits = 2)}$ versus $\tilde{r_{w2}} = \Sexpr{round(median(dplyr::filter(correlations, threshold == 0.5, type == "asymmetry", scaled == T)$V2, na.rm = T), digits = 2)}$).
+We found a strong agreement between relative species' importance in the 11 networks for which we were able to calulate them using both mutual dependencies and asymmetries (Spearman's rank correlation ranged between $\rho = [\Sexpr{round(min(dplyr::filter(correlations, threshold == 0.5, type == "asymmetry", scaled == T)$V3, na.rm = T), digits = 2)}, \Sexpr{round(max(dplyr::filter(correlations, threshold == 0.5, type == "asymmetry", scaled == T)$V3, na.rm = T), digits = 2)}]$, median $\tilde{\rho} = \Sexpr{round(median(dplyr::filter(correlations, threshold == 0.5, type == "asymmetry", scaled == T)$V3, na.rm = T), digits = 2)})$.
 Moreover both approaches identified a highly similar set of driver species (Jaccard similarity $J = [\Sexpr{round(min(dplyr::filter(correlations, threshold == 0.5, type == "asymmetry", scaled == T)$V4, na.rm = T), digits = 2)}, \Sexpr{round(max(dplyr::filter(correlations, threshold == 0.5, type == "asymmetry", scaled == T)$V4, na.rm = T), digits = 2)}]$, $\tilde{J} = \Sexpr{round(median(dplyr::filter(correlations, threshold == 0.5, type == "asymmetry", scaled == T)$V4, na.rm = T), digits = 2)})$.
-Therefore we employed the relative rankings obtained using asymmetries in the following analyses.
+Notably we found that the agreement was stronger for highly ranked species than for lowly ranked species ($\tilde{r_{w2}} = \Sexpr{round(median(dplyr::filter(correlations, threshold == 0.5, type == "asymmetry", scaled == T)$V1, na.rm = T), digits = 2)}$ versus $\tilde{r_{w2}} = \Sexpr{round(median(dplyr::filter(correlations, threshold == 0.5, type == "asymmetry", scaled == T)$V2, na.rm = T), digits = 2)}$) when using the weighted rank correlation coefficient $r_{w2}$.
+Given the similarities, we concentrated on the relative rankings obtained using asymmetries in the following results
 
@@
 
-Although plants showed significantly higher levels of importance than pollinators (Mann-Withney-Wilcoxon test, $p \Sexpr{fix_small_pvalue(wilcox.test(pp ~ guild, data = dd, alternative = "greater")$p.value)}$), this difference can be largely explained by the strength of dependency of the species (the sum of the dependencies for a given species).
-Indeed, when averaging over the set of GLMMs that accounted at least 95\% of the evidencee based on AICc, we found that the strength of dependency  is the single most important factor determining the relative importance of species for network control (\autoref{table:driver_model}, \autoref{fig:driver_model_alt}).
+Although plants showed significantly higher levels of importance than pollinators (Mann-Whitney-Wilcoxon test, $p = \Sexpr{fix_small_pvalue(wilcox.test(pp ~ guild, data = dd, alternative = "greater")$p.value, 3)}$), this difference can be largely explained by the strength of dependency of the species (the sum of the dependencies for a given species).
+Indeed, when averaging over the set of GLMMs that accounted at least 95\% of the evidence based on AICc, we found that the strength of dependency  is the single most important factor determining the relative importance of species for network control (\autoref{table:driver_model}, \autoref{fig:driver_model_alt}).
 In contrast, the number of visits a species makes (or receives) and its contribution to nestedness have only a marginal effect on its relative importance.

### 2016-05-20 paper/manuscript.Rmd
updated introduction and discussion implementing daniel's comments in an ecology letters format

@@
 ---
-title: "driver species paper"
-output: pdf_document
+title: "Biotic invasions reduce the manageability of mutualistic networks"
+csl: ecology-letters.csl
+output: html_document
+bibliography: references.bib
 ---
-
-**how is the control species number influenced by network structure?**
-
-Using both Bartomeus and Lopezaraiza dataset
-```{r, echo=FALSE}
+```{r libraries, echo = FALSE, warning = F, message = F}
+library(magrittr)
+library(knitr)
 library(ggplot2)
-library(magrittr)
-# load utility functions
-nn <- list.files("../code/functions", full.names = TRUE) %>% lapply(source)
-
-my_theme <- theme_classic() + theme(legend.position = "none", text = element_text(family = "Times"), axis.title.x = element_text(vjust = -0.7), axis.title.y = element_text(vjust = 1.5)) 
+library(glmulti)
+library(Hmisc)
+library(lme4)
+opts_knit$set (root.dir=normalizePath('../'))
 ```
 
-```{r, echo=FALSE, warning=FALSE, message=FALSE}
-n_driver <- read.csv("../data/n_driver_species.dat")
-random_n <- read.csv("../data/random_n_driver.csv")
-
-n_control <- n_driver %>%
-	dplyr::select(-keep) %>%
-	tidyr::separate(type, c("type", "keep"), "\\.", remove = T)
-
-random_n_z <- random_n %>% 
-	dplyr::group_by(net, type, keep, method) %>%
-	dplyr::summarise(n_driver_u = mean(n_driver, na.rm = T),
-									 n_driver_sd = sd(n_driver, na.rm = T)) %>%
-	dplyr::full_join(n_control) %>% 
-	dplyr::group_by() %>%
-	dplyr::mutate(n_driver_z_score = (n_driver - n_driver_u)/n_driver_sd)
-
-random_n_z %>% 
-	ggplot(aes(x  = as.character(interaction(type, keep)), y = n_driver_z_score)) +
-	geom_rect(ymin = -2, ymax = 2, xmin = -1, xmax = 10, fill = "grey90") +
-	geom_hline(yintercept = 0, size = 0.4) +
-	geom_vline(xintercept = seq(1.5, 5.5), linetype = 2) +
-	geom_boxplot(aes(fill = method)) +
-	scale_fill_discrete(name = "randomisations\nmantain\ndegree of", labels= c("plants", "pollinators", "both")) + 
-	my_theme + 
-	xlab("link structure scheme") +
-	ylab("standard score") +
-	theme(legend.position = "right",
-				axis.line.x = element_blank(), axis.ticks.x = element_blank())
+```{r auxiliary functions, echo = FALSE, warning = F, message = F}
+"./code/V2.0/functions" %>% 
+	list.files(full.names = T) %>%
+	plyr::l_ply(source)
 ```
 
-\newpage
-
-**what's the role of the dependency?**
-
-Using dataset by Ballantune to demonstrate congruency between visitation and effective pollination dependency.
-
-```{r, echo=FALSE, warning=FALSE, message=FALSE}
-random_dir_n <- read.csv("../data/random_dir_n_driver.csv")
-
-random_dir_n %>% 
-	dplyr::mutate(type = "weight") %>%
-	dplyr::group_by(net, type, keep) %>%
-	dplyr::summarise(n_driver_u = mean(n_driver, na.rm = T),
-									 n_driver_sd = sd(n_driver, na.rm = T)) %>%
-	dplyr::inner_join(n_control) %>% 
-	dplyr::group_by() %>%
-	dplyr::mutate(n_driver_z_score = (n_driver - n_driver_u)/n_driver_sd) %>% 
-	ggplot(aes(x  = as.character(interaction(type, keep)), y = n_driver_z_score)) +
-	geom_rect(ymin = -2, ymax = 2, xmin = -1, xmax = 10, fill = "grey90") +
-	geom_hline(yintercept = 0, size = 0.4) +
-	geom_vline(xintercept = seq(1.5, 2.5), linetype = 2) +
-	geom_jitter(position = position_jitter(height = 0), shape = 21) +
-	geom_boxplot(fill = "white", alpha = 0.5) +
-	scale_fill_discrete(name = "randomisations\nmantain\ndegree of", labels= c("plants", "pollinators", "both")) + 
-	my_theme + 
-	xlab("link structure scheme") +
-	ylab("standard score") +
-	theme(legend.position = "right",
-				axis.line.x = element_blank(), axis.ticks.x = element_blank())
+```{r plot theme, echo = FALSE, warning = F, message = F}
+fer_theme <- theme_bw() +
+	theme(text = element_text(family = "Times"),
+	      title = element_text(size = 7.5, hjust = 0),
+	      legend.title = element_text(size = 9),
+	      legend.text = element_text(size = 8),
+				axis.text = element_text(size = 8),
+				axis.title = element_text(size = 9, hjust = 0.5), 
+				strip.text = element_text(size = 9, hjust = 0), 
+				strip.background = element_blank(),
+				plot.margin = grid::unit(c(5, 0, 2, 0), "mm"))
 ```
 
-\newpage
+```{r read data and results, echo = FALSE, warning = F, message = F}
+net <- "./data/V2.0/networks" %>%
+	read_networks()
+meta <- readr::read_csv("data/ntw_info.csv") %>% dplyr::tbl_df() %>%
+	dplyr::rename(count = method)
+n_matched <- readRDS("./data/V2.0/n_matched.rds")
+a_m <- readRDS("./data/V2.0/n_matched_all_types.rds") 
+r_w <- readRDS("./data/V2.0/random_weights.rds") %>% dplyr::tbl_df() %>%
+  dplyr::rename_("net_name" = ".id")
+r_d <- readRDS("./data/V2.0/random_directions.rds") %>% dplyr::tbl_df() %>%
+  dplyr::rename_("net_name" = ".id")
+s_p <- readRDS("./data/V2.0/species_properties.rds") %>% dplyr::tbl_df()
+# mod <- readRDS("./data/V2.0/species_models.rds")
+driver <- c("./data/V2.0/matching_frequency") %>% 
+  list.files(full.names = T) %>%
+  lapply(list.files, full.names = T) %>% 
+  unlist() %>% 
+  lapply(read_allRDS)
+prop <- expand.grid(c("asymmetry", "max_dep"), 
+                    c("scaled_FALSE", "scaled_TRUE")) %>% plyr::alply(1)
+driver <- mapply(function(x, y){
+  attr(x, "type") <- as.character(y[,1])
+  attr(x, "scaled") <- stringr::str_split(as.character(y[,2]), "_") %>% unlist() %>% extract(2) %>% as.logical()
+  return(x)
+}, driver, prop)
+driver_bi <- "./data/V2.0/matching_frequency_bi" %>% 
+  read_allRDS()
+mod <- readRDS("./data/V2.0/detailed_species_models.rds")
+mo <- readRDS("./data/V2.0/detailed_species_models_data.rds")
+```
 
-**finally what makes a species relevant from management, and how invasive species fit there**?
+**E. Fernando Cagua^\*^, Kate L Wootton^§^, Daniel B. Stouffer^#^**
 
-exploring these and other factors related to especialization
+Center of Integrative Ecology, School of Biological Sciences, University of Canterbury, 8041 Christchurch, New Zealand
 
-```{r, echo=FALSE, warning=FALSE, message=FALSE, cache=TRUE}
-library(grid)
-library(gridExtra)
+^\*^ efc29@uclive.ac.nz 
+^§^ kate.l.wootton@gmail.com
+^#^ daniel.stouffer@canterbury.ac.nz
 
-folder <- "../data/redundancy/node/"
-node_redundancy <- list.files(folder, full.names = TRUE) %>%
-    plyr::ldply(function(x, name){
-        y <- read.csv(x) 
-        info <- basename(x) %>% 
-            stringr::str_sub(end = -5) %>% 
-            stringr::str_split("_") %>% 
-            unlist()
-        y %>%
-            dplyr::mutate(net = info[[1]],
-                                        type = info[2],
-                                        keep = info[3])
-    })
+**Running title:** Manageability of mutualistic networks.
 
-nr_sum <- node_redundancy %>%
-	dplyr::mutate(type = interaction(type, keep)) %>%
-	dplyr::group_by(net, type, robustness) %>%
-	dplyr::summarise(freq = n()) %>%
-	dplyr::group_by(net, type) %>%
-	dplyr::mutate(n_species = sum (freq)) %>%
-	dplyr::group_by() %>%
-	dplyr::mutate(prop = freq / n_species, 
-								type = as.character(type), 
-								robustness = as.character(robustness))
+**Keywords:** Network control, ecological networks, species importance, driver species (10 needed).
 
-net <- list.files("../data/networks/", full.names = TRUE) %>%
-    lapply(readRDS)
-names(net) <- list.files("../data/networks/", full.names = FALSE) %>%
-    stringr::str_split("\\.") %>% lapply(`[`, 1) %>% unlist ()
+**Article type:** Letter.
 
-node_redundancy %<>% 
-	plyr::ddply("net", function(x){
-		this_net <- net[[dplyr::first(x$net)]] %>%
-	# select only the largest connected component of the network
-			keep_largest_component()
-		nodes <- igraph::V(this_net)[x$n]$name
-		x %>%
-			dplyr::mutate(node = nodes)
-	}) %>% dplyr::tbl_df()
+**Number of words:** 150 max for Abstract; 5000 max for Main text.
 
-deg_strength <- plyr::ldply(net,function(x){
-	degree <- igraph::degree(x)
-	m <- igraph::as_adjacency_matrix(x, attr = "weight", sparse = F)
-	m[m == 0] <- NA 
-	m_int_strength <- apply(m, 1, mean, na.rm = T)
-	s_int_strength <- apply(m, 1, sum, na.rm = T)
-	ncont <- igraph::as_incidence_matrix(x, 
-														types = igraph::V(x)$type == "pla") %>%
-		nestedcontribution() %>% dplyr::add_rownames("node")
-	data.frame(node = names(degree), 
-						 degree = degree, 
-						 m_int_strength = m_int_strength,
-						 s_int_strength = s_int_strength) %>%
-		dplyr::full_join(ncont)
-}) %>% dplyr::rename_("net_name" = ".id")
+**Number of references:** XX
 
-net_info <- read.csv("../data/ntw_info.csv")
+**Number of displays:** 5 figures; 1 table.
 
-net_info %<>%
-	dplyr::mutate(ratio_pol_pla = n_pol/n_pla)
+**Correspondence to:** Daniel Stouffer (daniel.stouffer@canterbury.ac.nz) - +64 21 0825 8815 - School of Biological Sciences, University of Canterbury, 20 Kirkwood Ave, Christchurch 8013, New Zealand
 
-folder <- "../data/maximum_matchings_summary/" 
-files <- list.files(folder)
-node_mm <- plyr::adply(files, 1, function(x){
-	read.csv(file.path(folder, x)) %>%
-		dplyr::mutate(net = unlist(stringr::str_split(x, "_"))[1],
-									type = unlist(stringr::str_split(x, "_"))[2], 
-									keep = unlist(stringr::str_split(x, "_"))[3],
-									batch = unlist(stringr::str_split(x, "_"))[4])
-}) %>%
-	dplyr::select(-X1) %>%
-	dplyr::group_by(net, type, keep, node) %>%
-	dplyr::summarise(freq = sum(freq))
+**Authorship:** DBS conceived the idea, EFC performed all analysis. Both authors contributed to the development of the theoretical framework and the writing of the manuscript.
 
-ranked_mm <- node_mm %>%
-	dplyr::filter(!is.na(freq)) %>%
-	dplyr::group_by(net, type, keep) %>%
-	dplyr::mutate(r = rank(freq, ties.method = "random"),
-								f_f = freq/max(freq), 
-								type.keep = as.character(interaction(type, keep)))  %>%
-	dplyr::rename(net_name = net)
+**Data accessibility:** All data used in this manuscript has already been published by @Lopezaraiza-Mikel2007, @Bartomeus2008, and @Ballantyne2015.
+To access the data, authors should refer to the original sources.
 
-invasive_sp <- data.frame(node = c("p_4", "p_25"), invs.species = TRUE)
+# Abstract
 
-ranked_with_inv <- 
-	ranked_mm %>% 
-	dplyr::group_by() %>%
-	dplyr::full_join(invasive_sp) %>% 
-	dplyr::full_join(net_info)
+150 words
 
-imp <- ranked_with_inv %>%
-	dplyr::full_join(deg_strength) %>%
-	dplyr::filter(!is.na(type.keep), 
-								type == "weight",
-								keep == "A" | keep == "all") %>%
-	tidyr::separate(node, into = c("categ", "number"), sep = "_", remove = F)
+# Introduction
 
-inv <- imp %>% dplyr::filter(!is.na(invs.species))
+Complex systems are characterised by non-linear relationships in which the whole is greater than the sum of its parts [@Jorgensen1998; @Levin1999; @Montoya2006].
+Within community ecology, a complex systems approach has led to the development of a rich suite of analytical and simulation tools with which to understand, for example, the role of species when embedded in an intricate network of interactions [@Pascual2005; @Bascompte2009; @Stouffer2012].
+The inherent complexity of nature, however, has hindered---or at least greatly complicated---our ability to find management solutions to the many problems ecological communities face. 
+To overcome this obstacle, we require a framework that allow us to explain, predict, and manage ecological communities, particularly when they are faced with perturbations [@Sole2001; @Green2005].
+Moreover, such a framework needs to be able to account for their complex structure, and the dynamics that determine the state of each species, and the community as a whole.
 
-p1 <- imp %>%
-	ggplot(aes(x = m_int_strength, y = f_f)) +
-	geom_point(aes(fill = categ),
-						 shape = 21, 
-						 alpha = 0.5) +
-	scale_shape_manual(values = c(21, 22)) +
-	facet_wrap(~type) +
-	geom_smooth(aes(colour = categ, fill = categ), 
-							family = "binomial", method = "gam", colour = "grey10") +
-	geom_point(data = inv, fill = "red", size = 2.5, shape = 21) +
-	my_theme +
-	xlab("mean interaction strength") +
-	ylab("species frequency\nin control sets") +
-	scale_color_discrete(name = "", labels = c("pollinators", "plants")) +
-	scale_fill_discrete(name = "", labels = c("pollinators", "plants")) +
-	theme(legend.position = "right", strip.background = element_blank())
+Among the various possibilities, control theory is a strong candidate as it is designed to deal with determining and supervising the behavior of general dynamical systems, and is well equiped to deal with the many feedbacks presents in ecological communities [@Liu2015].
+What is more, existing research in the field has established a strong link between the structure of complex networks and their controlability, demonstrating that it is in principle possible to alter a whole ecological community's composition by modifying the abundances of only a few species [@Liu2011; @Cornelius2013; @Ruths2014].
+However the link between the structure of complex networks and our ability to manage and conserve them is still ambiguous [@Tylianakis2010].
+For instance, biotic invasions, as a major driver of global change, can induce dramatic changes on the patterns of interactions that determine the structure of ecological networks [@Baxter2004; @Tylianakis2008; @Ehrenfeld2010a].
+The difficulty of returning invaded communities to their predisturbance state is apparent based on the limited success of restoration projects [@Suding2004; @Rodewald2015; @Smith2016]. 
+Although it therefore presents a double challenge, understanding how differences in network structure before and after the invasion impact our ability to manage them is a critical first step towards a fully informed recovery.
 
-p2 <- imp %>%
-	ggplot(aes(x = degree, y = f_f)) +
-	geom_point(aes(fill = categ),
-						 shape = 21, 
-						 alpha = 0.5) +
-	scale_shape_manual(values = c(21, 22)) +
-	facet_wrap(~type) +
-	geom_smooth(aes(colour = categ, fill = categ), 
-							family = "binomial", method = "gam", colour = "grey10") +
-	geom_point(data = inv, fill = "red", size = 2.5, shape = 21) +
-	my_theme +
-	xlab("degree") +
-	ylab("species frequency\nin control sets") +
-	scale_color_discrete(name = "", labels = c("pollinators", "plants")) +
-	scale_fill_discrete(name = "", labels = c("pollinators", "plants")) +
-	theme(legend.position = "right", strip.background = element_blank())
+Beyond conservation objectives, tools from control theory should also provide general insights for commmunity ecology.
+An application of control theory to ecological networks explicitly takes into account the extent to which changes in the abbundances of one species may ripple to the community [@Cornelius2013].
+Therefore, it can provide an indication of which species are important from a dynamic perspective---key, as these species underpin informed attempts to alter (or maintain) the ecosystem state. 
+For instance, it has been previously used to highlight the disproportionate influence that humans have on marine food-webs [@Isbell2013].
+Nevertheless control theory has not been widely adopted in an ecological context, perhaps because the tools necessary to account for variation on the strength of interspecific effects, which are characteristic of ecological networks, are not there yet.
 
-p3 <- imp %>%
-	ggplot(aes(x = nestedcontribution, y = f_f)) +
-	geom_point(aes(fill = categ),
-						 shape = 21, 
-						 alpha = 0.5) +
-	scale_shape_manual(values = c(21, 22)) +
-	facet_wrap(~type) +
-	geom_smooth(aes(colour = categ, fill = categ), 
-							family = "binomial", method = "gam", colour = "grey10") +
-	geom_point(data = inv, fill = "red", size = 2.5, shape = 21) +
-	my_theme +
-	xlab("contribution to nestedness") +
-	ylab("species frequency\nin control sets") +
-	scale_color_discrete(name = "", labels = c("pollinators", "plants")) +
-	scale_fill_discrete(name = "", labels = c("pollinators", "plants")) +
-	theme(legend.position = "right", strip.background = element_blank())
+Here, we expand previous theory of the control of complex systems to an ecological context.
+We then use a set of ten paired invaded and uninvaded plant-pollinator communities to investigate the link between network structure and our ability to manage them. 
+Specifically we ask two key questions framed in the context of a plant invasion.
+First, we quantify the manageability of pollination communities. 
+Second, we ask whether some species are more important than others at driving the population dynamics of the community and which factors determine this importance.
+We focus on this particular application for a variety of reasons. 
+First, biotic invasions are known to produce tractable changes in the structure of ecological networks, and these changes can be particularly pronounced in mutualistic networks between plants and pollinators where biotic invasions have been shown to modify the strength of species interactions and the degree of network nestedness and connectivity [@Olesen2002; @Aizen2008; @Bartomeus2008; @Vila2009; @Traveset2013].
+Second, plant-pollinator networks provide an ideal framework to answer these questions. 
+On one hand, community networks that quantify relative levels of interaction are readily available. 
+On the other, the bipartite nature of pollination networks makes it is possible to simplify assumptions of how these interactions translate into interspecific effects.
 
-grid.arrange(p1, p2, p3, ncol = 1)
-```
+## Discussion
+
+Our results reveal that the structural differences associated to biotic invasions are reflected in a potential decrease in our ability to alter the state of the community. 
+Furthermore invasive mutualists are driver species in the communities they invade.
+As driver species, they occupy a dominant role in which changes on their abbundance have the potential to cascade trough the community and in turn affect the abbundances of several other species in the community.
+
+At a community level, we demonstrate that the manageability of mutualistic networks is governed by the asymmetric nature of mutual dependencies---which constitute the foundations of the structure and stability of mutualistic networks [@Memmott2004; @Vazquez2004; @Bascompte2006; @Lever2014; @Astegiano2015].
+Indeed, our empirical networks exhibit markedly lower levels of manageability compared to randomisations in which the visitation network was unchanged but where the observed patterns of dependence were broken.
+However, consistent with previous results [@Liu2011], we show that the manageability of empirical networks was indistinguishable from that of networks with a random structure (in terms of modularity and nestedness for example) that maintained the degree or strength of each species in the community.
+Therefore, the asymmetries at the species level (specialization-generalization asymmetries) and the link level (interaction's dependence asymmetries) appear to be sufficiently constrained by the distribution of species degree and strength [@Melian2002].
+This strong relationship between the asymmetric dependences and manageability might explain why invasive species reduce the manageability of their communities. 
+Invasive species have been previously found to excarcebate the assymetries in the network and presumably increasse the stability of thir community [@Aizen2008; @Bartomeus2008; @Henriksson2016].
+
+The changes on the asymmetries found in the invaded networks are also reflected at a species level in a high relative importance of invasive species.
+However we found that invasive plants, are not inherently different to their native counterparts, but are rather governed by the same rules of niche and competition that determine species coexistence [@Stouffer2014].
+Invasive plants, just like any other mutualist, tend to be driver species to the degree to which their interaction partners are collectively more dependent on them than the other way around.
+Although previous studies have found that super-generalists, like invasive species, play a central role in their networks [@Vila2009; @Palacio2016], our results go one step beyond and indicate that dependence strength, rather than generalism or other metrics of centrality, explains best the importance of species for the community dynamics.
+
+Because of their effects on other species in the community, driver species might be natural candidates for management interventions.
+For instance, despite inconsistent outcomes, our results suggest that current restoration approaches that focus on direct eradication of invasive species might indeed be an effective way to modify ecosystem state.
+Nevertheless, our results also indicate that removals must be executed with caution as invaded commmunities tend to be dependent on them and therefore vulnerable to their erradication [@Traveset2013; @Albrecht2014].
+Although useful for identifying conservation priorities, our approach is different to previous attempts to quantify species importance that concentrate on measures of centrality, position, co-extinction or uniqueness [@Jordan2006; @Jordan2009; @Lai2012; @McDonald-Madden2016].
+Instead the concept of driver species is more akin to the original concept of keystone species, which illustrated how changes on the abbundance of a key species in turn affect the abbundances of other members of the community [@Paine1969; @Paine1995].
+However, while the keystone species were traditionally identified by infering the effects of a perturbation on a community's population dynamics [@Mills1993], the driver species concept operates the other way round, and uses the communuty dynamics, underpinned by the interspecific effects, to infer the effects of a perturbation.
+While it is challenging to quantify the dependence of species in an ecological community, an experimental approach to identofy dynamically important species might be even more difficult*add cite*.
+
+Overall, we confirm previous studies that suggested that, in contrast to other types of complex systems, the structure of ecological networks renders them remarkably difficult to control [@Liu2011; @Ruths2014].
+In a hypothetical situation in which the goal were to regulate the abbundances of all species in a pollination community, our results suggest that we would need to directly intervene the abbundances of at least 40-90% of those species.
+Fully controlling an ecological community is out of the question, as designing and implementing the management interventions needed is currently impractical. 
+Nevertheless, the ``manageability'' of an ecological community, which is related to the number of species that would require a directed intervention, can provide a simple, straightforward, and theoretically-informed indication of the degree to which the community is self-regulated and therefore how difficult it might be to modify its state.
+
+In this study, we illustrate how a control-theoretic approach can be adopted when estimating the effect of a major driver of global change on mutualistic communities.
+Note though that it can be easily extended to understand the structural effects of other kind of perturbations and for systems governed by different types of species interactions. 
+Moreover, we see great potential by explicitly integrating control theory with dynamic models of species densities [@Cornelius2013; @Gibson2016]. 
+From an ecological perspective, this integration can provide deeper insights into the relationship between controllability and species coexistence. 
+It can also help identify potential trade-offs between persistence at the species and the community level *add refs*. 
+From a conservation perspective, the combined approach can extend things beyond the identification of ideal targets for intervention to design informed interventions that legitimately achieve restoration goals.
+
+## Theory of community manageability
+
+### Maximum matching
+
+The number of nodes necessary to fully control a complex network can be calculated by counting the number of unmatched nodes in the network's maximum matching [@Liu2011].
+In a directed network, a given matching is a subset of links in which no two links share a common starting node or a common ending node; a node is then matched if it is the ending node of one of the links in the matching and unmatched otherwise (Figure 1a).
+A given matching is then maximum if both *(i)* the number of matched links---known as matching size---is maximal and *(ii)* the sum of the weights of the matched links---known as matching weight---is the largest possible among all possible matchings of that size [@West2001].
+To find the maximum matching, we it is useful to adopt an alternative bipartite representation of the network in which the two levels indicate the outgoing and incoming links to each node (Figure 1b).
+Finding a matching in this alternative representation is equivalent to finding a set of links such that each node on the top level is matched to at most one node on the bottom level, and vice versa [@West2001; @Csardi2006a].
+
+## Acknowledgments
+
+The authors thank Dr.
+Takeuki Uno for the insight provided to find the set of all maximum matching algorithms, and Jason Tylianakis, Bernat Bramon, Matthew Hutchinson, and Marilia Gaiarsa for feedback in early stages of the project.
+EFC acknowledges the support from the University of Canterbury Doctoral Scholarship, the University of Canterbury Meadow Mushrooms Postgraduate Scholarship, a New Zealand International Doctoral Research Scholarship, and a travel grant from the European Space Agency.
+DBS acknowledges the support of a Marsden Fast-Start grant and a Rutherford Discovery Fellowship, administered by the Royal Society of New Zealand.
+
+## References

### 2016-06-12 paper/manuscript.Rmd
format manuscript in ecology letters format, add abstract and final comments from Daniel and Jason

@@
 
-**Running title:** Manageability of mutualistic networks.
+* **Running title:** Manageability of mutualistic networks.
 
-**Keywords:** Network control, ecological networks, species importance, driver species (10 needed).
+* **Keywords:** Network control, ecological networks, species importance, driver species, food webs, pollination, management interventions, food web, asymmetry
 
-**Article type:** Letter.
+* **Article type:** Letter.
 
-**Number of words:** 150 max for Abstract; 5000 max for Main text.
+* **Number of words:** ~ 154 abstract; ~ 4850 main text.
 
-**Number of references:** XX
+* **Number of references:** ~ 63
 
-**Number of displays:** 5 figures; 1 table.
+* **Number of displays:** 5 figures; 1 table.
 
-**Correspondence to:** Daniel Stouffer (daniel.stouffer@canterbury.ac.nz) - +64 21 0825 8815 - School of Biological Sciences, University of Canterbury, 20 Kirkwood Ave, Christchurch 8013, New Zealand
+* **Correspondence to:** Daniel Stouffer (daniel.stouffer@canterbury.ac.nz) - +64 21 0825 8815 - School of Biological Sciences, University of Canterbury, 20 Kirkwood Ave, Christchurch 8013, New Zealand
 
-**Authorship:** DBS conceived the idea, EFC performed all analysis. Both authors contributed to the development of the theoretical framework and the writing of the manuscript.
+* **Authorship:** DBS conceived the idea, EFC performed all analysis. EFC, KLW and DBS contributed to the development of the theoretical framework. EFC and DBS wrote the manuscript.
 
-**Data accessibility:** All data used in this manuscript has already been published by @Lopezaraiza-Mikel2007, @Bartomeus2008, and @Ballantyne2015.
-To access the data, authors should refer to the original sources.
+* **Data accessibility:** All data used in this manuscript has already been published by @Lopezaraiza-Mikel2007, @Bartomeus2008, and @Ballantyne2015.
+The reader should refer to the original sources to access the data.
 
@@
 
-150 words
+Biotic invasions can severely disrupt ecological communities. 
+However, it is unknown how this disruption, underpinned by changes on ecosystem dynamics, affects our ability to manage ecological communities. 
+Here, we expand current theory on the control of complex systems to compare the theoretical manageability of ten paired invaded and uninvaded plant-pollinator communities and identify the driver species within them—those most important to manage in order to maximise the persistence of the community because of their disproportionate potential to affect the abundances of many other species.
+We found that pollination networks in which an invasive primary producer was present, had substantially lower levels of manageability than their uninvaded counterparts. 
+In addition, invasive plants were found to be driver species in every single one of the communities they occupy. 
+The dominant position of driver species is underpinned by a high asymmetry on the dependence of their interaction partners and not degree or other metrics of centrality.
 
@@
 Within community ecology, a complex systems approach has led to the development of a rich suite of analytical and simulation tools with which to understand, for example, the role of species when embedded in an intricate network of interactions [@Pascual2005; @Bascompte2009; @Stouffer2012].
-The inherent complexity of nature, however, has hindered---or at least greatly complicated---our ability to find management solutions to the many problems ecological communities face. 
+The inherent complexity of nature, however, has hindered—or at least greatly complicated—our ability to find management solutions to the many problems ecological communities face. 
 To overcome this obstacle, we require a framework that allow us to explain, predict, and manage ecological communities, particularly when they are faced with perturbations [@Sole2001; @Green2005].
@@
 
-Among the various possibilities, control theory is a strong candidate as it is designed to deal with determining and supervising the behavior of general dynamical systems, and is well equiped to deal with the many feedbacks presents in ecological communities [@Liu2015].
-What is more, existing research in the field has established a strong link between the structure of complex networks and their controlability, demonstrating that it is in principle possible to alter a whole ecological community's composition by modifying the abundances of only a few species [@Liu2011; @Cornelius2013; @Ruths2014].
-However the link between the structure of complex networks and our ability to manage and conserve them is still ambiguous [@Tylianakis2010].
-For instance, biotic invasions, as a major driver of global change, can induce dramatic changes on the patterns of interactions that determine the structure of ecological networks [@Baxter2004; @Tylianakis2008; @Ehrenfeld2010a].
+Among the various possibilities, control theory appear to be a strong candidate as it is designed to deal with determining and supervising the behavior of general dynamical systems, and is well equipped to deal with the many feedbacks presents in ecological communities [@Liu2015].
+Existing research in the field has established a strong link between the structure of complex networks and their controllability, while demonstrating that it is in principle possible to alter a whole ecological community's composition by modifying the abundances of only a few species [@Liu2011; @Cornelius2013; @Ruths2014].
+Applications of control theory to ecological networks can also explicitly take into account the extent to which changes in the abundances of one species may ripple to the community [@Cornelius2013].
+Therefore, they can provide an indication of which species are most relevant
+from a dynamic perspective, a particularly important feature given that these
+species underpin informed attempts to alter (or maintain) the ecosystem state.
+
+Despite these advances, the link between the structure of complex networks and our ability to manage and conserve them is still ambiguous [@Tylianakis2010].
+To complicate things further, biotic invasions—a major driver of global change—can themselves induce dramatic changes on the patterns of interactions that determine the structure of ecological networks [@Baxter2004; @Tylianakis2008; @Ehrenfeld2010a].
 The difficulty of returning invaded communities to their predisturbance state is apparent based on the limited success of restoration projects [@Suding2004; @Rodewald2015; @Smith2016]. 
 Although it therefore presents a double challenge, understanding how differences in network structure before and after the invasion impact our ability to manage them is a critical first step towards a fully informed recovery.
-
-Beyond conservation objectives, tools from control theory should also provide general insights for commmunity ecology.
-An application of control theory to ecological networks explicitly takes into account the extent to which changes in the abbundances of one species may ripple to the community [@Cornelius2013].
-Therefore, it can provide an indication of which species are important from a dynamic perspective---key, as these species underpin informed attempts to alter (or maintain) the ecosystem state. 
-For instance, it has been previously used to highlight the disproportionate influence that humans have on marine food-webs [@Isbell2013].
-Nevertheless control theory has not been widely adopted in an ecological context, perhaps because the tools necessary to account for variation on the strength of interspecific effects, which are characteristic of ecological networks, are not there yet.
+Though they could seem a natural pairing, a control-theoretic perspective has not been widely adopted in a invasion context, perhaps because of a lack of appropriate methodological tools that can account for observed variation on the strength of interspecific effects that are characteristic of ecological networks [@Liu2011; @Isbell2013].
 
@@
 Specifically we ask two key questions framed in the context of a plant invasion.
-First, we quantify the manageability of pollination communities. 
-Second, we ask whether some species are more important than others at driving the population dynamics of the community and which factors determine this importance.
+First, we ask wether invaded networks have lower levels of manageability than their uninvaded counterparts, this is, whether they require more species to be managed to achieve the same level of control.
+Second, we ask whether some species are more important than others at driving the population dynamics of the community and which factors determine this importance; we aim to determine which species are most imortant to manage in order to maximise the persistence of the remainder of the community.
 We focus on this particular application for a variety of reasons. 
@@
 On one hand, community networks that quantify relative levels of interaction are readily available. 
-On the other, the bipartite nature of pollination networks makes it is possible to simplify assumptions of how these interactions translate into interspecific effects.
+On the other, the bipartite nature of pollination networks makes it possible to simplify assumptions of how these interactions translate into interspecific effects.
+
+## Theoretical framework
+
+### Manageability
+
+The number of nodes necessary to fully control a complex network can be calculated by counting the number of unmatched nodes in the network's maximum matching [@Liu2011]. 
+In a directed network, a given matching is a subset of links in which no two links share a common starting node or a common ending node; a node is then matched if it is the ending node of one of the links in the matching and unmatched otherwise (Figure 1a).
+A given matching is then maximum if both *(i)* the number of matched links—known as matching size—is maximal and *(ii)* the sum of the weights of the matched links—known as matching weight—is the largest possible among all possible matchings of that size [@West2001].
+To find the maximum matching, it is useful to adopt an alternative bipartite representation of the network in which the two levels indicate the outgoing and incoming links to each node (Figure 1b). 
+Finding a matching in this alternative representation is equivalent to finding a set of links such that each node on the top level is matched to at most one node on the bottom level, and vice versa [@West2001; @Csardi2006a].
+
+```{r fig_explain-mm, message=FALSE, warning=FALSE, include=FALSE}
+
+sp_names <- c("a[1]", "a[2]", "a[3]", "p[1]", "p[2]")
+
+adj_matrix <- c(0,0,0,1,0,
+								0,0,0,1,1,
+								0,0,0,0,0,
+								0,0,1,0,0,
+								0,0,1,0,0) %>%
+	matrix(nrow = 5, byrow = T) %>%
+	`rownames<-`(sp_names) %>%
+	`colnames<-`(sp_names)
+
+net <- adj_matrix %>% 
+	igraph::graph_from_adjacency_matrix(mode = "directed") 
+igraph::V(net)$type <- c(F, F, F, T, T)
+igraph::E(net)$weight <- 1
+
+layoutCoordinates <- cbind(c(0,1,2,0.5,1.5), 
+													 c(1,1,1,0,0)) %>%
+	`colnames<-`(c("x", "y"))
+
+adj_list <- adj_matrix %>% 
+	reshape2::melt() %>% 
+	dplyr::filter(value > 0)
+
+# Generate an edge path for each pair of connected nodes
+n <- 17
+allEdges <- lapply(1:nrow(adj_list), edgeMaker, len = n, curved = FALSE)
+allEdges <- do.call(rbind, allEdges) %>%
+	dplyr::filter(Sequence != n) %>%
+	dplyr::mutate(Group = factor(Group),
+				 type = Group)
+
+new_lev <- c("m", "u", "m", "m", "u")
+levels(allEdges$type) <- new_lev
+
+nodes <- data.frame(layoutCoordinates) %>%
+	dplyr::mutate(spe = sp_names,
+								spe_c = c("m", "m", "u", "m", "u"), 
+								pos = rep(c(0.3, -0.3), c(3,2)))
+
+p1 <- ggplot(allEdges) +  # Pretty simple plot code
+	geom_path(aes(x = x, y = y, group = Group, colour = type, size = type), 
+						arrow = arrow(type = "closed", angle = 15, length = grid::unit(0.1, "inches"))) + # and taper
+	geom_point(data = nodes,  # Add nodes
+						 aes(x = x, y = y , fill = spe_c), size = 5, pch = 21,
+						 colour = "black") + 
+	geom_text(data = nodes, aes(x = x, y = y + pos, label = spe), size = 3, parse = T, family = "Times") +
+	scale_fill_manual(values = c("#636363", "white")) + 
+	scale_colour_manual(values = c("#636363", "#bdbdbd")) +
+	my_theme + xlab("") + ylab("") + 
+  	xlim(c(-0.09, 2.09)) + ylim(c(-0.48, 1.48)) +
+ theme(plot.margin=unit(c(4,4,-4,-4),"mm")) +
+	scale_size_manual(values = c(0.5, 0.5)) +
+  ggtitle("a) directed network")
+
+net <- digraph_bipartite(net)
+adj_matrix <- net %>% igraph::as_adjacency_matrix(sparse = F, type = "upper")
+layoutCoordinates <- cbind(rep(0:4, 2), rep(c(1,0), each = 5)) %>%
+	`colnames<-`(c("x", "y"))
+
+adj_list <- adj_matrix %>% 
+	reshape2::melt() %>% 
+	dplyr::filter(value > 0)
+
+# Generate an edge path for each pair of connected nodes
+n <- 100
+allEdges <- lapply(1:nrow(adj_list), edgeMaker, len = n, curved = FALSE)
+allEdges <- do.call(rbind, allEdges) %>%
+	dplyr::filter(Sequence != n,
+								Sequence != 1) %>%
+	dplyr::mutate(Group = factor(Group),
+				 type = Group)
+
+new_lev <- c("m", "m", "u", "m", "u")
+levels(allEdges$type) <- new_lev
+
+nodes <- data.frame(layoutCoordinates) %>%
+	dplyr::mutate(spe = rep(sp_names, 2),
+								spe_l = c(paste0(sp_names, " %->% phantom(0)"), paste0(sp_names, " %<-% phantom(0)")),
+								spe_c = c(c("m", "m", "u", "m", "u"), rep("u",5)), 
+								pos = rep(c(0.3, -0.3), each = 5))
+
+p2 <- ggplot(allEdges) +  # Pretty simple plot code
+	geom_path(aes(x = x, y = y, group = Group, colour = type, size = type)) + # and taper
+	geom_point(data = nodes,  # Add nodes
+						 aes(x = x, y = y, fill = spe_c), size = 5, pch = 21,
+						 colour = "black") + 
+	geom_text(data = nodes, aes(x = x + 0.08, y = y + pos, label = spe_l), parse = T, size = 3, family = "Times") +
+	# coord_flip()  + scale_x_reverse() + scale_y_reverse() +
+	scale_fill_manual(values = c("#636363", "white")) + 
+	scale_colour_manual(values = c("#636363", "#bdbdbd")) +
+	xlim(c(-0.12, 4.12)) + ylim(c(-0.48, 1.48)) +
+	my_theme + xlab("") + ylab("") +
+	scale_size_manual(values = c(0.5, 0.5)) +
+  ggtitle("b) alternative bipartite representation")
+
+pdf("./paper/figures/fig_1.pdf", width = 6.2, height = 1.6, family = "Times", title = "Figure 1", compress = F)
+multiplot(p1, p2, layout = matrix(nrow = 1, c(1,1,1,2,2,2,2,2)))
+dev.off
+```
+
+Given a maximum matching, the link to network controllability has a largely intuitive basis. 
+In control theory, a network is fully controllable when each node has a ``superior'', that is, an input that drives its dynamics. 
+Consequently, each matched nodes can be controlled by the node pointing to it.
+Unmatched nodes, on the other hand, have no superior in the network and must be directly controlled by external inputs [@Liu2011]. 
+In an ecological context, this is what could be referred to as management interventions. 
+Building on this analogy, systems that require a large number of external inputs are more difficult or costly to control. 
+Therefore, the manageability $m$ of a community can be approximated by the proportion of species on which we would need to apply management interventions in order to gain full control of the abundances of *all* species in the ecological community $$m = 1- \frac{n_d}{s},$$ where $m$ ranges between zero and one, $n_d$ is the number of species needed to gain full control and $s$ is the total number of species in the community.
+
+### Relative importance
+
+The manageability of a community $m$ provides an indication of the magnitude of $n_d$ but not the identity of the species that compose this set. 
+This is rather important since maximum matchings are often not unique in a given network and different sets of species of size $n_d$ could potentially be used to control the network [@Liu2011]. 
+Species vary in terms of the frequency with which they are classified as superior nodes (Figure 1), and this frequency provides an indication of their relative importance in driving the state of the community.
+Ecologically, these distinctions are crucial because resources are limited and therefore ecological interventions should be focused on species that might provide the largest impact. 
+Superior nodes drive the dynamics of other species and are therefore important for the controlability of the network because they either require external input or because the are part of the chain that transmit the external imputs to other species; we therefore call *driver species* those that are identified as being a superior node in *all* possible matchings, and hence those most likely to have a disproportionate effect on the abundances of other species in their community.
+
+As previously described, a maximum matching in a weighted network is one whose links have the largest possible total weight among all possible matchings. 
+One way to calculate the species importance, and identify the driver species, would be to consider only maximum matchings. 
+However, empirical interaction strengths are to some extent stochastic and depend on proximate factors such as sampling method and intensity [@Gibson2011]. 
+This means that there are multiple matchings that have maximal size in weighted networks, but are not maximum matchings because their total weight is not maximal. 
+One could therefore instead relax the matching weight requirement and computed all possible matchings in the network that have the same maximal size while allowing for some tolerance regarding the weight.
+To compute all the matchings with maximal size, one can first generate the network's line graph—another representation in which nodes are the links of the original network and links represent common ending points [@West2001]—followed by calculation of the complement of this line graph.
+This latter step generates a graph in which nodes are connected if and only if they are not connected in the line graph.
+All possible matchings of maximal size can be found by enumerating all cliques (subgraphs in which all nodes are fully connected to each other) of maximum size [@Csardi2006a; @Gutin2013].
+
+## Methods
+
+In the last section, we outlined the theoretical and computational underpinnings of our approach. 
+Now we illustrate its empirical application using ten pairs of plant-pollinator communities for which we explored their manageability and the relative importance of their constituent species. 
+The networks were constructed from previously published visitation data collected from pollination communities in Bristol, UK [@Lopezaraiza-Mikel2007] and in Cap de Creus National Park, Spain [@Bartomeus2008].
+Notably, each network pair was composed of a community invaded by a plant and a community ''free'' of the invasive species (Table S1). 
+In the four British uninvaded communities, the non-invaded plots were obtained by experimentally removing all the flowers of the invasive species *Impatients grandulifera*. 
+In contrast, the Spanish uninvaded communities were obtained from plots that had not yet been colonised by either of the invasive species *Carpobrotus affine acinaciformis* or *Opuntia stricta*. 
+The structure of all networks was determined using visitation frequency which has been shown to be an appropriate surrogate for interspecific effects in pollination networks [@Vazquez2005; @Bascompte2006].
+To examine whether this decision would influence our results, we also evaluated the effect of using pollinator efficiency or importance as alternative measures of species interactions in a different dataset [@NeEman2010; @Ballantyne2015], and we found quantitatively similar results for all of these options (see Supplementary Information).
+
+### Community manageability
+
+Given the different networks, we began by quantifying their manageability.
+To do so, we calculated the maximum matching of the corresponding pollination network, and estimated the minimum proportion of species that need directed interventions to fully control the species abundances in the community.
+To simplify the analysis, if a network had more than one component (two species are in different components if there exists no path between them), note that we only analysed the largest.
+Smaller components, were found in eleven out of the twenty studied networks and were ussually composed by just one plant and one pollinator.
+
+#### Weighting & directing links
+
+Recall that the aforementioned maximum matching algorithm requires a directed network in which a link between species $i$ and $j$ pointing to species $j$ indicates that the abundance of $j$ can be affected by the abundance of $i$.
+This implies that we need first to identify a directionality for the links between species that in consistent with the dynamics of the community. 
+In some ecological networks, establishing the directionality is relatively straightforward, for example when links represent biomass transfer or energy flow. 
+Interspecific effects in pollination networks, however, are not strictly directed since the benefit is mutual between interacting species. 
+Nevertheless, the relative extent to which a given pair of interacting species affect each other can be quantified by the magnitude of the mutual dependence [@Bascompte2006]. 
+The dependency of plant $i$ on pollinator $j$, $d_{ij}$, is the proportion of the visits coming from pollinator $j$ compared to all pollinator visits to plant $i$. 
+Likewise, the dependency of pollinator $j$ on plant $i$, $d_{ji}$, is the ratio of the visits by pollinator $j$ to plant $i$ and all visits of pollinator $j$.
+As the dependencies are bidirectional, adopting this assumption generates a weighted bipartite network in which interacting pairs are connected by two directed links (Figure 2b).
+
+Mutual dependencies have previously been shown to be highly asymmetric in natural communities [@Bascompte2006]; in other words, if a plant species is largely dependent on a pollinator species, then that pollinator tends to depend rather weakly on the plant.
+This suggests that it may be possible to relax the assumption of bidirectional dependences and simplify the network further such that interacting species are only connected by one directed link when mutual dependencies are asymmetric (Figure 2c).
+The extent to which a species $i$ affects species $j$ relative to the extent to which species $j$ affects species $i$ can be summarised by the interaction asymmetry given by $$a(i,j) = \frac{\left | d_{ij}-d_{ji} \right |}{max\left ( d_{ij}, d_{ji} \right )}.$$
+Employing an unidrectional interaction asymmetry, as a surrogate of bidirectional mutual dependences, confers an additional advantage for our purposes since it dramatically reduces the number of links in the network.
+This translates into a substantial reduction of the time and memory required for the computation of of all possible maximum matchings in a network, particularly for large networks (see ''relative importance of species'' subsection below).
+
+```{r fig_explain-control-direction, message=FALSE, warning=FALSE, include=FALSE}
+sp_names <- c("a[1]", "a[2]", "a[3]", "p[1]", "p[2]")
+
+adj_matrix <- c(0,0,0,0,0,
+								0,0,0,0,1,
+								0,0,0,0,0,
+								1,1,1,0,0, 
+								0,0,1,0,0) %>%
+	matrix(nrow = 5, byrow = T) %>%
+	`rownames<-`(sp_names) %>%
+	`colnames<-`(sp_names)
+
+net <- adj_matrix %>% 
+	igraph::graph_from_adjacency_matrix(mode = "directed") 
+igraph::V(net)$type <- c(F, F, F, T, T)
+igraph::E(net)$weight <- 1
+
+layoutCoordinates <- cbind(c(0,1,2,0.5,1.5), 
+													 c(1,1,1,0,0)) %>%
+	`colnames<-`(c("x", "y"))
+
+adj_list <- adj_matrix %>% 
+	reshape2::melt() %>% 
+	dplyr::filter(value > 0)
+
+# Generate an edge path for each pair of connected nodes
+n <- 17
+allEdges <- lapply(1:nrow(adj_list), edgeMaker, len = n, curved = FALSE)
+allEdges <- do.call(rbind, allEdges) %>%
+	dplyr::filter(Sequence != n) %>%
+	dplyr::mutate(Group = factor(Group),
+				 type = Group)
+
+new_lev <- c("m", "u", "m", "m", "u")
+levels(allEdges$type) <- new_lev
+
+nodes <- data.frame(layoutCoordinates) %>%
+	dplyr::mutate(spe = sp_names,
+								spe_c = c("m", "m", "u", "m", "u"), 
+								pos = rep(c(0.3, -0.3), c(3,2)))
+
+weights <- allEdges %>%
+  dplyr::filter(Sequence == 12) %>%
+  dplyr::mutate(weight = c(1, 2, 1, 1, 2))
+
+p1 <- ggplot(allEdges) +  # Pretty simple plot code
+	geom_path(aes(x = x, y = y, group = Group, size = type), colour = "#bdbdbd") + # and taper
+	geom_point(data = nodes,  # Add nodes
+						 aes(x = x, y = y ), size = 5, pch = 21,
+						 colour = "black", fill = "white") + 
+	# geom_text(data = nodes, aes(x = x, y = y + pos, label = spe), size = 3, parse = T, family = "Times") +
+  geom_point(data = weights, aes(x = x, y= y), size = 2.5, alpha = 0.25, colour = "white") +
+  geom_text(data = weights, aes(x = x, y= y, label = weight), size = 2.5, family = "Times") +
+	scale_fill_manual(values = c("#636363", "white")) + 
+	scale_colour_manual(values = c("#636363", "#bdbdbd")) +
+	my_theme + xlab("") + ylab("") + 
+  	xlim(c(-0.09, 2.09)) + ylim(c(-0.15, 1.15)) +
+ theme(plot.margin=unit(c(4,4,-4,-4),"mm")) +
+	scale_size_manual(values = c(0.5, 0.5)) +
+  ggtitle("a) visitation frequency")
+
+############################
+sp_names <- c("a[1]", "a[2]", "a[3]", "p[1]", "p[2]")
+
+adj_matrix <- c(0,0,0,1,0,
+								0,0,0,1,1,
+								0,0,0,1,1,
+								1,1,1,0,0,
+								0,1,1,0,0) %>%
+	matrix(nrow = 5, byrow = T) %>%
+	`rownames<-`(sp_names) %>%
+	`colnames<-`(sp_names)
+
+net_exp <- adj_matrix %>% 
+	igraph::graph_from_adjacency_matrix(mode = "directed") 
+igraph::V(net_exp)$type <- c(F, F, F, T, T)
+igraph::E(net_exp)$weight <- 1
+
+layoutCoordinates <- cbind(c(0,1,2,0.5,1.5), 
+													 c(1,1,1,0,0)) %>%
+	`colnames<-`(c("x", "y"))
+
+adj_list <- adj_matrix %>% 
+	reshape2::melt() %>% 
+	dplyr::filter(value > 0)
+
+# Generate an edge path for each pair of connected nodes
+n <- 17
+allEdges <- lapply(1:nrow(adj_list), edgeMaker, len = n, curved = FALSE)
+allEdges <- do.call(rbind, allEdges) %>%
+	dplyr::filter(Sequence != n) %>%
+	dplyr::mutate(Group = factor(Group),
+				 type = Group)
+
+new_lev <- c("m", "u", "m", "u", "u", "u", "m", "u", "u", "m")
+dir <- c("m", "m", "m", "m", "m", "u", "u", "u", "u", "u")
+dir2 <- c("m", "u", "m", "u", "u", "u", "m", "m", "u", "m")
+id <- 1:10
+allEdges %<>% dplyr::mutate(dir = type,
+                            dir2 = dir)
+levels(allEdges$type) <- new_lev
+levels(allEdges$dir) <- dir
+levels(allEdges$dir2) <- dir2
+allEdges %<>% 
+  dplyr::mutate(dir = as.numeric(dir),
+                dir2 = as.numeric(dir2),
+                dir = plyr::mapvalues(dir, c(1,2), c(0.03, -0.03)),
+                dir2 = plyr::mapvalues(dir2, c(1,2), c(0.03, -0.03)))
+
+nodes <- data.frame(layoutCoordinates) %>%
+	dplyr::mutate(spe = sp_names,
+								spe_c = c("u", "m", "m", "m", "m"), 
+								pos = rep(c(0.3, -0.3), c(3,2)))
+
+# ggplot(allEdges) +  # Pretty simple plot code
+# 	geom_path(aes(x = x + dir, y = y + dir2, group = Group, colour = type, size = type), 
+# 						arrow = arrow(type = "closed", angle = 15, length = grid::unit(0.1, "inches")))
+
+weights <- allEdges %>%
+  dplyr::filter(Sequence == 12) %>%
+  dplyr::mutate(weight = c("1", "0.5", "0.5", "0.5", "0.5", "0.25", "0.5", "0.25", "0.66", "0.33"))
+
+p2 <- ggplot(allEdges) +  # Pretty simple plot code
+	geom_path(aes(x = x + dir, y = y + dir2, group = Group, size = type), 
+						arrow = arrow(type = "closed", angle = 15, length = grid::unit(0.1, "inches")), colour = "#bdbdbd") + # and taper
+	geom_point(data = nodes,  # Add nodes
+						 aes(x = x, y = y ), size = 5, pch = 21,
+						 colour = "black", fill = "white") +  
+	# geom_text(data = nodes, aes(x = x, y = y + pos, label = spe), size = 3, parse = T, family = "Times") +
+  geom_point(data = weights, aes(x = x + dir*3, y= y), size = 2.5, alpha = 0.25, colour = "white") +
+  geom_text(data = weights, aes(x = x + dir*3, y= y, label = weight), size = 2.5, family = "Times", parse = T) +
+	scale_fill_manual(values = c("#636363", "white")) + 
+	scale_colour_manual(values = c("#636363", "#bdbdbd")) +
+	my_theme + xlab("") + ylab("") + 
+  xlim(c(-0.09, 2.09)) + ylim(c(-0.15, 1.15)) +
+ theme(plot.margin=unit(c(4,4,-4,-4),"mm")) +
+	scale_size_manual(values = c(0.5, 0.5)) +
+  ggtitle("b) mutual dependence")
+
+####################################
+
+sp_names <- c("a[1]", "a[2]", "a[3]", "p[1]", "p[2]")
+
+adj_matrix <- c(0,0,0,0,0,
+								0,0,0,1,1,
+								0,0,0,0,0,
+								1,1,1,0,0,
+								0,0,1,0,0) %>%
+	matrix(nrow = 5, byrow = T) %>%
+	`rownames<-`(sp_names) %>%
+	`colnames<-`(sp_names)
+
+net <- adj_matrix %>% 
+	igraph::graph_from_adjacency_matrix(mode = "directed") 
+igraph::V(net)$type <- c(F, F, F, T, T)
+igraph::E(net)$weight <- 1
+
+layoutCoordinates <- cbind(c(0,1,2,0.5,1.5), 
+													 c(1,1,1,0,0)) %>%
+	`colnames<-`(c("x", "y"))
+
+adj_list <- adj_matrix %>% 
+	reshape2::melt() %>% 
+	dplyr::filter(value > 0)
+
+# Generate an edge path for each pair of connected nodes
+n <- 17
+allEdges <- lapply(1:nrow(adj_list), edgeMaker, len = n, curved = FALSE)
+allEdges <- do.call(rbind, allEdges) %>%
+	dplyr::filter(Sequence != n) %>%
+	dplyr::mutate(Group = factor(Group),
+				 type = Group)
+
+# new_lev <- c("m", "u", "m", "m", "u")
+# levels(allEdges$type) <- new_lev
+
+nodes <- data.frame(layoutCoordinates) %>%
+	dplyr::mutate(spe = sp_names,
+								# spe_c = c("m", "m", "u", "m", "u"), 
+								pos = rep(c(0.3, -0.3), c(3,2)))
+
+weights <- allEdges %>%
+  dplyr::filter(Sequence == 12) %>%
+  dplyr::mutate(weight = c("0.75", " ", "0.5", "0.33", " ", "0.25"))
+
+p3 <- ggplot(allEdges) +  # Pretty simple plot code
+	geom_path(aes(x = x, y = y, group = Group), size = 0.5,
+						arrow = arrow(type = "closed", angle = 15, length = grid::unit(0.1, "inches")), colour = "#bdbdbd") + # and taper
+	geom_point(data = nodes,  # Add nodes
+						 aes(x = x, y = y ), size = 5, pch = 21,
+						 colour = "black", fill = "white") + 
+	# geom_text(data = nodes, aes(x = x, y = y + pos, label = spe), size = 3, parse = T, family = "Times") +
+   geom_point(data = weights, aes(x = x, y= y), size = 2.5, alpha = 0.25, colour = "white") +
+  geom_text(data = weights, aes(x = x, y= y, label = weight), size = 2.5, family = "Times") +
+	scale_fill_manual(values = c("#636363", "white")) + 
+	scale_colour_manual(values = c("#636363", "#bdbdbd")) +
+	my_theme + xlab("") + ylab("") + 
+  	xlim(c(-0.09, 2.09)) + ylim(c(-0.15, 1.15)) +
+ theme(plot.margin=unit(c(4,4,-4,-4),"mm")) +
+	# scale_size_manual(values = c(0.5, 0.5)) +
+  ggtitle("c) interaction asymmetry")
+
+###########################
+pdf("./paper/figures/fig_2.pdf", width = 6.2, height = 1.5, family = "Times", compress = F, title = "Figure 2")
+multiplot(p1, p2, p3, cols = 3)
+dev.off()
+```
+
+#### Data analysis
+
+Although understanding the variability of manageability across ecological networks is an useful result itself, we also wanted to test whether invasion status has an impact on the observed manageability values.
+We therefore used a set of generalised linear models (with binomial error structure) to investigate the effect of invasion status while also controlling for factors related to species richness, since one might naively expect to see a negative relationship between diversity and manageability [@Menge1995].
+These covariates included the total number of species, plant richness, polinators richness, the ratio of plants to pollinators richness, and the study site (as a two level factor). 
+We assessed competing models by comparing the Akaike Information Criterion corrected for small sample sizes (AICc), and report results for the most parsimonious model.
+
+We next explored whether real networks differ in their architecture from random ones in a way that affects manageability. 
+Previous research indicates a direct link between a network's degree distribution and the number of nodes necessary to fully control it [@Liu2011], but the strength and applicability of this relationship has not been tested for in weighted ecological networks.
+We therefore compared the manageability of the empirical networks to networks generated by three null models which varied in terms of the constraints they impose. 
+The first set of random visitation networks maintain the connectivity of the empirical network, but both degree (its number of interactions) and strength (its total sum of visits) were allowed to vary.
+The second set was generated by maintaining each species' degree while varying the number of visits per species. 
+Finally, the third set of random networks mantained the species' strength while varying their degrees. Randomisations were generated using vegan 2.3-3 [@Oksansen2016]. 
+After generating the randomized networks under these three schemes, we then calculated the mutual dependences and interaction asymmetries of each and determined their manageability using the maximum matching algorithm.
+Finally we calculated the average rank (akin to a p-value) of the manageability of each empirical network compared to the corresponding manageabilites of each set of 999 randomisations.
+
+The dependency asymmetry plays a fundamental role in determining the direction of control in each two-species interaction and therefore has the potential to influence the network manageability results above.
+We therefore performed an additional randomisation in which we kept the structure of network constant but randomised the direction of the interaction asymmetries. 
+That is, we first calculated the asymmetries for each community and then shuffled the direction of the link between each pair of species. 
+Similar as in previous null models, we calculated the average rank of the empirical manageability as compared to those of the randomisations.
+
+### Relative importance of species
+
+Our second key question is related to how species differ in their importance for driving the population dynamics of the community. 
+To quantify this importance in each network, we computed all possible matchings that have the same size as the networks' maximum matching. 
+We then calculated the frequency with which each species is deemed to be a superior node in the set of matchings that had a total weight greater or equal to 0.5 times the weight of the maximum matching.
+We selected this threshold as it provided a high agreement between networks quantified by visitation and pollination efficiency as well as between our weighting/directionality assumptions (mutual dependences and interaction asymmetries); however, the choice of this threshold had a negligible impact on the results (Supplementary Information).
+
+We then asked the question of whether some species-level structural properties can predict our estimates of species importance.
+Although the species importance calculated from mutual dependences contains full information, even in sparse networks, like these studied here, the number of maximal matchings increases exponentially with the number of links and nodes in a network.
+Unfortunately, this means that the large number of links in the most diverse communities rendered the computation unfeasible when we used mutual dependencies. 
+Taking this limitation into account, we compared the relative network manageability obtained when using asymmetries to those found when using mutual dependencies to test if they gave consistent results.
+The comparison was performed for eleven of the twenty networks (those for which the number of matchings was smaller than $4\times 10^{10}$), using a paired Spearman correlation test, a weighted correlation coefficient $r_{w2}$ (which gives more weight to higer ranks; @PintoDaCosta2015-), and a Jaccard similarity of the driver species in both approaches.
+All three approaches identified a high similarity in relative ranks. 
+Consequently, we focused on the results when using the asymmetries rather than mutual dependencies when further investigating the factors that determine species' relative importance since this also allows us to obtain results for all 20 networks.
+
+We used a generalised linear mixed-effects model (GLMM) with binomial error structure with the relative importance as the response variable. 
+As predictors in this model, we included measures of centrality (degree and eigen-centrality), which have been found to be strong predictors of importance in a coextintion context [@Memmott2004]; a measure related to network robustness (contribution to nestedness), as nestedness has been proposed as one of the key properties that promote stability in mutualistic networks [@Saavedra2011; @Thebault2010]; two measures of strength of association and dependence (visitation and dependency strength), as their distribution determines the extent of interspecific effects.
+In addition, we also included guild and invasive status as categorical fixed effects; although the importance of plants and pollinators or invasive and non-invasive species could respond differently to our structural metrics, our dataset did not contain enough variation to include the corresponding interactions terms for these latter two predictors.
+All network metrics were calculated using the R package bipartite 2.06 [@Dormann2008]. 
+We lastly allowed for variation between different communities by including the network identity as a random effect [@Bates2015a]. 
+Candidate models were compared using AICc and the relative importance of the explanatory variables was evaluated using the sum of Akaike weights over candidate models that accounted for 95% of the evidence [@Burnham2003; @Bates2014; @Barton2016].
+Coeficient estimates were avaraged following [@Buckland1997a] while confidence intervals were calculated following [@Lukacs2010].
+
+## Results
+
+### Community manageabiity
+
+```{r n_driver, message = FALSE, warning = FALSE, include = FALSE}
+n_driver <- a_m %>%
+  dplyr::inner_join(meta) %>%
+  dplyr::filter(count == "visitation") %>%
+  dplyr::mutate(n_sp = n_pla + n_pol, 
+                n_dr = n_sp - n_matched,
+                n_dr_p = n_dr / n_sp)
+
+src_bi_w <- n_driver %>%
+  dplyr::filter(type == "z-bi" | type == "weight",
+                study != "ballantyne") %>%
+  dplyr::select(net_name, type, n_dr_p) %>%
+  tidyr::spread(type, n_dr_p) %$%
+  cor.test(weight, `z-bi`, method = "spearman")
+
+n_driver %<>%
+  dplyr::filter(!is.na(inv))
+
+n_driver_wb <- dplyr::filter(n_driver, 
+                             type == "z-bi" | type == "weight")
+
+# Models
+m0 <- glm(cbind(n_dr, n_matched) ~ n_pla * n_pol + study + inv + type,
+          data = n_driver_wb,
+          family = "binomial")
+m_nr <- glm(cbind(n_dr, n_matched) ~ I(n_pla/n_pol) + study + inv + type,
+          data = n_driver_wb,
+          family = "binomial")
+m8 <- glm(cbind(n_dr, n_matched) ~ I(n_pla/n_pol) + inv + type,
+          data = n_driver_wb,
+          family = "binomial")
+m9 <- glm(cbind(n_dr, n_matched) ~ I(n_pla/n_pol) + study + type,
+          data = n_driver_wb,
+          family = "binomial")
+m1 <- glm(cbind(n_dr, n_matched) ~ I(n_pla/n_pol) + type,
+          data = n_driver_wb,
+          family = "binomial")
+m2 <- glm(cbind(n_dr, n_matched) ~ study + type,
+          data = n_driver_wb,
+          family = "binomial")
+m3 <- glm(cbind(n_dr, n_matched) ~ I(n_pla + n_pol) + type,
+          data = n_driver_wb,
+          family = "binomial")
+m4 <- glm(cbind(n_dr, n_matched) ~ n_pla + type,
+          data = n_driver_wb,
+          family = "binomial")
+m5 <- glm(cbind(n_dr, n_matched) ~ n_pol + type,
+          data = n_driver_wb,
+          family = "binomial")
+m6 <- glm(cbind(n_dr, n_matched) ~ inv + type,
+          data = n_driver_wb,
+          family = "binomial")
+m7 <- glm(cbind(n_dr, n_matched) ~ study + inv + type,
+          data = n_driver_wb,
+          family = "binomial")
+```
+
+All of the networks studied here had levels of manageability between `r round(min(1-dplyr::filter(n_driver, type == "z-bi")$n_dr_p), digits = 2)` and `r round(max(1-dplyr::filter(n_driver, type == "z-bi")$n_dr_p), digits = 2)` (mean `r round(mean(1-dplyr::filter(n_driver, type == "z-bi")$n_dr_p), digits = 2)`) when we considered bidirectional links weighted by the mutual dependences.
+This was in strong agreement with the results obtained using the dependence asymmetry in which manageability ranged between `r round(min(1-dplyr::filter(n_driver, type == "weight")$n_dr_p), digits = 2)` and `r round(max(1-dplyr::filter(n_driver, type == "weight")$n_dr_p), digits = 2)` (mean `r round(mean(1-dplyr::filter(n_driver, type == "weight")$n_dr_p), digits = 2)`; Spearman rank correlation `r round(src_bi_w$estimate, digits = 2)`, $p `r fix_small_pvalue(src_bi_w$p.value)`$).
+In addition, we found that invaded communities were significantly more difficult to manage than uninvaded ones even when controlling for potential diversity effects.
+Out of the various covariates we explored—total number of species, plant richness, pollinator richness, and the ratio of plant to pollinator richness—only the ratio of plant to pollinator richness was retained in the final model as determined by the AICc (Figure 3, Table S3).
+
+```{r fig_explaining-n-driver, include = FALSE, warning = FALSE, message = FALSE}
+
+par_res <- as.data.frame(residuals(m8, "partial"))
+names(par_res) <- paste0(make.names(names(par_res)), "_res")
+par_res %<>%
+  dplyr::bind_cols(m8$data) %>%
+  dplyr::mutate(res_res = residuals(m8, "response"), 
+                res_wor = residuals(m8, "working"))
+
+f3 <- par_res %>%
+  ggplot(aes(x = inv, y = inv_res)) +
+  # facet_wrap(~type) +
+  geom_boxplot(size = 0.3,
+               colour = "grey10", outlier.shape = 21, outlier.size = 1) +
+  fer_theme +
+  scale_x_discrete(labels = c("un-invaded", "invaded"), name = "") +
+  ylab("adjusted manageability") +
+  coord_flip() +
+  theme(
+        legend.position = "none",
+				plot.margin = grid::unit(c(2, 1, 2, 0), "mm"), 
+				# panel.grid.minor.x = element_blank(),
+				panel.grid.minor.y = element_blank())
+
+pdf("./paper/figures/fig_3.pdf", height = 1.7, width = 3.245, family = "Times", compress = F, title = "Figure 3")
+f3
+dev.off()
+```
+
+```{r randomisations_z-scores, include = FALSE, warning = FALSE, message = FALSE}
+r <- r_w %>%
+  dplyr::bind_rows(dplyr::mutate(r_d, type = "weight")) %>%
+  dplyr::inner_join(meta) %>%
+  dplyr::filter(study != "ballantyne") %>%
+  dplyr::mutate(n_dr = n_pla + n_pol - n_matched)
+
+# non-parametric
+z_scores <- r$method %>%
+  unique() %>%
+  plyr::ldply(function(x){
+    n_driver %>%
+      dplyr::mutate(type = stringr::str_replace(type, "-", "_")) %>%
+      dplyr::filter(type == "weight" | type == "z_bi") %>%
+      dplyr::mutate(method = x)
+  }) %>%
+  dplyr::bind_rows(r) %>%
+  dplyr::filter(!(type == "z_bi" & method == "r0")) %>%
+  dplyr::group_by(net_name, method, type) %>%
+  dplyr::mutate(z_r = rank(n_dr, na.last = NA),
+                z_r = z_r/n(),
+                z_s = qlogis(z_r),
+                z_s = replace(z_s, (is.infinite(z_s) & z_s > 0) | z_s > qlogis(0.999), qlogis(0.999)),
+                z_s = replace(z_s, is.infinite(z_s) & z_s < 0, qlogis(0.001))) %>%
+  dplyr::filter(is.na(sim))
+```
+
+When exploring the effect of network structure itself, we observed that the manageability of empirical networks was, in general, not significantly different to the manageability of network randomisations that maintained the degree or the strength of individual species (Figure 4).
+However, when comparing the empirical network to less constrained randomisations that only maintained the original connectance but in which species had different degrees and strengths, we found that empirical networks showed a significant tendency to have smaller values of manageability.
+Furthermore, this pattern was even more marked when we maintained the network structure but randomised only the direction of the asymmetries (Figure 4).
+
+```{r fig_randomisations, include = FALSE, warning = FALSE, message = FALSE}
+z_scores_method_order <- c("r0","swsh_both", "quasiswap_count","r00_ind", "r00_samp", "r00_both")
+
+f4 <- z_scores %>%
+  dplyr::group_by() %>%
+  dplyr::mutate(method = factor(method, levels = z_scores_method_order),
+                m_n = as.numeric(method),
+                m_n = replace(m_n, m_n == 3, 3.5)) %>%
+  dplyr::filter(!method %in% c("r00_both", "r00_ind")) %>%
+  ggplot(aes(x = method, y = -1 * z_s)) +
+  geom_rect(aes(xmin = 0.5, xmax = 4.5, ymin = -Inf, ymax = qlogis(0.025)), fill = "#f0f0f0") +
+  geom_rect(aes(xmin = 0.5, xmax = 4.5, ymin = Inf, ymax = qlogis(0.975)), fill = "#f0f0f0") +
+
+  # geom_hline(yintercept = c(-0), linetype = 2, alpha = 0.7, size = 0.25) + 
+  geom_vline(aes(xintercept = 1.5), alpha = 0.6, size = 0.25) +
+   geom_hline(yintercept = 0, size = 0.25, linetype = 2, colour = "grey30") +
+  geom_boxplot(aes(fill = type), size = 0.3,
+               colour = "grey10", outlier.shape = 21, outlier.size = 1) +
+  # geom_point(aes(y = 9, colour = sign <= 0.05), shape = 8, size = 1) +
+  scale_fill_manual(values = c("white", "#bdbdbd")) +
+  scale_x_discrete(
+    labels = rev(c("only maintain\nconnectance", "maintain strength\nrandomise degree", "maintain degree\nrandomise strength", "random\nassymetry")),
+    # breaks = c("r00_samp", "swsh_both", "quasiswap_count", "r0"),
+    expand = c(0,0)) +
+  scale_y_continuous(breaks = qlogis(c(0.001, 0.025, 0.5, 0.975,0.999)), 
+                     labels = plogis(qlogis(c(0.001, 0.025, 0.5, 0.975,0.999)))) + 
+  xlab("") +
+    coord_flip() +
+  ylab("mean rank of empirical manageability") + 
+  fer_theme +
+  theme(
+        legend.position = "none",
+				plot.margin = grid::unit(c(2, 1, 2, 0), "mm"), 
+				# panel.grid.minor.x = element_blank(),
+				panel.grid.minor.y = element_blank())
+
+pdf("./paper/figures/fig_4.pdf", height = 2.7, width = 3.245, family = "Times", compress = FALSE, title = "Figure 4")
+f4
+dev.off()
+```
+
+### Relative importance of species
+
+```{r rel-importance, include = FALSE, warning = FALSE, message = FALSE}
+d_sp <- driver %>%
+  plyr::ldply(function(x) {
+    get_frequencies(x) %>%
+      dplyr::mutate(type = attr(x, "type"),
+                    scaled = attr(x, "scaled"))
+  })
+
+d_sp_bi <- driver_bi %>%
+  get_frequencies() %>%
+      dplyr::mutate(type = "z_bi",
+                    scaled = FALSE)
+
+d_sp <- dplyr::bind_rows(d_sp, d_sp_bi) %>%
+  dplyr::inner_join(meta)
+# d freq is the best proxy seems to be consistent with the invasive species being at the top rank for the bidirectional links
+# d_sp %>%
+#   dplyr::filter(inv, type == "z_bi") %>%
+#   dplyr::group_by(net_name, threshold) %>% 
+#   dplyr::mutate(d_freq_rank = rank(-d_freq, ties.method = "min")) %>%
+#   dplyr::filter(species %in% c("p_4", "p_25"))
+#
+
+correlations <- expand.grid(type = c("asymmetry", "max_dep"),
+            scaled = c(TRUE, FALSE)) %>%
+  plyr::ddply(c("type", "scaled"), function(x){
+    d_sp %>%
+      dplyr::filter(count == "visitation", 
+                    study != "ballantyne") %>% 
+      plyr::ddply(c("net_name", "threshold"), function(y){
+        u <- y %>% 
+          dplyr::filter(type == "z_bi" | 
+                          (type == x$type & scaled == x$scaled)) %>%
+          dplyr::group_by(type) %>%
+          dplyr::mutate(d_freq_rank = rank(-d_reim)) %>%
+          dplyr::select(species, type, d_freq_rank) %>%
+          tidyr::spread(type, d_freq_rank) %>%
+          `class<-`("data.frame")
+
+        if(ncol(u) == 3) {
+          a <- sets::as.set(u[u[, 2] == min(u[, 2]), 1])
+          b <- sets::as.set(u[u[, 3] == min(u[, 3]), 1])
+          c(rw2(u[,2], u[,3]), rw2(rank(-u[,2]), rank(-u[,3])), cor(u[,2], u[,3], method = "spearman"), sets::set_similarity(a, b))
+        } 
+        else c(NA, NA, NA, NA)
+
+      })
+  })
+
+corr_imp <- expand.grid(type = c("asymmetry", "max_dep"),
+            scaled = c(TRUE, FALSE)) %>%
+  plyr::ddply(c("type", "scaled"), function(x){
+    d_sp %>%
+      dplyr::filter(study == "ballantyne") %>% 
+      plyr::ddply(c("threshold"), function(y){
+        u <- y %>% 
+          dplyr::filter((type == "z_bi" & count == "importance") |
+                          (type == x$type & scaled == x$scaled & count == "visitation")) %>%
+          dplyr::group_by(type) %>%
+          dplyr::mutate(d_freq_rank = rank(-d_reim)) %>%
+          dplyr::select(species, type, d_freq_rank) %>%
+          tidyr::spread(type, d_freq_rank) %>%
+          `class<-`("data.frame")
+
+        if(ncol(u) == 3) rw2(u[,2], u[,3])
+        else NA
+
+      })
+  })
+```
+
+We found a strong agreement between the values of relative species' importance in the 11 networks for which we were able to calculate them using both mutual dependencies and asymmetries (Spearman's rank correlation ranged between $\rho = [
+`r round(min(dplyr::filter(correlations, threshold == 0.5, type == "asymmetry", scaled == T)$V3, na.rm = T), digits = 2)`, `r round(max(dplyr::filter(correlations, threshold == 0.5, type == "asymmetry", scaled == T)$V3, na.rm = T), digits = 2)`]$, median $\tilde{\rho} =
+`r round(median(dplyr::filter(correlations, threshold == 0.5, type == "asymmetry", scaled == T)$V3, na.rm = T), digits = 2)`)$. 
+Moreover both approaches identified a highly similar set of driver species (Jaccard similarity $J = [
+`r round(min(dplyr::filter(correlations, threshold == 0.5, type == "asymmetry", scaled == T)$V4, na.rm = T), digits = 2)`, `r round(max(dplyr::filter(correlations, threshold == 0.5, type == "asymmetry", scaled == T)$V4, na.rm = T), digits = 2)`]$, $\tilde{J} =
+`r round(median(dplyr::filter(correlations, threshold == 0.5, type == "asymmetry", scaled == T)$V4, na.rm = T), digits = 2)`)$. 
+Notably, we found that the agreement was stronger for highly ranked species than for lowly ranked species ($\tilde{r_{w2}} = `r round(median(dplyr::filter(correlations, threshold == 0.5, type == "asymmetry", scaled == T)$V1, na.rm = T), digits = 2)`$ versus $\tilde{r_{w2}} = `r round(median(dplyr::filter(correlations, threshold == 0.5, type == "asymmetry", scaled == T)$V2, na.rm = T), digits = 2)`$) when using the weighted rank correlation coefficient $r_{w2}$.
+Given the overall similarities, we concentrated on the relative rankings obtained using asymmetries in the following results.
+
+```{r importance, include = FALSE, warning = FALSE, message = FALSE, results = "hide"}
+glmer.glmulti<-function(formula,data,random="",...){
+  glmer(paste(deparse(formula, width.cutoff = 500),random),data=data,...)
+}
+
+setMethod('getfit', 'glmerMod', function(object, ...) {
+  summ <- coef(summary(object))
+  summ1 <- summ[,1:2,drop=FALSE]
+  ## if (length(dimnames(summ)[[1]])==1) {
+  ##     summ1 <- matrix(summ1, nr=1,
+  ##                     dimnames=list(c("(Intercept)"),
+  ##                     c("Estimate","Std. Error")))
+  ## }
+  cbind(summ1, df=rep(times =10000,length(fixef(object))))
+})
+
+imp <- mod %>% 
+  coef.glmulti(select = 0.95) %>%
+  as.data.frame() %>%
+  dplyr::add_rownames("factor") %>%
+  dplyr::mutate(pare = grepl("(", factor, fixed =T),
+                factor = plyr::mapvalues(factor, 
+                                         c("de", "n", "vi", "eig_cen", 
+                                           "guildpol", "d", "invasiveTRUE"),
+                                         c("dependency strength", 
+                                           "contribution to nestedness",
+                                           "visitation strength",
+                                           "eigen-centrality", 
+                                           "guild (pollinator)", "degree", "invasive sp."))) %>% 
+  dplyr::arrange(-pare, -Importance, -Estimate, factor) %>% 
+  dplyr::select(-pare)
+
+print_table <- . %>%
+  # dplyr::mutate(factor = paste0("$", factor, "$")) %>%
+  magrittr::set_names(c("factor", "est.", "var", "No. mod.", "imp.", "C.I.")) %>% 
+  dplyr::select(-var) %>%
+  kable(format = "latex", align = "c", booktabs = T, digits = 2, escape = F, linesep = "") 
+```
+
+```{r species, include = FALSE, warning = FALSE, message = FALSE}
+data <- mo
+net <- "./data/V2.0/networks" %>%
+	read_networks()
+
+guild <- c("pla", "pol") %>%
+  plyr::ldply(function(y){
+    o <- lapply(net, function(x) igraph::V(x)[igraph::V(x)$type == y]$name) %>%
+      unlist() %>% unique()
+    data.frame(guild = y, species = o)
+  })
+
+invasive_sp <- dplyr::filter(meta, inv) %>%
+  dplyr::mutate(species = plyr::mapvalues(invader, 
+                                          c("car", "op", "imp"),
+                                          c("p_4", "p_25", "Impatiens glandulifera")), 
+                invasive = T) %>%
+  dplyr::select(net_name, species, invasive)
+
+connected_sp <- data %>% dplyr::select(net_name, species) %>% 
+  dplyr::mutate(connected = T)
+
+s_p_s <- s_p %>%
+  dplyr::full_join(invasive_sp) %>%
+  dplyr::mutate(invasive = replace(invasive, is.na(invasive), FALSE)) %>%
+  dplyr::inner_join(guild) %>%
+  dplyr::inner_join(meta) %>%
+  dplyr::filter(study != "ballantyne") %>%
+  dplyr::inner_join(connected_sp)
+
+dd <- data %>% lapply(as.vector) %>% as.data.frame()
+dd <- s_p_s %>%
+  dplyr::select(net_name, species, invasive, connected) %>%
+  dplyr::inner_join(dd) %>%
+  dplyr::mutate(pp = predict.glmulti(mod, select = 0.2, newdata = ., re.form = NA),
+                pp = as.vector(pp),
+                pp = plogis(pp),
+                de2 = de * attr(data$de, "scaled:scale") + attr(data$de, "scaled:center"))
+
+trans <- function(x, orig){
+  x * attr(orig, "scaled:scale") + attr(orig, "scaled:center")
+}
+
+b_trans <- function(x, orig){
+  (x - attr(orig, "scaled:center")) / attr(orig, "scaled:scale")
+}
+
+pred4 <- data.frame(de = rep(b_trans(exp(c(seq(log(trans(min(data$de), data$de)),
+                                log(trans(max(data$de), data$de)),
+                                length = 500))), data$de),3),
+            n = rep(c(-1,0,1), each = 500),
+            vi = rep(c(-1,0,1), each = 500),
+            type = rep(c("exp", "mean", "exp"), each = 500),
+            # vi = seq(min(data$vi), max(data$vi), length.out = 500),
+            eig_cen = mean(data$eig_cen, na.rm = T),
+            d = mean(data$d, na.rm = T),
+            guild = "pla") %>%
+  dplyr::filter(!(n == 2 & vi == -2),
+                !(n == -2 & vi == 2)) %>%
+  dplyr::mutate(q = predict.glmulti(mod,
+                                    select = 2 %>% `class<-`("integer"),
+                                    newdata = .,
+                                    re.form = NA)$averages %>%
+                  as.vector(),
+                p = plogis(q)) %>%
+  dplyr::mutate(de = de * attr(data$de, "scaled:scale") + attr(data$de, "scaled:center"),
+                vi = vi * attr(data$vi, "scaled:scale") + attr(data$vi, "scaled:center"))
+
+```
+
+Invasive species were driver species in every single network they were present, this is, they had the highest relative ranking of species importance. 
+Overall, plants showed significantly higher levels of importance than pollinators (Mann-Whitney-Wilcoxon test, $p = `r fix_small_pvalue(wilcox.test(pp ~ guild, data = dd, alternative = "greater")$p.value, 3)`$).
+However, this difference can largely be explained by the strength of dependency of the species (the sum of the dependencies for a given species). 
+Indeed, when averaging over the set of GLMMs that accounted at least 95\% of the evidence based on AICc, we found that species' strength of dependency is the single most important factor determining the relative importance of species for network control (Table 1, Figure 5).
+In contrast, the number of visits a species makes (or receives) and its contribution to nestedness have only a marginal effect on its relative importance.
+
+```{r fig_species-alt, include = FALSE, warning = FALSE, message = FALSE}
+
+data_pp <- data
+data_pp$pred_ri <- plogis(predict.glmulti(mod, select = as.integer(1), re.form = NA))
+data_pp$de_s <- data$de * attr(data$de, "scaled:scale") + attr(data$de, "scaled:center")
+data_pp <- lapply(data_pp, as.vector) %>% as.data.frame
+
+f5 <- pred4 %>%
+  ggplot() +
+  geom_line(aes(x = de, y = p, linetype = type, colour = type, group = interaction(n, vi)), show.legend = F, size = 0.5) +
+  scale_x_log10(expand = c(0,0)) +
+   geom_point(data = dplyr::arrange(data_pp, invasive), aes(x = de_s, y = pred_ri, fill = invasive, shape = guild, size = invasive), show.legend = F) +
+    scale_shape_manual(values = c(21, 23)) +
+  scale_size_manual(values = c(1,1.5)) +
+  scale_fill_manual(values = c("white","#e41a1c")) + 
+  scale_color_manual(values = c("#525252", "black")) +
+  scale_linetype_manual(values = c(2, 1)) +
+  xlab("dependency strength") +
+  ylab("relative importance") +
+  fer_theme
+
+pdf("./paper/figures/fig_5.pdf", height = 2.2, width = 3.245, family = "Times", compress = F, title = "Figure 5")
+f5
+dev.off()
+```
 
@@
 
-Our results reveal that the structural differences associated to biotic invasions are reflected in a potential decrease in our ability to alter the state of the community. 
-Furthermore invasive mutualists are driver species in the communities they invade.
-As driver species, they occupy a dominant role in which changes on their abbundance have the potential to cascade trough the community and in turn affect the abbundances of several other species in the community.
+Our results reveal that the structural differences associated to biotic invasions are reflected in a potential decrease in our ability to alter the state of the community post invasion. 
+Furthermore invasive mutualists were always driver species in the communities they invade.
+As driver species, they occupy a dominant role in which changes on their abundance have the potential to propagate broadly trough the community and in turn affect the abundances of many other species.
 
-At a community level, we demonstrate that the manageability of mutualistic networks is governed by the asymmetric nature of mutual dependencies---which constitute the foundations of the structure and stability of mutualistic networks [@Memmott2004; @Vazquez2004; @Bascompte2006; @Lever2014; @Astegiano2015].
+At a community level, we demonstrate that the manageability of mutualistic networks is strongly governed by the asymmetric nature of mutual dependencies—which constitute the foundations of the structure and stability of mutualistic networks [@Memmott2004; @Vazquez2004; @Bascompte2006; @Lever2014; @Astegiano2015].
 Indeed, our empirical networks exhibit markedly lower levels of manageability compared to randomisations in which the visitation network was unchanged but where the observed patterns of dependence were broken.
@@
 Therefore, the asymmetries at the species level (specialization-generalization asymmetries) and the link level (interaction's dependence asymmetries) appear to be sufficiently constrained by the distribution of species degree and strength [@Melian2002].
-This strong relationship between the asymmetric dependences and manageability might explain why invasive species reduce the manageability of their communities. 
-Invasive species have been previously found to excarcebate the assymetries in the network and presumably increasse the stability of thir community [@Aizen2008; @Bartomeus2008; @Henriksson2016].
+Generally speaking, this strong relationship between the asymmetric dependences and manageability might explain why invasive species reduce the manageability of their communities. 
+Invasive species have been previously found to exacerbate the asymmetries in the network and presumably increase the stability of their community [@Aizen2008; @Bartomeus2008; @Henriksson2016].
 
-The changes on the asymmetries found in the invaded networks are also reflected at a species level in a high relative importance of invasive species.
-However we found that invasive plants, are not inherently different to their native counterparts, but are rather governed by the same rules of niche and competition that determine species coexistence [@Stouffer2014].
-Invasive plants, just like any other mutualist, tend to be driver species to the degree to which their interaction partners are collectively more dependent on them than the other way around.
-Although previous studies have found that super-generalists, like invasive species, play a central role in their networks [@Vila2009; @Palacio2016], our results go one step beyond and indicate that dependence strength, rather than generalism or other metrics of centrality, explains best the importance of species for the community dynamics.
+The changes on the asymmetries we found in the invaded networks are also reflected at a species level by the high relative importance of invasive species.
+However we found that invasive plants, are not inherently different to their native counterparts [@Stouffer2014].
+Invasive plants, just like any other mutualist in our data set, tend to be driver species to the degree to which their interaction partners are collectively more dependent on them than the other way around.
+Although previous studies have found that super-generalists, like invasive species, play a central role in their networks [@Vila2009; @Palacio2016], our results take this one more and indicate that it is dependence strength, rather than generalism or other metrics of centrality, the factor that best explains how important a species is for it's community dynamics.
 
 Because of their effects on other species in the community, driver species might be natural candidates for management interventions. 
-For instance, despite inconsistent outcomes, our results suggest that current restoration approaches that focus on direct eradication of invasive species might indeed be an effective way to modify ecosystem state.
-Nevertheless, our results also indicate that removals must be executed with caution as invaded commmunities tend to be dependent on them and therefore vulnerable to their erradication [@Traveset2013; @Albrecht2014].
+For instance, despite inconsistent outcomes in practice, our results suggest that current restoration approaches that focus on direct eradication of invasive species might indeed be an effective way to modify ecosystem state.
+Nevertheless, our results also indicate that removals must be executed with caution as invaded communities tend to be highly dependent on invaders and therefore acutely vulnerable to their eradication [@Traveset2013; @Albrecht2014].
 Although useful for identifying conservation priorities, our approach is different to previous attempts to quantify species importance that concentrate on measures of centrality, position, co-extinction or uniqueness [@Jordan2006; @Jordan2009; @Lai2012; @McDonald-Madden2016].
-Instead the concept of driver species is more akin to the original concept of keystone species, which illustrated how changes on the abbundance of a key species in turn affect the abbundances of other members of the community [@Paine1969; @Paine1995].
-However, while the keystone species were traditionally identified by infering the effects of a perturbation on a community's population dynamics [@Mills1993], the driver species concept operates the other way round, and uses the communuty dynamics, underpinned by the interspecific effects, to infer the effects of a perturbation.
-While it is challenging to quantify the dependence of species in an ecological community, an experimental approach to identofy dynamically important species might be even more difficult*add cite*.
+Instead the concept of driver species is more akin to the original concept of keystone species, which illustrated how changes on the abundance of a key species in turn affect the abundances of other members of the community [@Paine1969; @Paine1995].
+However, while keystone species were traditionally identified by inferring the effects of a perturbation on a community's population dynamics [@Mills1993], the driver species concept operates the other way round; namely, it uses the community dynamics, underpinned by the interspecific effects, to infer the effects of a perturbation.
+While it is challenging to quantify the dependence of species in an ecological community, an experimental approach to identify dynamically important species might be even more difficult to implement *[FDO: add ref]*.
 
-Overall, we confirm previous studies that suggested that, in contrast to other types of complex systems, the structure of ecological networks renders them remarkably difficult to control [@Liu2011; @Ruths2014].
-In a hypothetical situation in which the goal were to regulate the abbundances of all species in a pollination community, our results suggest that we would need to directly intervene the abbundances of at least 40-90% of those species.
-Fully controlling an ecological community is out of the question, as designing and implementing the management interventions needed is currently impractical. 
-Nevertheless, the ``manageability'' of an ecological community, which is related to the number of species that would require a directed intervention, can provide a simple, straightforward, and theoretically-informed indication of the degree to which the community is self-regulated and therefore how difficult it might be to modify its state.
+Overall, our investigation confirms the conclusions of previous studies that suggested that, in contrast to other types of complex systems, the structure of ecological networks renders them remarkably difficult to control [@Liu2011; @Ruths2014].
+In a hypothetical situation in which the goal were to regulate the abundances of all species in a pollination community, our results indeed suggest that we would need to directly intervene the abundances of at least 40-90% of those species.
+Fully controlling an ecological community is no doubt an idealistaion, as designing and implementing the management interventions needed is currently impractical. 
+Nevertheless, the ''manageability'' of an ecological community, which is related to the number of species that would require a directed intervention, can provide a simple, straightforward, and theoretically-informed indication of the degree to which the community is self-regulated and therefore how difficult it might be to modify its state in one way or another.
 
-In this study, we illustrate how a control-theoretic approach can be adopted when estimating the effect of a major driver of global change on mutualistic communities.
+In this study, we illustrate how a control-theoretic approach can be adopted when estimating the effect of invasions—a major driver of global change—on mutualistic communities.
 Note though that it can be easily extended to understand the structural effects of other kind of perturbations and for systems governed by different types of species interactions. 
@@
 From an ecological perspective, this integration can provide deeper insights into the relationship between controllability and species coexistence. 
-It can also help identify potential trade-offs between persistence at the species and the community level *add refs*. 
-From a conservation perspective, the combined approach can extend things beyond the identification of ideal targets for intervention to design informed interventions that legitimately achieve restoration goals.
-
-## Theory of community manageability
-
-### Maximum matching
-
-The number of nodes necessary to fully control a complex network can be calculated by counting the number of unmatched nodes in the network's maximum matching [@Liu2011].
-In a directed network, a given matching is a subset of links in which no two links share a common starting node or a common ending node; a node is then matched if it is the ending node of one of the links in the matching and unmatched otherwise (Figure 1a).
-A given matching is then maximum if both *(i)* the number of matched links---known as matching size---is maximal and *(ii)* the sum of the weights of the matched links---known as matching weight---is the largest possible among all possible matchings of that size [@West2001].
-To find the maximum matching, we it is useful to adopt an alternative bipartite representation of the network in which the two levels indicate the outgoing and incoming links to each node (Figure 1b).
-Finding a matching in this alternative representation is equivalent to finding a set of links such that each node on the top level is matched to at most one node on the bottom level, and vice versa [@West2001; @Csardi2006a].
+It can also help identify potential trade-offs between persistence at the species and the community level *[FDO: add ref]*. 
+From a conservation perspective, the combined approach can shift our focus beyond the identification of ideal targets for intervention to design informed interventions that legitimately achieve restoration goals.
 

### 2016-06-12 paper/legends.Rmd
add figure legends

--- 2016-05-16 paper/manuscript.Rnw
@@
-\documentclass[a4paper,10pt]{article}
-\usepackage[margin=22.5mm]{geometry}
+---
+title: 
+csl: ecology-letters.csl
+output: html_document
+bibliography: references.bib
+---
 
-% abstract + title + authors 
-\usepackage{abstract}
-\renewcommand{\abstractnamefont}{\normalfont\bfseries}
-\renewcommand{\abstracttextfont}{\normalfont\small\itshape} 
-\usepackage{titlesec}
-\usepackage{authblk}
-\usepackage{datetime}
-\newdateformat{usvardate}{
-\monthname[\THEMONTH] \ordinal{DAY}, \THEYEAR}
-
-% keywords
-\providecommand{\keywords}[1]{\textbf{\textit{Keywords---}} #1}
-
-% math
-\usepackage{amssymb}
-\usepackage{newtxmath}
-\usepackage{xfrac}
-
-% manuscript looking document
-\usepackage{setspace}
-\usepackage{lineno,xcolor}
-\setlength{\parskip}{0.5em}
-
-% comments
-\usepackage[draft, textsize = scriptsize, color = gray]{todonotes}
-
-% graphics
-\usepackage{graphicx}
-\usepackage{float}
-\usepackage{sidecap}
-\sidecaptionvpos{figure}{t}
-\usepackage[font=small]{caption}
-\usepackage{subfig}
-\usepackage{caption}
-
-% table
-\usepackage{booktabs}
-
-% box
-\usepackage{tcolorbox}
-
-% references & links
-\usepackage[
-backend=bibtex,
-style= authoryear,
-citestyle = authoryear,
-url=false,
-doi=true,
-isbn=false
-]{biblatex}
-\addbibresource{references.bib}
-
-\usepackage{hyperref}
-\hypersetup{
-    colorlinks=true,
-    citecolor=magenta,
-    linkcolor=magenta
-}
-\usepackage{doi}
-\begin{document}
-\renewcommand*{\bibfont}{\small}
-% line numbers
-\linenumbers
-\setlength\linenumbersep{15pt}
-\renewcommand\linenumberfont{\normalfont\footnotesize\sffamily\color{gray}}
-
-\doublespacing
-%\onehalfspacing
-
-% title
-% Article title
-  \title{
-  {\LARGE \textsc{Biotic invasions reduce the manageability of mutualistic networks}}}
-
-% Authors and Affiliations
-  \author{\large E. Fernando Cagua}
-  \author{\large Kate L. Wootton}
-  \author{\large Daniel B. Stouffer}
-  \affil{\normalsize Center of Integrative Ecology, School of Biological Sciences, University of Canterbury}
- \date{}
-
-\maketitle
-
-Alternative title:
-
-\textsc{Network manageability in the context of species invasion}
-
-<<libraries, echo = FALSE, warning = F, message = F>>=
-library(magrittr)
-library(knitr)
-library(ggplot2)
-library(glmulti)
-library(Hmisc)
-library(lme4)
-opts_knit$set (root.dir=normalizePath('../'))
-@
-
-<<auxiliary functions, echo = FALSE, warning = F, message = F>>=
-"./code/V2.0/functions" %>% 
-	list.files(full.names = T) %>%
-	plyr::l_ply(source)
-@
-
-<<plot theme, echo = FALSE, warning = F, message = F>>=
-fer_theme <- theme_bw() +
-	theme(text = element_text(family = "Times"),
-	      title = element_text(size = 7.5, hjust = 0),
-	      legend.title = element_text(size = 9),
-	      legend.text = element_text(size = 8),
-				axis.text = element_text(size = 8),
-				axis.title = element_text(size = 9, hjust = 0.5), 
-				strip.text = element_text(size = 9, hjust = 0), 
-				strip.background = element_blank(),
-				plot.margin = grid::unit(c(5, 0, 2, 0), "mm"))
-@
-
-<<read data and results, echo = FALSE, warning = F, message = F>>=
-net <- "./data/V2.0/networks" %>%
-	read_networks()
-meta <- readr::read_csv("data/ntw_info.csv") %>% dplyr::tbl_df() %>%
-	dplyr::rename(count = method)
-n_matched <- readRDS("./data/V2.0/n_matched.rds")
-a_m <- readRDS("./data/V2.0/n_matched_all_types.rds") 
-r_w <- readRDS("./data/V2.0/random_weights.rds") %>% dplyr::tbl_df() %>%
-  dplyr::rename_("net_name" = ".id")
-r_d <- readRDS("./data/V2.0/random_directions.rds") %>% dplyr::tbl_df() %>%
-  dplyr::rename_("net_name" = ".id")
-s_p <- readRDS("./data/V2.0/species_properties.rds") %>% dplyr::tbl_df()
-# mod <- readRDS("./data/V2.0/species_models.rds")
-driver <- c("./data/V2.0/matching_frequency") %>% 
-  list.files(full.names = T) %>%
-  lapply(list.files, full.names = T) %>% 
-  unlist() %>% 
-  lapply(read_allRDS)
-prop <- expand.grid(c("asymmetry", "max_dep"), 
-                    c("scaled_FALSE", "scaled_TRUE")) %>% plyr::alply(1)
-driver <- mapply(function(x, y){
-  attr(x, "type") <- as.character(y[,1])
-  attr(x, "scaled") <- stringr::str_split(as.character(y[,2]), "_") %>% unlist() %>% extract(2) %>% as.logical()
-  return(x)
-}, driver, prop)
-driver_bi <- "./data/V2.0/matching_frequency_bi" %>% 
-  read_allRDS()
-mod <- readRDS("./data/V2.0/detailed_species_models.rds")
-mo <- readRDS("./data/V2.0/detailed_species_models_data.rds")
-@
-
-\section*{Introduction}
-
-Complex systems, such as ecological communities, are characterised by non-linear relationships in which the whole is greater than the sum of its parts \todo{add refs}.
-This complex systems approach has led to the development of a rich suite of analytical and simulation tools with which to understand the role of species when embedded in an intricate network of interactions\todo{add refs}.
-However, in contrast to other types of complex systems like neural, intra-organizational, or trust neworks, ecological networks do not have a hierarchical or distributed structure but rather tend to be closed systems in which resources recirculate\todo{add ref}.
-As such, ecosystems contain multiple feedbacks that allow them to self-regulate and, therefore, function relatively independent from external stimulation\todo{add ref}.
-This complex propertes have hindered, or at least complicated, our ability to find management solutions to the many problems ecological communities face.
-A framework that allow us to explain, predict, and manage ecological communities, particularly when they are faced with perturbations, needs to be able to account for their complex structure, and the dynamics that determine the state of each species---and the community as a whole.
-Control theory might be a good candidate framework as it is designed to deal with determining and supervising the behavior of a dynamical system and is well equiped to deal with the many feedbacks presents in ecological communities\todo{add ref}.
-
-Research stemming from control theory has established a strong link between the structure of complex networks and their controlability, and that, in principle, it is possible to alter a ecological community's composition by modifying the abundances of only a few species \autocite{Liu2011, Cornelius2013}.
-Based on this work, it has been suggested that the degree distribution of ecological networks makes them inherently difficult to control \autocite{Liu2011, Ruths2014}.
-This theoretical result is in agreement with many examples in which the management and restoration of ecological communities is more challenging than aticipated.
-For instance, biotic invasions, as a major drivers of global change, can induce dramatic changes on the patterns of interactions that determine the structure of ecological networks \autocite{Baxter2004, Tylianakis2008, Ehrenfeld2010a}.
-The difficulties of returning invaded communities to a predisturbance state can be evidenced by the limited amount of success of restoration projects \autocite{Suding2004, Rodewald2015, Smith2016}.
-Although it is a double challenge, understanding how differences in network structure before and after the invasion impact our ability to manage them is a first step towards an informed recovery.
-
-A control theoretical approach not only might provide insight to conservation but also for ecological science: by explicitly taking into account the extent to which changes in the abbundances of one species may ripple trough the community, applying control theory to ecological networks can provide an indication of which species are important from a dynamic perspective, and therefore crucial when attempting to alter (or maintain) the ecosystem state.
-Nevertheless, although it has been prevoiously used to highlight the disproportionate influence that humans have on marine food-webs \autocite{Isbell2013}, control theory has has rarely been aplied in an ecological context.
-One reason might be that the control of complex networks is still a young field and the tools necessary to account for variation on the strength of interspecific effects, which are characteristic of ecological networks, are not there.
-
-Here, we expand previous theory of the control of complex systems and use a set of ten paired invaded and uninvaded plant-pollinator communities to investigate the link between network structure and our ability to manage them.
-We focus on biotic invasions because they can produce tractable changes in the structure of ecological networks.
-These changes can be particularly pronounced in mutualistic networks of plants and pollinators where biotic invasions have been shown to modify the strength of species interactions and the degree of network nestedness and connectivity \autocite{Olesen2002, Aizen2008, Bartomeus2008, Vila2009, Traveset2013}.
-In addition plant-pollinator networks provide an ideal framework to answer these questions.
-On one hand, community networks that quantify relative levels of interaction are readily available.
-On the other, the bipartite nature of pollination networks makes it is possible to simplify assumptions of how these interactions translate into interspecific effects.
-Specifically we ask two key questions framed in the context of a plant invasion.
-First, we quantify the manageability of pollination communities.
-Second, we ask whether some species are more important than others at driving the population dynamics of the community and which factors determine this importance.
-
-\section*{Theory of community manageability}
-
-\subsection*{Maximum matching}
-
-The number of nodes necessary to fully control a complex network can be calculated by counting the number of unmatched nodes in the network's maximum matching \autocite{Liu2011}.
-In a directed network, a given matching is a subset of links in which no two links share a common starting node or a common ending node; a node is then matched if it is the ending node of one of the links in the matching and unmatched otherwise(\autoref{fig:explain_mm}a).
-A given matching is then maximum if both \textit{(i)} the number of matched links---known as matching size---is maximal and \textit{(ii)} the sum of the weights of the matched links---known as matching weight---is the largest possible among all possible matchings of that size \autocite{West2001}.
-To find the maximum matching, we it is useful to adopt an alternative bipartite representation of the network in which the two levels indicate the outgoing and incoming links to each node (\autoref{fig:explain_mm}b).
-Finding a matching in this alternative representation is equivalent to finding a set of links such that each node on the top level is matched to at most one node on the bottom level, and vice versa \autocite{West2001, Csardi2006a}.
-
-\begin{figure}
-\centering
-<<fig explain mm, echo = FALSE, warning = F, message = F, results = "asis", fig.height=1.6, fig.width=6.2>>=
-
-sp_names <- c("a[1]", "a[2]", "a[3]", "p[1]", "p[2]")
-
-adj_matrix <- c(0,0,0,1,0,
-								0,0,0,1,1,
-								0,0,0,0,0,
-								0,0,1,0,0,
-								0,0,1,0,0) %>%
-	matrix(nrow = 5, byrow = T) %>%
-	`rownames<-`(sp_names) %>%
-	`colnames<-`(sp_names)
-
-net <- adj_matrix %>% 
-	igraph::graph_from_adjacency_matrix(mode = "directed") 
-igraph::V(net)$type <- c(F, F, F, T, T)
-igraph::E(net)$weight <- 1
-
-layoutCoordinates <- cbind(c(0,1,2,0.5,1.5), 
-													 c(1,1,1,0,0)) %>%
-	`colnames<-`(c("x", "y"))
-
-adj_list <- adj_matrix %>% 
-	reshape2::melt() %>% 
-	dplyr::filter(value > 0)
-
-# Generate an edge path for each pair of connected nodes
-n <- 17
-allEdges <- lapply(1:nrow(adj_list), edgeMaker, len = n, curved = FALSE)
-allEdges <- do.call(rbind, allEdges) %>%
-	dplyr::filter(Sequence != n) %>%
-	dplyr::mutate(Group = factor(Group),
-				 type = Group)
-
-new_lev <- c("m", "u", "m", "m", "u")
-levels(allEdges$type) <- new_lev
-
-nodes <- data.frame(layoutCoordinates) %>%
-	dplyr::mutate(spe = sp_names,
-								spe_c = c("m", "m", "u", "m", "u"), 
-								pos = rep(c(0.3, -0.3), c(3,2)))
-
-p1 <- ggplot(allEdges) +  # Pretty simple plot code
-	geom_path(aes(x = x, y = y, group = Group, colour = type, size = type), 
-						arrow = arrow(type = "closed", angle = 15, length = grid::unit(0.1, "inches"))) + # and taper
-	geom_point(data = nodes,  # Add nodes
-						 aes(x = x, y = y , fill = spe_c), size = 5, pch = 21,
-						 colour = "black") + 
-	geom_text(data = nodes, aes(x = x, y = y + pos, label = spe), size = 3, parse = T, family = "Times") +
-	scale_fill_manual(values = c("#636363", "white")) + 
-	scale_colour_manual(values = c("#636363", "#bdbdbd")) +
-	my_theme + xlab("") + ylab("") + 
-  	xlim(c(-0.09, 2.09)) + ylim(c(-0.48, 1.48)) +
- theme(plot.margin=unit(c(4,4,-4,-4),"mm")) +
-	scale_size_manual(values = c(0.5, 0.5)) +
-  ggtitle("a) directed network")
-
-net <- digraph_bipartite(net)
-adj_matrix <- net %>% igraph::as_adjacency_matrix(sparse = F, type = "upper")
-layoutCoordinates <- cbind(rep(0:4, 2), rep(c(1,0), each = 5)) %>%
-	`colnames<-`(c("x", "y"))
-
-adj_list <- adj_matrix %>% 
-	reshape2::melt() %>% 
-	dplyr::filter(value > 0)
-
-# Generate an edge path for each pair of connected nodes
-n <- 100
-allEdges <- lapply(1:nrow(adj_list), edgeMaker, len = n, curved = FALSE)
-allEdges <- do.call(rbind, allEdges) %>%
-	dplyr::filter(Sequence != n,
-								Sequence != 1) %>%
-	dplyr::mutate(Group = factor(Group),
-				 type = Group)
-
-new_lev <- c("m", "m", "u", "m", "u")
-levels(allEdges$type) <- new_lev
-
-nodes <- data.frame(layoutCoordinates) %>%
-	dplyr::mutate(spe = rep(sp_names, 2),
-								spe_l = c(paste0(sp_names, " %->% phantom(0)"), paste0(sp_names, " %<-% phantom(0)")),
-								spe_c = c(c("m", "m", "u", "m", "u"), rep("u",5)), 
-								pos = rep(c(0.3, -0.3), each = 5))
-
-p2 <- ggplot(allEdges) +  # Pretty simple plot code
-	geom_path(aes(x = x, y = y, group = Group, colour = type, size = type)) + # and taper
-	geom_point(data = nodes,  # Add nodes
-						 aes(x = x, y = y, fill = spe_c), size = 5, pch = 21,
-						 colour = "black") + 
-	geom_text(data = nodes, aes(x = x + 0.08, y = y + pos, label = spe_l), parse = T, size = 3, family = "Times") +
-	# coord_flip()  + scale_x_reverse() + scale_y_reverse() +
-	scale_fill_manual(values = c("#636363", "white")) + 
-	scale_colour_manual(values = c("#636363", "#bdbdbd")) +
-	xlim(c(-0.12, 4.12)) + ylim(c(-0.48, 1.48)) +
-	my_theme + xlab("") + ylab("") +
-	scale_size_manual(values = c(0.5, 0.5)) +
-  ggtitle("b) alternative bipartite representation")
-
-multiplot(p1, p2, layout = matrix(nrow = 1, c(1,1,1,2,2,2,2,2)))
-@
-\caption{\label{fig:explain_mm} Finding a maximum matching in a complex network.
+**Figure 1:**
+Finding a maximum matching in a complex network. 
 a) We start with a directed network  in which the direction of the link represent the direction of control. 
@@
 In both (a) and (b) we show one of the possible maximum matchings of a network (dark grey links) that defines a set of matched ($p_1$, $p_2$, and $a_3$), unmatched ($a_1$ and $a_2$) and superior nodes ($a_1$, $a_2$, and $p_1$; dark grey circles).
-The minimum number of species neccessary to control this network equates to the number of unmatched nodes $n_d = 2$, which gives a manageability of $m = 0.8$.}
-\end{figure}
+The minimum number of species neccessary to control this network equates to the number of unmatched nodes $n_d = 2$, which gives a manageability of $m = 0.8$.
 
-Given a maximum matching, the link to network controllability has an intuitive basis.
-In control theory, a network is fully controlable when each node has a ``superior'', that is, an input that drives its dynamics.
-Consequently, each matched nodes can be controled by the node pointing to it.
-Unmatched nodes, on the other hand, have no superior in the network and must be directly controlled by external inputs \autocite{Liu2011}.
-In an ecological context, this is what we refer to as management interventions.
-Building on this, systems that require a large number of external inputs are more difficult or costly to control.
-Therefore, the manageability $m$ of a community can be approximated by the proportion of species on which we would need to apply management interventions in order to gain full control of the abundances of \textit{all} species in the ecological community $$m = 1- \frac{n_d}{s},$$ where $m$ ranges between zero and one, $n_d$ is the number of species needed to gain full control and $s$ is the total number of species in the community.
-
-\subsection*{Relative importance}
-
-The manageability of a community $m$ provides an indication of the magnitude of $n_d$ but not the identity of the species that compose this set.
-This is rather important since maximum matchings are often not unique in for a given network and different sets of species of size $n_d$ could potentially be used to control the network \autocite{Liu2011}.
-Species vary in terms of the frequency with which they are classified as superior nodes (\autoref{fig:explain_mm}), and this frequency provides an indication of their relative importance in driving the state of the community.
-Ecologically, these distinctions are crucial because resources are limited and therefore ecological inteventions should be focused on species that might provide the largest impact.
-As superior nodes \autoref{fig:explain_mm} drive the dynamics of other species and are therefore important for the controlability of the network because they either require external input or because the are part of the chain that transmit the external imputs to other species, we therefore call \textit{driver species} those that are identified as being a superior node in all possible matchings, and hence those most likely to have a disproportionate effect on the abundances of other species in their community.
-
-As previously described, a maximum matching in a weighted network is one whose links have the largest possible total weight among all possible matchings.
-One way to calculate the species importance, and identify the driver species, would be to consider only maximum matchings.
-However empirical intraction strengths are to some extent stochastic and depend on proximate factors such as sampling method and intensity \autocite{Rezende2007}.
-This means that in weighted networks there is a number of matchings that have maximal size, but are not maximum matchings because their total weight is not maximal.
-We therefore relaxed the matching weight requirement and computed all possible matchings in the network that have the same maximal size while allowing for some tolerance regarding the weight.
-To compute all the matchings with maximal size, we first generated the network's line graph---another representation in which nodes are the links of the original network and links represent common ending points \autocite{West2001}.
-We then calculated the complement of the line graph: a graph in which nodes are connected if and only if they are not connected in the line graph.
-All possible matchings of maximal size can be found by enumerating all cliques (subgraphs in which every node is linked to every other) of maximum size, which equates to $1-n_d$m in this complement graph \autocite{Csardi2006a, Gutin2013}.
-
-\section*{Methods}
-
-In the last section, we outlined the theoretical and computational underpinings of our approach.
-Now we illustrate its empirical application using ten pairs of plant-pollinator communities for which we explored their manageability and the relative importance of their constituent species.
-The networks were constructed from previously published visitation data collected from pollination communities in Bristol, UK \autocite{Lopezaraiza-Mikel2007} and in Cap de Creus National Park, Spain \autocite{Bartomeus2008}.
-Notably, each network pair was composed of a community invaded by a plant and a community ``free'' of the invasive species (Table S1).
-In the four British uninvaded communities, the non-invaded plots were obtained by experimentally removing all the flowers of the invasive species \textit{Impatients grandulifera}.
-In contrast, the Spanish uninvaded communities were obtained from plots that had not yet been colonised by either of the invasive species \textit{Carpobrotus affine acinaciformis} or \textit{Opuntia stricta}.
-The structure of these networks was determined using visitation frequency which has been shown to be an appropriate surrogate for interspecific effects in pollination networks \autocite{Vazquez2005, Bascompte2006}.
-To examine whether this decision would influence our results, we also evaluated the effect of using pollinator efficiency or importance as alternative measures of species interactions in a different dataset \autocite{NeEman2010, Ballantyne2015}, and we found quantitatively results for all of these options (see Supplementary Information).
-
-\subsection*{Community manageability}
-
-Given the different networks, we started by quantifying their manageability.
-To do so, we calculated the maximum matching of the corresponding pollination network, and estimated the minimum number of species that need directed intervecntions to fully control the species abbundances in the community.
-If a network had more than one component (two species are in different components if there exists no path between them), we only analysed the largest one.
-
-\subsubsection*{Weighting \& directing links}
-
-Recall that the aforementioned maximum matching algorithm requires a directed network in which a link between species $i$ and $j$ pointing to species $j$ indicates that the abundance of $j$ can be affected by the abundance of $i$.
-This implies that we need first to identify a directionality for the links between species that in consistent with the dynamics of the comunity.
-In some ecological networks, establishing a directionality is relatively straightforward, for example when links represent biomass transfer or energy flow.
-Interspecific effects in pollination networks, however, are not strictly directed since the benefit is mutual between interacting species.
-Nevertheless, the relative extent to which a given pair of interacting species affect each other can be quantified by the magnitude of the mutual dependence \autocite{Bascompte2006}.
-The dependency of plant $i$ on pollinator $j$, $d_{ij}$, is the proportion of the visits coming from pollinator $j$ compared to all pollinator visits to plant $i$.
-Likewise, the dependency of pollinator $j$ on plant $i$, $d_{ji}$, is the ratio of the visits by pollinator $j$ to plant $i$ and all visits of pollinator $j$.
-As the dependencies are bidirectional, adopting this assumption generates a weighted bipartite network in which interacting pairs are connected by two directed links (\autoref{fig:explain_cd}b).
-
-Mutual dependencies have been shown to be highly assymetric in natural communities \autocite{Bascompte2006}; in other words, if a plant species is largely dependent on a pollinator species, then that pollinator tends to depend rather weakly on the plant.
-This suggests that it may be possible to relax the assumption of bidirectional dependences and simplify the network further such that interacting species are only connected by one directed link when mutual dependencies are assymetric (\autoref{fig:explain_cd}c).
-The extent to which a species $i$ affects species $j$ relative to the extent to which species $j$ affects species $i$ can be summarised by the interaction asymmetry given by $$a(i,j) = \frac{\left | d_{ij}-d_{ji} \right |}{\textup{max}\left ( d_{ij}, d_{ji} \right )}.$$
-
-Employing an unidrectional interaction asymmetry, as a surrogate of bidirectional mutual dependences, dramatically reduces the number of links in the network, which provides substantial reduction of the time and memory required for the computation of of all posible maximum matchings in a network, particularly for large networks (see ``relative importance of species'' subsection below).
-
-\begin{figure}
-\centering
-<<fig explain control direction, echo = FALSE, warning = F, message = F, results = "asis", fig.height=1.5, fig.width=6.2>>=
-sp_names <- c("a[1]", "a[2]", "a[3]", "p[1]", "p[2]")
-
-adj_matrix <- c(0,0,0,0,0,
-								0,0,0,0,1,
-								0,0,0,0,0,
-								1,1,1,0,0, 
-								0,0,1,0,0) %>%
-	matrix(nrow = 5, byrow = T) %>%
-	`rownames<-`(sp_names) %>%
-	`colnames<-`(sp_names)
-
-net <- adj_matrix %>% 
-	igraph::graph_from_adjacency_matrix(mode = "directed") 
-igraph::V(net)$type <- c(F, F, F, T, T)
-igraph::E(net)$weight <- 1
-
-layoutCoordinates <- cbind(c(0,1,2,0.5,1.5), 
-													 c(1,1,1,0,0)) %>%
-	`colnames<-`(c("x", "y"))
-
-adj_list <- adj_matrix %>% 
-	reshape2::melt() %>% 
-	dplyr::filter(value > 0)
-
-# Generate an edge path for each pair of connected nodes
-n <- 17
-allEdges <- lapply(1:nrow(adj_list), edgeMaker, len = n, curved = FALSE)
-allEdges <- do.call(rbind, allEdges) %>%
-	dplyr::filter(Sequence != n) %>%
-	dplyr::mutate(Group = factor(Group),
-				 type = Group)
-
-new_lev <- c("m", "u", "m", "m", "u")
-levels(allEdges$type) <- new_lev
-
-nodes <- data.frame(layoutCoordinates) %>%
-	dplyr::mutate(spe = sp_names,
-								spe_c = c("m", "m", "u", "m", "u"), 
-								pos = rep(c(0.3, -0.3), c(3,2)))
-
-weights <- allEdges %>%
-  dplyr::filter(Sequence == 12) %>%
-  dplyr::mutate(weight = c(1, 2, 1, 1, 2))
-
-p1 <- ggplot(allEdges) +  # Pretty simple plot code
-	geom_path(aes(x = x, y = y, group = Group, size = type), colour = "#bdbdbd") + # and taper
-	geom_point(data = nodes,  # Add nodes
-						 aes(x = x, y = y ), size = 5, pch = 21,
-						 colour = "black", fill = "white") + 
-	# geom_text(data = nodes, aes(x = x, y = y + pos, label = spe), size = 3, parse = T, family = "Times") +
-  geom_point(data = weights, aes(x = x, y= y), size = 2.5, alpha = 0.25, colour = "white") +
-  geom_text(data = weights, aes(x = x, y= y, label = weight), size = 2.5, family = "Times") +
-	scale_fill_manual(values = c("#636363", "white")) + 
-	scale_colour_manual(values = c("#636363", "#bdbdbd")) +
-	my_theme + xlab("") + ylab("") + 
-  	xlim(c(-0.09, 2.09)) + ylim(c(-0.15, 1.15)) +
- theme(plot.margin=unit(c(4,4,-4,-4),"mm")) +
-	scale_size_manual(values = c(0.5, 0.5)) +
-  ggtitle("a) visitation frequency")
-
-############################
-sp_names <- c("a[1]", "a[2]", "a[3]", "p[1]", "p[2]")
-
-adj_matrix <- c(0,0,0,1,0,
-								0,0,0,1,1,
-								0,0,0,1,1,
-								1,1,1,0,0,
-								0,1,1,0,0) %>%
-	matrix(nrow = 5, byrow = T) %>%
-	`rownames<-`(sp_names) %>%
-	`colnames<-`(sp_names)
-
-net_exp <- adj_matrix %>% 
-	igraph::graph_from_adjacency_matrix(mode = "directed") 
-igraph::V(net_exp)$type <- c(F, F, F, T, T)
-igraph::E(net_exp)$weight <- 1
-
-layoutCoordinates <- cbind(c(0,1,2,0.5,1.5), 
-													 c(1,1,1,0,0)) %>%
-	`colnames<-`(c("x", "y"))
-
-adj_list <- adj_matrix %>% 
-	reshape2::melt() %>% 
-	dplyr::filter(value > 0)
-
-# Generate an edge path for each pair of connected nodes
-n <- 17
-allEdges <- lapply(1:nrow(adj_list), edgeMaker, len = n, curved = FALSE)
-allEdges <- do.call(rbind, allEdges) %>%
-	dplyr::filter(Sequence != n) %>%
-	dplyr::mutate(Group = factor(Group),
-				 type = Group)
-
-new_lev <- c("m", "u", "m", "u", "u", "u", "m", "u", "u", "m")
-dir <- c("m", "m", "m", "m", "m", "u", "u", "u", "u", "u")
-dir2 <- c("m", "u", "m", "u", "u", "u", "m", "m", "u", "m")
-id <- 1:10
-allEdges %<>% dplyr::mutate(dir = type,
-                            dir2 = dir)
-levels(allEdges$type) <- new_lev
-levels(allEdges$dir) <- dir
-levels(allEdges$dir2) <- dir2
-allEdges %<>% 
-  dplyr::mutate(dir = as.numeric(dir),
-                dir2 = as.numeric(dir2),
-                dir = plyr::mapvalues(dir, c(1,2), c(0.03, -0.03)),
-                dir2 = plyr::mapvalues(dir2, c(1,2), c(0.03, -0.03)))
-
-nodes <- data.frame(layoutCoordinates) %>%
-	dplyr::mutate(spe = sp_names,
-								spe_c = c("u", "m", "m", "m", "m"), 
-								pos = rep(c(0.3, -0.3), c(3,2)))
-
-# ggplot(allEdges) +  # Pretty simple plot code
-# 	geom_path(aes(x = x + dir, y = y + dir2, group = Group, colour = type, size = type), 
-# 						arrow = arrow(type = "closed", angle = 15, length = grid::unit(0.1, "inches")))
-
-weights <- allEdges %>%
-  dplyr::filter(Sequence == 12) %>%
-  dplyr::mutate(weight = c("1", "0.5", "0.5", "0.5", "0.5", "0.25", "0.5", "0.25", "0.66", "0.33"))
-
-p2 <- ggplot(allEdges) +  # Pretty simple plot code
-	geom_path(aes(x = x + dir, y = y + dir2, group = Group, size = type), 
-						arrow = arrow(type = "closed", angle = 15, length = grid::unit(0.1, "inches")), colour = "#bdbdbd") + # and taper
-	geom_point(data = nodes,  # Add nodes
-						 aes(x = x, y = y ), size = 5, pch = 21,
-						 colour = "black", fill = "white") +  
-	# geom_text(data = nodes, aes(x = x, y = y + pos, label = spe), size = 3, parse = T, family = "Times") +
-  geom_point(data = weights, aes(x = x + dir*3, y= y), size = 2.5, alpha = 0.25, colour = "white") +
-  geom_text(data = weights, aes(x = x + dir*3, y= y, label = weight), size = 2.5, family = "Times", parse = T) +
-	scale_fill_manual(values = c("#636363", "white")) + 
-	scale_colour_manual(values = c("#636363", "#bdbdbd")) +
-	my_theme + xlab("") + ylab("") + 
-  xlim(c(-0.09, 2.09)) + ylim(c(-0.15, 1.15)) +
- theme(plot.margin=unit(c(4,4,-4,-4),"mm")) +
-	scale_size_manual(values = c(0.5, 0.5)) +
-  ggtitle("b) mutual dependence")
-
-####################################
-
-sp_names <- c("a[1]", "a[2]", "a[3]", "p[1]", "p[2]")
-
-adj_matrix <- c(0,0,0,0,0,
-								0,0,0,1,1,
-								0,0,0,0,0,
-								1,1,1,0,0,
-								0,0,1,0,0) %>%
-	matrix(nrow = 5, byrow = T) %>%
-	`rownames<-`(sp_names) %>%
-	`colnames<-`(sp_names)
-
-net <- adj_matrix %>% 
-	igraph::graph_from_adjacency_matrix(mode = "directed") 
-igraph::V(net)$type <- c(F, F, F, T, T)
-igraph::E(net)$weight <- 1
-
-layoutCoordinates <- cbind(c(0,1,2,0.5,1.5), 
-													 c(1,1,1,0,0)) %>%
-	`colnames<-`(c("x", "y"))
-
-adj_list <- adj_matrix %>% 
-	reshape2::melt() %>% 
-	dplyr::filter(value > 0)
-
-# Generate an edge path for each pair of connected nodes
-n <- 17
-allEdges <- lapply(1:nrow(adj_list), edgeMaker, len = n, curved = FALSE)
-allEdges <- do.call(rbind, allEdges) %>%
-	dplyr::filter(Sequence != n) %>%
-	dplyr::mutate(Group = factor(Group),
-				 type = Group)
-
-# new_lev <- c("m", "u", "m", "m", "u")
-# levels(allEdges$type) <- new_lev
-
-nodes <- data.frame(layoutCoordinates) %>%
-	dplyr::mutate(spe = sp_names,
-								# spe_c = c("m", "m", "u", "m", "u"), 
-								pos = rep(c(0.3, -0.3), c(3,2)))
-
-weights <- allEdges %>%
-  dplyr::filter(Sequence == 12) %>%
-  dplyr::mutate(weight = c("0.75", " ", "0.5", "0.33", " ", "0.25"))
-
-p3 <- ggplot(allEdges) +  # Pretty simple plot code
-	geom_path(aes(x = x, y = y, group = Group), size = 0.5,
-						arrow = arrow(type = "closed", angle = 15, length = grid::unit(0.1, "inches")), colour = "#bdbdbd") + # and taper
-	geom_point(data = nodes,  # Add nodes
-						 aes(x = x, y = y ), size = 5, pch = 21,
-						 colour = "black", fill = "white") + 
-	# geom_text(data = nodes, aes(x = x, y = y + pos, label = spe), size = 3, parse = T, family = "Times") +
-   geom_point(data = weights, aes(x = x, y= y), size = 2.5, alpha = 0.25, colour = "white") +
-  geom_text(data = weights, aes(x = x, y= y, label = weight), size = 2.5, family = "Times") +
-	scale_fill_manual(values = c("#636363", "white")) + 
-	scale_colour_manual(values = c("#636363", "#bdbdbd")) +
-	my_theme + xlab("") + ylab("") + 
-  	xlim(c(-0.09, 2.09)) + ylim(c(-0.15, 1.15)) +
- theme(plot.margin=unit(c(4,4,-4,-4),"mm")) +
-	# scale_size_manual(values = c(0.5, 0.5)) +
-  ggtitle("c) interaction asymmetry")
-
-###########################
-
-multiplot(p1, p2, p3, cols = 3)
-
-@
-\caption{\label{fig:explain_cd} Different ways to depict quantitative mutualistic networks.
+**Figure 2:** 
+Different ways to depict quantitative mutualistic networks. 
 a) Pollination networks are usually described by the number of visits between each plant and animal species. 
 b) Given visitation data the mutual dependencies between interacting species depend directly on the relative visitation frequency. 
-c) The relative differences of dependencies---the interaction asymmetry---then provides a mean to simplify the interspecific effects.}
-\end{figure}
+c) The relative differences of dependencies---the interaction asymmetry---then provides a means to simplify the interspecific effects.
 
-\subsubsection*{Data analysis}
-
-Although understanding the variability of manageability across ecological networks is an useful result itself, we also wanted to test whether network attributes, like invasion status, have an impact on the observed manageability values.
-We therefore used a set of generalised linear models (with binomial error structure) to investigate the effect of invasion status while controling for factors related to species richness, since one might naively expect to see a negative relationship between diversity and manageability \autocite{Menge1995}.
-These covariates inlcuded the total number of species, plant richness, polinators richness, the ratio of plants to pollinators richness, and the study site.
-We assessed competing models by comparing the Akaike Information Criterion corrected for small sample sizes (AICc), and report results for the most parsimonious one.
-
-We next explored the extent to which structural properties of the empirical networks influence their manageability.
-Previous research indicates a direct link between a network's degree distribution and the number of nodes necessary to fully control it \autocite{Liu2011}, but the strength and applicability of this relationship has not been tested for in weighted ecological networks.
-We therefore compared the manageability of the empirical networks to networks generated by three null models which varied in terms of the constraints they impose.
-The first set of random visitation networks maintain the connectivity of the empirical network, but both degree (its number of interactions) and strength (its total sum of visits) were allowed to vary.
-A second set set was generated by maintaining each species' degree while varying the number of visits per species.
-Finally a third set of random networks mantained the species' strength while varying their degrees.
-Randomisations were generated using vegan 2.3-3 \autocite{Oksansen2016}.
-After generating the randomized networks under these three schemes, we then calculated the mutual dependences and interaction asymmetries of each and determined their manageability using the maximum matching algorithm.
-Finally we calculated the average rank (akin to a p-value) of the manageability of each empirical network compared to the corresponding manageabilites of each set of 999 randomisations.
-
-The dependency asymmetry plays a fundamental role in determining the direction of control in each two-species interaction and therefore has the potential to influence the network manageability results above.
-We therefore performed an additional randomisation in which we kept the structure of network consistent but randomised the direction of the interaction asymmetries.
-That is, we first calculated the assymetries for each community and then shuffled the direction of the link between species.
-Similar as in previous null models, we calculated the average rank of the empirical manageability as compared to those of the randomisations.
-
-\subsection*{Relative importance of species}
-
-Our second key question is related to how different species differ in their importance for the population dynamics of the community.
-To quantify this importance in each network, we computed all possible matchings that have the same size as the networks' maximum matching.
-We then calculated the frequency with which each species is deemed to be a superior node in the set of matchings that had a total weight greater or equal to 0.5 times the weight of the maximum matching.
-We selected this threshold as it provided a high agreement between networks quantified by visitation and pollination efficiency as well as between our weighting/directionality assumptions (mutual dependences and inetraction asymmetries); however the choice of this threshold had a negligible impact on the results (Supplementary Information).
-
-Even in sparse networks, like these studied here, the number of maximal matchings increasses exponentially with the number of links and nodes in a network.
-Unfortunately, this means that the large number of links in the most diverse communities rendered the computation unfeasible when we used mutual dependecies.
-Taking this limitation into account, we compared the relative network manageability obtained when using asymmetries to those found when using mutual dependencies for eleven of the twenty networks (those for which the number of matchings was smaller than $4\times 10^{10}$).
-The comparison was performed using a paired Spearman correlation test, a weighted correlation coefficient $r_{w2}$ (which gives more weight to higer ranks; \cite{PintoDaCosta2015}), and a Jaccard similarity of the driver species in both approaches.
-All three approaches identified a high similarity in relative ranks.
-Therefore, we focused on the results from the assymetries, rather than mutual dependences, to further investigate the factors that determine species' relative importance since this also allows us to obtain results for all networks.
-
-Given the species importance obtained using the interaction asymmetries, we then asked the question of whether some species-level structural properties can predict the relative importance of species.
-To do so, we used a generalised linear mixed-effects model (GLMM) with a logistic link function to evaluate the relationship between the species' relative importance and a suite of structural measures.
-As predictors in this model, we specifically included measures of centrality (degree and eigen-centrality), which have been found to be strong predictors of importance in a coextintion context \autocite{Memmott2004}; a measure related to network robustness (contribution to nestedness), as nestedness has been proposed as one of the key properties that promote stability in mutualistic networks \autocite{Saavedra2011}; and measures of strength of association and dependence (visitation and dependency strength), as their distribution determine the extent of interspecific effects; and whether the species was invasive or not.
-In addition we also included guild and invasive status as fixed effects; although the importance of plants and pollinators or invasive and non-invasive species could respond differently to our structural metrics, our dataset did not contain enough variation to include the corresponding interactions terms.
-All metrics were calculated using the R package bipartite 2.06 \autocite{Dormann2008}.
-We allowed for variation between different communities by including the network identity as a random effect \autocite{Bates2015a}.
-Candidate models were compared using AICc and the relative importance of the explanatory variables was evaluated using the sum of Akaike weights over candidate models that accounted for 95\% of the evidence \autocite{Burnham2003, Bates2014, Barton2016}.
-
-\section*{Results}
-
-\subsection*{Community manageability}
-
-<<n_driver, echo = FALSE, warning = F, message = F>>=
-# find n_driver
-n_driver <- a_m %>%
-  dplyr::inner_join(meta) %>%
-  dplyr::filter(count == "visitation") %>%
-  dplyr::mutate(n_sp = n_pla + n_pol, 
-                n_dr = n_sp - n_matched,
-                n_dr_p = n_dr / n_sp)
-
-src_bi_w <- n_driver %>%
-  dplyr::filter(type == "z-bi" | type == "weight",
-                study != "ballantyne") %>%
-  dplyr::select(net_name, type, n_dr_p) %>%
-  tidyr::spread(type, n_dr_p) %$%
-  cor.test(weight, `z-bi`, method = "spearman")
-
-# # Wilcoxon signed rank test invasive vs non invasive
-# wt <- n_driver %>%
-#   dplyr::select(site, inv, n_dr_p) %>%
-#   dplyr::filter(!is.na(inv)) %>%
-#   dplyr::mutate(n_dr_p = qlogis(n_dr_p)) %>%
-#   tidyr::spread(inv, n_dr_p) %>%
-#   dplyr::select(-site) %>%
-#   as.matrix()
-n_driver %<>%
-  dplyr::filter(!is.na(inv))
-# wt <-  wilcox.test(x = wt[, 1], y = wt[, 2], paired = T)
-
-n_driver_wb <- dplyr::filter(n_driver, 
-                             type == "z-bi" | type == "weight")
-
-# Models
-m0 <- glm(cbind(n_dr, n_matched) ~ n_pla * n_pol + study + inv + type,
-          data = n_driver_wb,
-          family = "binomial")
-m_nr <- glm(cbind(n_dr, n_matched) ~ I(n_pla/n_pol) + study + inv + type,
-          data = n_driver_wb,
-          family = "binomial")
-m8 <- glm(cbind(n_dr, n_matched) ~ I(n_pla/n_pol) + inv + type,
-          data = n_driver_wb,
-          family = "binomial")
-m9 <- glm(cbind(n_dr, n_matched) ~ I(n_pla/n_pol) + study + type,
-          data = n_driver_wb,
-          family = "binomial")
-m1 <- glm(cbind(n_dr, n_matched) ~ I(n_pla/n_pol) + type,
-          data = n_driver_wb,
-          family = "binomial")
-m2 <- glm(cbind(n_dr, n_matched) ~ study + type,
-          data = n_driver_wb,
-          family = "binomial")
-m3 <- glm(cbind(n_dr, n_matched) ~ I(n_pla + n_pol) + type,
-          data = n_driver_wb,
-          family = "binomial")
-m4 <- glm(cbind(n_dr, n_matched) ~ n_pla + type,
-          data = n_driver_wb,
-          family = "binomial")
-m5 <- glm(cbind(n_dr, n_matched) ~ n_pol + type,
-          data = n_driver_wb,
-          family = "binomial")
-m6 <- glm(cbind(n_dr, n_matched) ~ inv + type,
-          data = n_driver_wb,
-          family = "binomial")
-m7 <- glm(cbind(n_dr, n_matched) ~ study + inv + type,
-          data = n_driver_wb,
-          family = "binomial")
-@
-
-The networks studied here had levels of manageability between \Sexpr{round(min(1-dplyr::filter(n_driver, type == "z-bi")$n_dr_p), digits = 2)} and \Sexpr{round(max(1-dplyr::filter(n_driver, type == "z-bi")$n_dr_p), digits = 2)} (mean \Sexpr{round(mean(1-dplyr::filter(n_driver, type == "z-bi")$n_dr_p), digits = 2)}) when we considered bidirectional links weighted by the mutual dependences.
-This was in strong agreement  to the results obtained using the dependence asymmetry in which manageability ranged between \Sexpr{round(min(1-dplyr::filter(n_driver, type == "weight")$n_dr_p), digits = 2)} and \Sexpr{round(max(1-dplyr::filter(n_driver, type == "weight")$n_dr_p), digits = 2)} (\Sexpr{round(mean(1-dplyr::filter(n_driver, type == "weight")$n_dr_p), digits = 2)}; Spearman rank correlation \Sexpr{round(src_bi_w$estimate, digits = 2)}, $p = \Sexpr{as.numeric(format(src_bi_w$p.value, digits = 2))}$).
-In addition we found that invaded communities were significanlty more difficult to manage than uninvaded ones even when controling for diversity.
-Out of the explored factors---total number of species, plant richness, pollinator richness, and the ratio of plant to pollinator richness---only the ratio of plant to pollinator richness was retained in the final model as determined by the AICc (\autoref{fig:n_driver_explanatory}, Table S3).
-
-\begin{figure}
-\centering
-<<fig explaining n_driver, echo = FALSE, warning = F, message = F, results = "asis", fig.height=1.7, fig.width=3.245>>=
-
-par_res <- as.data.frame(residuals(m8, "partial"))
-names(par_res) <- paste0(make.names(names(par_res)), "_res")
-par_res %<>%
-  dplyr::bind_cols(m8$data) %>%
-  dplyr::mutate(res_res = residuals(m8, "response"), 
-                res_wor = residuals(m8, "working"))
-
-par_res %>%
-  ggplot(aes(x = inv, y = inv_res)) +
-  # facet_wrap(~type) +
-  geom_boxplot(size = 0.3,
-               colour = "grey10", outlier.shape = 21, outlier.size = 1) +
-  fer_theme +
-  scale_x_discrete(labels = c("un-invaded", "invaded"), name = "") +
-  ylab("adjusted manageability") +
-  coord_flip() +
-  theme(
-        legend.position = "none",
-				plot.margin = grid::unit(c(2, 1, 2, 0), "mm"), 
-				# panel.grid.minor.x = element_blank(),
-				panel.grid.minor.y = element_blank())
-
-# p <- predict(m8, type = "response", se.fit = F)
-# 
-# n_driver_wb %>%
-#   dplyr::mutate(fit = predict(m8, type = "response", se.fit = T)$fit,
-#                 se =  predict(m8, type = "response", se.fit = T)$se) %>%
-#   dplyr::filter(type == "z-bi" | type == "weight") %>% 
-#   ggplot(aes(x = n_pla/n_pol, y = 1-n_dr_p)) +
-#   geom_line(aes(y = 1-fit, colour = type, linetype = inv), size = 0.5) + 
-#   geom_point(aes(fill = type, shape = inv), show.legend = T, size = 1.25) +
-#   ylab("manegeability") + 
-#   xlab("plant / pollinator richness") +
-#   scale_fill_manual(values = c("#ffffff", "#bdbdbd"),
-#                       name = "direction of control", 
-#                       labels = c("asymmetry", "mutual dependence")) +
-#   scale_colour_manual(values = c("black", "#bdbdbd"),
-#                       name = "direction of control", 
-#                       labels = c("asymmetry", "mutual dependence")) + 
-#   scale_shape_manual(values = c(21, 23), 
-#                      name = "invasion status", 
-#                      labels = c("invaded", "non invaded")) +
-#   scale_linetype_manual(values = c(1, 12), 
-#                         name = "invasion status", 
-#                         labels = c("invaded", "non invaded")) +
-#   fer_theme +
-#   theme(plot.margin = grid::unit(c(5, 1, 2, 0), "mm"), 
-#         legend.position = "none", 
-#         # legend.title = element_blank(),
-#         legend.key = element_rect(fill = "white", 
-#                                   colour = "white"),
-#         legend.key.size = grid::unit(4, "mm"),
-#         legend.background = element_rect(colour = "black", size = 0.2),
-#         legend.box = "horizontal",
-#         legend.direction = "vertical") 
-@
-\caption{\label{fig:n_driver_explanatory} Invaded communities have lower levels of manageability than uninvaded communities even when controling for the ratio of plant to pollinator richness.
+**Figure 3:**
+Invaded communities have lower levels of manageability than uninvaded communities even when controling for the ratio of plant to pollinator richness. 
 Adjusted manageability corrsponds to the partial working residuals of the invasion status. 
 The box covers the 25th–75th percentiles, the middle line marks the median, and the maximum length of the whiskers is 1.5 times the interquartile range. 
-Points outside this range show up as outliers.}
-\end{figure}
+Points outside this range show up as outliers.
 
-<<randomisations z_scores, echo = FALSE, warning= FALSE, message = FALSE>>=
-r <- r_w %>%
-  dplyr::bind_rows(dplyr::mutate(r_d, type = "weight")) %>%
-  dplyr::inner_join(meta) %>%
-  dplyr::filter(study != "ballantyne") %>%
-  dplyr::mutate(n_dr = n_pla + n_pol - n_matched)
-
-# non-parametric
-z_scores <- r$method %>%
-  unique() %>%
-  plyr::ldply(function(x){
-    n_driver %>%
-      dplyr::mutate(type = stringr::str_replace(type, "-", "_")) %>%
-      dplyr::filter(type == "weight" | type == "z_bi") %>%
-      dplyr::mutate(method = x)
-  }) %>%
-  dplyr::bind_rows(r) %>%
-  dplyr::filter(!(type == "z_bi" & method == "r0")) %>%
-  dplyr::group_by(net_name, method, type) %>%
-  dplyr::mutate(z_r = rank(n_dr, na.last = NA),
-                z_r = z_r/n(),
-                z_s = qlogis(z_r),
-                z_s = replace(z_s, (is.infinite(z_s) & z_s > 0) | z_s > qlogis(0.999), qlogis(0.999)),
-                z_s = replace(z_s, is.infinite(z_s) & z_s < 0, qlogis(0.001))) %>%
-  dplyr::filter(is.na(sim))
-
-@
-
-The manageability of empirical networks was, in general, not significantly different to the manageability of network randomisations that maintained the degree or the strength of individual species (\autoref{fig:randomisations}).
-However, when comparing the empirical network to less constrained randomisations that only maintained the original connectance but in which species had different degrees and strengths, we found that empirical networks tended to have smaller values of manageability.
-This pattern is even more marked when we maintained the network structure but randomised only the direction of the asymmetries (\autoref{fig:randomisations}).
-
-\begin{figure}
-\centering
-<<fig randomisations, echo = FALSE, warning = F, message = F, fig.height=2.7, fig.width=3.245>>=
-
-# z_scores <- r %>%
-#   dplyr::group_by(net_name, method) %>%
-#   dplyr::summarise(mu = mean(n_dr, na.rm = T),
-#                    sigma = sd(n_dr, na.rm = T)) %>%
-#   dplyr::inner_join(n_driver) %>%
-#   dplyr::group_by() %>%
-#   dplyr::mutate(z_s = (n_dr - mu)/sigma)
-
-z_scores_method_order <- c("r0","swsh_both", "quasiswap_count","r00_ind", "r00_samp", "r00_both")
-
-z_scores %>%
-  dplyr::group_by() %>%
-  dplyr::mutate(method = factor(method, levels = z_scores_method_order),
-                m_n = as.numeric(method),
-                m_n = replace(m_n, m_n == 3, 3.5)) %>%
-  dplyr::filter(!method %in% c("r00_both", "r00_ind")) %>%
-  ggplot(aes(x = method, y = -1 * z_s)) +
-  geom_rect(aes(xmin = 0.5, xmax = 4.5, ymin = -Inf, ymax = qlogis(0.025)), fill = "#f0f0f0") +
-  geom_rect(aes(xmin = 0.5, xmax = 4.5, ymin = Inf, ymax = qlogis(0.975)), fill = "#f0f0f0") +
-
-  # geom_hline(yintercept = c(-0), linetype = 2, alpha = 0.7, size = 0.25) + 
-  geom_vline(aes(xintercept = 1.5), alpha = 0.6, size = 0.25) +
-   geom_hline(yintercept = 0, size = 0.25, linetype = 2, colour = "grey30") +
-  geom_boxplot(aes(fill = type), size = 0.3,
-               colour = "grey10", outlier.shape = 21, outlier.size = 1) +
-  # geom_point(aes(y = 9, colour = sign <= 0.05), shape = 8, size = 1) +
-  scale_fill_manual(values = c("white", "#bdbdbd")) +
-  scale_x_discrete(
-    labels = rev(c("only maintain\nconnectance", "maintain strength\nrandomise degree", "maintain degree\nrandomise strength", "random\nassymetry")),
-    # breaks = c("r00_samp", "swsh_both", "quasiswap_count", "r0"),
-    expand = c(0,0)) +
-  scale_y_continuous(breaks = qlogis(c(0.001, 0.025, 0.5, 0.975,0.999)), 
-                     labels = plogis(qlogis(c(0.001, 0.025, 0.5, 0.975,0.999)))) + 
-  xlab("") +
-    coord_flip() +
-  ylab("mean rank of empirical manageability") + 
-  fer_theme +
-  theme(
-        legend.position = "none",
-				plot.margin = grid::unit(c(2, 1, 2, 0), "mm"), 
-				# panel.grid.minor.x = element_blank(),
-				panel.grid.minor.y = element_blank())
-
-@
-\caption{\label{fig:randomisations} The manageability of empirical networks compared to network randomisations.
-For each of four randomisation approaches, we shouw that---akin to a p-value---an scaled mean rank $< 0.025$ or $> 0.975$ (shaded areas in light grey) suggest a significant difference between the empirical network and its randomisations.
+**Figure 4:**
+The manageability of empirical networks compared to network randomisations. 
+For each of four randomisation approaches, we show that---akin to a p-value---an scaled mean rank $< 0.025$ or $> 0.975$ (shaded areas in light grey) suggest a significant difference between the empirical network and its randomisations.
 The empirical manageability is much smaller than those of randomisations in which the direction of assymmetries has been randomised. 
@@
 Dark grey and white boxplots represent manageabilities obtained using mutual dependencies and asymmetries respectively. 
-All boxes are as in \autoref{fig:n_driver_explanatory}.}
-\end{figure}
+All boxes are as in Figure 3.
 
-\subsection*{Relative importance of species}
+**Figure 5:**
+Dependency strength is the single most important factor explaining the importance of species for network control. 
+Visitation levels and contribution to nestedness had a significant albeit small effect on the importance (dashed lines correspond to ± one standard deviation on these factors). 
+Invasive species (red) were invariably classified as driver species (those having the maximum importance for network control.
 
-<<rel importance, echo = FALSE, warning = F, message = F>>=
-d_sp <- driver %>%
-  plyr::ldply(function(x) {
-    get_frequencies(x) %>%
-      dplyr::mutate(type = attr(x, "type"),
-                    scaled = attr(x, "scaled"))
-  })
-
-d_sp_bi <- driver_bi %>%
-  get_frequencies() %>%
-      dplyr::mutate(type = "z_bi",
-                    scaled = FALSE)
-
-d_sp <- dplyr::bind_rows(d_sp, d_sp_bi) %>%
-  dplyr::inner_join(meta)
-# d freq is the best proxy seems to be consistent with the invasive species being at the top rank for the bidirectional links
-# d_sp %>%
-#   dplyr::filter(inv, type == "z_bi") %>%
-#   dplyr::group_by(net_name, threshold) %>% 
-#   dplyr::mutate(d_freq_rank = rank(-d_freq, ties.method = "min")) %>%
-#   dplyr::filter(species %in% c("p_4", "p_25"))
-#
-
-correlations <- expand.grid(type = c("asymmetry", "max_dep"),
-            scaled = c(TRUE, FALSE)) %>%
-  plyr::ddply(c("type", "scaled"), function(x){
-    d_sp %>%
-      dplyr::filter(count == "visitation", 
-                    study != "ballantyne") %>% 
-      plyr::ddply(c("net_name", "threshold"), function(y){
-        u <- y %>% 
-          dplyr::filter(type == "z_bi" | 
-                          (type == x$type & scaled == x$scaled)) %>%
-          dplyr::group_by(type) %>%
-          dplyr::mutate(d_freq_rank = rank(-d_reim)) %>%
-          dplyr::select(species, type, d_freq_rank) %>%
-          tidyr::spread(type, d_freq_rank) %>%
-          `class<-`("data.frame")
-
-        if(ncol(u) == 3) {
-          a <- sets::as.set(u[u[, 2] == min(u[, 2]), 1])
-          b <- sets::as.set(u[u[, 3] == min(u[, 3]), 1])
-          c(rw2(u[,2], u[,3]), rw2(rank(-u[,2]), rank(-u[,3])), cor(u[,2], u[,3], method = "spearman"), sets::set_similarity(a, b))
-        } 
-        else c(NA, NA, NA, NA)
-
-      })
-  })
-
-corr_imp <- expand.grid(type = c("asymmetry", "max_dep"),
-            scaled = c(TRUE, FALSE)) %>%
-  plyr::ddply(c("type", "scaled"), function(x){
-    d_sp %>%
-      dplyr::filter(study == "ballantyne") %>% 
-      plyr::ddply(c("threshold"), function(y){
-        u <- y %>% 
-          dplyr::filter((type == "z_bi" & count == "importance") |
-                          (type == x$type & scaled == x$scaled & count == "visitation")) %>%
-          dplyr::group_by(type) %>%
-          dplyr::mutate(d_freq_rank = rank(-d_reim)) %>%
-          dplyr::select(species, type, d_freq_rank) %>%
-          tidyr::spread(type, d_freq_rank) %>%
-          `class<-`("data.frame")
-
-        if(ncol(u) == 3) rw2(u[,2], u[,3])
-        else NA
-
-      })
-  })
-
-# correlations %>%
-#   ggplot(aes(x = threshold, y = V1, colour = interaction(type, scaled))) +
-#   geom_line(aes(linetype = net_name)) +
-#   geom_smooth(se = F)
-
-# 
-# corr_imp %>%
-#   ggplot(aes(x = threshold, y = V1, colour = interaction(type, scaled))) +
-#   geom_line()
-
-# d_sp %>%
-#   dplyr::group_by(net_name, type, scaled) %>%
-#   dplyr::mutate(importance = rank(-d_reim, ties.method = "min"),
-#                 importance = importance / max(importance)) %>%
-#   dplyr::filter(type == "z_bi" |
-#                   (type == "asymmetry" & scaled == F)) %>%
-#   ggplot(aes(x = net_name, y = importance)) +
-#   geom_boxplot(aes(fill = interaction(type, scaled)))
-
-@
-
-We found a strong agreement between relative species' importance in the 11 networks for which we were able to calulate them using both mutual dependencies and asymmetries (Spearman's rank correlation ranged between $\rho = [\Sexpr{round(min(dplyr::filter(correlations, threshold == 0.5, type == "asymmetry", scaled == T)$V3, na.rm = T), digits = 2)}, \Sexpr{round(max(dplyr::filter(correlations, threshold == 0.5, type == "asymmetry", scaled == T)$V3, na.rm = T), digits = 2)}]$, median $\tilde{\rho} = \Sexpr{round(median(dplyr::filter(correlations, threshold == 0.5, type == "asymmetry", scaled == T)$V3, na.rm = T), digits = 2)})$.
-Moreover both approaches identified a highly similar set of driver species (Jaccard similarity $J = [\Sexpr{round(min(dplyr::filter(correlations, threshold == 0.5, type == "asymmetry", scaled == T)$V4, na.rm = T), digits = 2)}, \Sexpr{round(max(dplyr::filter(correlations, threshold == 0.5, type == "asymmetry", scaled == T)$V4, na.rm = T), digits = 2)}]$, $\tilde{J} = \Sexpr{round(median(dplyr::filter(correlations, threshold == 0.5, type == "asymmetry", scaled == T)$V4, na.rm = T), digits = 2)})$.
-Notably we found that the agreement was stronger for highly ranked species than for lowly ranked species ($\tilde{r_{w2}} = \Sexpr{round(median(dplyr::filter(correlations, threshold == 0.5, type == "asymmetry", scaled == T)$V1, na.rm = T), digits = 2)}$ versus $\tilde{r_{w2}} = \Sexpr{round(median(dplyr::filter(correlations, threshold == 0.5, type == "asymmetry", scaled == T)$V2, na.rm = T), digits = 2)}$) when using the weighted rank correlation coefficient $r_{w2}$.
-Given the similarities, we concentrated on the relative rankings obtained using asymmetries in the following results
-
-<<importance, echo = FALSE, warning = F, message = F, results = "hide">>=
-glmer.glmulti<-function(formula,data,random="",...){
-  glmer(paste(deparse(formula, width.cutoff = 500),random),data=data,...)
-}
-
-setMethod('getfit', 'glmerMod', function(object, ...) {
-  summ <- coef(summary(object))
-  summ1 <- summ[,1:2,drop=FALSE]
-  ## if (length(dimnames(summ)[[1]])==1) {
-  ##     summ1 <- matrix(summ1, nr=1,
-  ##                     dimnames=list(c("(Intercept)"),
-  ##                     c("Estimate","Std. Error")))
-  ## }
-  cbind(summ1, df=rep(times =10000,length(fixef(object))))
-})
-
-imp <- mod %>% 
-  coef.glmulti(select = 0.95) %>%
-  as.data.frame() %>%
-  dplyr::add_rownames("factor") %>%
-  dplyr::mutate(pare = grepl("(", factor, fixed =T),
-                factor = plyr::mapvalues(factor, 
-                                         c("de", "n", "vi", "eig_cen", 
-                                           "guildpol", "d", "invasiveTRUE"),
-                                         c("dependency strength", 
-                                           "contribution to nestedness",
-                                           "visitation strength",
-                                           "eigen-centrality", 
-                                           "guild (pollinator)", "degree", "invasive sp."))) %>% 
-  dplyr::arrange(-pare, -Importance, -Estimate, factor) %>% 
-  dplyr::select(-pare)
-
-print_table <- . %>%
-  # dplyr::mutate(factor = paste0("$", factor, "$")) %>%
-  magrittr::set_names(c("factor", "est.", "var", "No. mod.", "imp.", "C.I.")) %>% 
-  dplyr::select(-var) %>%
-  kable(format = "latex", align = "c", booktabs = T, digits = 2, escape = F, linesep = "") 
-@
-
-<<species, echo = FALSE, warning = F, message = F, fig.height=4.4, fig.width=3.1>>=
-data <- mo
-net <- "./data/V2.0/networks" %>%
-	read_networks()
-# pred <- expand.grid(de = c(seq(min(data$de), max(data$de), length = 20000), mean(data$de)),
-#             n = c(seq(min(data$n), max(data$n), length = 2), mean(data$n)),
-#             vi = c(seq(min(data$vi), max(data$vi), length = 2), mean(data$vi)), 
-#             eig_cen = mean(data$eig_cen, na.rm = T), 
-#             guild = "pla") %>%
-#   dplyr::mutate(q = predict.glmulti(mod, 
-#                                     select = 0.95, 
-#                                     newdata = ., 
-#                                     re.form = NA)$averages %>%
-#                   as.vector(), 
-#                 p = plogis(q)) %>%
-#   dplyr::mutate(de = de * attr(data$de, "scaled:scale") + attr(data$de, "scaled:center"),
-#                 vi = vi * attr(data$vi, "scaled:scale") + attr(data$vi, "scaled:center"),
-#                 n = n * attr(data$n, "scaled:scale") + attr(data$n, "scaled:center"))
-#   # dplyr::filter(de == mean(data$de)) %>%
-#   
-# p1 <- pred %>%
-#   dplyr::filter(vi == unique(vi)[3]) %>%
-#   ggplot(aes(x = de, y = p)) +
-#   geom_line(aes(colour = as.factor(n), group = as.factor(n)), size = 1) +
-#   scale_colour_manual(name = "contribution to nestedness",
-#                       labels = c("max.", "mean", "min"),
-#                       values = c("#cccccc", "#969696", "#525252")) +
-#   # scale_x_continuous(expand = c(0,0)) +
-#   scale_y_continuous(limits = c(0,1)) +
-#   scale_x_log10() + 
-#   # xlab("degree") +
-#   # ylab("strength of dependencies") +
-#   stat_contour(colour = "black", size = 0.75) +
-#   fer_theme + theme(panel.grid = element_blank(), legend.position = "top") 
-# 
-# p2 <- pred %>%
-#   dplyr::filter(n == unique(n)[3]) %>%
-#   ggplot(aes(x = de, y = p)) +
-#   geom_line(aes(colour = as.factor(vi), group = as.factor(vi)), size = 1) +
-#   # scale_fill_gradient(name = "relative\nimportance", high = "#f0f0f0", low = "#525252") +
-#   # scale_x_continuous(expand = c(0,0)) +
-#   scale_y_continuous(limits = c(0,1)) +
-#   scale_x_log10() + 
-#   # xlab("degree") +
-#   # ylab("strength of dependencies") +
-#   stat_contour(colour = "black", size = 0.75) +
-#   fer_theme + theme(panel.grid = element_blank(), legend.position = "top")
-#
-
-guild <- c("pla", "pol") %>%
-  plyr::ldply(function(y){
-    o <- lapply(net, function(x) igraph::V(x)[igraph::V(x)$type == y]$name) %>%
-      unlist() %>% unique()
-    data.frame(guild = y, species = o)
-  })
-
-invasive_sp <- dplyr::filter(meta, inv) %>%
-  dplyr::mutate(species = plyr::mapvalues(invader, 
-                                          c("car", "op", "imp"),
-                                          c("p_4", "p_25", "Impatiens glandulifera")), 
-                invasive = T) %>%
-  dplyr::select(net_name, species, invasive)
-
-connected_sp <- data %>% dplyr::select(net_name, species) %>% 
-  dplyr::mutate(connected = T)
-
-s_p_s <- s_p %>%
-  dplyr::full_join(invasive_sp) %>%
-  dplyr::mutate(invasive = replace(invasive, is.na(invasive), FALSE)) %>%
-  dplyr::inner_join(guild) %>%
-  dplyr::inner_join(meta) %>%
-  dplyr::filter(study != "ballantyne") %>%
-  dplyr::inner_join(connected_sp)
-
-dd <- data %>% lapply(as.vector) %>% as.data.frame()
-dd <- s_p_s %>%
-  dplyr::select(net_name, species, invasive, connected) %>%
-  dplyr::inner_join(dd) %>%
-  dplyr::mutate(pp = predict.glmulti(mod, select = 0.2, newdata = ., re.form = NA),
-                pp = as.vector(pp),
-                pp = plogis(pp),
-                de2 = de * attr(data$de, "scaled:scale") + attr(data$de, "scaled:center"))
-
-#
-# d <- s_p_s %>%
-#   dplyr::rename(n = nestedcontribution, 
-#                 de = d_strength, 
-#                 vi = v_strength) %>%
-#   dplyr::select(de, n, vi, eig_cen, guild)
-# 
-# d %>% s_p_s %>%
-#   dplyr::select(guild)
-# 
-# pp <-  predict(mod, newdata = d, select = 0.95, re.form = NA)$averages
-# 
-# species <- s_p_s %>%
-#   dplyr::mutate(pp = plogis(as.vector(pp)))
-
-trans <- function(x, orig){
-  x * attr(orig, "scaled:scale") + attr(orig, "scaled:center")
-}
-
-b_trans <- function(x, orig){
-  (x - attr(orig, "scaled:center")) / attr(orig, "scaled:scale")
-}
-
-# juju <- function(x) 10^x
-
-# 
-# pred2 <- expand.grid(de = b_trans(exp(c(seq(log(trans(min(data$de), data$de)),
-#                                 log(trans(max(data$de), data$de)), 
-#                                 length = 500))), data$de),
-#             n = c(seq(min(data$n), max(data$n), length = 500)),
-#             vi = mean(data$vi), 
-#             eig_cen = mean(data$eig_cen, na.rm = T), 
-#             guild = "pla") %>%
-#   dplyr::mutate(q = predict.glmulti(mod, 
-#                                     select = 0.95, 
-#                                     newdata = ., 
-#                                     re.form = NA)$averages %>%
-#                   as.vector(), 
-#                 p = plogis(q)) %>%
-#   dplyr::mutate(de = de * attr(data$de, "scaled:scale") + attr(data$de, "scaled:center"),
-#                 vi = vi * attr(data$vi, "scaled:scale") + attr(data$vi, "scaled:center"),
-#                 n = n * attr(data$n, "scaled:scale") + attr(data$n, "scaled:center"))
-# 
-# p3 <- pred2 %>%
-#   ggplot() +
-#   geom_tile(aes(fill = p, x = de, y = n, z = p)) + 
-#   scale_x_log10(expand = c(0,0)) +
-#   scale_y_continuous(expand = c(0,0)) +
-#   scale_fill_continuous(limits = c(0,1), low = "#ffffff", high = "#636363") +
-#  
-#   geom_point(data = s_p_s, aes(x = d_strength, y = nestedcontribution, shape = guild, colour = invasive), size = 1) +
-#    # stat_contour(aes(x = de, y = n, z = p), 
-#                # colour = "black", size = 0.5, bins = 5) +
-#   fer_theme + 
-#   scale_shape_manual(values = c(21, 22)) +
-#   scale_color_manual(values = c("#525252","#e41a1c")) + 
-#   theme(panel.grid = element_blank(), legend.position = "none",
-# 				plot.margin = grid::unit(c(0, 0, 2, 0), "mm")) +
-#   xlab("dependency strength") +
-#   ylab("contribution to nestedness")
-# 
-# 
-# pred3 <- expand.grid(de = b_trans(exp(c(seq(log(trans(min(data$de), data$de)),
-#                                 log(trans(max(data$de), data$de)), 
-#                                 length = 500))), data$de),
-#             n = c(mean(data$n)),
-#             vi = b_trans(exp(c(seq(log(trans(min(data$vi), data$vi)),
-#                                 log(trans(max(data$vi), data$vi)),
-#                                 length = 500))), data$vi),
-#             # vi = seq(min(data$vi), max(data$vi), length.out = 500),
-#             eig_cen = mean(data$eig_cen, na.rm = T), 
-#             guild = "pla") %>%
-#   dplyr::mutate(q = predict.glmulti(mod, 
-#                                     select = 0.95, 
-#                                     newdata = ., 
-#                                     re.form = NA)$averages %>%
-#                   as.vector(), 
-#                 p = plogis(q)) %>%
-#   dplyr::mutate(de = de * attr(data$de, "scaled:scale") + attr(data$de, "scaled:center"),
-#                 vi = vi * attr(data$vi, "scaled:scale") + attr(data$vi, "scaled:center"),
-#                 n = n * attr(data$n, "scaled:scale") + attr(data$n, "scaled:center"))
-# 
-# p4 <- pred3 %>%
-#   ggplot() +
-#   geom_tile(aes(x = de, y = vi, z = p, fill = p)) + 
-#   scale_x_log10(expand = c(0,0)) +
-#   scale_y_log10(expand = c(0,0)) +
-#   scale_fill_continuous(limits = c(0,1), low = "#ffffff", high = "#636363", name = "") +
-#   geom_point(data = s_p_s, aes(x = d_strength, y = v_strength, shape = guild, colour = invasive), size = 1, show.legend = F) +
-#   # geom_contour(aes(x = de, y = vi, z = p), colour = "black", size = 0.5, bins = 5) +
-#   fer_theme + theme(panel.grid = element_blank(), legend.position = "top",
-# 				plot.margin = grid::unit(c(5, 0, -2, 0), "mm"),
-# 				legend.key.height = grid::unit(3, "mm"),
-# 				legend.key.width = grid::unit(6, "mm")) +
-#   scale_shape_manual(values = c(21, 22)) +
-#   scale_color_manual(values = c("#525252","#e41a1c")) + 
-#   xlab("") +
-#   ylab("visitation strength")
-# 
-# ratio <- function(x){
-#   o <- round(x * 1000)
-#   rep(c(1,2), times = c(o, 1000-o)) %>%
-#     matrix(ncol = 1)
-# }
-
-# 
-# pred4 <- expand.grid(de = b_trans(exp(c(seq(log(trans(min(data$de), data$de)),
-#                                 log(trans(max(data$de), data$de)), 
-#                                 length = 500))), data$de),
-#             n = mean(data$n),
-#             vi = c(-1, 0, 1),
-#             # vi = seq(min(data$vi), max(data$vi), length.out = 500),
-#             eig_cen = mean(data$eig_cen, na.rm = T), 
-#             guild = "pla") %>%
-#   dplyr::filter(!(n == max(data$n) & vi == min(data$vi)),
-#                 !(n == min(data$n) & vi == max(data$vi))) %>%
-#   dplyr::mutate(q = predict.glmulti(mod, 
-#                                     select = 0.95, 
-#                                     newdata = ., 
-#                                     re.form = NA)$averages %>%
-#                   as.vector(), 
-#                 p = plogis(q)) %>%
-#   dplyr::mutate(de = de * attr(data$de, "scaled:scale") + attr(data$de, "scaled:center"),
-#                 vi = vi * attr(data$vi, "scaled:scale") + attr(data$vi, "scaled:center"),
-#                 n = n * attr(data$n, "scaled:scale") + attr(data$n, "scaled:center"))
-# 
-# pred4 %>%
-#   ggplot(aes(x = de, y = p)) +
-#   geom_line(aes(colour = as.factor(n), linetype = as.factor(vi))) + 
-#   scale_x_log10(expand = c(0,0)) +
-#   fer_theme
-# 
-#
-
-pred4 <- data.frame(de = rep(b_trans(exp(c(seq(log(trans(min(data$de), data$de)),
-                                log(trans(max(data$de), data$de)),
-                                length = 500))), data$de),3),
-            n = rep(c(-1,0,1), each = 500),
-            vi = rep(c(-1,0,1), each = 500),
-            type = rep(c("exp", "mean", "exp"), each = 500),
-            # vi = seq(min(data$vi), max(data$vi), length.out = 500),
-            eig_cen = mean(data$eig_cen, na.rm = T),
-            d = mean(data$d, na.rm = T),
-            guild = "pla") %>%
-  dplyr::filter(!(n == 2 & vi == -2),
-                !(n == -2 & vi == 2)) %>%
-  dplyr::mutate(q = predict.glmulti(mod,
-                                    select = 2 %>% `class<-`("integer"),
-                                    newdata = .,
-                                    re.form = NA)$averages %>%
-                  as.vector(),
-                p = plogis(q)) %>%
-  dplyr::mutate(de = de * attr(data$de, "scaled:scale") + attr(data$de, "scaled:center"),
-                vi = vi * attr(data$vi, "scaled:scale") + attr(data$vi, "scaled:center"))
-
-# multiplot(p4, p3, layout = ratio(0.57))
-
-@
-
-Although plants showed significantly higher levels of importance than pollinators (Mann-Whitney-Wilcoxon test, $p = \Sexpr{fix_small_pvalue(wilcox.test(pp ~ guild, data = dd, alternative = "greater")$p.value, 3)}$), this difference can be largely explained by the strength of dependency of the species (the sum of the dependencies for a given species).
-Indeed, when averaging over the set of GLMMs that accounted at least 95\% of the evidence based on AICc, we found that the strength of dependency  is the single most important factor determining the relative importance of species for network control (\autoref{table:driver_model}, \autoref{fig:driver_model_alt}).
-In contrast, the number of visits a species makes (or receives) and its contribution to nestedness have only a marginal effect on its relative importance.
-\begin{table}
-\centering
-\small
-<<table importance 1, echo = FALSE, warning = F, message = F, results = "asis">>=
-print_table(imp)
-@
-\caption{\label{table:driver_model} The strength of dependency, contribution to nestedness and visitation strength had a significative effect on all the models that accounted for 95\% of the evidence based on AICc.
-Coeficient estimates were avaraged following \textcite{Buckland1997a}; confidence intervals were calculated following \textcite{Lukacs2010}.}
-\end{table}
-
-\begin{figure}
-\centering
-<<fig species alt, echo = FALSE, warning = F, message = F, fig.height=2.2, fig.width=3.1>>=
-
-data_pp <- data
-data_pp$pred_ri <- plogis(predict.glmulti(mod, select = as.integer(1), re.form = NA))
-data_pp$de_s <- data$de * attr(data$de, "scaled:scale") + attr(data$de, "scaled:center")
-data_pp <- lapply(data_pp, as.vector) %>% as.data.frame
-
-pred4 %>%
-  ggplot() +
-  geom_line(aes(x = de, y = p, linetype = type, colour = type, group = interaction(n, vi)), show.legend = F, size = 0.5) +
-  scale_x_log10(expand = c(0,0)) +
-   geom_point(data = dplyr::arrange(data_pp, invasive), aes(x = de_s, y = pred_ri, fill = invasive, shape = guild, size = invasive), show.legend = F) +
-    scale_shape_manual(values = c(21, 23)) +
-  scale_size_manual(values = c(1,1.5)) +
-  scale_fill_manual(values = c("white","#e41a1c")) + 
-  scale_color_manual(values = c("#525252", "black")) +
-  scale_linetype_manual(values = c(2, 1)) +
-  xlab("dependency strength") +
-  ylab("relative importance") +
-  fer_theme
-@
-\caption{\label{fig:driver_model_alt} Dependency strength is the single most important factor explaining the importance of species for network control.
-Visitation levels and contribution to nestedness had a significant albeit small effect on the importance (dashed lines correspond to \textpm one standard deviation on these factors).
-Invasive species (red) were invariably classified as driver species (those having the maximum importance for network control.}
-\end{figure}
-
-\section*{Discussion}
-
-Our results reveal that invasive mutualists are driver species in the communities they invade.
-As driver species, they occupy a dominant role in which changes on their abbundance have the potential to cascade trough the community and in turn affect the abbundances of several other species in the community.
-They achieve that by alterning the distribution of the strength of mutual dependencies and the interaction asymmetries---which constitute the foundations of the structure of mutualistic networks \autocite{Vazquez2004, Bascompte2006}.
-Furthermore, these structural differences caused by invasive species at a community level are reflected in a potential decrease in our ability to alter the state of the community.
-
-We confirm previous studies that suggested that in contrast with other kind of complex networks, the structure of ecological networks renders them remarkably difficult to control \autocite{Liu2011, Ruths2014}.
-In a hypothetical situation in which the goal were to regulate the abbundances of all species in a pollination community, our results suggest that we would need to directly intervene the abbundances of at least 40-90\% of those species.
-Fully controling an ecological community is out of the question, as designing and implementating the management interventions needed is currently impractical.
-Nevertheless, the ``manageability'' of an ecological community, which is related to the number of species that would require a directed intervention, can provide a simple, straightforward, and theoretically-informed indication of the degree to which the community is self-regulated and therefore how difficult it might be to modify its state.
-
-Asymmertic depedences have previously found to be related to the stability and persistence of pollination networks \autocite{Memmott2004, Vazquez2004, Lever2014, Astegiano2015}.
-Here, we demonstrate that the manageability of mutualistic networks is also governed by the asymetric nature of mutual dependeces.
-Indeed, our empirical networks have markedly lower levels of manageability compared to randomisations in which the visitation network was unchanged, but the patterns of dependence were broken by randomising the direction of the asymmetries.
-However, consistent with previous results \autocite{Liu2011}, we show that the manageability of empirical networks was indistinguishable from that of networks with a random structure (in terms of modularity and nestedness for example) but that maintained the degree or strength of each species in the community.
-This suggest that the asymmetries at the species (specialization-generalization asymmetries) and the link level (interaction's dependence asymmetries) appear to be sufficiently defined by the distribution of species degree and strength \autocite{Melian2002}.
-Furthermore, we found that invasive species, by altering the patterns of assymetry, reduce the manageability of their communities \autocite{Henriksson2016}.
-This result is in agreement with previous studies that suggest that invasors erode native pollination webs by ursurpating interactions and exarcerbate the asymmerties in the network, which in turn might increasse the stability of the community \autocite{Aizen2008, Bartomeus2008}.
-
-The changes on the asymmetries found in the invaded networks are not only reflected in the manageability at a community level: invaders were found to be driver species in every single community in which they were present.
-Invasive plants have usually been found to be super-generalists thus playing a central role in their networks \autocite{Vila2009, Palacio2016}.
-Nevertheless, we found that dependence strength, rather than generalism or other metrics of centrality, explains best the importance of species for the community dynamics.
-Specifically, driver species tend to be those whose interaction partners are collectively more dependent on them than the other way arround.
-However, the influence of dependence strength was held regardless of wheter the species was invasive or not, which corroborates previous observations that suggest that exotic species, although having different traits\todo{add cite}, are not inherently different to their native counterparts, but are rather governed by the same rules of niche and competition that determine species coexistence \autocite{Stouffer2014}.
-Invasive species have been shown to have the ability to transform the structure of ecological communities \autocite{Aizen2008, Albrecht2014}, our results suggest that they also may have the ability to heavily influence the abbundances of other species in the ecosystem.
-
-Because of their effects on other species in the community, driver species might be natural candidates for management interventions.
-For instance, despite inconsistent outcomes, our results suggest that current restoration approaches that focus on direct eradication of invasive species might indeed be an effective way to modify ecosystem state.
-Nevertheless, our results also indicate that removals must be executed with caution as invaded commmunities tend to be dependent on them and therefore vulnerable to their erradication \autocite{Traveset2013, Albrecht2014}.
-Although useful for identifying conservation priorities, our approach is different to previous attempts to quantify species importance that concentrate on measures of centrality, position, coextintion or uniqueness \autocite{Jordan2006,Jordan2009, Lai2012, McDonald-Madden2016}.
-Instead the concept of driver species is more akin to the original concept of keystone species, which illustrated how changes on the abbundance of a key species in turn affect the abbundances of other members of the community \autocite{Paine1969, Paine1995}.
-However, while the keystone species were traditionally identified by infering the effects of a perturbation on a community's population dynamics \autocite{Mills1993}, the driver species concept operates the other way round, and uses the communuty dynamics, underpinned by the interspecific effects, to infer the effects of a perturbation.
-While it is challenging to quantify the dependence of species in an ecological community, an experimental approach to identofy dynamically important species might be even more difficult\todo{add cite}.
-
-Here we ilustrate how a control theoretic approach can be used to study the effect on mutualistic communities of a major driver of global change, however it can be easily extended to understand the structural effects of other kind of preturbations and species interactions.
-Moreover, we see great potential by explicitly integrating control theory with dynamics models of species densities \autocite{Cornelius2013, Gibson2016}.
-From an ecological perspective, it can provide key insight on determining the relationship between controlability and species coexistence, as well as determining the trade-offs between persistence at the species and the community level.
-From a conservation perspective, a combined approach can be useful, not only to idetify ideal targets for management interventions, but also to design informed, rather than hopeful, interventions that achieve restoration goals.
-
-\section*{Acknoledgements}
-
-The authors thank Dr.
-Takeuki Uno for the insight provided to find the set of all maximum matching algorithms, and Jason Tylianakis, Bernat Bramon, Matthew Hutchinson, and Marilia Gaiarsa for feedback in early stages of the project.
-EFC acknowledges the support from the University of Canterbury Doctoral Scholarship, the University of Canterbury Meadow Mushroooms Postgraduate Scholarship, a New Zealand International Doctoral Research Scholarship, and a travel grant from the European Space Agency.
-DBS ackloledges the support of a Marsden Fast-Start grant and a Rutherford Discovery Fellowship, administered by the Royal Society of New Zealand.
-
-\printbibliography
-
-\end{document}
+**Table 1:**
+The strength of dependency, contribution to nestedness and visitation strength had a significative effect on all the models that accounted for 95\% of the evidence based on AICc. .

### 2016-06-12 paper/drafts_and_revisions/manuscript_DBS_2016-05-19.Rnw
move drafts to own folder, remove old formats

--- 2016-05-16 paper/manuscript.Rnw
@@
   \author{\large Daniel B. Stouffer}
-  \affil{\normalsize Center of Integrative Ecology, School of Biological Sciences, University of Canterbury}
+  \affil{\normalsize Centre for Integrative Ecology, School of Biological Sciences, University of Canterbury}
  \date{}
@@
 
-Complex systems, such as ecological communities, are characterised by non-linear relationships in which the whole is greater than the sum of its parts \todo{add refs}.
-This complex systems approach has led to the development of a rich suite of analytical and simulation tools with which to understand the role of species when embedded in an intricate network of interactions\todo{add refs}.
+Complex systems are characterised by non-linear relationships and emergent behaviors in which the whole is greater than the sum of its parts \todo{add refs}.
+When applied in community ecology, this complex-systems approach has led to the development of a rich suite of analytical and simulation tools with which to understand, for example, the role of species when embedded in a complex interaction network \todo{add refs}.
+{\bf DBS: I'm not sure I buy the following two sentences.}
 However, in contrast to other types of complex systems like neural, intra-organizational, or trust neworks, ecological networks do not have a hierarchical or distributed structure but rather tend to be closed systems in which resources recirculate\todo{add ref}.
 As such, ecosystems contain multiple feedbacks that allow them to self-regulate and, therefore, function relatively independent from external stimulation\todo{add ref}.
-This complex propertes have hindered, or at least complicated, our ability to find management solutions to the many problems ecological communities face.
+This complexity has hindered---or at least greatly complicated---our ability to find management solutions to the many problems ecological communities face.
+{\bf DBS: Transition missing here. It's also not clear if the above is a better place to conclude the paragraph or if the following fits better here or as the start of the next paragraph.}
 A framework that allow us to explain, predict, and manage ecological communities, particularly when they are faced with perturbations, needs to be able to account for their complex structure, and the dynamics that determine the state of each species---and the community as a whole.
-Control theory might be a good candidate framework as it is designed to deal with determining and supervising the behavior of a dynamical system and is well equiped to deal with the many feedbacks presents in ecological communities\todo{add ref}.
-
-Research stemming from control theory has established a strong link between the structure of complex networks and their controlability, and that, in principle, it is possible to alter a ecological community's composition by modifying the abundances of only a few species \autocite{Liu2011, Cornelius2013}.
-Based on this work, it has been suggested that the degree distribution of ecological networks makes them inherently difficult to control \autocite{Liu2011, Ruths2014}.
-This theoretical result is in agreement with many examples in which the management and restoration of ecological communities is more challenging than aticipated.
+
+Among the various possibilities, control theory is a strong candidate as it is designed to deal with determining and supervising the behavior of general dynamical systems and is well equiped to deal with the many feedbacks presents in ecological communities\todo{add ref}.
+What's more, existing research in the field has established a strong link between the structure of complex networks and their controlability, demonstrating that it is in principle possible to alter a whole ecological community's composition by modifying the abundances of only a few species \autocite{Liu2011, Cornelius2013}.
+{\bf DBS: The following sentence doesn't really fit; can we cut it or rephrase to make the connection clearer?}
+Based on this work, it has likewise been suggested that the degree distribution of ecological networks makes them inherently difficult to control \autocite{Liu2011, Ruths2014}.
+This theoretical result is in agreement with many examples in which the management and restoration of ecological communities is more challenging than anticipated.
 For instance, biotic invasions, as a major drivers of global change, can induce dramatic changes on the patterns of interactions that determine the structure of ecological networks \autocite{Baxter2004, Tylianakis2008, Ehrenfeld2010a}.
-The difficulties of returning invaded communities to a predisturbance state can be evidenced by the limited amount of success of restoration projects \autocite{Suding2004, Rodewald2015, Smith2016}.
-Although it is a double challenge, understanding how differences in network structure before and after the invasion impact our ability to manage them is a first step towards an informed recovery.
-
-A control theoretical approach not only might provide insight to conservation but also for ecological science: by explicitly taking into account the extent to which changes in the abbundances of one species may ripple trough the community, applying control theory to ecological networks can provide an indication of which species are important from a dynamic perspective, and therefore crucial when attempting to alter (or maintain) the ecosystem state.
-Nevertheless, although it has been prevoiously used to highlight the disproportionate influence that humans have on marine food-webs \autocite{Isbell2013}, control theory has has rarely been aplied in an ecological context.
+The difficulty of returning invaded communities to their predisturbance state is apparent based on the limited success of many restoration projects \autocite{Suding2004, Rodewald2015, Smith2016}.
+Although it therefore presents a double challenge, understanding how differences in network structure before and after the invasion impact our ability to manage them is a critical first step towards a fully informed recovery.
+
+Beyond conservation objectives, tools from control theory should also provide general ecological insights into problems of key importance in commmunity ecology.
+{\bf DBS: The next sentence is a run on. Try to break it into two.}
+In particular, by explicitly taking into account the extent to which changes in the abbundances of one species may ripple trough the community, applying control theory to ecological networks can provide an indication of which species are important from a holistic dynamic perspective since they underpin informed attempts to alter (or maintain) the ecosystem state.
+Nevertheless, although it has been prevoiously used to highlight the disproportionate influence that humans have on marine food-webs \autocite{Isbell2013}, control theory has not been widely adopted in an ecological context.
+{\bf DBS: The following feels very wishy washy. Would the contents of this paragraph work better as paragraph \#2?}
 One reason might be that the control of complex networks is still a young field and the tools necessary to account for variation on the strength of interspecific effects, which are characteristic of ecological networks, are not there.
 
-Here, we expand previous theory of the control of complex systems and use a set of ten paired invaded and uninvaded plant-pollinator communities to investigate the link between network structure and our ability to manage them.
-We focus on biotic invasions because they can produce tractable changes in the structure of ecological networks.
-These changes can be particularly pronounced in mutualistic networks of plants and pollinators where biotic invasions have been shown to modify the strength of species interactions and the degree of network nestedness and connectivity \autocite{Olesen2002, Aizen2008, Bartomeus2008, Vila2009, Traveset2013}.
-In addition plant-pollinator networks provide an ideal framework to answer these questions.
+Here, we expand previous theory of the control of complex systems to an ecological context.
+We then use a set of ten paired invaded and uninvaded plant-pollinator communities to investigate the link between network structure and our ability to manage them.
+We focus on this particular application for a variety of reasons.
+First, biotic invasions are known to produce tractable changes in the structure of ecological networks, and these changes can be particularly pronounced in mutualistic networks between plants and pollinators where biotic invasions have been shown to modify the strength of species interactions and the degree of network nestedness and connectivity \autocite{Olesen2002, Aizen2008, Bartomeus2008, Vila2009, Traveset2013}.
+Second, plant-pollinator networks provide an ideal framework to answer these questions.
 On one hand, community networks that quantify relative levels of interaction are readily available.
@@
 Second, we ask whether some species are more important than others at driving the population dynamics of the community and which factors determine this importance.
+{\bf DBS: I'm not convinced by the order in which the info is presented in this paragraph.
+For example, I don't really like that the conclusion is the questions as they might work better closer to the start of the paragraph.}
 
@@
 A given matching is then maximum if both \textit{(i)} the number of matched links---known as matching size---is maximal and \textit{(ii)} the sum of the weights of the matched links---known as matching weight---is the largest possible among all possible matchings of that size \autocite{West2001}.
-To find the maximum matching, we it is useful to adopt an alternative bipartite representation of the network in which the two levels indicate the outgoing and incoming links to each node (\autoref{fig:explain_mm}b).
+To find the maximum matching, it is useful to adopt an alternative bipartite representation of the network in which the two levels indicate the outgoing and incoming links to each node (\autoref{fig:explain_mm}b).
 Finding a matching in this alternative representation is equivalent to finding a set of links such that each node on the top level is matched to at most one node on the bottom level, and vice versa \autocite{West2001, Csardi2006a}.
@@
 
-Given a maximum matching, the link to network controllability has an intuitive basis.
-In control theory, a network is fully controlable when each node has a ``superior'', that is, an input that drives its dynamics.
-Consequently, each matched nodes can be controled by the node pointing to it.
+Given a maximum matching, the link to network controllability has a largely intuitive basis.
+In control theory, a network is fully controllable when each node has a ``superior'', that is, an input that drives its dynamics.
+Consequently, each matched nodes can be controlled by the node pointing to it.
 Unmatched nodes, on the other hand, have no superior in the network and must be directly controlled by external inputs \autocite{Liu2011}.
-In an ecological context, this is what we refer to as management interventions.
-Building on this, systems that require a large number of external inputs are more difficult or costly to control.
+In an ecological context, this is what could be referred to as management interventions.
+Building on this analogy, systems that require a large number of external inputs are more difficult or costly to control.
 Therefore, the manageability $m$ of a community can be approximated by the proportion of species on which we would need to apply management interventions in order to gain full control of the abundances of \textit{all} species in the ecological community $$m = 1- \frac{n_d}{s},$$ where $m$ ranges between zero and one, $n_d$ is the number of species needed to gain full control and $s$ is the total number of species in the community.
@@
 The manageability of a community $m$ provides an indication of the magnitude of $n_d$ but not the identity of the species that compose this set.
-This is rather important since maximum matchings are often not unique in for a given network and different sets of species of size $n_d$ could potentially be used to control the network \autocite{Liu2011}.
+This is rather important since maximum matchings are often not unique in a given network and different sets of species of size $n_d$ could potentially be used to control the network \autocite{Liu2011}.
 Species vary in terms of the frequency with which they are classified as superior nodes (\autoref{fig:explain_mm}), and this frequency provides an indication of their relative importance in driving the state of the community.
-Ecologically, these distinctions are crucial because resources are limited and therefore ecological inteventions should be focused on species that might provide the largest impact.
-As superior nodes \autoref{fig:explain_mm} drive the dynamics of other species and are therefore important for the controlability of the network because they either require external input or because the are part of the chain that transmit the external imputs to other species, we therefore call \textit{driver species} those that are identified as being a superior node in all possible matchings, and hence those most likely to have a disproportionate effect on the abundances of other species in their community.
+Ecologically, these distinctions are crucial because resources are limited and therefore ecological interventions should be focused on species that might provide the largest impact.
+Superior nodes \autoref{fig:explain_mm} drive the dynamics of other species and are therefore important for the controlability of the network because they either require external input or because the are part of the chain that transmit the external imputs to other species; we therefore call \textit{driver species} those that are identified as being a superior node in \emph{all} possible matchings, and hence those most likely to have a disproportionate effect on the abundances of other species in their community.
 
@@
 One way to calculate the species importance, and identify the driver species, would be to consider only maximum matchings.
-However empirical intraction strengths are to some extent stochastic and depend on proximate factors such as sampling method and intensity \autocite{Rezende2007}.
-This means that in weighted networks there is a number of matchings that have maximal size, but are not maximum matchings because their total weight is not maximal.
-We therefore relaxed the matching weight requirement and computed all possible matchings in the network that have the same maximal size while allowing for some tolerance regarding the weight.
-To compute all the matchings with maximal size, we first generated the network's line graph---another representation in which nodes are the links of the original network and links represent common ending points \autocite{West2001}.
-We then calculated the complement of the line graph: a graph in which nodes are connected if and only if they are not connected in the line graph.
-All possible matchings of maximal size can be found by enumerating all cliques (subgraphs in which every node is linked to every other) of maximum size, which equates to $1-n_d$m in this complement graph \autocite{Csardi2006a, Gutin2013}.
+However, empirical interaction strengths are to some extent stochastic and depend on proximate factors such as sampling method and intensity \autocite{Rezende2007, and_more}.
+This means that there are multiple matchings that have maximal size in weighted networks, but are not maximum matchings because their total weight is not maximal.
+One could therefore instead relax the matching weight requirement and computed all possible matchings in the network that have the same maximal size while allowing for some tolerance regarding the weight.
+To compute all the matchings with maximal size, one can first generate the network's line graph---another representation in which nodes are the links of the original network and links represent common ending points \autocite{West2001}---followed by calculation of the complement of this line graph.
+This latter step generates a graph in which nodes are connected if and only if they are not connected in the line graph.
+All possible matchings of maximal size can be found by enumerating all cliques (subgraphs in which all nodes are fully connected to each other) of maximum size
+{\bf DBS: Cut this part?}, which equates to $1-n_d$m in this complement graph
+\autocite{Csardi2006a, Gutin2013}.
 
@@
 
-In the last section, we outlined the theoretical and computational underpinings of our approach.
+In the last section, we outlined the theoretical and computational underpinnings of our approach.
 Now we illustrate its empirical application using ten pairs of plant-pollinator communities for which we explored their manageability and the relative importance of their constituent species.
@@
 In contrast, the Spanish uninvaded communities were obtained from plots that had not yet been colonised by either of the invasive species \textit{Carpobrotus affine acinaciformis} or \textit{Opuntia stricta}.
-The structure of these networks was determined using visitation frequency which has been shown to be an appropriate surrogate for interspecific effects in pollination networks \autocite{Vazquez2005, Bascompte2006}.
-To examine whether this decision would influence our results, we also evaluated the effect of using pollinator efficiency or importance as alternative measures of species interactions in a different dataset \autocite{NeEman2010, Ballantyne2015}, and we found quantitatively results for all of these options (see Supplementary Information).
+The structure of all networks was determined using visitation frequency which has been shown to be an appropriate surrogate for interspecific effects in pollination networks \autocite{Vazquez2005, Bascompte2006}.
+To examine whether this decision would influence our results, we also evaluated the effect of using pollinator efficiency or importance as alternative measures of species interactions in a different dataset \autocite{NeEman2010, Ballantyne2015}, and we found quantitatively similar results for all of these options (see Supplementary Information).
 
@@
 
-Given the different networks, we started by quantifying their manageability.
-To do so, we calculated the maximum matching of the corresponding pollination network, and estimated the minimum number of species that need directed intervecntions to fully control the species abbundances in the community.
-If a network had more than one component (two species are in different components if there exists no path between them), we only analysed the largest one.
+Given the different networks, we began by quantifying their manageability.
+To do so, we calculated the maximum matching of the corresponding pollination network, and estimated the minimum number of species that need directed interventions to fully control the species abundances in the community.
+If a network had more than one component (two species are in different components if there exists no path between them), note that we only analysed the largest.
 
@@
 Recall that the aforementioned maximum matching algorithm requires a directed network in which a link between species $i$ and $j$ pointing to species $j$ indicates that the abundance of $j$ can be affected by the abundance of $i$.
-This implies that we need first to identify a directionality for the links between species that in consistent with the dynamics of the comunity.
-In some ecological networks, establishing a directionality is relatively straightforward, for example when links represent biomass transfer or energy flow.
+This implies that we need first to identify a directionality for the links between species that in consistent with the dynamics of the community.
+In some ecological networks, establishing the directionality is relatively straightforward, for example when links represent biomass transfer or energy flow.
 Interspecific effects in pollination networks, however, are not strictly directed since the benefit is mutual between interacting species.
@@
 
-Mutual dependencies have been shown to be highly assymetric in natural communities \autocite{Bascompte2006}; in other words, if a plant species is largely dependent on a pollinator species, then that pollinator tends to depend rather weakly on the plant.
-This suggests that it may be possible to relax the assumption of bidirectional dependences and simplify the network further such that interacting species are only connected by one directed link when mutual dependencies are assymetric (\autoref{fig:explain_cd}c).
-The extent to which a species $i$ affects species $j$ relative to the extent to which species $j$ affects species $i$ can be summarised by the interaction asymmetry given by $$a(i,j) = \frac{\left | d_{ij}-d_{ji} \right |}{\textup{max}\left ( d_{ij}, d_{ji} \right )}.$$
-
-Employing an unidrectional interaction asymmetry, as a surrogate of bidirectional mutual dependences, dramatically reduces the number of links in the network, which provides substantial reduction of the time and memory required for the computation of of all posible maximum matchings in a network, particularly for large networks (see ``relative importance of species'' subsection below).
+Mutual dependencies have previously been shown to be highly asymmetric in natural communities \autocite{Bascompte2006}; in other words, if a plant species is largely dependent on a pollinator species, then that pollinator tends to depend rather weakly on the plant.
+This suggests that it may be possible to relax the assumption of bidirectional dependences and simplify the network further such that interacting species are only connected by one directed link when mutual dependencies are asymmetric (\autoref{fig:explain_cd}c).
+The extent to which a species $i$ affects species $j$ relative to the extent to which species $j$ affects species $i$ can be summarised by the interaction asymmetry given by $$a(i,j) = \frac{\left | d_{ij}-d_{ji} \right |}{\textup{max}\left ( d_{ij}, d_{ji} \right )}.$$ Employing an unidrectional interaction asymmetry, as a surrogate of bidirectional mutual dependences, confers an additional advantage for our purposes since it dramatically reduces the number of links in the network; this translates into a substantial reduction of the time and memory required for the computation of of all possible maximum matchings in a network, particularly for large networks (see ``relative importance of species'' subsection below).
 
@@
 
-Although understanding the variability of manageability across ecological networks is an useful result itself, we also wanted to test whether network attributes, like invasion status, have an impact on the observed manageability values.
-We therefore used a set of generalised linear models (with binomial error structure) to investigate the effect of invasion status while controling for factors related to species richness, since one might naively expect to see a negative relationship between diversity and manageability \autocite{Menge1995}.
-These covariates inlcuded the total number of species, plant richness, polinators richness, the ratio of plants to pollinators richness, and the study site.
-We assessed competing models by comparing the Akaike Information Criterion corrected for small sample sizes (AICc), and report results for the most parsimonious one.
+Although understanding the variability of manageability across ecological networks is an useful result itself, we also wanted to test whether invasion status has an impact on the observed manageability values.
+We therefore used a set of generalised linear models (with binomial error structure) to investigate the effect of invasion status while also controlling for factors related to species richness, since one might naively expect to see a negative relationship between diversity and manageability \autocite{Menge1995}.
+These covariates included the total number of species, plant richness, polinators richness, the ratio of plants to pollinators richness, and the study site.
+We assessed competing models by comparing the Akaike Information Criterion corrected for small sample sizes (AICc), and report results for the most parsimonious model.
 
@@
 The first set of random visitation networks maintain the connectivity of the empirical network, but both degree (its number of interactions) and strength (its total sum of visits) were allowed to vary.
-A second set set was generated by maintaining each species' degree while varying the number of visits per species.
-Finally a third set of random networks mantained the species' strength while varying their degrees.
+The second set was generated by maintaining each species' degree while varying the number of visits per species.
+Finally, the third set of random networks mantained the species' strength while varying their degrees.
 Randomisations were generated using vegan 2.3-3 \autocite{Oksansen2016}.
@@
 The dependency asymmetry plays a fundamental role in determining the direction of control in each two-species interaction and therefore has the potential to influence the network manageability results above.
-We therefore performed an additional randomisation in which we kept the structure of network consistent but randomised the direction of the interaction asymmetries.
-That is, we first calculated the assymetries for each community and then shuffled the direction of the link between species.
-Similar as in previous null models, we calculated the average rank of the empirical manageability as compared to those of the randomisations.
+We therefore performed an additional randomisation in which we kept the structure of network constant but randomised the direction of the interaction asymmetries.
+That is, we first calculated the asymmetries for each community and then shuffled the direction of the link between each pair of species.
+{\bf DBS: State that this has no effect when assymetry = 0?} Similar as in previous null models, we calculated the average rank of the empirical manageability as compared to those of the randomisations.
 
@@
 
-Our second key question is related to how different species differ in their importance for the population dynamics of the community.
+Our second key question is related to how species differ in their importance for driving the population dynamics of the community.
 To quantify this importance in each network, we computed all possible matchings that have the same size as the networks' maximum matching.
 We then calculated the frequency with which each species is deemed to be a superior node in the set of matchings that had a total weight greater or equal to 0.5 times the weight of the maximum matching.
-We selected this threshold as it provided a high agreement between networks quantified by visitation and pollination efficiency as well as between our weighting/directionality assumptions (mutual dependences and inetraction asymmetries); however the choice of this threshold had a negligible impact on the results (Supplementary Information).
-
-Even in sparse networks, like these studied here, the number of maximal matchings increasses exponentially with the number of links and nodes in a network.
-Unfortunately, this means that the large number of links in the most diverse communities rendered the computation unfeasible when we used mutual dependecies.
+We selected this threshold as it provided a high agreement between networks quantified by visitation and pollination efficiency as well as between our weighting/directionality assumptions (mutual dependences and interaction asymmetries); however, the choice of this threshold had a negligible impact on the results (Supplementary Information).
+
+Even in sparse networks, like these studied here, the number of maximal matchings increases exponentially with the number of links and nodes in a network.
+Unfortunately, this means that the large number of links in the most diverse communities rendered the computation unfeasible when we used mutual dependencies.
 Taking this limitation into account, we compared the relative network manageability obtained when using asymmetries to those found when using mutual dependencies for eleven of the twenty networks (those for which the number of matchings was smaller than $4\times 10^{10}$).
@@
 All three approaches identified a high similarity in relative ranks.
-Therefore, we focused on the results from the assymetries, rather than mutual dependences, to further investigate the factors that determine species' relative importance since this also allows us to obtain results for all networks.
-
-Given the species importance obtained using the interaction asymmetries, we then asked the question of whether some species-level structural properties can predict the relative importance of species.
-To do so, we used a generalised linear mixed-effects model (GLMM) with a logistic link function to evaluate the relationship between the species' relative importance and a suite of structural measures.
-As predictors in this model, we specifically included measures of centrality (degree and eigen-centrality), which have been found to be strong predictors of importance in a coextintion context \autocite{Memmott2004}; a measure related to network robustness (contribution to nestedness), as nestedness has been proposed as one of the key properties that promote stability in mutualistic networks \autocite{Saavedra2011}; and measures of strength of association and dependence (visitation and dependency strength), as their distribution determine the extent of interspecific effects; and whether the species was invasive or not.
-In addition we also included guild and invasive status as fixed effects; although the importance of plants and pollinators or invasive and non-invasive species could respond differently to our structural metrics, our dataset did not contain enough variation to include the corresponding interactions terms.
-All metrics were calculated using the R package bipartite 2.06 \autocite{Dormann2008}.
-We allowed for variation between different communities by including the network identity as a random effect \autocite{Bates2015a}.
+Consequently, we focused on the results when using the asymmetries rather than mutual dependencies when further investigating the factors that determine species' relative importance since this also allows us to obtain results for all XX networks.
+
+We then asked the question of whether some species-level structural properties can predict our estimates of species importance using a generalised linear mixed-effects model (GLMM) with  binomial error structure.
+As predictors in this model, we included measures of centrality (degree and eigen-centrality), which have been found to be strong predictors of importance in a coextintion context \autocite{Memmott2004}; a measure related to network robustness (contribution to nestedness), as nestedness has been proposed as one of the key properties that promote stability in mutualistic networks \autocite{Saavedra2011}; two measures of strength of association and dependence (visitation and dependency strength), as their distribution determine the extent of interspecific effects; and a categorical predictor that indicates whether the species was invasive or not.
+{\bf DBS: Isn't the last predictor from the previous list the same as `invasive status' in the following one?} In addition, we also included guild and invasive status as fixed effects; although the importance of plants and pollinators or invasive and non-invasive species could respond differently to our structural metrics, our dataset did not contain enough variation to include the corresponding interactions terms for these latter two predictors.
+All network metrics were calculated using the R package bipartite 2.06 \autocite{Dormann2008}.
+We lastly allowed for variation between different communities by including the network identity as a random effect \autocite{Bates2015a}.
 Candidate models were compared using AICc and the relative importance of the explanatory variables was evaluated using the sum of Akaike weights over candidate models that accounted for 95\% of the evidence \autocite{Burnham2003, Bates2014, Barton2016}.
@@
 
-The networks studied here had levels of manageability between \Sexpr{round(min(1-dplyr::filter(n_driver, type == "z-bi")$n_dr_p), digits = 2)} and \Sexpr{round(max(1-dplyr::filter(n_driver, type == "z-bi")$n_dr_p), digits = 2)} (mean \Sexpr{round(mean(1-dplyr::filter(n_driver, type == "z-bi")$n_dr_p), digits = 2)}) when we considered bidirectional links weighted by the mutual dependences.
-This was in strong agreement  to the results obtained using the dependence asymmetry in which manageability ranged between \Sexpr{round(min(1-dplyr::filter(n_driver, type == "weight")$n_dr_p), digits = 2)} and \Sexpr{round(max(1-dplyr::filter(n_driver, type == "weight")$n_dr_p), digits = 2)} (\Sexpr{round(mean(1-dplyr::filter(n_driver, type == "weight")$n_dr_p), digits = 2)}; Spearman rank correlation \Sexpr{round(src_bi_w$estimate, digits = 2)}, $p = \Sexpr{as.numeric(format(src_bi_w$p.value, digits = 2))}$).
-In addition we found that invaded communities were significanlty more difficult to manage than uninvaded ones even when controling for diversity.
-Out of the explored factors---total number of species, plant richness, pollinator richness, and the ratio of plant to pollinator richness---only the ratio of plant to pollinator richness was retained in the final model as determined by the AICc (\autoref{fig:n_driver_explanatory}, Table S3).
+All of the networks studied here had levels of manageability between \Sexpr{round(min(1-dplyr::filter(n_driver, type == "z-bi")$n_dr_p), digits = 2)} and \Sexpr{round(max(1-dplyr::filter(n_driver, type == "z-bi")$n_dr_p), digits = 2)} (mean \Sexpr{round(mean(1-dplyr::filter(n_driver, type == "z-bi")$n_dr_p), digits = 2)}) when we considered bidirectional links weighted by the mutual dependences.
+This was in strong agreement with the results obtained using the dependence asymmetry in which manageability ranged between \Sexpr{round(min(1-dplyr::filter(n_driver, type == "weight")$n_dr_p), digits = 2)} and \Sexpr{round(max(1-dplyr::filter(n_driver, type == "weight")$n_dr_p), digits = 2)} (\Sexpr{round(mean(1-dplyr::filter(n_driver, type == "weight")$n_dr_p), digits = 2)}; Spearman rank correlation \Sexpr{round(src_bi_w$estimate, digits = 2)}, $p = \Sexpr{as.numeric(format(src_bi_w$p.value, digits = 2))}$).
+In addition, we found that invaded communities were significantly more difficult to manage than uninvaded ones even when controlling for potential diversity effects.
+Out of the various covariates we explored---total number of species, plant richness, pollinator richness, and the ratio of plant to pollinator richness---only the ratio of plant to pollinator richness was retained in the final model as determined by the AICc (\autoref{fig:n_driver_explanatory}, Table S3).
+{\bf DBS: Should we say what the effect was or is the table enough?}
 
@@
 
-The manageability of empirical networks was, in general, not significantly different to the manageability of network randomisations that maintained the degree or the strength of individual species (\autoref{fig:randomisations}).
-However, when comparing the empirical network to less constrained randomisations that only maintained the original connectance but in which species had different degrees and strengths, we found that empirical networks tended to have smaller values of manageability.
-This pattern is even more marked when we maintained the network structure but randomised only the direction of the asymmetries (\autoref{fig:randomisations}).
+When exploring the effect of network structure itself, we observed that the manageability of empirical networks was, in general, not significantly different to the manageability of network randomisations that maintained the degree or the strength of individual species (\autoref{fig:randomisations}).
+However, when comparing the empirical network to less constrained randomisations that only maintained the original connectance but in which species had different degrees and strengths, we found that empirical networks showed a significant tendency to have smaller values of manageability.
+Furthermore, this pattern was even more marked when we maintained the network structure but randomised only the direction of the asymmetries (\autoref{fig:randomisations}).
 
@@
 
-We found a strong agreement between relative species' importance in the 11 networks for which we were able to calulate them using both mutual dependencies and asymmetries (Spearman's rank correlation ranged between $\rho = [\Sexpr{round(min(dplyr::filter(correlations, threshold == 0.5, type == "asymmetry", scaled == T)$V3, na.rm = T), digits = 2)}, \Sexpr{round(max(dplyr::filter(correlations, threshold == 0.5, type == "asymmetry", scaled == T)$V3, na.rm = T), digits = 2)}]$, median $\tilde{\rho} = \Sexpr{round(median(dplyr::filter(correlations, threshold == 0.5, type == "asymmetry", scaled == T)$V3, na.rm = T), digits = 2)})$.
+We found a strong agreement between the values of relative species' importance in the 11 networks for which we were able to calculate them using both mutual dependencies and asymmetries (Spearman's rank correlation ranged between $\rho = [\Sexpr{round(min(dplyr::filter(correlations, threshold == 0.5, type == "asymmetry", scaled == T)$V3, na.rm = T), digits = 2)}, \Sexpr{round(max(dplyr::filter(correlations, threshold == 0.5, type == "asymmetry", scaled == T)$V3, na.rm = T), digits = 2)}]$, median $\tilde{\rho} = \Sexpr{round(median(dplyr::filter(correlations, threshold == 0.5, type == "asymmetry", scaled == T)$V3, na.rm = T), digits = 2)})$.
 Moreover both approaches identified a highly similar set of driver species (Jaccard similarity $J = [\Sexpr{round(min(dplyr::filter(correlations, threshold == 0.5, type == "asymmetry", scaled == T)$V4, na.rm = T), digits = 2)}, \Sexpr{round(max(dplyr::filter(correlations, threshold == 0.5, type == "asymmetry", scaled == T)$V4, na.rm = T), digits = 2)}]$, $\tilde{J} = \Sexpr{round(median(dplyr::filter(correlations, threshold == 0.5, type == "asymmetry", scaled == T)$V4, na.rm = T), digits = 2)})$.
-Notably we found that the agreement was stronger for highly ranked species than for lowly ranked species ($\tilde{r_{w2}} = \Sexpr{round(median(dplyr::filter(correlations, threshold == 0.5, type == "asymmetry", scaled == T)$V1, na.rm = T), digits = 2)}$ versus $\tilde{r_{w2}} = \Sexpr{round(median(dplyr::filter(correlations, threshold == 0.5, type == "asymmetry", scaled == T)$V2, na.rm = T), digits = 2)}$) when using the weighted rank correlation coefficient $r_{w2}$.
-Given the similarities, we concentrated on the relative rankings obtained using asymmetries in the following results
+Notably, we found that the agreement was stronger for highly ranked species than for lowly ranked species ($\tilde{r_{w2}} = \Sexpr{round(median(dplyr::filter(correlations, threshold == 0.5, type == "asymmetry", scaled == T)$V1, na.rm = T), digits = 2)}$ versus $\tilde{r_{w2}} = \Sexpr{round(median(dplyr::filter(correlations, threshold == 0.5, type == "asymmetry", scaled == T)$V2, na.rm = T), digits = 2)}$) when using the weighted rank correlation coefficient $r_{w2}$.
+Given the overall similarities, we concentrated on the relative rankings obtained using asymmetries in the following results.
 
@@
 
-Although plants showed significantly higher levels of importance than pollinators (Mann-Whitney-Wilcoxon test, $p = \Sexpr{fix_small_pvalue(wilcox.test(pp ~ guild, data = dd, alternative = "greater")$p.value, 3)}$), this difference can be largely explained by the strength of dependency of the species (the sum of the dependencies for a given species).
-Indeed, when averaging over the set of GLMMs that accounted at least 95\% of the evidence based on AICc, we found that the strength of dependency  is the single most important factor determining the relative importance of species for network control (\autoref{table:driver_model}, \autoref{fig:driver_model_alt}).
+Overall, plants showed significantly higher levels of importance than pollinators (Mann-Whitney-Wilcoxon test, $p = \Sexpr{fix_small_pvalue(wilcox.test(pp ~ guild, data = dd, alternative = "greater")$p.value, 3)}$).
+However, this difference can largely be explained by the strength of dependency of the species (the sum of the dependencies for a given species).
+Indeed, when averaging over the set of GLMMs that accounted at least 95\% of the evidence based on AICc, we found that species' strength of dependency is the single most important factor determining the relative importance of species for network control (\autoref{table:driver_model}, \autoref{fig:driver_model_alt}).
 In contrast, the number of visits a species makes (or receives) and its contribution to nestedness have only a marginal effect on its relative importance.
@@
 
-\section*{Acknoledgements}
+\section*{Acknowledgments}
 
@@
 Takeuki Uno for the insight provided to find the set of all maximum matching algorithms, and Jason Tylianakis, Bernat Bramon, Matthew Hutchinson, and Marilia Gaiarsa for feedback in early stages of the project.
-EFC acknowledges the support from the University of Canterbury Doctoral Scholarship, the University of Canterbury Meadow Mushroooms Postgraduate Scholarship, a New Zealand International Doctoral Research Scholarship, and a travel grant from the European Space Agency.
-DBS ackloledges the support of a Marsden Fast-Start grant and a Rutherford Discovery Fellowship, administered by the Royal Society of New Zealand.
+EFC acknowledges the support from the University of Canterbury Doctoral Scholarship, the University of Canterbury Meadow Mushrooms Postgraduate Scholarship, a New Zealand International Doctoral Research Scholarship, and a travel grant from the European Space Agency.
+DBS acknowledges the support of a Marsden Fast-Start grant and a Rutherford Discovery Fellowship, administered by the Royal Society of New Zealand.
 

### 2016-06-12 paper/drafts_and_revisions/manuscript_DBS_2016-05-20.Rnw
move drafts to own folder, remove old formats

--- 2016-06-12 paper/drafts_and_revisions/manuscript_DBS_2016-05-19.Rnw
@@
 
+\todo{DBS: Why start with the species-level results? This dovetails from the order of the rest of the paper.}
 Our results reveal that invasive mutualists are driver species in the communities they invade.
@@
 
-We confirm previous studies that suggested that in contrast with other kind of complex networks, the structure of ecological networks renders them remarkably difficult to control \autocite{Liu2011, Ruths2014}.
+We confirm previous studies that suggested that, in contrast with other kind of complex networks, the structure of ecological networks renders them remarkably difficult to control \autocite{Liu2011, Ruths2014}.
 In a hypothetical situation in which the goal were to regulate the abbundances of all species in a pollination community, our results suggest that we would need to directly intervene the abbundances of at least 40-90\% of those species.
-Fully controling an ecological community is out of the question, as designing and implementating the management interventions needed is currently impractical.
+Fully controlling an ecological community is out of the question, as designing and implementing the management interventions needed is currently impractical.
 Nevertheless, the ``manageability'' of an ecological community, which is related to the number of species that would require a directed intervention, can provide a simple, straightforward, and theoretically-informed indication of the degree to which the community is self-regulated and therefore how difficult it might be to modify its state.
 
-Asymmertic depedences have previously found to be related to the stability and persistence of pollination networks \autocite{Memmott2004, Vazquez2004, Lever2014, Astegiano2015}.
-Here, we demonstrate that the manageability of mutualistic networks is also governed by the asymetric nature of mutual dependeces.
-Indeed, our empirical networks have markedly lower levels of manageability compared to randomisations in which the visitation network was unchanged, but the patterns of dependence were broken by randomising the direction of the asymmetries.
-However, consistent with previous results \autocite{Liu2011}, we show that the manageability of empirical networks was indistinguishable from that of networks with a random structure (in terms of modularity and nestedness for example) but that maintained the degree or strength of each species in the community.
-This suggest that the asymmetries at the species (specialization-generalization asymmetries) and the link level (interaction's dependence asymmetries) appear to be sufficiently defined by the distribution of species degree and strength \autocite{Melian2002}.
+Asymmertic depedences have previously been found to be related to the general stability and persistence properties of pollination networks \autocite{Memmott2004, Vazquez2004, Lever2014, Astegiano2015}.
+Here, we demonstrate that the manageability of mutualistic networks is similarly governed by the asymmetric nature of mutual dependencies.
+Indeed, our empirical networks exhibit markedly lower levels of manageability compared to randomisations in which the visitation network was unchanged but where the observed patterns of dependence were broken \todo{DBS: Can we cut the rest of the sentence?} by randomising the direction of the asymmetries.
+However, consistent with previous results \autocite{Liu2011}, we show that the manageability of empirical networks was indistinguishable from that of networks with a random structure (in terms of modularity and nestedness for example) that maintained the degree or strength of each species in the community.
+This suggest that the asymmetries at the species level (specialization-generalization asymmetries) and the link level (interaction's dependence asymmetries) appear to be sufficiently constrained by the distribution of species degree and strength \autocite{Melian2002}.
 Furthermore, we found that invasive species, by altering the patterns of assymetry, reduce the manageability of their communities \autocite{Henriksson2016}.
-This result is in agreement with previous studies that suggest that invasors erode native pollination webs by ursurpating interactions and exarcerbate the asymmerties in the network, which in turn might increasse the stability of the community \autocite{Aizen2008, Bartomeus2008}.
+This result is in agreement with previous studies that suggest that invaders erode native pollination webs by usurping interactions and exacerbating the asymmetries in the network, an observation which might in turn increase the stability of the community \autocite{Aizen2008, Bartomeus2008}.
 
@@
 Nevertheless, we found that dependence strength, rather than generalism or other metrics of centrality, explains best the importance of species for the community dynamics.
-Specifically, driver species tend to be those whose interaction partners are collectively more dependent on them than the other way arround.
+Specifically, driver species tend to be those whose interaction partners are collectively more dependent on them than the other way around.
 However, the influence of dependence strength was held regardless of wheter the species was invasive or not, which corroborates previous observations that suggest that exotic species, although having different traits\todo{add cite}, are not inherently different to their native counterparts, but are rather governed by the same rules of niche and competition that determine species coexistence \autocite{Stouffer2014}.
@@
 Nevertheless, our results also indicate that removals must be executed with caution as invaded commmunities tend to be dependent on them and therefore vulnerable to their erradication \autocite{Traveset2013, Albrecht2014}.
-Although useful for identifying conservation priorities, our approach is different to previous attempts to quantify species importance that concentrate on measures of centrality, position, coextintion or uniqueness \autocite{Jordan2006,Jordan2009, Lai2012, McDonald-Madden2016}.
+Although useful for identifying conservation priorities, our approach is different to previous attempts to quantify species importance that concentrate on measures of centrality, position, co-extinction or uniqueness \autocite{Jordan2006,Jordan2009, Lai2012, McDonald-Madden2016}.
 Instead the concept of driver species is more akin to the original concept of keystone species, which illustrated how changes on the abbundance of a key species in turn affect the abbundances of other members of the community \autocite{Paine1969, Paine1995}.
@@
 
-Here we ilustrate how a control theoretic approach can be used to study the effect on mutualistic communities of a major driver of global change, however it can be easily extended to understand the structural effects of other kind of preturbations and species interactions.
-Moreover, we see great potential by explicitly integrating control theory with dynamics models of species densities \autocite{Cornelius2013, Gibson2016}.
-From an ecological perspective, it can provide key insight on determining the relationship between controlability and species coexistence, as well as determining the trade-offs between persistence at the species and the community level.
-From a conservation perspective, a combined approach can be useful, not only to idetify ideal targets for management interventions, but also to design informed, rather than hopeful, interventions that achieve restoration goals.
+In this study, we illustrate how a control-theoretic approach can be adopted when estimating the effect  of a major driver of global change on mutualistic communities.
+Note though that it can be easily extended to understand the structural effects of other kind of perturbations and for systems governed by different types of species interactions.
+Moreover, we see great potential by explicitly integrating control theory with dynamic models of species densities \autocite{Cornelius2013, Gibson2016}.
+From an ecological perspective, this integration can provide deeper insights into the relationship between controllability and species coexistence.
+It can also help identify potential trade-offs between persistence at the species and the community level \todo{add refs}.
+From a conservation perspective, the combined approach can extend things beyond the identification of ideal targets for intervention to design informed interventions that legitimately achieve restoration goals.
 
@@
 
-The authors thank Dr.
-Takeuki Uno for the insight provided to find the set of all maximum matching algorithms, and Jason Tylianakis, Bernat Bramon, Matthew Hutchinson, and Marilia Gaiarsa for feedback in early stages of the project.
+The authors thank Dr.\ Takeuki Uno for the insight provided to find the set of all maximum matching algorithms, and Jason Tylianakis, Bernat Bramon, Matthew Hutchinson, and Marilia Gaiarsa for feedback in early stages of the project.
 EFC acknowledges the support from the University of Canterbury Doctoral Scholarship, the University of Canterbury Meadow Mushrooms Postgraduate Scholarship, a New Zealand International Doctoral Research Scholarship, and a travel grant from the European Space Agency.

### 2016-07-02 paper/covering_letter.tex
first draft covering letter

\documentclass[10pt, a4paper]{letter}

\begin{document}

\begin{letter}{
       %\vspace*{20pt}
       Prof. XX\\
       Chief Editor\\
       Ecology Letters}

\opening{Dear Proffesor}

We are submitting the manuscript entitled ``Biotic invasions reduce the manageability of mutualistic networks'' to be considered for publication at \emph{Ecology Letters}.

Central to this manuscript is the introduction and development of the concept of \textbf{theoretical manageability}.
Based on the patterns of interactions between species, this idea can provide two main pieces of information. 
First, it allows to quantify the \textit{community manageability}---an indication of the difficulty to control the abbundances of all species in the community. 
Second it allows to identify the \textit{driver species}--- those with a disproportionate ability to alter other species' abundances.  
We use this concept as a framework to study the changes caused by biotic invasions to the community manageability and examine the role played by individual species.

Multiple empirical observations have suggested that the structural changes caused by invasions may lead to increased ecosystem resilience. 
Our study is the first to use empirical data to provide explicit theoretical support to this idea. 
Furthermore, our approach to quantify the relative importance of species is unique at that is based on the structure that underpin the community dynamics while at the same time having a direct link with management. 
Not only our results highlight the ability that some species, and invaders in particular, have to drive the dynamics of other species in the community, but also identifies "asymmetric dependence" as the key factor driving these interspecific differences.

We developed the ideas of community manageability and driver species with the underlying motivation to study the consequences of biotic invasions in mutualistic systems. 
Nevertheless, understanding how drivers of ecosystem change affect ecosystem dynamics is not exclusive to mutualistic communities. 
Indeed, we envisage the application of the concepts we introduce to answer a wide range of ecological questions in communities structured by different types of interactions.
The methodology necessary for its implementation---an extension of recently developed tools at the interface of complex systems and control theory---is thoroughly detailed in the manuscript.

In addition, although our study lies fundamentally within ecological theory, it has ramifications pertinent to ecological application. 
We think that concepts like theoretical manageability have the potential to stimulate much needed research that shorten the gap between ecological theory and management.
Hopefully setting us on the track to informed, rather than hopeful, ecosystem interventions.

The enclosed work represents a novel work also for all co-authors involved and no work published, in press, or submitted during this or last year has been cited.

\closing{Regards,}

Daniel B. Stouffer

\end{letter}

\end{document}

### 2016-07-09 paper/manuscript.Rmd
add supplemetary info

@@
 ---
+
 ```{r libraries, echo = FALSE, warning = F, message = F}
@@
 ```{r auxiliary functions, echo = FALSE, warning = F, message = F}
-"./code/V2.0/functions" %>% 
+"./code/functions" %>% 
 	list.files(full.names = T) %>%
@@
 ```{r read data and results, echo = FALSE, warning = F, message = F}
-net <- "./data/V2.0/networks" %>%
+net <- "./data/processed/networks" %>%
 	read_networks()
@@
 	dplyr::rename(count = method)
-n_matched <- readRDS("./data/V2.0/n_matched.rds")
-a_m <- readRDS("./data/V2.0/n_matched_all_types.rds") 
-r_w <- readRDS("./data/V2.0/random_weights.rds") %>% dplyr::tbl_df() %>%
+n_matched <- readRDS("./data/processed/n_matched.rds")
+a_m <- readRDS("./data/processed/n_matched_all_types.rds") 
+r_w <- readRDS("./data/processed/random_weights.rds") %>% dplyr::tbl_df() %>%
   dplyr::rename_("net_name" = ".id")
-r_d <- readRDS("./data/V2.0/random_directions.rds") %>% dplyr::tbl_df() %>%
+r_d <- readRDS("./data/processed/random_directions.rds") %>% dplyr::tbl_df() %>%
   dplyr::rename_("net_name" = ".id")
-s_p <- readRDS("./data/V2.0/species_properties.rds") %>% dplyr::tbl_df()
+s_p <- readRDS("./data/processed/species_properties.rds") %>% dplyr::tbl_df()
 # mod <- readRDS("./data/V2.0/species_models.rds")
-driver <- c("./data/V2.0/matching_frequency") %>% 
+driver <- c("./data/processed/matching_frequency") %>% 
   list.files(full.names = T) %>%
@@
 }, driver, prop)
-driver_bi <- "./data/V2.0/matching_frequency_bi" %>% 
+driver_bi <- "./data/processed/matching_frequency_bi" %>% 
   read_allRDS()
-mod <- readRDS("./data/V2.0/detailed_species_models.rds")
-mo <- readRDS("./data/V2.0/detailed_species_models_data.rds")
+mod <- readRDS("./data/processed/detailed_species_models.rds")
+mo <- readRDS("./data/processed/detailed_species_models_data.rds")
 ```
@@
 
-Center of Integrative Ecology, School of Biological Sciences, University of Canterbury, 8041 Christchurch, New Zealand
+Centre for Integrative Ecology, School of Biological Sciences, University of Canterbury, 8041 Christchurch, New Zealand
 
@@
 The structure of all networks was determined using visitation frequency which has been shown to be an appropriate surrogate for interspecific effects in pollination networks [@Vazquez2005; @Bascompte2006].
-To examine whether this decision would influence our results, we also evaluated the effect of using pollinator efficiency or importance as alternative measures of species interactions in a different dataset [@NeEman2010; @Ballantyne2015], and we found quantitatively similar results for all of these options (see Supplementary Information).
+To examine whether this decision would influence our results, we also evaluated the effect of using pollinator efficiency or importance as alternative measures of species interactions in a different dataset [@NeEman2010; @Ballantyne2015], and we found quantitatively similar results for all of these options (Supplementary Information S1).
 
@@
 The extent to which a species $i$ affects species $j$ relative to the extent to which species $j$ affects species $i$ can be summarised by the interaction asymmetry given by $$a(i,j) = \frac{\left | d_{ij}-d_{ji} \right |}{max\left ( d_{ij}, d_{ji} \right )}.$$
-Employing an unidrectional interaction asymmetry, as a surrogate of bidirectional mutual dependences, confers an additional advantage for our purposes since it dramatically reduces the number of links in the network.
+Employing an unidrectional interaction asymmetry, as a surrogate of bidirectional mutual dependences, does not alter the relative manageabilities of different networks (Supplementary Information S2). 
+Moreover, it confers an additional advantage for our purposes since it dramatically reduces the number of links in the network. 
 This translates into a substantial reduction of the time and memory required for the computation of of all possible maximum matchings in a network, particularly for large networks (see ''relative importance of species'' subsection below).
@@
 We then calculated the frequency with which each species is deemed to be a superior node in the set of matchings that had a total weight greater or equal to 0.5 times the weight of the maximum matching.
-We selected this threshold as it provided a high agreement between networks quantified by visitation and pollination efficiency as well as between our weighting/directionality assumptions (mutual dependences and interaction asymmetries); however, the choice of this threshold had a negligible impact on the results (Supplementary Information).
+We selected this threshold as it provided a high agreement between networks quantified by visitation and pollination efficiency as well as between our weighting/directionality assumptions (mutual dependences and interaction asymmetries); however, the choice of this threshold had a negligible impact on the results (Supplementary Information S3).
 
@@
 data <- mo
-net <- "./data/V2.0/networks" %>%
+net <- "./data/processed/networks" %>%
 	read_networks()

### 2016-07-09 paper/supp_info.Rmd
add supplemetary info

@@
 ---
-title: "Supplementary Information"
-classoption: a4paper
-output:
-  pdf_document:
-    fig_caption: yes
-    fig_crop: no
-    number_sections: yes
+title: "Biotic invasions reduce the manageability of mutualistic networks"
+csl: ecology-letters.csl
+output: pdf_document
+subtitle: "Supplementary information"
 bibliography: references.bib
@@
 library(ggplot2)
+library(glmulti)
+library(Hmisc)
+library(lme4)
 opts_knit$set (root.dir=normalizePath('../'))
@@
 ```{r auxiliary functions, echo = FALSE, warning = F, message = F}
-"./code/V2.0/functions" %>% 
+"./code/functions" %>% 
 	list.files(full.names = T) %>%
 	plyr::l_ply(source)
-
-# figure counter
-fig_count <- dplyr::data_frame(ref = "NA", count = 0)
-fig_n <- function(ref) {
-  fig_count <<- rbind(fig_count,
-                      dplyr::data_frame(ref = ref,
-                                        count = dplyr::last(fig_count$count) + 1))
-  return(dplyr::last(fig_count$count))
-}
-fig_r <- function(ref) fig_count$count[fig_count$ref == ref]
-
-# table counter
-tbl_count <- dplyr::data_frame(ref = "NA", count = 0)
-tbl_n <- function(ref) {
-  tbl_count <<- rbind(tbl_count,
-                      dplyr::data_frame(ref = ref,
-                                        count = dplyr::last(tbl_count$count) + 1))
-  return(dplyr::last(tbl_count$count))
-}
-tbl_r <- function(ref) tbl_count$count[tbl_count$ref == ref]
 ```
@@
 	dplyr::rename(count = method)
-n_matched <- readRDS("./data/V2.0/n_matched.rds")
-m_f <- readRDS("./data/V2.0/matching_frequency.rds")
+n_matched <- readRDS("./data/processed/n_matched.rds")
+a_m <- readRDS("./data/processed/n_matched_all_types.rds") 
+r_w <- readRDS("./data/processed/random_weights.rds") %>% dplyr::tbl_df() %>%
+  dplyr::rename_("net_name" = ".id")
+r_d <- readRDS("./data/processed/random_directions.rds") %>% dplyr::tbl_df() %>%
+  dplyr::rename_("net_name" = ".id")
+s_p <- readRDS("./data/processed/species_properties.rds") %>% dplyr::tbl_df()
+# mod <- readRDS("./data/processed/species_models.rds")
+driver <- c("./data/processed/matching_frequency") %>% 
+  list.files(full.names = T) %>%
+  lapply(list.files, full.names = T) %>% 
+  unlist() %>% 
+  lapply(read_allRDS)
+prop <- expand.grid(c("asymmetry", "max_dep"), 
+                    c("scaled_FALSE", "scaled_TRUE")) %>% plyr::alply(1)
+driver <- mapply(function(x, y){
+  attr(x, "type") <- as.character(y[,1])
+  attr(x, "scaled") <- stringr::str_split(as.character(y[,2]), "_") %>% unlist() %>% extract(2) %>% as.logical()
+  return(x)
+}, driver, prop)
+driver_bi <- "./data/processed/matching_frequency_bi" %>% 
+  read_allRDS()
+mod <- readRDS("./data/processed/detailed_species_models.rds")
+mo <- readRDS("./data/processed/detailed_species_models_data.rds")
 ```
 
-# Visitation frequency vs. pollen deposition
+*Table S1: Properties of the analysed plant-pollinator communities.
+$n_d$ and manageability values correspond to the assumption  that a species that depends more strongly on an interaction partner is controled by the partner.
+British networks were assembled by @Lopezaraiza-Mikel2007, Spanish were networks assembled by @Bartomeus2008.*
+```{r n_driver, echo = FALSE, warning = F, message = F, results = "asis"}
+# find n_driver
+n_driver <- n_matched %>%
+  dplyr::full_join(meta) %>% 
+  dplyr::filter(!is.na(inv)) %>%
+  dplyr::mutate(n_dr = n_pla + n_pol - n_matched,
+                n_dr_p = n_matched / (n_pla + n_pol))
 
-The number of driver species in a pollination community and the relative importance of each species depend both of the strength of mutual dependencies between plant pollinators and the structure of the pollination network.
-Traditionally pollination networks have been represented using visitation frequency, but a flower visitor is not necessarely a pollinator.
-It has been shown that wether pollination networks are represented using visitation or actual pollen deposition can have effects on the network structure and presumably on the strength of mutuial dependency.
+n_driver %>%
+  dplyr::select(site, inv, n_pla, n_pol, n_dr, n_dr_p, study) %>%
+  dplyr::arrange(study, site, inv) %>%
+  dplyr::mutate(site = rep(1:dplyr::n_distinct(site), each = 2),
+                inv = plyr::mapvalues(inv, c(TRUE, FALSE), c("yes", "no")),
+                n_dr_p = round(n_dr_p, digits = 2),
+                study = plyr::mapvalues(study, 
+                                        c("bartomeus", "lopezaraiza"),
+                                        c("Cap de Creus, Spain",
+                                          "Bristol, United Kingdom"))) %>%
+  dplyr::rename_("invaded" = "inv",
+                 "No. pla." = "n_pla",
+                 "No. pol." = "n_pol",
+                 "$n_d$" = "n_dr",
+                 "manageability" = "n_dr_p",
+                 "source" = "study") %>%
+  kable(align = "c", booktabs = T, 
+        linesep = c("", "\\addlinespace"), escape = F)
+```
 
-We investigated the effects of using visitation, pollen deposition (effective pollination) and pollinator importance (the product of visitation frequency and effective single visit pollen deposition).
-We used available data collected by @Ballantyne2015 from a low diversity pollination community at a dry lowland heathland in Dorset, UK (50° 43.7'N 2° 07.2'W).
+\newpage
 
-Deposition networks, a proxy pollinator efficiency, were quantified using the mean Single Visit Deposition---the number of conspecific pollen grains effectively deposited on a virgin stigma during a single visit by a particular animal [@NeEman2010; @King2013; @Ballantyne2015].
-Visitation networks were constructed counting the visits to flowers during Single Visit Depositions.
-Pollinator importance networks were consrtucted as the product of pollinator efficiency and visit frequency.
+# S1: Visitation as a proxy for species interdependence
 
-```{r matrix representation, echo = FALSE, warning = F, message = F, fig.height=5.5}
-# get network weights 
+Visitation frequency has been shown to be an appropriate surrogate for inter-specific effects in pollination networks [@Vazquez2005; @Bascompte2006]. 
+Nevertheless visitation is not equivalent to pollen deposition and might be insufficient to reflect the dependencies of plants on animals and vice versa [@Alarcon2010; @King2013]. 
+We therefore investigated the effect of calculating the dependencies using visitation or pollination effectiveness and importance---two metrics more proximate to plant reproductive success (Figure S1).
+We did this by comparing *(i)* the manageability of the community and *(ii)* the percentage of interactions that maintained the direction of dependency. 
+To do that, we used data collected by @Ballantyne2015 from a low diversity pollination community at a dry lowland heathland in Dorset, UK  (50° 43.7'N 2° 07.2'W). 
+First, deposition networks were quantified using the mean Single Visit Deposition---the number of conspecific pollen grains effectively deposited on a virgin stigma during a single visit by a particular animal [@NeEman2010; @King2013; @Ballantyne2015].
+Second, visitation networks were constructed counting the visits to flowers during Single Visit Depositions. 
+Finally, pollinator importance networks were constructed as the product of pollinator efficiency and visit frequency.
+
+```{r get n_driver, echo = FALSE, warning = F, message = F}
+n_driver <- meta %>%
+  dplyr::inner_join(n_matched) %>% 
+  dplyr::mutate(n_driver = 1 - n_matched / (n_pla + n_pol))
+```
+
+We first investigated the effects at a network scale. 
+Despite marked differences in the distribution of weights of the three networks, the minimum number of driver species to control the whole community was consistent among the three different approaches (`r 1-round(n_driver$n_driver[n_driver$net_name == "bal_eff"], digits = 2)` for deposition, `r 1-round(n_driver$n_driver[n_driver$net_name == "bal_vis"], digits = 2)` for the visitation, and `r 1-round(n_driver$n_driver[n_driver$net_name == "bal_imp"], digits = 2)` for the pollinator importance network).
+
+The choice of weighting used can also have an impact on the relative importance of species.
+Therefore we calculated the frequency that each species is present in the possible sets of driver species under the three schemes. 
+Although visitation and deposition produce strikingly different results, we found a very strong agreement between the order produced by visitation and importance (Table S2). 
+Finally, we investigated whether the asymmetry of mutual dependency, which defines the direction of control, was consistent among the three possible weighting schemes.
+We found again that the direction of the dominant dependency was maintained was consistent for 95\% of the interactions weighted by visitation or importance, the two most appropriate metrics for pollinator and plant dependency (Table S2).
+
+All together, evidence supports the idea that visitation is a suitable metric to estimate the mutual dependency of species pairs.
+First it is directly related to pollinator foraging.
+Second it produces results consistent, at least within our controllability framework, with plant reproductive success (as estimated by the importance metric).
+
+```{r fig_visitation, echo = FALSE, warning = F, message = F, fig.height=4, fig.width=7, fig.align="center"}
 p <- net[meta$net_name[meta$study == "ballantyne" & meta$count != "binary"]] %>%
 	plyr::ldply(function(x) {
-		data.frame(vname = igraph::E(net[[1]]) %>% attr("vnames"), 
+		data.frame(vname = igraph::E(x) %>% attr("vnames"), 
 							weight = igraph::E(x)$weight)
-	}) %>%
+	}, .inform = T) %>%
 	dplyr::rename_("net_name" = ".id") %>%
@@
 ```
-*__Figure S`r fig_n("ballantyne_ntw")`:__ distribution of interaction weights for the pollen deposition, visitation and pollinator importance networks.
-Note that the _x_ axis in the density plots have been log-transformed.*
+_Figure S1: Distribution of interaction weights for the pollen deposition, visitation and pollinator importance networks. Note that the *x* axis in the density plots have been log-transformed._
 
-```{r, echo = FALSE, warning = F, message = F}
-n_driver <- meta %>%
-  dplyr::inner_join(n_matched) %>% 
-  dplyr::mutate(n_driver = 1 - n_matched / (n_pla + n_pol))
-```
+*Table S2: Spearman correlation coefficients (with p-value) of the relative importance of species and the percentage of interactions that share the direction of dependency obtained using the three weighting schemes and an unweighted scheme*
+```{r table correlations, echo = FALSE, warning = F, message = F, results = "asis"}
+d_sp <- driver %>%
+  plyr::ldply(function(x) {
+    get_frequencies(x) %>%
+      dplyr::mutate(type = attr(x, "type"),
+                    scaled = attr(x, "scaled"))
+  }) %>%
+  dplyr::inner_join(meta)
 
-We first investigated the effects at a network scale.
-Despite marked differences in the distribution of weights of the three networks (Figure S`r fig_r("ballantyne_ntw")`), the minimum number of driver species to control the whole community was consistent among the three different approaches (`r round(n_driver$n_driver[n_driver$net_name == "bal_eff"]*100)`% for deposition, `r round(n_driver$n_driver[n_driver$net_name == "bal_vis"]*100)`% for the visitation, and `r round(n_driver$n_driver[n_driver$net_name == "bal_imp"]*100)`% for the pollinator importance network).
-
-*__Table S`r tbl_n("corr_weights")`:__ spearman correlation coefficients (with p-value) of the relative importance of species and the percentage of interactions that share the direction of dependency obtained using the three weighting schemes and an unweighted scheme.
-Significant correlations are highlighted in bold.*
-```{r, echo = FALSE, warning = F, message = F}
-drivers_b <- m_f[meta$net_name[meta$study == "ballantyne"]] %>%
-	plyr::ldply(function(x){
-	  dplyr::data_frame(species = names(x),
-	                    d_freq = attr(x, "n_matchings") - x,
-	                    d_reim = 1 - x / attr(x, "n_matchings"),
-	                    d_rank = rank(d_reim, ties.method = "average"))
-	}) %>%
-	dplyr::rename_("net_name" = ".id")
-
-correlations <- drivers_b %>%
-  dplyr::select(net_name, species, d_freq) %>%
-  tidyr::spread(net_name, d_freq) %>%
+correlations <- d_sp %>%
+	dplyr::filter(study == "ballantyne",
+								threshold == 0.5,
+								type == "asymmetry",
+								scaled == F) %>%
+	dplyr::group_by(net_name, threshold, type, scaled) %>%
+	dplyr::mutate(d_weight = d_weight/max(d_weight),
+								d_rank = rank(-d_weight, ties.method = "average")) %>%
+	dplyr::group_by() %>%
+	dplyr::select(net_name, species, d_rank) %>%
+	tidyr::spread(net_name, d_rank) %>%
   dplyr::select(-species) %>%
@@
   b <- ""
-  if(y < 0.05) b <- "**"
-  paste0(b, round(x, digits = 2), " (", round(y, digits = 4), ")", b)
+  if(y < 0.05) b <- ""
+  paste0(b, round(x, digits = 2), " (", fix_small_pvalue(y, 3), ")", b)
 }
@@
     x %>% 
-      bipartite_digraph(type = "weight", keep = "all") %>%
+      bipartite_digraph(type = "weight", keep = "all", weight.type = "asymmetry") %>%
       igraph::ends(igraph::E(.)) %>% 
@@
     length(intersect(dir_net_b[[x[1]]], dir_net_b[[x[2]]])) /
-      length(igraph::E(net[[1]]))
+      length(dir_net_b[[x[1]]])
   }) %>%
@@
   matrix(ncol = length(dir_net_b)) %>% magrittr::set_colnames(nam) %>%
-  magrittr::set_rownames(nam) %>% `[<-`(lower.tri(.), lt) %>% kable(align = "c")
+  magrittr::set_rownames(nam) %>% `[<-`(lower.tri(.), lt) %>% 
+  kable(align = "c", booktabs = T)
+
 ```
 
-The choice of weighting used can also have an impact on the realtive importance of species.
-Therefore we calculated the frequency that each species is present in the possible sets of driver species under the three schemes.
-Although visitation and deposition produce strikingly different results, we found a very strong agreement between the order produced by visitation and importance (Table S`r tbl_r("corr_weights")`).
-Arguably, visitation best reflects the dependency of animals to plants, as usually animals forage for pollen or nectar regardless of wether effective pollination occurs or not.
-Contrastingly, importance, the product between visit frequency and pollinator effectiveness, best relefect the dependency of plants to animals.
+\newpage
 
-Finally, we investigated whether the asymmetry of mutual dependency, which defines the direction of control, was consistent among the three posible weighting schemes.
-We found again that the direction of the dominant dependency was mantained was consistent for 95% of the interactions weighted by visitation or importance (Table S`r tbl_r("corr_weights")`), the two most appropriate metrics for pollinator and plant dependency.
+# S2: Direction of control
 
-All together, evidence supports the idea that visitation is a suitable metric to estimate the mutual dependency of species pairs.
-First it is directly related to pollinator foraging.
-Second it produces results consistent, at least within our controllability framework, with plant reproductive success (as estimated by the importance metric).
+We calculated the number of driver species necessary to control the whole community under the assumption that a species that depends more strongly on an interaction partner is more likely to be controlled by the partner.
+We tested the robustness of this assumption by comparing the relative number of driver species assuming that *(i)* the dependency asymmetry does not imply an unidirectional control direction, rather a species could control all its interaction partners and vice versa, *(ii)* that plants depend on pollinators, and that *(iii)* pollinators depend on plants.
+Our results using the direction of the largest dependency are consistent with the proposed alternatives: although we obtained different absolute numbers of driver species, their relative numbers are not statistically different (Figure S3, Table S3).
+
+```{r explain matching pla-pol, echo = FALSE, warning = F, message = F, results = "asis", fig.height=4.2, fig.width=5.75, fig.align="center"}
+my_theme <- theme_bw() +
+	#scale_color_brewer(palette = "Paired") +
+	theme(legend.position = "none",
+				text = element_text(family = "Times"),
+				plot.margin=unit(c(4,0,-4,0),"mm"),
+				panel.margin=unit(c(0,0,0,0),"mm"),
+				# panel.border = element_rect(colour = "grey10", size = 0.5),
+				panel.border = element_blank(),
+				axis.text = element_blank(),
+				axis.ticks.x = element_blank(),
+				axis.ticks.y = element_blank(),
+				axis.title = element_text(size = 9),
+				plot.title = element_text(hjust = 0.05, vjust = -1.5, size = 9),
+				panel.grid = element_blank())
+
+# Function to generate paths between each connected node
+edgeMaker <- function(whichRow, len = 100, curved = TRUE){
+	fromC <- layoutCoordinates[adj_list[whichRow, 1], ]  # Origin
+	toC <- layoutCoordinates[adj_list[whichRow, 2], ]  # Terminus
+
+	# Add curve:
+	graphCenter <- colMeans(layoutCoordinates)  # Center of the overall graph
+	bezierMid <- c(fromC[1], toC[2])  # A midpoint, for bended edges
+	distance1 <- sum((graphCenter - bezierMid)^2)
+	if(distance1 < sum((graphCenter - c(toC[1], fromC[2]))^2)){
+		bezierMid <- c(toC[1], fromC[2])
+	}  # To select the best Bezier midpoint
+	bezierMid <- (fromC + toC + bezierMid) / 3  # Moderate the Bezier midpoint
+	if(curved == FALSE){bezierMid <- (fromC + toC) / 2}  # Remove the curve
+
+	edge <- data.frame(bezier(c(fromC[1], bezierMid[1], toC[1]),  # Generate
+														c(fromC[2], bezierMid[2], toC[2]),  # X & y
+														evaluation = len))  # Bezier path coordinates
+	edge$Sequence <- 1:len  # For size and colour weighting in plot
+	edge$Group <- paste(adj_list[whichRow, 1:2], collapse = ">")
+	return(edge)
+}
+
+############## First ################
+
+sp_names <- c("a[1]", "a[2]", "a[3]", "p[1]", "p[2]")
+
+adj_matrix <- c(0,0,0,0,0,
+								0,0,0,0,0,
+								0,0,0,0,0,
+								1,1,1,0,0,
+								0,1,1,0,0) %>%
+	matrix(nrow = 5, byrow = T) %>%
+	`rownames<-`(sp_names) %>%
+	`colnames<-`(sp_names)
+
+net_exp <- adj_matrix %>% 
+	igraph::graph_from_adjacency_matrix(mode = "directed") 
+igraph::V(net_exp)$type <- c(F, F, F, T, T)
+igraph::E(net_exp)$weight <- 1
+
+layoutCoordinates <- cbind(c(0,1,2,0.5,1.5), 
+													 c(1,1,1,0,0)) %>%
+	`colnames<-`(c("x", "y"))
+
+adj_list <- adj_matrix %>% 
+	reshape2::melt() %>% 
+	dplyr::filter(value > 0)
+
+# Generate an edge path for each pair of connected nodes
+n <- 17
+allEdges <- lapply(1:nrow(adj_list), edgeMaker, len = n, curved = FALSE)
+allEdges <- do.call(rbind, allEdges) %>%
+	dplyr::filter(Sequence != n) %>%
+	dplyr::mutate(Group = factor(Group),
+				 type = Group)
+
+new_lev <- c("m", "u", "u", "m", "u")
+levels(allEdges$type) <- new_lev
+
+nodes <- data.frame(layoutCoordinates) %>%
+	dplyr::mutate(spe = sp_names,
+								spe_c = c("m", "m", "u", "u", "u"), 
+								pos = rep(c(0.25, -0.25), c(3,2)))
+
+p1 <- ggplot(allEdges) +  # Pretty simple plot code
+	geom_path(aes(x = x, y = y, group = Group, colour = type, size = type), 
+						arrow = arrow(type = "closed", angle = 15, length = grid::unit(0.1, "inches"))) + # and taper
+	geom_point(data = nodes,  # Add nodes
+						 aes(x = x, y = y , fill = spe_c), size = 5, pch = 21,
+						 colour = "black") + 
+	geom_text(data = nodes, aes(x = x, y = y + pos, label = spe), size = 3, parse = T) +
+	scale_fill_manual(values = c("#636363", "white")) + 
+	scale_colour_manual(values = c("#636363", "#bdbdbd")) +
+	my_theme + xlab("") + ylab("") + ylim(c(-0.27, 1.26)) +
+ theme(plot.margin=unit(c(4,4,-4,-4),"mm")) +
+	scale_size_manual(values = c(0.5, 0.5))
+
+net_exp <- digraph_bipartite(net_exp)
+adj_matrix <- net_exp %>% igraph::as_adjacency_matrix(sparse = F, type = "upper")
+layoutCoordinates <- cbind(rep(0:4, 2), rep(c(1,0), each = 5)) %>%
+	`colnames<-`(c("x", "y"))
+
+adj_list <- adj_matrix %>% 
+	reshape2::melt() %>% 
+	dplyr::filter(value > 0)
+
+# Generate an edge path for each pair of connected nodes
+n <- 100
+allEdges <- lapply(1:nrow(adj_list), edgeMaker, len = n, curved = FALSE)
+allEdges <- do.call(rbind, allEdges) %>%
+	dplyr::filter(Sequence != n,
+								Sequence != 1) %>%
+	dplyr::mutate(Group = factor(Group),
+				 type = Group)
+
+new_lev <- c("m", "u", "u", "m", "u")
+levels(allEdges$type) <- new_lev
+
+nodes <- data.frame(layoutCoordinates) %>%
+	dplyr::mutate(spe = rep(sp_names, 2),
+								spe_l = c(paste0(sp_names, " %->% phantom(0)"), paste0(sp_names, " %<-% phantom(0)")),
+								spe_c = c(rep("u",5), c("m", "m", "u", "u", "u")), 
+								pos = rep(c(0.25, -0.25), each = 5))
+
+p2 <- ggplot(allEdges) +  # Pretty simple plot code
+	geom_path(aes(x = x, y = y, group = Group, colour = type, size = type)) + # and taper
+	geom_point(data = nodes,  # Add nodes
+						 aes(x = x, y = y, fill = spe_c), size = 5, pch = 21,
+						 colour = "black") + 
+	geom_text(data = nodes, aes(x = x + 0.08, y = y + pos, label = spe_l), parse = T, size = 3) +
+	# coord_flip()  + scale_x_reverse() + scale_y_reverse() +
+	scale_fill_manual(values = c("#636363", "white")) + 
+	scale_colour_manual(values = c("#636363", "#bdbdbd")) +
+	xlim(c(-0.12, 4.12)) + ylim(c(-0.27, 1.26)) +
+	my_theme + xlab("") + ylab("") +
+	scale_size_manual(values = c(0.5, 0.5))
+
+############### Second ##########
+
+sp_names <- c("a[1]", "a[2]", "a[3]", "p[1]", "p[2]")
+
+adj_matrix <- c(0,0,0,1,0,
+								0,0,0,1,1,
+								0,0,0,1,1,
+								0,0,0,0,0,
+								0,0,0,0,0) %>%
+	matrix(nrow = 5, byrow = T) %>%
+	`rownames<-`(sp_names) %>%
+	`colnames<-`(sp_names)
+
+net_exp <- adj_matrix %>% 
+	igraph::graph_from_adjacency_matrix(mode = "directed") 
+igraph::V(net_exp)$type <- c(F, F, F, T, T)
+igraph::E(net_exp)$weight <- 1
+
+layoutCoordinates <- cbind(c(0,1,2,0.5,1.5), 
+													 c(1,1,1,0,0)) %>%
+	`colnames<-`(c("x", "y"))
+
+adj_list <- adj_matrix %>% 
+	reshape2::melt() %>% 
+	dplyr::filter(value > 0)
+
+# Generate an edge path for each pair of connected nodes
+n <- 17
+allEdges <- lapply(1:nrow(adj_list), edgeMaker, len = n, curved = FALSE)
+allEdges <- do.call(rbind, allEdges) %>%
+	dplyr::filter(Sequence != n) %>%
+	dplyr::mutate(Group = factor(Group),
+				 type = Group)
+
+new_lev <- c("m", "u", "m", "u", "u")
+levels(allEdges$type) <- new_lev
+
+nodes <- data.frame(layoutCoordinates) %>%
+	dplyr::mutate(spe = sp_names,
+								spe_c = c("u", "u", "u", "m", "m"), 
+								pos = rep(c(0.25, -0.25), c(3,2)))
+
+p3 <- ggplot(allEdges) +  # Pretty simple plot code
+	geom_path(aes(x = x, y = y, group = Group, colour = type, size = type), 
+						arrow = arrow(type = "closed", angle = 15, length = grid::unit(0.1, "inches"))) + # and taper
+	geom_point(data = nodes,  # Add nodes
+						 aes(x = x, y = y , fill = spe_c), size = 5, pch = 21,
+						 colour = "black") + 
+	geom_text(data = nodes, aes(x = x, y = y + pos, label = spe), size = 3, parse = T) +
+	scale_fill_manual(values = c("#636363", "white")) + 
+	scale_colour_manual(values = c("#636363", "#bdbdbd")) +
+	my_theme + xlab("") + ylab("") + ylim(c(-0.27, 1.26)) +
+ theme(plot.margin=unit(c(4,4,-4,-4),"mm")) +
+	scale_size_manual(values = c(0.5, 0.5))
+
+net_exp <- digraph_bipartite(net_exp)
+adj_matrix <- net_exp %>% igraph::as_adjacency_matrix(sparse = F, type = "upper")
+layoutCoordinates <- cbind(rep(0:4, 2), rep(c(1,0), each = 5)) %>%
+	`colnames<-`(c("x", "y"))
+
+adj_list <- adj_matrix %>% 
+	reshape2::melt() %>% 
+	dplyr::filter(value > 0)
+
+# Generate an edge path for each pair of connected nodes
+n <- 100
+allEdges <- lapply(1:nrow(adj_list), edgeMaker, len = n, curved = FALSE)
+allEdges <- do.call(rbind, allEdges) %>%
+	dplyr::filter(Sequence != n,
+								Sequence != 1) %>%
+	dplyr::mutate(Group = factor(Group),
+				 type = Group)
+
+new_lev <- c("m", "m", "u", "u", "u")
+levels(allEdges$type) <- new_lev
+
+nodes <- data.frame(layoutCoordinates) %>%
+	dplyr::mutate(spe = rep(sp_names, 2),
+								spe_l = c(paste0(sp_names, " %->% phantom(0)"), paste0(sp_names, " %<-% phantom(0)")),
+								spe_c = c(rep("u",5), c("u", "u", "u", "m", "m")), 
+								pos = rep(c(0.25, -0.25), each = 5))
+
+p4 <- ggplot(allEdges) +  # Pretty simple plot code
+	geom_path(aes(x = x, y = y, group = Group, colour = type, size = type)) + # and taper
+	geom_point(data = nodes,  # Add nodes
+						 aes(x = x, y = y, fill = spe_c), size = 5, pch = 21,
+						 colour = "black") + 
+	geom_text(data = nodes, aes(x = x + 0.08, y = y + pos, label = spe_l), parse = T, size = 3) +
+	# coord_flip()  + scale_x_reverse() + scale_y_reverse() +
+	scale_fill_manual(values = c("#636363", "white")) + 
+	scale_colour_manual(values = c("#636363", "#bdbdbd")) +
+	xlim(c(-0.12, 4.12)) + ylim(c(-0.27, 1.26)) +
+	my_theme + xlab("") + ylab("") +
+	scale_size_manual(values = c(0.5, 0.5))
+
+############ Third ################
+
+sp_names <- c("a[1]", "a[2]", "a[3]", "p[1]", "p[2]")
+
+adj_matrix <- c(0,0,0,1,0,
+								0,0,0,1,1,
+								0,0,0,1,1,
+								1,1,1,0,0,
+								0,1,1,0,0) %>%
+	matrix(nrow = 5, byrow = T) %>%
+	`rownames<-`(sp_names) %>%
+	`colnames<-`(sp_names)
+
+net_exp <- adj_matrix %>% 
+	igraph::graph_from_adjacency_matrix(mode = "directed") 
+igraph::V(net_exp)$type <- c(F, F, F, T, T)
+igraph::E(net_exp)$weight <- 1
+
+layoutCoordinates <- cbind(c(0,1,2,0.5,1.5), 
+													 c(1,1,1,0,0)) %>%
+	`colnames<-`(c("x", "y"))
+
+adj_list <- adj_matrix %>% 
+	reshape2::melt() %>% 
+	dplyr::filter(value > 0)
+
+# Generate an edge path for each pair of connected nodes
+n <- 17
+allEdges <- lapply(1:nrow(adj_list), edgeMaker, len = n, curved = FALSE)
+allEdges <- do.call(rbind, allEdges) %>%
+	dplyr::filter(Sequence != n) %>%
+	dplyr::mutate(Group = factor(Group),
+				 type = Group)
+
+new_lev <- c("m", "u", "m", "u", "u", "u", "m", "u", "u", "m")
+dir <- c("m", "m", "m", "m", "m", "u", "u", "u", "u", "u")
+dir2 <- c("m", "u", "m", "u", "u", "u", "m", "m", "u", "m")
+id <- 1:10
+allEdges %<>% dplyr::mutate(dir = type,
+                            dir2 = dir)
+levels(allEdges$type) <- new_lev
+levels(allEdges$dir) <- dir
+levels(allEdges$dir2) <- dir2
+allEdges %<>% 
+  dplyr::mutate(dir = as.numeric(dir),
+                dir2 = as.numeric(dir2),
+                dir = plyr::mapvalues(dir, c(1,2), c(0.03, -0.03)),
+                dir2 = plyr::mapvalues(dir2, c(1,2), c(0.03, -0.03)))
+
+nodes <- data.frame(layoutCoordinates) %>%
+	dplyr::mutate(spe = sp_names,
+								spe_c = c("u", "m", "m", "m", "m"), 
+								pos = rep(c(0.25, -0.25), c(3,2)))
+
+# ggplot(allEdges) +  # Pretty simple plot code
+# 	geom_path(aes(x = x + dir, y = y + dir2, group = Group, colour = type, size = type), 
+# 						arrow = arrow(type = "closed", angle = 15, length = grid::unit(0.1, "inches")))
+
+p5 <- ggplot(allEdges) +  # Pretty simple plot code
+	geom_path(aes(x = x + dir, y = y + dir2, group = Group, colour = type, size = type), 
+						arrow = arrow(type = "closed", angle = 15, length = grid::unit(0.1, "inches"))) + # and taper
+	geom_point(data = nodes,  # Add nodes
+						 aes(x = x, y = y , fill = spe_c), size = 5, pch = 21,
+						 colour = "black") + 
+	geom_text(data = nodes, aes(x = x, y = y + pos, label = spe), size = 3, parse = T) +
+	scale_fill_manual(values = c("#636363", "white")) + 
+	scale_colour_manual(values = c("#636363", "#bdbdbd")) +
+	my_theme + xlab("") + ylab("") + ylim(c(-0.27, 1.26)) +
+ theme(plot.margin=unit(c(4,4,-4,-4),"mm")) +
+	scale_size_manual(values = c(0.5, 0.5))
+
+net_exp <- digraph_bipartite(net_exp)
+adj_matrix <- net_exp %>% igraph::as_adjacency_matrix(sparse = F, type = "upper")
+layoutCoordinates <- cbind(rep(0:4, 2), rep(c(1,0), each = 5)) %>%
+	`colnames<-`(c("x", "y"))
+
+adj_list <- adj_matrix %>% 
+	reshape2::melt() %>% 
+	dplyr::filter(value > 0)
+
+# Generate an edge path for each pair of connected nodes
+n <- 100
+allEdges <- lapply(1:nrow(adj_list), edgeMaker, len = n, curved = FALSE)
+allEdges <- do.call(rbind, allEdges) %>%
+	dplyr::filter(Sequence != n,
+								Sequence != 1) %>%
+	dplyr::mutate(Group = factor(Group),
+				 type = Group)
+
+new_lev <- c("m", "m", "u", "u", "u", "u", "m", "u", "u", "m")
+levels(allEdges$type) <- new_lev
+
+nodes <- data.frame(layoutCoordinates) %>%
+	dplyr::mutate(spe = rep(sp_names, 2),
+								spe_l = c(paste0(sp_names, " %->% phantom(0)"), paste0(sp_names, " %<-% phantom(0)")),
+								spe_c = c(rep("u",5), c("u", "m", "m", "m", "m")), 
+								pos = rep(c(0.25, -0.25), each = 5))
+
+p6 <- ggplot(allEdges) +  # Pretty simple plot code
+	geom_path(aes(x = x, y = y, group = Group, colour = type, size = type)) + # and taper
+	geom_point(data = nodes,  # Add nodes
+						 aes(x = x, y = y, fill = spe_c), size = 5, pch = 21,
+						 colour = "black") + 
+	geom_text(data = nodes, aes(x = x + 0.08, y = y + pos, label = spe_l), parse = T, size = 3) +
+	# coord_flip()  + scale_x_reverse() + scale_y_reverse() +
+	scale_fill_manual(values = c("#636363", "white")) + 
+	scale_colour_manual(values = c("#636363", "#bdbdbd")) +
+	xlim(c(-0.12, 4.12)) + ylim(c(-0.27, 1.26)) +
+	my_theme + xlab("") + ylab("") +
+	scale_size_manual(values = c(0.5, 0.5))
+
+cowplot::plot_grid(p1, p2, p3, p4, p5, p6, 
+									 ncol = 2, 
+									 rel_widths = c(3,5),
+									 labels = c("a", "", "b", "", "c", ""),
+									 label_size = 10,
+									 hjust = 0, vjust = 1)
+```
+*Figure S2: One of the possible maximum matchings for each of the assumptions regarding the direction of control: a) plants can drive the abbundance of pollinators but not otherwise, b) pollinators can drive the abbundance of plants but not otherwise; c) plants can drive the abbundance of pollinators with the same likelyhood than pollinators can modify the abbundance of plants*
+
+```{r fig alternative assumptions, echo = FALSE, warning = F, message = F, fig.height=1.5, fig.width=4.3, fig.align="center"}
+a_m_driver <- a_m %>% 
+  dplyr::full_join(meta) %>%
+  dplyr::filter(study != "ballantyne") %>% 
+  dplyr::mutate(type = factor(type, 
+                              levels =  c("AB", "BA", "weight", "z-bi"),
+                              labels = c("pla. to pol.", "pol. to pla.", "dependency", "bidirectional")),
+                type_l  = as.character(type)) %>%
+  dplyr::mutate(n_driver = n_pla + n_pol - n_matched, 
+                n_driver_rel = 1 - n_matched / (n_pla + n_pol))
+
+type_l <- unique(a_m_driver$type_l)
+
+a_m_driver %>%
+  ggplot(aes(x = type, y = 1 - n_driver_rel), parse = T) +
+  geom_boxplot(size = 0.25, colour = "grey10",
+							 outlier.shape = 21, outlier.size = 1) +
+  coord_flip() + 
+  xlab("") +
+  ylab("manageability") + 
+  fer_theme + 
+  theme(plot.margin = grid::unit(c(0,1,2,0), "mm"))
+
+```
+*Figure S3: Proportion of driver species necessary to control the full pollination network under four different assumptions of the direction of control.*
+
+*Table S3: pearman correlation coefficients of the number of driver species necessary to control the full pollination network under the four different assumptions of the direction of control.*
+```{r table alternative assumptions, echo = FALSE, warning = F, message = F, results = "asis"}
+
+corr_matrix <- a_m_driver %>%
+  dplyr::select(net_name, type, n_driver) %>%
+  tidyr::spread(type, n_driver) %>%
+  dplyr::select(-net_name) %>%
+  as.matrix() %>%
+  cor(method = "spearman") %>%
+  round(digits = 2)
+
+corr_matrix[lower.tri(corr_matrix, diag = T)] <- ""
+corr_matrix <- corr_matrix[, -1]
+corr_matrix <- corr_matrix[-(nrow(corr_matrix)), ]
+kable(corr_matrix, align = "c", booktabs = T)
+
+```
+
+\newpage
+
+# S3: Threshold
+
+To calculate the relative importance of a species we calculated the frequency at which they are superior nodes in a set of accepted maximal matchings.
+Maximal matchings were accepted if the matching weight was over a certain threshold.
+The threshold was defined as a proportion of the maximum matching's weight.
+
+The number of accepted maximal matchings increased rapidly as the threshold at which they are accepted decreases.
+Nevertheless this number stabilises below approximately 0.6-0.7 for both the mutual dependence and the interaction asymmetry weightings.
+
+```{r number maximal matchings, echo = FALSE, warning = F, message = F, fig.height=2.5, fig.width=7, fig.align="center"}
+d_sp_bi <- driver_bi %>%
+  get_frequencies() %>%
+      dplyr::mutate(type = "z_bi",
+                    scaled = FALSE) %>%
+  dplyr::inner_join(meta)
+
+d_sp <- d_sp %>% dplyr::bind_rows(d_sp_bi)
+
+d_sp %>%
+	dplyr::filter(scaled == FALSE, 
+								study != "ballantyne", 
+								type != "max_dep") %>%
+	dplyr::mutate(type = plyr::mapvalues(type, c("asymmetry", "z_bi"),
+																			 c("interaction asymmetry",
+																			 	"mutual dependence"))) %>%
+	dplyr::group_by(net_name, threshold, type) %>%
+	dplyr::summarise(n_matchings = mean(n_matchings)) %>%
+	ggplot(aes(x = threshold, y = n_matchings, group = interaction(net_name, type))) +
+	geom_point(shape = 21) +
+	geom_line() +
+	scale_x_continuous(breaks = seq(0,1, by = 0.1)) + 
+	scale_y_log10() +
+	facet_wrap(~type) +
+	fer_theme + 
+  theme(plot.margin = grid::unit(c(0,1,2,0), "mm")) +
+	ylab("number of maximal matchings")
+
+```
+*Figure S4: Number of maximal matchings as a function of the threshold. Each line correspond to one network.*
+
+Next we examined how the relative importance of species changes with the chosen threshold.
+When only maximum matchings are accepted (threshold is one) species tend to be superior nodes in all or none of the matchings, which equates to relative importances of one or zero.
+Using the weights given my the mutual dependencies some species reach intermediate levels of importance as the threshold decreases.
+Contrastingly, this pattern is not observed when weights are given by the interaction asymmetry.
+In this case the stark contrast between important and unimportant species is maintained in most cases.
+
+Finally, we performed some tests to evaluate the impact that choosing a particular threshold would have in our results.
+First, using the data in @Ballantyne2015, we calculated the correlation between the relative importance of species in two network representations of the community: *(i)* the visitation network weighted by the interaction asymmetries, and *(ii)* the pollination importance network weighted by the bidirectional mutual dependences.
+The first network representation correspond to the type of networks used on all our analyses, while the second is a representation closer to the actual interspecific effects that underpin community dynamics.
+We calculated these correlations using the weighted rank correlation coefficient, which is biased to give more relevance to the agreement of the most important species [@PintoDaCosta2015].
+Second, in a similar fashion to the previous comparison, for the paired invaded-uninvaded networks, we calculated the correlation between the relative importance of species obtained when the maximum matchings were calculated on a network weighted by the interaction asymmetries and weighted by the mutual dependences.
+
+We found that any threshold that as long as some maximal matchings with a weight smaller than the maximum, the choice of the threshold has little impact on the consistency of the results obtained using different approaches.
+We chose 0.5 as it showed the largest mean correlation between mutual dependences and interaction asymmetries.
+Nevertheless, the difference was marginal and any threshold <= 0.9 would have provided very similar results.
+
+```{r rel importance vs. threshold, echo = FALSE, warning = F, message = F, fig.height=8.8, fig.width=7, fig.align="center"}
+net_desc <- n_matched %>%
+  dplyr::full_join(meta) %>% 
+  dplyr::filter(!is.na(inv)) %>%
+  dplyr::mutate(n_dr = n_pla + n_pol - n_matched,
+                n_dr_p = n_matched / (n_pla + n_pol)) %>%
+  dplyr::select(site, inv, n_pla, n_pol, n_dr, n_dr_p, study, net_name) %>%
+  dplyr::arrange(study, site, inv) %>%
+  dplyr::mutate(site = rep(1:dplyr::n_distinct(site), each = 2),
+  							inv = plyr::mapvalues(inv, c(TRUE, FALSE), c("inv.", "uninv.")),
+  							desc = paste(site, "-", inv)) %>%
+	dplyr::select(net_name, desc)
+
+cor_d_sp <- d_sp %>%
+	dplyr::group_by(net_name, threshold, type, scaled) %>%
+	dplyr::mutate(d_weight = d_weight/max(d_weight),
+								d_imp = d_freq/n_matchings,
+								d_rank = rank(-d_imp, ties.method = "average")) %>%
+	dplyr::group_by() %>%
+	dplyr::filter(net_name %in% unique(d_sp_bi$net_name),
+								scaled == FALSE, 
+								type != "max_dep")
+
+cor_d_sp %>%
+	dplyr::mutate(type = plyr::mapvalues(type, c("asymmetry", "z_bi"),
+																			 c("interaction asymmetry",
+																			 	"mutual dependence"))) %>%
+	dplyr::filter(study != "ballantyne") %>%
+	dplyr::group_by(net_name, type, scaled, species) %>%
+	dplyr::arrange(threshold) %>%
+	dplyr::mutate(i_imp = dplyr::first(d_imp)) %>%
+	dplyr::group_by() %>%
+	dplyr::inner_join(net_desc) %>%
+	ggplot(aes(x = threshold, y = d_imp)) +
+	geom_line(aes(group = interaction(species, net_name, type, scaled),
+								colour = i_imp)) +
+	geom_point(aes(colour = i_imp), size = 1) +
+	facet_grid(desc~type) +
+	fer_theme + 
+  theme(plot.margin = grid::unit(c(0,1,2,0), "mm"), 
+  			legend.position = "none") +
+	scale_colour_gradient2(low = "#377eb8", high = "#e41a1c", mid = "grey", midpoint = 0.5) + 
+	ylab("relative species importance")
+```
+*Figure S5: Relative importance of species for different thresholds.
+Each line correspond to a species within a network.
+The colour of the line corresponds to the relative importance obtained when all maximal matchings are accepted (threshold is zero).
+Only networks for which we were able to calculate the relative importance using mutual dependences are shown, but patterns of relative importance calculated using interaction asymetries are similar for the remainding networks.
+Network numbers correspond to those in Table S1.*
+
+```{r correlations, echo = FALSE, warning = F, message = F, fig.height=2, fig.width=7, fig.align="center"}
+p1 <- cor_d_sp %>%
+	dplyr::filter(study == "ballantyne") %>%
+	plyr::ddply("threshold", function(x){
+		x %<>%
+			dplyr::filter((type == "asymmetry" & count == "visitation") |
+											(type == "z_bi" & count == "importance")) %>%
+			dplyr::mutate(class = paste(type, count, sep = ".")) %>%
+			dplyr::select(species, class, d_rank) %>%
+			tidyr::spread(class, d_rank)
+		rw2(x$asymmetry.visitation, x$z_bi.importance)
+	}) %>%
+	ggplot(aes(x = threshold, y = V1)) +
+	geom_point() +
+	geom_line() +
+	scale_x_continuous(breaks = seq(0, 1, 0.1)) +
+	fer_theme + 
+  theme(legend.position = "none") +
+	ylab("weighted rank correlation")
+
+p2 <- cor_d_sp %>%
+	dplyr::filter(study != "ballantyne") %>%
+	plyr::ddply(c("net_name", "threshold"), function(x){
+		x %<>%
+			dplyr::select(species, type, d_rank) %>%
+			tidyr::spread(type, d_rank)
+		rw2(x$asymmetry, x$z_bi)
+	}, .inform = T) %>%
+	dplyr::group_by(threshold) %>%
+	dplyr::mutate(mean_cor = mean(V1)) %>%
+	ggplot(aes(x = threshold, y = V1, group = net_name)) +
+	geom_point(colour = "grey", size = 1, shape = 21) +
+	geom_line(colour = "grey") +
+	geom_line(aes(y = mean_cor), size = 1) +
+	geom_point(aes(y = mean_cor)) +
+	fer_theme + 
+  theme(legend.position = "none") +
+	ylab("weighted rank correlation")
+
+cowplot::plot_grid(p1, p2, labels = "AUTO", label_size = 10, vjust = 1)
+```
+*Figure S6: Weighted rank correlation coeficient $\tilde{r}_{w2}$ between (A) the relative importance of species given by the importance network in @Ballantyne2015 weighted by mutual dependences and the visitation network weighted by the interaction asymetries.
+(B) the relative importance of species given by mutual dependences and interaction asymmetries for a subset of the paired invaded-uninvaded networks.
+The black line corresponds to the mean correlation per threshold, and grey lines correspond to the correlation for each individual network.*
 

### 2016-07-10 paper/supp_info.Rmd
rework supplementary info

@@
 
-*Table S3: pearman correlation coefficients of the number of driver species necessary to control the full pollination network under the four different assumptions of the direction of control.*
+*Table S3: Spearman correlation coefficients of the number of driver species necessary to control the full pollination network under the four different assumptions of the direction of control.*
 ```{r table alternative assumptions, echo = FALSE, warning = F, message = F, results = "asis"}
@@
 
+*Table S4: Model selection table for the manageability of studied communities.
+Type refers to wether the manageability was calculated using mutual dependences or interaction asymetries.
+"y" and "n" indicate wheter a variable was included in the model or not.*
+```{r models, echo = F, message=F, warning=F, results="asis"}
+n_driver <- a_m %>%
+  dplyr::inner_join(meta) %>%
+  dplyr::filter(count == "visitation") %>%
+  dplyr::mutate(n_sp = n_pla + n_pol, 
+                n_dr = n_sp - n_matched,
+                n_dr_p = n_dr / n_sp)
+
+src_bi_w <- n_driver %>%
+  dplyr::filter(type == "z-bi" | type == "weight",
+                study != "ballantyne") %>%
+  dplyr::select(net_name, type, n_dr_p) %>%
+  tidyr::spread(type, n_dr_p) %$%
+  cor.test(weight, `z-bi`, method = "spearman")
+
+n_driver %<>%
+  dplyr::filter(!is.na(inv))
+
+n_driver_wb <- dplyr::filter(n_driver, 
+                             type == "z-bi" | type == "weight")
+
+# Models
+m0 <- glm(cbind(n_dr, n_matched) ~ n_pla * n_pol + study + inv + type,
+          data = n_driver_wb,
+          family = "binomial")
+m_nr <- glm(cbind(n_dr, n_matched) ~ I(n_pla/n_pol) + study + inv + type,
+          data = n_driver_wb,
+          family = "binomial")
+m8 <- glm(cbind(n_dr, n_matched) ~ I(n_pla/n_pol) + inv + type,
+          data = n_driver_wb,
+          family = "binomial")
+m9 <- glm(cbind(n_dr, n_matched) ~ I(n_pla/n_pol) + study + type,
+          data = n_driver_wb,
+          family = "binomial")
+m1 <- glm(cbind(n_dr, n_matched) ~ I(n_pla/n_pol) + type,
+          data = n_driver_wb,
+          family = "binomial")
+m2 <- glm(cbind(n_dr, n_matched) ~ study + type,
+          data = n_driver_wb,
+          family = "binomial")
+m3 <- glm(cbind(n_dr, n_matched) ~ I(n_pla + n_pol) + type,
+          data = n_driver_wb,
+          family = "binomial")
+m4 <- glm(cbind(n_dr, n_matched) ~ n_pla + type,
+          data = n_driver_wb,
+          family = "binomial")
+m5 <- glm(cbind(n_dr, n_matched) ~ n_pol + type,
+          data = n_driver_wb,
+          family = "binomial")
+m6 <- glm(cbind(n_dr, n_matched) ~ inv + type,
+          data = n_driver_wb,
+          family = "binomial")
+m7 <- glm(cbind(n_dr, n_matched) ~ study + inv + type,
+          data = n_driver_wb,
+          family = "binomial")
+
+mod_table <- MuMIn::model.sel(m0, m_nr, m8, m9, m1, m2, m3, m4, m5, m6, m7) %>%
+	as.data.frame() %>% 
+	`rownames<-`(NULL) %>%
+	dplyr::select(-1) %>% 
+	lapply(function(y) {
+		if (class(y) == "factor"){
+			y <- as.character(y)
+			y <- replace(y, y == "+", "y")
+			y <- replace(y, is.na(y), "n")
+		} 
+		if (class(y) == "numeric" & any(is.na(y))){
+			y <- replace(y, !is.na(y), "y")
+			y <- replace(y, is.na(y), "n")
+		}
+		y
+	}) %>% as.data.frame()
+
+names(mod_table)[1:8] <- c("invaded", "$n_p$", "$n_a$", "study", "type", "$n_p:n_a$", "$n_p/n_a$", "$n_p+n_a$")
+
+mod_table %<>%
+	dplyr::mutate(logLik = round(logLik, 1), 
+								AICc = round(AICc, 1),
+								delta = round (delta, 1),
+								weight = round(weight, 3))
+
+mod_table %>% knitr::kable(booktabs = T)
+```
+
 \newpage
-
 # S3: Threshold

### 2016-07-10 paper/legends.Rmd
update abstract, incorporate daniel's suggestions and synch with suppl info

@@
 Finding a maximum matching in a complex network. 
-a) We start with a directed network  in which the direction of the link represent the direction of control. 
-This is, a link from $a_1$ to $p_1$ indicates that the state of $p_1$ (density/abundances in an ecological context) are influenced by the state of $a_1$. 
+a) We start with a directed network  in which the direction of the link represent the direction of control; that is, a link from $a_1$ to $p_1$ indicates that the state of $p_1$ (density/abundances in an ecological context) is influenced by the state of $a_1$.
 b) To facilitate the computation of the maximum matching, we can use an alternative representation of the directed network in which each node in (a) is represented by two nodes that indicate their outgoing and incoming links.
 In both (a) and (b) we show one of the possible maximum matchings of a network (dark grey links) that defines a set of matched ($p_1$, $p_2$, and $a_3$), unmatched ($a_1$ and $a_2$) and superior nodes ($a_1$, $a_2$, and $p_1$; dark grey circles).
-The minimum number of species neccessary to control this network equates to the number of unmatched nodes $n_d = 2$, which gives a manageability of $m = 0.8$.
+The minimum number of species necessary to control this network equates to the number of unmatched nodes $n_d = 2$, which gives a manageability value of $m = 0.8$.
 
@@
 Different ways to depict quantitative mutualistic networks. 
-a) Pollination networks are usually described by the number of visits between each plant and animal species. 
-b) Given visitation data the mutual dependencies between interacting species depend directly on the relative visitation frequency. 
-c) The relative differences of dependencies---the interaction asymmetry---then provides a means to simplify the interspecific effects.
+a) Pollination networks are typically described by the number of visits between each plant and animal species. 
+b) Given visitation data, the mutual dependencies between interacting species are calculated directly based on the relative visitation frequencies. 
+c) The relative differences of dependencies—the interaction asymmetry—then provides a means to identify the dominant direction of the interspecific effects.
 
 **Figure 3:**
-Invaded communities have lower levels of manageability than uninvaded communities even when controling for the ratio of plant to pollinator richness. 
-Adjusted manageability corrsponds to the partial working residuals of the invasion status. 
+Invaded communities have lower levels of manageability than uninvaded communities even when controlling for the ratio of plant to pollinator richness. 
+Adjusted manageability is given by the partial working residuals of the invasion status in our generalised linear mixed model. 
 The box covers the 25th–75th percentiles, the middle line marks the median, and the maximum length of the whiskers is 1.5 times the interquartile range. 
-Points outside this range show up as outliers.
+All points outside this range are indicated by the circles.
 
@@
 The manageability of empirical networks compared to network randomisations. 
-For each of four randomisation approaches, we show that---akin to a p-value---an scaled mean rank $< 0.025$ or $> 0.975$ (shaded areas in light grey) suggest a significant difference between the empirical network and its randomisations.
-The empirical manageability is much smaller than those of randomisations in which the direction of assymmetries has been randomised. 
-In contrast the manageability of network in which the visitation strength or degree was mantained was not significantly different to the manageability of the empirical networks. 
-Dark grey and white boxplots represent manageabilities obtained using mutual dependencies and asymmetries respectively. 
+For each randomisation approach, we show the standarised rank of the empirical value compared to the set of randomisations. 
+An scaled mean rank—akin to a p-value— less than 0.025 or greater than 0.975 (the areas shaded in light grey) suggests a significant difference between the empirical network and its randomisations. 
+The empirical manageability is much smaller than that of network randomisations in which the direction of asymmetries has been randomised. 
+In contrast, the manageability of networks in which the visitation strengths or degrees were maintained were not significantly different to the manageability of the empirical networks. 
+Dark grey and white boxplots represent manageabilities obtained using interactions weighted by mutual dependencies and asymmetries respectively. 
 All boxes are as in Figure 3.
@@
 Visitation levels and contribution to nestedness had a significant albeit small effect on the importance (dashed lines correspond to ± one standard deviation on these factors). 
-Invasive species (red) were invariably classified as driver species (those having the maximum importance for network control.
+Invasive species (circles) were invariably classified as driver species—those having the maximum importance for network control.
 

### 2016-07-10 paper/manuscript.Rmd
update abstract, incorporate daniel's suggestions and synch with suppl info

@@
 
-* **Number of words:** ~ 154 abstract; ~ 4850 main text.
+* **Number of words:** ~ 153 abstract; ~ 4785 main text.
 
@@
 
-* **Correspondence to:** Daniel Stouffer (daniel.stouffer@canterbury.ac.nz) - +64 21 0825 8815 - School of Biological Sciences, University of Canterbury, 20 Kirkwood Ave, Christchurch 8013, New Zealand
-
-* **Authorship:** DBS conceived the idea, EFC performed all analysis. EFC, KLW and DBS contributed to the development of the theoretical framework. EFC and DBS wrote the manuscript.
-
-* **Data accessibility:** All data used in this manuscript has already been published by @Lopezaraiza-Mikel2007, @Bartomeus2008, and @Ballantyne2015.
+* **Correspondence to:** Daniel Stouffer (daniel.stouffer@canterbury.ac.nz) - +64 3 364 2729 - Centre for Integrative Ecology, School of Biological Sciences, University of Canterbury, Private Bag 4800, Christchurch 8140, New Zealand
+
+* **Authorship:** DBS conceived the idea; EFC, KLW and DBS contributed to the development of the theoretical framework. EFC performed all analysis. EFC and DBS wrote the manuscript.
+
+* **Data accessibility:** All data used in this manuscript have already been published by @Lopezaraiza-Mikel2007, @Bartomeus2008, and @Ballantyne2015.
 The reader should refer to the original sources to access the data.
@@
 
-Biotic invasions can severely disrupt ecological communities. 
-However, it is unknown how this disruption, underpinned by changes on ecosystem dynamics, affects our ability to manage ecological communities. 
-Here, we expand current theory on the control of complex systems to compare the theoretical manageability of ten paired invaded and uninvaded plant-pollinator communities and identify the driver species within them—those most important to manage in order to maximise the persistence of the community because of their disproportionate potential to affect the abundances of many other species.
-We found that pollination networks in which an invasive primary producer was present, had substantially lower levels of manageability than their uninvaded counterparts. 
-In addition, invasive plants were found to be driver species in every single one of the communities they occupy. 
-The dominant position of driver species is underpinned by a high asymmetry on the dependence of their interaction partners and not degree or other metrics of centrality.
+It is unknown how the disruption caused by biotic invasions, and other perturbations, affects our ability to manage ecological communities. 
+Here, we expand current theory on the controllability of complex systems to assess the theoretical manageability of ten paired invaded and uninvaded plant-pollinator communities and identify the driver species within them—those most important to manage because of their disproportionate potential to affect the abundances of many other species.
+We found that invaded pollination networks might be more resilient than their uninvaded counterparts as they showed substantially lower levels of manageability.
+Remarkably, invasive plants were found to be driver species in every single one of the communities they occupy; their dominant position was generally underpinned by high asymmetry in the dependence of their interaction partners.
+Our results provide theoretical explanation for the observed challenges involved on the restoration of invaded communities, but also provide useful insight for the design of informed management interventions.
 
@@
 Complex systems are characterised by non-linear relationships in which the whole is greater than the sum of its parts [@Jorgensen1998; @Levin1999; @Montoya2006].
-Within community ecology, a complex systems approach has led to the development of a rich suite of analytical and simulation tools with which to understand, for example, the role of species when embedded in an intricate network of interactions [@Pascual2005; @Bascompte2009; @Stouffer2012].
+Within community ecology, a complex systems approach has led to the development of a variety of analytical and simulation tools with which to understand, for example, the role of species when embedded in an intricate network of interactions [@Pascual2005; @Bascompte2009; @Stouffer2012].
 The inherent complexity of nature, however, has hindered—or at least greatly complicated—our ability to find management solutions to the many problems ecological communities face. 
@@
 Among the various possibilities, control theory appear to be a strong candidate as it is designed to deal with determining and supervising the behavior of general dynamical systems, and is well equipped to deal with the many feedbacks presents in ecological communities [@Liu2015].
-Existing research in the field has established a strong link between the structure of complex networks and their controllability, while demonstrating that it is in principle possible to alter a whole ecological community's composition by modifying the abundances of only a few species [@Liu2011; @Cornelius2013; @Ruths2014].
-Applications of control theory to ecological networks can also explicitly take into account the extent to which changes in the abundances of one species may ripple to the community [@Cornelius2013].
+Research in the field has established a strong link between the structure of complex networks and their controllability, while also demonstrating that it is in principle possible to alter a whole ecological community's composition by modifying the abundances of only a few species [@Liu2011; @Cornelius2013; @Ruths2014].
+Applications of control theory to ecological networks can also take into account the extent to which changes in the abundances of one species may ripple trough the community [@Cornelius2013].
 Therefore, they can provide an indication of which species are most relevant
 from a dynamic perspective, a particularly important feature given that these
-species underpin informed attempts to alter (or maintain) the ecosystem state.
+species underpin informed attempts to both alter or maintain the ecosystem state.
 
 Despite these advances, the link between the structure of complex networks and our ability to manage and conserve them is still ambiguous [@Tylianakis2010].
-To complicate things further, biotic invasions—a major driver of global change—can themselves induce dramatic changes on the patterns of interactions that determine the structure of ecological networks [@Baxter2004; @Tylianakis2008; @Ehrenfeld2010a].
-The difficulty of returning invaded communities to their predisturbance state is apparent based on the limited success of restoration projects [@Suding2004; @Rodewald2015; @Smith2016]. 
-Although it therefore presents a double challenge, understanding how differences in network structure before and after the invasion impact our ability to manage them is a critical first step towards a fully informed recovery.
-Though they could seem a natural pairing, a control-theoretic perspective has not been widely adopted in a invasion context, perhaps because of a lack of appropriate methodological tools that can account for observed variation on the strength of interspecific effects that are characteristic of ecological networks [@Liu2011; @Isbell2013].
+To complicate things further, biotic invasions—a major driver of global change—can induce dramatic changes on the patterns of interactions that determine the structure of ecological networks [@Baxter2004; @Tylianakis2008; @Ehrenfeld2010a].
+Although understanding how differences in network structure before and after the invasion impact our ability to manage them presents a double challenge, it is a critical first step towards a fully informed recovery.
+Despite the pairing potential, a control-theoretic perspective has not been widely adopted in a invasion context. 
+This is perhaps because of a lack of appropriate methodological tools that can account for observed variation on the strength of interspecific effects that are characteristic of ecological networks [@Liu2011; @Isbell2013].
 
@@
 We then use a set of ten paired invaded and uninvaded plant-pollinator communities to investigate the link between network structure and our ability to manage them. 
-Specifically we ask two key questions framed in the context of a plant invasion.
-First, we ask wether invaded networks have lower levels of manageability than their uninvaded counterparts, this is, whether they require more species to be managed to achieve the same level of control.
-Second, we ask whether some species are more important than others at driving the population dynamics of the community and which factors determine this importance; we aim to determine which species are most imortant to manage in order to maximise the persistence of the remainder of the community.
-We focus on this particular application for a variety of reasons. 
+We ask two specific questions framed in the context of a plant invasion.
+First, we ask whether invaded networks have lower levels of manageability than their uninvaded counterparts; that is, whether they require more species to be managed to achieve the same level of control.
+Second, we ask whether some species are more important than others at driving the population dynamics of the community and which factors determine this importance. 
+We aim to determine which species are most important to manage in order to maximise the persistence of the remainder of the community.
+We focus on these particular applications for a variety of reasons. 
 First, biotic invasions are known to produce tractable changes in the structure of ecological networks, and these changes can be particularly pronounced in mutualistic networks between plants and pollinators where biotic invasions have been shown to modify the strength of species interactions and the degree of network nestedness and connectivity [@Olesen2002; @Aizen2008; @Bartomeus2008; @Vila2009; @Traveset2013].
@@
 A given matching is then maximum if both *(i)* the number of matched links—known as matching size—is maximal and *(ii)* the sum of the weights of the matched links—known as matching weight—is the largest possible among all possible matchings of that size [@West2001].
-To find the maximum matching, it is useful to adopt an alternative bipartite representation of the network in which the two levels indicate the outgoing and incoming links to each node (Figure 1b). 
+To find the maximum matching, it is convenient to adopt an alternative bipartite representation of the network in which the two levels indicate the outgoing and incoming links to each node (Figure 1b).
 Finding a matching in this alternative representation is equivalent to finding a set of links such that each node on the top level is matched to at most one node on the bottom level, and vice versa [@West2001; @Csardi2006a].
@@
 Given a maximum matching, the link to network controllability has a largely intuitive basis. 
-In control theory, a network is fully controllable when each node has a ``superior'', that is, an input that drives its dynamics. 
+In control theory, a network is fully controllable when each node has a "superior"", that is, an input that drives its dynamics. 
 Consequently, each matched nodes can be controlled by the node pointing to it.
@@
 Building on this analogy, systems that require a large number of external inputs are more difficult or costly to control. 
-Therefore, the manageability $m$ of a community can be approximated by the proportion of species on which we would need to apply management interventions in order to gain full control of the abundances of *all* species in the ecological community $$m = 1- \frac{n_d}{s},$$ where $m$ ranges between zero and one, $n_d$ is the number of species needed to gain full control and $s$ is the total number of species in the community.
+Therefore, the manageability $m$ of a community can be approximated by the proportion of species on which we would need to apply management interventions in order to gain full control of the abundances of *all* species in the ecological community.
+This is given by $$m = 1- \frac{n_d}{s},$$ where $m$ ranges between zero and one, $n_d$ is the number of species needed to gain full control and $s$ is the total number of species in the community.
 
@@
 The manageability of a community $m$ provides an indication of the magnitude of $n_d$ but not the identity of the species that compose this set. 
-This is rather important since maximum matchings are often not unique in a given network and different sets of species of size $n_d$ could potentially be used to control the network [@Liu2011]. 
-Species vary in terms of the frequency with which they are classified as superior nodes (Figure 1), and this frequency provides an indication of their relative importance in driving the state of the community.
-Ecologically, these distinctions are crucial because resources are limited and therefore ecological interventions should be focused on species that might provide the largest impact. 
-Superior nodes drive the dynamics of other species and are therefore important for the controlability of the network because they either require external input or because the are part of the chain that transmit the external imputs to other species; we therefore call *driver species* those that are identified as being a superior node in *all* possible matchings, and hence those most likely to have a disproportionate effect on the abundances of other species in their community.
+This difference is rather important since maximum matchings are often not unique in a given network and different sets of species of size $n_d$ could potentially be used to control the network [@Liu2011].
+Species vary in terms of the frequency with which they are classified as superior nodes, and this frequency provides an indication of their relative importance in driving the state of the community. 
+Ecologically, these distinctions are crucial because resources are limited and therefore ecological interventions should ideally be focused on species that might provide the largest impact. 
+Superior nodes drive the dynamics of other species and are therefore important for the controllability of the network because they either require external input or because the are part of the chain that transmit the external inputs to other species; we therefore call *driver species* those that are identified as being a superior node in *all* possible matchings, and hence those most likely to have a disproportionate effect on the abundances of other species in their community.
 
@@
 However, empirical interaction strengths are to some extent stochastic and depend on proximate factors such as sampling method and intensity [@Gibson2011]. 
-This means that there are multiple matchings that have maximal size in weighted networks, but are not maximum matchings because their total weight is not maximal. 
-One could therefore instead relax the matching weight requirement and computed all possible matchings in the network that have the same maximal size while allowing for some tolerance regarding the weight.
-To compute all the matchings with maximal size, one can first generate the network's line graph—another representation in which nodes are the links of the original network and links represent common ending points [@West2001]—followed by calculation of the complement of this line graph.
-This latter step generates a graph in which nodes are connected if and only if they are not connected in the line graph.
-All possible matchings of maximal size can be found by enumerating all cliques (subgraphs in which all nodes are fully connected to each other) of maximum size [@Csardi2006a; @Gutin2013].
+This implies that there will often be multiple matchings that have maximal size in weighted networks but that are not maximum matchings because their total weight is not maximal. 
+One could accommodate this uncertainty by relaxing the matching weight requirement and computing all possible matchings in the network that have the same maximal size while allowing for some tolerance regarding the weight.
+One alternative to compute all the matchings with maximal size, is to first generate the network's line graph—another representation in which nodes are the links of the original network and links represent common ending points [@West2001].
+Then calculate the complement of this line graph, which generates a graph in which nodes are connected if and only if they are not connected in the line graph.
+Finally, all possible matchings of maximal size can be found by enumerating every clique (subgraphs in which all nodes are fully connected to each other) of maximum size in this complement graph [@Csardi2006a; @Gutin2013].
 
@@
 The structure of all networks was determined using visitation frequency which has been shown to be an appropriate surrogate for interspecific effects in pollination networks [@Vazquez2005; @Bascompte2006].
-To examine whether this decision would influence our results, we also evaluated the effect of using pollinator efficiency or importance as alternative measures of species interactions in a different dataset [@NeEman2010; @Ballantyne2015], and we found quantitatively similar results for all of these options (Supplementary Information S1).
+To examine whether this decision would influence our results, we also evaluated the effect of using pollinator efficiency or importance as alternative measures of species interactions in a different data set [@NeEman2010; @Ballantyne2015], and we found quantitatively similar results for all of these options (Supplementary Information S1).
 
 ### Community manageability
+
+```{r component_lost, echo = F}
+net <- "./data/processed/networks" %>%
+	read_networks()
+
+a <- net %>% 
+	lapply(igraph::E) %>%
+	lapply(length)
+
+b <- net %>%
+	lapply(keep_largest_component) %>%
+	lapply(igraph::E) %>%
+	lapply(length)
+
+int_lost <- ((mapply(magrittr::subtract, a, b) / unlist(a)) * 100) %>% mean() %>% round(1)
+```
 
@@
 To do so, we calculated the maximum matching of the corresponding pollination network, and estimated the minimum proportion of species that need directed interventions to fully control the species abundances in the community.
-To simplify the analysis, if a network had more than one component (two species are in different components if there exists no path between them), note that we only analysed the largest.
-Smaller components, were found in eleven out of the twenty studied networks and were ussually composed by just one plant and one pollinator.
+To simplify the analysis we only analysed the largest component in a network if it had more than one (two species are in different components if there exists no path between them and are hence independent of each other in terms of network control).
+Smaller components were present in eleven out of the twenty networks and were typically composed of just one plant and one pollinator. 
+Their removal represented an overall loss of `r int_lost`% of the total species interactions.
 
@@
 Likewise, the dependency of pollinator $j$ on plant $i$, $d_{ji}$, is the ratio of the visits by pollinator $j$ to plant $i$ and all visits of pollinator $j$.
-As the dependencies are bidirectional, adopting this assumption generates a weighted bipartite network in which interacting pairs are connected by two directed links (Figure 2b).
-
-Mutual dependencies have previously been shown to be highly asymmetric in natural communities [@Bascompte2006]; in other words, if a plant species is largely dependent on a pollinator species, then that pollinator tends to depend rather weakly on the plant.
+As the dependencies are not symmetric, its use generates a weighted bipartite network in which all interacting pairs are connected by two directed links (Figure 2b).
+
+Given the respective dependences, the extent to which a species $i$ affects species $j$ relative to the extent to which $j$ affects $i$ can be summarised by the interaction asymmetry given by $$a(i,j) = \frac{\left | d_{ij}-d_{ji} \right |}{max\left ( d_{ij}, d_{ji} \right )}.$$
+Mutual dependencies have previously been shown to be highly asymmetric in natural communities [@Bascompte2006]; in other words, if a plant species is largely dependent on a pollinator species, then that pollinator tends to depend rather weakly on the plant (or vice versa).
 This suggests that it may be possible to relax the assumption of bidirectional dependences and simplify the network further such that interacting species are only connected by one directed link when mutual dependencies are asymmetric (Figure 2c).
-The extent to which a species $i$ affects species $j$ relative to the extent to which species $j$ affects species $i$ can be summarised by the interaction asymmetry given by $$a(i,j) = \frac{\left | d_{ij}-d_{ji} \right |}{max\left ( d_{ij}, d_{ji} \right )}.$$
-Employing an unidrectional interaction asymmetry, as a surrogate of bidirectional mutual dependences, does not alter the relative manageabilities of different networks (Supplementary Information S2). 
+Changing to unidirectional interactions determined by the observed direction of asymmetry, as a surrogate of bidirectional mutual dependences, does not alter the relative manageabilities of different networks (Supplementary Information S2).
 Moreover, it confers an additional advantage for our purposes since it dramatically reduces the number of links in the network. 
-This translates into a substantial reduction of the time and memory required for the computation of of all possible maximum matchings in a network, particularly for large networks (see ''relative importance of species'' subsection below).
+This translates into a substantial reduction of the time and memory required for the computation of all possible maximum matchings in a network, particularly for large networks (see "Relative importance of species" subsection below).
 
@@
 
-#### Data analysis
+#### Statistical analysis
 
@@
 We therefore used a set of generalised linear models (with binomial error structure) to investigate the effect of invasion status while also controlling for factors related to species richness, since one might naively expect to see a negative relationship between diversity and manageability [@Menge1995].
-These covariates included the total number of species, plant richness, polinators richness, the ratio of plants to pollinators richness, and the study site (as a two level factor). 
+These covariates included the total number of species, plant richness, pollinators richness, the ratio of plants to pollinators richness, and the study site (as a two level factor). 
 We assessed competing models by comparing the Akaike Information Criterion corrected for small sample sizes (AICc), and report results for the most parsimonious model.
@@
 Previous research indicates a direct link between a network's degree distribution and the number of nodes necessary to fully control it [@Liu2011], but the strength and applicability of this relationship has not been tested for in weighted ecological networks.
-We therefore compared the manageability of the empirical networks to networks generated by three null models which varied in terms of the constraints they impose. 
-The first set of random visitation networks maintain the connectivity of the empirical network, but both degree (its number of interactions) and strength (its total sum of visits) were allowed to vary.
-The second set was generated by maintaining each species' degree while varying the number of visits per species. 
-Finally, the third set of random networks mantained the species' strength while varying their degrees. Randomisations were generated using vegan 2.3-3 [@Oksansen2016]. 
-After generating the randomized networks under these three schemes, we then calculated the mutual dependences and interaction asymmetries of each and determined their manageability using the maximum matching algorithm.
-Finally we calculated the average rank (akin to a p-value) of the manageability of each empirical network compared to the corresponding manageabilites of each set of 999 randomisations.
-
-The dependency asymmetry plays a fundamental role in determining the direction of control in each two-species interaction and therefore has the potential to influence the network manageability results above.
+We therefore compared the manageability of the empirical networks to networks generated by two null models which varied in terms of the constraints they impose. 
+The first set was generated by maintaining each species' degree (its number of interactions) while varying the number of visits per species. 
+Finally, the third set of random networks maintained the species' strength (its total sum of visits) while varying their degrees. 
+Randomisations were generated using vegan 2.3-3 [@Oksansen2016]. 
+After generating the randomized networks under these two schemes, we then calculated the mutual dependences and interaction asymmetries of each and determined their manageability using our maximum matching framework
+Finally, we calculated the average rank (akin to a p-value) of the manageability of each empirical network compared to the corresponding manageabilites of each set of 999 randomisations.
+
+Beyond network structure, the dependency asymmetry plays a fundamental role in determining the direction of control in each two-species interaction and therefore has the potential to influence the network manageability results above.
 We therefore performed an additional randomisation in which we kept the structure of network constant but randomised the direction of the interaction asymmetries. 
 That is, we first calculated the asymmetries for each community and then shuffled the direction of the link between each pair of species. 
-Similar as in previous null models, we calculated the average rank of the empirical manageability as compared to those of the randomisations.
+Similar as to the other null models, we calculated the average rank of the empirical manageability as compared to those of the randomisations.
 
@@
 
-We then asked the question of whether some species-level structural properties can predict our estimates of species importance.
 Although the species importance calculated from mutual dependences contains full information, even in sparse networks, like these studied here, the number of maximal matchings increases exponentially with the number of links and nodes in a network.
@@
 Taking this limitation into account, we compared the relative network manageability obtained when using asymmetries to those found when using mutual dependencies to test if they gave consistent results.
-The comparison was performed for eleven of the twenty networks (those for which the number of matchings was smaller than $4\times 10^{10}$), using a paired Spearman correlation test, a weighted correlation coefficient $r_{w2}$ (which gives more weight to higer ranks; @PintoDaCosta2015-), and a Jaccard similarity of the driver species in both approaches.
+The comparison was performed for eleven of the twenty networks (those for which the number of matchings was smaller than $4\times 10^{10}$), using a paired Spearman correlation test, a weighted correlation coefficient $r_{w2}$ (which gives more weight to higher ranks; @PintoDaCosta2015-), and a Jaccard similarity of the driver species in both approaches.
 All three approaches identified a high similarity in relative ranks. 
@@
 
+#### Statistical analysis
+
+We then asked the question of whether some species-level structural properties can predict our estimates of species importance.
 We used a generalised linear mixed-effects model (GLMM) with binomial error structure with the relative importance as the response variable. 
-As predictors in this model, we included measures of centrality (degree and eigen-centrality), which have been found to be strong predictors of importance in a coextintion context [@Memmott2004]; a measure related to network robustness (contribution to nestedness), as nestedness has been proposed as one of the key properties that promote stability in mutualistic networks [@Saavedra2011; @Thebault2010]; two measures of strength of association and dependence (visitation and dependency strength), as their distribution determines the extent of interspecific effects.
-In addition, we also included guild and invasive status as categorical fixed effects; although the importance of plants and pollinators or invasive and non-invasive species could respond differently to our structural metrics, our dataset did not contain enough variation to include the corresponding interactions terms for these latter two predictors.
+As predictors in this model, we included measures of centrality (degree and eigen-centrality), which have been found to be strong predictors of importance in a coextinction context [@Memmott2004]; a measure related to network robustness (contribution to nestedness), as nestedness has been proposed as one of the key properties that promote stability in mutualistic networks [@Saavedra2011; @Thebault2010]; two measures of strength of association and dependence (visitation and dependency strength), as their distribution determines the extent of interspecific effects [@Bascompte2006].
+In addition, we also included guild and invasive status as categorical fixed effects; although the importance of plants and pollinators or invasive and non-invasive species could respond differently to our structural metrics, our data set did not contain enough variation to include the corresponding interactions terms for these latter two predictors.
 All network metrics were calculated using the R package bipartite 2.06 [@Dormann2008]. 
@@
 Candidate models were compared using AICc and the relative importance of the explanatory variables was evaluated using the sum of Akaike weights over candidate models that accounted for 95% of the evidence [@Burnham2003; @Bates2014; @Barton2016].
-Coeficient estimates were avaraged following [@Buckland1997a] while confidence intervals were calculated following [@Lukacs2010].
+Coefficient estimates were averaged following [@Buckland1997a] while confidence intervals were calculated following [@Lukacs2010].
 
@@
 This was in strong agreement with the results obtained using the dependence asymmetry in which manageability ranged between `r round(min(1-dplyr::filter(n_driver, type == "weight")$n_dr_p), digits = 2)` and `r round(max(1-dplyr::filter(n_driver, type == "weight")$n_dr_p), digits = 2)` (mean `r round(mean(1-dplyr::filter(n_driver, type == "weight")$n_dr_p), digits = 2)`; Spearman rank correlation `r round(src_bi_w$estimate, digits = 2)`, $p `r fix_small_pvalue(src_bi_w$p.value)`$).
-In addition, we found that invaded communities were significantly more difficult to manage than uninvaded ones even when controlling for potential diversity effects.
-Out of the various covariates we explored—total number of species, plant richness, pollinator richness, and the ratio of plant to pollinator richness—only the ratio of plant to pollinator richness was retained in the final model as determined by the AICc (Figure 3, Table S3).
+In addition, we found that invaded communities were significantly more difficult to manage than uninvaded ones even when controlling for potential diversity effects (Figure 3). 
+Out of the various covariates we explored—total number of species, plant richness, pollinator richness, and the ratio of plant to pollinator richness—only the ratio of plant to pollinator richness was retained in the final model as determined by the AICc (Table S4).
 
@@
 When exploring the effect of network structure itself, we observed that the manageability of empirical networks was, in general, not significantly different to the manageability of network randomisations that maintained the degree or the strength of individual species (Figure 4).
-However, when comparing the empirical network to less constrained randomisations that only maintained the original connectance but in which species had different degrees and strengths, we found that empirical networks showed a significant tendency to have smaller values of manageability.
-Furthermore, this pattern was even more marked when we maintained the network structure but randomised only the direction of the asymmetries (Figure 4).
+However, when comparing the empirical network to randomisations that maintained the network structure but randomised only the direction of the asymmetries, we found that empirical networks showed a significant tendency to have smaller values of manageability
 
@@
                 m_n = replace(m_n, m_n == 3, 3.5)) %>%
-  dplyr::filter(!method %in% c("r00_both", "r00_ind")) %>%
+  dplyr::filter(!method %in% c("r00_both", "r00_ind", "r00_samp")) %>%
   ggplot(aes(x = method, y = -1 * z_s)) +
-  geom_rect(aes(xmin = 0.5, xmax = 4.5, ymin = -Inf, ymax = qlogis(0.025)), fill = "#f0f0f0") +
-  geom_rect(aes(xmin = 0.5, xmax = 4.5, ymin = Inf, ymax = qlogis(0.975)), fill = "#f0f0f0") +
+  geom_rect(aes(xmin = 0.5, xmax = 3.5, ymin = -Inf, ymax = qlogis(0.025)), fill = "#f0f0f0") +
+  geom_rect(aes(xmin = 0.5, xmax = 3.5, ymin = Inf, ymax = qlogis(0.975)), fill = "#f0f0f0") +
 
@@
   scale_x_discrete(
-    labels = rev(c("only maintain\nconnectance", "maintain strength\nrandomise degree", "maintain degree\nrandomise strength", "random\nassymetry")),
+    labels = rev(c("maintain strength\nrandomise degree", "maintain degree\nrandomise strength", "random\nassymetry")),
     # breaks = c("r00_samp", "swsh_both", "quasiswap_count", "r0"),
@@
 
-pdf("./paper/figures/fig_4.pdf", height = 2.7, width = 3.245, family = "Times", compress = FALSE, title = "Figure 4")
+pdf("./paper/figures/fig_4.pdf", height = 2.1, width = 3.245, family = "Times", compress = FALSE, title = "Figure 4")
 f4
@@
   kable(format = "latex", align = "c", booktabs = T, digits = 2, escape = F, linesep = "")
+
+imp %>%
+	magrittr::set_names(c("factor", "est.", "var", "No. mod.", "imp.", "C.I.")) %>% 
+  dplyr::select(-var) %>% 
+	dplyr::mutate(est. = round(est., 2), 
+								imp. = round(imp., 2), 
+								C.I. = round(C.I., 2)) %>% 
+	write.csv("./paper/Table 1.csv", row.names = F)
 ```
@@
 
-Invasive species were driver species in every single network they were present, this is, they had the highest relative ranking of species importance. 
+Invasive species were driver species in every single network they were present, that is, they always had the highest relative ranking of species importance (Figure 5). 
 Overall, plants showed significantly higher levels of importance than pollinators (Mann-Whitney-Wilcoxon test, $p = `r fix_small_pvalue(wilcox.test(pp ~ guild, data = dd, alternative = "greater")$p.value, 3)`$).
@@
 Indeed, when averaging over the set of GLMMs that accounted at least 95\% of the evidence based on AICc, we found that species' strength of dependency is the single most important factor determining the relative importance of species for network control (Table 1, Figure 5).
-In contrast, the number of visits a species makes (or receives) and its contribution to nestedness have only a marginal effect on its relative importance.
+In contrast, the number of visits a species makes (or receives) and its contribution to nestedness had only a marginal effect on its relative importance.
 
@@
   scale_x_log10(expand = c(0,0)) +
-   geom_point(data = dplyr::arrange(data_pp, invasive), aes(x = de_s, y = pred_ri, fill = invasive, shape = guild, size = invasive), show.legend = F) +
+   geom_point(data = dplyr::arrange(data_pp, invasive) %>% dplyr::filter(invasive == T), aes(x = de_s, y = pred_ri, fill = invasive, shape = guild, size = invasive), show.legend = F) +
     scale_shape_manual(values = c(21, 23)) +
-  scale_size_manual(values = c(1,1.5)) +
+  scale_size_manual(values = c(1.5,1.5)) +
   scale_fill_manual(values = c("white","#e41a1c")) + 
@@
 
-Our results reveal that the structural differences associated to biotic invasions are reflected in a potential decrease in our ability to alter the state of the community post invasion. 
-Furthermore invasive mutualists were always driver species in the communities they invade.
-As driver species, they occupy a dominant role in which changes on their abundance have the potential to propagate broadly trough the community and in turn affect the abundances of many other species.
+Our results reveal that the structural differences associated with biotic invasions are reflected in a potential decrease in our ability to alter the state of the community post invasion. 
+Furthermore, invasive mutualists were always driver species in the communities they invade.
+As driver species, they occupy a particularly dominant role in which changes on their abundance have the potential to propagate broadly trough the community and in turn affect the abundances of many other species.
 
@@
 Generally speaking, this strong relationship between the asymmetric dependences and manageability might explain why invasive species reduce the manageability of their communities. 
-Invasive species have been previously found to exacerbate the asymmetries in the network and presumably increase the stability of their community [@Aizen2008; @Bartomeus2008; @Henriksson2016].
+Invasive species have been previously found to exacerbate the asymmetries in the network and ostensibly increase the stability of their community [@Aizen2008; @Bartomeus2008; @Henriksson2016].
 
@@
 Invasive plants, just like any other mutualist in our data set, tend to be driver species to the degree to which their interaction partners are collectively more dependent on them than the other way around.
-Although previous studies have found that super-generalists, like invasive species, play a central role in their networks [@Vila2009; @Palacio2016], our results take this one more and indicate that it is dependence strength, rather than generalism or other metrics of centrality, the factor that best explains how important a species is for it's community dynamics.
+Previous studies have found that super-generalists, like invasive species, play a central role in their networks [@Vila2009; @Palacio2016].
+Our results take this one step further and indicate that dependence strength, rather than generalism or other metrics of centrality, is the factor that best explains how important a species is for its community's dynamics.
 
 Because of their effects on other species in the community, driver species might be natural candidates for management interventions. 
-For instance, despite inconsistent outcomes in practice, our results suggest that current restoration approaches that focus on direct eradication of invasive species might indeed be an effective way to modify ecosystem state.
+For instance, despite inconsistent outcomes in practice [@Suding2004; Rodewald2015; Smith2016], our results suggest that current restoration approaches that focus on direct eradication of invasive species might indeed be an effective way to modify ecosystem state.
 Nevertheless, our results also indicate that removals must be executed with caution as invaded communities tend to be highly dependent on invaders and therefore acutely vulnerable to their eradication [@Traveset2013; @Albrecht2014].
@@
 However, while keystone species were traditionally identified by inferring the effects of a perturbation on a community's population dynamics [@Mills1993], the driver species concept operates the other way round; namely, it uses the community dynamics, underpinned by the interspecific effects, to infer the effects of a perturbation.
-While it is challenging to quantify the dependence of species in an ecological community, an experimental approach to identify dynamically important species might be even more difficult to implement *[FDO: add ref]*.
+While it is challenging to quantify the dependence of species in an ecological community, an experimental approach to identify dynamically important species might be even more difficult to implement.
 
@@
 Moreover, we see great potential by explicitly integrating control theory with dynamic models of species densities [@Cornelius2013; @Gibson2016]. 
-From an ecological perspective, this integration can provide deeper insights into the relationship between controllability and species coexistence. 
-It can also help identify potential trade-offs between persistence at the species and the community level *[FDO: add ref]*. 
+From an ecological perspective, this integration can provide even deeper insights into the relationship between controllability and species coexistence. 
+It can also help identify potential trade-offs between persistence at the species and the community level. 
 From a conservation perspective, the combined approach can shift our focus beyond the identification of ideal targets for intervention to design informed interventions that legitimately achieve restoration goals.

### 2016-07-18 paper/legends.Rmd
more edits

@@
 In both (a) and (b) we show one of the possible maximum matchings of a network (dark grey links) that defines a set of matched ($p_1$, $p_2$, and $a_3$), unmatched ($a_1$ and $a_2$) and superior nodes ($a_1$, $a_2$, and $p_1$; dark grey circles).
-The minimum number of species necessary to control this network equates to the number of unmatched nodes $n_d = 2$, which gives a manageability value of $m = 0.8$.
+The minimum number of species necessary to control this network equates to the number of unmatched nodes $n_d = 2$, which gives an overall manageability of $m = 0.8$.
 
@@
 For each randomisation approach, we show the standarised rank of the empirical value compared to the set of randomisations. 
-An scaled mean rank—akin to a p-value— less than 0.025 or greater than 0.975 (the areas shaded in light grey) suggests a significant difference between the empirical network and its randomisations. 
+A scaled mean rank—akin to a p-value— less than 0.025 or greater than 0.975 (the areas shaded in light grey) suggests a significant difference between the empirical network and its randomisations. 
 The empirical manageability is much smaller than that of network randomisations in which the direction of asymmetries has been randomised. 

### 2016-07-18 paper/manuscript.Rmd
more edits

@@
 ---
-title: "Biotic invasions reduce the manageability of mutualistic networks"
+title: "Biotic invasions reduce the manageability of pollination networks"
 csl: ecology-letters.csl
@@
 
-Centre for Integrative Ecology, School of Biological Sciences, University of Canterbury, 8041 Christchurch, New Zealand
+Centre for Integrative Ecology, School of Biological Sciences, University of Canterbury, Private Bag 4800, Christchurch 8041, New Zealand
 
@@
 
-* **Running title:** Manageability of mutualistic networks.
-
-* **Keywords:** Network control, ecological networks, species importance, driver species, food webs, pollination, management interventions, food web, asymmetry
+* **Running title:** Manageability of pollination networks.
+
+* **Keywords:** Network control, ecological networks, species importance, driver species, food webs, mutualism, management interventions, food web, interaction asymmetry, mutual dependence
 
@@
 
-* **Number of words:** ~ 153 abstract; ~ 4785 main text.
-
-* **Number of references:** ~ 63
+* **Number of words:** ~ 151 abstract; ~ 4790 main text.
+
+* **Number of references:** ~ 61
 
@@
 
-It is unknown how the disruption caused by biotic invasions, and other perturbations, affects our ability to manage ecological communities. 
-Here, we expand current theory on the controllability of complex systems to assess the theoretical manageability of ten paired invaded and uninvaded plant-pollinator communities and identify the driver species within them—those most important to manage because of their disproportionate potential to affect the abundances of many other species.
-We found that invaded pollination networks might be more resilient than their uninvaded counterparts as they showed substantially lower levels of manageability.
-Remarkably, invasive plants were found to be driver species in every single one of the communities they occupy; their dominant position was generally underpinned by high asymmetry in the dependence of their interaction partners.
-Our results provide theoretical explanation for the observed challenges involved on the restoration of invaded communities, but also provide useful insight for the design of informed management interventions.
+It is generally unknown how the disruptions caused by perturbations such as biotic invasions, affect our ability to manage ecological communities. 
+Here, we expand current theory on the controllability of complex systems to quantitatively assess the theoretical (relative) manageability of ten pairs of uninvaded and invaded plant-pollinator communities.
+Intriguingly, we found that invaded pollination networks might be more resilient than their uninvaded counterparts as they showed substantially lower levels of manageability.
+We also developed theory to help identify each community's driver species—those most important to manage because of their disproportionate potential to affect the abundances of all other species. 
+Remarkably, invasive plants were found to be driver species in every community in which they were found; their dominant position was generally underpinned by high asymmetry in the dependence of their interaction partners.
+Our results provide a theoretical explanation for the known challenges associated with the restoration of invaded communities, and also provide insight into the design of informed management interventions.
+
+*Shorter version*: 
+It is generally unknown how the disruptions caused by perturbations like biotic invasions, affect our ability to manage ecological communities. 
+Here, we expand current theory on the controllability of complex systems to assess the theoretical manageability of ten pairs of uninvaded and invaded plant-pollinator communities.
+We found that invaded pollination networks might be more resilient than their uninvaded counterparts as they showed substantially lower manageability.
+We also identify each community's driver species—those most important to manage because of their disproportionate potential to affect the abundances of all other species. 
+Remarkably, invasive plants were found to be driver species in every community in which they were found; their dominant position was generally underpinned by high asymmetry in the dependence of their interaction partners.
+Our results provide a theoretical explanation for the known challenges associated with the restoration of invaded communities, and also provide insight into the design of informed management interventions.
 
@@
 
-Among the various possibilities, control theory appear to be a strong candidate as it is designed to deal with determining and supervising the behavior of general dynamical systems, and is well equipped to deal with the many feedbacks presents in ecological communities [@Liu2015].
+Among the various possibilities, control theory appears to be a strong candidate as it is designed to deal with determining and supervising the behavior of general dynamical systems, and is well equipped to deal with the many feedbacks presents in ecological communities [@Liu2015].
 Research in the field has established a strong link between the structure of complex networks and their controllability, while also demonstrating that it is in principle possible to alter a whole ecological community's composition by modifying the abundances of only a few species [@Liu2011; @Cornelius2013; @Ruths2014].
-Applications of control theory to ecological networks can also take into account the extent to which changes in the abundances of one species may ripple trough the community [@Cornelius2013].
+Applications of control theory to ecological networks can also take into account the extent to which changes in the abundances of one species may ripple through the community [@Cornelius2013].
 Therefore, they can provide an indication of which species are most relevant
 from a dynamic perspective, a particularly important feature given that these
-species underpin informed attempts to both alter or maintain the ecosystem state.
+species should underpin informed attempts to both alter or maintain the ecosystem state.
 
@@
 Although understanding how differences in network structure before and after the invasion impact our ability to manage them presents a double challenge, it is a critical first step towards a fully informed recovery.
-Despite the pairing potential, a control-theoretic perspective has not been widely adopted in a invasion context. 
+Despite the apparent overlap, a control-theoretic perspective has not been widely adopted in an invasion context. 
 This is perhaps because of a lack of appropriate methodological tools that can account for observed variation on the strength of interspecific effects that are characteristic of ecological networks [@Liu2011; @Isbell2013].
 
-Here, we expand previous theory of the control of complex systems to an ecological context.
-We then use a set of ten paired invaded and uninvaded plant-pollinator communities to investigate the link between network structure and our ability to manage them. 
+To bridge this gap, we expand previous theory of the control of complex systems to an ecological context.
+We then use a set of ten pairs of uninvaded and invaded plant-pollinator communities to investigate the link between invasion, network structure and ecological management. 
 We ask two specific questions framed in the context of a plant invasion.
-First, we ask whether invaded networks have lower levels of manageability than their uninvaded counterparts; that is, whether they require more species to be managed to achieve the same level of control.
+First, we ask whether invaded networks have lower levels of manageability than their uninvaded counterparts; that is, whether they require a greater proportion of species to be managed to achieve the same level of control.
 Second, we ask whether some species are more important than others at driving the population dynamics of the community and which factors determine this importance. 
-We aim to determine which species are most important to manage in order to maximise the persistence of the remainder of the community.
 We focus on these particular applications for a variety of reasons. 
@@
 Given a maximum matching, the link to network controllability has a largely intuitive basis. 
-In control theory, a network is fully controllable when each node has a "superior"", that is, an input that drives its dynamics. 
+In control theory, a network is fully controllable when each node has a "superior", that is, an input that drives its dynamics. 
 Consequently, each matched nodes can be controlled by the node pointing to it.
 Unmatched nodes, on the other hand, have no superior in the network and must be directly controlled by external inputs [@Liu2011]. 
-In an ecological context, this is what could be referred to as management interventions. 
+In an ecological context, these external inputs are what could be referred to as management interventions. 
 Building on this analogy, systems that require a large number of external inputs are more difficult or costly to control. 
-Therefore, the manageability $m$ of a community can be approximated by the proportion of species on which we would need to apply management interventions in order to gain full control of the abundances of *all* species in the ecological community.
-This is given by $$m = 1- \frac{n_d}{s},$$ where $m$ ranges between zero and one, $n_d$ is the number of species needed to gain full control and $s$ is the total number of species in the community.
+Therefore, the manageability *m* of a community can be approximated by the proportion of species on which we would need to apply management interventions in order to gain full control of the abundances of *all* species in the ecological community.
+This is given by $$m = 1- \frac{n_d}{s},$$ where *m* ranges between zero and one, *n~d~* is the number of species needed to gain full control and *s* is the total number of species in the community.
 
@@
 
-The manageability of a community $m$ provides an indication of the magnitude of $n_d$ but not the identity of the species that compose this set. 
-This difference is rather important since maximum matchings are often not unique in a given network and different sets of species of size $n_d$ could potentially be used to control the network [@Liu2011].
-Species vary in terms of the frequency with which they are classified as superior nodes, and this frequency provides an indication of their relative importance in driving the state of the community. 
-Ecologically, these distinctions are crucial because resources are limited and therefore ecological interventions should ideally be focused on species that might provide the largest impact. 
-Superior nodes drive the dynamics of other species and are therefore important for the controllability of the network because they either require external input or because the are part of the chain that transmit the external inputs to other species; we therefore call *driver species* those that are identified as being a superior node in *all* possible matchings, and hence those most likely to have a disproportionate effect on the abundances of other species in their community.
+The manageability of a community *m* provides an indication of the magnitude of $n_d$ but not the identity of the species that compose this set. 
+This difference is rather important since maximum matchings are often not unique in a given network and different sets of species of size *n~d~* could potentially be used to control the network [@Liu2011].
+That is, species vary in terms of the frequency with which they are classified as superior nodes, and this frequency provides an indication of their relative importance in driving the state of the community.
+Ecologically, these distinctions are relevant because resources are limited and therefore ecological interventions should ideally be focused on species that might provide the largest impact. 
+Superior nodes drive the dynamics of other species and are therefore important for the controllability of the network because they either require external input or because they are part of the chain that transmit the external inputs to other species; we therefore call *driver species* those that are identified as being a superior node in *all* possible matchings, and hence those most likely to have a disproportionate effect on the abundances of other species in their community.
 
@@
 This implies that there will often be multiple matchings that have maximal size in weighted networks but that are not maximum matchings because their total weight is not maximal. 
-One could accommodate this uncertainty by relaxing the matching weight requirement and computing all possible matchings in the network that have the same maximal size while allowing for some tolerance regarding the weight.
+We can accommodate this uncertainty by relaxing the matching weight requirement and computing all possible matchings in the network that have the same maximal size while allowing for some tolerance regarding the weight.
 One alternative to compute all the matchings with maximal size, is to first generate the network's line graph—another representation in which nodes are the links of the original network and links represent common ending points [@West2001].
@@
 The networks were constructed from previously published visitation data collected from pollination communities in Bristol, UK [@Lopezaraiza-Mikel2007] and in Cap de Creus National Park, Spain [@Bartomeus2008].
-Notably, each network pair was composed of a community invaded by a plant and a community ''free'' of the invasive species (Table S1). 
+Notably, each network pair was composed of a community invaded by a plant and a community "free" of the invasive species (Table S1). 
 In the four British uninvaded communities, the non-invaded plots were obtained by experimentally removing all the flowers of the invasive species *Impatients grandulifera*. 
@@
 The structure of all networks was determined using visitation frequency which has been shown to be an appropriate surrogate for interspecific effects in pollination networks [@Vazquez2005; @Bascompte2006].
-To examine whether this decision would influence our results, we also evaluated the effect of using pollinator efficiency or importance as alternative measures of species interactions in a different data set [@NeEman2010; @Ballantyne2015], and we found quantitatively similar results for all of these options (Supplementary Information S1).
+To examine whether this decision would influence our results, we also evaluated the effect of using pollinator efficiency or importance as alternative measures of species interactions in a different data set that lacked invasive species [@NeEman2010; @Ballantyne2015], and we found quantitatively similar results for all of these options (Supplementary Information S1).
 
@@
 int_lost <- ((mapply(magrittr::subtract, a, b) / unlist(a)) * 100) %>% mean() %>% round(1)
+
+a <- net %>% 
+	lapply(igraph::V) %>%
+	lapply(length)
+
+b <- net %>%
+	lapply(keep_largest_component) %>%
+	lapply(igraph::V) %>%
+	lapply(length)
+
+sp_lost <- ((mapply(magrittr::subtract, a, b) / unlist(a)) * 100) %>% mean() %>% round(1)
 ```
@@
 To do so, we calculated the maximum matching of the corresponding pollination network, and estimated the minimum proportion of species that need directed interventions to fully control the species abundances in the community.
-To simplify the analysis we only analysed the largest component in a network if it had more than one (two species are in different components if there exists no path between them and are hence independent of each other in terms of network control).
+To simplify the analysis, we only considered the largest component in a network if it had more than one (two species are in different components if there exists no path between them and are hence independent of each other in terms of network control).
 Smaller components were present in eleven out of the twenty networks and were typically composed of just one plant and one pollinator. 
-Their removal represented an overall loss of `r int_lost`% of the total species interactions.
+Their removal represented an average loss of `r sp_lost`% of the species and `r int_lost`% of the interactions.
 
@@
 
-Recall that the aforementioned maximum matching algorithm requires a directed network in which a link between species $i$ and $j$ pointing to species $j$ indicates that the abundance of $j$ can be affected by the abundance of $i$.
+Recall that the aforementioned maximum matching algorithm requires a directed network in which a link between species *i* and *j* pointing to species *j* indicates that the abundance of *j* can be affected by the abundance of *i*.
 This implies that we need first to identify a directionality for the links between species that in consistent with the dynamics of the community. 
@@
 Nevertheless, the relative extent to which a given pair of interacting species affect each other can be quantified by the magnitude of the mutual dependence [@Bascompte2006]. 
-The dependency of plant $i$ on pollinator $j$, $d_{ij}$, is the proportion of the visits coming from pollinator $j$ compared to all pollinator visits to plant $i$. 
-Likewise, the dependency of pollinator $j$ on plant $i$, $d_{ji}$, is the ratio of the visits by pollinator $j$ to plant $i$ and all visits of pollinator $j$.
+The dependency of plant *i* on pollinator *j*, *d~ij~*, is the proportion of the visits coming from pollinator *j* compared to all pollinator visits to plant *i*. 
+Likewise, the dependency of pollinator *j* on plant *i*, *d~ji~*, is the ratio of the visits by pollinator *j* to plant *i* and all visits of pollinator *j*.
 As the dependencies are not symmetric, its use generates a weighted bipartite network in which all interacting pairs are connected by two directed links (Figure 2b).
 
-Given the respective dependences, the extent to which a species $i$ affects species $j$ relative to the extent to which $j$ affects $i$ can be summarised by the interaction asymmetry given by $$a(i,j) = \frac{\left | d_{ij}-d_{ji} \right |}{max\left ( d_{ij}, d_{ji} \right )}.$$
+Given the respective dependences, the extent to which a species $i$ affects species *j* relative to the extent to which *j* affects *i* can be summarised by the interaction asymmetry given by $$a(i,j) = \frac{\left | d_{ij}-d_{ji} \right |}{max\left ( d_{ij}, d_{ji} \right )}.$$
 Mutual dependencies have previously been shown to be highly asymmetric in natural communities [@Bascompte2006]; in other words, if a plant species is largely dependent on a pollinator species, then that pollinator tends to depend rather weakly on the plant (or vice versa).
-This suggests that it may be possible to relax the assumption of bidirectional dependences and simplify the network further such that interacting species are only connected by one directed link when mutual dependencies are asymmetric (Figure 2c).
+This suggests that it may be possible to relax the assumption of bidirectional dependences further and simplify the network such that interacting species are connected by only one directed link when mutual dependencies are asymmetric (Figure 2c).
 Changing to unidirectional interactions determined by the observed direction of asymmetry, as a surrogate of bidirectional mutual dependences, does not alter the relative manageabilities of different networks (Supplementary Information S2).
@@
 
-Although understanding the variability of manageability across ecological networks is an useful result itself, we also wanted to test whether invasion status has an impact on the observed manageability values.
+Although understanding the variability of manageability across ecological networks is a useful result itself, we also wanted to test whether invasion status has an impact on the observed manageability values.
 We therefore used a set of generalised linear models (with binomial error structure) to investigate the effect of invasion status while also controlling for factors related to species richness, since one might naively expect to see a negative relationship between diversity and manageability [@Menge1995].
@@
 
-We next explored whether real networks differ in their architecture from random ones in a way that affects manageability. 
+We next explored whether real networks differ in their architecture from random ones in a concerted way that affects manageability. 
 Previous research indicates a direct link between a network's degree distribution and the number of nodes necessary to fully control it [@Liu2011], but the strength and applicability of this relationship has not been tested for in weighted ecological networks.
 We therefore compared the manageability of the empirical networks to networks generated by two null models which varied in terms of the constraints they impose. 
-The first set was generated by maintaining each species' degree (its number of interactions) while varying the number of visits per species. 
-Finally, the third set of random networks maintained the species' strength (its total sum of visits) while varying their degrees. 
-Randomisations were generated using vegan 2.3-3 [@Oksansen2016]. 
+The first set was generated by maintaining each species' degree (its number of interactions) while allowing the number of visits per species to vary. 
+The second set of random networks maintained each species' strength (its total sum of visits) while allowing their degrees to vary. 
+Randomisations were generated using vegan 2.3-3 [@Oksanen2016]. 
 After generating the randomized networks under these two schemes, we then calculated the mutual dependences and interaction asymmetries of each and determined their manageability using our maximum matching framework
@@
 That is, we first calculated the asymmetries for each community and then shuffled the direction of the link between each pair of species. 
-Similar as to the other null models, we calculated the average rank of the empirical manageability as compared to those of the randomisations.
+Similar as to the other null models, we calculated the average rank of the empirical manageability when compared to those of the randomisations.
 
@@
 
-Although the species importance calculated from mutual dependences contains full information, even in sparse networks, like these studied here, the number of maximal matchings increases exponentially with the number of links and nodes in a network.
+Although the species importance calculated from mutual dependences contains full information, even in sparse networks, like those studied here, the number of maximal matchings increases exponentially with the number of links and nodes in a network.
 Unfortunately, this means that the large number of links in the most diverse communities rendered the computation unfeasible when we used mutual dependencies. 
 Taking this limitation into account, we compared the relative network manageability obtained when using asymmetries to those found when using mutual dependencies to test if they gave consistent results.
-The comparison was performed for eleven of the twenty networks (those for which the number of matchings was smaller than $4\times 10^{10}$), using a paired Spearman correlation test, a weighted correlation coefficient $r_{w2}$ (which gives more weight to higher ranks; @PintoDaCosta2015-), and a Jaccard similarity of the driver species in both approaches.
+The comparison was performed for eleven of the twenty networks (those for which the number of matchings was smaller than 4 x 10^10^), using a paired Spearman correlation test, a weighted correlation coefficient *r~w2~* [which gives more weight to higher ranks; @PintoDaCosta2015], and a Jaccard similarity of the driver species in both approaches.
 All three approaches identified a high similarity in relative ranks. 
@@
 We then asked the question of whether some species-level structural properties can predict our estimates of species importance.
-We used a generalised linear mixed-effects model (GLMM) with binomial error structure with the relative importance as the response variable. 
-As predictors in this model, we included measures of centrality (degree and eigen-centrality), which have been found to be strong predictors of importance in a coextinction context [@Memmott2004]; a measure related to network robustness (contribution to nestedness), as nestedness has been proposed as one of the key properties that promote stability in mutualistic networks [@Saavedra2011; @Thebault2010]; two measures of strength of association and dependence (visitation and dependency strength), as their distribution determines the extent of interspecific effects [@Bascompte2006].
+We used a generalised linear mixed-effects model (with binomial error structure) with the relative importance as the response variable. 
+As predictors in this model, we included measures of centrality (degree and eigen-centrality), which have been found to be strong predictors of importance in a coextinction context [@Memmott2004]; a measure related to network robustness (contribution to nestedness), as nestedness has been proposed as one of the key properties that promote stability in mutualistic networks [@Saavedra2011]; two measures of strength of association and dependence (visitation and dependency strength), as their distribution determines the extent of interspecific effects [@Bascompte2006].
 In addition, we also included guild and invasive status as categorical fixed effects; although the importance of plants and pollinators or invasive and non-invasive species could respond differently to our structural metrics, our data set did not contain enough variation to include the corresponding interactions terms for these latter two predictors.
 All network metrics were calculated using the R package bipartite 2.06 [@Dormann2008]. 
-We lastly allowed for variation between different communities by including the network identity as a random effect [@Bates2015a]. 
-Candidate models were compared using AICc and the relative importance of the explanatory variables was evaluated using the sum of Akaike weights over candidate models that accounted for 95% of the evidence [@Burnham2003; @Bates2014; @Barton2016].
+We lastly allowed for variation between different communities by including the network identity as a random effect [@Bates2015]. 
+Candidate models were compared using AICc and the relative importance of the explanatory variables was evaluated using the sum of Akaike weights over candidate models that accounted for 95% of the evidence [@Burnham2003; @Bates2015; @Barton2016].
 Coefficient estimates were averaged following [@Buckland1997a] while confidence intervals were calculated following [@Lukacs2010].
@@
 All of the networks studied here had levels of manageability between `r round(min(1-dplyr::filter(n_driver, type == "z-bi")$n_dr_p), digits = 2)` and `r round(max(1-dplyr::filter(n_driver, type == "z-bi")$n_dr_p), digits = 2)` (mean `r round(mean(1-dplyr::filter(n_driver, type == "z-bi")$n_dr_p), digits = 2)`) when we considered bidirectional links weighted by the mutual dependences.
-This was in strong agreement with the results obtained using the dependence asymmetry in which manageability ranged between `r round(min(1-dplyr::filter(n_driver, type == "weight")$n_dr_p), digits = 2)` and `r round(max(1-dplyr::filter(n_driver, type == "weight")$n_dr_p), digits = 2)` (mean `r round(mean(1-dplyr::filter(n_driver, type == "weight")$n_dr_p), digits = 2)`; Spearman rank correlation `r round(src_bi_w$estimate, digits = 2)`, $p `r fix_small_pvalue(src_bi_w$p.value)`$).
+This was in strong agreement with the results obtained using the dependence asymmetry in which manageability ranged between `r round(min(1-dplyr::filter(n_driver, type == "weight")$n_dr_p), digits = 2)` and `r round(max(1-dplyr::filter(n_driver, type == "weight")$n_dr_p), digits = 2)` (mean `r round(mean(1-dplyr::filter(n_driver, type == "weight")$n_dr_p), digits = 2)`; Spearman rank correlation `r round(src_bi_w$estimate, digits = 2)`, *p* `r fix_small_pvalue(src_bi_w$p.value)`).
 In addition, we found that invaded communities were significantly more difficult to manage than uninvaded ones even when controlling for potential diversity effects (Figure 3). 
@@
   fer_theme +
-  scale_x_discrete(labels = c("un-invaded", "invaded"), name = "") +
+  scale_x_discrete(labels = c("uninvaded", "invaded"), name = "") +
   ylab("adjusted manageability") +
@@
 When exploring the effect of network structure itself, we observed that the manageability of empirical networks was, in general, not significantly different to the manageability of network randomisations that maintained the degree or the strength of individual species (Figure 4).
-However, when comparing the empirical network to randomisations that maintained the network structure but randomised only the direction of the asymmetries, we found that empirical networks showed a significant tendency to have smaller values of manageability
+However, when comparing the empirical network to randomisations that maintained the network structure but randomised only the direction of the asymmetries, we found that empirical networks showed a significant tendency to have smaller values of manageability.
 
@@
 
-We found a strong agreement between the values of relative species' importance in the 11 networks for which we were able to calculate them using both mutual dependencies and asymmetries (Spearman's rank correlation ranged between $\rho = [
-`r round(min(dplyr::filter(correlations, threshold == 0.5, type == "asymmetry", scaled == T)$V3, na.rm = T), digits = 2)`, `r round(max(dplyr::filter(correlations, threshold == 0.5, type == "asymmetry", scaled == T)$V3, na.rm = T), digits = 2)`]$, median $\tilde{\rho} =
-`r round(median(dplyr::filter(correlations, threshold == 0.5, type == "asymmetry", scaled == T)$V3, na.rm = T), digits = 2)`)$. 
-Moreover both approaches identified a highly similar set of driver species (Jaccard similarity $J = [
-`r round(min(dplyr::filter(correlations, threshold == 0.5, type == "asymmetry", scaled == T)$V4, na.rm = T), digits = 2)`, `r round(max(dplyr::filter(correlations, threshold == 0.5, type == "asymmetry", scaled == T)$V4, na.rm = T), digits = 2)`]$, $\tilde{J} =
-`r round(median(dplyr::filter(correlations, threshold == 0.5, type == "asymmetry", scaled == T)$V4, na.rm = T), digits = 2)`)$. 
-Notably, we found that the agreement was stronger for highly ranked species than for lowly ranked species ($\tilde{r_{w2}} = `r round(median(dplyr::filter(correlations, threshold == 0.5, type == "asymmetry", scaled == T)$V1, na.rm = T), digits = 2)`$ versus $\tilde{r_{w2}} = `r round(median(dplyr::filter(correlations, threshold == 0.5, type == "asymmetry", scaled == T)$V2, na.rm = T), digits = 2)`$) when using the weighted rank correlation coefficient $r_{w2}$.
+We found a strong agreement between the values of relative species' importance in the 11 networks for which we were able to calculate them using both mutual dependencies and asymmetries (Spearman's rank correlation ranged between *ρ* = [`r round(min(dplyr::filter(correlations, threshold == 0.5, type == "asymmetry", scaled == T)$V3, na.rm = T), digits = 2)`, `r round(max(dplyr::filter(correlations, threshold == 0.5, type == "asymmetry", scaled == T)$V3, na.rm = T), digits = 2)`], median `r round(median(dplyr::filter(correlations, threshold == 0.5, type == "asymmetry", scaled == T)$V3, na.rm = T), digits = 2)`).
+Moreover, both approaches identified a highly similar set of driver species (Jaccard similarity *J* = [`r round(min(dplyr::filter(correlations, threshold == 0.5, type == "asymmetry", scaled == T)$V4, na.rm = T), digits = 2)`, `r round(max(dplyr::filter(correlations, threshold == 0.5, type == "asymmetry", scaled == T)$V4, na.rm = T), digits = 2)`], median
+`r round(median(dplyr::filter(correlations, threshold == 0.5, type == "asymmetry", scaled == T)$V4, na.rm = T), digits = 2)`). 
+Notably, we found that the agreement was stronger for highly ranked species than for lowly ranked species (mean *r~w2~* = `r round(median(dplyr::filter(correlations, threshold == 0.5, type == "asymmetry", scaled == T)$V1, na.rm = T), digits = 2)` versus `r round(median(dplyr::filter(correlations, threshold == 0.5, type == "asymmetry", scaled == T)$V2, na.rm = T), digits = 2)`) when using the weighted rank correlation coefficient.
 Given the overall similarities, we concentrated on the relative rankings obtained using asymmetries in the following results.
@@
 Invasive species were driver species in every single network they were present, that is, they always had the highest relative ranking of species importance (Figure 5). 
-Overall, plants showed significantly higher levels of importance than pollinators (Mann-Whitney-Wilcoxon test, $p = `r fix_small_pvalue(wilcox.test(pp ~ guild, data = dd, alternative = "greater")$p.value, 3)`$).
+Overall, plants showed significantly higher levels of importance than pollinators (Mann-Whitney-Wilcoxon test, *p* = `r fix_small_pvalue(wilcox.test(pp ~ guild, data = dd, alternative = "greater")$p.value, 3)`).
 However, this difference can largely be explained by the strength of dependency of the species (the sum of the dependencies for a given species). 
-Indeed, when averaging over the set of GLMMs that accounted at least 95\% of the evidence based on AICc, we found that species' strength of dependency is the single most important factor determining the relative importance of species for network control (Table 1, Figure 5).
+Indeed, when averaging over the set of models that accounted at least 95\% of the evidence based on AICc, we found that species' strength of dependency is the single most important factor determining the relative importance of species for network control (Table 1, Figure 5).
 In contrast, the number of visits a species makes (or receives) and its contribution to nestedness had only a marginal effect on its relative importance.
@@
 Indeed, our empirical networks exhibit markedly lower levels of manageability compared to randomisations in which the visitation network was unchanged but where the observed patterns of dependence were broken.
-However, consistent with previous results [@Liu2011], we show that the manageability of empirical networks was indistinguishable from that of networks with a random structure (in terms of modularity and nestedness for example) that maintained the degree or strength of each species in the community.
+However, consistent with previous results [@Liu2011], we show that the manageability of empirical networks was indistinguishable from that of networks with a random structure that maintained the degree or strength of each species in the community.
 Therefore, the asymmetries at the species level (specialization-generalization asymmetries) and the link level (interaction's dependence asymmetries) appear to be sufficiently constrained by the distribution of species degree and strength [@Melian2002].
@@
 
-The changes on the asymmetries we found in the invaded networks are also reflected at a species level by the high relative importance of invasive species.
-However we found that invasive plants, are not inherently different to their native counterparts [@Stouffer2014].
+The changes in the asymmetries we found in the invaded networks are also reflected at a species level by the high relative importance of invasive species.
+However, we found that invasive plants are not inherently different to their native counterparts [@Stouffer2014].
 Invasive plants, just like any other mutualist in our data set, tend to be driver species to the degree to which their interaction partners are collectively more dependent on them than the other way around.
@@
 Because of their effects on other species in the community, driver species might be natural candidates for management interventions. 
-For instance, despite inconsistent outcomes in practice [@Suding2004; Rodewald2015; Smith2016], our results suggest that current restoration approaches that focus on direct eradication of invasive species might indeed be an effective way to modify ecosystem state.
-Nevertheless, our results also indicate that removals must be executed with caution as invaded communities tend to be highly dependent on invaders and therefore acutely vulnerable to their eradication [@Traveset2013; @Albrecht2014].
+For instance, despite inconsistent outcomes in practice [@Suding2004; @Rodewald2015; @Smith2016], our results suggest that current restoration approaches that focus on direct eradication of invasive species might indeed be an effective way to modify ecosystem state.
+Nevertheless, our results also indicate that removals must be exercised with caution as invaded communities tend to be highly dependent on invaders and therefore acutely vulnerable to their eradication [@Traveset2013; @Albrecht2014].
 Although useful for identifying conservation priorities, our approach is different to previous attempts to quantify species importance that concentrate on measures of centrality, position, co-extinction or uniqueness [@Jordan2006; @Jordan2009; @Lai2012; @McDonald-Madden2016].
 Instead the concept of driver species is more akin to the original concept of keystone species, which illustrated how changes on the abundance of a key species in turn affect the abundances of other members of the community [@Paine1969; @Paine1995].
-However, while keystone species were traditionally identified by inferring the effects of a perturbation on a community's population dynamics [@Mills1993], the driver species concept operates the other way round; namely, it uses the community dynamics, underpinned by the interspecific effects, to infer the effects of a perturbation.
-While it is challenging to quantify the dependence of species in an ecological community, an experimental approach to identify dynamically important species might be even more difficult to implement.
+However, while keystone species were traditionally identified by gauging how a community's population dynamics respond to a perturbation [@Mills1993], the driver species concept operates the other way round; namely, it uses the community dynamics, underpinned by the interspecific effects, to infer the effects of a perturbation.
+While it is challenging to quantify the dependence of species in an ecological community, a purely experimental approach that identifies dynamically important species in a similar manner might be even more difficult to implement.
 
 Overall, our investigation confirms the conclusions of previous studies that suggested that, in contrast to other types of complex systems, the structure of ecological networks renders them remarkably difficult to control [@Liu2011; @Ruths2014].
-In a hypothetical situation in which the goal were to regulate the abundances of all species in a pollination community, our results indeed suggest that we would need to directly intervene the abundances of at least 40-90% of those species.
+In a hypothetical situation in which the goal were to regulate the abundances of all species in a pollination community, our results indeed suggest that we would need to directly intervene with the abundances of at least 40-90% of those species.
 Fully controlling an ecological community is no doubt an idealistaion, as designing and implementing the management interventions needed is currently impractical. 
@@
 In this study, we illustrate how a control-theoretic approach can be adopted when estimating the effect of invasions—a major driver of global change—on mutualistic communities.
-Note though that it can be easily extended to understand the structural effects of other kind of perturbations and for systems governed by different types of species interactions. 
+Notably, it can also be extended to understand the structural effects of other kind of perturbations and for systems governed by different types of interactions. 
 Moreover, we see great potential by explicitly integrating control theory with dynamic models of species densities [@Cornelius2013; @Gibson2016]. 

### 2016-07-18 code/12-species_models_bi.R
check model of species characteristics vs importance using mutual dependences ranking

@@ -1,0 +1,116 @@
+library(magrittr)
+library(foreach)
+library(doMC) 
+library(glmulti)
+
+registerDoMC(cores = as.numeric(commandArgs(trailingOnly = T)[1]))
+setwd("~/github/driver-species/")
+
+"./code/functions" %>% 
+	list.files(full.names = T) %>%
+	plyr::l_ply(source)
+
+driver <- c("./data/processed/matching_frequency_bi")  %>% 
+	read_allRDS()
+
+d_sp <- driver %>%
+	get_frequencies() %>%
+	dplyr::mutate(type = "z_bi",
+								scaled = FALSE)
+
+# merge with species information
+drivers <- dplyr::inner_join(d_sp, s_p) %>% 
+	dplyr::mutate(d_s_m = d_strength / degree, 
+								v_s_m = v_strength / degree)
+net <- "./data/processed/networks" %>%
+	read_networks()
+
+guild <- c("pla", "pol") %>%
+	plyr::ldply(function(y){
+		o <- lapply(net, function(x) igraph::V(x)[igraph::V(x)$type == y]$name) %>%
+			unlist() %>% unique()
+		data.frame(guild = y, species = o)
+	})
+
+# insert guild information
+drivers <- drivers %>%
+	dplyr::inner_join(guild) %>% 
+	dplyr::inner_join(meta) 
+# drivers %>%
+# dplyr::filter(threshold == 0.5,
+#               type == "asymmetry",
+#               scaled == F, 
+#               study != "ballantyne") %>%
+# ggplot(aes(x = guild, y = d_reim)) +
+# geom_violin(aes(fill = guild))
+
+# explore correlations
+factor_correlations <- drivers %>%
+	plyr::dlply("guild", function(x){
+		x %>% 
+			dplyr::select(nestedcontribution, degree, d_strength, v_strength, eig_cen) %>%
+			as.matrix() %>%
+			cor()
+	})
+
+# basic models
+library(lme4)
+setMethod('getfit', 'glmerMod', function(object, ...) {
+	summ <- coef(summary(object))
+	summ1 <- summ[,1:2,drop=FALSE]
+	## if (length(dimnames(summ)[[1]])==1) {
+	##     summ1 <- matrix(summ1, nr=1,
+	##                     dimnames=list(c("(Intercept)"),
+	##                     c("Estimate","Std. Error")))
+	## }
+	cbind(summ1, df=rep(times =10000,length(fixef(object))))
+})
+
+
[…]

### 2016-07-18 paper/covering_letter.tex
update cover letter

@@
        %\vspace*{20pt}
-       Prof. XX\\
-       Chief Editor\\
+       Prof. Tim Coulson\\
+       Editor in Chief\\
        Ecology Letters}
 
-\opening{Dear Proffesor}
+\opening{Dear Proffesor Coulson,}
 
-We are submitting the manuscript entitled ``Biotic invasions reduce the manageability of mutualistic networks'' to be considered for publication at \emph{Ecology Letters}.
+We are submitting the manuscript entitled ``Biotic invasions reduce the manageability of pollination networks'' to be considered for publication at \emph{Ecology Letters}.
 
-Central to this manuscript is the introduction and development of the concept of \textbf{theoretical manageability}.
+Central to this manuscript is the introduction, development, and application of the theoretical concept of \textbf{ecological manageability}.
 Based on the patterns of interactions between species, this idea can provide two main pieces of information. 
-First, it allows to quantify the \textit{community manageability}---an indication of the difficulty to control the abbundances of all species in the community. 
-Second it allows to identify the \textit{driver species}--- those with a disproportionate ability to alter other species' abundances.  
-We use this concept as a framework to study the changes caused by biotic invasions to the community manageability and examine the role played by individual species.
+First, it allows to quantify the \textit{community manageability}---an indication of the difficulty of controlling the abundances of all species in the community. 
+Second it allows to identify \textit{driver species}--- those species with a disproportionate ability to alter other species' abundances.  
+Here, we use this concept as a framework to study the changes induced by biotic invasions to pollination networks.
 
 Multiple empirical observations have suggested that the structural changes caused by invasions may lead to increased ecosystem resilience. 
-Our study is the first to use empirical data to provide explicit theoretical support to this idea. 
-Furthermore, our approach to quantify the relative importance of species is unique at that is based on the structure that underpin the community dynamics while at the same time having a direct link with management.
-Not only our results highlight the ability that some species, and invaders in particular, have to drive the dynamics of other species in the community, but also identifies "asymmetric dependence" as the key factor driving these interspecific differences.
+Our study is the first to use empirical data to provide theoretical support for this idea. 
+Furthermore, our approach to identify driver species and quantify their relative importance, is unique in that it is based directly on the aspects of network structure that determine the behavior of the community as a holistic dynamical system.
+Our results also highlight the extent to which some species---invaders in particular---can drive the dynamics of other species across their community, and also identify ``asymmetric dependence'' as the potential mechanism driving the interspecific differences.
 
-We developed the ideas of community manageability and driver species with the underlying motivation to study the consequences of biotic invasions in mutualistic systems. 
-Nevertheless, understanding how drivers of ecosystem change affect ecosystem dynamics is not exclusive to mutualistic communities. 
+Despite our focus, understanding how drivers of ecosystem change affect ecosystem dynamics is not exclusive to mutualistic communities. 
 Indeed, we envisage the application of the concepts we introduce to answer a wide range of ecological questions in communities structured by different types of interactions.
-The methodology necessary for its implementation---an extension of recently developed tools at the interface of complex systems and control theory---is thoroughly detailed in the manuscript.
+As such, we have sought to highlight the methodology necessary for its implementation---an extension of recently developed tools at the interface of complex systems and control theory---thoroughout the manuscript.
 
-In addition, although our study lies fundamentally within ecological theory, it has ramifications pertinent to ecological application. 
-We think that concepts like theoretical manageability have the potential to stimulate much needed research that shorten the gap between ecological theory and management.
-Hopefully setting us on the track to informed, rather than hopeful, ecosystem interventions.
+Our study fundamentally lies within ecological theory, yet it has ramifications pertinent to ecological application. 
+Indeed, we show in the paper that concepts like ``manageability'' have the potential to stimulate much needed research that reduce the gap between theory and management.
+Hopefully our study and more like it will set us on the track to informed, rather than hopeful, ecosystem interventions.
 
-The enclosed work represents a novel work also for all co-authors involved and no work published, in press, or submitted during this or last year has been cited.
+Lastly, please note that the enclosed work represents a novel contribution for all co-authors involved and no related work published, in press, or submitted during this or last year has been cited.
 

### 2016-07-19 paper/supp_info.Rmd
changes Daniel made to the PDF of the SI prior to submission

@@
   attr(x, "scaled") <- stringr::str_split(as.character(y[,2]), "_") %>% unlist() %>% extract(2) %>% as.logical()
+
   return(x)
@@
 $n_d$ and manageability values correspond to the assumption  that a species that depends more strongly on an interaction partner is controled by the partner.
-British networks were assembled by @Lopezaraiza-Mikel2007, Spanish were networks assembled by @Bartomeus2008.*
+British networks were assembled by @Lopezaraiza-Mikel2007, whereas Spanish were networks assembled by @Bartomeus2008.*
 ```{r n_driver, echo = FALSE, warning = F, message = F, results = "asis"}
@@
 
-All together, evidence supports the idea that visitation is a suitable metric to estimate the mutual dependency of species pairs.
-First it is directly related to pollinator foraging.
-Second it produces results consistent, at least within our controllability framework, with plant reproductive success (as estimated by the importance metric).
+Altogether, evidence supports the idea that visitation is a suitable metric to estimate the mutual dependency of species pairs.
+First, it is directly related to pollinator foraging.
+Second, it produces results consistent, at least within our controllability framework, with plant reproductive success (as estimated by the importance metric).
 
@@
 ```
-_Figure S1: Distribution of interaction weights for the pollen deposition, visitation and pollinator importance networks. Note that the *x* axis in the density plots have been log-transformed._
+_Figure S1: Distribution of interaction weights for the pollen deposition, visitation and pollinator importance networks. Note that the *x* axes in the density plots have been log-transformed._
 
-*Table S2: Spearman correlation coefficients (with p-value) of the relative importance of species and the percentage of interactions that share the direction of dependency obtained using the three weighting schemes and an unweighted scheme*
+*Table S2: Spearman correlation coefficients (with p-value) of the relative importance of species and the percentage of interactions that share the direction of dependency obtained using the three weighting schemes and an unweighted scheme.*
 ```{r table correlations, echo = FALSE, warning = F, message = F, results = "asis"}
@@
 We calculated the number of driver species necessary to control the whole community under the assumption that a species that depends more strongly on an interaction partner is more likely to be controlled by the partner.
-We tested the robustness of this assumption by comparing the relative number of driver species assuming that *(i)* the dependency asymmetry does not imply an unidirectional control direction, rather a species could control all its interaction partners and vice versa, *(ii)* that plants depend on pollinators, and that *(iii)* pollinators depend on plants.
+We tested the robustness of this assumption by comparing the relative number of driver species assuming that *(i)* the dependency asymmetry does not imply a unidirectional control direction, rather a species could control all its interaction partners and vice versa, *(ii)* that plants depend on pollinators, and that *(iii)* pollinators depend on plants.
 Our results using the direction of the largest dependency are consistent with the proposed alternatives: although we obtained different absolute numbers of driver species, their relative numbers are not statistically different (Figure S3, Table S3).
@@
 ```
-*Figure S2: One of the possible maximum matchings for each of the assumptions regarding the direction of control: a) plants can drive the abbundance of pollinators but not otherwise, b) pollinators can drive the abbundance of plants but not otherwise; c) plants can drive the abbundance of pollinators with the same likelyhood than pollinators can modify the abbundance of plants*
+*Figure S2: One of the possible maximum matchings for each of the assumptions regarding the direction of control: a) plants can drive the abundance of pollinators but not otherwise, b) pollinators can drive the abundance of plants but not otherwise; c) plants can drive the abundance of pollinators with the same likelihood than pollinators can modify the abundance of plants.*
 
@@
 *Table S4: Model selection table for the manageability of studied communities.
-Type refers to wether the manageability was calculated using mutual dependences or interaction asymetries.
-"y" and "n" indicate wheter a variable was included in the model or not.*
+Type refers to whether the manageability was calculated using mutual dependences or interaction asymmetries.
+"y" and "n" indicate whether a variable was included in the model or not.*
 ```{r models, echo = F, message=F, warning=F, results="asis"}
@@
 The colour of the line corresponds to the relative importance obtained when all maximal matchings are accepted (threshold is zero).
-Only networks for which we were able to calculate the relative importance using mutual dependences are shown, but patterns of relative importance calculated using interaction asymetries are similar for the remainding networks.
+Only networks for which we were able to calculate the relative importance using mutual dependences are shown, but patterns of relative importance calculated using interaction asymmetries are similar for the remaining networks.
 Network numbers correspond to those in Table S1.*
@@
 ```
-*Figure S6: Weighted rank correlation coeficient $\tilde{r}_{w2}$ between (A) the relative importance of species given by the importance network in @Ballantyne2015 weighted by mutual dependences and the visitation network weighted by the interaction asymetries.
+*Figure S6: Weighted rank correlation coefficient $\tilde{r}_{w2}$ between (A) the relative importance of species given by the importance network in @Ballantyne2015 weighted by mutual dependences and the visitation network weighted by the interaction asymmetries.
 (B) the relative importance of species given by mutual dependences and interaction asymmetries for a subset of the paired invaded-uninvaded networks.

### 2016-11-21 paper/EL-reviewer-comments-1.Rmd
Reviewer comments initial commit

---
title: "Response to reviewer comments ELE-00738-2016"
date: "21 November 2016"
output: pdf_document
---

Dear Prof. Jonathan Chase,

We are grateful for the opportunity to resubmit a revised manuscript for your consideration. We have endeavored to incorporate all reviewers' feedback into the manuscript and we feel the attached draft constitutes an important improvement from the previous version. We were impressed by the quality of the reviews; they all were particularly thoughtful, clear, and constructive. It is evident that all three anonymous reviewers have given a fair and careful consideration to our manuscript. Therefore, we would like to especially thank them---not with the customary platitude usual in response letters, but with sincere gratitude for their valuable feedback.

The reviewers identified major limitations in our manuscript. Specifically with regards to the terminology, the underlying  structural control, and the lack of detail in the presentation of the empirical networks. In the current version, we have thoroughly addressed all these concerns and improved the robustness of the analyisis and the clarity of the concepts. Detailed responses to each comment, one by one, are provided below.

Fernando Cagua

******************************************

## Referee 1

In ms ELE-00738-2016, the authors seek to apply ideas from control theory (specifically, structural controllability) to bipartite ecological networks. The main idea of structural control theory, at least in the recent applied literature, is that some nodes are recipients of external, time-varying control signals that proceed to propagate through a network in such a way as to drive the state of every node in the network to a desired configuration in finite time. There tend to be many ways to do this, and nodes can further be characterized by the frequency with which they exist on key paths leading through the network.

These ideas have been used as additional measures to describe the topological characteristics of networks as they relate to their control. The novelty of the present ms is in extending these ideas in a rigorous way to mutualistic ecological networks, which to my knowledge has not yet been done (some existing work includes ecological networks, but usually in a somewhat cursory way).

This is a powerful premise and, at least in principle, a ms with such a focus could be a good candidate for publication in Ecology Letters. However, I have numerous concerns with the manuscript. The methodological assumptions of structural control are never discussed (i.e., what is the assumed form of the dynamic relationship between interacting nodes?), the extent to which this is or is not realistic in an ecological context is not discussed (it seems to me that there are important caveats), other details of the theory are left unexplained, a key term is used in a different context than in the control literature (which will needlessly confuse readers), and some of the statistical analysis seems questionable.

I expound on this overview in some detail below. I regret that I cannot be more enthusiastic about the manuscript in its current form and I wish the authors luck as they revise their manuscript.

- The authors begin by stating, "Complex systems are characterised by non-linear relationships...", however, there is an entire branch of work devoted to network control that explicitly assumes linearity on the level of specific interaction (see e.g. doi 10.1126/science.1242063 and doi 10.1038/nature10011, both of which the authors cite). It seems to me that the authors could simply remove this bit of text and restructure the sentence to make the same point -- that complex systems are often viewed as being "greater than the sum of its parts."

    *Accepted; changed.*

The paragraph on lines 50-62 cites papers published no earlier than 2011. However, to support the following argument "Despite these advances, the link between the structure of complex networks and our ability to manage and conserve them is still ambiguous", the authors cite a paper that predates all of them (Tylianakis et al. 2010). The paper in question highlights practical challenges to conservation; many if not all of them remain today (which I suspect is the authors' argument). I suggest the authors revise the text to make the contribution of this reference clear.

Comment 3
Lines 95-97: "The number of nodes necessary to fully control a complex network can be calculated by counting the number of unmatched nodes in the network's maximum matching (Liu et al. 97 2011)."

This statement must be contextualized by the assumed nature of the dynamical relationships in this framework. It therefore seems to me that this statement should be preceded by a discussion of those details (indeed, the authors argue that this is necessary in the Introduction, on lines 48-49).

Furthermore, the authors need to discuss the appropriateness of this framework to ecological systems. The input control signals that drive even relatively simple networks to specified states can be very sensitive to initial conditions and complicated (indeed, they usually aren't calculated at all). How can a control scheme be implemented even in principle if nodes represent species populations and a control signal calls for a fractional change in a node state variable over the course of minutes? Furthermore, how do the authors interpret the methods by which cycles are controlled in linear control theory (see e.g. doi 10.1126/science.1242063 and its supplementary material) in the context of ecological management? How frequent are cycles in the authors' ecological networks?

I should emphasize that I am a fan of control theory and I think it is interesting to apply it as the authors do in this ms. However, the caveats that come along with the points I outline above need to be made clear for the reader.

The authors might be interested in doi 10.1063/1.4931570 for a discussion of some relevant ideas.

Comment 4
Lines 101-103: "(ii) the sum of the weights of the matched links—known as matching weight—is the largest possible among all possible matchings of that size (West 2001)."

The authors go on to cite Liu et al. 2011, but that report (and many others cited in the present ms) considers "structural controllability", which assumes binary edge weights (i.e., they exist or they do not). Is condition (ii) appropriate here? If so, why? The authors get at this later in the ms (lines 145-152, where it looks as if edges are indeed binarized), but for readers familiar with the structural control literature, there is room for confusion as they come to this point in the ms. This may be mitigated as the authors address my comment 3, but it seems appropriate for me to raise this point explicitly as well.

Comment 5
When defining n_d on line 119, it is more accurate to say that it is the "minimum number" of species needed to gain full control.

Comment 6
Lines 132-133: "...we therefore call driver species those that are identified as being a superior node in all possible matchings..."
I have several comments here. First, shouldn't this be "all possible maximum matchings"?

Second, a node with no outgoing edges will clearly never be a superior node and will therefore not be a driver node. I assume that this never happens in the mutualistic networks under consideration, but this probably bears mentioning so as to help develop the reader's intuition for this assessment. In any event it would be useful for the reader to see a simple network (or several) to provide clear examples of driver nodes and non-driver nodes. For instance, how can a node with an outgoing edge not be a driver node?

Finally, the term "driver species" (or more generically, "driver node") has a specific meaning in the control literature (doi 10.1038/nature10011): what the authors here denote with n_d on line 118. To avoid confusion with those familiar with the control theory literature (and those readers who are inspired by this ms to delve into it), I suggest a change of terminology. Perhaps "key species"?

Comment 7
The approach described in lines 145-152 would be clearer if the authors included a figure demonstrating each step for a simple network.

Comment 8
Lines 173-176: "To do so, we calculated the maximum matching of the corresponding pollination network, and estimated the minimum proportion of species that need directed interventions to fully control the species abundances in the community." Why is this an estimate? The number of species that need to be directly controlled can be determined unambiguously.

Comment 9
It seems to me that the number of interactions would also be an interesting factor to consider in the statistical analysis (discussed beginning on line 213).

Comment 10
Lines 225-228: "Previous research indicates a direct link between a network's degree distribution and the number of nodes necessary to fully control it (Liu et al. 2011), but the strength and applicability of this relationship has not been tested for in weighted ecological networks."

The authors go on to discuss null models that vary edge weights. However (as mentioned in comment 4), it seems to me that the edge weight is ultimately not a factor when determining the manageability of the network, at least once it has been mapped to unidirectional and unweighted edges. The methodology and rationale here needs to be clarified. For instance, is the effect of changing edge weight restricted to affecting interaction asymmetry and thereby the unidirectional projection of the interactions? If so, how does this differ from the null model that does this explicitly (described on lines 239-246)? Does edge weight play any other role in this analysis? (Its role is clear in the section beginning on line 247.)

Comment 11
It seems useful to mention the typical size of the networks at the beginning of the results, if not earlier. In addition, the fact that the mean value of m is 0.37 means that roughly two thirds of the species in these communities need to be directly controlled, at least according to this modeling framework. It seems to me that this merits explicit comment in the Discussion.

Indeed, in the Discussion the authors say for example, "Because of their effects on other species in the community, driver species might be natural candidates for management interventions." This may be true, but it seems to me that the role of the directly-controlled species (that populate n_d), which serve as the gateway for the control signals to the rest of the network, merits discussion here as well. How are the two related? Do the authors envision a scenario where a control signal is actually being sent in to the network? Or do they rather envision a scenario where no controls are being used (which is counter to the central idea of structural controllability), and are they instead identifying these drivers nodes simply to provide a proxy measure of the effect of node state perturbations on the rest of the network? The latter seems more plausible than the former, but in any case more detail is needed.

Comment 12
Figure 3 should show the distributions of m as well as the adjusted value of m. I suggest also providing more detail about how the adjusted value is calculated (in the current version there is one technical sentence that non-experts will not be able to follow).

Comment 13
In Appendix S2 (referenced in the ms on lines 205-208), the authors state that the relative number of driver species, while different for the approaches there discussed, are not significantly different from one another. However, the statistical test used is a Spearman correlation coefficient, which does not measure the difference in e.g. population means but rather the extent to which their relationship is monotonic.

Minor comments
Line  236: there is a missing period.

Referee: 2

Comments for the Authors
General comments
This manuscript proposes to apply the methods published in previous papers (e.g. Liu et al, Nature 2011) on the controllability of complex systems to invaded pollination networks. Note that controllability is rebranded “manageability” (unless it has a different meaning in this paper?). The manuscript also proposes to identify the nodes to manage or driver species. This is a fascinating area of research.
Performing a controllability study on ten pairs of uninvaded and invaded plant-pollinator networks, the main finding is that invaded networks require a higher number of nodes to control than their non-invaded counterpart and invasive plants were driver species in all studied communities.
The study is scientifically sound. However the manuscript is dense and difficult to read. In particular the section Theoretical framework and its subsection are confusing and should be merged with the Methods section. The discussion should be strengthen.
In its current form, it is unlikely that readers will be able to understand or replicate the research presented – which is a shame considering the authors went through a lot of trouble to apply a control theory study in an ecological context. An overall simplification of the language/sentences and jargon used will increase the readability of this manuscript. Ruths (2014, Science) and Liu (2011, Nature) are doing a better job at explaining maximum matching, driver nodes and the overall challenge of controllability.
Specific comments
1)      Consider being more specific in your abstract.
2)      L74 “we _expand_ previous theory of the control of complex systems to an ecological context”. Do you mean apply? Please clarify your contribution without ambiguity.
3)      Section Manageability (L94).
a.      Please first define manageability before maximum matching.
b.      The maximum matching paragraph is difficult to understand. Reword.
4)      Section Relative importance (L121).
a.      It seems that the abstract refers to this section as being a novel way to identify communities’ driver species. However it is very unclear that this is a novel contribution. Please clarify in the text and provide details in supplementary information. It is also unclear from the Methods section.
5)      Discussion:
a.      McDonaldMadden et al (2016) actually show that network metrics are not useful to prioritise the management of foodweb, i.e. to determine which species should be managed first (if required). Please edit current text and analyse differences with your work.
b.      Please provide some insight into how your method/analysis/results would differ for non- pollinator invaded networks.
c.      Please discuss the caveats of your approach. I suggest moving some of the statistical analyses in sup info if word limit is an issue.

6)      The maximum matching algorithm is computationally expensive as noted by the authors. In Ruths & Ruths (2014) the authors come with an interesting alternative to calculate the minimum number of independent controls (driver species) using only the number of source nodes, external dilation points and internal dilation points; and a heuristic using source and sink nodes. What is the profile of the pollinator networks studied? Would the Ruths & Ruths approach be an easier way of reaching the same conclusions? Would it bring complementary information?
7)      A few typos in main text and sup info.
8)      Is there a compelling reason to change controllability to “manageability”? Walters did the same thing with “adaptive management” in lieu of “adaptive control”.
30 years later, no one remembers where “adaptive management” originally came from and it has become a keyword in ecology. As a result, ecologists have been cut from the theoretical advances in control theory and most often have no clue that these are the same thing.

Referee: 3

Comments for the Authors
In this work Cagua et al apply tools rooted in control theory to ecological networks and discuss how this approach could be used for management of natural systems, with emphasis on the effects of invasive species. This is an exciting work. It presents to ecologists a novel way of studying the relationship between topology and dynamics that is less dependent (when compared to other methods) on particular choices about how dynamics are modeled. The authors illustrate the potential of this approach by exploring how invasive species change system dynamics and manageability. My only concern about this manuscript is that the authors need to be more careful and more explicit about some limitations of this approach and the generality of their results, specially considering the implications of their results for management.

Only one type of interaction is being considered here when species are involved in multiple types of interactions. An assumption that is not explicit in the text is that all the factors controlling population densities are the interactions between plants and pollinators. The boundaries of a network, including the types of interactions that are considered or not, are often arbitrarily defined. However, this approach is highly dependent on the topology of the network and thus on how we define the network. I know this limitation applies to any study on system dynamics, but it becomes more serious when we argue that management decisions can be based on a single technique. I have two suggestions. First, the authors should discuss in detail these assumptions and their limitations. Second, It would be helpful if the authors could test the robustness of their results to sampling. The results show that invasive species change manageability. This suggests that manageability may be sensitive to sampling. A sensitivity analysis where species are added and removed from the network under different wiring schemes would help us understand the behavior of the manageability index when networks are undersampled and would allow a more informed discussion on how the choices we make when delimiting the network affect estimates of controllability. Weak links should not have a strong effect on controllability and considering the networks were built using visitation frequency, most of the strong interactions were likely sampled. Still, it would be great to show that the method is robust and this would make it easier to justify that even in the absence of complete sampling this technique is in fact useful for management.

See more specific comments below.

Ln 25. I don't think that the statement that you "expand theory on the controllability of complex systems" is accurate. It is not clear to me how these results contribute to expand the general theory

Ln 52, typo: presents

Ln 59. Please rewrite this sentence. it's not clear what "they" refers to here.

Ln 78. It is not clear why this is the direction of the hypothesis. Did you already have any indication that networks with invasive species should have lower manageability? Is there any theoretical explanation for this expectation?

Ln 95-98. It is very hard to keep track of all those definitions - matching, matched nodes, matched links, matching size, matching weight, maximum matching. I found myself going back and forth several times between the framework, methods and results sections. A glossary would help a lot.

Ln 99. Indicate how the matching is represented in the figure. e.g.,  "(dark grey links in Figure 1a)"

Figure 1.Indicate the driver nodes in these networks

Ln 128. Be clear about the meaning of resources here. I understand you mean financial resources not  resources in the ecological sense.

Ln 236. Typo: missing period

Ln 293: Typo: reference

Ln 303-305. Please explain here which is the response variable that the ratio of plant to pollinator can explain.

Ln 326. "The strength of the dependency" has been defined as species strength by Bascompte et al. 2006. Why are you using a different term here?  When you say strength of the dependency it is not clear if you mean strength of dependencies of a given species on other species or the strength of the dependencies of all species on the species of interest. Moreover sometimes you use dependence and others dependency.

Ln 336. Liu et al. 2011 found that driver nodes were often peripheral nodes in the network instead of network hubs. Here you find the opposite. How can you explain these differences?

Ln 343 and Figure 4. Here and in the figure legend you say the level of manageability of empirical networks is lower, but in the figure you show an index that goes in the opposite direction, i.e.,  we see lower values for the randomization. It would be better to present these results in a more intuitive way.

Ln 362. Again the idea that supergeneralists tend to be driver species contrasts with Liu et al. results. This should be explored in more detail in the discussion.

Ln 372. It is important to say that vulnerability is related change, but that it is had to predict in which direction the system will change

Figure 5 legend. Please include here the definition of dependency strength so the reader does not need to go back and forth.

## Editor's Comments

This was a difficult decision.  Like all the reviewers, I think this work has huge potential, and could have major impacts in applied ecology.  However, you are unclear in your terminology wrt to the major research field you apply to this interesting ecological setting and your exposition is opaque (for example, how exactly are manageability and controllability related? – see the important caution from R2 and the detailed comments from R1).  This makes it incredibly hard to follow your work, even for someone who works in network controllability.  There also seems to be key controllability methodological work you could more effectively leverage.  I applaud the close link of theory and empiricism, but more details of the field network pairs would be helpful.  Really major revisions will be required to get this ms into a form that appeals to both newcomers and experts in the field, and the manuscript will have to be re-reviewed (likely by a mix of the same and some new reviewers), but it does have excellent potential, so I encourage the authors to carefully and thoroughly deal with all of the reviewer comments.

*Thanks for the encouraging feedback*

### 2016-12-05 paper/EL-reviewer-comments-1.Rmd
some modifications to the methods

@@
 output: pdf_document
+bibliography: references.bib
 ---
@@
 
-The paragraph on lines 50-62 cites papers published no earlier than 2011.
+- The paragraph on lines 50-62 cites papers published no earlier than 2011.
 However, to support the following argument "Despite these advances, the link between the structure of complex networks and our ability to manage and conserve them is still ambiguous", the authors cite a paper that predates all of them (Tylianakis et al.
@@
 
-Comment 3
-Lines 95-97: "The number of nodes necessary to fully control a complex network can be calculated by counting the number of unmatched nodes in the network's maximum matching (Liu et al. 97 2011)."
+    *Accepted; changed.
+We revised the text to better reflect the contribution of @Tylianakis2010 at the same time we added a reference to a more recent paper by @Kaiser-Bunbury2015 who explicitly deals with oportunities, limitations and implications of applying network metrics in conservation science.*
 
-This statement must be contextualized by the assumed nature of the dynamical relationships in this framework.
+- Lines 95-97: "The number of nodes necessary to fully control a complex network can be calculated by counting the number of unmatched nodes in the network's maximum matching (Liu et al.
+97 2011)." This statement must be contextualized by the assumed nature of the dynamical relationships in this framework.
 It therefore seems to me that this statement should be preceded by a discussion of those details (indeed, the authors argue that this is necessary in the Introduction, on lines 48-49).
 
-Furthermore, the authors need to discuss the appropriateness of this framework to ecological systems.
+- Furthermore, the authors need to discuss the appropriateness of this framework to ecological systems.
 The input control signals that drive even relatively simple networks to specified states can be very sensitive to initial conditions and complicated (indeed, they usually aren't calculated at all).
@@
 How frequent are cycles in the authors' ecological networks?
-
 I should emphasize that I am a fan of control theory and I think it is interesting to apply it as the authors do in this ms.
 However, the caveats that come along with the points I outline above need to be made clear for the reader.
-
 The authors might be interested in doi 10.1063/1.4931570 for a discussion of some relevant ideas.
 
-Comment 4
-Lines 101-103: "(ii) the sum of the weights of the matched links—known as matching weight—is the largest possible among all possible matchings of that size (West 2001)."
+    * Acepted; changed.*
 
-The authors go on to cite Liu et al.
+- Lines 101-103: "(ii) the sum of the weights of the matched links—known as matching weight—is the largest possible among all possible matchings of that size (West 2001)." The authors go on to cite Liu et al.
 2011, but that report (and many others cited in the present ms) considers "structural controllability", which assumes binary edge weights (i.e., they exist or they do not).
@@
 
-Comment 5
-When defining n_d on line 119, it is more accurate to say that it is the "minimum number" of species needed to gain full control.
+- When defining n_d on line 119, it is more accurate to say that it is the "minimum number" of species needed to gain full control.
 
-Comment 6
-Lines 132-133: "...we therefore call driver species those that are identified as being a superior node in all possible matchings..."
+- Lines 132-133: "...we therefore call driver species those that are identified as being a superior node in all possible matchings..."
 I have several comments here. First, shouldn't this be "all possible maximum matchings"?
@@
 
-Comment 7
-The approach described in lines 145-152 would be clearer if the authors included a figure demonstrating each step for a simple network.
+- The approach described in lines 145-152 would be clearer if the authors included a figure demonstrating each step for a simple network.
 
-Comment 8
-Lines 173-176: "To do so, we calculated the maximum matching of the corresponding pollination network, and estimated the minimum proportion of species that need directed interventions to fully control the species abundances in the community." Why is this an estimate?
+- Lines 173-176: "To do so, we calculated the maximum matching of the corresponding pollination network, and estimated the minimum proportion of species that need directed interventions to fully control the species abundances in the community." Why is this an estimate?
 The number of species that need to be directly controlled can be determined unambiguously.
 
-Comment 9
-It seems to me that the number of interactions would also be an interesting factor to consider in the statistical analysis (discussed beginning on line 213).
+- It seems to me that the number of interactions would also be an interesting factor to consider in the statistical analysis (discussed beginning on line 213).
 
-Comment 10
-Lines 225-228: "Previous research indicates a direct link between a network's degree distribution and the number of nodes necessary to fully control it (Liu et al.
+- Lines 225-228: "Previous research indicates a direct link between a network's degree distribution and the number of nodes necessary to fully control it (Liu et al.
 2011), but the strength and applicability of this relationship has not been tested for in weighted ecological networks."
@@
 
-Comment 11
-It seems useful to mention the typical size of the networks at the beginning of the results, if not earlier.
+- It seems useful to mention the typical size of the networks at the beginning of the results, if not earlier.
 In addition, the fact that the mean value of m is 0.37 means that roughly two thirds of the species in these communities need to be directly controlled, at least according to this modeling framework.
@@
 
-Comment 12
-Figure 3 should show the distributions of m as well as the adjusted value of m.
+- Figure 3 should show the distributions of m as well as the adjusted value of m.
 I suggest also providing more detail about how the adjusted value is calculated (in the current version there is one technical sentence that non-experts will not be able to follow).
 
-Comment 13
-In Appendix S2 (referenced in the ms on lines 205-208), the authors state that the relative number of driver species, while different for the approaches there discussed, are not significantly different from one another.
+- In Appendix S2 (referenced in the ms on lines 205-208), the authors state that the relative number of driver species, while different for the approaches there discussed, are not significantly different from one another.
 However, the statistical test used is a Spearman correlation coefficient, which does not measure the difference in e.g.
@@
 
-Referee: 2
+## Referee 2
 
-Comments for the Authors
-General comments
 This manuscript proposes to apply the methods published in previous papers (e.g.
@@
 Ruths (2014, Science) and Liu (2011, Nature) are doing a better job at explaining maximum matching, driver nodes and the overall challenge of controllability.
-Specific comments
-1)      Consider being more specific in your abstract.
-2)      L74 “we _expand_ previous theory of the control of complex systems to an ecological context”. Do you mean apply? Please clarify your contribution without ambiguity.
-3)      Section Manageability (L94).
-a.      Please first define manageability before maximum matching.
-b.      The maximum matching paragraph is difficult to understand. Reword.
-4)      Section Relative importance (L121).
-a.
+
+- Consider being more specific in your abstract.
+
+- L74 “we expand previous theory of the control of complex systems to an ecological context”. Do you mean apply? Please clarify your contribution without ambiguity.
+
+    *Acepted; changed.
+The sentence now reads "To bridge this gap, we propose methods to apply previous theory on the control of complex systems into an ecological context and implement them in empirical data"*
+
+- Section Manageability (L94). Please first define manageability before maximum matching. Also, the maximum matching paragraph is difficult to understand. Reword.
+
+- Section Relative importance (L121).
 It seems that the abstract refers to this section as being a novel way to identify communities’ driver species.
@@
 It is also unclear from the Methods section.
-5)      Discussion:
-a.
+
+- Discussion.
 McDonaldMadden et al (2016) actually show that network metrics are not useful to prioritise the management of foodweb, i.e.
@@
 Please edit current text and analyse differences with your work.
-b.      Please provide some insight into how your method/analysis/results would differ for non- pollinator invaded networks.
-c.      Please discuss the caveats of your approach. I suggest moving some of the statistical analyses in sup info if word limit is an issue.
 
-6)      The maximum matching algorithm is computationally expensive as noted by the authors.
+- Discussion. Please provide some insight into how your method/analysis/results would differ for non- pollinator invaded networks.
+
+- Discussion. Please discuss the caveats of your approach. I suggest moving some of the statistical analyses in sup info if word limit is an issue.
+
+- The maximum matching algorithm is computationally expensive as noted by the authors.
 In Ruths & Ruths (2014) the authors come with an interesting alternative to calculate the minimum number of independent controls (driver species) using only the number of source nodes, external dilation points and internal dilation points; and a heuristic using source and sink nodes.
@@
 Would it bring complementary information?
-7)      A few typos in main text and sup info.
-8)      Is there a compelling reason to change controllability to “manageability”? Walters did the same thing with “adaptive management” in lieu of “adaptive control”.
+
+- A few typos in main text and sup info.
+
+- Is there a compelling reason to change controllability to “manageability”?
+Walters did the same thing with “adaptive management” in lieu of “adaptive control”.
 30 years later, no one remembers where “adaptive management” originally came from and it has become a keyword in ecology.
@@
 
-Referee: 3
+## Referee 3
 
-Comments for the Authors
 In this work Cagua et al apply tools rooted in control theory to ecological networks and discuss how this approach could be used for management of natural systems, with emphasis on the effects of invasive species.
@@
 *Thanks for the encouraging feedback*
+
+## References

### 2016-12-05 paper/manuscript.Rmd
some modifications to the methods

@@
 
-It is generally unknown how the disruptions caused by perturbations such as biotic invasions, affect our ability to manage ecological communities. 
-Here, we expand current theory on the controllability of complex systems to quantitatively assess the theoretical (relative) manageability of ten pairs of uninvaded and invaded plant-pollinator communities.
-Intriguingly, we found that invaded pollination networks might be more resilient than their uninvaded counterparts as they showed substantially lower levels of manageability.
-We also developed theory to help identify each community's driver species—those most important to manage because of their disproportionate potential to affect the abundances of all other species. 
-Remarkably, invasive plants were found to be driver species in every community in which they were found; their dominant position was generally underpinned by high asymmetry in the dependence of their interaction partners.
+It is generally unknown how the disruptions caused by perturbations like biotic invasions affect our ability to manage ecological communities. 
+Here, we expand theory on the controllability of complex systems to assess the theoretical manageability of ten pairs of uninvaded and invaded plant-pollinator communities. 
+We found that invaded pollination networks appear more resilient than their uninvaded counterparts as they showed substantially lower manageability. 
+We also introduce a novel way to identify communities’ driver species—those most important to manage because of their disproportionate potential to affect the abundances of all other species. 
+Remarkably, we observed that invasive plants were driver species in every community in which they were found, and their dominant position was underpinned by the high asymmetry in the dependence of their interaction partners.
 Our results provide a theoretical explanation for the known challenges associated with the  restoration of invaded communities, and also provide insight into the design of informed management interventions.
 
-*Shorter version*: 
-It is generally unknown how the disruptions caused by perturbations like biotic invasions, affect our ability to manage ecological communities. 
-Here, we expand current theory on the controllability of complex systems to assess the theoretical manageability of ten pairs of uninvaded and invaded plant-pollinator communities.
-We found that invaded pollination networks might be more resilient than their uninvaded counterparts as they showed substantially lower manageability.
-We also identify each community's driver species—those most important to manage because of their disproportionate potential to affect the abundances of all other species. 
-Remarkably, invasive plants were found to be driver species in every community in which they were found; their dominant position was generally underpinned by high asymmetry in the dependence of their interaction partners.
-Our results provide a theoretical explanation for the known challenges associated with the restoration of invaded communities, and also provide insight into the design of informed management interventions.
-
 # Introduction
 
-Complex systems are characterised by non-linear relationships in which the whole is greater than the sum of its parts [@Jorgensen1998; @Levin1999; @Montoya2006].
+Complex systems are characterised by relationships in which the whole is often greater than the sum of its parts [@Jorgensen1998; @Levin1999; @Montoya2006].
 Within community ecology, a complex systems approach has led to the development of a variety of analytical and simulation tools with which to understand, for example, the role of species when embedded in an intricate network of interactions [@Pascual2005; @Bascompte2009; @Stouffer2012].
@@
 Applications of control theory to ecological networks can also take into account the extent to which changes in the abundances of one species may ripple through the community [@Cornelius2013].
-Therefore, they can provide an indication of which species are most relevant
-from a dynamic perspective, a particularly important feature given that these
-species should underpin informed attempts to both alter or maintain the ecosystem state.
-
-Despite these advances, the link between the structure of complex networks and our ability to manage and conserve them is still ambiguous [@Tylianakis2010].
+Therefore, they can provide an indication of which species are most relevant from a dynamic perspective, a particularly important feature given that these species should underpin informed attempts to both alter or maintain the ecosystem state.
+
+Despite these advances, practical challenges to the conservation of interaction networks still persist [@Tylianakis2010] and the link between the structure of complex networks and our ability to manage and conserve them is still ambiguous [@Kaiser-Bunbury2015].
 To complicate things further, biotic invasions—a major driver of global change—can induce dramatic changes on the patterns of interactions that determine the structure of ecological networks [@Baxter2004; @Tylianakis2008; @Ehrenfeld2010a].
@@
 
-To bridge this gap, we expand previous theory of the control of complex systems to an ecological context.
-We then use a set of ten pairs of uninvaded and invaded plant-pollinator communities to investigate the link between invasion, network structure and ecological management. 
-We ask two specific questions framed in the context of a plant invasion.
+To bridge this gap, we propose methods to apply previous theory on the control of complex systems into an ecological context and implement them using empirical data.
+Specifically we use a set of ten pairs of uninvaded and invaded plant-pollinator communities to investigate the link between invasion, network structure and ecological management. 
+We ask two questions framed in the context of a plant invasion.
 First, we ask whether invaded networks have lower levels of manageability than their uninvaded counterparts; that is, whether they require a greater proportion of species to be managed to achieve the same level of control.
@@
 
-## Theoretical framework
-
-### Manageability
+## Methods
+
+### Theoretical framework
+
+Dynamical contstraints
+
+#### Controlability
+
+The structural controllability of a complex system can be approximated by the proportion of nodes to which we would need to apply external control input signals in order to gain full control of the state of all nodes in the network.
+This finding is based on the premise that a complex network behaves like a dynamical system in which the state of a given node can be potentially modified by altering state of any of the nodes pointing to it.
+In an ecological community species populations can often be viewed as a function of the populations of the species they interact with.
+This ability to treat communities as a network of coupled dynamic entities enables the application of control theory in ecological settings, hence provide an explicit link between network structure and managament applications.
+
+Indeed, in an ecological context, external control input signals that modify the state of a node (a species' population) could be refered as management interventions.
+Building on this analogy, systems that require a large number of external inputs are more difficult or costly to control. 
+Therefore, the manageability of a community is inversely related to its controllability *c*.
+This is given by $$c = \frac{n_d}{s},$$ where *c* ranges between zero and one, *n~d~* is the minimum number of species to which management interventions are needed to gain full control, and *s* is the total number of species in the community.
+Although the
+
+systems, and hence where s
+Ecological communities are a prime candidate
+In an ecological context
 
@@
 Unmatched nodes, on the other hand, have no superior in the network and must be directly controlled by external inputs [@Liu2011].
+
 In an ecological context, these external inputs are what could be referred to as management interventions. 
@@
 
-### Relative importance
+#### Relative importance
 
@@
 
-## Methods
+### Empirical data
 
@@
 
-### Community manageability
+#### Community manageability
 
@@
 
-#### Weighting & directing links
+##### Weighting & directing links
 
@@
 
-#### Statistical analysis
+##### Statistical analysis
 
@@
 
-### Relative importance of species
+#### Relative importance of species
 
@@
       })
-  })
+  }, .progress = "text")
 

### 2016-12-09 paper/EL-reviewer-comments-1.Rmd
Theoretical framework

@@
 date: "21 November 2016"
+header-includes:
+   - \usepackage{setspace}
 output: pdf_document
+classoption: a4paper
 bibliography: references.bib
 ---
+
+\onehalfspacing
 
@@
 We have endeavored to incorporate all reviewers' feedback into the manuscript and we feel the attached draft constitutes an important improvement from the previous version.
-We were impressed by the quality of the reviews; they all were particularly thoughtful, clear, and constructive.
+We were impressed by the quality of the reviews; they all were thoughtful, clear, and constructive.
 It is evident that all three anonymous reviewers have given a fair and careful consideration to our manuscript.
-Therefore, we would like to especially thank them---not with the customary platitude usual in response letters, but with sincere gratitude for their valuable feedback.
+We would like to thank them for the truly valuable feedback.
 
@@
 Specifically with regards to the terminology, the underlying  structural control, and the lack of detail in the presentation of the empirical networks.
-In the current version, we have thoroughly addressed all these concerns and improved the robustness of the analyisis and the clarity of the concepts.
+In the current version, we have thoroughly addressed all these concerns and improved both the robustness of the analyisis and the clarity of the concepts.
 Detailed responses to each comment, one by one, are provided below.
@@
 
-    *Accepted; changed.
-We revised the text to better reflect the contribution of @Tylianakis2010 at the same time we added a reference to a more recent paper by @Kaiser-Bunbury2015 who explicitly deals with oportunities, limitations and implications of applying network metrics in conservation science.*
+    *We revised the text to better reflect the contribution of @Tylianakis2010 at the same time we added a reference to a more recent paper by @Kaiser-Bunbury2015 who explicitly deals with oportunities, limitations and implications of applying network metrics in conservation science.*
 
@@
 It therefore seems to me that this statement should be preceded by a discussion of those details (indeed, the authors argue that this is necessary in the Introduction, on lines 48-49).
-
-- Furthermore, the authors need to discuss the appropriateness of this framework to ecological systems.
+Furthermore, the authors need to discuss the appropriateness of this framework to ecological systems.
 The input control signals that drive even relatively simple networks to specified states can be very sensitive to initial conditions and complicated (indeed, they usually aren't calculated at all).
 How can a control scheme be implemented even in principle if nodes represent species populations and a control signal calls for a fractional change in a node state variable over the course of minutes?
-Furthermore, how do the authors interpret the methods by which cycles are controlled in linear control theory (see e.g.
+
+    *Thanks to this comment and those from other reviewers have helped us identify some shortcomming on the way we were introducing the control framework in the paper.
+We have largely rewritten the 'Theoretical framework' section and we start by offering a brief overview of control theory which emphasize on a dynamical perspective to complex networks (Line XXX).
+We then follow with a paragraph devoted to how structural controlability is unable to provide information about the particulars of the control signal and the feasibility of its application (Line XXX).
+Without disregard the usefulness of the proposed approach, we also mention in this paragraph, and later on the discussion (Line XXX), how recently developed numerical methods [@Cornelius2013] might offer exiting results in this regard.*
+
+- Furthermore, how do the authors interpret the methods by which cycles are controlled in linear control theory (see e.g.
 doi 10.1126/science.1242063 and its supplementary material) in the context of ecological management?
@@
 
-    * Acepted; changed.*
+    *Thanks for pointing this out.
+In fact we thoroughly implememnted the approach of [@Ruths2014] at initial stages of the project.
+However we found that the profile of the network depends to an extreme degree on the chosen link directionality and very little on the particulars of a given network.
+Because of that reason we decided to exclude this approach altogether from the final draft.
+Nevertheless, due to this comment and one of Referee 2 we included this treatment in the Supplementary Materials Section XX and reference it briefly in the manuscript (Line XXX).
+In SM SectionXX we explain that because we focus on bipartite networks, cycles only appear, and in fact dominate, when we consider the case of bidirectional links.
+We are particularly grateful for the reference to @Motter2015.
+We were unaware of this paper and has been extremely useful to contextualise our work in the broader control theory.*
 
@@
 
+    *Indeed most of the literature treats the problem of controlability on unweighted networks.
+It has been shown, however, at least in pollination networks like the ones used in our paper, that the interaction weights carry important information about the patterns and processes in the community.
+In the paper we use the visitation weights directly or indirectly in two different aspects.
+First, we use them to determine the direction of control (via the dependence asymetry).
+Second, which directly adresses the reviewer's comment, we use it to give priority to matchings that have the largest weight, which potentially also have the largest impact on the network state for a given management intervention.
+Because the weights determine to some extent the dynamical relationships between species, our approach attempt to incorporate more realism to the structural controllability approach.
+We acknoweledge our presentation was confusing, especially for readers familiar wit the control literature, and therefore have added a whole paragraph in the method describing our rationale (Lines XXX)*
+
 - When defining n_d on line 119, it is more accurate to say that it is the "minimum number" of species needed to gain full control.
+
+    *We have rewritten that section and the equivalent sentence now reads "It has been shown that a particular network that can be expressed as a state space system of the form $\dot{x} = Ax + Bu(t)$ is controllable if there exists a minimum number of nodes in the network (N~D~ > 0) to which is possible to aply an external control signal that propagates trough the network to in turn drive the state of every other node in the network to a particular configuration [@Kalman1963; @Liu2011]."*
 
@@
 
-Second, a node with no outgoing edges will clearly never be a superior node and will therefore not be a driver node.
+    *We are sorry for the impresicion.
+It should have been "all possible maximum cardinality matchings".
+In any case, because of the suggestion about the driver species concept we have decided to remove this sentence.
+We also reworded the text in Lines XXX to clarify why our approach to identify species importance is not exclsively centered on maximum matchings.*
+
+- Second, a node with no outgoing edges will clearly never be a superior node and will therefore not be a driver node.
 I assume that this never happens in the mutualistic networks under consideration, but this probably bears mentioning so as to help develop the reader's intuition for this assessment.
@@
 
-Finally, the term "driver species" (or more generically, "driver node") has a specific meaning in the control literature (doi 10.1038/nature10011): what the authors here denote with n_d on line 118.
+    *Thanks to this suggestion and those of other reviewers, we have made important changes to Figure 1.
+On it we include a better ilustration of our methodology for a simple network while paying special effort to bring clarity to the different node categories as superior, matched and unmatched nodes.
+TO DO*
+
+- Finally, the term "driver species" (or more generically, "driver node") has a specific meaning in the control literature (doi 10.1038/nature10011): what the authors here denote with n_d on line 118.
 To avoid confusion with those familiar with the control theory literature (and those readers who are inspired by this ms to delve into it), I suggest a change of terminology.
@@
 
+    *Overall our choice of terminology was poor.
+We have eliminated the term "driver species" from the manuscript and now just mention, in the referee's words, how the frequency with which species exist on key paths trough the network provides indication of their relative importance.*
+
 - The approach described in lines 145-152 would be clearer if the authors included a figure demonstrating each step for a simple network.
+
+    *Thanks for pointing this out.
+As suggested, we have included a figure that help explains our method to compute all possible maximum cardinality matchings.
+However because the methodology itself is not one of our main contributions and because of space limitations we have included that figure in the Supplementary Material.
+TO DO.*
 
@@
 
-    *Acepted; changed.
-The sentence now reads "To bridge this gap, we propose methods to apply previous theory on the control of complex systems into an ecological context and implement them in empirical data"*
+    *The sentence now reads "To bridge this gap, we propose methods to apply previous theory on the control of complex systems into an ecological context and implement them in empirical data"*
 
 - Section Manageability (L94). Please first define manageability before maximum matching. Also, the maximum matching paragraph is difficult to understand. Reword.
+
+    *We have pretty much rewritten the "Theoretical framework" section following the reviewers advise.
+We start with a brief introduction to structural controllability (Lines XXX), follow with a definition of manageability (Lines XXX) and finalise with details and computational considerations for its calculation.*
 
@@
 It is also unclear from the Methods section.
+
+     *Thanks for the observation.
+We have reworded large segments of this section.
+Specifically now explain how the approach builds on existing structural controllability theory by incorporating the weight of the interactions.
+Moreover, now we included more details about the rationale behind our approach.
+By being more specific we hope the reader to be able to identify the theretic and computational novelties of our approach with respect to existing "ranking" methods.
+We also strive to further clarify the novelty in the discussion section (Lines XXX).
+TO DO*
 
@@
 
-Only one type of interaction is being considered here when species are involved in multiple types of interactions.
+ - Only one type of interaction is being considered here when species are involved in multiple types of interactions.
 An assumption that is not explicit in the text is that all the factors controlling population densities are the interactions between plants and pollinators.
@@
 First, the authors should discuss in detail these assumptions and their limitations.
+
+    *PARTIAL ANSWER: We have included some comments about the general limitations of the structural controlability approach in the "Theoretical Framework" section (Lines XXX). Furthermore*
+
 Second, It would be helpful if the authors could test the robustness of their results to sampling.
@@
 
-Ln 95-98.
+- Ln 95-98.
 It is very hard to keep track of all those definitions - matching, matched nodes, matched links, matching size, matching weight, maximum matching.
@@
 
-Ln 99. Indicate how the matching is represented in the figure. e.g.,  "(dark grey links in Figure 1a)"
+    *Thanks.
+We have rewritten a large section of the methods and tried to be more clear when defining new terms by providing some examples and using a more logical sequence to go from one concept to the next (Lines XXX).
+We have also included a short glossary with the most important definitions.
+TO DO*
 
-Figure 1.Indicate the driver nodes in these networks
+- Ln 99. Indicate how the matching is represented in the figure. e.g.,  "(dark grey links in Figure 1a)". Figure 1.Indicate the driver nodes in these networks
 
-Ln 128. Be clear about the meaning of resources here. I understand you mean financial resources not  resources in the ecological sense.
+    *We have redesigned Figure 1 and now we indicate more clearly how the matching works and specify which are the superior, matched, and unmatched nodes.
+Also because we also illustrate the methods to obtain the relative importance, it is easier to highlight which are the key species in a simple network.*
+
+- Ln 128. Be clear about the meaning of resources here. I understand you mean financial resources not  resources in the ecological sense.
+
+    *Indeed.
+We apologise for the imprecision.
+We indeed mean financial resources.
+We have modified the sentence to improve clarity and it now reads "Ecologically, these distinctions are relevant because management and conservation resources are limited and therefore ecological interventions should ideally be focused on species that might provide the largest impact."*
 

### 2016-12-09 paper/draft_2.Rmd
Theoretical framework

---
title: "Biotic invasions reduce the manageability of pollination networks"
csl: ecology-letters.csl
header-includes:
   - \usepackage{setspace}
output: pdf_document
geometry: outer=6cm, top=2cm, bottom=2cm
classoption: twoside, a4paper
bibliography: references.bib
---

\doublespacing

# Methods

## Theoretical framework

At the core of control theory of complex networks is the idea that the state of a node depends on the state of the nodes it interacts with. 
The particular shape of this dependency being determined both by the dynamical relationship among interacting nodes as well as the structure of the links in the network. 
It has been shown that a particular network that can be expressed as a state space system of the form $\dot{x} = Ax + Bu(t)$ is controllable if there exists a minimum number of nodes in the network (*N~D~ > 0*) to which is possible to apply an external control signal that propagates trough the network to in turn drive the state of every other node in the network to a particular configuration [@Kalman1963; @Liu2011].
Conveniently the information necessary to determine whether a network is controllable and the number of driver nodes *N~D~*, is fully contained in the network structure.

Strictly speaking, although the network structure tells us whether the system is controllable or not, it provides no information about the characteristics of the control signal or the feasibility of its implementation [@Motter2015].
Numerical algorithms to identify the control signal already exist [@Cornelius2013] however, they have the important limitation of requiring full knowledge of the dynamical relationships among nodes; an approach not yet possible for empirical ecological applications.
Instead, structural controllability, even when using only information regarding the network architecture, can provide a powerful indication of our ability to control it.

### Manageability

The number of driver nodes *N~D~* not only determines whether a network is controllable but can also, from a structural perspective, provides an indication of how difficult its control might be.
This is so because intuitively systems that require a large number of external inputs are more difficult or costly to control.
In an ecological context, external signals that modify the state of a node (a species' population) can be viewed as management interventions.
Building on this analogy, the manageability of an ecological community can be understood in the context of how difficult is to modify the abundances of species in the community using external interventions—a common theme in ecosystem management, conservation, and restoration.
We, therefore, use the density of driver nodes $n_D = \frac{N_D}{S},$ as an index of the manageability of an ecological community, where *S* is the total number of species.

It has been recently shown that the problem of calculating *N~D~* is equivalent to finding a maximum matching in the network [@Liu2011].
In a directed network, a matching is a subset of *links* in which no two of them share a common starting or ending node (Figure 1a).
A given matching has *maximal cardinality* if the number of matched links (which is also known as the matching size) is the largest possible.
A maximal cardinality matching is then called *maximum matching* if the sum of the weights of the matched links (also known as matching weight) is the largest possible [@West2001].
It follows that for binary link (unweighted) networks all maximal cardinality matchings are also maximum matchings.

Once we have a matching, with the subset of links that constitute it, we can also characterise the nodes in the network according to it.
A node is said to be *matched* if it is at the end of a matched link and *unmatched* otherwise. 
Finally, a node is said to be *superior* if it is at the start of a matched link (note that all unmatched nodes are also superior but not vice versa).
These node categories help us linking a maximum matching back to the concept of network controllability in an intuitive way.
Each matched node can be controlled by the node that is pointing to it—its superior.
Unmatched nodes, on the other hand, are the driver nodes because they have no superior in the network and must be directly controlled by an external input [@Liu2011].

**Computational considerations.** Finding find the maximum matchings, especially in large, directed, and highly connected networks can be an expensive operation.
Although other less computationally expensive approaches to characterise the control profile of complex networks that are based on heuristics do exist [@Ruths2014], we found them to be extremely sensitive to assumptions regarding the direction of control (Supplementary Materials Section 2).
Our strategy, instead, is to adopt an alternative bipartite representation of the directed network in which the two levels indicate the outgoing and incoming links to each node (Supplementary Section 2). 
We then used an algorithm implemented in *igraph* to find the maximum bipartite matching in this alternative representation [@Csardi2006a].

### Relative importance

While calculating *n~D~* provides an indication of the manageability of an ecological community, it does provide sufficient information about the identity of the species that compose this set. 
This difference is rather important since maximum matchings are often not unique in a given network and different sets of species of size *N~D~* could potentially be used to control the network [@Liu2011]. 
That is, species can be further characterised in terms of the frequency with which they  exist on key paths leading through the network, which provides an indication of their relative importance in driving the state of the community. 
Ecologically, these distinctions are relevant because management and conservation resources are limited and therefore ecological interventions should ideally be focused on species that might provide the largest impact.

We focus on superior nodes and not exclusively on driver/unmatched nodes, as is customary in the control literature, because realistically, from an ecological perspective, we are not yet able to aim for full control of the abundances of all species in the community.
Superior nodes, which include driver nodes, are important for the controllability of the network not only because they might require external control signal but essentially because they are part of the chain that transmits the control signal to other species.

Traditionally, structural controllability assumes unweighted links—they exist or not and hence results are entirely based on topology.
However, it has been shown that using weighted links can reveal important ecological patterns and processes that might be undetectable in unweighted networks [@Scotti2007; @Tylianakis2007; @Vazquez2007; @Kaiser-Bunbury2010a].
Here we use the quantitative version of the maximum matching algorithm, hence giving priority to the species that participate in the pathways that potentially have the largest impact on the community.
By incorporating the role of the dynamical relationships between species without being overly dependent on the particular choices about how dynamics are modelled, we address to some extent one of the limitations of structural controllability.

As previously described, a maximum matching in a weighted network is one whose links have the largest possible total weight among all possible matchings. 
One way to calculate the species importance would be to consider only maximum matchings. 
However, empirical interaction strengths are to some extent stochastic and depend on proximate factors such as sampling method and intensity [@Gibson2011].
This implies that there will often be multiple maximal cardinality matchings but that are maximum matchings because of their total weight, although comparatively large, is not maximal. 
As using only maximum matchings in empirical networks might be therefore too restrictive, we relax the matching weight requirement and compute all possible matchings in the network that have the same maximal size while allowing for some tolerance regarding the weight.

**Computational considerations.** One alternative to computing all the maximum cardinality matchings is to first generate the network's line graph—another representation in which nodes are the links of the original network and links represent common ending points [@West2001]. 
Then calculate the complement of this line graph, which generates a graph in which nodes are connected if and only if they are not connected in the line graph. 
Finally, all possible matchings of maximal size can be found by enumerating every clique (subgraphs in which all nodes are fully connected to each other) of maximum size in this complement graph [@Csardi2006a; @Gutin2013].

# References

### 2016-12-13 paper/draft_2.Rmd
Add daniel's changes and Figure 1

@@
    - \usepackage{setspace}
-output: pdf_document
-geometry: outer=6cm, top=2cm, bottom=2cm
+output: 
+  pdf_document:
+    fig_crop: false
+# geometry: outer=6cm, top=2cm, bottom=2cm
 classoption: twoside, a4paper
@@
 
+```{r libraries, echo = F, include = F}
+library(igraph)
+library(magrittr)
+library(dplyr)
+library(latex2exp)
+
+"../code/functions" %>% 
+	list.files(full.names = T) %>%
+	plyr::l_ply(source)
+
+```
+
+```{r example networks, include = F, message = F, warning = F, }
+
+sp_names_fancy <- c(TeX("$p_1$"), TeX("$p_2$"), TeX("$p_3$"), TeX("$a_1$"), TeX("$a_2$"))
+sp_names_fancy_b <- c(TeX("$\\mathbf{p_1}$"), TeX("$\\mathbf{p_2}$"), TeX("$\\mathbf{p_3}$"), TeX("$\\mathbf{a_1}$"), TeX("$\\mathbf{a_2}$"))
+
+sp_names <- c("p1", "p2", "p3", "a1", "a2")
+
+adj_matrix <- c(0,0,0,1,0,
+								0,0,0,2,5,
+								0,0,0,0,0,
+								0,0,1,0,0,
+								0,0,1,0,0) %>%
+	matrix(nrow = 5, byrow = T)
+
+net <- adj_matrix %>% 
+	graph_from_adjacency_matrix(mode = "undirected", weighted = TRUE) 
+igraph::V(net)$type <- c(F, F, F, T, T)
+igraph::V(net)$name <- sp_names
+
+base_net <- net
+bi_net <- net %>%
+	keep_largest_component() %>%
+	bipartite_digraph(type = "z-bi", weight.type = "assymetry") 
+as_net <- net %>%
+	keep_largest_component() %>%
+	bipartite_digraph(type = "weight", weight.type = "asymmetry")
+
+fam <- "Helvetica"
+# layout is based on the bidirectional network
+set.seed(1)
+
+lay <- bi_net %>%
+	layout_nicely()
+v_c <- "white"
+l_c <- "black"
+l_s <- 0.9
+ma <- c(0,0,0,0)
+label_pos_x <- -1
+label_pos_y <- 1
+
+pal <- RColorBrewer::brewer.pal(5, "PuOr")
+```
+
+# Glossary
+
+Driver node
+  ~
+
+Matched/unmatched link
+  ~
+
+Matched/unmatched node
+  ~
+
+Matching
+  ~
+
+Matching size
+  ~
+
+Matching weight
+  ~
+
+Maximal cardinality matching
+  ~
+
+Maximum matching
+  ~
+
+Superior node
+  ~
+
 # Methods
@@
 
-At the core of control theory of complex networks is the idea that the state of a node depends on the state of the nodes it interacts with. 
-The particular shape of this dependency being determined both by the dynamical relationship among interacting nodes as well as the structure of the links in the network. 
-It has been shown that a particular network that can be expressed as a state space system of the form $\dot{x} = Ax + Bu(t)$ is controllable if there exists a minimum number of nodes in the network (*N~D~ > 0*) to which is possible to apply an external control signal that propagates trough the network to in turn drive the state of every other node in the network to a particular configuration [@Kalman1963; @Liu2011].
-Conveniently the information necessary to determine whether a network is controllable and the number of driver nodes *N~D~*, is fully contained in the network structure.
+At the core of control theory of complex networks is the idea that the state of a node depends on the state of the nodes it interacts with, and particular form of this dependency is determined both by the dynamic relationship among interacting nodes as well as the structure of the links in the network.
+A complex network can usually be simplified as a linear system of the form $\dot{x} = Ax + Bu(t)$, where the change over time of its state ($\dot{x}$) depends on its current state *x*, an external time-varying input *u(t)*, and the matrices *A* and *B*, which encapsulate information about the network structure and how the network responds to the external input, respectively.
+Previous research has shown that such a system is controllable if there exists a minimum number of nodes in the network ($D \geq 0$) to which is possible to apply an external control signal that propagates trough the network to in turn drive the state of every other node in the network to a particular configuration [@Kalman1963; @Liu2011].
+Conveniently, the information necessary to determine whether a network is controllable, and the number of driver nodes *D*, is fully contained in the network structure [@Liu2011; @Motter2015]
 
-Strictly speaking, although the network structure tells us whether the system is controllable or not, it provides no information about the characteristics of the control signal or the feasibility of its implementation [@Motter2015].
-Numerical algorithms to identify the control signal already exist [@Cornelius2013] however, they have the important limitation of requiring full knowledge of the dynamical relationships among nodes; an approach not yet possible for empirical ecological applications.
-Instead, structural controllability, even when using only information regarding the network architecture, can provide a powerful indication of our ability to control it.
+Strictly speaking, the network structure tells us whether a linear approximation of the system is controllable or not, but it provides limited information about the characteristics of the control signal or the feasibility of its implementation [@Motter2015].
+Despite this limitation, structural controllability provides important information of our ability to control a system without requiring full and precise knowledge of the dynamical relationships among nodes.
+This means that structural controlability can be applied on a wide range of readily available network representations of ecological communities. 
+Moreover, when quantitative data about species iteractions is available, we show how some of the limitations of structural controllability can be overcome by incorporating the role of dynamical relationships without being overly dependent on the particular choices about how dynamics are modelled.
 
@@
 
-The number of driver nodes *N~D~* not only determines whether a network is controllable but can also, from a structural perspective, provides an indication of how difficult its control might be.
-This is so because intuitively systems that require a large number of external inputs are more difficult or costly to control.
-In an ecological context, external signals that modify the state of a node (a species' population) can be viewed as management interventions.
-Building on this analogy, the manageability of an ecological community can be understood in the context of how difficult is to modify the abundances of species in the community using external interventions—a common theme in ecosystem management, conservation, and restoration.
-We, therefore, use the density of driver nodes $n_D = \frac{N_D}{S},$ as an index of the manageability of an ecological community, where *S* is the total number of species.
+The number of driver nodes *D* not only determines whether a network is controllable, but can also provide a structural indication of how difficult its control might be.
+This is because systems that require a large number of external input signals are intuitively more difficult or costly to control.
+In an ecological context, external signals that modify the state of a node (this is a species' population) can be thought of as management interventions.
+We, therefore, use the density of driver nodes $n_D = \frac{D}{S},$ as an index of the manageability of an ecological community, where *S* is the total number of species.
+From this perspective, the manageability of an ecological community can be understood in the context of how difficult is to modify the abundances of species in the community using external interventions—a common theme in ecosystem management, conservation, and restoration.
 
-It has been recently shown that the problem of calculating *N~D~* is equivalent to finding a maximum matching in the network [@Liu2011].
-In a directed network, a matching is a subset of *links* in which no two of them share a common starting or ending node (Figure 1a).
-A given matching has *maximal cardinality* if the number of matched links (which is also known as the matching size) is the largest possible.
-A maximal cardinality matching is then called *maximum matching* if the sum of the weights of the matched links (also known as matching weight) is the largest possible [@West2001].
-It follows that for binary link (unweighted) networks all maximal cardinality matchings are also maximum matchings.
+It has been recently shown that calculating *D* is equivalent to finding a maximum matching in the network [@Liu2011].
+In a directed network, a matching is a subset of links in which no two of them share a common starting or ending node (Figure 1).
+A given matching has *maximal cardinality* if the number of matched links (also refered to as the *matching size*) is the largest possible.
+A maximal cardinality matching is then called a *maximum matching* if the sum of the weights of the matched links (also refered to as matching weight) is again the largest possible [@West2001].
+Note that this implies that for unweighted binary networks all maximal cardinality matchings are also maximum matchings.
 
-Once we have a matching, with the subset of links that constitute it, we can also characterise the nodes in the network according to it.
+Once we have the subset of links that constitute a matching, we can also classify the nodes in the network (Figure 1).
 A node is said to be *matched* if it is at the end of a matched link and *unmatched* otherwise. 
-Finally, a node is said to be *superior* if it is at the start of a matched link (note that all unmatched nodes are also superior but not vice versa).
-These node categories help us linking a maximum matching back to the concept of network controllability in an intuitive way.
+A node is also said to be *superior* if it is at the start of a matched link (note that all unmatched nodes are also superior but not vice versa).
+Notably, these node categories help us to intuitively link a maximum matching back to the concept of network controllability as follows.
 Each matched node can be controlled by the node that is pointing to it—its superior.
-Unmatched nodes, on the other hand, are the driver nodes because they have no superior in the network and must be directly controlled by an external input [@Liu2011].
+Unmatched nodes, on the other hand, are the driver nodes *D* because they have no superior in the network and must be directly controlled by an external input [@Liu2011].
 
-**Computational considerations.** Finding find the maximum matchings, especially in large, directed, and highly connected networks can be an expensive operation.
-Although other less computationally expensive approaches to characterise the control profile of complex networks that are based on heuristics do exist [@Ruths2014], we found them to be extremely sensitive to assumptions regarding the direction of control (Supplementary Materials Section 2).
-Our strategy, instead, is to adopt an alternative bipartite representation of the directed network in which the two levels indicate the outgoing and incoming links to each node (Supplementary Section 2).
-We then used an algorithm implemented in *igraph* to find the maximum bipartite matching in this alternative representation [@Csardi2006a].
+```{r figure 1, echo = F, message = F, warning = F, fig.width = 6.2, fig.height = 1.8, results= "hide", fig.cap = "**Matchings of a simple network**.
+We start with a network in which the direction of the links indicate the direction of control (a); that is, a link from *a~1~* to *p~1~*, for instance, indicates that the state of *p~1~* (density/abundances in an ecological context) is influenced by the state of *a~1~*.
+This network has two maximal cardinality matchings (b, c); this is, two configurations in which it would be possible to excert full control of the network.
+The three matched links (blue arrows) represent the possible control paths trough the network and provide indication of the matched nodes (also in blue), which are controlled by superior nodes within the network (bold node labels).
+Unmatched nodes (in orange) are also called driver nodes because full network control requires external signals to be applied on them, and therefore, the manageability of the network can be infered from the density of unmatched nodes *n~D~ = D/S = 2/5*.
+Out of the two maximal cardinality matchings (b, c) only one of them has maximum weight and therefore is a maximum matching (c); note that if the network were unweighted both maximal cardinality matchings would also be maximum matchings.
+Further examples can be found in the Supplemental Material SXX."}
+layout(matrix(c(1,2,3,4, 4, 4), 2, 3, byrow = TRUE),
+  	heights=c(8,1))
+par( mar=c(0,0,0,0))
+
+as_net %>% 
+	plot(layout = lay, 
+			 vertex.color = v_c, 
+			 vertex.size = 30,
+			 vertex.label = sp_names_fancy,
+			 vertex.label.family = fam,
+			 vertex.label.color = l_c,
+			 edge.label = round(E(.)$weight,1), 
+			 edge.label.family = fam,
+			 edge.label.color = l_c,
+			 edge.label.cex = l_s,
+			 edge.curved = F,
+			 edge.arrow.size = 0.5,
+			 margin = ma)
+
+text(label_pos_x, label_pos_y, "a)", adj = c(0,0))
+
+as_mat <- as_net %>%
+	digraph_bipartite() %>% 
+	max_bipartite_match()
+
+as_all_mat <- as_net %>%
+	digraph_bipartite() %>%
+	igraph::make_line_graph() %>%
+	igraph::complementer() %>% 
+	igraph::max_cliques(min = as_mat$matching_size) %>%
+	rev()
+
+text_pos_x <- 0.5
+text_pos_y <- -0.7
+
+base_as_net <- as_net
+E(as_net)$weight <- round(E(as_net)$weight, 1)
+
+1:length(as_all_mat) %>%
+	plyr::l_ply(function(x){
+
+		E(as_net)$matched <- 2
+		E(as_net)$matched[as_all_mat[[x]]] <- 4
+
+		igraph::V(as_net)$matched <- 2
+		igraph::V(as_net)$matched[igraph::V(as_net)$name %in%
+																ends(as_net, as_all_mat[[x]])[, 2]] <- 4
+
+		igraph::V(as_net)$superior <- 1
+		igraph::V(as_net)$superior[igraph::V(as_net)$name %in%
+																ends(as_net, as_all_mat[[x]])[, 1]] <- 2
+
+		names_fancy <- sp_names_fancy
+		names_fancy[igraph::V(as_net)$name %in%
+																ends(as_net, as_all_mat[[x]])[, 1]] <-
+			sp_names_fancy_b[igraph::V(as_net)$name %in%
+																ends(as_net, as_all_mat[[x]])[, 1]]
+
+		matching_weight <- sum(E(as_net)$weight[as_all_mat[[x]]])
+
+		as_net %>% 
+			plot(layout = lay, 
+					 vertex.size = 30,
+					 vertex.label = names_fancy,
+					 vertex.label.family = fam,
+					 vertex.label.color = l_c,
+					 vertex.label.cex = igraph::V(.)$superior * 0.1 + 0.9,
+					 # vertex.shape = igraph::V(.)$vertex.shape,
+					 vertex.color = pal[igraph::V(.)$matched],
+					 edge.color = pal[E(.)$matched],
+					 edge.label = NA, 
+					 edge.width = E(.)$matched/2,
+					 edge.label.family = fam,
+					 edge.label.color = igraph::E(.)$matched,
+					 edge.label.cex = l_s,
+					 edge.curved = F,
+					 edge.arrow.size = 0.5,
+					 margin = ma) %>% 
+			print()
+
+		igraph::V(as_net)$name <- sp_names
+
+		text(label_pos_x, label_pos_y, paste0(letters[1+x], ")"), adj = c(0,0))
+		text(text_pos_x, text_pos_y, cex = 0.95,
+				 paste0("D = ", length(igraph::V(as_net)) - as_mat$matching_size, "\n",
+				 			 "matching size: ", as_mat$matching_size, "\n",
+				 			 "matching weight: ", round(matching_weight, 1)))
+})
+
+as_net <- base_as_net
+
+plot.new()
+legend(0.16, 0.9, legend = c("unmatched link", "matched link"), horiz = TRUE,
+			 lty = 1, 
+			 col = pal[c(2, 4)],
+			 lwd = 2, cex = 0.9, xjust=0.5, yjust=1, bty = "n")
+
+legend(0.57, 0.9, legend = c("unmatched node", "matched node"), horiz = TRUE,
+			 pch = 21, 
+			 pt.bg = pal[c(2, 4)],
+			 pt.cex = 2,
+			 cex = 0.9, xjust=0.5, yjust=1, bty = "n")
+
+legend(1-0.16 + 0.05, 0.9, legend = expression(paste(bold("(bold label)"), " ", "superior nodes")), horiz = TRUE,
+			 cex = 0.9, xjust=0.5, yjust=1, bty = "n")
+
+matching <- net %>%
+	matched_frequency(type = "z-bi", weight.type = "asymmetry", prop = 0)
+```
 
@@
 
-While calculating *n~D~* provides an indication of the manageability of an ecological community, it does provide sufficient information about the identity of the species that compose this set. 
+While calculating *n~D~* provides an indication of the manageability of an ecological community, it does not provide information about the identity of the species that compose this set. 
 This difference is rather important since maximum matchings are often not unique in a given network and different sets of species of size *N~D~* could potentially be used to control the network [@Liu2011].
-That is, species can be further characterised in terms of the frequency with which they  exist on key paths leading through the network, which provides an indication of their relative importance in driving the state of the community.
-Ecologically, these distinctions are relevant because management and conservation resources are limited and therefore ecological interventions should ideally be focused on species that might provide the largest impact.
+Ecologically, these distinctions are also relevant because management and conservation resources are limited and therefore ecological interventions should ideally be focused on the set of species that might provide the largest impact.
+Consequently, species can be further characterised in terms of the frequency with which they exist on key paths leading through the network, which provides an indication of their relative importance in driving the state of the community.
 
-We focus on superior nodes and not exclusively on driver/unmatched nodes, as is customary in the control literature, because realistically, from an ecological perspective, we are not yet able to aim for full control of the abundances of all species in the community.
-Superior nodes, which include driver nodes, are important for the controllability of the network not only because they might require external control signal but essentially because they are part of the chain that transmits the control signal to other species.
+Specifically, in an unweighted network to approximate a species importance for network control it is possible compute all the maximum matchings and calculate the frequency at which each species is classified as a superior node.
+Because our networks are weighted, we compute all maximal cardinality matchings and not just the maximum matchings. 
+We do so because empirical interaction strengths are to some extent stochastic and depend on proximate factors such as sampling method and intensity [@Gibson2011], and therefore using only maximum matchings in empirical networks might be therefore too restrictive.
+Furthermore, we focus on superior nodes and not exclusively on driver/unmatched nodes, as is customary in the control literature, because realistically, from an ecological perspective, we are not yet able to aim for full control of the abundances of all species in the community.
+Superior nodes, of which driver nodes are a subset, are important for the controllability of the network not only because they might require an external control signal but, essentially, because they are part of the chain that transmits the control signal to other species.
 
-Traditionally, structural controllability assumes unweighted links—they exist or not and hence results are entirely based on topology.
+It is worth to note that ,traditionally, structural controllability assumes unweighted links—they exist or not—and hence results are entirely based on topology.
 However, it has been shown that using weighted links can reveal important ecological patterns and processes that might be undetectable in unweighted networks [@Scotti2007; @Tylianakis2007; @Vazquez2007; @Kaiser-Bunbury2010a].
-Here we use the quantitative version of the maximum matching algorithm, hence giving priority to the species that participate in the pathways that potentially have the largest impact on the community.
-By incorporating the role of the dynamical relationships between species without being overly dependent on the particular choices about how dynamics are modelled, we address to some extent one of the limitations of structural controllability.
-
-As previously described, a maximum matching in a weighted network is one whose links have the largest possible total weight among all possible matchings. 
-One way to calculate the species importance would be to consider only maximum matchings. 
-However, empirical interaction strengths are to some extent stochastic and depend on proximate factors such as sampling method and intensity [@Gibson2011].
-This implies that there will often be multiple maximal cardinality matchings but that are maximum matchings because of their total weight, although comparatively large, is not maximal. 
-As using only maximum matchings in empirical networks might be therefore too restrictive, we relax the matching weight requirement and compute all possible matchings in the network that have the same maximal size while allowing for some tolerance regarding the weight.
-
-**Computational considerations.** One alternative to computing all the maximum cardinality matchings is to first generate the network's line graph—another representation in which nodes are the links of the original network and links represent common ending points [@West2001].
-Then calculate the complement of this line graph, which generates a graph in which nodes are connected if and only if they are not connected in the line graph. 
-Finally, all possible matchings of maximal size can be found by enumerating every clique (subgraphs in which all nodes are fully connected to each other) of maximum size in this complement graph [@Csardi2006a; @Gutin2013].
+By using the quantitative version of the maximum matching algorithm, we give priority to the species that participate in the pathways that potentially have the largest impact on the community; effectively incorporating, at least partially, the dynamics of the system.
 

### 2016-12-14 paper/EL-reviewer-comments-1.Rmd
Full methods

@@
 
+    *We apologise for the poor choice of words.
+As the referee points out it is not an estimation but an exact calculation.
+The sentence now reads "To do so, we calculated the maximum matching of the corresponding pollination network, and determined the minimum proportion of species that need directed interventions to fully control the species abundances in the community".*
+
 - It seems to me that the number of interactions would also be an interesting factor to consider in the statistical analysis (discussed beginning on line 213).
 
+    *Thanks for the observation. We have now included the number of interactions in the network as an extra explanatory variable. TO DO*
+
 - Lines 225-228: "Previous research indicates a direct link between a network's degree distribution and the number of nodes necessary to fully control it (Liu et al.
-2011), but the strength and applicability of this relationship has not been tested for in weighted ecological networks."
-
-The authors go on to discuss null models that vary edge weights.
+2011), but the strength and applicability of this relationship has not been tested for in weighted ecological networks." The authors go on to discuss null models that vary edge weights.
 However (as mentioned in comment 4), it seems to me that the edge weight is ultimately not a factor when determining the manageability of the network, at least once it has been mapped to unidirectional and unweighted edges.
@@
 (Its role is clear in the section beginning on line 247.)
+
+    *In retrospect we realise that we did not have a clear rationale to include an randomisation of the link weights.
+As the referee points out, a change on the weights would only be reflected on a potential change on the interaction asymmetry.
+We identifyed two problems with this approach: first the changes aren't easily tractable, and second there is not a standard way to randomise weight in quantiative networks and the particular choice of the algorithm might influence the results.
+We therefore decided to remove the null model that maintained the degree of species and randomised the weight of the links as the effect of the asymetry is explicitly tackled by the second approach in which we maintain the structure but randomise the asymmetry.*
 
@@
 
+    *Thanks. We corrected it.*
+
 Ln 293: Typo: reference
+
+    *Thanks. We corrected it.*
 

### 2016-12-14 paper/draft_2.Rmd
Full methods

@@
 title: "Biotic invasions reduce the manageability of pollination networks"
+classoption: a4paper
 csl: ecology-letters.csl
+output:
+  pdf_document:
+    fig_crop: no
+  html_document: default
 header-includes:
 - \usepackage{setspace}
-output: 
-  pdf_document:
-    fig_crop: false
-# geometry: outer=6cm, top=2cm, bottom=2cm
-classoption: twoside, a4paper
+- \usepackage{float}
+documentclass: artikel1
 bibliography: references.bib
@@
 
+```{r load data, include = F}
+net <- "../data/processed/networks" %>%
+	read_networks()
+meta <- readr::read_csv("../data/ntw_info.csv") %>% dplyr::tbl_df() %>%
+	dplyr::rename(count = method)
+```
+
 ```{r example networks, include = F, message = F, warning = F, }
@@
 
-net <- adj_matrix %>% 
+example_net <- adj_matrix %>% 
 	graph_from_adjacency_matrix(mode = "undirected", weighted = TRUE) 
-igraph::V(net)$type <- c(F, F, F, T, T)
-igraph::V(net)$name <- sp_names
+igraph::V(example_net)$type <- c(F, F, F, T, T)
+igraph::V(example_net)$name <- sp_names
 
-base_net <- net
-bi_net <- net %>%
+base_net <- example_net
+bi_net <- example_net %>%
 	keep_largest_component() %>%
 	bipartite_digraph(type = "z-bi", weight.type = "assymetry") 
-as_net <- net %>%
+as_net <- example_net %>%
 	keep_largest_component() %>%
@@
 
-# Glossary
-
-Driver node
-  ~
-
-Matched/unmatched link
-  ~
-
-Matched/unmatched node
-  ~
-
-Matching
-  ~
-
-Matching size
-  ~
-
-Matching weight
-  ~
-
-Maximal cardinality matching
-  ~
-
-Maximum matching
-  ~
-
-Superior node
-  ~
-
 # Methods
@@
 
-At the core of control theory of complex networks is the idea that the state of a node depends on the state of the nodes it interacts with, and particular form of this dependency is determined both by the dynamic relationship among interacting nodes as well as the structure of the links in the network.
+At the core of control theory of complex networks is the idea that the state of a node depends on the state of the nodes it interacts with, and the particular form of this dependency is determined both by the dynamic relationship among interacting nodes as well as the structure of the links in the network.
 A complex network can usually be simplified as a linear system of the form $\dot{x} = Ax + Bu(t)$, where the change over time of its state ($\dot{x}$) depends on its current state *x*, an external time-varying input *u(t)*, and the matrices *A* and *B*, which encapsulate information about the network structure and how the network responds to the external input, respectively.
@@
 Strictly speaking, the network structure tells us whether a linear approximation of the system is controllable or not, but it provides limited information about the characteristics of the control signal or the feasibility of its implementation [@Motter2015].
-Despite this limitation, structural controllability provides important information of our ability to control a system without requiring full and precise knowledge of the dynamical relationships among nodes.
-This means that structural controlability can be applied on a wide range of readily available network representations of ecological communities. 
-Moreover, when quantitative data about species iteractions is available, we show how some of the limitations of structural controllability can be overcome by incorporating the role of dynamical relationships without being overly dependent on the particular choices about how dynamics are modelled.
+Despite this limitation, structural controllability provides important information about our ability to control a system without requiring full and precise knowledge of the dynamical relationships among nodes.
+This means that structural controllability can be applied to a wide range of readily available network representations of ecological communities. 
+Moreover, when quantitative data about species interactions is available, we show how some of the limitations of structural controllability can be overcome by incorporating the role of dynamical relationships without being overly dependent on the particular choices about how dynamics are modelled.
 
@@
 
-The number of driver nodes *D* not only determines whether a network is controllable, but can also provide a structural indication of how difficult its control might be.
+The number of driver nodes *D* not only determines whether a network is controllable but can also provide a structural indication of how difficult its control might be.
 This is because systems that require a large number of external input signals are intuitively more difficult or costly to control.
@@
 In a directed network, a matching is a subset of links in which no two of them share a common starting or ending node (Figure 1).
-A given matching has *maximal cardinality* if the number of matched links (also refered to as the *matching size*) is the largest possible.
-A maximal cardinality matching is then called a *maximum matching* if the sum of the weights of the matched links (also refered to as matching weight) is again the largest possible [@West2001].
+A given matching has *maximal cardinality* if the number of matched links (also referred to as the *matching size*) is the largest possible.
+A maximal cardinality matching is then called a *maximum matching* if the sum of the weights of the matched links (also referred to as matching weight) is again the largest possible [@West2001].
 Note that this implies that for unweighted binary networks all maximal cardinality matchings are also maximum matchings.
@@
 
-```{r figure 1, echo = F, message = F, warning = F, fig.width = 6.2, fig.height = 1.8, results= "hide", fig.cap = "**Matchings of a simple network**.
+```{r figure 1, echo = F, message = F, warning = F, fig.width = 6.2, fig.height = 1.8, results= "hide", fig.pos = "t", fig.cap = "**Matchings of a simple network**.
 We start with a network in which the direction of the links indicate the direction of control (a); that is, a link from *a~1~* to *p~1~*, for instance, indicates that the state of *p~1~* (density/abundances in an ecological context) is influenced by the state of *a~1~*.
-This network has two maximal cardinality matchings (b, c); this is, two configurations in which it would be possible to excert full control of the network.
-The three matched links (blue arrows) represent the possible control paths trough the network and provide indication of the matched nodes (also in blue), which are controlled by superior nodes within the network (bold node labels).
-Unmatched nodes (in orange) are also called driver nodes because full network control requires external signals to be applied on them, and therefore, the manageability of the network can be infered from the density of unmatched nodes *n~D~ = D/S = 2/5*.
+This network has two maximal cardinality matchings (b, c); this is, two configurations in which it would be possible to exert full control of the network.
+The three matched links (blue arrows) represent the possible control paths trough the network and provide an indication of the matched nodes (also in blue), which are controlled by superior nodes within the network (bold node labels).
+Unmatched nodes (in orange) are also called driver nodes because full network control requires external signals to be applied to them, and therefore, the manageability of the network can be inferred from the density of unmatched nodes *n~D~ = D/S = 2/5*.
 Out of the two maximal cardinality matchings (b, c) only one of them has maximum weight and therefore is a maximum matching (c); note that if the network were unweighted both maximal cardinality matchings would also be maximum matchings.
@@
 
-matching <- net %>%
-	matched_frequency(type = "z-bi", weight.type = "asymmetry", prop = 0)
 ```
@@
 While calculating *n~D~* provides an indication of the manageability of an ecological community, it does not provide information about the identity of the species that compose this set. 
-This difference is rather important since maximum matchings are often not unique in a given network and different sets of species of size *N~D~* could potentially be used to control the network [@Liu2011].
+This difference is rather important since maximum matchings are often not unique in a given network and different sets of species of size *~D~* could potentially be used to control the network [@Liu2011].
 Ecologically, these distinctions are also relevant because management and conservation resources are limited and therefore ecological interventions should ideally be focused on the set of species that might provide the largest impact.
@@
 We do so because empirical interaction strengths are to some extent stochastic and depend on proximate factors such as sampling method and intensity [@Gibson2011], and therefore using only maximum matchings in empirical networks might be therefore too restrictive.
-Furthermore, we focus on superior nodes and not exclusively on driver/unmatched nodes, as is customary in the control literature, because realistically, from an ecological perspective, we are not yet able to aim for full control of the abundances of all species in the community.
-Superior nodes, of which driver nodes are a subset, are important for the controllability of the network not only because they might require an external control signal but, essentially, because they are part of the chain that transmits the control signal to other species.
+Furthermore, we focus not only on driver/unmatched nodes, as is customary in the control literature, but also on superior nodes because realistically, from an ecological perspective, we are not yet able to aim for full control of the abundances of all species in the community.
+Superior nodes, of which driver nodes are a subset, are important for the controllability of the network not just because they might require an external control signal but, essentially, because they are part of the chain that transmits the control signal to other species.
 
-It is worth to note that ,traditionally, structural controllability assumes unweighted links—they exist or not—and hence results are entirely based on topology.
+It is worth to note that, traditionally, structural controllability assumes unweighted links—they exist or not—and hence results are entirely based on topology.
 However, it has been shown that using weighted links can reveal important ecological patterns and processes that might be undetectable in unweighted networks [@Scotti2007; @Tylianakis2007; @Vazquez2007; @Kaiser-Bunbury2010a].
@@
 
+## Empirical application
+
+```{r network summaries, include = F}
+lop <- filter(meta, study == "lopezaraiza") %>% mutate(size = n_pla + n_pol) %$% size %>% summary() 
+bar <- filter(meta, study == "bartomeus") %>% mutate(size = n_pla + n_pol) %$% size %>% summary() 
+```
+
+Now we describe the application of the previously described framework to ten paired pollination networks constructed from previously published visitation data. 
+Notably, each network pair was composed of a community invaded by a plant and a community "free" of the invasive species. 
+Four network pairs were obtained from natural or semi-natural vegetation communities in the city of Bristol, UK [@Lopezaraiza-Mikel2007]. 
+These networks are comprised by between `r lop[1]` and `r lop[6]` species (mean `r round(lop[4])`) and non-invaded plots were obtained by experimentally removing all the flowers of the invasive species *Impatients grandulifera*.
+The six remaining network pairs were obtained from lower diversity Mediterranean shrublands in Cap de Creus National Park, Spain [@Bartomeus2008].
+These networks are comprised by between `r bar[1]` and `r bar[6]` species (mean `r round(bar[4])`) and, contrastingly, uninvaded communities were obtained from plots that had not yet been colonised by either of the invasive species *Carpobrotus affine acinaciformis* or *Opuntia stricta*.
+Further details about the empirical networks can be found in the Supplementary Information XXX.
+
+The structure of all studied networks was determined using visitation frequency which has been shown to be an appropriate surrogate for interspecific effects in pollination networks [@Vazquez2005; @Bascompte2006].
+To examine whether this decision would influence our results, we also evaluated the effect of using pollinator efficiency or importance as alternative measures of species interactions in a different data set that lacked invasive species [@NeEman2010; @Ballantyne2015], and we found quantitatively similar results for all of these options (Supplementary Information XXX).
+Furthermore, because our approach depends to a large degree on the network topology, we evaluated the robustness of our results to undersampling.
+The sensitivity analysis indicated that the proposed methods can be applied even in the absence of complete sampling (Supplementary Information XXX).
+
+### Manageability
+
+```{r component_lost, echo = F, eval = T}
+a <- net %>%
+	lapply(igraph::E) %>%
+	lapply(length)
+
+b <- net %>%
+	lapply(keep_largest_component) %>%
+	lapply(igraph::E) %>%
+	lapply(length)
+
+int_lost <- ((mapply(magrittr::subtract, a, b) / unlist(a)) * 100) %>% mean() %>% round(1)
+
+a <- net %>%
+	lapply(igraph::V) %>%
+	lapply(length)
+
+b <- net %>%
+	lapply(keep_largest_component) %>%
+	lapply(igraph::V) %>%
+	lapply(length)
+
+sp_lost <- ((mapply(magrittr::subtract, a, b) / unlist(a)) * 100) %>% mean() %>% round(1)
+```
+
+Given the different networks, we began by quantifying their manageability.
+To do so, we calculated the maximum matching of the corresponding pollination network and determined the minimum proportion of species that need directed interventions to fully control the species abundances in the community.
+To simplify the analysis, we only considered the largest component in a network if it had more than one (two species are in different components if there exists no path between them and are hence independent of each other in terms of network control).
+Smaller components were present in eleven out of the twenty networks and were typically composed of just one plant and one pollinator. 
+Their removal represented an average loss of `r sp_lost`% of the species and `r int_lost`% of the interactions.
+
+#### Weighting & directing links
+
+Recall that the aforementioned maximum matching algorithm requires a directed network in which a link between species *i* and *j* pointing to species *j* indicates that the abundance of *j* can be affected by the abundance of *i*.
+This implies that we need first to identify a directionality for the links between species that is consistent with the dynamics of the community. 
+In some ecological networks, establishing the directionality is relatively straightforward, for example when links represent biomass transfer or energy flow. 
+Interspecific effects in pollination networks, however, are not strictly directed since the benefit is mutual between interacting species. 
+Nevertheless, the relative extent to which a given pair of interacting species affect each other can be quantified by the magnitude of the mutual dependence [@Bascompte2006]. 
+The dependency of plant *i* on pollinator *j*, *d~ij~*, is the proportion of the visits coming from pollinator *j* compared to all pollinator visits to plant *i*. 
+Likewise, the dependency of pollinator *j* on plant *i*, *d~ji~*, is the ratio of the visits by pollinator *j* to plant *i* and all visits of pollinator *j*.
+As the dependencies are not symmetric, its use generates a weighted bipartite network in which all interacting pairs are connected by two directed links (Figure 2b).
+
+```{r, echo = F, fig.width = 6.2, fig.height = 1.6, message = F, warning = F, fig.pos = "T", fig.cap = "Different ways to depict quantitative mutualistic networks.
+(a) Pollination networks are typically described by the number of visits between each plant and animal species.
+(b) Given visitation data, the mutual dependencies between interacting species are calculated directly based on the relative visitation frequencies.
+(c) The relative differences of dependencies—the interaction asymmetry—then provide a means to identify the dominant direction of the interspecific effects."}
+
+par(mfrow=c(1,3), mar=c(0,0,0,0))
+
+base_net %>%
+	plot(layout = lay, 
+			 vertex.color = v_c, 
+			 vertex.size = 30,
+			 vertex.label = sp_names_fancy,
+			 vertex.label.family = fam,
+			 vertex.label.color = l_c,
+			 edge.label = E(.)$weight, 
+			 edge.label.family = fam,
+			 edge.label.color = l_c,
+			 edge.label.cex = l_s,
+			 edge.curved = F,
+			 frame = F,
+			 margin = ma)
+text(label_pos_x, label_pos_y, "a)", adj = c(0,0))
+
+bi_net %>% 
+	plot(layout = lay, 
+			 vertex.color = v_c, 
+			 vertex.size = 30,
+			 vertex.label = sp_names_fancy,
+			 vertex.label.family = fam,
+			 vertex.label.color = l_c,
+			 edge.label = round(E(.)$weight,1), 
+			 edge.label.family = fam,
+			 edge.label.color = l_c,
+			 edge.label.cex = l_s,
+			 edge.curved = T,
+			 edge.arrow.size = 0.5,
+			 margin = ma)
+text(label_pos_x, label_pos_y, "b)", adj = c(0,0))
+
+as_net %>% 
+	plot(layout = lay, 
+			 vertex.color = v_c, 
+			 vertex.size = 30,
+			 vertex.label = sp_names_fancy,
+			 vertex.label.family = fam,
+			 vertex.label.color = l_c,
+			 edge.label = round(E(.)$weight,1), 
+			 edge.label.family = fam,
+			 edge.label.color = l_c,
+			 edge.label.cex = l_s,
+			 edge.curved = F,
+			 edge.arrow.size = 0.5,
+			 margin = ma)
+text(label_pos_x, label_pos_y, "c)", adj = c(0,0))
+
+```
+
+Given the respective dependences, the extent to which a species $i$ affects species *j* relative to the extent to which *j* affects *i* can be summarised by the interaction asymmetry given by $$a(i,j) = \frac{\left | d_{ij}-d_{ji} \right |}{max\left ( d_{ij}, d_{ji} \right )}.$$
+Mutual dependencies have previously been shown to be highly asymmetric in natural communities [@Bascompte2006]; in other words, if a plant species is largely dependent on a pollinator species, then that pollinator tends to depend rather weakly on the plant (or vice versa).
+This suggests that it may be possible to relax the assumption of bidirectional dependences further and simplify the network such that interacting species are connected by only one directed link when mutual dependencies are asymmetric (Figure 2c).
+Changing to unidirectional interactions determined by the observed direction of asymmetry, as a surrogate of bidirectional mutual dependences does not alter the relative *n~D~* of different networks (Supplementary Information XXX).
+Moreover, it confers an additional advantage for our purposes since it dramatically reduces the number of links in the network. 
+This translates into a substantial reduction of the time and memory required for the computation of all possible maximum matchings in a network, particularly for large networks (see "Relative importance" subsection below).
+
+#### Computational considerations
+
+Finding the maximum matchings, especially in large, directed, and highly connected networks can be an expensive operation.
+Although other less computationally expensive approaches to characterise the control profile of complex networks that are based on heuristics do exist [@Ruths2014], we found them to be extremely sensitive to assumptions regarding the direction of control (Supplementary Materials Section 2).
+Our strategy, instead, is to adopt an alternative bipartite representation of the directed network in which the two levels indicate the outgoing and incoming links to each node (Supplementary Section XXX).
+Once we had this alternative representation, then used the maximum bipartite matching algorithm implemented in `igraph` [@Csardi2006a].
+
+#### Statistical analysis
+
+Although understanding the variability of manageability across ecological networks is a useful result itself, we also wanted to test whether invasion status has an impact on the observed *n~D~*. 
+We, therefore, used a set of generalised linear models (with binomial error structure) to investigate the effect of invasion status while also controlling for factors related to species richness, since one might naively expect to see a negative relationship between diversity and manageability [@Menge1995].
+These covariates included the total number of species, plant richness, pollinators richness, the ratio of plants to pollinators richness, and the study site (as a two-level factor). 
+We assessed competing models by comparing the Akaike Information Criterion corrected for small sample sizes (AICc), and report results for the most parsimonious model.
+
+We next explored whether real networks differ in their architecture from random ones in a concerted way that affects manageability. 
+Previous research indicates a direct link between a network's degree distribution and the number of nodes necessary to fully control it [@Liu2011], but the strength and applicability of this relationship have not been tested for in weighted ecological networks.
+We, therefore, compared the driver node density *n~D~* of the empirical networks to networks generated by a null model that maintained each species' strength (its total sum of visits) while allowing their degrees (its number of interactions) to vary.
+Randomisations were generated using vegan 2.3-3 [@Oksanen2016]. 
+After generating the randomised networks, we then calculated the mutual dependences and interaction asymmetries of each and determined *n~D~*  using our maximum matching framework.
+Finally, we calculated the average rank (akin to a p-value) of *n~D~* for each empirical network compared to the corresponding one of each set of 999 randomisations.
+
+Beyond network structure, the dependency asymmetry plays a fundamental role in determining the direction of control in each two-species interaction and therefore has the potential to influence the network *n~D~* results above.
+We, therefore, performed an additional randomisation in which we kept the structure of network constant but randomised the direction of the interaction asymmetries. 
+That is, we first calculated the asymmetries for each community and then shuffled the direction of the link between each pair of species. 
+Similar as to the other null models, we calculated the average rank of the empirical *n~D~* when compared to that of the randomisations.
+
+### Relative importance
+
+Our second key question is related to how species differ in their importance for driving the population dynamics of the community. 
+To quantify this importance we computed all maximal cardinality matchings in each network. 
+We then calculated the frequency with which each species is deemed to be a superior and a driver node in the set of matchings that had a total weight greater or equal to 0.5 times the weight of the maximum matching.
+We selected this threshold as it provided a high agreement between networks quantified by visitation and pollination efficiency as well as between our weighting/directionality assumptions (mutual dependences and interaction asymmetries); however, the choice of this threshold had a negligible impact on the results (Supplementary Information XXX).
+
+Although the species importance calculated from mutual dependences contains full information, even in sparse networks, like those studied here, the number of maximal matchings increases exponentially with the number of links and nodes in a network.
+Unfortunately, this means that the large number of links in the most diverse communities rendered the computation unfeasible when we used mutual dependencies. 
+Taking this limitation into account, we compared the relative species ranks obtained when using asymmetries to those found when using mutual dependencies to test if they gave consistent results. 
+The comparison was performed for eleven of the twenty networks (those for which the number of matchings was smaller than 4 x 10^10^), using a paired Spearman correlation test, a weighted correlation coefficient *r~w2~* [which gives more weight to higher ranks; @PintoDaCosta2015], and a Jaccard similarity of the driver species in both approaches.
+All three approaches identified a high similarity in relative ranks. 
+Consequently, we focused on the results when using the asymmetries rather than mutual dependencies when further investigating the factors that determine species' relative importance since this also allows us to obtain results for all 20 networks.
+
+#### Computational considerations
+
+To compute all the maximum cardinality matchings we first generate the network's line graph—another representation in which nodes are the links of the original network and links represent common ending points [@West2001].
+Then calculate the complement of this line graph, which generates a graph in which nodes are connected if and only if they are not connected in the line graph. 
+Finally, all possible matchings of maximal size can be found by enumerating every clique (subgraphs in which all nodes are fully connected to each other) of maximum size in this complement graph [@Csardi2006a; @Gutin2013].
+A graphical representation of this procedure can be found in Supplementary Information Fig XX.
+
+#### Statistical analysis
+
+We then asked the question of whether some species-level structural properties can predict our metrics of species importance—the frequency to which a species is a driver or a superior node.
+We used a set of generalised linear mixed-effects models (with binomial error structure) with the relative frequencies as the response variables. 
+As predictors in this model, we included measures of centrality (degree and eigen-centrality), which have been found to be strong predictors of importance in a coextinction context [@Memmott2004]; a measure related to network robustness (contribution to nestedness), as nestedness has been proposed as one of the key properties that promote stability in mutualistic networks [@Saavedra2011]; two measures of strength of association and dependence (visitation and dependency strength), as their distribution determines the extent of interspecific effects [@Bascompte2006].
+In addition, we also included guild and invasive status as categorical fixed effects; although the importance of plants and pollinators or invasive and non-invasive species could respond differently to our structural metrics, our data set did not contain enough variation to include the corresponding interactions terms for these latter two predictors.
+All network metrics were calculated using the R package bipartite 2.06 [@Dormann2008]. 
+We lastly allowed for variation between different communities by including the network identity as a random effect [@Bates2015]. 
+Candidate models were compared using AICc and the relative importance of the explanatory variables was evaluated using the sum of Akaike weights over candidate models that accounted for 95% of the evidence [@Burnham2003; @Bates2015; @Barton2016].
+Coefficient estimates were averaged following @Buckland1997a while confidence intervals were calculated following [@Lukacs2010].
+
+# Appendix 1: Glossary
+
+Driver node
+  ~
+
+Matched/unmatched link
+  ~
+
+Matched/unmatched node
+  ~
+
+Matching
+  ~
+
+Matching size
+  ~
+
+Matching weight
+  ~
+
+Maximal cardinality matching
+  ~
+
+Maximum matching
+  ~
+
+Superior node
+  ~
+
 # References

### 2016-12-14 paper/EL-reviewer-comments-1.Rmd
Revise introduction, spelling and glossary

@@
 title: "Response to reviewer comments ELE-00738-2016"
-date: "21 November 2016"
+date: "14 December 2016"
 header-includes:
@@
 
-    *The sentence now reads "To bridge this gap, we propose methods to apply previous theory on the control of complex systems into an ecological context and implement them in empirical data"*
+    *The sentence now reads "To bridge this gap, we develop methods to apply previous theory on the control of complex systems into an ecological context and implement them using empirical data, while taking into account the quantitative differences that exist among species interactions."*
 
@@
 
-Ln 25. I don't think that the statement that you "expand theory on the controllability of complex systems" is accurate. It is not clear to me how these results contribute to expand the general theory
+- Ln 25.
+I don't think that the statement that you "expand theory on the controllability of complex systems" is accurate.
+It is not clear to me how these results contribute to expand the general theory
 
-Ln 52, typo: presents
+    *Thank you.
+We have apologise for the imprecision.
+The sentence now reads "To bridge this gap, we develop methods to apply previous theory on the control of complex systems into an ecological context and implement them using empirical data, while taking into account the quantitative differences that exist among species interactions", which better reflects our contribution.*
 
-Ln 59. Please rewrite this sentence. it's not clear what "they" refers to here.
+- Ln 52, typo: presents
 
-Ln 78.
+    *Thanks. It's been changed.*
+
+- Ln 59. Please rewrite this sentence. it's not clear what "they" refers to here.
+
+    *Thanks.
+The subject was intended to be "control theory".
+We have rephrased the sentence to improve clarity and it now reads "Therefore, control theory can potentially provide an indication of which species are most relevant from a structural and dynamic perspective, a particularly important feature given that these species should underpin informed attempts to both alter or maintain the ecosystem state".*
+
+- Ln 78.
 It is not clear why this is the direction of the hypothesis.
@@
 Is there any theoretical explanation for this expectation?
+
+    *We based the direction of the hypothesis in the general feeling of failure of several restoration ecology programmes.
+However, in retrospect, we realise that the academic evidence to substantiate the hypotheis was insufficient.
+We have reframed the sentence to indicate that invaded communities might have different levels of manageability but without an a priori expectation on the direction of this difference.
+REVISE, CHECK WITH WARWICK*
 
@@
 
-Ln 236. Typo: missing period
+- Ln 236. Typo: missing period
 
@@
 
-Ln 293: Typo: reference
+- Ln 293: Typo: reference
 

### 2016-12-14 paper/draft_2.Rmd
Revise introduction, spelling and glossary

@@
 
+# Introduction
+
+Complex systems are characterised by relationships in which the whole is often greater than the sum of its parts [@Jorgensen1998; @Levin1999; @Montoya2006].
+Within community ecology, a complex systems approach has led to the development of a variety of analytical and simulation tools with which to understand, for example, the role of species when embedded in an intricate network of interactions [@Pascual2005; @Bascompte2009; @Stouffer2012].
+The inherent complexity of nature, however, has hindered—or at least greatly complicated—our ability to find management solutions to the many problems ecological communities face. 
+To overcome this obstacle, we require a framework that allows us to explain, predict, and manage ecological communities, particularly when they are confronted with perturbations [@Sole2001; @Green2005].
+Moreover, such a framework needs to be able to account for their complex structure, and the dynamics that determine the state of each species, and the community as a whole.
+
+Among the various possibilities, control theory appears to be a strong candidate as it is designed to deal with determining and supervising the behaviour of general dynamical systems, and is well equipped to deal with the many feedbacks present in ecological communities [@Liu2015].
+Research in the field has established a strong link between the structure of complex networks and their controllability, while also demonstrating that it is in principle possible to alter a whole ecological community's composition by modifying the abundances of only a few species [@Liu2011; @Cornelius2013; @Ruths2014].
+Applications of control theory to ecological networks can also take into account the extent to which changes in the abundances of one species may ripple through the community [@Cornelius2013].
+Therefore, control theory could provide an indication of which species are most relevant from a structural and dynamic perspective, a particularly important feature given that these species should underpin informed attempts to both alter or maintain the ecosystem state.
+
+Despite these advances, practical challenges to the conservation of interaction networks persist [@Tylianakis2010], and the link between the structure of complex networks and our ability to manage and conserve them is still ambiguous [@Kaiser-Bunbury2015].
+To complicate things further, biotic invasions—a major driver of global change—can induce dramatic changes in the patterns of interactions that determine the structure of ecological networks [@Baxter2004; @Tylianakis2008; @Ehrenfeld2010a].
+Although understanding how differences in network structure before and after the invasion impact our ability to manage them presents a double challenge, it is a critical first step towards a fully informed recovery.
+Despite the apparent overlap, a control-theoretic perspective has not been widely adopted in an invasion context. 
+This is perhaps because of a lack of appropriate methodological tools that can account for the observed variation in the strength of interspecific effects that are characteristic of ecological networks [@Liu2011; @Isbell2013].
+
+To bridge this gap, we develop methods to apply previous theory on the control of complex systems into an ecological context and implement them using empirical data, while taking into account the quantitative differences that exist among species interactions.
+Specifically, we use a set of ten pairs of uninvaded and invaded plant-pollinator communities to investigate the link between invasion, network structure and ecological management. 
+We ask two questions framed in the context of a plant invasion.
+First, we ask whether invaded networks have differnt levels of manageability than their uninvaded counterparts; that is, whether they require a different proportion of species to be managed to achieve the same level of control.
+Second, we ask whether some species are more important than others at driving the population dynamics of the community and which factors determine this importance. 
+We focus on these particular applications for a variety of reasons. 
+First, biotic invasions are known to produce tractable changes in the structure of ecological networks, and these changes can be particularly pronounced in mutualistic networks between plants and pollinators where biotic invasions have been shown to modify the strength of species interactions and the degree of network nestedness and connectivity [@Olesen2002; @Aizen2008; @Bartomeus2008; @Vila2009; @Traveset2013].
+Second, plant-pollinator networks provide an ideal framework to answer these questions. 
+On the one hand, community networks that quantify relative levels of interaction are readily available. 
+On the other, the bipartite nature of pollination networks makes it possible to simplify assumptions of how these interactions translate into interspecific effects.
+
 # Methods
@@
 A node is said to be *matched* if it is at the end of a matched link and *unmatched* otherwise. 
-A node is also said to be *superior* if it is at the start of a matched link (note that all unmatched nodes are also superior but not vice versa).
+A node is also said to be *superior* if it is at the start of a matched link (note that a node cannot be superior if it has no outgoing links).
 Notably, these node categories help us to intuitively link a maximum matching back to the concept of network controllability as follows.
@@
 
-```{r, echo = F, fig.width = 6.2, fig.height = 1.6, message = F, warning = F, fig.pos = "T", fig.cap = "Different ways to depict quantitative mutualistic networks.
+```{r figure 2, echo = F, fig.width = 6.2, fig.height = 1.6, message = F, warning = F, fig.pos = "T", fig.cap = "**Different ways to depict quantitative mutualistic networks**.
 (a) Pollination networks are typically described by the number of visits between each plant and animal species.
@@
 Candidate models were compared using AICc and the relative importance of the explanatory variables was evaluated using the sum of Akaike weights over candidate models that accounted for 95% of the evidence [@Burnham2003; @Bates2015; @Barton2016].
-Coefficient estimates were averaged following @Buckland1997a while confidence intervals were calculated following [@Lukacs2010].
+Coefficient estimates were averaged following @Buckland1997a while confidence intervals were calculated following @Lukacs2010.
 
@@
 Driver node
-  ~
+  ~ An unmatched node in a maximal cardinality matching or a maximum matching.
+From the control perspective driver nodes are those to which external control signals must ble applied in order to gain full control of the network.
 
 Matched/unmatched link
-  ~
+  ~ A link if said to be *matched* if it is part of a matching and *unmatched* otherwise.
 
 Matched/unmatched node
-  ~
+  ~ A node is said to be *matched* if it is at the end of a matched link and *unmatched* otherwise.
 
 Matching
-  ~
+  ~ A subset of links in which no two of them share a common starting or ending node.
 
 Matching size
-  ~
+  ~ The number of matched links in a particular matching.
 
 Matching weight
-  ~
+  ~ The sum of the weights of all matched links in a particular matching.
 
 Maximal cardinality matching
-  ~
+  ~ A matching with the largest possible size. In unweighted networks all maximal cardinality matchings are also maximum matchings.
 
 Maximum matching
-  ~
+  ~ A matching with the largest possible size *and* weight.
 
 Superior node
-  ~
+  ~ The node at the start of a matched link. From the control perspective superior nodes compose the chain that propagate the control signal(s) trough the network.
 

### 2016-12-15 paper/draft_2.Rmd
Initial results

@@
   html_document: default
+  word_document: default
 header-includes:
@@
 library(latex2exp)
+library(ggplot2)
 
 "../code/functions" %>% 
+	list.files(full.names = T) %>%
+	plyr::l_ply(source)
+
+"../code/plotting_functions" %>% 
 	list.files(full.names = T) %>%
@@
 	dplyr::rename(count = method)
+n_driver <- readRDS("../data/processed/n_driver.rds")
+manag_models <- readRDS("../data/processed/models_manageability.rds")
+src_bi_w <- readRDS("../data/processed/manageability_bi_vs_weight.rds")
+```
+
+```{r plot theme, echo = FALSE, warning = F, message = F}
+fer_theme <- theme_bw() +
+	theme(text = element_text(family = "Times"),
+	      title = element_text(size = 7.5, hjust = 0),
+	      legend.title = element_text(size = 9),
+	      legend.text = element_text(size = 8),
+				axis.text = element_text(size = 8),
+				axis.title = element_text(size = 9, hjust = 0.5), 
+				strip.text = element_text(size = 9, hjust = 0), 
+				strip.background = element_blank(),
+				plot.margin = grid::unit(c(5, 0, 2, 0), "mm"))
 ```
@@
 We ask two questions framed in the context of a plant invasion.
-First, we ask whether invaded networks have differnt levels of manageability than their uninvaded counterparts; that is, whether they require a different proportion of species to be managed to achieve the same level of control.
+First, on the basis of the complexities involved with invasive species erradication and ecosystem restoration [@Woodford2016], we ask whether invaded networks have lower levels of manageability than their uninvaded counterparts; that is, whether they require a greater proportion of species to be managed to achieve the same level of control.
 Second, we ask whether some species are more important than others at driving the population dynamics of the community and which factors determine this importance. 
@@
 We, therefore, used a set of generalised linear models (with binomial error structure) to investigate the effect of invasion status while also controlling for factors related to species richness, since one might naively expect to see a negative relationship between diversity and manageability [@Menge1995].
-These covariates included the total number of species, plant richness, pollinators richness, the ratio of plants to pollinators richness, and the study site (as a two-level factor). 
+These covariates included the total number of species, plant richness, pollinators richness, the ratio of plants to pollinators richness, the link density (connectance), and the study site (as a two-level factor).
 We assessed competing models by comparing the Akaike Information Criterion corrected for small sample sizes (AICc), and report results for the most parsimonious model.
@@
 
+# Results
+
+## Manageability
+
+All of the networks studied had a driver node density *n~D~* between `r round(min(dplyr::filter(n_driver, type == "z-bi")$n_dr_p), digits = 2)` and `r round(max(dplyr::filter(n_driver, type == "z-bi")$n_dr_p), digits = 2)` (mean `r round(mean(dplyr::filter(n_driver, type == "z-bi")$n_dr_p), digits = 2)`) when we considered bidirectional links weighted by the mutual dependences.
+This was in strong agreement with the results obtained using the dependence asymmetry for which *n~D~* ranged between `r round(min(dplyr::filter(n_driver, type == "weight")$n_dr_p), digits = 2)` and `r round(max(dplyr::filter(n_driver, type == "weight")$n_dr_p), digits = 2)` (mean `r round(mean(dplyr::filter(n_driver, type == "weight")$n_dr_p), digits = 2)`; Spearman rank correlation `r round(src_bi_w$estimate, digits = 2)`, *p* `r fix_small_pvalue(src_bi_w$p.value)`).
+In addition, we found that invaded communities had less driver node density than uninvaded ones even when controlling for potential diversity effects (Figure 3), suggesting that. 
+Out of the various covariates we explored—total number of species, plant richness, pollinator richness, link density (connectance), and the ratio of plant to pollinator richness—only the ratio of plant to pollinator richness was retained in the final model as determined by the AICc (Table S4).
+
+```{r fig_explaining-n-driver, echo = FALSE, warning = FALSE, message = FALSE, fig.width = 3.245, fig.height = 3.2, fig.cap = "asdasd"}
+
+par_res <- as.data.frame(residuals(manag_models@objects[[1]], "partial"))
+names(par_res) <- paste0(make.names(names(par_res)), "_res")
+par_res %<>%
+  dplyr::bind_cols(manag_models@objects[[1]]$data)
+
+p1 <- par_res %>%
+  ggplot(aes(x = inv, y = inv_res)) +
+  # facet_wrap(~type) +
+  geom_boxplot(size = 0.3,
+               colour = "grey10", outlier.shape = 21, outlier.size = 1) +
+  fer_theme +
+  scale_x_discrete(labels = c("uninvaded", "invaded"), name = "") +
+  ylab(expression(paste(n[D], " partial residuals"))) +
+  coord_flip() +
+  theme(
+        legend.position = "none",
+				plot.margin = grid::unit(c(2, 1, 2, 0), "mm"), 
+				# panel.grid.minor.x = element_blank(),
+				panel.grid.minor.y = element_blank())
+
+p2 <- par_res %>%
+  ggplot(aes(x = n_pla/n_pol, y = I.n_pla.n_pol._res)) +
+	geom_smooth(method = "lm", se = F, colour = "black", size = 0.5) +
+	geom_point(shape = 21) + 
+	fer_theme +
+	scale_x_continuous(name = "ratio plant / pollinators") +
+	scale_y_continuous(name = expression(paste(n[D], " partial residuals")))
+
+cowplot::plot_grid(p1, p2, ncol = 1, align = "v")
+# pdf("./paper/figures/fig_3.pdf", height = 1.7, width = 3.245, family = "Times", compress = F, title = "Figure 3")
+# f3
+# dev.off()
+```
+
 # Appendix 1: Glossary

### 2016-12-15 paper/draft_2.Rmd
Minor changes to introduction after Daniel's comments

@@
 ---
-title: "Biotic invasions reduce the manageability of pollination networks"
+title: "Biotic invasions fuck with the manageability of pollination networks"
 classoption: a4paper
@@
 Within community ecology, a complex systems approach has led to the development of a variety of analytical and simulation tools with which to understand, for example, the role of species when embedded in an intricate network of interactions [@Pascual2005; @Bascompte2009; @Stouffer2012].
-The inherent complexity of nature, however, has hindered—or at least greatly complicated—our ability to find management solutions to the many problems ecological communities face. 
+The inherent complexity of nature, however, has regularly hindered—or at least greatly complicated—our ability to find management solutions to the many problems ecological communities face. 
 To overcome this obstacle, we require a framework that allows us to explain, predict, and manage ecological communities, particularly when they are confronted with perturbations [@Sole2001; @Green2005].
-Moreover, such a framework needs to be able to account for their complex structure, and the dynamics that determine the state of each species, and the community as a whole.
+Ideally, such a framework needs to be able to account for their complex structure, and the dynamics that determine the state of each species, and the community as a whole.
 
-Among the various possibilities, control theory appears to be a strong candidate as it is designed to deal with determining and supervising the behaviour of general dynamical systems, and is well equipped to deal with the many feedbacks present in ecological communities [@Liu2015].
+Among the various possibilities, control theory appears to be a strong candidate as it is designed to deal with determining and supervising the behaviour of general dynamical systems [@Motter2015], and is well equipped to deal with the many feedbacks present in ecological communities [@Liu2015].
 Research in the field has established a strong link between the structure of complex networks and their controllability, while also demonstrating that it is in principle possible to alter a whole ecological community's composition by modifying the abundances of only a few species [@Liu2011; @Cornelius2013; @Ruths2014].

### 2016-12-15 code/14-manageability_models.R
Manageability models

@@ -1,0 +1,56 @@
+library(magrittr)
+
+net <- "../data/processed/networks" %>%
+	read_networks()
+meta <- readr::read_csv("../data/ntw_info.csv") %>% dplyr::tbl_df() %>%
+	dplyr::rename(count = method)
+n_matched <- readRDS("../data/processed/n_matched.rds")
+a_m <- readRDS("../data/processed/n_matched_all_types.rds") 
+
+spp_lc <- net %>%
+	plyr::ldply(function(x){
+		keep_largest_component(x) %>%
+			igraph::V() %>%
+			length()
+	}) %>%
+	`names<-`(c("net_name", "n_spp_lc"))
+
+n_links <- net %>%
+	plyr::ldply(function(x){
+		keep_largest_component(x) %>%
+			igraph::E() %>%
+			length()
+	}) %>%
+	`names<-`(c("net_name", "n_links"))
+
+
+n_driver <- a_m %>%
+	dplyr::inner_join(meta) %>%
+	dplyr::inner_join(n_links) %>%
+	dplyr::inner_join(spp_lc) %>%
+	dplyr::filter(count == "visitation") %>%
+	dplyr::mutate(n_sp = n_pla + n_pol,
+								n_dr = n_sp - n_matched,
+								n_dr_lc = n_spp_lc - n_matched, 
+								n_dr_p = n_dr / n_sp)
+
+src_bi_w <- n_driver %>%
+	dplyr::filter(type == "z-bi" | type == "weight",
+								study != "ballantyne") %>%
+	dplyr::select(net_name, type, n_dr_p) %>%
+	tidyr::spread(type, n_dr_p) %$%
+	cor.test(weight, `z-bi`, method = "spearman")
+
+n_driver %<>%
+	dplyr::filter(!is.na(inv))
+
+n_driver_wb <- dplyr::filter(n_driver, 
+														 type == "z-bi" | type == "weight")
+
+library(glmulti)
+
+models_n <- glmulti(cbind(n_dr, n_matched) ~ I(n_pla/n_pol) + study + inv + type + I(n_links/(n_pla*n_pol)), data = n_driver_wb, family = "binomial", level = 1)
+
+saveRDS(n_driver, "../data/processed/n_driver.rds", ascii = T, compress = F)
+saveRDS(models_n, "../data/processed/models_manageability.rds")
+saveRDS(src_bi_w, "../data/processed/manageability_bi_vs_weight.rds", ascii = T, compress = F)

### 2016-12-16 paper/draft_2.Rmd
Partial changes to methods

@@
 
-At the core of control theory of complex networks is the idea that the state of a node depends on the state of the nodes it interacts with, and the particular form of this dependency is determined both by the dynamic relationship among interacting nodes as well as the structure of the links in the network.
-A complex network can usually be simplified as a linear system of the form $\dot{x} = Ax + Bu(t)$, where the change over time of its state ($\dot{x}$) depends on its current state *x*, an external time-varying input *u(t)*, and the matrices *A* and *B*, which encapsulate information about the network structure and how the network responds to the external input, respectively.
-Previous research has shown that such a system is controllable if there exists a minimum number of nodes in the network ($D \geq 0$) to which is possible to apply an external control signal that propagates trough the network to in turn drive the state of every other node in the network to a particular configuration [@Kalman1963; @Liu2011].
-Conveniently, the information necessary to determine whether a network is controllable, and the number of driver nodes *D*, is fully contained in the network structure [@Liu2011; @Motter2015]
+At the core of control theory of complex networks rests the idea that the state of a node depends on the state of the nodes it interacts with, and the particular form of this dependency is determined both by the dynamic relationship among interacting nodes as well as the structure of the links in the network.
+A large proportion of the recent advances on control theory have focused on linear systems as a first step to understand the controllability of nonlinear dynamics, in fact showing that fundamental can insight about the control of complex systems can be addressed without a detailed knowledge of the nonlinear dynamics and the system parameters [@Liu2015].
+We therefore focus on complex networks whose dynamics can be locally linearised, at least near equilibium points, to the form $\frac{dx}{dt} = Ax + Bu(t)$, where the change over time of its state ($\frac{dx}{dt}$) depends on its current state *x* (the species' populations in an ecological context), an external time-varying input *u(t)*, and the matrices *A* and *B*, which encapsulate information about the network structure and how the network responds to the external input, respectively.
+Previous research has shown that such a system is controllable if there exists a minimum subset *D* of nodes in the network ($S > D \geq 1$, where *S* is the total number of species) to which to apply an external control signal that will propagate through the network and in turn drive the state of every other node in the network to a desired configuration in finite time [@Kalman1963; @Liu2011].
+Conveniently, the information necessary to determine whether a network is controllable, and the number of driver nodes *D* is fully contained in the network structure [@Liu2011; @Motter2015].
 
-Strictly speaking, the network structure tells us whether a linear approximation of the system is controllable or not, but it provides limited information about the characteristics of the control signal or the feasibility of its implementation [@Motter2015].
-Despite this limitation, structural controllability provides important information about our ability to control a system without requiring full and precise knowledge of the dynamical relationships among nodes.
+We emphasise that, strictly speaking, the network structure tells us whether a linear approximation of the system is controllable or not, but it provides limited information about the characteristics of the control signal or the feasibility of its implementation [@Motter2015].
+Despite this limitation, structural controllability provides a strong indication about our ability to control a system without requiring full and precise knowledge of the dynamical relationships among nodes.
 This means that structural controllability can be applied to a wide range of readily available network representations of ecological communities. 
-Moreover, when quantitative data about species interactions is available, we show how some of the limitations of structural controllability can be overcome by incorporating the role of dynamical relationships without being overly dependent on the particular choices about how dynamics are modelled.
+Moreover, wh show here how quantitative data about species interactions can help us move past some of the limitations of structural controllability by better approximating the role of dynamical relationships without being overly dependent on the specific choices of how these dynamics are modelled or characterised.
 
@@
 
-The number of driver nodes *D* not only determines whether a network is controllable but can also provide a structural indication of how difficult its control might be.
+The number of driver nodes *D* not only determines whether a network is controllable or not but can also provide a structural indication of how difficult its control might be.
 This is because systems that require a large number of external input signals are intuitively more difficult or costly to control.
-In an ecological context, external signals that modify the state of a node (this is a species' population) can be thought of as management interventions.
-We, therefore, use the density of driver nodes $n_D = \frac{D}{S},$ as an index of the manageability of an ecological community, where *S* is the total number of species.
+In an ecological context, external signals that modify the state of a node can be thought of as management interventions.
+We therefore use the density of driver nodes $n_D = \frac{D}{S},$ as an index of the manageability of an ecological community.
 From this perspective, the manageability of an ecological community can be understood in the context of how difficult is to modify the abundances of species in the community using external interventions—a common theme in ecosystem management, conservation, and restoration.
@@
 It has been recently shown that calculating *D* is equivalent to finding a maximum matching in the network [@Liu2011].
-In a directed network, a matching is a subset of links in which no two of them share a common starting or ending node (Figure 1).
+In a directed network, a *matching* consists of a subset of links in which no two of them share a common starting or ending node (Figure 1).
 A given matching has *maximal cardinality* if the number of matched links (also referred to as the *matching size*) is the largest possible.
-A maximal cardinality matching is then called a *maximum matching* if the sum of the weights of the matched links (also referred to as matching weight) is again the largest possible [@West2001].
+A maximal cardinality matching is then called a *maximum matching* if the sum of the weights of the matched links (also referred to as *matching weight*) is again the largest possible [@West2001].
 Note that this implies that for unweighted binary networks all maximal cardinality matchings are also maximum matchings.
@@
 A node is said to be *matched* if it is at the end of a matched link and *unmatched* otherwise. 
-A node is also said to be *superior* if it is at the start of a matched link (note that a node cannot be superior if it has no outgoing links).
+A node is also said to be *superior* if it is at the start of a matched link.
+Note that a node cannot be superior if it has no outgoing links.
 Notably, these node categories help us to intuitively link a maximum matching back to the concept of network controllability as follows.
-Each matched node can be controlled by the node that is pointing to it—its superior.
-Unmatched nodes, on the other hand, are the driver nodes *D* because they have no superior in the network and must be directly controlled by an external input [@Liu2011].
+Unmatched nodes are the driver nodes *D* because they have no superior in the network and must be directly controlled by an external input [@Liu2011].
+Each matched node, on the other hand, can be controlled by the node that is pointing to it—its superior.
 
 ```{r figure 1, echo = F, message = F, warning = F, fig.width = 6.2, fig.height = 1.8, results= "hide", fig.pos = "t", fig.cap = "**Matchings of a simple network**.
-We start with a network in which the direction of the links indicate the direction of control (a); that is, a link from *a~1~* to *p~1~*, for instance, indicates that the state of *p~1~* (density/abundances in an ecological context) is influenced by the state of *a~1~*.
-This network has two maximal cardinality matchings (b, c); this is, two configurations in which it would be possible to exert full control of the network.
-The three matched links (blue arrows) represent the possible control paths trough the network and provide an indication of the matched nodes (also in blue), which are controlled by superior nodes within the network (bold node labels).
-Unmatched nodes (in orange) are also called driver nodes because full network control requires external signals to be applied to them, and therefore, the manageability of the network can be inferred from the density of unmatched nodes *n~D~ = D/S = 2/5*.
-Out of the two maximal cardinality matchings (b, c) only one of them has maximum weight and therefore is a maximum matching (c); note that if the network were unweighted both maximal cardinality matchings would also be maximum matchings.
+(a) We start with a network in which the direction of the links indicates the potential direction of control; for example a link from *a~1~* to *p~1~* indicates that the state of *p~1~* is influenced by the state of *a~1~*.
+(b & c) This network has two maximal cardinality matchings; that is, two configurations in which it would be possible to exert full control of the network via external input signals to a minimal set of nodes.
+In both cases, the three matched links (purple arrows) represent the control paths through the network and provide an indication of the matched nodes (purple), which are controlled by superior nodes within the network (bold node labels).
+Unmatched nodes (orange) are called driver nodes because full network control requires external signals to be applied to them.
+Out of the two maximal cardinality matchings only one (c) has maximum weight and therefore is also a maximum matching.
 Further examples can be found in the Supplemental Material SXX."}
@@
 While calculating *n~D~* provides an indication of the manageability of an ecological community, it does not provide information about the identity of the species that compose this set. 
-This difference is rather important since maximum matchings are often not unique in a given network and different sets of species of size *~D~* could potentially be used to control the network [@Liu2011].
-Ecologically, these distinctions are also relevant because management and conservation resources are limited and therefore ecological interventions should ideally be focused on the set of species that might provide the largest impact.
-Consequently, species can be further characterised in terms of the frequency with which they exist on key paths leading through the network, which provides an indication of their relative importance in driving the state of the community.
+This difference is rather important since maximum matchings are often not unique in a given network and different sets of species of size *D* could potentially be used to control the network [@Liu2011].
+Ecologically, these distinctions are acutely relevant because management and conservation resources are limited and therefore ecological interventions should ideally be focused on the set of species that might provide the largest impact.
+Consequently, we will show how species can be further characterised in terms of the frequency with which they exist on key paths leading through the network, which provides an indication of their relative importance in driving the state of the community.
 
@@
 Because our networks are weighted, we compute all maximal cardinality matchings and not just the maximum matchings. 
-We do so because empirical interaction strengths are to some extent stochastic and depend on proximate factors such as sampling method and intensity [@Gibson2011], and therefore using only maximum matchings in empirical networks might be therefore too restrictive.
-Furthermore, we focus not only on driver/unmatched nodes, as is customary in the control literature, but also on superior nodes because realistically, from an ecological perspective, we are not yet able to aim for full control of the abundances of all species in the community.
+We do so because empirical interaction strengths are to some extent stochastic and depend on proximate factors such as sampling method and intensity [@Gibson2011], and therefore using only maximum matchings in weighted empirical networks might be therefore too restrictive.
+Furthermore, we focus not only on driver nodes, as is customary in the control literature, but also on superior nodes because realistically, from an ecological perspective, we are not yet able to aim for full control of the abundances of all species in the community.
 Superior nodes, of which driver nodes are a subset, are important for the controllability of the network not just because they might require an external control signal but, essentially, because they are part of the chain that transmits the control signal to other species.
@@
 
-Now we describe the application of the previously described framework to ten paired pollination networks constructed from previously published visitation data. 
-Notably, each network pair was composed of a community invaded by a plant and a community "free" of the invasive species. 
-Four network pairs were obtained from natural or semi-natural vegetation communities in the city of Bristol, UK [@Lopezaraiza-Mikel2007]. 
-These networks are comprised by between `r lop[1]` and `r lop[6]` species (mean `r round(lop[4])`) and non-invaded plots were obtained by experimentally removing all the flowers of the invasive species *Impatients grandulifera*.
-The six remaining network pairs were obtained from lower diversity Mediterranean shrublands in Cap de Creus National Park, Spain [@Bartomeus2008].
-These networks are comprised by between `r bar[1]` and `r bar[6]` species (mean `r round(bar[4])`) and, contrastingly, uninvaded communities were obtained from plots that had not yet been colonised by either of the invasive species *Carpobrotus affine acinaciformis* or *Opuntia stricta*.
+We now describe the application of the previously defined framework to ten paired pollination networks, where each network pair was composed of a community invaded by a plant and a community "free" of the invasive species.
+Four pairs were obtained from natural or semi-natural vegetation communities in the city of Bristol, UK [@Lopezaraiza-Mikel2007]. 
+These networks are comprised of `r lop[1]`-`r lop[6]` species (mean `r round(lop[4])`), and non-invaded plots were obtained by experimentally removing all the flowers of the invasive species *Impatients grandulifera*.
+The other six pairs were obtained from lower diversity Mediterranean shrublands in Cap de Creus National Park, Spain [@Bartomeus2008].
+These networks are comprised of `r bar[1]`-`r bar[6]` species (mean `r round(bar[4])`); in contrast to the above, contrastingly, uninvaded communities were obtained from plots that had not yet been colonised by either of the invasive species *Carpobrotus affine acinaciformis* or *Opuntia stricta*.
 Further details about the empirical networks can be found in the Supplementary Information XXX.
 
-The structure of all studied networks was determined using visitation frequency which has been shown to be an appropriate surrogate for interspecific effects in pollination networks [@Vazquez2005; @Bascompte2006].
-To examine whether this decision would influence our results, we also evaluated the effect of using pollinator efficiency or importance as alternative measures of species interactions in a different data set that lacked invasive species [@NeEman2010; @Ballantyne2015], and we found quantitatively similar results for all of these options (Supplementary Information XXX).
+We then specified the structure of all networks using pollinator visitation frequency, which has been shown to be an appropriate surrogate for interspecific effects in pollination networks [@Vazquez2005; @Bascompte2006].
+To examine whether this decision would influence our results, we also evaluated the effect of using pollinator efficiency or pollinator importance as alternative measures of species interactions in a different data set that lacked invasive species [@NeEman2010; @Ballantyne2015], and we found quantitatively similar results for all three of these options (Supplementary Information XXX).
 Furthermore, because our approach depends to a large degree on the network topology, we evaluated the robustness of our results to undersampling.
+Specifically, we removed links with a probability inversely proportional to its weight effectivelly simulating 
 The sensitivity analysis indicated that the proposed methods can be applied even in the absence of complete sampling (Supplementary Information XXX).

### 2017-01-10 paper/draft_2.Rmd
Minor modifications to the introduction

@@
 
-To bridge this gap, we develop methods to apply previous theory on the control of complex systems into an ecological context and implement them using empirical data, while taking into account the quantitative differences that exist among species interactions.
+To bridge this gap, we outline an approach to apply theory on the control of complex systems in an ecological context and implement them using empirical data.
+Furthermore, we introduce methods with which to take into account the important quantitative differences that exist among species interactions.
 Specifically, we use a set of ten pairs of uninvaded and invaded plant-pollinator communities to investigate the link between invasion, network structure and ecological management. 
-We ask two questions framed in the context of a plant invasion.
-First, on the basis of the complexities involved with invasive species erradication and ecosystem restoration [@Woodford2016], we ask whether invaded networks have lower levels of manageability than their uninvaded counterparts; that is, whether they require a greater proportion of species to be managed to achieve the same level of control.
+While doing so, we ask two questions framed in the context of a plant invasion.
+First, on grounded on the difficulties usually involved with invasive species erradication and ecosystem restoration [@Woodford2016], we ask whether invaded networks have lower levels of "manageability" than their uninvaded counterparts; that is, whether they require a greater proportion of species to be managed to achieve the same level of control.
 Second, we ask whether some species are more important than others at driving the population dynamics of the community and which factors determine this importance. 

### 2017-01-10 paper/draft_2.Rmd
Add awcknoledgements

@@
 
+## Acknowledgments
+
+The authors thank Dr.
+Takeuki Uno for the insight provided to find the set of all maximum matching algorithms, and Jason Tylianakis, Bernat Bramon, Warwick Allen, Matthew Hutchinson, and Marilia Gaiarsa for feedback and valuable discussions.
+EFC acknowledges the support from the University of Canterbury Doctoral Scholarship, the University of Canterbury Meadow Mushrooms Postgraduate Scholarship, a New Zealand International Doctoral Research Scholarship, and a travel grant from the European Space Agency.
+DBS acknowledges the support of a Marsden Fast-Start grant and a Rutherford Discovery Fellowship, administered by the Royal Society of New Zealand.
+
 # References

### 2017-01-10 paper/draft_2.Rmd
Update glossary

@@
   ~ An unmatched node in a maximal cardinality matching or a maximum matching.
-From the control perspective driver nodes are those to which external control signals must ble applied in order to gain full control of the network.
+From the control perspective, driver nodes are those to which external control signals must be applied in order to gain full control of the network.
 
 Matched/unmatched link
-  ~ A link if said to be *matched* if it is part of a matching and *unmatched* otherwise.
+  ~ A link is refered to as *matched* if it is part of a matching, and *unmatched* otherwise.
 
 Matched/unmatched node
-  ~ A node is said to be *matched* if it is at the end of a matched link and *unmatched* otherwise.
+  ~ A node is refered to as *matched* if it is at the end of a matched link, and *unmatched* otherwise.
 
 Matching
-  ~ A subset of links in which no two of them share a common starting or ending node.
+  ~ A set of links in which no two of them share a common starting or ending node.
 
 Matching size
-  ~ The number of matched links in a particular matching.
+  ~ The number of matched links in a  matching.
 
@@
 Maximal cardinality matching
-  ~ A matching with the largest possible size. In unweighted networks all maximal cardinality matchings are also maximum matchings.
+  ~ A matching with the largest possible matching size. In unweighted networks, all maximal cardinality matchings are also maximum matchings.
 
 Maximum matching
-  ~ A matching with the largest possible size *and* weight.
+  ~ A matching with the largest possible matching size *and* matching weight.
 
 Superior node
-  ~ The node at the start of a matched link. From the control perspective superior nodes compose the chain that propagate the control signal(s) trough the network.
+  ~ The node at the start of a matched link. From the control perspective, superior nodes make up the chain(s) that propagate the control signal(s) through the network.
 

### 2017-01-10 paper/draft_2.Rmd
Update methods with daniel's comments

@@
 
-At the core of control theory of complex networks rests the idea that the state of a node depends on the state of the nodes it interacts with, and the particular form of this dependency is determined both by the dynamic relationship among interacting nodes as well as the structure of the links in the network.
-A large proportion of the recent advances on control theory have focused on linear systems as a first step to understand the controllability of nonlinear dynamics, in fact showing that fundamental can insight about the control of complex systems can be addressed without a detailed knowledge of the nonlinear dynamics and the system parameters [@Liu2015].
-We therefore focus on complex networks whose dynamics can be locally linearised, at least near equilibium points, to the form $\frac{dx}{dt} = Ax + Bu(t)$, where the change over time of its state ($\frac{dx}{dt}$) depends on its current state *x* (the species' populations in an ecological context), an external time-varying input *u(t)*, and the matrices *A* and *B*, which encapsulate information about the network structure and how the network responds to the external input, respectively.
-Previous research has shown that such a system is controllable if there exists a minimum subset *D* of nodes in the network ($S > D \geq 1$, where *S* is the total number of species) to which to apply an external control signal that will propagate through the network and in turn drive the state of every other node in the network to a desired configuration in finite time [@Kalman1963; @Liu2011].
-Conveniently, the information necessary to determine whether a network is controllable, and the number of driver nodes *D* is fully contained in the network structure [@Liu2011; @Motter2015].
+Disregarding practical considerations, any network could, in theory, be fully controlled if we control the state of every single node individually.
+At the core of control theory of complex networks, however, rest the idea the state of a node depends on the state of the nodes it interacts with, and the particular form of this dependence is determined both by the dynamic relationship among interacting nodes as well as the structure of the links in the network.
+This property can, therefore, be harnessed to find a minimum subset of driver nodes *D* to which to apply external input signals which then drive the state of every other node in the network to a desired configuration in finite time [@Kalman1963; @Liu2011].
 
-We emphasise that, strictly speaking, the network structure tells us whether a linear approximation of the system is controllable or not, but it provides limited information about the characteristics of the control signal or the feasibility of its implementation [@Motter2015].
-Despite this limitation, structural controllability provides a strong indication about our ability to control a system without requiring full and precise knowledge of the dynamical relationships among nodes.
-This means that structural controllability can be applied to a wide range of readily available network representations of ecological communities. 
-Moreover, wh show here how quantitative data about species interactions can help us move past some of the limitations of structural controllability by better approximating the role of dynamical relationships without being overly dependent on the specific choices of how these dynamics are modelled or characterised.
+Conveniently, the information necessary to determine whether a network with linear dynamics is controllable, and the minimum number of driver nodes *D* is fully contained in the network structure [@Liu2011; @Motter2015].
+We, therefore, start from the assumption that that an ecological network can, at least near equilibrium points, be described by $\frac{dx}{dt} = Ax + Bu(t)$, where the change over time of its state ($\frac{dx}{dt}$) depends on its current state *x* (the species' populations in an ecological context), an external time-varying input *u(t)*, and the matrices *A* and *B*, which encapsulate information about the network structure and how the network responds to the external input, respectively.
+Even though this might be a strong assumption, it has been shown that fundamental insight about the control of complex systems can be gained without a detailed knowledge of the nonlinear dynamics and the system parameters [@Liu2015]; an important step towards understanding the controllability of systems with nonlinear dynamics [@Liu2011].
+This means that this structural controllability can be applied to a wide range of readily available network representations of ecological communities to provide a strong indication of our ability to control them.
+Moreover, we show here how quantitative data about species interactions can help us move past some of the limitations of structural controllability by better approximating the role of dynamical relationships without being overly dependent on the specific choices of how these dynamics are modelled or characterised.
 
@@
 This is because systems that require a large number of external input signals are intuitively more difficult or costly to control.
-In an ecological context, external signals that modify the state of a node can be thought of as management interventions.
-We therefore use the density of driver nodes $n_D = \frac{D}{S},$ as an index of the manageability of an ecological community.
-From this perspective, the manageability of an ecological community can be understood in the context of how difficult is to modify the abundances of species in the community using external interventions—a common theme in ecosystem management, conservation, and restoration.
+In an ecological context, external inputs that modify the state of a node can be thought of as management interventions.
+Therefore, the density of driver nodes $n_D = \frac{D}{S},$ can be seen as a metric of the extent to which network structure can be harnessed for network control.
+For instance, while a hypothetical "network" in which species do not interact but instead function independently from each other would require direct interventions in eversy single species to achieve full control, a linear food chain would require just one species to be directly controlled to knock-on cascading effects trough the trophic levels that compose it.
+From this perspective, it is possible to use *n~D~* as an index of the manageability of an ecological community, understood in the context of how difficult is to modify the abundances of species in the community using external interventions—a common theme in ecosystem management, conservation, and restoration.
 
 It has been recently shown that calculating *D* is equivalent to finding a maximum matching in the network [@Liu2011].
-In a directed network, a *matching* consists of a subset of links in which no two of them share a common starting or ending node (Figure 1).
+In a directed network, a *matching* consists of a subset of links in which o two of them share a common starting or ending node (Figure 1).
 A given matching has *maximal cardinality* if the number of matched links (also referred to as the *matching size*) is the largest possible.
@@
 Note that a node cannot be superior if it has no outgoing links.
-Notably, these node categories help us to intuitively link a maximum matching back to the concept of network controllability as follows.
-Unmatched nodes are the driver nodes *D* because they have no superior in the network and must be directly controlled by an external input [@Liu2011].
+Notably, these node categories are what help us to link a maximum matching back to the concept of network controllability as follows.
+Unmatched nodes are the *driver nodes* *D* because they have no superior in the network and must be directly controlled by an external input [@Liu2011].
 Each matched node, on the other hand, can be controlled by the node that is pointing to it—its superior.
@@
 This difference is rather important since maximum matchings are often not unique in a given network and different sets of species of size *D* could potentially be used to control the network [@Liu2011].
-Ecologically, these distinctions are acutely relevant because management and conservation resources are limited and therefore ecological interventions should ideally be focused on the set of species that might provide the largest impact.
-Consequently, we will show how species can be further characterised in terms of the frequency with which they exist on key paths leading through the network, which provides an indication of their relative importance in driving the state of the community.
+Ecologically, these distinctions are acutely relevant because management and conservation resources are limited, and therefore ecological interventions should ideally be focused on the set of species that might provide the largest impact.
+Consequently, species can be further characterised regarding the frequency with which an external input signal could be applied to them in order to control the full network. 
+In other words, the frequency *f~D~* with which a species is classified as a driver node.
+However, the role of driver nodes is still ambiguous when full network controllability is unfeasible or undesired—often the case in ecological settings.
+Alternatively, species can also be characterised by the frequency *f~S~* with which they are classified as superior nodes.
+This is, the frequency with which they exist on key paths through the network that transmits the control signal to other species.
+We show how, together, *f~D~* and *f~S~* can provide an indication of a species' relative importance in driving the state of the community.
 
-Specifically, in an unweighted network to approximate a species importance for network control it is possible compute all the maximum matchings and calculate the frequency at which each species is classified as a superior node.
-Because our networks are weighted, we compute all maximal cardinality matchings and not just the maximum matchings. 
+Most commonly, structural controllability assumes unweighted networks—links exist or not, and hence *f~D~* and *f~S~* can be calculated by computing all possible maximum matchings. 
+However, it has been shown that using weighted links can reveal significant ecological patterns and processes that might be undetectable in unweighted networks [@Scotti2007; @Tylianakis2007; @Vazquez2007; @Kaiser-Bunbury2010a].
+We, therefore, use a quantitative version of the maximum matching algorithm and instead calculate all maximal cardinality matchings and rank them by their matching weight. 
 We do so because empirical interaction strengths are to some extent stochastic and depend on proximate factors such as sampling method and intensity [@Gibson2011], and therefore using only maximum matchings in weighted empirical networks might be therefore too restrictive.
-Furthermore, we focus not only on driver nodes, as is customary in the control literature, but also on superior nodes because realistically, from an ecological perspective, we are not yet able to aim for full control of the abundances of all species in the community.
-Superior nodes, of which driver nodes are a subset, are important for the controllability of the network not just because they might require an external control signal but, essentially, because they are part of the chain that transmits the control signal to other species.
-
-It is worth to note that, traditionally, structural controllability assumes unweighted links—they exist or not—and hence results are entirely based on topology.
-However, it has been shown that using weighted links can reveal important ecological patterns and processes that might be undetectable in unweighted networks [@Scotti2007; @Tylianakis2007; @Vazquez2007; @Kaiser-Bunbury2010a].
-By using the quantitative version of the maximum matching algorithm, we give priority to the species that participate in the pathways that potentially have the largest impact on the community; effectively incorporating, at least partially, the dynamics of the system.
+By incorporating the interaction weight we give priority to the species that participate in the pathways that potentially have the largest impact on the community; effectively incorporating, at least partially, the dynamics of the system.
 
@@
 Furthermore, because our approach depends to a large degree on the network topology, we evaluated the robustness of our results to undersampling.
-Specifically, we removed links with a probability inversely proportional to its weight effectivelly simulating 
-The sensitivity analysis indicated that the proposed methods can be applied even in the absence of complete sampling (Supplementary Information XXX).
+Specifically, we calculated *n~D~*, and species relative importance (see below) for 500 random subsamples of each empirirical network in which the weakest links were more likely to be removed. 
+The sensitivity analysis indicated that even in the absence of complete sampling a control theoretic approach can be applied (Supplementary Information XXX).
 
@@
 
-Given the different networks, we began by quantifying their manageability.
-To do so, we calculated the maximum matching of the corresponding pollination network and determined the minimum proportion of species that need directed interventions to fully control the species abundances in the community.
+We began by quantifying the manageability of each of the aforementioned networks.
+To do so, we calculated the networks' maximum matching and determined the minimum proportion of species *n~D~* that need external input signals—a management intervention—to fully control the species abundances in the community.
 To simplify the analysis, we only considered the largest component in a network if it had more than one (two species are in different components if there exists no path between them and are hence independent of each other in terms of network control).
@@
 Recall that the aforementioned maximum matching algorithm requires a directed network in which a link between species *i* and *j* pointing to species *j* indicates that the abundance of *j* can be affected by the abundance of *i*.
-This implies that we need first to identify a directionality for the links between species that is consistent with the dynamics of the community. 
+This implies that we need first to identify a directionality for the links between species that is consistent with the dynamics of the community (Figure 2). 
 In some ecological networks, establishing the directionality is relatively straightforward, for example when links represent biomass transfer or energy flow. 
@@
 Nevertheless, the relative extent to which a given pair of interacting species affect each other can be quantified by the magnitude of the mutual dependence [@Bascompte2006]. 
-The dependency of plant *i* on pollinator *j*, *d~ij~*, is the proportion of the visits coming from pollinator *j* compared to all pollinator visits to plant *i*. 
-Likewise, the dependency of pollinator *j* on plant *i*, *d~ji~*, is the ratio of the visits by pollinator *j* to plant *i* and all visits of pollinator *j*.
-As the dependencies are not symmetric, its use generates a weighted bipartite network in which all interacting pairs are connected by two directed links (Figure 2b).
+The dependence of plant *i* on pollinator *j*, *d~ij~*, is the proportion of the visits coming from pollinator *j* compared to all pollinator visits to plant *i*. 
+Likewise, the dependence of pollinator *j* on plant *i*, *d~ji~*, is the proportion of the visits by pollinator *j* to plant *i* and all visits of pollinator *j*.
+As the dependences are not symmetric, their use generates a weighted bipartite network in which all interacting pairs are connected by two directed links (Figure 2b).
 
@@
 (a) Pollination networks are typically described by the number of visits between each plant and animal species.
-(b) Given visitation data, the mutual dependencies between interacting species are calculated directly based on the relative visitation frequencies.
-(c) The relative differences of dependencies—the interaction asymmetry—then provide a means to identify the dominant direction of the interspecific effects."}
+(b) Given visitation data, the mutual dependences between interacting species are calculated directly based on the relative visitation frequencies.
+(c) The relative differences of dependences—the interaction asymmetry—then provide a means to identify the dominant direction of the interspecific effects."}
 
@@
 Given the respective dependences, the extent to which a species $i$ affects species *j* relative to the extent to which *j* affects *i* can be summarised by the interaction asymmetry given by $$a(i,j) = \frac{\left | d_{ij}-d_{ji} \right |}{max\left ( d_{ij}, d_{ji} \right )}.$$
-Mutual dependencies have previously been shown to be highly asymmetric in natural communities [@Bascompte2006]; in other words, if a plant species is largely dependent on a pollinator species, then that pollinator tends to depend rather weakly on the plant (or vice versa).
-This suggests that it may be possible to relax the assumption of bidirectional dependences further and simplify the network such that interacting species are connected by only one directed link when mutual dependencies are asymmetric (Figure 2c).
-Changing to unidirectional interactions determined by the observed direction of asymmetry, as a surrogate of bidirectional mutual dependences does not alter the relative *n~D~* of different networks (Supplementary Information XXX).
-Moreover, it confers an additional advantage for our purposes since it dramatically reduces the number of links in the network. 
+Mutual dependences have previously been shown to be highly asymmetric in natural communities [@Bascompte2006]; in other words, if a plant species is largely dependent on a pollinator species, then that pollinator tends to depend rather weakly on the plant (or vice versa).
+This suggests that it may be possible to relax the assumption of bidirectional dependences further and simplify the network such that interacting species are connected by only one directed link when mutual dependences are asymmetric (Figure 2c).
+We found here that changing to unidirectional interactions determined by the observed direction of asymmetry, as a surrogate of bidirectional mutual dependences does not alter the relative *n~D~* of different networks (Supplementary Information XXX).
+Moreover, this simplification confers an additional advantage for our purposes since it dramatically reduces the number of links in the network. 
 This translates into a substantial reduction of the time and memory required for the computation of all possible maximum matchings in a network, particularly for large networks (see "Relative importance" subsection below).
 
-#### Computational considerations
-
-Finding the maximum matchings, especially in large, directed, and highly connected networks can be an expensive operation.
-Although other less computationally expensive approaches to characterise the control profile of complex networks that are based on heuristics do exist [@Ruths2014], we found them to be extremely sensitive to assumptions regarding the direction of control (Supplementary Materials Section 2).
-Our strategy, instead, is to adopt an alternative bipartite representation of the directed network in which the two levels indicate the outgoing and incoming links to each node (Supplementary Section XXX).
-Once we had this alternative representation, then used the maximum bipartite matching algorithm implemented in `igraph` [@Csardi2006a].
+Finding the maximum matchings can be an expensive operation especially in large, directed, and highly connected networks.
+Although less computationally expensive heuristics to characterise the control profile of complex networks do exist [@Ruths2014], we found their use to be extremely sensitive to assumptions regarding the direction of control (Supplementary Materials Section 2).
+Consequently, we have adopted a strategy based on an alternative bipartite representation of the directed network in which the two levels indicate the outgoing and incoming links to each node (Supplementary Section XXX).
+Once we had this alternative representation, then used the maximum bipartite matching algorithm implemented in `igraph` on each empirica [@Csardi2006a].
 
@@
 
-Although understanding the variability of manageability across ecological networks is a useful result itself, we also wanted to test whether invasion status has an impact on the observed *n~D~*. 
+Although understanding the variability of manageability across ecological networks is a useful result itself, we also wanted to test whether invasion status had an impact on the observed *n~D~*. 
 We, therefore, used a set of generalised linear models (with binomial error structure) to investigate the effect of invasion status while also controlling for factors related to species richness, since one might naively expect to see a negative relationship between diversity and manageability [@Menge1995].
@@
 Previous research indicates a direct link between a network's degree distribution and the number of nodes necessary to fully control it [@Liu2011], but the strength and applicability of this relationship have not been tested for in weighted ecological networks.
-We, therefore, compared the driver node density *n~D~* of the empirical networks to networks generated by a null model that maintained each species' strength (its total sum of visits) while allowing their degrees (its number of interactions) to vary.
+We therefore compared the driver node density *n~D~* of the empirical networks to networks generated by a null model that maintained each species' strength (its total sum of visits) while allowing their degrees (its number of interactions) to vary.
 Randomisations were generated using vegan 2.3-3 [@Oksanen2016]. 
@@
 
-Beyond network structure, the dependency asymmetry plays a fundamental role in determining the direction of control in each two-species interaction and therefore has the potential to influence the network *n~D~* results above.
+Beyond network structure, the dependence asymmetry plays a fundamental role in determining the direction of control in each two-species interaction and therefore has the potential to influence the network *n~D~* results above.
 We, therefore, performed an additional randomisation in which we kept the structure of network constant but randomised the direction of the interaction asymmetries. 
-That is, we first calculated the asymmetries for each community and then shuffled the direction of the link between each pair of species. 
-Similar as to the other null models, we calculated the average rank of the empirical *n~D~* when compared to that of the randomisations.
+That is, we first calculated the observed asymmetries for each community and then shuffled the direction of the link between each pair of species. 
+Similar to the other null models, we calculated the average rank of the empirical *n~D~* when compared to that of the randomisations.
 
@@
 
-Our second key question is related to how species differ in their importance for driving the population dynamics of the community. 
+Our second key question is related to how species differ in their ability to drive the population dynamics of the community. 
 To quantify this importance we computed all maximal cardinality matchings in each network. 
-We then calculated the frequency with which each species is deemed to be a superior and a driver node in the set of matchings that had a total weight greater or equal to 0.5 times the weight of the maximum matching.
-We selected this threshold as it provided a high agreement between networks quantified by visitation and pollination efficiency as well as between our weighting/directionality assumptions (mutual dependences and interaction asymmetries); however, the choice of this threshold had a negligible impact on the results (Supplementary Information XXX).
+We then calculated the frequency with which each species *i* is deemed to be a driver (*f~D~*) or a superior node (*f~S~*) in the set of matchings that had a matching weight greater or equal to 0.5 times the weight of the maximum matching.
+We selected this threshold as it provided a high agreement between networks quantified by visitation and pollination efficiency as well as between our weighting/directionality assumptions; however, the choice of this threshold had a negligible impact on any results (Supplementary Information XXX).
 
-Although the species importance calculated from mutual dependences contains full information, even in sparse networks, like those studied here, the number of maximal matchings increases exponentially with the number of links and nodes in a network.
-Unfortunately, this means that the large number of links in the most diverse communities rendered the computation unfeasible when we used mutual dependencies. 
-Taking this limitation into account, we compared the relative species ranks obtained when using asymmetries to those found when using mutual dependencies to test if they gave consistent results. 
+Even in sparse networks, like those studied here, the number of maximal matchings increases exponentially with the number of links and nodes in a network. 
+Unfortunately, this means that the large number of links in the most diverse communities rendered the computation unfeasible when we used mutual dependences. 
+Taking this limitation into account, we compared the relative species ranks obtained when using asymmetries to those found when using mutual dependences to test if they gave consistent results. 
 The comparison was performed for eleven of the twenty networks (those for which the number of matchings was smaller than 4 x 10^10^), using a paired Spearman correlation test, a weighted correlation coefficient *r~w2~* [which gives more weight to higher ranks; @PintoDaCosta2015], and a Jaccard similarity of the driver species in both approaches.
-All three approaches identified a high similarity in relative ranks. 
-Consequently, we focused on the results when using the asymmetries rather than mutual dependencies when further investigating the factors that determine species' relative importance since this also allows us to obtain results for all 20 networks.
+All three approaches identified a high similarity in relative ranks (STILL NEED TO CHECK THAT FOR BOTH *f~D~* AND *f~S~*). 
+Consequently, we focused on the results when using the asymmetries rather than mutual dependences when further investigating the factors that determine species' relative importance since this also allows us to obtain results for all 20 networks.
 
-#### Computational considerations
-
-To compute all the maximum cardinality matchings we first generate the network's line graph—another representation in which nodes are the links of the original network and links represent common ending points [@West2001].
-Then calculate the complement of this line graph, which generates a graph in which nodes are connected if and only if they are not connected in the line graph. 
-Finally, all possible matchings of maximal size can be found by enumerating every clique (subgraphs in which all nodes are fully connected to each other) of maximum size in this complement graph [@Csardi2006a; @Gutin2013].
+To compute all the maximum cardinality matchings, we first generate the network's line graph—another representation in which nodes are the links of the original network and links represent common ending points [@West2001].
+We then calculate the complement of this line graph, which generates a graph in which nodes are connected if and only if they are not connected in the line graph. 
+Finally, all possible maximal cardinality matchings can be found by enumerating every clique (subgraphs in which all nodes are fully connected to each other) of size *D* in this complement graph [@Csardi2006a; @Gutin2013].
 A graphical representation of this procedure can be found in Supplementary Information Fig XX.
@@
 
-We then asked the question of whether some species-level structural properties can predict our metrics of species importance—the frequency to which a species is a driver or a superior node.
+We then examined whether some species-level structural properties can predict our metrics of species importance—the frequency to which a species is a driver or a superior node (*f~D~* and *f~S~* respectively).
 We used a set of generalised linear mixed-effects models (with binomial error structure) with the relative frequencies as the response variables. 
-As predictors in this model, we included measures of centrality (degree and eigen-centrality), which have been found to be strong predictors of importance in a coextinction context [@Memmott2004]; a measure related to network robustness (contribution to nestedness), as nestedness has been proposed as one of the key properties that promote stability in mutualistic networks [@Saavedra2011]; two measures of strength of association and dependence (visitation and dependency strength), as their distribution determines the extent of interspecific effects [@Bascompte2006].
-In addition, we also included guild and invasive status as categorical fixed effects; although the importance of plants and pollinators or invasive and non-invasive species could respond differently to our structural metrics, our data set did not contain enough variation to include the corresponding interactions terms for these latter two predictors.
+As predictors in this model, we included measures of centrality (degree and eigen-centrality), which have been found to be strong predictors of importance in a coextinction context [@Memmott2004]; a measure related to network robustness (contribution to nestedness), as nestedness has been proposed as one of the key properties that promote stability in mutualistic networks [@Saavedra2011]; and two measures of strength of association and dependence (visitation and dependence strength), as their distribution determines the extent of interspecific effects [@Bascompte2006].
+In addition, we also included guild and invasive status as categorical fixed effects.
+Although the importance of plants and pollinators or invasive and non-invasive species could respond differently to our structural metrics, our data set did not contain enough variation to include the corresponding interactions terms for these latter two predictors.
 All network metrics were calculated using the R package bipartite 2.06 [@Dormann2008]. 

### 2017-01-17 code/tinkering/plotting_matching_for_small_network.R
Tinkering to plot the matchings of one of the empirical networks

@@ -1,0 +1,39 @@
+
+igraph::E(dir)$matched <- 2
+igraph::E(dir)$matched[mat2[j, ]] <- 4
+
+igraph::V(dir)$matched <- 2
+igraph::V(dir)$matched[igraph::V(dir)$name %in%
+														ends(dir, mat2[j, ])[, 2]] <- 4
+
+igraph::V(dir)$superior <- 1
+igraph::V(dir)$superior[igraph::V(dir)$name %in%
+													 	ends(dir, mat2[j, ])[, 1]] <- 2
+
+names_fancy <- sp_names_fancy
+names_fancy[igraph::V(dir)$name %in%
+							ends(dir, mat2[j, ])[, 1]] <-
+	sp_names_fancy_b[igraph::V(dir)$name %in%
+									 	ends(dir, mat2[j, ])[, 1]]
+
+matching_weight <- sum(E(dir)$weight[mat2[j, ]])
+
+dir %>% 
+	plot(
+			 vertex.size = 30,
+			 vertex.label.family = fam,
+			 vertex.label.color = l_c,
+			 vertex.label.cex = igraph::V(.)$superior * 1.2 ,
+			 # vertex.shape = igraph::V(.)$vertex.shape,
+			 vertex.color = pal[igraph::V(.)$matched],
+			 edge.color = pal[igraph::E(.)$matched],
+			 # edge.color = c("#B2ABD2", "#FDB863"),
+			 edge.label = round(E(.)$weight,2), 
+			 edge.width = E(.)$matched/2,
+			 edge.label.family = fam,
+			 edge.label.color = igraph::E(.)$matched,
+			 edge.label.cex = l_s,
+			 edge.curved = T,
+			 edge.arrow.size = 0.5,
+			 margin = ma, 
+			 palette = pal)

### 2017-01-17 paper/draft_2.Rmd
Correct asymmetry typo

@@
 	keep_largest_component() %>%
-	bipartite_digraph(type = "z-bi", weight.type = "assymetry") 
+	bipartite_digraph(type = "z-bi", weight.type = "asymetry") 
 as_net <- example_net %>%

### 2017-01-17 paper/draft_2.Rmd
Change size of vertex in figure 1 and 2

@@
 			 vertex.color = v_c, 
-			 vertex.size = 30,
+			 vertex.size = 35,
 			 vertex.label = sp_names_fancy,
@@
 			plot(layout = lay, 
-					 vertex.size = 30,
+					 vertex.size = igraph::V(.)$superior * 10 + 20,
 					 vertex.label = names_fancy,
@@
 			 col = pal[c(2, 4)],
-			 lwd = 2, cex = 0.9, xjust=0.5, yjust=1, bty = "n")
+			 lwd = 2, cex = 0.9, xjust=0.5, yjust=0.8, bty = "n")
 
@@
 			 pt.cex = 2,
-			 cex = 0.9, xjust=0.5, yjust=1, bty = "n")
+			 cex = 0.9, xjust=0.5, yjust=0.8, bty = "n")
 
-legend(1-0.16 + 0.05, 0.9, legend = expression(paste(bold("(bold label)"), " ", "superior nodes")), horiz = TRUE,
-			 cex = 0.9, xjust=0.5, yjust=1, bty = "n")
+legend(1-0.16 + 0.05, 0.9, legend = expression(paste(bold("  superior node"))), horiz = TRUE,
+			 pch = 21, 
+			 # pt.bg = pal[c(2, 4)],
+			 pt.cex = c(3),
+			 cex = 0.9, xjust=0.5, yjust=0.8, bty = "n")
+
+# legend(1-0.16 + 0.05, 0.9, legend = expression(paste(bold("(bold label)"), " ", "superior nodes")), horiz = TRUE,
+# 			 cex = 0.9, xjust=0.5, yjust=1, bty = "n")
 
@@
 ```{r figure 2, echo = F, fig.width = 6.2, fig.height = 1.6, message = F, warning = F, fig.pos = "T", fig.cap = "**Different ways to depict quantitative mutualistic networks**.
-(a) Pollination networks are typically described by the number of visits between each plant and animal species.
-(b) Given visitation data, the mutual dependences between interacting species are calculated directly based on the relative visitation frequencies.
-(c) The relative differences of dependences—the interaction asymmetry—then provide a means to identify the dominant direction of the interspecific effects."}
+(a) Pollination networks are frequently described by the observed number of visits between each plant and animal species.
+(b) Based on that visitation data, the mutual dependences between interacting species are calculated directly based on the relative visitation frequencies.
+(c) The relative differences of these  dependences—the interaction asymmetry—then provide a means to estimate the dominant direction of the interspecific effects."}
 

### 2017-01-17 paper/draft_2.Rmd
Minor changes to the methods

@@
 Finding the maximum matchings can be an expensive operation especially in large, directed, and highly connected networks.
-Although less computationally expensive heuristics to characterise the control profile of complex networks do exist [@Ruths2014], we found their use to be extremely sensitive to assumptions regarding the direction of control (Supplementary Materials Section 2).
+Although less computationally expensive heuristics to approximate the control profile of complex networks do exist [@Ruths2014], we found their use to be extremely sensitive to assumptions regarding the direction of control (Supplementary Materials Section 2).
 Consequently, we have adopted a strategy based on an alternative bipartite representation of the directed network in which the two levels indicate the outgoing and incoming links to each node (Supplementary Section XXX).
-Once we had this alternative representation, then used the maximum bipartite matching algorithm implemented in `igraph` on each empirica [@Csardi2006a].
+Once we had this alternative representation, then, on each network, we used the maximum bipartite matching algorithm implemented in the `max_bipartite_match` function of igraph 1.0.1 [@Csardi2006a].
 
@@
 We therefore compared the driver node density *n~D~* of the empirical networks to networks generated by a null model that maintained each species' strength (its total sum of visits) while allowing their degrees (its number of interactions) to vary.
-Randomisations were generated using vegan 2.3-3 [@Oksanen2016]. 
+Randomisations were generated using the function `commsim` in vegan 2.3-3 [@Oksanen2016]. 
 After generating the randomised networks, we then calculated the mutual dependences and interaction asymmetries of each and determined *n~D~*  using our maximum matching framework.

### 2017-01-17 paper/draft_2.Rmd
Add some results

@@
 src_bi_w <- readRDS("../data/processed/manageability_bi_vs_weight.rds")
+r_w <- readRDS("../data/processed/random_weights.rds") %>% dplyr::tbl_df() %>%
+  dplyr::rename_("net_name" = ".id")
+r_d <- readRDS("../data/processed/random_directions.rds") %>% dplyr::tbl_df() %>%
+  dplyr::rename_("net_name" = ".id")
+
+prop <- expand.grid(c("asymmetry", "max_dep"), 
+                    c("scaled_FALSE", "scaled_TRUE")) %>% plyr::alply(1)
+driver <- c("../data/processed/matching_frequency") %>% 
+  list.files(full.names = T) %>%
+  lapply(list.files, full.names = T) %>% 
+  unlist() %>% 
+  lapply(read_allRDS)
+driver <- mapply(function(x, y){
+  attr(x, "type") <- as.character(y[,1])
+  attr(x, "scaled") <- stringr::str_split(as.character(y[,2]), "_") %>% unlist() %>% extract(2) %>% as.logical()
+  return(x)
+}, driver, prop)
+driver_bi <- "../data/processed/matching_frequency_bi" %>% 
+  read_allRDS()
 ```
@@
 This was in strong agreement with the results obtained using the dependence asymmetry for which *n~D~* ranged between `r round(min(dplyr::filter(n_driver, type == "weight")$n_dr_p), digits = 2)` and `r round(max(dplyr::filter(n_driver, type == "weight")$n_dr_p), digits = 2)` (mean `r round(mean(dplyr::filter(n_driver, type == "weight")$n_dr_p), digits = 2)`; Spearman rank correlation `r round(src_bi_w$estimate, digits = 2)`, *p* `r fix_small_pvalue(src_bi_w$p.value)`).
-In addition, we found that invaded communities had less driver node density than uninvaded ones even when controlling for potential diversity effects (Figure 3), suggesting that. 
-Out of the various covariates we explored—total number of species, plant richness, pollinator richness, link density (connectance), and the ratio of plant to pollinator richness—only the ratio of plant to pollinator richness was retained in the final model as determined by the AICc (Table S4).
+In addition, we found that invaded communities had less driver node density than uninvaded ones even when controlling for potential diversity effects (Figure 3a). 
+Out of the various covariates we explored—total number of species, plant richness, pollinator richness, link density (connectance), and the ratio of plant to pollinator richness—only the ratio of plant to pollinator richness was retained in the final model as determined by the AICc (Figure 3b; Table S4).
 
-```{r fig_explaining-n-driver, echo = FALSE, warning = FALSE, message = FALSE, fig.width = 3.245, fig.height = 3.2, fig.cap = "asdasd"}
+```{r fig_explaining-n-driver, echo = FALSE, warning = FALSE, message = FALSE, fig.width = 3.245, fig.height = 3.2, fig.cap = " Coovariates of driver node density.
+(a) Invaded communities have lower proportion of driver nodes *n~D~* than uninvaded communities even when controlling for factors related to species richness.
+The box covers the 25th–75th percentiles, the middle line marks the median, and the maximum length of the whiskers is 1.5 times the interquartile range.
+All points outside this range are indicated by the circles.
+(b) Out of the biodiversity metrics, only the ratio of plants to pollinators showed a significant relationship with *n~D~*.
+In both plots, residuals correspond to the partial working residuals of the invasion status in our generalised linear mixed model."}
 
@@
 	scale_x_continuous(name = "ratio plant / pollinators") +
-	scale_y_continuous(name = expression(paste(n[D], " partial residuals")))
+	scale_y_continuous(name = expression(paste(n[D], " partial residuals"))) +
+	theme(axis.title.y = element_text(vjust = 1, margin = margin(1,-3,1,1, unit = "lines")))
 
-cowplot::plot_grid(p1, p2, ncol = 1, align = "v")
-# pdf("./paper/figures/fig_3.pdf", height = 1.7, width = 3.245, family = "Times", compress = F, title = "Figure 3")
+cowplot::plot_grid(p1, p2, ncol = 1, align = "v") +
+	cowplot::draw_plot_label(label = c("a)", "b)"), size = 8, fontface = "plain", y = c(1, 0.5))
+# pdf("../paper/figures/fig_3.pdf", height = 1.7, width = 3.245, family = "Times", compress = F, title = "Figure 3")
 # f3
 # dev.off()
+
+```
+
+When exploring the effect of network structure itself, we observed that the manageability of empirical networks was, in general, not significantly different to the manageability of network randomisations that maintained the degree or the strength of individual species (Figure 4).
+However, when comparing the empirical network to randomisations that maintained the network structure but randomised only the direction of the asymmetries, we found that empirical networks showed a significant tendency to have smaller values of manageability.
+
+```{r fig_randomisations, echo = FALSE, warning = FALSE, message = FALSE, fig.width = 3.245, fig.height = 1.6, fig.cap = "The manageability of empirical networks compared to network randomisations.
+For each randomisation approach, we show the standarised rank of the empirical value compared to the set of randomisations.
+A scaled mean rank—akin to a p-value— less than 0.025 or greater than 0.975 (the areas shaded in light grey) suggests a significant difference between the empirical network and its randomisations.
+The empirical manageability is much smaller than that of network randomisations in which the direction of asymmetries has been randomised.
+In contrast, the manageability of networks in which the species degrees were randomly shuffled were not significantly different to the manageability of the empirical networks.
+Dark grey and white boxplots represent manageabilities obtained using interactions weighted by mutual dependences and asymmetries respectively.
+All boxes are as in Figure 3a."}
+r <- r_w %>%
+  dplyr::bind_rows(dplyr::mutate(r_d, type = "weight")) %>%
+  dplyr::inner_join(meta) %>%
+  dplyr::filter(study != "ballantyne") %>%
+  dplyr::mutate(n_dr = n_pla + n_pol - n_matched)
+
+# non-parametric
+z_scores <- r$method %>%
+  unique() %>%
+  plyr::ldply(function(x){
+    n_driver %>%
+      dplyr::mutate(type = stringr::str_replace(type, "-", "_")) %>%
+      dplyr::filter(type == "weight" | type == "z_bi") %>%
+      dplyr::mutate(method = x)
+  }) %>%
+  dplyr::bind_rows(r) %>%
+  dplyr::filter(!(type == "z_bi" & method == "r0")) %>%
+  dplyr::group_by(net_name, method, type) %>%
+  dplyr::mutate(z_r = rank(n_dr, na.last = NA),
+                z_r = z_r/n(),
+                z_s = qlogis(z_r),
+                z_s = replace(z_s, (is.infinite(z_s) & z_s > 0) | z_s > qlogis(0.999), qlogis(0.999)),
+                z_s = replace(z_s, is.infinite(z_s) & z_s < 0, qlogis(0.001))) %>%
+  dplyr::filter(is.na(sim))
+
+z_scores_method_order <- c("r0","swsh_both", "quasiswap_count","r00_ind", "r00_samp", "r00_both")
+
+z_scores %>%
+  dplyr::group_by() %>%
+  dplyr::mutate(method = factor(method, levels = z_scores_method_order),
+                m_n = as.numeric(method),
+                m_n = replace(m_n, m_n == 3, 3.5)) %>%
+  dplyr::filter(!method %in% c("r00_both", "r00_ind", "r00_samp", 
+  														 "swsh_both")) %>% # the maintain degree randomise strength option
+  ggplot(aes(x = method, y = -1 * z_s)) +
+  geom_rect(aes(xmin = 0.5, xmax = 2.5, ymin = -Inf, ymax = qlogis(0.025)), fill = "#f0f0f0") +
+  geom_rect(aes(xmin = 0.5, xmax = 2.5, ymin = Inf, ymax = qlogis(0.975)), fill = "#f0f0f0") +
+
+  # geom_hline(yintercept = c(-0), linetype = 2, alpha = 0.7, size = 0.25) + 
+  geom_vline(aes(xintercept = 1.5), alpha = 0.6, size = 0.25) +
+   geom_hline(yintercept = 0, size = 0.25, linetype = 2, colour = "grey30") +
+  geom_boxplot(aes(fill = type), size = 0.3,
+               colour = "grey10", outlier.shape = 21, outlier.size = 1) +
+  # geom_point(aes(y = 9, colour = sign <= 0.05), shape = 8, size = 1) +
+  scale_fill_manual(values = c("white", "#bdbdbd")) +
+  scale_x_discrete(
+    labels = rev(c("random degree", # "maintain degree\nrandomise strength", 
+    							 "random\nassymetry")),
+    # breaks = c(#"r00_samp", #"swsh_both",
+    					 # "quasiswap_count", "r0"),
+    expand = c(0,0)) +
+  scale_y_continuous(breaks = qlogis(c(0.001, 0.025, 0.5, 0.975,0.999)), 
+                     labels = plogis(qlogis(c(0.001, 0.025, 0.5, 0.975,0.999)))) + 
+  xlab("") +
+    coord_flip() +
+  ylab("mean rank of empirical manageability") + 
+  fer_theme +
+  theme(
+        legend.position = "none",
+				plot.margin = grid::unit(c(2, 1, 2, 0), "mm"), 
+				# panel.grid.minor.x = element_blank(),
+				panel.grid.minor.y = element_blank())
+```
+
+## Relative importance
+
+```{r}
+d_sp <- driver %>%
+  plyr::ldply(function(x) {
+    get_frequencies(x) %>%
+      dplyr::mutate(type = attr(x, "type"),
+                    scaled = attr(x, "scaled"))
+  }) %>% 
+	dplyr::filter(scaled == FALSE)
+
+d_sp_bi <- driver_bi %>%
+  get_frequencies() %>%
+      dplyr::mutate(type = "z_bi",
+                    scaled = FALSE)
+
+d_sp <- dplyr::bind_rows(d_sp, d_sp_bi) %>%
+  dplyr::inner_join(meta) 
 ```

### 2017-01-17 paper/supp_info_2.Rmd
Add figures to explain matching in example networks

---
title: "Biotic invasions fuck with the manageability of pollination networks"
subtitle: "Supporting Information"
classoption: a4paper
csl: ecology-letters.csl
output:
  pdf_document:
    fig_crop: no
  html_document: default
  word_document: default
header-includes:
- \usepackage{setspace}
- \usepackage{float}
- \renewcommand{\figurename}{Figure SI}
documentclass: artikel1
bibliography: references.bib
---

\doublespacing

```{r libraries, echo = F, include = F}
library(igraph)
library(magrittr)
library(dplyr)
library(latex2exp)
library(ggplot2)
library(RColorBrewer)

"../code/functions" %>% 
	list.files(full.names = T) %>%
	plyr::l_ply(source)

"../code/plotting_functions" %>% 
	list.files(full.names = T) %>%
	plyr::l_ply(source)

```

```{r load data, include = F}
net <- "../data/processed/networks" %>%
	read_networks()
meta <- readr::read_csv("../data/ntw_info.csv") %>% dplyr::tbl_df() %>%
	dplyr::rename(count = method)
n_driver <- readRDS("../data/processed/n_driver.rds")
manag_models <- readRDS("../data/processed/models_manageability.rds")
src_bi_w <- readRDS("../data/processed/manageability_bi_vs_weight.rds")
r_w <- readRDS("../data/processed/random_weights.rds") %>% dplyr::tbl_df() %>%
  dplyr::rename_("net_name" = ".id")
r_d <- readRDS("../data/processed/random_directions.rds") %>% dplyr::tbl_df() %>%
  dplyr::rename_("net_name" = ".id")

prop <- expand.grid(c("asymmetry", "max_dep"), 
                    c("scaled_FALSE", "scaled_TRUE")) %>% plyr::alply(1)
driver <- c("../data/processed/matching_frequency") %>% 
  list.files(full.names = T) %>%
  lapply(list.files, full.names = T) %>% 
  unlist() %>% 
  lapply(read_allRDS)
driver <- mapply(function(x, y){
  attr(x, "type") <- as.character(y[,1])
  attr(x, "scaled") <- stringr::str_split(as.character(y[,2]), "_") %>% unlist() %>% extract(2) %>% as.logical()
  return(x)
}, driver, prop)
driver_bi <- "../data/processed/matching_frequency_bi" %>% 
  read_allRDS()
```

```{r plot theme, echo = FALSE, warning = F, message = F}
fer_theme <- theme_bw() +
	theme(text = element_text(family = "Times"),
	      title = element_text(size = 7.5, hjust = 0),
	      legend.title = element_text(size = 9),
	      legend.text = element_text(size = 8),
				axis.text = element_text(size = 8),
				axis.title = element_text(size = 9, hjust = 0.5), 
				strip.text = element_text(size = 9, hjust = 0), 
				strip.background = element_blank(),
				plot.margin = grid::unit(c(5, 0, 2, 0), "mm"))
```

```{r example networks, include = F, message = F, warning = F, }

sp_names_fancy <- c(TeX("$p_1$"), TeX("$p_2$"), TeX("$p_3$"), TeX("$a_1$"), TeX("$a_2$"))
sp_names_fancy_b <- c(TeX("$\\mathbf{p_1}$"), TeX("$\\mathbf{p_2}$"), TeX("$\\mathbf{p_3}$"), TeX("$\\mathbf{a_1}$"), TeX("$\\mathbf{a_2}$"))

sp_names <- c("p1", "p2", "p3", "a1", "a2")

adj_matrix <- c(0,0,0,1,0,
								0,0,0,2,5,
								0,0,0,0,0,
								0,0,1,0,0,
								0,0,1,0,0) %>%
	matrix(nrow = 5, byrow = T)

example_net <- adj_matrix %>% 
	graph_from_adjacency_matrix(mode = "undirected", weighted = TRUE) 
igraph::V(example_net)$type <- c(F, F, F, T, T)
igraph::V(example_net)$name <- sp_names

base_net <- example_net
bi_net <- example_net %>%
	keep_largest_component() %>%
	bipartite_digraph(type = "z-bi", weight.type = "asymmetry") 
as_net <- example_net %>%
	keep_largest_component() %>%
	bipartite_digraph(type = "weight", weight.type = "asymmetry")

fam <- "Helvetica"
# layout is based on the bidirectional network
set.seed(1)

lay <- bi_net %>%
	layout_nicely()
v_c <- "white"
l_c <- "black"
l_s <- 0.9
ma <- c(0,0,0,0)
label_pos_x <- -1
label_pos_y <- 1

pal <- RColorBrewer::brewer.pal(5, "PuOr")

# BIDIRECTIONAL MATCHINGS

as_mat <- bi_net %>%
	digraph_bipartite() %>% 
	max_bipartite_match()

as_all_mat <- bi_net %>%
	digraph_bipartite(type = "z-bi") %>%
	igraph::make_line_graph() %>%
	igraph::complementer() %>% 
	igraph::max_cliques(min = as_mat$matching_size) %>%
	rev()

text_pos_x <- 0.5
text_pos_y <- -0.7

base_bi_net <- bi_net
E(bi_net)$weight <- round(E(bi_net)$weight, 1)

nets <- 1:length(as_all_mat) %>%
	plyr::llply(function(x){

		igraph::E(bi_net)$matched <- 2
		igraph::E(bi_net)$matched[as_all_mat[[x]]] <- 4

		igraph::V(bi_net)$matched <- 2
		igraph::V(bi_net)$matched[igraph::V(bi_net)$name %in%
																ends(bi_net, as_all_mat[[x]])[, 2]] <- 4

		igraph::V(bi_net)$superior <- 1
		igraph::V(bi_net)$superior[igraph::V(bi_net)$name %in%
																ends(bi_net, as_all_mat[[x]])[, 1]] <- 2

		names_fancy <- sp_names_fancy
		names_fancy[igraph::V(bi_net)$name %in%
																ends(bi_net, as_all_mat[[x]])[, 1]] <-
			sp_names_fancy_b[igraph::V(bi_net)$name %in%
																ends(bi_net, as_all_mat[[x]])[, 1]]

		matching_weight <- sum(E(bi_net)$weight[as_all_mat[[x]]])

		n_edges <- length(igraph::E(bi_net))
		has_cycles <- igraph::E(bi_net)[setdiff(1:n_edges, as_all_mat[[x]])] %>%
			igraph::delete_edges(bi_net, .) %>% 
			igraph::is_dag() %>%
			magrittr::not()

		list(
			bi_net = bi_net,
			names_fancy = names_fancy,
			as_mat = as_mat, 
			as_all_mat = as_all_mat[[x]], 
			matching_weight = matching_weight,
			has_cycles = has_cycles
		)

})

nets <- nets[order(!unlist(lapply(nets, function(x) x$has_cycles)), unlist(lapply(nets, function(x) x$matching_weight)), decreasing = T)]
```

# S1: Finding a complex network's matchings

Each species can control at most one other species

```{r fig-direction-of-control, echo = F, message = F, warning = F, fig.width = 6.2, fig.height = 3.2, results = "hide", fig.cap = "**Finding a maximum matching in a complex network**. (a) We start with a directed network in which the direction of the link represents the direction of control. (b) Our strategy to find find the number of driver species is based on an alternative representation of the directed network in which each node in (a) is represented by two nodes that indicate their outgoing and incoming links. Finding a maximum matching in this alternative representation is equivalent to finding the largest possible set of edges in which one node in the left hand side is connected to at most one node in the right hand side. It is then easy to identify the roles of each node in this representation: nodes on the right hand side that are connected to a matched link (purple) are matched, while those connected to a matched link on the left hand side are superior. (c) This information can then be mapped back to the original representation to identify the control paths and the driver nodes in the network. (d, e, and f) Ilustrate the approach for a network with bidirectional links."}
# par(mfrow=c(2,2), mar=c(0,0,0,0))
bi_sp_names_fancy <- c( TeX("$p_1^-$"), TeX("$p_2^-$"), TeX("$p_3^-$"), TeX("$a_1^-$"), TeX("$a_2^-$"), TeX("$p_1^+$"), TeX("$p_2^+$"), TeX("$p_3^+$"), TeX("$a_1^+$"), TeX("$a_2^+$"))

bi_sp_names_fancy_b <- c( TeX("$p_1^-$"), TeX("$p_2^-$"), TeX("$p_3^-$"), TeX("$a_1^-$"), TeX("$a_2^-$"), TeX("$\\mathbf{p_1^+}$"), TeX("$\\mathbf{p_2^+}$"), TeX("$\\mathbf{p_3^+}$"), TeX("$\\mathbf{a_1^+}$"), TeX("$\\mathbf{a_2^+}$"))

par(mfrow=c(2,3), mar= c(0,0,0,0))

# ASYMMETRY
as_net %>% 
	plot(layout = lay, 
			 vertex.color = v_c, 
			 vertex.size = 35,
			 vertex.label = sp_names_fancy,
			 vertex.label.family = fam,
			 vertex.label.color = l_c,
			 edge.label = round(E(.)$weight,1), 
			 edge.label.family = fam,
			 edge.label.color = l_c,
			 edge.label.cex = l_s,
			 edge.curved = F,
			 edge.arrow.size = 0.5,
			 margin = ma)

text(label_pos_x, label_pos_y, "a)", adj = c(0,0))

as_mat <- as_net %>%
	digraph_bipartite() %>% 
	max_bipartite_match()

as_all_mat <- as_net %>%
	digraph_bipartite() %>%
	igraph::make_line_graph() %>%
	igraph::complementer() %>% 
	igraph::max_cliques(min = as_mat$matching_size) %>%
	rev()

text_pos_x <- 0.5
text_pos_y <- -0.7

base_as_net <- as_net
E(as_net)$weight <- round(E(as_net)$weight, 1)

bi_as_net <- as_net %>%
	digraph_bipartite()

igraph::V(bi_as_net)$matched <- 2
igraph::V(bi_as_net)$matched[igraph::V(bi_as_net)$name %in%
														 	ends(bi_as_net, as_all_mat[[1]])[, 2]] <- 4
igraph::V(bi_as_net)$matched[1:5] <- NA

igraph::V(bi_as_net)$superior <- 30
igraph::V(bi_as_net)$superior[igraph::V(bi_as_net)$name %in%
														 	ends(bi_as_net, as_all_mat[[1]])[, 1]] <- 40
igraph::V(bi_as_net)$superior[6:10] <- 35

igraph::E(bi_as_net)$matched <- 2
		igraph::E(bi_as_net)$matched[as_all_mat[[1]]] <- 4

bi_as_net %>%
	plot(layout = matrix(c(rep(c(-0.5, 0.9), each = 5), rep(seq(-0.8, 0.8, length.out = 5), 2)), ncol = 2), 
			 # vertex.size = igraph::V(.)$superior,
			 vertex.size = 30, 
			 vertex.label = c(bi_sp_names_fancy[6:10], bi_sp_names_fancy[1:5]),
			 vertex.label.family = fam,
			 vertex.label.color = l_c,
			 # vertex.label.cex = igraph::V(.)$superior * 0.1 + 0.9,
			 # vertex.color = pal[igraph::V(.)$matched],
			 vertex.color = NA,
			 edge.color = pal[E(.)$matched],
			 edge.label = NA, 
			 edge.width = E(.)$matched/2,
			 edge.label.family = fam,
			 edge.label.color = igraph::E(.)$matched,
			 edge.label.cex = l_s,
			 edge.curved = F,
			 edge.arrow.size = 0.5,
			 margin = ma, 
			 rescale = F)

text(-0.95, 0.825, "b)", adj = c(0,0))

E(as_net)$matched <- 2
		E(as_net)$matched[as_all_mat[[1]]] <- 4

		igraph::V(as_net)$matched <- 2
		igraph::V(as_net)$matched[igraph::V(as_net)$name %in%
																ends(as_net, as_all_mat[[1]])[, 2]] <- 4

		igraph::V(as_net)$superior <- 1
		igraph::V(as_net)$superior[igraph::V(as_net)$name %in%
																ends(as_net, as_all_mat[[1]])[, 1]] <- 2

		names_fancy <- sp_names_fancy
		names_fancy[igraph::V(as_net)$name %in%
																ends(as_net, as_all_mat[[1]])[, 1]] <-
			sp_names_fancy_b[igraph::V(as_net)$name %in%
																ends(as_net, as_all_mat[[1]])[, 1]]

		matching_weight <- sum(E(as_net)$weight[as_all_mat[[1]]])

		as_net %>% 
			plot(layout = lay, 
					 vertex.size = igraph::V(.)$superior * 10 + 20,
					 vertex.label = names_fancy,
					 vertex.label.family = fam,
					 vertex.label.color = l_c,
					 vertex.label.cex = igraph::V(.)$superior * 0.1 + 0.9,
					 # vertex.shape = igraph::V(.)$vertex.shape,
					 vertex.color = pal[igraph::V(.)$matched],
					 edge.color = pal[E(.)$matched],
					 edge.label = NA, 
					 edge.width = E(.)$matched/2,
					 edge.label.family = fam,
					 edge.label.color = igraph::E(.)$matched,
					 edge.label.cex = l_s,
					 edge.curved = F,
					 edge.arrow.size = 0.5,
					 margin = ma) %>% 
			print()

text(label_pos_x, label_pos_y, "c)", adj = c(0,0))

bi_net %>% 
	plot(layout = lay, 
			 vertex.color = v_c, 
			 vertex.size = 35,
			 vertex.label = sp_names_fancy,
			 vertex.label.family = fam,
			 vertex.label.color = l_c,
			 edge.label = round(E(.)$weight,1), 
			 edge.label.family = fam,
			 edge.label.color = l_c,
			 edge.label.cex = l_s,
			 edge.curved = T,
			 edge.arrow.size = 0.5,
			 margin = ma)
text(label_pos_x, label_pos_y, "d)", adj = c(0,0))

i <- 1
bi_bi_net <- nets[[i]]$bi_net %>%
	digraph_bipartite(type = "z-bi")

		igraph::E(bi_bi_net)$matched <- 2
		igraph::E(bi_bi_net)$matched[nets[[i]]$as_all_mat] <- 4

		igraph::V(bi_bi_net)$matched <- 2
		igraph::V(bi_bi_net)$matched[igraph::V(bi_bi_net)$name %in%
																ends(bi_bi_net, nets[[i]]$as_all_mat)[, 1]] <- 4
		igraph::V(bi_bi_net)$matched[6:10] <- NA

		igraph::V(bi_bi_net)$superior <- 30
		igraph::V(bi_bi_net)$superior[igraph::V(bi_bi_net)$name %in%
																ends(bi_bi_net, nets[[i]]$as_all_mat)[, 2]] <- 40
		igraph::V(bi_bi_net)$superior[1:5] <- 35

		bi_names_fancy <- bi_sp_names_fancy
		bi_names_fancy[igraph::V(bi_bi_net)$name %in%
									ends(bi_bi_net, nets[[i]]$as_all_mat)[, 2]] <-
			bi_sp_names_fancy_b[igraph::V(bi_bi_net)$name %in%
														ends(bi_bi_net, nets[[i]]$as_all_mat)[, 2]]

bi_bi_net %>%
	plot(layout = matrix(c(rep(c(0.9,-0.5), each = 5), rep(seq(-0.8, 0.8, length.out = 5), 2)), ncol = 2), 
			 # vertex.size = igraph::V(.)$superior,
			 vertex.size = 30,
			 vertex.label = bi_sp_names_fancy, 
			 vertex.label.family = fam,
			 vertex.label.color = l_c,
			 # vertex.color = pal[igraph::V(.)$matched],
			 vertex.color = NA, 
			 edge.color = pal[igraph::E(.)$matched],
			 # edge.label = round(E(.)$weight,1), 
			 edge.label.family = fam,
			 edge.width = E(.)$matched/2,
			 edge.label.color = l_c,
			 edge.label.cex = l_s,
			 edge.curved = F,
			 edge.arrow.size = 0.5,
			 margin =  ma, 
			 # asp = 0.5, 
			 rescale = F)

text(-0.95, 0.825, "e)", adj = c(0,0))

nets[[1]]$bi_net %>%
	plot(layout = lay, 
			 vertex.label = nets[[1]]$names_fancy,
			 vertex.size = igraph::V(.)$superior * 10 + 20,
			 vertex.label.family = fam,
			 vertex.label.color = l_c,
			 vertex.color = pal[igraph::V(.)$matched],
			 edge.color = pal[igraph::E(.)$matched],
			 # edge.label = round(E(.)$weight,1), 
			 edge.label.family = fam,
			 edge.label.color = l_c,
			 edge.label.cex = l_s,
			 edge.curved = T,
			 edge.arrow.size = 0.5,
			 edge.width = E(.)$matched/2,
			 margin = ma, 
			 # asp = 0.5, 
			 rescale = T)

text(label_pos_x, label_pos_y, "f)", adj = c(0,0))

```

```{r fig-finding-all-matchings, echo = F, message = F, warning = F, fig.width = 6.2, fig.height = 1.6, results = "hide", fig.cap = "**Finding all possible maximum cardinality matchings**. "}
par(mfrow=c(1,3), mar= c(0,0,0,0))

as_mat <- as_net %>%
	digraph_bipartite() %>% 
	max_bipartite_match()

as_all_mat <- as_net %>%
	digraph_bipartite() %>%
	igraph::make_line_graph() %>%
	igraph::complementer() %>% 
	igraph::max_cliques(min = as_mat$matching_size) %>%
	rev()

text_pos_x <- 0.5
text_pos_y <- -0.7

base_as_net <- as_net
E(as_net)$weight <- round(E(as_net)$weight, 1)

bi_as_net <- as_net %>%
	digraph_bipartite()

igraph::V(bi_as_net)$matched <- 2
igraph::V(bi_as_net)$matched[igraph::V(bi_as_net)$name %in%
														 	ends(bi_as_net, as_all_mat[[1]])[, 2]] <- 4
igraph::V(bi_as_net)$matched[1:5] <- NA

igraph::V(bi_as_net)$superior <- 30
igraph::V(bi_as_net)$superior[igraph::V(bi_as_net)$name %in%
														 	ends(bi_as_net, as_all_mat[[1]])[, 1]] <- 40
igraph::V(bi_as_net)$superior[6:10] <- 35

igraph::E(bi_as_net)$matched <- 2
		igraph::E(bi_as_net)$matched[as_all_mat[[1]]] <- 4
# 																 
# bi_as_net %>%
# 	plot(layout = matrix(c(rep(c(-0.5, 0.9), each = 5), rep(seq(-0.8, 0.8, length.out = 5), 2)), ncol = 2), 
# 			 # vertex.size = igraph::V(.)$superior,
# 			 vertex.size = 30, 
# 			 vertex.label =  c(bi_sp_names_fancy[6:10], bi_sp_names_fancy[1:5]),
# 			 vertex.label.family = fam,
# 			 vertex.label.color = l_c,
# 			 # vertex.label.cex = igraph::V(.)$superior * 0.1 + 0.9,
# 			 # vertex.color = pal[igraph::V(.)$matched],
# 			 vertex.color = NA,
# 			 # edge.color = pal[E(.)$matched],
# 			 edge.label = NA, 
# 			 # edge.width = E(.)$matched/2,
# 			 edge.label.family = fam,
# 			 edge.label.color = igraph::E(.)$matched,
# 			 edge.label.cex = l_s,
# 			 edge.curved = F,
# 			 edge.arrow.size = 0.5,
# 			 margin = ma, 
# 			 rescale = F)
# 
# text(-0.95, 0.825, "a)", adj = c(0,0))

###

bi_as_net %>% 
	delete_vertices(c(1, 3, 7)) %>% 
	plot(vertex.size = 35, 
			 vertex.label = c(bi_sp_names_fancy[6:10], bi_sp_names_fancy[1:5])[-c(1,3,7)], 
			 vertex.color = "white", 
			 edge.label = 1:5,
			 vertex.label.family = fam,
			 vertex.label.color = l_c,
			 edge.label.family = fam,
			 edge.label.color = l_c,
			 edge.label.cex = l_s,
			 edge.curved = F,
			 edge.arrow.size = 0.5,
			 margin = ma, 
			 layout = layout_in_circle)

text(-1, 1, "a)", adj = c(0,0))

set.seed(2)
bi_as_net %>%
		igraph::make_line_graph() %>% 
	plot(vertex.size = 35, 
			 # vertex.label = c(bi_sp_names_fancy[6:10], bi_sp_names_fancy[1:5])[-c(1,3,7)], 
			 vertex.color = "white", 
			 # edge.label = 1:5,
			 vertex.label.family = fam,
			 vertex.label.color = l_c,
			 edge.label.family = fam,
			 edge.label.color = l_c,
			 edge.label.cex = l_s,
			 edge.curved = F,
			 edge.arrow.size = 0.5,
			 margin = ma, 
			 layout = layout_in_circle)

text(-1, 1, "b)", adj = c(0,0))

nam <- ends(bi_net, 1:length(igraph::E(bi_as_net)))

comp <- bi_as_net %>%
		igraph::make_line_graph() %>% 
		igraph::complementer()

colo <- c("#d7191c", "grey70", "#d7191c", "#2b83ba", "grey70", "#2b83ba", "#814E6B")
vertices <- layout_in_circle(comp)
plot.new()
scaling_x <- 0.94
scaling_y <- 0.58
centring_x <- -0.01
centring_y <- 0.2
# polygon((vertices[c(1,3,5), 1] + 1)/2 * scaling_x + centring_x, (vertices[c(1,3,5), 2] + 1) /2 *scaling_y +centring_y, col = "#d7191c")
par(new = T)
comp %>%
	plot(vertex.size = 35, 
			 # vertex.label = c(bi_sp_names_fancy[6:10], bi_sp_names_fancy[1:5])[-c(1,3,7)], 
			 vertex.color = NA, 
			 # edge.label = 1:5,
			 vertex.label.family = fam,
			 vertex.label.color = l_c,
			 edge.color = colo, 
			 edge.label.family = fam,
			 edge.label.color = l_c,
			 edge.label.cex = l_s,
			 edge.curved = F,
			 edge.arrow.size = 0.5,
			 margin = ma, 
			 layout = layout_in_circle)

text(-1, 1, "c)", adj = c(0,0))

# 
# igraph::max_cliques(min = matching$matching_size, 
# 												max = matching$matching_size,
# 												file = temporary_file)

```

```{r fig-matchings-bidirectional, echo = F, message = F, warning = F, fig.width = 6.2, fig.height = 3.2, results = "hide"}
par(mfrow=c(2,3), mar=c(0,0,0,0))

bi_net %>% 
	plot(layout = lay, 
			 vertex.color = v_c, 
			 vertex.size = 30,
			 vertex.label = sp_names_fancy,
			 vertex.label.family = fam,
			 vertex.label.color = l_c,
			 edge.label = round(E(.)$weight,1), 
			 edge.label.family = fam,
			 edge.label.color = l_c,
			 edge.label.cex = l_s,
			 edge.curved = T,
			 edge.arrow.size = 0.5,
			 margin = ma)

text(label_pos_x, label_pos_y, "a)", adj = c(0,0))

1:4 %>%
	plyr::l_ply(function(x, pal){

		attach(nets[[x]], pos = 1, warn.conflicts = F)

		nets[[x]]$bi_net %>% 
			plot(layout = lay, 
					 vertex.size = 30,
					 vertex.label = names_fancy,
					 vertex.label.family = fam,
					 vertex.label.color = l_c,
					 vertex.label.cex = igraph::V(.)$superior * 0.1 + 0.9,
					 # vertex.shape = igraph::V(.)$vertex.shape,
					 vertex.color = pal[igraph::V(.)$matched],
					 edge.color = pal[igraph::E(.)$matched],
					 # edge.color = c("#B2ABD2", "#FDB863"),
					 edge.label = NA, 
					 edge.width = E(.)$matched/2,
					 edge.label.family = fam,
					 edge.label.color = igraph::E(.)$matched,
					 edge.label.cex = l_s,
					 edge.curved = T,
					 edge.arrow.size = 0.5,
					 margin = ma, 
					 palette = pal) %>% 
			print()

		igraph::V(bi_net)$name <- sp_names

		text(label_pos_x, label_pos_y, paste0(letters[1+x], ")"), adj = c(0,0))
		text(text_pos_x, text_pos_y, cex = 0.95,
				 paste0("D = ", length(igraph::V(bi_net)) - as_mat$matching_size, "\n",
				 			 "matching size: ", as_mat$matching_size, "\n",
				 			 "matching weight: ", round(matching_weight, 1)))
	}, pal)

plot.new()
legend(0.5, 0.7, legend = c("unmatched link", "matched link"), horiz = F,
			 lty = 1, 
			 col = pal[c(2, 4)],
			 lwd = 2, cex = 0.9, xjust=0.5, yjust=1, bty = "n")

legend(0.5, 0.5, legend = c("unmatched node", "matched node"), horiz = F,
			 pch = 21, 
			 pt.bg = pal[c(2, 4)],
			 pt.cex = 2,
			 cex = 0.9, xjust=0.5, yjust=1, bty = "n")

legend(0.5, 0.3, legend = expression(paste(bold("(bold label)"), " ", "superior nodes")), horiz = TRUE,
			 cex = 0.9, xjust=0.5, yjust=1, bty = "n")

```

```{r  fig-matchings-bidirectional-no, echo = F, message = F, warning = F, fig.width = 6.2, fig.height = 4.8, results = "hide"}

par(mfrow=c(3,4), mar=c(0,0,0,0))
5:length(nets) %>%
	plyr::l_ply(function(x, pal){

		attach(nets[[x]], pos = 1, warn.conflicts = F)

		nets[[x]]$bi_net %>% 
			plot(layout = lay, 
					 vertex.size = 30,
					 vertex.label = names_fancy,
					 vertex.label.family = fam,
					 vertex.label.color = l_c,
					 vertex.label.cex = igraph::V(.)$superior * 0.1 + 0.9,
					 # vertex.shape = igraph::V(.)$vertex.shape,
					 vertex.color = pal[igraph::V(.)$matched],
					 edge.color = pal[igraph::E(.)$matched],
					 # edge.color = c("#B2ABD2", "#FDB863"),
					 edge.label = NA, 
					 edge.width = E(.)$matched/2,
					 edge.label.family = fam,
					 edge.label.color = igraph::E(.)$matched,
					 edge.label.cex = l_s,
					 edge.curved = T,
					 edge.arrow.size = 0.5,
					 margin = ma, 
					 palette = pal) %>% 
			print()

		igraph::V(bi_net)$name <- sp_names

		# text(label_pos_x, label_pos_y, paste0(letters[1+x-5], ")"), adj = c(0,0))
		# text(text_pos_x, text_pos_y, cex = 0.95,
		# 		 paste0("D = ", length(igraph::V(bi_net)) - as_mat$matching_size, "\n",
		# 		 			 "matching size: ", as_mat$matching_size, "\n",
		# 		 			 "matching weight: ", round(matching_weight, 1)))
	}, pal)

```

### 2017-01-24 paper/supp_info_2.Rmd
Paper with bidirectional links

@@
 - \usepackage{float}
-- \renewcommand{\figurename}{Figure SI}
+- \renewcommand{\figurename}{Supporting Figure}
 documentclass: artikel1
@@
 
-Each species can control at most one other species
+Our approach to find the minumum number of driver nodes relies on finding maximum matchings and maximum cardinality matchings.
+Most existing algorithms are designed to work with undirected bipartie networks, where finding the maximum matching is equivalent to finding the maximum flow between the two levels.
 
-```{r fig-direction-of-control, echo = F, message = F, warning = F, fig.width = 6.2, fig.height = 3.2, results = "hide", fig.cap = "**Finding a maximum matching in a complex network**.
-(a) We start with a directed network in which the direction of the link represents the direction of control.
-(b) Our strategy to find find the number of driver species is based on an alternative representation of the directed network in which each node in (a) is represented by two nodes that indicate their outgoing and incoming links.
+We start with a directed network in which the direction of the link represents the direction of control (Supporting figure 1a).
+We then construct an alternative representation of the directed network in which each node of the directed network is represented by two nodes that indicate their outgoing and incoming links (Supporting figure 1b).
 Finding a maximum matching in this alternative representation is equivalent to finding the largest possible set of edges in which one node in the left hand side is connected to at most one node in the right hand side.
-It is then easy to identify the roles of each node in this representation: nodes on the right hand side that are connected to a matched link (purple) are matched, while those connected to a matched link on the left hand side are superior.
-(c) This information can then be mapped back to the original representation to identify the control paths and the driver nodes in the network.
-(d, e, and f) Ilustrate the approach for a network with bidirectional links."}
+To find the maximum matching we use the push-relabel algorithm implemented in `max_bipartite_matching` in the R package igraph 1.0.1 [@Csardi2006a].
+Once we have the matching shown in the Supporting Figure 1b, it is then easy to identify the roles of each node in this representation: nodes on the right hand side that are connected to a matched link (purple) are matched, while those connected to a matched link on the left hand side are superior.
+This information can then be mapped back to the original representation to identify the control paths and the driver nodes in the network (Supporting Figure 1c).
+Supporting Figure 1d, e, and f ilustrate this approach for a network with bidirectional links.
+
+```{r fig-direction-of-control, echo = F, message = F, warning = F, fig.width = 6.2, fig.height = 3.4, results = "hide", fig.cap = "**Finding a maximum matching in a complex network**.
+(a & d) Directed networks that indicate the direction of control between species.
+(b & e) Alternative bipartite representations of the directed networks.
+(c & f) The matchings in the bipartite representation mapped back to the original network."}
 # par(mfrow=c(2,2), mar=c(0,0,0,0))
@@
 
-par(mfrow=c(2,3), mar= c(0,0,0,0))
-
+# par(mfrow=c(2,3), mar= c(0,0,0,0))
+layout(matrix(c(1,2,3,4, 5, 6, 7, 7, 7), 3, 3, byrow = TRUE),
+  	heights=c(8,8,1))
+par( mar=c(0,0,0,0))
 # ASYMMETRY
@@
 
+## LEGEND 
+plot.new()
+legend(0.16, 0.9, legend = c("unmatched link", "matched link"), horiz = TRUE,
+			 lty = 1, 
+			 col = pal[c(2, 4)],
+			 lwd = 2, cex = 0.9, xjust=0.5, yjust=0.8, bty = "n")
+
+legend(0.57, 0.9, legend = c("unmatched node", "matched node"), horiz = TRUE,
+			 pch = 21, 
+			 pt.bg = pal[c(2, 4)],
+			 pt.cex = 2,
+			 cex = 0.9, xjust=0.5, yjust=0.8, bty = "n")
+
+legend(1-0.16 + 0.05, 0.9, legend = expression(paste(bold("  superior node"))), horiz = TRUE,
+			 pch = 21, 
+			 # pt.bg = pal[c(2, 4)],
+			 pt.cex = c(3),
+			 cex = 0.9, xjust=0.5, yjust=0.8, bty = "n")
 ```
 
-```{r fig-finding-all-matchings, echo = F, message = F, warning = F, fig.width = 6.2, fig.height = 1.6, results = "hide", fig.cap = "**Finding all possible maximum cardinality matchings**. "}
-par(mfrow=c(1,3), mar= c(0,0,0,0))
+The algorithm implemented in `max_bipartite_matching`, however, is only able to find **one** of the, possibly many, maximum matchings in a network.
+One maximum matching is sufficient to calculate *n~D~* and hence to provide indication of a communitie's manageability, however it is not possible to estimate the role of individual species.
+To do that we need to calculate all possible maximum matchings (or all maximal cardinality matchings in weighted networks like ours).
+We start from the alternative bipartite representation in Supporting Figure 1b and assign an identity to each of the links in the network (shown as numbers in Supporting Figure 2a).
+We will call this bipartite representation *B*.
+We then construct the line graph of the alternative bipartite representation *L(B)* (Supporting Figure 2b).
+Each node in *L(B)* represents a link in *B* and are connected to each other only if they share a common node in *B*.
+We calculate the complement graph of *L(B)* and idetify all the maximum cliques (Supporting Figure 2c).
+Here some extra definitions are neccessary.
+First, the complement of *L(B)*, *H*, is a graph with the same nodes as *L(B)* but that has a link between two given nodes if and only if there is not a link in *L(B)*.
+Second, a clique is a subset of nodes such that any two of them are linked.
+Lastly, a maximum clique is a clique such that there are no cliques with more nodes.
+In this example there are two maximum cliques: that one formed by 1, 3 and 5, and by 2, 3 and 5.
+The final step is then to map these cliques into the original network to obtain all possible maximum cardinality matchings as shown in Figure 1 in the main text.
+
+```{r fig-finding-all-matchings, echo = F, message = F, warning = F, fig.width = 6.2, fig.height = 1.8, results = "hide", fig.cap = "**Finding all possible maximum cardinality matchings**.
+(a) Alternative bipartite representation of a directed network.
+(b) Line graph of the network in a.
+(c) Complement of the network in b.
+The two maximum cliques are shown in red and blue."}
+layout(matrix(c(1,2,3,4, 5, 6), 2, 3, byrow = TRUE),
+  	heights=c(8,1))
+par( mar=c(0,0,0,0))
 
@@
 # 												file = temporary_file)
+## Legends
 
+plot.new()
+text(0.5, 0.5, expression(paste(italic(B), ": bipartite representation")), adj = c(0.5,0.75))
+
+plot.new()
+text(0.5, 0.5, expression(paste(italic(L(B)), ": line graph of ", italic(B))), adj = c(0.5,0.75))
+
+plot.new()
+text(0.5, 0.5, expression(paste(italic(H), ": complement of ", italic(L(B)))) , adj = c(0.5,0.75))
 ```
 
-```{r fig-matchings-bidirectional, echo = F, message = F, warning = F, fig.width = 6.2, fig.height = 3.2, results = "hide"}
+In the main text we show all maximum cardinality matchings for a example network in which the direction of control is based on the dependence asymmetries (Figure 1).
+For completeness, here we show all the maximum cardinality matchings for an example network in which the links are bidirectional (Supporting Figure 3).
+
+Empirical network example here.
+
+It is important to note that our approach to find all the maximum matchings, which is based on the alternative bipartite representation of the directed network and a series of network transofrmations, has an important disadvantage.
+Namely, that it is possible tha cycles in network figure 4
+
+```{r fig-matchings-bidirectional, echo = F, message = F, warning = F, fig.width = 6.2, fig.height = 3.2, results = "hide", fig.cap = "SAD"}
 par(mfrow=c(2,3), mar=c(0,0,0,0))
@@
 
-```{r  fig-matchings-bidirectional-no, echo = F, message = F, warning = F, fig.width = 6.2, fig.height = 4.8, results = "hide"}
+```{r  fig-matchings-bidirectional-no, echo = F, message = F, warning = F, fig.width = 6.2, fig.height = 4.8, results = "hide", fig.cap= "asd asd"}
 
@@
 ```
+
+# References

### 2017-01-25 paper/draft_2.Rmd
Paper with bidirectional links
Script to calculate asymmetry matchings on the cluster

@@
 
-Despite these advances, practical challenges to the conservation of interaction networks persist [@Tylianakis2010], and the link between the structure of complex networks and our ability to manage and conserve them is still ambiguous [@Kaiser-Bunbury2015].
+Despite these advances, practical challenges to the conservation of interaction networks persist [@Tylianakis2010], and the link between the structure of complex networks and our ability to manage and conserve them is still ambiguous [@Bluthgen2010; @Kaiser-Bunbury2015].
 To complicate things further, biotic invasions—a major driver of global change—can induce dramatic changes in the patterns of interactions that determine the structure of ecological networks [@Baxter2004; @Tylianakis2008; @Ehrenfeld2010a].
 Although understanding how differences in network structure before and after the invasion impact our ability to manage them presents a double challenge, it is a critical first step towards a fully informed recovery.
-Despite the apparent overlap, a control-theoretic perspective has not been widely adopted in an invasion context. 
+Despite the apparent overlap, a control-theoretic perspective has not been adopted in an invasion context. 
 This is perhaps because of a lack of appropriate methodological tools that can account for the observed variation in the strength of interspecific effects that are characteristic of ecological networks [@Liu2011; @Isbell2013].
@@
 To bridge this gap, we outline an approach to apply theory on the control of complex systems in an ecological context and implement them using empirical data.
-Furthermore, we introduce methods with which to take into account the important quantitative differences that exist among species interactions.
 Specifically, we use a set of ten pairs of uninvaded and invaded plant-pollinator communities to investigate the link between invasion, network structure and ecological management. 
 While doing so, we ask two questions framed in the context of a plant invasion.
-First, on grounded on the difficulties usually involved with invasive species erradication and ecosystem restoration [@Woodford2016], we ask whether invaded networks have lower levels of "manageability" than their uninvaded counterparts; that is, whether they require a greater proportion of species to be managed to achieve the same level of control.
+First, grounded on the difficulties usually involved with invasive species erradication and ecosystem restoration [@Woodford2016], we ask whether invaded networks have lower levels of "manageability" than their uninvaded counterparts; that is, whether they require a greater proportion of species to be managed to achieve the same level of control.
 Second, we ask whether some species are more important than others at driving the population dynamics of the community and which factors determine this importance. 
@@
 Disregarding practical considerations, any network could, in theory, be fully controlled if we control the state of every single node individually.
-At the core of control theory of complex networks, however, rest the idea the state of a node depends on the state of the nodes it interacts with, and the particular form of this dependence is determined both by the dynamic relationship among interacting nodes as well as the structure of the links in the network.
-This property can, therefore, be harnessed to find a minimum subset of driver nodes *D* to which to apply external input signals which then drive the state of every other node in the network to a desired configuration in finite time [@Kalman1963; @Liu2011].
+At the core of control theory of complex networks, however, rests the idea that the state of a node depends on the state of the nodes it interacts with, and the particular form of this dependence is determined both by the dynamic relationship among interacting nodes as well as the structure of the links in the network.
+This principle can, therefore, be harnessed to find a subset of driver nodes to which to apply external input signals which then drive the state of every other node in the network to a desired configuration.
 
-Conveniently, the information necessary to determine whether a network with linear dynamics is controllable, and the minimum number of driver nodes *D* is fully contained in the network structure [@Liu2011; @Motter2015].
+Conveniently, the information necessary to determine whether a network with linear dynamics is controllable, and, equivalently, the minimum number of driver nodes *D* is fully contained in the network structure [@Kalman1963; @Liu2011; @Motter2015].
 We, therefore, start from the assumption that that an ecological network can, at least near equilibrium points, be described by $\frac{dx}{dt} = Ax + Bu(t)$, where the change over time of its state ($\frac{dx}{dt}$) depends on its current state *x* (the species' populations in an ecological context), an external time-varying input *u(t)*, and the matrices *A* and *B*, which encapsulate information about the network structure and how the network responds to the external input, respectively.
-Even though this might be a strong assumption, it has been shown that fundamental insight about the control of complex systems can be gained without a detailed knowledge of the nonlinear dynamics and the system parameters [@Liu2015]; an important step towards understanding the controllability of systems with nonlinear dynamics [@Liu2011].
-This means that this structural controllability can be applied to a wide range of readily available network representations of ecological communities to provide a strong indication of our ability to control them.
-Moreover, we show here how quantitative data about species interactions can help us move past some of the limitations of structural controllability by better approximating the role of dynamical relationships without being overly dependent on the specific choices of how these dynamics are modelled or characterised.
+Even though linearity might be a strong assumption, it has been shown that fundamental insight about the control of complex systems can be gained without a detailed knowledge of the nonlinear dynamics and the system parameters [@Liu2015], an important step towards ultimately understanding the controllability of systems with nonlinear dynamics [@Liu2011].
+This means that structural controllability can be applied to a wide range of readily available network representations of ecological communities to provide a strong indication of our ability to control them.
+Moreover, we show here how quantitative data about species interactions can help us move past some of the limitations of structural controllability by better approximating the role of interspecific dynamical relationships without being overly dependent on the specific choices of how these dynamics are modelled or characterised.
 
@@
 It has been recently shown that calculating *D* is equivalent to finding a maximum matching in the network [@Liu2011].
-In a directed network, a *matching* consists of a subset of links in which o two of them share a common starting or ending node (Figure 1).
+In a directed network, a *matching* consists of a subset of links in which no two of them share a common starting or ending node (Figure 1).
 A given matching has *maximal cardinality* if the number of matched links (also referred to as the *matching size*) is the largest possible.
@@
 Out of the two maximal cardinality matchings only one (c) has maximum weight and therefore is also a maximum matching.
-Further examples can be found in the Supplemental Material SXX."}
+Further examples can be found in the Supporting Information S1."}
 layout(matrix(c(1,2,3,4, 4, 4), 2, 3, byrow = TRUE),
@@
 
-While calculating *n~D~* provides an indication of the manageability of an ecological community, it does not provide information about the identity of the species that compose this set. 
-This difference is rather important since maximum matchings are often not unique in a given network and different sets of species of size *D* could potentially be used to control the network [@Liu2011].
+While calculating *n~D~* provides an indication of the manageability of an ecological community, it does not provide information about the identity of the species that compose the set of driver nodes.
 Ecologically, these distinctions are acutely relevant because management and conservation resources are limited, and therefore ecological interventions should ideally be focused on the set of species that might provide the largest impact.
-Consequently, species can be further characterised regarding the frequency with which an external input signal could be applied to them in order to control the full network. 
-In other words, the frequency *f~D~* with which a species is classified as a driver node.
-However, the role of driver nodes is still ambiguous when full network controllability is unfeasible or undesired—often the case in ecological settings.
-Alternatively, species can also be characterised by the frequency *f~S~* with which they are classified as superior nodes.
-This is, the frequency with which they exist on key paths through the network that transmits the control signal to other species.
-We show how, together, *f~D~* and *f~S~* can provide an indication of a species' relative importance in driving the state of the community.
+Maximum matchings in a network are often not unique, and each different maximum matching indicates a unique path that can potentially be used to control the network. 
+We harness this property and use a network's multiple maximum matchings to characterise a species' relative importance in driving the state of the community. 
+One possibility is to characterise a species by the frequency *f~D~* with which it is classified as a driver node.
+However, the role of driver nodes is still ambiguous when **full** network controllability is unfeasible or undesired—which is often the case in ecological settings.
+We therefore also calculate the frequency *f~S~* with which a species is classified as superior nodes, this is the frequency with which they are part of possible control paths—intervention strategies from a management perspective.
 
@@
 However, it has been shown that using weighted links can reveal significant ecological patterns and processes that might be undetectable in unweighted networks [@Scotti2007; @Tylianakis2007; @Vazquez2007; @Kaiser-Bunbury2010a].
-We, therefore, use a quantitative version of the maximum matching algorithm and instead calculate all maximal cardinality matchings and rank them by their matching weight. 
-We do so because empirical interaction strengths are to some extent stochastic and depend on proximate factors such as sampling method and intensity [@Gibson2011], and therefore using only maximum matchings in weighted empirical networks might be therefore too restrictive.
-By incorporating the interaction weight we give priority to the species that participate in the pathways that potentially have the largest impact on the community; effectively incorporating, at least partially, the dynamics of the system.
+For example, a species *A* interacts with both species *B* and *C* but depends strongly on *B* and only weakly on *C*. 
+Intuitively, a management intervention designed to indirectly modify the abundance of a species *A* is more likely to succeed if the abundance of *B*, rather than *C*, is directly controlled.
+A complication of including the interaction weight when calculating the maximum matching, however, is that empirical interaction strengths are to some extent stochastic and depend on proximate factors such as sampling method and intensity [@Gibson2011].
+We circumvent this issue by calculating all maximal cardinality matchings and subsequently ranking them by their matching weight. 
+By following this approach, we effectively give priority to the species that participate in the pathways that potentially have the largest impact on the community while acknowledging the limitations associated with sampling and its potential restrictions.
 
@@
 The other six pairs were obtained from lower diversity Mediterranean shrublands in Cap de Creus National Park, Spain [@Bartomeus2008].
-These networks are comprised of `r bar[1]`-`r bar[6]` species (mean `r round(bar[4])`); in contrast to the above, contrastingly, uninvaded communities were obtained from plots that had not yet been colonised by either of the invasive species *Carpobrotus affine acinaciformis* or *Opuntia stricta*.
-Further details about the empirical networks can be found in the Supplementary Information XXX.
+These networks are comprised of `r bar[1]`-`r bar[6]` species (mean `r round(bar[4])`); in contrast to the above, uninvaded communities were obtained from plots that had not yet been colonised by either of the invasive species *Carpobrotus affine acinaciformis* or *Opuntia stricta*.
+Further details about the empirical networks can be found in the Supporting Information Table 1.
 

### 2017-01-25 paper/supp_info_2.Rmd
Script to calculate asymmetry matchings on the cluster

@@
     fig_crop: no
+    keep_tex: yes
   html_document: default
@@
 - \usepackage{float}
+- \usepackage{rotating}
 - \renewcommand{\figurename}{Supporting Figure}
+- \renewcommand{\tablename}{Supporting Table}
 documentclass: artikel1
 bibliography: references.bib
+nocite: | 
+  @Lopezaraiza-Mikel2007, @Bartomeus2008
 ---
@@
 	plyr::l_ply(source)
+
+mutate_cond <- function(.data, condition, ..., envir = parent.frame()) {
+  condition <- eval(substitute(condition), .data, envir)
+  .data[condition, ] <- .data[condition, ] %>% dplyr::mutate(...)
+  .data
+}
 
@@
   read_allRDS()
+
+n_matched <- readRDS("../data/processed/n_matched.rds")
+
 ```
@@
 fer_theme <- theme_bw() +
-	theme(text = element_text(family = "Times"),
-	      title = element_text(size = 7.5, hjust = 0),
-	      legend.title = element_text(size = 9),
-	      legend.text = element_text(size = 8),
-				axis.text = element_text(size = 8),
-				axis.title = element_text(size = 9, hjust = 0.5), 
-				strip.text = element_text(size = 9, hjust = 0), 
+	theme(text = element_text(family = "Helvetica"),
+	      title = element_text(size = 7, hjust = 0),
+	      legend.title = element_text(size = 8),
+	      legend.text = element_text(size = 7),
+				axis.text = element_text(size = 7),
+				axis.title = element_text(size = 8, hjust = 0.5), 
+				strip.text = element_text(size = 8, hjust = 0), 
 				strip.background = element_blank(),
@@
 
-In the main text we show all maximum cardinality matchings for a example network in which the direction of control is based on the dependence asymmetries (Figure 1).
-For completeness, here we show all the maximum cardinality matchings for an example network in which the links are bidirectional (Supporting Figure 3).
+In the main text we show all maximum cardinality matchings for a simple example network.
+To further ilustrate our methodology, here we also show the approach for the smallest of our empirical networks, the uninvaded network at site 10 (Supporting Table 1; Supporting Figure 3).
+The largest component of this network is composed by 16 species of which 2 are non-invasive plants and the rest are pollinators.
+The one-to-one relationship between matched and superior nodes implies that in order to achieve full network controllability, most pollinators would be unmatched, and hence driver species that require external intervention.
+At the same time, both plants in the community, *Heracleum sphpndylum* and *Rubus fructicosus* and one of the pollinators *Orthotylus/Lygocorus* tend to be classified as superior nodes.
 
-Empirical network example here.
+```{r fig-SA_exp, echo = F, message = F, warning = F, fig.width = 6.2, fig.height = 6.2, results = "hide", fig.cap = "**Illustration of the procedure with one empirical network**.
+(a) The initial visitation network.
+(b) The directed network in which the direction of control and the magnitude of the asymmetry are determined based on the mutual dependences.
+(c) One of the possible maximum matchings calculated using the procedures illustrated in the Supporting Figure 1 and 2."}
+par(mfrow=c(2,2), mar=c(0,0,0,0))
+n <- keep_largest_component(net$SA_exp)
+replace_names <- data.frame(sp_name = igraph::V(n)$name) %>%
+	dplyr::mutate(sp_number = 1:nrow(.),
+								sp_letter = letters[sp_number], 
+								sp_name = stringr::str_replace(sp_name, "[0-9]", ""),
+								sp_name = stringr::str_replace(sp_name, "\\?rutitarse", "rufitarse"))
+set.seed(7)
+
+la <- igraph::layout_nicely(n)
+n %>%
+	plot(vertex.color = v_c, 
+			 vertex.size = 15,
+			 vertex.label = replace_names$sp_letter,
+			 vertex.label.family = fam,
+			 vertex.label.color = l_c,
+			 vertex.label.cex = 0.9,
+			 edge.label = round(igraph::E(.)$weight,1), 
+			 edge.label.family = fam,
+			 edge.label.color = l_c,
+			 edge.label.cex = l_s*0.8,
+			 edge.curved = F,
+			 edge.arrow.size = 0.5,
+			 margin = ma, 
+			 layout = la)
+text(label_pos_x, label_pos_y, paste0(letters[1], ")"), adj = c(0,0))
+
+as_net <- n %>%
+	bipartite_digraph(type = "weight", keep = "all", weight.type = "asymmetry", scale = F)
+
+as_net %>%	
+	plot(vertex.color = v_c, 
+			 vertex.size = 15,
+			 vertex.label = replace_names$sp_letter,
+			 vertex.label.family = fam,
+			 vertex.label.color = l_c,
+			 vertex.label.cex = 0.9,
+			 edge.label = round(igraph::E(.)$weight,2), 
+			 edge.label.family = fam,
+			 edge.label.color = l_c,
+			 edge.label.cex = l_s*0.8,
+			 edge.curved = F,
+			 edge.arrow.size = 0.5,
+			 margin = ma, 
+			 layout = la)
+
+text(label_pos_x, label_pos_y, paste0(letters[2], ")"), adj = c(0,0))
+
+as_mat <- as_net %>%
+	digraph_bipartite() %>% 
+	max_bipartite_match()
+
+as_all_mat <- as_net %>%
+	digraph_bipartite() %>%
+	igraph::make_line_graph() %>%
+	igraph::complementer() %>% 
+	igraph::max_cliques(min = as_mat$matching_size) %>%
+	rev()
+
+text_pos_x <- 0.5
+text_pos_y <- -0.7
+
+base_as_net <- n
+# E(as_net)$weight <- round(E(as_net)$weight, 1)
+
+or <- as_all_mat %>%
+	plyr::laply(function(x){
+		sum(E(as_net)$weight[x])
+	}) %>% order(decreasing = T)
+
+as_all_mat <- as_all_mat[or]
+
+1 %>%
+	plyr::l_ply(function(x){
+
+		E(as_net)$matched <- 2
+		E(as_net)$matched[as_all_mat[[x]]] <- 4
+
+		igraph::V(as_net)$matched <- 2
+		igraph::V(as_net)$matched[igraph::V(as_net)$name %in%
+																ends(as_net, as_all_mat[[x]])[, 2]] <- 4
+
+		igraph::V(as_net)$superior <- 1
+		igraph::V(as_net)$superior[igraph::V(as_net)$name %in%
+																ends(as_net, as_all_mat[[x]])[, 1]] <- 2
+
+		# names_fancy <- sp_names_fancy
+		# names_fancy[igraph::V(as_net)$name %in%
+		# 														ends(as_net, as_all_mat[[x]])[, 1]] <-
+		# 	sp_names_fancy_b[igraph::V(as_net)$name %in%
+		# 														ends(as_net, as_all_mat[[x]])[, 1]]
+		# 
+		matching_weight <- sum(E(as_net)$weight[as_all_mat[[x]]])
+
+		as_net %>% 
+			plot(layout = la, 
+					 vertex.size = igraph::V(.)$superior * 7 + 7,
+					 vertex.label = replace_names$sp_letter,
+					 vertex.label.family = fam,
+					 vertex.label.color = l_c,
+					 vertex.label.font = igraph::V(.)$superior,
+					 vertex.label.cex = igraph::V(.)$superior * 0.1 + 0.9,
+					 # vertex.shape = igraph::V(.)$vertex.shape,
+					 vertex.color = pal[igraph::V(.)$matched],
+					 edge.color = pal[E(.)$matched],
+					 edge.label = NA, 
+					 edge.width = E(.)$matched/2,
+					 edge.label.family = fam,
+					 edge.label.color = igraph::E(.)$matched,
+					 edge.label.cex = l_s,
+					 edge.curved = F,
+					 edge.arrow.size = 0.5,
+					 margin = ma) %>% 
+			print()
+
+		igraph::V(as_net)$name <- sp_names
+
+		text(label_pos_x, label_pos_y, paste0(letters[2+x], ")"), adj = c(0,0))
+		text(text_pos_x + 0.2, text_pos_y + 0.1, cex = 0.95,
+				 paste0("D = ", length(igraph::V(as_net)) - as_mat$matching_size, "\n",
+				 			 "matching size: ", as_mat$matching_size, "\n",
+				 			 "matching weight: ", round(matching_weight, 1)))
+})
+
+plot.new()
+
+legend(0.28, 0.95, legend = replace_names$sp_name, horiz = F, bty = "n", text.font = 3, cex = 0.9)
+legend(0.2, 0.95, legend = replace_names$sp_letter, horiz = F, bty = "n", text.font = 2, cex = 0.9)
+
+# library(grid)
+# library(gridExtra)
+# 
+# ttt <- tableGrob(replace_names) 
+# grid.newpage()
+# grid.draw(ttt)
+
+```
+
+In addition, here we also show all the maximum cardinality matchings for an example network in which the links are bidirectional (Supporting Figure 4).
+It is important to note that using bidirectional is problematic for a couple
 
@@
 
+# S2: Properties of empirical networks
+
+```{r calc-network-properties, echo = F, message = F}
+net_prop <- net %>%
+	plyr::ldply(function(x){
+		x <- keep_largest_component(x)
+		bipartite::networklevel(igraph::as_incidence_matrix(x, 
+																												types = igraph::V(x)$type == "pla",
+																												attr = "weight"),
+														index = c("connectance", "web asymmetry", 
+																			"ISA", 
+																			"weighted NODF")) %>%
+			as.list() %>% as.data.frame() %>%
+			dplyr::mutate(n_sp = length(igraph::V(x)),
+										n_pla = sum(igraph::V(x)$type == "pla"),
+										n_pol = sum(igraph::V(x)$type == "pol"))
+	})
+
+library(xtable)
+
+names(net_prop)[1] <- "net_name"
+
+net_prop <- meta %>%
+	dplyr::mutate(n_s_t = n_pla + n_pol) %>%
+	dplyr::select(-n_pla, -n_pol) %>%
+	dplyr::inner_join(net_prop)
+
+```
+
+The studied networks had species richess ranging between `r min(net_prop$n_s_t)` and `r max(net_prop$n_s_t)` (`r min(net_prop$n_sp)`-`r max(net_prop$n_sp)` when considering only the largest component in each network).
+As evidenced by the overall network asymmetry *AS* [@Bluthgen2007] networks had a low ratio of plants to pollinators.
+Furthermore, networks had relatively low levels of nestedness [when measured using the quantitative version of the NODF index; @Almeida-Neto2011].
+Details for each network can be found in Supporting Table 1.
+
+```{r table-network-properties, results = "asis", echo = F, message = F, warning = F, fig.width = 6.2, fig.height = 4.8, sanitize = FALSE}
+
+net_prop %>%
+	dplyr::select(-net_name, -count, -net) %>%
+	dplyr::filter(study != "ballantyne") %>%
+	dplyr::arrange(study, site, inv) %>%
+	mutate_cond(inv == FALSE, invader = "—") %>%
+  dplyr::mutate(site = rep(1:dplyr::n_distinct(site), each = 2),
+                inv = plyr::mapvalues(inv, c(TRUE, FALSE), c("yes", "no")),
+                study = plyr::mapvalues(study, 
+                                        c("bartomeus", "lopezaraiza"),
+                                        c("Cap de Creus, Spain",
+                                          "Bristol, United Kingdom"))) %>%
+	dplyr::select(site, invader, n_s_t, n_sp, n_pla, n_pol, connectance, web.asymmetry, weighted.NODF, study) %>%
+	dplyr::rename_("$R$" = "n_s_t",
+								 "$n_p$" = "n_pla",
+								 "$n_a$" = "n_pol",
+								 "location" = "study",
+								 "$n_s$" = "n_sp",
+								 "$c$"= "connectance", 
+								 "NODF" = "weighted.NODF",
+								 # "$\\bar{a}$" = "interaction.strength.asymmetry",
+								 "$AS$" = "web.asymmetry") %>%
+	xtable::xtable(caption = "\\textbf{Properties of the analysed plant-pollinator communities}.
+Invasive plants were \\textit{Carpobrotus affine acinaciformis} (car), \\textit{Opuntia stricta} (op), and \\textit{Impatients grandulifera} (imp).
+All properties, with the exception of the networks' total species richness ($R$), correspond to the network's largest component.
+Specifically we show the number of species ($n_s$), the number of plants ($n_p$), the number of pollinators ($n_a$), the network connectance ($c$), the network assymetry ($AS$), and the network nestedness (NODF index).
+British networks were assembled by Lopezaraiza-Mikel et al.
+(2007), Spanish were networks assembled by Bartomeus et al.
+(2008).") %>%
+	print(#floating.environment = "sidewaystable", 
+		comment = FALSE, sanitize.text.function = function(x){x}, include.rownames = FALSE)
+
+# knitr::kable(meta)
+```
+
+# S3: Visitation as a proxy for species interdependence
+
+Visitation frequency has been shown to be an appropriate surrogate for inter-specific effects in pollination networks [@Vazquez2005; @Bascompte2006]. 
+Nevertheless visitation is not equivalent to pollen deposition and might be insufficient to reflect the dependencies of plants on animals and vice versa [@Alarcon2010; @King2013]. 
+We therefore investigated the effect of calculating the dependencies using visitation or pollination effectiveness and importance---two metrics more proximate to plant reproductive success (Supporting Figure 6).
+We did this by comparing *(i)* the manageability of the community and *(ii)* the percentage of interactions that maintained the direction of dependency. 
+To do that, we used data collected by @Ballantyne2015 from a low diversity pollination community at a dry lowland heathland in Dorset, UK  (50° 43.7'N 2° 07.2'W). 
+First, deposition networks were quantified using the mean Single Visit Deposition---the number of conspecific pollen grains effectively deposited on a virgin stigma during a single visit by a particular animal [@NeEman2010; @King2013; @Ballantyne2015].
+Second, visitation networks were constructed counting the visits to flowers during Single Visit Depositions. 
+Finally, pollinator importance networks were constructed as the product of pollinator efficiency and visit frequency.
+
+```{r fig-visitation-vs-deposition-vs-importance, echo = F, message = F, warning = F, fig.width = 6.2, fig.height = 4, results = "hide", fig.cap= "**Distribution of interaction weights for the pollen deposition, visitation and pollinator importance networks**.
+Note that the *x* axis in the density plots have been log-transformed."}
+n_driver <- meta %>%
+  dplyr::inner_join(n_matched) %>% 
+  dplyr::mutate(n_driver = 1 - n_matched / (n_pla + n_pol))
+
+p <- net[meta$net_name[meta$study == "ballantyne" & meta$count != "binary"]] %>%
+	plyr::ldply(function(x) {
+		data.frame(vname = igraph::E(x) %>% attr("vnames"), 
+							weight = igraph::E(x)$weight)
+	}, .inform = T) %>%
+	dplyr::rename_("net_name" = ".id") %>%
+	dplyr::mutate(net_name_f = factor(net_name,  
+																		levels = c( 'bal_eff','bal_vis','bal_imp'),
+																		labels = c("a) Deposition", "b) Visitation", "c) Importance")), 
+	              pla = stringr::str_split_fixed(vname, "\\|", 2)[, 1],
+	              pol = stringr::str_split_fixed(vname, "\\|", 2)[, 2]) %>%
+  plyr::dlply("net_name_f", function(x){
+    p1 <- x %>%
+      ggplot(aes(x = pol, y = pla)) +
+      geom_tile(aes(fill = weight, width = 0.9, height = 0.9)) + 
+      coord_fixed() +
+      scale_fill_gradient(low = "#f0f0f0", high = "#525252") +
+      ylab("plants") +
+      xlab("pollinators") + 
+      fer_theme +
+      theme(axis.text = element_blank(), 
+            axis.ticks = element_blank(), 
+            legend.position = "right", 
+            legend.title = element_blank(), 
+            plot.margin = grid::unit(c(6,0,2,5), "mm"),
+            panel.grid = element_blank(),
+            legend.key.width = grid::unit(4, "mm"),
+            legend.key.height = grid::unit(4, "mm"))
+    p2 <- x %>% ggplot(aes(x = weight)) +
+      scale_x_log10() +
+      stat_density(aes(y =..density..), geom = "line") +
+      xlab("link weight") + 
+      ylab("density") +
+      ggtitle(x$net_name_f[1]) +
+      fer_theme +
+      theme(plot.margin = grid::unit(c(2,2,0,0), "mm"))
+    list(p1, p2)
+  })
+
+cowplot::plot_grid(p[[1]][[2]], p[[1]][[1]], p[[2]][[2]], p[[2]][[1]], p[[3]][[2]], p[[3]][[1]], ncol = 2, rel_widths = c(1.5,2))  
+```
+
+We first investigated the effects at a network scale. 
+Despite marked differences in the distribution of weights of the three networks, the minimum number of driver species to control the whole community was consistent among the three different approaches (`r 1-round(n_driver$n_driver[n_driver$net_name == "bal_eff"], digits = 2)` for deposition, `r 1-round(n_driver$n_driver[n_driver$net_name == "bal_vis"], digits = 2)` for the visitation, and `r 1-round(n_driver$n_driver[n_driver$net_name == "bal_imp"], digits = 2)` for the pollinator importance network).
+
+The choice of weighting used can also have an impact on the relative importance of species.
+Therefore we calculated the frequency that each species is present in the possible sets of driver species under the three schemes. 
+Although visitation and deposition produce strikingly different results, we found a very strong agreement between the order produced by visitation and importance (Supporting Table 2). 
+Finally, we investigated whether the asymmetry of mutual dependency, which defines the direction of control, was consistent among the three possible weighting schemes.
+We found again that the direction of the dominant dependency was maintained was consistent for 95\% of the interactions weighted by visitation or importance, the two most appropriate metrics for pollinator and plant dependency (Supporting Table 2).
+
+```{r table-correlations-visitation-vs-efficiency, echo = FALSE, warning = F, message = F, results = "asis"}
+d_sp <- driver %>%
+  plyr::ldply(function(x) {
+    get_frequencies(x) %>%
+      dplyr::mutate(type = attr(x, "type"),
+                    scaled = attr(x, "scaled"))
+  }) %>%
+  dplyr::inner_join(meta)
+
+correlations <- d_sp %>%
+	dplyr::filter(study == "ballantyne",
+								threshold == 0.5,
+								type == "asymmetry",
+								scaled == F) %>%
+	dplyr::group_by(net_name, threshold, type, scaled) %>%
+	dplyr::mutate(d_weight = d_weight/max(d_weight),
+								d_rank = rank(-d_weight, ties.method = "average")) %>%
+	dplyr::group_by() %>%
+	dplyr::select(net_name, species, d_rank) %>%
+	tidyr::spread(net_name, d_rank) %>%
+  dplyr::select(-species) %>%
+  as.matrix() %>%
+  Hmisc::rcorr(type = "spearman")
+
+my_paste <- function(x, y){
+  if(is.na(y)) return ("-")
+  b <- ""
+  if(y < 0.05) b <- ""
+  paste0(b, round(x, digits = 2), " (", fix_small_pvalue(y, 3), ")", b)
+}
+
+dir_net_b <- net[meta$net_name[meta$study == "ballantyne"]] %>%
+  lapply(function(x){
+    x %>% 
+      bipartite_digraph(type = "weight", keep = "all", weight.type = "asymmetry") %>%
+      igraph::ends(igraph::E(.)) %>% 
+      apply(1, function(y) paste(y[1], y[2]))
+  })
+
+# same order as the correlations 
+dir_net_b <- dir_net_b[colnames(correlations$P)]
+
+lt <- combn(length(dir_net_b), 2) %>%
+  apply(2, function(x){
+    length(intersect(dir_net_b[[x[1]]], dir_net_b[[x[2]]])) /
+      length(dir_net_b[[x[1]]])
+  }) %>%
+  magrittr::multiply_by(100) %>% round() %>% paste0("%")
+
+nam <- c("unweighted","deposition", "importance", "visitation")
+
+mapply(my_paste, correlations$r, correlations$P) %>%
+  matrix(ncol = length(dir_net_b)) %>% magrittr::set_colnames(nam) %>%
+  magrittr::set_rownames(nam) %>% `[<-`(lower.tri(.), lt) %>% 
+  xtable::xtable(caption = "\\textbf{Correlation of $n_d$ among network weighting schemes}.
+Spearman correlation coeffcients (with p-value) of the relative importance of species and the percentage of interactions that share the direction of dependency obtained using the three weighting schemes and an unweighted scheme.") %>%
+	print(comment = FALSE, include.rownames = FALSE)
+
+```
+
+Altogether, evidence supports the idea that visitation is a suitable metric to estimate the mutual dependency of species pairs.
+First, it is directly related to pollinator foraging.
+Second, it produces results consistent, at least within our controllability framework, with plant reproductive success (as estimated by the importance metric).
+
 # References

### 2017-01-25 paper/supp_info_2.tex
Script to calculate asymmetry matchings on the cluster

\documentclass[a4paper]{artikel1}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
  \newcommand{\euro}{€}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\usepackage[margin=1in]{geometry}
\usepackage{hyperref}
\PassOptionsToPackage{usenames,dvipsnames}{color} % color is loaded by hyperref
\hypersetup{unicode=true,
            pdftitle={Biotic invasions fuck with the manageability of pollination networks},
            pdfsubject={Supporting Information},
            pdfborder={0 0 0},
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{0}

%%% Use protect on footnotes to avoid problems with footnotes in titles
\let\rmarkdownfootnote\footnote%
\def\footnote{\protect\rmarkdownfootnote}

%%% Change title format to be more compact
\usepackage{titling}

% Create subtitle command for use in maketitle
\newcommand{\subtitle}[1]{
  \posttitle{
    \begin{center}\large#1\end{center}
    }
}

\setlength{\droptitle}{-2em}
  \title{Biotic invasions fuck with the manageability of pollination networks}
  \pretitle{\vspace{\droptitle}\centering\huge}
  \posttitle{\par}
\subtitle{Supporting Information}
  \author{}
  \preauthor{}\postauthor{}
  \date{}
  \predate{}\postdate{}

\usepackage{setspace}
\usepackage{float}
\usepackage{rotating}
\renewcommand{\figurename}{Supporting Figure}
\renewcommand{\tablename}{Supporting Table}

% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

\begin{document}
\maketitle

\doublespacing

\section{S1: Finding a complex network's
matchings}\label{s1-finding-a-complex-networks-matchings}

Our approach to find the minumum number of driver nodes relies on
finding maximum matchings and maximum cardinality matchings. Most
existing algorithms are designed to work with undirected bipartie
networks, where finding the maximum matching is equivalent to finding
the maximum flow between the two levels.

We start with a directed network in which the direction of the link
represents the direction of control (Supporting figure 1a). We then
construct an alternative representation of the directed network in which
each node of the directed network is represented by two nodes that
indicate their outgoing and incoming links (Supporting figure 1b).
Finding a maximum matching in this alternative representation is
equivalent to finding the largest possible set of edges in which one
node in the left hand side is connected to at most one node in the right
hand side. To find the maximum matching we use the push-relabel
algorithm implemented in \texttt{max\_bipartite\_matching} in the R
package igraph 1.0.1 (Csardi \& Nepusz 2006). Once we have the matching
shown in the Supporting Figure 1b, it is then easy to identify the roles
of each node in this representation: nodes on the right hand side that
are connected to a matched link (purple) are matched, while those
connected to a matched link on the left hand side are superior. This
information can then be mapped back to the original representation to
identify the control paths and the driver nodes in the network
(Supporting Figure 1c). Supporting Figure 1d, e, and f ilustrate this
approach for a network with bidirectional links.

\begin{figure}[htbp]
\centering
\includegraphics{supp_info_2_files/figure-latex/fig-direction-of-control-1.pdf}
\caption{\textbf{Finding a maximum matching in a complex network}. (a \&
d) Directed networks that indicate the direction of control between
species. (b \& e) Alternative bipartite representations of the directed
networks. (c \& f) The matchings in the bipartite representation mapped
back to the original network.}
\end{figure}

The algorithm implemented in \texttt{max\_bipartite\_matching}, however,
is only able to find \textbf{one} of the, possibly many, maximum
matchings in a network. One maximum matching is sufficient to calculate
\emph{n\textsubscript{D}} and hence to provide indication of a
communitie's manageability, however it is not possible to estimate the
role of individual species. To do that we need to calculate all possible
maximum matchings (or all maximal cardinality matchings in weighted
networks like ours). We start from the alternative bipartite
representation in Supporting Figure 1b and assign an identity to each of
the links in the network (shown as numbers in Supporting Figure 2a). We
will call this bipartite representation \emph{B}. We then construct the
line graph of the alternative bipartite representation \emph{L(B)}
(Supporting Figure 2b). Each node in \emph{L(B)} represents a link in
\emph{B} and are connected to each other only if they share a common
node in \emph{B}. We calculate the complement graph of \emph{L(B)} and
idetify all the maximum cliques (Supporting Figure 2c). Here some extra
definitions are neccessary. First, the complement of \emph{L(B)},
\emph{H}, is a graph with the same nodes as \emph{L(B)} but that has a
link between two given nodes if and only if there is not a link in
\emph{L(B)}. Second, a clique is a subset of nodes such that any two of
them are linked. Lastly, a maximum clique is a clique such that there
are no cliques with more nodes. In this example there are two maximum
cliques: that one formed by 1, 3 and 5, and by 2, 3 and 5. The final
step is then to map these cliques into the original network to obtain
all possible maximum cardinality matchings as shown in Figure 1 in the
main text.

\begin{figure}[htbp]
\centering
\includegraphics{supp_info_2_files/figure-latex/fig-finding-all-matchings-1.pdf}
\caption{\textbf{Finding all possible maximum cardinality matchings}.
(a) Alternative bipartite representation of a directed network. (b) Line
graph of the network in a. (c) Complement of the network in b. The two
maximum cliques are shown in red and blue.}
\end{figure}

In the main text we show all maximum cardinality matchings for a simple
example network. To further ilustrate our methodology, here we also show
the approach for the smallest of our empirical networks, the uninvaded
network at site 10 (Supporting Table 1; Supporting Figure 3). The
largest component of this network is composed by 16 species of which 2
are non-invasive plants and the rest are pollinators. The one-to-one
relationship between matched and superior nodes implies that in order to
achieve full network controllability, most pollinators would be
unmatched, and hence driver species that require external intervention.
At the same time, both plants in the community, \emph{Heracleum
sphpndylum} and \emph{Rubus fructicosus} and one of the pollinators
\emph{Orthotylus/Lygocorus} tend to be classified as superior nodes.

\begin{figure}[htbp]
\centering
\includegraphics{supp_info_2_files/figure-latex/fig-SA_exp-1.pdf}
\caption{\textbf{Illustration of the procedure with one empirical
network}. (a) The initial visitation network. (b) The directed network
in which the direction of control and the magnitude of the asymmetry are
determined based on the mutual dependences. (c) One of the possible
maximum matchings calculated using the procedures illustrated in the
Supporting Figure 1 and 2.}
\end{figure}

In addition, here we also show all the maximum cardinality matchings for
an example network in which the links are bidirectional (Supporting
Figure 4). It is important to note that using bidirectional is
problematic for a couple

It is important to note that our approach to find all the maximum
matchings, which is based on the alternative bipartite representation of
the directed network and a series of network transofrmations, has an
important disadvantage. Namely, that it is possible tha cycles in
network figure 4

\begin{figure}[htbp]
\centering
\includegraphics{supp_info_2_files/figure-latex/fig-matchings-bidirectional-1.pdf}
\caption{SAD}
\end{figure}

\begin{figure}[htbp]
\centering
\includegraphics{supp_info_2_files/figure-latex/fig-matchings-bidirectional-no-1.pdf}
\caption{asd asd}
\end{figure}

\section{S2: Properties of empirical
networks}\label{s2-properties-of-empirical-networks}

The studied networks had species richess ranging between 19 and 87
(16-86 when considering only the largest component in each network). As
evidenced by the overall network asymmetry \emph{AS} (Blüthgen \emph{et
al.} 2007) networks had a low ratio of plants to pollinators.
Furthermore, networks had relatively low levels of nestedness (when
measured using the quantitative version of the NODF index; Almeida-Neto
\& Ulrich 2011). Details for each network can be found in Supporting
Table 1.

\begin{table}[ht]
\centering
\begin{tabular}{rlrrrrrrrl}
  \hline
site & invader & $R$ & $n_s$ & $n_p$ & $n_a$ & $c$ & $AS$ & NODF & location \\ 
  \hline
  1 & — &  35 &  35 &   9 &  26 & 0.17 & -0.49 & 8.68 & Cap de Creus, Spain \\ 
    1 & car &  57 &  57 &  10 &  47 & 0.17 & -0.65 & 13.27 & Cap de Creus, Spain \\ 
    2 & — &  40 &  38 &   9 &  29 & 0.18 & -0.53 & 12.66 & Cap de Creus, Spain \\ 
    2 & car &  38 &  38 &  11 &  27 & 0.21 & -0.42 & 15.04 & Cap de Creus, Spain \\ 
    3 & — &  31 &  29 &   6 &  23 & 0.22 & -0.59 & 14.30 & Cap de Creus, Spain \\ 
    3 & op &  33 &  28 &   6 &  22 & 0.24 & -0.57 & 13.29 & Cap de Creus, Spain \\ 
    4 & — &  35 &  35 &  10 &  25 & 0.17 & -0.43 & 12.43 & Cap de Creus, Spain \\ 
    4 & car &  57 &  57 &  14 &  43 & 0.14 & -0.51 & 13.70 & Cap de Creus, Spain \\ 
    5 & — &  35 &  33 &   7 &  26 & 0.23 & -0.58 & 13.05 & Cap de Creus, Spain \\ 
    5 & op &  32 &  32 &   8 &  24 & 0.19 & -0.50 & 10.96 & Cap de Creus, Spain \\ 
    6 & — &  30 &  25 &   7 &  18 & 0.23 & -0.44 & 9.77 & Cap de Creus, Spain \\ 
    6 & op &  37 &  37 &   9 &  28 & 0.17 & -0.51 & 12.45 & Cap de Creus, Spain \\ 
    7 & — &  37 &  30 &   3 &  27 & 0.38 & -0.80 & 24.86 & Bristol, United Kingdom \\ 
    7 & imp &  57 &  57 &   8 &  49 & 0.20 & -0.72 & 14.36 & Bristol, United Kingdom \\ 
    8 & — &  48 &  43 &   3 &  40 & 0.36 & -0.86 & 6.84 & Bristol, United Kingdom \\ 
    8 & imp &  87 &  83 &  13 &  70 & 0.12 & -0.69 & 8.67 & Bristol, United Kingdom \\ 
    9 & — &  55 &  53 &  11 &  42 & 0.14 & -0.58 & 13.77 & Bristol, United Kingdom \\ 
    9 & imp &  86 &  86 &  11 &  75 & 0.13 & -0.74 & 13.40 & Bristol, United Kingdom \\ 
   10 & — &  19 &  16 &   2 &  14 & 0.57 & -0.75 & 13.35 & Bristol, United Kingdom \\ 
   10 & imp &  54 &  49 &   5 &  44 & 0.26 & -0.80 & 9.04 & Bristol, United Kingdom \\ 
   \hline
\end{tabular}
\caption{\textbf{Properties of the analysed plant-pollinator communities}. Invasive plants were \textit{Carpobrotus affine acinaciformis} (car), \textit{Opuntia stricta} (op), and \textit{Impatients grandulifera} (imp). All properties, with the exception of the networks' total species richness ($R$), correspond to the network's largest component. Specifically we show the number of species ($n_s$), the number of plants ($n_p$), the number of pollinators ($n_a$), the network connectance ($c$), the network assymetry ($AS$), and the network nestedness (NODF index). British networks were assembled by Lopezaraiza-Mikel et al. (2007), Spanish were networks assembled by Bartomeus et al. (2008).} 
\end{table}

\section{S3: Visitation as a proxy for species
interdependence}\label{s3-visitation-as-a-proxy-for-species-interdependence}

Visitation frequency has been shown to be an appropriate surrogate for
inter-specific effects in pollination networks (Vázquez \emph{et al.}
2005; Bascompte \emph{et al.} 2006). Nevertheless visitation is not
equivalent to pollen deposition and might be insufficient to reflect the
dependencies of plants on animals and vice versa (Alarcón 2010; King
\emph{et al.} 2013). We therefore investigated the effect of calculating
the dependencies using visitation or pollination effectiveness and
importance---two metrics more proximate to plant reproductive success
(Supporting Figure 6). We did this by comparing \emph{(i)} the
manageability of the community and \emph{(ii)} the percentage of
interactions that maintained the direction of dependency. To do that, we
used data collected by Ballantyne \emph{et al.} (2015) from a low
diversity pollination community at a dry lowland heathland in Dorset, UK
(50° 43.7'N 2° 07.2'W). First, deposition networks were quantified using
the mean Single Visit Deposition---the number of conspecific pollen
grains effectively deposited on a virgin stigma during a single visit by
a particular animal (Ne'Eman \emph{et al.} 2010; King \emph{et al.}
2013; Ballantyne \emph{et al.} 2015). Second, visitation networks were
constructed counting the visits to flowers during Single Visit
Depositions. Finally, pollinator importance networks were constructed as
the product of pollinator efficiency and visit frequency.

\begin{figure}[htbp]
\centering
\includegraphics{supp_info_2_files/figure-latex/fig-visitation-vs-deposition-vs-importance-1.pdf}
\caption{\textbf{Distribution of interaction weights for the pollen
deposition, visitation and pollinator importance networks}. Note that
the \emph{x} axis in the density plots have been log-transformed.}
\end{figure}

We first investigated the effects at a network scale. Despite marked
differences in the distribution of weights of the three networks, the
minimum number of driver species to control the whole community was
consistent among the three different approaches (0.33 for deposition,
0.33 for the visitation, and 0.38 for the pollinator importance
network).

The choice of weighting used can also have an impact on the relative
importance of species. Therefore we calculated the frequency that each
species is present in the possible sets of driver species under the
three schemes. Although visitation and deposition produce strikingly
different results, we found a very strong agreement between the order
produced by visitation and importance (Supporting Table 2). Finally, we
investigated whether the asymmetry of mutual dependency, which defines
the direction of control, was consistent among the three possible
weighting schemes. We found again that the direction of the dominant
dependency was maintained was consistent for 95\% of the interactions
weighted by visitation or importance, the two most appropriate metrics
for pollinator and plant dependency (Supporting Table 2).

\begin{table}[ht]
\centering
\begin{tabular}{llll}
  \hline
unweighted & deposition & importance & visitation \\ 
  \hline
- & 0.93 ($<$ 0.001) & 0.85 ($<$ 0.001) & 0.85 ($<$ 0.001) \\ 
  87\% & - & 0.86 ($<$ 0.001) & 0.87 ($<$ 0.001) \\ 
  77\% & 74\% & - & 1 ($<$ 0.001) \\ 
  82\% & 74\% & 95\% & - \\ 
   \hline
\end{tabular}
\caption{\textbf{Correlation of $n_d$ among network weighting schemes}. Spearman correlation coeffcients (with p-value) of the relative importance of species and the percentage of interactions that share the direction of dependency obtained using the three weighting schemes and an unweighted scheme.} 
\end{table}

Altogether, evidence supports the idea that visitation is a suitable
metric to estimate the mutual dependency of species pairs. First, it is
directly related to pollinator foraging. Second, it produces results
consistent, at least within our controllability framework, with plant
reproductive success (as estimated by the importance metric).

\section*{References}\label{references}
\addcontentsline{toc}{section}{References}

\hypertarget{refs}{}
\hypertarget{ref-Alarcon2010}{}
Alarcón, R. (2010). Congruence between visitation and pollen-transport
networks in a California plant-pollinator community. \emph{Oikos}, 119,
35--44.

\hypertarget{ref-Almeida-Neto2011}{}
Almeida-Neto, M. \& Ulrich, W. (2011). A straightforward computational
approach for measuring nestedness using quantitative matrices.
\emph{Environmental Modelling and Software}, 26, 173--178.

\hypertarget{ref-Ballantyne2015}{}
Ballantyne, G., Baldock, K.C.R. \& Willmer, P.G. (2015). Constructing
more informative plant-pollinator networks: visitation and pollen
deposition networks in a heathland plant community. \emph{Proceedings of
the Royal Society B}, 282, 20151130.

\hypertarget{ref-Bartomeus2008}{}
Bartomeus, I., Vilà, M. \& Santamaría, L. (2008). Contrasting effects of
invasive plants in plant-pollinator networks. \emph{Oecologia}, 155,
761--770.

\hypertarget{ref-Bascompte2006}{}
Bascompte, J., Jordano, P. \& Olesen, J.M. (2006). Asymetric
Coevolutionary Networks Facilitate Biodiversity Maintenance.
\emph{Science}, 312, 431--433.

\hypertarget{ref-Bluthgen2007}{}
Blüthgen, N., Menzel, F., Hovestadt, T., Fiala, B. \& Blüthgen, N.
(2007). Specialization, Constraints, and Conflicting Interests in
Mutualistic Networks. \emph{Current Biology}, 17, 341--346.

\hypertarget{ref-Csardi2006a}{}
Csardi, G. \& Nepusz, T. (2006). The igraph software package for complex
network research. \emph{InterJournal, Complex Systems}, 1695, 1--9.

\hypertarget{ref-King2013}{}
King, C., Ballantyne, G. \& Willmer, P.G. (2013). Why flower visitation
is a poor proxy for pollination: Measuring single-visit pollen
deposition, with implications for pollination networks and conservation.
\emph{Methods in Ecology and Evolution}, 4, 811--818.

\hypertarget{ref-Lopezaraiza-Mikel2007}{}
Lopezaraiza-Mikel, M.E., Hayes, R.B., Whalley, M.R. \& Memmott, J.
(2007). The impact of an alien plant on a native plant-pollinator
network: An experimental approach. \emph{Ecology Letters}, 10, 539--550.

\hypertarget{ref-NeEman2010}{}
Ne'Eman, G., Jürgens, A., Newstrom-Lloyd, L., Potts, S.G. \& Dafni, A.
(2010). A framework for comparing pollinator performance: Effectiveness
and efficiency. \emph{Biological Reviews}, 85, 435--451.

\hypertarget{ref-Vazquez2005}{}
Vázquez, D.P., Morris, W.F. \& Jordano, P. (2005). Interaction frequency
as a surrogate for the total effect of animal mutualists on plants.
\emph{Ecology Letters}, 8, 1088--1094.

\end{document}

### 2017-01-25 code/_04-calculate_matchings.sh

@@ -1,0 +1,14 @@
+#!/bin/bash
+
+#$ -V
+#$ -cwd
+#$ -j y
+#$ -S /bin/bash
+##$ -pe multi_thread ${n_cores} # needs to be specified externally
+#$ -m a
+#$ -M efc29@uclive.ac.nz
+#$ -r yes
+#$ -l mem_free=16G,h_vmem=16G
+
+Rscript --no-save --no-restore 04-calculate_matchings.R $1
+exit 0

### 2017-02-13 paper/EL-reviewer-comments-1.Rmd
Move editor's comments to the beginning
Add comments to editor + daniel's feedback

@@
 date: "14 December 2016"
-header-includes:
-   - \usepackage{setspace}
 output: pdf_document
@@
 bibliography: references.bib
+header-includes:
+- \usepackage{setspace}
 ---
@@
 In the current version, we have thoroughly addressed all these concerns and improved both the robustness of the analyisis and the clarity of the concepts. 
-Detailed responses to each comment, one by one, are provided below.
+Detailed responses to each comment, one by one, are provided in the corresponding section.
 
@@
 ******************************************
+
+## Response to the handling editor
+
+We are thankful for the encouraging assessment that our work "has excellent potential" and "could have major impacts on applied ecology". 
+We have fully addressed the flaws pointed by all the reviewers and, in the process, took advantage of this opportunity to incorporate some further changes that in our opinion improved the quality and thoroughness of our assessment.
+
+The most substantial change is related to the result that ecological invasions reduce the manageability of the studied pollination networks. 
+After revising the manuscript, we found that the effect of invasion is actually the opposite of what we initially reported. 
+This result arises from a regression in which the response variable was the proportion of driver nodes. 
+Our previous conclusion arose from a trivial mistake on the interpretation of this result for which we are apologetic. 
+This regression indicates that the invasion status is *inversely* related to $n_D$ (the density of driver nodes) and **not** to our previous definition of manageability $m = 1- n_D$. 
+We highlight that although the corrected result now contradicts our hypothesis, our postulate has remained unchanged and the applicability of our approach is maintained. 
+It is possible that the root of the mistake was, as you and the reviewers helpfully pointed out, that our definition of manageability and its relation to previous conceptions of controllability were confusing.
+Now, we refrain from giving a mathematical definition to manageability and instead focus on $n_D$, an unambiguous metric clearly defined in the structural controllability literature.
+
+We extend this approach to our investigation on the relative importance of species. 
+In the previous manuscript, we referred to species that were classified as superior nodes in all possible control strategies as *driver species*. 
+Because of the similarities with the term *driver node*, which has been used in previous literature and we also use in our manuscript, it was extremely easy to misinterpret the terms and follow our rationale.
+Now, we have removed the term driver species and instead focus on two straightforward metrics: $f_D$ and $f_S$, which more clearly correspond to the frequency to which a species is classified as a driver or superior node, respectively.
+
+Finally, we have made important modifications to the section in which we explain the theoretical underpinnings of structural controllability. 
+We hope it is easier to follow both for experts and newcomers. 
+We also have included a significant amount of detail and extra examples in the supplementary material to simplify the lives of those interested in applying the proposed approach or replicating our results.
 
@@
 
-## Editor's Comments
-
-This was a difficult decision.
-Like all the reviewers, I think this work has huge potential, and could have major impacts in applied ecology.
-However, you are unclear in your terminology wrt to the major research field you apply to this interesting ecological setting and your exposition is opaque (for example, how exactly are manageability and controllability related?
-– see the important caution from R2 and the detailed comments from R1).
-This makes it incredibly hard to follow your work, even for someone who works in network controllability.
-There also seems to be key controllability methodological work you could more effectively leverage.
-I applaud the close link of theory and empiricism, but more details of the field network pairs would be helpful.
-Really major revisions will be required to get this ms into a form that appeals to both newcomers and experts in the field, and the manuscript will have to be re-reviewed (likely by a mix of the same and some new reviewers), but it does have excellent potential, so I encourage the authors to carefully and thoroughly deal with all of the reviewer comments.
-
-*Thanks for the encouraging feedback*
-
 ## References

### 2017-02-13 paper/EL-reviewer-comments-1.Rmd
From interpretation to implementation error

@@
 This result arises from a regression in which the response variable was the proportion of driver nodes. 
-Our previous conclusion arose from a trivial mistake on the interpretation of this result for which we are apologetic. 
-This regression indicates that the invasion status is *inversely* related to $n_D$ (the density of driver nodes) and **not** to our previous definition of manageability $m = 1- n_D$. 
+Our previous conclusion arose from a trivial mistake on the implementation of this regression for which we are extremely apologetic. 
+The regression indicates that the invasion status is *inversely* related to $n_D$ (the density of driver nodes) and **not** to our previous definition of manageability $m = 1- n_D$. 
 We highlight that although the corrected result now contradicts our hypothesis, our postulate has remained unchanged and the applicability of our approach is maintained. 

### 2017-02-14 paper/EL-reviewer-comments-1.Rmd
Daniel edits to the 'egg on face' section

@@
 Our previous conclusion arose from a trivial mistake on the implementation of this regression for which we are extremely apologetic. 
-The regression indicates that the invasion status is *inversely* related to $n_D$ (the density of driver nodes) and **not** to our previous definition of manageability $m = 1- n_D$. 
-We highlight that although the corrected result now contradicts our hypothesis, our postulate has remained unchanged and the applicability of our approach is maintained. 
-It is possible that the root of the mistake was, as you and the reviewers helpfully pointed out, that our definition of manageability and its relation to previous conceptions of controllability were confusing.
-Now, we refrain from giving a mathematical definition to manageability and instead focus on $n_D$, an unambiguous metric clearly defined in the structural controllability literature.
+The regression indicates that the invasion status is *inversely* related to $n_D$ (the density of driver nodes) and **not** to our previous definition of manageability $m = 1 - n_D$.
+In catching this error, the editor and reviewers will note that revised result now contradicts our hypothesis and has also led to our having to amend the title of the paper.
+Nevertheless, we hope that you will agree that both our overall objective and the applicability of our approach is maintained.
 
-We extend this approach to our investigation on the relative importance of species. 
+Upon reflection, we also suspect that the root of the mistake was, as you and the reviewers helped point out, that our definition of manageability and its relation to existing concept of controllability were confusing.
+In the revised paper, we refrain from giving a mathematical definition of manageability and instead focus on $n_D$, an unambiguous metric clearly defined in the structural controllability literature.
+We also extend these attempts to use the existing nomenclature rather than introduce new terms in our investigation of the relative importance of species.
 In the previous manuscript, we referred to species that were classified as superior nodes in all possible control strategies as *driver species*. 
-Because of the similarities with the term *driver node*, which has been used in previous literature and we also use in our manuscript, it was extremely easy to misinterpret the terms and follow our rationale.
-Now, we have removed the term driver species and instead focus on two straightforward metrics: $f_D$ and $f_S$, which more clearly correspond to the frequency to which a species is classified as a driver or superior node, respectively.
+Because of the strong similarities with the term *driver node*, which has been used in previous literature and we also use in our manuscript, it was extremely easy to misinterpret the terms and follow our rationale.
+Now, we have removed the term driver species and instead focus on two well-defined metrics: $f_D$ and $f_S$, which correspond to the frequency to which a species is classified as a driver or superior node, respectively.
 

### 2017-02-14 paper/draft_2.Rmd
Remove grid from paper's theme

@@
 				strip.background = element_blank(),
-				plot.margin = grid::unit(c(5, 0, 2, 0), "mm"))
+				plot.margin = grid::unit(c(5, 0, 2, 0), "mm"),
+				panel.grid = element_blank())
 ```

### 2017-02-14 paper/supp_info_2.Rmd
Add rationale behind cycles and bidirectional networks

@@
 
-In addition, here we also show all the maximum cardinality matchings for an example network in which the links are bidirectional (Supporting Figure 4).
-It is important to note that using bidirectional is problematic for a couple
-
-It is important to note that our approach to find all the maximum matchings, which is based on the alternative bipartite representation of the directed network and a series of network transofrmations, has an important disadvantage.
-Namely, that it is possible tha cycles in network figure 4
-
-```{r fig-matchings-bidirectional, echo = F, message = F, warning = F, fig.width = 6.2, fig.height = 3.2, results = "hide", fig.cap = "SAD"}
+In addition, here we also show all the maximum cardinality matchings for an example network in which the links are weighted based on the mutual dependences (Supporting Figure 4).
+It is important to note that using mutual dependencies is problematic for a couple of reasons.
+
+First, having two links between species and using our maximum matching approach to calculate the control configurations, result in matchings that include cycle forming links (Supporting Figure 5).
+Strictly speaking these configurations are maximum matchings in the alternative bipartite configuration (Supporting Figure 1e) but are not in the directed network (Supporting Figure 1f).
+While bidirectional links are the norm when using mutual dependences, they only appear in the asymmetry-weighted networks whenever the mutual dependences between two species symmetric.
+In this special case, we include two links weighted with 0.5 to reflect the fact that the species affect each other in the same proportion.
+Whenever present, we filter out the cycle containing matchings before conducting any analysis.
+In the special case when the network has no matchings that correspond to control configurations, we reduce by one the size of the cliques we enumerate in *H* (Supporting Figure 2).
+
+Second, the number of maximal matchings increasses dispproportionally fast with the number of links in a network.
+For instance, our example network in Figure 1, which is composed by uni-directional links weighted by the asymmetry, has two different maximum matchings.
+In contrast, the equivalent network with bidirectional links has 16 different maximum matchings (Supporting Figure 4 and 5).
+To further ilustrate this growth, some of our empirical networks, had approximately ten thousand different maximum matchings using asymmetries but one hundred million when using mutual dependences.
+This exponential growth, and the computational cost of filtering matchings with cycles, surpassed the capabilities of the available computational resources and rendered us unable to calculate all possible maximum matchings when using mutual dependences in most of our networks.
+
+```{r fig-matchings-bidirectional, echo = F, message = F, warning = F, fig.width = 6.2, fig.height = 3.2, results = "hide", fig.cap = "**Matchings of a simple network with bidirectional links**.
+(a) A network with bidirectional links.
+(b-e) Possible control configurations." }
 par(mfrow=c(2,3), mar=c(0,0,0,0))
@@
 
-```{r  fig-matchings-bidirectional-no, echo = F, message = F, warning = F, fig.width = 6.2, fig.height = 4.8, results = "hide", fig.cap= "asd asd"}
+```{r  fig-matchings-bidirectional-no, echo = F, message = F, warning = F, fig.width = 6.2, fig.height = 4.8, results = "hide", fig.cap= "**Cycles in a bidirectional network**.
+Our approach finds twelve configurations for Supporting Figure 4a that are not actual matchings."}
 

### 2017-02-14 paper/supp_info_2.Rmd
Minor changes to network properties table

@@
 		x <- keep_largest_component(x)
+		n_pla <- sum(igraph::V(x)$type == "pla")
+		n_pol <- sum(igraph::V(x)$type == "pol")
 		bipartite::networklevel(igraph::as_incidence_matrix(x, 
@@
 			as.list() %>% as.data.frame() %>%
-			dplyr::mutate(n_sp = length(igraph::V(x)),
-										n_pla = sum(igraph::V(x)$type == "pla"),
-										n_pol = sum(igraph::V(x)$type == "pol"))
+			dplyr::mutate(n_sp = length(igraph::V(x))) %>%
+			dplyr::mutate(n_pla = n_pla,
+										n_pol = n_pol)
 	})

### 2017-02-14 paper/supp_info_2.Rmd
Edits in code and text for visitation vs deposition

@@
 To do that, we used data collected by @Ballantyne2015 from a low diversity pollination community at a dry lowland heathland in Dorset, UK  (50° 43.7'N 2° 07.2'W). 
-First, deposition networks were quantified using the mean Single Visit Deposition---the number of conspecific pollen grains effectively deposited on a virgin stigma during a single visit by a particular animal [@NeEman2010; @King2013; @Ballantyne2015].
+First, deposition networks were quantified using the mean single visit deposition---the number of conspecific pollen grains effectively deposited on a virgin stigma during a single visit by a particular animal [@NeEman2010; @King2013; @Ballantyne2015].
 Second, visitation networks were constructed counting the visits to flowers during Single Visit Depositions. 
@@
 
-We first investigated the effects at a network scale. 
-Despite marked differences in the distribution of weights of the three networks, the minimum number of driver species to control the whole community was consistent among the three different approaches (`r 1-round(n_driver$n_driver[n_driver$net_name == "bal_eff"], digits = 2)` for deposition, `r 1-round(n_driver$n_driver[n_driver$net_name == "bal_vis"], digits = 2)` for the visitation, and `r 1-round(n_driver$n_driver[n_driver$net_name == "bal_imp"], digits = 2)` for the pollinator importance network).
-
-The choice of weighting used can also have an impact on the relative importance of species.
-Therefore we calculated the frequency that each species is present in the possible sets of driver species under the three schemes. 
-Although visitation and deposition produce strikingly different results, we found a very strong agreement between the order produced by visitation and importance (Supporting Table 2). 
-Finally, we investigated whether the asymmetry of mutual dependency, which defines the direction of control, was consistent among the three possible weighting schemes.
+At a network scale, despite marked differences in the distribution of weights of the three networks (Supporting Figure 6), the driver node density *n~D~* was consistent among the three different approaches (`r 1-round(n_driver$n_driver[n_driver$net_name == "bal_eff"], digits = 2)` for deposition, `r 1-round(n_driver$n_driver[n_driver$net_name == "bal_vis"], digits = 2)` for the visitation, and `r 1-round(n_driver$n_driver[n_driver$net_name == "bal_imp"], digits = 2)` for the pollinator importance network).
+
+The choice of weighting used can also have an impact on at the species level.
+Therefore we calculated *f~D~* and *f~S~* (the frequency at which each species is classified as a driver or superior node, respectively, within the set of all possible matchings in a network) and calculated it's correlation among three times of weighting schemes.
+Although visitation and deposition produce moderately different results, we found a very strong agreement between the order produced by visitation and importance (Supporting Table 2). 
+Finally, we also investigated whether the asymmetry of mutual dependency, which defines the direction of control, was consistent among the three possible weighting schemes.
 We found again that the direction of the dominant dependency was maintained was consistent for 95\% of the interactions weighted by visitation or importance, the two most appropriate metrics for pollinator and plant dependency (Supporting Table 2).
@@
 								d_rank = rank(-d_weight, ties.method = "average")) %>%
+	dplyr::group_by(net_name, species) %>% 
+	dplyr::summarise(d_rank = mean(d_rank)) %>%
 	dplyr::group_by() %>%
 	dplyr::select(net_name, species, d_rank) %>% 
+	dplyr::distinct() %>%
 	tidyr::spread(net_name, d_rank) %>%
@@
   magrittr::set_rownames(nam) %>% `[<-`(lower.tri(.), lt) %>% 
-  xtable::xtable(caption = "\\textbf{Correlation of $n_d$ among network weighting schemes}.
-Spearman correlation coeffcients (with p-value) of the relative importance of species and the percentage of interactions that share the direction of dependency obtained using the three weighting schemes and an unweighted scheme.") %>%
-	print(comment = FALSE, include.rownames = FALSE)
+  xtable::xtable(caption = "\\textbf{Agreement among network weighting schemes}.
+Spearman correlation coeffcients (with p-value) of specie's $f_D$ and the percentage of interactions that share the direction of dependency obtained using the three weighting schemes and an unweighted scheme.") %>%
+	print(comment = FALSE, include.rownames = TRUE)
 

### 2017-02-14 paper/supp_info_2.Rmd
Sensitivity analysis

@@
 
+# S4: Sensitivity analysis
+
+Our approach is fundamentaly based on the network structure. 
+Often, the majority of the interactions that determine this structure are weak, which in our networks means that most interactions are formed by a small number of observed pollination visits, and therefore those weak intercations are less conspicuous in the field than strong ones.
+To strengthen the case of pur approach, we therefore evaluated the robustness of our results to simulated sampling limitations.
+
+To do so, for each network, we removed a portion of the links and calculated how three control metrics of the subsampled network compare to those of the full network. 
+Specifically, we calculated the difference between the $n_D$ of the subsampled and the full network, the spearman correlation between the vectors $f_D$—which contain the frequency with wich each species is classified as a driver species, and the spearman correlation between $f_S$—which contain the frequency with which each species is classified as a superior node.
+We removed links from the full network with a probability inversly proportional to the interaction weight, and varied the portion of links removed between 0.5 and 0.95 at 0.05 increments. 
+We repeated the procedure ten times for each portion level and each network to obtain a total sample size of $n=2000$.
+
+Overall, the results of the sensitivity analysis indicate that our approach might be useful for management even in the absence of complete sampling. 
+Specifically as the proportion of sampled interaction decreassed, the variability of $n_D$ increassed, but was overall very similar when compared to that obtained using all available interactions (Supporting Figure 7a).
+Similarly, the correlation between the relative frequency with which species are classified as a driver ($f_D$) or as a superior node ($f_S$) was correlated ever for *extreme* levels of undersampling.
+For instance, we found that with a sampling level of 0.5, the mean spearman correlation coefficient was 0.66 for $f_D$ and 0.76 for $f_S$. 
+Finally, the resulst suggest that the relative ranking of species is better conserved in $f_S$ than for $f_D$ troughout all levels subsampling levels.
+
+```{r fig-subsampling-sensitivity, echo = F, message = F, warning = F, fig.width = 4.5, fig.height = 3.5, results = "hide", fig.cap= "**Sensitivity to subsampling**.
+(a) The difference between the *n~D~* of the subsampled and the full networks.
+(b) The spearman correlation of the relative importance of species between the subsampled and the full networks."}
+n_d_sampling <- readRDS("../data/processed/sampling_robustness/n_d_sampling.rds")
+
+p1 <- n_d_sampling %>% 
+	dplyr::filter(!grepl("bal", net_name)) %>%
+	ggplot(aes(x = sampling_proportion, y = n_d_base-n_d)) +
+	geom_hline(yintercept = 0, linetype = 1, size = 0.3, colour = "grey") +
+	xlab("sampling proportion") +
+	ylab(expression(paste(Delta, n[D]))) +
+	geom_boxplot(aes(x = as.factor(sampling_proportion)), size = 0.3,
+               colour = "grey10", outlier.shape = 21, outlier.size = 1) +
+	fer_theme
+
+f_sampling <- readRDS("../data/processed/sampling_robustness/f_sampling.rds")
+
+p2 <- f_sampling %>%
+	dplyr::filter(!grepl("bal", net_name)) %>%
+	ggplot(aes(x = as.factor(sampling_proportion), y = correlation)) +
+	geom_boxplot(aes(fill = frequency), size = 0.3,
+               colour = "grey10", outlier.shape = 21, outlier.size = 1) +
+	xlab("sampling proportion") +
+	ylab("spearman correlation") +
+	scale_fill_brewer(labels = expression(f[D], f[S]), name = "") +
+	fer_theme +
+	theme(legend.position = c(0.875,0.175), legend.justification = "center", 
+				legend.direction = "horizontal", legend.key = element_blank())
+
+cowplot::plot_grid(p1, p2, ncol = 1, align = "v", rel_heights = c(1,1), labels = c("a)", "b)"), label_size = 8)
+
+f_sampling %>%
+	dplyr::filter(!grepl("bal", net_name)) %>%
+	dplyr::filter(sampling_proportion == 0.5) %>%
+	dplyr::group_by(frequency) %>%
+	dplyr::summarise(correlation = mean(correlation))
+```
+
 # References

### 2017-02-15 paper/draft_2.Rmd
Update title?

@@
 ---
-title: "Biotic invasions fuck with the manageability of pollination networks"
+title: "The manageability of pollination networks in an invasion context"
 classoption: a4paper

### 2017-02-15 paper/draft_2.Rmd
Better introduce biotic invasions

@@
 To overcome this obstacle, we require a framework that allows us to explain, predict, and manage ecological communities, particularly when they are confronted with perturbations [@Sole2001; @Green2005].
-Ideally, such a framework needs to be able to account for their complex structure, and the dynamics that determine the state of each species, and the community as a whole.
+Ideally, such a framework needs to be able to account for their complex structure and the dynamics that determine the species abbundances and the state of the community.
 
-Among the various possibilities, control theory appears to be a strong candidate as it is designed to deal with determining and supervising the behaviour of general dynamical systems [@Motter2015], and is well equipped to deal with the many feedbacks present in ecological communities [@Liu2015].
-Research in the field has established a strong link between the structure of complex networks and their controllability, while also demonstrating that it is in principle possible to alter a whole ecological community's composition by modifying the abundances of only a few species [@Liu2011; @Cornelius2013; @Ruths2014].
-Applications of control theory to ecological networks can also take into account the extent to which changes in the abundances of one species may ripple through the community [@Cornelius2013].
-Therefore, control theory could provide an indication of which species are most relevant from a structural and dynamic perspective, a particularly important feature given that these species should underpin informed attempts to both alter or maintain the ecosystem state.
+Among the various possibilities, *control theory* appears to be a strong candidate.
+This method, widely used in engineering to determine and supervise the behaviour of dynamical systems [@Motter2015], is well equipped to deal with the many feedbacks present in ecological communities [@Liu2015].
+Research in the this area has established a strong link between the structure of complex networks and their *controllability*—the relative ability of manipulating network components to drive the system to a desired state [@Liu2011; @Cornelius2013; @Ruths2014].
+These advances suggest that it is in principle possible to alter a whole ecological community's composition by modifying the abundances of only a few species.
+Furthermore, applications of control theory to ecological networks can also take into account the extent to which changes in the abundances of one species may ripple through the community [@Cornelius2013].
+Therefore, control theory could also be harnessed to provide an indication of which species are most relevant from a structural and dynamic perspective.
 
-Despite these advances, practical challenges to the conservation of interaction networks persist [@Tylianakis2010], and the link between the structure of complex networks and our ability to manage and conserve them is still ambiguous [@Bluthgen2010; @Kaiser-Bunbury2015].
-To complicate things further, biotic invasions—a major driver of global change—can induce dramatic changes in the patterns of interactions that determine the structure of ecological networks [@Baxter2004; @Tylianakis2008; @Ehrenfeld2010a].
-Although understanding how differences in network structure before and after the invasion impact our ability to manage them presents a double challenge, it is a critical first step towards a fully informed recovery.
+This information is valuable not only from an ecological perspective, but it might be also relevant to address management and conservation challenges.  
+This is particularly true in the context of biotic invasions, where identifying key players in the community is a prerequisite to informed attempts to either alter the state of invaded ecosystem and maintain the state of uninvaded ones.
+Despite recent advances in network theory, practical challenges to the conservation of interaction networks persist [@Tylianakis2010], and the link between the structure of complex networks and our ability to manage and conserve them, is still ambiguous [@Bluthgen2010; @Kaiser-Bunbury2015].
+To complicate things further, biotic invasions can induce dramatic changes in the patterns of interactions that determine the structure of ecological networks [@Baxter2004; @Tylianakis2008; @Ehrenfeld2010a].
+Understanding how the differences in network structure before and after the invasion impact our ability to manage the communities doububle challenge, it is a critical first step towards a fully informed recovery.
 Despite the apparent overlap, a control-theoretic perspective has not been adopted in an invasion context. 

### 2017-02-15 paper/draft_2.Rmd
Change the convention for superior, matched and unmatched nodes in Fig 1

@@
 
-```{r figure 1, echo = F, message = F, warning = F, fig.width = 6.2, fig.height = 1.8, results= "hide", fig.pos = "t", fig.cap = "**Matchings of a simple network**.
+```{r figure 1, echo = F, message = F, warning = F, fig.width = 6.2, fig.height = 1.9, results= "hide", fig.pos = "t", fig.cap = "**Matchings of a simple network**.
 (a) We start with a network in which the direction of the links indicates the potential direction of control; for example a link from *a~1~* to *p~1~* indicates that the state of *p~1~* is influenced by the state of *a~1~*.
 (b & c) This network has two maximal cardinality matchings; that is, two configurations in which it would be possible to exert full control of the network via external input signals to a minimal set of nodes.
-In both cases, the three matched links (purple arrows) represent the control paths through the network and provide an indication of the matched nodes (purple), which are controlled by superior nodes within the network (bold node labels).
+In both cases, the three matched links (purple arrows) represent the control paths through the network and provide an indication of the matched nodes (purple), which are controlled by superior nodes within the network (circular nodes).
 Unmatched nodes (orange) are called driver nodes because full network control requires external signals to be applied to them.
@@
 Further examples can be found in the Supporting Information S1."}
-layout(matrix(c(1,2,3,4, 4, 4), 2, 3, byrow = TRUE),
-  	heights=c(8,1))
+layout(matrix(c(1, 1, 2, 4, 3, 4), 2, 3),
+  	heights=c(8,2))
 par( mar=c(0,0,0,0))
@@
 
-text(label_pos_x, label_pos_y, "a)", adj = c(0,0))
+text(label_pos_x, label_pos_y, "(a)", adj = c(0,0), font = 2)
 
@@
 
-		E(as_net)$matched <- 2
-		E(as_net)$matched[as_all_mat[[x]]] <- 4
+		E(as_net)$matched <- 1
+		E(as_net)$matched[as_all_mat[[x]]] <- 5
 
-		igraph::V(as_net)$matched <- 2
+		E(as_net)$matched_width <- 1
+		E(as_net)$matched_width[as_all_mat[[x]]] <- 1.5
+
+		igraph::V(as_net)$matched <- 1
 		igraph::V(as_net)$matched[igraph::V(as_net)$name %in%
+																ends(as_net, as_all_mat[[x]])[, 2]] <- 5
+
+		igraph::V(as_net)$matched_fill <- 2
+		igraph::V(as_net)$matched_fill[igraph::V(as_net)$name %in%
 																ends(as_net, as_all_mat[[x]])[, 2]] <- 4
@@
 
+		igraph::V(as_net)$sup_shape <- "square"
+		igraph::V(as_net)$sup_shape[igraph::V(as_net)$name %in%
+																ends(as_net, as_all_mat[[x]])[, 1]] <- "circle"
+
 		names_fancy <- sp_names_fancy
-		names_fancy[igraph::V(as_net)$name %in%
-																ends(as_net, as_all_mat[[x]])[, 1]] <-
-			sp_names_fancy_b[igraph::V(as_net)$name %in%
-																ends(as_net, as_all_mat[[x]])[, 1]]
+		# names_fancy[igraph::V(as_net)$name %in%
+		# 														ends(as_net, as_all_mat[[x]])[, 1]] <-
+		# 	sp_names_fancy_b[igraph::V(as_net)$name %in%
+		# 														ends(as_net, as_all_mat[[x]])[, 1]]
 
@@
 			plot(layout = lay, 
-					 vertex.size = igraph::V(.)$superior * 10 + 20,
+					 # vertex.size = igraph::V(.)$superior * 10 + 20,
+					 vertex.size = 30,
+					 vertex.color = pal[igraph::V(.)$matched_fill],
+					 vertex.shape = igraph::V(.)$sup_shape,
 					 vertex.label = names_fancy,
@@
 					 vertex.label.color = l_c,
-					 vertex.label.cex = igraph::V(.)$superior * 0.1 + 0.9,
+					 vertex.label.cex = 1,
 					 # vertex.shape = igraph::V(.)$vertex.shape,
-					 vertex.color = pal[igraph::V(.)$matched],
+					 vertex.frame.color = pal[igraph::V(.)$matched],
 					 edge.color = pal[E(.)$matched],
 					 edge.label = NA, 
-					 edge.width = E(.)$matched/2,
+					 edge.width = E(.)$matched_width,
 					 edge.label.family = fam,
@@
 
-		text(label_pos_x, label_pos_y, paste0(letters[1+x], ")"), adj = c(0,0))
-		text(text_pos_x, text_pos_y, cex = 0.95,
+		text(label_pos_x, label_pos_y, paste0("(",letters[1+x], ")"), adj = c(0,0), font = 2)
+		text(text_pos_x, text_pos_y, cex = 0.9,
 				 paste0("D = ", length(igraph::V(as_net)) - as_mat$matching_size, "\n",
@@
 plot.new()
-legend(0.16, 0.9, legend = c("unmatched link", "matched link"), horiz = TRUE,
+legend(0.25, 0.8, legend = c("unmatched link", "matched link"), horiz = TRUE,
 			 lty = 1, 
-			 col = pal[c(2, 4)],
+			 col = pal[c(1, 5)],
 			 lwd = 2, cex = 0.9, xjust=0.5, yjust=0.8, bty = "n")
 
-legend(0.57, 0.9, legend = c("unmatched node", "matched node"), horiz = TRUE,
+legend(0.8, 0.8, legend = c("unmatched node", "matched node"), horiz = TRUE,
 			 pch = 21, 
 			 pt.bg = pal[c(2, 4)],
+			 col = pal[c(1,5)],
 			 pt.cex = 2,
@@
 
-legend(1-0.16 + 0.05, 0.9, legend = expression(paste(bold("  superior node"))), horiz = TRUE,
-			 pch = 21, 
+legend(0.5, 0.35, legend = c("superior node", "non-superior node"), horiz = TRUE,
+			 pch = c(21, 22), 
 			 # pt.bg = pal[c(2, 4)],
-			 pt.cex = c(3),
+			 pt.cex = 2,
 			 cex = 0.9, xjust=0.5, yjust=0.8, bty = "n")

### 2017-02-15 paper/draft_2.Rmd
Daniel's and lupe's suggestions to the theoretical framework

@@
 
-Conveniently, the information necessary to determine whether a network with linear dynamics is controllable, and, equivalently, the minimum number of driver nodes *D* is fully contained in the network structure [@Kalman1963; @Liu2011; @Motter2015].
-We, therefore, start from the assumption that that an ecological network can, at least near equilibrium points, be described by $\frac{dx}{dt} = Ax + Bu(t)$, where the change over time of its state ($\frac{dx}{dt}$) depends on its current state *x* (the species' populations in an ecological context), an external time-varying input *u(t)*, and the matrices *A* and *B*, which encapsulate information about the network structure and how the network responds to the external input, respectively.
+Conveniently, in a network with linear dynamics the information necessary to determine the minimum number of driver nodes *D* is fully contained in the network structure [@Kalman1963; @Liu2011; @Motter2015].
+We, therefore, start  here from the assumption that that an ecological network can, at least near equilibrium points, be described by $\frac{dx}{dt} = Ax + Bu(t)$, where the change over time of its state ($\frac{dx}{dt}$) depends on its current state *x* (for example the species' populations), an external time-varying input *u(t)*, and the matrices *A* and *B*, which encapsulate information about the network structure and how the species respond to the external input, respectively.
 Even though linearity might be a strong assumption, it has been shown that fundamental insight about the control of complex systems can be gained without a detailed knowledge of the nonlinear dynamics and the system parameters [@Liu2015], an important step towards ultimately understanding the controllability of systems with nonlinear dynamics [@Liu2011].
@@
 
-The number of driver nodes *D* not only determines whether a network is controllable or not but can also provide a structural indication of how difficult its control might be.
+The number of driver nodes *D* can provide a structural indication of how difficult its control might be.
 This is because systems that require a large number of external input signals are intuitively more difficult or costly to control.
 In an ecological context, external inputs that modify the state of a node can be thought of as management interventions.
-Therefore, the density of driver nodes $n_D = \frac{D}{S},$ can be seen as a metric of the extent to which network structure can be harnessed for network control.
-For instance, while a hypothetical "network" in which species do not interact but instead function independently from each other would require direct interventions in eversy single species to achieve full control, a linear food chain would require just one species to be directly controlled to knock-on cascading effects trough the trophic levels that compose it.
+Therefore, the density of driver nodes $n_D = \frac{D}{S}$, where *S* is the total number of species in the community, can be seen as a metric of the extent to which network structure can be harnessed for network control.
+For instance, while a hypothetical "network" in which species do not interact but instead function independently from each other would require direct interventions in every single species to achieve full control, a linear food chain would require just one species to be directly controlled to knock-on cascading effects trough the trophic levels that compose it.
 From this perspective, it is possible to use *n~D~* as an index of the manageability of an ecological community, understood in the context of how difficult is to modify the abundances of species in the community using external interventions—a common theme in ecosystem management, conservation, and restoration.
@@
 It has been recently shown that calculating *D* is equivalent to finding a maximum matching in the network [@Liu2011].
-In a directed network, a *matching* consists of a subset of links in which no two of them share a common starting or ending node (Figure 1).
+In a directed network, a *matching* consists of a subset of links in which no two of them share a common starting or ending node (Figure 1, Supporting Information S1).
 A given matching has *maximal cardinality* if the number of matched links (also referred to as the *matching size*) is the largest possible.
 A maximal cardinality matching is then called a *maximum matching* if the sum of the weights of the matched links (also referred to as *matching weight*) is again the largest possible [@West2001].
-Note that this implies that for unweighted binary networks all maximal cardinality matchings are also maximum matchings.
+Note that this implies that for unweighted binary networks, all maximal cardinality matchings are also maximum matchings.
 
@@
 Unmatched nodes are the *driver nodes* *D* because they have no superior in the network and must be directly controlled by an external input [@Liu2011].
-Each matched node, on the other hand, can be controlled by the node that is pointing to it—its superior.
+Each matched node, on the other hand, can be controlled by its superior.
 
@@
 Maximum matchings in a network are often not unique, and each different maximum matching indicates a unique path that can potentially be used to control the network. 
-We harness this property and use a network's multiple maximum matchings to characterise a species' relative importance in driving the state of the community. 
+We harness this property and use a network's complete set of multiple maximum matchings to characterise a species' relative importance in driving the state of the community. 
 One possibility is to characterise a species by the frequency *f~D~* with which it is classified as a driver node.
 However, the role of driver nodes is still ambiguous when **full** network controllability is unfeasible or undesired—which is often the case in ecological settings.
-We therefore also calculate the frequency *f~S~* with which a species is classified as superior nodes, this is the frequency with which they are part of possible control paths—intervention strategies from a management perspective.
+We therefore also calculate the frequency *f~S~* with which a species is classified as superior nodes since this is the frequency with which they form part of possible control paths—intervention strategies from a management perspective.
 
-Most commonly, structural controllability assumes unweighted networks—links exist or not, and hence *f~D~* and *f~S~* can be calculated by computing all possible maximum matchings. 
+Most commonly, structural controllability assumes unweighted networks—links exist or not, and hence *f~D~* and *f~S~* can be calculated by computing all possible maximum cardinality matchings. 
 However, it has been shown that using weighted links can reveal significant ecological patterns and processes that might be undetectable in unweighted networks [@Scotti2007; @Tylianakis2007; @Vazquez2007; @Kaiser-Bunbury2010a].
@@
 We circumvent this issue by calculating all maximal cardinality matchings and subsequently ranking them by their matching weight. 
-By following this approach, we effectively give priority to the species that participate in the pathways that potentially have the largest impact on the community while acknowledging the limitations associated with sampling and its potential restrictions.
+By following this approach, we effectively give priority to the species that participate in the pathways that potentially have the largest impact on the community while acknowledging the limitations associated with sampling and its potential restrictions [@Jordano2016].
 

### 2017-02-15 paper/supp_info_2.Rmd
Move cycles to it's own independent section

@@
 # grid.draw(ttt)
-
-```
-
-In addition, here we also show all the maximum cardinality matchings for an example network in which the links are weighted based on the mutual dependences (Supporting Figure 4).
-It is important to note that using mutual dependencies is problematic for a couple of reasons.
-
-First, having two links between species and using our maximum matching approach to calculate the control configurations, result in matchings that include cycle forming links (Supporting Figure 5).
-Strictly speaking these configurations are maximum matchings in the alternative bipartite configuration (Supporting Figure 1e) but are not in the directed network (Supporting Figure 1f).
-While bidirectional links are the norm when using mutual dependences, they only appear in the asymmetry-weighted networks whenever the mutual dependences between two species symmetric.
-In this special case, we include two links weighted with 0.5 to reflect the fact that the species affect each other in the same proportion.
-Whenever present, we filter out the cycle containing matchings before conducting any analysis.
-In the special case when the network has no matchings that correspond to control configurations, we reduce by one the size of the cliques we enumerate in *H* (Supporting Figure 2).
-
-Second, the number of maximal matchings increasses dispproportionally fast with the number of links in a network.
-For instance, our example network in Figure 1, which is composed by uni-directional links weighted by the asymmetry, has two different maximum matchings.
-In contrast, the equivalent network with bidirectional links has 16 different maximum matchings (Supporting Figure 4 and 5).
-To further ilustrate this growth, some of our empirical networks, had approximately ten thousand different maximum matchings using asymmetries but one hundred million when using mutual dependences.
-This exponential growth, and the computational cost of filtering matchings with cycles, surpassed the capabilities of the available computational resources and rendered us unable to calculate all possible maximum matchings when using mutual dependences in most of our networks.
-
-```{r fig-matchings-bidirectional, echo = F, message = F, warning = F, fig.width = 6.2, fig.height = 3.2, results = "hide", fig.cap = "**Matchings of a simple network with bidirectional links**.
-(a) A network with bidirectional links.
-(b-e) Possible control configurations." }
-par(mfrow=c(2,3), mar=c(0,0,0,0))
-
-bi_net %>% 
-	plot(layout = lay, 
-			 vertex.color = v_c, 
-			 vertex.size = 30,
-			 vertex.label = sp_names_fancy,
-			 vertex.label.family = fam,
-			 vertex.label.color = l_c,
-			 edge.label = round(E(.)$weight,1), 
-			 edge.label.family = fam,
-			 edge.label.color = l_c,
-			 edge.label.cex = l_s,
-			 edge.curved = T,
-			 edge.arrow.size = 0.5,
-			 margin = ma)
-
-text(label_pos_x, label_pos_y, "a)", adj = c(0,0))
-
-1:4 %>%
-	plyr::l_ply(function(x, pal){
-
-		attach(nets[[x]], pos = 1, warn.conflicts = F)
-
-		nets[[x]]$bi_net %>% 
-			plot(layout = lay, 
-					 vertex.size = 30,
-					 vertex.label = names_fancy,
-					 vertex.label.family = fam,
-					 vertex.label.color = l_c,
-					 vertex.label.cex = igraph::V(.)$superior * 0.1 + 0.9,
-					 # vertex.shape = igraph::V(.)$vertex.shape,
-					 vertex.color = pal[igraph::V(.)$matched],
-					 edge.color = pal[igraph::E(.)$matched],
-					 # edge.color = c("#B2ABD2", "#FDB863"),
-					 edge.label = NA, 
-					 edge.width = E(.)$matched/2,
-					 edge.label.family = fam,
-					 edge.label.color = igraph::E(.)$matched,
-					 edge.label.cex = l_s,
-					 edge.curved = T,
-					 edge.arrow.size = 0.5,
-					 margin = ma, 
-					 palette = pal) %>% 
-			print()
-
-		igraph::V(bi_net)$name <- sp_names
-
-		text(label_pos_x, label_pos_y, paste0(letters[1+x], ")"), adj = c(0,0))
-		text(text_pos_x, text_pos_y, cex = 0.95,
-				 paste0("D = ", length(igraph::V(bi_net)) - as_mat$matching_size, "\n",
-				 			 "matching size: ", as_mat$matching_size, "\n",
-				 			 "matching weight: ", round(matching_weight, 1)))
-	}, pal)
-
-plot.new()
-legend(0.5, 0.7, legend = c("unmatched link", "matched link"), horiz = F,
-			 lty = 1, 
-			 col = pal[c(2, 4)],
-			 lwd = 2, cex = 0.9, xjust=0.5, yjust=1, bty = "n")
-
-legend(0.5, 0.5, legend = c("unmatched node", "matched node"), horiz = F,
-			 pch = 21, 
-			 pt.bg = pal[c(2, 4)],
-			 pt.cex = 2,
-			 cex = 0.9, xjust=0.5, yjust=1, bty = "n")
-
-legend(0.5, 0.3, legend = expression(paste(bold("(bold label)"), " ", "superior nodes")), horiz = TRUE,
-			 cex = 0.9, xjust=0.5, yjust=1, bty = "n")
-
-```
-
-```{r  fig-matchings-bidirectional-no, echo = F, message = F, warning = F, fig.width = 6.2, fig.height = 4.8, results = "hide", fig.cap= "**Cycles in a bidirectional network**.
-Our approach finds twelve configurations for Supporting Figure 4a that are not actual matchings."}
-
-par(mfrow=c(3,4), mar=c(0,0,0,0))
-5:length(nets) %>%
-	plyr::l_ply(function(x, pal){
-
-		attach(nets[[x]], pos = 1, warn.conflicts = F)
-
-		nets[[x]]$bi_net %>% 
-			plot(layout = lay, 
-					 vertex.size = 30,
-					 vertex.label = names_fancy,
-					 vertex.label.family = fam,
-					 vertex.label.color = l_c,
-					 vertex.label.cex = igraph::V(.)$superior * 0.1 + 0.9,
-					 # vertex.shape = igraph::V(.)$vertex.shape,
-					 vertex.color = pal[igraph::V(.)$matched],
-					 edge.color = pal[igraph::E(.)$matched],
-					 # edge.color = c("#B2ABD2", "#FDB863"),
-					 edge.label = NA, 
-					 edge.width = E(.)$matched/2,
-					 edge.label.family = fam,
-					 edge.label.color = igraph::E(.)$matched,
-					 edge.label.cex = l_s,
-					 edge.curved = T,
-					 edge.arrow.size = 0.5,
-					 margin = ma, 
-					 palette = pal) %>% 
-			print()
-
-		igraph::V(bi_net)$name <- sp_names
-
-		# text(label_pos_x, label_pos_y, paste0(letters[1+x-5], ")"), adj = c(0,0))
-		# text(text_pos_x, text_pos_y, cex = 0.95,
-		# 		 paste0("D = ", length(igraph::V(bi_net)) - as_mat$matching_size, "\n",
-		# 		 			 "matching size: ", as_mat$matching_size, "\n",
-		# 		 			 "matching weight: ", round(matching_weight, 1)))
-	}, pal)
 
@@
 Nevertheless visitation is not equivalent to pollen deposition and might be insufficient to reflect the dependencies of plants on animals and vice versa [@Alarcon2010; @King2013]. 
-We therefore investigated the effect of calculating the dependencies using visitation or pollination effectiveness and importance---two metrics more proximate to plant reproductive success (Supporting Figure 6).
+We therefore investigated the effect of calculating the dependencies using visitation or pollination effectiveness and importance---two metrics more proximate to plant reproductive success (Supporting Figure 4).
 We did this by comparing *(i)* the manageability of the community and *(ii)* the percentage of interactions that maintained the direction of dependency. 
@@
 
-At a network scale, despite marked differences in the distribution of weights of the three networks (Supporting Figure 6), the driver node density *n~D~* was consistent among the three different approaches (`r 1-round(n_driver$n_driver[n_driver$net_name == "bal_eff"], digits = 2)` for deposition, `r 1-round(n_driver$n_driver[n_driver$net_name == "bal_vis"], digits = 2)` for the visitation, and `r 1-round(n_driver$n_driver[n_driver$net_name == "bal_imp"], digits = 2)` for the pollinator importance network).
+At a network scale, despite marked differences in the distribution of weights of the three networks (Supporting Figure 4), the driver node density *n~D~* was consistent among the three different approaches (`r 1-round(n_driver$n_driver[n_driver$net_name == "bal_eff"], digits = 2)` for deposition, `r 1-round(n_driver$n_driver[n_driver$net_name == "bal_vis"], digits = 2)` for the visitation, and `r 1-round(n_driver$n_driver[n_driver$net_name == "bal_imp"], digits = 2)` for the pollinator importance network).
 
@@
 Overall, the results of the sensitivity analysis indicate that our approach might be useful for management even in the absence of complete sampling. 
-Specifically as the proportion of sampled interaction decreassed, the variability of $n_D$ increassed, but was overall very similar when compared to that obtained using all available interactions (Supporting Figure 7a).
-Similarly, the correlation between the relative frequency with which species are classified as a driver ($f_D$) or as a superior node ($f_S$) was correlated ever for *extreme* levels of undersampling.
+Specifically as the proportion of sampled interaction decreassed, the variability of $n_D$ increassed, but was overall very similar when compared to that obtained using all available interactions (Supporting Figure 5a).
+Similarly, the correlation between the relative frequency with which species are classified as a driver ($f_D$) or as a superior node ($f_S$) was correlated ever for *extreme* levels of undersampling (Supporting figure 5b).
 For instance, we found that with a sampling level of 0.5, the mean spearman correlation coefficient was 0.66 for $f_D$ and 0.76 for $f_S$. 
@@
 
+# S5: Chosing the direction of control
+
+At a first glance our decision to adopt the direction the assymetries and not the bidirectional dependences as the direction of control might seem uneccessary. 
+Nevertheless we find that it better reflect
+Our decision to adopt the direction of asymmetries as the direction of control is basedmainIn addition, here we also show all the maximum cardinality matchings for an example network in which the links are weighted based on the mutual dependences (Supporting Figure 6).
+It is important to note that using mutual dependencies is problematic for a couple of reasons.
+
+First, having two links between species and using our maximum matching approach to calculate the control configurations, result in matchings that include cycle forming links (Supporting Figure 7).
+Strictly speaking these configurations are maximum matchings in the alternative bipartite configuration (Supporting Figure 1e) but are not in the directed network (Supporting Figure 1f).
+While bidirectional links are the norm when using mutual dependences, they only appear in the asymmetry-weighted networks whenever the mutual dependences between two species symmetric.
+In this special case, we include two links weighted with 0.5 to reflect the fact that the species affect each other in the same proportion.
+Whenever present, we filter out the cycle containing matchings before conducting any analysis.
+In the special case when the network has no matchings that correspond to control configurations, we reduce by one the size of the cliques we enumerate in *H* (Supporting Figure 2).
+
+Second, the number of maximal matchings increasses dispproportionally fast with the number of links in a network.
+For instance, our example network in Figure 1, which is composed by uni-directional links weighted by the asymmetry, has two different maximum matchings.
+In contrast, the equivalent network with bidirectional links has 16 different maximum matchings (Supporting Figure 6 and 7).
+To further ilustrate this growth, some of our empirical networks, had approximately ten thousand different maximum matchings using asymmetries but one hundred million when using mutual dependences.
+This exponential growth, and the computational cost of filtering matchings with cycles, surpassed the capabilities of the available computational resources and rendered us unable to calculate all possible maximum matchings when using mutual dependences in most of our networks.
+
+```{r fig-matchings-bidirectional, echo = F, message = F, warning = F, fig.width = 6.2, fig.height = 3.2, results = "hide", fig.cap = "**Matchings of a simple network with bidirectional links**.
+(a) A network with bidirectional links.
+(b-e) Possible control configurations." }
+par(mfrow=c(2,3), mar=c(0,0,0,0))
+
+bi_net %>% 
+	plot(layout = lay, 
+			 vertex.color = v_c, 
+			 vertex.size = 30,
+			 vertex.label = sp_names_fancy,
+			 vertex.label.family = fam,
+			 vertex.label.color = l_c,
+			 edge.label = round(E(.)$weight,1), 
+			 edge.label.family = fam,
+			 edge.label.color = l_c,
+			 edge.label.cex = l_s,
+			 edge.curved = T,
+			 edge.arrow.size = 0.5,
+			 margin = ma)
+
+text(label_pos_x, label_pos_y, "a)", adj = c(0,0))
+
+1:4 %>%
+	plyr::l_ply(function(x, pal){
+
+		attach(nets[[x]], pos = 1, warn.conflicts = F)
+
+		nets[[x]]$bi_net %>% 
+			plot(layout = lay, 
+					 vertex.size = 30,
+					 vertex.label = names_fancy,
+					 vertex.label.family = fam,
+					 vertex.label.color = l_c,
+					 vertex.label.cex = igraph::V(.)$superior * 0.1 + 0.9,
+					 # vertex.shape = igraph::V(.)$vertex.shape,
+					 vertex.color = pal[igraph::V(.)$matched],
+					 edge.color = pal[igraph::E(.)$matched],
+					 # edge.color = c("#B2ABD2", "#FDB863"),
+					 edge.label = NA, 
+					 edge.width = E(.)$matched/2,
+					 edge.label.family = fam,
+					 edge.label.color = igraph::E(.)$matched,
+					 edge.label.cex = l_s,
+					 edge.curved = T,
+					 edge.arrow.size = 0.5,
+					 margin = ma, 
+					 palette = pal) %>% 
+			print()
+
+		igraph::V(bi_net)$name <- sp_names
+
+		text(label_pos_x, label_pos_y, paste0(letters[1+x], ")"), adj = c(0,0))
+		text(text_pos_x, text_pos_y, cex = 0.95,
+				 paste0("D = ", length(igraph::V(bi_net)) - as_mat$matching_size, "\n",
+				 			 "matching size: ", as_mat$matching_size, "\n",
+				 			 "matching weight: ", round(matching_weight, 1)))
+	}, pal)
+
+plot.new()
+legend(0.5, 0.7, legend = c("unmatched link", "matched link"), horiz = F,
+			 lty = 1, 
+			 col = pal[c(2, 4)],
+			 lwd = 2, cex = 0.9, xjust=0.5, yjust=1, bty = "n")
+
+legend(0.5, 0.5, legend = c("unmatched node", "matched node"), horiz = F,
+			 pch = 21, 
+			 pt.bg = pal[c(2, 4)],
+			 pt.cex = 2,
+			 cex = 0.9, xjust=0.5, yjust=1, bty = "n")
+
+legend(0.5, 0.3, legend = expression(paste(bold("(bold label)"), " ", "superior nodes")), horiz = TRUE,
+			 cex = 0.9, xjust=0.5, yjust=1, bty = "n")
+
+```
+
+```{r  fig-matchings-bidirectional-no, echo = F, message = F, warning = F, fig.width = 6.2, fig.height = 4.8, results = "hide", fig.cap= "**Cycles in a bidirectional network**.
+Our approach finds twelve configurations for Supporting Figure 6a that are not actual matchings."}
+
+par(mfrow=c(3,4), mar=c(0,0,0,0))
+5:length(nets) %>%
+	plyr::l_ply(function(x, pal){
+
+		attach(nets[[x]], pos = 1, warn.conflicts = F)
+
+		nets[[x]]$bi_net %>% 
+			plot(layout = lay, 
+					 vertex.size = 30,
+					 vertex.label = names_fancy,
+					 vertex.label.family = fam,
+					 vertex.label.color = l_c,
+					 vertex.label.cex = igraph::V(.)$superior * 0.1 + 0.9,
+					 # vertex.shape = igraph::V(.)$vertex.shape,
+					 vertex.color = pal[igraph::V(.)$matched],
+					 edge.color = pal[igraph::E(.)$matched],
+					 # edge.color = c("#B2ABD2", "#FDB863"),
+					 edge.label = NA, 
+					 edge.width = E(.)$matched/2,
+					 edge.label.family = fam,
+					 edge.label.color = igraph::E(.)$matched,
+					 edge.label.cex = l_s,
+					 edge.curved = T,
+					 edge.arrow.size = 0.5,
+					 margin = ma, 
+					 palette = pal) %>% 
+			print()
+
+		igraph::V(bi_net)$name <- sp_names
+
+		# text(label_pos_x, label_pos_y, paste0(letters[1+x-5], ")"), adj = c(0,0))
+		# text(text_pos_x, text_pos_y, cex = 0.95,
+		# 		 paste0("D = ", length(igraph::V(bi_net)) - as_mat$matching_size, "\n",
+		# 		 			 "matching size: ", as_mat$matching_size, "\n",
+		# 		 			 "matching weight: ", round(matching_weight, 1)))
+	}, pal)
+
+```
+
 # References

### 2017-02-16 paper/supp_info_2.Rmd
Add direction of control section

@@
   dplyr::rename_("net_name" = ".id")
+a_m <- readRDS("../data/processed/n_matched_all_types.rds")
 
@@
 
-At a first glance our decision to adopt the direction the assymetries and not the bidirectional dependences as the direction of control might seem uneccessary. 
-Nevertheless we find that it better reflect
-Our decision to adopt the direction of asymmetries as the direction of control is basedmainIn addition, here we also show all the maximum cardinality matchings for an example network in which the links are weighted based on the mutual dependences (Supporting Figure 6).
-It is important to note that using mutual dependencies is problematic for a couple of reasons.
-
-First, having two links between species and using our maximum matching approach to calculate the control configurations, result in matchings that include cycle forming links (Supporting Figure 7).
-Strictly speaking these configurations are maximum matchings in the alternative bipartite configuration (Supporting Figure 1e) but are not in the directed network (Supporting Figure 1f).
-While bidirectional links are the norm when using mutual dependences, they only appear in the asymmetry-weighted networks whenever the mutual dependences between two species symmetric.
+Our decision to adopt the direction of asymmetries as the direction of control, while coherent with ecological processes, confers several advantages. 
+First it is consistent with previous studies, which facilitates the comparability between our findings and those in other systems explored using structural controlability. 
+Second, it reduces the number of control cycles in the network—which require special treatment in our approach. 
+And third, the reduced number of links, facilitates the computation of all possible maximum matchings.
+
+For ilustration, we show all maximum cardinality matchings for an example network in which links are weighted based on the mutual dependences (Supporting figure 6). 
+We note, however, that using mutual dependences, or any set up that can lead to bidirectional links, is problematic for a couple of reasons. 
+First, having two links between interacting species and using our maximum matching approach to calculate the control configurations, can result in matchings that include cycle inducing links (Supporting Figure 7).
+Strictly speaking these configurations are maximum matchings in the alternative bipartite configuration (Supporting Figure 1e) but not in the directed network (Supporting Figure 1f). 
+While bidirectional links are the norm when using mutual dependences, they only appear in the asymmetry-weighted networks whenever the mutual dependences between two species are strictly symmetric. 
 In this special case, we include two links weighted with 0.5 to reflect the fact that the species affect each other in the same proportion.
-Whenever present, we filter out the cycle containing matchings before conducting any analysis.
-In the special case when the network has no matchings that correspond to control configurations, we reduce by one the size of the cliques we enumerate in *H* (Supporting Figure 2).
-
-Second, the number of maximal matchings increasses dispproportionally fast with the number of links in a network.
-For instance, our example network in Figure 1, which is composed by uni-directional links weighted by the asymmetry, has two different maximum matchings.
-In contrast, the equivalent network with bidirectional links has 16 different maximum matchings (Supporting Figure 6 and 7).
-To further ilustrate this growth, some of our empirical networks, had approximately ten thousand different maximum matchings using asymmetries but one hundred million when using mutual dependences.
-This exponential growth, and the computational cost of filtering matchings with cycles, surpassed the capabilities of the available computational resources and rendered us unable to calculate all possible maximum matchings when using mutual dependences in most of our networks.
 
@@
 
-```{r  fig-matchings-bidirectional-no, echo = F, message = F, warning = F, fig.width = 6.2, fig.height = 4.8, results = "hide", fig.cap= "**Cycles in a bidirectional network**.
+```{r  fig-matchings-bidirectional-no, echo = F, message = F, warning = F, fig.width = 6.2, fig.height = 2.4, results = "hide", fig.cap= "**Cycles in a bidirectional network**.
 Our approach finds twelve configurations for Supporting Figure 6a that are not actual matchings."}
 
-par(mfrow=c(3,4), mar=c(0,0,0,0))
+par(mfrow=c(2,6), mar=c(0,0,0,0))
 5:length(nets) %>%
@@
 			plot(layout = lay, 
-					 vertex.size = 30,
+					 vertex.size = 35,
 					 vertex.label = names_fancy,
@@
 					 vertex.label.color = l_c,
-					 vertex.label.cex = igraph::V(.)$superior * 0.1 + 0.9,
+					 vertex.label.cex = igraph::V(.)$superior * 0.1 + 0.6,
 					 # vertex.shape = igraph::V(.)$vertex.shape,
@@
 					 edge.label = NA, 
-					 edge.width = E(.)$matched/2,
+					 edge.width = E(.)$matched/3,
 					 edge.label.family = fam,
@@
 
+We consider two approaches to tackle this limitation. 
+The first approach, is to calculate the matching(s) as usual and then, before calculating $f_S$ and $f_D$, filter out the cycle (Supporting Figure 7). 
+In the special case that the network has no maximal matchings that correspond to feasible control configurations, because they all include cycles, we reduce the size of the cliques we enumerate in $H$ (Supporting figure 2) and repeat.
+The second approach is, instead of calculating the matching(s) for the network with bidirectional cycles, we calculate the matching(s) of $2^n$ unidirectional versions of the network, where $n$ is the number of cycles in the network (Supporting figure 8).
+We then average over the unidirectional networks to find the overall $f_S$ and $f_D$ for a given species.
+
+The number of maximal matchings increases disproportionally fast with the number of links in a network. 
+For instance, our example network in Figure 1, which is composed of unidirectional links weighted by the asymmetry, has two different maximum matchings. 
+In contrast, the equivalent network with bidirectional links has 16 different maximum matchings (Supporting Figure 6 and 7). 
+To further ilustrate the implications of this growth, some of our empirical networks had approximately ten thousand different maximum matchings using asymmetries but one hundred million when using mutual dependences.
+This exponential growth, and the computational cost of either filtering matchings with cycles or calculating the matchings for $2^n$ networks, surpassed the capabilities of the available computational resources and rendered us unable to calculate all possible maximum matchings when using mutual dependences in most of our bidirectional networks.
+Nevertheless, as most of our networks weighted by asymmetry had between zero and four cycles, we successfully used the second approach explained in the previous paragraph to calculate the all maximum matchings for these networks.
+
+```{r fig-tackle-cycles, echo = F, message = F, warning = F, fig.width = 3.3, fig.height = 1.5, results = "hide", fig.cap= "**Dealing with cycles**.
+The network on the left, which has *n = 2* cycles, can be decomposed in *2^n^* unidirectional networs."}
+layout(matrix(c(1,2,3, 1,4, 5), ncol = 3, byrow = TRUE), widths = c(2, 1,1))
+par( mar=c(0,0,0,0))
+
+set.seed(3)
+g_one_bi <- matrix(c(0,1,1,1,0,1,1,0,0), ncol = 3) %>%
+	igraph::graph_from_adjacency_matrix()
+lay_g_one_bi <- layout_nicely(g_one_bi)
+
+plot(g_one_bi, 
+		 edge.curved = c(T, T, T, T, T), 
+		 layout = lay_g_one_bi, 
+		 vertex.color = NA, 
+		 vertex.label = NA,
+		 vertex.size = 30, 
+				 edge.arrow.size = 0.5,
+		 margin = c(0,0,0,0.5))
+text(-1, 1.1, "(a)", font = 2, cex = 0.9)
+text(1.65, 1.1, "(b)", font = 2, cex = 0.9)
+
+# xline <- 1.5
+# arrows(x0 = xline, y0=-2, x1=xline, y1=2, col='grey30', length=0, lwd=1)
+per <- gtools::permutations(2, 2, v = c(1,3), repeats.allowed = T)
+per[, 2] <- per[, 2] + 1
+per %>%
+	plyr::a_ply(1, function(x){
+		print(x)
+	g_one_bi%>% 
+		delete_edges(x) %>% 
+		plot(layout = lay_g_one_bi, 
+				 vertex.color = NA, 
+				 vertex.label = NA,
+				 vertex.size = 40, 
+				 edge.arrow.size = 0.3)
+
+})
+
+```
+
+We highlight that althoug the direction of control might affect the $f_S$ and $f_D$, it doesn't affect strongly the network's relative density of driver nodes $n_D$. 
+We reached this conclusion by calculating the $n_D$ obtained assuming that (a) the direction of control is governed by the asymmetry or (b) bidirectional dependences, (c) that plants depend on pollinators, and that (d) pollinators depend on plants.
+Although the $n_D$ values were quantitatively different between the approaches (Supporting figure 9), the Spearman correlation among these four options suggested a very high agreement (Supporting table 3).
+
+```{r fig-alternative-assumptions, echo = F, message = F, warning = F, fig.width = 4, fig.height = 1.6, results = "hide", fig.cap= "**Absolute differences among asumptions on the direction of control.**"}
+
+a_m_driver <- a_m %>% 
+  dplyr::full_join(meta) %>%
+  dplyr::filter(study != "ballantyne") %>% 
+  dplyr::mutate(type = factor(type, 
+                              levels =  c("AB", "BA", "weight", "z-bi"),
+                              labels = c("pla. to pol.", "pol. to pla.", "asymmetry", "bidirectional dep.")),
+                type_l  = as.character(type)) %>%
+  dplyr::mutate(n_driver = n_pla + n_pol - n_matched, 
+                n_driver_rel = 1 - n_matched / (n_pla + n_pol))
+
+type_l <- unique(a_m_driver$type_l)
+
+a_m_driver %>%
+  ggplot(aes(x = type, y = n_driver_rel), parse = T) +
+  geom_boxplot(size = 0.25, colour = "grey10",
+							 outlier.shape = 21, outlier.size = 1) +
+  coord_flip() + 
+  xlab("") +
+  ylab(expression(n[D])) + 
+  fer_theme + 
+  theme(plot.margin = grid::unit(c(0,1,2,0), "mm"))
+
+```
+
+```{r table-alternative-assumptions, echo = FALSE, warning = F, message = F, results = "asis", sanitize = FALSE}
+
+corr_matrix <- a_m_driver %>%
+  dplyr::select(net_name, type, n_driver) %>%
+  tidyr::spread(type, n_driver) %>%
+  dplyr::select(-net_name) %>%
+  as.matrix() %>%
+  cor(method = "spearman") %>%
+  round(digits = 2)
+
+corr_matrix[lower.tri(corr_matrix, diag = T)] <- ""
+corr_matrix <- corr_matrix[, -1]
+corr_matrix <- corr_matrix[-(nrow(corr_matrix)), ]
+
+ corr_matrix %>% 
+  xtable::xtable(caption = "\\textbf{Agreement among assumptions on the direction of control}.
+Spearman correlation coefficients of the number of driver nodes $n_D$ four different assumptions of the direction of control..") %>%
+	print(comment = FALSE, include.rownames = TRUE)
+
+```
+
+# S6: Using control profile heuristics
+
 # References

### 2017-02-17 paper/supp_info_2.Rmd
Fix figure names, numbers and format

@@
 - \usepackage{float}
-- \usepackage{rotating}
-- \renewcommand{\figurename}{Supporting Figure}
-- \renewcommand{\tablename}{Supporting Table}
+- \renewcommand{\thefigure}{S\arabic{figure}}
+- \renewcommand{\thetable}{S\arabic{table}}
+- \usepackage[tableposition=top]{caption}
 documentclass: artikel1
@@
 
+		igraph::E(bi_net)$matched_col <- 1
+		igraph::E(bi_net)$matched_col[as_all_mat[[x]]] <- 5
+
 		igraph::V(bi_net)$matched <- 2
@@
 
+		igraph::V(bi_net)$matched_border <- 1
+		igraph::V(bi_net)$matched_border[igraph::V(bi_net)$name %in%
+																ends(bi_net, as_all_mat[[x]])[, 2]] <- 5
+
 		igraph::V(bi_net)$superior <- 1
@@
 
+		igraph::V(bi_net)$superior_shape <- "circle"
+		igraph::V(bi_net)$superior_shape[igraph::V(bi_net)$name %in%
+																ends(bi_net, as_all_mat[[x]])[, 1]] <- "square"
+
 		names_fancy <- sp_names_fancy
-		names_fancy[igraph::V(bi_net)$name %in%
-																ends(bi_net, as_all_mat[[x]])[, 1]] <-
-			sp_names_fancy_b[igraph::V(bi_net)$name %in%
-																ends(bi_net, as_all_mat[[x]])[, 1]]
+		# names_fancy[igraph::V(bi_net)$name %in%
+		# 														ends(bi_net, as_all_mat[[x]])[, 1]] <-
+		# 	sp_names_fancy_b[igraph::V(bi_net)$name %in%
+		# 														ends(bi_net, as_all_mat[[x]])[, 1]]
 
@@
 
-We start with a directed network in which the direction of the link represents the direction of control (Supporting figure 1a).
-We then construct an alternative representation of the directed network in which each node of the directed network is represented by two nodes that indicate their outgoing and incoming links (Supporting figure 1b).
+We start with a directed network in which the direction of the link represents the direction of control (Figure S1a).
+We then construct an alternative representation of the directed network in which each node of the directed network is represented by two nodes that indicate their outgoing and incoming links (Figure S1b).
 Finding a maximum matching in this alternative representation is equivalent to finding the largest possible set of edges in which one node in the left hand side is connected to at most one node in the right hand side.
 To find the maximum matching we use the push-relabel algorithm implemented in `max_bipartite_matching` in the R package igraph 1.0.1 [@Csardi2006a].
-Once we have the matching shown in the Supporting Figure 1b, it is then easy to identify the roles of each node in this representation: nodes on the right hand side that are connected to a matched link (purple) are matched, while those connected to a matched link on the left hand side are superior.
-This information can then be mapped back to the original representation to identify the control paths and the driver nodes in the network (Supporting Figure 1c).
-Supporting Figure 1d, e, and f ilustrate this approach for a network with bidirectional links.
+Once we have the matching shown in the Figure S1b, it is then easy to identify the roles of each node in this representation: nodes on the right hand side that are connected to a matched link (purple) are matched, while those connected to a matched link on the left hand side are superior.
+This information can then be mapped back to the original representation to identify the control paths and the driver nodes in the network (Figure S1c).
+Figure S1d, e, and f ilustrate this approach for a network with bidirectional links.
 
@@
 layout(matrix(c(1,2,3,4, 5, 6, 7, 7, 7), 3, 3, byrow = TRUE),
-  	heights=c(8,8,1))
+  	heights=c(8,8,2))
 par( mar=c(0,0,0,0))
@@
 
-text(label_pos_x, label_pos_y, "a)", adj = c(0,0))
+text(label_pos_x, label_pos_y, "(a)", adj = c(0,0), font = 2, cex = 0.9)
 
@@
 
+igraph::E(bi_as_net)$matched_col <- 1
+igraph::E(bi_as_net)$matched_col[as_all_mat[[1]]] <- 5
+
 bi_as_net %>%
@@
 			 vertex.color = NA,
-			 edge.color = pal[E(.)$matched],
+			 edge.color = pal[E(.)$matched_col],
 			 edge.label = NA, 
@@
 
-text(-0.95, 0.825, "b)", adj = c(0,0))
+text(-0.95, 0.825, "(b)", adj = c(0,0), font = 2, cex = 0.9)
 
@@
 E(as_net)$matched[as_all_mat[[1]]] <- 4
+
+E(as_net)$matched_col <- 1
+E(as_net)$matched_col[as_all_mat[[1]]] <- 5
 
@@
 
+igraph::V(as_net)$matched_border <- 1
+igraph::V(as_net)$matched_border[igraph::V(as_net)$name %in%
+														ends(as_net, as_all_mat[[1]])[, 2]] <- 5
+
 igraph::V(as_net)$superior <- 1
@@
 
+igraph::V(as_net)$superior_shape <- "circle"
+igraph::V(as_net)$superior_shape[igraph::V(as_net)$name %in%
+													 	ends(as_net, as_all_mat[[1]])[, 1]] <- "square"
+
 names_fancy <- sp_names_fancy
-		names_fancy[igraph::V(as_net)$name %in%
-																ends(as_net, as_all_mat[[1]])[, 1]] <-
-			sp_names_fancy_b[igraph::V(as_net)$name %in%
-																ends(as_net, as_all_mat[[1]])[, 1]]
+# names_fancy[igraph::V(as_net)$name %in%
+# 							ends(as_net, as_all_mat[[1]])[, 1]] <-
+# 	sp_names_fancy_b[igraph::V(as_net)$name %in%
+# 									 	ends(as_net, as_all_mat[[1]])[, 1]]
 
@@
 	plot(layout = lay, 
-					 vertex.size = igraph::V(.)$superior * 10 + 20,
+			 vertex.size = 30,
+			 vertex.shape = igraph::V(.)$superior_shape,
 			 vertex.label = names_fancy,
@@
 			 vertex.color = pal[igraph::V(.)$matched],
-					 edge.color = pal[E(.)$matched],
+			 vertex.frame.color = pal[igraph::V(.)$matched_border],
+			 edge.color = pal[E(.)$matched_col],
 			 edge.label = NA, 
@@
 
-text(label_pos_x, label_pos_y, "c)", adj = c(0,0))
+text(label_pos_x, label_pos_y, "(c)", adj = c(0,0), font = 2, cex = 0.9)
 
@@
 			 margin = ma)
-text(label_pos_x, label_pos_y, "d)", adj = c(0,0))
+text(label_pos_x, label_pos_y, "(d)", adj = c(0,0), font = 2, cex = 0.9)
 
@@
 igraph::E(bi_bi_net)$matched[nets[[i]]$as_all_mat] <- 4
+
+igraph::E(bi_bi_net)$matched_col <- 1
+igraph::E(bi_bi_net)$matched_col[nets[[i]]$as_all_mat] <- 5
 
@@
 			 vertex.color = NA, 
-			 edge.color = pal[igraph::E(.)$matched],
+			 edge.color = pal[igraph::E(.)$matched_col],
 			 # edge.label = round(E(.)$weight,1), 
@@
 
-text(-0.95, 0.825, "e)", adj = c(0,0))
+text(-0.95, 0.825, "(e)", adj = c(0,0), font = 2, cex = 0.9)
 
@@
 			 vertex.label = nets[[1]]$names_fancy,
-			 vertex.size = igraph::V(.)$superior * 10 + 20,
+			 vertex.shape = igraph::V(.)$superior_shape,
+			 vertex.size = 30,
 			 vertex.label.family = fam,
@@
 			 vertex.color = pal[igraph::V(.)$matched],
-			 edge.color = pal[igraph::E(.)$matched],
+			 vertex.frame.color = pal[igraph::V(.)$matched_border],
+			 edge.color = pal[igraph::E(.)$matched_col],
 			 # edge.label = round(E(.)$weight,1), 
@@
 
-text(label_pos_x, label_pos_y, "f)", adj = c(0,0))
+text(label_pos_x, label_pos_y, "(f)", adj = c(0,0), font = 2, cex = 0.9)
 
@@
 plot.new()
-legend(0.16, 0.9, legend = c("unmatched link", "matched link"), horiz = TRUE,
+legend(0.55, 0.8, legend = c("unmatched link", "matched link"), horiz = TRUE,
 			 lty = 1, 
-			 col = pal[c(2, 4)],
+			 col = pal[c(1, 5)],
 			 lwd = 2, cex = 0.9, xjust=0.5, yjust=0.8, bty = "n")
 
-legend(0.57, 0.9, legend = c("unmatched node", "matched node"), horiz = TRUE,
+legend(0.89, 0.8, legend = c("unmatched node", "matched node"), horiz = TRUE,
 			 pch = 21, 
 			 pt.bg = pal[c(2, 4)],
+			 col = pal[c(1,5)],
 			 pt.cex = 2,
@@
 
-legend(1-0.16 + 0.05, 0.9, legend = expression(paste(bold("  superior node"))), horiz = TRUE,
-			 pch = 21, 
+legend(0.7, 0.35, legend = c("superior node", "non-superior node"),
+			 horiz = TRUE,
+			 pch = c(22, 21), 
 			 # pt.bg = pal[c(2, 4)],
-			 pt.cex = c(3),
+			 pt.cex = 2,
 			 cex = 0.9, xjust=0.5, yjust=0.8, bty = "n")
@@
 To do that we need to calculate all possible maximum matchings (or all maximal cardinality matchings in weighted networks like ours).
-We start from the alternative bipartite representation in Supporting Figure 1b and assign an identity to each of the links in the network (shown as numbers in Supporting Figure 2a).
+We start from the alternative bipartite representation in Figure S1b and assign an identity to each of the links in the network (shown as numbers in Figure S2a).
 We will call this bipartite representation *B*.
-We then construct the line graph of the alternative bipartite representation *L(B)* (Supporting Figure 2b).
+We then construct the line graph of the alternative bipartite representation *L(B)* (Figure S2b).
 Each node in *L(B)* represents a link in *B* and are connected to each other only if they share a common node in *B*.
-We calculate the complement graph of *L(B)* and idetify all the maximum cliques (Supporting Figure 2c).
+We calculate the complement graph of *L(B)* and idetify all the maximum cliques (Figure S2c).
 Here some extra definitions are neccessary.
@@
 
-text(-1, 1, "a)", adj = c(0,0))
+text(-1, 1, "(a)", adj = c(0,0), font = 2, cex = 0.9)
 
@@
 
-text(-1, 1, "b)", adj = c(0,0))
+text(-1, 1, "(b)", adj = c(0,0), font = 2, cex = 0.9)
 
@@
 
-text(-1, 1, "c)", adj = c(0,0))
+text(-1, 1, "(c)", adj = c(0,0), font = 2, cex = 0.9)
 
@@
 In the main text we show all maximum cardinality matchings for a simple example network.
-To further ilustrate our methodology, here we also show the approach for the smallest of our empirical networks, the uninvaded network at site 10 (Supporting Table 1; Supporting Figure 3).
+To further ilustrate our methodology, here we also show the approach for the smallest of our empirical networks, the uninvaded network at site 10 (Table S1; Figure S3).
 The largest component of this network is composed by 16 species of which 2 are non-invasive plants and the rest are pollinators.
@@
 (b) The directed network in which the direction of control and the magnitude of the asymmetry are determined based on the mutual dependences.
-(c) One of the possible maximum matchings calculated using the procedures illustrated in the Supporting Figure 1 and 2."}
+(c) One of the possible maximum matchings calculated using the procedures illustrated in the Figure S1 and S2."}
 par(mfrow=c(2,2), mar=c(0,0,0,0))
@@
 			 layout = la)
-text(label_pos_x, label_pos_y, paste0(letters[1], ")"), adj = c(0,0))
+text(label_pos_x, label_pos_y, paste0("(", letters[1], ")"), adj = c(0,0), font = 2, cex = 0.8)
 
@@
 
-text(label_pos_x, label_pos_y, paste0(letters[2], ")"), adj = c(0,0))
+text(label_pos_x, label_pos_y, paste0("(", letters[2], ")"), adj = c(0,0), font = 2, cex = 0.8)
 
@@
 
+		E(as_net)$matched_col <- 1
+		E(as_net)$matched_col[as_all_mat[[x]]] <- 5
+
 		igraph::V(as_net)$matched <- 2
@@
 																ends(as_net, as_all_mat[[x]])[, 2]] <- 4
+		igraph::V(as_net)$matched_border <- 1
+		igraph::V(as_net)$matched_border[igraph::V(as_net)$name %in%
+																ends(as_net, as_all_mat[[x]])[, 2]] <- 5
 
@@
 																ends(as_net, as_all_mat[[x]])[, 1]] <- 2
+
+		igraph::V(as_net)$superior_shape <- "circle"
+		igraph::V(as_net)$superior_shape[igraph::V(as_net)$name %in%
+																ends(as_net, as_all_mat[[x]])[, 1]] <- "square"
 
@@
 			plot(layout = la, 
-					 vertex.size = igraph::V(.)$superior * 7 + 7,
+					 vertex.size = 15,
 					 vertex.label = replace_names$sp_letter,
+					 vertex.shape = igraph::V(.)$superior_shape,
 					 vertex.label.family = fam,
@@
 					 vertex.color = pal[igraph::V(.)$matched],
-					 edge.color = pal[E(.)$matched],
+					 vertex.frame.color = pal[igraph::V(.)$matched_border],
+					 edge.color = pal[E(.)$matched_col],
 					 edge.label = NA, 
@@
 					 edge.label.family = fam,
-					 edge.label.color = igraph::E(.)$matched,
+					 edge.label.color = igraph::E(.)$matched_col,
 					 edge.label.cex = l_s,
@@
 
-		text(label_pos_x, label_pos_y, paste0(letters[2+x], ")"), adj = c(0,0))
-		text(text_pos_x + 0.2, text_pos_y + 0.1, cex = 0.95,
+		text(label_pos_x, label_pos_y, paste0("(", letters[2+x], ")"), adj = c(0,0), font = 2, cex = 0.8)
+		text(text_pos_x + 0.2, text_pos_y + 0.1, cex = 0.85,
 				 paste0("D = ", length(igraph::V(as_net)) - as_mat$matching_size, "\n",
@@
 
-legend(0.28, 0.95, legend = replace_names$sp_name, horiz = F, bty = "n", text.font = 3, cex = 0.9)
-legend(0.2, 0.95, legend = replace_names$sp_letter, horiz = F, bty = "n", text.font = 2, cex = 0.9)
+legend(0.28, 0.95, legend = replace_names$sp_name, horiz = F, bty = "n", text.font = 3, cex = 0.8)
+legend(0.2, 0.95, legend = replace_names$sp_letter, horiz = F, bty = "n", text.font = 2, cex = 0.8)
 
@@
 Furthermore, networks had relatively low levels of nestedness [when measured using the quantitative version of the NODF index; @Almeida-Neto2011].
-Details for each network can be found in Supporting Table 1.
+Details for each network can be found in Table S1.
 
@@
 	print(#floating.environment = "sidewaystable", 
-		comment = FALSE, sanitize.text.function = function(x){x}, include.rownames = FALSE)
+		comment = FALSE, sanitize.text.function = function(x){x}, include.rownames = FALSE, caption.placement = "top")
 
@@
 Nevertheless visitation is not equivalent to pollen deposition and might be insufficient to reflect the dependencies of plants on animals and vice versa [@Alarcon2010; @King2013]. 
-We therefore investigated the effect of calculating the dependencies using visitation or pollination effectiveness and importance---two metrics more proximate to plant reproductive success (Supporting Figure 4).
+We therefore investigated the effect of calculating the dependencies using visitation or pollination effectiveness and importance---two metrics more proximate to plant reproductive success (Figure S4).
 We did this by comparing *(i)* the manageability of the community and *(ii)* the percentage of interactions that maintained the direction of dependency. 
@@
 																		levels = c( 'bal_eff','bal_vis','bal_imp'),
-																		labels = c("a) Deposition", "b) Visitation", "c) Importance")), 
+																		labels = c("Deposition", "Visitation", "Importance")), 
 	              pla = stringr::str_split_fixed(vname, "\\|", 2)[, 1],
@@
 
-cowplot::plot_grid(p[[1]][[2]], p[[1]][[1]], p[[2]][[2]], p[[2]][[1]], p[[3]][[2]], p[[3]][[1]], ncol = 2, rel_widths = c(1.5,2))  
-```
-
-At a network scale, despite marked differences in the distribution of weights of the three networks (Supporting Figure 4), the driver node density *n~D~* was consistent among the three different approaches (`r 1-round(n_driver$n_driver[n_driver$net_name == "bal_eff"], digits = 2)` for deposition, `r 1-round(n_driver$n_driver[n_driver$net_name == "bal_vis"], digits = 2)` for the visitation, and `r 1-round(n_driver$n_driver[n_driver$net_name == "bal_imp"], digits = 2)` for the pollinator importance network).
+cowplot::plot_grid(p[[1]][[2]], p[[1]][[1]], p[[2]][[2]], p[[2]][[1]], p[[3]][[2]], p[[3]][[1]], ncol = 2, rel_widths = c(1.5,2), labels = c("(a)", "", "(b)","", "(c)"), label_size = 8)  
+```
+
+At a network scale, despite marked differences in the distribution of weights of the three networks (Figure S4), the driver node density *n~D~* was consistent among the three different approaches (`r 1-round(n_driver$n_driver[n_driver$net_name == "bal_eff"], digits = 2)` for deposition, `r 1-round(n_driver$n_driver[n_driver$net_name == "bal_vis"], digits = 2)` for the visitation, and `r 1-round(n_driver$n_driver[n_driver$net_name == "bal_imp"], digits = 2)` for the pollinator importance network).
 
@@
 Therefore we calculated *f~D~* and *f~S~* (the frequency at which each species is classified as a driver or superior node, respectively, within the set of all possible matchings in a network) and calculated it's correlation among three times of weighting schemes.
-Although visitation and deposition produce moderately different results, we found a very strong agreement between the order produced by visitation and importance (Supporting Table 2). 
+Although visitation and deposition produce moderately different results, we found a very strong agreement between the order produced by visitation and importance (Table S2). 
 Finally, we also investigated whether the asymmetry of mutual dependency, which defines the direction of control, was consistent among the three possible weighting schemes.
-We found again that the direction of the dominant dependency was maintained was consistent for 95\% of the interactions weighted by visitation or importance, the two most appropriate metrics for pollinator and plant dependency (Supporting Table 2).
+We found again that the direction of the dominant dependency was maintained was consistent for 95\% of the interactions weighted by visitation or importance, the two most appropriate metrics for pollinator and plant dependency (Table S2).
 
@@
 Spearman correlation coeffcients (with p-value) of specie's $f_D$ and the percentage of interactions that share the direction of dependency obtained using the three weighting schemes and an unweighted scheme.") %>%
-	print(comment = FALSE, include.rownames = TRUE)
+	print(comment = FALSE, include.rownames = TRUE, caption.placement = "top")
 
@@
 Overall, the results of the sensitivity analysis indicate that our approach might be useful for management even in the absence of complete sampling. 
-Specifically as the proportion of sampled interaction decreassed, the variability of $n_D$ increassed, but was overall very similar when compared to that obtained using all available interactions (Supporting Figure 5a).
-Similarly, the correlation between the relative frequency with which species are classified as a driver ($f_D$) or as a superior node ($f_S$) was correlated ever for *extreme* levels of undersampling (Supporting figure 5b).
+Specifically as the proportion of sampled interaction decreassed, the variability of $n_D$ increassed, but was overall very similar when compared to that obtained using all available interactions (Figure S5a).
+Similarly, the correlation between the relative frequency with which species are classified as a driver ($f_D$) or as a superior node ($f_S$) was correlated ever for *extreme* levels of undersampling (Figure S5b).
 For instance, we found that with a sampling level of 0.5, the mean spearman correlation coefficient was 0.66 for $f_D$ and 0.76 for $f_S$. 
@@
 
-cowplot::plot_grid(p1, p2, ncol = 1, align = "v", rel_heights = c(1,1), labels = c("a)", "b)"), label_size = 8)
-
-f_sampling %>%
-	dplyr::filter(!grepl("bal", net_name)) %>%
-	dplyr::filter(sampling_proportion == 0.5) %>%
-	dplyr::group_by(frequency) %>%
-	dplyr::summarise(correlation = mean(correlation))
+cowplot::plot_grid(p1, p2, ncol = 1, align = "v", rel_heights = c(1,1), labels = c("(a)", "(b)"), label_size = 8)
+
+# f_sampling %>%
+#   dplyr::filter(!grepl("bal", net_name)) %>%
+# 	dplyr::filter(sampling_proportion == 0.5) %>%
+# 	dplyr::group_by(frequency) %>%
+# 	dplyr::summarise(correlation = mean(correlation))
 ```
@@
 
-For ilustration, we show all maximum cardinality matchings for an example network in which links are weighted based on the mutual dependences (Supporting figure 6). 
+For ilustration, we show all maximum cardinality matchings for an example network in which links are weighted based on the mutual dependences (Figure S6). 
 We note, however, that using mutual dependences, or any set up that can lead to bidirectional links, is problematic for a couple of reasons. 
-First, having two links between interacting species and using our maximum matching approach to calculate the control configurations, can result in matchings that include cycle inducing links (Supporting Figure 7).
-Strictly speaking these configurations are maximum matchings in the alternative bipartite configuration (Supporting Figure 1e) but not in the directed network (Supporting Figure 1f). 
+First, having two links between interacting species and using our maximum matching approach to calculate the control configurations, can result in matchings that include cycle inducing links (Figure S7).
+Strictly speaking these configurations are maximum matchings in the alternative bipartite configuration (Figure S1e) but not in the directed network (Figure S1f). 
 While bidirectional links are the norm when using mutual dependences, they only appear in the asymmetry-weighted networks whenever the mutual dependences between two species are strictly symmetric. 
@@
 					 vertex.label.color = l_c,
+					 vertex.shape = igraph::V(.)$superior_shape,
 					 vertex.label.cex = igraph::V(.)$superior * 0.1 + 0.9,
@@
 					 vertex.color = pal[igraph::V(.)$matched],
-					 edge.color = pal[igraph::E(.)$matched],
+					 vertex.frame.color = pal[igraph::V(.)$matched_border],
+					 edge.color = pal[igraph::E(.)$matched_col],
 					 # edge.color = c("#B2ABD2", "#FDB863"),
@@
 
-		text(label_pos_x, label_pos_y, paste0(letters[1+x], ")"), adj = c(0,0))
-		text(text_pos_x, text_pos_y, cex = 0.95,
+		text(label_pos_x, label_pos_y, paste0("(",letters[1+x], ")"), adj = c(0,0), font = 2, cex = 0.8)
+		text(text_pos_x, text_pos_y, cex = 0.8,
 				 paste0("D = ", length(igraph::V(bi_net)) - as_mat$matching_size, "\n",
@@
 plot.new()
-legend(0.5, 0.7, legend = c("unmatched link", "matched link"), horiz = F,
+legend(0.3, 0.7, legend = c("unmatched link", "matched link"), horiz = F,
 			 lty = 1, 
-			 col = pal[c(2, 4)],
-			 lwd = 2, cex = 0.9, xjust=0.5, yjust=1, bty = "n")
-
-legend(0.5, 0.5, legend = c("unmatched node", "matched node"), horiz = F,
+			 col = pal[c(1, 5)],
+			 lwd = 2, cex = 0.9, xjust=0.08, yjust=1, bty = "n")
+
+legend(0.3, 0.5, legend = c("unmatched node", "matched node"), horiz = F,
 			 pch = 21, 
 			 pt.bg = pal[c(2, 4)],
+			 col = pal[c(1, 5)],
 			 pt.cex = 2,
-			 cex = 0.9, xjust=0.5, yjust=1, bty = "n")
-
-legend(0.5, 0.3, legend = expression(paste(bold("(bold label)"), " ", "superior nodes")), horiz = TRUE,
-			 cex = 0.9, xjust=0.5, yjust=1, bty = "n")
+			 cex = 0.9, xjust=0, yjust=1, bty = "n")
+
+legend(0.3, 0.3, legend = c("superior node", "non-superior node"),
+			 horiz = F,
+			 pch = c(22, 21), 
+			 # pt.bg = pal[c(2, 4)],
+			 pt.cex = 2,
+			 cex = 0.9, xjust=0, yjust=1, bty = "n")
 
@@
 ```{r  fig-matchings-bidirectional-no, echo = F, message = F, warning = F, fig.width = 6.2, fig.height = 2.4, results = "hide", fig.cap= "**Cycles in a bidirectional network**.
-Our approach finds twelve configurations for Supporting Figure 6a that are not actual matchings."}
+Our approach finds twelve configurations for Figure S6a that are not actual matchings."}
 
@@
 					 vertex.label.cex = igraph::V(.)$superior * 0.1 + 0.6,
+					 vertex.frame.color = igraph::V(.)$matched_col,
+					 vertex.shape = igraph::V(.)$superior_shape,
 					 # vertex.shape = igraph::V(.)$vertex.shape,
 					 vertex.color = pal[igraph::V(.)$matched],
-					 edge.color = pal[igraph::E(.)$matched],
+					 edge.color = pal[igraph::E(.)$matched_col],
 					 # edge.color = c("#B2ABD2", "#FDB863"),
@@
 We consider two approaches to tackle this limitation. 
-The first approach, is to calculate the matching(s) as usual and then, before calculating $f_S$ and $f_D$, filter out the cycle (Supporting Figure 7). 
-In the special case that the network has no maximal matchings that correspond to feasible control configurations, because they all include cycles, we reduce the size of the cliques we enumerate in $H$ (Supporting figure 2) and repeat.
-The second approach is, instead of calculating the matching(s) for the network with bidirectional cycles, we calculate the matching(s) of $2^n$ unidirectional versions of the network, where $n$ is the number of cycles in the network (Supporting figure 8).
+The first approach, is to calculate the matching(s) as usual and then, before calculating $f_S$ and $f_D$, filter out the cycle (Figure S7). 
+In the special case that the network has no maximal matchings that correspond to feasible control configurations, because they all include cycles, we reduce the size of the cliques we enumerate in $H$ (Figure S2) and repeat.
+The second approach is, instead of calculating the matching(s) for the network with bidirectional cycles, we calculate the matching(s) of $2^n$ unidirectional versions of the network, where $n$ is the number of cycles in the network (Figure S8).
 We then average over the unidirectional networks to find the overall $f_S$ and $f_D$ for a given species.
@@
 For instance, our example network in Figure 1, which is composed of unidirectional links weighted by the asymmetry, has two different maximum matchings. 
-In contrast, the equivalent network with bidirectional links has 16 different maximum matchings (Supporting Figure 6 and 7). 
+In contrast, the equivalent network with bidirectional links has 16 different maximum matchings (Figure S6 and S7). 
 To further ilustrate the implications of this growth, some of our empirical networks had approximately ten thousand different maximum matchings using asymmetries but one hundred million when using mutual dependences.
@@
 We reached this conclusion by calculating the $n_D$ obtained assuming that (a) the direction of control is governed by the asymmetry or (b) bidirectional dependences, (c) that plants depend on pollinators, and that (d) pollinators depend on plants.
-Although the $n_D$ values were quantitatively different between the approaches (Supporting figure 9), the Spearman correlation among these four options suggested a very high agreement (Supporting table 3).
+Although the $n_D$ values were quantitatively different between the approaches (Figure S9), the Spearman correlation among these four options suggested a very high agreement (Table S3).
 
@@
 Spearman correlation coefficients of the number of driver nodes $n_D$ four different assumptions of the direction of control..") %>%
-	print(comment = FALSE, include.rownames = TRUE)
+	print(comment = FALSE, include.rownames = TRUE, caption.placement = "top")
 

### 2017-02-17 paper/supp_info_2.Rmd
Incorporate daniel's edits

@@
 Our approach to find the minumum number of driver nodes relies on finding maximum matchings and maximum cardinality matchings.
-Most existing algorithms are designed to work with undirected bipartie networks, where finding the maximum matching is equivalent to finding the maximum flow between the two levels.
 
 We start with a directed network in which the direction of the link represents the direction of control (Figure S1a). 
-We then construct an alternative representation of the directed network in which each node of the directed network is represented by two nodes that indicate their outgoing and incoming links (Figure S1b).
-Finding a maximum matching in this alternative representation is equivalent to finding the largest possible set of edges in which one node in the left hand side is connected to at most one node in the right hand side.
+We then construct an alternative representation of the directed network in which each node of the directed network is represented by two nodes that indicate their outgoing and incoming links respectively (Figure S1b).
+Finding a maximum matching in this alternative representation is equivalent to finding the largest possible set of edges in which one node on the left-hand side is connected to at most one node on the right-hand side.
 To find the maximum matching we use the push-relabel algorithm implemented in `max_bipartite_matching` in the R package igraph 1.0.1 [@Csardi2006a]. 
-Once we have the matching shown in the Figure S1b, it is then easy to identify the roles of each node in this representation: nodes on the right hand side that are connected to a matched link (purple) are matched, while those connected to a matched link on the left hand side are superior.
+Once we have the matching (shown in the Figure S1b) it is then easy to identify the roles of each node in this representation: nodes on the left-hand side that are connected to a matched (purple) link are superior while those connected to a matched link on the right-hand side are matched.
 This information can then be mapped back to the original representation to identify the control paths and the driver nodes in the network (Figure S1c). 
@@
 
-The algorithm implemented in `max_bipartite_matching`, however, is only able to find **one** of the, possibly many, maximum matchings in a network.
-One maximum matching is sufficient to calculate *n~D~* and hence to provide indication of a communitie's manageability, however it is not possible to estimate the role of individual species.
-To do that we need to calculate all possible maximum matchings (or all maximal cardinality matchings in weighted networks like ours).
-We start from the alternative bipartite representation in Figure S1b and assign an identity to each of the links in the network (shown as numbers in Figure S2a).
+The algorithm implemented in `max_bipartite_matching`, however, is only able to find **one** of the possibly many maximum matchings in a network. 
+Though one maximum matching is enough to calculate *n~D~* and hence to provide indication of a communitie's manageability, it is not sufficient to estimate the role of individual species. 
+To do that, we need to calculate all possible maximum matchings (or, equivalently, all maximal cardinality matchings in weighted networks like ours). 
+To do this, we again start from the alternative bipartite representation in Figure S1b and assign an identity to each of the links in the network (shown as numbers in Figure S2a).
 We will call this bipartite representation *B*. 
 We then construct the line graph of the alternative bipartite representation *L(B)* (Figure S2b). 
-Each node in *L(B)* represents a link in *B* and are connected to each other only if they share a common node in *B*.
-We calculate the complement graph of *L(B)* and idetify all the maximum cliques (Figure S2c).
+Each node in *L(B)* represents a link in *B* and these are connected to each other only if and only if they share a common node in *B*. 
+We then calculate the complement graph of *L(B)* and identify all the maximal cliques (Figure S2c). 
 Here some extra definitions are neccessary. 
@@
 Lastly, a maximum clique is a clique such that there are no cliques with more nodes. 
-In this example there are two maximum cliques: that one formed by 1, 3 and 5, and by 2, 3 and 5.
+In this example, there are two maximum cliques: that one formed by 1, 3 and 5, and the one formed by 2, 3 and 5. 
 The final step is then to map these cliques into the original network to obtain all possible maximum cardinality matchings as shown in Figure 1 in the main text.
@@
 ```{r fig-finding-all-matchings, echo = F, message = F, warning = F, fig.width = 6.2, fig.height = 1.8, results = "hide", fig.cap = "**Finding all possible maximum cardinality matchings**.
-(a) Alternative bipartite representation of a directed network.
+(a) Alternative bipartite representation of the directed network in Figure S1a.
 (b) Line graph of the network in a.
@@
 
-In the main text we show all maximum cardinality matchings for a simple example network.
+In the main text, we show all maximum cardinality matchings for a simple example network. 
 To further ilustrate our methodology, here we also show the approach for the smallest of our empirical networks, the uninvaded network at site 10 (Table S1; Figure S3). 
-The largest component of this network is composed by 16 species of which 2 are non-invasive plants and the rest are pollinators.
+The largest component of this network is composed of 16 species of which 2 are non-invasive plants and the rest are pollinators. 
 The one-to-one relationship between matched and superior nodes implies that in order to achieve full network controllability, most pollinators would be unmatched, and hence driver species that require external intervention.
-At the same time, both plants in the community, *Heracleum sphpndylum* and *Rubus fructicosus* and one of the pollinators *Orthotylus/Lygocorus* tend to be classified as superior nodes.
-
-```{r fig-SA_exp, echo = F, message = F, warning = F, fig.width = 6.2, fig.height = 6.2, results = "hide", fig.cap = "**Illustration of the procedure with one empirical network**.
+At the same time, both plants in the community, *Heracleum sphpndylum* and *Rubus fructicosus*, and one of the pollinators, *Orthotylus/Lygocorus*, tend to be classified as superior nodes.
+
+```{r fig-SA_exp, echo = F, message = F, warning = F, fig.width = 6.2, fig.height = 6.2, results = "hide", fig.cap = "**Illustration of the procedure with an empirical network**.
 (a) The initial visitation network.
-(b) The directed network in which the direction of control and the magnitude of the asymmetry are determined based on the mutual dependences.
-(c) One of the possible maximum matchings calculated using the procedures illustrated in the Figure S1 and S2."}
+(b) The directed network in which the direction of control is determined based on the mutual dependences and assymetries.
+(c) One of the possible maximum matchings calculated using the procedures illustrated in the Figures S1 and S2."}
 par(mfrow=c(2,2), mar=c(0,0,0,0))
@@
 
-The studied networks had species richess ranging between `r min(net_prop$n_s_t)` and `r max(net_prop$n_s_t)` (`r min(net_prop$n_sp)`-`r max(net_prop$n_sp)` when considering only the largest component in each network).
-As evidenced by the overall network asymmetry *AS* [@Bluthgen2007] networks had a low ratio of plants to pollinators.
-Furthermore, networks had relatively low levels of nestedness [when measured using the quantitative version of the NODF index; @Almeida-Neto2011].
-Details for each network can be found in Table S1.
+The networks studied had species richness ranging between `r min(net_prop$n_s_t)` and `r max(net_prop$n_s_t)` (`r min(net_prop$n_sp)`-`r max(net_prop$n_sp)` when considering only the largest component in each network).
+As shown by the network asymmetry *AS* [@Bluthgen2007] the networks overall had a low ratio of plants to pollinators. 
+Furthermore, networks had relatively low levels of nestedness [when measured using the quantitative version of the NODF index; @Almeida-Neto2011]. Details for each network can be found in Table S1.
 
@@
 All properties, with the exception of the networks' total species richness ($R$), correspond to the network's largest component.
-Specifically we show the number of species ($n_s$), the number of plants ($n_p$), the number of pollinators ($n_a$), the network connectance ($c$), the network assymetry ($AS$), and the network nestedness (NODF index).
+We show the number of species ($n_s$), the number of plants ($n_p$), the number of pollinators ($n_a$), the network connectance ($c$), the network assymetry ($AS$), and the network nestedness (NODF index).
 British networks were assembled by Lopezaraiza-Mikel et al.
@@
 The choice of weighting used can also have an impact on at the species level.
-Therefore we calculated *f~D~* and *f~S~* (the frequency at which each species is classified as a driver or superior node, respectively, within the set of all possible matchings in a network) and calculated it's correlation among three times of weighting schemes.
+Therefore we calculated *f~D~* and *f~S~* (the frequency at which each species is classified as a driver or superior node, respectively, within the set of all possible matchings in a network) and calculated it's correlation among all three weighting schemes.
 Although visitation and deposition produce moderately different results, we found a very strong agreement between the order produced by visitation and importance (Table S2). 
@@
   xtable::xtable(caption = "\\textbf{Agreement among network weighting schemes}.
-Spearman correlation coeffcients (with p-value) of specie's $f_D$ and the percentage of interactions that share the direction of dependency obtained using the three weighting schemes and an unweighted scheme.") %>%
+Spearman correlation coeffcients (with p-value) of species' $f_D$ and the percentage of interactions that share the direction of dependency obtained using the three weighting schemes and an unweighted scheme.") %>%
 	print(comment = FALSE, include.rownames = TRUE, caption.placement = "top")
@@
 (a) A network with bidirectional links.
-(b-e) Possible control configurations." }
+(b-e) All possible control configurations." }
 par(mfrow=c(2,3), mar=c(0,0,0,0))
@@
 ```{r  fig-matchings-bidirectional-no, echo = F, message = F, warning = F, fig.width = 6.2, fig.height = 2.4, results = "hide", fig.cap= "**Cycles in a bidirectional network**.
-Our approach finds twelve configurations for Figure S6a that are not actual matchings."}
+Our approach finds twelve configurations for Figure S6a that are matchings in the alternative bipartite representation, but not actual matchings in the directed network."}
 

### 2017-02-20 paper/supp_info_2.Rmd
Use figure refs and labels instead of manual numbers in text

@@
 output:
-  pdf_document:
+  bookdown::pdf_document2:
     fig_crop: no
@@
 
-# S1: Finding a complex network's matchings
+# Finding a complex network's matchings
 
@@
 
-We start with a directed network in which the direction of the link represents the direction of control (Figure S1a). 
-We then construct an alternative representation of the directed network in which each node of the directed network is represented by two nodes that indicate their outgoing and incoming links respectively (Figure S1b).
+We start with a directed network in which the direction of the link represents the direction of control (Figure \@ref(fig:fig-direction-of-control)a). 
+We then construct an alternative representation of the directed network in which each node of the directed network is represented by two nodes that indicate their outgoing and incoming links respectively (Figure \@ref(fig:fig-direction-of-control)b).
 Finding a maximum matching in this alternative representation is equivalent to finding the largest possible set of edges in which one node on the left-hand side is connected to at most one node on the right-hand side.
 To find the maximum matching we use the push-relabel algorithm implemented in `max_bipartite_matching` in the R package igraph 1.0.1 [@Csardi2006a]. 
-Once we have the matching (shown in the Figure S1b) it is then easy to identify the roles of each node in this representation: nodes on the left-hand side that are connected to a matched (purple) link are superior while those connected to a matched link on the right-hand side are matched.
-This information can then be mapped back to the original representation to identify the control paths and the driver nodes in the network (Figure S1c). 
-Figure S1d, e, and f ilustrate this approach for a network with bidirectional links.
+Once we have the matching (shown in the Figure \@ref(fig:fig-direction-of-control)b) it is then easy to identify the roles of each node in this representation: nodes on the left-hand side that are connected to a matched (purple) link are superior while those connected to a matched link on the right-hand side are matched.
+This information can then be mapped back to the original representation to identify the control paths and the driver nodes in the network (Figure \@ref(fig:fig-direction-of-control)c). 
+Figure \@ref(fig:fig-direction-of-control)d, e, and f ilustrate this approach for a network with bidirectional links.
 
@@
 To do that, we need to calculate all possible maximum matchings (or, equivalently, all maximal cardinality matchings in weighted networks like ours). 
-To do this, we again start from the alternative bipartite representation in Figure S1b and assign an identity to each of the links in the network (shown as numbers in Figure S2a).
+To do this, we again start from the alternative bipartite representation in Figure \@ref(fig:fig-direction-of-control)b and assign an identity to each of the links in the network (shown as numbers in Figure \@ref(fig:fig-finding-all-matchings)a).
 We will call this bipartite representation *B*. 
-We then construct the line graph of the alternative bipartite representation *L(B)* (Figure S2b). 
+We then construct the line graph of the alternative bipartite representation *L(B)* (Figure \@ref(fig:fig-finding-all-matchings)b). 
 Each node in *L(B)* represents a link in *B* and these are connected to each other only if and only if they share a common node in *B*. 
-We then calculate the complement graph of *L(B)* and identify all the maximal cliques (Figure S2c). 
+We then calculate the complement graph of *L(B)* and identify all the maximal cliques (Figure \@ref(fig:fig-finding-all-matchings)c). 
 Here some extra definitions are neccessary. 
@@
 ```{r fig-finding-all-matchings, echo = F, message = F, warning = F, fig.width = 6.2, fig.height = 1.8, results = "hide", fig.cap = "**Finding all possible maximum cardinality matchings**.
-(a) Alternative bipartite representation of the directed network in Figure S1a.
+(a) Alternative bipartite representation of the directed network in Figure \\@ref(fig:fig-direction-of-control)a.
 (b) Line graph of the network in a.
@@
 In the main text, we show all maximum cardinality matchings for a simple example network. 
-To further ilustrate our methodology, here we also show the approach for the smallest of our empirical networks, the uninvaded network at site 10 (Table S1; Figure S3). 
+To further ilustrate our methodology, here we also show the approach for the smallest of our empirical networks, the uninvaded network at site 10 (Table S1; Figure \@ref(fig:fig-SA-exp)). 
 The largest component of this network is composed of 16 species of which 2 are non-invasive plants and the rest are pollinators. 
@@
 
-```{r fig-SA_exp, echo = F, message = F, warning = F, fig.width = 6.2, fig.height = 6.2, results = "hide", fig.cap = "**Illustration of the procedure with an empirical network**.
+```{r fig-SA-exp, echo = F, message = F, warning = F, fig.width = 6.2, fig.height = 6.2, results = "hide", fig.cap = "**Illustration of the procedure with an empirical network**.
 (a) The initial visitation network.
 (b) The directed network in which the direction of control is determined based on the mutual dependences and assymetries.
-(c) One of the possible maximum matchings calculated using the procedures illustrated in the Figures S1 and S2."}
+(c) One of the possible maximum matchings calculated using the procedures illustrated in the Figures \\@ref(fig:fig-direction-of-control) and \\@ref(fig:ig-finding-all-matchings)."}
 par(mfrow=c(2,2), mar=c(0,0,0,0))
@@
 
-# S3: Visitation as a proxy for species interdependence
+# Visitation as a proxy for species interdependence
 
@@
 Nevertheless visitation is not equivalent to pollen deposition and might be insufficient to reflect the dependencies of plants on animals and vice versa [@Alarcon2010; @King2013]. 
-We therefore investigated the effect of calculating the dependencies using visitation or pollination effectiveness and importance---two metrics more proximate to plant reproductive success (Figure S4).
+We therefore investigated the effect of calculating the dependencies using visitation or pollination effectiveness and importance---two metrics more proximate to plant reproductive success (Figure \@ref(fig:fig-visitation-vs-deposition-vs-importance)).
 We did this by comparing *(i)* the manageability of the community and *(ii)* the percentage of interactions that maintained the direction of dependency. 
@@
 
-At a network scale, despite marked differences in the distribution of weights of the three networks (Figure S4), the driver node density *n~D~* was consistent among the three different approaches (`r 1-round(n_driver$n_driver[n_driver$net_name == "bal_eff"], digits = 2)` for deposition, `r 1-round(n_driver$n_driver[n_driver$net_name == "bal_vis"], digits = 2)` for the visitation, and `r 1-round(n_driver$n_driver[n_driver$net_name == "bal_imp"], digits = 2)` for the pollinator importance network).
+At a network scale, despite marked differences in the distribution of weights of the three networks (Figure \@ref(fig:fig-visitation-vs-deposition-vs-importance)), the driver node density *n~D~* was consistent among the three different approaches (`r 1-round(n_driver$n_driver[n_driver$net_name == "bal_eff"], digits = 2)` for deposition, `r 1-round(n_driver$n_driver[n_driver$net_name == "bal_vis"], digits = 2)` for the visitation, and `r 1-round(n_driver$n_driver[n_driver$net_name == "bal_imp"], digits = 2)` for the pollinator importance network).
 
@@
 
-# S4: Sensitivity analysis
+# Sensitivity analysis
 
@@
 Overall, the results of the sensitivity analysis indicate that our approach might be useful for management even in the absence of complete sampling. 
-Specifically as the proportion of sampled interaction decreassed, the variability of $n_D$ increassed, but was overall very similar when compared to that obtained using all available interactions (Figure S5a).
-Similarly, the correlation between the relative frequency with which species are classified as a driver ($f_D$) or as a superior node ($f_S$) was correlated ever for *extreme* levels of undersampling (Figure S5b).
+Specifically as the proportion of sampled interaction decreassed, the variability of $n_D$ increassed, but was overall very similar when compared to that obtained using all available interactions (Figure \@ref(fig:fig-subsampling-sensitivity)a).
+Similarly, the correlation between the relative frequency with which species are classified as a driver ($f_D$) or as a superior node ($f_S$) was correlated ever for *extreme* levels of undersampling (Figure \@ref(fig:fig-subsampling-sensitivity)b).
 For instance, we found that with a sampling level of 0.5, the mean spearman correlation coefficient was 0.66 for $f_D$ and 0.76 for $f_S$. 
@@
 
-# S5: Chosing the direction of control
+# Chosing the direction of control
 
@@
 
-For ilustration, we show all maximum cardinality matchings for an example network in which links are weighted based on the mutual dependences (Figure S6). 
+For ilustration, we show all maximum cardinality matchings for an example network in which links are weighted based on the mutual dependences (Figure \@ref(fig:fig-matchings-bidirectional)). 
 We note, however, that using mutual dependences, or any set up that can lead to bidirectional links, is problematic for a couple of reasons. 
-First, having two links between interacting species and using our maximum matching approach to calculate the control configurations, can result in matchings that include cycle inducing links (Figure S7).
-Strictly speaking these configurations are maximum matchings in the alternative bipartite configuration (Figure S1e) but not in the directed network (Figure S1f). 
+First, having two links between interacting species and using our maximum matching approach to calculate the control configurations, can result in matchings that include cycle inducing links (Figure \@ref(fig:fig-matchings-bidirectional-no)).
+Strictly speaking these configurations are maximum matchings in the alternative bipartite configuration (Figure \@ref(fig:fig-direction-of-control)e) but not in the directed network (Figure \@ref(fig:fig-direction-of-control)f).
 While bidirectional links are the norm when using mutual dependences, they only appear in the asymmetry-weighted networks whenever the mutual dependences between two species are strictly symmetric. 
@@
 ```{r  fig-matchings-bidirectional-no, echo = F, message = F, warning = F, fig.width = 6.2, fig.height = 2.4, results = "hide", fig.cap= "**Cycles in a bidirectional network**.
-Our approach finds twelve configurations for Figure S6a that are matchings in the alternative bipartite representation, but not actual matchings in the directed network."}
+Our approach finds twelve configurations for Figure \\@ref(fig:fig-matchings-bidirectional)a that are matchings in the alternative bipartite representation, but not actual matchings in the directed network."}
 
@@
 We consider two approaches to tackle this limitation. 
-The first approach, is to calculate the matching(s) as usual and then, before calculating $f_S$ and $f_D$, filter out the cycle (Figure S7). 
-In the special case that the network has no maximal matchings that correspond to feasible control configurations, because they all include cycles, we reduce the size of the cliques we enumerate in $H$ (Figure S2) and repeat.
-The second approach is, instead of calculating the matching(s) for the network with bidirectional cycles, we calculate the matching(s) of $2^n$ unidirectional versions of the network, where $n$ is the number of cycles in the network (Figure S8).
+The first approach, is to calculate the matching(s) as usual and then, before calculating $f_S$ and $f_D$, filter out the cycle containing matchings (Figure \@ref(fig:fig-matchings-bidirectional-no)).
+In the special case that the network has no maximal matchings that correspond to feasible control configurations, because they all include cycles, we reduce the size of the cliques we enumerate in $H$ (Figure \@ref(fig:fig-finding-all-matchings)) and repeat.
+The second approach is, instead of calculating the matching(s) for the network with bidirectional cycles, we calculate the matching(s) of $2^n$ unidirectional versions of the network, where $n$ is the number of cycles in the network (Figure \@ref(fig:fig-tackle-cycles)).
 We then average over the unidirectional networks to find the overall $f_S$ and $f_D$ for a given species.
-
-The number of maximal matchings increases disproportionally fast with the number of links in a network. 
-For instance, our example network in Figure 1, which is composed of unidirectional links weighted by the asymmetry, has two different maximum matchings. 
-In contrast, the equivalent network with bidirectional links has 16 different maximum matchings (Figure S6 and S7). 
-To further ilustrate the implications of this growth, some of our empirical networks had approximately ten thousand different maximum matchings using asymmetries but one hundred million when using mutual dependences.
-This exponential growth, and the computational cost of either filtering matchings with cycles or calculating the matchings for $2^n$ networks, surpassed the capabilities of the available computational resources and rendered us unable to calculate all possible maximum matchings when using mutual dependences in most of our bidirectional networks.
-Nevertheless, as most of our networks weighted by asymmetry had between zero and four cycles, we successfully used the second approach explained in the previous paragraph to calculate the all maximum matchings for these networks.
 
@@
 
+The number of maximal matchings increases disproportionally fast with the number of links in a network. 
+For instance, our example network in Figure 1, which is composed of unidirectional links weighted by the asymmetry, has two different maximum matchings. 
+In contrast, the equivalent network with bidirectional links has 16 different maximum matchings (Figure \@ref(fig:fig-matchings-bidirectional) and \@ref(fig:fig-matchings-bidirectional-no)). 
+To further ilustrate the implications of this growth, some of our empirical networks had approximately ten thousand different maximum matchings using asymmetries but one hundred million when using mutual dependences.
+This exponential growth, and the computational cost of either filtering matchings with cycles or calculating the matchings for $2^n$ networks, surpassed the capabilities of the available computational resources and rendered us unable to calculate all possible maximum matchings when using mutual dependences in most of our bidirectional networks.
+Nevertheless, as most of our networks weighted by asymmetry had between zero and four cycles, we successfully used the second approach explained in the previous paragraph to calculate the all maximum matchings for these networks.
+
 We highlight that althoug the direction of control might affect the $f_S$ and $f_D$, it doesn't affect strongly the network's relative density of driver nodes $n_D$. 
 We reached this conclusion by calculating the $n_D$ obtained assuming that (a) the direction of control is governed by the asymmetry or (b) bidirectional dependences, (c) that plants depend on pollinators, and that (d) pollinators depend on plants.
-Although the $n_D$ values were quantitatively different between the approaches (Figure S9), the Spearman correlation among these four options suggested a very high agreement (Table S3).
+Although the $n_D$ values were quantitatively different between the approaches (Figure \@ref(fig:fig-alternative-assumptions)), the Spearman correlation among these four options suggested a very high agreement (Table S3).
 

### 2017-02-20 paper/supp_info_2.Rmd
Add control profiles analysis

@@
 
-# S2: Properties of empirical networks
+# Control profiles
+
+@Ruths2014 proposed a heuristic-based method to provide insight of what might be required to control a network.
+The method is based on the idea that the reasons behind a node being classified as a driver node can be precisely identified, and that the relative contribution of these reasons can be used to characterise the control profile of the network.
+Specifically, nodes can be deemed to be driver nodes for three reasons:
+
+1. **Because it is a source node**. Source nodes are nodes that exclusively have outgoing links. Therefore, other nodes cannot control it, but instead, it must be externally controlled. 
+2. **Because of an external dilation**. Dilations occur whenever a control signal needs to branch out in order to reach all nodes in a network. 
+One kind of dilation, which arises due to a surplus of sink nodes (those that only have incoming links) is called external dilation. 
+This concept might be easier to understand by looking at Figure \@ref(fig:fig-SA-exp)c. 
+The source node *a* branches out into nine paths, but it can only control one of them. 
+We say then, that the sink nodes *d* to *k* become driver nodes because of an external dilation.
+3. **Because of an internal dilation**. The remaining dilations (those that do not arise from a surplus of sink nodes) are called internal dilations. 
+Node *j* in Figure \@ref(fig:fig-SA-exp)c and the driver nodes in Figure \@ref(fig:fig-matchings-bidirectional) are examples of this category.
+
+Mathematically, the number of driver nodes $N_D$ is the sum of the number of source nodes, the number of external dilation points, and the number of internal dilation points, $N_D = N_s + N_e + N_i$. 
+A network can then be characterised by the relative proportion of the three kind of controls $$\eta_s + \eta_e + \eta_i = 1,$$ where $\eta_s = N_s/N_D$, $\eta_e = N_e/N_D$, and $\eta_i = N_i/N_D$. 
+These terms can be calculated with relative ease.
+$N_D$ can be calculated using a maximum matching algorithm. 
+$N_s$ can be calculated by inspecting the network's degree distribution.
+$N_e = max(0,N_t - N_s)$, where $N_t$ is the number of sink nodes in the network.
+And we can solve for $N_i$ once we have all other information.
+
+Applying this framework to our networks directed by the asymmetry we identify that they are all external dilation dominated (Figure \@ref(fig:fig-control-profiles)).
+@Ruths2014 explains that "external-dilation-dominated networks exhibited strong aspects of top-down control". 
+Because of the surplus of sink nodes, an external intervention that is applied to a source node will induce a correlated response among their subordinate species. 
+For example, an increase in the abundance of *Heracleum sphondylum* (Figure \@ref(fig:fig-SA-exp)) is likely to induce an increase in the abundance of the pollinators it interacts with.
+Therefore it can be expected that in order to fully control the network it is not sufficient to apply interventions to the source nodes.
+
+The control profile of our pollination networks provides additional justification to our decision to determine the importance of a species, not only by virtue of $f_D$, but also by $f_S$.
+Many species that act like control sinks in our network, will be classified as a driver node, because they are necessary to *fully* control the dynamics of the community, as opposed to playing a central role influencing the abundance of other species in the community.
+
+Using this approach also highlights the importance of appropiately selecting the direction of control (See Section 6). 
+A network with bidirectional links weighted by the mutual dependences would have zero source nodes and zero sink nodes. 
+Therefore, the control profile of such a network would have been completely uninformative, as it would just highlight that the proportion of internal dilations is $\eta_i = 1$.
+
+```{r fig-control-profiles, echo = F, message = F, warning = F, fig.width = 6.2, fig.height = 2.6, results = "hide", fig.cap= "**Control profiles of the studied networks**.
+Following @Ruths2014, profiles are shown in a ternary plot in which the cornders correspond to points (1, 0, 0), (0, 1, 0), and (0, 0, 1) in the three-dimensional $(\\eta_s, \\eta_e, \\eta_i)$ space such that $\\eta_s + \\eta_e + \\eta_i = 1$, and $\\eta_s, \\eta_e$, and $\\eta_i > 0$."}
+n_driver <- meta %>%
+  dplyr::inner_join(n_matched) %>% 
+  dplyr::mutate(n_driver = 1 - n_matched / (n_pla + n_pol))
+
+profiles <- net %>%
+	plyr::ldply(function(x){
+		d <- x %>% 
+			keep_largest_component() %>%
+			bipartite_digraph(type = "weight",
+												keep = "all",
+												weight.type = "asymmetry", 
+												scale = F)
+		E(d)$weight <- 1
+		out_degree <- igraph::degree(d, mode = "out") 
+    in_degree <- igraph::degree(d, mode = "in") 
+    n_sources <- sum(out_degree > 0 & in_degree == 0) 
+    n_sinks <- sum(out_degree == 0 & in_degree > 0) 
+    n_ext_dil <- max(0,n_sinks - n_sources) 
+    n_sp <- length(igraph::V(d))
+    data.frame(n_sources = n_sources, n_sinks = n_sinks,  
+               n_ext_dil = n_ext_dil, n_sp = n_sp)
+	}) %>%
+	dplyr::rename(net_name = .id) %>%
+	dplyr::mutate()
+
+profiles %<>%
+	dplyr::inner_join(n_driver) %>%
+	dplyr::mutate(n_driver = n_sp - n_matched,
+								n_int_dil = n_driver - n_sources - n_ext_dil,
+								eta_s = n_sources / n_driver,
+								eta_e = n_ext_dil / n_driver,
+								eta_i = n_int_dil / n_driver)
+
+library(ggtern)
+
+# p1 <- 
+profiles %>%
+ 	dplyr::filter(!grepl("bal_bin", net_name)) %>%
+ 	ggplot(aes(x = eta_s, z = eta_e, y = eta_i)) + 
+	geom_mask() +
+  geom_point(fill = "gray70", shape = 21, size = 2, alpha = 0.7) + 
+	coord_tern(expand = T) +
+ 	labs(x = "$\\eta_s$",
+ 			 y = "$\\eta_i$",
+ 			 z = "$\\eta_e$",
+ 			 Tarrow = "internal dilation",
+ 			 Rarrow = "external dilation",
+ 			 Larrow = "source") +
+	fer_theme +
+ 	# tern_limit(0.2,0.2, 1) +
+ 	theme(panel.grid = element_line(colour = "grey90", size = 0.3),
+ 				plot.title = element_text(margin = margin(-14, 0, 0, 0)),
+ 				plot.margin = margin(t = -10),
+ 				plot.background = element_blank()) +
+ 	percent_custom("%") +
+ 	theme_nogrid_minor() +
+ 	theme_showarrows() +
+ 	theme_arrowlarge() +
+ 	theme_latex(TRUE) 
+# 
+# p2 <- profiles %>% 
+# 	dplyr::filter(!grepl("bal_bin", net_name)) %>%
+# 	ggplot(aes(eta_e, n_driver/n_sp)) +
+# 	geom_point(shape = 21) +
+# 	# scale_x_log10() + scale_y_log10() +
+# 	geom_smooth(method = "lm", colour = "black", size = 0.5) +
+# 	# scale_x_log10() +
+# 	fer_theme +
+# 	theme(plot.margin = margin(r = 2, t = 18, b = 21),
+#  				plot.background = element_blank()) +
+# 	xlab(expression(eta[s])) +
+# 	ylab(expression(n[D]))
+# 
+# grid.arrange(grobs = list(
+# 	grid::textGrob("(a)", x = 0, y = -2, gp = grid::gpar(font = 2, cex = 0.7), just = "left"),
+# 	grid::textGrob("(b)", x = 0, y = -2, gp = grid::gpar(font = 2, cex = 0.7), just = "left"), 
+# 	p1, p2), nrow = 2, heights = c(1,30), widths = c(1, 1.4))
+```
+
+# Properties of empirical networks
 
@@
 Note that the *x* axis in the density plots have been log-transformed."}
-n_driver <- meta %>%
-  dplyr::inner_join(n_matched) %>% 
-  dplyr::mutate(n_driver = 1 - n_matched / (n_pla + n_pol))
 

### 2017-02-21 paper/supp_info_2.Rmd
Matching threshold

@@
 
-# S6: Using control profile heuristics
+# Matching's weight threshold
+
+We use the frequency with which a species is classified as a driver node $f_D$ and the frequency with which a species is classified as a superior node $f_S$ in a set of accepted maximal matchings to infer their relative importance.
+Maximal matchings were accepted if the matching weight was over a certain threshold. 
+This threshold was defined as a proportion of the maximum matching's weight. 
+Here we evaluate the impact that a particular choice of this threshold has on $f_D$ and $f_S$.
+
+The number of accepted maximal matchings increased rapidly as the threshold at which they are accepted decreases.
+Nevertheless this number stabilises below approximately 0.6-0.7 (Figure \@ref(fig:fig-n-matchings)).
+
+```{r fig-n-matchings, echo = F, message = F, warning = F, fig.width = 3.2, fig.height = 2.4, results = "hide", fig.cap= "**Number of maximal matchings as a function of the weight threshold**.
+Each line correspond to one network."}
+d_sp %>%
+	dplyr::filter(scaled == FALSE, 
+								study != "ballantyne", 
+								type == "asymmetry") %>%
+	dplyr::group_by(net_name, threshold) %>%
+	dplyr::summarise(n_matchings = mean(unique(n_matchings))) %>%
+	ggplot(aes(x = threshold, y = n_matchings)) +
+	geom_line(aes(group = net_name), colour = "grey20", size = 0.3) +
+	scale_y_log10() +
+	scale_x_reverse() +
+	ylab("maximal matchings") +
+	fer_theme
+```
+
+We then examined how the relative importance of species changes with the chosen threshold. 
+We observe, that regardless of the matching weight's threshold species tend to be superior nodes in all or none of the matchings, which equates to $f_S$ values of one or zero, and the contrast between important and unimportant species is maintained (Figure \@ref(fig:fig-f-s-rankings)).
+Contrastingly, species' $f_D$ reach intermediate levels of importance and show higher variability across thresholds (Figure \@ref(fig:fig-f-d-rankings)).
+
+```{r fig-f-s-rankings, echo = F, message = F, warning = F, fig.width = 6.2, fig.height = 9, results = "hide", fig.cap="**Frequency with which a species was classified as a superior node ($f_S$) as a function of the matching weight threshold**.
+Rows correspond to study sites."}
+sites <- net_prop %>% dplyr::arrange(study, site, inv) %$% site %>% unique()
+threshold_data <- d_sp %>%
+			dplyr::filter(scaled == FALSE, 
+										study != "ballantyne", 
+										type == "asymmetry") %>%
+			dplyr::mutate(f_s = d_freq / n_matchings, 
+										f_d = (n_matchings - m_freq) / n_matchings, 
+										site = factor(site, sites), 
+										site_num = as.numeric(site)) %>%
+			dplyr::group_by(net_name, threshold, species) %>%
+			dplyr::summarise(f_s = mean(f_s),
+											 f_d = mean(f_d), 
+											 site = dplyr::first(site),
+											 site_num = dplyr::first(site_num),
+											 inv = dplyr::first(inv)) %>%
+			dplyr::group_by() %>%
+			dplyr::mutate(site_num = site_num -1, # to account for ballantynes
+										inv = plyr::mapvalues(inv, c(T, F), 
+																					c("invaded", "uninvaded")))
+p <- c("f_s", "f_d") %>%
+	plyr::llply(function(x){
+		threshold_data %>% 
+			# dplyr::group_by(net_name, species) %>%
+			# dplyr::arrange(threshold) %>%
+			# dplyr::mutate(initial = dplyr::first(f_s)) %>%
+			# dplyr::group_by() %>%
+			# reshape2::melt(measure.vars = c("f_s", "f_d"), value.name = "f") %>% 
+			# dplyr::group_by() %>% View
+			ggplot(aes_string(x = "threshold", y = x)) +
+			geom_line(aes(group = species), size = 0.2) +
+			# geom_point(size = 0.5) +
+			facet_grid(site_num ~ inv) +
+			fer_theme
+	})
+
+p[[1]] + ylab(expression(f[S]))
+```
+
+```{r fig-f-d-rankings, echo = F, message = F, warning = F, fig.width = 6.2, fig.height = 9, results = "hide", fig.cap= "**Frequency with which a species was classified as a superior node ($f_D$) as a function of the matching weight threshold**.
+Rows correspond to study sites."}
+p[[2]] + ylab(expression(f[D]))
+
+```
+
+Finally, we examined the agreement across thresholds by calculating the Spearman correlation matrix of species' $f_S$ and $f_D$ for each network. 
+The mean of those matrices is shown in Table S4. 
+Overall, among all thresholds, we found a very high agreement for $f_S$, and high to very high for $f_D$. 
+With the exception of using a threshold of 1 (only maximum matchings are accepted), the choice of the threshold has little impact on the relative importance of species. 
+For convenience, we use an intermediate level of 0.5. 
+Nevertheless, the differences are marginal and any threshold $<= 0.9$ is likely to produce very similar results.
+
+```{r table-correlations-thresholds, echo = F, message = F, warning = F, results = "asis", sanitize = F}
+correlation_matrix <- c("f_s", "f_d") %>%
+	plyr::llply(function(x){
+		threshold_data %>%
+			plyr::daply("net_name", get_corr_matrix, column = x) %>%
+			plyr::aaply(c(2, 3), mean)
+	})
+
+correlation_matrix_o <- correlation_matrix[[1]]
+correlation_matrix_o[upper.tri(correlation_matrix_o)] <- 
+	correlation_matrix[[2]][upper.tri(correlation_matrix[[2]])]
+c_m <- round(correlation_matrix_o, 2)
+c_m[is.na(c_m)] <- "—"
+
+xtable::xtable(c_m, caption = "\\textbf{Spearman correlation coefficient among different matching weight thresholds}.
+The upper triangle shows values for $f_D$ and the lower triangle shows values for $f_S$") %>%
+	print(comment = FALSE, include.rownames = TRUE, caption.placement = "top")
+```
 

### 2017-02-21 paper/supp_info_2.Rmd
Fix the reading of the new all matchings

@@
   plyr::ldply(function(x) {
-    get_frequencies(x) %>%
+    o <- get_frequencies(x) %>%
       dplyr::mutate(type = attr(x, "type"),
                     scaled = attr(x, "scaled"))
+    net_names_with_extension <- unique(o$net_name) %>% as.character()
+    net_names_without_extension <- 
+    	strsplit(net_names_with_extension, "_", fixed = T) %>%
+    	lapply(function(x){ 
+    		if(x[length(x)] %in% LETTERS) {
+    			x[-length(x)]
+    		} else {
+    			x
+    		}
+    		}) %>%
+    	lapply(paste, collapse = "_") %>% unlist()
+    o %>% dplyr::mutate(
+    	net_name = plyr::mapvalues(net_name, net_names_with_extension,
+    														 net_names_without_extension)
+    )
   }) %>%

### 2017-02-21 paper/supp_info_2.Rmd
Add explanation about missing network

@@
 Contrastingly, species' $f_D$ reach intermediate levels of importance and show higher variability across thresholds (Figure \@ref(fig:fig-f-d-rankings)). 
+We note here that we were unable to compute all the maximum cardinality matchings for one of our networks (uninvaded community in site 8). 
+We estimate the number of matchings to be more than one billion, which surpassed our available computational resources.
 
@@
 																					c("invaded", "uninvaded")))
+# not finished note
+note <- data.frame(site_num = 8, inv = "invaded", text = "results not available")
+
 p <- c("f_s", "f_d") %>%
@@
 			# dplyr::group_by() %>% View
-			ggplot(aes_string(x = "threshold", y = x)) +
-			geom_line(aes(group = species), size = 0.2) +
+			ggplot() +
+			geom_line(aes_string(x = "threshold", group = "species", y = x), size = 0.2) +
+			geom_text(data = note, aes(label = text), x = 0.5, y = 0.5, size = 3) +
 			# geom_point(size = 0.5) +
@@
 	correlation_matrix[[2]][upper.tri(correlation_matrix[[2]])]
-c_m <- round(correlation_matrix_o, 2)
+c_m <- round(correlation_matrix_o, 3)
 c_m[is.na(c_m)] <- "—"

### 2017-02-23 paper/draft_2.Rmd
Minor changes to theme

@@
   read_allRDS()
+mod <- readRDS("../data/processed/detailed_species_models.rds")
+mo <- readRDS("../data/processed/detailed_species_models_data.rds")
 ```
@@
 fer_theme <- theme_bw() +
-	theme(text = element_text(family = "Times"),
-	      title = element_text(size = 7.5, hjust = 0),
-	      legend.title = element_text(size = 9),
-	      legend.text = element_text(size = 8),
-				axis.text = element_text(size = 8),
-				axis.title = element_text(size = 9, hjust = 0.5), 
-				strip.text = element_text(size = 9, hjust = 0), 
+	theme(text = element_text(family = "Helvetica"),
+	      title = element_text(size = 7, hjust = 0),
+	      legend.title = element_text(size = 8),
+	      legend.text = element_text(size = 7),
+				axis.text = element_text(size = 7),
+				axis.title = element_text(size = 8, hjust = 0.5), 
+				strip.text = element_text(size = 8, hjust = 0), 
 				strip.background = element_blank(),
-				plot.margin = grid::unit(c(5, 0, 2, 0), "mm"),
+				plot.margin = grid::unit(c(5, 0.5, 2, 0), "mm"),
 				panel.grid = element_blank())

### 2017-02-23 paper/supp_info_2.Rmd
Minor changes to theme

@@
 				strip.background = element_blank(),
-				plot.margin = grid::unit(c(5, 0, 2, 0), "mm"),
+				plot.margin = grid::unit(c(5, 0.5, 2, 0), "mm"),
 				panel.grid = element_blank())

### 2017-02-23 paper/draft_2.Rmd
Use booktabs

@@
 - \usepackage{float}
+- \usepackage{booktabs}
+- \usepackage{caption} 
 documentclass: artikel1

### 2017-02-23 paper/supp_info_2.Rmd
Use booktabs

@@
 - \renewcommand{\thetable}{S\arabic{table}}
+- \usepackage{booktabs}
 - \usepackage[tableposition=top]{caption} 
@@
 	print(#floating.environment = "sidewaystable", 
-		comment = FALSE, sanitize.text.function = function(x){x}, include.rownames = FALSE, caption.placement = "top")
+		comment = FALSE, sanitize.text.function = function(x){x}, include.rownames = FALSE, caption.placement = "top", booktabs = T)
 
@@
 Spearman correlation coeffcients (with p-value) of species' $f_D$ and the percentage of interactions that share the direction of dependency obtained using the three weighting schemes and an unweighted scheme.") %>%
-	print(comment = FALSE, include.rownames = TRUE, caption.placement = "top")
+	print(comment = FALSE, include.rownames = TRUE, caption.placement = "top", booktabs = T)
 
@@
 Spearman correlation coefficients of the number of driver nodes $n_D$ four different assumptions of the direction of control..") %>%
-	print(comment = FALSE, include.rownames = TRUE, caption.placement = "top")
+	print(comment = FALSE, include.rownames = TRUE, caption.placement = "top", booktabs = T)
 
@@
 
-```{r table-correlations-thresholds, echo = F, message = F, warning = F, results = "asis", sanitize = F}
+```{r table-correlations-thresholds, echo = F, message = F, warning = F, results = "asis", sanitize = F, cache = T}
 correlation_matrix <- c("f_s", "f_d") %>%
@@
 The upper triangle shows values for $f_D$ and the lower triangle shows values for $f_S$") %>%
-	print(comment = FALSE, include.rownames = TRUE, caption.placement = "top")
+	print(comment = FALSE, include.rownames = TRUE, caption.placement = "top", booktabs = T)
 ```

### 2017-02-23 paper/supp_info_2.Rmd
Cache slow R chunks

@@
 ```{r fig-f-s-rankings, echo = F, message = F, warning = F, fig.width = 6.2, fig.height = 9, results = "hide", fig.cap="**Frequency with which a species was classified as a superior node ($f_S$) as a function of the matching weight threshold**.
-Rows correspond to study sites."}
+Rows correspond to study sites.", cache = T}
 sites <- net_prop %>% dplyr::arrange(study, site, inv) %$% site %>% unique()
@@
 ```{r fig-f-d-rankings, echo = F, message = F, warning = F, fig.width = 6.2, fig.height = 9, results = "hide", fig.cap= "**Frequency with which a species was classified as a superior node ($f_D$) as a function of the matching weight threshold**.
-Rows correspond to study sites."}
+Rows correspond to study sites.", cache = T}
 p[[2]] + ylab(expression(f[D]))

### 2017-02-23 paper/supp_info_2.Rmd
Add statistical models table

@@
 
+# Statistical models
+
+```{r table-nd-coef, echo = FALSE, warning = FALSE, message = FALSE, results = "asis", sanitize = FALSE}
+library(glmulti)
+
+manag_table <- manag_models %>%
+			coef.glmulti(select = 0.95) %>%
+  as.data.frame() %>%
+  tibble::rownames_to_column("factor") %>%
+  dplyr::mutate(pare = grepl("(", factor, fixed =T),
+                factor = plyr::mapvalues(factor, 
+                												 c("studylopezaraiza", "invTRUE",
+                												 	"I(n_links/(n_pla * n_pol))",
+                												 	"I(n_pla + n_pol)", 
+                												 	"I(n_pla/n_pol)"),
+                												 c("study site", "invasion status",
+                												 	"connectance", "spp. richness", 
+                												 	"ratio plant/pollinator"))) %>%
+  dplyr::arrange(-pare, -Importance, factor) %>% 
+  dplyr::select(-pare) %>%
+  magrittr::set_names(c(" ", "est.", "var", "mod.", "imp.", "C.I.")) %>%
+			dplyr::select(-var, -mod.)
+
+manag_table %>%
+	xtable::xtable(caption = "\\textbf{Coefficients of the $n_D$ models}. Estimates are averaged over the models that accounted for 95\\% of the evidence weight.",
+										 digits =  c(0, 0, 2, 2, 2),
+										 display = c("d", "s", "f", "f", "G")) %>%
+	print(booktabs = T, include.rownames = F,  caption.placement = "top", comment = F, sanitize.text.function = function(x){x})
+
+```
+
 # References

### 2017-02-23 paper/draft_2.Rmd
Update results

@@
 library(ggplot2)
+library(glmulti)
+library(lme4)
 
@@
 cowplot::plot_grid(p1, p2, ncol = 1, align = "v") +
-	cowplot::draw_plot_label(label = c("a)", "b)"), size = 8, fontface = "plain", y = c(1, 0.5))
+	cowplot::draw_plot_label(label = c("(a)", "(b)"), size = 8, fontface = "bold", y = c(1, 0.5))
 # pdf("../paper/figures/fig_3.pdf", height = 1.7, width = 3.245, family = "Times", compress = F, title = "Figure 3")
@@
 
-When exploring the effect of network structure itself, we observed that the manageability of empirical networks was, in general, not significantly different to the manageability of network randomisations that maintained the degree or the strength of individual species (Figure 4).
-However, when comparing the empirical network to randomisations that maintained the network structure but randomised only the direction of the asymmetries, we found that empirical networks showed a significant tendency to have smaller values of manageability.
+When exploring the effect of network structure itself, we observed that the driver node density $n_D$ of empirical networks was, in general, not significantly different to the manageability of network randomisations that maintained the degree of individual species (Figure 4).
+However, we found that the $n_D$ of empirical networks was significantly larger to that of randomisations that maintained the network structure but that differed only on the direction of the asymmetries.
 
-```{r fig_randomisations, echo = FALSE, warning = FALSE, message = FALSE, fig.width = 3.245, fig.height = 1.6, fig.cap = "The manageability of empirical networks compared to network randomisations.
+```{r fig_randomisations, echo = FALSE, warning = FALSE, message = FALSE, fig.width = 3.245, fig.height = 1.6, fig.cap = "**The driver node density _n~D~_ of empirical networks compared to network randomisations**.
 For each randomisation approach, we show the standarised rank of the empirical value compared to the set of randomisations.
 A scaled mean rank—akin to a p-value— less than 0.025 or greater than 0.975 (the areas shaded in light grey) suggests a significant difference between the empirical network and its randomisations.
-The empirical manageability is much smaller than that of network randomisations in which the direction of asymmetries has been randomised.
-In contrast, the manageability of networks in which the species degrees were randomly shuffled were not significantly different to the manageability of the empirical networks.
-Dark grey and white boxplots represent manageabilities obtained using interactions weighted by mutual dependences and asymmetries respectively.
+The empirical _n~D~_ is much smaller than that of network randomisations in which the direction of asymmetries has been randomised.
+In contrast, the manageability of networks in which the species degrees were randomly shuffled were not significantly different.
 All boxes are as in Figure 3a."}
@@
   														 "swsh_both")) %>% # the maintain degree randomise strength option
-  ggplot(aes(x = method, y = -1 * z_s)) +
+	dplyr::filter(type == "weight") %>%
+  ggplot(aes(x = method, y = z_s)) +
   geom_rect(aes(xmin = 0.5, xmax = 2.5, ymin = -Inf, ymax = qlogis(0.025)), fill = "#f0f0f0") +
@@
   # geom_hline(yintercept = c(-0), linetype = 2, alpha = 0.7, size = 0.25) + 
-  geom_vline(aes(xintercept = 1.5), alpha = 0.6, size = 0.25) +
+  # geom_vline(aes(xintercept = 1.5), alpha = 0.6, size = 0.25) +
    geom_hline(yintercept = 0, size = 0.25, linetype = 2, colour = "grey30") +
@@
     coord_flip() +
-  ylab("mean rank of empirical manageability") + 
+  ylab(expression(paste("empirical ", n[D], " rank (scaled)"))) + 
   fer_theme +
@@
 
-```{r}
-d_sp <- driver %>%
-  plyr::ldply(function(x) {
-    get_frequencies(x) %>%
-      dplyr::mutate(type = attr(x, "type"),
-                    scaled = attr(x, "scaled"))
-  }) %>% 
-	dplyr::filter(scaled == FALSE)
+Invasive species were classified as superior nodes *and* driver nodes in every single network they were present; that is, they always had the highest relative *f~S~* and *f~D~* (Figure 5a). 
+The model results suggest that this differences among invasive and native species are underpinned, not by any intrinsic property of the invasive species but instead, by species properties that apply to invasive and native species alike (Table 1).
+Specifically, we found that a species is more likely to be classified as a superior node if it had a large dependence strength (its sum of the dependences). 
+To a smaller extent, visitation strength (its sum of visits) and the species degree also had a positive relationship with $f_S$. 
+In contrast, the relationships between species structural properties and $f_D$ was more convoluted (Table 1). 
+Both invasive species (which for example tend to have a large degree, and high dependence strength) and pollinators (which generally have a smaller degree and dependence strength) were classified as driver nodes in a large proportion of the considered matchings.
 
-d_sp_bi <- driver_bi %>%
-  get_frequencies() %>%
-      dplyr::mutate(type = "z_bi",
-                    scaled = FALSE)
+```{r glmulti-functions, include = FALSE, warning = FALSE, message = FALSE, results = "hide"}
+glmer.glmulti<-function(formula,data,random="",...){
+  glmer(paste(deparse(formula, width.cutoff = 500),random),data=data,...)
+}
 
-d_sp <- dplyr::bind_rows(d_sp, d_sp_bi) %>%
-  dplyr::inner_join(meta) 
+setMethod('getfit', 'glmerMod', function(object, ...) {
+  summ <- coef(summary(object))
+  summ1 <- summ[,1:2,drop=FALSE]
+  ## if (length(dimnames(summ)[[1]])==1) {
+  ##     summ1 <- matrix(summ1, nr=1,
+  ##                     dimnames=list(c("(Intercept)"),
+  ##                     c("Estimate","Std. Error")))
+  ## }
+  cbind(summ1, df=rep(times =10000,length(fixef(object))))
+})
+```
+
+```{r fig-dependency-fs, echo = FALSE, warning = FALSE, message = FALSE, fig.width = 3.245, fig.height = 3.2, fig.cap = "**Relatiosnships between _f~S~_ and _f~D~_ and species' structural properties**.
+(a) In all networks were they were present, invasive species were classified as superior (_f~S~_) and driver (_f~D~_) nodes in all possible control configurations.
+(b) Dependency strength is the single most important factor explaining _f~S~_.
+Visitation strength and  degree also had an important albeit comparatively smaller effect (dashed lines correspond to ± one standard deviation on these factors).
+Invasive species are depicted as circles."}
+data <- mo 
+trans <- function(x, orig){
+  x * attr(orig, "scaled:scale") + attr(orig, "scaled:center")
+}
+
+b_trans <- function(x, orig){
+  (x - attr(orig, "scaled:center")) / attr(orig, "scaled:scale")
+}
+
+pred_data <- data.frame(de = rep(b_trans(exp(c(seq(
+	log(trans(min(data$de, na.rm = T), data$de)),
+	log(trans(max(data$de, na.rm = T), data$de)),
+                                length = 500))), data$de),3),
+            d = rep(c(-1,0,1), each = 500),
+            vi = rep(c(-1,0,1), each = 500),
+            type = rep(c("exp", "mean", "exp"), each = 500),
+            # vi = seq(min(data$vi), max(data$vi), length.out = 500),
+            eig_cen = mean(data$eig_cen, na.rm = T),
+            n = mean(data$n, na.rm = T),
+            guild = "pla")  %>%
+  dplyr::filter(!(n == 2 & vi == -2),
+                !(n == -2 & vi == 2)) %>%
+  dplyr::mutate(q = predict.glmulti(mod[[1]],
+                                    select = 2L,
+                                    newdata = .,
+                                    re.form = NA)$averages %>%
+                  as.vector(),
+                p = plogis(q)) %>%
+  dplyr::mutate(de = de * attr(data$de, "scaled:scale") + attr(data$de, "scaled:center"),
+                vi = vi * attr(data$vi, "scaled:scale") + attr(data$vi, "scaled:center"))
+
+data_pp <- data
+data_pp$pred_ri <- plogis(predict.glmulti(mod[[1]], re.form = NA, select = 1L))
+data_pp$de_s <- data$de * attr(data$de, "scaled:scale") + attr(data$de, "scaled:center")
+data_pp <- lapply(data_pp, as.vector) %>% as.data.frame
+
+p1 <- pred_data %>%
+  ggplot() +
+  geom_line(aes(x = de, y = p, linetype = type, colour = type, group = interaction(n, vi)), show.legend = F, size = 0.5) +
+  scale_x_log10(expand = c(0,0)) +
+   geom_point(data = dplyr::arrange(data_pp, invasive) %>% dplyr::filter(invasive == T), aes(x = de_s, y = pred_ri, fill = invasive, shape = guild, size = invasive), show.legend = F) +
+    scale_shape_manual(values = c(21, 23)) +
+  scale_size_manual(values = c(1.5,1.5)) +
+  scale_fill_manual(values = c("white","#e41a1c")) + 
+  scale_color_manual(values = c("#525252", "black")) +
+  scale_linetype_manual(values = c(2, 1)) +
+  xlab("dependency strength") +
+  ylab(expression(f[S])) +
+  fer_theme
+
+# invasive comparison plot
+p2 <- mo %>%
+	# dplyr::filter(guild == "pla") %>%
+	dplyr::select(invasive, f_s, f_d) %>%
+	reshape2::melt(measure.vars = c("f_s", "f_d")) %>%
+	ggplot(aes(y = value, x = invasive, colour = variable)) + 
+	geom_boxplot(size = 0.3, outlier.shape = 21, outlier.size = 1)  +
+    # coord_flip() +
+  ylab("proportion") + 
+	scale_x_discrete(name = "", labels = c("native", "invasive")) +
+  fer_theme +
+  theme(legend.position = c(0.99,0.02),
+  			legend.direction = "horizontal",
+  			legend.justification = c(1,0),
+				plot.margin = grid::unit(c(2, 1, 0, 0), "mm"), 
+				# panel.grid.minor.x = element_blank(),
+				panel.grid.minor.y = element_blank()) +
+	scale_color_manual(values = RColorBrewer::brewer.pal(5, "Greys")[c(5,4)],
+										 name = "", 
+										 labels = c(expression(f[S]), expression(f[D])))
+
+cowplot::plot_grid(p2, p1, ncol = 1, labels = c("(a)", "(b)"), label_size = 8, 
+									 hjust = 0, vjust = 1.1, align = "v", rel_heights = c(1,1.16))
+```
+
+```{r table-species-model-coef, echo = FALSE, warning = FALSE, message = FALSE, results = "asis", sanitize = FALSE, cache = T}
+coef_tables <- mod %>%
+	plyr::llply(function(x){
+		x %>%
+			coef.glmulti(select = 0.95) %>%
+  as.data.frame()  %>%
+  dplyr::add_rownames("factor") %>%
+  dplyr::mutate(pare = grepl("(", factor, fixed =T),
+                factor = plyr::mapvalues(factor, 
+                                         c("de", "n", "vi", "eig_cen", 
+                                           "guildpol", "d", "invasiveTRUE"),
+                                         c("dependency strength", 
+                                           "contribution to nestedness",
+                                           "visitation strength",
+                                           "eigen-centrality", 
+                                           "guild (pollinator)", "degree", "invasive sp."))) %>% 
+  magrittr::set_names(c("factor", "est.", "var", "mod.", "imp.", "C.I.", "pare")) %>%
+			dplyr::mutate(absEstimate = abs(est.)/C.I.) %>%
+  dplyr::arrange(-pare, -imp., -absEstimate, factor) %>% 
+  dplyr::select(-pare, - absEstimate)
+	})
+
+coef_tables %<>%
+	plyr::llply(function(x){
+		x %>%
+  magrittr::set_names(c(" ", "est.", "var", "mod.", "imp.", "C.I.")) %>%
+			dplyr::select(-var, -mod.)
+	})
+
+attr(coef_tables, "subheadings") <- paste0("$", names(mod), "$")
+coef_tables %>%
+	xtable::xtableList(caption = "\\textbf{Factors determining species importance}. Factor estimates correspond to the average over all models that accounted for 95\\% of the AIC evidence.",
+										 digits =  c(0, 0, 2, 2, 2),
+										 display = c("d", "s", "f", "f", "G")) %>%
+	print(booktabs = T, include.rownames = F,  caption.placement = "top", size = "\\small",comment = F, sanitize.text.function = function(x){x})
 ```
@@
 From the control perspective, driver nodes are those to which external control signals must be applied in order to gain full control of the network.
+
+*n~D~*
+  ~ The density of driver nodes
 

### 2017-02-23 paper/draft_2.Rmd
Changes to methods and intro with Daniel's suggestions

@@
 Specifically, we use a set of ten pairs of uninvaded and invaded plant-pollinator communities to investigate the link between invasion, network structure and ecological management. 
-While doing so, we ask two questions framed in the context of a plant invasion.
+While doing so, we focus on two particular questions.
 First, grounded on the difficulties usually involved with invasive species erradication and ecosystem restoration [@Woodford2016], we ask whether invaded networks have lower levels of "manageability" than their uninvaded counterparts; that is, whether they require a greater proportion of species to be managed to achieve the same level of control.
 Second, we ask whether some species are more important than others at driving the population dynamics of the community and which factors determine this importance. 
-We focus on these particular applications for a variety of reasons. 
+We focus on these two particular applications for a variety of reasons. 
 First, biotic invasions are known to produce tractable changes in the structure of ecological networks, and these changes can be particularly pronounced in mutualistic networks between plants and pollinators where biotic invasions have been shown to modify the strength of species interactions and the degree of network nestedness and connectivity [@Olesen2002; @Aizen2008; @Bartomeus2008; @Vila2009; @Traveset2013].
@@
 
-Disregarding practical considerations, any network could, in theory, be fully controlled if we control the state of every single node individually.
+Disregarding practical considerations, any network could hypothetically be fully controlled if we control the state of every single node individually.
 At the core of control theory of complex networks, however, rests the idea that the state of a node depends on the state of the nodes it interacts with, and the particular form of this dependence is determined both by the dynamic relationship among interacting nodes as well as the structure of the links in the network.
-This principle can, therefore, be harnessed to find a subset of driver nodes to which to apply external input signals which then drive the state of every other node in the network to a desired configuration.
+This principle can, therefore, be harnessed to find a subset of *driver nodes* to which to apply external input signals which then drive the state of every other node in the network to a desired configuration.
 
@@
 Therefore, the density of driver nodes $n_D = \frac{D}{S}$, where *S* is the total number of species in the community, can be seen as a metric of the extent to which network structure can be harnessed for network control.
-For instance, while a hypothetical "network" in which species do not interact but instead function independently from each other would require direct interventions in every single species to achieve full control, a linear food chain would require just one species to be directly controlled to knock-on cascading effects trough the trophic levels that compose it.
+For instance, while a hypothetical "network" in which species do not interact but instead function independently from each other would require direct interventions in every single species to achieve full control, a linear food chain would require just one species to be directly controlled to harness cascading effects through the trophic levels that compose it.
 From this perspective, it is possible to use *n~D~* as an index of the manageability of an ecological community, understood in the context of how difficult is to modify the abundances of species in the community using external interventions—a common theme in ecosystem management, conservation, and restoration.
@@
 
-# legend(1-0.16 + 0.05, 0.9, legend = expression(paste(bold("(bold label)"), " ", "superior nodes")), horiz = TRUE,
+n
 # 			 cex = 0.9, xjust=0.5, yjust=1, bty = "n")
@@
 ```
+
+Note that this framework requires a directed network in which the direction of the links corresponds to the direction of control. 
+In the "Empirical application" section below, we explain our approach to determining the link direction in pollination networks.
 
@@
 One possibility is to characterise a species by the frequency *f~D~* with which it is classified as a driver node.
-However, the role of driver nodes is still ambiguous when **full** network controllability is unfeasible or undesired—which is often the case in ecological settings.
-We therefore also calculate the frequency *f~S~* with which a species is classified as superior nodes since this is the frequency with which they form part of possible control paths—intervention strategies from a management perspective.
+However, the profile of our networks indicates that a large proportion of driver nodes are so, because of external interventions are required to achieve **full** controllability, and not because they influence the abbundance of other species (Supporting Information S2).
+Furthermore, the role of driver nodes is still ambiguous when **full** network controllability is unfeasible or undesired—which is often the case in ecological settings.
+We therefore also calculate the frequency *f~S~* with which a species is classified as superior nodes since this is the frequency with which they form part of possible control paths.
 
 Most commonly, structural controllability assumes unweighted networks—links exist or not, and hence *f~D~* and *f~S~* can be calculated by computing all possible maximum cardinality matchings. 
-However, it has been shown that using weighted links can reveal significant ecological patterns and processes that might be undetectable in unweighted networks [@Scotti2007; @Tylianakis2007; @Vazquez2007; @Kaiser-Bunbury2010a].
+However, we take the link weights into account when calculating the matchings because it has been shown that the weights can reveal significant ecological patterns and processes that might be undetectable in unweighted networks [@Scotti2007; @Tylianakis2007; @Vazquez2007; @Kaiser-Bunbury2010a].
 For example, a species *A* interacts with both species *B* and *C* but depends strongly on *B* and only weakly on *C*. 
@@
 
-We now describe the application of the previously defined framework to ten paired pollination networks, where each network pair was composed of a community invaded by a plant and a community "free" of the invasive species.
+We now describe the application of the previously defined framework to ten paired pollination networks.
+Each network pair was composed of a community invaded by a plant and a community "free" of the invasive species. 
 Four pairs were obtained from natural or semi-natural vegetation communities in the city of Bristol, UK [@Lopezaraiza-Mikel2007]. 
-These networks are comprised of `r lop[1]`-`r lop[6]` species (mean `r round(lop[4])`), and non-invaded plots were obtained by experimentally removing all the flowers of the invasive species *Impatients grandulifera*.
+These networks are comprised of `r lop[1]`--`r lop[6]` species (mean `r round(lop[4])`), and non-invaded plots were obtained by experimentally removing all the flowers of the invasive species *Impatients grandulifera*.
 The other six pairs were obtained from lower diversity Mediterranean shrublands in Cap de Creus National Park, Spain [@Bartomeus2008].
-These networks are comprised of `r bar[1]`-`r bar[6]` species (mean `r round(bar[4])`); in contrast to the above, uninvaded communities were obtained from plots that had not yet been colonised by either of the invasive species *Carpobrotus affine acinaciformis* or *Opuntia stricta*.
-Further details about the empirical networks can be found in the Supporting Information Table 1.
+These networks are comprised of `r bar[1]`--`r bar[6]` species (mean `r round(bar[4])`); in contrast to the above, uninvaded communities were obtained from plots that had not yet been colonised by either of the invasive species *Carpobrotus affine acinaciformis* or *Opuntia stricta*.
+Further details about the empirical networks can be found in the Supporting Information S3.
 
 We then specified the structure of all networks using pollinator visitation frequency, which has been shown to be an appropriate surrogate for interspecific effects in pollination networks [@Vazquez2005; @Bascompte2006].
-To examine whether this decision would influence our results, we also evaluated the effect of using pollinator efficiency or pollinator importance as alternative measures of species interactions in a different data set that lacked invasive species [@NeEman2010; @Ballantyne2015], and we found quantitatively similar results for all three of these options (Supplementary Information XXX).
-Furthermore, because our approach depends to a large degree on the network topology, we evaluated the robustness of our results to undersampling.
-Specifically, we calculated *n~D~*, and species relative importance (see below) for 500 random subsamples of each empirirical network in which the weakest links were more likely to be removed. 
-The sensitivity analysis indicated that even in the absence of complete sampling a control theoretic approach can be applied (Supplementary Information XXX).
+To further examine whether this decision would influence our results, we also evaluated the effect of using pollinator efficiency or pollinator importance as alternative measures of species interactions in a different data set that lacked invasive species [@NeEman2010; @Ballantyne2015], and we found quantitatively similar results for all three of these options (Supporting Information S4).
+In addition, because our approach depends to a large degree on the network topology, we evaluated the robustness of our results to the undersampling of ecological interactions.
+Specifically, we calculated *n~D~*, and species relative importance for 500 random subsamples of each empirical network in which the weakest links were more likely to be removed. 
+The sensitivity analysis indicated that, even in the absence of complete sampling, a control theoretic approach can still be applied (Supporting Information S5).
 
@@
 We began by quantifying the manageability of each of the aforementioned networks.
-To do so, we calculated the networks' maximum matching and determined the minimum proportion of species *n~D~* that need external input signals—a management intervention—to fully control the species abundances in the community.
-To simplify the analysis, we only considered the largest component in a network if it had more than one (two species are in different components if there exists no path between them and are hence independent of each other in terms of network control).
+To do so, we calculated the networks' maximum matching and determined the minimum proportion of species *n~D~* that need external input signals to fully control the species abundances in the community.
+Note that because all maximum matchings have the same matching size, it is only necessary to calculate one of them. 
+To simplify the analysis, if a network had more than one component (two species are in different components if there exists no path between them and are hence independent of each other in terms of network control) we only considered the largest.
 Smaller components were present in eleven out of the twenty networks and were typically composed of just one plant and one pollinator. 
@@
 
-Recall that the aforementioned maximum matching algorithm requires a directed network in which a link between species *i* and *j* pointing to species *j* indicates that the abundance of *j* can be affected by the abundance of *i*.
+Recall that the aforementioned maximum-matching approach requires a directed network in which a link between species *i* and *j* pointing to species *j* indicates that the abundance of *j* can be affected by the abundance of *i*.
 This implies that we need first to identify a directionality for the links between species that is consistent with the dynamics of the community (Figure 2). 
-In some ecological networks, establishing the directionality is relatively straightforward, for example when links represent biomass transfer or energy flow. 
+In some ecological networks, establishing the directionality can appear relatively straightforward, for example when links represent biomass transfer or energy flow. 
 Interspecific effects in pollination networks, however, are not strictly directed since the benefit is mutual between interacting species. 
-Nevertheless, the relative extent to which a given pair of interacting species affect each other can be quantified by the magnitude of the mutual dependence [@Bascompte2006]. 
+Nevertheless, the relative extent to which a given pair of interacting species affect each other can be quantified by the magnitude of the mutual dependence between them [@Bascompte2006]. 
 The dependence of plant *i* on pollinator *j*, *d~ij~*, is the proportion of the visits coming from pollinator *j* compared to all pollinator visits to plant *i*. 
 Likewise, the dependence of pollinator *j* on plant *i*, *d~ji~*, is the proportion of the visits by pollinator *j* to plant *i* and all visits of pollinator *j*.
-As the dependences are not symmetric, their use generates a weighted bipartite network in which all interacting pairs are connected by two directed links (Figure 2b).
+As the dependences are not necessarily symmetric, their use generates a weighted bipartite network in which all interacting pairs are connected by two directed links (Figure 2b).
 
@@
 			 margin = ma)
-text(label_pos_x, label_pos_y, "a)", adj = c(0,0))
+text(label_pos_x, label_pos_y, "(a)", adj = c(0,0), font = 2)
 
@@
 			 margin = ma)
-text(label_pos_x, label_pos_y, "b)", adj = c(0,0))
+text(label_pos_x, label_pos_y, "(b)", adj = c(0,0), font = 2)
 
@@
 			 margin = ma)
-text(label_pos_x, label_pos_y, "c)", adj = c(0,0))
+text(label_pos_x, label_pos_y, "(c)", adj = c(0,0), font = 2)
 
@@
 
-Given the respective dependences, the extent to which a species $i$ affects species *j* relative to the extent to which *j* affects *i* can be summarised by the interaction asymmetry given by $$a(i,j) = \frac{\left | d_{ij}-d_{ji} \right |}{max\left ( d_{ij}, d_{ji} \right )}.$$
-Mutual dependences have previously been shown to be highly asymmetric in natural communities [@Bascompte2006]; in other words, if a plant species is largely dependent on a pollinator species, then that pollinator tends to depend rather weakly on the plant (or vice versa).
-This suggests that it may be possible to relax the assumption of bidirectional dependences further and simplify the network such that interacting species are connected by only one directed link when mutual dependences are asymmetric (Figure 2c).
-We found here that changing to unidirectional interactions determined by the observed direction of asymmetry, as a surrogate of bidirectional mutual dependences does not alter the relative *n~D~* of different networks (Supplementary Information XXX).
-Moreover, this simplification confers an additional advantage for our purposes since it dramatically reduces the number of links in the network. 
-This translates into a substantial reduction of the time and memory required for the computation of all possible maximum matchings in a network, particularly for large networks (see "Relative importance" subsection below).
+Given the respective dependences, the extent to which a species *i* affects species *j* relative to the extent to which *j* affects *i* can be summarised by the interaction asymmetry [@Bascompte2006] given by $$a(i,j) = \frac{\left | d_{ij}-d_{ji} \right |}{max\left ( d_{ij}, d_{ji} \right )}.$$
+Previous research has shown that mutual dependences are often highly asymmetric in natural communities [@Bascompte2006]; in other words, if a plant species is largely dependent on a pollinator species, then that pollinator tends to depend rather weakly on the plant (or vice versa).
+We therefore simplified the network so that interacting species are connected by only one directed link when mutual dependences are asymmetric (Figure 2c).
+This simplification, while maintaining ecological realism, is advantageous for several reasons. 
+First, it is consistent with previous advances in structural controlability; second, it avoids complications related to the introduction of artificial control cycles; and third it significantly reduces the computational resources necessary for the application of our approach (Supporting Information S6).
+Furthermore, we show that changing to unidirectional interactions determined by the observed direction of asymmetry, as a surrogate of bidirectional mutual dependences does not alter the relative *n~D~* of different networks (Table S3).
 
-Finding the maximum matchings can be an expensive operation especially in large, directed, and highly connected networks.
-Although less computationally expensive heuristics to approximate the control profile of complex networks do exist [@Ruths2014], we found their use to be extremely sensitive to assumptions regarding the direction of control (Supplementary Materials Section 2).
-Consequently, we have adopted a strategy based on an alternative bipartite representation of the directed network in which the two levels indicate the outgoing and incoming links to each node (Supplementary Section XXX).
+To find a maximum matching, we adopted a strategy based on an alternative bipartite representation of the directed network in which the two levels indicate the outgoing and incoming links to each node (Supporting Information S1).
 Once we had this alternative representation, then, on each network, we used the maximum bipartite matching algorithm implemented in the `max_bipartite_match` function of igraph 1.0.1 [@Csardi2006a].
@@
 
-Although understanding the variability of manageability across ecological networks is a useful result itself, we also wanted to test whether invasion status had an impact on the observed *n~D~*. 
-We, therefore, used a set of generalised linear models (with binomial error structure) to investigate the effect of invasion status while also controlling for factors related to species richness, since one might naively expect to see a negative relationship between diversity and manageability [@Menge1995].
-These covariates included the total number of species, plant richness, pollinators richness, the ratio of plants to pollinators richness, the link density (connectance), and the study site (as a two-level factor).
-We assessed competing models by comparing the Akaike Information Criterion corrected for small sample sizes (AICc), and report results for the most parsimonious model.
+Although understanding the variability of manageability across ecological networks is a useful result in itself, we also wanted to test whether invasion status had an impact on the observed *n~D~*. 
+We, therefore, used a set of generalised linear models (with binomial error structure) to investigate the effect of invasion status while also controlling for factors related to species richness, since one might naively expect to see a negative relationship between richness and manageability [@Menge1995].
+These covariates included the total number of species, plant richness, pollinators richness, the ratio of plant to pollinator richness, the link density (connectance), and the study site (as a two-level factor).
+Candidate models were compared using AICc and the relative importance of the explanatory variables was evaluated using the sum of Akaike weights over candidate models that accounted for 95% of the evidence [@Burnham2003; @Bates2015; @Barton2016].
+Coefficient estimates were averaged following @Buckland1997a while confidence intervals were calculated following @Lukacs2010.
 
@@
 Previous research indicates a direct link between a network's degree distribution and the number of nodes necessary to fully control it [@Liu2011], but the strength and applicability of this relationship have not been tested for in weighted ecological networks.
-We therefore compared the driver node density *n~D~* of the empirical networks to networks generated by a null model that maintained each species' strength (its total sum of visits) while allowing their degrees (its number of interactions) to vary.
+We therefore compared the driver-node density *n~D~* of the empirical networks to networks generated by a null model that maintained each species' strength (its total sum of visits) while allowing their degrees (its number of interactions) to vary.
 Randomisations were generated using the function `commsim` in vegan 2.3-3 [@Oksanen2016]. 
-After generating the randomised networks, we then calculated the mutual dependences and interaction asymmetries of each and determined *n~D~*  using our maximum matching framework.
-Finally, we calculated the average rank (akin to a p-value) of *n~D~* for each empirical network compared to the corresponding one of each set of 999 randomisations.
+After generating the randomised networks, we then calculated the mutual dependences and interaction asymmetries of each, and determined *n~D~* using our maximum-matching framework.
+Finally, we calculated the average rank (akin to a p-value) of *n~D~* for each empirical network compared to the corresponding one of each set of 999 randomisations [@Veech2012].
 
 Beyond network structure, the dependence asymmetry plays a fundamental role in determining the direction of control in each two-species interaction and therefore has the potential to influence the network *n~D~* results above.
-We, therefore, performed an additional randomisation in which we kept the structure of network constant but randomised the direction of the interaction asymmetries. 
+We, therefore, performed an additional randomisation in which we kept the structure of each network constant but randomised the direction of the interaction asymmetries. 
 That is, we first calculated the observed asymmetries for each community and then shuffled the direction of the link between each pair of species. 
@@
 
-Our second key question is related to how species differ in their ability to drive the population dynamics of the community. 
-To quantify this importance we computed all maximal cardinality matchings in each network. 
+Our second key question was related to how species differ in their ability to drive the population dynamics of the community. 
+To quantify this importance, we computed all maximal cardinality matchings in each network. 
 We then calculated the frequency with which each species *i* is deemed to be a driver (*f~D~*) or a superior node (*f~S~*) in the set of matchings that had a matching weight greater or equal to 0.5 times the weight of the maximum matching.
-We selected this threshold as it provided a high agreement between networks quantified by visitation and pollination efficiency as well as between our weighting/directionality assumptions; however, the choice of this threshold had a negligible impact on any results (Supplementary Information XXX).
+We selected this threshold as it provided a high agreement between networks quantified by visitation and pollination efficiency as well as between our weighting/directionality assumptions; however, the choice of this threshold had a negligible impact on any results (Supporting Information S7).
 
-Even in sparse networks, like those studied here, the number of maximal matchings increases exponentially with the number of links and nodes in a network. 
-Unfortunately, this means that the large number of links in the most diverse communities rendered the computation unfeasible when we used mutual dependences. 
-Taking this limitation into account, we compared the relative species ranks obtained when using asymmetries to those found when using mutual dependences to test if they gave consistent results. 
-The comparison was performed for eleven of the twenty networks (those for which the number of matchings was smaller than 4 x 10^10^), using a paired Spearman correlation test, a weighted correlation coefficient *r~w2~* [which gives more weight to higher ranks; @PintoDaCosta2015], and a Jaccard similarity of the driver species in both approaches.
-All three approaches identified a high similarity in relative ranks (STILL NEED TO CHECK THAT FOR BOTH *f~D~* AND *f~S~*). 
-Consequently, we focused on the results when using the asymmetries rather than mutual dependences when further investigating the factors that determine species' relative importance since this also allows us to obtain results for all 20 networks.
-
-To compute all the maximum cardinality matchings, we first generate the network's line graph—another representation in which nodes are the links of the original network and links represent common ending points [@West2001].
-We then calculate the complement of this line graph, which generates a graph in which nodes are connected if and only if they are not connected in the line graph. 
-Finally, all possible maximal cardinality matchings can be found by enumerating every clique (subgraphs in which all nodes are fully connected to each other) of size *D* in this complement graph [@Csardi2006a; @Gutin2013].
-A graphical representation of this procedure can be found in Supplementary Information Fig XX.
+Details about the compuational procedure to find all maximum cardinality matchings of a network can be found in Supporting Information S1 and Figure S2.
 
@@
 
-We then examined whether some species-level structural properties can predict our metrics of species importance—the frequency to which a species is a driver or a superior node (*f~D~* and *f~S~* respectively).
+We then examined whether any species-level structural properties can predict our metrics of species importance—the frequency to which a species was a driver or a superior node (*f~D~* and *f~S~*, respectively).
 We used a set of generalised linear mixed-effects models (with binomial error structure) with the relative frequencies as the response variables. 
 As predictors in this model, we included measures of centrality (degree and eigen-centrality), which have been found to be strong predictors of importance in a coextinction context [@Memmott2004]; a measure related to network robustness (contribution to nestedness), as nestedness has been proposed as one of the key properties that promote stability in mutualistic networks [@Saavedra2011]; and two measures of strength of association and dependence (visitation and dependence strength), as their distribution determines the extent of interspecific effects [@Bascompte2006].
-In addition, we also included guild and invasive status as categorical fixed effects.
+To facilitate comparison among the continuous variables we scaled so that they all had a mean of zero and a standard deviation of one.
+In addition, we also included guild (plant or pollinator), and wether the species is invasive or not, as categorical fixed effects.
 Although the importance of plants and pollinators or invasive and non-invasive species could respond differently to our structural metrics, our data set did not contain enough variation to include the corresponding interactions terms for these latter two predictors.
 All network metrics were calculated using the R package bipartite 2.06 [@Dormann2008]. 
-We lastly allowed for variation between different communities by including the network identity as a random effect [@Bates2015]. 
-Candidate models were compared using AICc and the relative importance of the explanatory variables was evaluated using the sum of Akaike weights over candidate models that accounted for 95% of the evidence [@Burnham2003; @Bates2015; @Barton2016].
-Coefficient estimates were averaged following @Buckland1997a while confidence intervals were calculated following @Lukacs2010.
+Lastly, we allowed for variation between different communities by including the network identity as a random effect [@Bates2015]. 
+Candidate models and estimates were assessed using the same procedure as in the *n~D~* models.
 
@@
 
-All of the networks studied had a driver node density *n~D~* between `r round(min(dplyr::filter(n_driver, type == "z-bi")$n_dr_p), digits = 2)` and `r round(max(dplyr::filter(n_driver, type == "z-bi")$n_dr_p), digits = 2)` (mean `r round(mean(dplyr::filter(n_driver, type == "z-bi")$n_dr_p), digits = 2)`) when we considered bidirectional links weighted by the mutual dependences.
-This was in strong agreement with the results obtained using the dependence asymmetry for which *n~D~* ranged between `r round(min(dplyr::filter(n_driver, type == "weight")$n_dr_p), digits = 2)` and `r round(max(dplyr::filter(n_driver, type == "weight")$n_dr_p), digits = 2)` (mean `r round(mean(dplyr::filter(n_driver, type == "weight")$n_dr_p), digits = 2)`; Spearman rank correlation `r round(src_bi_w$estimate, digits = 2)`, *p* `r fix_small_pvalue(src_bi_w$p.value)`).
-In addition, we found that invaded communities had less driver node density than uninvaded ones even when controlling for potential diversity effects (Figure 3a). 
-Out of the various covariates we explored—total number of species, plant richness, pollinator richness, link density (connectance), and the ratio of plant to pollinator richness—only the ratio of plant to pollinator richness was retained in the final model as determined by the AICc (Figure 3b; Table S4).
+All of the networks studied had a driver node density *n~D~* between `r round(min(dplyr::filter(n_driver, type == "weight")$n_dr_p), digits = 2)` and `r round(max(dplyr::filter(n_driver, type == "weight")$n_dr_p), digits = 2)` (mean `r round(mean(dplyr::filter(n_driver, type == "weight")$n_dr_p), digits = 2)`.
+In addition, we found that, when controlling for potential species richness effects, the *n~D~* of invaded communities was smaller to those of non invaded communities (Figure 3a; Table S5). 
+Nevertheless of the various covariates we explored, the ratio of plant to pollinator showed the strongest relationship with *n~D~* (Table S4). 
+Specifically, we found that as the proportion of pollinators increasses and the ratio plant/pollinator balances, *n~D~* decreasses (all our communities had more pollinators than plants). 
+Other coovariates—connectance (link density) and species richness—had a neggative and comparatively less important relationship with *n~D~*.
 
-```{r fig_explaining-n-driver, echo = FALSE, warning = FALSE, message = FALSE, fig.width = 3.245, fig.height = 3.2, fig.cap = " Coovariates of driver node density.
+```{r fig_explaining-n-driver, echo = FALSE, warning = FALSE, message = FALSE, fig.width = 3.245, fig.height = 3.2, fig.cap = "**Coovariates of driver node density**.
 (a) Invaded communities have lower proportion of driver nodes *n~D~* than uninvaded communities even when controlling for factors related to species richness.
-The box covers the 25th–75th percentiles, the middle line marks the median, and the maximum length of the whiskers is 1.5 times the interquartile range.
+The boxes cover the 25th–75th percentiles, the middle lines mark the median, and the maximum length of the whiskers is 1.5 times the interquartile range.
 All points outside this range are indicated by the circles.
-(b) Out of the biodiversity metrics, only the ratio of plants to pollinators showed a significant relationship with *n~D~*.
+(b) Out of the richness metrics, the ratio of plants to pollinators showed an important relationship with *n~D~*.
 In both plots, residuals correspond to the partial working residuals of the invasion status in our generalised linear mixed model."}
 
-par_res <- as.data.frame(residuals(manag_models@objects[[1]], "partial"))
+par_res <- as.data.frame(residuals(manag_models@objects[[5]], "partial"))
 names(par_res) <- paste0(make.names(names(par_res)), "_res")

### 2017-02-23 paper/draft_2.Rmd
Add old discussion

@@
 
+# Discussion
+
+Our results reveal that the structural differences among associated with biotic invasions are reflected in a potential decrease in our ability to alter the state of the community post invasion. 
+Furthermore, invasive mutualists were always driver species in the communities they invade.
+As driver species, they occupy a particularly dominant role in which changes on their abundance have the potential to propagate broadly trough the community and in turn affect the abundances of many other species.
+
+At a community level, we demonstrate that the manageability of mutualistic networks is strongly governed by the asymmetric nature of mutual dependencies—which constitute the foundations of the structure and stability of mutualistic networks [@Memmott2004; @Vazquez2004; @Bascompte2006; @Lever2014; @Astegiano2015].
+Indeed, our empirical networks exhibit markedly lower levels of manageability compared to randomisations in which the visitation network was unchanged but where the observed patterns of dependence were broken.
+However, consistent with previous results [@Liu2011], we show that the manageability of empirical networks was indistinguishable from that of networks with a random structure that maintained the degree or strength of each species in the community.
+Therefore, the asymmetries at the species level (specialization-generalization asymmetries) and the link level (interaction's dependence asymmetries) appear to be sufficiently constrained by the distribution of species degree and strength [@Melian2002].
+Generally speaking, this strong relationship between the asymmetric dependences and manageability might explain why invasive species reduce the manageability of their communities. 
+Invasive species have been previously found to exacerbate the asymmetries in the network and ostensibly increase the stability of their community [@Aizen2008; @Bartomeus2008; @Henriksson2016].
+
+The changes in the asymmetries we found in the invaded networks are also reflected at a species level by the high relative importance of invasive species.
+However, we found that invasive plants are not inherently different to their native counterparts [@Stouffer2014].
+Invasive plants, just like any other mutualist in our data set, tend to be driver species to the degree to which their interaction partners are collectively more dependent on them than the other way around.
+Previous studies have found that super-generalists, like invasive species, play a central role in their networks [@Vila2009; @Palacio2016].
+Our results take this one step further and indicate that dependence strength, rather than generalism or other metrics of centrality, is the factor that best explains how important a species is for its community's dynamics.
+XXX - ADD STUFF ABOUT FS AND FD FOR MANAGEMENT AND CONTRASTS TO RUTHS
+
+Because of their effects on other species in the community, driver species might be natural candidates for management interventions. 
+For instance, despite inconsistent outcomes in practice [@Suding2004; @Rodewald2015; @Smith2016], our results suggest that current restoration approaches that focus on direct eradication of invasive species might indeed be an effective way to modify ecosystem state.
+Nevertheless, our results also indicate that removals must be exercised with caution as invaded communities tend to be highly dependent on invaders and therefore acutely vulnerable to their eradication [@Traveset2013; @Albrecht2014].
+Although useful for identifying conservation priorities, our approach is different to previous attempts to quantify species importance that concentrate on measures of centrality, position, co-extinction or uniqueness [@Jordan2006; @Jordan2009; @Lai2012; @McDonald-Madden2016].
+XXX ADD CAVEATS - MACDONALDMADDEN 2016 - NETWORK METRICS - POPULATION DENSITIES CONTROLED BY OTHER THINGS BUT POLLINATION 
+Instead the concept of driver species is more akin to the original concept of keystone species, which illustrated how changes on the abundance of a key species in turn affect the abundances of other members of the community [@Paine1969; @Paine1995].
+However, while keystone species were traditionally identified by gauging how a community's population dynamics respond to a perturbation [@Mills1993], the driver species concept operates the other way round; namely, it uses the community dynamics, underpinned by the interspecific effects, to infer the effects of a perturbation.
+While it is challenging to quantify the dependence of species in an ecological community, a purely experimental approach that identifies dynamically important species in a similar manner might be even more difficult to implement.
+
+Overall, our investigation confirms the conclusions of previous studies that suggested that, in contrast to other types of complex systems, the structure of ecological networks renders them remarkably difficult to control [@Liu2011; @Ruths2014].
+In a hypothetical situation in which the goal were to regulate the abundances of all species in a pollination community, our results indeed suggest that we would need to directly intervene with the abundances of at least 40-90% of those species.
+Fully controlling an ecological community is no doubt an idealistaion, as designing and implementing the management interventions needed is currently impractical. 
+Nevertheless, the ''manageability'' of an ecological community, which is related to the number of species that would require a directed intervention, can provide a simple, straightforward, and theoretically-informed indication of the degree to which the community is self-regulated and therefore how difficult it might be to modify its state in one way or another.
+XXX - ADD STUFF RELATING TO OTHER TYPES OF INTERACTIONS
+
+In this study, we illustrate how a control-theoretic approach can be adopted when estimating the effect of invasions—a major driver of global change—on mutualistic communities.
+Notably, it can also be extended to understand the structural effects of other kind of perturbations and for systems governed by different types of interactions. 
+Moreover, we see great potential by explicitly integrating control theory with dynamic models of species densities [@Cornelius2013; @Gibson2016]. 
+From an ecological perspective, this integration can provide even deeper insights into the relationship between controllability and species coexistence.
+It can also help identify potential trade-offs between persistence at the species and the community level. 
+From a conservation perspective, the combined approach can shift our focus beyond the identification of ideal targets for intervention to design informed interventions that legitimately achieve restoration goals.
+
 # Appendix 1: Glossary

### 2017-02-24 paper/draft_2.Rmd
Update discussion

--- 2017-02-23 paper/draft_2.Rmd
@@
 
+# Discussion
+
+Contrary to our initial hypothesis, we found some evidence that invaded communities might be easier to manage than uninvaded ones. 
+Our results reveal, however, that this effect is comparatively small and the structural differences among different networks are more importantly related to potential differences in our ability to alter the state of the community.
+Despite the small effect of invasion status at a network level, we found that invasive mutualists occupy a particularly dominant role in their communities. 
+Not only changes on their abundance have the potential to propagate broadly trough the community and in turn, affect the abundances of many other species, but they are also indispensable to fully control the plant-pollinator network.
+At a community level, we demonstrate that the manageability of mutualistic networks is strongly governed by the asymmetric nature of mutual dependencies—which constitute the foundations of the structure and stability of mutualistic networks [@Memmott2004; @Vazquez2004; @Bascompte2006; @Lever2014; @Astegiano2015].
+Moreover, these mutual dependences seem to be importantly constrained by the concerted effects of both, the patterns of species richness at each trophic guild, and the species' degree distribution [@Melian2002; @Bluthgen2007].
+Indeed, the difference between the driver node density (*n~D~*) of our empirical networks and that of randomisations depended strongly on the evaluated null model. 
+While the empirical *n~D~* was indistinguishable from that of networks with a random structure that maintained the degree or strength of each species in the community, it was much larger than that of randomisations in which the directed network was unchanged but where the observed patterns of dependence were broken.
+
+Invasive species have been previously found to exacerbate the asymmetries in their communities [@Aizen2008; @Bartomeus2008; @Henriksson2016]. 
+Although this might cause differences both at the community and the species level, we found that invasive plants are not inherently different to their native counterparts [@Stouffer2014].
+Invasive plants, just like any other mutualist in our data set, tend to be classified as a superior node with a frequency (*f~S~*) proportional to the degree to which their interaction partners are collectively more dependent on them than the other way around.
+Previous studies have found that super-generalists, like invasive species, play a central role in their networks [@Vila2009; @Palacio2016].
+Our results take this one step further and indicate that dependence strength, rather than generalism or other metrics of centrality, is the factor that best explains the cascading effects a species could trigger on its community.
+
+Because of the ability that our approach has to infer the magnitude of the effects that each species has on others in the community, it is tantalising to use it to select promising candidates for management interventions.
+The two indices we employed to characterise a species provide two complementary pieces of information. 
+Our first index, the frequency with which a species is classified as a driver node (*f~D~*) provides an indication of the likelihood the species is part of the set of species that need to be intervened in order to control of *all* species in the community.
+The driver node concept has received considerable attention in the structural control literature and indeed shows substantial potential to provide useful ecological insight. 
+Nevertheless, we anticipate two caveats that hinder its direct utility for management applications.
+First, unlike other types of complex systems, fully controlling an ecological community is realistically out of reach for all but the most simple ones; either because of the number of required interventions or the difficulties of their implementation [@Motter2015].
+For instance, our results suggest that full control of the pollination network would require direct interventions on 40-90% of the species.
+Second, @Ruths2014 established that driver nodes arise due to distinct mechanisms and therefore species with markedly different network metrics can be driver nodes in their community (Supporting information S2).
+
+Our second index *f~S~* is, however, directly related to the likelihood a species has to affect the abundance of another species in all of the considered control strategies. 
+Importantly, this is irrespective of whether controlling the entire network is desired/feasible or not. 
+In fact, because superior nodes are invariantly at the beginning of a matching link, species with a high *f~S~* are more likely to be the subjects of management interventions when controlling the abundances of a target set of species—and not the entire network—is desired [@Gao2014].
+An important advantage is that the target set of species does not has to be the same set to which interventions are applied. 
+For instance, despite inconsistent outcomes in practice [@Suding2004; @Rodewald2015; @Smith2016], our results suggest that current restoration approaches that focus on direct eradication of invasive species might indeed be an effective way to modify ecosystem state.
+Nevertheless, our results also indicate that removals must be exercised with caution as invaded communities tend to be highly dependent on invaders and therefore acutely vulnerable to their eradication [@Traveset2013; @Albrecht2014].
+
+Although *f~S~*, in particular, is promising for identifying species priorities, our approach is different to previous attempts to quantify species importance. 
+Existing metrics usually harness species features like centrality, position, co-extinction or uniqueness, to infer their effect on other species [@Allesina2004; @Jordan2006; @Jordan2009; @Lai2012]. 
+Contrastingly, our control-based approach, by definition, tackles that question directly.
+Although relatively simple to calculate, it has been shown that classic species-level network metrics do not necessarily reveal the best set of species to manage [@Eklof2013; @McDonald-Madden2016].
+Our approach, however, is not based on a single structural metric but acknowledges the existence of multiple management strategies; some more optimal than others in specific contexts. 
+Our, and other flexible approaches that take a network-wide approach might prove more useful to guide ecosystem management if we want to go beyond using network metrics to minimise topological species loss [@McDonald-Madden2016].
+
+Despite its conceptual advantages, our approach still relies on knowledge of the network of interaction between species. 
+Nevertheless, our results and previous basic research show that as long as the proportion of sampled links is enough to provide indication of the actual degree distribution (and in turn the species dependences), *n~D~*, *f~S~* and *f~D~* can still provide a simple, straightforward, and theoretically-informed indication of the degree to which the community is self-regulated and therefore how difficult it might be to modify its state in one way or another using some of the species that integrate it [Supporting Information S5; @Nepusz2012].
+
+In this study, we illustrate how a control-theoretic approach can be adopted in network ecology to evaluate the effect of invasions and another kind of perturbations. 
+Although, because of the degree constraints imposed by bipartite networks, our pollination specific results might not be relevant to other ecological systems, the approach we propose is applicable wherever species abundances are influenced by their interactions.
+Exciting open questions lie ahead: how to design the precise "control signals" to reach a desired ecosystem state or conservation outcome? 
+What are the implications of assuming linear species dynamics?
+How important is to include several interaction types for our understanding of manageability and species importance?
+What are the implications for species coexistence? 
+Which are the trade-offs between persistence at the species and the community level?
+
+Answering these questions might require its evaluation on different ecological systems, an explicit integration of control theory with numerical models of species densities [@Cornelius2013; @Gibson2016], and experimental tests on simple communities.
+Nevertheless, the rewards are encouraging. 
+Not only from a purely ecological perspective, but also from a conservation perspective, where an integrated approach can shift our focus beyond the identification of ideal targets for intervention to design informed interventions that legitimately achieve restoration goals.
+
 # Appendix 1: Glossary

### 2017-02-24 paper/draft_2.Rmd
Correct typos. Add distribution graph. Add paper metadata

@@
 - \usepackage{caption} 
+- \usepackage{lineno}
 documentclass: artikel1
@@
 \doublespacing
+\linenumbers
 
@@
 
+**E. Fernando Cagua^1\*^, Kate L Wootton^1,2§^, Daniel B. Stouffer^1#^**
+
+^1^ Centre for Integrative Ecology, School of Biological Sciences, University of Canterbury, Private Bag 4800, Christchurch 8041, New Zealand
+
+^2^ Current address: Stockolm, Cold & dark place in the Arctic Circle
+
+^\*^ efc29@uclive.ac.nz 
+^§^ kate.l.wootton@gmail.com
+^#^ daniel.stouffer@canterbury.ac.nz
+
+* **Running title:** Manageability of pollination networks.
+
+* **Keywords:** Network control, ecological networks, species importance, driver species, food webs, mutualism, management interventions, food web, interaction asymmetry, mutual dependence
+
+* **Article type:** Letter.
+
+* **Number of words:** ~ () abstract; ~ 5450 main text.
+
+* **Number of references:** 72
+
+* **Number of displays:** 5 figures; 1 table.
+
+* **Correspondence to:** Daniel Stouffer (daniel.stouffer@canterbury.ac.nz) - +64 3 364 2729 - Centre for Integrative Ecology, School of Biological Sciences, University of Canterbury, Private Bag 4800, Christchurch 8140, New Zealand
+
+* **Authorship:** DBS conceived the idea; EFC, DBS and KLW contributed to the development of the theoretical framework. EFC performed all analysis. EFC and DBS wrote the manuscript.
+
+* **Data accessibility:** All data used in this manuscript have already been published by @Lopezaraiza-Mikel2007, @Bartomeus2008, and @Ballantyne2015.
+The reader should refer to the original sources to access the data.
+
+\newpage
+
+# Abstract
+
+150 words
+
+\newpage
+
 # Introduction
 
-Complex systems are characterised by relationships in which the whole is often greater than the sum of its parts [@Jorgensen1998; @Levin1999; @Montoya2006].
+Complex systems are chahave bracterised by relationships in which the whole is often greater than the sum of its parts [@Jorgensen1998; @Levin1999; @Montoya2006].
 Within community ecology, a complex systems approach has led to the development of a variety of analytical and simulation tools with which to understand, for example, the role of species when embedded in an intricate network of interactions [@Pascual2005; @Bascompte2009; @Stouffer2012].
@@
 To overcome this obstacle, we require a framework that allows us to explain, predict, and manage ecological communities, particularly when they are confronted with perturbations [@Sole2001; @Green2005].
-Ideally, such a framework needs to be able to account for their complex structure and the dynamics that determine the species abbundances and the state of the community.
+Ideally, such a framework needs to be able to account for their complex structure and the dynamics that determine the species abundances and the state of the community.
 
@@
 This method, widely used in engineering to determine and supervise the behaviour of dynamical systems [@Motter2015], is well equipped to deal with the many feedbacks present in ecological communities [@Liu2015].
-Research in the this area has established a strong link between the structure of complex networks and their *controllability*—the relative ability of manipulating network components to drive the system to a desired state [@Liu2011; @Cornelius2013; @Ruths2014].
+Research in this area has established a strong link between the structure of complex networks and their *controllability*—the relative ability to manipulate network components to drive the system to a desired state [@Liu2011; @Cornelius2013; @Ruths2014].
 These advances suggest that it is in principle possible to alter a whole ecological community's composition by modifying the abundances of only a few species.
@@
 To complicate things further, biotic invasions can induce dramatic changes in the patterns of interactions that determine the structure of ecological networks [@Baxter2004; @Tylianakis2008; @Ehrenfeld2010a].
-Understanding how the differences in network structure before and after the invasion impact our ability to manage the communities doububle challenge, it is a critical first step towards a fully informed recovery.
+Understanding how the differences in network structure before and after the invasion impact our ability to manage the communities double challenge, it is a critical first step towards a fully informed recovery.
 Despite the apparent overlap, a control-theoretic perspective has not been adopted in an invasion context. 
@@
 While doing so, we focus on two particular questions.
-First, grounded on the difficulties usually involved with invasive species erradication and ecosystem restoration [@Woodford2016], we ask whether invaded networks have lower levels of "manageability" than their uninvaded counterparts; that is, whether they require a greater proportion of species to be managed to achieve the same level of control.
+First, grounded on the difficulties usually involved with invasive species eradication and ecosystem restoration [@Woodford2016], we ask whether invaded networks have lower levels of "manageability" than their uninvaded counterparts; that is, whether they require a greater proportion of species to be managed to achieve the same level of control.
 Second, we ask whether some species are more important than others at driving the population dynamics of the community and which factors determine this importance. 
@@
 
-Conveniently, in a network with linear dynamics the information necessary to determine the minimum number of driver nodes *D* is fully contained in the network structure [@Kalman1963; @Liu2011; @Motter2015].
-We, therefore, start here from the assumption that that an ecological network can, at least near equilibrium points, be described by $\frac{dx}{dt} = Ax + Bu(t)$, where the change over time of its state ($\frac{dx}{dt}$) depends on its current state *x* (for example the species' populations), an external time-varying input *u(t)*, and the matrices *A* and *B*, which encapsulate information about the network structure and how the species respond to the external input, respectively.
+Conveniently, in a network with linear dynamics, the information necessary to determine the minimum number of driver nodes *D* is fully contained in the network structure [@Kalman1963; @Liu2011; @Motter2015].
+We, therefore, start here from the assumption that an ecological network can, at least near equilibrium points, be described by $\frac{dx}{dt} = Ax + Bu(t)$, where the change over time of its state ($\frac{dx}{dt}$) depends on its current state *x* (for example the species' populations), an external time-varying input *u(t)*, and the matrices *A* and *B*, which encapsulate information about the network structure and how the species respond to the external input, respectively.
 Even though linearity might be a strong assumption, it has been shown that fundamental insight about the control of complex systems can be gained without a detailed knowledge of the nonlinear dynamics and the system parameters [@Liu2015], an important step towards ultimately understanding the controllability of systems with nonlinear dynamics [@Liu2011].
@@
 One possibility is to characterise a species by the frequency *f~D~* with which it is classified as a driver node.
-However, the profile of our networks indicates that a large proportion of driver nodes are so, because of external interventions are required to achieve **full** controllability, and not because they influence the abbundance of other species (Supporting Information S2).
-Furthermore, the role of driver nodes is still ambiguous when **full** network controllability is unfeasible or undesired—which is often the case in ecological settings.
+However, the profile of our networks indicates that a large proportion of driver nodes are so, because of external interventions are required to achieve **full** controllability, and not because they influence the abundance of other species (Supporting Information S2).
+Furthermore, the precise role of driver nodes is still ambiguous when full control is unfeasible or undesired—often the case in ecological settings.
 We therefore also calculate the frequency *f~S~* with which a species is classified as superior nodes since this is the frequency with which they form part of possible control paths.
@@
 In addition, because our approach depends to a large degree on the network topology, we evaluated the robustness of our results to the undersampling of ecological interactions.
-Specifically, we calculated *n~D~*, and species relative importance for 500 random subsamples of each empirical network in which the weakest links were more likely to be removed. 
+Specifically, we calculated *n~D~* and species relative importance for 500 random subsamples of each empirical network in which the weakest links were more likely to be removed. 
 The sensitivity analysis indicated that, even in the absence of complete sampling, a control theoretic approach can still be applied (Supporting Information S5).
@@
 This implies that we need first to identify a directionality for the links between species that is consistent with the dynamics of the community (Figure 2). 
-In some ecological networks, establishing the directionality can appear relatively straightforward, for example when links represent biomass transfer or energy flow. 
+In some ecological networks, establishing the directionality can appear relatively straightforward, for example when links represent biomass transfer or energy flow [@Isbell2013]. 
 Interspecific effects in pollination networks, however, are not strictly directed since the benefit is mutual between interacting species. 
@@
 Previous research has shown that mutual dependences are often highly asymmetric in natural communities [@Bascompte2006]; in other words, if a plant species is largely dependent on a pollinator species, then that pollinator tends to depend rather weakly on the plant (or vice versa).
-We therefore simplified the network so that interacting species are connected by only one directed link when mutual dependences are asymmetric (Figure 2c).
+We, therefore, simplified the network so that interacting species are connected by only one directed link when mutual dependences are asymmetric (Figure 2c).
 This simplification, while maintaining ecological realism, is advantageous for several reasons. 
-First, it is consistent with previous advances in structural controlability; second, it avoids complications related to the introduction of artificial control cycles; and third it significantly reduces the computational resources necessary for the application of our approach (Supporting Information S6).
+First, it is consistent with previous advances in structural controllability; second, it avoids complications related to the introduction of artificial control cycles; and third it significantly reduces the computational resources necessary for the application of our approach (Supporting Information S6).
 Furthermore, we show that changing to unidirectional interactions determined by the observed direction of asymmetry, as a surrogate of bidirectional mutual dependences does not alter the relative *n~D~* of different networks (Table S3).
@@
 Previous research indicates a direct link between a network's degree distribution and the number of nodes necessary to fully control it [@Liu2011], but the strength and applicability of this relationship have not been tested for in weighted ecological networks.
-We therefore compared the driver-node density *n~D~* of the empirical networks to networks generated by a null model that maintained each species' strength (its total sum of visits) while allowing their degrees (its number of interactions) to vary.
+We, therefore, compared the driver-node density *n~D~* of the empirical networks to networks generated by a null model that maintained each species' strength (its total sum of visits) while allowing their degrees (its number of interactions) to vary.
 Randomisations were generated using the function `commsim` in vegan 2.3-3 [@Oksanen2016]. 
-After generating the randomised networks, we then calculated the mutual dependences and interaction asymmetries of each, and determined *n~D~* using our maximum-matching framework.
+After generating the randomised networks, we then calculated the mutual dependences and interaction asymmetries of each and determined *n~D~* using our maximum-matching framework. 
 Finally, we calculated the average rank (akin to a p-value) of *n~D~* for each empirical network compared to the corresponding one of each set of 999 randomisations [@Veech2012].
@@
 To quantify this importance, we computed all maximal cardinality matchings in each network. 
-We then calculated the frequency with which each species *i* is deemed to be a driver (*f~D~*) or a superior node (*f~S~*) in the set of matchings that had a matching weight greater or equal to 0.5 times the weight of the maximum matching.
+We then calculated the frequency with which each species *i* is deemed to be a driver (*f~D~*) or a superior node (*f~S~*) in the set of matchings that had a matching weight greater or equal to 0.8 times the weight of the maximum matching.
 We selected this threshold as it provided a high agreement between networks quantified by visitation and pollination efficiency as well as between our weighting/directionality assumptions; however, the choice of this threshold had a negligible impact on any results (Supporting Information S7).
 
-Details about the compuational procedure to find all maximum cardinality matchings of a network can be found in Supporting Information S1 and Figure S2.
+Details about the computational procedure to find all maximum cardinality matchings of a network can be found in Supporting Information S1 and Figure S2.
 
@@
 To facilitate comparison among the continuous variables we scaled so that they all had a mean of zero and a standard deviation of one.
-In addition, we also included guild (plant or pollinator), and wether the species is invasive or not, as categorical fixed effects.
+In addition, we also included guild (plant or pollinator), and whether the species is invasive or not, as categorical fixed effects.
 Although the importance of plants and pollinators or invasive and non-invasive species could respond differently to our structural metrics, our data set did not contain enough variation to include the corresponding interactions terms for these latter two predictors.
@@
 All of the networks studied had a driver node density *n~D~* between `r round(min(dplyr::filter(n_driver, type == "weight")$n_dr_p), digits = 2)` and `r round(max(dplyr::filter(n_driver, type == "weight")$n_dr_p), digits = 2)` (mean `r round(mean(dplyr::filter(n_driver, type == "weight")$n_dr_p), digits = 2)`.
-In addition, we found that, when controlling for potential species richness effects, the *n~D~* of invaded communities was smaller to those of non invaded communities (Figure 3a; Table S5). 
-Nevertheless of the various covariates we explored, the ratio of plant to pollinator showed the strongest relationship with *n~D~* (Table S4). 
-Specifically, we found that as the proportion of pollinators increasses and the ratio plant/pollinator balances, *n~D~* decreasses (all our communities had more pollinators than plants). 
-Other coovariates—connectance (link density) and species richness—had a neggative and comparatively less important relationship with *n~D~*.
+In addition, we found that, when controlling for potential species richness effects, the *n~D~* of invaded communities was smaller to those of non-invaded communities (Figure 3a; Table S5). 
+Nevertheless, of the various covariates we explored, the ratio of plant to pollinator showed the strongest relationship with *n~D~* (Table S4). 
+Specifically, we found that as the proportion of pollinators increases and the ratio plant/pollinator balances, *n~D~* decreases (all our communities had more pollinators than plants). 
+Other coovariates—connectance (link density) and species richness—had a negative and comparatively less important relationship with *n~D~*.
 
-```{r fig_explaining-n-driver, echo = FALSE, warning = FALSE, message = FALSE, fig.width = 3.245, fig.height = 3.2, fig.cap = "**Coovariates of driver node density**.
-(a) Invaded communities have lower proportion of driver nodes *n~D~* than uninvaded communities even when controlling for factors related to species richness.
+```{r fig_explaining-n-driver, echo = FALSE, warning = FALSE, message = FALSE, fig.width = 3.245, fig.height = 4.8, fig.cap = "**Driver node density**.
+(a) Density distribution of the proportion of driver nodes (_n~D~_) for the twenty studied networks.
+(b) Invaded communities have lower proportion of *n~D~* than uninvaded communities even when controlling for factors related to species richness.
 The boxes cover the 25th–75th percentiles, the middle lines mark the median, and the maximum length of the whiskers is 1.5 times the interquartile range.
 All points outside this range are indicated by the circles.
-(b) Out of the richness metrics, the ratio of plants to pollinators showed an important relationship with *n~D~*.
+(c) Out of the richness metrics, the ratio of plants to pollinators showed an important relationship with *n~D~*.
 In both plots, residuals correspond to the partial working residuals of the invasion status in our generalised linear mixed model."}
@@
   dplyr::bind_cols(manag_models@objects[[1]]$data)
+
+p0 <- manag_models@objects[[1]]$data %>% 
+	ggplot(aes(x = n_dr_p)) + 
+	stat_density(size = 0.4, geom = "line") +
+	fer_theme +
+	xlab(expression(n[D])) +
+	ylab("density distribution") +
+	theme(axis.title.y = element_text(vjust = 1, margin = margin(1,-3,1,1, unit = "lines")))
 
@@
 
-cowplot::plot_grid(p1, p2, ncol = 1, align = "v") +
-	cowplot::draw_plot_label(label = c("(a)", "(b)"), size = 8, fontface = "bold", y = c(1, 0.5))
+cowplot::plot_grid(p0, p1, p2, ncol = 1, align = "v") +
+	cowplot::draw_plot_label(label = c("(a)", "(b)", "(c)"), size = 8, fontface = "bold", y = c(1, 0.66, 0.33))
 # pdf("../paper/figures/fig_3.pdf", height = 1.7, width = 3.245, family = "Times", compress = F, title = "Figure 3")
@@
 To a smaller extent, visitation strength (its sum of visits) and the species degree also had a positive relationship with $f_S$. 
-In contrast, the relationships between species structural properties and $f_D$ was more convoluted (Table 1). 
+In contrast, the relationships between species structural properties and $f_D$ were more convoluted (Table 1). 
 Both invasive species (which for example tend to have a large degree, and high dependence strength) and pollinators (which generally have a smaller degree and dependence strength) were classified as driver nodes in a large proportion of the considered matchings.
@@
 attr(coef_tables, "subheadings") <- paste0("$", names(mod), "$")
+attr(coef_tables, "message") <- "\\footnotesize Confidence intervals correspond to an alpha risk of 0.05."
 coef_tables %>%

### 2017-02-24 paper/supp_info_2.Rmd
Add citation for cliques
Adjust ugly legend

@@
 Second, a clique is a subset of nodes such that any two of them are linked. 
-Lastly, a maximum clique is a clique such that there are no cliques with more nodes. 
+Lastly, a maximum clique is a clique such that there are no cliques with more nodes [@Gutin2013]. 
 In this example, there are two maximum cliques: that one formed by 1, 3 and 5, and the one formed by 2, 3 and 5. 
@@
 	fer_theme +
-	theme(legend.position = c(0.875,0.175), legend.justification = "center", 
+	theme(legend.position = c(0.875,0.2), legend.justification = "center", 
 				legend.direction = "horizontal", legend.key = element_blank())

### 2017-02-24 paper/EL-reviewer-comments-1.Rmd
Add responses to Reviewer #1

@@
 
-    *We revised the text to better reflect the contribution of @Tylianakis2010 at the same time we added a reference to a more recent paper by @Kaiser-Bunbury2015 who explicitly deals with oportunities, limitations and implications of applying network metrics in conservation science.*
+    *We have now revised the text to better reflect the contribution of @Tylianakis2010.
+At the same time, we added a reference to a more recent paper by @Kaiser-Bunbury2015 that explicitly deals with opportunities, limitations and implications of applying network metrics in conservation science.*
 
@@
 
-    *Thanks to this comment and those from other reviewers have helped us identify some shortcomming on the way we were introducing the control framework in the paper.
-We have largely rewritten the 'Theoretical framework' section and we start by offering a brief overview of control theory which emphasize on a dynamical perspective to complex networks (Line XXX).
-We then follow with a paragraph devoted to how structural controlability is unable to provide information about the particulars of the control signal and the feasibility of its application (Line XXX).
-Without disregard the usefulness of the proposed approach, we also mention in this paragraph, and later on the discussion (Line XXX), how recently developed numerical methods [@Cornelius2013] might offer exiting results in this regard.*
+    *Thanks to this comment and those from other reviewers have helped us identify some shortcomings on the way we were introducing the control framework in the paper.
+We have largely rewritten the 'Theoretical framework' section.
+We start by offering a brief overview of control theory.
+In this overview, we emphasise our assumptions regarding the dynamical nature of the interactions.
+And follow with a brief discussion that indicates how structural controllability is unable to provide information about the particulars of the control signal and the feasibility of its application.
+Without disregard the usefulness of the proposed approach, we also mention at the end of the discussion how recently developed numerical methods [@Cornelius2013] might offer exciting results in this regard.*
 
@@
     *Thanks for pointing this out.
-In fact we thoroughly implememnted the approach of [@Ruths2014] at initial stages of the project.
-However we found that the profile of the network depends to an extreme degree on the chosen link directionality and very little on the particulars of a given network.
-Because of that reason we decided to exclude this approach altogether from the final draft.
-Nevertheless, due to this comment and one of Referee 2 we included this treatment in the Supplementary Materials Section XX and reference it briefly in the manuscript (Line XXX).
-In SM SectionXX we explain that because we focus on bipartite networks, cycles only appear, and in fact dominate, when we consider the case of bidirectional links.
-We are particularly grateful for the reference to @Motter2015.
-We were unaware of this paper and has been extremely useful to contextualise our work in the broader control theory.*
+In fact, we explored the implementation of the approach of [@Ruths2014] at initial stages of the project.
+However we decided to exclude this approach from the final draft, mainly due to space limitations.
+Nevertheless, due to this comment and one of Referee 2 we have rediscovered its value and use it to support our decision to include the analysis of superior nodes, and not just driver nodes, in our manuscript.
+We now dedicate a whole section in the Supporting Information (S2).
+In summary, we found our networks weighted by asymmetry to be external dilation dominated, and hence have only a small number of cycles.
+Networks weighted by mutual dependences are dominated by cycles and hence challenging to our approach.
+In another section in the Supporting Information (S6) we discuss the implications that using these networks have, and our approach to circumvent them.
+Finally we are grateful for the reference to @Motter2015.
+We were unaware of this paper and it has been extremely useful to contextualise our work in the broader control theory literature.*
 
@@
 
-    *Indeed most of the literature treats the problem of controlability on unweighted networks.
-It has been shown, however, at least in pollination networks like the ones used in our paper, that the interaction weights carry important information about the patterns and processes in the community.
-In the paper we use the visitation weights directly or indirectly in two different aspects.
-First, we use them to determine the direction of control (via the dependence asymetry).
-Second, which directly adresses the reviewer's comment, we use it to give priority to matchings that have the largest weight, which potentially also have the largest impact on the network state for a given management intervention.
-Because the weights determine to some extent the dynamical relationships between species, our approach attempt to incorporate more realism to the structural controllability approach.
-We acknoweledge our presentation was confusing, especially for readers familiar wit the control literature, and therefore have added a whole paragraph in the method describing our rationale (Lines XXX)*
+    *Indeed most of the literature treats the problem of controlability on unweighted/binary networks.
+In that special case maximum matchings are equivalent to maximum cardinality matchings.
+It has been shown, however, that the interaction weights carry important information in pollination networks about the patterns and processes in the community.
+In the paper we use the visitation weights directly or indirectly in two different ways.
+First, we use them to determine the potential direction of control (via the dependence asymmetry).
+Second—which directly adresses the reviewer's comment—we use them to give priority to matchings that have the largest weight since these arguably have the largest impact on the network state for a given management intervention.
+Because the weights determine to some extent the dynamical relationships between species, our approach attempts to incorporate more ecological realism to the structural controllability approach.
+We acknoweledge our earlier presentation of this rationale was confusing, especially for readers familiar with the control literature, and therefore have added a whole paragraph describing our rationale in the "Relative importance" subsection in the "Theoretical frameowrk".
+To minimise potential confusions we are more careful when introducing each of these concepts, and have added—as suggested by the reviewer—a glossary for easy reference.*
 
-- When defining n_d on line 119, it is more accurate to say that it is the "minimum number" of species needed to gain full control.
+- When defining *n~d~* on line 119, it is more accurate to say that it is the "minimum number" of species needed to gain full control.
 
-    *We have rewritten that section and the equivalent sentence now reads "It has been shown that a particular network that can be expressed as a state space system of the form $\dot{x} = Ax + Bu(t)$ is controllable if there exists a minimum number of nodes in the network (N~D~ > 0) to which is possible to aply an external control signal that propagates trough the network to in turn drive the state of every other node in the network to a particular configuration [@Kalman1963; @Liu2011]."*
+    *We have completely rewritten that section and the equivalent sentence now reads "Conveniently, in a network with linear dynamics, the information necessary to determine the minimum number of driver nodes D is fully contained in the network structure..."*
 
@@
 
-    *We are sorry for the impresicion.
+    *We are sorry for the imprecision.
 It should have been "all possible maximum cardinality matchings".
-In any case, because of the suggestion about the driver species concept we have decided to remove this sentence.
-We also reworded the text in Lines XXX to clarify why our approach to identify species importance is not exclsively centered on maximum matchings.*
+In any case, because of the reviewers' suggestion about the driver species concept we have now removed this sentence.
+We hope that the new text we have included on the "Relative importance" subsections, both in the "Theoretical framework" and "Empirical application", and in Supporting Information S7, helps clarify why our approach to identify species importance is not exclusively centred on maximum matchings.*
 
@@
     *Thanks to this suggestion and those of other reviewers, we have made important changes to Figure 1.
-On it we include a better ilustration of our methodology for a simple network while paying special effort to bring clarity to the different node categories as superior, matched and unmatched nodes.
-TO DO*
+In it, we include a better illustration of our methodology for a simple network while paying special effort to bring clarity to the different node categories as superior, driver, matched, and unmatched nodes.
+We hope the figure, in addition to our new introduction to the elements of a maximum matching, make the concept easier to understand.*
 
@@
 
-    *Overall our choice of terminology was poor.
-We have eliminated the term "driver species" from the manuscript and now just mention, in the referee's words, how the frequency with which species exist on key paths trough the network provides indication of their relative importance.*
+    *We agree that in hindsight, our choice of terminology was poor.
+We have eliminated the term "driver species", which had a different meaning to the usual concept of "control node", from the manuscript.
+Now, we stick to the terminology that is already used, and refrain for introducing a new term for the species that are classified as superior nodes in all possible control strategies.*
 
@@
 As suggested, we have included a figure that help explains our method to compute all possible maximum cardinality matchings.
-However because the methodology itself is not one of our main contributions and because of space limitations we have included that figure in the Supplementary Material.
-TO DO.*
+Nevertheless, because of space limitation, and because the methodology itself is not one of our main contributions, we have included the procedure and the figure in the Supporting Information (S1 and Figure S2).*
 
@@
 
-    *We apologise for the poor choice of words.
-As the referee points out it is not an estimation but an exact calculation.
+    *We again apologise for the poor choice of words.
+As the referee points out it, this is not an estimation but an exact calculation.
 The sentence now reads "To do so, we calculated the maximum matching of the corresponding pollination network, and determined the minimum proportion of species that need directed interventions to fully control the species abundances in the community".*
@@
 
-    *Thanks for the observation. We have now included the number of interactions in the network as an extra explanatory variable. TO DO*
+    *Thanks for the observation.
+We have now included the network connectance as an extra explanatory variable.
+We included connectance (link density) and not the number of links, because it allows comparisons across multiple networks of differing size.
+We found it to have a negative and moderate relationship with the density of driver nodes.*
 
@@
 
-    *In retrospect we realise that we did not have a clear rationale to include an randomisation of the link weights.
+    *In retrospect we realise that our rationale to include a randomisation of the link weights was not clear enough.
 As the referee points out, a change on the weights would only be reflected on a potential change on the interaction asymmetry.
 We identifyed two problems with this approach: first the changes aren't easily tractable, and second there is not a standard way to randomise weight in quantiative networks and the particular choice of the algorithm might influence the results.
-We therefore decided to remove the null model that maintained the degree of species and randomised the weight of the links as the effect of the asymetry is explicitly tackled by the second approach in which we maintain the structure but randomise the asymmetry.*
+We therefore decided to remove the null model that maintained the degree of species and randomised the weight of the links as the effect of the asymmetry is explicitly tackled by the second approach in which we maintain the structure but randomise the asymmetry.*
 
@@
 
-Indeed, in the Discussion the authors say for example, "Because of their effects on other species in the community, driver species might be natural candidates for management interventions." This may be true, but it seems to me that the role of the directly-controlled species (that populate n_d), which serve as the gateway for the control signals to the rest of the network, merits discussion here as well.
+    *Thanks for the suggestion.
+In the methods, where we describe the empirical application, we now state the minimum, maximum, and the mean number of species for both the networks from Bristol, UK and Cap de Creus, Spain.
+In addition, now we briefly discuss the proportion of driver nodes we found in the studied pollination networks in the fourth paragraph of the Discussion.
+We do so, in the context of highlighting the potential caveats of one of our metrics of species importance.*
+
+- Indeed, in the Discussion the authors say for example, "Because of their effects on other species in the community, driver species might be natural candidates for management interventions." This may be true, but it seems to me that the role of the directly-controlled species (that populate n_d), which serve as the gateway for the control signals to the rest of the network, merits discussion here as well.
 How are the two related?
@@
 
+    *Agreed.
+Given that driver nodes have received a considerable amount of attention in the control literature, we realise that neglecting them might be confusing, especially for readers familiar with control theory.
+We have fully incorporated this suggestion and our paper is now much more comprehensive.
+Now, to determine the potential importance of a species, we determine, not only its properties as a superior node, but also its properties as a driver node.
+We have dedicated a large proportion of the discussion to discuss the advantages and limitations of each of them and how they relate to each other and to realistic management applications.
+To do build this discussion we harnessed results from additional modelling analysis in the main text, as well as the lessons learned from the application of the @Ruths2014 control profiles approach.*
+
 - Figure 3 should show the distributions of m as well as the adjusted value of m.
 I suggest also providing more detail about how the adjusted value is calculated (in the current version there is one technical sentence that non-experts will not be able to follow).
+
+    *We have now included a subpanel in Figure 3 that depicts the distribution of _n~D~_ for our empirical networks.
+The adjusted values were merely partial residuals of the fitted statistical models.
+We therefore have changed the axis titles to reflect this fact and avoid confusion.*
 
@@
 
-Minor comments
-Line  236: there is a missing period.
+    *This was a mistake on our part.
+We were not interested in determining whether the __absolute__ value of n~D~ differs among approaches, but instead, we wanted to determine wether the __relative__ values showed agreement.
+This is, our primary concern was to test whether networks with a high n~D~ under the asymmetry weighting also had a high n~D~ under the bidirectional dependences weighting.
+We have changed the text in the Supporting Information (S6) to improve clarity.*
+
+- Minor comments. Line  236: there is a missing period.
+
+    *Thanks for pointing it out. We have added the period.*
 
@@
 This is a fascinating area of research.
+
 Performing a controllability study on ten pairs of uninvaded and invaded plant-pollinator networks, the main finding is that invaded networks require a higher number of nodes to control than their non-invaded counterpart and invasive plants were driver species in all studied communities.
@@
 The discussion should be strengthen.
+
 In its current form, it is unlikely that readers will be able to understand or replicate the research presented – which is a shame considering the authors went through a lot of trouble to apply a control theory study in an ecological context.
@@
 - Consider being more specific in your abstract.
+
+    *Thanks for pointing it out.
+Given the tight 150 word limit imposed by the Journal, we had some trouble highlighting the novelty of the approach while maintaining important details about the empirical application.
+We hope the current version of the abstract shows substantial improvement.*
 

### 2017-02-24 paper/EL-reviewer-comments-1.Rmd
Add responses to Reviewer #2

@@
 
-    *The sentence now reads "To bridge this gap, we develop methods to apply previous theory on the control of complex systems into an ecological context and implement them using empirical data, while taking into account the quantitative differences that exist among species interactions."*
+    *The sentence now reads "To bridge this gap, we outline an approach to apply theory on the control of complex systems in an ecological context and implement them using empirical data."*
 
@@
 
-    *We have pretty much rewritten the "Theoretical framework" section following the reviewers advise.
-We start with a brief introduction to structural controllability (Lines XXX), follow with a definition of manageability (Lines XXX) and finalise with details and computational considerations for its calculation.*
+    *In response to this and other comments, we have rewritten most of the "Theoretical framework" section.
+We start with a brief introduction to structural controllability, follow with a definition of manageability and finalise with details and computational and methodological considerations regarding its calculation.*
 
@@
      *Thanks for the observation.
-We have reworded large segments of this section.
-Specifically now explain how the approach builds on existing structural controllability theory by incorporating the weight of the interactions.
+As above, we have also reworded large segments of this section to make more clear what are and what are not novel contributions.
+Specifically, we now explain how the approach builds on existing structural controllability theory by incorporating the weight of the interactions.
+In addition, although the concept of driver and superior nodes are not novel in the control theory literature, most of the previous studies tend to focus on __a single__ matching.
+We instead exploit the fact that a single network may have multiple control configurations and evaluate the role of species in each of them.
+We now dedicate a large proportion of the discussion to these new metrics and how (even if not independent) they are conceptually different to previous attempts to rank species by importance.
+We also include extra development in the Supporting Information S7.
 Moreover, now we included more details about the rationale behind our approach.
-By being more specific we hope the reader to be able to identify the theretic and computational novelties of our approach with respect to existing "ranking" methods.
-We also strive to further clarify the novelty in the discussion section (Lines XXX).
-TO DO*
+By being more specific we hope the reader to be able to identify the theoretic and computational novelties of our approach with respect to existing "ranking" methods.*
 
@@
 
+    *Thank you.
+We acknowledge we did a poor job reflecting our work in the previous literature.
+We now include a paragraph in the discussion to explore the similarities and differences of our work with previous indices based on structural metrics.
+We explain how "our approach ...
+is not based on a single structural metric but acknowledges the existence of multiple management strategies; some more optimal than others in specific contexts".
+We also concur that more flexible approaches like ours and the one implemented by @McDonald-Madden2016* "that take a network-wide approach might prove more useful to guide ecosystem management if we want to go beyond using network metrics to minimise topological species loss".*
+
 - Discussion. Please provide some insight into how your method/analysis/results would differ for non- pollinator invaded networks.
 
+    *We now brifly mention in the Discussion how "because of the degree constraints imposed by bipartite networks, our pollination specific results might not be relevant to other ecological systems, the approach we propose is applicable wherever species abundances are influenced by their interactions".*
+
 - Discussion. Please discuss the caveats of your approach. I suggest moving some of the statistical analyses in sup info if word limit is an issue.
+
+    *We agree we did not discuss with enough detail the assumptions and caveats of our approach.
+As such, as we explain our methods we try to highlight the rationale behind them while being more explicit about the assumptions and limitations.
+Moreover, in the discussion, we now provide a fairer assessment of the extent to which our approach might be useful for practical applications.*
 
@@
 
+    *Calculating __one__ maximum matching for ecological networks with a few hundred species is not a computationally expensive operation, and therefore we use directly the algorithm and not the approximation proposed by @Ruths2014.
+Our most expensive computation was to find __all__ the possible maximum cardinality matchings to calculate species-level metrics.
+Lamentably the network's control profile does not provide species-level information and hence we couldn't use it to our advantage.
+Nevertheless, as suggested by you and another reviewed, we have included a section where in the Supporting information *(S2) where we explain that our networks are external dilation dominated.
+The @Ruths2016 has provided us with very useful insight on the selection of the direction of control and the utility of the concept of driver nodes for management applications.*
+
 - A few typos in main text and sup info.
+
+    *We have spell-checked all the text, and hope this time no typos have escaped from us.*
 
@@
 As a result, ecologists have been cut from the theoretical advances in control theory and most often have no clue that these are the same thing.
+
+    *Thank you for pointing this out.
+We maintain the word throughout our manuscript because it is more intuitive to develop the intuition of readers more familiar with ecological and conservation terminology.
+However, we do not use the word "manageability" in lieu of "controllability" in our manuscript anymore, and maintain the control theory terminology, especially in the methods section.
+In addition we have enriched the references so that its easier for the readers  to trace back our approach to the control literature.*
 

### 2017-02-24 paper/draft_2.Rmd
Change Liu2015 for Liu2016

@@
 Among the various possibilities, *control theory* appears to be a strong candidate.
-This method, widely used in engineering to determine and supervise the behaviour of dynamical systems [@Motter2015], is well equipped to deal with the many feedbacks present in ecological communities [@Liu2015].
+This method, widely used in engineering to determine and supervise the behaviour of dynamical systems [@Motter2015], is well equipped to deal with the many feedbacks present in ecological communities [@Liu2016].
 Research in this area has established a strong link between the structure of complex networks and their *controllability*—the relative ability to manipulate network components to drive the system to a desired state [@Liu2011; @Cornelius2013; @Ruths2014].
@@
 We, therefore, start here from the assumption that an ecological network can, at least near equilibrium points, be described by $\frac{dx}{dt} = Ax + Bu(t)$, where the change over time of its state ($\frac{dx}{dt}$) depends on its current state *x* (for example the species' populations), an external time-varying input *u(t)*, and the matrices *A* and *B*, which encapsulate information about the network structure and how the species respond to the external input, respectively.
-Even though linearity might be a strong assumption, it has been shown that fundamental insight about the control of complex systems can be gained without a detailed knowledge of the nonlinear dynamics and the system parameters [@Liu2015], an important step towards ultimately understanding the controllability of systems with nonlinear dynamics [@Liu2011].
+Even though linearity might be a strong assumption, it has been shown that fundamental insight about the control of complex systems can be gained without a detailed knowledge of the nonlinear dynamics and the system parameters [@Liu2016], an important step towards ultimately understanding the controllability of systems with nonlinear dynamics [@Liu2011].
 This means that structural controllability can be applied to a wide range of readily available network representations of ecological communities to provide a strong indication of our ability to control them.

### 2017-02-24 paper/draft_2.Rmd
Cosmetic changes
Change dependency to dependence troughout

@@
 
-**E. Fernando Cagua^1\*^, Kate L Wootton^1,2§^, Daniel B. Stouffer^1#^**
+**E. Fernando Cagua^1\*^, Kate L. Wootton^1,2§^, Daniel B. Stouffer^1#^**
 
@@
 First, biotic invasions are known to produce tractable changes in the structure of ecological networks, and these changes can be particularly pronounced in mutualistic networks between plants and pollinators where biotic invasions have been shown to modify the strength of species interactions and the degree of network nestedness and connectivity [@Olesen2002; @Aizen2008; @Bartomeus2008; @Vila2009; @Traveset2013].
-Second, plant-pollinator networks provide an ideal framework to answer these questions. 
+Second, although species are involved in multiple types of interactions, plant-pollinator networks provide an ideal framework to answer these questions. 
 On the one hand, community networks that quantify relative levels of interaction are readily available. 
@@
 We used a set of generalised linear mixed-effects models (with binomial error structure) with the relative frequencies as the response variables. 
-As predictors in this model, we included measures of centrality (degree and eigen-centrality), which have been found to be strong predictors of importance in a coextinction context [@Memmott2004]; a measure related to network robustness (contribution to nestedness), as nestedness has been proposed as one of the key properties that promote stability in mutualistic networks [@Saavedra2011]; and two measures of strength of association and dependence (visitation and dependence strength), as their distribution determines the extent of interspecific effects [@Bascompte2006].
+As predictors in this model, we included measures of centrality (degree and eigen-centrality), which have been found to be strong predictors of importance in a coextinction context [@Memmott2004]; a measure related to network robustness (contribution to nestedness), as nestedness has been proposed as one of the key properties that promote stability in mutualistic networks [@Saavedra2011]; and two measures of strength of association and dependence (visitation and dependence strength, this is the sum of visits a species receives or performs, and the sum of dependences of all species on the focal species, respectively), as their distribution determines the extent of interspecific effects [@Bascompte2006].
 To facilitate comparison among the continuous variables we scaled so that they all had a mean of zero and a standard deviation of one.
@@
 The model results suggest that this differences among invasive and native species are underpinned, not by any intrinsic property of the invasive species but instead, by species properties that apply to invasive and native species alike (Table 1).
-Specifically, we found that a species is more likely to be classified as a superior node if it had a large dependence strength (its sum of the dependences). 
+Specifically, we found that a species is more likely to be classified as a superior node if it had a large species strength (the sum of the dependences of other species on the species of interest). 
 To a smaller extent, visitation strength (its sum of visits) and the species degree also had a positive relationship with $f_S$. 
@@
 (a) In all networks were they were present, invasive species were classified as superior (_f~S~_) and driver (_f~D~_) nodes in all possible control configurations.
-(b) Dependency strength is the single most important factor explaining _f~S~_.
+(b) Dependence strength is the single most important factor explaining _f~S~_.
 Visitation strength and  degree also had an important albeit comparatively smaller effect (dashed lines correspond to ± one standard deviation on these factors).
@@
   scale_linetype_manual(values = c(2, 1)) +
-  xlab("dependency strength") +
+  xlab("dependence strength") +
   ylab(expression(f[S])) +
@@
                                            "guildpol", "d", "invasiveTRUE"),
-                                         c("dependency strength", 
+                                         c("species strength", 
                                            "contribution to nestedness",
@@
 Not only changes on their abundance have the potential to propagate broadly trough the community and in turn, affect the abundances of many other species, but they are also indispensable to fully control the plant-pollinator network.
-At a community level, we demonstrate that the manageability of mutualistic networks is strongly governed by the asymmetric nature of mutual dependencies—which constitute the foundations of the structure and stability of mutualistic networks [@Memmott2004; @Vazquez2004; @Bascompte2006; @Lever2014; @Astegiano2015].
+At a community level, we demonstrate that the manageability of mutualistic networks is strongly governed by the asymmetric nature of mutual dependences—which constitute the foundations of the structure and stability of mutualistic networks [@Memmott2004; @Vazquez2004; @Bascompte2006; @Lever2014; @Astegiano2015].
 Moreover, these mutual dependences seem to be importantly constrained by the concerted effects of both, the patterns of species richness at each trophic guild, and the species' degree distribution [@Melian2002; @Bluthgen2007].
@@
 Despite its conceptual advantages, our approach still relies on knowledge of the network of interaction between species. 
+We do not argue that management decisions should be based on a single technique. 
 Nevertheless, our results and previous basic research show that as long as the proportion of sampled links is enough to provide indication of the actual degree distribution (and in turn the species dependences), *n~D~*, *f~S~* and *f~D~* can still provide a simple, straightforward, and theoretically-informed indication of the degree to which the community is self-regulated and therefore how difficult it might be to modify its state in one way or another using some of the species that integrate it [Supporting Information S5; @Nepusz2012].
@@
 From the control perspective, driver nodes are those to which external control signals must be applied in order to gain full control of the network.
-
-*n~D~*
-  ~ The density of driver nodes
 
@@
   ~ A matching with the largest possible matching size *and* matching weight. 
-
 Superior node

### 2017-02-24 paper/supp_info_2.Rmd
Change dependency to dependence troughout

@@
 Visitation frequency has been shown to be an appropriate surrogate for inter-specific effects in pollination networks [@Vazquez2005; @Bascompte2006]. 
-Nevertheless visitation is not equivalent to pollen deposition and might be insufficient to reflect the dependencies of plants on animals and vice versa [@Alarcon2010; @King2013]. 
-We therefore investigated the effect of calculating the dependencies using visitation or pollination effectiveness and importance---two metrics more proximate to plant reproductive success (Figure \@ref(fig:fig-visitation-vs-deposition-vs-importance)).
-We did this by comparing *(i)* the manageability of the community and *(ii)* the percentage of interactions that maintained the direction of dependency. 
+Nevertheless visitation is not equivalent to pollen deposition and might be insufficient to reflect the dependences of plants on animals and vice versa [@Alarcon2010; @King2013]. 
+We therefore investigated the effect of calculating the dependences using visitation or pollination effectiveness and importance---two metrics more proximate to plant reproductive success (Figure \@ref(fig:fig-visitation-vs-deposition-vs-importance)).
+We did this by comparing *(i)* the manageability of the community and *(ii)* the percentage of interactions that maintained the direction of dependence. 
 To do that, we used data collected by @Ballantyne2015 from a low diversity pollination community at a dry lowland heathland in Dorset, UK  (50° 43.7'N 2° 07.2'W). 
@@
 Although visitation and deposition produce moderately different results, we found a very strong agreement between the order produced by visitation and importance (Table S2). 
-Finally, we also investigated whether the asymmetry of mutual dependency, which defines the direction of control, was consistent among the three possible weighting schemes.
-We found again that the direction of the dominant dependency was maintained was consistent for 95\% of the interactions weighted by visitation or importance, the two most appropriate metrics for pollinator and plant dependency (Table S2).
+Finally, we also investigated whether the asymmetry of mutual dependence, which defines the direction of control, was consistent among the three possible weighting schemes.
+We found again that the direction of the dominant dependence was maintained was consistent for 95\% of the interactions weighted by visitation or importance, the two most appropriate metrics for pollinator and plant dependence (Table S2).
 
@@
   xtable::xtable(caption = "\\textbf{Agreement among network weighting schemes}.
-Spearman correlation coeffcients (with p-value) of species' $f_D$ and the percentage of interactions that share the direction of dependency obtained using the three weighting schemes and an unweighted scheme.") %>%
+Spearman correlation coeffcients (with p-value) of species' $f_D$ and the percentage of interactions that share the direction of dependence obtained using the three weighting schemes and an unweighted scheme.") %>%
 	print(comment = FALSE, include.rownames = TRUE, caption.placement = "top", booktabs = T)
@@
 
-Altogether, evidence supports the idea that visitation is a suitable metric to estimate the mutual dependency of species pairs.
+Altogether, evidence supports the idea that visitation is a suitable metric to estimate the mutual dependence of species pairs.
 First, it is directly related to pollinator foraging.

### 2017-02-25 paper/draft_2.Rmd
Add explanatory arrows to figure 3

@@
 library(lme4)
+library(grid)
 
@@
 
-```{r fig_randomisations, echo = FALSE, warning = FALSE, message = FALSE, fig.width = 3.245, fig.height = 1.6, fig.cap = "**The driver node density _n~D~_ of empirical networks compared to network randomisations**.
+```{r fig_randomisations, echo = FALSE, warning = FALSE, message = FALSE, fig.width = 3.245, fig.height = 1.7, fig.cap = "**The driver node density _n~D~_ of empirical networks compared to network randomisations**.
 For each randomisation approach, we show the standarised rank of the empirical value compared to the set of randomisations.
@@
 
-z_scores %>%
+p1 <- z_scores %>%
   dplyr::group_by() %>%
@@
   fer_theme +
-  theme(
-        legend.position = "none",
-				plot.margin = grid::unit(c(2, 1, 2, 0), "mm"), 
+  theme(legend.position = "none",
+				plot.margin = grid::unit(c(-1, 1, 2, 0), "mm"), 
 				# panel.grid.minor.x = element_blank(),
-				panel.grid.minor.y = element_blank())
+				panel.grid.minor.y = element_blank(),
+				plot.background = element_blank())
+
+library(ggrepel)
+
+p2 <- data_frame(x = c(-0.05,0.05),
+					 xend = c(-1,1), 
+					 y = 0, yend = 0, 
+					 xtext = c(-0.5, 0.5),
+					 label = c("smaller\nthan random", "larger\nthan random")) %>%
+	ggplot(aes(x = x, y = y)) + 
+	geom_segment(aes(xend = xend, yend = yend), 
+							 arrow = arrow(angle = 15,
+							 							length = unit(3, "mm"), 
+							 							type = "open"), 
+							 size = 0.3, colour = "grey30") +
+	geom_label(aes(x = xtext, label = label), size = 2.2, y = 0.1, 
+						 label.size = 0, lineheight = 0.8, colour = NA,
+						 fill = "white") +
+	geom_text(aes(x = xtext, label = label), size = 2.2, y = 0.1, 
+						label.size = 0, lineheight = 0.8, colour = "grey10",
+						fill = "white") +
+	scale_x_continuous(expand = c(0,0)) +
+	scale_y_continuous(expand = c(0,0)) +
+	theme(plot.background = element_blank(), 
+				plot.margin = margin(0,0,0,0)) +
+	theme_void()
+
+cowplot::plot_grid(p2, p1, ncol = 1, align = "v", rel_heights = c(1.5,10))
 ```

### 2017-02-25 paper/draft_2.Rmd
A couple more phrasing mods for reviewer 3

@@
 
-* **Number of words:** ~ () abstract; ~ 5450 main text.
+* **Number of words:** ~ () abstract; approx. 5460 main text.
 
@@
 (a) In all networks were they were present, invasive species were classified as superior (_f~S~_) and driver (_f~D~_) nodes in all possible control configurations.
-(b) Dependence strength is the single most important factor explaining _f~S~_.
+(b) Species strength (the sum of the dependences of other species on the species of interest) is the single most important factor explaining _f~S~_.
 Visitation strength and  degree also had an important albeit comparatively smaller effect (dashed lines correspond to ± one standard deviation on these factors).
@@
   scale_linetype_manual(values = c(2, 1)) +
-  xlab("dependence strength") +
+  xlab("species strength") +
   ylab(expression(f[S])) +
@@
 For instance, despite inconsistent outcomes in practice [@Suding2004; @Rodewald2015; @Smith2016], our results suggest that current restoration approaches that focus on direct eradication of invasive species might indeed be an effective way to modify ecosystem state.
-Nevertheless, our results also indicate that removals must be exercised with caution as invaded communities tend to be highly dependent on invaders and therefore acutely vulnerable to their eradication [@Traveset2013; @Albrecht2014].
+Nevertheless, our results also indicate that removals must be exercised with caution. 
+Not only it is hard to predict the direction in which the system will change, but also, invaded communities tend to be highly dependent on invaders and therefore acutely vulnerable to their eradication [@Traveset2013; @Albrecht2014].
 

### 2017-02-25 paper/EL-reviewer-comments-1.Rmd
Response to Reviewer #3

@@
 Now, we have removed the term driver species and instead focus on two well-defined metrics: $f_D$ and $f_S$, which correspond to the frequency to which a species is classified as a driver or superior node, respectively.
+
+In addition, we now focus on the results obtained when we use the asymmetry of the dependences to direct the networks.
+We do so, because thanks to the reviewers comments, we identyfied some problems with the application of structural controllability when we use the mutual dependences to direct the network.
+Specifically, the problems arise from an absolute dominance of cycles and difficulties to the use of the maximum maximum matching algorithm to find a minimum set of driver nodes $D$.
 
@@
 is not based on a single structural metric but acknowledges the existence of multiple management strategies; some more optimal than others in specific contexts".
-We also concur that more flexible approaches like ours and the one implemented by @McDonald-Madden2016* "that take a network-wide approach might prove more useful to guide ecosystem management if we want to go beyond using network metrics to minimise topological species loss".*
+We also concur that more flexible approaches like ours and the one implemented by @McDonald-Madden2016 "that take a network-wide approach might prove more useful to guide ecosystem management if we want to go beyond using network metrics to minimise topological species loss".*
 
@@
 Lamentably the network's control profile does not provide species-level information and hence we couldn't use it to our advantage.
-Nevertheless, as suggested by you and another reviewed, we have included a section where in the Supporting information *(S2) where we explain that our networks are external dilation dominated.
-The @Ruths2016 has provided us with very useful insight on the selection of the direction of control and the utility of the concept of driver nodes for management applications.*
+Nevertheless, as suggested by you and another reviewed, we have included a section where in the Supporting information (S2) where we explain that our networks are external dilation dominated.
+The approach of @Ruths2014 has provided us with very useful insight on the selection of the direction of control and the utility of the concept of driver nodes for management applications.*
 
@@
 
-    *PARTIAL ANSWER: We have included some comments about the general limitations of the structural controlability approach in the "Theoretical Framework" section (Lines XXX). Furthermore*
+    *We have now included comments about the general limitations of the structural controllability appriach in the "Theoretical Framework" section.
+Furthermore, we are now explicit abuout the fact that species have multiple types of interactions and therefore our approach can only provide a partial picture when only one type of interaction is included.
+We do so both the Introduction and the Discussion.
+Finally, we are also explicit about the fact that we do not advocate for management decisions to be based solely on our approach, but how it can "provide a simple, straightforward, and theoretically-informed indication of the degree to which the community is self-regulated and therefore how difficult it might be to modify its state in one way or another using some of the species that integrate it".*
 
-Second, It would be helpful if the authors could test the robustness of their results to sampling.
+- Second, It would be helpful if the authors could test the robustness of their results to sampling.
 The results show that invasive species change manageability.
@@
 
-See more specific comments below.
+    *As suggested we have conducted a sensitivity analysis in which we remove links from our empirical networks with a probability inversely proportional to their strength.
+Due to space constraints, we have included the analysis in the Supporting Information S5.
+We found that our results are consistent even in serious cases of undersampling.*
 
@@
 We have apologise for the imprecision.
-The sentence now reads "To bridge this gap, we develop methods to apply previous theory on the control of complex systems into an ecological context and implement them using empirical data, while taking into account the quantitative differences that exist among species interactions", which better reflects our contribution.*
+The sentence now reads "To bridge this gap, we outline an approach to apply theory on the control of complex systems in an ecological context and implement them using empirical data.*
 
@@
 The subject was intended to be "control theory".
-We have rephrased the sentence to improve clarity and it now reads "Therefore, control theory can potentially provide an indication of which species are most relevant from a structural and dynamic perspective, a particularly important feature given that these species should underpin informed attempts to both alter or maintain the ecosystem state".*
+We have rephrased the sentence to improve clarity and it now reads "Therefore, control theory could also be harnessed to provide an indication of which species are most relevant from a structural and dynamic perspective".*
 
@@
     *We based the direction of the hypothesis in the general feeling of failure of several restoration ecology programmes.
-However, in retrospect, we realise that the academic evidence to substantiate the hypotheis was insufficient.
-We have reframed the sentence to indicate that invaded communities might have different levels of manageability but without an a priori expectation on the direction of this difference.
-REVISE, CHECK WITH WARWICK*
+However, in retrospect, we realise that we presented insuficient academic evidence to substantiate the hypotheis.
+Although the results have changed after the discovery of a mistake on the analysis, we have not changed the original direction of the hypothesis.
+Nevertheless, we have reframed the sentence to explain it better: "...
+grounded on the difficulties usually involved with invasive species eradication and ecosystem restoration [@Woodford2016], we ask whether invaded networks have lower levels of "manageability" than their uninvaded counterparts; that is, whether they require a greater proportion of species to be managed to achieve the same level of control"*
 
@@
     *Thanks.
-We have rewritten a large section of the methods and tried to be more clear when defining new terms by providing some examples and using a more logical sequence to go from one concept to the next (Lines XXX).
-We have also included a short glossary with the most important definitions.
-TO DO*
+We have rewritten a large section of the methods and tried to be more clear when defining new terms by providing some examples and using a more logical sequence to go from one concept to the next.
+We have also included a short glossary with the most important definitions at the end of the manuscript.*
 
@@
 
-    *Indeed.
-We apologise for the imprecision.
-We indeed mean financial resources.
+    *We apologise for the imprecision as we meant financial resources.
 We have modified the sentence to improve clarity and it now reads "Ecologically, these distinctions are relevant because management and conservation resources are limited and therefore ecological interventions should ideally be focused on species that might provide the largest impact."*
@@
 
-Ln 303-305. Please explain here which is the response variable that the ratio of plant to pollinator can explain.
+- Ln 303-305. Please explain here which is the response variable that the ratio of plant to pollinator can explain.
 
-Ln 326.
+    *We eliminated ambiguity by rephrasing the sentence. It now reads "... of the various covariates we explored, the ratio of plant to pollinator showed the strongest relationship with n~D~".*
+
+- Ln 326.
 "The strength of the dependency" has been defined as species strength by Bascompte et al.
@@
 
-Ln 336. Liu et al. 2011 found that driver nodes were often peripheral nodes in the network instead of network hubs. Here you find the opposite. How can you explain these differences?
+    *We apologise for the potential confusion.
+By "the strength of dependency we meant species strength as defined by @Bascompte2006.
+We have modified the text in the Methods and the Results to avoid potential confusion.
+We also stick to dependence troughout the manuscript*
 
-Ln 343 and Figure 4.
+- Ln 336. Liu et al. 2011 found that driver nodes were often peripheral nodes in the network instead of network hubs. Here you find the opposite. How can you explain these differences?
+
+    *Our results agree in fact agree with those of @Liu2011.
+However, this was confusing because our poor choice of terminology (we used driver species as a term to refer to species with a high probability of being superior nodes).
+Using our results, and insight obtained from @Ruths2014, we now explain that peripheral nodes tend to be driver because they are needed to achieve full control, but that network hubs are also often driver nodes, as they act as source nodes from which control signals can be transferred.
+Furthermore, our analysis at the species level is now more comprehensive, as it includes information on their role as both driver and superior nodes.*
+
+- Ln 343 and Figure 4.
 Here and in the figure legend you say the level of manageability of empirical networks is lower, but in the figure you show an index that goes in the opposite direction, i.e.,  we see lower values for the randomization.
@@
 
-Ln 362. Again the idea that supergeneralists tend to be driver species contrasts with Liu et al. results. This should be explored in more detail in the discussion.
+    *Figure 4 represents the rank of the emprical network compared to that of the randomisations.
+We have now included explanatory arrows and modified the axis titles and the caption to facilitate the interpretation.
+Hopefully now it's much easier to understand.*
 
-Ln 372. It is important to say that vulnerability is related change, but that it is had to predict in which direction the system will change
+- Ln 362. Again the idea that supergeneralists tend to be driver species contrasts with Liu et al. results. This should be explored in more detail in the discussion.
 
-Figure 5 legend. Please include here the definition of dependency strength so the reader does not need to go back and forth.
+    *Following from the clarifications provided in the response two the comment for Line 336.
+We hope the discussion, which clearly distinguishes between driver and superior nodes explicates the apparent contrasting results.*
+
+- Ln 372. It is important to say that vulnerability is related change, but that it is had to predict in which direction the system will change
+
+    *Thank you.
+We have implemented this suggestion and the text now reads "Not only it is hard to predict the direction in which the system will change, but also, invaded communities tend to be highly dependent on invaders and therefore acutely vulnerable to their eradication"*
+
+- Figure 5 legend. Please include here the definition of dependency strength so the reader does not need to go back and forth.
+
+    *Done.*
 

### 2017-02-25 paper/draft_2.Rmd
Add abstract draft

@@
 
-* **Number of words:** ~ () abstract; approx. 5460 main text.
+* **Number of words:** 183 abstract; approx. 5460 main text.
 
@@
 
-150 words
+It is generally unknown how the disruptions caused by perturbations like biotic invasions affect our ability to manage ecological communities.
+Here, we capitalise on recent advances in control theory to assess the "manageability" of ten pairs of uninvaded and invaded plant-pollinator communities.
+We found that the manageability of the studied networks is strongly determined by the relative richness of plants and pollinators, which in turns constraint the species' degree distribution.
+Furthermore, we characterise species potential to be candidates for management interventions using metrics that explore the entire space of control strategies.
+Specifically, we use the extent to which species (i) are necessary to steer the state of the community,  and (ii) are able to affect the abundance of other species.
+Remarkably, we found that invasive plants have a dominant position in every community in which they were found and that this dominance is underpinned by the high asymmetry in the dependence of their interaction partners.
+Our results highlight the advantages of using a control theoretic framework to answer ecological questions, at the same time it provides insight into the design of informed management interventions.
 

### 2017-02-25 paper/supp_info_2.Rmd
Add authors

@@
 ---
-title: "Biotic invasions fuck with the manageability of pollination networks"
+title: "The manageability of pollination networks in an invasion context"
 subtitle: "Supporting Information"
+author: "E. Fernando Cagua, Kate L. Wootton, Daniel B. Stouffer"
 classoption: a4paper

### 2017-02-26 paper/draft_2.Rmd
Minor corrections
References to Figure 3. Fix a definition. Put model summary table in the proper place

@@
 
-All of the networks studied had a driver node density *n~D~* between `r round(min(dplyr::filter(n_driver, type == "weight")$n_dr_p), digits = 2)` and `r round(max(dplyr::filter(n_driver, type == "weight")$n_dr_p), digits = 2)` (mean `r round(mean(dplyr::filter(n_driver, type == "weight")$n_dr_p), digits = 2)`.
-In addition, we found that, when controlling for potential species richness effects, the *n~D~* of invaded communities was smaller to those of non-invaded communities (Figure 3a; Table S5). 
-Nevertheless, of the various covariates we explored, the ratio of plant to pollinator showed the strongest relationship with *n~D~* (Table S4). 
+All of the networks studied had a driver node density *n~D~* between `r round(min(dplyr::filter(n_driver, type == "weight")$n_dr_p), digits = 2)` and `r round(max(dplyr::filter(n_driver, type == "weight")$n_dr_p), digits = 2)` (mean `r round(mean(dplyr::filter(n_driver, type == "weight")$n_dr_p), digits = 2)`; Figure 3a).
+In addition, we found that, when controlling for potential species richness effects, the *n~D~* of invaded communities was smaller to those of non-invaded communities (Figure 3b; Table S5). 
+Nevertheless, of the various covariates we explored, the ratio of plant to pollinator showed the strongest relationship with *n~D~* (Table S4; Figure 3c). 
 Specifically, we found that as the proportion of pollinators increases and the ratio plant/pollinator balances, *n~D~* decreases (all our communities had more pollinators than plants). 
@@
   ~ A matching with the largest possible matching size *and* matching weight.
+
 Superior node

### 2017-02-26 paper/supp_info_2.Rmd
Minor corrections
References to Figure 3. Fix a definition. Put model summary table in the proper place

@@
 										 display = c("d", "s", "f", "f", "G")) %>%
-	print(booktabs = T, include.rownames = F,  caption.placement = "top", comment = F, sanitize.text.function = function(x){x})
+	print(booktabs = T, include.rownames = F,  caption.placement = "top", comment = F, sanitize.text.function = function(x){x}, table.placement = "H")
 

### 2017-02-28 paper/draft_2.Rmd
New title and metadata

@@
 ---
-title: "The manageability of pollination networks in an invasion context"
+title: "Quantifying the manageability of pollination networks in an invasion context"
 classoption: a4paper
@@
 
-* **Authorship:** DBS conceived the idea; EFC, DBS and KLW contributed to the development of the theoretical framework. EFC performed all analysis. EFC and DBS wrote the manuscript.
+* **Authorship:** DBS conceived the idea; all authors contributed to the development of the theoretical framework. EFC performed all analysis. EFC and DBS wrote the manuscript.
 

### 2017-02-28 paper/draft_2.Rmd
Revise intro

@@
 
-Complex systems are chahave bracterised by relationships in which the whole is often greater than the sum of its parts [@Jorgensen1998; @Levin1999; @Montoya2006].
+Complex systems are characterised by relationships in which the whole is often greater than the sum of its parts [@Jorgensen1998; @Levin1999; @Montoya2006].
 Within community ecology, a complex systems approach has led to the development of a variety of analytical and simulation tools with which to understand, for example, the role of species when embedded in an intricate network of interactions [@Pascual2005; @Bascompte2009; @Stouffer2012].
@@
 
-Among the various possibilities, *control theory* appears to be a strong candidate.
+Among the various possibilities, *control theory* appears to be a strong candidate [@Isbell2013].
 This method, widely used in engineering to determine and supervise the behaviour of dynamical systems [@Motter2015], is well equipped to deal with the many feedbacks present in ecological communities [@Liu2016].
@@
 
-This information is valuable not only from an ecological perspective, but it might be also relevant to address management and conservation challenges. 
+This information is valuable not only for basic ecology, but it might be also relevant to address more applied management and conservation challenges. 
 This is particularly true in the context of biotic invasions, where identifying key players in the community is a prerequisite to informed attempts to either alter the state of invaded ecosystem and maintain the state of uninvaded ones.
-Despite recent advances in network theory, practical challenges to the conservation of interaction networks persist [@Tylianakis2010], and the link between the structure of complex networks and our ability to manage and conserve them, is still ambiguous [@Bluthgen2010; @Kaiser-Bunbury2015].
+Despite recent advances in network theory, practical challenges to the conservation of interaction networks persist [@Tylianakis2010], and the link between the structure of complex networks and our ability to manage and conserve them is still ambiguous [@Bluthgen2010; @Kaiser-Bunbury2015].
 To complicate things further, biotic invasions can induce dramatic changes in the patterns of interactions that determine the structure of ecological networks [@Baxter2004; @Tylianakis2008; @Ehrenfeld2010a].
-Understanding how the differences in network structure before and after the invasion impact our ability to manage the communities double challenge, it is a critical first step towards a fully informed recovery.
+Understanding how the differences in network structure before and after the invasion impact our ability to manage the communities is thus a double challenge, but it is also the critical first step towards a fully informed recovery.
 Despite the apparent overlap, a control-theoretic perspective has not been adopted in an invasion context. 
@@
 
-To bridge this gap, we outline an approach to apply theory on the control of complex systems in an ecological context and implement them using empirical data.
+To bridge this gap, we outline an approach to apply theory on the control of complex systems in an ecological context and implement it using empirical data.
 Specifically, we use a set of ten pairs of uninvaded and invaded plant-pollinator communities to investigate the link between invasion, network structure and ecological management. 
 While doing so, we focus on two particular questions.
-First, grounded on the difficulties usually involved with invasive species eradication and ecosystem restoration [@Woodford2016], we ask whether invaded networks have lower levels of "manageability" than their uninvaded counterparts; that is, whether they require a greater proportion of species to be managed to achieve the same level of control.
+First, grounded in the difficulties usually involved with invasive-species eradication and ecosystem restoration [@Woodford2016], we ask whether invaded networks have lower levels of "manageability" than their uninvaded counterparts; that is, whether they require a greater proportion of species to be managed to achieve the same level of control.
 Second, we ask whether some species are more important than others at driving the population dynamics of the community and which factors determine this importance. 
 We focus on these two particular applications for a variety of reasons. 
-First, biotic invasions are known to produce tractable changes in the structure of ecological networks, and these changes can be particularly pronounced in mutualistic networks between plants and pollinators where biotic invasions have been shown to modify the strength of species interactions and the degree of network nestedness and connectivity [@Olesen2002; @Aizen2008; @Bartomeus2008; @Vila2009; @Traveset2013].
-Second, although species are involved in multiple types of interactions, plant-pollinator networks provide an ideal framework to answer these questions. 
+Biotic invasions are known to produce tractable changes in the structure of ecological networks, and these changes can be particularly pronounced in mutualistic networks between plants and pollinators where biotic invasions have been shown to modify the strength of species interactions and the degree of network nestedness and connectivity [@Olesen2002; @Aizen2008; @Bartomeus2008; @Vila2009; @Traveset2013].
+Furthermore, although species are involved in multiple types of interactions, plant-pollinator networks provide an ideal framework to answer these questions. 
 On the one hand, community networks that quantify relative levels of interaction are readily available. 

### 2017-02-28 paper/draft_2.Rmd
Change to submission formating

@@
     fig_crop: no
+    includes:
+      after_body: after_body.md
   html_document: default
@@
 - \usepackage{booktabs}
+- \usepackage{tocloft} 
 - \usepackage{caption}
+- \captionsetup{labelsep=none,textformat=empty}
 - \usepackage{lineno}
+- \usepackage[nomarkers,tablesfirst, nolists]{endfloat}
+- \cftpagenumbersoff{figure}
+- \cftpagenumbersoff{table}
 documentclass: artikel1
@@
 \linenumbers
+\renewcommand*\listfigurename{Figure legends}
+\renewcommand*\listtablename{Table legends}
 

### 2017-02-28 paper/draft_2.Rmd
Update methods

@@
 
-Disregarding practical considerations, any network could hypothetically be fully controlled if we control the state of every single node individually.
+Disregarding practical considerations, any network (community) could hypothetically be fully controlled if we control the state of every single node (species) individually.
 At the core of control theory of complex networks, however, rests the idea that the state of a node depends on the state of the nodes it interacts with, and the particular form of this dependence is determined both by the dynamic relationship among interacting nodes as well as the structure of the links in the network.
-This principle can, therefore, be harnessed to find a subset of *driver nodes* to which to apply external input signals which then drive the state of every other node in the network to a desired configuration.
+This principle can therefore be harnessed to find a subset of *driver nodes* to which to apply external input signals which then drive the state of every other node in the network to a desired configuration.
 
-Conveniently, in a network with linear dynamics, the information necessary to determine the minimum number of driver nodes *D* is fully contained in the network structure [@Kalman1963; @Liu2011; @Motter2015].
-We, therefore, start here from the assumption that an ecological network can, at least near equilibrium points, be described by $\frac{dx}{dt} = Ax + Bu(t)$, where the change over time of its state ($\frac{dx}{dt}$) depends on its current state *x* (for example the species' populations), an external time-varying input *u(t)*, and the matrices *A* and *B*, which encapsulate information about the network structure and how the species respond to the external input, respectively.
+Conveniently the information necessary to determine the minimum number of driver nodes *D* in a network with linear dynamics is fully contained in the network structure [@Kalman1963; @Liu2011; @Motter2015].
+We, therefore, start here from the assumption that an ecological network can, at least near equilibrium points, be described by $\frac{dx}{dt} = Ax + Bu(t)$, where the change over time of its state ($\frac{dx}{dt}$) depends on its current state *x* (for example the species' abundances), an external time-varying input *u(t)*, and two matrices *A* and *B*, which encapsulate information about the network structure and how the species respond to the external input, respectively.
 Even though linearity might be a strong assumption, it has been shown that fundamental insight about the control of complex systems can be gained without a detailed knowledge of the nonlinear dynamics and the system parameters [@Liu2016], an important step towards ultimately understanding the controllability of systems with nonlinear dynamics [@Liu2011].
@@
 
-The number of driver nodes *D* can provide a structural indication of how difficult its control might be.
+The number of driver nodes *D* can provide a structural indication of how difficult a network's control might be.
 This is because systems that require a large number of external input signals are intuitively more difficult or costly to control.
 In an ecological context, external inputs that modify the state of a node can be thought of as management interventions.
-Therefore, the density of driver nodes $n_D = \frac{D}{S}$, where *S* is the total number of species in the community, can be seen as a metric of the extent to which network structure can be harnessed for network control.
-For instance, while a hypothetical "network" in which species do not interact but instead function independently from each other would require direct interventions in every single species to achieve full control, a linear food chain would require just one species to be directly controlled to harness cascading effects through the trophic levels that compose it.
+Therefore, the density of driver nodes $n_D = \frac{D}{S}$, where *S* is the total number of species in the community, can be seen as a measure of the extent to which network structure can be harnessed for network control.
+For instance, while a hypothetical "network" in which species do not interact but instead function independently from each other would require direct interventions for every single species to achieve full control, a linear food chain would require just one species to be directly controlled to harness cascading effects through the trophic levels that compose it.
 From this perspective, it is possible to use *n~D~* as an index of the manageability of an ecological community, understood in the context of how difficult is to modify the abundances of species in the community using external interventions—a common theme in ecosystem management, conservation, and restoration.
@@
 A maximal cardinality matching is then called a *maximum matching* if the sum of the weights of the matched links (also referred to as *matching weight*) is again the largest possible [@West2001].
-Note that this implies that for unweighted binary networks, all maximal cardinality matchings are also maximum matchings.
 
-Once we have the subset of links that constitute a matching, we can also classify the nodes in the network (Figure 1).
+Once we have the subset of links that constitute a matching, we can also classify the nodes in the network based on that matching (Figure 1).
 A node is said to be *matched* if it is at the end of a matched link and *unmatched* otherwise. 
@@
 Note that a node cannot be superior if it has no outgoing links.
-Notably, these node categories are what help us to link a maximum matching back to the concept of network controllability as follows.
+Notably, these node categories are what help us to link a maximum matching back to the concept of network controllability, as follows.
 Unmatched nodes are the *driver nodes* *D* because they have no superior in the network and must be directly controlled by an external input [@Liu2011].
@@
 (a) We start with a network in which the direction of the links indicates the potential direction of control; for example a link from *a~1~* to *p~1~* indicates that the state of *p~1~* is influenced by the state of *a~1~*.
+The numbers indicate the weight of each link.
 (b & c) This network has two maximal cardinality matchings; that is, two configurations in which it would be possible to exert full control of the network via external input signals to a minimal set of nodes.
@@
 plot.new()
-legend(0.25, 0.8, legend = c("unmatched link", "matched link"), horiz = TRUE,
+legend(0.20, 0.8, legend = c("unmatched link", "matched link"), horiz = TRUE,
 			 lty = 1, 
@@
 
-legend(0.8, 0.8, legend = c("unmatched node", "matched node"), horiz = TRUE,
+legend(0.835, 0.8, legend = c("unmatched node (driver)", "matched node"), horiz = TRUE,
 			 pch = 21, 
@@
 While calculating *n~D~* provides an indication of the manageability of an ecological community, it does not provide information about the identity of the species that compose the set of driver nodes.
-Ecologically, these distinctions are acutely relevant because management and conservation resources are limited, and therefore ecological interventions should ideally be focused on the set of species that might provide the largest impact.
-Maximum matchings in a network are often not unique, and each different maximum matching indicates a unique path that can potentially be used to control the network. 
-We harness this property and use a network's complete set of multiple maximum matchings to characterise a species' relative importance in driving the state of the community. 
-One possibility is to characterise a species by the frequency *f~D~* with which it is classified as a driver node.
-However, the profile of our networks indicates that a large proportion of driver nodes are so, because of external interventions are required to achieve **full** controllability, and not because they influence the abundance of other species (Supporting Information S2).
+Ecologically, potential differences between species are acutely relevant because management and conservation resources are limited, and therefore ecological interventions should ideally be focused on the set of species that might provide the largest impact.
+Moreover, maximum matchings in a network are often not unique, and each different maximum matching indicates a unique path that can potentially be used to control the network. 
+We harness this property and use a network's complete set of maximum matchings to characterise each species' relative importance in driving the state of the community. 
+One possibility is to characterise a species by the frequency *f~D~* with which it is classified as a driver node within this set of matchings.
+However, the profile of our networks indicates that a large proportion of driver nodes are classified as such, because of external interventions that are required to achieve **full** controllability and not because they influence the abundance of other species (Supporting Information S2).
 Furthermore, the precise role of driver nodes is still ambiguous when full control is unfeasible or undesired—often the case in ecological settings.
@@
 
-Most commonly, structural controllability assumes unweighted networks—links exist or not, and hence *f~D~* and *f~S~* can be calculated by computing all possible maximum cardinality matchings. 
-However, we take the link weights into account when calculating the matchings because it has been shown that the weights can reveal significant ecological patterns and processes that might be undetectable in unweighted networks [@Scotti2007; @Tylianakis2007; @Vazquez2007; @Kaiser-Bunbury2010a].
-For example, a species *A* interacts with both species *B* and *C* but depends strongly on *B* and only weakly on *C*. 
+Most commonly, structural controllability assumes unweighted networks—links exist or not, and hence *f~D~* and *f~S~* can be calculated by computing all possible maximum-cardinality matchings. 
+However, we take the link weights into account when calculating the matchings here because it has been shown that the weights can reveal significant ecological patterns and processes that might be undetectable in unweighted networks [@Scotti2007; @Tylianakis2007; @Vazquez2007; @Kaiser-Bunbury2010a].
+For example, a species *A* may interact with both species *B* and *C* but depends strongly on *B* and only weakly on *C*. 
 Intuitively, a management intervention designed to indirectly modify the abundance of a species *A* is more likely to succeed if the abundance of *B*, rather than *C*, is directly controlled.
 A complication of including the interaction weight when calculating the maximum matching, however, is that empirical interaction strengths are to some extent stochastic and depend on proximate factors such as sampling method and intensity [@Gibson2011].
-We circumvent this issue by calculating all maximal cardinality matchings and subsequently ranking them by their matching weight. 
+We overcome this issue by calculating all maximal cardinality matchings and then ranking them by their matching weight. 
 By following this approach, we effectively give priority to the species that participate in the pathways that potentially have the largest impact on the community while acknowledging the limitations associated with sampling and its potential restrictions [@Jordano2016].
@@
 
-Recall that the aforementioned maximum-matching approach requires a directed network in which a link between species *i* and *j* pointing to species *j* indicates that the abundance of *j* can be affected by the abundance of *i*.
+As we noted earlier, the aforementioned maximum-matching approach requires a directed network in which a link between species *i* and *j* pointing to species *j* indicates that the abundance of *j* can be affected by the abundance of *i*.
 This implies that we need first to identify a directionality for the links between species that is consistent with the dynamics of the community (Figure 2). 
@@
 
-Given the respective dependences, the extent to which a species *i* affects species *j* relative to the extent to which *j* affects *i* can be summarised by the interaction asymmetry [@Bascompte2006] given by $$a(i,j) = \frac{\left | d_{ij}-d_{ji} \right |}{max\left ( d_{ij}, d_{ji} \right )}.$$
+Given the respective dependences, the extent to which a species *i* affects species *j* relative to the extent to which *j* affects *i* can be summarised by the interaction asymmetry [@Bascompte2006] given by $$a(i,j) = a(j,i) = \frac{\left | d_{ij}-d_{ji} \right |}{max\left ( d_{ij}, d_{ji} \right )}.$$
 Previous research has shown that mutual dependences are often highly asymmetric in natural communities [@Bascompte2006]; in other words, if a plant species is largely dependent on a pollinator species, then that pollinator tends to depend rather weakly on the plant (or vice versa).
@@
 First, it is consistent with previous advances in structural controllability; second, it avoids complications related to the introduction of artificial control cycles; and third it significantly reduces the computational resources necessary for the application of our approach (Supporting Information S6).
-Furthermore, we show that changing to unidirectional interactions determined by the observed direction of asymmetry, as a surrogate of bidirectional mutual dependences does not alter the relative *n~D~* of different networks (Table S3).
+Furthermore, we show that changing to unidirectional interactions determined by the observed direction of asymmetry, as a surrogate of bidirectional mutual dependences, does not alter the relative *n~D~* of different networks (Table S3).
 
-To find a maximum matching, we adopted a strategy based on an alternative bipartite representation of the directed network in which the two levels indicate the outgoing and incoming links to each node (Supporting Information S1).
-Once we had this alternative representation, then, on each network, we used the maximum bipartite matching algorithm implemented in the `max_bipartite_match` function of igraph 1.0.1 [@Csardi2006a].
+To find a maximum matching in a network with interaction directions and weights determined by the asymmetry, we adopted a strategy based on an alternative bipartite representation of the directed network with two levels that indicate the outgoing and incoming links to each node (Supporting Information S1).
+Once we had this alternative representation we used the maximum bipartite matching algorithm implemented in the `max_bipartite_match` function of igraph 1.0.1 [@Csardi2006a] on each network.
 
@@
 
-Although understanding the variability of manageability across ecological networks is a useful result in itself, we also wanted to test whether invasion status had an impact on the observed *n~D~*. 
-We, therefore, used a set of generalised linear models (with binomial error structure) to investigate the effect of invasion status while also controlling for factors related to species richness, since one might naively expect to see a negative relationship between richness and manageability [@Menge1995].
+Although understanding the variability of manageability across ecological networks is a useful result in itself, we also wanted to test whether invasion status or other predictors had an impact on the observed *n~D~*.
+We, therefore, used a set of generalised linear models (with binomial error structure) to investigate the effect of invasion status while also including covariates related to species richness, since one might naively expect to see a negative relationship between richness and manageability [@Menge1995].
 These covariates included the total number of species, plant richness, pollinators richness, the ratio of plant to pollinator richness, the link density (connectance), and the study site (as a two-level factor).
@@
 Previous research indicates a direct link between a network's degree distribution and the number of nodes necessary to fully control it [@Liu2011], but the strength and applicability of this relationship have not been tested for in weighted ecological networks.
-We, therefore, compared the driver-node density *n~D~* of the empirical networks to networks generated by a null model that maintained each species' strength (its total sum of visits) while allowing their degrees (its number of interactions) to vary.
-Randomisations were generated using the function `commsim` in vegan 2.3-3 [@Oksanen2016]. 
+We therefore compared the driver-node density *n~D~* of the empirical networks to networks generated by a null model that maintained each species' strength (its total sum of visits) while allowing their degrees (its number of interactions) to vary.
+Randomisations were generated using the quasiswap-count algorithm and the function `commsim` in vegan 2.3-3 [@Oksanen2016]. 
 After generating the randomised networks, we then calculated the mutual dependences and interaction asymmetries of each and determined *n~D~* using our maximum-matching framework. 
@@
 Beyond network structure, the dependence asymmetry plays a fundamental role in determining the direction of control in each two-species interaction and therefore has the potential to influence the network *n~D~* results above.
-We, therefore, performed an additional randomisation in which we kept the structure of each network constant but randomised the direction of the interaction asymmetries. 
+We therefore performed an additional randomisation in which we kept the structure of each network constant but randomised the direction of the interaction asymmetries. 
 That is, we first calculated the observed asymmetries for each community and then shuffled the direction of the link between each pair of species. 
@@
 We selected this threshold as it provided a high agreement between networks quantified by visitation and pollination efficiency as well as between our weighting/directionality assumptions; however, the choice of this threshold had a negligible impact on any results (Supporting Information S7).
-
 Details about the computational procedure to find all maximum cardinality matchings of a network can be found in Supporting Information S1 and Figure S2.
@@
 
-We then examined whether any species-level structural properties can predict our metrics of species importance—the frequency to which a species was a driver or a superior node (*f~D~* and *f~S~*, respectively).
+We then examined whether any species-level structural properties could predict our metrics of species importance—the frequency to which a species was a driver or a superior node (*f~D~* and *f~S~*, respectively).
 We used a set of generalised linear mixed-effects models (with binomial error structure) with the relative frequencies as the response variables. 
-As predictors in this model, we included measures of centrality (degree and eigen-centrality), which have been found to be strong predictors of importance in a coextinction context [@Memmott2004]; a measure related to network robustness (contribution to nestedness), as nestedness has been proposed as one of the key properties that promote stability in mutualistic networks [@Saavedra2011]; and two measures of strength of association and dependence (visitation and dependence strength, this is the sum of visits a species receives or performs, and the sum of dependences of all species on the focal species, respectively), as their distribution determines the extent of interspecific effects [@Bascompte2006].
-To facilitate comparison among the continuous variables we scaled so that they all had a mean of zero and a standard deviation of one.
-In addition, we also included guild (plant or pollinator), and whether the species is invasive or not, as categorical fixed effects.
+As predictors in this model, we included measures of centrality (degree and eigen-centrality), which have been found to be strong predictors of importance in a coextinction context [@Memmott2004]; a measure related to network robustness (contribution to nestedness), as nestedness has been proposed as one of the key properties that promote stability in mutualistic networks [@Saavedra2011]; a measure of strength of association (visitation strength, the sum of visits a species receives or performs) and a measure of strength of dependence (species strength, the sum of dependences of all species on the focal species), as their distribution determines the extent of interspecific effects [@Bascompte2006].
+To facilitate comparison among the continuous variables, we scaled them so that they all had a mean of zero and a standard deviation of one.
+In addition, we also included guild (plant or pollinator) and whether the species is invasive or not as categorical fixed effects.
 Although the importance of plants and pollinators or invasive and non-invasive species could respond differently to our structural metrics, our data set did not contain enough variation to include the corresponding interactions terms for these latter two predictors.
@@
 Lastly, we allowed for variation between different communities by including the network identity as a random effect [@Bates2015]. 
-Candidate models and estimates were assessed using the same procedure as in the *n~D~* models.
+Candidate models and estimates were assessed using the same procedure as in the  models *n~D~*.
 
@@
 (b) Species strength (the sum of the dependences of other species on the species of interest) is the single most important factor explaining _f~S~_.
-Visitation strength and  degree also had an important albeit comparatively smaller effect (dashed lines correspond to ± one standard deviation on these factors).
+Visitation strength and  degree also had an important albeit comparatively smaller effect (dashed lines correspond to one standard deviation on these factors).
 Invasive species are depicted as circles."}
@@
 attr(coef_tables, "subheadings") <- paste0("$", names(mod), "$")
-attr(coef_tables, "message") <- "\\footnotesize Confidence intervals correspond to an alpha risk of 0.05."
 coef_tables %>%
-	xtable::xtableList(caption = "\\textbf{Factors determining species importance}. Factor estimates correspond to the average over all models that accounted for 95\\% of the AIC evidence.",
+	xtable::xtableList(caption = "\\textbf{Factors determining species importance}.
+Factor estimates correspond to the average over all models that accounted for 95\\% of the AIC evidence.
+Confidence intervals correspond to $\\alpha = 0.05$.",
 										 digits =  c(0, 0, 2, 2, 2),

### 2017-02-28 paper/draft_2.Rmd
Update awknowledgements

@@
 The authors thank Dr.
-Takeuki Uno for the insight provided to find the set of all maximum matching algorithms, and Jason Tylianakis, Bernat Bramon, Warwick Allen, Matthew Hutchinson, and Marilia Gaiarsa for feedback and valuable discussions.
+Takeuki Uno for the insight provided to find the set of all maximum matching algorithms, and Jason Tylianakis, Bernat Bramon Mora, Guadalupe Peralta, Rogini Runghen, Warwick Allen, Matthew Hutchinson, and Marilia Gaiarsa for feedback and valuable discussions.
 EFC acknowledges the support from the University of Canterbury Doctoral Scholarship, the University of Canterbury Meadow Mushrooms Postgraduate Scholarship, a New Zealand International Doctoral Research Scholarship, and a travel grant from the European Space Agency.

### 2017-02-28 paper/draft_2.Rmd
Update results

@@
 
-All of the networks studied had a driver node density *n~D~* between `r round(min(dplyr::filter(n_driver, type == "weight")$n_dr_p), digits = 2)` and `r round(max(dplyr::filter(n_driver, type == "weight")$n_dr_p), digits = 2)` (mean `r round(mean(dplyr::filter(n_driver, type == "weight")$n_dr_p), digits = 2)`; Figure 3a).
+All of the networks studied had a driver-node density *n~D~* between `r round(min(dplyr::filter(n_driver, type == "weight")$n_dr_p), digits = 2)` and `r round(max(dplyr::filter(n_driver, type == "weight")$n_dr_p), digits = 2)` (mean `r round(mean(dplyr::filter(n_driver, type == "weight")$n_dr_p), digits = 2)`; Figure 3a).
 In addition, we found that, when controlling for potential species richness effects, the *n~D~* of invaded communities was smaller to those of non-invaded communities (Figure 3b; Table S5). 
-Nevertheless, of the various covariates we explored, the ratio of plant to pollinator showed the strongest relationship with *n~D~* (Table S4; Figure 3c). 
-Specifically, we found that as the proportion of pollinators increases and the ratio plant/pollinator balances, *n~D~* decreases (all our communities had more pollinators than plants). 
-Other coovariates—connectance (link density) and species richness—had a negative and comparatively less important relationship with *n~D~*.
+Nevertheless, of the various covariates we explored, the ratio of plants to pollinators showed the strongest relationship with *n~D~* (Table S4; Figure 3c). 
+Specifically, we found that, as the proportion of pollinators increases and the ratio plant/pollinator approaches unity, *n~D~* decreases (all our communities had more pollinators than plants). 
+Other covariates—connectance (link density) and species richness—had negative, but comparatively less important relationships with *n~D~*.
 
-```{r fig_explaining-n-driver, echo = FALSE, warning = FALSE, message = FALSE, fig.width = 3.245, fig.height = 4.8, fig.cap = "**Driver node density**.
-(a) Density distribution of the proportion of driver nodes (_n~D~_) for the twenty studied networks.
-(b) Invaded communities have lower proportion of *n~D~* than uninvaded communities even when controlling for factors related to species richness.
+```{r fig_explaining-n-driver, echo = FALSE, warning = FALSE, message = FALSE, fig.width = 3.245, fig.height = 4.8, fig.cap = "**Driver-node density**.
+(a) Histogram of the driver-node density (_n~D~_) for the twenty studied networks.
+(b) Invaded communities have lower *n~D~* than uninvaded communities even when controlling for factors related to species richness.
 The boxes cover the 25th–75th percentiles, the middle lines mark the median, and the maximum length of the whiskers is 1.5 times the interquartile range.
-All points outside this range are indicated by the circles.
-(c) Out of the richness metrics, the ratio of plants to pollinators showed an important relationship with *n~D~*.
-In both plots, residuals correspond to the partial working residuals of the invasion status in our generalised linear mixed model."}
+(c) Out of the richness metrics, the ratio of plants to pollinators showed a strong, negative relationship with *n~D~*.
+In both plots, partial residuals correspond to the partial working residuals of the invasion status in our generalised linear mixed model."}
 
@@
 	fer_theme +
-	xlab(expression(n[D])) +
-	ylab("density distribution") +
+	xlab(expression(paste("driver-node density (", n[D], ")"))) +
+	ylab("density") +
 	theme(axis.title.y = element_text(vjust = 1, margin = margin(1,-3,1,1, unit = "lines")))
@@
 	fer_theme +
-	scale_x_continuous(name = "ratio plant / pollinators") +
+	scale_x_continuous(name = "ratio of plants to pollinators") +
 	scale_y_continuous(name = expression(paste(n[D], " partial residuals"))) +
@@
 
-When exploring the effect of network structure itself, we observed that the driver node density $n_D$ of empirical networks was, in general, not significantly different to the manageability of network randomisations that maintained the degree of individual species (Figure 4).
-However, we found that the $n_D$ of empirical networks was significantly larger to that of randomisations that maintained the network structure but that differed only on the direction of the asymmetries.
+When exploring the effect of network structure itself, we observed that the driver-node density $n_D$ of empirical networks was, in general, not significantly different to the manageability of network randomisations that maintained the degree of individual species (Figure 4).
+However, we found that the $n_D$ of empirical networks was significantly larger than that of randomisations that maintained the network structure but that differed only on the direction of the asymmetries.
 
-```{r fig_randomisations, echo = FALSE, warning = FALSE, message = FALSE, fig.width = 3.245, fig.height = 1.7, fig.cap = "**The driver node density _n~D~_ of empirical networks compared to network randomisations**.
+```{r fig_randomisations, echo = FALSE, warning = FALSE, message = FALSE, fig.width = 3.245, fig.height = 1.7, fig.cap = "**The driver-node density _n~D~_ of empirical networks compared to network randomisations**.
 For each randomisation approach, we show the standarised rank of the empirical value compared to the set of randomisations.
 A scaled mean rank—akin to a p-value— less than 0.025 or greater than 0.975 (the areas shaded in light grey) suggests a significant difference between the empirical network and its randomisations.
-The empirical _n~D~_ is much smaller than that of network randomisations in which the direction of asymmetries has been randomised.
+The empirical _n~D~_ is much larger than that of network randomisations in which the direction of asymmetries has been randomised.
 In contrast, the manageability of networks in which the species degrees were randomly shuffled were not significantly different.
@@
     labels = rev(c("random degree", # "maintain degree\nrandomise strength", 
-    							 "random\nassymetry")),
+    							 "random\nasymmetry")),
     # breaks = c(#"r00_samp", #"swsh_both",
@@
 Invasive species were classified as superior nodes *and* driver nodes in every single network they were present; that is, they always had the highest relative *f~S~* and *f~D~* (Figure 5a). 
-The model results suggest that this differences among invasive and native species are underpinned, not by any intrinsic property of the invasive species but instead, by species properties that apply to invasive and native species alike (Table 1).
+The model results suggest that these differences between invasive and native species are not underpinned by any intrinsic property of the invasive species, instead, they are due to species properties that apply to invasive and native species alike (Table 1).
 Specifically, we found that a species is more likely to be classified as a superior node if it had a large species strength (the sum of the dependences of other species on the species of interest). 
@@
 
-```{r fig-dependency-fs, echo = FALSE, warning = FALSE, message = FALSE, fig.width = 3.245, fig.height = 3.2, fig.cap = "**Relatiosnships between _f~S~_ and _f~D~_ and species' structural properties**.
+```{r fig-dependency-fs, echo = FALSE, warning = FALSE, message = FALSE, fig.width = 3.245, fig.height = 3.2, fig.cap = "**Relationships between _f~S~_ and _f~D~_ and species structural properties**.
 (a) In all networks were they were present, invasive species were classified as superior (_f~S~_) and driver (_f~D~_) nodes in all possible control configurations.
 (b) Species strength (the sum of the dependences of other species on the species of interest) is the single most important factor explaining _f~S~_.
-Visitation strength and  degree also had an important albeit comparatively smaller effect (dashed lines correspond to one standard deviation on these factors).
+Visitation strength and degree also had an important albeit comparatively smaller effect (dashed lines correspond to one standard deviation of these factors).
 Invasive species are depicted as circles."}
@@
   geom_line(aes(x = de, y = p, linetype = type, colour = type, group = interaction(n, vi)), show.legend = F, size = 0.5) +
-  scale_x_log10(expand = c(0,0)) +
+  scale_x_log10(expand = c(0,0), breaks = c(0.01, 0.1, 1, 10, 100)) +
    geom_point(data = dplyr::arrange(data_pp, invasive) %>% dplyr::filter(invasive == T), aes(x = de_s, y = pred_ri, fill = invasive, shape = guild, size = invasive), show.legend = F) +
@@
 	dplyr::select(invasive, f_s, f_d) %>%
+	dplyr::mutate(invasive = plyr::mapvalues(invasive, c(F,T), c("native", "invasive"))) %>%
 	reshape2::melt(measure.vars = c("f_s", "f_d")) %>%
-	ggplot(aes(y = value, x = invasive, colour = variable)) + 
+	ggplot(aes(y = value, x = variable)) + 
 	geom_boxplot(size = 0.3, outlier.shape = 21, outlier.size = 1)  +
@@
   ylab("proportion") + 
-	scale_x_discrete(name = "", labels = c("native", "invasive")) +
+	scale_x_discrete(labels = parse(text = c("f[S]", "f[D]")), name = "") +
+	# scale_x_discrete(name = "", labels = c("native", "invasive")) +
   fer_theme +
@@
   			legend.justification = c(1,0),
-				plot.margin = grid::unit(c(2, 1, 0, 0), "mm"), 
+				plot.margin = grid::unit(c(-1, 1, -3, 0), "mm"), 
 				# panel.grid.minor.x = element_blank(),
-				panel.grid.minor.y = element_blank()) +
+				panel.grid.minor.y = element_blank(),
+				strip.text = element_text(size = 8, hjust = 1, vjust = -1)) +
 	scale_color_manual(values = RColorBrewer::brewer.pal(5, "Greys")[c(5,4)],
 										 name = "", 
-										 labels = c(expression(f[S]), expression(f[D])))
+										 labels = c(expression(f[S]), expression(f[D]))) +
+	facet_grid(~invasive)
 
@@
 Moreover, these mutual dependences seem to be importantly constrained by the concerted effects of both, the patterns of species richness at each trophic guild, and the species' degree distribution [@Melian2002; @Bluthgen2007].
-Indeed, the difference between the driver node density (*n~D~*) of our empirical networks and that of randomisations depended strongly on the evaluated null model. 
+Indeed, the difference between the driver-node density (*n~D~*) of our empirical networks and that of randomisations depended strongly on the evaluated null model. 
 While the empirical *n~D~* was indistinguishable from that of networks with a random structure that maintained the degree or strength of each species in the community, it was much larger than that of randomisations in which the directed network was unchanged but where the observed patterns of dependence were broken.
@@
 Our first index, the frequency with which a species is classified as a driver node (*f~D~*) provides an indication of the likelihood the species is part of the set of species that need to be intervened in order to control of *all* species in the community.
-The driver node concept has received considerable attention in the structural control literature and indeed shows substantial potential to provide useful ecological insight. 
+The driver-node concept has received considerable attention in the structural control literature and indeed shows substantial potential to provide useful ecological insight. 
 Nevertheless, we anticipate two caveats that hinder its direct utility for management applications.

### 2017-02-28 paper/draft_2.Rmd
Update discussion
Search for (FDO XXX) to find sections that might require attention

@@
 (b) Species strength (the sum of the dependences of other species on the species of interest) is the single most important factor explaining _f~S~_.
-Visitation strength and degree also had an important albeit comparatively smaller effect (dashed lines correspond to one standard deviation of these factors).
+Visitation strength and degree also had an important albeit comparatively smaller effect (dashed lines correspond to $\\pm$ one standard deviation of these factors).
 Invasive species are depicted as circles."}
@@
 		x %>%
-  magrittr::set_names(c(" ", "est.", "var", "mod.", "imp.", "C.I.")) %>%
+			dplyr::select(factor, imp., est., var, mod., C.I.) %>%
+			magrittr::set_names(c(" ", "imp.", "est.", "var", "mod.",  "C.I.")) %>%
 			dplyr::select(-var, -mod.)
@@
 coef_tables %>%
-	xtable::xtableList(caption = "\\textbf{Factors determining species importance}.
+	xtable::xtableList(caption = "\\textbf{Factors explaining species importance}.
 Factor estimates correspond to the average over all models that accounted for 95\\% of the AIC evidence.
@@
 
-Contrary to our initial hypothesis, we found some evidence that invaded communities might be easier to manage than uninvaded ones. 
-Our results reveal, however, that this effect is comparatively small and the structural differences among different networks are more importantly related to potential differences in our ability to alter the state of the community.
-Despite the small effect of invasion status at a network level, we found that invasive mutualists occupy a particularly dominant role in their communities. 
-Not only changes on their abundance have the potential to propagate broadly trough the community and in turn, affect the abundances of many other species, but they are also indispensable to fully control the plant-pollinator network.
+Contrary to our initial hypothesis, we found some evidence that invaded communities might be easier to manage than uninvaded ones from a control-theoretic perspective. 
+Our results reveal, however, that this effect is comparatively small and the structural differences among different networks are more strongly related to potential differences in our ability to alter the state of the community via external interventions.
+Despite the small effect of invasion status at a network level, we found that invasive mutualists occupy a particularly dominant role in their communities for two reasons. 
+(FDO revision) First, as species with a high *f~S~*, changes on their abundance have the potential to propagate broadly through the community and in turn, affect the abundances of many other species. 
+Second, as species with a high *f~D~*, they are also indispensable to fully control the plant-pollinator network. 
 At a community level, we demonstrate that the manageability of mutualistic networks is strongly governed by the asymmetric nature of mutual dependences—which constitute the foundations of the structure and stability of mutualistic networks [@Memmott2004; @Vazquez2004; @Bascompte2006; @Lever2014; @Astegiano2015].
-Moreover, these mutual dependences seem to be importantly constrained by the concerted effects of both, the patterns of species richness at each trophic guild, and the species' degree distribution [@Melian2002; @Bluthgen2007].
-Indeed, the difference between the driver-node density (*n~D~*) of our empirical networks and that of randomisations depended strongly on the evaluated null model. 
-While the empirical *n~D~* was indistinguishable from that of networks with a random structure that maintained the degree or strength of each species in the community, it was much larger than that of randomisations in which the directed network was unchanged but where the observed patterns of dependence were broken.
+Moreover, these mutual dependences seem to be constrained by the effects of both the patterns of species richness at each trophic guild and a network's degree distribution [@Melian2002; @Bluthgen2007].
+Indeed, the difference between the driver-node density (*n~D~*) of our empirical networks and that of randomisations depended strongly on the null model's randomisation approach. 
+While the empirical *n~D~* was indistinguishable from that of networks with a random structure that maintained the degree of each species in the community, it was larger than that of randomisations in which the directed network was unchanged but where the observed patterns of dependence were broken.
 
@@
 Invasive plants, just like any other mutualist in our data set, tend to be classified as a superior node with a frequency (*f~S~*) proportional to the degree to which their interaction partners are collectively more dependent on them than the other way around.
-Previous studies have found that super-generalists, like invasive species, play a central role in their networks [@Vila2009; @Palacio2016].
+Previous studies have found that supergeneralists, like invasive species, play a central role in their networks [@Vila2009; @Palacio2016].
 Our results take this one step further and indicate that dependence strength, rather than generalism or other metrics of centrality, is the factor that best explains the cascading effects a species could trigger on its community.
@@
 Because of the ability that our approach has to infer the magnitude of the effects that each species has on others in the community, it is tantalising to use it to select promising candidates for management interventions.
-The two indices we employed to characterise a species provide two complementary pieces of information. 
-Our first index, the frequency with which a species is classified as a driver node (*f~D~*) provides an indication of the likelihood the species is part of the set of species that need to be intervened in order to control of *all* species in the community.
-The driver-node concept has received considerable attention in the structural control literature and indeed shows substantial potential to provide useful ecological insight. 
+To this end, the two indices we employed to characterise a species provide two complementary pieces of information. 
+(FDO revise grammar) Our first index, the frequency with which a species is classified as a driver node (*f~D~*) provides an indication of the likelihood that a species is part of the set of species that need to be manipulated in order to control of *all* species in the community.
+The driver-node concept has received considerable attention in the structural-control literature and indeed shows substantial potential to provide useful ecological insight. 
 Nevertheless, we anticipate two caveats that hinder its direct utility for management applications.
-First, unlike other types of complex systems, fully controlling an ecological community is realistically out of reach for all but the most simple ones; either because of the number of required interventions or the difficulties of their implementation [@Motter2015].
-For instance, our results suggest that full control of the pollination network would require direct interventions on 40-90% of the species.
+First, unlike some other types of complex systems, fully controlling an ecological community is almost certainly out of reach for all but the simplest ones, due to either the number of required interventions or the difficulties of their implementation [@Motter2015].
+For instance, our results suggest that full control of the pollination networks would require direct interventions on 40-90% of the species.
 Second, @Ruths2014 established that driver nodes arise due to distinct mechanisms and therefore species with markedly different network metrics can be driver nodes in their community (Supporting information S2).
 
-Our second index *f~S~* is, however, directly related to the likelihood a species has to affect the abundance of another species in all of the considered control strategies. 
+Our second index *f~S~* is, however, directly related to the likelihood a species affects the abundance of another species in all of the control strategies considered. 
 Importantly, this is irrespective of whether controlling the entire network is desired/feasible or not. 
-In fact, because superior nodes are invariantly at the beginning of a matching link, species with a high *f~S~* are more likely to be the subjects of management interventions when controlling the abundances of a target set of species—and not the entire network—is desired [@Gao2014].
-An important advantage is that the target set of species does not has to be the same set to which interventions are applied. 
+In fact, because superior nodes are invariably at the beginning of a matched link, species with a high *f~S~* are more likely to be the subjects of management interventions when controlling the abundances of a target set of species—as opposed to the entire network—is desired [@Gao2014].
+An important advantage here is that the target set of species does not have to be the same set to which interventions are applied. 
 For instance, despite inconsistent outcomes in practice [@Suding2004; @Rodewald2015; @Smith2016], our results suggest that current restoration approaches that focus on direct eradication of invasive species might indeed be an effective way to modify ecosystem state.
 Nevertheless, our results also indicate that removals must be exercised with caution. 
-Not only it is hard to predict the direction in which the system will change, but also, invaded communities tend to be highly dependent on invaders and therefore acutely vulnerable to their eradication [@Traveset2013; @Albrecht2014].
+Not only it is hard to predict the direction in which the system will change, but invaded communities also tend to be highly dependent on invaders and therefore acutely vulnerable to their eradication [@Traveset2013; @Albrecht2014].
 
-Although *f~S~*, in particular, is promising for identifying species priorities, our approach is different to previous attempts to quantify species importance. 
+(FDO check) Despite the apparent similarities, our approach is different to previous attempts to quantify species importance. 
 Existing metrics usually harness species features like centrality, position, co-extinction or uniqueness, to infer their effect on other species [@Allesina2004; @Jordan2006; @Jordan2009; @Lai2012]. 
-Contrastingly, our control-based approach, by definition, tackles that question directly.
-Although relatively simple to calculate, it has been shown that classic species-level network metrics do not necessarily reveal the best set of species to manage [@Eklof2013; @McDonald-Madden2016].
-Our approach, however, is not based on a single structural metric but acknowledges the existence of multiple management strategies; some more optimal than others in specific contexts. 
-Our, and other flexible approaches that take a network-wide approach might prove more useful to guide ecosystem management if we want to go beyond using network metrics to minimise topological species loss [@McDonald-Madden2016].
+In contrast, our control-based approach tackles that question directly.
+Although they are relatively simple to calculate, it has been shown that classic species-level network metrics do not necessarily reveal the best set of species to manage [@Eklof2013; @McDonald-Madden2016].
+Our approach, however, is not based on a single structural metric but instead acknowledges the existence of multiple management strategies.
+(FDO check) By allowing for the fact that some are more optimal than others in different contexts, control theory implicitly highlights that management decisions should be based on a single technique.
+As such, ours and other flexible approaches that take a network-wide approach might prove more useful to guide ecosystem management if we want to go beyond using network metrics to minimise topological species loss [@McDonald-Madden2016].
 
 Despite its conceptual advantages, our approach still relies on knowledge of the network of interaction between species. 
-We do not argue that management decisions should be based on a single technique. 
-Nevertheless, our results and previous basic research show that as long as the proportion of sampled links is enough to provide indication of the actual degree distribution (and in turn the species dependences), *n~D~*, *f~S~* and *f~D~* can still provide a simple, straightforward, and theoretically-informed indication of the degree to which the community is self-regulated and therefore how difficult it might be to modify its state in one way or another using some of the species that integrate it [Supporting Information S5; @Nepusz2012].
+Nevertheless, our results and previous basic research show that, as long as the proportion of sampled links is enough to provide indication of the actual degree distribution (and in turn the species dependences), *n~D~*, *f~S~* and *f~D~* can still provide a simple, straightforward, and theoretically informed indication of the degree to which the community is self regulated and therefore how difficult it might be to modify its state in one way or another using some of its constituent species [Supporting Information S5; @Nepusz2012].
 
-In this study, we illustrate how a control-theoretic approach can be adopted in network ecology to evaluate the effect of invasions and another kind of perturbations. 
-Although, because of the degree constraints imposed by bipartite networks, our pollination specific results might not be relevant to other ecological systems, the approach we propose is applicable wherever species abundances are influenced by their interactions.
-Exciting open questions lie ahead: how to design the precise "control signals" to reach a desired ecosystem state or conservation outcome? 
+In this study, we illustrate how a control-theoretic approach can be better adopted in network ecology to evaluate the effect of invasions and other kinds of perturbations. 
+Although our pollination specific results might not be directly translatable to other ecological systems because of the degree constrains imposed by bipartite networks, the approach we propose is applicable wherever species abundances are influenced by their interactions.
+Exciting open questions lie ahead. How to design the precise "control signals" to reach a desired ecosystem state or conservation outcome? 
 What are the implications of assuming linear species dynamics?
-How important is to include several interaction types for our understanding of manageability and species importance?
+How important it is to include several interaction types for our understanding of manageability and species importance?
 What are the implications for species coexistence? 
 Which are the trade-offs between persistence at the species and the community level? 
-
-Answering these questions might require its evaluation on different ecological systems, an explicit integration of control theory with numerical models of species densities [@Cornelius2013; @Gibson2016], and experimental tests on simple communities.
-Nevertheless, the rewards are encouraging. 
-Not only from a purely ecological perspective, but also from a conservation perspective, where an integrated approach can shift our focus beyond the identification of ideal targets for intervention to design informed interventions that legitimately achieve restoration goals.
+Answering each of these questions might require its evaluation in different ecological systems, an explicit integration of control theory with numerical models of species densities [@Cornelius2013; @Gibson2016], and experimental tests on simple communities.
+Nevertheless, the potential rewards are encouraging from both an ecological perspective as well as a conservation perspective, where an integrated approach can shift our focus beyond the identification of ideal targets for intervention to the design of informed interventions that legitimately achieve restoration goals.
 
@@
 Matching weight
-  ~ The sum of the weights of all matched links in a particular matching.
+  ~ The sum of the weights of all matched links in a matching.
 
 Maximal cardinality matching
-  ~ A matching with the largest possible matching size. In unweighted networks, all maximal cardinality matchings are also maximum matchings.
+  ~ A matching with the largest possible matching size. In unweighted/binary networks, all maximal cardinality matchings are also maximum matchings.
 
 Maximum matching
-  ~ A matching with the largest possible matching size *and* matching weight.
+  ~ A matching with the largest possible matching size *and* largest possible matching weight.
 
 Superior node
-  ~ The node at the start of a matched link. From the control perspective, superior nodes make up the chain(s) that propagate the control signal(s) through the network.
+  ~ The node at the start of a matched link. From the control perspective, superior nodes make up the chains that propagate the control signals through the network.
 

### 2017-02-28 paper/draft_2.Rmd
Update abstract and metadata

@@
 
-* **Number of words:** 183 abstract; approx. 5460 main text.
+* **Number of words:** 160 abstract; approx. 5600 main text.
 
@@
 
-It is generally unknown how the disruptions caused by perturbations like biotic invasions affect our ability to manage ecological communities.
 Here, we capitalise on recent advances in control theory to assess the "manageability" of ten pairs of uninvaded and invaded plant-pollinator communities. 
-We found that the manageability of the studied networks is strongly determined by the relative richness of plants and pollinators, which in turns constraint the species' degree distribution.
-Furthermore, we characterise species potential to be candidates for management interventions using metrics that explore the entire space of control strategies.
-Specifically, we use the extent to which species (i) are necessary to steer the state of the community,  and (ii) are able to affect the abundance of other species.
-Remarkably, we found that invasive plants have a dominant position in every community in which they were found and that this dominance is underpinned by the high asymmetry in the dependence of their interaction partners.
-Our results highlight the advantages of using a control theoretic framework to answer ecological questions, at the same time it provides insight into the design of informed management interventions.
+We found that the manageability of the networks is most strongly determined by the relative richness of plants to pollinators, which in turn constraints the species' degree distribution. 
+We also characterise species' potential to be candidates for management interventions by exploring the entire space of control strategies. 
+Specifically, we determine the extent to which species (i) are necessary to steer the state of the community and (ii) are able to affect the abundance of other species. 
+We found that invasive plants have a dominant position in every community in which they were found and that this dominance is underpinned by the high asymmetry in the dependence of their interaction partners.
+Our results highlight the advantages of using a control theoretic framework to explore ecological questions as well as provide insight into the design of informed management interventions.
 

### 2017-02-28 paper/supp_info_2.Rmd
Update supporting information

@@
 
-Our approach to find the minumum number of driver nodes relies on finding maximum matchings and maximum cardinality matchings.
-
+Our approach to find the minumum number of driver nodes relies on finding maximum matchings and maximal cardinality matchings. 
 We start with a directed network in which the direction of the link represents the direction of control (Figure \@ref(fig:fig-direction-of-control)a). 
@@
 This information can then be mapped back to the original representation to identify the control paths and the driver nodes in the network (Figure \@ref(fig:fig-direction-of-control)c). 
-Figure \@ref(fig:fig-direction-of-control)d, e, and f ilustrate this approach for a network with bidirectional links.
+Figure \@ref(fig:fig-direction-of-control)d--f illustrate this approach for a network with bidirectional links.
 
@@
 
-The algorithm implemented in `max_bipartite_matching`, however, is only able to find **one** of the possibly many maximum matchings in a network. 
-Though one maximum matching is enough to calculate *n~D~* and hence to provide indication of a communitie's manageability, it is not sufficient to estimate the role of individual species. 
+The algorithm implemented in `max_bipartite_matching`, however, is only able to find **one** of possibly many maximum matchings in a network. 
+Though one maximum matching is enough to calculate *n~D~* and hence to provide indication of the manageability of a community, it is not sufficient to estimate the role of individual species. 
 To do that, we need to calculate all possible maximum matchings (or, equivalently, all maximal cardinality matchings in weighted networks like ours). 
 To do this, we again start from the alternative bipartite representation in Figure \@ref(fig:fig-direction-of-control)b and assign an identity to each of the links in the network (shown as numbers in Figure \@ref(fig:fig-finding-all-matchings)a).
-We will call this bipartite representation *B*. 
-We then construct the line graph of the alternative bipartite representation *L(B)* (Figure \@ref(fig:fig-finding-all-matchings)b). 
-Each node in *L(B)* represents a link in *B* and these are connected to each other only if and only if they share a common node in *B*. 
-We then calculate the complement graph of *L(B)* and identify all the maximal cliques (Figure \@ref(fig:fig-finding-all-matchings)c). 
-Here some extra definitions are neccessary. 
-First, the complement of *L(B)*, *H*, is a graph with the same nodes as *L(B)* but that has a link between two given nodes if and only if there is not a link in *L(B)*. 
-Second, a clique is a subset of nodes such that any two of them are linked. 
-Lastly, a maximum clique is a clique such that there are no cliques with more nodes [@Gutin2013]. 
-In this example, there are two maximum cliques: that one formed by 1, 3 and 5, and the one formed by 2, 3 and 5. 
-The final step is then to map these cliques into the original network to obtain all possible maximum cardinality matchings as shown in Figure 1 in the main text.
-
-```{r fig-finding-all-matchings, echo = F, message = F, warning = F, fig.width = 6.2, fig.height = 1.8, results = "hide", fig.cap = "**Finding all possible maximum cardinality matchings**.
+We will call this bipartite representation *P*. 
+We then construct the line graph of the alternative bipartite representation *L(P)* (Figure \@ref(fig:fig-finding-all-matchings)b). 
+Each node in *L(P)* represents a link in *P* and these are connected to each other only if and only if they share a common node in *P*. 
+We then calculate *H*, the complement graph of *L(P)* and identify all of its maximal cliques (Figure \@ref(fig:fig-finding-all-matchings)c). 
+Here some extra definitions are necessary. 
+First, *H* is a graph with the same nodes as *L(P)* but that has a link between two nodes if and only if there is not a link in *L(P)*. 
+Second, a clique is a subset of nodes such that all pairs of them are linked. 
+Lastly, a maximal clique is a clique such that there are no cliques composed of more nodes [@Gutin2013]. 
+In this example, there are two maximal cliques: the one formed by 1, 3 and 5, and the one formed by 2, 3 and 5. 
+The final step is then to map these cliques onto the original network to obtain all possible maximal cardinality matchings as shown in Figure 1 in the main text.
+
+```{r fig-finding-all-matchings, echo = F, message = F, warning = F, fig.width = 6.2, fig.height = 1.8, results = "hide", fig.cap = "**Finding all possible maximal cardinality matchings**.
 (a) Alternative bipartite representation of the directed network in Figure \\@ref(fig:fig-direction-of-control)a.
@@
 (c) Complement of the network in b.
-The two maximum cliques are shown in red and blue."}
+The two maximal cliques are shown in red and blue."}
 layout(matrix(c(1,2,3,4, 5, 6), 2, 3, byrow = TRUE),
@@
 plot.new()
-text(0.5, 0.5, expression(paste(italic(B), ": bipartite representation")), adj = c(0.5,0.75))
+text(0.5, 0.5, expression(paste(italic(P), ": bipartite representation")), adj = c(0.5,0.75))
 
 plot.new()
-text(0.5, 0.5, expression(paste(italic(L(B)), ": line graph of ", italic(B))), adj = c(0.5,0.75))
+text(0.5, 0.5, expression(paste(italic(L(P)), ": line graph of ", italic(P))), adj = c(0.5,0.75))
 
 plot.new()
-text(0.5, 0.5, expression(paste(italic(H), ": complement of ", italic(L(B)))) , adj = c(0.5,0.75))
-```
-
-In the main text, we show all maximum cardinality matchings for a simple example network. 
-To further ilustrate our methodology, here we also show the approach for the smallest of our empirical networks, the uninvaded network at site 10 (Table S1; Figure \@ref(fig:fig-SA-exp)). 
-The largest component of this network is composed of 16 species of which 2 are non-invasive plants and the rest are pollinators. 
-The one-to-one relationship between matched and superior nodes implies that in order to achieve full network controllability, most pollinators would be unmatched, and hence driver species that require external intervention.
-At the same time, both plants in the community, *Heracleum sphpndylum* and *Rubus fructicosus*, and one of the pollinators, *Orthotylus/Lygocorus*, tend to be classified as superior nodes.
+text(0.5, 0.5, expression(paste(italic(H), ": complement of ", italic(L(P)))) , adj = c(0.5,0.75))
+```
+
+In the main text, we show all maximal cardinality matchings for a simple example network. 
+To further ilustrate our methodology here, we also show the approach for the smallest of our empirical networks, the uninvaded network at site 10 (Table S1; Figure \@ref(fig:fig-SA-exp)). 
+The largest component of this network is composed of 16 species of which two are non-invasive plants and the other 14 are pollinators. 
+The one-to-one relationship between matched and superior nodes implies that in order to achieve full network controllability, most pollinators would be unmatched, and hence are classified as driver nodes that require external intervention.
+At the same time, both plants in the community, *Heracleum sphondylum* and *Rubus fructicosus*, and one of the pollinators, *Orthotylus/Lygocorus*, tend to be classified as superior nodes.
 
@@
 (a) The initial visitation network.
-(b) The directed network in which the direction of control is determined based on the mutual dependences and assymetries.
-(c) One of the possible maximum matchings calculated using the procedures illustrated in the Figures \\@ref(fig:fig-direction-of-control) and \\@ref(fig:ig-finding-all-matchings)."}
+(b) The directed network in which the direction of control is determined based on the mutual dependences and asymmetries.
+(c) One of the possible maximum matchings calculated using the procedures illustrated in the Figures \\@ref(fig:fig-direction-of-control) and \\@ref(fig:fig-finding-all-matchings).
+Legend as in Figure \\@ref(fig:fig-direction-of-control)"}
 par(mfrow=c(2,2), mar=c(0,0,0,0))
@@
 
-@Ruths2014 proposed a heuristic-based method to provide insight of what might be required to control a network.
+@Ruths2014 proposed a heuristic-based method to provide insight into what might be required to control a network.
 The method is based on the idea that the reasons behind a node being classified as a driver node can be precisely identified, and that the relative contribution of these reasons can be used to characterise the control profile of the network.
-Specifically, nodes can be deemed to be driver nodes for three reasons:
-
-1. **Because it is a source node**. Source nodes are nodes that exclusively have outgoing links. Therefore, other nodes cannot control it, but instead, it must be externally controlled. 
+Specifically, nodes can be deemed to be driver nodes for any three reasons:
+
+1. **Because it is a source node**. Source nodes are nodes that exclusively have outgoing links. Therefore, other nodes cannot control it and it must be externally controlled instead. 
 2. **Because of an external dilation**. Dilations occur whenever a control signal needs to branch out in order to reach all nodes in a network. 
@@
 The source node *a* branches out into nine paths, but it can only control one of them. 
-We say then, that the sink nodes *d* to *k* become driver nodes because of an external dilation.
+We say then that the sink nodes *d* to *k* become driver nodes because of an external dilation.
 3. **Because of an internal dilation**. The remaining dilations (those that do not arise from a surplus of sink nodes) are called internal dilations. 
@@
 
-Mathematically, the number of driver nodes $N_D$ is the sum of the number of source nodes, the number of external dilation points, and the number of internal dilation points, $N_D = N_s + N_e + N_i$. 
-A network can then be characterised by the relative proportion of the three kind of controls $$\eta_s + \eta_e + \eta_i = 1,$$ where $\eta_s = N_s/N_D$, $\eta_e = N_e/N_D$, and $\eta_i = N_i/N_D$. 
+Mathematically, the number of driver nodes *D* is the sum of the number of source nodes, the number of external dilation points, and the number of internal dilation points, $D = N_s + N_e + N_i$. 
+A network can then be characterised by the relative proportion of the three kind of controls $$\eta_s + \eta_e + \eta_i = 1,$$ where $\eta_s = N_s/D$, $\eta_e = N_e/D$, and $\eta_i = N_i/D$. 
 These terms can be calculated with relative ease.
-$N_D$ can be calculated using a maximum matching algorithm. 
+$D$ can be calculated using a maximum matching algorithm. 
 $N_s$ can be calculated by inspecting the network's degree distribution.
@@
 
-Applying this framework to our networks directed by the asymmetry we identify that they are all external dilation dominated (Figure \@ref(fig:fig-control-profiles)).
+Upon applying this framework to our networks with directions determined by asymmetry we, identify that they are all external dilation dominated (Figure \@ref(fig:fig-control-profiles)).
 @Ruths2014 explains that "external-dilation-dominated networks exhibited strong aspects of top-down control". 
@@
 For example, an increase in the abundance of *Heracleum sphondylum* (Figure \@ref(fig:fig-SA-exp)) is likely to induce an increase in the abundance of the pollinators it interacts with.
-Therefore it can be expected that in order to fully control the network it is not sufficient to apply interventions to the source nodes.
-
-The control profile of our pollination networks provides additional justification to our decision to determine the importance of a species, not only by virtue of $f_D$, but also by $f_S$.
-Many species that act like control sinks in our network, will be classified as a driver node, because they are necessary to *fully* control the dynamics of the community, as opposed to playing a central role influencing the abundance of other species in the community.
-
-Using this approach also highlights the importance of appropiately selecting the direction of control (See Section 6). 
+Therefore it can be expected that in order to fully control the network it is not sufficient to just apply interventions to the source nodes.
+
+The control profile of our pollination networks provides additional justification for our decision to determine the importance of a species not only by its $f_D$ but also with $f_S$.
+Many species that act like control sinks in our network will be classified as a driver node because they are necessary to *fully* control the dynamics of the community as opposed to playing a central role in influencing the abundance of other species in the community.
+
+Using th @Ruths2014 approach also highlights the importance of appropiately selecting the direction of control (see Section 6). 
 A network with bidirectional links weighted by the mutual dependences would have zero source nodes and zero sink nodes. 
@@
 ```{r fig-control-profiles, echo = F, message = F, warning = F, fig.width = 6.2, fig.height = 2.6, results = "hide", fig.cap= "**Control profiles of the studied networks**.
-Following @Ruths2014, profiles are shown in a ternary plot in which the cornders correspond to points (1, 0, 0), (0, 1, 0), and (0, 0, 1) in the three-dimensional $(\\eta_s, \\eta_e, \\eta_i)$ space such that $\\eta_s + \\eta_e + \\eta_i = 1$, and $\\eta_s, \\eta_e$, and $\\eta_i > 0$."}
+Following @Ruths2014, profiles are shown in a ternary plot in which the corners correspond to points (1, 0, 0), (0, 1, 0), and (0, 0, 1) in the three-dimensional $(\\eta_s, \\eta_e, \\eta_i)$ space such that $\\eta_s + \\eta_e + \\eta_i = 1$, and $\\eta_s, \\eta_e$, and $\\eta_i > 0$."}
 n_driver <- meta %>%
@@
 
-The networks studied had species richness ranging between `r min(net_prop$n_s_t)` and `r max(net_prop$n_s_t)` (`r min(net_prop$n_sp)`-`r max(net_prop$n_sp)` when considering only the largest component in each network).
-As shown by the network asymmetry *AS* [@Bluthgen2007] the networks overall had a low ratio of plants to pollinators. 
-Furthermore, networks had relatively low levels of nestedness [when measured using the quantitative version of the NODF index; @Almeida-Neto2011]. Details for each network can be found in Table S1.
+The networks studied had species richness ranging between `r min(net_prop$n_s_t)` and `r max(net_prop$n_s_t)` (`r min(net_prop$n_sp)`--`r max(net_prop$n_sp)` when considering only the largest component in each network).
+As shown by the network asymmetry *AS* [@Bluthgen2007], the networks had a low ratio of plants to pollinators overall. 
+Furthermore, the networks had relatively low levels of nestedness [when measured using the quantitative version of the NODF index; @Almeida-Neto2011].
+Details for each network can be found in Table S1.
 
@@
 All properties, with the exception of the networks' total species richness ($R$), correspond to the network's largest component.
-We show the number of species ($n_s$), the number of plants ($n_p$), the number of pollinators ($n_a$), the network connectance ($c$), the network assymetry ($AS$), and the network nestedness (NODF index).
+We show the number of species ($n_s$), the number of plants ($n_p$), the number of pollinators ($n_a$), the network connectance ($c$), the network asymmetry ($AS$), and the network nestedness (NODF index).
 British networks were assembled by Lopezaraiza-Mikel et al.
@@
 We did this by comparing *(i)* the manageability of the community and *(ii)* the percentage of interactions that maintained the direction of dependence. 
-To do that, we used data collected by @Ballantyne2015 from a low diversity pollination community at a dry lowland heathland in Dorset, UK  (50° 43.7'N 2° 07.2'W). 
+To do this, we used data collected by @Ballantyne2015 from a low diversity pollination community at a dry lowland heathland in Dorset, UK  (50° 43.7'N 2° 07.2'W). 
 First, deposition networks were quantified using the mean single visit deposition---the number of conspecific pollen grains effectively deposited on a virgin stigma during a single visit by a particular animal [@NeEman2010; @King2013; @Ballantyne2015].
-Second, visitation networks were constructed counting the visits to flowers during Single Visit Depositions. 
+Second, visitation networks were constructed by counting the visits to flowers during Single Visit Depositions. 
 Finally, pollinator importance networks were constructed as the product of pollinator efficiency and visit frequency.
@@
 ```{r fig-visitation-vs-deposition-vs-importance, echo = F, message = F, warning = F, fig.width = 6.2, fig.height = 4, results = "hide", fig.cap= "**Distribution of interaction weights for the pollen deposition, visitation and pollinator importance networks**.
-Note that the *x* axis in the density plots have been log-transformed."}
+Note that the *x* axes in the density plots have been log-transformed."}
 
@@
       xlab("link weight") + 
-      ylab("density") +
+      ylab("prob. density") +
       ggtitle(x$net_name_f[1]) +
@@
 
-At a network scale, despite marked differences in the distribution of weights of the three networks (Figure \@ref(fig:fig-visitation-vs-deposition-vs-importance)), the driver node density *n~D~* was consistent among the three different approaches (`r 1-round(n_driver$n_driver[n_driver$net_name == "bal_eff"], digits = 2)` for deposition, `r 1-round(n_driver$n_driver[n_driver$net_name == "bal_vis"], digits = 2)` for the visitation, and `r 1-round(n_driver$n_driver[n_driver$net_name == "bal_imp"], digits = 2)` for the pollinator importance network).
-
-The choice of weighting used can also have an impact on at the species level.
-Therefore we calculated *f~D~* and *f~S~* (the frequency at which each species is classified as a driver or superior node, respectively, within the set of all possible matchings in a network) and calculated it's correlation among all three weighting schemes.
+At a network scale (Figure \@ref(fig:fig-visitation-vs-deposition-vs-importance)), the driver-node density *n~D~* was consistent among the three weighting schemes (`r 1-round(n_driver$n_driver[n_driver$net_name == "bal_eff"], digits = 2)` for deposition, `r 1-round(n_driver$n_driver[n_driver$net_name == "bal_vis"], digits = 2)` for the visitation, and `r 1-round(n_driver$n_driver[n_driver$net_name == "bal_imp"], digits = 2)` for the pollinator-importance network, respectively).
+The choice of weighting can also have an impact on at the species level.
+Therefore we calculated *f~D~* and *f~S~* (the frequency at which each species is classified as a driver or superior node, respectively, within the set of all possible maximal cardinality matchings in a network) and calculated it's correlation among all three weighting schemes.
 Although visitation and deposition produce moderately different results, we found a very strong agreement between the order produced by visitation and importance (Table S2). 
@@
 
-Altogether, evidence supports the idea that visitation is a suitable metric to estimate the mutual dependence of species pairs.
+Altogether, the evidence supports the idea that visitation is a suitable metric to estimate the mutual dependence of species pairs.
 First, it is directly related to pollinator foraging.
-Second, it produces results consistent, at least within our controllability framework, with plant reproductive success (as estimated by the importance metric).
+Second, it produces results within our controllability framework that are consistent with plant reproductive success (as estimated by the importance metric).
 
@@
 Our approach is fundamentaly based on the network structure. 
-Often, the majority of the interactions that determine this structure are weak, which in our networks means that most interactions are formed by a small number of observed pollination visits, and therefore those weak intercations are less conspicuous in the field than strong ones.
-To strengthen the case of pur approach, we therefore evaluated the robustness of our results to simulated sampling limitations.
-
-To do so, for each network, we removed a portion of the links and calculated how three control metrics of the subsampled network compare to those of the full network. 
-Specifically, we calculated the difference between the $n_D$ of the subsampled and the full network, the spearman correlation between the vectors $f_D$—which contain the frequency with wich each species is classified as a driver species, and the spearman correlation between $f_S$—which contain the frequency with which each species is classified as a superior node.
-We removed links from the full network with a probability inversly proportional to the interaction weight, and varied the portion of links removed between 0.5 and 0.95 at 0.05 increments. 
-We repeated the procedure ten times for each portion level and each network to obtain a total sample size of $n=2000$.
-
-Overall, the results of the sensitivity analysis indicate that our approach might be useful for management even in the absence of complete sampling. 
-Specifically as the proportion of sampled interaction decreassed, the variability of $n_D$ increassed, but was overall very similar when compared to that obtained using all available interactions (Figure \@ref(fig:fig-subsampling-sensitivity)a).
-Similarly, the correlation between the relative frequency with which species are classified as a driver ($f_D$) or as a superior node ($f_S$) was correlated ever for *extreme* levels of undersampling (Figure \@ref(fig:fig-subsampling-sensitivity)b).
-For instance, we found that with a sampling level of 0.5, the mean spearman correlation coefficient was 0.66 for $f_D$ and 0.76 for $f_S$. 
-Finally, the resulst suggest that the relative ranking of species is better conserved in $f_S$ than for $f_D$ troughout all levels subsampling levels.
+Often, the majority of the interactions that make up this structure are weak; in our networks this means that most interactions are formed by a small number of observed pollination visits, and therefore those weak intercations are less conspicuous in the field than strong ones.
+To strengthen the case of our approach, we therefore evaluated the robustness of our results to simulated sampling limitations.
+
+To do so we removed a portion of the links, for each network, and calculated how three control metrics of the subsampled network compare to those of the full network. 
+Specifically, we calculated the difference between the $n_D$ of the subsampled and the full network, the Spearman correlation between the vectors $f_D$—which contain the frequency with which each species is classified as a driver species, and the Spearman correlation between $f_S$—which contain the frequency with which each species is classified as a superior node.
+We removed links from the full network with a probability inversly proportional to the interaction weight, and varied the portion of links removed between 50% and 95% at 5% increments. 
+We repeated the procedure ten times for each removed level and each network to obtain a total sample size of $n=2000$.
+
+Overall, the results of the sensitivity analysis indicate that our approach might still be useful for management even in the absence of complete sampling. 
+Specifically, as the proportion of sampled interaction decreased, the variability of $n_D$ increased, but was overall very similar to that obtained when using all available interactions (Figure \@ref(fig:fig-subsampling-sensitivity)a).
+Similarly, the correlation between the relative frequency with which species are classified as a driver ($f_D$) or as a superior node ($f_S$) was highly correlated even for *extreme* levels of undersampling (Figure \@ref(fig:fig-subsampling-sensitivity)b).
+For instance, we found that with a sampling level of 50%, the mean Spearman correlation coefficient was 0.66 for $f_D$ and 0.76 for $f_S$. 
+Finally, the results suggest that the relative ranking of species is better conserved in $f_S$ than for $f_D$ throughout all subsampling levels.
 
@@
 
-Our decision to adopt the direction of asymmetries as the direction of control, while coherent with ecological processes, confers several advantages. 
-First it is consistent with previous studies, which facilitates the comparability between our findings and those in other systems explored using structural controlability. 
+Our decision to adopt the direction of asymmetries as the direction of control is coherent with ecological processes and also confers several advantages. 
+First, it is consistent with previous studies, which facilitates the comparability between our findings and those in other systems explored using structural controllability. 
 Second, it reduces the number of control cycles in the network—which require special treatment in our approach. 
-And third, the reduced number of links, facilitates the computation of all possible maximum matchings.
-
-For ilustration, we show all maximum cardinality matchings for an example network in which links are weighted based on the mutual dependences (Figure \@ref(fig:fig-matchings-bidirectional)). 
-We note, however, that using mutual dependences, or any set up that can lead to bidirectional links, is problematic for a couple of reasons. 
+Third, the reduced number of links facilitates the computation of all possible maximum matchings.
+
+For ilustration, we show all maximal cardinality matchings for an example network in which links are weighted based on the mutual dependences and not asymmetries (Figure \@ref(fig:fig-matchings-bidirectional)).
+We note, however, that using mutual dependences, or indeed any set up that can lead to bidirectional links, is problematic for a couple of reasons. 
 First, having two links between interacting species and using our maximum matching approach to calculate the control configurations, can result in matchings that include cycle inducing links (Figure \@ref(fig:fig-matchings-bidirectional-no)).
-Strictly speaking these configurations are maximum matchings in the alternative bipartite configuration (Figure \@ref(fig:fig-direction-of-control)e) but not in the directed network (Figure \@ref(fig:fig-direction-of-control)f).
+Strictly speaking these configurations are maximal cardinality matchings in the alternative bipartite configuration (Figure \@ref(fig:fig-direction-of-control)e) but not in the directed network (Figure \@ref(fig:fig-direction-of-control)f).
 While bidirectional links are the norm when using mutual dependences, they only appear in the asymmetry-weighted networks whenever the mutual dependences between two species are strictly symmetric. 
-In this special case, we include two links weighted with 0.5 to reflect the fact that the species affect each other in the same proportion.
+In this special case, we include two links weighted with 0.5 to reflect the fact that the species affect each other to the same extent.
 
@@
 ```{r  fig-matchings-bidirectional-no, echo = F, message = F, warning = F, fig.width = 6.2, fig.height = 2.4, results = "hide", fig.cap= "**Cycles in a bidirectional network**.
-Our approach finds twelve configurations for Figure \\@ref(fig:fig-matchings-bidirectional)a that are matchings in the alternative bipartite representation, but not actual matchings in the directed network."}
+Our approach finds twelve configurations for Figure \\@ref(fig:fig-matchings-bidirectional)a that are matchings in the alternative bipartite representation but not in the directed network."}
 
@@
 
-We consider two approaches to tackle this limitation. 
-The first approach, is to calculate the matching(s) as usual and then, before calculating $f_S$ and $f_D$, filter out the cycle containing matchings (Figure \@ref(fig:fig-matchings-bidirectional-no)).
-In the special case that the network has no maximal matchings that correspond to feasible control configurations, because they all include cycles, we reduce the size of the cliques we enumerate in $H$ (Figure \@ref(fig:fig-finding-all-matchings)) and repeat.
-The second approach is, instead of calculating the matching(s) for the network with bidirectional cycles, we calculate the matching(s) of $2^n$ unidirectional versions of the network, where $n$ is the number of cycles in the network (Figure \@ref(fig:fig-tackle-cycles)).
-We then average over the unidirectional networks to find the overall $f_S$ and $f_D$ for a given species.
+We consider two ways to tackle this limitation. 
+The first, is to calculate the matching(s) as usual and then, before calculating $f_S$ and $f_D$, filter out the cycle containing matchings (Figure \@ref(fig:fig-matchings-bidirectional-no)). 
+In the special case that the network has no maximal cardinality matchings that correspond to feasible control configurations because they all include cycles, we reduce the size of the cliques we enumerate in $H$ (Figure \@ref(fig:fig-finding-all-matchings)) and repeat.
+Instead of calculating the matching(s) for the network with bidirectional cycles, in the second approach, we calculate the matching(s) of $2^n$ unidirectional versions of the network, where $n$ is the number of bidirectional cycles in the network (Figure \@ref(fig:fig-tackle-cycles)).
+We then average the results of these unidirectional networks to find the overall $f_S$ and $f_D$ for a given species.
 
 ```{r fig-tackle-cycles, echo = F, message = F, warning = F, fig.width = 3.3, fig.height = 1.5, results = "hide", fig.cap= "**Dealing with cycles**.
-The network on the left, which has *n = 2* cycles, can be decomposed in *2^n^* unidirectional networs."}
+The network on the left, which has *n = 2* bidirectional cycles, can be decomposed into *2^n^* unidirectional networks."}
 layout(matrix(c(1,2,3, 1,4, 5), ncol = 3, byrow = TRUE), widths = c(2, 1,1))
@@
 
-The number of maximal matchings increases disproportionally fast with the number of links in a network. 
-For instance, our example network in Figure 1, which is composed of unidirectional links weighted by the asymmetry, has two different maximum matchings. 
-In contrast, the equivalent network with bidirectional links has 16 different maximum matchings (Figure \@ref(fig:fig-matchings-bidirectional) and \@ref(fig:fig-matchings-bidirectional-no)). 
-To further ilustrate the implications of this growth, some of our empirical networks had approximately ten thousand different maximum matchings using asymmetries but one hundred million when using mutual dependences.
-This exponential growth, and the computational cost of either filtering matchings with cycles or calculating the matchings for $2^n$ networks, surpassed the capabilities of the available computational resources and rendered us unable to calculate all possible maximum matchings when using mutual dependences in most of our bidirectional networks.
-Nevertheless, as most of our networks weighted by asymmetry had between zero and four cycles, we successfully used the second approach explained in the previous paragraph to calculate the all maximum matchings for these networks.
-
-We highlight that althoug the direction of control might affect the $f_S$ and $f_D$, it doesn't affect strongly the network's relative density of driver nodes $n_D$. 
-We reached this conclusion by calculating the $n_D$ obtained assuming that (a) the direction of control is governed by the asymmetry or (b) bidirectional dependences, (c) that plants depend on pollinators, and that (d) pollinators depend on plants.
+The number of maximal cardinality matchings increases disproportionally fast with the number of links in a network. 
+For instance, our example network in Figure 1, which is composed of unidirectional links weighted by the asymmetry, has two different maximal cardinality matchings. 
+In contrast, the equivalent network with bidirectional links has 16 different maximal cardinality matchings (Figure \@ref(fig:fig-matchings-bidirectional) and \@ref(fig:fig-matchings-bidirectional-no)).
+To further illustrate the implications of this growth, some of our empirical networks had approximately ten thousand different maximal cardinality matchings using asymmetries but one hundred million when using mutual dependences.
+Consequently, the computational cost of either filtering matchings with cycles or calculating the matchings for $2^n$ networks surpassed the capabilities of our available computational resources and rendered us unable to calculate all possible maximal cardinality matchings when using mutual dependences in most of our bidirectional networks.
+Nevertheless, as most of our networks weighted by asymmetry had between zero and four cycles, we successfully used the second approach explained in the previous paragraph to calculate the all maximal cardinality matchings for these networks.
+
+We highlight that although the direction of control might affect the $f_S$ and $f_D$, it doesn't strongly affect the network's relative driver-node density $n_D$. 
+We reached this conclusion by calculating the $n_D$ obtained assuming that (a) the direction of control is governed by the asymmetry, (b) bidirectional dependences, (c) that plants depend on pollinators, or that (d) pollinators depend on plants.
 Although the $n_D$ values were quantitatively different between the approaches (Figure \@ref(fig:fig-alternative-assumptions)), the Spearman correlation among these four options suggested a very high agreement (Table S3).
@@
   xtable::xtable(caption = "\\textbf{Agreement among assumptions on the direction of control}.
-Spearman correlation coefficients of the number of driver nodes $n_D$ four different assumptions of the direction of control..") %>%
+Spearman correlation coefficients of the driver-nodes density $n_D$ four different assumptions of the direction of control..") %>%
 	print(comment = FALSE, include.rownames = TRUE, caption.placement = "top", booktabs = T)
@@
 
-We use the frequency with which a species is classified as a driver node $f_D$ and the frequency with which a species is classified as a superior node $f_S$ in a set of accepted maximal matchings to infer their relative importance.
-Maximal matchings were accepted if the matching weight was over a certain threshold. 
+We use the frequency with which a species is classified as a driver node $f_D$ and the frequency with which a species is classified as a superior node $f_S$ in a set of accepted maximal cardinality matchings to infer their relative importance.
+Maximal cardinality matchings were accepted if the matching weight was over a certain threshold. 
 This threshold was defined as a proportion of the maximum matching's weight. 
-Here we evaluate the impact that a particular choice of this threshold has on $f_D$ and $f_S$.
-
-The number of accepted maximal matchings increased rapidly as the threshold at which they are accepted decreases.
-Nevertheless this number stabilises below approximately 0.6-0.7 (Figure \@ref(fig:fig-n-matchings)).
-
-```{r fig-n-matchings, echo = F, message = F, warning = F, fig.width = 3.2, fig.height = 2.4, results = "hide", fig.cap= "**Number of maximal matchings as a function of the weight threshold**.
-Each line correspond to one network."}
+Here we evaluate the impact that a particular choice of this threshold has on both $f_D$ and $f_S$. 
+The number of accepted maximal cardinality matchings increased rapidly as the threshold at which they are accepted decreases. 
+Nevertheless, this number stabilises below approximately 0.6-0.7 (Figure \@ref(fig:fig-n-matchings)).
+
+```{r fig-n-matchings, echo = F, message = F, warning = F, fig.width = 3.2, fig.height = 2.4, results = "hide", fig.cap= "**Number of maximal cardinality matchings as a function of the weight threshold**.
+Each line corresponds to one network."}
 d_sp %>%
@@
 	scale_x_reverse() +
-	ylab("maximal matchings") +
+	ylab("maximal cardinality matchings") +
 	fer_theme
@@
 
-We then examined how the relative importance of species changes with the chosen threshold. 
-We observe, that regardless of the matching weight's threshold species tend to be superior nodes in all or none of the matchings, which equates to $f_S$ values of one or zero, and the contrast between important and unimportant species is maintained (Figure \@ref(fig:fig-f-s-rankings)).
-Contrastingly, species' $f_D$ reach intermediate levels of importance and show higher variability across thresholds (Figure \@ref(fig:fig-f-d-rankings)). 
-We note here that we were unable to compute all the maximum cardinality matchings for one of our networks (uninvaded community in site 8). 
-We estimate the number of matchings to be more than one billion, which surpassed our available computational resources.
+We then examined how species relative importance changes with the chosen threshold. 
+We observed, that regardless of the matching weight's threshold, species tended to be superior nodes in all or none of the matchings, which equates to $f_S$ values of one or zero, and the differences between important and unimportant species were maintained (Figure \@ref(fig:fig-f-s-rankings)).
+In contrast, species' $f_D$ reached intermediate levels of importance and showed higher variability across thresholds (Figure \@ref(fig:fig-f-d-rankings)). 
+We note here that we were unable to compute all the maximal cardinality matchings for one of our networks (uninvaded community in site 8). 
+This is because, we estimated the number of matchings to be more than one billion, and this surpassed our available computational resources.
 
 ```{r fig-f-s-rankings, echo = F, message = F, warning = F, fig.width = 6.2, fig.height = 9, results = "hide", fig.cap="**Frequency with which a species was classified as a superior node ($f_S$) as a function of the matching weight threshold**.
-Rows correspond to study sites.", cache = T}
+Rows correspond to network pairs.", cache = T}
 sites <- net_prop %>% dplyr::arrange(study, site, inv) %$% site %>% unique()
@@
 
-```{r fig-f-d-rankings, echo = F, message = F, warning = F, fig.width = 6.2, fig.height = 9, results = "hide", fig.cap= "**Frequency with which a species was classified as a superior node ($f_D$) as a function of the matching weight threshold**.
-Rows correspond to study sites.", cache = T}
+```{r fig-f-d-rankings, echo = F, message = F, warning = F, fig.width = 6.2, fig.height = 9, results = "hide", fig.cap= "**Frequency with which a species was classified as a driver node ($f_D$) as a function of the matching weight threshold**.
+Rows correspond to network pairs.", cache = T}
 p[[2]] + ylab(expression(f[D]))
@@
 The mean of those matrices is shown in Table S4. 
-Overall, among all thresholds, we found a very high agreement for $f_S$, and high to very high for $f_D$. 
-With the exception of using a threshold of 1 (only maximum matchings are accepted), the choice of the threshold has little impact on the relative importance of species. 
-For convenience, we use an intermediate level of 0.5. 
+Among all thresholds, we found a very high agreement for $f_S$, and high to very high for $f_D$. 
+With the exception of using a threshold of 1 (only maximum matchings are accepted), the choice of the threshold has limited impact on the relative importance of species. 
+For convenience, we use an intermediate level of 0.8. 
 Nevertheless, the differences are marginal and any threshold $<= 0.9$ is likely to produce very similar results.

### 2017-02-28 paper/draft_2.Rmd
Add space

@@
 We selected this threshold as it provided a high agreement between networks quantified by visitation and pollination efficiency as well as between our weighting/directionality assumptions; however, the choice of this threshold had a negligible impact on any results (Supporting Information S7).
-Details about the computational procedure to find all maximum cardinality matchings of a network can be found in Supporting Information S1 and Figure S2.
+Details about the computational procedure to find all maximal cardinality matchings of a network can be found in Supporting Information S1 and Figure S2.
 

### 2017-02-28 paper/EL-reviewer-comments-1.Rmd
Move cover letter to its own file

@@
 title: "Response to reviewer comments ELE-00738-2016"
-date: "14 December 2016"
+date: "28 February 2017"
 output: pdf_document
@@
 
-Dear Prof. Jonathan Chase,
-
-We are grateful for the opportunity to resubmit a revised manuscript for your consideration. 
-We have endeavored to incorporate all reviewers' feedback into the manuscript and we feel the attached draft constitutes an important improvement from the previous version. 
-We were impressed by the quality of the reviews; they all were thoughtful, clear, and constructive. 
-It is evident that all three anonymous reviewers have given a fair and careful consideration to our manuscript. 
-We would like to thank them for the truly valuable feedback.
-
-The reviewers identified major limitations in our manuscript. 
-Specifically with regards to the terminology, the underlying  structural control, and the lack of detail in the presentation of the empirical networks. 
-In the current version, we have thoroughly addressed all these concerns and improved both the robustness of the analyisis and the clarity of the concepts. 
-Detailed responses to each comment, one by one, are provided in the corresponding section.
-
-Fernando Cagua
-
-******************************************
-
 ## Response to the handling editor
@@
 
-The most substantial change is related to the result that ecological invasions reduce the manageability of the studied pollination networks. 
+The most substantial change is related to the earlier result that ecological invasions reduce the manageability of the studied pollination networks. 
 After revising the manuscript, we found that the effect of invasion is actually the opposite of what we initially reported. 
 This result arises from a regression in which the response variable was the proportion of driver nodes. 
-Our previous conclusion arose from a trivial mistake on the implementation of this regression for which we are extremely apologetic. 
-The regression indicates that the invasion status is *inversely* related to $n_D$ (the density of driver nodes) and **not** to our previous definition of manageability $m = 1 - n_D$.
-In catching this error, the editor and reviewers will note that revised result now contradicts our hypothesis and has also led to our having to amend the title of the paper.
+Our previous conclusion arose from a mistake in our implementation of this regression for which we are extremely apologetic. 
+In actual form, the regression indicates that the invasion status is *inversely* related to $n_D$ (the density of driver nodes) as opposed to our previous definition of manageability $m = 1 - n_D$. 
+After catching this error, the editor and reviewers will now note that revised result now contradicts our hypothesis and has also led to our having to amend the title of the paper.
 Nevertheless, we hope that you will agree that both our overall objective and the applicability of our approach is maintained.
 
-Upon reflection, we also suspect that the root of the mistake was, as you and the reviewers helped point out, that our definition of manageability and its relation to existing concept of controllability were confusing.
+Upon reflection, we also suspect that the root of the mistake was, as you and the reviewers helped point out, that our definition of manageability and its relation to the existing concept of controllability were overly confusing.
 In the revised paper, we refrain from giving a mathematical definition of manageability and instead focus on $n_D$, an unambiguous metric clearly defined in the structural controllability literature. 
@@
 In the previous manuscript, we referred to species that were classified as superior nodes in all possible control strategies as *driver species*. 
-Because of the strong similarities with the term *driver node*, which has been used in previous literature and we also use in our manuscript, it was extremely easy to misinterpret the terms and follow our rationale.
-Now, we have removed the term driver species and instead focus on two well-defined metrics: $f_D$ and $f_S$, which correspond to the frequency to which a species is classified as a driver or superior node, respectively.
+Because of the strong similarities with the term *driver node*, which has been used in previous literature and that we also use in our manuscript, it was extremely easy to misinterpret the terms and completely follow our rationale.
+We have now removed the term driver species and instead focus on two well-defined metrics: $f_D$ and $f_S$, which correspond to the frequency to which a species is classified as a driver or superior node, respectively.
 
-In addition, we now focus on the results obtained when we use the asymmetry of the dependences to direct the networks.
-We do so, because thanks to the reviewers comments, we identyfied some problems with the application of structural controllability when we use the mutual dependences to direct the network.
+In addition, we now focus exclusively on the results obtained when we use the asymmetry of the dependences to direct the networks. 
+We do so, because thanks to the reviewers comments, we identyfied some novel problems with the application of structural controllability when we use the mutual dependences into direct the network. 
 Specifically, the problems arise from an absolute dominance of cycles and difficulties to the use of the maximum maximum matching algorithm to find a minimum set of driver nodes $D$. 
+We elaborate on these on the new version in Lines 212--224 and Supporting Information S6.
 
@@
 
-## Referee 1
+## Reviewer 1
 
@@
 
-    *Thanks to this comment and those from other reviewers have helped us identify some shortcomings on the way we were introducing the control framework in the paper.
-We have largely rewritten the 'Theoretical framework' section.
+    *Thanks for this comment and those from other reviewers have helped us identify some shortcomings on the way we were introducing the control framework in the paper.
+In reposnse, we have largely rewritten the 'Theoretical framework' section.
 We start by offering a brief overview of control theory.
 In this overview, we emphasise our assumptions regarding the dynamical nature of the interactions.
-And follow with a brief discussion that indicates how structural controllability is unable to provide information about the particulars of the control signal and the feasibility of its application.
-Without disregard the usefulness of the proposed approach, we also mention at the end of the discussion how recently developed numerical methods [@Cornelius2013] might offer exciting results in this regard.*
+We then follow with a brief discussion that indicates how structural controllability is unable to provide information about the particulars of the control signal and the feasibility of its application.
+Without disregarding the usefulness of the proposed approach, we also mention at the end of the discussion how recently developed numerical methods [e.g.
+@Cornelius2013] might offer exciting results in this regard.*
 

### 2017-02-28 paper/draft_2.Rmd
took care of FDO comments and left one DBS for FDO

@@
 Contrary to our initial hypothesis, we found some evidence that invaded communities might be easier to manage than uninvaded ones from a control-theoretic perspective. 
-Our results reveal, however, that this effect is comparatively small and the structural differences among different networks are more strongly related to potential differences in our ability to alter the state of the community via external interventions.
+Our results reveal, however, that this effect is comparatively small, and the structural differences among different networks are more strongly related to potential differences in our ability to alter the state of the community via external interventions.
 Despite the small effect of invasion status at a network level, we found that invasive mutualists occupy a particularly dominant role in their communities for two reasons. 
-(FDO revision) First, as species with a high *f~S~*, changes on their abundance have the potential to propagate broadly through the community and in turn, affect the abundances of many other species. 
-Second, as species with a high *f~D~*, they are also indispensable to fully control the plant-pollinator network. 
+First, as species with a high *f~S~*, changes on their abundance have the potential to propagate broadly through the community and, in turn, affect the abundances of many other species. 
+Second, as species with a high *f~D~*, they are also indispensable when it comes to fully controlling the plant-pollinator network. 
 At a community level, we demonstrate that the manageability of mutualistic networks is strongly governed by the asymmetric nature of mutual dependences—which constitute the foundations of the structure and stability of mutualistic networks [@Memmott2004; @Vazquez2004; @Bascompte2006; @Lever2014; @Astegiano2015].
@@
 Because of the ability that our approach has to infer the magnitude of the effects that each species has on others in the community, it is tantalising to use it to select promising candidates for management interventions.
-To this end, the two indices we employed to characterise a species provide two complementary pieces of information. 
-(FDO revise grammar) Our first index, the frequency with which a species is classified as a driver node (*f~D~*) provides an indication of the likelihood that a species is part of the set of species that need to be manipulated in order to control of *all* species in the community.
-The driver-node concept has received considerable attention in the structural-control literature and indeed shows substantial potential to provide useful ecological insight. 
+To this end, the two indices we have used to characterise a species provide two complementary pieces of information. 
+Our first index *f~D~*---the frequency with which a species is classified as a driver node---provides an indication of the likelihood that a species forms part of the set of species that must be manipulated in order to control *all* species in the community.
+This driver-node concept has received considerable attention in the structural-control literature and indeed shows substantial potential to provide useful ecological insight. 
 Nevertheless, we anticipate two caveats that hinder its direct utility for management applications.
-First, unlike some other types of complex systems, fully controlling an ecological community is almost certainly out of reach for all but the simplest ones, due to either the number of required interventions or the difficulties of their implementation [@Motter2015].
-For instance, our results suggest that full control of the pollination networks would require direct interventions on 40-90% of the species.
-Second, @Ruths2014 established that driver nodes arise due to distinct mechanisms and therefore species with markedly different network metrics can be driver nodes in their community (Supporting information S2).
+First, unlike some other types of complex systems, fully controlling an ecological community is almost certainly out of reach for all but the simplest, due to either the number of required interventions or the practical difficulties of their implementation [@Motter2015].
+For instance, our results suggest that full control of the pollination networks would require direct interventions on anywhere from 40--90% of the species.
+Second, @Ruths2014 established that driver nodes arise due to distinct mechanisms and therefore species with markedly different network metrics can act as driver nodes in their community (Supporting Information S2).
 
 Our second index *f~S~* is, however, directly related to the likelihood a species affects the abundance of another species in all of the control strategies considered. 
-Importantly, this is irrespective of whether controlling the entire network is desired/feasible or not. 
-In fact, because superior nodes are invariably at the beginning of a matched link, species with a high *f~S~* are more likely to be the subjects of management interventions when controlling the abundances of a target set of species—as opposed to the entire network—is desired [@Gao2014].
+Importantly, this is irrespective of whether controlling the entire network is ultimately desired and/or feasible. 
+In fact, because superior nodes are always at the beginning of a matched link, species with a high *f~S~* are more likely to be the subjects of management interventions when controlling the abundances of a target set of species—as opposed to the entire network—is desired [@Gao2014].
 An important advantage here is that the target set of species does not have to be the same set to which interventions are applied. 
@@
 
-(FDO check) Despite the apparent similarities, our approach is different to previous attempts to quantify species importance. 
-Existing metrics usually harness species features like centrality, position, co-extinction or uniqueness, to infer their effect on other species [@Allesina2004; @Jordan2006; @Jordan2009; @Lai2012]. 
+Despite the apparent similarities, our approach is different to previous attempts to quantify species importance in a few key ways.
+Existing metrics usually harness species featuresi, like centrality, position, co-extinction or uniqueness, to infer their effect on other species [@Allesina2004; @Jordan2006; @Jordan2009; @Lai2012]. 
 In contrast, our control-based approach tackles that question directly.
@@
 Our approach, however, is not based on a single structural metric but instead acknowledges the existence of multiple management strategies.
-(FDO check) By allowing for the fact that some are more optimal than others in different contexts, control theory implicitly highlights that management decisions should be based on a single technique.
+By allowing for the fact that some strategies are better than others depending on the context, control theory implicitly highlights that management decisions should (DBS) not be based on a single technique.
 As such, ours and other flexible approaches that take a network-wide approach might prove more useful to guide ecosystem management if we want to go beyond using network metrics to minimise topological species loss [@McDonald-Madden2016].

### 2017-02-28 paper/draft_2.Rmd
Added Kate's address and removed "we, therefore, "

@@
 
-^2^ Current address: Stockolm, Cold & dark place in the Arctic Circle
+^2^ Current address: Department of Ecology, Swedish University of Agricultural Sciences, Box 7044, SE-750 07 Uppsala, Sweden
 
@@
 Previous research has shown that mutual dependences are often highly asymmetric in natural communities [@Bascompte2006]; in other words, if a plant species is largely dependent on a pollinator species, then that pollinator tends to depend rather weakly on the plant (or vice versa).
-We, therefore, simplified the network so that interacting species are connected by only one directed link when mutual dependences are asymmetric (Figure 2c).
+We therefore simplified the network so that interacting species are connected by only one directed link when mutual dependences are asymmetric (Figure 2c).
 This simplification, while maintaining ecological realism, is advantageous for several reasons. 
@@
 Although understanding the variability of manageability across ecological networks is a useful result in itself, we also wanted to test whether invasion status or other predictors had an impact on the observed *n~D~*.
-We, therefore, used a set of generalised linear models (with binomial error structure) to investigate the effect of invasion status while also including covariates related to species richness, since one might naively expect to see a negative relationship between richness and manageability [@Menge1995].
+We therefore used a set of generalised linear models (with binomial error structure) to investigate the effect of invasion status while also including covariates related to species richness, since one might naively expect to see a negative relationship between richness and manageability [@Menge1995].
 These covariates included the total number of species, plant richness, pollinators richness, the ratio of plant to pollinator richness, the link density (connectance), and the study site (as a two-level factor).

### 2017-02-28 paper/draft_2.Rmd
Double checking Daniel's mods

@@
 
-* **Authorship:** DBS conceived the idea; all authors contributed to the development of the theoretical framework. EFC performed all analysis. EFC and DBS wrote the manuscript.
+* **Authorship:** DBS conceived the idea; all authors contributed to the development of the theoretical framework.
+EFC performed all analysis.
+EFC and DBS wrote the manuscript.
+All authors contributed to its revision.
 
@@
 Conveniently the information necessary to determine the minimum number of driver nodes *D* in a network with linear dynamics is fully contained in the network structure [@Kalman1963; @Liu2011; @Motter2015].
-We, therefore, start here from the assumption that an ecological network can, at least near equilibrium points, be described by $\frac{dx}{dt} = Ax + Bu(t)$, where the change over time of its state ($\frac{dx}{dt}$) depends on its current state *x* (for example the species' abundances), an external time-varying input *u(t)*, and two matrices *A* and *B*, which encapsulate information about the network structure and how the species respond to the external input, respectively.
+We therefore start here from the assumption that an ecological network can, at least near equilibrium points, be described by $\frac{dx}{dt} = Ax + Bu(t)$, where the change over time of its state ($\frac{dx}{dt}$) depends on its current state *x* (for example the species' abundances), an external time-varying input *u(t)*, and two matrices *A* and *B*, which encapsulate information about the network structure and how the species respond to the external input, respectively.
 Even though linearity might be a strong assumption, it has been shown that fundamental insight about the control of complex systems can be gained without a detailed knowledge of the nonlinear dynamics and the system parameters [@Liu2016], an important step towards ultimately understanding the controllability of systems with nonlinear dynamics [@Liu2011].
@@
 Specifically, we calculated *n~D~* and species relative importance for 500 random subsamples of each empirical network in which the weakest links were more likely to be removed. 
-The sensitivity analysis indicated that, even in the absence of complete sampling, a control theoretic approach can still be applied (Supporting Information S5).
+The sensitivity analysis indicated that, even in the absence of complete sampling, a control-theoretic approach can still be applied (Supporting Information S5).
 
@@
 Lastly, we allowed for variation between different communities by including the network identity as a random effect [@Bates2015]. 
-Candidate models and estimates were assessed using the same procedure as in the  models *n~D~*.
+Candidate models and estimates were assessed using the same procedure as in the  models for *n~D~*.
 
@@
 The model results suggest that these differences between invasive and native species are not underpinned by any intrinsic property of the invasive species, instead, they are due to species properties that apply to invasive and native species alike (Table 1).
-Specifically, we found that a species is more likely to be classified as a superior node if it had a large species strength (the sum of the dependences of other species on the species of interest). 
-To a smaller extent, visitation strength (its sum of visits) and the species degree also had a positive relationship with $f_S$. 
-In contrast, the relationships between species structural properties and $f_D$ were more convoluted (Table 1). 
-Both invasive species (which for example tend to have a large degree, and high dependence strength) and pollinators (which generally have a smaller degree and dependence strength) were classified as driver nodes in a large proportion of the considered matchings.
+Specifically, we found that a species is more likely to be classified as a superior node if it had a large species strength (the sum of the dependences of all other species on the species of interest).
+To a smaller extent, visitation strength (a species' sum of visits) and the species degree also had a positive relationship with $f_S$. 
+In contrast, the relationships between species structural properties and $f_D$ were more less clear cut (Table 1). 
+Both invasive species (which for example tend to have a large degree, and high dependence strength) and pollinators (which generally have a smaller degree and dependence strength) were classified as driver nodes in a large proportion of the matchings.
 
@@
 Invasive species have been previously found to exacerbate the asymmetries in their communities [@Aizen2008; @Bartomeus2008; @Henriksson2016]. 
-Although this might cause differences both at the community and the species level, we found that invasive plants are not inherently different to their native counterparts [@Stouffer2014].
+Although this might cause differences both at the community and the species level, we found that invasive plants are not inherently different to their native counterparts [@Stouffer2014; Emer2016a].
 Invasive plants, just like any other mutualist in our data set, tend to be classified as a superior node with a frequency (*f~S~*) proportional to the degree to which their interaction partners are collectively more dependent on them than the other way around.
@@
 Our approach, however, is not based on a single structural metric but instead acknowledges the existence of multiple management strategies.
-By allowing for the fact that some strategies are better than others depending on the context, control theory implicitly highlights that management decisions should (DBS) not be based on a single technique.
+By allowing for the fact that some strategies are better than others depending on the context, control theory implicitly highlights that management decisions should not be based on a single technique.
 As such, ours and other flexible approaches that take a network-wide approach might prove more useful to guide ecosystem management if we want to go beyond using network metrics to minimise topological species loss [@McDonald-Madden2016].

### 2017-02-28 paper/draft_2.Rmd

@@
 ```{r fig_explaining-n-driver, echo = FALSE, warning = FALSE, message = FALSE, fig.width = 3.245, fig.height = 4.8, fig.cap = "**Driver-node density**.
-(a) Histogram of the driver-node density (_n~D~_) for the twenty studied networks.
+(a) Histogram of the driver-node density (_n~D~_) for the twenty networks.
 (b) Invaded communities have lower *n~D~* than uninvaded communities even when controlling for factors related to species richness.
@@
 Invasive species have been previously found to exacerbate the asymmetries in their communities [@Aizen2008; @Bartomeus2008; @Henriksson2016]. 
-Although this might cause differences both at the community and the species level, we found that invasive plants are not inherently different to their native counterparts [@Stouffer2014; Emer2016a].
+Although this might cause differences both at the community and the species level, we found that invasive plants are not inherently different to their native counterparts [@Stouffer2014; @Emer2016a].
 Invasive plants, just like any other mutualist in our data set, tend to be classified as a superior node with a frequency (*f~S~*) proportional to the degree to which their interaction partners are collectively more dependent on them than the other way around.
@@
 Answering each of these questions might require its evaluation in different ecological systems, an explicit integration of control theory with numerical models of species densities [@Cornelius2013; @Gibson2016], and experimental tests on simple communities.
-Nevertheless, the potential rewards are encouraging from both an ecological perspective as well as a conservation perspective, where an integrated approach can shift our focus beyond the identification of ideal targets for intervention to the design of informed interventions that legitimately achieve restoration goals.
+Nevertheless, the potential rewards are encouraging from both an ecological and conservation perspective, where an integrated approach can shift our focus beyond the identification of ideal targets for intervention to the design of informed interventions that legitimately achieve restoration goals.
 

### 2017-02-28 paper/EL-reviewer-comments-1.Rmd
Revise response to reviewers

@@
 output: pdf_document
+csl: ecology-letters.csl
 classoption: a4paper
@@
 Our previous conclusion arose from a mistake in our implementation of this regression for which we are extremely apologetic. 
-In actual form, the regression indicates that the invasion status is *inversely* related to $n_D$ (the density of driver nodes) as opposed to our previous definition of manageability $m = 1 - n_D$. 
+In actual fact, the regression indicates that the invasion status is *inversely* related to $n_D$ (the density of driver nodes) as opposed to our previous definition of manageability $m = 1 - n_D$. 
 After catching this error, the editor and reviewers will now note that revised result now contradicts our hypothesis and has also led to our having to amend the title of the paper.
@@
 
-    *Thanks for this comment and those from other reviewers have helped us identify some shortcomings on the way we were introducing the control framework in the paper.
+    *Thanks for this comment and those from other reviewers which have helped us identify some shortcomings on the way we were introducing the control framework in the paper.
 In reposnse, we have largely rewritten the 'Theoretical framework' section.
@@
 Without disregarding the usefulness of the proposed approach, we also mention at the end of the discussion how recently developed numerical methods [e.g.
-@Cornelius2013] might offer exciting results in this regard.*
+@Cornelius2013] might offer future avenues results in this regard (Lines 401--404)*
 
@@
 In fact, we explored the implementation of the approach of [@Ruths2014] at initial stages of the project.
-However we decided to exclude this approach from the final draft, mainly due to space limitations.
+However, we earlier decided to exclude this approach from the final draft, mainly due to space limitations.
 Nevertheless, due to this comment and one of Referee 2 we have rediscovered its value and use it to support our decision to include the analysis of superior nodes, and not just driver nodes, in our manuscript.
-We now dedicate a whole section in the Supporting Information (S2).
-In summary, we found our networks weighted by asymmetry to be external dilation dominated, and hence have only a small number of cycles.
-Networks weighted by mutual dependences are dominated by cycles and hence challenging to our approach.
-In another section in the Supporting Information (S6) we discuss the implications that using these networks have, and our approach to circumvent them.
+Though space constraints remain and we can only mention it briefly in the main text (Lines 358--360), we also dedicate a whole section in the Supporting Information (S2) to this subject.
+To summarise here, we found our networks weighted by asymmetry to be external dilation dominated, and hence have only a small number of cycles.
+Networks weighted by mutual dependences are dominated by cycles and hence challenging to address with our approach.
+In another section in the Supporting Information (S6), we discuss the implications of using these networks and our approach to circumvent them.
 Finally we are grateful for the reference to @Motter2015.
-We were unaware of this paper and it has been extremely useful to contextualise our work in the broader control theory literature.*
+We were unaware of this paper and it has been extremely useful to contextualise our work in the broader control-theory literature.*
 
@@
 
-    *Indeed most of the literature treats the problem of controlability on unweighted/binary networks.
-In that special case maximum matchings are equivalent to maximum cardinality matchings.
+    *The reviewer is absolutely correct most of the literature treats the problem of controlability on unweighted/binary networks.
+In that special case, maximum matchings are equivalent to maximum cardinality matchings.
 It has been shown, however, that the interaction weights carry important information in pollination networks about the patterns and processes in the community.
-In the paper we use the visitation weights directly or indirectly in two different ways.
+In the paper, we use the visitation weights directly or indirectly in two different ways.
 First, we use them to determine the potential direction of control (via the dependence asymmetry).
-Second—which directly adresses the reviewer's comment—we use them to give priority to matchings that have the largest weight since these arguably have the largest impact on the network state for a given management intervention.
-Because the weights determine to some extent the dynamical relationships between species, our approach attempts to incorporate more ecological realism to the structural controllability approach.
-We acknoweledge our earlier presentation of this rationale was confusing, especially for readers familiar with the control literature, and therefore have added a whole paragraph describing our rationale in the "Relative importance" subsection in the "Theoretical frameowrk".
-To minimise potential confusions we are more careful when introducing each of these concepts, and have added—as suggested by the reviewer—a glossary for easy reference.*
+Second—which directly addresses the reviewer's comment—we use them to give priority to matchings that have the largest weight since these arguably have the largest impact on the network state for a given management intervention.
+Because the weights determine the dynamical relationships between species, our approach attempts to incorporate more ecological realism to the structural-controllability approach.
+We acknoweledge our earlier presentation of this rationale was confusing, especially for readers familiar with the control literature, and have therefore added a whole paragraph describing our rationale in the "Relative importance" subsection in the "Theoretical framework" section (Lines 154--168).
+To minimise potential confusions, we are more careful when introducing each of these concepts, and have added—as suggested by the reviewer—a glossary for easy reference.*
 
@@
 
-    *We have completely rewritten that section and the equivalent sentence now reads "Conveniently, in a network with linear dynamics, the information necessary to determine the minimum number of driver nodes D is fully contained in the network structure..."*
+    *We have completely rewritten that section and the corresponding sentence (Lines 95--97) now reads "Conveniently the information necessary to determine the minimum number of driver nodes *D* in a network with linear dynamics is fully contained in the network structure..."*
 
@@
     *We are sorry for the imprecision.
-It should have been "all possible maximum cardinality matchings".
-In any case, because of the reviewers' suggestion about the driver species concept we have now removed this sentence.
-We hope that the new text we have included on the "Relative importance" subsections, both in the "Theoretical framework" and "Empirical application", and in Supporting Information S7, helps clarify why our approach to identify species importance is not exclusively centred on maximum matchings.*
+It should have been "all possible maximal-cardinality matchings".
+In any case, because of the reviewers' suggestion about the driver species concept, we have now removed this sentence altogether.
+We hope that the new text we have included in the "Relative importance" subsections, both in the "Theoretical framework" and "Empirical application" section, and in Supporting Information S7, helps clarify why our approach to identify species importance is not exclusively centred on maximum matchings.*
 
@@
     *Thanks to this suggestion and those of other reviewers, we have made important changes to Figure 1.
-In it, we include a better illustration of our methodology for a simple network while paying special effort to bring clarity to the different node categories as superior, driver, matched, and unmatched nodes.
+In it, we include a better illustration of our methodology for a simple network while paying special effort to bring clarity to the different node categories of superior, driver, matched, and unmatched nodes.
 We hope the figure, in addition to our new introduction to the elements of a maximum matching, make the concept easier to understand.*
@@
 
-    *We agree that in hindsight, our choice of terminology was poor.
+    *In hindsight, we agree that our choice of terminology was poor.
 We have eliminated the term "driver species", which had a different meaning to the usual concept of "control node", from the manuscript.
-Now, we stick to the terminology that is already used, and refrain for introducing a new term for the species that are classified as superior nodes in all possible control strategies.*
+Now, we stick to the terminology that is already used, and refrain for introducing a new term for species that are classified as superior nodes in all possible control strategies.*
 
@@
     *Thanks for pointing this out.
-As suggested, we have included a figure that help explains our method to compute all possible maximum cardinality matchings.
-Nevertheless, because of space limitation, and because the methodology itself is not one of our main contributions, we have included the procedure and the figure in the Supporting Information (S1 and Figure S2).*
+Exactly as suggested, we have included a figure that helps explain our method to compute all possible maximum cardinality matchings.
+Nevertheless, because of space limitations and because the methodology itself is not one of our main contributions, we have included the procedure and the figure in the Supporting Information (S1 and Figure S2).*
 
@@
 As the referee points out it, this is not an estimation but an exact calculation.
-The sentence now reads "To do so, we calculated the maximum matching of the corresponding pollination network, and determined the minimum proportion of species that need directed interventions to fully control the species abundances in the community".*
+The sentence (Lines 190--192) now reads "To do so, we calculated the networks' maximum matching and determined the minimum proportion of species *n~D~* that need external input signals to fully control the species abundances in the community".*
 
@@
 
-    *In retrospect we realise that our rationale to include a randomisation of the link weights was not clear enough.
-As the referee points out, a change on the weights would only be reflected on a potential change on the interaction asymmetry.
-We identifyed two problems with this approach: first the changes aren't easily tractable, and second there is not a standard way to randomise weight in quantiative networks and the particular choice of the algorithm might influence the results.
-We therefore decided to remove the null model that maintained the degree of species and randomised the weight of the links as the effect of the asymmetry is explicitly tackled by the second approach in which we maintain the structure but randomise the asymmetry.*
+    *In retrospect, we realise that our rationale to include a randomisation of the link weights was not clear enough.
+As the referee points out, a change to the weights would only be reflected in a potential change on the interaction asymmetry.
+We identifyed two problems with this approach: first the changes aren't easily tractable, and second there is not a standard way to randomise weights in quantiative networks and the particular choice of the algorithm might influence the results.
+We therefore decided to remove the null model that maintained the degree of species and randomised the weight of the links as the effect of the asymmetry is explicitly tackled by the second approach in which we maintain the structure but randomise the asymmetries.*
 
@@
     *Thanks for the suggestion.
-In the methods, where we describe the empirical application, we now state the minimum, maximum, and the mean number of species for both the networks from Bristol, UK and Cap de Creus, Spain.
-In addition, now we briefly discuss the proportion of driver nodes we found in the studied pollination networks in the fourth paragraph of the Discussion.
-We do so, in the context of highlighting the potential caveats of one of our metrics of species importance.*
+In the methods where we describe the empirical application, we now state the minimum, maximum, and the mean number of species for both the networks from Bristol, UK and Cap de Creus, Spain.
+In addition, now we briefly discuss the proportion of driver nodes we found in the pollination networks in the fourth paragraph of the Discussion.
+We also do so in the context of highlighting the potential caveats of one of our metrics of species importance.*
 
@@
 
-    *Agreed.
-Given that driver nodes have received a considerable amount of attention in the control literature, we realise that neglecting them might be confusing, especially for readers familiar with control theory.
+    *We agree completely with the Reviewer here.
+Given that driver nodes have received a considerable amount of attention in the control literature, we now realise that neglecting them might be confusing, especially for readers familiar with control theory.
 We have fully incorporated this suggestion and our paper is now much more comprehensive.
-Now, to determine the potential importance of a species, we determine, not only its properties as a superior node, but also its properties as a driver node.
-We have dedicated a large proportion of the discussion to discuss the advantages and limitations of each of them and how they relate to each other and to realistic management applications.
-To do build this discussion we harnessed results from additional modelling analysis in the main text, as well as the lessons learned from the application of the @Ruths2014 control profiles approach.*
+To determine the potential importance of a species in the revised manuscript, we determine not only its properties as a superior node but also its properties as a driver node.
+We have dedicated a large proportion of the discussion to discuss the advantages and limitations of each of these, plus how they relate to each other and to realistic management applications.
+To do build this discussion, we harnessed results from additional modelling analysis in the main text, as well as the lessons learned from the application of the @Ruths2014 control-profiles approach.*
 
@@
     *This was a mistake on our part.
-We were not interested in determining whether the __absolute__ value of n~D~ differs among approaches, but instead, we wanted to determine wether the __relative__ values showed agreement.
-This is, our primary concern was to test whether networks with a high n~D~ under the asymmetry weighting also had a high n~D~ under the bidirectional dependences weighting.
+We were not interested in determining whether the __absolute__ value of n~D~ differs among approaches, but instead, we wanted to determine whether the __relative__ values showed agreement.
+That is, our primary concern was to test whether networks with a high n~D~ under the asymmetry weighting also had a high n~D~ under the bidirectional dependences weighting.
 We have changed the text in the Supporting Information (S6) to improve clarity.*
@@
 
-    *Thanks for pointing it out. We have added the period.*
+    *Thanks for pointing this out. We have added the period.*
 
@@
 
-    *Thanks for pointing it out.
-Given the tight 150 word limit imposed by the Journal, we had some trouble highlighting the novelty of the approach while maintaining important details about the empirical application.
-We hope the current version of the abstract shows substantial improvement.*
+    *Given the tight 150 word limit imposed by the journal, we had some trouble highlighting the novelty of our approach while also maintaining important details about the empirical application.
+We hope the revised version of the abstract is improved in this regard.*
 
@@
 
-    *The sentence now reads "To bridge this gap, we outline an approach to apply theory on the control of complex systems in an ecological context and implement them using empirical data."*
+    *The sentence (Lines 70--71) now reads "To bridge this gap, we outline an approach to apply theory on the control of complex systems in an ecological context and implement it using empirical data."*
 
@@
      *Thanks for the observation.
-As above, we have also reworded large segments of this section to make more clear what are and what are not novel contributions.
-Specifically, we now explain how the approach builds on existing structural controllability theory by incorporating the weight of the interactions.
-In addition, although the concept of driver and superior nodes are not novel in the control theory literature, most of the previous studies tend to focus on __a single__ matching.
-We instead exploit the fact that a single network may have multiple control configurations and evaluate the role of species in each of them.
+As above, we have also reworded large segments of this section to make what are and what are not novel contributions clearer.
+Specifically, we now explain how the approach builds on existing structural-controllability theory by incorporating the weight of the interactions.
+In addition, although the concept of driver and superior nodes are not novel in the control theory literature, most of the previous studies tend to focus on a __single__ matching.
+Here, we instead exploit the fact that a single network may have multiple control configurations and evaluate the role of species in each of them.
 We now dedicate a large proportion of the discussion to these new metrics and how (even if not independent) they are conceptually different to previous attempts to rank species by importance.
 We also include extra development in the Supporting Information S7.
-Moreover, now we included more details about the rationale behind our approach.
-By being more specific we hope the reader to be able to identify the theoretic and computational novelties of our approach with respect to existing "ranking" methods.*
+Moreover, now we include more details about the rationale behind our approach.
+By being more specific, we hope the reader to be able to identify the theoretical and computational novelties of our approach with respect to existing "ranking" methods.*
 
@@
 
-    *Thank you.
-We acknowledge we did a poor job reflecting our work in the previous literature.
+    *Thank you for this suggestion.
+We acknowledge that we did a poor job embodying our work in the previous literature.
 We now include a paragraph in the discussion to explore the similarities and differences of our work with previous indices based on structural metrics.
-We explain how "our approach ...
-is not based on a single structural metric but acknowledges the existence of multiple management strategies; some more optimal than others in specific contexts".
+We explain (Lines 380--385) how "our approach...
+is not based on a single structural metric but instead acknowledges the existence of multiple management strategies.
+By allowing for the fact that some strategies are better than others depending on the context, control theory implicitly highlights that management decisions should not be based on a single technique".
 We also concur that more flexible approaches like ours and the one implemented by @McDonald-Madden2016 "that take a network-wide approach might prove more useful to guide ecosystem management if we want to go beyond using network metrics to minimise topological species loss".*
@@
 
-    *We now brifly mention in the Discussion how "because of the degree constraints imposed by bipartite networks, our pollination specific results might not be relevant to other ecological systems, the approach we propose is applicable wherever species abundances are influenced by their interactions".*
+    *We now brifly mention in the Discussion (Lines 394--397) how "although our pollination specific results might not be directly translatable to other ecological systems because of the degree constrains imposed by bipartite networks, the approach we propose is applicable wherever species abundances are influenced by their interactions".*
 
@@
 
-    *We agree we did not discuss with enough detail the assumptions and caveats of our approach.
-As such, as we explain our methods we try to highlight the rationale behind them while being more explicit about the assumptions and limitations.
-Moreover, in the discussion, we now provide a fairer assessment of the extent to which our approach might be useful for practical applications.*
+    *We agree that we did not previously discuss the assumptions and caveats of our approach with enough detail.
+As such, as we now try to better highlight the rationale behind our methods while being more explicit about the assumptions and limitations.
+Moreover we now provide a fairer assessment of the extent to which our approach might be useful for practical applications in the discussion.*
 
@@
 Our most expensive computation was to find __all__ the possible maximum cardinality matchings to calculate species-level metrics.
-Lamentably the network's control profile does not provide species-level information and hence we couldn't use it to our advantage.
-Nevertheless, as suggested by you and another reviewed, we have included a section where in the Supporting information (S2) where we explain that our networks are external dilation dominated.
-The approach of @Ruths2014 has provided us with very useful insight on the selection of the direction of control and the utility of the concept of driver nodes for management applications.*
+Unfortunately, a network's control profile simply does not provide species-level information and hence we couldn't use it to our advantage.
+Nevertheless, as suggested here and by another reviewer, we have included a section in the Supporting Information (S2) where we explain that our networks are external dilation dominated.
+Consequently, the approach of @Ruths2014 has provided us with very useful insight on the selection of the direction of control and the utility of the concept of driver nodes for management applications (Lines 221--226 and 358--360).*
 
@@
 
-    *We have spell-checked all the text, and hope this time no typos have escaped from us.*
+    *We have spellchecked and revised all the text and hope that this time no typos have escaped us.*
 
@@
     *Thank you for pointing this out.
-We maintain the word throughout our manuscript because it is more intuitive to develop the intuition of readers more familiar with ecological and conservation terminology.
-However, we do not use the word "manageability" in lieu of "controllability" in our manuscript anymore, and maintain the control theory terminology, especially in the methods section.
-In addition we have enriched the references so that its easier for the readers  to trace back our approach to the control literature.*
+We still use the word within our manuscript because we found it is useful for to develop their intuition relative to ecological and conservation terminology.
+However, we do not use the word "manageability" as exchangable with "controllability" anymore and maintain the control-theory terminology, especially in the methods section.
+In addition, we have added additional references so that its easier for the readers to link back our approach to the control literature.*
 
@@
 
-    *We have now included comments about the general limitations of the structural controllability appriach in the "Theoretical Framework" section.
-Furthermore, we are now explicit abuout the fact that species have multiple types of interactions and therefore our approach can only provide a partial picture when only one type of interaction is included.
-We do so both the Introduction and the Discussion.
-Finally, we are also explicit about the fact that we do not advocate for management decisions to be based solely on our approach, but how it can "provide a simple, straightforward, and theoretically-informed indication of the degree to which the community is self-regulated and therefore how difficult it might be to modify its state in one way or another using some of the species that integrate it".*
+    *We have now included comments about the general limitations of the structural-controllability approach in the "Theoretical framework" section.
+Furthermore, we are now explicit about the fact that species have multiple types of interactions and therefore our approach can only provide a partial picture when only one type of interaction is included.
+We do so both the Introduction and the Discussion (Lines 83--85 and 399--400).
+Finally, we are also explicit about the fact that we do not advocate for management decisions to be based solely on our approach (Lines 381--383), but how it can "simple, straightforward, and theoretically informed indication of the degree to which the community is self regulated and therefore how difficult it might be to modify its state in one way or another using some of its constituent species" (Lines 387--392).*
 
@@
 
-    *As suggested we have conducted a sensitivity analysis in which we remove links from our empirical networks with a probability inversely proportional to their strength.
+    *As suggested, we have conducted a sensitivity analysis in which we remove links from our empirical networks with a probability inversely proportional to their strength.
 Due to space constraints, we have included the analysis in the Supporting Information S5.
-We found that our results are consistent even in serious cases of undersampling.*
+Notably, we found that our results are consistent even in serious cases of undersampling.*
 
@@
     *Thank you.
-We have apologise for the imprecision.
-The sentence now reads "To bridge this gap, we outline an approach to apply theory on the control of complex systems in an ecological context and implement them using empirical data.*
+We apologise for the imprecision.
+The sentence (Lines 70--71) now reads "To bridge this gap, we outline an approach to apply theory on the control of complex systems in an ecological context and implement it using empirical data".*
 
@@
     *Thanks.
-The subject was intended to be "control theory".
-We have rephrased the sentence to improve clarity and it now reads "Therefore, control theory could also be harnessed to provide an indication of which species are most relevant from a structural and dynamic perspective".*
+We have rephrased the sentence (Lines 53--54) to improve clarity and it now reads "Therefore, control theory could also be harnessed to provide an indication of which species are most relevant from a structural and dynamic perspective".*
 
@@
     *We based the direction of the hypothesis in the general feeling of failure of several restoration ecology programmes.
-However, in retrospect, we realise that we presented insuficient academic evidence to substantiate the hypotheis.
+However, in retrospect, we realise that we presented insufficient academic evidence to substantiate the hypotheis.
 Although the results have changed after the discovery of a mistake on the analysis, we have not changed the original direction of the hypothesis.
 Nevertheless, we have reframed the sentence to explain it better: "...
-grounded on the difficulties usually involved with invasive species eradication and ecosystem restoration [@Woodford2016], we ask whether invaded networks have lower levels of "manageability" than their uninvaded counterparts; that is, whether they require a greater proportion of species to be managed to achieve the same level of control"*
+grounded on the difficulties usually involved with invasive species eradication and ecosystem restoration [@Woodford2016], we ask whether invaded networks have lower levels of manageability than their uninvaded counterparts; that is, whether they require a greater proportion of species to be managed to achieve the same level of control"*
 
@@
 
-    *Thanks.
-We have rewritten a large section of the methods and tried to be more clear when defining new terms by providing some examples and using a more logical sequence to go from one concept to the next.
+    *We have rewritten a large section of the methods and tried to be more clear when defining new terms by providing some examples and using a more logical sequence to go from one concept to the next.
 We have also included a short glossary with the most important definitions at the end of the manuscript.*
@@
     *We have redesigned Figure 1 and now we indicate more clearly how the matching works and specify which are the superior, matched, and unmatched nodes.
-Also because we also illustrate the methods to obtain the relative importance, it is easier to highlight which are the key species in a simple network.*
+Because we also illustrate the methods to obtain the relative importance, it is now easier to highlight which are the key species in a simple network.*
 
@@
     *We apologise for the imprecision as we meant financial resources.
-We have modified the sentence to improve clarity and it now reads "Ecologically, these distinctions are relevant because management and conservation resources are limited and therefore ecological interventions should ideally be focused on species that might provide the largest impact."*
+We have modified the sentence to improve clarity (Lines 140--143) and it now reads "Ecologically, potential differences between species are acutely relevant because management and conservation resources are limited, and therefore ecological interventions should ideally be focused on the set of species that might provide the largest impact".*
 
@@
 
-    *We eliminated ambiguity by rephrasing the sentence. It now reads "... of the various covariates we explored, the ratio of plant to pollinator showed the strongest relationship with n~D~".*
+    *We have attempted to eliminate ambiguity by rephrasing the sentence (Lines 295--297).
+It now reads "...
+of the various covariates we explored, the ratio of plants to pollinators showed the strongest relationship with n~D~".*
 
@@
     *We apologise for the potential confusion.
-By "the strength of dependency we meant species strength as defined by @Bascompte2006.
+By "the strength of dependency" we meant species strength as defined by @Bascompte2006.
 We have modified the text in the Methods and the Results to avoid potential confusion.
-We also stick to dependence troughout the manuscript*
+We also stick to dependence throughout the manuscript*
 
@@
 
-    *Our results agree in fact agree with those of @Liu2011.
-However, this was confusing because our poor choice of terminology (we used driver species as a term to refer to species with a high probability of being superior nodes).
-Using our results, and insight obtained from @Ruths2014, we now explain that peripheral nodes tend to be driver because they are needed to achieve full control, but that network hubs are also often driver nodes, as they act as source nodes from which control signals can be transferred.
+    *In fact, our results agree with those of @Liu2011.
+However, this was likely confusing because our poor choice of terminology (we used driver species as a term to refer to species with a high probability of being superior nodes).
+Using our results, and insights obtained from @Ruths2014, we now explain that peripheral nodes tend to be driver because they are needed to achieve full control, but that network hubs are also often driver nodes, as they act as source nodes from which control signals can be transferred.
 Furthermore, our analysis at the species level is now more comprehensive, as it includes information on their role as both driver and superior nodes.*
@@
 We have now included explanatory arrows and modified the axis titles and the caption to facilitate the interpretation.
-Hopefully now it's much easier to understand.*
+Hopefully it's now much easier to understand.*
 
@@
 
-    *Following from the clarifications provided in the response two the comment for Line 336.
-We hope the discussion, which clearly distinguishes between driver and superior nodes explicates the apparent contrasting results.*
+    *The clarifications we provide in the response to the comment for Line 336 should help carify this comment as well.
+We hope that the discussion, which now clearly distinguishes between driver and superior nodes further explains the apparent contrasting results.*
 
@@
     *Thank you.
-We have implemented this suggestion and the text now reads "Not only it is hard to predict the direction in which the system will change, but also, invaded communities tend to be highly dependent on invaders and therefore acutely vulnerable to their eradication"*
+We have implemented this suggestion and the text (Lines 371-373) now reads "Not only it is hard to predict the direction in which the system will change, but invaded communities also tend to be highly dependent on invaders and therefore acutely vulnerable to their eradication"*
 

### 2017-02-28 paper/draft_2.Rmd
Add extra reference to Ruths in the methods

@@
 This simplification, while maintaining ecological realism, is advantageous for several reasons. 
-First, it is consistent with previous advances in structural controllability; second, it avoids complications related to the introduction of artificial control cycles; and third it significantly reduces the computational resources necessary for the application of our approach (Supporting Information S6).
+First, it is consistent with previous advances in structural controllability; second, it avoids complications related to the introduction of artificial control cycles [@Ruths2014]; and third it significantly reduces the computational resources necessary for the application of our approach (Supporting Information S6).
 Furthermore, we show that changing to unidirectional interactions determined by the observed direction of asymmetry, as a surrogate of bidirectional mutual dependences, does not alter the relative *n~D~* of different networks (Table S3).

### 2017-02-28 paper/supporting_information.Rmd
Rename files

--- 2017-02-28 paper/supp_info_2.Rmd
@@
 ---
-title: "The manageability of pollination networks in an invasion context"
+title: "Quantifying the manageability of pollination networks in an invasion context"
 subtitle: "Supporting Information"
@@
 
-```{r fig-f-s-rankings, echo = F, message = F, warning = F, fig.width = 6.2, fig.height = 9, results = "hide", fig.cap="**Frequency with which a species was classified as a superior node ($f_S$) as a function of the matching weight threshold**.
+```{r fig-f-s-rankings, echo = F, message = F, warning = F, fig.width = 6.2, fig.height = 9, results = "hide", fig.cap="**Relative requency with which a species was classified as a superior node ($f_S$) as a function of the matching weight threshold**.
 Rows correspond to network pairs.", cache = T}
@@
 
-```{r fig-f-d-rankings, echo = F, message = F, warning = F, fig.width = 6.2, fig.height = 9, results = "hide", fig.cap= "**Frequency with which a species was classified as a driver node ($f_D$) as a function of the matching weight threshold**.
+```{r fig-f-d-rankings, echo = F, message = F, warning = F, fig.width = 6.2, fig.height = 9, results = "hide", fig.cap= "**Relative frequency with which a species was classified as a driver node ($f_D$) as a function of the matching weight threshold**.
 Rows correspond to network pairs.", cache = T}

### 2017-02-28 paper/response_to_reviewers.Rmd
Remove date

---
title: "Response to reviewer comments ELE-00738-2016"
output: pdf_document
csl: ecology-letters.csl
classoption: a4paper
bibliography: references.bib
header-includes:
- \usepackage{setspace}
---

\onehalfspacing

## Response to the handling editor

We are thankful for the encouraging assessment that our work "has excellent potential" and "could have major impacts on applied ecology". 
We have fully addressed the flaws pointed by all the reviewers and, in the process, took advantage of this opportunity to incorporate some further changes that in our opinion improved the quality and thoroughness of our assessment.

The most substantial change is related to the earlier result that ecological invasions reduce the manageability of the studied pollination networks. 
After revising the manuscript, we found that the effect of invasion is actually the opposite of what we initially reported. 
This result arises from a regression in which the response variable was the proportion of driver nodes. 
Our previous conclusion arose from a mistake in our implementation of this regression for which we are extremely apologetic. 
In actual fact, the regression indicates that the invasion status is *inversely* related to $n_D$ (the density of driver nodes) as opposed to our previous definition of manageability $m = 1 - n_D$. 
After catching this error, the editor and reviewers will now note that revised result now contradicts our hypothesis and has also led to our having to amend the title of the paper. Nevertheless, we hope that you will agree that both our overall objective and the applicability of our approach is maintained.

Upon reflection, we also suspect that the root of the mistake was, as you and the reviewers helped point out, that our definition of manageability and its relation to the existing concept of controllability were overly confusing. 
In the revised paper, we refrain from giving a mathematical definition of manageability and instead focus on $n_D$, an unambiguous metric clearly defined in the structural controllability literature. 
We also extend these attempts to use the existing nomenclature rather than introduce new terms in our investigation of the relative importance of species. 
In the previous manuscript, we referred to species that were classified as superior nodes in all possible control strategies as *driver species*. 
Because of the strong similarities with the term *driver node*, which has been used in previous literature and that we also use in our manuscript, it was extremely easy to misinterpret the terms and completely follow our rationale. 
We have now removed the term driver species and instead focus on two well-defined metrics: $f_D$ and $f_S$, which correspond to the frequency to which a species is classified as a driver or superior node, respectively.

In addition, we now focus exclusively on the results obtained when we use the asymmetry of the dependences to direct the networks. 
We do so, because thanks to the reviewers comments, we identyfied some novel problems with the application of structural controllability when we use the mutual dependences into direct the network. 
Specifically, the problems arise from an absolute dominance of cycles and difficulties to the use of the maximum maximum matching algorithm to find a minimum set of driver nodes $D$. 
We elaborate on these on the new version in Lines 212--224 and Supporting Information S6.

Finally, we have made important modifications to the section in which we explain the theoretical underpinnings of structural controllability. 
We hope it is easier to follow both for experts and newcomers. 
We also have included a significant amount of detail and extra examples in the supplementary material to simplify the lives of those interested in applying the proposed approach or replicating our results.

## Reviewer 1

In ms ELE-00738-2016, the authors seek to apply ideas from control theory (specifically, structural controllability) to bipartite ecological networks. The main idea of structural control theory, at least in the recent applied literature, is that some nodes are recipients of external, time-varying control signals that proceed to propagate through a network in such a way as to drive the state of every node in the network to a desired configuration in finite time. There tend to be many ways to do this, and nodes can further be characterized by the frequency with which they exist on key paths leading through the network.

These ideas have been used as additional measures to describe the topological characteristics of networks as they relate to their control. The novelty of the present ms is in extending these ideas in a rigorous way to mutualistic ecological networks, which to my knowledge has not yet been done (some existing work includes ecological networks, but usually in a somewhat cursory way).

This is a powerful premise and, at least in principle, a ms with such a focus could be a good candidate for publication in Ecology Letters. However, I have numerous concerns with the manuscript. The methodological assumptions of structural control are never discussed (i.e., what is the assumed form of the dynamic relationship between interacting nodes?), the extent to which this is or is not realistic in an ecological context is not discussed (it seems to me that there are important caveats), other details of the theory are left unexplained, a key term is used in a different context than in the control literature (which will needlessly confuse readers), and some of the statistical analysis seems questionable.

I expound on this overview in some detail below. I regret that I cannot be more enthusiastic about the manuscript in its current form and I wish the authors luck as they revise their manuscript.

- The authors begin by stating, "Complex systems are characterised by non-linear relationships...", however, there is an entire branch of work devoted to network control that explicitly assumes linearity on the level of specific interaction (see e.g. doi 10.1126/science.1242063 and doi 10.1038/nature10011, both of which the authors cite). It seems to me that the authors could simply remove this bit of text and restructure the sentence to make the same point -- that complex systems are often viewed as being "greater than the sum of its parts."

    *Accepted; changed.*

- The paragraph on lines 50-62 cites papers published no earlier than 2011. However, to support the following argument "Despite these advances, the link between the structure of complex networks and our ability to manage and conserve them is still ambiguous", the authors cite a paper that predates all of them (Tylianakis et al. 2010). The paper in question highlights practical challenges to conservation; many if not all of them remain today (which I suspect is the authors' argument). I suggest the authors revise the text to make the contribution of this reference clear.

    *We have now revised the text to better reflect the contribution of @Tylianakis2010. At the same time, we added a reference to a more recent paper by @Kaiser-Bunbury2015 that explicitly deals with opportunities, limitations and implications of applying network metrics in conservation science.*

- Lines 95-97: "The number of nodes necessary to fully control a complex network can be calculated by counting the number of unmatched nodes in the network's maximum matching (Liu et al. 97 2011)." This statement must be contextualized by the assumed nature of the dynamical relationships in this framework. It therefore seems to me that this statement should be preceded by a discussion of those details (indeed, the authors argue that this is necessary in the Introduction, on lines 48-49). Furthermore, the authors need to discuss the appropriateness of this framework to ecological systems. The input control signals that drive even relatively simple networks to specified states can be very sensitive to initial conditions and complicated (indeed, they usually aren't calculated at all). How can a control scheme be implemented even in principle if nodes represent species populations and a control signal calls for a fractional change in a node state variable over the course of minutes?

    *Thanks for this comment and those from other reviewers which have helped us identify some shortcomings on the way we were introducing the control framework in the paper. In reposnse, we have largely rewritten the 'Theoretical framework' section. We start by offering a brief overview of control theory. In this overview, we emphasise our assumptions regarding the dynamical nature of the interactions. We then follow with a brief discussion that indicates how structural controllability is unable to provide information about the particulars of the control signal and the feasibility of its application. Without disregarding the usefulness of the proposed approach, we also mention at the end of the discussion how recently developed numerical methods [e.g. @Cornelius2013] might offer future avenues results in this regard (Lines 401--404)*

- Furthermore, how do the authors interpret the methods by which cycles are controlled in linear control theory (see e.g. doi 10.1126/science.1242063 and its supplementary material) in the context of ecological management? How frequent are cycles in the authors' ecological networks? I should emphasize that I am a fan of control theory and I think it is interesting to apply it as the authors do in this ms. However, the caveats that come along with the points I outline above need to be made clear for the reader. The authors might be interested in doi 10.1063/1.4931570 for a discussion of some relevant ideas.

    *Thanks for pointing this out. In fact, we explored the implementation of the approach of [@Ruths2014] at initial stages of the project. However, we earlier decided to exclude this approach from the final draft, mainly due to space limitations. Nevertheless, due to this comment and one of Referee 2 we have rediscovered its value and use it to support our decision to include the analysis of superior nodes, and not just driver nodes, in our manuscript. Though space constraints remain and we can only mention it briefly in the main text (Lines 358--360), we also dedicate a whole section in the Supporting Information (S2) to this subject. To summarise here, we found our networks weighted by asymmetry to be external dilation dominated, and hence have only a small number of cycles. Networks weighted by mutual dependences are dominated by cycles and hence challenging to address with our approach. In another section in the Supporting Information (S6), we discuss the implications of using these networks and our approach to circumvent them. Finally we are grateful for the reference to @Motter2015. We were unaware of this paper and it has been extremely useful to contextualise our work in the broader control-theory literature.*

- Lines 101-103: "(ii) the sum of the weights of the matched links—known as matching weight—is the largest possible among all possible matchings of that size (West 2001)." The authors go on to cite Liu et al. 2011, but that report (and many others cited in the present ms) considers "structural controllability", which assumes binary edge weights (i.e., they exist or they do not). Is condition (ii) appropriate here? If so, why? The authors get at this later in the ms (lines 145-152, where it looks as if edges are indeed binarized), but for readers familiar with the structural control literature, there is room for confusion as they come to this point in the ms. This may be mitigated as the authors address my comment 3, but it seems appropriate for me to raise this point explicitly as well.

    *The reviewer is absolutely correct most of the literature treats the problem of controlability on unweighted/binary networks. In that special case, maximum matchings are equivalent to maximum cardinality matchings. It has been shown, however, that the interaction weights carry important information in pollination networks about the patterns and processes in the community. In the paper, we use the visitation weights directly or indirectly in two different ways. First, we use them to determine the potential direction of control (via the dependence asymmetry). Second—which directly addresses the reviewer's comment—we use them to give priority to matchings that have the largest weight since these arguably have the largest impact on the network state for a given management intervention. Because the weights determine the dynamical relationships between species, our approach attempts to incorporate more ecological realism to the structural-controllability approach. We acknoweledge our earlier presentation of this rationale was confusing, especially for readers familiar with the control literature, and have therefore added a whole paragraph describing our rationale in the "Relative importance" subsection in the "Theoretical framework" section (Lines 154--168). To minimise potential confusions, we are more careful when introducing each of these concepts, and have added—as suggested by the reviewer—a glossary for easy reference.*

- When defining *n~d~* on line 119, it is more accurate to say that it is the "minimum number" of species needed to gain full control.

    *We have completely rewritten that section and the corresponding sentence (Lines 95--97) now reads "Conveniently the information necessary to determine the minimum number of driver nodes *D* in a network with linear dynamics is fully contained in the network structure..."*

- Lines 132-133: "...we therefore call driver species those that are identified as being a superior node in all possible matchings..."
I have several comments here. First, shouldn't this be "all possible maximum matchings"?

    *We are sorry for the imprecision. It should have been "all possible maximal-cardinality matchings". In any case, because of the reviewers' suggestion about the driver species concept, we have now removed this sentence altogether. We hope that the new text we have included in the "Relative importance" subsections, both in the "Theoretical framework" and "Empirical application" section, and in Supporting Information S7, helps clarify why our approach to identify species importance is not exclusively centred on maximum matchings.*

- Second, a node with no outgoing edges will clearly never be a superior node and will therefore not be a driver node. I assume that this never happens in the mutualistic networks under consideration, but this probably bears mentioning so as to help develop the reader's intuition for this assessment. In any event it would be useful for the reader to see a simple network (or several) to provide clear examples of driver nodes and non-driver nodes. For instance, how can a node with an outgoing edge not be a driver node?

    *Thanks to this suggestion and those of other reviewers, we have made important changes to Figure 1. In it, we include a better illustration of our methodology for a simple network while paying special effort to bring clarity to the different node categories of superior, driver, matched, and unmatched nodes. We hope the figure, in addition to our new introduction to the elements of a maximum matching, make the concept easier to understand.*

- Finally, the term "driver species" (or more generically, "driver node") has a specific meaning in the control literature (doi 10.1038/nature10011): what the authors here denote with n_d on line 118. To avoid confusion with those familiar with the control theory literature (and those readers who are inspired by this ms to delve into it), I suggest a change of terminology. Perhaps "key species"?

    *In hindsight, we agree that our choice of terminology was poor. We have eliminated the term "driver species", which had a different meaning to the usual concept of "control node", from the manuscript. Now, we stick to the terminology that is already used, and refrain for introducing a new term for species that are classified as superior nodes in all possible control strategies.*

- The approach described in lines 145-152 would be clearer if the authors included a figure demonstrating each step for a simple network.

    *Thanks for pointing this out. Exactly as suggested, we have included a figure that helps explain our method to compute all possible maximum cardinality matchings. Nevertheless, because of space limitations and because the methodology itself is not one of our main contributions, we have included the procedure and the figure in the Supporting Information (S1 and Figure S2).*

- Lines 173-176: "To do so, we calculated the maximum matching of the corresponding pollination network, and estimated the minimum proportion of species that need directed interventions to fully control the species abundances in the community." Why is this an estimate? The number of species that need to be directly controlled can be determined unambiguously.

    *We again apologise for the poor choice of words. As the referee points out it, this is not an estimation but an exact calculation. The sentence (Lines 190--192) now reads "To do so, we calculated the networks' maximum matching and determined the minimum proportion of species *n~D~* that need external input signals to fully control the species abundances in the community".*

- It seems to me that the number of interactions would also be an interesting factor to consider in the statistical analysis (discussed beginning on line 213).

    *Thanks for the observation. We have now included the network connectance as an extra explanatory variable. We included connectance (link density) and not the number of links, because it allows comparisons across multiple networks of differing size. We found it to have a negative and moderate relationship with the density of driver nodes.*

- Lines 225-228: "Previous research indicates a direct link between a network's degree distribution and the number of nodes necessary to fully control it (Liu et al. 2011), but the strength and applicability of this relationship has not been tested for in weighted ecological networks." The authors go on to discuss null models that vary edge weights. However (as mentioned in comment 4), it seems to me that the edge weight is ultimately not a factor when determining the manageability of the network, at least once it has been mapped to unidirectional and unweighted edges. The methodology and rationale here needs to be clarified. For instance, is the effect of changing edge weight restricted to affecting interaction asymmetry and thereby the unidirectional projection of the interactions? If so, how does this differ from the null model that does this explicitly (described on lines 239-246)? Does edge weight play any other role in this analysis? (Its role is clear in the section beginning on line 247.)

    *In retrospect, we realise that our rationale to include a randomisation of the link weights was not clear enough. As the referee points out, a change to the weights would only be reflected in a potential change on the interaction asymmetry. We identifyed two problems with this approach: first the changes aren't easily tractable, and second there is not a standard way to randomise weights in quantiative networks and the particular choice of the algorithm might influence the results. We therefore decided to remove the null model that maintained the degree of species and randomised the weight of the links as the effect of the asymmetry is explicitly tackled by the second approach in which we maintain the structure but randomise the asymmetries.*

- It seems useful to mention the typical size of the networks at the beginning of the results, if not earlier. In addition, the fact that the mean value of m is 0.37 means that roughly two thirds of the species in these communities need to be directly controlled, at least according to this modeling framework. It seems to me that this merits explicit comment in the Discussion.

    *Thanks for the suggestion. In the methods where we describe the empirical application, we now state the minimum, maximum, and the mean number of species for both the networks from Bristol, UK and Cap de Creus, Spain. In addition, now we briefly discuss the proportion of driver nodes we found in the pollination networks in the fourth paragraph of the Discussion. We also do so in the context of highlighting the potential caveats of one of our metrics of species importance.*

- Indeed, in the Discussion the authors say for example, "Because of their effects on other species in the community, driver species might be natural candidates for management interventions." This may be true, but it seems to me that the role of the directly-controlled species (that populate n_d), which serve as the gateway for the control signals to the rest of the network, merits discussion here as well. How are the two related? Do the authors envision a scenario where a control signal is actually being sent in to the network? Or do they rather envision a scenario where no controls are being used (which is counter to the central idea of structural controllability), and are they instead identifying these drivers nodes simply to provide a proxy measure of the effect of node state perturbations on the rest of the network? The latter seems more plausible than the former, but in any case more detail is needed.

    *We agree completely with the Reviewer here. Given that driver nodes have received a considerable amount of attention in the control literature, we now realise that neglecting them might be confusing, especially for readers familiar with control theory. We have fully incorporated this suggestion and our paper is now much more comprehensive. To determine the potential importance of a species in the revised manuscript, we determine not only its properties as a superior node but also its properties as a driver node. We have dedicated a large proportion of the discussion to discuss the advantages and limitations of each of these, plus how they relate to each other and to realistic management applications. To do build this discussion, we harnessed results from additional modelling analysis in the main text, as well as the lessons learned from the application of the @Ruths2014 control-profiles approach.*

- Figure 3 should show the distributions of m as well as the adjusted value of m. I suggest also providing more detail about how the adjusted value is calculated (in the current version there is one technical sentence that non-experts will not be able to follow).

    *We have now included a subpanel in Figure 3 that depicts the distribution of _n~D~_ for our empirical networks. The adjusted values were merely partial residuals of the fitted statistical models. We therefore have changed the axis titles to reflect this fact and avoid confusion.*

- In Appendix S2 (referenced in the ms on lines 205-208), the authors state that the relative number of driver species, while different for the approaches there discussed, are not significantly different from one another. However, the statistical test used is a Spearman correlation coefficient, which does not measure the difference in e.g. population means but rather the extent to which their relationship is monotonic.

    *This was a mistake on our part. We were not interested in determining whether the __absolute__ value of n~D~ differs among approaches, but instead, we wanted to determine whether the __relative__ values showed agreement. That is, our primary concern was to test whether networks with a high n~D~ under the asymmetry weighting also had a high n~D~ under the bidirectional dependences weighting. We have changed the text in the Supporting Information (S6) to improve clarity.*

- Minor comments. Line  236: there is a missing period.

    *Thanks for pointing this out. We have added the period.*

## Referee 2

This manuscript proposes to apply the methods published in previous papers (e.g. Liu et al, Nature 2011) on the controllability of complex systems to invaded pollination networks. Note that controllability is rebranded “manageability” (unless it has a different meaning in this paper?). The manuscript also proposes to identify the nodes to manage or driver species. This is a fascinating area of research.

Performing a controllability study on ten pairs of uninvaded and invaded plant-pollinator networks, the main finding is that invaded networks require a higher number of nodes to control than their non-invaded counterpart and invasive plants were driver species in all studied communities.
The study is scientifically sound. However the manuscript is dense and difficult to read. In particular the section Theoretical framework and its subsection are confusing and should be merged with the Methods section. The discussion should be strengthen.

In its current form, it is unlikely that readers will be able to understand or replicate the research presented – which is a shame considering the authors went through a lot of trouble to apply a control theory study in an ecological context. An overall simplification of the language/sentences and jargon used will increase the readability of this manuscript. Ruths (2014, Science) and Liu (2011, Nature) are doing a better job at explaining maximum matching, driver nodes and the overall challenge of controllability.

- Consider being more specific in your abstract.

    *Given the tight 150 word limit imposed by the journal, we had some trouble highlighting the novelty of our approach while also maintaining important details about the empirical application. We hope the revised version of the abstract is improved in this regard.*

- L74 “we expand previous theory of the control of complex systems to an ecological context”. Do you mean apply? Please clarify your contribution without ambiguity.

    *The sentence (Lines 70--71) now reads "To bridge this gap, we outline an approach to apply theory on the control of complex systems in an ecological context and implement it using empirical data."*

- Section Manageability (L94). Please first define manageability before maximum matching. Also, the maximum matching paragraph is difficult to understand. Reword.

    *In response to this and other comments, we have rewritten most of the "Theoretical framework" section. We start with a brief introduction to structural controllability, follow with a definition of manageability and finalise with details and computational and methodological considerations regarding its calculation.*

- Section Relative importance (L121). It seems that the abstract refers to this section as being a novel way to identify communities’ driver species. However it is very unclear that this is a novel contribution. Please clarify in the text and provide details in supplementary information. It is also unclear from the Methods section.

     *Thanks for the observation. As above, we have also reworded large segments of this section to make what are and what are not novel contributions clearer. Specifically, we now explain how the approach builds on existing structural-controllability theory by incorporating the weight of the interactions. In addition, although the concept of driver and superior nodes are not novel in the control theory literature, most of the previous studies tend to focus on a __single__ matching. Here, we instead exploit the fact that a single network may have multiple control configurations and evaluate the role of species in each of them. We now dedicate a large proportion of the discussion to these new metrics and how (even if not independent) they are conceptually different to previous attempts to rank species by importance. We also include extra development in the Supporting Information S7. Moreover, now we include more details about the rationale behind our approach. By being more specific, we hope the reader to be able to identify the theoretical and computational novelties of our approach with respect to existing "ranking" methods.*

- Discussion. McDonaldMadden et al (2016) actually show that network metrics are not useful to prioritise the management of foodweb, i.e. to determine which species should be managed first (if required). Please edit current text and analyse differences with your work.

    *Thank you for this suggestion. We acknowledge that we did a poor job embodying our work in the previous literature. We now include a paragraph in the discussion to explore the similarities and differences of our work with previous indices based on structural metrics. We explain (Lines 380--385) how "our approach... is not based on a single structural metric but instead acknowledges the existence of multiple management strategies. By allowing for the fact that some strategies are better than others depending on the context, control theory implicitly highlights that management decisions should not be based on a single technique". We also concur that more flexible approaches like ours and the one implemented by @McDonald-Madden2016 "that take a network-wide approach might prove more useful to guide ecosystem management if we want to go beyond using network metrics to minimise topological species loss".*

- Discussion. Please provide some insight into how your method/analysis/results would differ for non- pollinator invaded networks.

    *We now brifly mention in the Discussion (Lines 394--397) how "although our pollination specific results might not be directly translatable to other ecological systems because of the degree constrains imposed by bipartite networks, the approach we propose is applicable wherever species abundances are influenced by their interactions".*

- Discussion. Please discuss the caveats of your approach. I suggest moving some of the statistical analyses in sup info if word limit is an issue.

    *We agree that we did not previously discuss the assumptions and caveats of our approach with enough detail. As such, as we now try to better highlight the rationale behind our methods while being more explicit about the assumptions and limitations. Moreover we now provide a fairer assessment of the extent to which our approach might be useful for practical applications in the discussion.*

- The maximum matching algorithm is computationally expensive as noted by the authors. In Ruths & Ruths (2014) the authors come with an interesting alternative to calculate the minimum number of independent controls (driver species) using only the number of source nodes, external dilation points and internal dilation points; and a heuristic using source and sink nodes. What is the profile of the pollinator networks studied? Would the Ruths & Ruths approach be an easier way of reaching the same conclusions? Would it bring complementary information?

    *Calculating __one__ maximum matching for ecological networks with a few hundred species is not a computationally expensive operation, and therefore we use directly the algorithm and not the approximation proposed by @Ruths2014. Our most expensive computation was to find __all__ the possible maximum cardinality matchings to calculate species-level metrics. Unfortunately, a network's control profile simply does not provide species-level information and hence we couldn't use it to our advantage. Nevertheless, as suggested here and by another reviewer, we have included a section in the Supporting Information (S2) where we explain that our networks are external dilation dominated. Consequently, the approach of @Ruths2014 has provided us with very useful insight on the selection of the direction of control and the utility of the concept of driver nodes for management applications (Lines 221--226 and 358--360).*

- A few typos in main text and sup info.

    *We have spellchecked and revised all the text and hope that this time no typos have escaped us.*

- Is there a compelling reason to change controllability to “manageability”? Walters did the same thing with “adaptive management” in lieu of “adaptive control”. 30 years later, no one remembers where “adaptive management” originally came from and it has become a keyword in ecology. As a result, ecologists have been cut from the theoretical advances in control theory and most often have no clue that these are the same thing.

    *Thank you for pointing this out. We still use the word within our manuscript because we found it is useful for to develop their intuition relative to ecological and conservation terminology. However, we do not use the word "manageability" as exchangable with "controllability" anymore and maintain the control-theory terminology, especially in the methods section. In addition, we have added additional references so that its easier for the readers to link back our approach to the control literature.*

## Referee 3

In this work Cagua et al apply tools rooted in control theory to ecological networks and discuss how this approach could be used for management of natural systems, with emphasis on the effects of invasive species. This is an exciting work. It presents to ecologists a novel way of studying the relationship between topology and dynamics that is less dependent (when compared to other methods) on particular choices about how dynamics are modeled. The authors illustrate the potential of this approach by exploring how invasive species change system dynamics and manageability. My only concern about this manuscript is that the authors need to be more careful and more explicit about some limitations of this approach and the generality of their results, specially considering the implications of their results for management.

- Only one type of interaction is being considered here when species are involved in multiple types of interactions. An assumption that is not explicit in the text is that all the factors controlling population densities are the interactions between plants and pollinators. The boundaries of a network, including the types of interactions that are considered or not, are often arbitrarily defined. However, this approach is highly dependent on the topology of the network and thus on how we define the network. I know this limitation applies to any study on system dynamics, but it becomes more serious when we argue that management decisions can be based on a single technique. I have two suggestions. First, the authors should discuss in detail these assumptions and their limitations.

    *We have now included comments about the general limitations of the structural-controllability approach in the "Theoretical framework" section. Furthermore, we are now explicit about the fact that species have multiple types of interactions and therefore our approach can only provide a partial picture when only one type of interaction is included. We do so both the Introduction and the Discussion (Lines 83--85 and 399--400). Finally, we are also explicit about the fact that we do not advocate for management decisions to be based solely on our approach (Lines 381--383), but how it can "simple, straightforward, and theoretically informed indication of the degree to which the community is self regulated and therefore how difficult it might be to modify its state in one way or another using some of its constituent species" (Lines 387--392).*

- Second, It would be helpful if the authors could test the robustness of their results to sampling. The results show that invasive species change manageability. This suggests that manageability may be sensitive to sampling. A sensitivity analysis where species are added and removed from the network under different wiring schemes would help us understand the behavior of the manageability index when networks are undersampled and would allow a more informed discussion on how the choices we make when delimiting the network affect estimates of controllability. Weak links should not have a strong effect on controllability and considering the networks were built using visitation frequency, most of the strong interactions were likely sampled. Still, it would be great to show that the method is robust and this would make it easier to justify that even in the absence of complete sampling this technique is in fact useful for management.

    *As suggested, we have conducted a sensitivity analysis in which we remove links from our empirical networks with a probability inversely proportional to their strength. Due to space constraints, we have included the analysis in the Supporting Information S5. Notably, we found that our results are consistent even in serious cases of undersampling.*

- Ln 25. I don't think that the statement that you "expand theory on the controllability of complex systems" is accurate. It is not clear to me how these results contribute to expand the general theory

    *Thank you. We apologise for the imprecision. The sentence (Lines 70--71) now reads "To bridge this gap, we outline an approach to apply theory on the control of complex systems in an ecological context and implement it using empirical data".*

- Ln 52, typo: presents

    *Thanks. It's been changed.*

- Ln 59. Please rewrite this sentence. it's not clear what "they" refers to here.

    *Thanks. We have rephrased the sentence (Lines 53--54) to improve clarity and it now reads "Therefore, control theory could also be harnessed to provide an indication of which species are most relevant from a structural and dynamic perspective".*

- Ln 78. It is not clear why this is the direction of the hypothesis. Did you already have any indication that networks with invasive species should have lower manageability? Is there any theoretical explanation for this expectation?

    *We based the direction of the hypothesis in the general feeling of failure of several restoration ecology programmes. However, in retrospect, we realise that we presented insufficient academic evidence to substantiate the hypotheis. Although the results have changed after the discovery of a mistake on the analysis, we have not changed the original direction of the hypothesis. Nevertheless, we have reframed the sentence to explain it better: "... grounded on the difficulties usually involved with invasive species eradication and ecosystem restoration [@Woodford2016], we ask whether invaded networks have lower levels of manageability than their uninvaded counterparts; that is, whether they require a greater proportion of species to be managed to achieve the same level of control"*

- Ln 95-98. It is very hard to keep track of all those definitions - matching, matched nodes, matched links, matching size, matching weight, maximum matching. I found myself going back and forth several times between the framework, methods and results sections. A glossary would help a lot.

    *We have rewritten a large section of the methods and tried to be more clear when defining new terms by providing some examples and using a more logical sequence to go from one concept to the next. We have also included a short glossary with the most important definitions at the end of the manuscript.*

- Ln 99. Indicate how the matching is represented in the figure. e.g.,  "(dark grey links in Figure 1a)". Figure 1.Indicate the driver nodes in these networks

    *We have redesigned Figure 1 and now we indicate more clearly how the matching works and specify which are the superior, matched, and unmatched nodes. Because we also illustrate the methods to obtain the relative importance, it is now easier to highlight which are the key species in a simple network.*

- Ln 128. Be clear about the meaning of resources here. I understand you mean financial resources not  resources in the ecological sense.

    *We apologise for the imprecision as we meant financial resources. We have modified the sentence to improve clarity (Lines 140--143) and it now reads "Ecologically, potential differences between species are acutely relevant because management and conservation resources are limited, and therefore ecological interventions should ideally be focused on the set of species that might provide the largest impact".*

- Ln 236. Typo: missing period

    *Thanks. We corrected it.*

- Ln 293: Typo: reference

    *Thanks. We corrected it.*

- Ln 303-305. Please explain here which is the response variable that the ratio of plant to pollinator can explain.

    *We have attempted to eliminate ambiguity by rephrasing the sentence (Lines 295--297). It now reads "... of the various covariates we explored, the ratio of plants to pollinators showed the strongest relationship with n~D~".*

- Ln 326. "The strength of the dependency" has been defined as species strength by Bascompte et al. 2006. Why are you using a different term here?  When you say strength of the dependency it is not clear if you mean strength of dependencies of a given species on other species or the strength of the dependencies of all species on the species of interest. Moreover sometimes you use dependence and others dependency.

    *We apologise for the potential confusion. By "the strength of dependency" we meant species strength as defined by @Bascompte2006. We have modified the text in the Methods and the Results to avoid potential confusion. We also stick to dependence throughout the manuscript*

- Ln 336. Liu et al. 2011 found that driver nodes were often peripheral nodes in the network instead of network hubs. Here you find the opposite. How can you explain these differences?

    *In fact, our results agree with those of @Liu2011. However, this was likely confusing because our poor choice of terminology (we used driver species as a term to refer to species with a high probability of being superior nodes). Using our results, and insights obtained from @Ruths2014, we now explain that peripheral nodes tend to be driver because they are needed to achieve full control, but that network hubs are also often driver nodes, as they act as source nodes from which control signals can be transferred. Furthermore, our analysis at the species level is now more comprehensive, as it includes information on their role as both driver and superior nodes.*

- Ln 343 and Figure 4. Here and in the figure legend you say the level of manageability of empirical networks is lower, but in the figure you show an index that goes in the opposite direction, i.e.,  we see lower values for the randomization. It would be better to present these results in a more intuitive way.

    *Figure 4 represents the rank of the emprical network compared to that of the randomisations. We have now included explanatory arrows and modified the axis titles and the caption to facilitate the interpretation. Hopefully it's now much easier to understand.*

- Ln 362. Again the idea that supergeneralists tend to be driver species contrasts with Liu et al. results. This should be explored in more detail in the discussion.

    *The clarifications we provide in the response to the comment for Line 336 should help carify this comment as well. We hope that the discussion, which now clearly distinguishes between driver and superior nodes further explains the apparent contrasting results.*

- Ln 372. It is important to say that vulnerability is related change, but that it is had to predict in which direction the system will change

    *Thank you. We have implemented this suggestion and the text (Lines 371-373) now reads "Not only it is hard to predict the direction in which the system will change, but invaded communities also tend to be highly dependent on invaders and therefore acutely vulnerable to their eradication"*

- Figure 5 legend. Please include here the definition of dependency strength so the reader does not need to go back and forth.

    *Done.*

## References

### 2017-02-28 paper/supporting_information.Rmd
Don't keep tex file

@@
     fig_crop: no
-    keep_tex: yes
   html_document: default

### 2017-03-01 paper/manuscript.Rmd
the abstract now has 148 words

--- 2016-07-18 paper/manuscript.Rmd
@@
 ---
-title: "Biotic invasions reduce the manageability of pollination networks"
+title: "Quantifying the manageability of pollination networks in an invasion context"
+classoption: a4paper
 csl: ecology-letters.csl
-output: html_document
+output:
+  pdf_document:
+    fig_crop: no
+    includes:
+      after_body: after_body.md
+  html_document: default
+  word_document: default
+header-includes:
+- \usepackage{setspace}
+- \usepackage{float}
+- \usepackage{booktabs}
+- \usepackage{tocloft} 
+- \usepackage{caption}
+- \captionsetup{labelsep=none,textformat=empty}
+- \usepackage{lineno}
+- \usepackage[nomarkers,tablesfirst, nolists]{endfloat}
+- \cftpagenumbersoff{figure}
+- \cftpagenumbersoff{table}
+documentclass: artikel1
 bibliography: references.bib
@@
 
-```{r libraries, echo = FALSE, warning = F, message = F}
+\doublespacing
+\linenumbers
+\renewcommand*\listfigurename{Figure legends}
+\renewcommand*\listtablename{Table legends}
+
+```{r libraries, echo = F, include = F}
+library(igraph)
 library(magrittr)
-library(knitr)
+library(dplyr)
+library(latex2exp)
 library(ggplot2)
 library(glmulti)
-library(Hmisc)
 library(lme4)
-opts_knit$set (root.dir=normalizePath('../'))
-```
-
-```{r auxiliary functions, echo = FALSE, warning = F, message = F}
-"./code/functions" %>% 
+library(grid)
+
+"../code/functions" %>% 
 	list.files(full.names = T) %>%
 	plyr::l_ply(source)
-```
-
-```{r plot theme, echo = FALSE, warning = F, message = F}
-fer_theme <- theme_bw() +
-	theme(text = element_text(family = "Times"),
-	      title = element_text(size = 7.5, hjust = 0),
-	      legend.title = element_text(size = 9),
-	      legend.text = element_text(size = 8),
-				axis.text = element_text(size = 8),
-				axis.title = element_text(size = 9, hjust = 0.5), 
-				strip.text = element_text(size = 9, hjust = 0), 
-				strip.background = element_blank(),
-				plot.margin = grid::unit(c(5, 0, 2, 0), "mm"))
-```
-
-```{r read data and results, echo = FALSE, warning = F, message = F}
-net <- "./data/processed/networks" %>%
+
+"../code/plotting_functions" %>% 
+	list.files(full.names = T) %>%
+	plyr::l_ply(source)
+
+```
+
+```{r load data, include = F}
+net <- "../data/processed/networks" %>%
 	read_networks()
-meta <- readr::read_csv("data/ntw_info.csv") %>% dplyr::tbl_df() %>%
+meta <- readr::read_csv("../data/ntw_info.csv") %>% dplyr::tbl_df() %>%
 	dplyr::rename(count = method)
-n_matched <- readRDS("./data/processed/n_matched.rds")
-a_m <- readRDS("./data/processed/n_matched_all_types.rds") 
-r_w <- readRDS("./data/processed/random_weights.rds") %>% dplyr::tbl_df() %>%
+n_driver <- readRDS("../data/processed/n_driver.rds")
+manag_models <- readRDS("../data/processed/models_manageability.rds")
+src_bi_w <- readRDS("../data/processed/manageability_bi_vs_weight.rds")
+r_w <- readRDS("../data/processed/random_weights.rds") %>% dplyr::tbl_df() %>%
   dplyr::rename_("net_name" = ".id")
-r_d <- readRDS("./data/processed/random_directions.rds") %>% dplyr::tbl_df() %>%
+r_d <- readRDS("../data/processed/random_directions.rds") %>% dplyr::tbl_df() %>%
   dplyr::rename_("net_name" = ".id")
-s_p <- readRDS("./data/processed/species_properties.rds") %>% dplyr::tbl_df()
-# mod <- readRDS("./data/V2.0/species_models.rds")
-driver <- c("./data/processed/matching_frequency") %>% 
+
+prop <- expand.grid(c("asymmetry", "max_dep"), 
+                    c("scaled_FALSE", "scaled_TRUE")) %>% plyr::alply(1)
+driver <- c("../data/processed/matching_frequency") %>% 
   list.files(full.names = T) %>%
@@
   lapply(read_allRDS)
-prop <- expand.grid(c("asymmetry", "max_dep"), 
-                    c("scaled_FALSE", "scaled_TRUE")) %>% plyr::alply(1)
 driver <- mapply(function(x, y){
@@
 }, driver, prop)
-driver_bi <- "./data/processed/matching_frequency_bi" %>% 
+driver_bi <- "../data/processed/matching_frequency_bi" %>% 
   read_allRDS()
-mod <- readRDS("./data/processed/detailed_species_models.rds")
-mo <- readRDS("./data/processed/detailed_species_models_data.rds")
-```
-
-**E. Fernando Cagua^\*^, Kate L Wootton^§^, Daniel B. Stouffer^#^**
-
-Centre for Integrative Ecology, School of Biological Sciences, University of Canterbury, Private Bag 4800, Christchurch 8041, New Zealand
+mod <- readRDS("../data/processed/detailed_species_models.rds")
+mo <- readRDS("../data/processed/detailed_species_models_data.rds")
+```
+
+```{r plot theme, echo = FALSE, warning = F, message = F}
+fer_theme <- theme_bw() +
+	theme(text = element_text(family = "Helvetica"),
+	      title = element_text(size = 7, hjust = 0),
+	      legend.title = element_text(size = 8),
+	      legend.text = element_text(size = 7),
+				axis.text = element_text(size = 7),
+				axis.title = element_text(size = 8, hjust = 0.5), 
+				strip.text = element_text(size = 8, hjust = 0), 
+				strip.background = element_blank(),
+				plot.margin = grid::unit(c(5, 0.5, 2, 0), "mm"),
+				panel.grid = element_blank())
+```
+
+```{r example networks, include = F, message = F, warning = F, }
+
+sp_names_fancy <- c(TeX("$p_1$"), TeX("$p_2$"), TeX("$p_3$"), TeX("$a_1$"), TeX("$a_2$"))
+sp_names_fancy_b <- c(TeX("$\\mathbf{p_1}$"), TeX("$\\mathbf{p_2}$"), TeX("$\\mathbf{p_3}$"), TeX("$\\mathbf{a_1}$"), TeX("$\\mathbf{a_2}$"))
+
+sp_names <- c("p1", "p2", "p3", "a1", "a2")
+
+adj_matrix <- c(0,0,0,1,0,
+								0,0,0,2,5,
+								0,0,0,0,0,
+								0,0,1,0,0,
+								0,0,1,0,0) %>%
+	matrix(nrow = 5, byrow = T)
+
+example_net <- adj_matrix %>% 
+	graph_from_adjacency_matrix(mode = "undirected", weighted = TRUE) 
+igraph::V(example_net)$type <- c(F, F, F, T, T)
+igraph::V(example_net)$name <- sp_names
+
+base_net <- example_net
+bi_net <- example_net %>%
+	keep_largest_component() %>%
+	bipartite_digraph(type = "z-bi", weight.type = "asymetry") 
+as_net <- example_net %>%
+	keep_largest_component() %>%
+	bipartite_digraph(type = "weight", weight.type = "asymmetry")
+
+fam <- "Helvetica"
+# layout is based on the bidirectional network
+set.seed(1)
+
+lay <- bi_net %>%
+	layout_nicely()
+v_c <- "white"
+l_c <- "black"
+l_s <- 0.9
+ma <- c(0,0,0,0)
+label_pos_x <- -1
+label_pos_y <- 1
+
+pal <- RColorBrewer::brewer.pal(5, "PuOr")
+```
+
+**E. Fernando Cagua^1\*^, Kate L. Wootton^1,2§^, Daniel B. Stouffer^1#^**
+
+^1^ Centre for Integrative Ecology, School of Biological Sciences, University of Canterbury, Private Bag 4800, Christchurch 8041, New Zealand
+
+^2^ Current address: Department of Ecology, Swedish University of Agricultural Sciences, Box 7044, SE-750 07 Uppsala, Sweden
 
@@
 
-* **Number of words:** ~ 151 abstract; ~ 4790 main text.
-
-* **Number of references:** ~ 61
+* **Number of words:** 160 abstract; approx. 5600 main text.
+
+* **Number of references:** 72
 
@@
 
-* **Authorship:** DBS conceived the idea; EFC, KLW and DBS contributed to the development of the theoretical framework. EFC performed all analysis. EFC and DBS wrote the manuscript.
+* **Authorship:** DBS conceived the idea; all authors contributed to the development of the theoretical framework.
+EFC performed all analysis.
+EFC and DBS wrote the manuscript.
+All authors contributed to its revision.
 
@@
 
+\newpage
+
 # Abstract
 
-It is generally unknown how the disruptions caused by perturbations such as biotic invasions, affect our ability to manage ecological communities. 
-Here, we expand current theory on the controllability of complex systems to quantitatively assess the theoretical (relative) manageability of ten pairs of uninvaded and invaded plant-pollinator communities.
-Intriguingly, we found that invaded pollination networks might be more resilient than their uninvaded counterparts as they showed substantially lower levels of manageability.
-We also developed theory to help identify each community's driver species—those most important to manage because of their disproportionate potential to affect the abundances of all other species. 
-Remarkably, invasive plants were found to be driver species in every community in which they were found; their dominant position was generally underpinned by high asymmetry in the dependence of their interaction partners.
-Our results provide a theoretical explanation for the known challenges associated with the restoration of invaded communities, and also provide insight into the design of informed management interventions.
-
-*Shorter version*: 
-It is generally unknown how the disruptions caused by perturbations like biotic invasions, affect our ability to manage ecological communities. 
-Here, we expand current theory on the controllability of complex systems to assess the theoretical manageability of ten pairs of uninvaded and invaded plant-pollinator communities.
-We found that invaded pollination networks might be more resilient than their uninvaded counterparts as they showed substantially lower manageability.
-We also identify each community's driver species—those most important to manage because of their disproportionate potential to affect the abundances of all other species. 
-Remarkably, invasive plants were found to be driver species in every community in which they were found; their dominant position was generally underpinned by high asymmetry in the dependence of their interaction partners.
-Our results provide a theoretical explanation for the known challenges associated with the restoration of invaded communities, and also provide insight into the design of informed management interventions.
+Here, we leverage recent advances in control theory to assess the "manageability" of ten pairs of uninvaded and invaded plant-pollinator communities. 
+We found that the networks' manageability is most strongly determined by the ratio of plants to pollinator richness, which in turn constrains the networks' degree distribution. 
+We also characterise species' suitability for inclusion in management interventions by exploring the entire space of control strategies. 
+Specifically, we measure the extent to which species (i) are necessary to steer the state of the community and (ii) are able to affect the abundance of other species. 
+We found that invasive plants have a dominant position in every invaded community and that this dominance is underpinned by high asymmetry in the dependence of their interaction partners. 
+Our results highlight the advantages of the control-theoretic framework for ecological questions and provide novel insight into the design of informed management interventions.
+
+\newpage
 
@@
 
-Complex systems are characterised by non-linear relationships in which the whole is greater than the sum of its parts [@Jorgensen1998; @Levin1999; @Montoya2006].
+Complex systems are characterised by relationships in which the whole is often greater than the sum of its parts [@Jorgensen1998; @Levin1999; @Montoya2006].
 Within community ecology, a complex systems approach has led to the development of a variety of analytical and simulation tools with which to understand, for example, the role of species when embedded in an intricate network of interactions [@Pascual2005; @Bascompte2009; @Stouffer2012].
-The inherent complexity of nature, however, has hindered—or at least greatly complicated—our ability to find management solutions to the many problems ecological communities face. 
-To overcome this obstacle, we require a framework that allow us to explain, predict, and manage ecological communities, particularly when they are faced with perturbations [@Sole2001; @Green2005].
-Moreover, such a framework needs to be able to account for their complex structure, and the dynamics that determine the state of each species, and the community as a whole.
-
-Among the various possibilities, control theory appears to be a strong candidate as it is designed to deal with determining and supervising the behavior of general dynamical systems, and is well equipped to deal with the many feedbacks presents in ecological communities [@Liu2015].
-Research in the field has established a strong link between the structure of complex networks and their controllability, while also demonstrating that it is in principle possible to alter a whole ecological community's composition by modifying the abundances of only a few species [@Liu2011; @Cornelius2013; @Ruths2014].
-Applications of control theory to ecological networks can also take into account the extent to which changes in the abundances of one species may ripple through the community [@Cornelius2013].
-Therefore, they can provide an indication of which species are most relevant
-from a dynamic perspective, a particularly important feature given that these
-species should underpin informed attempts to both alter or maintain the ecosystem state.
-
-Despite these advances, the link between the structure of complex networks and our ability to manage and conserve them is still ambiguous [@Tylianakis2010].
-To complicate things further, biotic invasions—a major driver of global change—can induce dramatic changes on the patterns of interactions that determine the structure of ecological networks [@Baxter2004; @Tylianakis2008; @Ehrenfeld2010a].
-Although understanding how differences in network structure before and after the invasion impact our ability to manage them presents a double challenge, it is a critical first step towards a fully informed recovery.
-Despite the apparent overlap, a control-theoretic perspective has not been widely adopted in an invasion context. 
-This is perhaps because of a lack of appropriate methodological tools that can account for observed variation on the strength of interspecific effects that are characteristic of ecological networks [@Liu2011; @Isbell2013].
-
-To bridge this gap, we expand previous theory of the control of complex systems to an ecological context.
-We then use a set of ten pairs of uninvaded and invaded plant-pollinator communities to investigate the link between invasion, network structure and ecological management. 
-We ask two specific questions framed in the context of a plant invasion.
-First, we ask whether invaded networks have lower levels of manageability than their uninvaded counterparts; that is, whether they require a greater proportion of species to be managed to achieve the same level of control.
+The inherent complexity of nature, however, has regularly hindered—or at least greatly complicated—our ability to find management solutions to the many problems ecological communities face. 
+To overcome this obstacle, we require a framework that allows us to explain, predict, and manage ecological communities, particularly when they are confronted with perturbations [@Sole2001; @Green2005].
+Ideally, such a framework needs to be able to account for their complex structure and the dynamics that determine the species abundances and the state of the community.
+
+Among the various possibilities, *control theory* appears to be a strong candidate [@Isbell2013].
+This method, widely used in engineering to determine and supervise the behaviour of dynamical systems [@Motter2015], is well equipped to deal with the many feedbacks present in ecological communities [@Liu2016].
+Research in this area has established a strong link between the structure of complex networks and their *controllability*—the relative ability to manipulate network components to drive the system to a desired state [@Liu2011; @Cornelius2013; @Ruths2014].
+These advances suggest that it is in principle possible to alter a whole ecological community's composition by modifying the abundances of only a few species.
+Furthermore, applications of control theory to ecological networks can also take into account the extent to which changes in the abundances of one species may ripple through the community [@Cornelius2013].
+Therefore, control theory could also be harnessed to provide an indication of which species are most relevant from a structural and dynamic perspective.
+
+This information is valuable not only for basic ecology, but it might be also relevant to address more applied management and conservation challenges. 
+This is particularly true in the context of biotic invasions, where identifying key players in the community is a prerequisite to informed attempts to either alter the state of invaded ecosystem and maintain the state of uninvaded ones.
+Despite recent advances in network theory, practical challenges to the conservation of interaction networks persist [@Tylianakis2010], and the link between the structure of complex networks and our ability to manage and conserve them is still ambiguous [@Bluthgen2010; @Kaiser-Bunbury2015].
+To complicate things further, biotic invasions can induce dramatic changes in the patterns of interactions that determine the structure of ecological networks [@Baxter2004; @Tylianakis2008; @Ehrenfeld2010a].
+Understanding how the differences in network structure before and after the invasion impact our ability to manage the communities is thus a double challenge, but it is also the critical first step towards a fully informed recovery.
+Despite the apparent overlap, a control-theoretic perspective has not been adopted in an invasion context. 
+This is perhaps because of a lack of appropriate methodological tools that can account for the observed variation in the strength of interspecific effects that are characteristic of ecological networks [@Liu2011; @Isbell2013].
+
+To bridge this gap, we outline an approach to apply theory on the control of complex systems in an ecological context and implement it using empirical data.
+Specifically, we use a set of ten pairs of uninvaded and invaded plant-pollinator communities to investigate the link between invasion, network structure and ecological management. 
+While doing so, we focus on two particular questions.
+First, grounded in the difficulties usually involved with invasive-species eradication and ecosystem restoration [@Woodford2016], we ask whether invaded networks have lower levels of "manageability" than their uninvaded counterparts; that is, whether they require a greater proportion of species to be managed to achieve the same level of control.
 Second, we ask whether some species are more important than others at driving the population dynamics of the community and which factors determine this importance. 
-We focus on these particular applications for a variety of reasons. 
-First, biotic invasions are known to produce tractable changes in the structure of ecological networks, and these changes can be particularly pronounced in mutualistic networks between plants and pollinators where biotic invasions have been shown to modify the strength of species interactions and the degree of network nestedness and connectivity [@Olesen2002; @Aizen2008; @Bartomeus2008; @Vila2009; @Traveset2013].
-Second, plant-pollinator networks provide an ideal framework to answer these questions. 
-On one hand, community networks that quantify relative levels of interaction are readily available. 
+We focus on these two particular applications for a variety of reasons. 
+Biotic invasions are known to produce tractable changes in the structure of ecological networks, and these changes can be particularly pronounced in mutualistic networks between plants and pollinators where biotic invasions have been shown to modify the strength of species interactions and the degree of network nestedness and connectivity [@Olesen2002; @Aizen2008; @Bartomeus2008; @Vila2009; @Traveset2013].
+Furthermore, although species are involved in multiple types of interactions, plant-pollinator networks provide an ideal framework to answer these questions. 
+On the one hand, community networks that quantify relative levels of interaction are readily available. 
 On the other, the bipartite nature of pollination networks makes it possible to simplify assumptions of how these interactions translate into interspecific effects.
 
+# Methods
+
 ## Theoretical framework
 
+Disregarding practical considerations, any network (community) could hypothetically be fully controlled if we control the state of every single node (species) individually.
+At the core of control theory of complex networks, however, rests the idea that the state of a node depends on the state of the nodes it interacts with, and the particular form of this dependence is determined both by the dynamic relationship among interacting nodes as well as the structure of the links in the network.
+This principle can therefore be harnessed to find a subset of *driver nodes* to which to apply external input signals which then drive the state of every other node in the network to a desired configuration.
+
+Conveniently the information necessary to determine the minimum number of driver nodes *D* in a network with linear dynamics is fully contained in the network structure [@Kalman1963; @Liu2011; @Motter2015].
+We therefore start here from the assumption that an ecological network can, at least near equilibrium points, be described by $\frac{dx}{dt} = Ax + Bu(t)$, where the change over time of its state ($\frac{dx}{dt}$) depends on its current state *x* (for example the species' abundances), an external time-varying input *u(t)*, and two matrices *A* and *B*, which encapsulate information about the network structure and how the species respond to the external input, respectively.
+Even though linearity might be a strong assumption, it has been shown that fundamental insight about the control of complex systems can be gained without a detailed knowledge of the nonlinear dynamics and the system parameters [@Liu2016], an important step towards ultimately understanding the controllability of systems with nonlinear dynamics [@Liu2011].
+This means that structural controllability can be applied to a wide range of readily available network representations of ecological communities to provide a strong indication of our ability to control them.
+Moreover, we show here how quantitative data about species interactions can help us move past some of the limitations of structural controllability by better approximating the role of interspecific dynamical relationships without being overly dependent on the specific choices of how these dynamics are modelled or characterised.
+
 ### Manageability
 
-The number of nodes necessary to fully control a complex network can be calculated by counting the number of unmatched nodes in the network's maximum matching [@Liu2011]. 
-In a directed network, a given matching is a subset of links in which no two links share a common starting node or a common ending node; a node is then matched if it is the ending node of one of the links in the matching and unmatched otherwise (Figure 1a).
-A given matching is then maximum if both *(i)* the number of matched links—known as matching size—is maximal and *(ii)* the sum of the weights of the matched links—known as matching weight—is the largest possible among all possible matchings of that size [@West2001].
-To find the maximum matching, it is convenient to adopt an alternative bipartite representation of the network in which the two levels indicate the outgoing and incoming links to each node (Figure 1b).
-Finding a matching in this alternative representation is equivalent to finding a set of links such that each node on the top level is matched to at most one node on the bottom level, and vice versa [@West2001; @Csardi2006a].
-
-```{r fig_explain-mm, message=FALSE, warning=FALSE, include=FALSE}
-
-sp_names <- c("a[1]", "a[2]", "a[3]", "p[1]", "p[2]")
-
-adj_matrix <- c(0,0,0,1,0,
-								0,0,0,1,1,
-								0,0,0,0,0,
-								0,0,1,0,0,
-								0,0,1,0,0) %>%
-	matrix(nrow = 5, byrow = T) %>%
-	`rownames<-`(sp_names) %>%
-	`colnames<-`(sp_names)
-
-net <- adj_matrix %>% 
-	igraph::graph_from_adjacency_matrix(mode = "directed") 
-igraph::V(net)$type <- c(F, F, F, T, T)
-igraph::E(net)$weight <- 1
-
-layoutCoordinates <- cbind(c(0,1,2,0.5,1.5), 
-													 c(1,1,1,0,0)) %>%
-	`colnames<-`(c("x", "y"))
-
-adj_list <- adj_matrix %>% 
-	reshape2::melt() %>% 
-	dplyr::filter(value > 0)
-
-# Generate an edge path for each pair of connected nodes
-n <- 17
-allEdges <- lapply(1:nrow(adj_list), edgeMaker, len = n, curved = FALSE)
-allEdges <- do.call(rbind, allEdges) %>%
-	dplyr::filter(Sequence != n) %>%
-	dplyr::mutate(Group = factor(Group),
-				 type = Group)
-
-new_lev <- c("m", "u", "m", "m", "u")
-levels(allEdges$type) <- new_lev
-
-nodes <- data.frame(layoutCoordinates) %>%
-	dplyr::mutate(spe = sp_names,
-								spe_c = c("m", "m", "u", "m", "u"), 
-								pos = rep(c(0.3, -0.3), c(3,2)))
-
-p1 <- ggplot(allEdges) +  # Pretty simple plot code
-	geom_path(aes(x = x, y = y, group = Group, colour = type, size = type), 
-						arrow = arrow(type = "closed", angle = 15, length = grid::unit(0.1, "inches"))) + # and taper
-	geom_point(data = nodes,  # Add nodes
-						 aes(x = x, y = y , fill = spe_c), size = 5, pch = 21,
-						 colour = "black") + 
-	geom_text(data = nodes, aes(x = x, y = y + pos, label = spe), size = 3, parse = T, family = "Times") +
-	scale_fill_manual(values = c("#636363", "white")) + 
-	scale_colour_manual(values = c("#636363", "#bdbdbd")) +
-	my_theme + xlab("") + ylab("") + 
-  	xlim(c(-0.09, 2.09)) + ylim(c(-0.48, 1.48)) +
- theme(plot.margin=unit(c(4,4,-4,-4),"mm")) +
-	scale_size_manual(values = c(0.5, 0.5)) +
-  ggtitle("a) directed network")
-
-net <- digraph_bipartite(net)
-adj_matrix <- net %>% igraph::as_adjacency_matrix(sparse = F, type = "upper")
-layoutCoordinates <- cbind(rep(0:4, 2), rep(c(1,0), each = 5)) %>%
-	`colnames<-`(c("x", "y"))
-
-adj_list <- adj_matrix %>% 
-	reshape2::melt() %>% 
-	dplyr::filter(value > 0)
-
-# Generate an edge path for each pair of connected nodes
-n <- 100
-allEdges <- lapply(1:nrow(adj_list), edgeMaker, len = n, curved = FALSE)
-allEdges <- do.call(rbind, allEdges) %>%
-	dplyr::filter(Sequence != n,
-								Sequence != 1) %>%
-	dplyr::mutate(Group = factor(Group),
-				 type = Group)
-
-new_lev <- c("m", "m", "u", "m", "u")
-levels(allEdges$type) <- new_lev
-
-nodes <- data.frame(layoutCoordinates) %>%
-	dplyr::mutate(spe = rep(sp_names, 2),
-								spe_l = c(paste0(sp_names, " %->% phantom(0)"), paste0(sp_names, " %<-% phantom(0)")),
-								spe_c = c(c("m", "m", "u", "m", "u"), rep("u",5)), 
-								pos = rep(c(0.3, -0.3), each = 5))
-
-p2 <- ggplot(allEdges) +  # Pretty simple plot code
-	geom_path(aes(x = x, y = y, group = Group, colour = type, size = type)) + # and taper
-	geom_point(data = nodes,  # Add nodes
-						 aes(x = x, y = y, fill = spe_c), size = 5, pch = 21,
-						 colour = "black") + 
-	geom_text(data = nodes, aes(x = x + 0.08, y = y + pos, label = spe_l), parse = T, size = 3, family = "Times") +
-	# coord_flip()  + scale_x_reverse() + scale_y_reverse() +
-	scale_fill_manual(values = c("#636363", "white")) + 
-	scale_colour_manual(values = c("#636363", "#bdbdbd")) +
-	xlim(c(-0.12, 4.12)) + ylim(c(-0.48, 1.48)) +
-	my_theme + xlab("") + ylab("") +
-	scale_size_manual(values = c(0.5, 0.5)) +
-  ggtitle("b) alternative bipartite representation")
-
-pdf("./paper/figures/fig_1.pdf", width = 6.2, height = 1.6, family = "Times", title = "Figure 1", compress = F)
-multiplot(p1, p2, layout = matrix(nrow = 1, c(1,1,1,2,2,2,2,2)))
-dev.off
-```
-
-Given a maximum matching, the link to network controllability has a largely intuitive basis. 
-In control theory, a network is fully controllable when each node has a "superior", that is, an input that drives its dynamics. 
-Consequently, each matched nodes can be controlled by the node pointing to it.
-Unmatched nodes, on the other hand, have no superior in the network and must be directly controlled by external inputs [@Liu2011]. 
-In an ecological context, these external inputs are what could be referred to as management interventions. 
-Building on this analogy, systems that require a large number of external inputs are more difficult or costly to control. 
-Therefore, the manageability *m* of a community can be approximated by the proportion of species on which we would need to apply management interventions in order to gain full control of the abundances of *all* species in the ecological community.
-This is given by $$m = 1- \frac{n_d}{s},$$ where *m* ranges between zero and one, *n~d~* is the number of species needed to gain full control and *s* is the total number of species in the community.
+The number of driver nodes *D* can provide a structural indication of how difficult a network's control might be.
+This is because systems that require a large number of external input signals are intuitively more difficult or costly to control.
+In an ecological context, external inputs that modify the state of a node can be thought of as management interventions.
+Therefore, the density of driver nodes $n_D = \frac{D}{S}$, where *S* is the total number of species in the community, can be seen as a measure of the extent to which network structure can be harnessed for network control.
+For instance, while a hypothetical "network" in which species do not interact but instead function independently from each other would require direct interventions for every single species to achieve full control, a linear food chain would require just one species to be directly controlled to harness cascading effects through the trophic levels that compose it.
+From this perspective, it is possible to use *n~D~* as an index of the manageability of an ecological community, understood in the context of how difficult is to modify the abundances of species in the community using external interventions—a common theme in ecosystem management, conservation, and restoration.
+
+It has been recently shown that calculating *D* is equivalent to finding a maximum matching in the network [@Liu2011].
+In a directed network, a *matching* consists of a subset of links in which no two of them share a common starting or ending node (Figure 1, Supporting Information S1).
+A given matching has *maximal cardinality* if the number of matched links (also referred to as the *matching size*) is the largest possible.
+A maximal cardinality matching is then called a *maximum matching* if the sum of the weights of the matched links (also referred to as *matching weight*) is again the largest possible [@West2001].
+
+Once we have the subset of links that constitute a matching, we can also classify the nodes in the network based on that matching (Figure 1).
+A node is said to be *matched* if it is at the end of a matched link and *unmatched* otherwise. 
+A node is also said to be *superior* if it is at the start of a matched link.
+Note that a node cannot be superior if it has no outgoing links.
+Notably, these node categories are what help us to link a maximum matching back to the concept of network controllability, as follows.
+Unmatched nodes are the *driver nodes* *D* because they have no superior in the network and must be directly controlled by an external input [@Liu2011].
+Each matched node, on the other hand, can be controlled by its superior.
+
+```{r figure 1, echo = F, message = F, warning = F, fig.width = 6.2, fig.height = 1.9, results= "hide", fig.pos = "t", fig.cap = "**Matchings of a simple network**.
+(a) We start with a network in which the direction of the links indicates the potential direction of control; for example a link from *a~1~* to *p~1~* indicates that the state of *p~1~* is influenced by the state of *a~1~*.
+The numbers indicate the weight of each link.
+(b & c) This network has two maximal cardinality matchings; that is, two configurations in which it would be possible to exert full control of the network via external input signals to a minimal set of nodes.
+In both cases, the three matched links (purple arrows) represent the control paths through the network and provide an indication of the matched nodes (purple), which are controlled by superior nodes within the network (circular nodes).
+Unmatched nodes (orange) are called driver nodes because full network control requires external signals to be applied to them.
+Out of the two maximal cardinality matchings only one (c) has maximum weight and therefore is also a maximum matching.
+Further examples can be found in the Supporting Information S1."}
+layout(matrix(c(1, 1, 2, 4, 3, 4), 2, 3),
+  	heights=c(8,2))
+par( mar=c(0,0,0,0))
+
+as_net %>% 
+	plot(layout = lay, 
+			 vertex.color = v_c, 
+			 vertex.size = 35,
+			 vertex.label = sp_names_fancy,
+			 vertex.label.family = fam,
+			 vertex.label.color = l_c,
+			 edge.label = round(E(.)$weight,1), 
+			 edge.label.family = fam,
+			 edge.label.color = l_c,
+			 edge.label.cex = l_s,
+			 edge.curved = F,
+			 edge.arrow.size = 0.5,
+			 margin = ma)
+
+text(label_pos_x, label_pos_y, "(a)", adj = c(0,0), font = 2)
+
+as_mat <- as_net %>%
+	digraph_bipartite() %>% 
+	max_bipartite_match()
+
+as_all_mat <- as_net %>%
+	digraph_bipartite() %>%
+	igraph::make_line_graph() %>%
+	igraph::complementer() %>% 
+	igraph::max_cliques(min = as_mat$matching_size) %>%
+	rev()
+
+text_pos_x <- 0.5
+text_pos_y <- -0.7
+
+base_as_net <- as_net
+E(as_net)$weight <- round(E(as_net)$weight, 1)
+
+1:length(as_all_mat) %>%
+	plyr::l_ply(function(x){
+
+		E(as_net)$matched <- 1
+		E(as_net)$matched[as_all_mat[[x]]] <- 5
+
+		E(as_net)$matched_width <- 1
+		E(as_net)$matched_width[as_all_mat[[x]]] <- 1.5
+
+		igraph::V(as_net)$matched <- 1
+		igraph::V(as_net)$matched[igraph::V(as_net)$name %in%
+																ends(as_net, as_all_mat[[x]])[, 2]] <- 5
+
+		igraph::V(as_net)$matched_fill <- 2
+		igraph::V(as_net)$matched_fill[igraph::V(as_net)$name %in%
+																ends(as_net, as_all_mat[[x]])[, 2]] <- 4
+
+		igraph::V(as_net)$superior <- 1
+		igraph::V(as_net)$superior[igraph::V(as_net)$name %in%
+																ends(as_net, as_all_mat[[x]])[, 1]] <- 2
+
+		igraph::V(as_net)$sup_shape <- "square"
+		igraph::V(as_net)$sup_shape[igraph::V(as_net)$name %in%
+																ends(as_net, as_all_mat[[x]])[, 1]] <- "circle"
+
+		names_fancy <- sp_names_fancy
+		# names_fancy[igraph::V(as_net)$name %in%
+		# 														ends(as_net, as_all_mat[[x]])[, 1]] <-
+		# 	sp_names_fancy_b[igraph::V(as_net)$name %in%
+		# 														ends(as_net, as_all_mat[[x]])[, 1]]
+
+		matching_weight <- sum(E(as_net)$weight[as_all_mat[[x]]])
+
+		as_net %>% 
+			plot(layout = lay, 
+					 # vertex.size = igraph::V(.)$superior * 10 + 20,
+					 vertex.size = 30,
+					 vertex.color = pal[igraph::V(.)$matched_fill],
+					 vertex.shape = igraph::V(.)$sup_shape,
+					 vertex.label = names_fancy,
+					 vertex.label.family = fam,
+					 vertex.label.color = l_c,
+					 vertex.label.cex = 1,
+					 # vertex.shape = igraph::V(.)$vertex.shape,
+					 vertex.frame.color = pal[igraph::V(.)$matched],
+					 edge.color = pal[E(.)$matched],
+					 edge.label = NA, 
+					 edge.width = E(.)$matched_width,
+					 edge.label.family = fam,
+					 edge.label.color = igraph::E(.)$matched,
+					 edge.label.cex = l_s,
+					 edge.curved = F,
+					 edge.arrow.size = 0.5,
+					 margin = ma) %>% 
+			print()
+
+		igraph::V(as_net)$name <- sp_names
+
+		text(label_pos_x, label_pos_y, paste0("(",letters[1+x], ")"), adj = c(0,0), font = 2)
+		text(text_pos_x, text_pos_y, cex = 0.9,
+				 paste0("D = ", length(igraph::V(as_net)) - as_mat$matching_size, "\n",
+				 			 "matching size: ", as_mat$matching_size, "\n",
+				 			 "matching weight: ", round(matching_weight, 1)))
+})
+
+as_net <- base_as_net
+
+plot.new()
+legend(0.20, 0.8, legend = c("unmatched link", "matched link"), horiz = TRUE,
+			 lty = 1, 
+			 col = pal[c(1, 5)],
+			 lwd = 2, cex = 0.9, xjust=0.5, yjust=0.8, bty = "n")
+
+legend(0.835, 0.8, legend = c("unmatched node (driver)", "matched node"), horiz = TRUE,
+			 pch = 21, 
+			 pt.bg = pal[c(2, 4)],
+			 col = pal[c(1,5)],
+			 pt.cex = 2,
+			 cex = 0.9, xjust=0.5, yjust=0.8, bty = "n")
+
+legend(0.5, 0.35, legend = c("superior node", "non-superior node"), horiz = TRUE,
+			 pch = c(21, 22), 
+			 # pt.bg = pal[c(2, 4)],
+			 pt.cex = 2,
+			 cex = 0.9, xjust=0.5, yjust=0.8, bty = "n")
+
+n
+# 			 cex = 0.9, xjust=0.5, yjust=1, bty = "n")
+
+```
+
+Note that this framework requires a directed network in which the direction of the links corresponds to the direction of control. 
+In the "Empirical application" section below, we explain our approach to determining the link direction in pollination networks.
 
@@
 
-The manageability of a community *m* provides an indication of the magnitude of $n_d$ but not the identity of the species that compose this set. 
-This difference is rather important since maximum matchings are often not unique in a given network and different sets of species of size *n~d~* could potentially be used to control the network [@Liu2011].
-That is, species vary in terms of the frequency with which they are classified as superior nodes, and this frequency provides an indication of their relative importance in driving the state of the community.
-Ecologically, these distinctions are relevant because resources are limited and therefore ecological interventions should ideally be focused on species that might provide the largest impact. 
-Superior nodes drive the dynamics of other species and are therefore important for the controllability of the network because they either require external input or because they are part of the chain that transmit the external inputs to other species; we therefore call *driver species* those that are identified as being a superior node in *all* possible matchings, and hence those most likely to have a disproportionate effect on the abundances of other species in their community.
-
-As previously described, a maximum matching in a weighted network is one whose links have the largest possible total weight among all possible matchings. 
-One way to calculate the species importance, and identify the driver species, would be to consider only maximum matchings. 
-However, empirical interaction strengths are to some extent stochastic and depend on proximate factors such as sampling method and intensity [@Gibson2011]. 
-This implies that there will often be multiple matchings that have maximal size in weighted networks but that are not maximum matchings because their total weight is not maximal. 
-We can accommodate this uncertainty by relaxing the matching weight requirement and computing all possible matchings in the network that have the same maximal size while allowing for some tolerance regarding the weight.
-One alternative to compute all the matchings with maximal size, is to first generate the network's line graph—another representation in which nodes are the links of the original network and links represent common ending points [@West2001].
-Then calculate the complement of this line graph, which generates a graph in which nodes are connected if and only if they are not connected in the line graph.
-Finally, all possible matchings of maximal size can be found by enumerating every clique (subgraphs in which all nodes are fully connected to each other) of maximum size in this complement graph [@Csardi2006a; @Gutin2013].
-
-## Methods
-
-In the last section, we outlined the theoretical and computational underpinnings of our approach. 
-Now we illustrate its empirical application using ten pairs of plant-pollinator communities for which we explored their manageability and the relative importance of their constituent species. 
-The networks were constructed from previously published visitation data collected from pollination communities in Bristol, UK [@Lopezaraiza-Mikel2007] and in Cap de Creus National Park, Spain [@Bartomeus2008].
-Notably, each network pair was composed of a community invaded by a plant and a community "free" of the invasive species (Table S1). 
-In the four British uninvaded communities, the non-invaded plots were obtained by experimentally removing all the flowers of the invasive species *Impatients grandulifera*. 
-In contrast, the Spanish uninvaded communities were obtained from plots that had not yet been colonised by either of the invasive species *Carpobrotus affine acinaciformis* or *Opuntia stricta*. 
-The structure of all networks was determined using visitation frequency which has been shown to be an appropriate surrogate for interspecific effects in pollination networks [@Vazquez2005; @Bascompte2006].
-To examine whether this decision would influence our results, we also evaluated the effect of using pollinator efficiency or importance as alternative measures of species interactions in a different data set that lacked invasive species [@NeEman2010; @Ballantyne2015], and we found quantitatively similar results for all of these options (Supplementary Information S1).
-
-### Community manageability
-
-```{r component_lost, echo = F}
-net <- "./data/processed/networks" %>%
-	read_networks()
-
+While calculating *n~D~* provides an indication of the manageability of an ecological community, it does not provide information about the identity of the species that compose the set of driver nodes.
+Ecologically, potential differences between species are acutely relevant because management and conservation resources are limited, and therefore ecological interventions should ideally be focused on the set of species that might provide the largest impact.
+Moreover, maximum matchings in a network are often not unique, and each different maximum matching indicates a unique path that can potentially be used to control the network. 
+We harness this property and use a network's complete set of maximum matchings to characterise each species' relative importance in driving the state of the community. 
+One possibility is to characterise a species by the frequency *f~D~* with which it is classified as a driver node within this set of matchings.
+However, the profile of our networks indicates that a large proportion of driver nodes are classified as such, because of external interventions that are required to achieve **full** controllability and not because they influence the abundance of other species (Supporting Information S2).
+Furthermore, the precise role of driver nodes is still ambiguous when full control is unfeasible or undesired—often the case in ecological settings.
+We therefore also calculate the frequency *f~S~* with which a species is classified as superior nodes since this is the frequency with which they form part of possible control paths.
+
+Most commonly, structural controllability assumes unweighted networks—links exist or not, and hence *f~D~* and *f~S~* can be calculated by computing all possible maximum-cardinality matchings. 
+However, we take the link weights into account when calculating the matchings here because it has been shown that the weights can reveal significant ecological patterns and processes that might be undetectable in unweighted networks [@Scotti2007; @Tylianakis2007; @Vazquez2007; @Kaiser-Bunbury2010a].
+For example, a species *A* may interact with both species *B* and *C* but depends strongly on *B* and only weakly on *C*. 
+Intuitively, a management intervention designed to indirectly modify the abundance of a species *A* is more likely to succeed if the abundance of *B*, rather than *C*, is directly controlled.
+A complication of including the interaction weight when calculating the maximum matching, however, is that empirical interaction strengths are to some extent stochastic and depend on proximate factors such as sampling method and intensity [@Gibson2011].
+We overcome this issue by calculating all maximal cardinality matchings and then ranking them by their matching weight. 
+By following this approach, we effectively give priority to the species that participate in the pathways that potentially have the largest impact on the community while acknowledging the limitations associated with sampling and its potential restrictions [@Jordano2016].
+
+## Empirical application
+
+```{r network summaries, include = F}
+lop <- filter(meta, study == "lopezaraiza") %>% mutate(size = n_pla + n_pol) %$% size %>% summary() 
+bar <- filter(meta, study == "bartomeus") %>% mutate(size = n_pla + n_pol) %$% size %>% summary() 
+```
+
+We now describe the application of the previously defined framework to ten paired pollination networks.
+Each network pair was composed of a community invaded by a plant and a community "free" of the invasive species. 
+Four pairs were obtained from natural or semi-natural vegetation communities in the city of Bristol, UK [@Lopezaraiza-Mikel2007]. 
+These networks are comprised of `r lop[1]`--`r lop[6]` species (mean `r round(lop[4])`), and non-invaded plots were obtained by experimentally removing all the flowers of the invasive species *Impatients grandulifera*.
+The other six pairs were obtained from lower diversity Mediterranean shrublands in Cap de Creus National Park, Spain [@Bartomeus2008].
+These networks are comprised of `r bar[1]`--`r bar[6]` species (mean `r round(bar[4])`); in contrast to the above, uninvaded communities were obtained from plots that had not yet been colonised by either of the invasive species *Carpobrotus affine acinaciformis* or *Opuntia stricta*.
+Further details about the empirical networks can be found in the Supporting Information S3.
+
+We then specified the structure of all networks using pollinator visitation frequency, which has been shown to be an appropriate surrogate for interspecific effects in pollination networks [@Vazquez2005; @Bascompte2006].
+To further examine whether this decision would influence our results, we also evaluated the effect of using pollinator efficiency or pollinator importance as alternative measures of species interactions in a different data set that lacked invasive species [@NeEman2010; @Ballantyne2015], and we found quantitatively similar results for all three of these options (Supporting Information S4).
+In addition, because our approach depends to a large degree on the network topology, we evaluated the robustness of our results to the undersampling of ecological interactions.
+Specifically, we calculated *n~D~* and species relative importance for 500 random subsamples of each empirical network in which the weakest links were more likely to be removed. 
+The sensitivity analysis indicated that, even in the absence of complete sampling, a control-theoretic approach can still be applied (Supporting Information S5).
+
+### Manageability
+
+```{r component_lost, echo = F, eval = T}
 a <- net %>%
@@
 
-Given the different networks, we began by quantifying their manageability.
-To do so, we calculated the maximum matching of the corresponding pollination network, and estimated the minimum proportion of species that need directed interventions to fully control the species abundances in the community.
-To simplify the analysis, we only considered the largest component in a network if it had more than one (two species are in different components if there exists no path between them and are hence independent of each other in terms of network control).
+We began by quantifying the manageability of each of the aforementioned networks.
+To do so, we calculated the networks' maximum matching and determined the minimum proportion of species *n~D~* that need external input signals to fully control the species abundances in the community.
+Note that because all maximum matchings have the same matching size, it is only necessary to calculate one of them. 
+To simplify the analysis, if a network had more than one component (two species are in different components if there exists no path between them and are hence independent of each other in terms of network control) we only considered the largest.
 Smaller components were present in eleven out of the twenty networks and were typically composed of just one plant and one pollinator. 
@@
 
-Recall that the aforementioned maximum matching algorithm requires a directed network in which a link between species *i* and *j* pointing to species *j* indicates that the abundance of *j* can be affected by the abundance of *i*.
-This implies that we need first to identify a directionality for the links between species that in consistent with the dynamics of the community. 
-In some ecological networks, establishing the directionality is relatively straightforward, for example when links represent biomass transfer or energy flow. 
+As we noted earlier, the aforementioned maximum-matching approach requires a directed network in which a link between species *i* and *j* pointing to species *j* indicates that the abundance of *j* can be affected by the abundance of *i*.
+This implies that we need first to identify a directionality for the links between species that is consistent with the dynamics of the community (Figure 2). 
+In some ecological networks, establishing the directionality can appear relatively straightforward, for example when links represent biomass transfer or energy flow [@Isbell2013]. 
 Interspecific effects in pollination networks, however, are not strictly directed since the benefit is mutual between interacting species. 
-Nevertheless, the relative extent to which a given pair of interacting species affect each other can be quantified by the magnitude of the mutual dependence [@Bascompte2006]. 
-The dependency of plant *i* on pollinator *j*, *d~ij~*, is the proportion of the visits coming from pollinator *j* compared to all pollinator visits to plant *i*. 
-Likewise, the dependency of pollinator *j* on plant *i*, *d~ji~*, is the ratio of the visits by pollinator *j* to plant *i* and all visits of pollinator *j*.
-As the dependencies are not symmetric, its use generates a weighted bipartite network in which all interacting pairs are connected by two directed links (Figure 2b).
-
-Given the respective dependences, the extent to which a species $i$ affects species *j* relative to the extent to which *j* affects *i* can be summarised by the interaction asymmetry given by $$a(i,j) = \frac{\left | d_{ij}-d_{ji} \right |}{max\left ( d_{ij}, d_{ji} \right )}.$$
-Mutual dependencies have previously been shown to be highly asymmetric in natural communities [@Bascompte2006]; in other words, if a plant species is largely dependent on a pollinator species, then that pollinator tends to depend rather weakly on the plant (or vice versa).
-This suggests that it may be possible to relax the assumption of bidirectional dependences further and simplify the network such that interacting species are connected by only one directed link when mutual dependencies are asymmetric (Figure 2c).
-Changing to unidirectional interactions determined by the observed direction of asymmetry, as a surrogate of bidirectional mutual dependences, does not alter the relative manageabilities of different networks (Supplementary Information S2).
-Moreover, it confers an additional advantage for our purposes since it dramatically reduces the number of links in the network. 
-This translates into a substantial reduction of the time and memory required for the computation of all possible maximum matchings in a network, particularly for large networks (see "Relative importance of species" subsection below).
-
-```{r fig_explain-control-direction, message=FALSE, warning=FALSE, include=FALSE}
-sp_names <- c("a[1]", "a[2]", "a[3]", "p[1]", "p[2]")
-
-adj_matrix <- c(0,0,0,0,0,
-								0,0,0,0,1,
-								0,0,0,0,0,
-								1,1,1,0,0, 
-								0,0,1,0,0) %>%
-	matrix(nrow = 5, byrow = T) %>%
-	`rownames<-`(sp_names) %>%
-	`colnames<-`(sp_names)
-
-net <- adj_matrix %>% 
-	igraph::graph_from_adjacency_matrix(mode = "directed") 
-igraph::V(net)$type <- c(F, F, F, T, T)
-igraph::E(net)$weight <- 1
-
-layoutCoordinates <- cbind(c(0,1,2,0.5,1.5), 
-													 c(1,1,1,0,0)) %>%
-	`colnames<-`(c("x", "y"))
-
-adj_list <- adj_matrix %>% 
-	reshape2::melt() %>% 
-	dplyr::filter(value > 0)
-
-# Generate an edge path for each pair of connected nodes
-n <- 17
-allEdges <- lapply(1:nrow(adj_list), edgeMaker, len = n, curved = FALSE)
-allEdges <- do.call(rbind, allEdges) %>%
-	dplyr::filter(Sequence != n) %>%
-	dplyr::mutate(Group = factor(Group),
-				 type = Group)
-
-new_lev <- c("m", "u", "m", "m", "u")
-levels(allEdges$type) <- new_lev
-
-nodes <- data.frame(layoutCoordinates) %>%
-	dplyr::mutate(spe = sp_names,
-								spe_c = c("m", "m", "u", "m", "u"), 
-								pos = rep(c(0.3, -0.3), c(3,2)))
-
-weights <- allEdges %>%
-  dplyr::filter(Sequence == 12) %>%
-  dplyr::mutate(weight = c(1, 2, 1, 1, 2))
-
-p1 <- ggplot(allEdges) +  # Pretty simple plot code
-	geom_path(aes(x = x, y = y, group = Group, size = type), colour = "#bdbdbd") + # and taper
-	geom_point(data = nodes,  # Add nodes
-						 aes(x = x, y = y ), size = 5, pch = 21,
-						 colour = "black", fill = "white") + 
-	# geom_text(data = nodes, aes(x = x, y = y + pos, label = spe), size = 3, parse = T, family = "Times") +
-  geom_point(data = weights, aes(x = x, y= y), size = 2.5, alpha = 0.25, colour = "white") +
-  geom_text(data = weights, aes(x = x, y= y, label = weight), size = 2.5, family = "Times") +
-	scale_fill_manual(values = c("#636363", "white")) + 
-	scale_colour_manual(values = c("#636363", "#bdbdbd")) +
-	my_theme + xlab("") + ylab("") + 
-  	xlim(c(-0.09, 2.09)) + ylim(c(-0.15, 1.15)) +
- theme(plot.margin=unit(c(4,4,-4,-4),"mm")) +
-	scale_size_manual(values = c(0.5, 0.5)) +
-  ggtitle("a) visitation frequency")
-
-############################
-sp_names <- c("a[1]", "a[2]", "a[3]", "p[1]", "p[2]")
-
-adj_matrix <- c(0,0,0,1,0,
-								0,0,0,1,1,
-								0,0,0,1,1,
-								1,1,1,0,0,
-								0,1,1,0,0) %>%
-	matrix(nrow = 5, byrow = T) %>%
-	`rownames<-`(sp_names) %>%
-	`colnames<-`(sp_names)
-
-net_exp <- adj_matrix %>% 
-	igraph::graph_from_adjacency_matrix(mode = "directed") 
-igraph::V(net_exp)$type <- c(F, F, F, T, T)
-igraph::E(net_exp)$weight <- 1
-
-layoutCoordinates <- cbind(c(0,1,2,0.5,1.5), 
-													 c(1,1,1,0,0)) %>%
-	`colnames<-`(c("x", "y"))
-
-adj_list <- adj_matrix %>% 
-	reshape2::melt() %>% 
-	dplyr::filter(value > 0)
-
-# Generate an edge path for each pair of connected nodes
-n <- 17
-allEdges <- lapply(1:nrow(adj_list), edgeMaker, len = n, curved = FALSE)
-allEdges <- do.call(rbind, allEdges) %>%
-	dplyr::filter(Sequence != n) %>%
-	dplyr::mutate(Group = factor(Group),
-				 type = Group)
-
-new_lev <- c("m", "u", "m", "u", "u", "u", "m", "u", "u", "m")
-dir <- c("m", "m", "m", "m", "m", "u", "u", "u", "u", "u")
-dir2 <- c("m", "u", "m", "u", "u", "u", "m", "m", "u", "m")
-id <- 1:10
-allEdges %<>% dplyr::mutate(dir = type,
-                            dir2 = dir)
-levels(allEdges$type) <- new_lev
-levels(allEdges$dir) <- dir
-levels(allEdges$dir2) <- dir2
-allEdges %<>% 
-  dplyr::mutate(dir = as.numeric(dir),
-                dir2 = as.numeric(dir2),
-                dir = plyr::mapvalues(dir, c(1,2), c(0.03, -0.03)),
-                dir2 = plyr::mapvalues(dir2, c(1,2), c(0.03, -0.03)))
-
-nodes <- data.frame(layoutCoordinates) %>%
-	dplyr::mutate(spe = sp_names,
-								spe_c = c("u", "m", "m", "m", "m"), 
-								pos = rep(c(0.3, -0.3), c(3,2)))
-
-# ggplot(allEdges) +  # Pretty simple plot code
-# 	geom_path(aes(x = x + dir, y = y + dir2, group = Group, colour = type, size = type), 
-# 						arrow = arrow(type = "closed", angle = 15, length = grid::unit(0.1, "inches")))
-
-weights <- allEdges %>%
-  dplyr::filter(Sequence == 12) %>%
-  dplyr::mutate(weight = c("1", "0.5", "0.5", "0.5", "0.5", "0.25", "0.5", "0.25", "0.66", "0.33"))
-
-p2 <- ggplot(allEdges) +  # Pretty simple plot code
-	geom_path(aes(x = x + dir, y = y + dir2, group = Group, size = type), 
-						arrow = arrow(type = "closed", angle = 15, length = grid::unit(0.1, "inches")), colour = "#bdbdbd") + # and taper
-	geom_point(data = nodes,  # Add nodes
-						 aes(x = x, y = y ), size = 5, pch = 21,
-						 colour = "black", fill = "white") +  
-	# geom_text(data = nodes, aes(x = x, y = y + pos, label = spe), size = 3, parse = T, family = "Times") +
-  geom_point(data = weights, aes(x = x + dir*3, y= y), size = 2.5, alpha = 0.25, colour = "white") +
-  geom_text(data = weights, aes(x = x + dir*3, y= y, label = weight), size = 2.5, family = "Times", parse = T) +
-	scale_fill_manual(values = c("#636363", "white")) + 
-	scale_colour_manual(values = c("#636363", "#bdbdbd")) +
-	my_theme + xlab("") + ylab("") + 
-  xlim(c(-0.09, 2.09)) + ylim(c(-0.15, 1.15)) +
- theme(plot.margin=unit(c(4,4,-4,-4),"mm")) +
-	scale_size_manual(values = c(0.5, 0.5)) +
-  ggtitle("b) mutual dependence")
-
-####################################
-
-sp_names <- c("a[1]", "a[2]", "a[3]", "p[1]", "p[2]")
-
-adj_matrix <- c(0,0,0,0,0,
-								0,0,0,1,1,
-								0,0,0,0,0,
-								1,1,1,0,0,
-								0,0,1,0,0) %>%
-	matrix(nrow = 5, byrow = T) %>%
-	`rownames<-`(sp_names) %>%
-	`colnames<-`(sp_names)
-
-net <- adj_matrix %>% 
-	igraph::graph_from_adjacency_matrix(mode = "directed") 
-igraph::V(net)$type <- c(F, F, F, T, T)
-igraph::E(net)$weight <- 1
-
-layoutCoordinates <- cbind(c(0,1,2,0.5,1.5), 
-													 c(1,1,1,0,0)) %>%
-	`colnames<-`(c("x", "y"))
-
-adj_list <- adj_matrix %>% 
-	reshape2::melt() %>% 
-	dplyr::filter(value > 0)
-
-# Generate an edge path for each pair of connected nodes
-n <- 17
-allEdges <- lapply(1:nrow(adj_list), edgeMaker, len = n, curved = FALSE)
-allEdges <- do.call(rbind, allEdges) %>%
-	dplyr::filter(Sequence != n) %>%
-	dplyr::mutate(Group = factor(Group),
-				 type = Group)
-
-# new_lev <- c("m", "u", "m", "m", "u")
-# levels(allEdges$type) <- new_lev
-
-nodes <- data.frame(layoutCoordinates) %>%
-	dplyr::mutate(spe = sp_names,
-								# spe_c = c("m", "m", "u", "m", "u"), 
-								pos = rep(c(0.3, -0.3), c(3,2)))
-
-weights <- allEdges %>%
-  dplyr::filter(Sequence == 12) %>%
-  dplyr::mutate(weight = c("0.75", " ", "0.5", "0.33", " ", "0.25"))
-
-p3 <- ggplot(allEdges) +  # Pretty simple plot code
-	geom_path(aes(x = x, y = y, group = Group), size = 0.5,
-						arrow = arrow(type = "closed", angle = 15, length = grid::unit(0.1, "inches")), colour = "#bdbdbd") + # and taper
-	geom_point(data = nodes,  # Add nodes
-						 aes(x = x, y = y ), size = 5, pch = 21,
-						 colour = "black", fill = "white") + 
-	# geom_text(data = nodes, aes(x = x, y = y + pos, label = spe), size = 3, parse = T, family = "Times") +
-   geom_point(data = weights, aes(x = x, y= y), size = 2.5, alpha = 0.25, colour = "white") +
-  geom_text(data = weights, aes(x = x, y= y, label = weight), size = 2.5, family = "Times") +
-	scale_fill_manual(values = c("#636363", "white")) + 
-	scale_colour_manual(values = c("#636363", "#bdbdbd")) +
-	my_theme + xlab("") + ylab("") + 
-  	xlim(c(-0.09, 2.09)) + ylim(c(-0.15, 1.15)) +
- theme(plot.margin=unit(c(4,4,-4,-4),"mm")) +
-	# scale_size_manual(values = c(0.5, 0.5)) +
-  ggtitle("c) interaction asymmetry")
-
-###########################
-pdf("./paper/figures/fig_2.pdf", width = 6.2, height = 1.5, family = "Times", compress = F, title = "Figure 2")
-multiplot(p1, p2, p3, cols = 3)
-dev.off()
-```
+Nevertheless, the relative extent to which a given pair of interacting species affect each other can be quantified by the magnitude of the mutual dependence between them [@Bascompte2006]. 
+The dependence of plant *i* on pollinator *j*, *d~ij~*, is the proportion of the visits coming from pollinator *j* compared to all pollinator visits to plant *i*. 
+Likewise, the dependence of pollinator *j* on plant *i*, *d~ji~*, is the proportion of the visits by pollinator *j* to plant *i* and all visits of pollinator *j*.
+As the dependences are not necessarily symmetric, their use generates a weighted bipartite network in which all interacting pairs are connected by two directed links (Figure 2b).
+
+```{r figure 2, echo = F, fig.width = 6.2, fig.height = 1.6, message = F, warning = F, fig.pos = "T", fig.cap = "**Different ways to depict quantitative mutualistic networks**.
+(a) Pollination networks are frequently described by the observed number of visits between each plant and animal species.
+(b) Based on that visitation data, the mutual dependences between interacting species are calculated directly based on the relative visitation frequencies.
+(c) The relative differences of these  dependences—the interaction asymmetry—then provide a means to estimate the dominant direction of the interspecific effects."}
+
+par(mfrow=c(1,3), mar=c(0,0,0,0))
+
+base_net %>%
+	plot(layout = lay, 
+			 vertex.color = v_c, 
+			 vertex.size = 35,
+			 vertex.label = sp_names_fancy,
+			 vertex.label.family = fam,
+			 vertex.label.color = l_c,
+			 edge.label = E(.)$weight, 
+			 edge.label.family = fam,
+			 edge.label.color = l_c,
+			 edge.label.cex = l_s,
+			 edge.curved = F,
+			 frame = F,
+			 margin = ma)
+text(label_pos_x, label_pos_y, "(a)", adj = c(0,0), font = 2)
+
+bi_net %>% 
+	plot(layout = lay, 
+			 vertex.color = v_c, 
+			 vertex.size = 35,
+			 vertex.label = sp_names_fancy,
+			 vertex.label.family = fam,
+			 vertex.label.color = l_c,
+			 edge.label = round(E(.)$weight,1), 
+			 edge.label.family = fam,
+			 edge.label.color = l_c,
+			 edge.label.cex = l_s,
+			 edge.curved = T,
+			 edge.arrow.size = 0.5,
+			 margin = ma)
+text(label_pos_x, label_pos_y, "(b)", adj = c(0,0), font = 2)
+
+as_net %>% 
+	plot(layout = lay, 
+			 vertex.color = v_c, 
+			 vertex.size = 35,
+			 vertex.label = sp_names_fancy,
+			 vertex.label.family = fam,
+			 vertex.label.color = l_c,
+			 edge.label = round(E(.)$weight,1), 
+			 edge.label.family = fam,
+			 edge.label.color = l_c,
+			 edge.label.cex = l_s,
+			 edge.curved = F,
+			 edge.arrow.size = 0.5,
+			 margin = ma)
+text(label_pos_x, label_pos_y, "(c)", adj = c(0,0), font = 2)
+
+```
+
+Given the respective dependences, the extent to which a species *i* affects species *j* relative to the extent to which *j* affects *i* can be summarised by the interaction asymmetry [@Bascompte2006] given by $$a(i,j) = a(j,i) = \frac{\left | d_{ij}-d_{ji} \right |}{max\left ( d_{ij}, d_{ji} \right )}.$$
+Previous research has shown that mutual dependences are often highly asymmetric in natural communities [@Bascompte2006]; in other words, if a plant species is largely dependent on a pollinator species, then that pollinator tends to depend rather weakly on the plant (or vice versa).
+We therefore simplified the network so that interacting species are connected by only one directed link when mutual dependences are asymmetric (Figure 2c).
+This simplification, while maintaining ecological realism, is advantageous for several reasons. 
+First, it is consistent with previous advances in structural controllability; second, it avoids complications related to the introduction of artificial control cycles [@Ruths2014]; and third it significantly reduces the computational resources necessary for the application of our approach (Supporting Information S6).
+Furthermore, we show that changing to unidirectional interactions determined by the observed direction of asymmetry, as a surrogate of bidirectional mutual dependences, does not alter the relative *n~D~* of different networks (Table S3).
+
+To find a maximum matching in a network with interaction directions and weights determined by the asymmetry, we adopted a strategy based on an alternative bipartite representation of the directed network with two levels that indicate the outgoing and incoming links to each node (Supporting Information S1).
+Once we had this alternative representation we used the maximum bipartite matching algorithm implemented in the `max_bipartite_match` function of igraph 1.0.1 [@Csardi2006a] on each network.
 
@@
 
-Although understanding the variability of manageability across ecological networks is a useful result itself, we also wanted to test whether invasion status has an impact on the observed manageability values.
-We therefore used a set of generalised linear models (with binomial error structure) to investigate the effect of invasion status while also controlling for factors related to species richness, since one might naively expect to see a negative relationship between diversity and manageability [@Menge1995].
-These covariates included the total number of species, plant richness, pollinators richness, the ratio of plants to pollinators richness, and the study site (as a two level factor). 
-We assessed competing models by comparing the Akaike Information Criterion corrected for small sample sizes (AICc), and report results for the most parsimonious model.
+Although understanding the variability of manageability across ecological networks is a useful result in itself, we also wanted to test whether invasion status or other predictors had an impact on the observed *n~D~*.
+We therefore used a set of generalised linear models (with binomial error structure) to investigate the effect of invasion status while also including covariates related to species richness, since one might naively expect to see a negative relationship between richness and manageability [@Menge1995].
+These covariates included the total number of species, plant richness, pollinators richness, the ratio of plant to pollinator richness, the link density (connectance), and the study site (as a two-level factor).
+Candidate models were compared using AICc and the relative importance of the explanatory variables was evaluated using the sum of Akaike weights over candidate models that accounted for 95% of the evidence [@Burnham2003; @Bates2015; @Barton2016].
+Coefficient estimates were averaged following @Buckland1997a while confidence intervals were calculated following @Lukacs2010.
 
 We next explored whether real networks differ in their architecture from random ones in a concerted way that affects manageability. 
-Previous research indicates a direct link between a network's degree distribution and the number of nodes necessary to fully control it [@Liu2011], but the strength and applicability of this relationship has not been tested for in weighted ecological networks.
-We therefore compared the manageability of the empirical networks to networks generated by two null models which varied in terms of the constraints they impose. 
-The first set was generated by maintaining each species' degree (its number of interactions) while allowing the number of visits per species to vary. 
-The second set of random networks maintained each species' strength (its total sum of visits) while allowing their degrees to vary. 
-Randomisations were generated using vegan 2.3-3 [@Oksanen2016]. 
-After generating the randomized networks under these two schemes, we then calculated the mutual dependences and interaction asymmetries of each and determined their manageability using our maximum matching framework
-Finally, we calculated the average rank (akin to a p-value) of the manageability of each empirical network compared to the corresponding manageabilites of each set of 999 randomisations.
-
-Beyond network structure, the dependency asymmetry plays a fundamental role in determining the direction of control in each two-species interaction and therefore has the potential to influence the network manageability results above.
-We therefore performed an additional randomisation in which we kept the structure of network constant but randomised the direction of the interaction asymmetries. 
-That is, we first calculated the asymmetries for each community and then shuffled the direction of the link between each pair of species. 
-Similar as to the other null models, we calculated the average rank of the empirical manageability when compared to those of the randomisations.
-
-### Relative importance of species
-
-Our second key question is related to how species differ in their importance for driving the population dynamics of the community. 
-To quantify this importance in each network, we computed all possible matchings that have the same size as the networks' maximum matching. 
-We then calculated the frequency with which each species is deemed to be a superior node in the set of matchings that had a total weight greater or equal to 0.5 times the weight of the maximum matching.
-We selected this threshold as it provided a high agreement between networks quantified by visitation and pollination efficiency as well as between our weighting/directionality assumptions (mutual dependences and interaction asymmetries); however, the choice of this threshold had a negligible impact on the results (Supplementary Information S3).
-
-Although the species importance calculated from mutual dependences contains full information, even in sparse networks, like those studied here, the number of maximal matchings increases exponentially with the number of links and nodes in a network.
-Unfortunately, this means that the large number of links in the most diverse communities rendered the computation unfeasible when we used mutual dependencies. 
-Taking this limitation into account, we compared the relative network manageability obtained when using asymmetries to those found when using mutual dependencies to test if they gave consistent results.
-The comparison was performed for eleven of the twenty networks (those for which the number of matchings was smaller than 4 x 10^10^), using a paired Spearman correlation test, a weighted correlation coefficient *r~w2~* [which gives more weight to higher ranks; @PintoDaCosta2015], and a Jaccard similarity of the driver species in both approaches.
-All three approaches identified a high similarity in relative ranks. 
-Consequently, we focused on the results when using the asymmetries rather than mutual dependencies when further investigating the factors that determine species' relative importance since this also allows us to obtain results for all 20 networks.
+Previous research indicates a direct link between a network's degree distribution and the number of nodes necessary to fully control it [@Liu2011], but the strength and applicability of this relationship have not been tested for in weighted ecological networks.
+We therefore compared the driver-node density *n~D~* of the empirical networks to networks generated by a null model that maintained each species' strength (its total sum of visits) while allowing their degrees (its number of interactions) to vary.
+Randomisations were generated using the quasiswap-count algorithm and the function `commsim` in vegan 2.3-3 [@Oksanen2016]. 
+After generating the randomised networks, we then calculated the mutual dependences and interaction asymmetries of each and determined *n~D~* using our maximum-matching framework. 
+Finally, we calculated the average rank (akin to a p-value) of *n~D~* for each empirical network compared to the corresponding one of each set of 999 randomisations [@Veech2012].
+
+Beyond network structure, the dependence asymmetry plays a fundamental role in determining the direction of control in each two-species interaction and therefore has the potential to influence the network *n~D~* results above.
+We therefore performed an additional randomisation in which we kept the structure of each network constant but randomised the direction of the interaction asymmetries. 
+That is, we first calculated the observed asymmetries for each community and then shuffled the direction of the link between each pair of species. 
+Similar to the other null models, we calculated the average rank of the empirical *n~D~* when compared to that of the randomisations.
+
+### Relative importance
+
+Our second key question was related to how species differ in their ability to drive the population dynamics of the community. 
+To quantify this importance, we computed all maximal cardinality matchings in each network. 
+We then calculated the frequency with which each species *i* is deemed to be a driver (*f~D~*) or a superior node (*f~S~*) in the set of matchings that had a matching weight greater or equal to 0.8 times the weight of the maximum matching.
+We selected this threshold as it provided a high agreement between networks quantified by visitation and pollination efficiency as well as between our weighting/directionality assumptions; however, the choice of this threshold had a negligible impact on any results (Supporting Information S7).
+Details about the computational procedure to find all maximal cardinality matchings of a network can be found in Supporting Information S1 and Figure S2.
 
@@
 
-We then asked the question of whether some species-level structural properties can predict our estimates of species importance.
-We used a generalised linear mixed-effects model (with binomial error structure) with the relative importance as the response variable. 
-As predictors in this model, we included measures of centrality (degree and eigen-centrality), which have been found to be strong predictors of importance in a coextinction context [@Memmott2004]; a measure related to network robustness (contribution to nestedness), as nestedness has been proposed as one of the key properties that promote stability in mutualistic networks [@Saavedra2011]; two measures of strength of association and dependence (visitation and dependency strength), as their distribution determines the extent of interspecific effects [@Bascompte2006].
-In addition, we also included guild and invasive status as categorical fixed effects; although the importance of plants and pollinators or invasive and non-invasive species could respond differently to our structural metrics, our data set did not contain enough variation to include the corresponding interactions terms for these latter two predictors.
+We then examined whether any species-level structural properties could predict our metrics of species importance—the frequency to which a species was a driver or a superior node (*f~D~* and *f~S~*, respectively).
+We used a set of generalised linear mixed-effects models (with binomial error structure) with the relative frequencies as the response variables. 
+As predictors in this model, we included measures of centrality (degree and eigen-centrality), which have been found to be strong predictors of importance in a coextinction context [@Memmott2004]; a measure related to network robustness (contribution to nestedness), as nestedness has been proposed as one of the key properties that promote stability in mutualistic networks [@Saavedra2011]; a measure of strength of association (visitation strength, the sum of visits a species receives or performs) and a measure of strength of dependence (species strength, the sum of dependences of all species on the focal species), as their distribution determines the extent of interspecific effects [@Bascompte2006].
+To facilitate comparison among the continuous variables, we scaled them so that they all had a mean of zero and a standard deviation of one.
+In addition, we also included guild (plant or pollinator) and whether the species is invasive or not as categorical fixed effects.
+Although the importance of plants and pollinators or invasive and non-invasive species could respond differently to our structural metrics, our data set did not contain enough variation to include the corresponding interactions terms for these latter two predictors.
 All network metrics were calculated using the R package bipartite 2.06 [@Dormann2008]. 
-We lastly allowed for variation between different communities by including the network identity as a random effect [@Bates2015]. 
-Candidate models were compared using AICc and the relative importance of the explanatory variables was evaluated using the sum of Akaike weights over candidate models that accounted for 95% of the evidence [@Burnham2003; @Bates2015; @Barton2016].
-Coefficient estimates were averaged following [@Buckland1997a] while confidence intervals were calculated following [@Lukacs2010].
-
-## Results
-
-### Community manageabiity
-
-```{r n_driver, message = FALSE, warning = FALSE, include = FALSE}
-n_driver <- a_m %>%
-  dplyr::inner_join(meta) %>%
-  dplyr::filter(count == "visitation") %>%
-  dplyr::mutate(n_sp = n_pla + n_pol, 
-                n_dr = n_sp - n_matched,
-                n_dr_p = n_dr / n_sp)
-
-src_bi_w <- n_driver %>%
-  dplyr::filter(type == "z-bi" | type == "weight",
-                study != "ballantyne") %>%
-  dplyr::select(net_name, type, n_dr_p) %>%
-  tidyr::spread(type, n_dr_p) %$%
-  cor.test(weight, `z-bi`, method = "spearman")
-
-n_driver %<>%
-  dplyr::filter(!is.na(inv))
-
-n_driver_wb <- dplyr::filter(n_driver, 
-                             type == "z-bi" | type == "weight")
-
-# Models
-m0 <- glm(cbind(n_dr, n_matched) ~ n_pla * n_pol + study + inv + type,
-          data = n_driver_wb,
-          family = "binomial")
-m_nr <- glm(cbind(n_dr, n_matched) ~ I(n_pla/n_pol) + study + inv + type,
-          data = n_driver_wb,
-          family = "binomial")
-m8 <- glm(cbind(n_dr, n_matched) ~ I(n_pla/n_pol) + inv + type,
-          data = n_driver_wb,
-          family = "binomial")
-m9 <- glm(cbind(n_dr, n_matched) ~ I(n_pla/n_pol) + study + type,
-          data = n_driver_wb,
-          family = "binomial")
-m1 <- glm(cbind(n_dr, n_matched) ~ I(n_pla/n_pol) + type,
-          data = n_driver_wb,
-          family = "binomial")
-m2 <- glm(cbind(n_dr, n_matched) ~ study + type,
-          data = n_driver_wb,
-          family = "binomial")
-m3 <- glm(cbind(n_dr, n_matched) ~ I(n_pla + n_pol) + type,
-          data = n_driver_wb,
-          family = "binomial")
-m4 <- glm(cbind(n_dr, n_matched) ~ n_pla + type,
-          data = n_driver_wb,
-          family = "binomial")
-m5 <- glm(cbind(n_dr, n_matched) ~ n_pol + type,
-          data = n_driver_wb,
-          family = "binomial")
-m6 <- glm(cbind(n_dr, n_matched) ~ inv + type,
-          data = n_driver_wb,
-          family = "binomial")
-m7 <- glm(cbind(n_dr, n_matched) ~ study + inv + type,
-          data = n_driver_wb,
-          family = "binomial")
-```
-
-All of the networks studied here had levels of manageability between `r round(min(1-dplyr::filter(n_driver, type == "z-bi")$n_dr_p), digits = 2)` and `r round(max(1-dplyr::filter(n_driver, type == "z-bi")$n_dr_p), digits = 2)` (mean `r round(mean(1-dplyr::filter(n_driver, type == "z-bi")$n_dr_p), digits = 2)`) when we considered bidirectional links weighted by the mutual dependences.
-This was in strong agreement with the results obtained using the dependence asymmetry in which manageability ranged between `r round(min(1-dplyr::filter(n_driver, type == "weight")$n_dr_p), digits = 2)` and `r round(max(1-dplyr::filter(n_driver, type == "weight")$n_dr_p), digits = 2)` (mean `r round(mean(1-dplyr::filter(n_driver, type == "weight")$n_dr_p), digits = 2)`; Spearman rank correlation `r round(src_bi_w$estimate, digits = 2)`, *p* `r fix_small_pvalue(src_bi_w$p.value)`).
-In addition, we found that invaded communities were significantly more difficult to manage than uninvaded ones even when controlling for potential diversity effects (Figure 3). 
-Out of the various covariates we explored—total number of species, plant richness, pollinator richness, and the ratio of plant to pollinator richness—only the ratio of plant to pollinator richness was retained in the final model as determined by the AICc (Table S4).
-
-```{r fig_explaining-n-driver, include = FALSE, warning = FALSE, message = FALSE}
-
-par_res <- as.data.frame(residuals(m8, "partial"))
+Lastly, we allowed for variation between different communities by including the network identity as a random effect [@Bates2015]. 
+Candidate models and estimates were assessed using the same procedure as in the  models for *n~D~*.
+
+# Results
+
+## Manageability
+
+All of the networks studied had a driver-node density *n~D~* between `r round(min(dplyr::filter(n_driver, type == "weight")$n_dr_p), digits = 2)` and `r round(max(dplyr::filter(n_driver, type == "weight")$n_dr_p), digits = 2)` (mean `r round(mean(dplyr::filter(n_driver, type == "weight")$n_dr_p), digits = 2)`; Figure 3a).
+In addition, we found that, when controlling for potential species richness effects, the *n~D~* of invaded communities was smaller to those of non-invaded communities (Figure 3b; Table S5). 
+Nevertheless, of the various covariates we explored, the ratio of plants to pollinators showed the strongest relationship with *n~D~* (Table S4; Figure 3c). 
+Specifically, we found that, as the proportion of pollinators increases and the ratio plant/pollinator approaches unity, *n~D~* decreases (all our communities had more pollinators than plants). 
+Other covariates—connectance (link density) and species richness—had negative, but comparatively less important relationships with *n~D~*.
+
+```{r fig_explaining-n-driver, echo = FALSE, warning = FALSE, message = FALSE, fig.width = 3.245, fig.height = 4.8, fig.cap = "**Driver-node density**.
+(a) Histogram of the driver-node density (_n~D~_) for the twenty networks.
+(b) Invaded communities have lower *n~D~* than uninvaded communities even when controlling for factors related to species richness.
+The boxes cover the 25th–75th percentiles, the middle lines mark the median, and the maximum length of the whiskers is 1.5 times the interquartile range.
+(c) Out of the richness metrics, the ratio of plants to pollinators showed a strong, negative relationship with *n~D~*.
+In both plots, partial residuals correspond to the partial working residuals of the invasion status in our generalised linear mixed model."}
+
+par_res <- as.data.frame(residuals(manag_models@objects[[5]], "partial"))
 names(par_res) <- paste0(make.names(names(par_res)), "_res")
 par_res %<>%
-  dplyr::bind_cols(m8$data) %>%
-  dplyr::mutate(res_res = residuals(m8, "response"), 
-                res_wor = residuals(m8, "working"))
-
-f3 <- par_res %>%
+  dplyr::bind_cols(manag_models@objects[[1]]$data)
+
+p0 <- manag_models@objects[[1]]$data %>% 
+	ggplot(aes(x = n_dr_p)) + 
+	stat_density(size = 0.4, geom = "line") +
+	fer_theme +
+	xlab(expression(paste("driver-node density (", n[D], ")"))) +
+	ylab("density") +
+	theme(axis.title.y = element_text(vjust = 1, margin = margin(1,-3,1,1, unit = "lines")))
+
+p1 <- par_res %>%
   ggplot(aes(x = inv, y = inv_res)) +
@@
   scale_x_discrete(labels = c("uninvaded", "invaded"), name = "") +
-  ylab("adjusted manageability") +
+  ylab(expression(paste(n[D], " partial residuals"))) +
   coord_flip() +
@@
 
-pdf("./paper/figures/fig_3.pdf", height = 1.7, width = 3.245, family = "Times", compress = F, title = "Figure 3")
-f3
-dev.off()
-```
-
-```{r randomisations_z-scores, include = FALSE, warning = FALSE, message = FALSE}
+p2 <- par_res %>%
+  ggplot(aes(x = n_pla/n_pol, y = I.n_pla.n_pol._res)) +
+	geom_smooth(method = "lm", se = F, colour = "black", size = 0.5) +
+	geom_point(shape = 21) + 
+	fer_theme +
+	scale_x_continuous(name = "ratio of plants to pollinators") +
+	scale_y_continuous(name = expression(paste(n[D], " partial residuals"))) +
+	theme(axis.title.y = element_text(vjust = 1, margin = margin(1,-3,1,1, unit = "lines")))
+
+cowplot::plot_grid(p0, p1, p2, ncol = 1, align = "v") +
+	cowplot::draw_plot_label(label = c("(a)", "(b)", "(c)"), size = 8, fontface = "bold", y = c(1, 0.66, 0.33))
+# pdf("../paper/figures/fig_3.pdf", height = 1.7, width = 3.245, family = "Times", compress = F, title = "Figure 3")
+# f3
+# dev.off()
+
+```
+
+When exploring the effect of network structure itself, we observed that the driver-node density $n_D$ of empirical networks was, in general, not significantly different to the manageability of network randomisations that maintained the degree of individual species (Figure 4).
+However, we found that the $n_D$ of empirical networks was significantly larger than that of randomisations that maintained the network structure but that differed only on the direction of the asymmetries.
+
+```{r fig_randomisations, echo = FALSE, warning = FALSE, message = FALSE, fig.width = 3.245, fig.height = 1.7, fig.cap = "**The driver-node density _n~D~_ of empirical networks compared to network randomisations**.
+For each randomisation approach, we show the standarised rank of the empirical value compared to the set of randomisations.
+A scaled mean rank—akin to a p-value— less than 0.025 or greater than 0.975 (the areas shaded in light grey) suggests a significant difference between the empirical network and its randomisations.
+The empirical _n~D~_ is much larger than that of network randomisations in which the direction of asymmetries has been randomised.
+In contrast, the manageability of networks in which the species degrees were randomly shuffled were not significantly different.
+All boxes are as in Figure 3a."}
 r <- r_w %>%
@@
   dplyr::filter(is.na(sim))
-```
-
-When exploring the effect of network structure itself, we observed that the manageability of empirical networks was, in general, not significantly different to the manageability of network randomisations that maintained the degree or the strength of individual species (Figure 4).
-However, when comparing the empirical network to randomisations that maintained the network structure but randomised only the direction of the asymmetries, we found that empirical networks showed a significant tendency to have smaller values of manageability.
-
-```{r fig_randomisations, include = FALSE, warning = FALSE, message = FALSE}
+
 z_scores_method_order <- c("r0","swsh_both", "quasiswap_count","r00_ind", "r00_samp", "r00_both")
 
-f4 <- z_scores %>%
+p1 <- z_scores %>%
   dplyr::group_by() %>%
@@
                 m_n = replace(m_n, m_n == 3, 3.5)) %>%
-  dplyr::filter(!method %in% c("r00_both", "r00_ind", "r00_samp")) %>%
-  ggplot(aes(x = method, y = -1 * z_s)) +
-  geom_rect(aes(xmin = 0.5, xmax = 3.5, ymin = -Inf, ymax = qlogis(0.025)), fill = "#f0f0f0") +
-  geom_rect(aes(xmin = 0.5, xmax = 3.5, ymin = Inf, ymax = qlogis(0.975)), fill = "#f0f0f0") +
+  dplyr::filter(!method %in% c("r00_both", "r00_ind", "r00_samp", 
+  														 "swsh_both")) %>% # the maintain degree randomise strength option
+	dplyr::filter(type == "weight") %>%
+  ggplot(aes(x = method, y = z_s)) +
+  geom_rect(aes(xmin = 0.5, xmax = 2.5, ymin = -Inf, ymax = qlogis(0.025)), fill = "#f0f0f0") +
+  geom_rect(aes(xmin = 0.5, xmax = 2.5, ymin = Inf, ymax = qlogis(0.975)), fill = "#f0f0f0") +
 
   # geom_hline(yintercept = c(-0), linetype = 2, alpha = 0.7, size = 0.25) + 
-  geom_vline(aes(xintercept = 1.5), alpha = 0.6, size = 0.25) +
+  # geom_vline(aes(xintercept = 1.5), alpha = 0.6, size = 0.25) +
    geom_hline(yintercept = 0, size = 0.25, linetype = 2, colour = "grey30") +
@@
   scale_x_discrete(
-    labels = rev(c("maintain strength\nrandomise degree", "maintain degree\nrandomise strength", "random\nassymetry")),
-    # breaks = c("r00_samp", "swsh_both", "quasiswap_count", "r0"),
+    labels = rev(c("random degree", # "maintain degree\nrandomise strength", 
+    							 "random\nasymmetry")),
+    # breaks = c(#"r00_samp", #"swsh_both",
+    					 # "quasiswap_count", "r0"),
     expand = c(0,0)) +
@@
     coord_flip() +
-  ylab("mean rank of empirical manageability") + 
+  ylab(expression(paste("empirical ", n[D], " rank (scaled)"))) + 
   fer_theme +
-  theme(
-        legend.position = "none",
-				plot.margin = grid::unit(c(2, 1, 2, 0), "mm"), 
+  theme(legend.position = "none",
+				plot.margin = grid::unit(c(-1, 1, 2, 0), "mm"), 
 				# panel.grid.minor.x = element_blank(),
-				panel.grid.minor.y = element_blank())
-
-pdf("./paper/figures/fig_4.pdf", height = 2.1, width = 3.245, family = "Times", compress = FALSE, title = "Figure 4")
-f4
-dev.off()
-```
-
-### Relative importance of species
-
-```{r rel-importance, include = FALSE, warning = FALSE, message = FALSE}
-d_sp <- driver %>%
-  plyr::ldply(function(x) {
-    get_frequencies(x) %>%
-      dplyr::mutate(type = attr(x, "type"),
-                    scaled = attr(x, "scaled"))
-  })
-
-d_sp_bi <- driver_bi %>%
-  get_frequencies() %>%
-      dplyr::mutate(type = "z_bi",
-                    scaled = FALSE)
-
-d_sp <- dplyr::bind_rows(d_sp, d_sp_bi) %>%
-  dplyr::inner_join(meta)
-# d freq is the best proxy seems to be consistent with the invasive species being at the top rank for the bidirectional links
-# d_sp %>%
-#   dplyr::filter(inv, type == "z_bi") %>%
-#   dplyr::group_by(net_name, threshold) %>% 
-#   dplyr::mutate(d_freq_rank = rank(-d_freq, ties.method = "min")) %>%
-#   dplyr::filter(species %in% c("p_4", "p_25"))
-#
-
-correlations <- expand.grid(type = c("asymmetry", "max_dep"),
-            scaled = c(TRUE, FALSE)) %>%
-  plyr::ddply(c("type", "scaled"), function(x){
-    d_sp %>%
-      dplyr::filter(count == "visitation", 
-                    study != "ballantyne") %>% 
-      plyr::ddply(c("net_name", "threshold"), function(y){
-        u <- y %>% 
-          dplyr::filter(type == "z_bi" | 
-                          (type == x$type & scaled == x$scaled)) %>%
-          dplyr::group_by(type) %>%
-          dplyr::mutate(d_freq_rank = rank(-d_reim)) %>%
-          dplyr::select(species, type, d_freq_rank) %>%
-          tidyr::spread(type, d_freq_rank) %>%
-          `class<-`("data.frame")
-
-        if(ncol(u) == 3) {
-          a <- sets::as.set(u[u[, 2] == min(u[, 2]), 1])
-          b <- sets::as.set(u[u[, 3] == min(u[, 3]), 1])
-          c(rw2(u[,2], u[,3]), rw2(rank(-u[,2]), rank(-u[,3])), cor(u[,2], u[,3], method = "spearman"), sets::set_similarity(a, b))
-        } 
-        else c(NA, NA, NA, NA)
-
-      })
-  })
-
-corr_imp <- expand.grid(type = c("asymmetry", "max_dep"),
-            scaled = c(TRUE, FALSE)) %>%
-  plyr::ddply(c("type", "scaled"), function(x){
-    d_sp %>%
-      dplyr::filter(study == "ballantyne") %>% 
-      plyr::ddply(c("threshold"), function(y){
-        u <- y %>% 
-          dplyr::filter((type == "z_bi" & count == "importance") |
-                          (type == x$type & scaled == x$scaled & count == "visitation")) %>%
-          dplyr::group_by(type) %>%
-          dplyr::mutate(d_freq_rank = rank(-d_reim)) %>%
-          dplyr::select(species, type, d_freq_rank) %>%
-          tidyr::spread(type, d_freq_rank) %>%
-          `class<-`("data.frame")
-
-        if(ncol(u) == 3) rw2(u[,2], u[,3])
-        else NA
-
-      })
-  })
-```
-
-We found a strong agreement between the values of relative species' importance in the 11 networks for which we were able to calculate them using both mutual dependencies and asymmetries (Spearman's rank correlation ranged between *ρ* = [`r round(min(dplyr::filter(correlations, threshold == 0.5, type == "asymmetry", scaled == T)$V3, na.rm = T), digits = 2)`, `r round(max(dplyr::filter(correlations, threshold == 0.5, type == "asymmetry", scaled == T)$V3, na.rm = T), digits = 2)`], median `r round(median(dplyr::filter(correlations, threshold == 0.5, type == "asymmetry", scaled == T)$V3, na.rm = T), digits = 2)`).
-Moreover, both approaches identified a highly similar set of driver species (Jaccard similarity *J* = [`r round(min(dplyr::filter(correlations, threshold == 0.5, type == "asymmetry", scaled == T)$V4, na.rm = T), digits = 2)`, `r round(max(dplyr::filter(correlations, threshold == 0.5, type == "asymmetry", scaled == T)$V4, na.rm = T), digits = 2)`], median
-`r round(median(dplyr::filter(correlations, threshold == 0.5, type == "asymmetry", scaled == T)$V4, na.rm = T), digits = 2)`). 
-Notably, we found that the agreement was stronger for highly ranked species than for lowly ranked species (mean *r~w2~* = `r round(median(dplyr::filter(correlations, threshold == 0.5, type == "asymmetry", scaled == T)$V1, na.rm = T), digits = 2)` versus `r round(median(dplyr::filter(correlations, threshold == 0.5, type == "asymmetry", scaled == T)$V2, na.rm = T), digits = 2)`) when using the weighted rank correlation coefficient.
-Given the overall similarities, we concentrated on the relative rankings obtained using asymmetries in the following results.
-
-```{r importance, include = FALSE, warning = FALSE, message = FALSE, results = "hide"}
+				panel.grid.minor.y = element_blank(),
+				plot.background = element_blank())
+
+library(ggrepel)
+
+p2 <- data_frame(x = c(-0.05,0.05),
+					 xend = c(-1,1), 
+					 y = 0, yend = 0, 
+					 xtext = c(-0.5, 0.5),
+					 label = c("smaller\nthan random", "larger\nthan random")) %>%
+	ggplot(aes(x = x, y = y)) + 
+	geom_segment(aes(xend = xend, yend = yend), 
+							 arrow = arrow(angle = 15,
+							 							length = unit(3, "mm"), 
+							 							type = "open"), 
+							 size = 0.3, colour = "grey30") +
+	geom_label(aes(x = xtext, label = label), size = 2.2, y = 0.1, 
+						 label.size = 0, lineheight = 0.8, colour = NA,
+						 fill = "white") +
+	geom_text(aes(x = xtext, label = label), size = 2.2, y = 0.1, 
+						label.size = 0, lineheight = 0.8, colour = "grey10",
+						fill = "white") +
+	scale_x_continuous(expand = c(0,0)) +
+	scale_y_continuous(expand = c(0,0)) +
+	theme(plot.background = element_blank(), 
+				plot.margin = margin(0,0,0,0)) +
+	theme_void()
+
+cowplot::plot_grid(p2, p1, ncol = 1, align = "v", rel_heights = c(1.5,10))
+```
+
+## Relative importance
+
+Invasive species were classified as superior nodes *and* driver nodes in every single network they were present; that is, they always had the highest relative *f~S~* and *f~D~* (Figure 5a). 
+The model results suggest that these differences between invasive and native species are not underpinned by any intrinsic property of the invasive species, instead, they are due to species properties that apply to invasive and native species alike (Table 1).
+Specifically, we found that a species is more likely to be classified as a superior node if it had a large species strength (the sum of the dependences of all other species on the species of interest).
+To a smaller extent, visitation strength (a species' sum of visits) and the species degree also had a positive relationship with $f_S$. 
+In contrast, the relationships between species structural properties and $f_D$ were more less clear cut (Table 1). 
+Both invasive species (which for example tend to have a large degree, and high dependence strength) and pollinators (which generally have a smaller degree and dependence strength) were classified as driver nodes in a large proportion of the matchings.
+
+```{r glmulti-functions, include = FALSE, warning = FALSE, message = FALSE, results = "hide"}
 glmer.glmulti<-function(formula,data,random="",...){
@@
 })
-
-imp <- mod %>% 
+```
+
+```{r fig-dependency-fs, echo = FALSE, warning = FALSE, message = FALSE, fig.width = 3.245, fig.height = 3.2, fig.cap = "**Relationships between _f~S~_ and _f~D~_ and species structural properties**.
+(a) In all networks were they were present, invasive species were classified as superior (_f~S~_) and driver (_f~D~_) nodes in all possible control configurations.
+(b) Species strength (the sum of the dependences of other species on the species of interest) is the single most important factor explaining _f~S~_.
+Visitation strength and degree also had an important albeit comparatively smaller effect (dashed lines correspond to $\\pm$ one standard deviation of these factors).
+Invasive species are depicted as circles."}
+data <- mo 
+trans <- function(x, orig){
+  x * attr(orig, "scaled:scale") + attr(orig, "scaled:center")
+}
+
+b_trans <- function(x, orig){
+  (x - attr(orig, "scaled:center")) / attr(orig, "scaled:scale")
+}
+
+pred_data <- data.frame(de = rep(b_trans(exp(c(seq(
+	log(trans(min(data$de, na.rm = T), data$de)),
+	log(trans(max(data$de, na.rm = T), data$de)),
+                                length = 500))), data$de),3),
+            d = rep(c(-1,0,1), each = 500),
+            vi = rep(c(-1,0,1), each = 500),
+            type = rep(c("exp", "mean", "exp"), each = 500),
+            # vi = seq(min(data$vi), max(data$vi), length.out = 500),
+            eig_cen = mean(data$eig_cen, na.rm = T),
+            n = mean(data$n, na.rm = T),
+            guild = "pla")  %>%
+  dplyr::filter(!(n == 2 & vi == -2),
+                !(n == -2 & vi == 2)) %>%
+  dplyr::mutate(q = predict.glmulti(mod[[1]],
+                                    select = 2L,
+                                    newdata = .,
+                                    re.form = NA)$averages %>%
+                  as.vector(),
+                p = plogis(q)) %>%
+  dplyr::mutate(de = de * attr(data$de, "scaled:scale") + attr(data$de, "scaled:center"),
+                vi = vi * attr(data$vi, "scaled:scale") + attr(data$vi, "scaled:center"))
+
+data_pp <- data
+data_pp$pred_ri <- plogis(predict.glmulti(mod[[1]], re.form = NA, select = 1L))
+data_pp$de_s <- data$de * attr(data$de, "scaled:scale") + attr(data$de, "scaled:center")
+data_pp <- lapply(data_pp, as.vector) %>% as.data.frame
+
+p1 <- pred_data %>%
+  ggplot() +
+  geom_line(aes(x = de, y = p, linetype = type, colour = type, group = interaction(n, vi)), show.legend = F, size = 0.5) +
+  scale_x_log10(expand = c(0,0), breaks = c(0.01, 0.1, 1, 10, 100)) +
+   geom_point(data = dplyr::arrange(data_pp, invasive) %>% dplyr::filter(invasive == T), aes(x = de_s, y = pred_ri, fill = invasive, shape = guild, size = invasive), show.legend = F) +
+    scale_shape_manual(values = c(21, 23)) +
+  scale_size_manual(values = c(1.5,1.5)) +
+  scale_fill_manual(values = c("white","#e41a1c")) + 
+  scale_color_manual(values = c("#525252", "black")) +
+  scale_linetype_manual(values = c(2, 1)) +
+  xlab("species strength") +
+  ylab(expression(f[S])) +
+  fer_theme
+
+# invasive comparison plot
+p2 <- mo %>%
+	# dplyr::filter(guild == "pla") %>%
+	dplyr::select(invasive, f_s, f_d) %>%
+	dplyr::mutate(invasive = plyr::mapvalues(invasive, c(F,T), c("native", "invasive"))) %>%
+	reshape2::melt(measure.vars = c("f_s", "f_d")) %>%
+	ggplot(aes(y = value, x = variable)) + 
+	geom_boxplot(size = 0.3, outlier.shape = 21, outlier.size = 1)  +
+    # coord_flip() +
+  ylab("proportion") + 
+	scale_x_discrete(labels = parse(text = c("f[S]", "f[D]")), name = "") +
+	# scale_x_discrete(name = "", labels = c("native", "invasive")) +
+  fer_theme +
+  theme(legend.position = c(0.99,0.02),
+  			legend.direction = "horizontal",
+  			legend.justification = c(1,0),
+				plot.margin = grid::unit(c(-1, 1, -3, 0), "mm"), 
+				# panel.grid.minor.x = element_blank(),
+				panel.grid.minor.y = element_blank(),
+				strip.text = element_text(size = 8, hjust = 1, vjust = -1)) +
+	scale_color_manual(values = RColorBrewer::brewer.pal(5, "Greys")[c(5,4)],
+										 name = "", 
+										 labels = c(expression(f[S]), expression(f[D]))) +
+	facet_grid(~invasive)
+
+cowplot::plot_grid(p2, p1, ncol = 1, labels = c("(a)", "(b)"), label_size = 8, 
+									 hjust = 0, vjust = 1.1, align = "v", rel_heights = c(1,1.16))
+```
+
+```{r table-species-model-coef, echo = FALSE, warning = FALSE, message = FALSE, results = "asis", sanitize = FALSE, cache = T}
+coef_tables <- mod %>%
+	plyr::llply(function(x){
+		x %>%
 			coef.glmulti(select = 0.95) %>%
@@
                                            "guild (pollinator)", "degree", "invasive sp."))) %>% 
-  dplyr::arrange(-pare, -Importance, -Estimate, factor) %>% 
-  dplyr::select(-pare)
-
-print_table <- . %>%
-  # dplyr::mutate(factor = paste0("$", factor, "$")) %>%
-  magrittr::set_names(c("factor", "est.", "var", "No. mod.", "imp.", "C.I.")) %>% 
-  dplyr::select(-var) %>%
-  kable(format = "latex", align = "c", booktabs = T, digits = 2, escape = F, linesep = "")
-
-imp %>%
-	magrittr::set_names(c("factor", "est.", "var", "No. mod.", "imp.", "C.I.")) %>% 
-  dplyr::select(-var) %>% 
-	dplyr::mutate(est. = round(est., 2), 
-								imp. = round(imp., 2), 
-								C.I. = round(C.I., 2)) %>% 
-	write.csv("./paper/Table 1.csv", row.names = F)
-```
-
-```{r species, include = FALSE, warning = FALSE, message = FALSE}
-data <- mo
-net <- "./data/processed/networks" %>%
-	read_networks()
-
-guild <- c("pla", "pol") %>%
-  plyr::ldply(function(y){
-    o <- lapply(net, function(x) igraph::V(x)[igraph::V(x)$type == y]$name) %>%
-      unlist() %>% unique()
-    data.frame(guild = y, species = o)
+  magrittr::set_names(c("factor", "est.", "var", "mod.", "imp.", "C.I.", "pare")) %>%
+			dplyr::mutate(absEstimate = abs(est.)/C.I.) %>%
+  dplyr::arrange(-pare, -imp., -absEstimate, factor) %>% 
+  dplyr::select(-pare, - absEstimate) 
 	})
 
-invasive_sp <- dplyr::filter(meta, inv) %>%
-  dplyr::mutate(species = plyr::mapvalues(invader, 
-                                          c("car", "op", "imp"),
-                                          c("p_4", "p_25", "Impatiens glandulifera")), 
-                invasive = T) %>%
-  dplyr::select(net_name, species, invasive)
-
-connected_sp <- data %>% dplyr::select(net_name, species) %>% 
-  dplyr::mutate(connected = T)
-
-s_p_s <- s_p %>%
-  dplyr::full_join(invasive_sp) %>%
-  dplyr::mutate(invasive = replace(invasive, is.na(invasive), FALSE)) %>%
-  dplyr::inner_join(guild) %>%
-  dplyr::inner_join(meta) %>%
-  dplyr::filter(study != "ballantyne") %>%
-  dplyr::inner_join(connected_sp)
-
-dd <- data %>% lapply(as.vector) %>% as.data.frame()
-dd <- s_p_s %>%
-  dplyr::select(net_name, species, invasive, connected) %>%
-  dplyr::inner_join(dd) %>%
-  dplyr::mutate(pp = predict.glmulti(mod, select = 0.2, newdata = ., re.form = NA),
-                pp = as.vector(pp),
-                pp = plogis(pp),
-                de2 = de * attr(data$de, "scaled:scale") + attr(data$de, "scaled:center"))
-
-trans <- function(x, orig){
-  x * attr(orig, "scaled:scale") + attr(orig, "scaled:center")
-}
-
-b_trans <- function(x, orig){
-  (x - attr(orig, "scaled:center")) / attr(orig, "scaled:scale")
-}
-
-pred4 <- data.frame(de = rep(b_trans(exp(c(seq(log(trans(min(data$de), data$de)),
-                                log(trans(max(data$de), data$de)),
-                                length = 500))), data$de),3),
-            n = rep(c(-1,0,1), each = 500),
-            vi = rep(c(-1,0,1), each = 500),
-            type = rep(c("exp", "mean", "exp"), each = 500),
-            # vi = seq(min(data$vi), max(data$vi), length.out = 500),
-            eig_cen = mean(data$eig_cen, na.rm = T),
-            d = mean(data$d, na.rm = T),
-            guild = "pla") %>%
-  dplyr::filter(!(n == 2 & vi == -2),
-                !(n == -2 & vi == 2)) %>%
-  dplyr::mutate(q = predict.glmulti(mod,
-                                    select = 2 %>% `class<-`("integer"),
-                                    newdata = .,
-                                    re.form = NA)$averages %>%
-                  as.vector(),
-                p = plogis(q)) %>%
-  dplyr::mutate(de = de * attr(data$de, "scaled:scale") + attr(data$de, "scaled:center"),
-                vi = vi * attr(data$vi, "scaled:scale") + attr(data$vi, "scaled:center"))
-
-```
-
-Invasive species were driver species in every single network they were present, that is, they always had the highest relative ranking of species importance (Figure 5). 
-Overall, plants showed significantly higher levels of importance than pollinators (Mann-Whitney-Wilcoxon test, *p* = `r fix_small_pvalue(wilcox.test(pp ~ guild, data = dd, alternative = "greater")$p.value, 3)`).
-However, this difference can largely be explained by the strength of dependency of the species (the sum of the dependencies for a given species). 
-Indeed, when averaging over the set of models that accounted at least 95\% of the evidence based on AICc, we found that species' strength of dependency is the single most important factor determining the relative importance of species for network control (Table 1, Figure 5).
-In contrast, the number of visits a species makes (or receives) and its contribution to nestedness had only a marginal effect on its relative importance.
-
-```{r fig_species-alt, include = FALSE, warning = FALSE, message = FALSE}
-
-data_pp <- data
-data_pp$pred_ri <- plogis(predict.glmulti(mod, select = as.integer(1), re.form = NA))
-data_pp$de_s <- data$de * attr(data$de, "scaled:scale") + attr(data$de, "scaled:center")
-data_pp <- lapply(data_pp, as.vector) %>% as.data.frame
-
-f5 <- pred4 %>%
-  ggplot() +
-  geom_line(aes(x = de, y = p, linetype = type, colour = type, group = interaction(n, vi)), show.legend = F, size = 0.5) +
-  scale_x_log10(expand = c(0,0)) +
-   geom_point(data = dplyr::arrange(data_pp, invasive) %>% dplyr::filter(invasive == T), aes(x = de_s, y = pred_ri, fill = invasive, shape = guild, size = invasive), show.legend = F) +
-    scale_shape_manual(values = c(21, 23)) +
-  scale_size_manual(values = c(1.5,1.5)) +
-  scale_fill_manual(values = c("white","#e41a1c")) + 
-  scale_color_manual(values = c("#525252", "black")) +
-  scale_linetype_manual(values = c(2, 1)) +
-  xlab("dependency strength") +
-  ylab("relative importance") +
-  fer_theme
-
-pdf("./paper/figures/fig_5.pdf", height = 2.2, width = 3.245, family = "Times", compress = F, title = "Figure 5")
-f5
-dev.off()
-```
-
-## Discussion
-
-Our results reveal that the structural differences associated with biotic invasions are reflected in a potential decrease in our ability to alter the state of the community post invasion. 
-Furthermore, invasive mutualists were always driver species in the communities they invade.
-As driver species, they occupy a particularly dominant role in which changes on their abundance have the potential to propagate broadly trough the community and in turn affect the abundances of many other species.
-
-At a community level, we demonstrate that the manageability of mutualistic networks is strongly governed by the asymmetric nature of mutual dependencies—which constitute the foundations of the structure and stability of mutualistic networks [@Memmott2004; @Vazquez2004; @Bascompte2006; @Lever2014; @Astegiano2015].
-Indeed, our empirical networks exhibit markedly lower levels of manageability compared to randomisations in which the visitation network was unchanged but where the observed patterns of dependence were broken.
-However, consistent with previous results [@Liu2011], we show that the manageability of empirical networks was indistinguishable from that of networks with a random structure that maintained the degree or strength of each species in the community.
-Therefore, the asymmetries at the species level (specialization-generalization asymmetries) and the link level (interaction's dependence asymmetries) appear to be sufficiently constrained by the distribution of species degree and strength [@Melian2002].
-Generally speaking, this strong relationship between the asymmetric dependences and manageability might explain why invasive species reduce the manageability of their communities. 
-Invasive species have been previously found to exacerbate the asymmetries in the network and ostensibly increase the stability of their community [@Aizen2008; @Bartomeus2008; @Henriksson2016].
-
-The changes in the asymmetries we found in the invaded networks are also reflected at a species level by the high relative importance of invasive species.
-However, we found that invasive plants are not inherently different to their native counterparts [@Stouffer2014].
-Invasive plants, just like any other mutualist in our data set, tend to be driver species to the degree to which their interaction partners are collectively more dependent on them than the other way around.
-Previous studies have found that super-generalists, like invasive species, play a central role in their networks [@Vila2009; @Palacio2016].
-Our results take this one step further and indicate that dependence strength, rather than generalism or other metrics of centrality, is the factor that best explains how important a species is for its community's dynamics.
-
-Because of their effects on other species in the community, driver species might be natural candidates for management interventions. 
+coef_tables %<>%
+	plyr::llply(function(x){
+		x %>%
+			dplyr::select(factor, imp., est., var, mod., C.I.) %>%
+			magrittr::set_names(c(" ", "imp.", "est.", "var", "mod.",  "C.I.")) %>%
+			dplyr::select(-var, -mod.)
+	})
+
+attr(coef_tables, "subheadings") <- paste0("$", names(mod), "$")
+coef_tables %>%
+	xtable::xtableList(caption = "\\textbf{Factors explaining species importance}.
+Factor estimates correspond to the average over all models that accounted for 95\\% of the AIC evidence.
+Confidence intervals correspond to $\\alpha = 0.05$.",
+										 digits =  c(0, 0, 2, 2, 2),
+										 display = c("d", "s", "f", "f", "G")) %>%
+	print(booktabs = T, include.rownames = F,  caption.placement = "top", size = "\\small",comment = F, sanitize.text.function = function(x){x})
+```
+
+# Discussion
+
+Contrary to our initial hypothesis, we found some evidence that invaded communities might be easier to manage than uninvaded ones from a control-theoretic perspective. 
+Our results reveal, however, that this effect is comparatively small, and the structural differences among different networks are more strongly related to potential differences in our ability to alter the state of the community via external interventions.
+Despite the small effect of invasion status at a network level, we found that invasive mutualists occupy a particularly dominant role in their communities for two reasons. 
+First, as species with a high *f~S~*, changes on their abundance have the potential to propagate broadly through the community and, in turn, affect the abundances of many other species. 
+Second, as species with a high *f~D~*, they are also indispensable when it comes to fully controlling the plant-pollinator network. 
+At a community level, we demonstrate that the manageability of mutualistic networks is strongly governed by the asymmetric nature of mutual dependences—which constitute the foundations of the structure and stability of mutualistic networks [@Memmott2004; @Vazquez2004; @Bascompte2006; @Lever2014; @Astegiano2015].
+Moreover, these mutual dependences seem to be constrained by the effects of both the patterns of species richness at each trophic guild and a network's degree distribution [@Melian2002; @Bluthgen2007].
+Indeed, the difference between the driver-node density (*n~D~*) of our empirical networks and that of randomisations depended strongly on the null model's randomisation approach. 
+While the empirical *n~D~* was indistinguishable from that of networks with a random structure that maintained the degree of each species in the community, it was larger than that of randomisations in which the directed network was unchanged but where the observed patterns of dependence were broken.
+
+Invasive species have been previously found to exacerbate the asymmetries in their communities [@Aizen2008; @Bartomeus2008; @Henriksson2016]. 
+Although this might cause differences both at the community and the species level, we found that invasive plants are not inherently different to their native counterparts [@Stouffer2014; @Emer2016a].
+Invasive plants, just like any other mutualist in our data set, tend to be classified as a superior node with a frequency (*f~S~*) proportional to the degree to which their interaction partners are collectively more dependent on them than the other way around.
+Previous studies have found that supergeneralists, like invasive species, play a central role in their networks [@Vila2009; @Palacio2016].
+Our results take this one step further and indicate that dependence strength, rather than generalism or other metrics of centrality, is the factor that best explains the cascading effects a species could trigger on its community.
+
+Because of the ability that our approach has to infer the magnitude of the effects that each species has on others in the community, it is tantalising to use it to select promising candidates for management interventions.
+To this end, the two indices we have used to characterise a species provide two complementary pieces of information. 
+Our first index *f~D~*---the frequency with which a species is classified as a driver node---provides an indication of the likelihood that a species forms part of the set of species that must be manipulated in order to control *all* species in the community.
+This driver-node concept has received considerable attention in the structural-control literature and indeed shows substantial potential to provide useful ecological insight. 
+Nevertheless, we anticipate two caveats that hinder its direct utility for management applications.
+First, unlike some other types of complex systems, fully controlling an ecological community is almost certainly out of reach for all but the simplest, due to either the number of required interventions or the practical difficulties of their implementation [@Motter2015].
+For instance, our results suggest that full control of the pollination networks would require direct interventions on anywhere from 40--90% of the species.
+Second, @Ruths2014 established that driver nodes arise due to distinct mechanisms and therefore species with markedly different network metrics can act as driver nodes in their community (Supporting Information S2).
+
+Our second index *f~S~* is, however, directly related to the likelihood a species affects the abundance of another species in all of the control strategies considered. 
+Importantly, this is irrespective of whether controlling the entire network is ultimately desired and/or feasible. 
+In fact, because superior nodes are always at the beginning of a matched link, species with a high *f~S~* are more likely to be the subjects of management interventions when controlling the abundances of a target set of species—as opposed to the entire network—is desired [@Gao2014].
+An important advantage here is that the target set of species does not have to be the same set to which interventions are applied. 
 For instance, despite inconsistent outcomes in practice [@Suding2004; @Rodewald2015; @Smith2016], our results suggest that current restoration approaches that focus on direct eradication of invasive species might indeed be an effective way to modify ecosystem state.
-Nevertheless, our results also indicate that removals must be exercised with caution as invaded communities tend to be highly dependent on invaders and therefore acutely vulnerable to their eradication [@Traveset2013; @Albrecht2014].
-Although useful for identifying conservation priorities, our approach is different to previous attempts to quantify species importance that concentrate on measures of centrality, position, co-extinction or uniqueness [@Jordan2006; @Jordan2009; @Lai2012; @McDonald-Madden2016].
-Instead the concept of driver species is more akin to the original concept of keystone species, which illustrated how changes on the abundance of a key species in turn affect the abundances of other members of the community [@Paine1969; @Paine1995].
-However, while keystone species were traditionally identified by gauging how a community's population dynamics respond to a perturbation [@Mills1993], the driver species concept operates the other way round; namely, it uses the community dynamics, underpinned by the interspecific effects, to infer the effects of a perturbation.
-While it is challenging to quantify the dependence of species in an ecological community, a purely experimental approach that identifies dynamically important species in a similar manner might be even more difficult to implement.
-
-Overall, our investigation confirms the conclusions of previous studies that suggested that, in contrast to other types of complex systems, the structure of ecological networks renders them remarkably difficult to control [@Liu2011; @Ruths2014].
-In a hypothetical situation in which the goal were to regulate the abundances of all species in a pollination community, our results indeed suggest that we would need to directly intervene with the abundances of at least 40-90% of those species.
-Fully controlling an ecological community is no doubt an idealistaion, as designing and implementing the management interventions needed is currently impractical. 
-Nevertheless, the ''manageability'' of an ecological community, which is related to the number of species that would require a directed intervention, can provide a simple, straightforward, and theoretically-informed indication of the degree to which the community is self-regulated and therefore how difficult it might be to modify its state in one way or another.
-
-In this study, we illustrate how a control-theoretic approach can be adopted when estimating the effect of invasions—a major driver of global change—on mutualistic communities.
-Notably, it can also be extended to understand the structural effects of other kind of perturbations and for systems governed by different types of interactions. 
-Moreover, we see great potential by explicitly integrating control theory with dynamic models of species densities [@Cornelius2013; @Gibson2016]. 
-From an ecological perspective, this integration can provide even deeper insights into the relationship between controllability and species coexistence.
-It can also help identify potential trade-offs between persistence at the species and the community level. 
-From a conservation perspective, the combined approach can shift our focus beyond the identification of ideal targets for intervention to design informed interventions that legitimately achieve restoration goals.
+Nevertheless, our results also indicate that removals must be exercised with caution. 
+Not only it is hard to predict the direction in which the system will change, but invaded communities also tend to be highly dependent on invaders and therefore acutely vulnerable to their eradication [@Traveset2013; @Albrecht2014].
+
+Despite the apparent similarities, our approach is different to previous attempts to quantify species importance in a few key ways.
+Existing metrics usually harness species featuresi, like centrality, position, co-extinction or uniqueness, to infer their effect on other species [@Allesina2004; @Jordan2006; @Jordan2009; @Lai2012]. 
+In contrast, our control-based approach tackles that question directly.
+Although they are relatively simple to calculate, it has been shown that classic species-level network metrics do not necessarily reveal the best set of species to manage [@Eklof2013; @McDonald-Madden2016].
+Our approach, however, is not based on a single structural metric but instead acknowledges the existence of multiple management strategies. 
+By allowing for the fact that some strategies are better than others depending on the context, control theory implicitly highlights that management decisions should not be based on a single technique.
+As such, ours and other flexible approaches that take a network-wide approach might prove more useful to guide ecosystem management if we want to go beyond using network metrics to minimise topological species loss [@McDonald-Madden2016].
+
+Despite its conceptual advantages, our approach still relies on knowledge of the network of interaction between species. 
+Nevertheless, our results and previous basic research show that, as long as the proportion of sampled links is enough to provide indication of the actual degree distribution (and in turn the species dependences), *n~D~*, *f~S~* and *f~D~* can still provide a simple, straightforward, and theoretically informed indication of the degree to which the community is self regulated and therefore how difficult it might be to modify its state in one way or another using some of its constituent species [Supporting Information S5; @Nepusz2012].
+
+In this study, we illustrate how a control-theoretic approach can be better adopted in network ecology to evaluate the effect of invasions and other kinds of perturbations. 
+Although our pollination specific results might not be directly translatable to other ecological systems because of the degree constrains imposed by bipartite networks, the approach we propose is applicable wherever species abundances are influenced by their interactions.
+Exciting open questions lie ahead. How to design the precise "control signals" to reach a desired ecosystem state or conservation outcome? 
+What are the implications of assuming linear species dynamics?
+How important it is to include several interaction types for our understanding of manageability and species importance?
+What are the implications for species coexistence? 
+Which are the trade-offs between persistence at the species and the community level? 
+Answering each of these questions might require its evaluation in different ecological systems, an explicit integration of control theory with numerical models of species densities [@Cornelius2013; @Gibson2016], and experimental tests on simple communities.
+Nevertheless, the potential rewards are encouraging from both an ecological and conservation perspective, where an integrated approach can shift our focus beyond the identification of ideal targets for intervention to the design of informed interventions that legitimately achieve restoration goals.
+
+# Appendix 1: Glossary
+
+Driver node
+  ~ An unmatched node in a maximal cardinality matching or a maximum matching.
+From the control perspective, driver nodes are those to which external control signals must be applied in order to gain full control of the network.
+
+Matched/unmatched link
+  ~ A link is refered to as *matched* if it is part of a matching, and *unmatched* otherwise.
+
+Matched/unmatched node
+  ~ A node is refered to as *matched* if it is at the end of a matched link, and *unmatched* otherwise.
+
+Matching
+  ~ A set of links in which no two of them share a common starting or ending node.
+
+Matching size
+  ~ The number of matched links in a matching.
+
+Matching weight
+  ~ The sum of the weights of all matched links in a matching.
+
+Maximal cardinality matching
+  ~ A matching with the largest possible matching size. In unweighted/binary networks, all maximal cardinality matchings are also maximum matchings.
+
+Maximum matching
+  ~ A matching with the largest possible matching size *and* largest possible matching weight.
+
+Superior node
+  ~ The node at the start of a matched link. From the control perspective, superior nodes make up the chains that propagate the control signals through the network.
 
@@
 The authors thank Dr.
-Takeuki Uno for the insight provided to find the set of all maximum matching algorithms, and Jason Tylianakis, Bernat Bramon, Matthew Hutchinson, and Marilia Gaiarsa for feedback in early stages of the project.
+Takeuki Uno for the insight provided to find the set of all maximum matching algorithms, and Jason Tylianakis, Bernat Bramon Mora, Guadalupe Peralta, Rogini Runghen, Warwick Allen, Matthew Hutchinson, and Marilia Gaiarsa for feedback and valuable discussions.
 EFC acknowledges the support from the University of Canterbury Doctoral Scholarship, the University of Canterbury Meadow Mushrooms Postgraduate Scholarship, a New Zealand International Doctoral Research Scholarship, and a travel grant from the European Space Agency.
@@
 
-## References
+# References

### 2017-03-01 paper/manuscript.Rmd
First attempt to reduce length: to 5270
From ~5600 ~5270

@@
 
-* **Number of words:** 160 abstract; approx. 5600 main text.
+* **Number of words:** 148 abstract; approx. 5278 main text.
 
@@
 
-Complex systems are characterised by relationships in which the whole is often greater than the sum of its parts [@Jorgensen1998; @Levin1999; @Montoya2006].
-Within community ecology, a complex systems approach has led to the development of a variety of analytical and simulation tools with which to understand, for example, the role of species when embedded in an intricate network of interactions [@Pascual2005; @Bascompte2009; @Stouffer2012].
-The inherent complexity of nature, however, has regularly hindered—or at least greatly complicated—our ability to find management solutions to the many problems ecological communities face. 
+In a complex system, the whole is often greater than the sum of its parts [@Jorgensen1998; @Levin1999; @Montoya2006].
+Within community ecology, a complex-systems approach has led to the development of analytical and simulation tools with which to understand, for example, the role of species embedded in a network of interactions [@Pascual2005; @Bascompte2009; @Stouffer2012].
+The inherent complexity of nature, however, has regularly hindered—or at least complicated—our ability to find management solutions to many problems ecological communities face. 
 To overcome this obstacle, we require a framework that allows us to explain, predict, and manage ecological communities, particularly when they are confronted with perturbations [@Sole2001; @Green2005].
-Ideally, such a framework needs to be able to account for their complex structure and the dynamics that determine the species abundances and the state of the community.
+Ideally, such a framework is equipped to account for their complex structure and the dynamics that determine the species abundances and the state of the community.
 
 Among the various possibilities, *control theory* appears to be a strong candidate [@Isbell2013].
-This method, widely used in engineering to determine and supervise the behaviour of dynamical systems [@Motter2015], is well equipped to deal with the many feedbacks present in ecological communities [@Liu2016].
+Widely used in engineering to determine and supervise the behaviour of dynamical systems [@Motter2015], it is well equipped to deal with the many feedbacks present in ecological communities [@Liu2016].
 Research in this area has established a strong link between the structure of complex networks and their *controllability*—the relative ability to manipulate network components to drive the system to a desired state [@Liu2011; @Cornelius2013; @Ruths2014].
 These advances suggest that it is in principle possible to alter a whole ecological community's composition by modifying the abundances of only a few species.
-Furthermore, applications of control theory to ecological networks can also take into account the extent to which changes in the abundances of one species may ripple through the community [@Cornelius2013].
-Therefore, control theory could also be harnessed to provide an indication of which species are most relevant from a structural and dynamic perspective.
+Applications of control theory to ecological networks can also take into account the extent to which changes in the abundances of one species may ripple through the community [@Cornelius2013].
+Therefore, control theory could also be harnessed to help identify which species are most relevant from a structural and dynamic perspective.
 
 This information is valuable not only for basic ecology, but it might be also relevant to address more applied management and conservation challenges. 
-This is particularly true in the context of biotic invasions, where identifying key players in the community is a prerequisite to informed attempts to either alter the state of invaded ecosystem and maintain the state of uninvaded ones.
+This is particularly true in the context of biotic invasions, where identifying key players in the community is a prerequisite to informed attempts to alter the state of invaded ecosystems and maintain the state of uninvaded ones.
 Despite recent advances in network theory, practical challenges to the conservation of interaction networks persist [@Tylianakis2010], and the link between the structure of complex networks and our ability to manage and conserve them is still ambiguous [@Bluthgen2010; @Kaiser-Bunbury2015].
-To complicate things further, biotic invasions can induce dramatic changes in the patterns of interactions that determine the structure of ecological networks [@Baxter2004; @Tylianakis2008; @Ehrenfeld2010a].
-Understanding how the differences in network structure before and after the invasion impact our ability to manage the communities is thus a double challenge, but it is also the critical first step towards a fully informed recovery.
-Despite the apparent overlap, a control-theoretic perspective has not been adopted in an invasion context. 
-This is perhaps because of a lack of appropriate methodological tools that can account for the observed variation in the strength of interspecific effects that are characteristic of ecological networks [@Liu2011; @Isbell2013].
+To complicate things further, biotic invasions can induce dramatic changes in the patterns of interactions that determine the structure of ecological networks [@Baxter2004; @Tylianakis2008; @Ehrenfeld2010a], in particular pollination [@Olesen2002; @Aizen2008; @Bartomeus2008; @Vila2009; @Traveset2013].
+Understanding how the differences in network structure before and after invasion impact our ability to manage the communities is thus a double challenge, but it is also the critical first step towards a fully informed recovery.
+Despite the apparent overlap, the control-theoretic perspective has not been adopted in an invasion context.
 
-To bridge this gap, we outline an approach to apply theory on the control of complex systems in an ecological context and implement it using empirical data.
+To bridge this gap, we outline an approach to apply control theory in an ecological context and implement it using empirical data.
 Specifically, we use a set of ten pairs of uninvaded and invaded plant-pollinator communities to investigate the link between invasion, network structure and ecological management. 
@@
 Second, we ask whether some species are more important than others at driving the population dynamics of the community and which factors determine this importance.
-We focus on these two particular applications for a variety of reasons. 
-Biotic invasions are known to produce tractable changes in the structure of ecological networks, and these changes can be particularly pronounced in mutualistic networks between plants and pollinators where biotic invasions have been shown to modify the strength of species interactions and the degree of network nestedness and connectivity [@Olesen2002; @Aizen2008; @Bartomeus2008; @Vila2009; @Traveset2013].
-Furthermore, although species are involved in multiple types of interactions, plant-pollinator networks provide an ideal framework to answer these questions. 
-On the one hand, community networks that quantify relative levels of interaction are readily available. 
-On the other, the bipartite nature of pollination networks makes it possible to simplify assumptions of how these interactions translate into interspecific effects.
 
@@
 Disregarding practical considerations, any network (community) could hypothetically be fully controlled if we control the state of every single node (species) individually.
-At the core of control theory of complex networks, however, rests the idea that the state of a node depends on the state of the nodes it interacts with, and the particular form of this dependence is determined both by the dynamic relationship among interacting nodes as well as the structure of the links in the network.
-This principle can therefore be harnessed to find a subset of *driver nodes* to which to apply external input signals which then drive the state of every other node in the network to a desired configuration.
+At the core of control theory of complex networks, however, rests the idea that the state of a node depends on the state of the nodes it interacts with, and the form of this dependence is determined by both the dynamic relationship among interacting nodes and the structure of the links in the network.
+This principle can therefore be harnessed to find a subset of *driver nodes* to which to apply external input signals which then drive the state of every other node in the network to a desired configuration [@Liu2016].
 
 Conveniently the information necessary to determine the minimum number of driver nodes *D* in a network with linear dynamics is fully contained in the network structure [@Kalman1963; @Liu2011; @Motter2015].
-We therefore start here from the assumption that an ecological network can, at least near equilibrium points, be described by $\frac{dx}{dt} = Ax + Bu(t)$, where the change over time of its state ($\frac{dx}{dt}$) depends on its current state *x* (for example the species' abundances), an external time-varying input *u(t)*, and two matrices *A* and *B*, which encapsulate information about the network structure and how the species respond to the external input, respectively.
+We therefore start here from the assumption that an ecological network near equilibrium points can be described by $\frac{dx}{dt} = Ax + Bu(t)$, where the change of its state over time ($\frac{dx}{dt}$) depends on its current state *x* (for example the species' abundances), an external time-varying input *u(t)*, and two matrices *A* and *B*, which encapsulate information about the network structure and how the species respond to the external input, respectively.
 Even though linearity might be a strong assumption, it has been shown that fundamental insight about the control of complex systems can be gained without a detailed knowledge of the nonlinear dynamics and the system parameters [@Liu2016], an important step towards ultimately understanding the controllability of systems with nonlinear dynamics [@Liu2011].
-This means that structural controllability can be applied to a wide range of readily available network representations of ecological communities to provide a strong indication of our ability to control them.
-Moreover, we show here how quantitative data about species interactions can help us move past some of the limitations of structural controllability by better approximating the role of interspecific dynamical relationships without being overly dependent on the specific choices of how these dynamics are modelled or characterised.
+This means that structural controllability can be applied to a wide range of network representations of ecological communities to provide an indication of our ability to control them. 
+Moreover, we show here how quantitative data about species interactions can help us move past some of the limitations of structural controllability by better approximating the role of interspecific dynamic relationships without being overly dependent on the choices of how these dynamics are modelled or characterised.
 
@@
 
-The number of driver nodes *D* can provide a structural indication of how difficult a network's control might be.
+The number of driver nodes *D* provides a structural indication of how difficult a network's control might be.
 This is because systems that require a large number of external input signals are intuitively more difficult or costly to control.
 In an ecological context, external inputs that modify the state of a node can be thought of as management interventions.
-Therefore, the density of driver nodes $n_D = \frac{D}{S}$, where *S* is the total number of species in the community, can be seen as a measure of the extent to which network structure can be harnessed for network control.
-For instance, while a hypothetical "network" in which species do not interact but instead function independently from each other would require direct interventions for every single species to achieve full control, a linear food chain would require just one species to be directly controlled to harness cascading effects through the trophic levels that compose it.
+Therefore, the density of driver nodes $n_D = \frac{D}{S}$, where *S* is the total number of species in the community, is a measure of the extent to which network structure can be harnessed for network control.
+For instance, a hypothetical "network" in which species do not interact would require direct interventions for every single species to achieve full control, whereas a linear food chain would require just one species to be directly controlled to harness cascading effects through its trophic levels.
 From this perspective, it is possible to use *n~D~* as an index of the manageability of an ecological community, understood in the context of how difficult is to modify the abundances of species in the community using external interventions—a common theme in ecosystem management, conservation, and restoration.
@@
 Once we have the subset of links that constitute a matching, we can also classify the nodes in the network based on that matching (Figure 1).
-A node is said to be *matched* if it is at the end of a matched link and *unmatched* otherwise. 
-A node is also said to be *superior* if it is at the start of a matched link.
+A node is called *matched* if it is at the end of a matched link and *unmatched* otherwise. 
+A node is also called *superior* if it is at the start of a matched link.
 Note that a node cannot be superior if it has no outgoing links.
-Notably, these node categories are what help us to link a maximum matching back to the concept of network controllability, as follows.
+Notably, these node categories are what helps us to link a maximum matching back to the concept of network controllability, as follows.
 Unmatched nodes are the *driver nodes* *D* because they have no superior in the network and must be directly controlled by an external input [@Liu2011].
@@
 
-While calculating *n~D~* provides an indication of the manageability of an ecological community, it does not provide information about the identity of the species that compose the set of driver nodes.
-Ecologically, potential differences between species are acutely relevant because management and conservation resources are limited, and therefore ecological interventions should ideally be focused on the set of species that might provide the largest impact.
-Moreover, maximum matchings in a network are often not unique, and each different maximum matching indicates a unique path that can potentially be used to control the network. 
+While calculating *n~D~* measures the manageability of an ecological community, it does not provide information about the identity of the species that compose the set of driver nodes. 
+Ecologically, potential differences between species are relevant because management and conservation resources are limited, and therefore ecological interventions should be focused on the set of species that might provide the largest impact.
+Moreover, maximum matchings in a network are often not unique, and each maximum matching indicates unique paths that can potentially be used to control the network. 
 We harness this property and use a network's complete set of maximum matchings to characterise each species' relative importance in driving the state of the community. 
 One possibility is to characterise a species by the frequency *f~D~* with which it is classified as a driver node within this set of matchings.
-However, the profile of our networks indicates that a large proportion of driver nodes are classified as such, because of external interventions that are required to achieve **full** controllability and not because they influence the abundance of other species (Supporting Information S2).
-Furthermore, the precise role of driver nodes is still ambiguous when full control is unfeasible or undesired—often the case in ecological settings.
-We therefore also calculate the frequency *f~S~* with which a species is classified as superior nodes since this is the frequency with which they form part of possible control paths.
+However, the profile of our networks indicates that a large proportion of species were classified as driver nodes because of external interventions required to achieve **full** controllability and not because they influence the abundance of other species (Supporting Information S2).
+Furthermore, the precise role of driver nodes is more ambiguous when full control is unfeasible or undesired—often the case in ecological settings.
+We therefore also calculate the frequency *f~S~* with which a species is classified as a superior node since this is the frequency with which they form part of possible control paths.
 
 Most commonly, structural controllability assumes unweighted networks—links exist or not, and hence *f~D~* and *f~S~* can be calculated by computing all possible maximum-cardinality matchings. 
-However, we take the link weights into account when calculating the matchings here because it has been shown that the weights can reveal significant ecological patterns and processes that might be undetectable in unweighted networks [@Scotti2007; @Tylianakis2007; @Vazquez2007; @Kaiser-Bunbury2010a].
-For example, a species *A* may interact with both species *B* and *C* but depends strongly on *B* and only weakly on *C*. 
-Intuitively, a management intervention designed to indirectly modify the abundance of a species *A* is more likely to succeed if the abundance of *B*, rather than *C*, is directly controlled.
+However, we take the link weights into account when calculating the matchings here because the weights can reveal significant ecological patterns and processes that might be undetectable in unweighted networks [@Scotti2007; @Tylianakis2007; @Vazquez2007; @Kaiser-Bunbury2010a].
+Additionally, species *A* may interact with both species *B* and *C* but depends strongly on *B* and only weakly on *C*. 
+Intuitively, a management intervention designed to indirectly modify the abundance of species *A* is more likely to succeed if the abundance of *B*, rather than *C*, is directly controlled.
 A complication of including the interaction weight when calculating the maximum matching, however, is that empirical interaction strengths are to some extent stochastic and depend on proximate factors such as sampling method and intensity [@Gibson2011].
@@
 
-We now describe the application of the previously defined framework to ten paired pollination networks.
+We next applied the previously defined framework to ten paired pollination networks.
 Each network pair was composed of a community invaded by a plant and a community "free" of the invasive species. 
@@
 We then specified the structure of all networks using pollinator visitation frequency, which has been shown to be an appropriate surrogate for interspecific effects in pollination networks [@Vazquez2005; @Bascompte2006].
-To further examine whether this decision would influence our results, we also evaluated the effect of using pollinator efficiency or pollinator importance as alternative measures of species interactions in a different data set that lacked invasive species [@NeEman2010; @Ballantyne2015], and we found quantitatively similar results for all three of these options (Supporting Information S4).
-In addition, because our approach depends to a large degree on the network topology, we evaluated the robustness of our results to the undersampling of ecological interactions.
+To further examine whether this decision would influence our results, we also evaluated the effect of using pollinator efficiency or pollinator importance as alternative measures in a different data set that lacked invasive species [@NeEman2010; @Ballantyne2015], and we found quantitatively similar results for all three options (Supporting Information S4).
+Because our approach depends on the network topology, we also evaluated the robustness of our results to the undersampling of interactions.
 Specifically, we calculated *n~D~* and species relative importance for 500 random subsamples of each empirical network in which the weakest links were more likely to be removed. 
-The sensitivity analysis indicated that, even in the absence of complete sampling, a control-theoretic approach can still be applied (Supporting Information S5).
+Our sensitivity analysis indicated that, even in the absence of complete sampling, a control-theoretic approach can still be applied (Supporting Information S5).
 
@@
 
-We began by quantifying the manageability of each of the aforementioned networks.
+We began by quantifying the manageability of each network.
 To do so, we calculated the networks' maximum matching and determined the minimum proportion of species *n~D~* that need external input signals to fully control the species abundances in the community.
@@
 
-As we noted earlier, the aforementioned maximum-matching approach requires a directed network in which a link between species *i* and *j* pointing to species *j* indicates that the abundance of *j* can be affected by the abundance of *i*.
+As we noted earlier, the maximum-matching approach requires a directed network in which a link from species *i* to species *j* indicates that the abundance of *j* can be affected by the abundance of *i*.
 This implies that we need first to identify a directionality for the links between species that is consistent with the dynamics of the community (Figure 2). 
@@
 Nevertheless, the relative extent to which a given pair of interacting species affect each other can be quantified by the magnitude of the mutual dependence between them [@Bascompte2006]. 
-The dependence of plant *i* on pollinator *j*, *d~ij~*, is the proportion of the visits coming from pollinator *j* compared to all pollinator visits to plant *i*. 
-Likewise, the dependence of pollinator *j* on plant *i*, *d~ji~*, is the proportion of the visits by pollinator *j* to plant *i* and all visits of pollinator *j*.
-As the dependences are not necessarily symmetric, their use generates a weighted bipartite network in which all interacting pairs are connected by two directed links (Figure 2b).
+The dependence of plant *i* on pollinator *j*, *d~ij~*, is the proportion of the visits from pollinator *j* compared to all pollinator visits to plant *i*. 
+Likewise, the dependence of pollinator *j* on plant *i*, *d~ji~*, is the proportion of the visits by pollinator *j* to plant *i* compared to all visits of pollinator *j*.
+Using dependences generates a weighted bipartite network in which all interacting pairs are connected by two directed links (Figure 2b).
 
@@
 
-Given the respective dependences, the extent to which a species *i* affects species *j* relative to the extent to which *j* affects *i* can be summarised by the interaction asymmetry [@Bascompte2006] given by $$a(i,j) = a(j,i) = \frac{\left | d_{ij}-d_{ji} \right |}{max\left ( d_{ij}, d_{ji} \right )}.$$
+Given the respective dependences, the extent to which species *i* affects species *j* relative to the extent to which *j* affects *i* can be summarised by the interaction asymmetry [@Bascompte2006] given by $$a(i,j) = a(j,i) = \frac{\left | d_{ij}-d_{ji} \right |}{max\left ( d_{ij}, d_{ji} \right )}.$$
 Previous research has shown that mutual dependences are often highly asymmetric in natural communities [@Bascompte2006]; in other words, if a plant species is largely dependent on a pollinator species, then that pollinator tends to depend rather weakly on the plant (or vice versa).
@@
 First, it is consistent with previous advances in structural controllability; second, it avoids complications related to the introduction of artificial control cycles [@Ruths2014]; and third it significantly reduces the computational resources necessary for the application of our approach (Supporting Information S6).
-Furthermore, we show that changing to unidirectional interactions determined by the observed direction of asymmetry, as a surrogate of bidirectional mutual dependences, does not alter the relative *n~D~* of different networks (Table S3).
+Moreover, we found that changing to unidirectional interactions based on the direction of asymmetry does not alter the relative *n~D~* of different networks (Table S3).
 
@@
 
-Although understanding the variability of manageability across ecological networks is a useful result in itself, we also wanted to test whether invasion status or other predictors had an impact on the observed *n~D~*.
+We also wanted to test whether invasion status or other predictors had an impact on the observed values of *n~D~*. 
 We therefore used a set of generalised linear models (with binomial error structure) to investigate the effect of invasion status while also including covariates related to species richness, since one might naively expect to see a negative relationship between richness and manageability [@Menge1995].
@@
 After generating the randomised networks, we then calculated the mutual dependences and interaction asymmetries of each and determined *n~D~* using our maximum-matching framework. 
-Finally, we calculated the average rank (akin to a p-value) of *n~D~* for each empirical network compared to the corresponding one of each set of 999 randomisations [@Veech2012].
+Finally, we calculated the average rank (akin to a p-value) of *n~D~* for each empirical network compared to the corresponding values of each set of 999 randomisations [@Veech2012].
 
@@
 To quantify this importance, we computed all maximal cardinality matchings in each network. 
-We then calculated the frequency with which each species *i* is deemed to be a driver (*f~D~*) or a superior node (*f~S~*) in the set of matchings that had a matching weight greater or equal to 0.8 times the weight of the maximum matching.
+We then calculated the frequency with which each species *i* was a driver (*f~D~*) or a superior node (*f~S~*) in the set of matchings that had a matching weight greater or equal to 0.8 times the weight of the maximum matching.
 We selected this threshold as it provided a high agreement between networks quantified by visitation and pollination efficiency as well as between our weighting/directionality assumptions; however, the choice of this threshold had a negligible impact on any results (Supporting Information S7).
@@
 
-We then examined whether any species-level structural properties could predict our metrics of species importance—the frequency to which a species was a driver or a superior node (*f~D~* and *f~S~*, respectively).
+We then examined whether any species-level structural properties could predict our metrics of species importance—the frequency with which a species was a driver or a superior node (*f~D~* and *f~S~*, respectively).
 We used a set of generalised linear mixed-effects models (with binomial error structure) with the relative frequencies as the response variables. 
@@
 In addition, we also included guild (plant or pollinator) and whether the species is invasive or not as categorical fixed effects.
+Lastly, we allowed for variation between different communities by including the network identity as a random effect [@Bates2015]. 
 Although the importance of plants and pollinators or invasive and non-invasive species could respond differently to our structural metrics, our data set did not contain enough variation to include the corresponding interactions terms for these latter two predictors.
 All network metrics were calculated using the R package bipartite 2.06 [@Dormann2008]. 
-Lastly, we allowed for variation between different communities by including the network identity as a random effect [@Bates2015]. 
 Candidate models and estimates were assessed using the same procedure as in the  models for *n~D~*.
@@
 
-All of the networks studied had a driver-node density *n~D~* between `r round(min(dplyr::filter(n_driver, type == "weight")$n_dr_p), digits = 2)` and `r round(max(dplyr::filter(n_driver, type == "weight")$n_dr_p), digits = 2)` (mean `r round(mean(dplyr::filter(n_driver, type == "weight")$n_dr_p), digits = 2)`; Figure 3a).
+All of the networks had a driver-node density *n~D~* between `r round(min(dplyr::filter(n_driver, type == "weight")$n_dr_p), digits = 2)` and `r round(max(dplyr::filter(n_driver, type == "weight")$n_dr_p), digits = 2)` (mean `r round(mean(dplyr::filter(n_driver, type == "weight")$n_dr_p), digits = 2)`; Figure 3a).
 In addition, we found that, when controlling for potential species richness effects, the *n~D~* of invaded communities was smaller to those of non-invaded communities (Figure 3b; Table S5). 
 Nevertheless, of the various covariates we explored, the ratio of plants to pollinators showed the strongest relationship with *n~D~* (Table S4; Figure 3c). 
-Specifically, we found that, as the proportion of pollinators increases and the ratio plant/pollinator approaches unity, *n~D~* decreases (all our communities had more pollinators than plants). 
-Other covariates—connectance (link density) and species richness—had negative, but comparatively less important relationships with *n~D~*.
+Specifically as the proportion of pollinators increases and the ratio plant/pollinator approaches unity, *n~D~* decreases (all our communities had more pollinators than plants). 
+Other covariates—connectance (link density) and species richness—had negative, but comparatively less important, relationships with *n~D~*.
 
@@
 When exploring the effect of network structure itself, we observed that the driver-node density $n_D$ of empirical networks was, in general, not significantly different to the manageability of network randomisations that maintained the degree of individual species (Figure 4).
-However, we found that the $n_D$ of empirical networks was significantly larger than that of randomisations that maintained the network structure but that differed only on the direction of the asymmetries.
+However, we found that the $n_D$ of empirical networks was significantly larger than that of randomisations that maintained the network structure but that differed only in the direction of the asymmetries.
 
@@
 Invasive species were classified as superior nodes *and* driver nodes in every single network they were present; that is, they always had the highest relative *f~S~* and *f~D~* (Figure 5a). 
-The model results suggest that these differences between invasive and native species are not underpinned by any intrinsic property of the invasive species, instead, they are due to species properties that apply to invasive and native species alike (Table 1).
+The model results suggest that these differences between invasive and native species are not underpinned by any intrinsic property of the invasive species; instead, they are due to species properties that apply to invasive and native species alike (Table 1).
 Specifically, we found that a species is more likely to be classified as a superior node if it had a large species strength (the sum of the dependences of all other species on the species of interest).
-To a smaller extent, visitation strength (a species' sum of visits) and the species degree also had a positive relationship with $f_S$. 
-In contrast, the relationships between species structural properties and $f_D$ were more less clear cut (Table 1). 
-Both invasive species (which for example tend to have a large degree, and high dependence strength) and pollinators (which generally have a smaller degree and dependence strength) were classified as driver nodes in a large proportion of the matchings.
+To a smaller extent, visitation strength (a species' sum of visits) and degree also had a positive relationship with $f_S$. 
+In contrast, the relationships between species structural properties and $f_D$ were less clear cut (Table 1). 
+Both invasive species (which generally have a larger degree and high dependence strength) and pollinators (which generally have a smaller degree and low dependence strength) were classified as driver nodes in a large proportion of matchings.
 
@@
 Our results reveal, however, that this effect is comparatively small, and the structural differences among different networks are more strongly related to potential differences in our ability to alter the state of the community via external interventions.
-Despite the small effect of invasion status at a network level, we found that invasive mutualists occupy a particularly dominant role in their communities for two reasons. 
+Despite the small effect of invasion status at the network level, we found that invasive mutualists occupy a particularly dominant role in their communities for two reasons. 
 First, as species with a high *f~S~*, changes on their abundance have the potential to propagate broadly through the community and, in turn, affect the abundances of many other species. 
@@
 Although this might cause differences both at the community and the species level, we found that invasive plants are not inherently different to their native counterparts [@Stouffer2014; @Emer2016a].
-Invasive plants, just like any other mutualist in our data set, tend to be classified as a superior node with a frequency (*f~S~*) proportional to the degree to which their interaction partners are collectively more dependent on them than the other way around.
+Invasive plants, just like any other mutualist in our data set, tend to be classified as a superior node proportional to the degree to which their interaction partners are collectively more dependent on them than the other way around.
 Previous studies have found that supergeneralists, like invasive species, play a central role in their networks [@Vila2009; @Palacio2016].
@@
 
-Our second index *f~S~* is, however, directly related to the likelihood a species affects the abundance of another species in all of the control strategies considered. 
+Our second index *f~S~*, however, is directly related to the likelihood a species affects the abundance of another species in all of the control strategies considered. 
 Importantly, this is irrespective of whether controlling the entire network is ultimately desired and/or feasible. 
@@
 Despite the apparent similarities, our approach is different to previous attempts to quantify species importance in a few key ways.
-Existing metrics usually harness species featuresi, like centrality, position, co-extinction or uniqueness, to infer their effect on other species [@Allesina2004; @Jordan2006; @Jordan2009; @Lai2012]. 
+Existing metrics usually harness species features, like centrality, position, co-extinction or uniqueness, to infer their effect on other species [@Allesina2004; @Jordan2006; @Jordan2009; @Lai2012]. 
 In contrast, our control-based approach tackles that question directly.
-Although they are relatively simple to calculate, it has been shown that classic species-level network metrics do not necessarily reveal the best set of species to manage [@Eklof2013; @McDonald-Madden2016].
+Although they are relatively simple to calculate, classic species-level network metrics do not necessarily reveal the best set of species to manage [@Eklof2013; @McDonald-Madden2016].
 Our approach, however, is not based on a single structural metric but instead acknowledges the existence of multiple management strategies. 
 By allowing for the fact that some strategies are better than others depending on the context, control theory implicitly highlights that management decisions should not be based on a single technique.
-As such, ours and other flexible approaches that take a network-wide approach might prove more useful to guide ecosystem management if we want to go beyond using network metrics to minimise topological species loss [@McDonald-Madden2016].
+As such, ours and other flexible approaches that take a network-wide approach might prove more useful to guide ecosystem management [@McDonald-Madden2016].
 
@@
 In this study, we illustrate how a control-theoretic approach can be better adopted in network ecology to evaluate the effect of invasions and other kinds of perturbations. 
-Although our pollination specific results might not be directly translatable to other ecological systems because of the degree constrains imposed by bipartite networks, the approach we propose is applicable wherever species abundances are influenced by their interactions.
-Exciting open questions lie ahead. How to design the precise "control signals" to reach a desired ecosystem state or conservation outcome? 
+Although our pollination specific results might not be directly translatable to other ecological systems because of the degree constraints imposed by bipartite networks, the approach we propose is applicable wherever species abundances are influenced by their interactions, and exciting open questions lie ahead.
+How to design the precise "control signals" to reach a desired ecosystem state or conservation outcome?
 What are the implications of assuming linear species dynamics?

### 2017-03-02 paper/manuscript.Rmd
Move details about statistical analysis to the supporting information

@@
 
-* **Number of words:** 148 abstract; approx. 5278 main text.
+* **Number of words:** 148 abstract; approx. 4,974 main text.
 
-* **Number of references:** 72
+* **Number of references:** 65
 
@@
 These covariates included the total number of species, plant richness, pollinators richness, the ratio of plant to pollinator richness, the link density (connectance), and the study site (as a two-level factor).
-Candidate models were compared using AICc and the relative importance of the explanatory variables was evaluated using the sum of Akaike weights over candidate models that accounted for 95% of the evidence [@Burnham2003; @Bates2015; @Barton2016].
-Coefficient estimates were averaged following @Buckland1997a while confidence intervals were calculated following @Lukacs2010.
 
@@
 We therefore compared the driver-node density *n~D~* of the empirical networks to networks generated by a null model that maintained each species' strength (its total sum of visits) while allowing their degrees (its number of interactions) to vary.
-Randomisations were generated using the quasiswap-count algorithm and the function `commsim` in vegan 2.3-3 [@Oksanen2016]. 
-After generating the randomised networks, we then calculated the mutual dependences and interaction asymmetries of each and determined *n~D~* using our maximum-matching framework. 
-Finally, we calculated the average rank (akin to a p-value) of *n~D~* for each empirical network compared to the corresponding values of each set of 999 randomisations [@Veech2012].
-
 Beyond network structure, the dependence asymmetry plays a fundamental role in determining the direction of control in each two-species interaction and therefore has the potential to influence the network *n~D~* results above.
@@
 That is, we first calculated the observed asymmetries for each community and then shuffled the direction of the link between each pair of species.
-Similar to the other null models, we calculated the average rank of the empirical *n~D~* when compared to that of the randomisations.
+
+Additional details about the statistical models and the randomisations can be found in the Supporting Information S7.
 
@@
 We then calculated the frequency with which each species *i* was a driver (*f~D~*) or a superior node (*f~S~*) in the set of matchings that had a matching weight greater or equal to 0.8 times the weight of the maximum matching.
-We selected this threshold as it provided a high agreement between networks quantified by visitation and pollination efficiency as well as between our weighting/directionality assumptions; however, the choice of this threshold had a negligible impact on any results (Supporting Information S7).
+We selected this threshold as it provided a high agreement between networks quantified by visitation and pollination efficiency as well as between our weighting/directionality assumptions; however, the choice of this threshold had a negligible impact on any results (Supporting Information S8).
 Details about the computational procedure to find all maximal cardinality matchings of a network can be found in Supporting Information S1 and Figure S2.
@@
 As predictors in this model, we included measures of centrality (degree and eigen-centrality), which have been found to be strong predictors of importance in a coextinction context [@Memmott2004]; a measure related to network robustness (contribution to nestedness), as nestedness has been proposed as one of the key properties that promote stability in mutualistic networks [@Saavedra2011]; a measure of strength of association (visitation strength, the sum of visits a species receives or performs) and a measure of strength of dependence (species strength, the sum of dependences of all species on the focal species), as their distribution determines the extent of interspecific effects [@Bascompte2006].
-To facilitate comparison among the continuous variables, we scaled them so that they all had a mean of zero and a standard deviation of one.
 In addition, we also included guild (plant or pollinator) and whether the species is invasive or not as categorical fixed effects.
 Lastly, we allowed for variation between different communities by including the network identity as a random effect [@Bates2015]. 
-Although the importance of plants and pollinators or invasive and non-invasive species could respond differently to our structural metrics, our data set did not contain enough variation to include the corresponding interactions terms for these latter two predictors.
-All network metrics were calculated using the R package bipartite 2.06 [@Dormann2008]. 
-Candidate models and estimates were assessed using the same procedure as in the  models for *n~D~*.
+Supplementary details about the statistical models can be found in the Supporting Information S7.
 
@@
 All of the networks had a driver-node density *n~D~* between `r round(min(dplyr::filter(n_driver, type == "weight")$n_dr_p), digits = 2)` and `r round(max(dplyr::filter(n_driver, type == "weight")$n_dr_p), digits = 2)` (mean `r round(mean(dplyr::filter(n_driver, type == "weight")$n_dr_p), digits = 2)`; Figure 3a).
-In addition, we found that, when controlling for potential species richness effects, the *n~D~* of invaded communities was smaller to those of non-invaded communities (Figure 3b; Table S5). 
-Nevertheless, of the various covariates we explored, the ratio of plants to pollinators showed the strongest relationship with *n~D~* (Table S4; Figure 3c). 
+In addition, we found that, when controlling for potential species richness effects, the *n~D~* of invaded communities was smaller to those of non-invaded communities (Figure 3b). 
+Nevertheless, of the various covariates we explored, the ratio of plants to pollinators showed the strongest relationship with *n~D~* (Figure 3c; Table S5). 
 Specifically as the proportion of pollinators increases and the ratio plant/pollinator approaches unity, *n~D~* decreases (all our communities had more pollinators than plants). 
@@
 
-Despite its conceptual advantages, our approach still relies on knowledge of the network of interaction between species. 
-Nevertheless, our results and previous basic research show that, as long as the proportion of sampled links is enough to provide indication of the actual degree distribution (and in turn the species dependences), *n~D~*, *f~S~* and *f~D~* can still provide a simple, straightforward, and theoretically informed indication of the degree to which the community is self regulated and therefore how difficult it might be to modify its state in one way or another using some of its constituent species [Supporting Information S5; @Nepusz2012].
-
 In this study, we illustrate how a control-theoretic approach can be better adopted in network ecology to evaluate the effect of invasions and other kinds of perturbations. 

### 2017-03-02 paper/supporting_information.Rmd
Move details about statistical analysis to the supporting information

@@
 
+# Statistical methods
+
+## Manageability
+
+### Genrealised linear models for *n~D~*
+
+Candidate models were compared using AICc and the relative importance of the explanatory variables was evaluated using the sum of Akaike weights over candidate models that accounted for 95% of the evidence [@Burnham2003; @Bates2015; @Barton2016].
+Coefficient estimates were averaged following @Buckland1997a while confidence intervals were calculated following @Lukacs2010.
+Only models that accounted for 95% of the evidence weight were considered to quantify the relative importance of the fixed effects.
+
+### Network randomisations
+
+Randomisations that maintained the degree of the visitation networks were generated using the quasiswap-count algorithm and the function `commsim` in vegan 2.3-3 [@Oksanen2016]. 
+After generating the randomised networks, we then calculated the mutual dependences and interaction asymmetries of each and determined *n~D~* using our maximum-matching framework. 
+Finally, we calculated the average rank (akin to a p-value) of *n~D~* for each empirical network compared to the corresponding values of each set of 999 randomisations [@Veech2012].
+
+Similar as in the previous null model, to evaluate the effect of the direction of the asymmetries, we calculated the average rank of the empirical *n~D~* when compared to that of the randomisations.
+
+## Relative importance
+
+### Genrealised mixed effects models for *f~S~* and *f~D~*
+
+To facilitate comparison among the continuous variables, we scaled them so that they all had a mean of zero and a standard deviation of one. 
+Although the importance of plants and pollinators or invasive and non-invasive species could respond differently to our structural metrics, our data set did not contain enough variation to include the corresponding interactions terms for these latter two predictors.
+All network metrics were calculated using the R package bipartite 2.06 [@Dormann2008]. 
+Candidate models and estimates were assessed using the same procedure as in the  models for *n~D~*.
+
 # Matching's weight threshold
@@
 
-# Statistical models
+# *n~D~* models results
 

### 2017-03-02 paper/response_to_reviewers.Rmd
Update line numbers and extra line about the moves

@@
 Specifically, the problems arise from an absolute dominance of cycles and difficulties to the use of the maximum maximum matching algorithm to find a minimum set of driver nodes $D$. 
-We elaborate on these on the new version in Lines 212--224 and Supporting Information S6.
+We elaborate on these on the new version in Lines 201--212 and Supporting Information S6.
 
@@
 Without disregarding the usefulness of the proposed approach, we also mention at the end of the discussion how recently developed numerical methods [e.g.
-@Cornelius2013] might offer future avenues results in this regard (Lines 401--404)*
+@Cornelius2013] might offer future avenues results in this regard (Lines 363--369)*
 
@@
 Nevertheless, due to this comment and one of Referee 2 we have rediscovered its value and use it to support our decision to include the analysis of superior nodes, and not just driver nodes, in our manuscript.
-Though space constraints remain and we can only mention it briefly in the main text (Lines 358--360), we also dedicate a whole section in the Supporting Information (S2) to this subject.
+Though space constraints remain and we can only mention it briefly in the main text (Lines 328--330), we also dedicate a whole section in the Supporting Information (S2) to this subject.
 To summarise here, we found our networks weighted by asymmetry to be external dilation dominated, and hence have only a small number of cycles.
@@
 
-    *The reviewer is absolutely correct most of the literature treats the problem of controlability on unweighted/binary networks.
-In that special case, maximum matchings are equivalent to maximum cardinality matchings.
-It has been shown, however, that the interaction weights carry important information in pollination networks about the patterns and processes in the community.
-In the paper, we use the visitation weights directly or indirectly in two different ways.
-First, we use them to determine the potential direction of control (via the dependence asymmetry).
-Second—which directly addresses the reviewer's comment—we use them to give priority to matchings that have the largest weight since these arguably have the largest impact on the network state for a given management intervention.
-Because the weights determine the dynamical relationships between species, our approach attempts to incorporate more ecological realism to the structural-controllability approach.
-We acknoweledge our earlier presentation of this rationale was confusing, especially for readers familiar with the control literature, and have therefore added a whole paragraph describing our rationale in the "Relative importance" subsection in the "Theoretical framework" section (Lines 154--168).
-To minimise potential confusions, we are more careful when introducing each of these concepts, and have added—as suggested by the reviewer—a glossary for easy reference.*
-
 - When defining *n~d~* on line 119, it is more accurate to say that it is the "minimum number" of species needed to gain full control.
 
-    *We have completely rewritten that section and the corresponding sentence (Lines 95--97) now reads "Conveniently the information necessary to determine the minimum number of driver nodes *D* in a network with linear dynamics is fully contained in the network structure..."*
+    *We have completely rewritten that section and the corresponding sentence (Lines 84--86) now reads "Conveniently the information necessary to determine the minimum number of driver nodes *D* in a network with linear dynamics is fully contained in the network structure..."*
 
@@
 As the referee points out it, this is not an estimation but an exact calculation.
-The sentence (Lines 190--192) now reads "To do so, we calculated the networks' maximum matching and determined the minimum proportion of species *n~D~* that need external input signals to fully control the species abundances in the community".*
+The sentence (Lines 178--180) now reads "To do so, we calculated the networks' maximum matching and determined the minimum proportion of species *n~D~* that need external input signals to fully control the species abundances in the community".*
 
@@
 
-    *The sentence (Lines 70--71) now reads "To bridge this gap, we outline an approach to apply theory on the control of complex systems in an ecological context and implement it using empirical data."*
+    *The sentence (Lines 68--69) now reads "To bridge this gap, we outline an approach to apply theory on the control of complex systems in an ecological context and implement it using empirical data."*
 
@@
 We now include a paragraph in the discussion to explore the similarities and differences of our work with previous indices based on structural metrics.
-We explain (Lines 380--385) how "our approach...
+We explain (Lines 349--351) how "our approach...
 is not based on a single structural metric but instead acknowledges the existence of multiple management strategies.
@@
 
-    *We now brifly mention in the Discussion (Lines 394--397) how "although our pollination specific results might not be directly translatable to other ecological systems because of the degree constrains imposed by bipartite networks, the approach we propose is applicable wherever species abundances are influenced by their interactions".*
+    *We now brifly mention in the Discussion (Lines 356--358) how "although our pollination specific results might not be directly translatable to other ecological systems because of the degree constrains imposed by bipartite networks, the approach we propose is applicable wherever species abundances are influenced by their interactions...".*
 
@@
 As such, as we now try to better highlight the rationale behind our methods while being more explicit about the assumptions and limitations.
-Moreover we now provide a fairer assessment of the extent to which our approach might be useful for practical applications in the discussion.*
+Moreover we now provide a fairer assessment of the extent to which our approach might be useful for practical applications in the discussion.
+We note, however that the extended discussion (alongside with a better development of the theoretical framework), meant that we had to move some of the details about the statistical analysis to the Supporting Information (as suggested).*
 
@@
 Nevertheless, as suggested here and by another reviewer, we have included a section in the Supporting Information (S2) where we explain that our networks are external dilation dominated.
-Consequently, the approach of @Ruths2014 has provided us with very useful insight on the selection of the direction of control and the utility of the concept of driver nodes for management applications (Lines 221--226 and 358--360).*
+Consequently, the approach of @Ruths2014 has provided us with very useful insight on the selection of the direction of control and the utility of the concept of driver nodes for management applications (Lines 208--211 and 328--330).*
 
@@
     *We have now included comments about the general limitations of the structural-controllability approach in the "Theoretical framework" section.
-Furthermore, we are now explicit about the fact that species have multiple types of interactions and therefore our approach can only provide a partial picture when only one type of interaction is included.
-We do so both the Introduction and the Discussion (Lines 83--85 and 399--400).
-Finally, we are also explicit about the fact that we do not advocate for management decisions to be based solely on our approach (Lines 381--383), but how it can "simple, straightforward, and theoretically informed indication of the degree to which the community is self regulated and therefore how difficult it might be to modify its state in one way or another using some of its constituent species" (Lines 387--392).*
+Furthermore, we are now explicit about the fact that species have multiple types of interactions and therefore our approach can only provide a partial picture when only one type of interaction is included (Lines 361--362).
+Finally, we are also explicit about the fact that we do not advocate for management decisions to be based solely on our approach (Lines 351--353).*
 
@@
 We apologise for the imprecision.
-The sentence (Lines 70--71) now reads "To bridge this gap, we outline an approach to apply theory on the control of complex systems in an ecological context and implement it using empirical data".*
+The sentence (Lines 68--69) now reads "To bridge this gap, we outline an approach to apply theory on the control of complex systems in an ecological context and implement it using empirical data".*
 
@@
     *Thanks.
-We have rephrased the sentence (Lines 53--54) to improve clarity and it now reads "Therefore, control theory could also be harnessed to provide an indication of which species are most relevant from a structural and dynamic perspective".*
+We have rephrased the sentence (Lines 52--53) to improve clarity and it now reads "Therefore, control theory could also be harnessed to provide an indication of which species are most relevant from a structural and dynamic perspective".*
 
@@
     *We apologise for the imprecision as we meant financial resources.
-We have modified the sentence to improve clarity (Lines 140--143) and it now reads "Ecologically, potential differences between species are acutely relevant because management and conservation resources are limited, and therefore ecological interventions should ideally be focused on the set of species that might provide the largest impact".*
+We have modified the sentence to improve clarity (Lines 128--131) and it now reads "Ecologically, potential differences between species are relevant because management and conservation resources are limited, and therefore ecological interventions should be focused on the set of species that might provide the largest impact".*
 
@@
 
-    *We have attempted to eliminate ambiguity by rephrasing the sentence (Lines 295--297).
+    *We have attempted to eliminate ambiguity by rephrasing the sentence (Lines 266--268).
 It now reads "...
@@
     *Thank you.
-We have implemented this suggestion and the text (Lines 371-373) now reads "Not only it is hard to predict the direction in which the system will change, but invaded communities also tend to be highly dependent on invaders and therefore acutely vulnerable to their eradication"*
+We have implemented this suggestion and the text (Lines 341-343) now reads "Not only it is hard to predict the direction in which the system will change, but invaded communities also tend to be highly dependent on invaders and therefore acutely vulnerable to their eradication"*
 

### 2017-03-02 paper/manuscript.Rmd
Add extra awknowledgements and minor grammar changes

@@
 
-* **Number of words:** 148 abstract; approx. 4,974 main text.
+* **Number of words:** 148 abstract; approx. 4,970 main text.
 
@@
 Out of the two maximal cardinality matchings only one (c) has maximum weight and therefore is also a maximum matching.
-Further examples can be found in the Supporting Information S1."}
+Further examples can be found in Supporting Information S1."}
 layout(matrix(c(1, 1, 2, 4, 3, 4), 2, 3),
@@
 These networks are comprised of `r bar[1]`--`r bar[6]` species (mean `r round(bar[4])`); in contrast to the above, uninvaded communities were obtained from plots that had not yet been colonised by either of the invasive species *Carpobrotus affine acinaciformis* or *Opuntia stricta*.
-Further details about the empirical networks can be found in the Supporting Information S3.
+Further details about the empirical networks can be found in Supporting Information S3.
 
@@
 
-Additional details about the statistical models and the randomisations can be found in the Supporting Information S7.
+Additional details about the statistical models and the randomisations can be found in Supporting Information S7.
 
@@
 Lastly, we allowed for variation between different communities by including the network identity as a random effect [@Bates2015]. 
-Supplementary details about the statistical models can be found in the Supporting Information S7.
+Supplementary details about the statistical models can be found in Supporting Information S7.
 
@@
 
-The authors thank Dr.
-Takeuki Uno for the insight provided to find the set of all maximum matching algorithms, and Jason Tylianakis, Bernat Bramon Mora, Guadalupe Peralta, Rogini Runghen, Warwick Allen, Matthew Hutchinson, and Marilia Gaiarsa for feedback and valuable discussions.
+The authors thank Jane Memmott and coauthors, and eveyone that has made their data available to us, Takeuki Uno for the insight provided to find the set of all maximum matching algorithms, and Jason Tylianakis, Bernat Bramon Mora, Guadalupe Peralta, Rogini Runghen, Warwick Allen, Matthew Hutchinson, and Marilia Gaiarsa for feedback and valuable discussions.
 EFC acknowledges the support from the University of Canterbury Doctoral Scholarship, the University of Canterbury Meadow Mushrooms Postgraduate Scholarship, a New Zealand International Doctoral Research Scholarship, and a travel grant from the European Space Agency.

### 2017-04-26 paper/response_to_reviewers.Rmd
Add draft response to main editor/summarising remarks

@@
 ---
-title: "Response to reviewer comments ELE-00738-2016"
+title: "Response to comments ELE-00205-2017"
 output: pdf_document
@@
 
-## Response to the handling editor
+Dear Dr Jonathan Chase,
+
+We are thankful for the opportunity to resubmit the manuscript for consideration. 
+In the response to the handling editor section below, we have endeavoured to explain how our approach does still provide ecological insight despite the assumption of linearity. 
+To aid in the review process we have included in this document as well the response to the reviewers' and editor's comments of the previous submission (ELE-00738-2016).
+
+Before we dive into the responses, we would like to remark that the major concern identified by the new handling editor—the assumption of linearity—was not overlooked in the previous round of review. 
+In the initial version of the manuscript, we mainly focus on details of the method and the study system and only mention in passing that our approach is based on a linearization of the network of interactions.
+Reviewer 3 and 1 in particular, did not find this to be a fundamental problem, although they encouraged us to be explicit about this assumption and thoroughly discuss the implications of this simplification.
+In hindsight, perhaps we focused executively on the potential limitations of our approach and did a poor job justifying its advantages.
+
+We hope this response and the modifications made to the main text are convincing enough for the manuscript to be reconsidered for publication at Ecology Letters.
+
+****
+
+# Response to comments ELE-00738-2016
+
+## To the handling editor
 
@@
 
-## Reviewer 1
+## Reviewer 1 (ELE-00738-2016)
 
@@
 
-## Referee 2
+## Referee 2 (ELE-00738-2016)
 
@@
 
-## Referee 3
+## Referee 3 (ELE-00738-2016)
 

### 2017-05-01 paper/response_to_reviewers.Rmd
Add response to handling editor

@@
 In the response to the handling editor section below, we have endeavoured to explain how our approach does still provide ecological insight despite the assumption of linearity. 
-To aid in the review process we have included in this document as well the response to the reviewers' and editor's comments of the previous submission (ELE-00738-2016).
+To aid in the review process we have included in this document as well the response to the reviewers' and editor's comments of the previous submission (ELE-00738-2016) and have updated the references to line numbers when appropriate.
 
@@
 We hope this response and the modifications made to the main text are convincing enough for the manuscript to be reconsidered for publication at Ecology Letters.
+
+## Response to the handling editor
+
+We agree with the handling editor that the most notable limitation of our approach is that it is based on a linear approximation of the dynamics of the system. 
+Naturally, it is important to take this limitation into account when applying the framework. 
+We disagree, however, with the conclusion that this limitation renders the approach ecologically irrelevant.
+
+We approach the editor's comments in two stages. 
+First, we argue that linear models can be useful to describe the dynamics of ecological communities, and pollination communities in particular. 
+Additionally, we believe that the editor's observations potentially arises from a misunderstanding of the scope and goals of our study.
+Therefore, we then provide some further clarification in this regard and to structural controllability. 
+Finally, we provide a detailed account of the editions we have done to the manuscript in order to prevent this kind of misunderstandings.
+
+While ecological systems are inherently non-linear, variations of Lokta-Volterra and other linear response models have been widely and recently used in ecology to describe both multitrophic ecological communities [@Heckmann2012; @Heath2014] and mutualistic pollination networks [@Lever2014; @Rohr2014; @Valdovinos2016].
+Importantly several studies have found that, despite the lack of realism, parametrizations with linear responses can provide a good starting point to investigate community stability (ref), population size [@Mackinson2003], and relative species importance [@Zhao2016].
+Similarly, we view the structural controllability as a *starting point* to investigate the way ecological communities could be steered from an equilibrium point to another in an informed fashion.
+
+Furthermore, the editor points out that a structural controllability approach would not be useful in ecological systems because it will be "only valid in an infinitesimal border" around an initial equilibrium point.
+This comment would be completely appropriate if the local linear approximation at the equilibrium point were used to *design* the—inherently non-local—control trajectory that drives the system to an alternative state.
+Our manuscript, however, has a different aim. 
+We use the structure of interaction network and determine the set of possible "control interventions" to gain network and species-level ecological that could be used in management settings.
+
+In our manuscript, a control intervention is a set of species with which full control of the community could be gained. 
+The control interventions we study are optimal from a structural point of view.
+However, in practice, some of these interventions would be more appropriate than others depending on several factors like the starting and end state of the community, the feasibility of modifying the abundance of some species, the available resources, and naturally the particular dynamics of the system.
+As the behaviour of the community is governed by both structure and dynamics, by extension, our approach is ill suited to design a specific control trajectory. 
+Again, we emphasise that this was not our objective and that the development of numerical approaches like the one proposed by @Cornelius2013 might be more promising in this regard.
+
+Nevertheless, we see the fact that we focus on structure as and advantage rather than a disadvantage. 
+As one of the previous reviewers highlighted, our manuscript "...presents to ecologists a novel way of studying the relationship between topology and dynamics that is less dependent (when compared to other methods) on particular choices about how dynamics are modelled".
+It can, therefore, be used to gain insight from different ecological systems and is readily applicable to currently available data. 
+Furthermore, by focusing on the network structure, the conclusions obtained will be locally valid, not only close to equilibrium points but anywhere as long as the species interactions remain.
+
+Specifically, we made the following modifications to the manuscript. 
+In the intro we ...
+As before, in the methods section, we start by stating the assumption of linearity (Lines XXX). 
+However, we now also explicitly explain how this assumption does not invalidate the gained insight (Lines XXX). 
+Finally, in the discussion we ...
 

### 2017-05-01 paper/response_to_reviewers.Rmd
Daniel edits to response to chief editor

@@
 
-We are thankful for the opportunity to resubmit the manuscript for consideration. 
-In the response to the handling editor section below, we have endeavoured to explain how our approach does still provide ecological insight despite the assumption of linearity. 
-To aid in the review process we have included in this document as well the response to the reviewers' and editor's comments of the previous submission (ELE-00738-2016) and have updated the references to line numbers when appropriate.
+We are thankful for the opportunity to resubmit our manuscript for consideration. 
+In our response to the handling editor section (below), we have endeavoured to explain how our approach still provides ecological insight despite the assumption of linearity. 
+To aid in the review process, we have included the response to the reviewers' and editor's comments of the previous submission (ELE-00738-2016) in this document as well and have updated the references to line numbers when appropriate.
 
-Before we dive into the responses, we would like to remark that the major concern identified by the new handling editor—the assumption of linearity—was not overlooked in the previous round of review. 
-In the initial version of the manuscript, we mainly focus on details of the method and the study system and only mention in passing that our approach is based on a linearization of the network of interactions.
-Reviewer 3 and 1 in particular, did not find this to be a fundamental problem, although they encouraged us to be explicit about this assumption and thoroughly discuss the implications of this simplification.
-In hindsight, perhaps we focused executively on the potential limitations of our approach and did a poor job justifying its advantages.
+Before we dive into the detailed responses, we would like to draw your attention to the fact that the major concern identified by the new handling editor—the assumption of linearity—was not actually overlooked in the previous round of review.
+In the initial version of the manuscript, we mainly focused on details of the method and the study system and only mentioned in passing that our approach is based on a linearization of the network of interactions.
+Reviewers 3 and 1 in particular did not find this to be a fundamental problem; nevertheless they encouraged us to be explicit about this assumption and thoroughly discuss the implications of this simplification.
+In hindsight, perhaps these changes focused too intensely on the potential limitations of our approach and did a poorer job of justifying its advantages.
 

### 2017-05-02 paper/response_to_reviewers.Rmd
Rewrite respose to focus on specific mathematical definitions

--- 2017-04-26 paper/response_to_reviewers.Rmd
@@
 
-We are thankful for the opportunity to resubmit the manuscript for consideration. 
-In the response to the handling editor section below, we have endeavoured to explain how our approach does still provide ecological insight despite the assumption of linearity. 
-To aid in the review process we have included in this document as well the response to the reviewers' and editor's comments of the previous submission (ELE-00738-2016).
+We are thankful for the opportunity to resubmit our manuscript for consideration. 
+In our response to the handling editor section (below), we have endeavoured to explain how our approach still provides ecological insight despite the assumption of linearity. 
+To aid in the review process, we have included the response to the reviewers' and editor's comments of the previous submission (ELE-00738-2016) in this document as well and have updated the references to line numbers when appropriate.
 
-Before we dive into the responses, we would like to remark that the major concern identified by the new handling editor—the assumption of linearity—was not overlooked in the previous round of review. 
-In the initial version of the manuscript, we mainly focus on details of the method and the study system and only mention in passing that our approach is based on a linearization of the network of interactions.
-Reviewer 3 and 1 in particular, did not find this to be a fundamental problem, although they encouraged us to be explicit about this assumption and thoroughly discuss the implications of this simplification.
-In hindsight, perhaps we focused executively on the potential limitations of our approach and did a poor job justifying its advantages.
+Before we dive into the detailed responses, we would like to draw your attention to the fact that the major concern identified by the new handling editor—the assumption of linearity—was not actually overlooked in the previous round of review.
+In the initial version of the manuscript, we mainly focused on details of the method and the study system and only mentioned in passing that our approach is based on a linearization of the network of interactions.
+Reviewers 3 and 1 in particular did not find this to be a fundamental problem; nevertheless, they encouraged us to be explicit about this assumption and thoroughly discuss the implications of this simplification.
+In hindsight, perhaps these changes focused too intensely on the potential limitations of our approach and did a poorer job of justifying its advantages.
 
 We hope this response and the modifications made to the main text are convincing enough for the manuscript to be reconsidered for publication at Ecology Letters.
+
+## Response to the handling editor
+
+We agree with the handling editor that the most notable assumption of our approach is that it is based on a linear approximation of the dynamics of the system. 
+Naturally, it is important to take this into account when applying the framework. 
+We disagree, however, with the conclusion that this detail renders the approach ecologically irrelevant.
+
+We will approach the editor's comments in two stages below. 
+First, we will argue that linear models can be useful to describe the dynamics of ecological communities and pollination communities in particular. 
+Second, we believe that the editor's observations potentially arises from our failure to clearly delineate the scope and goals of our study.
+Therefore, we then provide some further clarification in this regard and to the goals of structural controllability in general. 
+Finally, we provide a detailed account of the edits we have made in the manuscript in order to prevent this kind of misunderstandings going forward.
+
+While ecological systems are inherently non-linear, variations of Lokta-Volterra and other models with linear functional response have been widely used in ecology to describe both multitrophic ecological communities [@Heckmann2012; @Heath2014] and mutualistic pollination networks [@Lever2014; @Rohr2014; @Valdovinos2016].
+Importantly several studies have found that despite the lack of "realism", parametrizations with linear responses still provide a valuable starting point to investigate community stability [@Allesina2012], population size [@Mackinson2003], and relative species importance [@Zhao2016].
+Similarly, we view the structural controllability as a *starting point* to investigate the way ecological communities could be steered from an equilibrium point to another in an informed fashion.
+
+An ecological system near equilibrium can be linearised by $\frac{dx}{dt} = \mathbf{A}x + \mathbf{B}u(t)$. 
+Here, $\mathbf{B}$ is the "input matrix" and $u(t)$ is the input or control vector. 
+The matrix $\mathbf{B}$ has size $S \times D$, where $S$ is the number of species in the community and $D$ is the number of species whose abundances are modified by the input vector. 
+The editor points out that a structural controllability approach would not be useful in ecological systems because it will be "only valid in an infinitesimal border" around an initial equilibrium point.
+This comment would be completely appropriate if our aim were to *design the control trajectory* that drives the system from an equilibrium point to an alternate stable state. 
+In other words, it would be inappropriate to design $u(t)$ based exclusively a local linear approximation at the initial equilibrium point. 
+Our manuscript, however, has a completely different aim.
+
+We use the structure of interaction network to determine the set of nodes that could be used to control the system. 
+This is, we use information contained in $\mathbf{A}$ to determine $\mathbf{B}$ (and by extension $D$). 
+Our most novel contributions are to use $D$ and knowledge of all the possible ways in which $\mathbf{B}$ can be parameterised in order to gain insight of the controllability of the network and role of the species that compose it.
+Understanding $\mathbf{B}$ is a prerequisite to designing $u(t)$, regardless of whether we are interested on controllability near an equilibrium point or along a linearisation of the system's nominal trajectory outside of equilibrium.
+Even existing numerical approaches that operate in a fully nonlinear setting like those proposed by @Cornelius2013 require previous knowledge of the set of nodes (species) to which to apply the control signal.
+
+We see the fact that we focus on $\mathbf{B}$ and the network structure as an advantage rather than a disadvantage. 
+As one of the previous reviewers highlighted, our manuscript "...presents to ecologists a novel way of studying the relationship between topology and dynamics that is less dependent (when compared to other methods) on particular choices about how dynamics are modelled".
+It can, therefore, be used to gain insight from different ecological systems and is readily applicable to currently available data.
+
+As it has been acknowledged in the control theory literature, "while many complex systems are characterised by nonlinear interactions between the components, the first step in any control challenge is to establish the controllability of the locally linearized system...
+Before we can explore the fully nonlinear dynamical setting, which is mathematically much harder, we must understand the impact of the topological characteristics on linear controllability, serving as a prerequisite of nonlinear controllability" [@Liu2016].
+
+Along similar lines to the above, we made the following modifications to the manuscript. 
+In the intro we ...
+As before, in the methods section, we start by stating the assumption of linearity (Lines XXX). 
+However, we now also explicitly explain how this assumption does not invalidate the gained insight (Lines XXX). 
+Finally, in the discussion we ...
 

### 2017-05-02 paper/response_to_reviewers.Rmd
Daniel's edits

@@
 We are thankful for the opportunity to resubmit our manuscript for consideration. 
-In our response to the handling editor section (below), we have endeavoured to explain how our approach still provides ecological insight despite the assumption of linearity. 
+In our response to the handling editor (below), we have endeavoured to explain how our approach still provides ecological insight despite the assumption of linearity. 
 To aid in the review process, we have included the response to the reviewers' and editor's comments of the previous submission (ELE-00738-2016) in this document as well and have updated the references to line numbers when appropriate.
@@
 Reviewers 3 and 1 in particular did not find this to be a fundamental problem; nevertheless, they encouraged us to be explicit about this assumption and thoroughly discuss the implications of this simplification.
-In hindsight, perhaps these changes focused too intensely on the potential limitations of our approach and did a poorer job of justifying its advantages.
+In hindsight, perhaps these changes focused too intensely on the potential limitations of our approach and did a poorer job of justifying its sustained advantages.
 
@@
 Second, we believe that the editor's observations potentially arises from our failure to clearly delineate the scope and goals of our study.
-Therefore, we then provide some further clarification in this regard and to the goals of structural controllability in general. 
-Finally, we provide a detailed account of the edits we have made in the manuscript in order to prevent this kind of misunderstandings going forward.
+Therefore, we then provide some further clarification in this regard and to the aims of structural controllability in general. 
+Finally, we provide a detailed account of the edits we have made in the manuscript in order to prevent this kind of misunderstanding going forward.
 
-While ecological systems are inherently non-linear, variations of Lokta-Volterra and other models with linear functional response have been widely used in ecology to describe both multitrophic ecological communities [@Heckmann2012; @Heath2014] and mutualistic pollination networks [@Lever2014; @Rohr2014; @Valdovinos2016].
-Importantly several studies have found that despite the lack of "realism", parametrizations with linear responses still provide a valuable starting point to investigate community stability [@Allesina2012], population size [@Mackinson2003], and relative species importance [@Zhao2016].
+While ecological systems are inherently non-linear, variations of Lokta-Volterra and other models with linear functional responses have been widely used in ecology to describe both multitrophic ecological communities [@Heckmann2012; @Heath2014] and mutualistic pollination networks [@Lever2014; @Rohr2014; @Valdovinos2016].
+Importantly, several studies have found that, despite the lack of "realism", parametrizations with linear responses still provide a valuable starting point to investigate community stability [@Tang2014], population size [@Mackinson2003], and relative species importance [@Zhao2016].
 Similarly, we view the structural controllability as a *starting point* to investigate the way ecological communities could be steered from an equilibrium point to another in an informed fashion.
 
-An ecological system near equilibrium can be linearised by $\frac{dx}{dt} = \mathbf{A}x + \mathbf{B}u(t)$. 
-Here, $\mathbf{B}$ is the "input matrix" and $u(t)$ is the input or control vector. 
-The matrix $\mathbf{B}$ has size $S \times D$, where $S$ is the number of species in the community and $D$ is the number of species whose abundances are modified by the input vector. 
-The editor points out that a structural controllability approach would not be useful in ecological systems because it will be "only valid in an infinitesimal border" around an initial equilibrium point.
-This comment would be completely appropriate if our aim were to *design the control trajectory* that drives the system from an equilibrium point to an alternate stable state. 
-In other words, it would be inappropriate to design $u(t)$ based exclusively a local linear approximation at the initial equilibrium point. 
+As noted in our manuscript, the dynamics of an ecological system near equilibrium can be represented by $\frac{dx}{dt} = \mathbf{A}x + \mathbf{B}u(t)$. 
+Here, $\mathbf{B}$ is the "input matrix" and $u(t)$ is the control vector. 
+The matrix $\mathbf{B}$ has size $S \times D$, where $S$ is the number of species in the community and $D$ is the number of species whose abundances are modified by the control vector. 
+The editor points out that a structural-controllability approach would not be useful in linear ecological systems because it will be "only valid in an infinitesimal border" around an initial equilibrium point.
+This comment would be completely appropriate if our aim were to design the time-varying control trajectory that drives the system from one equilibrium point another. 
+In other words, it would be inappropriate to design $u(t)$ based exclusively on a local linear approximation at the initial equilibrium.  
 Our manuscript, however, has a completely different aim.
 
-We use the structure of interaction network to determine the set of nodes that could be used to control the system. 
-This is, we use information contained in $\mathbf{A}$ to determine $\mathbf{B}$ (and by extension $D$). 
-Our most novel contributions are to use $D$ and knowledge of all the possible ways in which $\mathbf{B}$ can be parameterised in order to gain insight of the controllability of the network and role of the species that compose it.
-Understanding $\mathbf{B}$ is a prerequisite to designing $u(t)$, regardless of whether we are interested on controllability near an equilibrium point or along a linearisation of the system's nominal trajectory outside of equilibrium.
-Even existing numerical approaches that operate in a fully nonlinear setting like those proposed by @Cornelius2013 require previous knowledge of the set of nodes (species) to which to apply the control signal.
+We instead use the structure of interaction network to determine the set of nodes that could be used to control the system. 
+That is, we use the information contained in $\mathbf{A}$ to generate a supportable estimate of $\mathbf{B}$ (and by extension $D$). 
+Our most novel contributions are to use $D$ and knowledge of all the possible ways in which $\mathbf{B}$ can be structured in order to gain insight of the controllability of the network and the role of the species that compose it.
+Understanding $\mathbf{B}$ is a prerequisite to designing $u(t)$, regardless of whether we are interested in controllability near an equilibrium point or along a linearisation of the system's nominal trajectory outside of equilibrium.
+Indeed, even existing numerical approaches that operate in a fully nonlinear setting like those proposed by @Cornelius2013 require previous knowledge of the set of nodes (species) to which to apply the control signal.
 
-We see the fact that we focus on $\mathbf{B}$ and the network structure as an advantage rather than a disadvantage. 
+Furthermore, we see the fact that we focus on $\mathbf{B}$ and the network structure as an advantage rather than a disadvantage. 
 As one of the previous reviewers highlighted, our manuscript "...presents to ecologists a novel way of studying the relationship between topology and dynamics that is less dependent (when compared to other methods) on particular choices about how dynamics are modelled".

### 2017-05-03 paper/response_to_reviewers.Rmd
add minor changes to response

@@
 This comment would be completely appropriate if our aim were to design the time-varying control trajectory that drives the system from one equilibrium point another. 
-In other words, it would be inappropriate to design $u(t)$ based exclusively on a local linear approximation at the initial equilibrium.  
+In other words, it would be wrong to design $u(t)$ based exclusively on a local linear approximation at the initial equilibrium. 
 Our manuscript, however, has a completely different aim.
@@
 That is, we use the information contained in $\mathbf{A}$ to generate a supportable estimate of $\mathbf{B}$ (and by extension $D$). 
-Our most novel contributions are to use $D$ and knowledge of all the possible ways in which $\mathbf{B}$ can be structured in order to gain insight of the controllability of the network and the role of the species that compose it.
+Our most novel contributions are to use $D$ and knowledge of all the possible ways in which $\mathbf{B}$ can be str uctured in order to gain insight of the controllability of the network and the role of the species that compose it.
 Understanding $\mathbf{B}$ is a prerequisite to designing $u(t)$, regardless of whether we are interested in controllability near an equilibrium point or along a linearisation of the system's nominal trajectory outside of equilibrium.

### 2017-05-03 paper/manuscript.Rmd
update manuscript to address handling editor concerns

@@
 
-Conveniently the information necessary to determine the minimum number of driver nodes *D* in a network with linear dynamics is fully contained in the network structure [@Kalman1963; @Liu2011; @Motter2015].
-We therefore start here from the assumption that an ecological network near equilibrium points can be described by $\frac{dx}{dt} = Ax + Bu(t)$, where the change of its state over time ($\frac{dx}{dt}$) depends on its current state *x* (for example the species' abundances), an external time-varying input *u(t)*, and two matrices *A* and *B*, which encapsulate information about the network structure and how the species respond to the external input, respectively.
-Even though linearity might be a strong assumption, it has been shown that fundamental insight about the control of complex systems can be gained without a detailed knowledge of the nonlinear dynamics and the system parameters [@Liu2016], an important step towards ultimately understanding the controllability of systems with nonlinear dynamics [@Liu2011].
-This means that structural controllability can be applied to a wide range of network representations of ecological communities to provide an indication of our ability to control them. 
-Moreover, we show here how quantitative data about species interactions can help us move past some of the limitations of structural controllability by better approximating the role of interspecific dynamic relationships without being overly dependent on the choices of how these dynamics are modelled or characterised.
+Conveniently the information necessary to determine the minimum number of driver nodes *D* in a system with linear dynamics is fully contained in the network structure [@Kalman1963; @Liu2011; @Motter2015].
+Such a system can be described by $\frac{dx}{dt} = Ax + Bu(t)$, where the change of its state over time ($\frac{dx}{dt}$) depends on its current state *x* (for example the species' abundances), an external time-varying input *u(t)* (the control vector), and two matrices *A* and *B*, which encapsulate information about the network structure and how the species respond to the external input, respectively.
+The matrix *B* has size $S \times D$, where *S* is the number of species in the community. 
+Briefly, the focus of structural controllability, which we employ here, is to use the information contained in $\mathbf{A}$ to generate a supportable estimate of $\mathbf{B}$ (and by extension $D$).
+
+This focus allows us to gain insight of the controllability of the network and the role of the species that compose it without being overly dependent on the particular choices of how the system dynamics are modelled or characterised.
+The trade-off is that, because of the assumption that ecological communities can be modeled with linear functional responses, at least near equilibrium points, structural controllability is not adequate to design a the time varying control signal *u(t)* that can drive the system from one particular equilibrium to another.
+Nevertheless, the lessons gained when assuming linearity—both at the network and the species level—are a prerequisite for understanding nonlinear control [@Liu2011; @Liu2016].
 
@@
 In this study, we illustrate how a control-theoretic approach can be better adopted in network ecology to evaluate the effect of invasions and other kinds of perturbations. 
+We study the different ways a management intervention can be structured and provide a starting point for the study controllability of ecological systems.
 Although our pollination specific results might not be directly translatable to other ecological systems because of the degree constraints imposed by bipartite networks, the approach we propose is applicable wherever species abundances are influenced by their interactions, and exciting open questions lie ahead.
 How to design the precise "control signals" to reach a desired ecosystem state or conservation outcome? 
-What are the implications of assuming linear species dynamics?
+What are the implications of assuming fully nonlinear dynamics?
 How important it is to include several interaction types for our understanding of manageability and species importance?
@@
 Answering each of these questions might require its evaluation in different ecological systems, an explicit integration of control theory with numerical models of species densities [@Cornelius2013; @Gibson2016], and experimental tests on simple communities.
-Nevertheless, the potential rewards are encouraging from both an ecological and conservation perspective, where an integrated approach can shift our focus beyond the identification of ideal targets for intervention to the design of informed interventions that legitimately achieve restoration goals.
+Nevertheless, the potential rewards are encouraging from both an ecological and conservation perspective, where an integrated approach can shift the focus beyond the identification of ideal targets for intervention to the design of informed interventions that legitimately achieve restoration goals.
 

### 2017-05-04 paper/response_to_reviewers.Rmd
Minor corrections

--- 2017-05-02 paper/response_to_reviewers.Rmd
@@
 
-As noted in our manuscript, the dynamics of an ecological system near equilibrium can be represented by $\frac{dx}{dt} = \mathbf{A}x + \mathbf{B}u(t)$. 
+As noted in our manuscript, the dynamics of an ecological system near equilibrium can be represented by $\frac{dx}{dt} = \mathbf{A}x(t) + \mathbf{B}u(t)$. 
 Here, $\mathbf{B}$ is the "input matrix" and $u(t)$ is the control vector. 

### 2017-05-04 paper/drafts_and_revisions/submission_2016Jul11/covering_letter_dbs_2016-07_12.tex
Change folder names

--- 2016-07-18 paper/covering_letter.tex
@@
 
-Central to this manuscript is the introduction, development, and application of the theoretical concept of \textbf{ecological manageability}.
-Based on the patterns of interactions between species, this idea can provide two main pieces of information. 
-First, it allows to quantify the \textit{community manageability}---an indication of the difficulty of controlling the abundances of all species in the community. 
-Second it allows to identify \textit{driver species}--- those species with a disproportionate ability to alter other species' abundances.  
-Here, we use this concept as a framework to study the changes induced by biotic invasions to pollination networks.
+Central to this manuscript is the introduction, development, and application
+of the theoretical concept of \textbf{ecological manageability}. Based on the
+patterns of interactions between species, this idea can provide two main
+pieces of information. First, it allows us to quantify the \textit{community
+manageability}---an indication of the difficulty of controlling the abundances
+of all species in the community. Second it allows to identify \textit{driver
+species}--- those species with disproportionate ability to alter other
+species' abundances. Here, we use this concept as a framework to study the
+changes induced by biotic invasions to pollination networks.
 
-Multiple empirical observations have suggested that the structural changes caused by invasions may lead to increased ecosystem resilience. 
-Our study is the first to use empirical data to provide theoretical support for this idea. 
-Furthermore, our approach to identify driver species and quantify their relative importance, is unique in that it is based directly on the aspects of network structure that determine the behavior of the community as a holistic dynamical system.
-Our results also highlight the extent to which some species---invaders in particular---can drive the dynamics of other species across their community, and also identify ``asymmetric dependence'' as the potential mechanism driving the interspecific differences.
+Multiple empirical observations have suggested that the structural changes
+caused by invasions may lead to increased ecosystem resilience. Our study is
+the first to use empirical data to provide strong theoretical support for this
+idea. Furthermore, our approach to identify driver species and quantify their
+relative importance is unique in that it is based directly on the aspects of
+network structure that determine the behavior of the community as a holistic
+dynamical system. Our results also highlight the extent to which some
+species---invaders in particular---can drive the dynamics of other species
+across their community, and also identify ``asymmetric dependence'' as the
+potential key mechanism driving the interspecific differences.
 
-Despite our focus, understanding how drivers of ecosystem change affect ecosystem dynamics is not exclusive to mutualistic communities. 
-Indeed, we envisage the application of the concepts we introduce to answer a wide range of ecological questions in communities structured by different types of interactions.
-As such, we have sought to highlight the methodology necessary for its implementation---an extension of recently developed tools at the interface of complex systems and control theory---thoroughout the manuscript.
+Despite our focus, understanding how drivers of ecosystem change affect
+ecosystem dynamics is not exclusive to mutualistic communities. Indeed, we
+envisage the application of the concepts we introduce here to answer a wide
+range of ecological questions in communities structured by different types of
+interactions. As such, we have sought to highlight the methodology necessary
+for its implementation---an extension of recently developed tools at the
+interface of complex systems and control theory---thoroughout the manuscript.
 
-Our study fundamentally lies within ecological theory, yet it has ramifications pertinent to ecological application. 
-Indeed, we show in the paper that concepts like ``manageability'' have the potential to stimulate much needed research that reduce the gap between theory and management.
-Hopefully our study and more like it will set us on the track to informed, rather than hopeful, ecosystem interventions.
+While our study fundamentally lies within ecological theory, we cannot
+overlook its relevance to ecological applications. Indeed, we demonstrate in
+the paper itself that concepts like ``manageability'' have the potential to
+stimulate much needed research that shortens the gap between theory and
+management. Hopefully our study and more like it will set us on the track to
+informed, rather than hopeful, ecosystem interventions.
 
-Lastly, please note that the enclosed work represents a novel contribution for all co-authors involved and no related work published, in press, or submitted during this or last year has been cited.
+Lastly, please note that the enclosed work represents a novel contribution for
+all co-authors involved and no related work published, in press, or submitted
+during this or last year has been cited therein.
 

### 2017-05-04 paper/manuscript.Rmd

@@
 Disregarding practical considerations, any network (community) could hypothetically be fully controlled if we control the state of every single node (species) individually.
-At the core of control theory of complex networks, however, rests the idea that the state of a node depends on the state of the nodes it interacts with, and the form of this dependence is determined by both the dynamic relationship among interacting nodes and the structure of the links in the network.
-This principle can therefore be harnessed to find a subset of *driver nodes* to which to apply external input signals which then drive the state of every other node in the network to a desired configuration [@Liu2016].
+At the core of control theory of complex networks, however, sits the idea that the state of any given node depends on the state of the nodes it interacts with, and the form of this dependence is determined by both the dynamic relationship among interacting nodes and the structure of the links in the network.
+This principle can be leveraged to find a subset of *driver nodes* to which to apply external input signals which then drive the state of every other node in the network to a desired configuration [@Liu2016].
 
 Conveniently the information necessary to determine the minimum number of driver nodes *D* in a system with linear dynamics is fully contained in the network structure [@Kalman1963; @Liu2011; @Motter2015].
-Such a system can be described by $\frac{dx}{dt} = Ax + Bu(t)$, where the change of its state over time ($\frac{dx}{dt}$) depends on its current state *x* (for example the species' abundances), an external time-varying input *u(t)* (the control vector), and two matrices *A* and *B*, which encapsulate information about the network structure and how the species respond to the external input, respectively.
-The matrix *B* has size $S \times D$, where *S* is the number of species in the community. 
-Briefly, the focus of structural controllability, which we employ here, is to use the information contained in $\mathbf{A}$ to generate a supportable estimate of $\mathbf{B}$ (and by extension $D$).
+Such a system can be described by $\frac{dx}{dt} = Ax + Bu(t)$, where the change of its state over time ($\frac{dx}{dt}$) depends on its current state *x* (for example, the species' abundances), an external time-varying input *u(t)* (the control vector), and two matrices *A* and *B*, which encode information about the network structure and how the species respond to the external input, respectively.
+If *S* is the number of species in the community, the matrix *A* has size $S \times $S whereas the matrix *B* has size $S \times D$.
 
-This focus allows us to gain insight of the controllability of the network and the role of the species that compose it without being overly dependent on the particular choices of how the system dynamics are modelled or characterised.
-The trade-off is that, because of the assumption that ecological communities can be modeled with linear functional responses, at least near equilibrium points, structural controllability is not adequate to design a the time varying control signal *u(t)* that can drive the system from one particular equilibrium to another.
-Nevertheless, the lessons gained when assuming linearity—both at the network and the species level—are a prerequisite for understanding nonlinear control [@Liu2011; @Liu2016].
+The goal of structural controllability, which we employ here, is to use the information contained in $\mathbf{A}$ to generate a supportable estimate of $\mathbf{B}$ (and by extension $D$).
+This focus allows us to gain insight of the inherent controllability of a network, and the roles of the species that compose it, without being overly dependent on the particular choices of how the system dynamics are modelled or characterised.
+The trade-off is that, because of the assumption that ecological communities can be modeled with linear functional responses, structural controllability is not sufficient to fully design a the time-varying control signal *u(t)* that can drive the system from one particular equilibrium to another.
+Nevertheless, the lessons gained when assuming linearity---at both the network and the species level---are a prerequisite for understanding nonlinear control [@Liu2011; @Liu2016].
 
@@
 
-In this study, we illustrate how a control-theoretic approach can be better adopted in network ecology to evaluate the effect of invasions and other kinds of perturbations. 
-We study the different ways a management intervention can be structured and provide a starting point for the study controllability of ecological systems.
-Although our pollination specific results might not be directly translatable to other ecological systems because of the degree constraints imposed by bipartite networks, the approach we propose is applicable wherever species abundances are influenced by their interactions, and exciting open questions lie ahead.
+In this study, we illustrate how a control-theoretic approach can be employed in network ecology to evaluate the effect of invasions and other kinds of perturbations. 
+We study the different ways a management intervention can be structured and provide a starting point for the continued study of controllability in ecological contexts.
+Although our pollination-specific results might not be directly translatable to other ecological networks that do not have bipartite structures, the approach we propose is applicable wherever species abundances are influenced by their interactions, and exciting open questions lie ahead.
 How to design the precise "control signals" to reach a desired ecosystem state or conservation outcome? 

### 2017-05-04 paper/manuscript.Rmd
Fix mathematical notation

@@
 
-* **Number of words:** 148 abstract; approx. 4,970 main text.
+* **Number of words:** 148 abstract; approx. 5,006 main text.
 
@@
 Conveniently the information necessary to determine the minimum number of driver nodes *D* in a system with linear dynamics is fully contained in the network structure [@Kalman1963; @Liu2011; @Motter2015].
-Such a system can be described by $\frac{dx}{dt} = Ax + Bu(t)$, where the change of its state over time ($\frac{dx}{dt}$) depends on its current state *x* (for example, the species' abundances), an external time-varying input *u(t)* (the control vector), and two matrices *A* and *B*, which encode information about the network structure and how the species respond to the external input, respectively.
-If *S* is the number of species in the community, the matrix *A* has size $S \times $S whereas the matrix *B* has size $S \times D$.
+Such a system can be described by $\frac{dx}{dt} = \mathbf{A}x + \mathbf{B}u(t)$, where the change of its state over time ($\frac{dx}{dt}$) depends on its current state *x* (for example, the species' abundances), an external time-varying input *u(t)* (the control signal), and two matrices *A* and *B*, which encode information about the network structure and how the species respond to the external input, respectively.
+If *S* is the number of species in the community, the matrix **A** has size $S \times S$ whereas the matrix **B** has size $S \times D$.
 
-The goal of structural controllability, which we employ here, is to use the information contained in $\mathbf{A}$ to generate a supportable estimate of $\mathbf{B}$ (and by extension $D$).
+The goal of structural controllability, which we employ here, is to use the information contained in **A** to generate a supportable estimate of **B** (and by extension *D*).
 This focus allows us to gain insight of the inherent controllability of a network, and the roles of the species that compose it, without being overly dependent on the particular choices of how the system dynamics are modelled or characterised.
-The trade-off is that, because of the assumption that ecological communities can be modeled with linear functional responses, structural controllability is not sufficient to fully design a the time-varying control signal *u(t)* that can drive the system from one particular equilibrium to another.
+The trade-off is that, because of the assumption that ecological communities can be modelled with linear functional responses, structural controllability is not sufficient to fully design a the time-varying control signal *u(t)* that can drive the system from one particular equilibrium to another.
 Nevertheless, the lessons gained when assuming linearity---at both the network and the species level---are a prerequisite for understanding nonlinear control [@Liu2011; @Liu2016].
@@
 
-When exploring the effect of network structure itself, we observed that the driver-node density $n_D$ of empirical networks was, in general, not significantly different to the manageability of network randomisations that maintained the degree of individual species (Figure 4).
-However, we found that the $n_D$ of empirical networks was significantly larger than that of randomisations that maintained the network structure but that differed only in the direction of the asymmetries.
+When exploring the effect of network structure itself, we observed that the driver-node density *n~D~* of empirical networks was, in general, not significantly different to the manageability of network randomisations that maintained the degree of individual species (Figure 4).
+However, we found that the *n~D~* of empirical networks was significantly larger than that of randomisations that maintained the network structure but that differed only in the direction of the asymmetries.
 
@@
 Specifically, we found that a species is more likely to be classified as a superior node if it had a large species strength (the sum of the dependences of all other species on the species of interest).
-To a smaller extent, visitation strength (a species' sum of visits) and degree also had a positive relationship with $f_S$. 
-In contrast, the relationships between species structural properties and $f_D$ were less clear cut (Table 1). 
+To a smaller extent, visitation strength (a species' sum of visits) and degree also had a positive relationship with *f~S~*. 
+In contrast, the relationships between species structural properties and *f~D~* were less clear cut (Table 1). 
 Both invasive species (which generally have a larger degree and high dependence strength) and pollinators (which generally have a smaller degree and low dependence strength) were classified as driver nodes in a large proportion of matchings.

### 2017-05-04 paper/response_to_reviewers.Rmd
Include description of modifications to the manuscript

@@
 
-Along similar lines to the above, we made the following modifications to the manuscript. 
-In the intro we ...
-As before, in the methods section, we start by stating the assumption of linearity (Lines XXX). 
-However, we now also explicitly explain how this assumption does not invalidate the gained insight (Lines XXX). 
-Finally, in the discussion we ...
+Along similar lines to the above, we have rewritten the a couple of paragraphs at the beginning of the "Theoretical framework" subsection (Lines 84-99) where we clearly state the assumption of linearity and how it does not invalidate the gained insight.
+the following modifications to the manuscript.
+In addition, we hade some minor modifications to the last paragraph of the discussion to make more clear our contribution and how it relates to posible future research (Lines 356-371).
 

### 2017-05-04 paper/response_to_reviewers.Rmd
Fix line numbers

@@
 Nevertheless, due to this comment and one of Referee 2 we have rediscovered its value and use it to support our decision to include the analysis of superior nodes, and not just driver nodes, in our manuscript.
-Though space constraints remain and we can only mention it briefly in the main text (Lines 328--330), we also dedicate a whole section in the Supporting Information (S2) to this subject.
+Though space constraints remain and we can only mention it briefly in the main text (Lines 329--331), we also dedicate a whole section in the Supporting Information (S2) to this subject.
 To summarise here, we found our networks weighted by asymmetry to be external dilation dominated, and hence have only a small number of cycles.
@@
 As the referee points out it, this is not an estimation but an exact calculation.
-The sentence (Lines 178--180) now reads "To do so, we calculated the networks' maximum matching and determined the minimum proportion of species *n~D~* that need external input signals to fully control the species abundances in the community".*
+The sentence (Lines 179--181) now reads "To do so, we calculated the networks' maximum matching and determined the minimum proportion of species *n~D~* that need external input signals to fully control the species abundances in the community".*
 
@@
 We now include a paragraph in the discussion to explore the similarities and differences of our work with previous indices based on structural metrics.
-We explain (Lines 349--351) how "our approach...
+We explain (Lines 350--352) how "our approach...
 is not based on a single structural metric but instead acknowledges the existence of multiple management strategies.
@@
 
-    *We now brifly mention in the Discussion (Lines 356--358) how "although our pollination specific results might not be directly translatable to other ecological systems because of the degree constrains imposed by bipartite networks, the approach we propose is applicable wherever species abundances are influenced by their interactions...".*
+    *We now brifly mention in the Discussion (Lines 359--361) how "although our pollination specific results might not be directly translatable to other ecological systems because of the degree constrains imposed by bipartite networks, the approach we propose is applicable wherever species abundances are influenced by their interactions...".*
 
@@
 Nevertheless, as suggested here and by another reviewer, we have included a section in the Supporting Information (S2) where we explain that our networks are external dilation dominated.
-Consequently, the approach of @Ruths2014 has provided us with very useful insight on the selection of the direction of control and the utility of the concept of driver nodes for management applications (Lines 208--211 and 328--330).*
+Consequently, the approach of @Ruths2014 has provided us with very useful insight on the selection of the direction of control and the utility of the concept of driver nodes for management applications (Lines 209--212 and 329--331).*
 
@@
     *We have now included comments about the general limitations of the structural-controllability approach in the "Theoretical framework" section.
-Furthermore, we are now explicit about the fact that species have multiple types of interactions and therefore our approach can only provide a partial picture when only one type of interaction is included (Lines 361--362).
-Finally, we are also explicit about the fact that we do not advocate for management decisions to be based solely on our approach (Lines 351--353).*
+Furthermore, we are now explicit about the fact that species have multiple types of interactions and therefore our approach can only provide a partial picture when only one type of interaction is included (Lines 363--364).
+Finally, we are also explicit about the fact that we do not advocate for management decisions to be based solely on our approach (Lines 352--354).*
 
@@
     *We apologise for the imprecision as we meant financial resources.
-We have modified the sentence to improve clarity (Lines 128--131) and it now reads "Ecologically, potential differences between species are relevant because management and conservation resources are limited, and therefore ecological interventions should be focused on the set of species that might provide the largest impact".*
+We have modified the sentence to improve clarity (Lines 129--132) and it now reads "Ecologically, potential differences between species are relevant because management and conservation resources are limited, and therefore ecological interventions should be focused on the set of species that might provide the largest impact".*
 
@@
 
-    *We have attempted to eliminate ambiguity by rephrasing the sentence (Lines 266--268).
+    *We have attempted to eliminate ambiguity by rephrasing the sentence (Lines 267--269).
 It now reads "...

### 2017-06-16 paper/manuscript.Rmd
Changes to the theoretical framework part

@@
 
-Disregarding practical considerations, any network (community) could hypothetically be fully controlled if we control the state of every single node (species) individually.
-At the core of control theory of complex networks, however, sits the idea that the state of any given node depends on the state of the nodes it interacts with, and the form of this dependence is determined by both the dynamic relationship among interacting nodes and the structure of the links in the network.
-This principle can be leveraged to find a subset of *driver nodes* to which to apply external input signals which then drive the state of every other node in the network to a desired configuration [@Liu2016].
+At the core of representing ecological communities as complex systems sits the idea that the state of any given node depends on its state, the state of the nodes it interacts with, the state of the nodes they interact with, and so on.
+These dependencies are given by the structure of the interactions, the dynamic relationships between nodes, and the mechanisms of self-regulation. 
+This representation has been very useful for our understanding of ecological communities and might be advantageous for a more formal approach to ecological management based on control theory.
 
-Conveniently the information necessary to determine the minimum number of driver nodes *D* in a system with linear dynamics is fully contained in the network structure [@Kalman1963; @Liu2011; @Motter2015].
+The overall objective of control theory is to be able to steer a system from one state to another in finite time. 
+However, in complex systems like ecological communities, the large number of nodes and interactions as well as their non-linear dynamics render its control extremely challenging.
+On one theoretical extreme, for instance, any ecological community could be fully controlled if we control the state of every species independently. 
+On another, the mechanisms of self-regulation and the multiple feedback cycles found in ecological communities mean it is also theoretically possible to control the whole community by directly modifying the state of just a *single* species [@Cowan2012; @Markovsky2013].
+Although mathematically correct, neither of these options are practical in real-world applications: the first because it is infeasible to design and implement interventions that modify the abundance of every single species in a community, and the second because the control signal might require unreasonably large amounts of time, energy, or unattainable rapid changes on the state [@Yan2012; @Motter2015].
+Here we explore an intermediate point between these two trivial solutions.
+
+In particular, we leverage the principle of species interdependence to find an intermediate set of *driver nodes* to control the network [@Liu2016]. 
+When we focus on net interspecific effects, it is possible to identify a minimum number of nodes the control of which can theoretically drive the state of every other node in the network to a desired configuration.
+Conveniently the information necessary to determine this minimum number of driver nodes *D* is fully contained in the network structure [@Kalman1963; @Liu2011; @Motter2015]. 
 Such a system can be described by $\frac{dx}{dt} = \mathbf{A}x + \mathbf{B}u(t)$, where the change of its state over time ($\frac{dx}{dt}$) depends on its current state *x* (for example, the species' abundances), an external time-varying input *u(t)* (the control signal), and two matrices *A* and *B*, which encode information about the network structure and how the species respond to the external input, respectively.
@@
 This focus allows us to gain insight of the inherent controllability of a network, and the roles of the species that compose it, without being overly dependent on the particular choices of how the system dynamics are modelled or characterised.
-The trade-off is that, because of the assumption that ecological communities can be modelled with linear functional responses, structural controllability is not sufficient to fully design a the time-varying control signal *u(t)* that can drive the system from one particular equilibrium to another.
-Nevertheless, the lessons gained when assuming linearity---at both the network and the species level---are a prerequisite for understanding nonlinear control [@Liu2011; @Liu2016].
+The trade-off of our approach is that, because of the assumption of linearity, structural controllability alone does not allow us to fully design the time-varying control signal *u(t)* that can drive the system from one particular equilibrium to another.
+Nevertheless, the lessons gained when assuming linearity---at both the network and the species level---are a prerequisite for eventually understanding nonlinear control [@Liu2011; @Liu2016].
 

### 2017-06-16 paper/manuscript.Rmd
Add brief description of cycles in the methids

@@
 This simplification, while maintaining ecological realism, is advantageous for several reasons. 
-First, it is consistent with previous advances in structural controllability; second, it avoids complications related to the introduction of artificial control cycles [@Ruths2014]; and third it significantly reduces the computational resources necessary for the application of our approach (Supporting Information S6).
+First, it is consistent with previous advances in structural controllability; second, it prevents the singular case in which the network could be perfectly matched rendering $D=1$ as well as problems related to the introduction of artificial control cycles [@Ruths2014]; and third it significantly reduces the computational resources necessary for the application of our approach (Supporting Information S6).
 Moreover, we found that changing to unidirectional interactions based on the direction of asymmetry does not alter the relative *n~D~* of different networks (Table S3).

### 2017-06-16 paper/manuscript.Rmd
Proceedings B formatting

@@
 classoption: a4paper
-csl: ecology-letters.csl
+csl: proceedings-of-the-royal-society-b.csl
 output:
@@
 
-**E. Fernando Cagua^1\*^, Kate L. Wootton^1,2§^, Daniel B. Stouffer^1#^**
+**E. Fernando Cagua^1^, Kate L. Wootton^1,2^, Daniel B. Stouffer^1^**
 
@@
 
-^\*^ efc29@uclive.ac.nz 
-^§^ kate.l.wootton@gmail.com
-^#^ daniel.stouffer@canterbury.ac.nz
-
-* **Running title:** Manageability of pollination networks.
-
-* **Keywords:** Network control, ecological networks, species importance, driver species, food webs, mutualism, management interventions, food web, interaction asymmetry, mutual dependence
-
-* **Article type:** Letter.
-
-* **Number of words:** 148 abstract; approx. 5,006 main text.
-
-* **Number of references:** 65
-
-* **Number of displays:** 5 figures; 1 table.
-
-* **Correspondence to:** Daniel Stouffer (daniel.stouffer@canterbury.ac.nz) - +64 3 364 2729 - Centre for Integrative Ecology, School of Biological Sciences, University of Canterbury, Private Bag 4800, Christchurch 8140, New Zealand
-
-* **Authorship:** DBS conceived the idea; all authors contributed to the development of the theoretical framework.
-EFC performed all analysis.
-EFC and DBS wrote the manuscript.
-All authors contributed to its revision.
-
-* **Data accessibility:** All data used in this manuscript have already been published by @Lopezaraiza-Mikel2007, @Bartomeus2008, and @Ballantyne2015.
-The reader should refer to the original sources to access the data.
+**Author for correspondence:** Daniel Stouffer (daniel.stouffer@canterbury.ac.nz) - +64 3 364 2729 - Centre for Integrative Ecology, School of Biological Sciences, University of Canterbury, Private Bag 4800, Christchurch 8140, New Zealand
 
@@
 Our results highlight the advantages of the control-theoretic framework for ecological questions and provide novel insight into the design of informed management interventions.
+
+**Keywords:** Network control theory, ecological networks, species importance, driver species, mutualism, management interventions
 
@@
 
-# Methods
-
-## Theoretical framework
+# Theoretical framework
 
@@
 
-### Manageability
+## Manageability
 
@@
 Note that this framework requires a directed network in which the direction of the links corresponds to the direction of control. 
-In the "Empirical application" section below, we explain our approach to determining the link direction in pollination networks.
+In the "Methods" section below, we explain our approach to determining the link direction in pollination networks.
 
-### Relative importance
+## Relative importance
 
@@
 
-## Empirical application
+# Methods
 
@@
 
-#### Weighting & directing links
+### Weighting & directing links
 
@@
 
-#### Statistical analysis
+### Statistical analysis
 
@@
 
-### Relative importance
+## Relative importance
 
@@
 
+## Data accessibility
+
+All data used in this manuscript have already been published by @Lopezaraiza-Mikel2007, @Bartomeus2008, and @Ballantyne2015. The reader should refer to the original sources to access the data.
+
+## Competing interests
+
+We have no competing interests.
+
+## Author contributions
+
+DBS conceived the idea; all authors contributed to the development of the theoretical framework. EFC performed all analysis. EFC and DBS wrote the manuscript. All authors contributed to its revision.
+
 ## Acknowledgments
@@
 The authors thank Jane Memmott and coauthors, and eveyone that has made their data available to us, Takeuki Uno for the insight provided to find the set of all maximum matching algorithms, and Jason Tylianakis, Bernat Bramon Mora, Guadalupe Peralta, Rogini Runghen, Warwick Allen, Matthew Hutchinson, and Marilia Gaiarsa for feedback and valuable discussions.
+
+## Funding
+
 EFC acknowledges the support from the University of Canterbury Doctoral Scholarship, the University of Canterbury Meadow Mushrooms Postgraduate Scholarship, a New Zealand International Doctoral Research Scholarship, and a travel grant from the European Space Agency.

### 2017-06-16 paper/cover-letter.tex
Update cover letter for Proceedings B

--- 2016-07-18 paper/covering_letter.tex
@@
        %\vspace*{20pt}
-       Prof. Tim Coulson\\
+       Prof. Spencer Barret\\
        Editor in Chief\\
-       Ecology Letters}
+       Proceedings of the Royal Society B}
 
-\opening{Dear Proffesor Coulson,}
+\opening{Dear Proffesor Barrett,}
 
-We are submitting the manuscript entitled ``Biotic invasions reduce the manageability of pollination networks'' to be considered for publication at \emph{Ecology Letters}.
+We are submitting the manuscript entitled ``Quantifying the manageability of pollination networks in an invasion context'' to be considered for publication at \emph{Proceedings B}.
 
@@
 
-Multiple empirical observations have suggested that the structural changes caused by invasions may lead to increased ecosystem resilience. 
+Multiple empirical observations have suggested that the structural changes caused by invasions may lead to changes on ecosystem resilience. 
 Our study is the first to use empirical data to provide theoretical support for this idea. 

### 2017-06-30 paper/cover-letter.tex
sorry for not pushing this earlier

--- 2016-07-18 paper/covering_letter.tex
@@
-\documentclass[10pt, a4paper]{letter}
+\documentclass[12pt]{letter}
+
+\usepackage[britdate]{canterbury-letter}
+\usepackage{times}
+%\usepackage{letterbib}
+\usepackage{geometry}
+% \usepackage[round]{natbib}
+\usepackage{graphicx}
+%\graphicspath{ {../figures/ecology_figs/} }
+\geometry{a4paper}
+\usepackage[T1]{fontenc}
+\usepackage[utf8]{inputenc}
+\usepackage{authblk}
+\usepackage[running]{lineno}
+\usepackage{amsmath,amsfonts,amssymb}
+\usepackage[margin=10pt,font=small,labelfont=bf]{caption}
+
+\newenvironment{refquote}{\smallskip \begin{it}}{\end{it}\smallskip}
+
+\name{Dr.\ Daniel B.\ Stouffer}
+\position{Associate Professor}
+\department{School of Biological Sciences}
+\location{Private Bag 4800}
+\telephone{+64 3 364 2729}
+\email{daniel.stouffer@canterbury.ac.nz}
+\url{http://stoufferlab.org}
+
+% \date{14 junio 2017}
 
@@
        %\vspace*{20pt}
-       Prof. Tim Coulson\\
+       Prof. Spencer Barrett\\
        Editor in Chief\\
-       Ecology Letters}
+       Proceedings of the Royal Society B}
 
-\opening{Dear Proffesor Coulson,}
+\opening{Dear Professor Barrett,}
 
-We are submitting the manuscript entitled ``Biotic invasions reduce the manageability of pollination networks'' to be considered for publication at \emph{Ecology Letters}.
+We are submitting the manuscript entitled ``Quantifying the manageability of pollination networks in an invasion context'' to be considered for publication at \emph{Proceedings of the Royal Society B}.
 
@@
 Based on the patterns of interactions between species, this idea can provide two main pieces of information. 
-First, it allows to quantify the \textit{community manageability}---an indication of the difficulty of controlling the abundances of all species in the community. 
-Second it allows to identify \textit{driver species}--- those species with a disproportionate ability to alter other species' abundances.  
-Here, we use this concept as a framework to study the changes induced by biotic invasions to pollination networks.
+First, it allows us to quantify the \textit{community manageability}---an indication of the inherent difficulty of controlling the abundances of all species in the community. 
+Second it allows us to identify \textit{driver species}---those species whose manipulation exhibits a disproportionate ability to alter other species' abundances.
 
-Multiple empirical observations have suggested that the structural changes caused by invasions may lead to increased ecosystem resilience. 
-Our study is the first to use empirical data to provide theoretical support for this idea. 
-Furthermore, our approach to identify driver species and quantify their relative importance, is unique in that it is based directly on the aspects of network structure that determine the behavior of the community as a holistic dynamical system.
+Here, we use this concept and the information it provides as a framework to study the changes induced by biotic invasions to pollination networks. 
+Multiple empirical observations have suggested that the structural changes caused by invasions may lead to changes to ecosystem resilience. 
+Our study is the first to use empirical data to provide direct theoretical support for this idea. 
+Furthermore, our approach to identify driver species, and quantify their relative importance, is unique in that it is based directly on the aspects of network structure that determine the behavior of the community as a holistic dynamical system.
 Our results also highlight the extent to which some species---invaders in particular---can drive the dynamics of other species across their community, and also identify ``asymmetric dependence'' as the potential mechanism driving the interspecific differences.
@@
 Indeed, we envisage the application of the concepts we introduce to answer a wide range of ecological questions in communities structured by different types of interactions.
-As such, we have sought to highlight the methodology necessary for its implementation---an extension of recently developed tools at the interface of complex systems and control theory---thoroughout the manuscript.
+As such, we have sought to highlight the methodology necessary for its implementation---an extension of recently developed tools at the interface of complex systems and control theory---throughout the manuscript.
 
-Our study fundamentally lies within ecological theory, yet it has ramifications pertinent to ecological application. 
-Indeed, we show in the paper that concepts like ``manageability'' have the potential to stimulate much needed research that reduce the gap between theory and management.
+Our study fundamentally lies within ecological theory, yet it also has ramifications pertinent to ecological application. 
+Indeed, we show in the paper that concepts like ``manageability'' have the potential to stimulate much needed research that can reduce the gap between theory and management.
 Hopefully our study and more like it will set us on the track to informed, rather than hopeful, ecosystem interventions.
 
-Lastly, please note that the enclosed work represents a novel contribution for all co-authors involved and no related work published, in press, or submitted during this or last year has been cited.
+Thank you in advance for your consideration of our manuscript at your journal.
 
 \closing{Regards,}
-
-Daniel B. Stouffer
 

### 2017-06-30 paper/cover-letter.tex
Minor edit to cover letter to highlight uniquenes earlier on

@@
 Second it allows us to identify \textit{driver species}---those species whose manipulation exhibits a disproportionate ability to alter other species' abundances. 
+Furthermore, our approach to identify driver species, and quantify their relative importance, is unique in that it is based directly on the aspects of network structure that determine the behavior of the community as a holistic dynamical system.
 
-Here, we use this concept and the information it provides as a framework to study the changes induced by biotic invasions to pollination networks. 
+Here, we use the concept of ecological manageability and the information it provides as a framework to study the changes induced by biotic invasions to pollination networks. 
 Multiple empirical observations have suggested that the structural changes caused by invasions may lead to changes to ecosystem resilience. 
 Our study is the first to use empirical data to provide direct theoretical support for this idea. 
-Furthermore, our approach to identify driver species, and quantify their relative importance, is unique in that it is based directly on the aspects of network structure that determine the behavior of the community as a holistic dynamical system.
 Our results also highlight the extent to which some species---invaders in particular---can drive the dynamics of other species across their community, and also identify ``asymmetric dependence'' as the potential mechanism driving the interspecific differences.

### 2017-09-12 paper/manuscript.Rmd
Fix graphs by making unweighted networks

@@
 fam <- "Helvetica"
+
 # layout is based on the bidirectional network
 set.seed(1)
-
-lay <- bi_net %>%
+bi_net_uw <- bi_net
+E(bi_net_uw)$weight <- 1
+lay <- bi_net_uw %>%
 	layout_nicely()

### 2017-09-12 paper/supporting_information.Rmd
Fix graphs by making unweighted networks

@@
 set.seed(1)
-
-lay <- bi_net %>%
+bi_net_uw <- bi_net
+E(bi_net_uw)$weight <- 1
+lay <- bi_net_uw %>%
 	layout_nicely()

### 2017-09-12 paper/manuscript.Rmd
Remove 6 references = ~ 100 words

@@
 
-In a complex system, the whole is often greater than the sum of its parts [@Jorgensen1998; @Levin1999; @Montoya2006].
-Within community ecology, a complex-systems approach has led to the development of analytical and simulation tools with which to understand, for example, the role of species embedded in a network of interactions [@Pascual2005; @Bascompte2009; @Stouffer2012].
+In a complex system, the whole is often greater than the sum of its parts [@Montoya2006].
+Within community ecology, a complex-systems approach has led to the development of analytical and simulation tools with which to understand, for example, the role of species embedded in a network of interactions [@Bascompte2009; @Stouffer2012].
 The inherent complexity of nature, however, has regularly hindered—or at least complicated—our ability to find management solutions to many problems ecological communities face. 
-To overcome this obstacle, we require a framework that allows us to explain, predict, and manage ecological communities, particularly when they are confronted with perturbations [@Sole2001; @Green2005].
+To overcome this obstacle, we require a framework that allows us to explain, predict, and manage ecological communities, particularly when they are confronted with perturbations [@Green2005].
 Ideally, such a framework is equipped to account for their complex structure and the dynamics that determine the species abundances and the state of the community.
@@
 Despite recent advances in network theory, practical challenges to the conservation of interaction networks persist [@Tylianakis2010], and the link between the structure of complex networks and our ability to manage and conserve them is still ambiguous [@Bluthgen2010; @Kaiser-Bunbury2015].
-To complicate things further, biotic invasions can induce dramatic changes in the patterns of interactions that determine the structure of ecological networks [@Baxter2004; @Tylianakis2008; @Ehrenfeld2010a], in particular pollination [@Olesen2002; @Aizen2008; @Bartomeus2008; @Vila2009; @Traveset2013].
+To complicate things further, biotic invasions can induce dramatic changes in the patterns of interactions that determine the structure of ecological networks [@Tylianakis2008; @Ehrenfeld2010a], in particular pollination [@Olesen2002; @Aizen2008; @Bartomeus2008; @Vila2009; @Traveset2013].
 Understanding how the differences in network structure before and after invasion impact our ability to manage the communities is thus a double challenge, but it is also the critical first step towards a fully informed recovery.
@@
 Second, as species with a high *f~D~*, they are also indispensable when it comes to fully controlling the plant-pollinator network. 
-At a community level, we demonstrate that the manageability of mutualistic networks is strongly governed by the asymmetric nature of mutual dependences—which constitute the foundations of the structure and stability of mutualistic networks [@Memmott2004; @Vazquez2004; @Bascompte2006; @Lever2014; @Astegiano2015].
+At a community level, we demonstrate that the manageability of mutualistic networks is strongly governed by the asymmetric nature of mutual dependences—which constitute the foundations of the structure and stability of mutualistic networks [@Memmott2004; @Vazquez2004; @Bascompte2006; @Astegiano2015].
 Moreover, these mutual dependences seem to be constrained by the effects of both the patterns of species richness at each trophic guild and a network's degree distribution [@Melian2002; @Bluthgen2007].

### 2017-09-26 paper/manuscript.Rmd
Use Journal of ecology citation style

@@
 classoption: a4paper
-csl: proceedings-of-the-royal-society-b.csl
+csl: journal-of-ecology.csl
 output:

### 2017-09-26 paper/manuscript.Rmd
Move figures and tables to the body

@@
     fig_crop: no
-    includes:
-      after_body: after_body.md
   html_document: default
@@
 - \usepackage{booktabs}
-- \usepackage{tocloft} 
 - \usepackage{caption}
-- \captionsetup{labelsep=none,textformat=empty}
 - \usepackage{lineno}
-- \usepackage[nomarkers,tablesfirst, nolists]{endfloat}
-- \cftpagenumbersoff{figure}
-- \cftpagenumbersoff{table}
 documentclass: artikel1
@@
 \linenumbers
-\renewcommand*\listfigurename{Figure legends}
-\renewcommand*\listtablename{Table legends}
 

### 2017-10-01 paper/manuscript.Rmd
Modify abstract

@@
 
-Here, we leverage recent advances in control theory to assess the "manageability" of ten pairs of uninvaded and invaded plant-pollinator communities. 
-We found that the networks' manageability is most strongly determined by the ratio of plants to pollinator richness, which in turn constrains the networks' degree distribution. 
-We also characterise species' suitability for inclusion in management interventions by exploring the entire space of control strategies. 
+* Despite important advances in network ecology, the link between network structure and management and conservation is still tenuous.
+Perhaps in part because of a lack of theoretical framework, efforts to link network and management have been mainly focused on network properties and less on mechanisms.
+* Here, we leverage recent advances in control theory to assess the "manageability" of ecological networks.
+For simplicity we ilustrate its application using ten pairs of uninvaded and invaded plant-pollinator communities.
+Furthermore, we also characterise species' suitability for inclusion in management interventions by exploring the entire space of control strategies.
 Specifically, we measure the extent to which species (i) are necessary to steer the state of the community and (ii) are able to affect the abundance of other species.
-We found that invasive plants have a dominant position in every invaded community and that this dominance is underpinned by high asymmetry in the dependence of their interaction partners. 
-Our results highlight the advantages of the control-theoretic framework for ecological questions and provide novel insight into the design of informed management interventions.
+* We found that the networks' manageability is most strongly determined by the ratio of plants to pollinator richness, which in turn constrains the networks' degree distribution.
+We also found that invasive plants have a dominant position in every invaded community and that this dominance is underpinned by high asymmetry in the dependence of their interaction partners.
+* Our results provide novel insigt into the design of informed management interventions and lay foundations for further work on the control of ecological networks.
 

### 2017-10-02 paper/manuscript.Rmd
Update end sections
dbs edits to the abstract; based on some errors caught there, we should probably to run spellcheck on everything

--- 2017-09-26 paper/manuscript.Rmd
@@
 
-Here, we leverage recent advances in control theory to assess the "manageability" of ten pairs of uninvaded and invaded plant-pollinator communities. 
-We found that the networks' manageability is most strongly determined by the ratio of plants to pollinator richness, which in turn constrains the networks' degree distribution. 
-We also characterise species' suitability for inclusion in management interventions by exploring the entire space of control strategies. 
+1.
+Despite important advances in network ecology, the link between the structure of an interaction network and management or conservation is still tenuous.
+Perhaps in part because of a lack of theoretical framework, efforts to strengthen this link have been mainly focused on whole-network properties instead of underlying mechanisms.
+2.
+Here, we leverage recent advances in control theory to develop an approach to assess the "manageability" of ecological networks.
+We then illustrate its application using ten pairs of uninvaded and invaded plant-pollinator communities.
+We also characterise species' suitability for inclusion in management interventions by exploring the entire space of alternative control strategies.
 Specifically, we measure the extent to which species (i) are necessary to steer the state of the community and (ii) are able to affect the abundance of other species.
-We found that invasive plants have a dominant position in every invaded community and that this dominance is underpinned by high asymmetry in the dependence of their interaction partners. 
-Our results highlight the advantages of the control-theoretic framework for ecological questions and provide novel insight into the design of informed management interventions.
+3.
+We found that the networks' manageability is most strongly determined by the ratio of plant to pollinator richness, which in turn constrains the networks' degree distribution.
+We also found that invasive plants have a dominant position in every invaded community and that this dominance is underpinned by high asymmetries in the dependences of their interaction partners.
+4. Our results provide novel insight into the design of ecologically-informed management interventions and lay the foundation for further work on the control of ecological networks.
 
@@
 
-## Data accessibility
+## Acknowledgments
 
-All data used in this manuscript have already been published by @Lopezaraiza-Mikel2007, @Bartomeus2008, and @Ballantyne2015. The reader should refer to the original sources to access the data.
-
-## Competing interests
-
-We have no competing interests.
+The authors thank Jane Memmott and coauthors, and eveyone that has made their data available to us, Takeuki Uno for the insight provided to find the set of all maximum matching algorithms, and Jason Tylianakis, Bernat Bramon Mora, Guadalupe Peralta, Rogini Runghen, Warwick Allen, Matthew Hutchinson, and Marilia Gaiarsa for feedback and valuable discussions.
+EFC acknowledges the support from the University of Canterbury Doctoral Scholarship, the University of Canterbury Meadow Mushrooms Postgraduate Scholarship, a New Zealand International Doctoral Research Scholarship, and a travel grant from the European Space Agency.
+DBS acknowledges the support of a Marsden Fast-Start grant and a Rutherford Discovery Fellowship, administered by the Royal Society of New Zealand.
 
@@
 
-## Acknowledgments
+## Data accessibility
 
-The authors thank Jane Memmott and coauthors, and eveyone that has made their data available to us, Takeuki Uno for the insight provided to find the set of all maximum matching algorithms, and Jason Tylianakis, Bernat Bramon Mora, Guadalupe Peralta, Rogini Runghen, Warwick Allen, Matthew Hutchinson, and Marilia Gaiarsa for feedback and valuable discussions.
-
-## Funding
-
-EFC acknowledges the support from the University of Canterbury Doctoral Scholarship, the University of Canterbury Meadow Mushrooms Postgraduate Scholarship, a New Zealand International Doctoral Research Scholarship, and a travel grant from the European Space Agency.
-DBS acknowledges the support of a Marsden Fast-Start grant and a Rutherford Discovery Fellowship, administered by the Royal Society of New Zealand.
+All data used in this manuscript have already been published by @Lopezaraiza-Mikel2007, @Bartomeus2008, and @Ballantyne2015. The reader should refer to the original sources to access the data.
 

### 2017-10-15 paper/manuscript.Rmd
Keywords in alphabetical order
Add journal topic as keyword

@@
 
-**Keywords:** Network control theory, ecological networks, species importance, driver species, mutualism, management interventions
+**Keywords:** Driver species, ecological networks, management interventions, mutualism, network control theory, plant population and community dynamics, species importance
 

### 2018-03-26 publication/manuscript.Rmd
Start using drake

---
title: "Network control"
classoption: a4paper
csl: journal-of-ecology.csl
output: 
  bookdown::pdf_document2: 
    keep_tex: yes
    number_sections: false
toc: false
header-includes:
- \usepackage{setspace}
- \usepackage{float}
- \usepackage{booktabs}
- \usepackage{caption}
- \usepackage{lineno}
documentclass: artikel1
bibliography: references.bib
---

\doublespacing
\linenumbers

```{r example_network, include = F}
loadd(example_net)

base_net <- example_net
	bi_net <- example_net %>%
		keep_largest_component() %>%
		bipartite_digraph(type = "z-bi", weight.type = "asymetry") 
	as_net <- example_net %>%
		keep_largest_component() %>%
		bipartite_digraph(type = "weight", weight.type = "asymmetry")

	fam <- "Helvetica"

	# layout is based on the bidirectional network
	set.seed(1)
	bi_net_uw <- bi_net
	E(bi_net_uw)$weight <- 1
	lay <- bi_net_uw %>%
		layout_nicely()
	v_c <- "white"
	l_c <- "black"
	l_s <- 0.9
	ma <- c(0,0,0,0)
	label_pos_x <- -1
	label_pos_y <- 1
```

### 2018-03-26 make_paper.R

@@ -1,0 +1,43 @@
+# Because the project started way before I adopted a workflow management
+# strategy in R, and converting the scripts to adopt the workflow would require
+# a bit too much work, this workflow is limited to building the publication
+# files and the analyses added in the round of revisions from the Journal of
+# Ecology submission
+
+# LIBRARIES AND FUNCTIONS -------------------------------------------------
+
+library(drake)
+library(rmarkdown)
+library(tinytex)
+
+# required by paper or analysis
+library(latex2exp)
+library(igraph)
+
+# load functions
+f <- list.files("./functions/", full.names = T) %>% lapply(source)
+
+# DEFINE PLAN ----------------------------------------------------------------
+
+ilustrations <- drake_plan(example_net = generate_example_network())
+
+reporting <- drake_plan(
+	# 'publication/supp_info.tex' = render('publication/supporting_information.Rmd', quiet = TRUE),
+	# 'publication/supp_info.pdf' = latexmk('publication/supp_info.tex', clean = FALSE),
+	'publication/manuscript.tex' = render('publication/manuscript.Rmd', quiet = TRUE),
+	'publication/manuscript.pdf' = latexmk('publication/manuscript.tex', clean = FALSE),
+	file_targets = TRUE
+)
+
+
+# MAKE --------------------------------------------------------------------
+
+# set up plan
+project_plan <- rbind(ilustrations, reporting)
+project_config <- drake_config(project_plan)
+vis_drake_graph(project_config, split_columns = T, targets_only = T)
+
+# execute plan
+# make(project_plan, parallelism = "parLapply", jobs = 7)
+make(project_plan)
+

### 2018-03-27 publication/manuscript.Rmd
Start trying to make a new intro

@@
 \linenumbers
+
+**E. Fernando Cagua^1^, Kate L. Wootton^1,2^, Daniel B. Stouffer^1^**
+
+^1^ Centre for Integrative Ecology, School of Biological Sciences, University of Canterbury, Private Bag 4800, Christchurch 8041, New Zealand
+
+^2^ Current address: Department of Ecology, Swedish University of Agricultural Sciences, Box 7044, SE-750 07 Uppsala, Sweden
+
+**Author for correspondence:** Daniel Stouffer (daniel.stouffer@canterbury.ac.nz) - +64 3 364 2729 - Centre for Integrative Ecology, School of Biological Sciences, University of Canterbury, Private Bag 4800, Christchurch 8140, New Zealand
+
+\newpage
+
+# Introduction
+
+Networks have used to study the role of species in their community.
+Most approaches are rooted on the assumption that there is a link between a species centrality and its importance—its ability to modify the abundance of other species.
+However, recent studies show that definitions of role based on centrality, although simple, might not be a good proxy for the importance of a species for ecosystem functioning.
+Here we show that using a control theory can yield novel insights about a species role in the community.
 

### 2018-03-27 make_paper.R

@@ -13,6 +13,7 @@ library(tinytex)
 # required by paper or analysis
 library(latex2exp)
 library(igraph)
+library(ggplot2)
 
 # load functions
 f <- list.files("./functions/", full.names = T) %>% lapply(source)
@@ -39,5 +40,5 @@ vis_drake_graph(project_config, split_columns = T, targets_only = T)
 
 # execute plan
 # make(project_plan, parallelism = "parLapply", jobs = 7)
-make(project_plan)
+make(project_plan, graph = project_config$graph, config = project_config, session_info = T)
 

### 2018-03-29 publication/manuscript.Rmd
Keep on working on the intro

@@
 
-Networks have used to study the role of species in their community.
-Most approaches are rooted on the assumption that there is a link between a species centrality and its importance—its ability to modify the abundance of other species.
-However, recent studies show that definitions of role based on centrality, although simple, might not be a good proxy for the importance of a species for ecosystem functioning.
-Here we show that using a control theory can yield novel insights about a species role in the community.
+Within community ecology, a complex-systems approach has led to the development of analytical and simulation tools with which to understand the role of species embedded in a network of interactions [@Bascompte2009; @Stouffer2012].
+A particularly relevant dimension of a species role for ecosystem functioning is that which relates to its ability to alter the abundance of other species in the community. 
+This ability is often refered as species importance or "keystoness". 
+A significant proportion of the network tools used to estimate a species ability to modify its community is based on the assumption that there is a link between a species centrality and its importance.
+However, recent studies have shown that definitions of role based on centrality, although straightforward, might not adequately estimate the relative influence of a species on its community. 
+To overcome this issue, we require a framework that is equipped to account for the structure of the interactions in the community, but that also acknowledges the dynamics that determine species abundance and ultimately determine the state of the community.
+
+Among the various possibilities, *control theory* appears to be a strong candidate [@Isbell2013]. 
+Widely used in engineering to determine and supervise the behaviour of dynamical systems [@Motter2015], it is well equipped to deal with the many feedbacks present in ecological communities [@Liu2016].
+Furthermore, advances in this field have established a mathematically sound, and more direct, link between the structure of the network and the way nodes afect each other.
+s state  suggest that it is in principle possible to alter a whole ecological community's composition by modifying the abundances of only a few species
+
+Research in this area has established a strong link between the structure of complex networks and their *controllability*—the relative ability to manipulate network components to drive the system to a desired state [@Liu2011; @Cornelius2013; @Ruths2014].
+These advances suggest that it is in principle possible to alter a whole ecological community's composition by modifying the abundances of only a few species.
+Applications of control theory to ecological networks can also take into account the extent to which changes in the abundances of one species may ripple through the community [@Cornelius2013].
+Therefore, control theory could also be harnessed to help identify which species are most relevant from a structural and dynamic perspective.
 

### 2018-04-04 publication/manuscript.Rmd
Second paragraph of the introduction

@@
 However, recent studies have shown that definitions of role based on centrality, although straightforward, might not adequately estimate the relative influence of a species on its community. 
-To overcome this issue, we require a framework that is equipped to account for the structure of the interactions in the community, but that also acknowledges the dynamics that determine species abundance and ultimately determine the state of the community.
+To overcome this issue, we require a framework that is equipped to account for the structure of the interactions in the community, but that also acknowledges the dynamics that determine species abundance and ultimately the state of the community.
 
@@
 Widely used in engineering to determine and supervise the behaviour of dynamical systems [@Motter2015], it is well equipped to deal with the many feedbacks present in ecological communities [@Liu2016].
-Furthermore, advances in this field have established a mathematically sound, and more direct, link between the structure of the network and the way nodes afect each other.
+Furthermore, advances in this field have established a link between the structure of the network and the way nodes afect each other that is based, not on a-priori assumptions, but, on well-established advances on dynamical a complex systems theory.
+Despite the coincidences, the concepts and approaches of control theory are not commonly applied in an ecological context. 
+This is, in part, because in contrast with ecology, research on the control of complex networks is generally more concerned with driving the state the system as a whole rather than the nodes that compose the network.
+Here, we expand current methods of control theory and show how it can also be used to gain insight about the role of species in an ecological nework.
+
+We outline the approach using a set of ten pairs of uninvaded and invaded plant-pollinator communities. 
+We use invaded communities because there is strong empirical evidence that the invasive species played a role shaping the abundances of other species in the networks and therefore they are ideal candidates to test whether theoretical observations match empirical evidence.
+
+and effectively link the *controllability* of an ecological network with the role of particular species. 
+To do that we use a set
+
+Second we show plays in the context of affecting the abundance of other species.
+
+t its fundamental level, control theory is concerned on determining whether a system is at all controllable, this is, wether it can be driven to a desired state or not. 
+In other words, the objective is to controllability is a property of the system as a whole
+
+Here we develop
+
+On its fundamentals control theory is concerned on determining the
+
+We think that part of the reason control theory is not widely
+
 s state  suggest that it is in principle possible to alter a whole ecological community's composition by modifying the abundances of only a few species

### 2018-04-06 publication/manuscript.Rmd
Finish rewrite of the intro

--- 2018-03-29 publication/manuscript.Rmd
@@
 ---
-title: "Network control"
+title: "Ecological network control"
 classoption: a4paper
@@
 A particularly relevant dimension of a species role for ecosystem functioning is that which relates to its ability to alter the abundance of other species in the community. 
-This ability is often refered as species importance or "keystoness". 
+This ability is often referred as species importance or "keystoness". 
 A significant proportion of the network tools used to estimate a species ability to modify its community is based on the assumption that there is a link between a species centrality and its importance.
 However, recent studies have shown that definitions of role based on centrality, although straightforward, might not adequately estimate the relative influence of a species on its community. 
-To overcome this issue, we require a framework that is equipped to account for the structure of the interactions in the community, but that also acknowledges the dynamics that determine species abundance and ultimately determine the state of the community.
+To overcome this issue, we require a framework that is equipped to account for the structure of the interactions in the community, but that also acknowledges the dynamics that determine species abundance and ultimately the state of the community.
 
@@
 Widely used in engineering to determine and supervise the behaviour of dynamical systems [@Motter2015], it is well equipped to deal with the many feedbacks present in ecological communities [@Liu2016].
-Furthermore, advances in this field have established a mathematically sound, and more direct, link between the structure of the network and the way nodes afect each other.
-s state  suggest that it is in principle possible to alter a whole ecological community's composition by modifying the abundances of only a few species
+Furthermore, advances in this field have established a link between the structure of the network and the way nodes affect each other that is based on well-established advances in both dynamical and complex systems theory.
+As such, a priori assumptions about how particular node metrics, like centrality, are related to network functioning are not required
+Despite the coincidences between ecological and engineering systems, the concepts and approaches of control theory are not commonly applied in an ecological context. 
+This is, in part, because in contrast with ecology, research on the control of complex networks is generally more concerned with driving the state the system as a whole rather than the nodes that compose the network.
+At its fundamental level, control theory is concerned with determining whether a system is at all controllable, this is, whether it can be driven to a desired state or not. 
+Our first contribution is to expand existing methods control theory to effectively link the *controllability* of a network with the role of particular nodes.
 
-Research in this area has established a strong link between the structure of complex networks and their *controllability*—the relative ability to manipulate network components to drive the system to a desired state [@Liu2011; @Cornelius2013; @Ruths2014].
-These advances suggest that it is in principle possible to alter a whole ecological community's composition by modifying the abundances of only a few species.
-Applications of control theory to ecological networks can also take into account the extent to which changes in the abundances of one species may ripple through the community [@Cornelius2013].
-Therefore, control theory could also be harnessed to help identify which species are most relevant from a structural and dynamic perspective.
+After overcoming this first hurdle, we then apply the methods to an ecological problem and show how it can be used to gain insight into the role of species in an ecological network. 
+Specifically, we outline the approach using a set of ten pairs of uninvaded and invaded plant-pollinator communities. 
+We use invaded communities because there is strong empirical evidence showing that invasive species play an important role shaping the abundances of other species.
+Certainly so in the chosen networks [@Lopezaraiza-Mikel2007; @Bartomeus2008].
+Hence, this choice offers an opportunity to contrast theoretical observations with empirical evidence. 
+First, grounded in the difficulties usually involved with invasive-species eradication and ecosystem restoration [@Woodford2016], we ask whether invaded networks require a greater proportion of species to be managed to achieve the same level of control.
+Second, we ask—from a control theoretic perspective—wether there are differences among species in the role they play at driving the population of other members of the community and the factors related to these differences.
+Finally, we compare the proposed approach to current methods based on species centrality and show how these methods are indeed valuable but only paint a limited picture in regards to the "keystoness" of a species.
 

### 2018-04-18 publication/manuscript.Rmd
Link between problem and solution was not clear
Modifying intro

@@
 A significant proportion of the network tools used to estimate a species ability to modify its community is based on the assumption that there is a link between a species centrality and its importance.
-However, recent studies have shown that definitions of role based on centrality, although straightforward, might not adequately estimate the relative influence of a species on its community. 
-To overcome this issue, we require a framework that is equipped to account for the structure of the interactions in the community, but that also acknowledges the dynamics that determine species abundance and ultimately the state of the community.
+At first glance, this assumption makes sense because at the core of representing ecological communities as complex systems sits the idea that the abundance of any given species depends on its abundance, the abundance of the species it interacts with, the abundance of the species they interact with, and so on.
+More central species are better connected and hence should be more likely to affect the abundance of other species in the network. 
+However, the relationship between centrality and role is rather phenomenological, and recent studies have shown that definitions of role based on centrality, although straightforward, might not adequately estimate the relative influence of a species on its community.
+This has important consequences not only for the theoretical understanding of ecological communities but also for potential conservation applications. 
+An alternative, more mechanistically-grounded, approach to relate species to ecosystem functioning is needed.
 
-Among the various possibilities, *control theory* appears to be a strong candidate [@Isbell2013]. 
-Widely used in engineering to determine and supervise the behaviour of dynamical systems [@Motter2015], it is well equipped to deal with the many feedbacks present in ecological communities [@Liu2016].
-Furthermore, advances in this field have established a link between the structure of the network and the way nodes affect each other that is based on well-established advances in both dynamical and complex systems theory.
-As such, a priori assumptions about how particular node metrics, like centrality, are related to network functioning are not required
-Despite the coincidences between ecological and engineering systems, the concepts and approaches of control theory are not commonly applied in an ecological context. 
-This is, in part, because in contrast with ecology, research on the control of complex networks is generally more concerned with driving the state the system as a whole rather than the nodes that compose the network.
-At its fundamental level, control theory is concerned with determining whether a system is at all controllable, this is, whether it can be driven to a desired state or not. 
+Such an approach needs to account for the structure of the interactions in the community, just like centrality based methods, ideally without requiring a priori assumptions about how particular network metrics relate to changes in species abundance.
+Species abundances are also influenced by the dynamic relationships between nodes, and the mechanisms of self-regulation. 
+However, ecosystem dynamics can be modeled in numerous ways and empirical support to one or another is still ambiguous. 
+Therefore, the alternative approach should also acknowledge ecosystem dynamics without being overly dependent on the particular choices of how they are characterised.
+
+*Control theory* is a widely studied branch of engineering used to determine and supervise the behaviour of dynamical systems [@Motter2015]. 
+It is inherently designed to deal with system feedbacks and its application has been recently expanded to complex networks [@Liu2016]. 
+In correspondence with ecological questions, advances in this field have determined a link between the structure of the network and the way nodes affect each other. 
+Unlike ecological approaches, however, this link is based, not on a priori assumptions, but on well-established advances in both dynamical and complex systems theory. 
+Among the various possibilities, control theory appears to be a strong candidate to be used to define a species role for ecosystem functioning [@Isbell2013].
+
+Despite the numerous coincidences, the concepts and approaches of control theory are not yet commonly applied in an ecological context. 
+Possibly, this is in part because, in contrast with ecology, research on the control of complex networks is generally more concerned with the state of the system as a whole than the nodes that compose the network.
+At its fundamental level, control theory first determines whether a system is controllable or not, this is, it asks if a system can be driven to a desired state within a finite amount of time. 
+Nevertheless, it has been recently shown that asking for the controllability of a complex system is equivalent to asking whether there exists a non-trivial set of nodes with which is possible to control the state of the whole network.
+We note that this set of nodes is not unique, and that an examination of the possible sets of nodes provides a means to connect nodes with its ability to modify their system. 
 Our first contribution is to expand existing methods control theory to effectively link the *controllability* of a network with the role of particular nodes.
 
-After overcoming this first hurdle, we then apply the methods to an ecological problem and show how it can be used to gain insight into the role of species in an ecological network. 
+After overcoming this first hurdle, we can then apply the methods to an ecological problem and show how it can be used to gain insight into the role of species in an ecological network. 
 Specifically, we outline the approach using a set of ten pairs of uninvaded and invaded plant-pollinator communities. 
@@
 First, grounded in the difficulties usually involved with invasive-species eradication and ecosystem restoration [@Woodford2016], we ask whether invaded networks require a greater proportion of species to be managed to achieve the same level of control.
-Second, we ask—from a control theoretic perspective—wether there are differences among species in the role they play at driving the population of other members of the community and the factors related to these differences.
+Second, we ask—from a control theoretic perspective—whether there are differences among species in the role they play at driving the population of other members of the community and the factors related to these differences.
 Finally, we compare the proposed approach to current methods based on species centrality and show how these methods are indeed valuable but only paint a limited picture in regards to the "keystoness" of a species.
+
+# Methods
 

### 2018-04-19 publication/manuscript.Rmd
Read and use network metadata

@@
 
+```{r load-metadata}
+loadd(metadata)
+lop <- filter(metadata, study == "lopezaraiza") %>% mutate(size = n_pla + n_pol) %$% size %>% summary() 
+bar <- filter(metadata, study == "bartomeus") %>% mutate(size = n_pla + n_pol) %$% size %>% summary() 
+```
+
+We apply methods of control theory to ten paired pollination networks.
+Each network pair was composed of a community invaded by a plant and a community free of the invasive species. 
+Four pairs were obtained from natural or semi-natural vegetation communities in the city of Bristol, UK [@Lopezaraiza-Mikel2007]. 
+These networks are comprised of `r lop[1]`--`r lop[6]` species (mean `r round(lop[4])`), and non-invaded plots were obtained by experimentally removing all the flowers of the invasive species *Impatients grandulifera*.
+The other six pairs were obtained from lower diversity Mediterranean shrublands in Cap de Creus National Park, Spain [@Bartomeus2008].
+These networks are comprised of `r bar[1]`--`r bar[6]` species (mean `r round(bar[4])`); in contrast to the above, uninvaded communities were obtained from plots that had not yet been colonised by either of the invasive species *Carpobrotus affine acinaciformis* or *Opuntia stricta*.
+Supplementary Information S\@ref(S-empirical-networks)
+
 ```{r example_network, include = F}

### 2018-04-19 make_paper.R

@@ -15,6 +15,8 @@ library(tinytex)
 
 # required by paper or analysis
 library(latex2exp)
+library(readr)
+library(dplyr)
 library(igraph)
 library(ggplot2)
 
@@ -24,6 +26,10 @@ f <- list.files("./functions/", full.names = T) %>% lapply(source)
 # DEFINE PLAN ----------------------------------------------------------------
 
 ilustrations <- drake_plan(example_net = generate_example_network())
+read_data_plan <- drake_plan(
+	metadata = read_metadata('data/ntw_info.csv'),
+	strings_in_dots = 'filenames'
+)
 
 reporting <- drake_plan(
 	# 'publication/supp_info.tex' = render('publication/supporting_information.Rmd', quiet = TRUE),
@@ -37,7 +43,7 @@ reporting <- drake_plan(
 # MAKE --------------------------------------------------------------------
 
 # set up plan
-project_plan <- rbind(ilustrations, reporting)
+project_plan <- rbind(read_data_plan, reporting_plan)
 project_config <- drake_config(project_plan)
 vis_drake_graph(project_config, split_columns = T, targets_only = T)
 

### 2018-04-19 make_paper.R
Supplementary information needs to be compiled

@@ -19,9 +19,11 @@ library(readr)
 library(dplyr)
 library(igraph)
 library(ggplot2)
+library(latex2exp)
 
 # load functions
 f <- list.files("./functions/", full.names = T) %>% lapply(source)
+f <- list.files("functions", full.names = T) %>% lapply(source)
 
 # DEFINE PLAN ----------------------------------------------------------------
 
@@ -34,6 +36,9 @@ read_data_plan <- drake_plan(
 reporting <- drake_plan(
 	# 'publication/supp_info.tex' = render('publication/supporting_information.Rmd', quiet = TRUE),
 	# 'publication/supp_info.pdf' = latexmk('publication/supp_info.tex', clean = FALSE),
+reporting_plan <- drake_plan(
+	'publication/supp-info.tex' = render('publication/supp-info.Rmd', quiet = TRUE),
+	'publication/supp-info.pdf' = latexmk('publication/supp-info.tex', clean = FALSE),
 	'publication/manuscript.tex' = render('publication/manuscript.Rmd', quiet = TRUE),
 	'publication/manuscript.pdf' = latexmk('publication/manuscript.tex', clean = FALSE),
 	file_targets = TRUE

### 2018-04-19 publication/manuscript.Rmd
Enable cross referencing between manuscript and supplementary info

@@
 - \usepackage{lineno}
+- \usepackage{xr}
+- \externaldocument[S-]{supp-info}
 documentclass: artikel1

### 2018-04-19 publication/manuscript.Rmd
Add default parameters for R chunks

@@
 **Author for correspondence:** Daniel Stouffer (daniel.stouffer@canterbury.ac.nz) - +64 3 364 2729 - Centre for Integrative Ecology, School of Biological Sciences, University of Canterbury, Private Bag 4800, Christchurch 8140, New Zealand
+
+```{r setup, include=FALSE}
+knitr::opts_chunk$set(echo = FALSE, message = FALSE, 
+                      warning = FALSE)
+options(xtable.comment = FALSE, 
+        xtable.caption.placement = 'bottom',
+        xtable.size = 'small',
+        booktabs = TRUE)
+```
 
@@
 
-```{r example_network, include = F}
+```{r example-network, include = F, eval = F}
 loadd(example_net)

### 2018-04-20 publication/manuscript.Rmd
DBS comments on the revised into

--- 2018-04-19 publication/manuscript.Rmd
@@
 ---
-title: "Ecological network control"
+title: "Ecological network control" <!-- DBS really doesn't like the new title... -->
 classoption: a4paper
@@
 
+<!-- I think there is a sentence missing before or after the following sentence.
+If before, it's about the desire to understand roles; if after, it's about how species have many types of roles, and one of particular interest is the role in "functioning".
+That said, I'm not certain that 'functioning' is the best catch-all for what we explore here....
+-->
 Within community ecology, a complex-systems approach has led to the development of analytical and simulation tools with which to understand the role of species embedded in a network of interactions [@Bascompte2009; @Stouffer2012].
-A particularly relevant dimension of a species role for ecosystem functioning is that which relates to its ability to alter the abundance of other species in the community. 
-This ability is often referred as species importance or "keystoness". 
-A significant proportion of the network tools used to estimate a species ability to modify its community is based on the assumption that there is a link between a species centrality and its importance.
+A particularly relevant dimension of any species' role is its ability to alter the abundance of other species in the community, since this impacts ecosystem functioning, XXX, and YYY. 
+This ability is often referred as species importance or "keystoneness". 
+A significant proportion of the network tools used to estimate species roles in this context relies on the assumption that there is a link between a species centrality---DEFINE CENTRALITY VERBALLY---and its importance.
+<!-- Simplify the beginning of the following sentence as it's more complex than it need be, no pun intended. -->
 At first glance, this assumption makes sense because at the core of representing ecological communities as complex systems sits the idea that the abundance of any given species depends on its abundance, the abundance of the species it interacts with, the abundance of the species they interact with, and so on.
-More central species are better connected and hence should be more likely to affect the abundance of other species in the network. 
-However, the relationship between centrality and role is rather phenomenological, and recent studies have shown that definitions of role based on centrality, although straightforward, might not adequately estimate the relative influence of a species on its community.
+More central species, by definition, are better connected and hence should be more likely to affect the abundance of other species in the network.
+
+Though conceptually intuitive, the relationship between centrality and role is largely phenomenological, and recent studies have shown that definitions of role based on centrality might not adequately estimate the relative influence of a species on its community.
+<!-- Seems a bit weak.
+Would an example help?
+-->
 This has important consequences not only for the theoretical understanding of ecological communities but also for potential conservation applications.
-An alternative, more mechanistically-grounded, approach to relate species to ecosystem functioning is needed.
+<!-- Again, concrete examples help ground statements like this.
+-->
+As a results, community ecology could benefit considerably from an alternative, more mechanistically-grounded, approach to relate species to ecosystem functioning. <!-- are we sure functioning? -->
+Ideally, such an approach should account for the structure of the interactions in the community, just like centrality based methods, and without requiring a priori assumptions about how particular network metrics relate to changes in species abundance.
+This is because species abundances are also influenced by the dynamic relationships between nodes, and the mechanisms of self-regulation. 
+However, community and population dynamics can be modeled in innumerable ways, and empirical support for one versus another is often still ambiguous.
+Therefore, the ideal alternative approach should also acknowledge ecosystem dynamics without being overly dependent on the particular choices of how they are characterised.
 
-Such an approach needs to account for the structure of the interactions in the community, just like centrality based methods, ideally without requiring a priori assumptions about how particular network metrics relate to changes in species abundance.
-Species abundances are also influenced by the dynamic relationships between nodes, and the mechanisms of self-regulation. 
-However, ecosystem dynamics can be modeled in numerous ways and empirical support to one or another is still ambiguous. 
-Therefore, the alternative approach should also acknowledge ecosystem dynamics without being overly dependent on the particular choices of how they are characterised.
+Among the various possibilities, *control theory* appears to be a strong candidate to be used to define a species role for ecosystem functioning [@Isbell2013]. 
+*Control theory* is a widely studied branch of engineering used to determine and supervise the behaviour of dynamical systems [@Motter2015]. 
+It is inherently designed to deal with system feedbacks and its application has recently been expanded to complex networks [@Liu2016]. 
+In correspondence with ecological questions, advances in this field have established a clear link between the structure of the network and the way nodes affect each other. 
+Unlike ecological approaches, however, this link is not based on a priori assumptions but instead on well-established advances in both dynamical and complex-systems theory.
+<!-- Are we shooting ourselves in the foot since this isn't entirely true?
+That is, see comments from ELE about linearity and otherwise....
+-->
 
-*Control theory* is a widely studied branch of engineering used to determine and supervise the behaviour of dynamical systems [@Motter2015]. 
-It is inherently designed to deal with system feedbacks and its application has been recently expanded to complex networks [@Liu2016]. 
-In correspondence with ecological questions, advances in this field have determined a link between the structure of the network and the way nodes affect each other. 
-Unlike ecological approaches, however, this link is based, not on a priori assumptions, but on well-established advances in both dynamical and complex systems theory. 
-Among the various possibilities, control theory appears to be a strong candidate to be used to define a species role for ecosystem functioning [@Isbell2013].
-
-Despite the numerous coincidences, the concepts and approaches of control theory are not yet commonly applied in an ecological context. 
+Despite the apparent overlap, the concepts and approaches of control theory are not yet commonly applied in an ecological context. 
 Possibly, this is in part because, in contrast with ecology, research on the control of complex networks is generally more concerned with the state of the system as a whole than the nodes that compose the network.
-At its fundamental level, control theory first determines whether a system is controllable or not, this is, it asks if a system can be driven to a desired state within a finite amount of time. 
+<!-- Shift the "in contrast to ecology" into it's own sentence here?
+-->
+At its fundamental level, control theory first determines whether a system is controllable or not; that is, it asks if a system can be driven to a desired state within a finite amount of time. 
 Nevertheless, it has been recently shown that asking for the controllability of a complex system is equivalent to asking whether there exists a non-trivial set of nodes with which is possible to control the state of the whole network.
-We note that this set of nodes is not unique, and that an examination of the possible sets of nodes provides a means to connect nodes with its ability to modify their system. 
+<!-- This sentence needs simplification.
+-->
+Notably, this set of nodes is not always unique for a given network.
+This implies that an examination of the distinct sets of nodes provides a means to connect nodes with its *general* ability to modify the system to which they belong.
 Our first contribution is to expand existing methods control theory to effectively link the *controllability* of a network with the role of particular nodes.
+<!-- See comment below at very end of intro; I really don't think this sentence fits here....
+-->
 
 After overcoming this first hurdle, we can then apply the methods to an ecological problem and show how it can be used to gain insight into the role of species in an ecological network. 
+<!-- I think the offending sentence fits here better with a corresponding rewording if the first sentence of this paragraph which will below a lot from the sentence just below this comment of mine...
+-->
 Specifically, we outline the approach using a set of ten pairs of uninvaded and invaded plant-pollinator communities. 
-We use invaded communities because there is strong empirical evidence showing that invasive species play an important role shaping the abundances of other species.
-Certainly so in the chosen networks [@Lopezaraiza-Mikel2007; @Bartomeus2008].
-Hence, this choice offers an opportunity to contrast theoretical observations with empirical evidence. 
+We use invaded communities because there is strong empirical evidence showing that invasive species play an important role shaping the abundances of other species, and particularly in these 10 (???) networks [@Lopezaraiza-Mikel2007; @Bartomeus2008].
+This choice thus offers us an opportunity to explicitly contrast theoretical observations with empirical evidence. <!-- I love this point. You're peering into my soul! -->
 First, grounded in the difficulties usually involved with invasive-species eradication and ecosystem restoration [@Woodford2016], we ask whether invaded networks require a greater proportion of species to be managed to achieve the same level of control.
-Second, we ask—from a control theoretic perspective—whether there are differences among species in the role they play at driving the population of other members of the community and the factors related to these differences.
-Finally, we compare the proposed approach to current methods based on species centrality and show how these methods are indeed valuable but only paint a limited picture in regards to the "keystoness" of a species.
+<!-- I'd remove the grounded in....
+stuff, but that's just me.
+-->
+Second, we ask—from a control-theoretic perspective—whether there are key differences between species in the role they play at driving the population of other members of the community and identify the ecological factors related to these differences.
+Finally, we compare the proposed approach to current methods based on species centrality and show how these methods are indeed valuable but only paint a limited picture in regards to the "keystoneness" of a species.
+
+<!-- I don't really like how the "what we do" parts of the intro are split across two paragraphs. It feels clunky... -->
 
 # Methods
-
-```{r load-metadata}
-loadd(metadata)
-lop <- filter(metadata, study == "lopezaraiza") %>% mutate(size = n_pla + n_pol) %$% size %>% summary() 
-bar <- filter(metadata, study == "bartomeus") %>% mutate(size = n_pla + n_pol) %$% size %>% summary() 
-```
-
-We apply methods of control theory to ten paired pollination networks.
-Each network pair was composed of a community invaded by a plant and a community free of the invasive species. 
-Four pairs were obtained from natural or semi-natural vegetation communities in the city of Bristol, UK [@Lopezaraiza-Mikel2007]. 
-These networks are comprised of `r lop[1]`--`r lop[6]` species (mean `r round(lop[4])`), and non-invaded plots were obtained by experimentally removing all the flowers of the invasive species *Impatients grandulifera*.
-The other six pairs were obtained from lower diversity Mediterranean shrublands in Cap de Creus National Park, Spain [@Bartomeus2008].
-These networks are comprised of `r bar[1]`--`r bar[6]` species (mean `r round(bar[4])`); in contrast to the above, uninvaded communities were obtained from plots that had not yet been colonised by either of the invasive species *Carpobrotus affine acinaciformis* or *Opuntia stricta*.
-Supplementary Information S\@ref(S-empirical-networks)
 

### 2018-04-20 publication/manuscript.Rmd

@@
 
-```{r example_network, include = F}
+```{r load-metadata}
+loadd(metadata)
+lop <- filter(metadata, study == "lopezaraiza") %>% mutate(size = n_pla + n_pol) %$% size %>% summary() 
+bar <- filter(metadata, study == "bartomeus") %>% mutate(size = n_pla + n_pol) %$% size %>% summary() 
+```
+
+We apply methods of control theory to ten paired pollination networks.
+Each network pair was composed of a community invaded by a plant and a community free of the invasive species. 
+Four pairs were obtained from natural or semi-natural vegetation communities in the city of Bristol, UK [@Lopezaraiza-Mikel2007]. 
+These networks are comprised of `r lop[1]`--`r lop[6]` species (mean `r round(lop[4])`), and non-invaded plots were obtained by experimentally removing all the flowers of the invasive species *Impatients grandulifera*.
+The other six pairs were obtained from lower diversity Mediterranean shrublands in Cap de Creus National Park, Spain [@Bartomeus2008].
+These networks are comprised of `r bar[1]`--`r bar[6]` species (mean `r round(bar[4])`); in contrast to the above, uninvaded communities were obtained from plots that had not yet been colonised by either of the invasive species *Carpobrotus affine acinaciformis* or *Opuntia stricta*.
+Supplementary Information S\@ref(S-empirical-networks)
+
+```{r example-network, include = F, eval = F}
 loadd(example_net)

### 2018-04-28 paper/manuscript.Rmd
Ad syntheis heading to abstract
Add manuscript and supplementary information

--- 2017-10-02 paper/manuscript.Rmd
@@
 ---
-title: "Quantifying the manageability of pollination networks in an invasion context"
+title: "Working title: Ecological network control"
 classoption: a4paper
@@
 output: 
-  pdf_document:
-    fig_crop: no
-  html_document: default
-  word_document: default
+  bookdown::pdf_document2: 
+    keep_tex: yes
+    number_sections: false
+toc: false
 header-includes:
+- \usepackage{geometry}
+- \geometry{right=3in,marginparwidth=2.5in}
 - \usepackage{setspace}
@@
 \linenumbers
-
-```{r libraries, echo = F, include = F}
-library(igraph)
-library(magrittr)
-library(dplyr)
-library(latex2exp)
-library(ggplot2)
-library(glmulti)
-library(lme4)
-library(grid)
-
-"../code/functions" %>% 
-	list.files(full.names = T) %>%
-	plyr::l_ply(source)
-
-"../code/plotting_functions" %>% 
-	list.files(full.names = T) %>%
-	plyr::l_ply(source)
-
-```
-
-```{r load data, include = F}
-net <- "../data/processed/networks" %>%
-	read_networks()
-meta <- readr::read_csv("../data/ntw_info.csv") %>% dplyr::tbl_df() %>%
-	dplyr::rename(count = method)
-n_driver <- readRDS("../data/processed/n_driver.rds")
-manag_models <- readRDS("../data/processed/models_manageability.rds")
-src_bi_w <- readRDS("../data/processed/manageability_bi_vs_weight.rds")
-r_w <- readRDS("../data/processed/random_weights.rds") %>% dplyr::tbl_df() %>%
-  dplyr::rename_("net_name" = ".id")
-r_d <- readRDS("../data/processed/random_directions.rds") %>% dplyr::tbl_df() %>%
-  dplyr::rename_("net_name" = ".id")
-
-prop <- expand.grid(c("asymmetry", "max_dep"), 
-                    c("scaled_FALSE", "scaled_TRUE")) %>% plyr::alply(1)
-driver <- c("../data/processed/matching_frequency") %>% 
-  list.files(full.names = T) %>%
-  lapply(list.files, full.names = T) %>% 
-  unlist() %>% 
-  lapply(read_allRDS)
-driver <- mapply(function(x, y){
-  attr(x, "type") <- as.character(y[,1])
-  attr(x, "scaled") <- stringr::str_split(as.character(y[,2]), "_") %>% unlist() %>% extract(2) %>% as.logical()
-  return(x)
-}, driver, prop)
-driver_bi <- "../data/processed/matching_frequency_bi" %>% 
-  read_allRDS()
-mod <- readRDS("../data/processed/detailed_species_models.rds")
-mo <- readRDS("../data/processed/detailed_species_models_data.rds")
-```
-
-```{r plot theme, echo = FALSE, warning = F, message = F}
-fer_theme <- theme_bw() +
-	theme(text = element_text(family = "Helvetica"),
-	      title = element_text(size = 7, hjust = 0),
-	      legend.title = element_text(size = 8),
-	      legend.text = element_text(size = 7),
-				axis.text = element_text(size = 7),
-				axis.title = element_text(size = 8, hjust = 0.5), 
-				strip.text = element_text(size = 8, hjust = 0), 
-				strip.background = element_blank(),
-				plot.margin = grid::unit(c(5, 0.5, 2, 0), "mm"),
-				panel.grid = element_blank())
-```
-
-```{r example networks, include = F, message = F, warning = F, }
-
-sp_names_fancy <- c(TeX("$p_1$"), TeX("$p_2$"), TeX("$p_3$"), TeX("$a_1$"), TeX("$a_2$"))
-sp_names_fancy_b <- c(TeX("$\\mathbf{p_1}$"), TeX("$\\mathbf{p_2}$"), TeX("$\\mathbf{p_3}$"), TeX("$\\mathbf{a_1}$"), TeX("$\\mathbf{a_2}$"))
-
-sp_names <- c("p1", "p2", "p3", "a1", "a2")
-
-adj_matrix <- c(0,0,0,1,0,
-								0,0,0,2,5,
-								0,0,0,0,0,
-								0,0,1,0,0,
-								0,0,1,0,0) %>%
-	matrix(nrow = 5, byrow = T)
-
-example_net <- adj_matrix %>% 
-	graph_from_adjacency_matrix(mode = "undirected", weighted = TRUE) 
-igraph::V(example_net)$type <- c(F, F, F, T, T)
-igraph::V(example_net)$name <- sp_names
-
-base_net <- example_net
-bi_net <- example_net %>%
-	keep_largest_component() %>%
-	bipartite_digraph(type = "z-bi", weight.type = "asymetry") 
-as_net <- example_net %>%
-	keep_largest_component() %>%
-	bipartite_digraph(type = "weight", weight.type = "asymmetry")
-
-fam <- "Helvetica"
-
-# layout is based on the bidirectional network
-set.seed(1)
-bi_net_uw <- bi_net
-E(bi_net_uw)$weight <- 1
-lay <- bi_net_uw %>%
-	layout_nicely()
-v_c <- "white"
-l_c <- "black"
-l_s <- 0.9
-ma <- c(0,0,0,0)
-label_pos_x <- -1
-label_pos_y <- 1
-
-pal <- RColorBrewer::brewer.pal(5, "PuOr")
-```
 
@@
 
-\newpage
-
-# Abstract
-
-1.
-Despite important advances in network ecology, the link between the structure of an interaction network and management or conservation is still tenuous.
-Perhaps in part because of a lack of theoretical framework, efforts to strengthen this link have been mainly focused on whole-network properties instead of underlying mechanisms.
-2.
-Here, we leverage recent advances in control theory to develop an approach to assess the "manageability" of ecological networks.
-We then illustrate its application using ten pairs of uninvaded and invaded plant-pollinator communities.
-We also characterise species' suitability for inclusion in management interventions by exploring the entire space of alternative control strategies.
-Specifically, we measure the extent to which species (i) are necessary to steer the state of the community and (ii) are able to affect the abundance of other species.
-3.
-We found that the networks' manageability is most strongly determined by the ratio of plant to pollinator richness, which in turn constrains the networks' degree distribution.
-We also found that invasive plants have a dominant position in every invaded community and that this dominance is underpinned by high asymmetries in the dependences of their interaction partners.
-4. Our results provide novel insight into the design of ecologically-informed management interventions and lay the foundation for further work on the control of ecological networks.
-
-**Keywords:** Network control theory, ecological networks, species importance, driver species, mutualism, management interventions
+```{r setup, include=FALSE}
+knitr::opts_chunk$set(echo = FALSE, message = FALSE, 
+                      warning = FALSE)
+options(xtable.comment = FALSE, 
+        xtable.caption.placement = 'bottom',
+        xtable.size = 'small',
+        booktabs = TRUE)
+```
 
@@
 
-In a complex system, the whole is often greater than the sum of its parts [@Montoya2006].
-Within community ecology, a complex-systems approach has led to the development of analytical and simulation tools with which to understand, for example, the role of species embedded in a network of interactions [@Bascompte2009; @Stouffer2012].
-The inherent complexity of nature, however, has regularly hindered—or at least complicated—our ability to find management solutions to many problems ecological communities face. 
-To overcome this obstacle, we require a framework that allows us to explain, predict, and manage ecological communities, particularly when they are confronted with perturbations [@Green2005].
-Ideally, such a framework is equipped to account for their complex structure and the dynamics that determine the species abundances and the state of the community.
+A major goal in ecological research is to understand the role that species play in the biotic environment.
+Within community ecology, a complex-systems has led to the development of a variety analytical and simulation tools with which to understand the role of the role of species embedded in a network of interactions [@bascompte_assembly_2009; @stouffer_evolutionary_2012].
+A particularly relevant dimension of any species' role is its ability to alter the abundance of other species in the community, since this impacts ecosystem function and biodiversity and might have knock down effects on other processes and services.
+This ability is often referred as "keystoneness". 
+A significant proportion of the network tools used to estimate species roles in this context relies on the assumption that there is a link between a species centrality—a relative ranking of its importance that stems from social network research—and its ability to alter other species' abundance.
+At first glance, this assumption makes sense. 
+At the core of representing ecological communities as networks sits the idea that the abundance of a species also depends on the abundance of its neighbours (the species it interacts with) and, by extension, the abundance of its neighbours neighbours', and so on.
+More central species, by definition, are better connected and hence should be more likely to affect the abundance of other species in the network.
 
-Among the various possibilities, *control theory* appears to be a strong candidate [@Isbell2013].
-Widely used in engineering to determine and supervise the behaviour of dynamical systems [@Motter2015], it is well equipped to deal with the many feedbacks present in ecological communities [@Liu2016].
-Research in this area has established a strong link between the structure of complex networks and their *controllability*—the relative ability to manipulate network components to drive the system to a desired state [@Liu2011; @Cornelius2013; @Ruths2014].
-These advances suggest that it is in principle possible to alter a whole ecological community's composition by modifying the abundances of only a few species.
-Applications of control theory to ecological networks can also take into account the extent to which changes in the abundances of one species may ripple through the community [@Cornelius2013].
-Therefore, control theory could also be harnessed to help identify which species are most relevant from a structural and dynamic perspective.
+Though conceptually intuitive, the relationship between centrality and keystoness is largely phenomenological. 
+On one hand, there is more than a dozen indices of centrality used in ecology. 
+Chosing a particular metric can be a difficult task, especially because to date there are not clear methods to determine the suitability of an index to a particular application. 
+Furthermore, recent studies have shown that definitions of keystoness based on centrality might not adequately predict the cascading extintions keystone species are ususally associated to. 
+As a result, community ecology could benefit from an alternative, more mechanistically-grounded, approach to understand how species affect each other abbundance. 
+Species abundances are also influenced by the dynamic relationships between nodes, and the mechanisms of self-regulation, however, community and population dynamics can be modeled in innumerable ways, and empirical support for one versus another is often still ambiguous.
+The alternative approach should acknowledge ecosystem dynamics, but without being overly dependent on the particular choices of how they are characterised.
 
-This information is valuable not only for basic ecology, but it might be also relevant to address more applied management and conservation challenges. 
-This is particularly true in the context of biotic invasions, where identifying key players in the community is a prerequisite to informed attempts to alter the state of invaded ecosystems and maintain the state of uninvaded ones.
-Despite recent advances in network theory, practical challenges to the conservation of interaction networks persist [@Tylianakis2010], and the link between the structure of complex networks and our ability to manage and conserve them is still ambiguous [@Bluthgen2010; @Kaiser-Bunbury2015].
-To complicate things further, biotic invasions can induce dramatic changes in the patterns of interactions that determine the structure of ecological networks [@Tylianakis2008; @Ehrenfeld2010a], in particular pollination [@Olesen2002; @Aizen2008; @Bartomeus2008; @Vila2009; @Traveset2013].
-Understanding how the differences in network structure before and after invasion impact our ability to manage the communities is thus a double challenge, but it is also the critical first step towards a fully informed recovery.
-Despite the apparent overlap, the control-theoretic perspective has not been adopted in an invasion context.
+Among the various possibilities, *control theory* appears to be a strong candidate [@isbell_human_2013]. 
+Control theory is a widely studied branch of engineering used to determine and supervise the behaviour of dynamical systems [@motter_networkcontrology_2015]. 
+It is inherently designed to deal with system feedbacks and its application has recently been expanded to complex networks [@liu_control_2016]. 
+In correspondence with ecological questions, advances in this field have established a clear link between the structure of the network and the way nodes affect each other. 
+Unlike centrality indices, however, this link is not based on a priori assumptions between network metrics and keystoness, instead on well-established advances in both dynamical and complex-systems theory <!--STOUFFER: Are we shooting ourselves in the foot since this isn't entirely true?
+That is, see comments from ELE about linearity and otherwise.
+CAGUA: How about this modified phrasing?-->.
 
-To bridge this gap, we outline an approach to apply control theory in an ecological context and implement it using empirical data.
-Specifically, we use a set of ten pairs of uninvaded and invaded plant-pollinator communities to investigate the link between invasion, network structure and ecological management. 
-While doing so, we focus on two particular questions.
-First, grounded in the difficulties usually involved with invasive-species eradication and ecosystem restoration [@Woodford2016], we ask whether invaded networks have lower levels of "manageability" than their uninvaded counterparts; that is, whether they require a greater proportion of species to be managed to achieve the same level of control.
-Second, we ask whether some species are more important than others at driving the population dynamics of the community and which factors determine this importance.
+Despite the apparent overlap, the concepts and approaches of control theory are not yet commonly applied in an ecological context. 
+Possibly, this is in part because research on the control of complex networks is generally more concerned with the state of the system as a whole. 
+This is in contrast with the ecological role concept, where the focus is on the nodes that compose the network.
+At its fundamental level, control theory first determines whether a system is controllable or not; that is, it asks if a system can be driven to a desired state within a finite amount of time. 
+Although the controllability of a network is a whole-system property, it has been recently shown that asking for the controllability of a complex-system is equivalent to finding a particular set of nodes.
+A set with which is possible to control the state of the whole network. 
+Notably, this set of nodes is not always unique for a given network.
+This implies that an examination of the distinct sets provides a means to connect nodes with its *general* ability to modify the system to which they belong.
 
-# Theoretical framework
-
-At the core of representing ecological communities as complex systems sits the idea that the state of any given node depends on its state, the state of the nodes it interacts with, the state of the nodes they interact with, and so on.
-These dependencies are given by the structure of the interactions, the dynamic relationships between nodes, and the mechanisms of self-regulation. 
-This representation has been very useful for our understanding of ecological communities and might be advantageous for a more formal approach to ecological management based on control theory.
-
-The overall objective of control theory is to be able to steer a system from one state to another in finite time. 
-However, in complex systems like ecological communities, the large number of nodes and interactions as well as their non-linear dynamics render its control extremely challenging.
-On one theoretical extreme, for instance, any ecological community could be fully controlled if we control the state of every species independently. 
-On another, the mechanisms of self-regulation and the multiple feedback cycles found in ecological communities mean it is also theoretically possible to control the whole community by directly modifying the state of just a *single* species [@Cowan2012; @Markovsky2013].
-Although mathematically correct, neither of these options are practical in real-world applications: the first because it is infeasible to design and implement interventions that modify the abundance of every single species in a community, and the second because the control signal might require unreasonably large amounts of time, energy, or unattainable rapid changes on the state [@Yan2012; @Motter2015].
-Here we explore an intermediate point between these two trivial solutions.
-
-In particular, we leverage the principle of species interdependence to find an intermediate set of *driver nodes* to control the network [@Liu2016]. 
-When we focus on net interspecific effects, it is possible to identify a minimum number of nodes the control of which can theoretically drive the state of every other node in the network to a desired configuration.
-Conveniently the information necessary to determine this minimum number of driver nodes *D* is fully contained in the network structure [@Kalman1963; @Liu2011; @Motter2015]. 
-Such a system can be described by $\frac{dx}{dt} = \mathbf{A}x + \mathbf{B}u(t)$, where the change of its state over time ($\frac{dx}{dt}$) depends on its current state *x* (for example, the species' abundances), an external time-varying input *u(t)* (the control signal), and two matrices *A* and *B*, which encode information about the network structure and how the species respond to the external input, respectively.
-If *S* is the number of species in the community, the matrix **A** has size $S \times S$ whereas the matrix **B** has size $S \times D$.
-
-The goal of structural controllability, which we employ here, is to use the information contained in **A** to generate a supportable estimate of **B** (and by extension *D*).
-This focus allows us to gain insight of the inherent controllability of a network, and the roles of the species that compose it, without being overly dependent on the particular choices of how the system dynamics are modelled or characterised.
-The trade-off of our approach is that, because of the assumption of linearity, structural controllability alone does not allow us to fully design the time-varying control signal *u(t)* that can drive the system from one particular equilibrium to another.
-Nevertheless, the lessons gained when assuming linearity---at both the network and the species level---are a prerequisite for eventually understanding nonlinear control [@Liu2011; @Liu2016].
-
-## Manageability
-
-The number of driver nodes *D* provides a structural indication of how difficult a network's control might be.
-This is because systems that require a large number of external input signals are intuitively more difficult or costly to control.
-In an ecological context, external inputs that modify the state of a node can be thought of as management interventions.
-Therefore, the density of driver nodes $n_D = \frac{D}{S}$, where *S* is the total number of species in the community, is a measure of the extent to which network structure can be harnessed for network control.
-For instance, a hypothetical "network" in which species do not interact would require direct interventions for every single species to achieve full control, whereas a linear food chain would require just one species to be directly controlled to harness cascading effects through its trophic levels.
-From this perspective, it is possible to use *n~D~* as an index of the manageability of an ecological community, understood in the context of how difficult is to modify the abundances of species in the community using external interventions—a common theme in ecosystem management, conservation, and restoration.
-
-It has been recently shown that calculating *D* is equivalent to finding a maximum matching in the network [@Liu2011].
-In a directed network, a *matching* consists of a subset of links in which no two of them share a common starting or ending node (Figure 1, Supporting Information S1).
-A given matching has *maximal cardinality* if the number of matched links (also referred to as the *matching size*) is the largest possible.
-A maximal cardinality matching is then called a *maximum matching* if the sum of the weights of the matched links (also referred to as *matching weight*) is again the largest possible [@West2001].
-
-Once we have the subset of links that constitute a matching, we can also classify the nodes in the network based on that matching (Figure 1).
-A node is called *matched* if it is at the end of a matched link and *unmatched* otherwise. 
-A node is also called *superior* if it is at the start of a matched link.
-Note that a node cannot be superior if it has no outgoing links.
-Notably, these node categories are what helps us to link a maximum matching back to the concept of network controllability, as follows.
-Unmatched nodes are the *driver nodes* *D* because they have no superior in the network and must be directly controlled by an external input [@Liu2011].
-Each matched node, on the other hand, can be controlled by its superior.
-
-```{r figure 1, echo = F, message = F, warning = F, fig.width = 6.2, fig.height = 1.9, results= "hide", fig.pos = "t", fig.cap = "**Matchings of a simple network**.
-(a) We start with a network in which the direction of the links indicates the potential direction of control; for example a link from *a~1~* to *p~1~* indicates that the state of *p~1~* is influenced by the state of *a~1~*.
-The numbers indicate the weight of each link.
-(b & c) This network has two maximal cardinality matchings; that is, two configurations in which it would be possible to exert full control of the network via external input signals to a minimal set of nodes.
-In both cases, the three matched links (purple arrows) represent the control paths through the network and provide an indication of the matched nodes (purple), which are controlled by superior nodes within the network (circular nodes).
-Unmatched nodes (orange) are called driver nodes because full network control requires external signals to be applied to them.
-Out of the two maximal cardinality matchings only one (c) has maximum weight and therefore is also a maximum matching.
-Further examples can be found in Supporting Information S1."}
-layout(matrix(c(1, 1, 2, 4, 3, 4), 2, 3),
-  	heights=c(8,2))
-par( mar=c(0,0,0,0))
-
-as_net %>% 
-	plot(layout = lay, 
-			 vertex.color = v_c, 
-			 vertex.size = 35,
-			 vertex.label = sp_names_fancy,
-			 vertex.label.family = fam,
-			 vertex.label.color = l_c,
-			 edge.label = round(E(.)$weight,1), 
-			 edge.label.family = fam,
-			 edge.label.color = l_c,
-			 edge.label.cex = l_s,
-			 edge.curved = F,
-			 edge.arrow.size = 0.5,
-			 margin = ma)
-
-text(label_pos_x, label_pos_y, "(a)", adj = c(0,0), font = 2)
-
-as_mat <- as_net %>%
-	digraph_bipartite() %>% 
-	max_bipartite_match()
-
-as_all_mat <- as_net %>%
-	digraph_bipartite() %>%
-	igraph::make_line_graph() %>%
-	igraph::complementer() %>% 
-	igraph::max_cliques(min = as_mat$matching_size) %>%
-	rev()
-
-text_pos_x <- 0.5
-text_pos_y <- -0.7
-
-base_as_net <- as_net
-E(as_net)$weight <- round(E(as_net)$weight, 1)
-
-1:length(as_all_mat) %>%
-	plyr::l_ply(function(x){
-
-		E(as_net)$matched <- 1
-		E(as_net)$matched[as_all_mat[[x]]] <- 5
-
-		E(as_net)$matched_width <- 1
-		E(as_net)$matched_width[as_all_mat[[x]]] <- 1.5
-
-		igraph::V(as_net)$matched <- 1
-		igraph::V(as_net)$matched[igraph::V(as_net)$name %in%
-																ends(as_net, as_all_mat[[x]])[, 2]] <- 5
-
-		igraph::V(as_net)$matched_fill <- 2
-		igraph::V(as_net)$matched_fill[igraph::V(as_net)$name %in%
-																ends(as_net, as_all_mat[[x]])[, 2]] <- 4
-
-		igraph::V(as_net)$superior <- 1
-		igraph::V(as_net)$superior[igraph::V(as_net)$name %in%
-																ends(as_net, as_all_mat[[x]])[, 1]] <- 2
-
-		igraph::V(as_net)$sup_shape <- "square"
-		igraph::V(as_net)$sup_shape[igraph::V(as_net)$name %in%
-																ends(as_net, as_all_mat[[x]])[, 1]] <- "circle"
-
-		names_fancy <- sp_names_fancy
-		# names_fancy[igraph::V(as_net)$name %in%
-		# 														ends(as_net, as_all_mat[[x]])[, 1]] <-
-		# 	sp_names_fancy_b[igraph::V(as_net)$name %in%
-		# 														ends(as_net, as_all_mat[[x]])[, 1]]
-
-		matching_weight <- sum(E(as_net)$weight[as_all_mat[[x]]])
-
-		as_net %>% 
-			plot(layout = lay, 
-					 # vertex.size = igraph::V(.)$superior * 10 + 20,
-					 vertex.size = 30,
-					 vertex.color = pal[igraph::V(.)$matched_fill],
-					 vertex.shape = igraph::V(.)$sup_shape,
-					 vertex.label = names_fancy,
-					 vertex.label.family = fam,
-					 vertex.label.color = l_c,
-					 vertex.label.cex = 1,
-					 # vertex.shape = igraph::V(.)$vertex.shape,
-					 vertex.frame.color = pal[igraph::V(.)$matched],
-					 edge.color = pal[E(.)$matched],
-					 edge.label = NA, 
-					 edge.width = E(.)$matched_width,
-					 edge.label.family = fam,
-					 edge.label.color = igraph::E(.)$matched,
-					 edge.label.cex = l_s,
-					 edge.curved = F,
-					 edge.arrow.size = 0.5,
-					 margin = ma) %>% 
-			print()
-
-		igraph::V(as_net)$name <- sp_names
-
-		text(label_pos_x, label_pos_y, paste0("(",letters[1+x], ")"), adj = c(0,0), font = 2)
-		text(text_pos_x, text_pos_y, cex = 0.9,
-				 paste0("D = ", length(igraph::V(as_net)) - as_mat$matching_size, "\n",
-				 			 "matching size: ", as_mat$matching_size, "\n",
-				 			 "matching weight: ", round(matching_weight, 1)))
-})
-
-as_net <- base_as_net
-
-plot.new()
-legend(0.20, 0.8, legend = c("unmatched link", "matched link"), horiz = TRUE,
-			 lty = 1, 
-			 col = pal[c(1, 5)],
-			 lwd = 2, cex = 0.9, xjust=0.5, yjust=0.8, bty = "n")
-
-legend(0.835, 0.8, legend = c("unmatched node (driver)", "matched node"), horiz = TRUE,
-			 pch = 21, 
-			 pt.bg = pal[c(2, 4)],
-			 col = pal[c(1,5)],
-			 pt.cex = 2,
-			 cex = 0.9, xjust=0.5, yjust=0.8, bty = "n")
-
-legend(0.5, 0.35, legend = c("superior node", "non-superior node"), horiz = TRUE,
-			 pch = c(21, 22), 
-			 # pt.bg = pal[c(2, 4)],
-			 pt.cex = 2,
-			 cex = 0.9, xjust=0.5, yjust=0.8, bty = "n")
-
-n
-# 			 cex = 0.9, xjust=0.5, yjust=1, bty = "n")
-
-```
-
-Note that this framework requires a directed network in which the direction of the links corresponds to the direction of control. 
-In the "Methods" section below, we explain our approach to determining the link direction in pollination networks.
-
-## Relative importance
-
-While calculating *n~D~* measures the manageability of an ecological community, it does not provide information about the identity of the species that compose the set of driver nodes. 
-Ecologically, potential differences between species are relevant because management and conservation resources are limited, and therefore ecological interventions should be focused on the set of species that might provide the largest impact.
-Moreover, maximum matchings in a network are often not unique, and each maximum matching indicates unique paths that can potentially be used to control the network. 
-We harness this property and use a network's complete set of maximum matchings to characterise each species' relative importance in driving the state of the community. 
-One possibility is to characterise a species by the frequency *f~D~* with which it is classified as a driver node within this set of matchings.
-However, the profile of our networks indicates that a large proportion of species were classified as driver nodes because of external interventions required to achieve **full** controllability and not because they influence the abundance of other species (Supporting Information S2).
-Furthermore, the precise role of driver nodes is more ambiguous when full control is unfeasible or undesired—often the case in ecological settings.
-We therefore also calculate the frequency *f~S~* with which a species is classified as a superior node since this is the frequency with which they form part of possible control paths.
-
-Most commonly, structural controllability assumes unweighted networks—links exist or not, and hence *f~D~* and *f~S~* can be calculated by computing all possible maximum-cardinality matchings. 
-However, we take the link weights into account when calculating the matchings here because the weights can reveal significant ecological patterns and processes that might be undetectable in unweighted networks [@Scotti2007; @Tylianakis2007; @Vazquez2007; @Kaiser-Bunbury2010a].
-Additionally, species *A* may interact with both species *B* and *C* but depends strongly on *B* and only weakly on *C*. 
-Intuitively, a management intervention designed to indirectly modify the abundance of species *A* is more likely to succeed if the abundance of *B*, rather than *C*, is directly controlled.
-A complication of including the interaction weight when calculating the maximum matching, however, is that empirical interaction strengths are to some extent stochastic and depend on proximate factors such as sampling method and intensity [@Gibson2011].
-We overcome this issue by calculating all maximal cardinality matchings and then ranking them by their matching weight. 
-By following this approach, we effectively give priority to the species that participate in the pathways that potentially have the largest impact on the community while acknowledging the limitations associated with sampling and its potential restrictions [@Jordano2016].
+Here, we apply methods from control theory to an ecological problem and show how it can be used to gain insight into the role of species in an ecological network. 
+Specifically, we outline the approach using a set of ten pairs of uninvaded and invaded plant-pollinator communities. 
+We use invaded communities because there is strong empirical evidence showing that invasive species play an important role shaping the abundances of other species, and particularly in these ten networks [@lopezaraizamikel_impact_2007; @bartomeus_contrasting_2008-1].
+This choice thus offers us an opportunity to explicitly contrast theoretical observations with empirical evidence.
+First, grounded in the difficulties usually involved with invasive-species eradication and ecosystem restoration [@woodford_confronting_2016], we ask whether there are differences between the controllability of invaded and uninvaded networks.
+<!--STOUFFER: I'd remove the grounded in....
+stuff, but that's just me.
+CAGUA: I don't like it either.
+I tried removing but then it feels like this question is coming out of the blue.-->
+Then we expand existing methods control theory to effectively link the *controllability* of a network with the role of particular nodes. 
+We ask—from a control-theoretic perspective—whether there are key differences between species in the role they play at driving the population of other members of the community and identify the ecological factors related to these differences.
+Finally, we compare the proposed approach to current methods based on species centrality and show how these methods are indeed valuable but only paint a limited picture in regards to the "keystoneness" of a species.
 
@@
 
-```{r network summaries, include = F}
-lop <- filter(meta, study == "lopezaraiza") %>% mutate(size = n_pla + n_pol) %$% size %>% summary() 
-bar <- filter(meta, study == "bartomeus") %>% mutate(size = n_pla + n_pol) %$% size %>% summary() 
+```{r load-metadata}
+drake::loadd(metadata)
+lop <- dplyr::filter(metadata, study == "lopezaraiza") %>% 
+  dplyr::mutate(size = n_pla + n_pol) %$% size %>% summary() 
+bar <- dplyr::filter(metadata, study == "bartomeus") %>% 
+  dplyr::mutate(size = n_pla + n_pol) %$% size %>% summary() 
 ```
 
-We next applied the previously defined framework to ten paired pollination networks.
-Each network pair was composed of a community invaded by a plant and a community "free" of the invasive species. 
-Four pairs were obtained from natural or semi-natural vegetation communities in the city of Bristol, UK [@Lopezaraiza-Mikel2007]. 
-These networks are comprised of `r lop[1]`--`r lop[6]` species (mean `r round(lop[4])`), and non-invaded plots were obtained by experimentally removing all the flowers of the invasive species *Impatients grandulifera*.
-The other six pairs were obtained from lower diversity Mediterranean shrublands in Cap de Creus National Park, Spain [@Bartomeus2008].
-These networks are comprised of `r bar[1]`--`r bar[6]` species (mean `r round(bar[4])`); in contrast to the above, uninvaded communities were obtained from plots that had not yet been colonised by either of the invasive species *Carpobrotus affine acinaciformis* or *Opuntia stricta*.
-Further details about the empirical networks can be found in Supporting Information S3.
+We used ten paired pollination communities to test the control theoretic approach.
+Each community pair was composed of a community invaded by a plant and a community free of the invasive species. 
+Four pairs correspond to natural or semi-natural vegetation communities in the city of Bristol, UK [@lopezaraizamikel_impact_2007]. 
+These communities are comprised of `r lop[1]`--`r lop[6]` species (mean `r round(lop[4])`), and non-invaded plots were obtained by experimentally removing all the flowers of the invasive species *Impatients grandulifera*.
+The other six pairs were obtained from lower diversity Mediterranean shrublands in Cap de Creus National Park, Spain [@bartomeus_contrasting_2008-1].
+These communities are comprised of `r bar[1]`--`r bar[6]` species (mean `r round(bar[4])`); in contrast to the above, uninvaded communities were obtained from plots that had not yet been colonised by either of the invasive species *Carpobrotus affine acinaciformis* or *Opuntia stricta*.
+The structure of all these communities was defined by the pollinator visitation frequency, which has been shown to be an appropriate surrogate for interspecific effects in pollination networks [@vazquez_interaction_2005; @bascompte_asymmetric_2006].
+Full details about the empirical networks, the implications of using visitation frequency to quantify the strength of the associations, and the sensitivity of the control theoretic approach to undersampling of the interactions can be found in the Supplementary materials SX.
 
-We then specified the structure of all networks using pollinator visitation frequency, which has been shown to be an appropriate surrogate for interspecific effects in pollination networks [@Vazquez2005; @Bascompte2006].
-To further examine whether this decision would influence our results, we also evaluated the effect of using pollinator efficiency or pollinator importance as alternative measures in a different data set that lacked invasive species [@NeEman2010; @Ballantyne2015], and we found quantitatively similar results for all three options (Supporting Information S4).
-Because our approach depends on the network topology, we also evaluated the robustness of our results to the undersampling of interactions.
-Specifically, we calculated *n~D~* and species relative importance for 500 random subsamples of each empirical network in which the weakest links were more likely to be removed. 
-Our sensitivity analysis indicated that, even in the absence of complete sampling, a control-theoretic approach can still be applied (Supporting Information S5).
+The first step before applying methods of control theory is to construct a directed network that can provide an indication of the extent to which species affect each others abundance. 
+In some ecological networks, establishing the directionality can appear relatively straightforward, for example when links represent biomass transfer or energy flow [@isbell_human_2013]. 
+In pollination networks, however, this directionallity is less obvious as both species can in theory benefit from the interaction. 
+We overcome that obstacle by noting that the extent to which species *i* affects species *j* relative to the extent to which *j* affects *i* can be summarised by the interaction asymmetry [@bascompte_asymmetric_2006].
+This asymmetry is given by $$a(i,j) = a(j,i) = \frac{\left | d_{ij}-d_{ji} \right |}{max\left ( d_{ij}, d_{ji} \right )},$$ where the dependence of plant *i* on pollinator *j*, *d~ij~*, is the proportion of the visits from pollinator *j* compared to all pollinator visits to plant *i*.
+Previous research has shown that mutualistic interactions are often highly asymmetric in natural communities; in other words, if a plant species is largely dependent on a pollinator species, then that pollinator tends to depend rather weakly on the plant (or vice versa).
+By creating a directed link based on the asymmetry of their dependence we are able to generate a network that is consistent with the dynamics of the community while satisfyingh the requirements of structural controllability.
 
-## Manageability
+After constructing the directed network, we can now calculate the controllability of the different networks and investigate wether there are differences between invaded and uninvaded communities.
 
-```{r component_lost, echo = F, eval = T}
-a <- net %>%
-	lapply(igraph::E) %>%
-	lapply(length)
+## Controllability
 
-b <- net %>%
-	lapply(keep_largest_component) %>%
-	lapply(igraph::E) %>%
-	lapply(length)
+A system is said to be controllable if it is possible to steer it from an initial to an arbitrary final state within finite time [@kalman_mathematical_1963]. 
+A simple dynamic system can be described by $\frac{dx}{dt} = Ax + Bu(t)$, where the change of its state over time ($\frac{dx}{dt}$) depends on its current state *x* (for example, the species' abundances), an external time-varying input *u(t)* (the control signal), and two matrices *A* and *B*, which encode information about the network structure and how species respond to external inputs, respectively.
+In classic control theory, determining wether this system is controllable or not can easily be achieved by checking that its controllability matrix $R= [ \begin{matrix}B & AB & A^{2}B & ...& A^{n-1}B\end{matrix} ]$ has full rank.
+In complex systems, however, employing this rank condition, or numerical approximations of it, is unfeasible because it is hard to fully parameterize *A* and *B*. 
+Here we use an approach based on structural controllability, which assumes that we are confident that the elements of *A* and *B* have either non-zero or zero values (there is an interaction or not), but that we less sure about the precise magitude of the non-zero values [@lin_structural_1974].
+Essentially controllability is translated into a topological problem: a network is controllable if there are no inaccessible nodes—nodes without incoming links—or dilations—*expansions* of the network (Fig X).
 
-int_lost <- ((mapply(magrittr::subtract, a, b) / unlist(a)) * 100) %>% mean() %>% round(1)
+We are often able to estimate *A* in ecological networks, as it represents the interactions between species. 
+Part of the control problem resides on estimating a supportable estimation of *B*, which represents the links between external inputs and species. 
+Naively, any ecological community (and any system for that matter) could be controlled if we control the state of every species independently. 
+Such approach is typically unpractical so we are interested in finding a minimum driver node set (effectively finding *B*) with which to make the system contr
 
-a <- net %>%
-	lapply(igraph::V) %>%
-	lapply(length)
+Controllability is this
+But is hard to calculate.
+Therefore we use recent advances that show that it can be calculated using maximum matching algorithms.
 
-b <- net %>%
-	lapply(keep_largest_component) %>%
-	lapply(igraph::V) %>%
-	lapply(length)
-
-sp_lost <- ((mapply(magrittr::subtract, a, b) / unlist(a)) * 100) %>% mean() %>% round(1)
-```
-
-We began by quantifying the manageability of each network.
-To do so, we calculated the networks' maximum matching and determined the minimum proportion of species *n~D~* that need external input signals to fully control the species abundances in the community.
-Note that because all maximum matchings have the same matching size, it is only necessary to calculate one of them. 
-To simplify the analysis, if a network had more than one component (two species are in different components if there exists no path between them and are hence independent of each other in terms of network control) we only considered the largest.
-Smaller components were present in eleven out of the twenty networks and were typically composed of just one plant and one pollinator. 
-Their removal represented an average loss of `r sp_lost`% of the species and `r int_lost`% of the interactions.
-
-### Weighting & directing links
-
-As we noted earlier, the maximum-matching approach requires a directed network in which a link from species *i* to species *j* indicates that the abundance of *j* can be affected by the abundance of *i*.
-This implies that we need first to identify a directionality for the links between species that is consistent with the dynamics of the community (Figure 2). 
-In some ecological networks, establishing the directionality can appear relatively straightforward, for example when links represent biomass transfer or energy flow [@Isbell2013]. 
-Interspecific effects in pollination networks, however, are not strictly directed since the benefit is mutual between interacting species. 
-Nevertheless, the relative extent to which a given pair of interacting species affect each other can be quantified by the magnitude of the mutual dependence between them [@Bascompte2006]. 
-The dependence of plant *i* on pollinator *j*, *d~ij~*, is the proportion of the visits from pollinator *j* compared to all pollinator visits to plant *i*. 
-Likewise, the dependence of pollinator *j* on plant *i*, *d~ji~*, is the proportion of the visits by pollinator *j* to plant *i* compared to all visits of pollinator *j*.
-Using dependences generates a weighted bipartite network in which all interacting pairs are connected by two directed links (Figure 2b).
-
-```{r figure 2, echo = F, fig.width = 6.2, fig.height = 1.6, message = F, warning = F, fig.pos = "T", fig.cap = "**Different ways to depict quantitative mutualistic networks**.
-(a) Pollination networks are frequently described by the observed number of visits between each plant and animal species.
-(b) Based on that visitation data, the mutual dependences between interacting species are calculated directly based on the relative visitation frequencies.
-(c) The relative differences of these  dependences—the interaction asymmetry—then provide a means to estimate the dominant direction of the interspecific effects."}
-
-par(mfrow=c(1,3), mar=c(0,0,0,0))
-
-base_net %>%
-	plot(layout = lay, 
-			 vertex.color = v_c, 
-			 vertex.size = 35,
-			 vertex.label = sp_names_fancy,
-			 vertex.label.family = fam,
-			 vertex.label.color = l_c,
-			 edge.label = E(.)$weight, 
-			 edge.label.family = fam,
-			 edge.label.color = l_c,
-			 edge.label.cex = l_s,
-			 edge.curved = F,
-			 frame = F,
-			 margin = ma)
-text(label_pos_x, label_pos_y, "(a)", adj = c(0,0), font = 2)
-
-bi_net %>% 
-	plot(layout = lay, 
-			 vertex.color = v_c, 
-			 vertex.size = 35,
-			 vertex.label = sp_names_fancy,
-			 vertex.label.family = fam,
-			 vertex.label.color = l_c,
-			 edge.label = round(E(.)$weight,1), 
-			 edge.label.family = fam,
-			 edge.label.color = l_c,
-			 edge.label.cex = l_s,
-			 edge.curved = T,
-			 edge.arrow.size = 0.5,
-			 margin = ma)
-text(label_pos_x, label_pos_y, "(b)", adj = c(0,0), font = 2)
-
-as_net %>% 
-	plot(layout = lay, 
-			 vertex.color = v_c, 
-			 vertex.size = 35,
-			 vertex.label = sp_names_fancy,
-			 vertex.label.family = fam,
-			 vertex.label.color = l_c,
-			 edge.label = round(E(.)$weight,1), 
-			 edge.label.family = fam,
-			 edge.label.color = l_c,
-			 edge.label.cex = l_s,
-			 edge.curved = F,
-			 edge.arrow.size = 0.5,
-			 margin = ma)
-text(label_pos_x, label_pos_y, "(c)", adj = c(0,0), font = 2)
-
-```
-
-Given the respective dependences, the extent to which species *i* affects species *j* relative to the extent to which *j* affects *i* can be summarised by the interaction asymmetry [@Bascompte2006] given by $$a(i,j) = a(j,i) = \frac{\left | d_{ij}-d_{ji} \right |}{max\left ( d_{ij}, d_{ji} \right )}.$$
-Previous research has shown that mutual dependences are often highly asymmetric in natural communities [@Bascompte2006]; in other words, if a plant species is largely dependent on a pollinator species, then that pollinator tends to depend rather weakly on the plant (or vice versa).
-We therefore simplified the network so that interacting species are connected by only one directed link when mutual dependences are asymmetric (Figure 2c).
-This simplification, while maintaining ecological realism, is advantageous for several reasons. 
-First, it is consistent with previous advances in structural controllability; second, it prevents the singular case in which the network could be perfectly matched rendering $D=1$ as well as problems related to the introduction of artificial control cycles [@Ruths2014]; and third it significantly reduces the computational resources necessary for the application of our approach (Supporting Information S6).
-Moreover, we found that changing to unidirectional interactions based on the direction of asymmetry does not alter the relative *n~D~* of different networks (Table S3).
-
-To find a maximum matching in a network with interaction directions and weights determined by the asymmetry, we adopted a strategy based on an alternative bipartite representation of the directed network with two levels that indicate the outgoing and incoming links to each node (Supporting Information S1).
-Once we had this alternative representation we used the maximum bipartite matching algorithm implemented in the `max_bipartite_match` function of igraph 1.0.1 [@Csardi2006a] on each network.
-
-### Statistical analysis
-
-We also wanted to test whether invasion status or other predictors had an impact on the observed values of *n~D~*. 
-We therefore used a set of generalised linear models (with binomial error structure) to investigate the effect of invasion status while also including covariates related to species richness, since one might naively expect to see a negative relationship between richness and manageability [@Menge1995].
-These covariates included the total number of species, plant richness, pollinators richness, the ratio of plant to pollinator richness, the link density (connectance), and the study site (as a two-level factor).
-
-We next explored whether real networks differ in their architecture from random ones in a concerted way that affects manageability. 
-Previous research indicates a direct link between a network's degree distribution and the number of nodes necessary to fully control it [@Liu2011], but the strength and applicability of this relationship have not been tested for in weighted ecological networks.
-We therefore compared the driver-node density *n~D~* of the empirical networks to networks generated by a null model that maintained each species' strength (its total sum of visits) while allowing their degrees (its number of interactions) to vary.
-Beyond network structure, the dependence asymmetry plays a fundamental role in determining the direction of control in each two-species interaction and therefore has the potential to influence the network *n~D~* results above.
-We therefore performed an additional randomisation in which we kept the structure of each network constant but randomised the direction of the interaction asymmetries. 
-That is, we first calculated the observed asymmetries for each community and then shuffled the direction of the link between each pair of species.
-
-Additional details about the statistical models and the randomisations can be found in Supporting Information S7.
-
-## Relative importance
-
-Our second key question was related to how species differ in their ability to drive the population dynamics of the community. 
-To quantify this importance, we computed all maximal cardinality matchings in each network. 
-We then calculated the frequency with which each species *i* was a driver (*f~D~*) or a superior node (*f~S~*) in the set of matchings that had a matching weight greater or equal to 0.8 times the weight of the maximum matching.
-We selected this threshold as it provided a high agreement between networks quantified by visitation and pollination efficiency as well as between our weighting/directionality assumptions; however, the choice of this threshold had a negligible impact on any results (Supporting Information S8).
-Details about the computational procedure to find all maximal cardinality matchings of a network can be found in Supporting Information S1 and Figure S2.
-
-### Statistical analysis
-
-We then examined whether any species-level structural properties could predict our metrics of species importance—the frequency with which a species was a driver or a superior node (*f~D~* and *f~S~*, respectively).
-We used a set of generalised linear mixed-effects models (with binomial error structure) with the relative frequencies as the response variables. 
-As predictors in this model, we included measures of centrality (degree and eigen-centrality), which have been found to be strong predictors of importance in a coextinction context [@Memmott2004]; a measure related to network robustness (contribution to nestedness), as nestedness has been proposed as one of the key properties that promote stability in mutualistic networks [@Saavedra2011]; a measure of strength of association (visitation strength, the sum of visits a species receives or performs) and a measure of strength of dependence (species strength, the sum of dependences of all species on the focal species), as their distribution determines the extent of interspecific effects [@Bascompte2006].
-In addition, we also included guild (plant or pollinator) and whether the species is invasive or not as categorical fixed effects.
-Lastly, we allowed for variation between different communities by including the network identity as a random effect [@Bates2015]. 
-Supplementary details about the statistical models can be found in Supporting Information S7.
-
-# Results
-
-## Manageability
-
-All of the networks had a driver-node density *n~D~* between `r round(min(dplyr::filter(n_driver, type == "weight")$n_dr_p), digits = 2)` and `r round(max(dplyr::filter(n_driver, type == "weight")$n_dr_p), digits = 2)` (mean `r round(mean(dplyr::filter(n_driver, type == "weight")$n_dr_p), digits = 2)`; Figure 3a).
-In addition, we found that, when controlling for potential species richness effects, the *n~D~* of invaded communities was smaller to those of non-invaded communities (Figure 3b). 
-Nevertheless, of the various covariates we explored, the ratio of plants to pollinators showed the strongest relationship with *n~D~* (Figure 3c; Table S5). 
-Specifically as the proportion of pollinators increases and the ratio plant/pollinator approaches unity, *n~D~* decreases (all our communities had more pollinators than plants). 
-Other covariates—connectance (link density) and species richness—had negative, but comparatively less important, relationships with *n~D~*.
-
-```{r fig_explaining-n-driver, echo = FALSE, warning = FALSE, message = FALSE, fig.width = 3.245, fig.height = 4.8, fig.cap = "**Driver-node density**.
-(a) Histogram of the driver-node density (_n~D~_) for the twenty networks.
-(b) Invaded communities have lower *n~D~* than uninvaded communities even when controlling for factors related to species richness.
-The boxes cover the 25th–75th percentiles, the middle lines mark the median, and the maximum length of the whiskers is 1.5 times the interquartile range.
-(c) Out of the richness metrics, the ratio of plants to pollinators showed a strong, negative relationship with *n~D~*.
-In both plots, partial residuals correspond to the partial working residuals of the invasion status in our generalised linear mixed model."}
-
-par_res <- as.data.frame(residuals(manag_models@objects[[5]], "partial"))
-names(par_res) <- paste0(make.names(names(par_res)), "_res")
-par_res %<>%
-  dplyr::bind_cols(manag_models@objects[[1]]$data)
-
-p0 <- manag_models@objects[[1]]$data %>% 
-	ggplot(aes(x = n_dr_p)) + 
-	stat_density(size = 0.4, geom = "line") +
-	fer_theme +
-	xlab(expression(paste("driver-node density (", n[D], ")"))) +
-	ylab("density") +
-	theme(axis.title.y = element_text(vjust = 1, margin = margin(1,-3,1,1, unit = "lines")))
-
-p1 <- par_res %>%
-  ggplot(aes(x = inv, y = inv_res)) +
-  # facet_wrap(~type) +
-  geom_boxplot(size = 0.3,
-               colour = "grey10", outlier.shape = 21, outlier.size = 1) +
-  fer_theme +
-  scale_x_discrete(labels = c("uninvaded", "invaded"), name = "") +
-  ylab(expression(paste(n[D], " partial residuals"))) +
-  coord_flip() +
-  theme(
-        legend.position = "none",
-				plot.margin = grid::unit(c(2, 1, 2, 0), "mm"), 
-				# panel.grid.minor.x = element_blank(),
-				panel.grid.minor.y = element_blank())
-
-p2 <- par_res %>%
-  ggplot(aes(x = n_pla/n_pol, y = I.n_pla.n_pol._res)) +
-	geom_smooth(method = "lm", se = F, colour = "black", size = 0.5) +
-	geom_point(shape = 21) + 
-	fer_theme +
-	scale_x_continuous(name = "ratio of plants to pollinators") +
-	scale_y_continuous(name = expression(paste(n[D], " partial residuals"))) +
-	theme(axis.title.y = element_text(vjust = 1, margin = margin(1,-3,1,1, unit = "lines")))
-
-cowplot::plot_grid(p0, p1, p2, ncol = 1, align = "v") +
-	cowplot::draw_plot_label(label = c("(a)", "(b)", "(c)"), size = 8, fontface = "bold", y = c(1, 0.66, 0.33))
-# pdf("../paper/figures/fig_3.pdf", height = 1.7, width = 3.245, family = "Times", compress = F, title = "Figure 3")
-# f3
-# dev.off()
-
-```
-
-When exploring the effect of network structure itself, we observed that the driver-node density *n~D~* of empirical networks was, in general, not significantly different to the manageability of network randomisations that maintained the degree of individual species (Figure 4).
-However, we found that the *n~D~* of empirical networks was significantly larger than that of randomisations that maintained the network structure but that differed only in the direction of the asymmetries.
-
-```{r fig_randomisations, echo = FALSE, warning = FALSE, message = FALSE, fig.width = 3.245, fig.height = 1.7, fig.cap = "**The driver-node density _n~D~_ of empirical networks compared to network randomisations**.
-For each randomisation approach, we show the standarised rank of the empirical value compared to the set of randomisations.
-A scaled mean rank—akin to a p-value— less than 0.025 or greater than 0.975 (the areas shaded in light grey) suggests a significant difference between the empirical network and its randomisations.
-The empirical _n~D~_ is much larger than that of network randomisations in which the direction of asymmetries has been randomised.
-In contrast, the manageability of networks in which the species degrees were randomly shuffled were not significantly different.
-All boxes are as in Figure 3a."}
-r <- r_w %>%
-  dplyr::bind_rows(dplyr::mutate(r_d, type = "weight")) %>%
-  dplyr::inner_join(meta) %>%
-  dplyr::filter(study != "ballantyne") %>%
-  dplyr::mutate(n_dr = n_pla + n_pol - n_matched)
-
-# non-parametric
-z_scores <- r$method %>%
-  unique() %>%
-  plyr::ldply(function(x){
-    n_driver %>%
-      dplyr::mutate(type = stringr::str_replace(type, "-", "_")) %>%
-      dplyr::filter(type == "weight" | type == "z_bi") %>%
-      dplyr::mutate(method = x)
-  }) %>%
-  dplyr::bind_rows(r) %>%
-  dplyr::filter(!(type == "z_bi" & method == "r0")) %>%
-  dplyr::group_by(net_name, method, type) %>%
-  dplyr::mutate(z_r = rank(n_dr, na.last = NA),
-                z_r = z_r/n(),
-                z_s = qlogis(z_r),
-                z_s = replace(z_s, (is.infinite(z_s) & z_s > 0) | z_s > qlogis(0.999), qlogis(0.999)),
-                z_s = replace(z_s, is.infinite(z_s) & z_s < 0, qlogis(0.001))) %>%
-  dplyr::filter(is.na(sim))
-
-z_scores_method_order <- c("r0","swsh_both", "quasiswap_count","r00_ind", "r00_samp", "r00_both")
-
-p1 <- z_scores %>%
-  dplyr::group_by() %>%
-  dplyr::mutate(method = factor(method, levels = z_scores_method_order),
-                m_n = as.numeric(method),
-                m_n = replace(m_n, m_n == 3, 3.5)) %>%
-  dplyr::filter(!method %in% c("r00_both", "r00_ind", "r00_samp", 
-  														 "swsh_both")) %>% # the maintain degree randomise strength option
-	dplyr::filter(type == "weight") %>%
-  ggplot(aes(x = method, y = z_s)) +
-  geom_rect(aes(xmin = 0.5, xmax = 2.5, ymin = -Inf, ymax = qlogis(0.025)), fill = "#f0f0f0") +
-  geom_rect(aes(xmin = 0.5, xmax = 2.5, ymin = Inf, ymax = qlogis(0.975)), fill = "#f0f0f0") +
-
-  # geom_hline(yintercept = c(-0), linetype = 2, alpha = 0.7, size = 0.25) + 
-  # geom_vline(aes(xintercept = 1.5), alpha = 0.6, size = 0.25) +
-   geom_hline(yintercept = 0, size = 0.25, linetype = 2, colour = "grey30") +
-  geom_boxplot(aes(fill = type), size = 0.3,
-               colour = "grey10", outlier.shape = 21, outlier.size = 1) +
-  # geom_point(aes(y = 9, colour = sign <= 0.05), shape = 8, size = 1) +
-  scale_fill_manual(values = c("white", "#bdbdbd")) +
-  scale_x_discrete(
-    labels = rev(c("random degree", # "maintain degree\nrandomise strength", 
-    							 "random\nasymmetry")),
-    # breaks = c(#"r00_samp", #"swsh_both",
-    					 # "quasiswap_count", "r0"),
-    expand = c(0,0)) +
-  scale_y_continuous(breaks = qlogis(c(0.001, 0.025, 0.5, 0.975,0.999)), 
-                     labels = plogis(qlogis(c(0.001, 0.025, 0.5, 0.975,0.999)))) + 
-  xlab("") +
-    coord_flip() +
-  ylab(expression(paste("empirical ", n[D], " rank (scaled)"))) + 
-  fer_theme +
-  theme(legend.position = "none",
-				plot.margin = grid::unit(c(-1, 1, 2, 0), "mm"), 
-				# panel.grid.minor.x = element_blank(),
-				panel.grid.minor.y = element_blank(),
-				plot.background = element_blank())
-
-library(ggrepel)
-
-p2 <- data_frame(x = c(-0.05,0.05),
-					 xend = c(-1,1), 
-					 y = 0, yend = 0, 
-					 xtext = c(-0.5, 0.5),
-					 label = c("smaller\nthan random", "larger\nthan random")) %>%
-	ggplot(aes(x = x, y = y)) + 
-	geom_segment(aes(xend = xend, yend = yend), 
-							 arrow = arrow(angle = 15,
-							 							length = unit(3, "mm"), 
-							 							type = "open"), 
-							 size = 0.3, colour = "grey30") +
-	geom_label(aes(x = xtext, label = label), size = 2.2, y = 0.1, 
-						 label.size = 0, lineheight = 0.8, colour = NA,
-						 fill = "white") +
-	geom_text(aes(x = xtext, label = label), size = 2.2, y = 0.1, 
-						label.size = 0, lineheight = 0.8, colour = "grey10",
-						fill = "white") +
-	scale_x_continuous(expand = c(0,0)) +
-	scale_y_continuous(expand = c(0,0)) +
-	theme(plot.background = element_blank(), 
-				plot.margin = margin(0,0,0,0)) +
-	theme_void()
-
-cowplot::plot_grid(p2, p1, ncol = 1, align = "v", rel_heights = c(1.5,10))
-```
-
-## Relative importance
-
-Invasive species were classified as superior nodes *and* driver nodes in every single network they were present; that is, they always had the highest relative *f~S~* and *f~D~* (Figure 5a). 
-The model results suggest that these differences between invasive and native species are not underpinned by any intrinsic property of the invasive species; instead, they are due to species properties that apply to invasive and native species alike (Table 1).
-Specifically, we found that a species is more likely to be classified as a superior node if it had a large species strength (the sum of the dependences of all other species on the species of interest).
-To a smaller extent, visitation strength (a species' sum of visits) and degree also had a positive relationship with *f~S~*. 
-In contrast, the relationships between species structural properties and *f~D~* were less clear cut (Table 1). 
-Both invasive species (which generally have a larger degree and high dependence strength) and pollinators (which generally have a smaller degree and low dependence strength) were classified as driver nodes in a large proportion of matchings.
-
-```{r glmulti-functions, include = FALSE, warning = FALSE, message = FALSE, results = "hide"}
-glmer.glmulti<-function(formula,data,random="",...){
-  glmer(paste(deparse(formula, width.cutoff = 500),random),data=data,...)
-}
-
-setMethod('getfit', 'glmerMod', function(object, ...) {
-  summ <- coef(summary(object))
-  summ1 <- summ[,1:2,drop=FALSE]
-  ## if (length(dimnames(summ)[[1]])==1) {
-  ##     summ1 <- matrix(summ1, nr=1,
-  ##                     dimnames=list(c("(Intercept)"),
-  ##                     c("Estimate","Std. Error")))
-  ## }
-  cbind(summ1, df=rep(times =10000,length(fixef(object))))
-})
-```
-
-```{r fig-dependency-fs, echo = FALSE, warning = FALSE, message = FALSE, fig.width = 3.245, fig.height = 3.2, fig.cap = "**Relationships between _f~S~_ and _f~D~_ and species structural properties**.
-(a) In all networks were they were present, invasive species were classified as superior (_f~S~_) and driver (_f~D~_) nodes in all possible control configurations.
-(b) Species strength (the sum of the dependences of other species on the species of interest) is the single most important factor explaining _f~S~_.
-Visitation strength and degree also had an important albeit comparatively smaller effect (dashed lines correspond to $\\pm$ one standard deviation of these factors).
-Invasive species are depicted as circles."}
-data <- mo 
-trans <- function(x, orig){
-  x * attr(orig, "scaled:scale") + attr(orig, "scaled:center")
-}
-
-b_trans <- function(x, orig){
-  (x - attr(orig, "scaled:center")) / attr(orig, "scaled:scale")
-}
-
-pred_data <- data.frame(de = rep(b_trans(exp(c(seq(
-	log(trans(min(data$de, na.rm = T), data$de)),
-	log(trans(max(data$de, na.rm = T), data$de)),
-                                length = 500))), data$de),3),
-            d = rep(c(-1,0,1), each = 500),
-            vi = rep(c(-1,0,1), each = 500),
-            type = rep(c("exp", "mean", "exp"), each = 500),
-            # vi = seq(min(data$vi), max(data$vi), length.out = 500),
-            eig_cen = mean(data$eig_cen, na.rm = T),
-            n = mean(data$n, na.rm = T),
-            guild = "pla")  %>%
-  dplyr::filter(!(n == 2 & vi == -2),
-                !(n == -2 & vi == 2)) %>%
-  dplyr::mutate(q = predict.glmulti(mod[[1]],
-                                    select = 2L,
-                                    newdata = .,
-                                    re.form = NA)$averages %>%
-                  as.vector(),
-                p = plogis(q)) %>%
-  dplyr::mutate(de = de * attr(data$de, "scaled:scale") + attr(data$de, "scaled:center"),
-                vi = vi * attr(data$vi, "scaled:scale") + attr(data$vi, "scaled:center"))
-
-data_pp <- data
-data_pp$pred_ri <- plogis(predict.glmulti(mod[[1]], re.form = NA, select = 1L))
-data_pp$de_s <- data$de * attr(data$de, "scaled:scale") + attr(data$de, "scaled:center")
-data_pp <- lapply(data_pp, as.vector) %>% as.data.frame
-
-p1 <- pred_data %>%
-  ggplot() +
-  geom_line(aes(x = de, y = p, linetype = type, colour = type, group = interaction(n, vi)), show.legend = F, size = 0.5) +
-  scale_x_log10(expand = c(0,0), breaks = c(0.01, 0.1, 1, 10, 100)) +
-   geom_point(data = dplyr::arrange(data_pp, invasive) %>% dplyr::filter(invasive == T), aes(x = de_s, y = pred_ri, fill = invasive, shape = guild, size = invasive), show.legend = F) +
-    scale_shape_manual(values = c(21, 23)) +
-  scale_size_manual(values = c(1.5,1.5)) +
-  scale_fill_manual(values = c("white","#e41a1c")) + 
-  scale_color_manual(values = c("#525252", "black")) +
-  scale_linetype_manual(values = c(2, 1)) +
-  xlab("species strength") +
-  ylab(expression(f[S])) +
-  fer_theme
-
-# invasive comparison plot
-p2 <- mo %>%
-	# dplyr::filter(guild == "pla") %>%
-	dplyr::select(invasive, f_s, f_d) %>%
-	dplyr::mutate(invasive = plyr::mapvalues(invasive, c(F,T), c("native", "invasive"))) %>%
-	reshape2::melt(measure.vars = c("f_s", "f_d")) %>%
-	ggplot(aes(y = value, x = variable)) + 
-	geom_boxplot(size = 0.3, outlier.shape = 21, outlier.size = 1)  +
-    # coord_flip() +
-  ylab("proportion") + 
-	scale_x_discrete(labels = parse(text = c("f[S]", "f[D]")), name = "") +
-	# scale_x_discrete(name = "", labels = c("native", "invasive")) +
-  fer_theme +
-  theme(legend.position = c(0.99,0.02),
-  			legend.direction = "horizontal",
-  			legend.justification = c(1,0),
-				plot.margin = grid::unit(c(-1, 1, -3, 0), "mm"), 
-				# panel.grid.minor.x = element_blank(),
-				panel.grid.minor.y = element_blank(),
-				strip.text = element_text(size = 8, hjust = 1, vjust = -1)) +
-	scale_color_manual(values = RColorBrewer::brewer.pal(5, "Greys")[c(5,4)],
-										 name = "", 
-										 labels = c(expression(f[S]), expression(f[D]))) +
-	facet_grid(~invasive)
-
-cowplot::plot_grid(p2, p1, ncol = 1, labels = c("(a)", "(b)"), label_size = 8, 
-									 hjust = 0, vjust = 1.1, align = "v", rel_heights = c(1,1.16))
-```
-
-```{r table-species-model-coef, echo = FALSE, warning = FALSE, message = FALSE, results = "asis", sanitize = FALSE, cache = T}
-coef_tables <- mod %>%
-	plyr::llply(function(x){
-		x %>%
-			coef.glmulti(select = 0.95) %>%
-  as.data.frame()  %>%
-  dplyr::add_rownames("factor") %>%
-  dplyr::mutate(pare = grepl("(", factor, fixed =T),
-                factor = plyr::mapvalues(factor, 
-                                         c("de", "n", "vi", "eig_cen", 
-                                           "guildpol", "d", "invasiveTRUE"),
-                                         c("species strength", 
-                                           "contribution to nestedness",
-                                           "visitation strength",
-                                           "eigen-centrality", 
-                                           "guild (pollinator)", "degree", "invasive sp."))) %>% 
-  magrittr::set_names(c("factor", "est.", "var", "mod.", "imp.", "C.I.", "pare")) %>%
-			dplyr::mutate(absEstimate = abs(est.)/C.I.) %>%
-  dplyr::arrange(-pare, -imp., -absEstimate, factor) %>% 
-  dplyr::select(-pare, - absEstimate) 
-	})
-
-coef_tables %<>%
-	plyr::llply(function(x){
-		x %>%
-			dplyr::select(factor, imp., est., var, mod., C.I.) %>%
-			magrittr::set_names(c(" ", "imp.", "est.", "var", "mod.",  "C.I.")) %>%
-			dplyr::select(-var, -mod.)
-	})
-
-attr(coef_tables, "subheadings") <- paste0("$", names(mod), "$")
-coef_tables %>%
-	xtable::xtableList(caption = "\\textbf{Factors explaining species importance}.
-Factor estimates correspond to the average over all models that accounted for 95\\% of the AIC evidence.
-Confidence intervals correspond to $\\alpha = 0.05$.",
-										 digits =  c(0, 0, 2, 2, 2),
-										 display = c("d", "s", "f", "f", "G")) %>%
-	print(booktabs = T, include.rownames = F,  caption.placement = "top", size = "\\small",comment = F, sanitize.text.function = function(x){x})
-```
-
-# Discussion
-
-Contrary to our initial hypothesis, we found some evidence that invaded communities might be easier to manage than uninvaded ones from a control-theoretic perspective. 
-Our results reveal, however, that this effect is comparatively small, and the structural differences among different networks are more strongly related to potential differences in our ability to alter the state of the community via external interventions.
-Despite the small effect of invasion status at the network level, we found that invasive mutualists occupy a particularly dominant role in their communities for two reasons. 
-First, as species with a high *f~S~*, changes on their abundance have the potential to propagate broadly through the community and, in turn, affect the abundances of many other species. 
-Second, as species with a high *f~D~*, they are also indispensable when it comes to fully controlling the plant-pollinator network. 
-At a community level, we demonstrate that the manageability of mutualistic networks is strongly governed by the asymmetric nature of mutual dependences—which constitute the foundations of the structure and stability of mutualistic networks [@Memmott2004; @Vazquez2004; @Bascompte2006; @Astegiano2015].
-Moreover, these mutual dependences seem to be constrained by the effects of both the patterns of species richness at each trophic guild and a network's degree distribution [@Melian2002; @Bluthgen2007].
-Indeed, the difference between the driver-node density (*n~D~*) of our empirical networks and that of randomisations depended strongly on the null model's randomisation approach. 
-While the empirical *n~D~* was indistinguishable from that of networks with a random structure that maintained the degree of each species in the community, it was larger than that of randomisations in which the directed network was unchanged but where the observed patterns of dependence were broken.
-
-Invasive species have been previously found to exacerbate the asymmetries in their communities [@Aizen2008; @Bartomeus2008; @Henriksson2016]. 
-Although this might cause differences both at the community and the species level, we found that invasive plants are not inherently different to their native counterparts [@Stouffer2014; @Emer2016a].
-Invasive plants, just like any other mutualist in our data set, tend to be classified as a superior node proportional to the degree to which their interaction partners are collectively more dependent on them than the other way around.
-Previous studies have found that supergeneralists, like invasive species, play a central role in their networks [@Vila2009; @Palacio2016].
-Our results take this one step further and indicate that dependence strength, rather than generalism or other metrics of centrality, is the factor that best explains the cascading effects a species could trigger on its community.
-
-Because of the ability that our approach has to infer the magnitude of the effects that each species has on others in the community, it is tantalising to use it to select promising candidates for management interventions.
-To this end, the two indices we have used to characterise a species provide two complementary pieces of information. 
-Our first index *f~D~*---the frequency with which a species is classified as a driver node---provides an indication of the likelihood that a species forms part of the set of species that must be manipulated in order to control *all* species in the community.
-This driver-node concept has received considerable attention in the structural-control literature and indeed shows substantial potential to provide useful ecological insight. 
-Nevertheless, we anticipate two caveats that hinder its direct utility for management applications.
-First, unlike some other types of complex systems, fully controlling an ecological community is almost certainly out of reach for all but the simplest, due to either the number of required interventions or the practical difficulties of their implementation [@Motter2015].
-For instance, our results suggest that full control of the pollination networks would require direct interventions on anywhere from 40--90% of the species.
-Second, @Ruths2014 established that driver nodes arise due to distinct mechanisms and therefore species with markedly different network metrics can act as driver nodes in their community (Supporting Information S2).
-
-Our second index *f~S~*, however, is directly related to the likelihood a species affects the abundance of another species in all of the control strategies considered. 
-Importantly, this is irrespective of whether controlling the entire network is ultimately desired and/or feasible. 
-In fact, because superior nodes are always at the beginning of a matched link, species with a high *f~S~* are more likely to be the subjects of management interventions when controlling the abundances of a target set of species—as opposed to the entire network—is desired [@Gao2014].
-An important advantage here is that the target set of species does not have to be the same set to which interventions are applied. 
-For instance, despite inconsistent outcomes in practice [@Suding2004; @Rodewald2015; @Smith2016], our results suggest that current restoration approaches that focus on direct eradication of invasive species might indeed be an effective way to modify ecosystem state.
-Nevertheless, our results also indicate that removals must be exercised with caution. 
-Not only it is hard to predict the direction in which the system will change, but invaded communities also tend to be highly dependent on invaders and therefore acutely vulnerable to their eradication [@Traveset2013; @Albrecht2014].
-
-Despite the apparent similarities, our approach is different to previous attempts to quantify species importance in a few key ways.
-Existing metrics usually harness species features, like centrality, position, co-extinction or uniqueness, to infer their effect on other species [@Allesina2004; @Jordan2006; @Jordan2009; @Lai2012]. 
-In contrast, our control-based approach tackles that question directly.
-Although they are relatively simple to calculate, classic species-level network metrics do not necessarily reveal the best set of species to manage [@Eklof2013; @McDonald-Madden2016].
-Our approach, however, is not based on a single structural metric but instead acknowledges the existence of multiple management strategies. 
-By allowing for the fact that some strategies are better than others depending on the context, control theory implicitly highlights that management decisions should not be based on a single technique.
-As such, ours and other flexible approaches that take a network-wide approach might prove more useful to guide ecosystem management [@McDonald-Madden2016].
-
-In this study, we illustrate how a control-theoretic approach can be employed in network ecology to evaluate the effect of invasions and other kinds of perturbations. 
-We study the different ways a management intervention can be structured and provide a starting point for the continued study of controllability in ecological contexts.
-Although our pollination-specific results might not be directly translatable to other ecological networks that do not have bipartite structures, the approach we propose is applicable wherever species abundances are influenced by their interactions, and exciting open questions lie ahead.
-How to design the precise "control signals" to reach a desired ecosystem state or conservation outcome? 
-What are the implications of assuming fully nonlinear dynamics?
-How important it is to include several interaction types for our understanding of manageability and species importance?
-What are the implications for species coexistence? 
-Which are the trade-offs between persistence at the species and the community level? 
-Answering each of these questions might require its evaluation in different ecological systems, an explicit integration of control theory with numerical models of species densities [@Cornelius2013; @Gibson2016], and experimental tests on simple communities.
-Nevertheless, the potential rewards are encouraging from both an ecological and conservation perspective, where an integrated approach can shift the focus beyond the identification of ideal targets for intervention to the design of informed interventions that legitimately achieve restoration goals.
-
-# Appendix 1: Glossary
-
-Driver node
-  ~ An unmatched node in a maximal cardinality matching or a maximum matching.
-From the control perspective, driver nodes are those to which external control signals must be applied in order to gain full control of the network.
-
-Matched/unmatched link
-  ~ A link is refered to as *matched* if it is part of a matching, and *unmatched* otherwise.
-
-Matched/unmatched node
-  ~ A node is refered to as *matched* if it is at the end of a matched link, and *unmatched* otherwise.
-
-Matching
-  ~ A set of links in which no two of them share a common starting or ending node.
-
-Matching size
-  ~ The number of matched links in a matching.
-
-Matching weight
-  ~ The sum of the weights of all matched links in a matching.
-
-Maximal cardinality matching
-  ~ A matching with the largest possible matching size. In unweighted/binary networks, all maximal cardinality matchings are also maximum matchings.
-
-Maximum matching
-  ~ A matching with the largest possible matching size *and* largest possible matching weight.
-
-Superior node
-  ~ The node at the start of a matched link. From the control perspective, superior nodes make up the chains that propagate the control signals through the network.
-
-## Acknowledgments
-
-The authors thank Jane Memmott and coauthors, and eveyone that has made their data available to us, Takeuki Uno for the insight provided to find the set of all maximum matching algorithms, and Jason Tylianakis, Bernat Bramon Mora, Guadalupe Peralta, Rogini Runghen, Warwick Allen, Matthew Hutchinson, and Marilia Gaiarsa for feedback and valuable discussions.
-EFC acknowledges the support from the University of Canterbury Doctoral Scholarship, the University of Canterbury Meadow Mushrooms Postgraduate Scholarship, a New Zealand International Doctoral Research Scholarship, and a travel grant from the European Space Agency.
-DBS acknowledges the support of a Marsden Fast-Start grant and a Rutherford Discovery Fellowship, administered by the Royal Society of New Zealand.
-
-## Author contributions
-
-DBS conceived the idea; all authors contributed to the development of the theoretical framework. EFC performed all analysis. EFC and DBS wrote the manuscript. All authors contributed to its revision.
-
-## Data accessibility
-
-All data used in this manuscript have already been published by @Lopezaraiza-Mikel2007, @Bartomeus2008, and @Ballantyne2015. The reader should refer to the original sources to access the data.
+A maximum matching is this. 
+And can be calculatid this way. 
+And gives this information. 
+But its not unique.
+This can provide extra information. 
+Therefore we calculate them all.
 

### 2018-04-28 paper/supp-info.Rmd
Add manuscript and supplementary information

---
title: "Ecological network control"
subtitle: "Supplementary Information"
author: "Fernando Cagua, Kate L. Wootton, Daniel B. Stouffer"
classoption: a4paper
csl: journal-of-ecology.csl
documentclass: artikel1
output: 
  bookdown::pdf_document2: 
    keep_tex: yes
    toc: false
header-includes:
  - \usepackage{booktabs}
  - \usepackage{setspace}
bibliography: references.bib
---

\renewcommand\thefigure{S\arabic{figure}}    
\setcounter{figure}{0}

\renewcommand\thetable{S\arabic{table}}    
\setcounter{table}{0}

\renewcommand{\thesection}{S\arabic{section}}
\setcounter{section}{0}

\onehalfspacing

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, 
                      warning = FALSE)
options(xtable.comment = FALSE, 
        xtable.caption.placement = 'bottom',
        xtable.size = 'small',
        booktabs = TRUE)
```

# Characteristics of the epirical networks {#empirical-networks}

```{r}
drake::loadd(metadata)
drake::loadd(network_properties)

net_prop <- metadata %>%
	dplyr::mutate(n_s_t = n_pla + n_pol) %>%
	dplyr::select(-n_pla, -n_pol) %>%
	dplyr::inner_join(network_properties, by = "net_name")

```

The networks studied had species richness ranging between `r min(net_prop$n_s_t)` and `r max(net_prop$n_s_t)` when considering only the largest component in each network). 
As shown by the network asymmetry *AS* [@bluthgen_specialization_2007], the networks had a low ratio of plants to pollinators overall. 
Furthermore, the networks had relatively low levels of nestedness [when measured using the quantitative version of the NODF index; @almeida-neto_straightforward_2011]. Details for each network can be found in the Table \@ref(tab:table-network-properties).

```{r table-network-properties, results = "asis", sanitize = FALSE}

net_prop %>%
	dplyr::select(-net_name, -count, -net) %>%
	dplyr::filter(study != "ballantyne") %>%
	dplyr::arrange(study, site, inv) %>% 
	dplyr::mutate(invader = dplyr::case_when(
				 	invader == "car" ~ "\\textit{Carpobrotus affine}",
				 	invader == "op" ~ "\\textit{Opuntia stricta}",
				 	invader == "imp" ~ "\\textit{Impatients grandulifera}",
				 	TRUE ~ "—"
				 ),
				 invader = dplyr::if_else(inv, invader, "—")) %>%
	dplyr::mutate(site = rep(1:n_distinct(site), each = 2),
				 inv = dplyr::if_else(inv, "yes", "no"),
				 study = dplyr::case_when(
				 	study == "bartomeus" ~ "Cap de Creus, Spain",
				 	TRUE ~ "Bristol, United Kingdom"
				 )) %>% 
  dplyr::select(site, invader, n_s_t, n_sp, n_pla, n_pol, connectance, web.asymmetry, weighted.NODF, study) %>%
  dplyr::rename_("$R$" = "n_s_t",
					"$n_p$" = "n_pla",
					"$n_a$" = "n_pol",
					"location" = "study",
					"$n_s$" = "n_sp",
					"$c$"= "connectance", 
					"NODF" = "weighted.NODF",
					# "$\\bar{a}$" = "interaction.strength.asymmetry",
					"$AS$" = "web.asymmetry") %>%
	xtable::xtable(caption = "Properties of the analysed plant-pollinator communities. Here show the number of species ($n_s$), the number of plants ($n_p$), the number of pollinators ($n_a$), the network connectance ($c$), the network asymmetry ($AS$), and the network nestedness (NODF index). All properties correspond to the network's largest component. British networks were assembled by Lopezaraiza-Mikel et al. (2007), Spanish were networks assembled by Bartomeus et al. (2008).", 
         label= "tab:table-network-properties") %>%
	print(#floating.environment = "sidewaystable", 
		comment = FALSE, sanitize.text.function = function(x){x}, include.rownames = FALSE, caption.placement = "top", booktabs = T)

# knitr::kable(meta)
```

# References

### 2018-04-28 code/compile_pdf.R

@@ -1,0 +1,31 @@
+render_pdf <- function(rmd_file, output_file, clean_md = FALSE, clean_tex = FALSE, quiet = TRUE){
+  
+  output_tex <- paste0(tools::file_path_sans_ext(rmd_file), ".tex")
+  rmarkdown::render(rmd_file, 
+                    output_file = output_tex,
+                    output_dir = dirname(rmd_file),
+                    intermediates_dir = dirname(rmd_file),
+                    clean = clean_md,
+                    quiet = quiet)
+  
+  compile_pdf(output_tex,
+              output_file,
+              clean = clean_tex)
+}
+
+compile_pdf <- function(file_in, file_out, clean) {
+  
+  tinytex.output_dir <- getOption("tinytex.output_dir")
+  tinytex.engine_args <- getOption("tinytex.engine_args")
+  on.exit({
+    options(tinytex.output_dir = tinytex.output_dir, 
+            tinytex.engine_args = tinytex.engine_args)
+  })
+  
+  options(tinytex.output_dir = "paper", 
+          tinytex.engine_args = "'--output-directory=paper'")
+  
+  tinytex::latexmk(file_in,
+                   pdf_file = file_out,
+                   clean = clean)
+}

### 2018-04-28 main.R

@@ -42,7 +42,13 @@ basic_analysis_plan <- drake::drake_plan(
   strings_in_dots = "literals"
 )
 
+reporting_plan <- drake::drake_plan(
+  render_pdf(drake::knitr_in('paper/supp-info.Rmd'), 
+             drake::file_out('paper/supp-info.pdf'), clean_md = FALSE),
+  render_pdf(drake::knitr_in('paper/manuscript.Rmd'), 
+             drake::file_out('paper/manuscript.pdf'), clean_md = FALSE)
+)
 
-project_plan <- rbind(read_data_plan, basic_analysis_plan)
+project_plan <- rbind(read_data_plan, basic_analysis_plan, reporting_plan)
 project_config <- drake::drake_config(project_plan)
 drake::make(project_plan, config = project_config)

### 2018-05-02 paper/manuscript.Rmd
Define maximum matching

@@
 In classic control theory, determining wether this system is controllable or not can easily be achieved by checking that its controllability matrix $R= [ \begin{matrix}B & AB & A^{2}B & ...& A^{n-1}B\end{matrix} ]$ has full rank.
-In complex systems, however, employing this rank condition, or numerical approximations of it, is unfeasible because it is hard to fully parameterize *A* and *B*. 
+In complex systems, however, employing this rank condition, or numerical approximations of it, is unfeasible because it is hard to fully parameterize *A* and *B* (either the weights of the links change over time or because they are difficult to measures).
 Here we use an approach based on structural controllability, which assumes that we are confident that the elements of *A* and *B* have either non-zero or zero values (there is an interaction or not), but that we less sure about the precise magitude of the non-zero values [@lin_structural_1974].
@@
 Naively, any ecological community (and any system for that matter) could be controlled if we control the state of every species independently. 
-Such approach is typically unpractical so we are interested in finding a minimum driver node set (effectively finding *B*) with which to make the system contr
+Such approach is typically unpractical, we are instead interested in finding a minimum driver node set (effectively finding *B*) with which to make the system controllable. 
+However, a brute force search of this minimum driver node set is computationally prohibitive for most networks as it involves the evaluation of $2^N$ different controllability matrices. 
+We employ a recently developed approach that shows that the control problem of finding the minimum driver node set can be mapped into a purely graph theoretic problem: maximum matching [@liu_controllability_2011; @liu_control_2016].
 
-Controllability is this
-But is hard to calculate.
-Therefore we use recent advances that show that it can be calculated using maximum matching algorithms.
+Strictly speaking, a matching in an unweighted directed graph is defined as a set of links that do not share a common start or end nodes, a node is matched if its at the end of a matched link and unmatched if not, and the largest possible matching is called maximum  matching.
+Maximum matching is a widely studied topic in graph theory and has been used in multiple real life applications, from dating apps and wireless communications to transplant donations and peer to peer file sharing.
+Although seemingly unrelated, maximum matching is also connected to the controllability of a network because, as recently shown [@liu_controllability_2011], a matching can be decomposed into a set of paths that reveal how the control signal flows across the links in a network to reach every node that compose it.
+Unmatched nodes are the beginning of 
+The result is that the minimum driver node set corresponds exactly to the *unmatched* nodes, those that which the control signal
+
+to can be decomposed into a set of paths
 

### 2018-05-02 paper/manuscript.Rmd
Small edits to methods

@@
 
-We used ten paired pollination communities to test the control theoretic approach.
+We used ten paired pollination communities to apply the control theoretic approach.
 Each community pair was composed of a community invaded by a plant and a community free of the invasive species. 
@@
 
-The first step before applying methods of control theory is to construct a directed network that can provide an indication of the extent to which species affect each others abundance. 
-In some ecological networks, establishing the directionality can appear relatively straightforward, for example when links represent biomass transfer or energy flow [@isbell_human_2013]. 
+The first step before applying methods of control theory is to construct a directed network that is able to provide an indication of the extent to which species affect each others abundance. 
+In some ecological networks, establishing the directionality can be relatively straightforward, for example when links represent biomass transfer or energy flow [@isbell_human_2013]. 
 In pollination networks, however, this directionallity is less obvious as both species can in theory benefit from the interaction. 

### 2018-05-03 paper/manuscript.Rmd
Finish maximum matching explanation

@@
 
-Strictly speaking, a matching in an unweighted directed graph is defined as a set of links that do not share a common start or end nodes, a node is matched if its at the end of a matched link and unmatched if not, and the largest possible matching is called maximum  matching.
-Maximum matching is a widely studied topic in graph theory and has been used in multiple real life applications, from dating apps and wireless communications to transplant donations and peer to peer file sharing.
-Although seemingly unrelated, maximum matching is also connected to the controllability of a network because, as recently shown [@liu_controllability_2011], a matching can be decomposed into a set of paths that reveal how the control signal flows across the links in a network to reach every node that compose it.
-Unmatched nodes are the beginning of 
-The result is that the minimum driver node set corresponds exactly to the *unmatched* nodes, those that which the control signal
-
-to can be decomposed into a set of paths
-
-A maximum matching is this. 
-And can be calculatid this way. 
-And gives this information. 
-But its not unique.
-This can provide extra information. 
-Therefore we calculate them all.
+Maximum matching is a widely studied topic in graph theory and is commonly used in multiple applications, from dating apps and wireless communications to organ transplant allocation and peer to peer file sharing.
+A matching in an unweighted directed graph is as a set of links that do not share a common start or end nodes. 
+A node is said to be superior if it is at the beginning of a matched link and called matched if it is at the end. 
+Finally, the largest possible matching is called maximum matching. 
+These definitions, however offer little insight about how maximum matching is related to structural controllability. 
+The key is to note that these definitions imply that a matched node can have only one matched link pointing to it, and similarly a superior node can have at most one link leaving from it. 
+The result is that a matching can actually be decomposed into a set of paths that reveal how a control signal can flow across the links in a network to reach every node that compose it. 
+And so, as recently shown [@liu_controllability_2011], the minimum driver node set corresponds exactly to the *unmatched* nodes, those that are not controlled by other nodes in the network. 
+The algorithm we use to find a maximum matching in a network is fully detailed in the Supplementary Information Section XX.
 

### 2018-05-03 paper/manuscript.Rmd
Explain Nd to measure controllability

@@
 And so, as recently shown [@liu_controllability_2011], the minimum driver node set corresponds exactly to the *unmatched* nodes, those that are not controlled by other nodes in the network.
-The algorithm we use to find a maximum matching in a network is fully detailed in the Supplementary Information Section XX.
+
+## Differences between invaded and uninvaded networks
+
+Our first main objective is to investigate whether the controllability of a community is associated to invasion status or not. 
+Finding out exactly, how difficult is to control a network depends strongly on the particularities of the desired control trayectory as well as the dynamical relationpip between nodes. 
+However, we are interested in understanding the controllability of a network in a more general sense, such that it can be applied even when the precise control scenario is known only incompletely. 
+We instead employ an indicator that follows from our approach: the size of the minimum driver node set. 
+This simple metric provides general indication of how difficult controlling a network might be, as systems that require a large number of external inputs to be fully controlled are intuitively more difficult or costly to manage.
+Specifically, following the structural controllability literature, we use the size of the minimum driver node set relative to the total number of nodes $n_D = \frac{D}{S}$ as a measure of the extent to which the network structure can be harnessed to control the community.
+In an ecological context, external inputs can be thought of as management interventions that modify the abbundance of a particular species. 
+For instance, achieving full control in a "network" in which species do not interact at all is relatively difficult as we would require an intervention for every single species. 
+Conversely, the structure of a linear trophic chain can be harnessed to achieve full control using just one intervention targeted the top species; the control signal would then cascade trough the trophic levels and reach other species in the community.
 

### 2018-05-03 paper/manuscript.Rmd
Controllability models

@@
 - \usepackage{geometry}
-- \geometry{right=3in,marginparwidth=2.5in}
+# - \geometry{right=3in,marginparwidth=2.5in}
 - \usepackage{setspace}
@@
 
+The technical details of the algorithm we use to find a maximum matching in a network can be found in the Supplementary Information Section XX.
+
 ## Differences between invaded and uninvaded networks
@@
 
+After finding the minimum driver node set in each of our networks we want to test whether invasion status or other predictors are correlated to this metric of controllability. 
+We therefore use a set of generalised linear models (with binomial error structure) to investigate the effect of invasion status while also including covariates related to species richness, since one might naively expect to see a negative relationship between richness and controllability [@menge_indirect_1995].
+These covariates included the total number of species, plant richness, pollinators richness, the ratio of plant to pollinator richness, the link density (connectance), and the study site (as a two-level factor).
+
 # References

### 2018-05-03 paper/supp-info.Rmd
Xtable unneeded

@@
                       warning = FALSE)
-options(xtable.comment = FALSE, 
-        xtable.caption.placement = 'bottom',
-        xtable.size = 'small',
-        booktabs = TRUE)
 ```
@@
 					"$AS$" = "web.asymmetry") %>% 
-	xtable::xtable(caption = "Properties of the analysed plant-pollinator communities.
+  knitr::kable(escape = FALSE, booktabs = TRUE, digits = 2, caption = "Properties of the analysed plant-pollinator communities.
 Here show the number of species ($n_s$), the number of plants ($n_p$), the number of pollinators ($n_a$), the network connectance ($c$), the network asymmetry ($AS$), and the network nestedness (NODF index).
@@
 (2007), Spanish were networks assembled by Bartomeus et al.
-(2008).",
-         label= "tab:table-network-properties") %>%
-	print(#floating.environment = "sidewaystable", 
-		comment = FALSE, sanitize.text.function = function(x){x}, include.rownames = FALSE, caption.placement = "top", booktabs = T)
-
-# knitr::kable(meta)
+(2008).")
 ```

### 2018-05-08 paper/manuscript.Rmd
References to the supplementary material

@@
 The structure of all these communities was defined by the pollinator visitation frequency, which has been shown to be an appropriate surrogate for interspecific effects in pollination networks [@vazquez_interaction_2005; @bascompte_asymmetric_2006].
-Full details about the empirical networks, the implications of using visitation frequency to quantify the strength of the associations, and the sensitivity of the control theoretic approach to undersampling of the interactions can be found in the Supplementary materials SX.
+Full details about the empirical networks, the implications of using visitation frequency to quantify the strength of the associations, and the sensitivity of the control theoretic approach to undersampling of the interactions can be found in the supplementary information section \@ref(S-empirical-networks), XX, and XX.
 
@@
 Here we use an approach based on structural controllability, which assumes that we are confident that the elements of *A* and *B* have either non-zero or zero values (there is an interaction or not), but that we less sure about the precise magitude of the non-zero values [@lin_structural_1974].
-Essentially controllability is translated into a topological problem: a network is controllable if there are no inaccessible nodes—nodes without incoming links—or dilations—*expansions* of the network (Fig X).
+Essentially controllability is translated into a topological problem: a network is controllable if there are no inaccessible nodes—nodes without incoming links—or dilations—*expansions* of the network (see supplementary information section  \@ref(S-structural-controllability) for more details).
 
@@
 
-The technical details of the algorithm we use to find a maximum matching in a network can be found in the Supplementary Information Section XX.
+The technical details of the algorithm we use to find a maximum matching in a network can be found in the supplementary information section \@ref(S-one-maximum-matching).
 

### 2018-05-09 paper/manuscript.Rmd
Add structural controllability figure in manuscript

@@
 
+```{r, fig.cap="Consider the ", fig.height= 1.5, fig.width=3.5}
+drake::loadd(en_structural)
+
+# wether to save it as a pdf (for testing purposes)
+out_pdf <- F
+
+# format networks for plotting
+formated_en_structural <- en_structural %>%
+  purrr::map(~ fancify_vertex_name(.)) %>%
+  purrr::map(~ add_property(., element = "edge", attr_name = "color", 'TRUE ~ "black"')) %>%
+  purrr::map(~ add_property(., element = "edge", attr_name = "color", "type == 'a' ~ 'black'", "TRUE ~ 'azure4'")) %>%
+  purrr::map(~ add_property(., element = "vertex", attr_name = "color", "type == 'a' ~ 'white'", "TRUE ~ 'white'")) %>%
+  purrr::map(~ add_property(., element = "vertex", attr_name = "frame.color", "type == 'a' ~ 'black'", "TRUE ~ 'white'")) %>%
+  purrr::map(~ add_property(., element = "vertex", attr_name = "shape", "type == 'a' ~ 'circle'", "TRUE ~ 'square'")) %>%
+  purrr::map(~ add_property(., element = "vertex", attr_name = "size", "type == 'a' ~ 55", "TRUE ~ 25")) %>%
+  purrr::map(~ add_property(., element = "vertex", attr_name = "label.cex", "TRUE ~ 1")) %>%
+  purrr::map(~ add_property(., element = "vertex", attr_name = "label.color", "TRUE ~ 'black'"))
+
+if(out_pdf) pdf("test.pdf", width = 3.5, height = 1.5, paper='special')
+
+# make graphics device layout one row on top for headings, one column on the
+# left for headings and one in the middle for separator line
+layout(matrix(c(8,1,7,2,
+                9,3,7,4,
+                10,5,7,6), nrow = 3, ncol = 4, byrow = TRUE),
+       heights= c(0.25, 1, 1), 
+       widths = c(0.2, 1, 0.05, 1))
+par(mar=c(0.0,0,0,0), bg = "white", xpd = NA)
+
+# 1
+plot.new()
+text(0.5,0.25, "not controllable", adj = c(0.5,0), font = 2, cex = 0.9)
+
+# 2
+plot.new()
+text(0.5,0.25, "controllable", adj = c(0.5,0), font = 2, cex = 0.9)
+
+# 3-6
+for (i in 2:length(formated_en_structural)){
+  set.seed(5)
+  types <- igraph::V(formated_en_structural[[i]])$type ==
+    dplyr::first(igraph::V(formated_en_structural[[i]])$type)
+  l <- igraph::layout_as_bipartite(formated_en_structural[[i]], types) %>%
+    rescale_layout(xlim = c(-1.75, 1.75), ylim = c(-0.6, 0.6))
+  plot_examples(formated_en_structural[[i]], 
+                vertex.size = 45,
+                layout = l,
+                frame = F, 
+                rescale = F, 
+                margin = rep(0, 4))
+}
+
+# 7
+plot.new()
+segments(0,0,0,1, lty = 2, lwd = 0.5)
+# 8
+plot.new()
+# 9
+plot.new()
+text(0.5,0.5, "inaccessible\nnode", adj = c(0.5,0.5), font = 1, cex = 0.9, srt = 90)
+# 10
+plot.new()
+text(0.5,0.5, "dilation", adj = c(0.5,0.5), font = 1, cex = 0.9, srt = 90)
+
+if(out_pdf) dev.off()
+
+```
+
 We are often able to estimate *A* in ecological networks, as it represents the interactions between species. 

### 2018-05-09 main.R

@@ -42,6 +42,10 @@ basic_analysis_plan <- drake::drake_plan(
   strings_in_dots = "literals"
 )
 
+example_plots_plan <- drake::drake_plan(
+  en_structural = example_ntw_structural()
+)
+
 reporting_plan <- drake::drake_plan(
   render_pdf(drake::knitr_in('paper/supp-info.Rmd'), 
              drake::file_out('paper/supp-info.pdf'), clean_md = FALSE),
@@ -49,6 +53,6 @@ reporting_plan <- drake::drake_plan(
              drake::file_out('paper/manuscript.pdf'), clean_md = FALSE)
 )
 
-project_plan <- rbind(read_data_plan, basic_analysis_plan, reporting_plan)
+project_plan <- rbind(read_data_plan, basic_analysis_plan, example_plots_plan, reporting_plan)
 project_config <- drake::drake_config(project_plan)
 drake::make(project_plan, config = project_config)

### 2018-05-09 paper/supp-info.Rmd
Update looks of empirical data table in supp info

@@
 				 )) %>% 
-  dplyr::select(site, invader, n_s_t, n_sp, n_pla, n_pol, connectance, web.asymmetry, weighted.NODF, study) %>%
-  dplyr::rename_("$R$" = "n_s_t",
+  dplyr::select(site, invader, n_sp, n_pla, n_pol, connectance, web.asymmetry, weighted.NODF, study) %>%
+  dplyr::rename_(
+    # "$R$" = "n_s_t",
 					"$n_p$" = "n_pla",
@@
 					"$AS$" = "web.asymmetry") %>% 
-  knitr::kable(escape = FALSE, booktabs = TRUE, digits = 2, caption = "Properties of the analysed plant-pollinator communities.
+  knitr::kable(escape = FALSE, 
+               booktabs = TRUE, 
+               digits = 2, 
+               linesep = c("", "\\addlinespace"),
+               caption = "Properties of the analysed plant-pollinator communities.
 Here show the number of species ($n_s$), the number of plants ($n_p$), the number of pollinators ($n_a$), the network connectance ($c$), the network asymmetry ($AS$), and the network nestedness (NODF index).

### 2018-05-10 paper/manuscript.Rmd
Aesthetic changes to structural example plot

--- 2018-05-08 paper/manuscript.Rmd
@@
 
+```{r, fig.cap="Consider the ", fig.height= 1.5, fig.width=3.5}
+drake::loadd(en_structural)
+
+# wether to save it as a pdf (for testing purposes)
+out_pdf <- F
+
+# format networks for plotting
+formatted_en_structural <- en_structural %>%
+  purrr::map(~ fancify_vertex_name(.)) %>%
+  purrr::map(~ add_property(., element = "edge", attr_name = "color", 'TRUE ~ "black"')) %>%
+  purrr::map(~ add_property(., element = "edge", attr_name = "color", "type == 'a' ~ 'black'", "TRUE ~ 'azure4'")) %>%
+  purrr::map(~ add_property(., element = "vertex", attr_name = "color", "type == 'a' ~ 'white'", "TRUE ~ 'white'")) %>%
+  purrr::map(~ add_property(., element = "vertex", attr_name = "frame.color", "type == 'a' ~ 'black'", "TRUE ~ 'white'")) %>%
+  purrr::map(~ add_property(., element = "vertex", attr_name = "shape", "type == 'a' ~ 'circle'", "TRUE ~ 'square'")) %>%
+  purrr::map(~ add_property(., element = "vertex", attr_name = "size", "type == 'a' ~ 55", "TRUE ~ 25")) %>%
+  purrr::map(~ add_property(., element = "vertex", attr_name = "label.cex", "TRUE ~ 1")) %>%
+  purrr::map(~ add_property(., element = "vertex", attr_name = "label.color", "TRUE ~ 'black'"))
+
+if(out_pdf) pdf("test.pdf", width = 3.5, height = 1.5, paper='special')
+
+# make graphics device layout one row on top for headings, one column on the
+# left for headings and one in the middle for separator line
+layout(matrix(c(8,1,7,2,
+                9,3,7,4,
+                10,5,7,6), nrow = 3, ncol = 4, byrow = TRUE),
+       heights= c(0.25, 1, 1), 
+       widths = c(0.2, 1, 0.05, 1))
+par(mar=c(0.0,0,0,0), bg = "white", xpd = NA)
+
+# 1
+plot.new()
+text(0.5,0.25, "not controllable", adj = c(0.5,0), font = 2, cex = 0.9)
+
+# 2
+plot.new()
+text(0.5,0.25, "controllable", adj = c(0.5,0), font = 2, cex = 0.9)
+
+# 3-6
+for (i in 2:length(formatted_en_structural)){
+  set.seed(5)
+  types <- igraph::V(formatted_en_structural[[i]])$type ==
+    dplyr::first(igraph::V(formatted_en_structural[[i]])$type)
+  l <- igraph::layout_as_bipartite(formatted_en_structural[[i]], types) %>%
+    rescale_layout(xlim = c(-1.75, 1.75), ylim = c(-0.6, 0.6))
+  plot_examples(formatted_en_structural[[i]], 
+                layout = l,
+                frame = F, 
+                rescale = F, 
+                margin = rep(0, 4), 
+                edge.arrow.size = 0.4,
+                edge.label.family = "sans", 
+                vertex.label.family = "sans")
+}
+
+# 7
+plot.new()
+segments(0,0,0,1, lty = 2, lwd = 0.5)
+# 8
+plot.new()
+# 9
+plot.new()
+text(0.5,0.5, "inaccessible\nnode", adj = c(0.5,0.5), font = 1, cex = 0.9, srt = 90)
+# 10
+plot.new()
+text(0.5,0.5, "dilation", adj = c(0.5,0.5), font = 1, cex = 0.9, srt = 90)
+
+if(out_pdf) dev.off()
+
+```
+
 We are often able to estimate *A* in ecological networks, as it represents the interactions between species. 

### 2018-05-10 code/plot_ntw.R

@@ -50,7 +50,7 @@ add_vertex_edge <- function(x, vertex_name, vertex_type, edges_from, edges_to, e
 #' @param ... parameters for plot.igraph
 #'
 #'
-plot_examples <- function(x, edge.arrow.size = 0.5, margin = c(0,0,0,0), ...){
+plot_examples <- function(x, ...){
   igraph::plot.igraph(x, 
                       vertex.label = igraph::V(x)$name_fancy, 
                       vertex.label.cex = igraph::V(x)$label.cex,
@@ -59,13 +59,12 @@ plot_examples <- function(x, edge.arrow.size = 0.5, margin = c(0,0,0,0), ...){
                       vertex.color = igraph::V(x)$color,
                       # vertex.label.family = fam,
                       # vertex.label.color = l_c,
-                      # edge.label = round(E(.)$weight,1), 
+                      edge.width = igraph::E(x)$width,
+                      edge.label = igraph::E(x)$label,
+                      edge.label.x = igraph::E(x)$label.x,
+                      edge.label.color = igraph::E(x)$label.color,
+                      edge.label.font = igraph::E(x)$label.font,
                       # edge.label.family = fam,
-                      edge.label.color = igraph::E(x)$color,
-                      edge.curved = edge.curved,
-                      edge.arrow.size = edge.arrow.size,
-                      margin = margin, 
-                      layout = layout, 
                       ...)
 }
 

### 2018-05-10 code/bipartite_to_directed.R
Transform a bipartite network as directed

@@ -1,0 +1,91 @@
+
+#' Title
+#'
+#' @param x an incidence matrix or an igraph network. If an igraph network the higher level argument must be specified
+#' @param type type of directed links desired. Asymmetry produces a single
+#' @param higher_level 
+#'
+#' @return
+#' @export
+#'
+#' @examples
+as_directed_network <- function(x, 
+                                direction = c("asymmetry", "dependence", "top-down", "bottom-up"), 
+                                ties = c("both", "none", "top-down", "bottom-up"), higher_level){
+  # if is an igraph object construct an incidence matrix with the weights
+  if(class(x) == "igraph"){
+    types <- dplyr::data_frame(name = igraph::V(x)$name, type = igraph::V(x)$type)
+    x <- x %>% igraph::as_incidence_matrix(types = igraph::V(.)$type == higher_level, attr = "weight")
+  } else {
+    types <- dplyr::data_frame(name = c(rownames(x), colnames(x)), 
+                               type = c(rep(F, nrow(x)), rep(T, ncol(x))))
+  }
+  if(direction[1] == "top-down"){
+    y <- igraph::graph_from_incidence_matrix(x, directed = T, "in", weighted = T)
+  } else if(direction[1] == "bottom-up"){
+    y <- igraph::graph_from_incidence_matrix(x, directed = T, "out", weighted = T)
+  } else if(direction[1] %in% c("asymmetry", "dependence")){
+    y <- x %>%
+      bipartite::linklevel("dependence")
+    if(direction[1] == "asymmetry"){
+      y <- y %>% get_assymetry(ties = ties)
+    } 
+    y <- two_incidence_to_adjacency(y)
+    y <- igraph::graph_from_adjacency_matrix(y, mode = "directed", weighted = T)
+  }
+  y %>% 
+    assign_vertex_types(types)
+}
+
+assign_vertex_types <- function(x, types){
+  net_names <- dplyr::data_frame(name = igraph::V(x)$name)
+  net_name_type <- net_names %>% dplyr::inner_join(types, by = "name")
+  igraph::set_vertex_attr(x, "type", value = net_name_type$type)
+}
+
[…]

### 2018-05-10 paper/manuscript.Rmd
Make example direction networks

@@
 
+```{r, fig.cap="Consider the 2", fig.height= 0.9, fig.width=3.5}
+drake::loadd(en_direction)
+
+# wether to save it as a pdf (for testing purposes)
+out_pdf <- F
+
+# graph attributes
+formatted_en_direction <- en_direction  %>%
+  purrr::map(~ fancify_vertex_name(.)) %>%
+  purrr::map(~ add_property(., element = "edge", attr_name = "color", 'TRUE ~ "black"')) %>%
+  purrr::map(~ add_property(., element = "edge", attr_name = "label.color", 'TRUE ~ "black"')) %>%
+  purrr::map(~ add_property(., element = "edge", attr_name = "label.font", 'TRUE ~ 2')) %>%
+  purrr::map(~ add_property(., element = "vertex", attr_name = "color", "TRUE ~ 'white'")) %>%
+  purrr::map(~ add_property(., element = "vertex", attr_name = "frame.color", "TRUE ~ 'black'")) %>%
+  purrr::map(~ add_property(., element = "vertex", attr_name = "size", "TRUE ~ 55")) %>%
+  purrr::map(~ add_property(., element = "vertex", attr_name = "label.cex", "TRUE ~ 1")) %>%
+  purrr::map(~ add_property(., element = "vertex", attr_name = "label.color", "TRUE ~ 'black'"))
+formatted_en_direction[[1]] %<>%
+  igraph::set_edge_attr("label", value = igraph::E(.)$weight)
+formatted_en_direction[[2]] %<>%
+  igraph::set_edge_attr("label", value = "")
+
+if(out_pdf) pdf("test.pdf", width = 3.5, height = 0.9)
+
+# graph layout
+layout(matrix(c(1,5,2,
+                3,5,4), nrow = 2, ncol = 3, byrow = TRUE),
+       heights= c(0.35, 1), 
+       widths = c(1, 0.05, 1))
+par(mar=c(0.0,0,0,0), bg = "white", xpd = NA)
+
+# 1
+plot.new()
+text(0.5,0.25, "visitation network", adj = c(0.5,0), font = 2, cex = 0.9)
+
+# 2
+plot.new()
+text(0.5,0.25, "direction of control", adj = c(0.5,0), font = 2, cex = 0.9)
+
+# network layout
+l <- matrix(c(1,0,
+              2,0,
+              3,0,
+              1.5, 1,
+              2.5, 1), nrow = 5, ncol = 2, byrow = T)
+
+# 3-4
+for(i in 1:length(formatted_en_direction)){
+   set.seed(3)
+  types <- igraph::V(formatted_en_direction[[i]])$type ==
+    dplyr::first(igraph::V(formatted_en_direction[[i]])$type)
+  l <- l %>%
+    rescale_layout(xlim = c(-1, 1) * 1.75, ylim = c(-0.6, 0.7))
+  plot_examples(formatted_en_direction[[i]], 
+                layout = l, rescale = F, frame = F, margin = rep(0, 4), 
+                edge.arrow.size = 0.4,
+                edge.label.family = "sans", 
+                vertex.label.family = "sans")
+}
+
+# 5
+plot.new()
+segments(0,0,0,1, lty = 2, lwd = 0.5)
+
+if(out_pdf) dev.off()
+
+```
+
 After constructing the directed network, we can now calculate the controllability of the different networks and investigate wether there are differences between invaded and uninvaded communities.

### 2018-05-10 code/example_networks.R

@@ -31,3 +31,18 @@ example_ntw_structural <- function(){
   
 }
 
+
+example_ntw_directions <- function(){
+  en_vis <- list(
+    edges = dplyr::data_frame(from = c("p_1", "p_2", "p_2", "p_3", "p_3"), 
+                              to = c("a_1", "a_1", "a_2", "a_2", "a_1"), 
+                              weight = c(1, 2, 5, 1, 1)), 
+    vertex = dplyr::data_frame(name = c("p_1", "p_2", "p_3", "a_1", "a_2"), 
+                               type = c("p", "p", "p", "a", "a"))
+  )
+  
+  en_bip <- igraph::graph_from_data_frame(en_vis$edges, directed = F, vertices = en_vis$vertex) 
+  en_dir <- as_directed_network(en_bip, direction = "asymmetry", ties = "both", higher_level = "a")
+  
+  list(en_bip, en_dir)
+}

### 2018-05-10 main.R

@@ -43,7 +43,8 @@ basic_analysis_plan <- drake::drake_plan(
 )
 
 example_plots_plan <- drake::drake_plan(
-  en_structural = example_ntw_structural()
+  en_structural = example_ntw_structural(),
+  en_direction = example_ntw_directions()
 )
 
 reporting_plan <- drake::drake_plan(

### 2018-05-10 paper/manuscript.Rmd
Copy paste some content

@@
 In complex systems, however, employing this rank condition, or numerical approximations of it, is unfeasible because it is hard to fully parameterize *A* and *B* (either the weights of the links change over time or because they are difficult to measures).
-Here we use an approach based on structural controllability, which assumes that we are confident that the elements of *A* and *B* have either non-zero or zero values (there is an interaction or not), but that we less sure about the precise magitude of the non-zero values [@lin_structural_1974].
-Essentially controllability is translated into a topological problem: a network is controllable if there are no inaccessible nodes—nodes without incoming links—or dilations—*expansions* of the network (see supplementary information section  \@ref(S-structural-controllability) for more details).
+Here we use an approach based on the structural controllability theorem [@lin_structural_1974], which assumes that we are confident that the elements of *A* and *B* have either non-zero or zero values (there is an interaction or not), but that we less sure about the precise magitude of the non-zero values.
+Using this structural approach we can find out the controllability of a system under almost all non-zero parameter realisations.
+In addition, a graphical interpretation of the structural controllability theorem enables us to translate the control problem into a topological one: a network is controllable if there are no inaccessible nodes—nodes without incoming links—or dilations—*expansions* of the network (see supplementary information section  \@ref(S-structural-controllability) for more details).
 
@@
 Naively, any ecological community (and any system for that matter) could be controlled if we control the state of every species independently. 
-Such approach is typically unpractical, we are instead interested in finding a minimum driver node set (effectively finding *B*) with which to make the system controllable. 
+Such approach is typically unpractical. 
+We are instead interested in finding a minimum driver node set (effectively finding *B*) with which to make the system controllable. 
 However, a brute force search of this minimum driver node set is computationally prohibitive for most networks as it involves the evaluation of $2^N$ different controllability matrices. 
@@
 Maximum matching is a widely studied topic in graph theory and is commonly used in multiple applications, from dating apps and wireless communications to organ transplant allocation and peer to peer file sharing.
-A matching in an unweighted directed graph is as a set of links that do not share a common start or end nodes. 
+A matching in an unweighted directed graph is defined as a set of links that do not share a common start or end nodes. 
 A node is said to be superior if it is at the beginning of a matched link and called matched if it is at the end. 
 Finally, the largest possible matching is called maximum matching. 
-These definitions, however offer little insight about how maximum matching is related to structural controllability. 
+These definitions, however, offer little insight about how maximum matching is related to structural controllability. 
 The key is to note that these definitions imply that a matched node can have only one matched link pointing to it, and similarly a superior node can have at most one link leaving from it. 
@@
 These covariates included the total number of species, plant richness, pollinators richness, the ratio of plant to pollinator richness, the link density (connectance), and the study site (as a two-level factor).
+In addition, we also explored whether real networks differ in their architecture from random ones in a concerted way; further details about this procedure can be found in the supplementary information section \@ref(S-randomisations).
+
+## Species roles
+
+Our second key question is related to how species differ in their ability to drive the population dynamics of the community. 
+Ecologically, these differences are relevant because resources and data are limited, and therefore full control is unfeasible. 
+We are mostly interested in two specific aspects.
+First how species differ in their relative , second, how species
+
+is management interventions should be focused on the set of species that might provide the largest impact. 
+While calculating the size of the minimum drive node set can measure the controllability of an ecological community, it does not provide information about the role that particular species play.
+
+Moreover, maximum matchings in a network are often not unique, and each maximum matching indicates unique paths that can potentially be used to control the network. 
+We harness this property and use a network's complete set of maximum matchings to characterise each species' relative importance in driving the state of the community. 
+One possibility is to characterise a species by the frequency *f~D~* with which it is classified as a driver node within this set of matchings.
+However, the profile of our networks indicates that a large proportion of species were classified as driver nodes because of external interventions required to achieve **full** controllability and not because they influence the abundance of other species (Supporting Information S2).
+Furthermore, the precise role of driver nodes is more ambiguous when full control is unfeasible or undesired—often the case in ecological settings.
+We therefore also calculate the frequency *f~S~* with which a species is classified as a superior node since this is the frequency with which they form part of possible control paths.
+
+Most commonly, structural controllability assumes unweighted networks—links exist or not, and hence *f~D~* and *f~S~* can be calculated by computing all possible maximum-cardinality matchings. 
+However, we take the link weights into account when calculating the matchings here because the weights can reveal significant ecological patterns and processes that might be undetectable in unweighted networks [@Scotti2007; @Tylianakis2007; @Vazquez2007; @Kaiser-Bunbury2010a].
+Additionally, species *A* may interact with both species *B* and *C* but depends strongly on *B* and only weakly on *C*. 
+Intuitively, a management intervention designed to indirectly modify the abundance of species *A* is more likely to succeed if the abundance of *B*, rather than *C*, is directly controlled.
+A complication of including the interaction weight when calculating the maximum matching, however, is that empirical interaction strengths are to some extent stochastic and depend on proximate factors such as sampling method and intensity [@Gibson2011].
+We overcome this issue by calculating all maximal cardinality matchings and then ranking them by their matching weight. 
+By following this approach, we effectively give priority to the species that participate in the pathways that potentially have the largest impact on the community while acknowledging the limitations associated with sampling and its potential restrictions [@Jordano2016].
+
+Our second key question was related to how species differ in their ability to drive the population dynamics of the community. 
+To quantify this importance, we computed all maximal cardinality matchings in each network. 
+We then calculated the frequency with which each species *i* was a driver (*f~D~*) or a superior node (*f~S~*) in the set of matchings that had a matching weight greater or equal to 0.8 times the weight of the maximum matching.
+We selected this threshold as it provided a high agreement between networks quantified by visitation and pollination efficiency as well as between our weighting/directionality assumptions; however, the choice of this threshold had a negligible impact on any results (Supporting Information S8).
+Details about the computational procedure to find all maximal cardinality matchings of a network can be found in Supporting Information S1 and Figure S2.
 

### 2018-05-10 paper/supp-info.Rmd
Add skeleton
Copy paste some content

@@
 
+# Structural controllability {#structural-controllability}
+
+Structural controllability avoids the limitation of not knowing the exact values of the matrices *A* and *B*. 
+The graphical interpretation of structural controllability can be summed up in two conditions for controllability: A system is controllable if there
+
+The overall objective of control theory is to be able to steer a system from one state to another in finite time. 
+However, in complex systems like ecological communities, the large number of nodes and interactions as well as their non-linear dynamics render its control extremely challenging.
+On one theoretical extreme, for instance, any ecological community could be fully controlled if we control the state of every species independently. 
+On another, the mechanisms of self-regulation and the multiple feedback cycles found in ecological communities mean it is also theoretically possible to control the whole community by directly modifying the state of just a *single* species [@Cowan2012; @Markovsky2013].
+Although mathematically correct, neither of these options are practical in real-world applications: the first because it is infeasible to design and implement interventions that modify the abundance of every single species in a community, and the second because the control signal might require unreasonably large amounts of time, energy, or unattainable rapid changes on the state [@Yan2012; @Motter2015].
+Here we explore an intermediate point between these two trivial solutions.
+
+In particular, we leverage the principle of species interdependence to find an intermediate set of *driver nodes* to control the network [@Liu2016]. 
+When we focus on net interspecific effects, it is possible to identify a minimum number of nodes the control of which can theoretically drive the state of every other node in the network to a desired configuration.
+Conveniently the information necessary to determine this minimum number of driver nodes *D* is fully contained in the network structure [@Kalman1963; @Liu2011; @Motter2015]. 
+Such a system can be described by $\frac{dx}{dt} = \mathbf{A}x + \mathbf{B}u(t)$, where the change of its state over time ($\frac{dx}{dt}$) depends on its current state *x* (for example, the species' abundances), an external time-varying input *u(t)* (the control signal), and two matrices *A* and *B*, which encode information about the network structure and how the species respond to the external input, respectively.
+If *S* is the number of species in the community, the matrix **A** has size $S \times S$ whereas the matrix **B** has size $S \times D$.
+
+The goal of structural controllability, which we employ here, is to use the information contained in **A** to generate a supportable estimate of **B** (and by extension *D*).
+This focus allows us to gain insight of the inherent controllability of a network, and the roles of the species that compose it, without being overly dependent on the particular choices of how the system dynamics are modelled or characterised.
+The trade-off of our approach is that, because of the assumption of linearity, structural controllability alone does not allow us to fully design the time-varying control signal *u(t)* that can drive the system from one particular equilibrium to another.
+Nevertheless, the lessons gained when assuming linearity---at both the network and the species level---are a prerequisite for eventually understanding nonlinear control [@Liu2011; @Liu2016].
+
+**Add info about cacti. Inaccessible nodes and dilations.**
+
+# Maximum matching
+
+Our approach to find the minumum number of driver nodes relies on finding maximum matchings. 
+We start with a directed network in which the direction of the link represents the direction of control (Figure \@ref(fig:fig-direction-of-control)a). 
+We then construct an alternative representation of the directed network in which each node of the directed network is represented by two nodes that indicate their outgoing and incoming links respectively (Figure \@ref(fig:fig-direction-of-control)b).
+Finding a maximum matching in this alternative representation is equivalent to finding the largest possible set of edges in which one node on the left-hand side is connected to at most one node on the right-hand side.
+To find the maximum matching we use the push-relabel algorithm implemented in `max_bipartite_matching` in the R package igraph 1.0.1 [@Csardi2006a]. 
+Once we have the matching (shown in the Figure \@ref(fig:fig-direction-of-control)b) it is then easy to identify the roles of each node in this representation: nodes on the left-hand side that are connected to a matched (purple) link are superior while those connected to a matched link on the right-hand side are matched.
+This information can then be mapped back to the original representation to identify the control paths and the driver nodes in the network (Figure \@ref(fig:fig-direction-of-control)c). 
+Figure \@ref(fig:fig-direction-of-control)d--f illustrate this approach for a network with bidirectional links.
+
+## Finding a single maximum matching {#one-maximum-matching}
+
+## Finding all possible maximum matchings
+
+## Finding all possible minimum driver node sets
+
+# Empirical vs. random expectation of controllability {#randomisations}
+
 # References

### 2018-05-11 paper/manuscript.Rmd
join direction and controllablity figures together and add caption

@@
 
+```{r prepare-graph-direction}
+drake::loadd(en_direction)
+# graph attributes
+formatted_en_direction <- en_direction  %>%
+  purrr::map(~ fancify_vertex_name(.)) %>%
+  purrr::map(~ add_property(., element = "edge", attr_name = "color", 'TRUE ~ "black"')) %>%
+  purrr::map(~ add_property(., element = "edge", attr_name = "label.color", 'TRUE ~ "black"')) %>%
+  purrr::map(~ add_property(., element = "edge", attr_name = "label.font", 'TRUE ~ 2')) %>%
+  purrr::map(~ add_property(., element = "vertex", attr_name = "color", "TRUE ~ 'white'")) %>%
+  purrr::map(~ add_property(., element = "vertex", attr_name = "frame.color", "TRUE ~ 'black'")) %>%
+  purrr::map(~ add_property(., element = "vertex", attr_name = "size", "TRUE ~ 55")) %>%
+  purrr::map(~ add_property(., element = "vertex", attr_name = "label.cex", "TRUE ~ 1")) %>%
+  purrr::map(~ add_property(., element = "vertex", attr_name = "label.color", "TRUE ~ 'black'"))
+
+formatted_en_direction[[1]] %<>%
+  igraph::set_edge_attr("width", value = igraph::E(.)$weight * 0.5)
+formatted_en_direction[[2]] %<>%
+  igraph::set_edge_attr("width", value = 1)
+
+direction_layout <- matrix(c(1,0,
+                             2,0,
+                             3,0,
+                             1.5, 1,
+                             2.5, 1), nrow = 5, ncol = 2, byrow = T)
+```
+
+```{r prepare-graph-structural}
+drake::loadd(en_structural)
+
+# format networks for plotting
+formatted_en_structural <- en_structural %>%
+  purrr::map(~ fancify_vertex_name(.)) %>%
+  purrr::map(~ add_property(., element = "edge", attr_name = "color", 'TRUE ~ "black"')) %>%
+  purrr::map(~ add_property(., element = "edge", attr_name = "lty", "type == 'a' ~ 1", "TRUE ~ 3")) %>%
+  purrr::map(~ add_property(., element = "vertex", attr_name = "color", "type == 'a' ~ 'white'", "TRUE ~ 'white'")) %>%
+  purrr::map(~ add_property(., element = "vertex", attr_name = "frame.color", "type == 'a' ~ 'black'", "TRUE ~ 'white'")) %>%
+  purrr::map(~ add_property(., element = "vertex", attr_name = "shape", "type == 'a' ~ 'circle'", "TRUE ~ 'square'")) %>%
+  purrr::map(~ add_property(., element = "vertex", attr_name = "size", "type == 'a' ~ 55", "TRUE ~ 45")) %>%
+  purrr::map(~ add_property(., element = "vertex", attr_name = "label.cex", "TRUE ~ 1")) %>%
+  purrr::map(~ add_property(., element = "vertex", attr_name = "label.color", "TRUE ~ 'black'"))
+```
+
+```{r example-network-common-plotting-par}
+plot_example_ntw <- function(x, ...){
+  plot_examples(x, rescale = F, 
+                frame = F, 
+                margin = rep(0, 4), 
+                edge.arrow.size = 0.4,
+                edge.label.family = "sans", 
+                vertex.label.family = "sans", ...)
+}
+
+```
+
 We used ten paired pollination communities to apply the control theoretic approach.
@@
 Previous research has shown that mutualistic interactions are often highly asymmetric in natural communities; in other words, if a plant species is largely dependent on a pollinator species, then that pollinator tends to depend rather weakly on the plant (or vice versa).
-By creating a directed link based on the asymmetry of their dependence we are able to generate a network that is consistent with the dynamics of the community while satisfyingh the requirements of structural controllability.
+We then create a directed link between species *i* and *j* when $d_{ij}-d_{ji} \geq 0$ to establish the most likely direction of control between a species pair (Figure \@ref(fig:fig-example-networks)a).
+By basing the direction of the links on the asymmetry of their dependence, we are able to generate a network that is consistent with the dynamics of the community while satisfyingh the requirements of structural controllability.
 
-```{r, fig.cap="Consider the 2", fig.height= 0.9, fig.width=3.5}
-drake::loadd(en_direction)
+```{r fig-example-networks, fig.width=3.5, fig.height=2.6, fig.cap="(a) To establish the direction of control we start with a weighted visitation network (right side).
+In this network, the width of the links correspond to the frequency of visitation.
+We then calculate the dependencies between species pairs and create a directed network (left side) in which the direction of the links correspond to the direction of the assymetry of their dependence.
+For instance, the population of plant $p_1$ is likely to be affected by the population of pollinator $a_1$ to a larger extent that the population of $a_1$ depends on $p_1$ because $a_1$ interacts more strongly with other species in the community; hence the direction of control between these two species can be simplyfied with a directed link from $a_1$ to $p_1$.
+(b) A system is structurally controllable if there are no inaccessible links or dilations.
+The network on the top left is not controllable because node $x_3$ is inaccessible from the input node $u_1$ in the system.
+The network in the bottom left is not controllable because there is a dilation in which node $x_2$ is being used to control two nodes simultaneously.
+Both systems can be made controllable by adding an extra input node (right panel)."}
+out_pdf <- F
+height1 <- 0.9
+height2 <- 1.5
 
-# wether to save it as a pdf (for testing purposes)
-out_pdf <- F
+if(out_pdf) pdf("test.pdf", width = 3.5, height = height1 + height2 + 0.2, paper='special')
 
-# graph attributes
-formatted_en_direction <- en_direction  %>%
-  purrr::map(~ fancify_vertex_name(.)) %>%
-  purrr::map(~ add_property(., element = "edge", attr_name = "color", 'TRUE ~ "black"')) %>%
-  purrr::map(~ add_property(., element = "edge", attr_name = "label.color", 'TRUE ~ "black"')) %>%
-  purrr::map(~ add_property(., element = "edge", attr_name = "label.font", 'TRUE ~ 2')) %>%
-  purrr::map(~ add_property(., element = "vertex", attr_name = "color", "TRUE ~ 'white'")) %>%
-  purrr::map(~ add_property(., element = "vertex", attr_name = "frame.color", "TRUE ~ 'black'")) %>%
-  purrr::map(~ add_property(., element = "vertex", attr_name = "size", "TRUE ~ 55")) %>%
-  purrr::map(~ add_property(., element = "vertex", attr_name = "label.cex", "TRUE ~ 1")) %>%
-  purrr::map(~ add_property(., element = "vertex", attr_name = "label.color", "TRUE ~ 'black'"))
-formatted_en_direction[[1]] %<>%
-  igraph::set_edge_attr("label", value = igraph::E(.)$weight)
-formatted_en_direction[[2]] %<>%
-  igraph::set_edge_attr("label", value = "")
+c(01,10,12,11,91,
+  90,13,12,14,91, 
+  80,80,80,80,80, 
+  02,20,28,21,93,
+  22,24,28,25,93,
+  23,26,28,27,93) %>%
+  dplyr::dense_rank() %>%
+  matrix(nrow = 6, ncol = 5, byrow = T) %>%
+  layout(heights = c(height1 * 0.25, height1 * 0.75, height1 * 0.2, height2 * 0.1, height2 * 0.45, height2 * 0.45),
+         widths = c(0.2, 1, 0.05, 1, 0.2))
+par(mar = rep(0,4), bg = "white")
 
-if(out_pdf) pdf("test.pdf", width = 3.5, height = 0.9)
-
-# graph layout
-layout(matrix(c(1,5,2,
-                3,5,4), nrow = 2, ncol = 3, byrow = TRUE),
-       heights= c(0.35, 1), 
-       widths = c(1, 0.05, 1))
-par(mar=c(0.0,0,0,0), bg = "white", xpd = NA)
-
-# 1
-plot.new()
-text(0.5,0.25, "visitation network", adj = c(0.5,0), font = 2, cex = 0.9)
-
-# 2
-plot.new()
-text(0.5,0.25, "direction of control", adj = c(0.5,0), font = 2, cex = 0.9)
-
-# network layout
-l <- matrix(c(1,0,
-              2,0,
-              3,0,
-              1.5, 1,
-              2.5, 1), nrow = 5, ncol = 2, byrow = T)
-
-# 3-4
+## LABELS
+# 01
+standalone_text("(a)", y = 0.75)
+# 02
+standalone_text("(b)", y = 0.75)
+## FIGURE A
+# 10
+standalone_text("visitation network", y = 0.25, adj = c(0.5,0), font = 2)
+# 11
+standalone_text("direction of control", y = 0.25, adj = c(0.5,0), font = 2)
+# 12
+standalone_vline(lty = 2)
+# 13-14
 for(i in 1:length(formatted_en_direction)){
-   set.seed(3)
-  types <- igraph::V(formatted_en_direction[[i]])$type ==
-    dplyr::first(igraph::V(formatted_en_direction[[i]])$type)
-  l <- l %>%
-    rescale_layout(xlim = c(-1, 1) * 1.75, ylim = c(-0.6, 0.7))
-  plot_examples(formatted_en_direction[[i]], 
-                layout = l, rescale = F, frame = F, margin = rep(0, 4), 
-                edge.arrow.size = 0.4,
-                edge.label.family = "sans", 
-                vertex.label.family = "sans")
+  l <- rescale_layout(direction_layout, xlim = c(-1, 1) * 1.75, ylim = c(-0.6, 0.7))
+  plot_example_ntw(formatted_en_direction[[i]], layout = l)
 }
-
-# 5
-plot.new()
-segments(0,0,0,1, lty = 2, lwd = 0.5)
+## FIGURE B
+# 20
+standalone_text("not controllable", y = 0.25, adj = c(0.5,0), font = 2)
+# 21
+standalone_text("controllable", y = 0.25, adj = c(0.5,0), font = 2)
+# 22
+standalone_text("inaccessible\nnode", srt = 90)
+# 23
+standalone_text("dilation", srt = 90)
+# 24-27
+for (i in 2:length(formatted_en_structural)){
+  types <- igraph::V(formatted_en_structural[[i]])$type == dplyr::first(igraph::V(formatted_en_structural[[i]])$type)
+  l <- igraph::layout_as_bipartite(formatted_en_structural[[i]], types) %>%
+    rescale_layout(xlim = c(-1.75, 1.75), ylim = c(-0.6, 0.6))
+  plot_example_ntw(formatted_en_structural[[i]], layout = l)
+}
+# 28
+standalone_vline(lty = 2)
+## DIV LINES
+# 80
+standalone_hline()
 
 if(out_pdf) dev.off()
-
 ```
@@
 Using this structural approach we can find out the controllability of a system under almost all non-zero parameter realisations.
-In addition, a graphical interpretation of the structural controllability theorem enables us to translate the control problem into a topological one: a network is controllable if there are no inaccessible nodes—nodes without incoming links—or dilations—*expansions* of the network (see supplementary information section  \@ref(S-structural-controllability) for more details).
-
-```{r, fig.cap="Consider the ", fig.height= 1.5, fig.width=3.5}
-drake::loadd(en_structural)
-
-# wether to save it as a pdf (for testing purposes)
-out_pdf <- F
-
-# format networks for plotting
-formatted_en_structural <- en_structural %>%
-  purrr::map(~ fancify_vertex_name(.)) %>%
-  purrr::map(~ add_property(., element = "edge", attr_name = "color", 'TRUE ~ "black"')) %>%
-  purrr::map(~ add_property(., element = "edge", attr_name = "color", "type == 'a' ~ 'black'", "TRUE ~ 'azure4'")) %>%
-  purrr::map(~ add_property(., element = "vertex", attr_name = "color", "type == 'a' ~ 'white'", "TRUE ~ 'white'")) %>%
-  purrr::map(~ add_property(., element = "vertex", attr_name = "frame.color", "type == 'a' ~ 'black'", "TRUE ~ 'white'")) %>%
-  purrr::map(~ add_property(., element = "vertex", attr_name = "shape", "type == 'a' ~ 'circle'", "TRUE ~ 'square'")) %>%
-  purrr::map(~ add_property(., element = "vertex", attr_name = "size", "type == 'a' ~ 55", "TRUE ~ 25")) %>%
-  purrr::map(~ add_property(., element = "vertex", attr_name = "label.cex", "TRUE ~ 1")) %>%
-  purrr::map(~ add_property(., element = "vertex", attr_name = "label.color", "TRUE ~ 'black'"))
-
-if(out_pdf) pdf("test.pdf", width = 3.5, height = 1.5, paper='special')
-
-# make graphics device layout one row on top for headings, one column on the
-# left for headings and one in the middle for separator line
-layout(matrix(c(8,1,7,2,
-                9,3,7,4,
-                10,5,7,6), nrow = 3, ncol = 4, byrow = TRUE),
-       heights= c(0.25, 1, 1), 
-       widths = c(0.2, 1, 0.05, 1))
-par(mar=c(0.0,0,0,0), bg = "white", xpd = NA)
-
-# 1
-plot.new()
-text(0.5,0.25, "not controllable", adj = c(0.5,0), font = 2, cex = 0.9)
-
-# 2
-plot.new()
-text(0.5,0.25, "controllable", adj = c(0.5,0), font = 2, cex = 0.9)
-
-# 3-6
-for (i in 2:length(formatted_en_structural)){
-  set.seed(5)
-  types <- igraph::V(formatted_en_structural[[i]])$type ==
-    dplyr::first(igraph::V(formatted_en_structural[[i]])$type)
-  l <- igraph::layout_as_bipartite(formatted_en_structural[[i]], types) %>%
-    rescale_layout(xlim = c(-1.75, 1.75), ylim = c(-0.6, 0.6))
-  plot_examples(formatted_en_structural[[i]], 
-                layout = l,
-                frame = F, 
-                rescale = F, 
-                margin = rep(0, 4), 
-                edge.arrow.size = 0.4,
-                edge.label.family = "sans", 
-                vertex.label.family = "sans")
-}
-
-# 7
-plot.new()
-segments(0,0,0,1, lty = 2, lwd = 0.5)
-# 8
-plot.new()
-# 9
-plot.new()
-text(0.5,0.5, "inaccessible\nnode", adj = c(0.5,0.5), font = 1, cex = 0.9, srt = 90)
-# 10
-plot.new()
-text(0.5,0.5, "dilation", adj = c(0.5,0.5), font = 1, cex = 0.9, srt = 90)
-
-if(out_pdf) dev.off()
-
-```
+In addition, a graphical interpretation of the structural controllability theorem enables us to translate the control problem into a topological one: a network is controllable if there are no inaccessible nodes—nodes without incoming links—or dilations—*expansions* of the network (Figure \@ref(fig:fig-example-networks)b; see supplementary information section \@ref(S-structural-controllability) for more details).
 

### 2018-05-11 code/plot_ntw.R

@@ -60,6 +60,7 @@ plot_examples <- function(x, ...){
                       # vertex.label.family = fam,
                       # vertex.label.color = l_c,
                       edge.width = igraph::E(x)$width,
+                      edge.lty = igraph::E(x)$lty,
                       edge.label = igraph::E(x)$label,
                       edge.label.x = igraph::E(x)$label.x,
                       edge.label.color = igraph::E(x)$label.color,

### 2018-05-11 paper/supp-info.Rmd
Describe structural controllability in the supp info

--- 2018-05-09 paper/supp-info.Rmd
@@
 
+# Structural controllability {#structural-controllability}
+
+Structural controllability avoids the limitation of not knowing the exact values of the matrices *A* and *B*. 
+The graphical interpretation of structural controllability can be summed up in two conditions for controllability: A system is controllable if there are no inaccessible nodes or dilations.
+A node is inaccessible if there are no directed paths between it and the input nodes.
+"Dilations are subgraohs in which a small subset of nodes attempts to rule a larger subset of nodes.
+In other workds there are more 'subordinates' than 'superiors'" [@liu_control_2016].
+
+The goal of structural controllability is to use the information contained in **A** to generate a supportable estimate of **B**.
+This focus allows us to gain insight of the inherent controllability of a network, and the roles of the species that compose it, without being overly dependent on the particular choices of how the system dynamics are modelled or characterised.
+The trade-off of this approach is that, because of the assumption of linearity, structural controllability alone does not allow us to fully design the time-varying control signal *u(t)* that can drive the system from one particular equilibrium to another.
+Nevertheless, the lessons gained when assuming linearity---at both the network and the species level---are a prerequisite for eventually understanding nonlinear control [@liu_controllability_2011; @liu_control_2016].
+
+# Maximum matching
+
+Our approach to find the minumum number of driver nodes relies on finding maximum matchings. 
+We start with a directed network in which the direction of the link represents the direction of control (Figure \@ref(fig:fig-direction-of-control)a). 
+We then construct an alternative representation of the directed network in which each node of the directed network is represented by two nodes that indicate their outgoing and incoming links respectively (Figure \@ref(fig:fig-direction-of-control)b).
+Finding a maximum matching in this alternative representation is equivalent to finding the largest possible set of edges in which one node on the left-hand side is connected to at most one node on the right-hand side.
+To find the maximum matching we use the push-relabel algorithm implemented in `max_bipartite_matching` in the R package igraph 1.0.1 [@Csardi2006a]. 
+Once we have the matching (shown in the Figure \@ref(fig:fig-direction-of-control)b) it is then easy to identify the roles of each node in this representation: nodes on the left-hand side that are connected to a matched (purple) link are superior while those connected to a matched link on the right-hand side are matched.
+This information can then be mapped back to the original representation to identify the control paths and the driver nodes in the network (Figure \@ref(fig:fig-direction-of-control)c). 
+Figure \@ref(fig:fig-direction-of-control)d--f illustrate this approach for a network with bidirectional links.
+
+## Finding a single maximum matching {#one-maximum-matching}
+
+## Finding all possible maximum matchings
+
+## Finding all possible minimum driver node sets
+
+# Empirical vs. random expectation of controllability {#randomisations}
+
 # References

### 2018-05-11 paper/manuscript.Rmd
Reference supp section on structural controllabillity

@@
 Using this structural approach we can find out the controllability of a system under almost all non-zero parameter realisations.
-In addition, a graphical interpretation of the structural controllability theorem enables us to translate the control problem into a topological one: a network is controllable if there are no inaccessible nodes—nodes without incoming links—or dilations—*expansions* of the network (Figure \@ref(fig:fig-example-networks)b; see supplementary information section \@ref(S-structural-controllability) for more details).
+In addition, a graphical interpretation of the structural controllability theorem enables us to translate the control problem into a topological one: a network is controllable if there are no inaccessible nodes—nodes without incoming links—or dilations—*expansions* of the network (Figure \@ref(fig:fig-example-networks)b; supplementary information section \@ref(S-structural-controllability)).
 

### 2018-05-15 paper/manuscript.Rmd
Change type for control_type attribute for consistency

@@
   purrr::map(~ add_property(., element = "edge", attr_name = "color", 'TRUE ~ "black"')) %>%
-  purrr::map(~ add_property(., element = "edge", attr_name = "lty", "type == 'a' ~ 1", "TRUE ~ 3")) %>%
-  purrr::map(~ add_property(., element = "vertex", attr_name = "color", "type == 'a' ~ 'white'", "TRUE ~ 'white'")) %>%
-  purrr::map(~ add_property(., element = "vertex", attr_name = "frame.color", "type == 'a' ~ 'black'", "TRUE ~ 'white'")) %>%
-  purrr::map(~ add_property(., element = "vertex", attr_name = "shape", "type == 'a' ~ 'circle'", "TRUE ~ 'square'")) %>%
-  purrr::map(~ add_property(., element = "vertex", attr_name = "size", "type == 'a' ~ 55", "TRUE ~ 45")) %>%
+  purrr::map(~ add_property(., element = "edge", attr_name = "lty", "control_type == 'a' ~ 1", "TRUE ~ 3")) %>%
+  purrr::map(~ add_property(., element = "vertex", attr_name = "color", "control_type == 'a' ~ 'white'", "TRUE ~ 'white'")) %>%
+  purrr::map(~ add_property(., element = "vertex", attr_name = "frame.color", "control_type == 'a' ~ 'black'", "TRUE ~ 'white'")) %>%
+  purrr::map(~ add_property(., element = "vertex", attr_name = "shape", "control_type == 'a' ~ 'circle'", "TRUE ~ 'square'")) %>%
+  purrr::map(~ add_property(., element = "vertex", attr_name = "size", "control_type == 'a' ~ 55", "TRUE ~ 45")) %>%
   purrr::map(~ add_property(., element = "vertex", attr_name = "label.cex", "TRUE ~ 1")) %>%

### 2018-05-15 code/example_networks.R

@@ -2,25 +2,25 @@ example_ntw_structural <- function(){
   en_controllable <- list(
     edges = dplyr::data_frame(from = c("x_1", "x_2", "u_1"), 
                               to   = c("x_2", "x_3", "x_1"),
-                              type = c("a", "a", "b")), 
+                              control_type = c("a", "a", "b")), 
     vertex = dplyr::data_frame(name = c("x_1", "x_2", "x_3", "u_1"), 
-                               type = c("a", "a", "a", "b"))
+                               control_type = c("a", "a", "a", "b"))
   )
   
   en_inaccessible <- list(
     edges = dplyr::data_frame(from = c("x_1", "x_3", "u_1"), 
                               to   = c("x_2", "x_2", "x_1"),
-                              type = c("a", "a", "b")), 
+                              control_type = c("a", "a", "b")), 
     vertex = dplyr::data_frame(name = c("x_1", "x_2", "x_3", "u_1"),
-                               type = c("a", "a", "a", "b"))
+                               control_type = c("a", "a", "a", "b"))
   )
   
   en_dilation <- list(
     edges = dplyr::data_frame(from = c("x_2", "x_2", "u_1"), 
                               to   = c("x_1", "x_3", "x_2"),
-                              type = c("a", "a", "b")),
+                              control_type = c("a", "a", "b")),
     vertex = dplyr::data_frame(name = c("x_1", "x_2", "x_3", "u_1"), 
-                               type = c("a", "a", "a", "b"))
+                               control_type = c("a", "a", "a", "b"))
   )
   
   en_inaccessible_ok <- add_vertex_edge(en_inaccessible, "u_2", "b", "u_2", "x_3", "b")

### 2018-05-15 code/example_networks.R
Two more example networks (chain and star) for maximum matchings

@@ -46,3 +46,49 @@ example_ntw_directions <- function(){
   
   list(en_bip, en_dir)
 }
+
+example_matchings_chain <- function(){
+  list(
+    edges = dplyr::data_frame(from = c("x_1", "x_2", "x_3"), 
+                              to =   c("x_2", "x_3", "x_4"), 
+                              control_type = c(rep("a", 3))), 
+    vertex = dplyr::data_frame(name = c("x_1", "x_2", "x_3", "x_4"), 
+                               control_type = c(rep("a", 4)))
+  ) %$%
+    igraph::graph_from_data_frame(edges, directed = T, vertices = vertex)
+}
+
+
+example_matchings_star <- function(){
+  list(
+    edges = dplyr::data_frame(from = c("x_1", "x_1", "x_1", "x_1"), 
+                              to   = c("x_2", "x_3", "x_4", "x_5")), 
+    vertex = dplyr::data_frame(name = c("x_1", "x_2", "x_3", "x_4", "x_5"))
+  ) %$%
+    igraph::graph_from_data_frame(edges, directed = T, vertices = vertex) 
+}
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+

### 2018-05-18 code/example_networks.R
Minor changes to example networks

@@ -36,18 +36,20 @@ example_ntw_directions <- function(){
   en_vis <- list(
     edges = dplyr::data_frame(from = c("p_1", "p_2", "p_2", "p_3", "p_3"), 
                               to = c("a_1", "a_1", "a_2", "a_2", "a_1"), 
-                              weight = c(1, 2, 5, 1, 1)), 
+                              weight = c(1, 2, 3, 1, 1)), 
     vertex = dplyr::data_frame(name = c("p_1", "p_2", "p_3", "a_1", "a_2"), 
                                type = c("p", "p", "p", "a", "a"))
   )
   
   en_bip <- igraph::graph_from_data_frame(en_vis$edges, directed = F, vertices = en_vis$vertex) 
   en_dir <- as_directed_network(en_bip, direction = "asymmetry", ties = "both", higher_level = "a")
+  # plot(en_dir)
+  # length(all_matchings(en_dir))
   
   list(en_bip, en_dir)
 }
 
-example_matchings_chain <- function(){
+example_ntw_matchings_chain <- function(){
   list(
     edges = dplyr::data_frame(from = c("x_1", "x_2", "x_3"), 
                               to =   c("x_2", "x_3", "x_4"), 
@@ -59,11 +61,17 @@ example_matchings_chain <- function(){
 }
 
 
-example_matchings_star <- function(){
+example_ntw_matchings_star <- function(){
   list(
-    edges = dplyr::data_frame(from = c("x_1", "x_1", "x_1", "x_1"), 
-                              to   = c("x_2", "x_3", "x_4", "x_5")), 
-    vertex = dplyr::data_frame(name = c("x_1", "x_2", "x_3", "x_4", "x_5"))
+    edges = dplyr::data_frame(from = c("x_1", "x_1", "x_1"), 
+                              to   = c("x_2", "x_3", "x_4" )), 
+    vertex = dplyr::data_frame(name = c("x_1", "x_2", "x_3", "x_4"))
   ) %$%
     igraph::graph_from_data_frame(edges, directed = T, vertices = vertex) 
+}
+
+matchings_example_networks <- function(x){
+  x %>%
+    all_matchings() %>%
+    purrr::map(add_control_nodes)
 }

### 2018-05-18 paper/manuscript.Rmd
Include figures from function outputs

--- 2018-05-11 paper/manuscript.Rmd
@@
 
-```{r prepare-graph-direction}
-drake::loadd(en_direction)
-# graph attributes
-formatted_en_direction <- en_direction  %>%
-  purrr::map(~ fancify_vertex_name(.)) %>%
-  purrr::map(~ add_property(., element = "edge", attr_name = "color", 'TRUE ~ "black"')) %>%
-  purrr::map(~ add_property(., element = "edge", attr_name = "label.color", 'TRUE ~ "black"')) %>%
-  purrr::map(~ add_property(., element = "edge", attr_name = "label.font", 'TRUE ~ 2')) %>%
-  purrr::map(~ add_property(., element = "vertex", attr_name = "color", "TRUE ~ 'white'")) %>%
-  purrr::map(~ add_property(., element = "vertex", attr_name = "frame.color", "TRUE ~ 'black'")) %>%
-  purrr::map(~ add_property(., element = "vertex", attr_name = "size", "TRUE ~ 55")) %>%
-  purrr::map(~ add_property(., element = "vertex", attr_name = "label.cex", "TRUE ~ 1")) %>%
-  purrr::map(~ add_property(., element = "vertex", attr_name = "label.color", "TRUE ~ 'black'"))
-
-formatted_en_direction[[1]] %<>%
-  igraph::set_edge_attr("width", value = igraph::E(.)$weight * 0.5)
-formatted_en_direction[[2]] %<>%
-  igraph::set_edge_attr("width", value = 1)
-
-direction_layout <- matrix(c(1,0,
-                             2,0,
-                             3,0,
-                             1.5, 1,
-                             2.5, 1), nrow = 5, ncol = 2, byrow = T)
-```
-
-```{r prepare-graph-structural}
-drake::loadd(en_structural)
-
-# format networks for plotting
-formatted_en_structural <- en_structural %>%
-  purrr::map(~ fancify_vertex_name(.)) %>%
-  purrr::map(~ add_property(., element = "edge", attr_name = "color", 'TRUE ~ "black"')) %>%
-  purrr::map(~ add_property(., element = "edge", attr_name = "lty", "type == 'a' ~ 1", "TRUE ~ 3")) %>%
-  purrr::map(~ add_property(., element = "vertex", attr_name = "color", "type == 'a' ~ 'white'", "TRUE ~ 'white'")) %>%
-  purrr::map(~ add_property(., element = "vertex", attr_name = "frame.color", "type == 'a' ~ 'black'", "TRUE ~ 'white'")) %>%
-  purrr::map(~ add_property(., element = "vertex", attr_name = "shape", "type == 'a' ~ 'circle'", "TRUE ~ 'square'")) %>%
-  purrr::map(~ add_property(., element = "vertex", attr_name = "size", "type == 'a' ~ 55", "TRUE ~ 45")) %>%
-  purrr::map(~ add_property(., element = "vertex", attr_name = "label.cex", "TRUE ~ 1")) %>%
-  purrr::map(~ add_property(., element = "vertex", attr_name = "label.color", "TRUE ~ 'black'"))
-```
-
-```{r example-network-common-plotting-par}
-plot_example_ntw <- function(x, ...){
-  plot_examples(x, rescale = F, 
-                frame = F, 
-                margin = rep(0, 4), 
-                edge.arrow.size = 0.4,
-                edge.label.family = "sans", 
-                vertex.label.family = "sans", ...)
-}
-
-```
-
 We used ten paired pollination communities to apply the control theoretic approach.
@@
 By basing the direction of the links on the asymmetry of their dependence, we are able to generate a network that is consistent with the dynamics of the community while satisfyingh the requirements of structural controllability.
+```{r}
+drake::loadd(fig_struct_control)
+```
 
-```{r fig-example-networks, fig.width=3.5, fig.height=2.6, fig.cap="(a) To establish the direction of control we start with a weighted visitation network (right side).
+```{r fig-example-networks, fig.width=fig_struct_control$width, fig.height=fig_struct_control$height, fig.cap="(a) To establish the direction of control we start with a weighted visitation network (on the right).
 In this network, the width of the links correspond to the frequency of visitation.
-We then calculate the dependencies between species pairs and create a directed network (left side) in which the direction of the links correspond to the direction of the assymetry of their dependence.
+We then calculate the dependencies between species pairs and create a directed network (left) in which the direction of the links correspond to the direction of the assymetry of their dependence.
 For instance, the population of plant $p_1$ is likely to be affected by the population of pollinator $a_1$ to a larger extent that the population of $a_1$ depends on $p_1$ because $a_1$ interacts more strongly with other species in the community; hence the direction of control between these two species can be simplyfied with a directed link from $a_1$ to $p_1$.
 (b) A system is structurally controllable if there are no inaccessible links or dilations.
-The network on the top left is not controllable because node $x_3$ is inaccessible from the input node $u_1$ in the system.
-The network in the bottom left is not controllable because there is a dilation in which node $x_2$ is being used to control two nodes simultaneously.
-Both systems can be made controllable by adding an extra input node (right panel)."}
-out_pdf <- F
-height1 <- 0.9
-height2 <- 1.5
-
-if(out_pdf) pdf("test.pdf", width = 3.5, height = height1 + height2 + 0.2, paper='special')
-
-c(01,10,12,11,91,
-  90,13,12,14,91, 
-  80,80,80,80,80, 
-  02,20,28,21,93,
-  22,24,28,25,93,
-  23,26,28,27,93) %>%
-  dplyr::dense_rank() %>%
-  matrix(nrow = 6, ncol = 5, byrow = T) %>%
-  layout(heights = c(height1 * 0.25, height1 * 0.75, height1 * 0.2, height2 * 0.1, height2 * 0.45, height2 * 0.45),
-         widths = c(0.2, 1, 0.05, 1, 0.2))
-par(mar = rep(0,4), bg = "white")
-
-## LABELS
-# 01
-standalone_text("(a)", y = 0.75)
-# 02
-standalone_text("(b)", y = 0.75)
-## FIGURE A
-# 10
-standalone_text("visitation network", y = 0.25, adj = c(0.5,0), font = 2)
-# 11
-standalone_text("direction of control", y = 0.25, adj = c(0.5,0), font = 2)
-# 12
-standalone_vline(lty = 2)
-# 13-14
-for(i in 1:length(formatted_en_direction)){
-  l <- rescale_layout(direction_layout, xlim = c(-1, 1) * 1.75, ylim = c(-0.6, 0.7))
-  plot_example_ntw(formatted_en_direction[[i]], layout = l)
-}
-## FIGURE B
-# 20
-standalone_text("not controllable", y = 0.25, adj = c(0.5,0), font = 2)
-# 21
-standalone_text("controllable", y = 0.25, adj = c(0.5,0), font = 2)
-# 22
-standalone_text("inaccessible\nnode", srt = 90)
-# 23
-standalone_text("dilation", srt = 90)
-# 24-27
-for (i in 2:length(formatted_en_structural)){
-  types <- igraph::V(formatted_en_structural[[i]])$type == dplyr::first(igraph::V(formatted_en_structural[[i]])$type)
-  l <- igraph::layout_as_bipartite(formatted_en_structural[[i]], types) %>%
-    rescale_layout(xlim = c(-1.75, 1.75), ylim = c(-0.6, 0.6))
-  plot_example_ntw(formatted_en_structural[[i]], layout = l)
-}
-# 28
-standalone_vline(lty = 2)
-## DIV LINES
-# 80
-standalone_hline()
-
-if(out_pdf) dev.off()
+The network on the bottom left is not controllable because node $x_3$ is inaccessible from the input node $u_1$ in the system.
+The network in the bottom right is not controllable because there is a dilation in which node $x_2$ is being used to control two nodes simultaneously.
+Both systems can be made controllable by adding an extra input node (top)."}
+replayPlot(fig_struct_control$plot)
 ```
@@
 The key is to note that these definitions imply that a matched node can have only one matched link pointing to it, and similarly a superior node can have at most one link leaving from it. 
-The result is that a matching can actually be decomposed into a set of paths that reveal how a control signal can flow across the links in a network to reach every node that compose it. 
+The result is that a matching can actually be decomposed into a set of paths that reveal how a control signal can flow across the links in a network to reach every node that compose it (Figure 1cXX). 
 And so, as recently shown [@liu_controllability_2011], the minimum driver node set corresponds exactly to the *unmatched* nodes, those that are not controlled by other nodes in the network.
+
+```{r}
+drake::loadd(fig_control_config)
+```
+
+```{r fig-control-configuration, fig.height=fig_control_config$height, fig.width=fig_control_config$width,fig.cap = "ASD"}
+replayPlot(fig_control_config$plot)
+```
 

### 2018-05-18 code/matchings.R
Typo

@@ -205,7 +205,7 @@ add_control_nodes <- function(x, base_name = "u"){
   new_vertices_names <- paste(base_name, 1:n_new_vertices, sep = "_")
   
   x %>% 
-    igraph::add_vertices(n_new_vertices, name = new_vertices_names, contol_type = "b") %>%
+    igraph::add_vertices(n_new_vertices, name = new_vertices_names, control_type = "b") %>%
     igraph::add_edges(edges = rbind(new_vertices_names, driver_nodes$name), control_type = "b") %>%
     return()
 }

### 2018-05-18 paper/manuscript.Rmd
Swap inaccessible and dilations in figure 1

@@
 (b) A system is structurally controllable if there are no inaccessible links or dilations.
-The network on the bottom left is not controllable because node $x_3$ is inaccessible from the input node $u_1$ in the system.
-The network in the bottom right is not controllable because there is a dilation in which node $x_2$ is being used to control two nodes simultaneously.
+The network on the bottom left is not controllable because there is a dilation in which node $x_2$ is being used to control two nodes simultaneously.
+The network in the bottom right  is not controllable because node $x_3$ is inaccessible from the input node $u_1$ in the system.
 Both systems can be made controllable by adding an extra input node (top)."}

### 2018-05-18 code/fig_example_structural_control.R

@@ -110,16 +110,16 @@ make_fig_structural_control <- function(en_direction, en_structural, pdf_out = N
   }
   ## FIGURE B
   # 20
-  standalone_text("inaccessible node", y = 0.5, adj = c(0.5,0), font = 1)
-  # 21
   standalone_text("dilation", y = 0.5, adj = c(0.5,0), font = 1)
+  # 21
+  standalone_text("inaccessible node", y = 0.5, adj = c(0.5,0), font = 1)
   # 22
   standalone_text("controllable", srt = 90, font = 2)
   # 23
   standalone_text("not\ncontrollable", srt = 90, font = 2)
   # 24-27
-  for (i in c(3,5,2,4)){
-    if(i == 5)   text(-2.27, 1, "(b)", adj = c(0,1.2), font = 1)
+  for (i in c(5,3,4,2)){
+    if(i == 3)   text(-2.26, 1, "(b)", adj = c(0,1.3), font = 1)
 
     types <- igraph::V(formatted_en_structural[[i]])$control_type == dplyr::first(igraph::V(formatted_en_structural[[i]])$control_type)
     l <- igraph::layout_as_bipartite(formatted_en_structural[[i]], types) %>%
@@ -155,4 +155,4 @@ make_fig_structural_control <- function(en_direction, en_structural, pdf_out = N
   ))
 }
 
-# replayPlot(make_fig_structural_control(en_direction, en_structural, "test.pdf")$plot)
+replayPlot(make_fig_structural_control(en_direction, en_structural, "test.pdf")$plot)

### 2018-05-18 paper/manuscript.Rmd
Better explain matchings

@@
 A simple dynamic system can be described by $\frac{dx}{dt} = Ax + Bu(t)$, where the change of its state over time ($\frac{dx}{dt}$) depends on its current state *x* (for example, the species' abundances), an external time-varying input *u(t)* (the control signal), and two matrices *A* and *B*, which encode information about the network structure and how species respond to external inputs, respectively.
-In classic control theory, determining wether this system is controllable or not can easily be achieved by checking that its controllability matrix $R= [ \begin{matrix}B & AB & A^{2}B & ...& A^{n-1}B\end{matrix} ]$ has full rank.
-In complex systems, however, employing this rank condition, or numerical approximations of it, is unfeasible because it is hard to fully parameterize *A* and *B* (either the weights of the links change over time or because they are difficult to measures).
+In classic control theory, determining wether this system is controllable can easily be achieved by checking that its controllability matrix $R= [ \begin{matrix}B & AB & A^{2}B & ...& A^{n-1}B\end{matrix} ]$ has full rank.
+In complex systems, however, employing this rank condition, or numerical approximations of it, is unfeasible because it is hard to fully parameterize *A* and *B* (either because the weight of the links change over time or because they are difficult to measure).
 Here we use an approach based on the structural controllability theorem [@lin_structural_1974], which assumes that we are confident that the elements of *A* and *B* have either non-zero or zero values (there is an interaction or not), but that we less sure about the precise magitude of the non-zero values.
 Using this structural approach we can find out the controllability of a system under almost all non-zero parameter realisations.
-In addition, a graphical interpretation of the structural controllability theorem enables us to translate the control problem into a topological one: a network is controllable if there are no inaccessible nodes—nodes without incoming links—or dilations—*expansions* of the network (Figure \@ref(fig:fig-example-networks)b; supplementary information section \@ref(S-structural-controllability)).
+Structural controllability also has a graphical interpretation that allow us to translate the control problem into a topological one: a network is controllable if there are no inaccessible nodes—nodes without incoming links—or dilations—*expansions* of the network (Figure \@ref(fig:fig-example-networks)b; supplementary information section \@ref(S-structural-controllability)).
 
@@
 However, a brute force search of this minimum driver node set is computationally prohibitive for most networks as it involves the evaluation of $2^N$ different controllability matrices. 
-We employ a recently developed approach that shows that the control problem of finding the minimum driver node set can be mapped into a purely graph theoretic problem: maximum matching [@liu_controllability_2011; @liu_control_2016].
+We employ a recently developed approach that shows that the control problem of finding the minimum driver node set can be mapped into a graph theoretic problem: maximum matching [@liu_controllability_2011; @liu_control_2016].
 
-Maximum matching is a widely studied topic in graph theory and is commonly used in multiple applications, from dating apps and wireless communications to organ transplant allocation and peer to peer file sharing.
-A matching in an unweighted directed graph is defined as a set of links that do not share a common start or end nodes. 
-A node is said to be superior if it is at the beginning of a matched link and called matched if it is at the end. 
-Finally, the largest possible matching is called maximum matching. 
-These definitions, however, offer little insight about how maximum matching is related to structural controllability. 
-The key is to note that these definitions imply that a matched node can have only one matched link pointing to it, and similarly a superior node can have at most one link leaving from it. 
-The result is that a matching can actually be decomposed into a set of paths that reveal how a control signal can flow across the links in a network to reach every node that compose it (Figure 1cXX). 
-And so, as recently shown [@liu_controllability_2011], the minimum driver node set corresponds exactly to the *unmatched* nodes, those that are not controlled by other nodes in the network.
+Maximum matching is a widely studied topic in graph theory and is commonly used in multiple applications, ranging from dating apps and wireless communications to organ transplant allocation and peer to peer file sharing.
+A matching in an unweighted directed graph is defined as a set of links that do not share a common start or end nodes; the largest possible matching is called maximum matching. 
+For example, in a network composed by jobs and job applicants, a matching is any pairing between applicants and positions that satisfies the basic constrain of any applicant being assigned to at most one position and visceversa.
+A maximum matching would then be such a pairing that maximises the number of applicants with jobs and the number of positions filled. 
+The definition of maximum matching, however, offer little insight about how it is related to structural controllability. 
+The key is to note that the conditions of structural controllability imply that there needs to be a one to one relationship between *superior* and *subordinate* nodes (Figure \@ref(fig:fig-example-networks)b, bottom left).
+We use the maximum matching algorithm to pair superior to subordinate nodes in a way consistent with these conditions. 
+The result is that a matching can actually be decomposed into a set of paths that reveal how a control signal can flow across the links in a network to reach every node that compose it. 
+And so, as recently shown [@liu_controllability_2011], the minimum driver node set, those to which an external control signal should be applied to make the system controllable, corresponds exactly to the *unmatched* nodes in the network (Figure \@ref(fig:fig-control-configuration)).
 

### 2018-05-18 paper/manuscript.Rmd
Add superior/subordinate to description of figure of structural control

@@
 Previous research has shown that mutualistic interactions are often highly asymmetric in natural communities; in other words, if a plant species is largely dependent on a pollinator species, then that pollinator tends to depend rather weakly on the plant (or vice versa).
-We then create a directed link between species *i* and *j* when $d_{ij}-d_{ji} \geq 0$ to establish the most likely direction of control between a species pair (Figure \@ref(fig:fig-example-networks)a).
+We therefore create a directed link between species *i* and *j* when $d_{ij}-d_{ji} \geq 0$ to establish the most likely direction of control between a species pair (Figure \@ref(fig:fig-example-networks)a).
 By basing the direction of the links on the asymmetry of their dependence, we are able to generate a network that is consistent with the dynamics of the community while satisfyingh the requirements of structural controllability.
@@
 (b) A system is structurally controllable if there are no inaccessible links or dilations.
-The network on the bottom left is not controllable because there is a dilation in which node $x_2$ is being used to control two nodes simultaneously.
+The network on the bottom left is not controllable because there is a dilation in which node $x_2$ is being used to control two nodes simultaneously, in other workds there are less superiors ($x_2$) than subordinates ($x_1$ and $x_2$ ).
 The network in the bottom right  is not controllable because node $x_3$ is inaccessible from the input node $u_1$ in the system.

### 2018-05-18 code/fig_example_structural_control.R
Comment test line for figure of structural control

@@ -155,4 +155,4 @@ make_fig_structural_control <- function(en_direction, en_structural, pdf_out = N
   ))
 }
 
-replayPlot(make_fig_structural_control(en_direction, en_structural, "test.pdf")$plot)
+# replayPlot(make_fig_structural_control(en_direction, en_structural, "test.pdf")$plot)

### 2018-05-19 paper/manuscript.Rmd
Improve legend figure controllability

@@
 
-```{r fig-example-networks, fig.width=fig_struct_control$width, fig.height=fig_struct_control$height, fig.cap="(a) To establish the direction of control we start with a weighted visitation network (on the right).
-In this network, the width of the links correspond to the frequency of visitation.
-We then calculate the dependencies between species pairs and create a directed network (left) in which the direction of the links correspond to the direction of the assymetry of their dependence.
-For instance, the population of plant $p_1$ is likely to be affected by the population of pollinator $a_1$ to a larger extent that the population of $a_1$ depends on $p_1$ because $a_1$ interacts more strongly with other species in the community; hence the direction of control between these two species can be simplyfied with a directed link from $a_1$ to $p_1$.
-(b) A system is structurally controllable if there are no inaccessible links or dilations.
-The network on the bottom left is not controllable because there is a dilation in which node $x_2$ is being used to control two nodes simultaneously, in other workds there are less superiors ($x_2$) than subordinates ($x_1$ and $x_2$ ).
-The network in the bottom right  is not controllable because node $x_3$ is inaccessible from the input node $u_1$ in the system.
+```{r fig-example-networks, fig.width=fig_struct_control$width, fig.height=fig_struct_control$height, fig.cap="Direction of control and controllability conditions.
+(a) To establish the direction of control we start with a weighted visitation network (on the left).
+In this network, the width of the links corresponds to the frequency of visitation between animals $a_i$ and plants $p_i$, with wider link indicating more visits.
+Plant $p_1$ is visited exclusively by $a_1$ but $p_1$ represents only a small fraction of the floral resources of $a_1$.
+Therefore the population of $p_1$ is more likely to be affected by $a_1$ than visceversa.
+We represent this with a directed link from $a_1$ to $p_1$ (right).
+The direction of control between all other species pairs can be similarly determined by inspecting the difference between their relative dependences.
+(b) Once we have established the directions of control we can determine wether the network is controllable or not.
+A system defined by a directed network (with state nodes $x_i$; species populations in an ecological context) and control inputs (nodes $u_i$, orange links) is structurally controllable if it satisfies two conditions: it has no dilations (expansions in the network) and no inaccessible nodes.
+The system on the top left is not controllable because there is a dilation in which node $x_2$ is being used to control two nodes simultaneously, in other workds there are less superiors ($x_2$) than subordinates ($x_1$ and $x_3$).
+The network in the top right is not controllable because node $x_3$ is inaccessible for the only input node $u_1$ in the system.
 Both systems can be made controllable by adding an extra input node (top)."}

### 2018-05-19 paper/manuscript.Rmd
Improve matching explanation

@@
 A matching in an unweighted directed graph is defined as a set of links that do not share a common start or end nodes; the largest possible matching is called maximum matching. 
-For example, in a network composed by jobs and job applicants, a matching is any pairing between applicants and positions that satisfies the basic constrain of any applicant being assigned to at most one position and visceversa.
-A maximum matching would then be such a pairing that maximises the number of applicants with jobs and the number of positions filled. 
-The definition of maximum matching, however, offer little insight about how it is related to structural controllability. 
-The key is to note that the conditions of structural controllability imply that there needs to be a one to one relationship between *superior* and *subordinate* nodes (Figure \@ref(fig:fig-example-networks)b, bottom left).
-We use the maximum matching algorithm to pair superior to subordinate nodes in a way consistent with these conditions. 
+For example, in a network composed by jobs and job applicants, a matching is any pairing between applicants and positions that satisfies one basic constrain: an applicant can be assigned to at most one position and visceversa.
+Consequently, a maximum matching is an optimal pairing, one that maximises the number of applicants with jobs and the number of positions filled. 
+At first glance, however, is  hard to identify how exactlty matchings are related to structural controllability. 
+The key is to note that the conditions of structural controllability imply that, just like the one to one relationship between jobs and applicants, there needs to be a one to one relationship between *superior* and *subordinate* nodes (Figure \@ref(fig:fig-example-networks)b, bottom left).
+We use the maximum matching algorithm to find an optimal pairing of superior and subordinate nodes in a way consistent with the controllability conditions. 
 The result is that a matching can actually be decomposed into a set of paths that reveal how a control signal can flow across the links in a network to reach every node that compose it. 
-And so, as recently shown [@liu_controllability_2011], the minimum driver node set, those to which an external control signal should be applied to make the system controllable, corresponds exactly to the *unmatched* nodes in the network (Figure \@ref(fig:fig-control-configuration)).
+And so, as recently shown [@liu_controllability_2011], the minimum driver node set, those to which an external control input should be applied to make the system controllable, corresponds exactly to the *unmatched* nodes in the network (Figure \@ref(fig:fig-control-configuration)).
 

### 2018-05-19 paper/manuscript.Rmd
Minor editing changes

@@
 (b) Once we have established the directions of control we can determine wether the network is controllable or not.
-A system defined by a directed network (with state nodes $x_i$; species populations in an ecological context) and control inputs (nodes $u_i$, orange links) is structurally controllable if it satisfies two conditions: it has no dilations (expansions in the network) and no inaccessible nodes.
+A system defined by a directed network (with state nodes $x_i$; species populations in an ecological context) and external control inputs (nodes $u_i$, orange links) is structurally controllable if it satisfies two conditions: it has no dilations (expansions in the network) and no inaccessible nodes.
 The system on the top left is not controllable because there is a dilation in which node $x_2$ is being used to control two nodes simultaneously, in other workds there are less superiors ($x_2$) than subordinates ($x_1$ and $x_3$).
@@
 Using this structural approach we can find out the controllability of a system under almost all non-zero parameter realisations.
-Structural controllability also has a graphical interpretation that allow us to translate the control problem into a topological one: a network is controllable if there are no inaccessible nodes—nodes without incoming links—or dilations—*expansions* of the network (Figure \@ref(fig:fig-example-networks)b; supplementary information section \@ref(S-structural-controllability)).
+Structural controllability also has a graphical interpretation that allow us to translate the control problem into a topological one: a network is controllable if there are no inaccessible nodes—nodes without incoming links—or dilations—*expansions* of the network (Figure \@ref(fig:fig-example-networks)b; Supplementary Information section \@ref(S-structural-controllability)).
 

### 2018-05-19 paper/supp-info.Rmd
Minor editing changes

@@
 Structural controllability avoids the limitation of not knowing the exact values of the matrices *A* and *B*. 
-The graphical interpretation of structural controllability can be summed up in two conditions for controllability: A system is controllable if there are no inaccessible nodes or dilations.
+Using structural controllability controllability can be boiled down to two conditions: a system is controllable if there are no inaccessible nodes or dilations.
 A node is inaccessible if there are no directed paths between it and the input nodes.
-"Dilations are subgraohs in which a small subset of nodes attempts to rule a larger subset of nodes.
+"Dilations are subgraphs in which a small subset of nodes attempts to rule a larger subset of nodes.
 In other workds there are more 'subordinates' than 'superiors'" [@liu_control_2016].

### 2018-05-19 code/fig_example_direction.R

@@ -56,7 +56,7 @@ make_fig_control_configurations <- function(en_chain, en_star, en_direction, pdf
                legend_height)
   d <- 30
   x <- 3.4
-  widths <- c(0.05, x/3-x/2/d, x/d, x/2-x/3-x/d, x/d, x/2-x/3-x/d/2, x/3, 0.05)
+  widths <- c(0.005, x/3-x/2/d, x/d, x/2-x/3-x/d, x/d, x/2-x/3-x/d/2, x/3, 0.005)
   
   pdf(pdf_out, width = sum(widths), height = sum(heights), paper='special')
   if(is.null(pdf_out)) dev.control("enable")
@@ -65,8 +65,8 @@ make_fig_control_configurations <- function(en_chain, en_star, en_direction, pdf
     03,34,33,35,35,35,35,94,
     84,84,82,82,82,82,82,82,
     92,92,45,90,90,90,90,90,
-    04,40,45,41,41,41,42,97,
     96,40,45,43,43,43,43,97,
+    04,40,45,41,41,41,42,97,
     93,93,45,91,91,91,91,91,
     83,83,83,83,83,83,83,83,
     05,50,53,51,51,51,52,98,
@@ -75,7 +75,7 @@ make_fig_control_configurations <- function(en_chain, en_star, en_direction, pdf
     matrix(ncol = 8, byrow = T) %>%
     layout(heights = heights,
            widths = widths)
-  par(mar = rep(0,4), bg = "white", xpd = NA)
+  par(mar = rep(0,4), bg = "NA", xpd = NA)
   
   plot.new()
   
@@ -162,8 +162,8 @@ make_fig_control_configurations <- function(en_chain, en_star, en_direction, pdf
   for(i in 1:3){
     l <- matrix(c(1,2,2,2,0,3,3,
                   2,3,2,1, 2,(3:1)[-i]), 7,2)  %>%
-      rescale_layout(xlim = c(-1, 1) * 1.8, ylim = c(-1,1) * 0.75)
-    plot_example_ntw(en_star_matchings[[i]], layout = l)
+      rescale_layout(xlim = c(-1, 1) * 1.8, ylim = c(-1,1) * 0.93)
+    plot_example_ntw(en_star_matchings[[i]], layout = l, margin = rep(0.5,4))
   }
   # 45
   # standalone_vline(lty = 2)

### 2018-05-21 paper/supp-info.Rmd
Add figure maximum matching to supp info

@@
 ## Finding a single maximum matching {#one-maximum-matching}
+```{r}
+drake::loadd(fig_supp_matching)
+```
+
+```{r fig-maximum-matching-procedure, fig.height=fig_supp_matching$height, fig.width=fig_supp_matching$width,fig.cap = "Finding a maximum matching in a complex network.
+(left) Directed network that indicate the direction of control between species.
+(center) Alternative bipartite representations of the directed networks.
+(right) The matchings in the bipartite representation mapped back to the original network."}
+replayPlot(fig_supp_matching$plot)
+```
 

### 2018-05-21 code/fig_supp_maximum_matching.R

@@ -1,0 +1,104 @@
+make_fig_maximum_matching <- function(en_direction, pdf_out = NULL){
+  
+  n1 <- en_direction[[2]]
+  n3 <- en_direction[[2]] %>%
+    maximum_matching()
+  n2 <- igraph::graph_attr(n3, "bipartite_representation")
+  
+  n1 %<>%
+    ntw_format_theme()
+  
+  n2 %<>% igraph::vertex_attr("name") %>% 
+    stringr::str_replace("..f", "^+") %>%
+    stringr::str_replace("..t", "^-") %>%
+    igraph::set_vertex_attr(n2, "name", value = .) %>%
+    igraph::set_vertex_attr("type", value = "a") %>%
+    ntw_format_theme() %>%  
+    add_property(element = "edge", attr_name = "color", attr_base = "matched", 'type ~ get_color("matched")', '!type ~ get_color("unmatched")', 'TRUE ~ get_color("control")') %>%
+    add_property(element = "vertex", attr_name = "size",attr_base = "type", "TRUE ~ 55")
+
+  n3 %<>%
+    ntw_format_theme() %>%
+    ntw_matched_theme(named = T) %>%
+    add_property(element = "vertex", attr_name = "size",attr_base = "type", "TRUE ~ 55")
+ 
+  heading_height <- 0.25
+  fig_height <- 0.75
+  legend_height <- 0.2
+  
+  total_width <- fig_sizes()$two_column_width
+  
+  heights <- c(heading_height,
+               fig_height,
+               legend_height)
+  widths <- c(total_width/3, total_width/3, total_width/3)
+  
+  # FIG DEVICE HERE
+  pdf(pdf_out, width = sum(widths), height = sum(heights), paper='special')
+  if(is.null(pdf_out)) dev.control("enable")
+  
+  c(01,02,03,
+    10,11,12,
+    80,80,80) %>%
+    dplyr::dense_rank() %>%
+    matrix(ncol = 3, byrow = T) %>%
+    layout(widths = widths, heights = heights)
+  par(mar = rep(0,4), bg = "white", xpd = NA)
+  
+  # titles
+  standalone_text("directed network", font = 2)
+  standalone_text("alternative bipartite representation", font = 2)
+  standalone_text("matching in original network", font = 2)
+  # directed network
[…]

### 2018-05-21 code/fig_example_direction.R
Adjust figure widths

@@ -59,7 +59,7 @@ make_fig_control_configurations <- function(en_chain, en_star, en_direction, pdf
                desc_height,
                legend_height)
   d <- 30
-  x <- 3.5
+  x <- fig_sizes()$one_column_width
   widths <- c(x/3, 2*x/3/6, 2*x/3/6, 2*x/3/6, 2*x/3/6, 2*x/3/6, 2*x/3/6)
   
   pdf(pdf_out, width = sum(widths), height = sum(heights), paper='special')
@@ -130,7 +130,7 @@ make_fig_control_configurations <- function(en_chain, en_star, en_direction, pdf
        border = NA)
 
   # 32
-  standalone_text("control configurations", y = 0.5, adj = c(0.5,0), font = 2)
+  standalone_text("maximum matchings / control configurations", y = 0.5, adj = c(0.5,0), font = 2)
   # 33
   # standalone_vline(lty = 2)
   # plot.new()
@@ -176,15 +176,15 @@ make_fig_control_configurations <- function(en_chain, en_star, en_direction, pdf
   y_desc <- 0.7
   standalone_text("N = 4", y = y_desc)
   
-  standalone_text(latex2exp::TeX("$matching\\,size = 3 \\;\\;\\; D = 1 \\;\\;\\; n_d = 0.25$"), y = y_desc)
+  standalone_text(latex2exp::TeX("$matching\\,size = 3 \\;\\;\\; D = 1 \\;\\;\\; n_D = 0.25$"), y = y_desc)
   
   standalone_text("N = 4", y = y_desc)
   
-  standalone_text(latex2exp::TeX("$matching\\,size = 1 \\;\\;\\; D = 3 \\;\\;\\; n_d = 0.75$"), y = y_desc)
+  standalone_text(latex2exp::TeX("$matching\\,size = 1 \\;\\;\\; D = 3 \\;\\;\\; n_D = 0.75$"), y = y_desc)
   
   standalone_text("N = 5", y = y_desc)
   
-  standalone_text(latex2exp::TeX("$matching\\,size = 3 \\;\\;\\; D = 2 \\;\\;\\; n_d = 0.40$"), y = y_desc)
+  standalone_text(latex2exp::TeX("$matching\\,size = 3 \\;\\;\\; D = 2 \\;\\;\\; n_D = 0.40$"), y = y_desc)
   
   # plot.new()
   plot.new()
[…]

### 2018-05-21 code/fig_example_structural_control.R

@@ -38,8 +38,8 @@ make_fig_structural_control <- function(en_direction, en_structural, pdf_out = N
                div_height, plot_2_height, 
                legend_height)
   d <- 30
-  x <- 3.2
-  margin_h <- (3.5-x)
+  x <- 3.1
+  margin_h <- (fig_sizes()$one_column_width-x)
   widths <- c(margin_h, x/3-x/2/d, x/d, x/2-x/3-x/d, x/d, x/2-x/3-x/d/2, x/3,0.001)
   
   pdf(pdf_out, width = sum(widths), height = sum(heights), paper='special') 
@@ -158,4 +158,5 @@ make_fig_structural_control <- function(en_direction, en_structural, pdf_out = N
   ))
 }
 
+# drake::loadd(en_structural, en_direction)
 # replayPlot(make_fig_structural_control(en_direction, en_structural, "test.pdf")$plot)

### 2018-05-21 code/plot_ntw.R

@@ -171,8 +171,8 @@ ntw_control_network_theme <- . %>%
 
 ntw_matched_theme <- function(x, named = F){
   x %<>%  
-  add_property(element = "vertex", attr_name = "color", attr_base = "matched", 'type ~ get_color("matched")', '!type ~ get_color("unmatched")', 'TRUE ~ get_color("bg")') %>%
-  add_property(element = "edge", attr_name = "color", attr_base = "matched", 'type ~ get_color("matched")', '!type ~ get_color("unmatched")', 'TRUE ~ get_color("control")') %>%
+    add_property(element = "vertex", attr_name = "color", attr_base = "matched", 'type ~ get_color("matched")', '!type ~ get_color("unmatched")', 'TRUE ~ get_color("bg")') %>%
+    add_property(element = "edge", attr_name = "color", attr_base = "matched", 'type ~ get_color("matched")', '!type ~ get_color("unmatched")', 'TRUE ~ get_color("control")') %>%
     add_property(element = "vertex", attr_name = "size",attr_base = "type", "TRUE ~ 25") %>%
     add_property(element = "vertex", attr_name = "label.color", attr_base = "matched", 'type ~ "white"', '!type ~ "black"', 'TRUE ~ "black"')
   
@@ -196,3 +196,10 @@ direction_layout <- function(){
            1.5, 1,
            2.5, 1), nrow = 5, ncol = 2, byrow = T)
 } 
+
+fig_sizes <- function(){
+  list(
+    one_column_width = 3.4,
+    two_column_width = 7
+  )
+}

### 2018-05-21 paper/manuscript.Rmd
Add legend figure control configurations

@@
 
-```{r fig-control-configuration, fig.height=fig_control_config$height, fig.width=fig_control_config$width,fig.cap = "ASD"}
+```{r fig-control-configuration, fig.height=fig_control_config$height, fig.width=fig_control_config$width,fig.cap = "Maximum matchings and control configurations.
+In directed networks a maximum matching is the largest possible set of links that do not share start or end nodes (dark purple).
+Maximum matchings are not necessarly unique, instead each of them is related to a possible minimum driver node set in the network (the nodes to which an external control input, in orange, should be applied in order to ensure controllability).
+The size of the minimum driver node set *D* corresponds exactly to the number of unmatched nodes (the number of nodes in the network *N* minus the matching size).
+To account for network size, we use size of the minimum driver node set relative to the total number of nodes *n~D~ = D/N* as a measure of the extent to which the network structure can be harnessed to control the system."}
 replayPlot(fig_control_config$plot)

### 2018-05-21 main.R
Figure supp in main

@@ -48,7 +48,8 @@ example_plots_plan <- drake::drake_plan(
   en_chain = example_ntw_matchings_chain(),
   en_star = example_ntw_matchings_star(), 
   fig_control_config = make_fig_control_configurations(en_chain, en_star, en_direction), 
-  fig_struct_control = make_fig_structural_control(en_direction, en_structural)
+  fig_struct_control = make_fig_structural_control(en_direction, en_structural),
+  fig_supp_matching = make_fig_maximum_matching(en_direction)
 )
 
 reporting_plan <- drake::drake_plan(

### 2018-05-21 paper/supp-info.Rmd
Text maximum matching supp info

@@
 
+## Finding a single maximum matching {#one-maximum-matching}
+
 Our approach to find the minumum number of driver nodes relies on finding maximum matchings. 
-We start with a directed network in which the direction of the link represents the direction of control (Figure \@ref(fig:fig-direction-of-control)a). 
-We then construct an alternative representation of the directed network in which each node of the directed network is represented by two nodes that indicate their outgoing and incoming links respectively (Figure \@ref(fig:fig-direction-of-control)b).
+We start with a directed network in which the direction of the link represents the direction of control (Figure \@ref(fig:fig-maximum-matching-procedure) left panel). 
+We then construct an alternative representation of the directed network in which each node of the directed network is represented by two nodes that indicate their outgoing and incoming links respectively (Figure \@ref(fig:fig-maximum-matching-procedure) center panel).
 Finding a maximum matching in this alternative representation is equivalent to finding the largest possible set of edges in which one node on the left-hand side is connected to at most one node on the right-hand side.
 To find the maximum matching we use the push-relabel algorithm implemented in `max_bipartite_matching` in the R package igraph 1.0.1 [@Csardi2006a]. 
-Once we have the matching (shown in the Figure \@ref(fig:fig-direction-of-control)b) it is then easy to identify the roles of each node in this representation: nodes on the left-hand side that are connected to a matched (purple) link are superior while those connected to a matched link on the right-hand side are matched.
-This information can then be mapped back to the original representation to identify the control paths and the driver nodes in the network (Figure \@ref(fig:fig-direction-of-control)c). 
-Figure \@ref(fig:fig-direction-of-control)d--f illustrate this approach for a network with bidirectional links.
+Once we have the matching (shown in the Figure \@ref(fig:fig-maximum-matching-procedure) center panel) it is then easy to identify the roles of each node in this representation: nodes on the top-level that are connected to a matched (dark purple) link are superior while those connected to a matched link on the bottom-level are matched.
+This information can then be mapped back to the original representation to identify the control paths and the driver nodes in the network (Figure \@ref(fig:fig-maximum-matching-procedure) right panel).
 
-## Finding a single maximum matching {#one-maximum-matching}
 ```{r}

### 2018-05-21 paper/manuscript.Rmd
Using N instead of S for species number for consistency

@@
 This simple metric provides general indication of how difficult controlling a network might be, as systems that require a large number of external inputs to be fully controlled are intuitively more difficult or costly to manage.
-Specifically, following the structural controllability literature, we use the size of the minimum driver node set relative to the total number of nodes $n_D = \frac{D}{S}$ as a measure of the extent to which the network structure can be harnessed to control the community.
+Specifically, following the structural controllability literature, we use the size of the minimum driver node set relative to the total number of nodes $n_D = \frac{D}{N}$ as a measure of the extent to which the network structure can be harnessed to control the community.
 In an ecological context, external inputs can be thought of as management interventions that modify the abbundance of a particular species. 

### 2018-05-22 code/fig_all_matchings.R
Figure all maximum matchings in supp info

@@ -1,0 +1,94 @@
+make_fig_all_matchings <- function(en_direction, pdf_out = NULL){
+  n0 <- maximum_matching(en_direction[[2]])
+  n1 <- igraph::graph_attr(n0, "bipartite_representation")
+  n2 <- igraph::make_line_graph(n1) 
+  n3 <- igraph::complementer(n2)
+  cliques <- igraph::max_cliques(n3, 
+                                 min = igraph::graph_attr(n0, "matching_size"), 
+                                 max = igraph::graph_attr(n0, "matching_size"))
+
+  n1 %<>% igraph::vertex_attr("name") %>% 
+    stringr::str_replace("..f", "^+") %>%
+    stringr::str_replace("..t", "^-") %>%
+    igraph::set_vertex_attr(n1, "name", value = .) %>%
+    igraph::set_vertex_attr("type", value = "a") %>%
+    ntw_format_theme() %>%
+    add_property(element = "vertex", attr_name = "size",attr_base = "type", "TRUE ~ 25")
+  
+  line_names <- paste(igraph::ends(n1, 1:5)[,1], igraph::ends(n1, 1:5)[,2], sep = "-")
+  
+  n2 %<>%
+    igraph::set_vertex_attr("name", value = line_names) %>%
+    ntw_format_theme() %>%
+    add_property(element = "vertex", attr_name = "size",attr_base = "type", "TRUE ~ 45") %>%
+    add_property(element = "vertex", attr_name = "color", attr_base = "type", "TRUE ~ 'white'") %>%
+    add_property(element = "vertex", attr_name = "frame.color", attr_base = "type", "TRUE ~ 'white'") %>%
+    add_property(element = "vertex", attr_name = "shape", attr_base = "type", "TRUE ~ 'rectangle'")
+  
+  n3 %<>%
+    igraph::set_vertex_attr("name", value = line_names) %>%
+    ntw_format_theme() %>%
+    add_property(element = "vertex", attr_name = "size",attr_base = "type", "TRUE ~ 45") %>%
+    add_property(element = "vertex", attr_name = "color", attr_base = "type", "TRUE ~ 'white'") %>%
+    add_property(element = "vertex", attr_name = "frame.color", attr_base = "type", "TRUE ~ 'white'") %>%
[…]

### 2018-05-22 code/plot_ntw.R

@@ -59,6 +59,8 @@ plot_examples <- function(x, ...){
                       vertex.label.color = igraph::V(x)$label.color,
                       vertex.size = igraph::V(x)$size,
                       vertex.color = igraph::V(x)$color,
+                      vertex.frame.color = igraph::V(x)$frame.color,
+                      vertex.shape = igraph::V(x)$shape,
                       # vertex.label.family = fam,
                       # vertex.label.color = l_c,
                       edge.width = igraph::E(x)$width,
@@ -149,19 +151,21 @@ plot_example_ntw <- function(x, ...){
 }
 
 # common formatting
-ntw_format_theme <- .  %>%
-  fancify_vertex_name() %>%
-  add_property(element = "edge", attr_name = "color", attr_base = "type", 'TRUE ~ "black"') %>%
-  add_property(element = "edge", attr_name = "label.color", attr_base = "type",'TRUE ~ "black"') %>%
-  add_property(element = "edge", attr_name = "label.font", attr_base = "type",'TRUE ~ 2') %>%
-  add_property(element = "vertex", attr_name = "color",attr_base = "type", "TRUE ~ get_color('base')") %>%
-  add_property(element = "vertex", attr_name = "frame.color", attr_base = "type","TRUE ~ 'black'") %>%
-  add_property(element = "vertex", attr_name = "size",attr_base = "type", "TRUE ~ 55") %>%
-  add_property(element = "vertex", attr_name = "label.cex", attr_base = "type","TRUE ~ 1") %>%
-  add_property(element = "vertex", attr_name = "label.color", attr_base = "type","TRUE ~ 'black'") %>%
-  add_property(element = "edge",attr_name = "arrow.size", attr_base = "control_type", "TRUE ~ 0.4") %>%
-  add_property(element = "edge",attr_name = "arrow.width", attr_base = "control_type", "TRUE ~ 0.7") 
-
+ntw_format_theme <- function(x){
+  x %>%
+    fancify_vertex_name() %>%
+    add_property(element = "edge", attr_name = "color", attr_base = "type", 'TRUE ~ "black"') %>%
+    add_property(element = "edge", attr_name = "label.color", attr_base = "type",'TRUE ~ "black"') %>%
+    add_property(element = "edge", attr_name = "label.font", attr_base = "type",'TRUE ~ 2') %>%
[…]

### 2018-05-22 main.R

@@ -49,7 +49,8 @@ example_plots_plan <- drake::drake_plan(
   en_star = example_ntw_matchings_star(), 
   fig_control_config = make_fig_control_configurations(en_chain, en_star, en_direction), 
   fig_struct_control = make_fig_structural_control(en_direction, en_structural),
-  fig_supp_matching = make_fig_maximum_matching(en_direction)
+  fig_supp_matching = make_fig_maximum_matching(en_direction), 
+  fig_all_matching = make_fig_all_matchings(en_direction)
 )
 
 reporting_plan <- drake::drake_plan(

### 2018-05-22 paper/supp-info.Rmd
Figure all maximum matchings in supp info
Add figure example network

@@
 
+```{r}
+drake::loadd(fig_all_matching)
+```
+
+```{r fig-all-maximum-matching, fig.height=fig_all_matching$height, fig.width=fig_all_matching$width,fig.cap = "Finding a maximum matching in a complex network.
+(left) Directed network that indicate the direction of control between species.
+(center) Alternative bipartite representations of the directed networks.
+(right) The matchings in the bipartite representation mapped back to the original network."}
+replayPlot(fig_all_matching$plot)
+```
+
+```{r}
+drake::loadd(fig_small_network)
+```
+
+```{r fig-small-network, fig.height=fig_small_network$height, fig.width=fig_small_network$width,fig.cap = "**Illustration of the procedure with an empirical network**.
+(a) The initial visitation network.
+(b) The directed network in which the direction of control is determined based on the mutual dependences and asymmetries.
+(c) One of the possible maximum matchings calculated using the procedures illustrated in the Figures \\@ref(fig:fig-direction-of-control) and \\@ref(fig:fig-finding-all-matchings)"}
+replayPlot(fig_small_network$plot)
+```
+
 ## Finding all possible minimum driver node sets

### 2018-05-22 code/fig_small_ntw_example.R

@@ -1,0 +1,108 @@
+make_small_network <- function(networks, pdf_out = NULL){
+  node_size <- 40
+  n1 <- networks$SA_exp
+  v_names <- dplyr::data_frame(full_name = igraph::V(n1)$name) %>%
+    dplyr::mutate(abb_name = letters[1:nrow(.)],
+                  full_name = stringr::str_replace(full_name, "[0-9]", ""),
+                  full_name = stringr::str_replace(full_name, "\\?rutitarse", "rufitarse"))
+  n1 %<>% igraph::set_vertex_attr("name", value = v_names$abb_name)  %>%
+    ntw_format_theme() %>%
+    igraph::set_vertex_attr("size", value = node_size) %>%
+    igraph::set_edge_attr("label", value = igraph::E(.)$weight) %>%
+    igraph::set_edge_attr("color", value = "grey")
+  n2 <- as_directed_network(n1, higher_level = "pol")  %>%
+    ntw_format_theme() %>%
+    igraph::set_vertex_attr("size", value = node_size)
+  n3 <- maximum_matching(n2) %>%
+    ntw_matched_theme(named = T) %>%
+    igraph::set_vertex_attr("size", value = node_size)
+  
+  heading_height <- 0.25
+  fig_height <- 1
+  legend_height <- 0.15
+  table_height <- 1
+  heights <- c(heading_height, fig_height,
+               heading_height, fig_height,
+               heading_height, fig_height, legend_height, 
+               table_height)
+  
+  total_width <- fig_sizes()$two_column_width
+  x <- total_width/2
+  widths <- c(x, x)
+  
+  pdf(pdf_out, width = sum(widths), height = sum(heights), paper='special')
+  if(is.null(pdf_out)) dev.control("enable")
+  
+  c(20,20,
+    10,10,
+    21,21,
+    11,11,
+    22,22,
+    12,12,
+    80,80,
+    90,90) %>%
+    dplyr::dense_rank() %>%
+    matrix(ncol = 2, byrow = T) %>%
+  layout(widths = widths, heights = heights)
+  par(mar = rep(0,4), bg = "white", xpd = NA)
+  
+  l <- igraph::layout_as_bipartite(n1, igraph::V(n1)$type == "pla") %>%
[…]

### 2018-05-22 main.R

@@ -50,7 +50,8 @@ example_plots_plan <- drake::drake_plan(
   fig_control_config = make_fig_control_configurations(en_chain, en_star, en_direction), 
   fig_struct_control = make_fig_structural_control(en_direction, en_structural),
   fig_supp_matching = make_fig_maximum_matching(en_direction), 
-  fig_all_matching = make_fig_all_matchings(en_direction)
+  fig_all_matching = make_fig_all_matchings(en_direction), 
+  fig_small_network = make_small_network(networks)
 )
 
 reporting_plan <- drake::drake_plan(

### 2018-05-23 paper/supp-info.Rmd
Finding all matchings section in supp info

--- 2018-05-21 paper/supp-info.Rmd
@@
   - \usepackage{setspace}
+  - \usepackage{xr}
+  - \externaldocument[M-]{manuscript}
 bibliography: references.bib
@@
 
-## Finding all possible maximum matchings
+## Finding all possible maximum matchings {#all-maximum-matching}
+
+The algorithm implemented in `max_bipartite_matching`, however, is only able to find **one** of possibly many maximum matchings in a network. 
+Though one maximum matching is enough to calculate *n~D~* and hence to provide indication of the manageability of a community, it is not sufficient to estimate the role of individual species. 
+To do that, we need to calculate all possible maximum matchings (or, equivalently, all maximal cardinality matchings in weighted networks like ours). 
+To do this, we again start from the alternative bipartite representation in Figure \@ref(fig:fig-maximum-matching-procedure)b and assign an identity to each of the links in the network.
+We will call this bipartite representation *P*. 
+We then construct the line graph of the alternative bipartite representation *L(P)* (Figure \@ref(fig:fig-all-maximum-matching)). 
+Each node in *L(P)* represents a link in *P* and these are connected to each other if and only if they share a common node in *P*. 
+We then calculate *H*, the complement graph of *L(P)* and identify all of its maximal cliques (Figure \@ref(fig:fig-all-maximum-matching)). 
+Here some extra definitions are necessary. 
+First, *H* is a graph with the same nodes as *L(P)* but that has a link between two nodes if and only if there is not a link in *L(P)*. 
+Second, a clique is a subset of nodes such that all pairs of them are linked. 
+Lastly, a maximal clique is a clique such that there are no cliques composed of more nodes [@Gutin2013]. 
+In this example, there are two maximal cliques: the one formed by 1, 3 and 5, and the one formed by 2, 3 and 5. 
+The final step is then to map these cliques onto the original network to obtain all possible maximal cardinality matchings as shown in Figure \@ref(M-fig:fig-control-configuration) in the main text.
+
+```{r}
+drake::loadd(fig_all_matching)
+```
+
+```{r fig-all-maximum-matching, fig.height=fig_all_matching$height, fig.width=fig_all_matching$width,fig.cap = "Finding all possible maximum matchings.
+From left to right: alternative bipartite representation of the directed network in Figure \\@ref(fig:fig-maximum-matching-procedure)a.
+Line graph of the network.
+Complement of the network.
+The two maximal cliques are shown in dark purple."}
+replayPlot(fig_all_matching$plot)
+```
+
+To further ilustrate our methodology here, we also show the approach for the smallest of our empirical networks, the uninvaded network at site 10 (Table \@ref(tab:table-network-properties); Figure \@ref(fig:fig-small-network)).
+This network is composed of 19 species of which three are non-invasive plants and the other 16 are pollinators. 
+The one-to-one relationship between matched and superior nodes implies that in order to achieve full network controllability, most pollinators would be unmatched, and hence are classified as driver nodes that require external intervention.
+At the same time, both plants in the community, *Heracleum sphondylum* and *Rubus fructicosus*, and one of the pollinators, *Orthotylus/Lygocorus*, tend to be classified as superior nodes.
+
+```{r}
+drake::loadd(fig_small_network)
+```
+
+```{r fig-small-network, fig.height=fig_small_network$height, fig.width=fig_small_network$width,fig.cap = "Illustration of the procedure with an empirical community.
+The visitation network (top), the number of visits between species pairs is shown on each link.
+The directed network in which the direction of control is determined based on the mutual dependences (middle).
+One of the possible maximum matchings of this network (bottom)."}
+replayPlot(fig_small_network$plot)
+```
 

### 2018-05-23 code/fig_all_matchings.R

@@ -13,7 +13,7 @@ make_fig_all_matchings <- function(en_direction, pdf_out = NULL){
     igraph::set_vertex_attr(n1, "name", value = .) %>%
     igraph::set_vertex_attr("type", value = "a") %>%
     ntw_format_theme() %>%
-    add_property(element = "vertex", attr_name = "size",attr_base = "type", "TRUE ~ 35")
+    add_property(element = "vertex", attr_name = "size",attr_base = "type", "TRUE ~ 33")
   
   line_names <- paste(igraph::ends(n1, 1:5)[,1], igraph::ends(n1, 1:5)[,2], sep = "-")
   
@@ -78,7 +78,6 @@ make_fig_all_matchings <- function(en_direction, pdf_out = NULL){
   standalone_text("L(P): line graph of P", font = 2)
   standalone_text("H: complement of L(P)", font = 2)
   standalone_text("max. cliques in H", font = 2)
-  
   
   p <- recordPlot()
   dev.off()

### 2018-05-24 paper/manuscript.Rmd
Species roles section in the methods
Pending the statistical analyses

@@
 
+While calculating the size of the minimum drive node set can measure the controllability of an ecological community, it does not provide information about the role that particular species play. 
 Our second key question is related to how species differ in their ability to drive the population dynamics of the community. 
 Ecologically, these differences are relevant because resources and data are limited, and therefore full control is unfeasible. 
-We are mostly interested in two specific aspects.
-First how species differ in their relative , second, how species
+To answer this question, we make two kind of distinctions between species from a control perspective.
 
-is management interventions should be focused on the set of species that might provide the largest impact. 
-While calculating the size of the minimum drive node set can measure the controllability of an ecological community, it does not provide information about the role that particular species play.
+First, we harness the fact that maximum matchings in a network are often not unique, and each maximum matching indicates unique paths that can potentially be used to control the network. 
+Specifically we use the frequency with which a species is part of the multiple minimum driver node sets, its control capacity $\phi$, as an estimation of its relative importance in driving the state of the community as a whole [@jia_control_2013].
+For example, a species with a control capacity $\phi_i= 1$ is a one that requires external input in every single control configuration. 
+This is, if we were to drive the community to an arbitrary alternate state, we would need to apply a management intervention to this species under any optimal control strategy.
 
-Moreover, maximum matchings in a network are often not unique, and each maximum matching indicates unique paths that can potentially be used to control the network. 
-We harness this property and use a network's complete set of maximum matchings to characterise each species' relative importance in driving the state of the community. 
-One possibility is to characterise a species by the frequency *f~D~* with which it is classified as a driver node within this set of matchings.
-However, the profile of our networks indicates that a large proportion of species were classified as driver nodes because of external interventions required to achieve **full** controllability and not because they influence the abundance of other species (Supporting Information S2).
-Furthermore, the precise role of driver nodes is more ambiguous when full control is unfeasible or undesired—often the case in ecological settings.
-We therefore also calculate the frequency *f~S~* with which a species is classified as a superior node since this is the frequency with which they form part of possible control paths.
+Intuitively, to calculate a species control capacity $\phi$ we need to enumerate all possible maximum matchings (we detail the algorithm to find all maximum matchings in the Supplementary Information section \@ref(S-all-maximum-matching)).
+However, enumerating all maximum matchings extremely expensive from a computational perspective—a network with a couple dozen nodes could be controlled with several hundred million unique matchinghs. 
+To solve this problem we instead employ a recently developed algorithm that reveals the control correlations between the nodes in the graph [@zhang_input_2016, Supplementary Information section \@ref(S-input-graph)].
+Using this algorithm we are able to obtain every minimum driver node set with information obtained from a single maximum matching. 
+The end result is that we are now able to calculate the control capacity $\phi_i$ of every node in linear time—rather than polynomial as the algoritm for matching enumeration requires.
 
-Most commonly, structural controllability assumes unweighted networks—links exist or not, and hence *f~D~* and *f~S~* can be calculated by computing all possible maximum-cardinality matchings. 
-However, we take the link weights into account when calculating the matchings here because the weights can reveal significant ecological patterns and processes that might be undetectable in unweighted networks [@Scotti2007; @Tylianakis2007; @Vazquez2007; @Kaiser-Bunbury2010a].
-Additionally, species *A* may interact with both species *B* and *C* but depends strongly on *B* and only weakly on *C*. 
-Intuitively, a management intervention designed to indirectly modify the abundance of species *A* is more likely to succeed if the abundance of *B*, rather than *C*, is directly controlled.
-A complication of including the interaction weight when calculating the maximum matching, however, is that empirical interaction strengths are to some extent stochastic and depend on proximate factors such as sampling method and intensity [@Gibson2011].
-We overcome this issue by calculating all maximal cardinality matchings and then ranking them by their matching weight. 
-By following this approach, we effectively give priority to the species that participate in the pathways that potentially have the largest impact on the community while acknowledging the limitations associated with sampling and its potential restrictions [@Jordano2016].
+A species control capacity $\phi$ allow us to identify species that are critical to change or maintain the state of the community. 
+However, in ecological settings, changing the state of the community as a whole is often not required or undesired. 
+Consequently, we make a second distinction between nodes based on wether they form part of possible control paths in the network and therefore are likely to influence the abbundance of another species.
+We identify those species by checking wether they are classified as a superior node, this is they are at the beginning of a matched link. 
+While unmatched nodes correspond to those that should be influenced with an external control input, superior nodes correspond to those that influence other species internally. 
+Conveniently, with the execption of some patological cases, superior nodes are such across every control configuration and therefore knowing one maximum matching provides enough information on whether a species is likely to play an important role at influencing the abundance of other species or not.
 
-Our second key question was related to how species differ in their ability to drive the population dynamics of the community. 
-To quantify this importance, we computed all maximal cardinality matchings in each network. 
-We then calculated the frequency with which each species *i* was a driver (*f~D~*) or a superior node (*f~S~*) in the set of matchings that had a matching weight greater or equal to 0.8 times the weight of the maximum matching.
-We selected this threshold as it provided a high agreement between networks quantified by visitation and pollination efficiency as well as between our weighting/directionality assumptions; however, the choice of this threshold had a negligible impact on any results (Supporting Information S8).
-Details about the computational procedure to find all maximal cardinality matchings of a network can be found in Supporting Information S1 and Figure S2.
+We then examined whether any species-level structural properties could predict a species control capacity $\phi$ and the likelihood of being a superior node.
+Still need to decide how to do this and how to compare traditional centrality metrics to the new control based ones.
 

### 2018-05-24 paper/manuscript.Rmd
Refs from manuscript to supp info are now in parenthesis to improve flow

@@
 The key is to note that the conditions of structural controllability imply that, just like the one to one relationship between jobs and applicants, there needs to be a one to one relationship between *superior* and *subordinate* nodes (Figure \@ref(fig:fig-example-networks)b, bottom left).
-We use the maximum matching algorithm to find an optimal pairing of superior and subordinate nodes in a way consistent with the controllability conditions. 
+We use the maximum matching algorithm to find an optimal pairing of superior and subordinate nodes in a way consistent with the controllability conditions (supplementary information section \@ref(S-one-maximum-matching)).
 The result is that a matching can actually be decomposed into a set of paths that reveal how a control signal can flow across the links in a network to reach every node that compose it. 
@@
 ```
-
-The technical details of the algorithm we use to find a maximum matching in a network can be found in the supplementary information section \@ref(S-one-maximum-matching).
 
@@
 These covariates included the total number of species, plant richness, pollinators richness, the ratio of plant to pollinator richness, the link density (connectance), and the study site (as a two-level factor).
-In addition, we also explored whether real networks differ in their architecture from random ones in a concerted way; further details about this procedure can be found in the supplementary information section \@ref(S-randomisations).
+In addition, we also explored whether real networks differ in their architecture from random ones in a concerted way (supplementary information section \@ref(S-randomisations)).
 

### 2018-05-24 code/fig_input_graph.R
Add figure input graph
Addresses #5

@@ -1,0 +1,135 @@
+get_input_graph_step_nets <- function(x){
+  n1 <- x %>%
+    control_capacity() %>%
+    ntw_format_theme()
+  
+  n2 <- n1 %>%
+    ntw_format_theme() %>%
+    ntw_matched_theme(named = T) %>%
+    add_property(element = "vertex", attr_name = "size",attr_base = "type", "TRUE ~ 55")
+  
+  n3 <- n1$input_graph %>%
+    ntw_format_theme() %>%
+    add_property(element = "vertex", attr_name = "color",attr_base = "input_node", "type == TRUE ~ get_color('dark')", "TRUE ~ get_color('base')") %>%
+    add_property(element = "vertex", attr_name = "label.color",attr_base = "input_node", "type == TRUE ~ 'white'", "TRUE ~ 'black'") 
+  
+  list(n1, n2, n3)
+}
+
+make_fig_input_graph <- function(en_direction, en_star, en_chain, pdf_out = NULL){
+  
+  n1 <- get_input_graph_step_nets(en_direction[[2]])
+  n2 <- get_input_graph_step_nets(en_star)
+  n3 <- get_input_graph_step_nets(en_chain)
+  
+  heading_height <- 0.25
+  fig_height <- 0.75
+  sep_height <- 0.05
+  legend_height <- 0.2
+  heights <- c(heading_height, fig_height, sep_height, fig_height, sep_height, fig_height, legend_height)
+  
+  total_width <- fig_sizes()$two_column_width
+  x <- total_width/3
+  widths <- c(x, x, x)
+  
+  pdf(pdf_out, width = sum(widths), height = sum(heights), paper='special')
+  if(is.null(pdf_out)) dev.control("enable")
+  
+  c(80,81,82,
+    10,11,12,
+    90,90,90,
+    20,21,22,
+    91,91,91,
+    30,31,32,
+    70,70,70) %>%
+    dplyr::dense_rank() %>%
+    matrix(ncol = 3, byrow = T) %>%
+    layout(widths = widths, heights = heights)
+  par(mar = rep(0,4), bg = "white", xpd = NA)
+  
+  ## DIRECTION NETWORK
+  # directed network
+  l <- direction_layout() %>%
+    rescale_layout(xlim = c(-1, 1)* 1.25, ylim = c(-1, 1)* 0.5)
[…]

### 2018-05-24 code/plot_ntw.R

@@ -135,6 +135,7 @@ get_color <- function(x = T){
     x == "unmatched" ~ my_pallete()$light_purple,
     x == "control" ~ my_pallete()$dark_orange,
     x == "base" ~ my_pallete()$light, 
+    x == "dark" ~ "grey10",
     x == "bg" ~ "grey95",
     x == "bg_dark" ~ "grey90",
     TRUE ~ "white"

### 2018-05-24 main.R

@@ -51,7 +51,8 @@ example_plots_plan <- drake::drake_plan(
   fig_struct_control = make_fig_structural_control(en_direction, en_structural),
   fig_supp_matching = make_fig_maximum_matching(en_direction), 
   fig_all_matching = make_fig_all_matchings(en_direction), 
-  fig_small_network = make_small_network(networks)
+  fig_small_network = make_small_network(networks),
+  fig_input_graph = make_fig_input_graph(en_direction, en_star, en_chain)
 )
 
 reporting_plan <- drake::drake_plan(

### 2018-05-24 paper/reviewers-response.Rmd
Compose reviewers comments doccument
Close #7

---
title: "Ecological network control"
subtitle: "Response to Reviewers"
author: "Fernando Cagua, Kate L. Wootton, Daniel B. Stouffer"
classoption: a4paper
csl: journal-of-ecology.csl
documentclass: artikel1
output: 
  bookdown::pdf_document2: 
    keep_tex: yes
    toc: false
header-includes:
  - \usepackage{booktabs}
  - \usepackage{setspace}
  - \usepackage{xr}
  - \externaldocument[M-]{manuscript}
bibliography: references.bib
---

\doublespacing

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, 
                      warning = FALSE)
```

# Editor comments

> "I agree with the AE and reviewers that this is an interesting and potentially important manuscript. I support the AE's decision to reject but invite resubmission for all the reasons mentioned. I encourage resubmission if you feel that you can better bring out the conceptual importance of their work for plant ecologists. If you wish to strengthen the applied focus with specific conservation recommendations then you may wish to submit to Journal of Applied Ecology. Reviewer 1 offers suggestions for both approaches. I hope that you choose the former."

#  Assocciate Editor comments

> Both reviewers see potential value in the application of control theory to species interaction networks and found the work to be of interest. I agree that the method and its application to plant-pollinator networks are interesting, particularly the findings that contrast invaded vs uninvaded networks and use novel metrics to describe the influence of invasive species in networks. Both reviewers also note, however, that the current ms falls short of clearly and convincingly demonstrating the utility of control theory in making management decisions. They call for more in-depth exploration and illustration of what novel and important contributions this method would make to conservation. For these reasons, this work may be better-suited to a more applied journal (e.g., Journal of Applied Ecology), assuming the ms is revised in the recommended direction.

# Reviewer one comments

> I read with great interest the manuscript by Cagua et al. on “Quantifying the manageability of pollination networks in an invasion context”. The authors use control theory to develop an approach to assess how ecological networks – here pollination networks – can be managed, and test the approach on ten pairs of invaded and uninvaded plant-pollinator communities. Overall, the methodological approach appears to be sound (I’m not familiar with control theory, so I’ll have to leave in-depth assessment to an expert), the descriptions and rationale behind the assumptions used to develop the methods are logical and reasonable, and the illustration of the concept using published networks seems appropriate. Also, although the manuscript may require a few minor edits it is well and clearly written. I do, however, have some concerns about the applicability of the approach and the findings, which I’ll describe in more detail below.

> When I first read the title and the abstract of the manuscript I was excited about the prospect of reading about a way forward using ecological networks to improve ecosystem conservation. Now, having read the manuscript twice, I’m not persuaded that the proposed approach really advances our ability to conserve or restore ecological communities as the authors claim, or whether the approach provides primarily another, rather complex, way of analysing networks and describing the role of species in networks. As it is, the authors fail to convince me that the developed approach really advances our ability to prioritise species for ecosystem conservation, nor does the manuscript offer novel insights into the role and importance of certain species in a network and for ecosystem functioning. I’ve little doubt that there are ecological and theoretical justifications for combining control and network theory, but the authors don’t yet show that their proposed methods are overly useful in applied conservation.

> I can see two ways forward: the authors re-arrange and re-word the manuscript to focus on the ecological advances that such an approach would bring to explaining and predicting network structure; or the authors describe in more detail a few scenarios in which conservation practitioners and managers could apply the proposed method to ‘improve’ management strategies or measure the efficacy of interventions. The latter would require a stronger justification of the advantages of control-theory approach compared to the classic species-level network metrics.

> In short, I feel that the manuscript is currently a hybrid between ecological theory and applied conservation without being fully beneficial for either of the two disciplines. With a few changes to the manuscript, the interpretation and presentation of the results, and a re-write of the discussion with more tangible points and concrete examples from practical experience, the manuscript has the potential to be a solid contribution to the field of applied ecology.

> One last minor remark, the authors have overlooked some key references in the field of restoration/conservation and ecological interactions/networks, which would strengthen the manuscript further, e.g. 
Harvey, E., Gounand, I., Ward, C.L. & Altermatt, F. (2017) Bridging ecology and conservation: from ecological networks to ecosystem function. Journal of Applied Ecology, 54, 371-379; 
Devoto, M., Bailey, S., Craze, P. & Memmott, J. (2012) Understanding and planning ecological restoration of plant–pollinator networks. Ecology Letters, 15, 319-32; 
Kaiser-Bunbury, C.N., Mougal, J., Whittington, A.E., Valentin, T., Gabriel, R., Olesen, J.M. & Blüthgen, N. (2017) Ecosystem restoration strengthens pollination network resilience and function. Nature, 542, 223-227;
Pires, M.M., Marquitti, F.M.D. & Guimarães Jr, P.R. (2017) The friendship paradox in species-rich ecological networks: Implications for conservation and monitoring. Biological Conservation, 209, 245-252.

# Reviewer two comments

> The management of complex ecological networks is of vast importance for the conservation of the natural world. While the field of ecological networks is vast few have tackle this question in a practical way. This paper would make a significant contribution to a field that needs to change direction if it is to help inform conservation as often purported in studies from the this field.

> The control theory approach is very interesting. I think however there needs to be more clarity in the paper. It is hard to read. A reworking of it including using descriptions of the variable through out instead of variable names would improve this.

> Better context needs to be given for previous work to look at the management of networks in ecology. There are a few papers and knowing how this one differs from these (not just the ones that look at node importance for example) is important. Some of these papers are mentioned in the discussion but in the intro it is important to know what they do and why this paper is novel.

> Finally I think it is important to provide context about what kind of decisions are being made and could be informed by this approach. Who is managing plant-pollinator networks and what choices would they actually be making. Some examples should be expanded on. And also how would the outputs of this work actual inform choices and guide prioritization

> And finally I think mentioning the extreme uncertainty mostly seen in networks in the real world is key, how can approaches deal with this needs to be discussed. What do we need to think about interms of key information to use this approach.

### 2018-05-24 main.R

@@ -59,7 +59,9 @@ reporting_plan <- drake::drake_plan(
   render_pdf(drake::knitr_in('paper/supp-info.Rmd'), 
              drake::file_out('paper/supp-info.pdf'), clean_md = FALSE),
   render_pdf(drake::knitr_in('paper/manuscript.Rmd'), 
-             drake::file_out('paper/manuscript.pdf'), clean_md = FALSE)
+             drake::file_out('paper/manuscript.pdf'), clean_md = FALSE),
+  render_pdf(drake::knitr_in('paper/reviewers-response.Rmd'), 
+             drake::file_out('paper/reviewers-response.pdf'), clean_md = FALSE)
 )
 
 project_plan <- rbind(read_data_plan, basic_analysis_plan, example_plots_plan, reporting_plan)

### 2018-05-25 paper/cover-letter.tex
Add cover letter (tex file)
Addresses #8

--- 2017-06-16 paper/cover-letter.tex
@@
-\documentclass[10pt, a4paper]{letter}
+\documentclass{letter}
+\usepackage[a4paper, total={5in, 9.1in}]{geometry}
+\usepackage{setspace}
+\signature{Fernando Cagua \\ (in behalf of all authors)}
+\address{Centre for Integrative Ecology \\ School of Biological Sciences \\ University of Canterbury \\ Private Bag 4800 \\ 8140 Christchurch \\ New Zealand}
+\begin{document}
+\begin{letter}{James Ross \\ Assistant Editor \\ Journal of Ecology}
+\opening{Dear James:}
 
-\begin{document}
+\onehalfspacing
 
-\begin{letter}{
-       %\vspace*{20pt}
-       Prof. Spencer Barret\\
-       Editor in Chief\\
-       Proceedings of the Royal Society B}
+We are thankful to the senior and associate editors, Prof. James Ross and Prof. Nicole Rafferty, and two anonymus reviewers for the insightful comments to improve the manuscript. 
+We are also grateful for the opportunity to resubmit. 
+In the attached documment you can find a detailed response to each of their comments. 
+Here we summarise the main changes to the manuscript.
 
-\opening{Dear Proffesor Barrett,}
+Briefly, our paper explores the possible applications of control theory in an ecological context. 
+We see potential in our paper to contribute to both applied and theoretical aspects in ecology. 
+However in our initial submission we lingered midway between these two directions and—as the editors and reviewers pointed out—we failed to address either option successfuly.
+We have re-inspected our manuscript and tink that the theoretical insights are stronger. 
+As a consequence in this revision we have chosen to focus on the conceptual aspect of our approach at the expense of numerous, but weak, connections with conservation and applied ecology.
 
-We are submitting the manuscript entitled ``Quantifying the manageability of pollination networks in an invasion context'' to be considered for publication at \emph{Proceedings B}.
+Adopting a primarely conceptual focus allowed us to be clearer about the justification, methodology and potential insights of our approach. 
+However, improving clarity while successfully tying the conceptual motivation with our findings required more than some changes to some paragraphs or sections of the manuscript. 
+Therefore, we have rewriten almost entirely the manuscript and the supplementary materials. 
+We maintain the methodology and findings, but there has been a major change in the way we justify the study, introduce novel concepts to the ecological domain, and present our conclusions.
 
-Central to this manuscript is the introduction, development, and application of the theoretical concept of \textbf{ecological manageability}.
-Based on the patterns of interactions between species, this idea can provide two main pieces of information. 
-First, it allows to quantify the \textit{community manageability}---an indication of the difficulty of controlling the abundances of all species in the community. 
-Second it allows to identify \textit{driver species}--- those species with a disproportionate ability to alter other species' abundances.  
-Here, we use this concept as a framework to study the changes induced by biotic invasions to pollination networks.
-
-Multiple empirical observations have suggested that the structural changes caused by invasions may lead to changes on ecosystem resilience. 
-Our study is the first to use empirical data to provide theoretical support for this idea. 
-Furthermore, our approach to identify driver species and quantify their relative importance, is unique in that it is based directly on the aspects of network structure that determine the behavior of the community as a holistic dynamical system.
-Our results also highlight the extent to which some species---invaders in particular---can drive the dynamics of other species across their community, and also identify ``asymmetric dependence'' as the potential mechanism driving the interspecific differences.
-
-Despite our focus, understanding how drivers of ecosystem change affect ecosystem dynamics is not exclusive to mutualistic communities. 
-Indeed, we envisage the application of the concepts we introduce to answer a wide range of ecological questions in communities structured by different types of interactions.
-As such, we have sought to highlight the methodology necessary for its implementation---an extension of recently developed tools at the interface of complex systems and control theory---thoroughout the manuscript.
-
-Our study fundamentally lies within ecological theory, yet it has ramifications pertinent to ecological application. 
-Indeed, we show in the paper that concepts like ``manageability'' have the potential to stimulate much needed research that reduce the gap between theory and management.
-Hopefully our study and more like it will set us on the track to informed, rather than hopeful, ecosystem interventions.
-
-Lastly, please note that the enclosed work represents a novel contribution for all co-authors involved and no related work published, in press, or submitted during this or last year has been cited.
+We look forward to further feedback and hope that the editors and reviewers find these changes satisfactory.
 
 \closing{Regards,}
-
-Daniel B. Stouffer
-
 \end{letter}
-
 \end{document}

### 2018-05-25 main.R

@@ -61,7 +61,9 @@ reporting_plan <- drake::drake_plan(
   render_pdf(drake::knitr_in('paper/manuscript.Rmd'), 
              drake::file_out('paper/manuscript.pdf'), clean_md = FALSE),
   render_pdf(drake::knitr_in('paper/reviewers-response.Rmd'), 
-             drake::file_out('paper/reviewers-response.pdf'), clean_md = FALSE)
+             drake::file_out('paper/reviewers-response.pdf'), clean_md = TRUE, clean_tex = TRUE), 
+  compile_pdf(drake::file_in('paper/cover-letter.tex'), 
+              drake::file_out('paper/cover-letter.pdf'))
 )
 
 project_plan <- rbind(read_data_plan, basic_analysis_plan, example_plots_plan, reporting_plan)

### 2018-05-25 paper/manuscript.Rmd
Describe things to do in methods

@@
 We then examined whether any species-level structural properties could predict a species control capacity $\phi$ and the likelihood of being a superior node.
-Still need to decide how to do this and how to compare traditional centrality metrics to the new control based ones.
+*TODO: Still need to decide how to do this and how to compare traditional centrality metrics to the new control based ones.
+Will probably base the comparision on stability/feasibility metrics or/and on coextinction of species groups.*
 

### 2018-05-25 paper/reviewers-response.Rmd
Add some responses to reviewers comments
Close #8

@@
 title: "Ecological network control"
-subtitle: "Response to Reviewers"
+subtitle: "JEcol-2017-0720 - Detailed response to comments"
 author: "Fernando Cagua, Kate L. Wootton, Daniel B. Stouffer"
@@
     toc: false
+    number_sections: false
 header-includes:
-  - \usepackage{booktabs}
   - \usepackage{setspace}
@@
   - \externaldocument[M-]{manuscript}
-bibliography: references.bib
+  - \externaldocument[S-]{supp-info}
 ---
@@
 ```
+
+We are thankful to the editors, James Ross and Nicole Rafferty, and two anonymus reviewers for the insightful comments to improve the manuscript. 
+In the following sections you can find a detailed response to each comment. 
+Here we summarise the main changes to the manuscript.
 
@@
 
+Thanks to the Senior Editor, James Ross, for his comments his decision to allow resubmission. 
+From the two reccomended alternatives, in line with the editor's preference, we have chosen to focus on the conceptual importance of our work. 
+To do this effectively, we had to rewrite both the manuscript and the supplementary materials almost completely. 
+We think the extra effort was wort as we feel the paper is does a better job at explaining clearly the untility of the proposed approach.
+
 #  Assocciate Editor comments
 
-> Both reviewers see potential value in the application of control theory to species interaction networks and found the work to be of interest.
+> "Both reviewers see potential value in the application of control theory to species interaction networks and found the work to be of interest.
 I agree that the method and its application to plant-pollinator networks are interesting, particularly the findings that contrast invaded vs uninvaded networks and use novel metrics to describe the influence of invasive species in networks.
@@
 They call for more in-depth exploration and illustration of what novel and important contributions this method would make to conservation.
-For these reasons, this work may be better-suited to a more applied journal (e.g., Journal of Applied Ecology), assuming the ms is revised in the recommended direction.
+For these reasons, this work may be better-suited to a more applied journal (e.g., Journal of Applied Ecology), assuming the ms is revised in the recommended direction."
 
-# Reviewer one comments
+We thank the Associate Editor Nicole Rafferty for the constructive feedback and highlighting the strengths of the paper. 
+As we described in the cover letter and in the response to the senior editor, we opted for strengthening the conceptual component rather than empahsising its application in specific management and conservation scenarios.
+We took this decision because of mainly two reasons. 
+First, the empirical data we use does not explicitly inlcudes any management or conservation scenarios. 
+As a consequence, despite the potential of the approach, at the moment we lack direct evidence of the utility of the approach for management decisons. 
+Second, we think that a conceptual approach offered a greater opportunity to highlight the stongest/most interesting aspects of the paper. 
+Namely the contrasts between invaded and uninvaded communities and the role of invasive species, as the reviewer points out.
 
-> I read with great interest the manuscript by Cagua et al.
-on “Quantifying the manageability of pollination networks in an invasion context”.
+# Reviewer comments #1
+
+> "The management of complex ecological networks is of vast importance for the conservation of the natural world.
+While the field of ecological networks is vast few have tackle this question in a practical way.
+This paper would make a significant contribution to a field that needs to change direction if it is to help inform conservation as often purported in studies from the this field."
+
+> "The control theory approach is very interesting.
+I think however there needs to be more clarity in the paper.
+It is hard to read.
+A reworking of it including using descriptions of the variable through out instead of variable names would improve this."
+
+> Better context needs to be given for previous work to look at the management of networks in ecology.
+There are a few papers and knowing how this one differs from these (not just the ones that look at node importance for example) is important.
+Some of these papers are mentioned in the discussion but in the intro it is important to know what they do and why this paper is novel.
+
+> Finally I think it is important to provide context about what kind of decisions are being made and could be informed by this approach.
+Who is managing plant-pollinator networks and what choices would they actually be making.
+Some examples should be expanded on.
+And also how would the outputs of this work actual inform choices and guide prioritization
+
+> And finally I think mentioning the extreme uncertainty mostly seen in networks in the real world is key, how can approaches deal with this needs to be discussed.
+What do we need to think about interms of key information to use this approach.
+
+# Reviewer comments #2
+
+> "I read with great interest the manuscript by Cagua et al.
+on 'Quantifying the manageability of pollination networks in an invasion context'.
 The authors use control theory to develop an approach to assess how ecological networks – here pollination networks – can be managed, and test the approach on ten pairs of invaded and uninvaded plant-pollinator communities.
@@
 Also, although the manuscript may require a few minor edits it is well and clearly written.
-I do, however, have some concerns about the applicability of the approach and the findings, which I’ll describe in more detail below.
+I do, however, have some concerns about the applicability of the approach and the findings, which I’ll describe in more detail below."
 
-> When I first read the title and the abstract of the manuscript I was excited about the prospect of reading about a way forward using ecological networks to improve ecosystem conservation.
+We are thankful to the reviewer for pointing out some strengths of our work. We maintain the methodological approach, we have striven to maintain them in the current revusion.
+
+> "When I first read the title and the abstract of the manuscript I was excited about the prospect of reading about a way forward using ecological networks to improve ecosystem conservation.
 Now, having read the manuscript twice, I’m not persuaded that the proposed approach really advances our ability to conserve or restore ecological communities as the authors claim, or whether the approach provides primarily another, rather complex, way of analysing networks and describing the role of species in networks.
 As it is, the authors fail to convince me that the developed approach really advances our ability to prioritise species for ecosystem conservation, nor does the manuscript offer novel insights into the role and importance of certain species in a network and for ecosystem functioning.
-I’ve little doubt that there are ecological and theoretical justifications for combining control and network theory, but the authors don’t yet show that their proposed methods are overly useful in applied conservation.
+I’ve little doubt that there are ecological and theoretical justifications for combining control and network theory, but the authors don’t yet show that their proposed methods are overly useful in applied conservation."
 
-> I can see two ways forward: the authors re-arrange and re-word the manuscript to focus on the ecological advances that such an approach would bring to explaining and predicting network structure; or the authors describe in more detail a few scenarios in which conservation practitioners and managers could apply the proposed method to ‘improve’ management strategies or measure the efficacy of interventions.
-The latter would require a stronger justification of the advantages of control-theory approach compared to the classic species-level network metrics.
+> "I can see two ways forward: the authors re-arrange and re-word the manuscript to focus on the ecological advances that such an approach would bring to explaining and predicting network structure; or the authors describe in more detail a few scenarios in which conservation practitioners and managers could apply the proposed method to ‘improve’ management strategies or measure the efficacy of interventions.
+The latter would require a stronger justification of the advantages of control-theory approach compared to the classic species-level network metrics."
 
@@
 Biological Conservation, 209, 245-252.
-
-# Reviewer two comments
-
-> The management of complex ecological networks is of vast importance for the conservation of the natural world.
-While the field of ecological networks is vast few have tackle this question in a practical way.
-This paper would make a significant contribution to a field that needs to change direction if it is to help inform conservation as often purported in studies from the this field.
-
-> The control theory approach is very interesting.
-I think however there needs to be more clarity in the paper.
-It is hard to read.
-A reworking of it including using descriptions of the variable through out instead of variable names would improve this.
-
-> Better context needs to be given for previous work to look at the management of networks in ecology.
-There are a few papers and knowing how this one differs from these (not just the ones that look at node importance for example) is important.
-Some of these papers are mentioned in the discussion but in the intro it is important to know what they do and why this paper is novel.
-
-> Finally I think it is important to provide context about what kind of decisions are being made and could be informed by this approach.
-Who is managing plant-pollinator networks and what choices would they actually be making.
-Some examples should be expanded on.
-And also how would the outputs of this work actual inform choices and guide prioritization
-
-> And finally I think mentioning the extreme uncertainty mostly seen in networks in the real world is key, how can approaches deal with this needs to be discussed.
-What do we need to think about interms of key information to use this approach.

### 2018-05-26 paper/supp-info.Rmd
Move example network to maximum matching section from all maximum
Add figure input graph
Addresses #5
Add explanation of control adjacency and input graph in supp info
Close #6

@@
 
+To further ilustrate our methodology here, we also show the approach for the smallest of our empirical networks, the uninvaded network at site 10 (Table \@ref(tab:table-network-properties); Figure \@ref(fig:fig-small-network)).
+This network is composed of 19 species of which three are non-invasive plants and the other 16 are pollinators. 
+The one-to-one relationship between matched and superior nodes implies that in order to achieve full network controllability, most pollinators would be unmatched, and hence are classified as driver nodes that require external intervention.
+At the same time, both plants in the community, *Heracleum sphondylum* and *Rubus fructicosus*, and one of the pollinators, *Orthotylus/Lygocorus*, tend to be classified as superior nodes.
+
+```{r}
+drake::loadd(fig_small_network)
+```
+
+```{r fig-small-network, fig.height=fig_small_network$height, fig.width=fig_small_network$width,fig.cap = "Illustration of the procedure with an empirical community.
+The visitation network (top), the number of visits between species pairs is shown on each link.
+The directed network in which the direction of control is determined based on the mutual dependences (middle).
+One of the possible maximum matchings of this network (bottom)."}
+replayPlot(fig_small_network$plot)
+```
+
 ## Finding all possible maximum matchings {#all-maximum-matching}
@@
 
-To further ilustrate our methodology here, we also show the approach for the smallest of our empirical networks, the uninvaded network at site 10 (Table \@ref(tab:table-network-properties); Figure \@ref(fig:fig-small-network)).
-This network is composed of 19 species of which three are non-invasive plants and the other 16 are pollinators. 
-The one-to-one relationship between matched and superior nodes implies that in order to achieve full network controllability, most pollinators would be unmatched, and hence are classified as driver nodes that require external intervention.
-At the same time, both plants in the community, *Heracleum sphondylum* and *Rubus fructicosus*, and one of the pollinators, *Orthotylus/Lygocorus*, tend to be classified as superior nodes.
+## Control adjacency and the input graph {#input-graph}
+
+The algorithm proposed by @zhang_input_2016 enable us to find all minimum driver node sets without calculating all possible maximum matchings. 
+The algorithm is based on the construction of the input graph of the directed network. 
+Components in the input graph reveal the correlations between nodes from a structural control perspective (Figure \@ref(fig:fig-input-graph)). 
+The input graph is constructed based in the *control adjacency* of nodes in a maximum matching. 
+Two nodes $x_i$ and $x_j$ are said to be control adjacent if there is a node $x_k$ connecting $x_i$ and $x_j$ with an unmatched link $x_k-x_i$ and a matched link $x_k-x_j$. 
+For example $a_1$ is control adjacent to $a_2$ in the top panel of Figure \@ref(fig:fig-input-graph). 
+If a node $x_i$ is part of a minimum driver node set then every node in the same component of $x_i$ in the input graph is a possible driver node. 
+Every node within the same component in the input graph has the same control capacity $\phi$ and the control capacity $\phi_i$ of node $x_i$ is inversely proportional to the number of nodes in the same component of $x_i$.
 
 ```{r}
-drake::loadd(fig_small_network)
+drake::loadd(fig_input_graph)
 ```
 
-```{r fig-small-network, fig.height=fig_small_network$height, fig.width=fig_small_network$width,fig.cap = "Illustration of the procedure with an empirical community.
-The visitation network (top), the number of visits between species pairs is shown on each link.
-The directed network in which the direction of control is determined based on the mutual dependences (middle).
-One of the possible maximum matchings of this network (bottom)."}
-replayPlot(fig_small_network$plot)
+```{r fig-input-graph, fig.height=fig_input_graph$height, fig.width=fig_input_graph$width,fig.cap = "Input graph.
+Two nodes $x_i$ and $x_j$ are said to be control adjacent if there is a node $x_k$ connecting $x_i$ and $x_j$ with an unmatched link $x_k-x_i$ and a matched link $x_k-x_j$.
+For example, in the top panel, $a_1$ is control adjacent to $a_2$ (via $p_2$), $p_1$ is control adjacent to $p_3$ (via $a_1$) and $p_2$ has no control adjacent nodes.
+As $a_1$ and $p_2$ belong to the minimum driver node set under the control configuration found with the maximum matching shown, then every node in the same component as these two nodes is also a possible driver node.
+By combining the nodes from the components with minimum driver node sets is possible to enumerate the different control configurations.
+For example the network in the top panel has two possible minimum driver node sets $[p_2, a_1]$ and $[p_2, a_2]$ (Figure \\@ref(M-fig:fig-control-configuration)).
+The network in the middle panel has three minimum driver node sets $[x_1, x_2]$, $[x_1, x_3]$, and $[x_1, x_4]$.
+Finally the network in the bottom pannel has only one $[x_1]$."}
+replayPlot(fig_input_graph$plot)
 ```
-
-## Finding all possible minimum driver node sets
 

### 2018-05-26 paper/reviewers-response.Rmd
Add more responses to reviewers - Close # 8

@@
   - \externaldocument[S-]{supp-info}
+  - \usepackage[most]{tcolorbox}
+  - \definecolor{block-gray}{gray}{0.9}
+  - \newtcolorbox{myquote}{colback=block-gray,grow to right by=-10mm,grow to left by=-10mm, boxrule=0pt,boxsep=0pt,breakable}
 ---
@@
 
+We are grateful to the reviewer for the positive feedback and encouraging words.
+
 > "The control theory approach is very interesting.
@@
 
-> Better context needs to be given for previous work to look at the management of networks in ecology.
+Previously we used two sections to explain our approach: a section called "Theoretical framework" where we described the control methods, and another called "Methods" where we described their application on empirical data.
+At the moment we though this was the best approach, but in hindsight we realise separating these two aspects made it hard to understand the control concepts and their relationship with ecology. 
+As mentioned by the reviewer, this problem was compounded by abundant jargon and mathematical notation. 
+Therefore, to improve clarity, we have now combined the two sections into a single "Methods" section in which we explain the theory alongside with the empirical application. 
+We also spend more time providing intuitive explanations of the concepts of control theory and have moved most of the technical details to the supplementary information. 
+Moving the technical details to the supplementary information allowed us to use less jargon and simplify the notation.
+
+> "Better context needs to be given for previous work to look at the management of networks in ecology.
 There are a few papers and knowing how this one differs from these (not just the ones that look at node importance for example) is important.
-Some of these papers are mentioned in the discussion but in the intro it is important to know what they do and why this paper is novel.
+Some of these papers are mentioned in the discussion but in the intro it is important to know what they do and why this paper is novel."
+
+Thanks for this observation. 
+We have chosen to emphasise on the conceptual aspects of the work and therefore treat management applications only in the discussion. 
+Nevertheless we have rewritten the introduction and take care to be clear at explaining how this study relates to previous work and how it differs from these.
 
@@
 > One last minor remark, the authors have overlooked some key references in the field of restoration/conservation and ecological interactions/networks, which would strengthen the manuscript further, e.g.
-Harvey, E., Gounand, I., Ward, C.L. & Altermatt, F. (2017) Bridging ecology and conservation: from ecological networks to ecosystem function. Journal of Applied Ecology, 54, 371-379; 
-Devoto, M., Bailey, S., Craze, P. & Memmott, J. (2012) Understanding and planning ecological restoration of plant–pollinator networks. Ecology Letters, 15, 319-32; 
-Kaiser-Bunbury, C.N., Mougal, J., Whittington, A.E., Valentin, T., Gabriel, R., Olesen, J.M.
+
+> * Harvey, E., Gounand, I., Ward, C.L. & Altermatt, F. (2017) Bridging ecology and conservation: from ecological networks to ecosystem function. Journal of Applied Ecology, 54, 371-379; 
+> * Devoto, M., Bailey, S., Craze, P. & Memmott, J. (2012) Understanding and planning ecological restoration of plant–pollinator networks. Ecology Letters, 15, 319-32; 
+> * Kaiser-Bunbury, C.N., Mougal, J., Whittington, A.E., Valentin, T., Gabriel, R., Olesen, J.M.
 & Blüthgen, N.
@@
 Nature, 542, 223-227;
-Pires, M.M., Marquitti, F.M.D.
+> * Pires, M.M., Marquitti, F.M.D.
 & Guimarães Jr, P.R.

### 2018-05-26 paper/reviewers-response.Rmd
Spellchecking close #11
close #11

@@
 Thanks to the Senior Editor, James Ross, for his comments his decision to allow resubmission. 
-From the two reccomended alternatives, in line with the editor's preference, we have chosen to focus on the conceptual importance of our work. 
+From the two recommended alternatives, in line with the editor's preference, we have chosen to focus on the conceptual importance of our work. 
 To do this effectively, we had to rewrite both the manuscript and the supplementary materials almost completely. 
-We think the extra effort was wort as we feel the paper is does a better job at explaining clearly the untility of the proposed approach.
+We think the extra effort was wort as we feel the paper does a better job at explaining clearly the utility of the proposed approach.
 
@@
 We thank the Associate Editor Nicole Rafferty for the constructive feedback and highlighting the strengths of the paper. 
-As we described in the cover letter and in the response to the senior editor, we opted for strengthening the conceptual component rather than empahsising its application in specific management and conservation scenarios.
+As we described in the cover letter and in the response to the senior editor, we opted for strengthening the conceptual component rather than emphasising its application in specific management and conservation scenarios.
 We took this decision because of mainly two reasons. 
-First, the empirical data we use does not explicitly inlcudes any management or conservation scenarios. 
-As a consequence, despite the potential of the approach, at the moment we lack direct evidence of the utility of the approach for management decisons. 
-Second, we think that a conceptual approach offered a greater opportunity to highlight the stongest/most interesting aspects of the paper. 
-Namely the contrasts between invaded and uninvaded communities and the role of invasive species, as the reviewer points out.
+First, the empirical data we use does not explicitly includes any management or conservation scenarios. 
+As a consequence, despite the potential of the approach, at the moment we lack direct evidence of the utility of the approach for management decisions. 
+Second, we think that a conceptual approach offered a greater opportunity to highlight the strongest/most interesting aspects of the paper. 
+Namely, the contrasts between invaded and uninvaded communities and the role of invasive species, as the reviewer points out.
 
@@
 > "The management of complex ecological networks is of vast importance for the conservation of the natural world.
-While the field of ecological networks is vast few have tackle this question in a practical way.
-This paper would make a significant contribution to a field that needs to change direction if it is to help inform conservation as often purported in studies from the this field."
+While the field of ecological networks is vast few have tackled this question in a practical way.
+This paper would make a significant contribution to a field that needs to change direction if it is to help inform conservation as often purported in studies from this field."
 
@@
 It is hard to read.
-A reworking of it including using descriptions of the variable through out instead of variable names would improve this."
+A reworking of it including using descriptions of the variable throughout instead of variable names would improve this."
 
 Previously we used two sections to explain our approach: a section called "Theoretical framework" where we described the control methods, and another called "Methods" where we described their application on empirical data.
-At the moment we though this was the best approach, but in hindsight we realise separating these two aspects made it hard to understand the control concepts and their relationship with ecology. 
+At that moment we thought this was the best approach, but in hindsight, we realise separating these two aspects made it hard to understand the control concepts and their relationship with ecology. 
 As mentioned by the reviewer, this problem was compounded by abundant jargon and mathematical notation. 
@@
 There are a few papers and knowing how this one differs from these (not just the ones that look at node importance for example) is important.
-Some of these papers are mentioned in the discussion but in the intro it is important to know what they do and why this paper is novel."
+Some of these papers are mentioned in the discussion but in the intro, it is important to know what they do and why this paper is novel."
 
@@
 We have chosen to emphasise on the conceptual aspects of the work and therefore treat management applications only in the discussion. 
-Nevertheless we have rewritten the introduction and take care to be clear at explaining how this study relates to previous work and how it differs from these.
+Nevertheless, we have rewritten the introduction and take care to be clear at explaining how this study relates to previous work and how it differs from these.
 
@@
 > And finally I think mentioning the extreme uncertainty mostly seen in networks in the real world is key, how can approaches deal with this needs to be discussed.
-What do we need to think about interms of key information to use this approach.
+What do we need to think about in terms of key information to use this approach?
 

### 2018-05-26 paper/manuscript.Rmd
Spellchecking close #11
close #11

@@
 Within community ecology, a complex-systems has led to the development of a variety analytical and simulation tools with which to understand the role of the role of species embedded in a network of interactions [@bascompte_assembly_2009; @stouffer_evolutionary_2012].
-A particularly relevant dimension of any species' role is its ability to alter the abundance of other species in the community, since this impacts ecosystem function and biodiversity and might have knock down effects on other processes and services.
-This ability is often referred as "keystoneness". 
+A particularly relevant dimension of any species' role is its ability to alter the abundance of other species in the community—since this impacts ecosystem function and biodiversity and might have knock-down effects on other processes and services.
+This ability is often referred to as "keystonness". 
 A significant proportion of the network tools used to estimate species roles in this context relies on the assumption that there is a link between a species centrality—a relative ranking of its importance that stems from social network research—and its ability to alter other species' abundance.
 At first glance, this assumption makes sense. 
-At the core of representing ecological communities as networks sits the idea that the abundance of a species also depends on the abundance of its neighbours (the species it interacts with) and, by extension, the abundance of its neighbours neighbours', and so on.
+At the core of representing ecological communities as networks sits the idea that the abundance of a species also depends on the abundance of its neighbours (the species it interacts with) and, by extension, the abundance of its neighbours' neighbours, and so on.
 More central species, by definition, are better connected and hence should be more likely to affect the abundance of other species in the network.
@@
 On one hand, there is more than a dozen indices of centrality used in ecology. 
-Chosing a particular metric can be a difficult task, especially because to date there are not clear methods to determine the suitability of an index to a particular application. 
-Furthermore, recent studies have shown that definitions of keystoness based on centrality might not adequately predict the cascading extintions keystone species are ususally associated to. 
-As a result, community ecology could benefit from an alternative, more mechanistically-grounded, approach to understand how species affect each other abbundance. 
-Species abundances are also influenced by the dynamic relationships between nodes, and the mechanisms of self-regulation, however, community and population dynamics can be modeled in innumerable ways, and empirical support for one versus another is often still ambiguous.
+Choosing a particular metric can be a difficult task, especially because to date there are no clear methods to determine the suitability of an index to a particular application. 
+Furthermore, recent studies have shown that definitions of keystoness based on centrality might not adequately predict the cascading extinctions keystone species are usually associated to. 
+As a result, community ecology could benefit from an alternative, more mechanistically-grounded, approach to understand how species affect each other abundance. 
+Species abundances are also influenced by the dynamic relationships between nodes, and the mechanisms of self-regulation, however, community and population dynamics can be modelled in innumerable ways, and empirical support for one versus another is often still ambiguous.
 The alternative approach should acknowledge ecosystem dynamics, but without being overly dependent on the particular choices of how they are characterised.
@@
 In correspondence with ecological questions, advances in this field have established a clear link between the structure of the network and the way nodes affect each other. 
-Unlike centrality indices, however, this link is not based on a priori assumptions between network metrics and keystoness, instead on well-established advances in both dynamical and complex-systems theory <!--STOUFFER: Are we shooting ourselves in the foot since this isn't entirely true?
+Unlike centrality indices, however, this link is not based on a priori assumptions between network metrics and keystoness, instead, it is based on well-established advances in both dynamical and complex-systems theory <!--STOUFFER: Are we shooting ourselves in the foot since this isn't entirely true?
 That is, see comments from ELE about linearity and otherwise.
@@
 We ask—from a control-theoretic perspective—whether there are key differences between species in the role they play at driving the population of other members of the community and identify the ecological factors related to these differences.
-Finally, we compare the proposed approach to current methods based on species centrality and show how these methods are indeed valuable but only paint a limited picture in regards to the "keystoneness" of a species.
+Finally, we compare the proposed approach to current methods based on species centrality and show how these methods are indeed valuable but only paint a limited picture in regards to the "keystonness" of a species.
 
@@
 
-The first step before applying methods of control theory is to construct a directed network that is able to provide an indication of the extent to which species affect each others abundance. 
+The first step in applying methods of control theory is to construct a directed network that is able to provide an indication of the extent to which species affect each other's abundance. 
 In some ecological networks, establishing the directionality can be relatively straightforward, for example when links represent biomass transfer or energy flow [@isbell_human_2013]. 
-In pollination networks, however, this directionallity is less obvious as both species can in theory benefit from the interaction. 
+In pollination networks, however, this directionality is less obvious as both species can, in theory, benefit from the interaction. 
 We overcome that obstacle by noting that the extent to which species *i* affects species *j* relative to the extent to which *j* affects *i* can be summarised by the interaction asymmetry [@bascompte_asymmetric_2006].
@@
 Previous research has shown that mutualistic interactions are often highly asymmetric in natural communities; in other words, if a plant species is largely dependent on a pollinator species, then that pollinator tends to depend rather weakly on the plant (or vice versa).
-We therefore create a directed link between species *i* and *j* when $d_{ij}-d_{ji} \geq 0$ to establish the most likely direction of control between a species pair (Figure \@ref(fig:fig-example-networks)a).
-By basing the direction of the links on the asymmetry of their dependence, we are able to generate a network that is consistent with the dynamics of the community while satisfyingh the requirements of structural controllability.
+We, therefore, create a directed link between species *i* and *j* when $d_{ij}-d_{ji} \geq 0$ to establish the most likely direction of control between a species pair (Figure \@ref(fig:fig-example-networks)a).
+By basing the direction of the links on the asymmetry of their dependence, we are able to generate a network that is consistent with the dynamics of the community while satisfying the requirements of structural controllability.
+
 ```{r}
@@
 
-After constructing the directed network, we can now calculate the controllability of the different networks and investigate wether there are differences between invaded and uninvaded communities.
+After constructing the directed network, we can now calculate the controllability of the different networks and investigate whether there are differences between invaded and uninvaded communities.
 
@@
 In classic control theory, determining wether this system is controllable can easily be achieved by checking that its controllability matrix $R= [ \begin{matrix}B & AB & A^{2}B & ...& A^{n-1}B\end{matrix} ]$ has full rank.
-In complex systems, however, employing this rank condition, or numerical approximations of it, is unfeasible because it is hard to fully parameterize *A* and *B* (either because the weight of the links change over time or because they are difficult to measure).
-Here we use an approach based on the structural controllability theorem [@lin_structural_1974], which assumes that we are confident that the elements of *A* and *B* have either non-zero or zero values (there is an interaction or not), but that we less sure about the precise magitude of the non-zero values.
+In complex systems, however, employing this rank condition, or numerical approximations of it, is unfeasible because it is hard to fully parameterize *A* and *B* (either because the weight of the links changes over time or because they are difficult to measure).
+Here we use an approach based on the structural controllability theorem [@lin_structural_1974], which assumes that we are confident that the elements of *A* and *B* have either non-zero or zero values (there is an interaction or not), but that we less sure about the precise magnitude of the non-zero values.
 Using this structural approach we can find out the controllability of a system under almost all non-zero parameter realisations.
-Structural controllability also has a graphical interpretation that allow us to translate the control problem into a topological one: a network is controllable if there are no inaccessible nodes—nodes without incoming links—or dilations—*expansions* of the network (Figure \@ref(fig:fig-example-networks)b; Supplementary Information section \@ref(S-structural-controllability)).
+Structural controllability also has a graphical interpretation that allows us to translate the control problem into a topological one: a network is controllable if there are no inaccessible nodes—nodes without incoming links—or dilations—*expansions* of the network (Figure \@ref(fig:fig-example-networks)b; Supplementary Information section \@ref(S-structural-controllability)).
 
@@
 Such approach is typically unpractical. 
-We are instead interested in finding a minimum driver node set (effectively finding *B*) with which to make the system controllable. 
+We are instead interested in finding a minimum driver node-set (effectively finding *B*) with which to make the system controllable. 
 However, a brute force search of this minimum driver node set is computationally prohibitive for most networks as it involves the evaluation of $2^N$ different controllability matrices. 
-We employ a recently developed approach that shows that the control problem of finding the minimum driver node set can be mapped into a graph theoretic problem: maximum matching [@liu_controllability_2011; @liu_control_2016].
+We employ a recently developed approach that shows that the control problem of finding the minimum driver node set can be mapped into a graph-theoretic problem: maximum matching [@liu_controllability_2011; @liu_control_2016].
 
-Maximum matching is a widely studied topic in graph theory and is commonly used in multiple applications, ranging from dating apps and wireless communications to organ transplant allocation and peer to peer file sharing.
+Maximum-matching is a widely studied topic in graph theory and is commonly used in multiple applications, ranging from dating apps and wireless communications to organ transplant allocation and peer to peer file sharing.
 A matching in an unweighted directed graph is defined as a set of links that do not share a common start or end nodes; the largest possible matching is called maximum matching. 
-For example, in a network composed by jobs and job applicants, a matching is any pairing between applicants and positions that satisfies one basic constrain: an applicant can be assigned to at most one position and visceversa.
+For example, in a network composed by jobs and job applicants, a matching is any pairing between applicants and positions that satisfies one basic constraint: an applicant can be assigned to at most one position and vice-versa.
 Consequently, a maximum matching is an optimal pairing, one that maximises the number of applicants with jobs and the number of positions filled. 
-At first glance, however, is  hard to identify how exactlty matchings are related to structural controllability. 
+At first glance, however, is hard to identify how exactly matchings are related to structural controllability. 
 The key is to note that the conditions of structural controllability imply that, just like the one to one relationship between jobs and applicants, there needs to be a one to one relationship between *superior* and *subordinate* nodes (Figure \@ref(fig:fig-example-networks)b, bottom left).
 We use the maximum matching algorithm to find an optimal pairing of superior and subordinate nodes in a way consistent with the controllability conditions (supplementary information section \@ref(S-one-maximum-matching)).
-The result is that a matching can actually be decomposed into a set of paths that reveal how a control signal can flow across the links in a network to reach every node that compose it. 
+The result is that a matching can actually be decomposed into a set of paths that reveal how a control signal can flow across the links in a network to reach every node that composes it. 
 And so, as recently shown [@liu_controllability_2011], the minimum driver node set, those to which an external control input should be applied to make the system controllable, corresponds exactly to the *unmatched* nodes in the network (Figure \@ref(fig:fig-control-configuration)).
@@
 ```{r fig-control-configuration, fig.height=fig_control_config$height, fig.width=fig_control_config$width,fig.cap = "Maximum matchings and control configurations.
-In directed networks a maximum matching is the largest possible set of links that do not share start or end nodes (dark purple).
-Maximum matchings are not necessarly unique, instead each of them is related to a possible minimum driver node set in the network (the nodes to which an external control input, in orange, should be applied in order to ensure controllability).
+In directed networks, a maximum matching is the largest possible set of links that do not share start or end nodes (dark purple).
+Maximum matchings are not necessarily unique, instead, each of them is related to a possible minimum driver node set in the network (the nodes to which an external control input, in orange, should be applied in order to ensure controllability).
 The size of the minimum driver node set *D* corresponds exactly to the number of unmatched nodes (the number of nodes in the network *N* minus the matching size).
-To account for network size, we use size of the minimum driver node set relative to the total number of nodes *n~D~ = D/N* as a measure of the extent to which the network structure can be harnessed to control the system."}
+To account for network size, we use the size of the minimum driver node set relative to the total number of nodes *n~D~ = D/N* as a measure of the extent to which the network structure can be harnessed to control the system."}
 replayPlot(fig_control_config$plot)
@@
 
-Our first main objective is to investigate whether the controllability of a community is associated to invasion status or not. 
-Finding out exactly, how difficult is to control a network depends strongly on the particularities of the desired control trayectory as well as the dynamical relationpip between nodes. 
+Our first main objective is to investigate whether the controllability of a community is associated with invasion status or not. 
+Finding out exactly, how difficult is to control a network depends strongly on the particularities of the desired control trajectory as well as the dynamical relationship between nodes. 
 However, we are interested in understanding the controllability of a network in a more general sense, such that it can be applied even when the precise control scenario is known only incompletely. 
 We instead employ an indicator that follows from our approach: the size of the minimum driver node set. 
-This simple metric provides general indication of how difficult controlling a network might be, as systems that require a large number of external inputs to be fully controlled are intuitively more difficult or costly to manage.
+This simple metric provides a general indication of how difficult controlling a network might be, as systems that require a large number of external inputs to be fully controlled are intuitively more difficult or costly to manage.
 Specifically, following the structural controllability literature, we use the size of the minimum driver node set relative to the total number of nodes $n_D = \frac{D}{N}$ as a measure of the extent to which the network structure can be harnessed to control the community.
-In an ecological context, external inputs can be thought of as management interventions that modify the abbundance of a particular species. 
+In an ecological context, external inputs can be thought of as management interventions that modify the abundance of a particular species. 
 For instance, achieving full control in a "network" in which species do not interact at all is relatively difficult as we would require an intervention for every single species. 
-Conversely, the structure of a linear trophic chain can be harnessed to achieve full control using just one intervention targeted the top species; the control signal would then cascade trough the trophic levels and reach other species in the community.
+Conversely, the structure of a linear trophic chain can be harnessed to achieve full control using just one intervention targeted the top species; the control signal would then cascade through the trophic levels and reach other species in the community.
 
 After finding the minimum driver node set in each of our networks we want to test whether invasion status or other predictors are correlated to this metric of controllability. 
-We therefore use a set of generalised linear models (with binomial error structure) to investigate the effect of invasion status while also including covariates related to species richness, since one might naively expect to see a negative relationship between richness and controllability [@menge_indirect_1995].
+We, therefore, use a set of generalised linear models (with binomial error structure) to investigate the effect of invasion status while also including covariates related to species richness, since one might naively expect to see a negative relationship between richness and controllability [@menge_indirect_1995].
 These covariates included the total number of species, plant richness, pollinators richness, the ratio of plant to pollinator richness, the link density (connectance), and the study site (as a two-level factor).
@@
 Ecologically, these differences are relevant because resources and data are limited, and therefore full control is unfeasible. 
-To answer this question, we make two kind of distinctions between species from a control perspective.
+To answer this question, we make two kinds of distinctions between species from a control perspective.
 
 First, we harness the fact that maximum matchings in a network are often not unique, and each maximum matching indicates unique paths that can potentially be used to control the network. 
-Specifically we use the frequency with which a species is part of the multiple minimum driver node sets, its control capacity $\phi$, as an estimation of its relative importance in driving the state of the community as a whole [@jia_control_2013].
+Specifically, we use the frequency with which a species is part of the multiple minimum driver node sets, its control capacity $\phi$, as an estimation of its relative importance in driving the state of the community as a whole [@jia_control_2013].
 For example, a species with a control capacity $\phi_i= 1$ is a one that requires external input in every single control configuration. 
@@
 Intuitively, to calculate a species control capacity $\phi$ we need to enumerate all possible maximum matchings (we detail the algorithm to find all maximum matchings in the Supplementary Information section \@ref(S-all-maximum-matching)).
-However, enumerating all maximum matchings extremely expensive from a computational perspective—a network with a couple dozen nodes could be controlled with several hundred million unique matchinghs. 
+However, enumerating all maximum matchings extremely expensive from a computational perspective—a network with a couple dozen nodes could be controlled with several hundred million unique matchings. 
 To solve this problem we instead employ a recently developed algorithm that reveals the control correlations between the nodes in the graph [@zhang_input_2016, Supplementary Information section \@ref(S-input-graph)].
 Using this algorithm we are able to obtain every minimum driver node set with information obtained from a single maximum matching. 
-The end result is that we are now able to calculate the control capacity $\phi_i$ of every node in linear time—rather than polynomial as the algoritm for matching enumeration requires.
+The end result is that we are now able to calculate the control capacity $\phi_i$ of every node in linear time—rather than polynomial as the algorithm for matching enumeration requires.
 
@@
 However, in ecological settings, changing the state of the community as a whole is often not required or undesired. 
-Consequently, we make a second distinction between nodes based on wether they form part of possible control paths in the network and therefore are likely to influence the abbundance of another species.
-We identify those species by checking wether they are classified as a superior node, this is they are at the beginning of a matched link. 
+Consequently, we make a second distinction between nodes based on whether they form part of possible control paths in the network and therefore are likely to influence the abundance of another species.
+We identify those species by checking whether they are classified as a superior node, this is they are at the beginning of a matched link. 
 While unmatched nodes correspond to those that should be influenced with an external control input, superior nodes correspond to those that influence other species internally. 
-Conveniently, with the execption of some patological cases, superior nodes are such across every control configuration and therefore knowing one maximum matching provides enough information on whether a species is likely to play an important role at influencing the abundance of other species or not.
+Conveniently, with the exception of some pathological cases, superior nodes are such across every control configuration and therefore knowing one maximum matching provides enough information on whether a species is likely to play an important role at influencing the abundance of other species or not.
 
@@
 *TODO: Still need to decide how to do this and how to compare traditional centrality metrics to the new control based ones.
-Will probably base the comparision on stability/feasibility metrics or/and on coextinction of species groups.*
+Will probably base the comparison on stability/feasibility metrics or/and on coextinction of species groups.*Maximum matchings and control configurations.
+In directed networks, a maximum matching is the largest possible set of links that do not share start or end nodes (dark purple).
+Maximum matchings are not necessarily unique, instead, each of them is related to a possible minimum driver node set in the network (the nodes to which an external control input, in orange, should be applied in order to ensure controllability).
+The size of the minimum driver node set *D* corresponds exactly to the number of unmatched nodes (the number of nodes in the network *N* minus the matching size).
+To account for network size, we use the size of the minimum driver node set relative to the total number of nodes *n~D~ = D/N* as a measure of the extent to which the network structure can be harnessed to control the system.
 

### 2018-05-26 paper/supp-info.Rmd
Spellchecking close #11
close #11

@@
 
-# Characteristics of the epirical networks {#empirical-networks}
+# Characteristics of the empirical networks {#empirical-networks}
 
@@
 ```{r table-network-properties, results = "asis", sanitize = FALSE}
-
 net_prop %>%
@@
 Structural controllability avoids the limitation of not knowing the exact values of the matrices *A* and *B*. 
-Using structural controllability controllability can be boiled down to two conditions: a system is controllable if there are no inaccessible nodes or dilations.
+Using structural controllability can be boiled down to two conditions: a system is controllable if there are no inaccessible nodes or dilations.
 A node is inaccessible if there are no directed paths between it and the input nodes.
 "Dilations are subgraphs in which a small subset of nodes attempts to rule a larger subset of nodes.
-In other workds there are more 'subordinates' than 'superiors'" [@liu_control_2016].
+In other words, there are more 'subordinates' than 'superiors'" [@liu_control_2016].
 
@@
 
-Our approach to find the minumum number of driver nodes relies on finding maximum matchings. 
+Our approach to finding the minimum number of driver nodes relies on finding maximum matchings. 
 We start with a directed network in which the direction of the link represents the direction of control (Figure \@ref(fig:fig-maximum-matching-procedure) left panel). 
-We then construct an alternative representation of the directed network in which each node of the directed network is represented by two nodes that indicate their outgoing and incoming links respectively (Figure \@ref(fig:fig-maximum-matching-procedure) center panel).
+We then construct an alternative representation of the directed network in which each node of the directed network is represented by two nodes that indicate their outgoing and incoming links respectively (Figure \@ref(fig:fig-maximum-matching-procedure) centre panel).
 Finding a maximum matching in this alternative representation is equivalent to finding the largest possible set of edges in which one node on the left-hand side is connected to at most one node on the right-hand side.
 To find the maximum matching we use the push-relabel algorithm implemented in `max_bipartite_matching` in the R package igraph 1.0.1 [@Csardi2006a]. 
-Once we have the matching (shown in the Figure \@ref(fig:fig-maximum-matching-procedure) center panel) it is then easy to identify the roles of each node in this representation: nodes on the top-level that are connected to a matched (dark purple) link are superior while those connected to a matched link on the bottom-level are matched.
+Once we have the matching (shown in the Figure \@ref(fig:fig-maximum-matching-procedure) center panel) it is then easy to identify the roles of each node in this representation: nodes on the top-level that are connected to a matched link (dark purple) are superior while those connected to a matched link on the bottom-level are matched.
 This information can then be mapped back to the original representation to identify the control paths and the driver nodes in the network (Figure \@ref(fig:fig-maximum-matching-procedure) right panel).
@@
 
-To further ilustrate our methodology here, we also show the approach for the smallest of our empirical networks, the uninvaded network at site 10 (Table \@ref(tab:table-network-properties); Figure \@ref(fig:fig-small-network)).
+To further illustrate our methodology here, we also show the approach for the smallest of our empirical networks, the uninvaded network at site 10 (Table \@ref(tab:table-network-properties); Figure \@ref(fig:fig-small-network)).
 This network is composed of 19 species of which three are non-invasive plants and the other 16 are pollinators. 
@@
 The algorithm implemented in `max_bipartite_matching`, however, is only able to find **one** of possibly many maximum matchings in a network. 
-Though one maximum matching is enough to calculate *n~D~* and hence to provide indication of the manageability of a community, it is not sufficient to estimate the role of individual species. 
+Though one maximum matching is enough to calculate *n~D~* and hence to provide an indication of the manageability of a community, it is not sufficient to estimate the role of individual species. 
 To do that, we need to calculate all possible maximum matchings (or, equivalently, all maximal cardinality matchings in weighted networks like ours). 
@@
 Line graph of the network.
-Complement of the network.
+The complement of the network.
 The two maximal cliques are shown in dark purple."}
@@
 Components in the input graph reveal the correlations between nodes from a structural control perspective (Figure \@ref(fig:fig-input-graph)). 
-The input graph is constructed based in the *control adjacency* of nodes in a maximum matching. 
+The input graph is constructed based on the *control adjacency* of nodes in a maximum matching. 
 Two nodes $x_i$ and $x_j$ are said to be control adjacent if there is a node $x_k$ connecting $x_i$ and $x_j$ with an unmatched link $x_k-x_i$ and a matched link $x_k-x_j$. 

### 2018-06-03 paper/cover-letter.tex
dbs edits to cover letter

@@
 \usepackage{setspace}
-\signature{Fernando Cagua \\ (in behalf of all authors)}
+\signature{Fernando Cagua \\ (on behalf of all authors)}
 \address{Centre for Integrative Ecology \\ School of Biological Sciences \\ University of Canterbury \\ Private Bag 4800 \\ 8140 Christchurch \\ New Zealand}
@@
 We are also grateful for the opportunity to resubmit. 
-In the attached documment you can find a detailed response to each of their comments. 
-Here we summarise the main changes to the manuscript.
+In the attached document, you can find a detailed response to each of their comments. 
+For your benefit, we also summarise here the main changes we have made to our manuscript.
 
 Briefly, our paper explores the possible applications of control theory in an ecological context. 
-We see potential in our paper to contribute to both applied and theoretical aspects in ecology. 
-However in our initial submission we lingered midway between these two directions and—as the editors and reviewers pointed out—we failed to address either option successfuly.
-We have re-inspected our manuscript and tink that the theoretical insights are stronger. 
-As a consequence in this revision we have chosen to focus on the conceptual aspect of our approach at the expense of numerous, but weak, connections with conservation and applied ecology.
+We honestly see potential in our paper to contribute to both applied and theoretical aspects in ecology. 
+However, our initial submission was caught between these two directions and---as the editors and reviewers rightly pointed out---we failed to satisfactorily address either option as a result.
+We have re-scrutinised our manuscript and concluded that the theoretical insights are stronger. 
+As a consequence, we have chosen to focus on the conceptual aspect of our approach in this revision at the expense of numerous, but weaker, connections with conservation and applied ecology.
 
-Adopting a primarely conceptual focus allowed us to be clearer about the justification, methodology and potential insights of our approach. 
+Adopting a primarily conceptual focus has allowed us to be clearer about the justification, methodology and potential insights of our approach. 
 However, improving clarity while successfully tying the conceptual motivation with our findings required more than some changes to some paragraphs or sections of the manuscript. 
-Therefore, we have rewriten almost entirely the manuscript and the supplementary materials. 
+Therefore, we have rewritten almost entirely the manuscript and the supplementary materials. 
 We maintain the methodology and findings, but there has been a major change in the way we justify the study, introduce novel concepts to the ecological domain, and present our conclusions.

### 2018-06-03 paper/cover-letter.tex
the senior editor is David Gibson

@@
 
-We are thankful to the senior and associate editors, Prof. James Ross and Prof. Nicole Rafferty, and two anonymus reviewers for the insightful comments to improve the manuscript. 
+We are thankful to the senior and associate editors, Prof.\ David Gibson and Prof.\ Nicole Rafferty, and two anonymous reviewers for the insightful comments to improve the manuscript. 
 We are also grateful for the opportunity to resubmit. 

### 2018-06-03 paper/reviewers-response.Rmd
dbs edits to response to editors and reviewer 1

@@
 
-We are thankful to the editors, James Ross and Nicole Rafferty, and two anonymus reviewers for the insightful comments to improve the manuscript. 
-In the following sections you can find a detailed response to each comment. 
-Here we summarise the main changes to the manuscript.
+We are thankful to the editors, David Gibson and Nicole Rafferty, and two anonymous reviewers for the insightful comments to improve the manuscript. 
+In the following sections, you can find a detailed response to each comment raised during the previous round of review.
 
@@
 
-Thanks to the Senior Editor, James Ross, for his comments his decision to allow resubmission. 
-From the two recommended alternatives, in line with the editor's preference, we have chosen to focus on the conceptual importance of our work. 
-To do this effectively, we had to rewrite both the manuscript and the supplementary materials almost completely. 
-We think the extra effort was wort as we feel the paper does a better job at explaining clearly the utility of the proposed approach.
+Thanks to the Senior Editor, David Gibson, for his comments and his willingness to allow resubmission. 
+After lengthy consideration of the the two recommended alternatives, we have chosen to focus on the conceptual importance of our work in line with the editor's stated preference. 
+To do this effectively, we ultimately ended up rewriting both the manuscript and the supplementary materials almost completely.
+We think the extra effort was worth it as we feel the current version does a much better job at explaining the utility and insights generated by the proposed approach.
 
-#  Assocciate Editor comments
+#  Associate Editor comments
 
@@
 
-We thank the Associate Editor Nicole Rafferty for the constructive feedback and highlighting the strengths of the paper. 
-As we described in the cover letter and in the response to the senior editor, we opted for strengthening the conceptual component rather than emphasising its application in specific management and conservation scenarios.
-We took this decision because of mainly two reasons. 
-First, the empirical data we use does not explicitly includes any management or conservation scenarios. 
-As a consequence, despite the potential of the approach, at the moment we lack direct evidence of the utility of the approach for management decisions. 
-Second, we think that a conceptual approach offered a greater opportunity to highlight the strongest/most interesting aspects of the paper. 
+We thank the Associate Editor, Nicole Rafferty, for the constructive feedback and highlighting the strengths of the paper. 
+As we noted above in our response to the Senior Editor, we opted to use our revisions to strengthen the conceptual component rather than emphasising its application in specific management and conservation scenarios.
+We opted to take this decision for two main reasons. 
+First, the empirical data we use does not explicitly include any management or conservation scenarios. 
+As a consequence and despite the potential of the approach, we currently lack *direct* evidence of the utility of the approach for management decisions.
+Second, we think that highlighting the conceptual approach offered a greater opportunity to draw attention to the strongest/most interesting aspects of the paper. 
 Namely, the contrasts between invaded and uninvaded communities and the role of invasive species, as the reviewer points out.
+
+XXX At end of last sentence above, which reviewer?
 
@@
 Previously we used two sections to explain our approach: a section called "Theoretical framework" where we described the control methods, and another called "Methods" where we described their application on empirical data.
-At that moment we thought this was the best approach, but in hindsight, we realise separating these two aspects made it hard to understand the control concepts and their relationship with ecology. 
+At that moment, we thought this was the best approach; in hindsight, we realise that separating these two aspects made it hard to understand the core control concepts and their relationship with ecology.
 As mentioned by the reviewer, this problem was compounded by abundant jargon and mathematical notation. 
-Therefore, to improve clarity, we have now combined the two sections into a single "Methods" section in which we explain the theory alongside with the empirical application. 
-We also spend more time providing intuitive explanations of the concepts of control theory and have moved most of the technical details to the supplementary information. 
-Moving the technical details to the supplementary information allowed us to use less jargon and simplify the notation.
+To improve clarity, we have now combined the two sections into a single "Methods" section in which we explain the theory alongside with the empirical application. 
+We also spend more time providing intuitive explanations of the concepts of control theory and have moved the most  technical details to the supplementary information.
+This latter move (shifting the technical details to the supplementary information) allowed us to use far less jargon and simplify the notation.
+We hope that the reviewer agrees that the new version is easier to follow.
 
@@
 Thanks for this observation. 
-We have chosen to emphasise on the conceptual aspects of the work and therefore treat management applications only in the discussion. 
-Nevertheless, we have rewritten the introduction and take care to be clear at explaining how this study relates to previous work and how it differs from these.
+In line with feedback from both editors, we have chosen to emphasise on the conceptual aspects of the work and reduced the core question of management applications to appear only in the discussion. 
+Nevertheless, we have also rewritten the introduction and took care to be clear at explaining how this study relates to and differs from previous work.
 
@@
 
+XXX answer missing XXX
+
 > And finally I think mentioning the extreme uncertainty mostly seen in networks in the real world is key, how can approaches deal with this needs to be discussed.
 What do we need to think about in terms of key information to use this approach?
+
+XXX answer missing XXX
 
@@
 
-We are thankful to the reviewer for pointing out some strengths of our work. We maintain the methodological approach, we have striven to maintain them in the current revusion.
+We are thankful to the reviewer for indicating the aspects which they believe were strengths of our work.
+We maintain the methodological approach in the latest version, and have used these details to determine which elements were essential to maintain in the current revision.
 

### 2018-06-04 paper/manuscript.Rmd

@@
 We, therefore, create a directed link between species *i* and *j* when $d_{ij}-d_{ji} \geq 0$ to establish the most likely direction of control between a species pair (Figure \@ref(fig:fig-example-networks)a).
+Sometimes, however, there is no assymetry in the dependences between species pairs ($d_{ij}=d_{ji}$), and we cannot infer the direction of control. 
+As such, we deem both species to be equally likely to affect each other and create two directed links between them, one from *i* to *j* and another from *j* to *i*. 
 By basing the direction of the links on the asymmetry of their dependence, we are able to generate a network that is consistent with the dynamics of the community while satisfying the requirements of structural controllability.
@@
 
-We then examined whether any species-level structural properties could predict a species control capacity $\phi$ and the likelihood of being a superior node.
+To examine whether any species-level structural properties could predict a species control capacity $\phi$ and the likelihood of being a superior node $sigma$, we calculated these properties for each of our networks.
+In the networks that contained reciprocal links (because there was not assymetry in the dependences of a species pair), we averaged a species' $\phi$ and $sigma$ across every possible "non-reciprocal" realisation of the network (more details can be found in the Supplementary Information section \@ref(S-reciprocal-links)).
 *TODO: Still need to decide how to do this and how to compare traditional centrality metrics to the new control based ones.
-Will probably base the comparison on stability/feasibility metrics or/and on coextinction of species groups.*Maximum matchings and control configurations.
-In directed networks, a maximum matching is the largest possible set of links that do not share start or end nodes (dark purple).
-Maximum matchings are not necessarily unique, instead, each of them is related to a possible minimum driver node set in the network (the nodes to which an external control input, in orange, should be applied in order to ensure controllability).
-The size of the minimum driver node set *D* corresponds exactly to the number of unmatched nodes (the number of nodes in the network *N* minus the matching size).
-To account for network size, we use the size of the minimum driver node set relative to the total number of nodes *n~D~ = D/N* as a measure of the extent to which the network structure can be harnessed to control the system.
+Will probably base the comparison on stability/feasibility metrics or/and on coextinction of species groups.*
 

### 2018-06-04 paper/supp-info.Rmd

@@
 
+## Networks with reciprocal links {#reciprocal-links}
+
+```{r}
+drake::loadd(directed_networks)
+recipr <- directed_networks %>%
+  purrr::map(igraph::reciprocity, mode = "ratio") %>%
+  unlist() %>% {
+    dplyr::data_frame(net_name = names(.), prop_bid = .)
+  } %>%
+  dplyr::inner_join(metadata, by = "net_name") %>%
+  dplyr::filter(study %in% c("bartomeus", "lopezaraiza"))
+```
+
+Our procedures to find minimum driver node sets is only adequate when there are no reciprocal (bidirectional) links in the network. 
+The proportion of reciprocal links in relatively low. 
+In fact the proportion of species pairs that are reciprocally connected in our empirical networks is just `r round(mean(recipr$prop_bid)*100, 2)`%. 
+However, reciprocal links are not a rare occurrence as `r sum(recipr$prop_bid != 0)` out of `r nrow(recipr)` empirical networks had at least one. 
+To calculate our controllability metrics at both the network (the relative size of the minimum driver node set, $n_D$) and species level (control capacity, $\phi$, and the likelihood of being a superior node, $\sigma$) we first need to generate all possible versions of the of the network that include only non-reciprocal links.
+
+Based on the available information, all of these network is as likely to be one that best represent the superior/matched relationships in the network. 
+As such, we average the three metrics ($n_D$, $\phi$, and $\sigma$) across all the networks without reciprocal links without weighting by the number of possible control configurations.
+
+```{r}
+drake::loadd(fig_bidirectional)
+```
+
+```{r fig-bidirectional, fig.height=fig_bidirectional$height, fig.width=fig_bidirectional$width,fig.cap = "In order to calculate the controllability metrics for a network with reciprocal links (left), we first decompose the network into several versions that contain no reciprocal links (right).
+As each of these networks represent a different equiprobable scenario, the controllability metrics for the network with reciprocal links are the unweighted mean of these metrics across the non-reciprocal networks."}
+replayPlot(fig_bidirectional$plot)
+```
+
 # Empirical vs. random expectation of controllability {#randomisations}

### 2018-06-04 paper/manuscript.Rmd
dbs edits to the manuscript and lots of leave behinds for fer

--- 2018-05-26 paper/manuscript.Rmd
@@
 
-A major goal in ecological research is to understand the role that species play in the biotic environment.
-Within community ecology, a complex-systems has led to the development of a variety analytical and simulation tools with which to understand the role of the role of species embedded in a network of interactions [@bascompte_assembly_2009; @stouffer_evolutionary_2012].
-A particularly relevant dimension of any species' role is its ability to alter the abundance of other species in the community—since this impacts ecosystem function and biodiversity and might have knock-down effects on other processes and services.
-This ability is often referred to as "keystonness". 
-A significant proportion of the network tools used to estimate species roles in this context relies on the assumption that there is a link between a species centrality—a relative ranking of its importance that stems from social network research—and its ability to alter other species' abundance.
-At first glance, this assumption makes sense. 
-At the core of representing ecological communities as networks sits the idea that the abundance of a species also depends on the abundance of its neighbours (the species it interacts with) and, by extension, the abundance of its neighbours' neighbours, and so on.
-More central species, by definition, are better connected and hence should be more likely to affect the abundance of other species in the network.
+A major goal in ecology is to understand the roles played by different species in the biotic environment.
+Within community ecology, a complex-systems approach has led to the development of a variety analytical and simulation tools with which to compare and contrast the roles of species embedded in a network of interactions [@bascompte_assembly_2009; @stouffer_evolutionary_2012].
+<!-- Add some older references as this is a long-standing research line; see the 2012 paper for some if you'd like. -->
+A particularly relevant dimension of any species' role is its ability to alter the abundance of other species in the community—since changes of this nature impact ecosystem function and biodiversity, and might have knock-on effects on other processes and services.
+This ability is often referred to as a species' "keystoneness" [refmissing].
 
-Though conceptually intuitive, the relationship between centrality and keystoness is largely phenomenological. 
+A significant proportion of the network tools used to estimate species roles in this context rely on the assumption that there is a link between a given species' centrality—a relative ranking of its importance that stems from social network research—and its ability to alter the abundances of other species.
+Taken at face value, the basis of this assumption is reasonably clear: a major justification for representing ecological communities as networks is the idea that the abundance of a species depends on the abundance of its neighbours (those species with which it interacts) and, by extension, the abundance of its neighbours' neighbours, and so on.
+By definition, more central species are better connected and hence should be more likely to affect the abundance of other species in the network.
+
+<!-- Beware that the paragraph above could rub some readers/reviewers (those that believe in the usefulness of centrality) the wrong way. -->
+
+<!-- I believe it should be 'keystoneness' and not 'keystoness'. I've tried to correct all, but please check this. -->
+
+<!-- I didn't do it, but I would think about joining the text below (up to "more mechanistically-grounded") with the above to make a single paragraph. It'd be long, but the thoughts flow well. -->
+
+Though conceptually intuitive, the relationship between centrality and keystoneness is largely phenomenological. 
 On one hand, there is more than a dozen indices of centrality used in ecology. 
 Choosing a particular metric can be a difficult task, especially because to date there are no clear methods to determine the suitability of an index to a particular application.
-Furthermore, recent studies have shown that definitions of keystoness based on centrality might not adequately predict the cascading extinctions keystone species are usually associated to. 
-As a result, community ecology could benefit from an alternative, more mechanistically-grounded, approach to understand how species affect each other abundance. 
-Species abundances are also influenced by the dynamic relationships between nodes, and the mechanisms of self-regulation, however, community and population dynamics can be modelled in innumerable ways, and empirical support for one versus another is often still ambiguous.
-The alternative approach should acknowledge ecosystem dynamics, but without being overly dependent on the particular choices of how they are characterised.
+<!-- I feel like the question of there being so many centralities distracts from the main line of thinking.
+You could arguably emphasize the phenomenological piece better (with an example?) and jump straight to the sentence below this comment.
+-->
+Furthermore, recent studies have shown that definitions of keystoneness based on centrality might not adequately predict the cascading extinctions keystone species are usually associated to. 
+As a result, community ecology could arguably benefit from an alternative, more mechanistically-grounded, approach to understand how species affect each other's abundance.
 
+Species abundances are also influenced by the specific dynamic relationships between nodes and the mechanisms of self-regulation; however, community and population dynamics can be modelled in innumerable ways, and empirical support for one versus another is often still ambiguous.
+The alternative approach should therefore acknowledge ecosystem dynamics, but without being overly dependent on the particular choices of how they are characterised.
 Among the various possibilities, *control theory* appears to be a strong candidate [@isbell_human_2013]. 
-Control theory is a widely studied branch of engineering used to determine and supervise the behaviour of dynamical systems [@motter_networkcontrology_2015]. 
+Control theory is a widely-studied branch of engineering used to determine and supervise the behaviour of dynamical systems [@motter_networkcontrology_2015]. 
 It is inherently designed to deal with system feedbacks and its application has recently been expanded to complex networks [@liu_control_2016]. 
-In correspondence with ecological questions, advances in this field have established a clear link between the structure of the network and the way nodes affect each other. 
-Unlike centrality indices, however, this link is not based on a priori assumptions between network metrics and keystoness, instead, it is based on well-established advances in both dynamical and complex-systems theory <!--STOUFFER: Are we shooting ourselves in the foot since this isn't entirely true?
+In concordance with long-standing ecological questions, advances in this field have established a clear link between the structure of the network and the way nodes affect each other. 
+Unlike centrality indices, however, this link is not based on a priori assumptions between network metrics and keystoneness but is instead based on well-established advances in both dynamical and complex-systems theory.
+<!--STOUFFER: Are we shooting ourselves in the foot since this isn't entirely true?
 That is, see comments from ELE about linearity and otherwise.
-CAGUA: How about this modified phrasing?-->.
+CAGUA: How about this modified phrasing?
+DBS: I approve.
+;)-->.
 
@@
 Possibly, this is in part because research on the control of complex networks is generally more concerned with the state of the system as a whole. 
-This is in contrast with the ecological role concept, where the focus is on the nodes that compose the network.
+This is, in contrast with the interest in ecological roles, where the focus is on the nodes that compose the network.
 At its fundamental level, control theory first determines whether a system is controllable or not; that is, it asks if a system can be driven to a desired state within a finite amount of time. 
-Although the controllability of a network is a whole-system property, it has been recently shown that asking for the controllability of a complex-system is equivalent to finding a particular set of nodes.
-A set with which is possible to control the state of the whole network. 
+Although the controllability of a network is a whole-system property, it has been recently shown that asking for the controllability of a complex-system is equivalent to finding a particular set of nodes: the set with which is possible to control the state of the whole network.
 Notably, this set of nodes is not always unique for a given network.
@@
 
-Here, we apply methods from control theory to an ecological problem and show how it can be used to gain insight into the role of species in an ecological network. 
+<!-- I feel like the paragraph above is trying to tell me two things and does neither very clearly.
+My gut tells me that it could probably be improved by removing the first sentence and worrying less about why it hasn't but ways in which the application to ecology could be improved.
+Does that make sense?
+-->
+
+Here, we apply methods from control theory to a particular ecological problem and show how it can be used to gain insight into the role of species in an ecological network. 
 Specifically, we outline the approach using a set of ten pairs of uninvaded and invaded plant-pollinator communities. 
-We use invaded communities because there is strong empirical evidence showing that invasive species play an important role shaping the abundances of other species, and particularly in these ten networks [@lopezaraizamikel_impact_2007; @bartomeus_contrasting_2008-1].
-This choice thus offers us an opportunity to explicitly contrast theoretical observations with empirical evidence.
-First, grounded in the difficulties usually involved with invasive-species eradication and ecosystem restoration [@woodford_confronting_2016], we ask whether there are differences between the controllability of invaded and uninvaded networks.
-<!--STOUFFER: I'd remove the grounded in....
-stuff, but that's just me.
-CAGUA: I don't like it either.
-I tried removing but then it feels like this question is coming out of the blue.-->
-Then we expand existing methods control theory to effectively link the *controllability* of a network with the role of particular nodes. 
+We use invaded communities because there is strong empirical evidence showing that invasive species play an important role shaping the abundances of other species, something which is particularly true in these ten networks [@lopezaraizamikel_impact_2007; @bartomeus_contrasting_2008-1].
+This choice thus offers us an opportunity to explicitly contrast our theoretical observations with empirical evidence.
+With these network, we first ask whether there are differences between the controllability of invaded and uninvaded networks.
+This question is motivated by in the difficulties commonly encountered with invasive-species eradication and ecosystem restoration [@woodford_confronting_2016].
+<!--STOUFFER: I'd remove the grounded in.... stuff, but that's just me.  CAGUA: I don't like it either. I tried removing but then it feels like this question is coming out of the blue.-->
+We then expand existing methods from control theory to effectively link the *controllability* of a network with the role of particular species.
 We ask—from a control-theoretic perspective—whether there are key differences between species in the role they play at driving the population of other members of the community and identify the ecological factors related to these differences.
-Finally, we compare the proposed approach to current methods based on species centrality and show how these methods are indeed valuable but only paint a limited picture in regards to the "keystonness" of a species.
+Finally, we compare the proposed approach to current methods based on species centrality and show how these methods are indeed valuable but ultimately paint a limited picture in regards to the dynamic "keystoneness" of a species.
 
@@
 
-We used ten paired pollination communities to apply the control theoretic approach.
+We used ten paired pollination communities to apply the control-theoretic approach.
 Each community pair was composed of a community invaded by a plant and a community free of the invasive species. 
@@
 The structure of all these communities was defined by the pollinator visitation frequency, which has been shown to be an appropriate surrogate for interspecific effects in pollination networks [@vazquez_interaction_2005; @bascompte_asymmetric_2006].
-Full details about the empirical networks, the implications of using visitation frequency to quantify the strength of the associations, and the sensitivity of the control theoretic approach to undersampling of the interactions can be found in the supplementary information section \@ref(S-empirical-networks), XX, and XX.
+Full details about the empirical networks, the implications of using visitation frequency to quantify the strength of the associations, and the sensitivity of the control-theoretic approach to undersampling of the interactions can be found in the supplementary information section \@ref(S-empirical-networks), XX, and XX.
 
@@
 This asymmetry is given by $$a(i,j) = a(j,i) = \frac{\left | d_{ij}-d_{ji} \right |}{max\left ( d_{ij}, d_{ji} \right )},$$ where the dependence of plant *i* on pollinator *j*, *d~ij~*, is the proportion of the visits from pollinator *j* compared to all pollinator visits to plant *i*.
-Previous research has shown that mutualistic interactions are often highly asymmetric in natural communities; in other words, if a plant species is largely dependent on a pollinator species, then that pollinator tends to depend rather weakly on the plant (or vice versa).
+Previous research has shown that mutualistic interactions are often highly asymmetric in natural communities; in other words, if a plant species is largely dependent on a pollinator species, that pollinator tends to depend rather weakly on the plant (and vice versa).
 We, therefore, create a directed link between species *i* and *j* when $d_{ij}-d_{ji} \geq 0$ to establish the most likely direction of control between a species pair (Figure \@ref(fig:fig-example-networks)a).
+<!-- The sentence above is slightly ambiguous. Shouldn't it say "create a directed link from species *i* to species *j*"? -->
+Sometimes there is no observed asymmetry between species pairs ($d_{ij}=d_{ji}$), and we cannot infer a dominant  direction of control. 
+When this occurs, we deem both species to be equally likely to affect each other and create two directed links between them, one from *i* to *j* and another from *j* to *i*. 
 By basing the direction of the links on the asymmetry of their dependence, we are able to generate a network that is consistent with the dynamics of the community while satisfying the requirements of structural controllability.
@@
 
+<!-- The sentence above needs a paragraph to belong to. It's too lonely. Seriously. -->
+
 ## Controllability
@@
 A system is said to be controllable if it is possible to steer it from an initial to an arbitrary final state within finite time [@kalman_mathematical_1963]. 
+<!-- The sentence above and the sentence below both work well as leading sentences for a paragraph but neither works well as a second.
+Can you find somewhere to fold the one above into the paragraph (or elsewhere) or rewrite the beginning of the one below?
+-->
 A simple dynamic system can be described by $\frac{dx}{dt} = Ax + Bu(t)$, where the change of its state over time ($\frac{dx}{dt}$) depends on its current state *x* (for example, the species' abundances), an external time-varying input *u(t)* (the control signal), and two matrices *A* and *B*, which encode information about the network structure and how species respond to external inputs, respectively.
-In classic control theory, determining wether this system is controllable can easily be achieved by checking that its controllability matrix $R= [ \begin{matrix}B & AB & A^{2}B & ...& A^{n-1}B\end{matrix} ]$ has full rank.
-In complex systems, however, employing this rank condition, or numerical approximations of it, is unfeasible because it is hard to fully parameterize *A* and *B* (either because the weight of the links changes over time or because they are difficult to measure).
-Here we use an approach based on the structural controllability theorem [@lin_structural_1974], which assumes that we are confident that the elements of *A* and *B* have either non-zero or zero values (there is an interaction or not), but that we less sure about the precise magnitude of the non-zero values.
+In classic control theory, determining wether this system is controllable can be achieved by checking that its controllability matrix $R= [ \begin{matrix}B & AB & A^{2}B & ...& A^{n-1}B\end{matrix} ]$ has full rank.
+In complex systems, however, employing this rank condition, or numerical approximations of it, is infeasible because it is hard to fully parameterize *A* and *B* (either because the weight of the links changes over time or because they are difficult to measure).
+Here we use an approach based on the structural controllability theorem [@lin_structural_1974], which assumes that we are confident about which elements of *A* and *B* have either non-zero or zero values (there is an interaction or not), but that we less sure about the precise magnitude of the non-zero values.
 Using this structural approach we can find out the controllability of a system under almost all non-zero parameter realisations.
 Structural controllability also has a graphical interpretation that allows us to translate the control problem into a topological one: a network is controllable if there are no inaccessible nodes—nodes without incoming links—or dilations—*expansions* of the network (Figure \@ref(fig:fig-example-networks)b; Supplementary Information section \@ref(S-structural-controllability)).
+<!-- The last sentence of the paragraph above sticks out a bit. -->
 
-We are often able to estimate *A* in ecological networks, as it represents the interactions between species. 
-Part of the control problem resides on estimating a supportable estimation of *B*, which represents the links between external inputs and species. 
-Naively, any ecological community (and any system for that matter) could be controlled if we control the state of every species independently. 
-Such approach is typically unpractical. 
-We are instead interested in finding a minimum driver node-set (effectively finding *B*) with which to make the system controllable. 
-However, a brute force search of this minimum driver node set is computationally prohibitive for most networks as it involves the evaluation of $2^N$ different controllability matrices. 
-We employ a recently developed approach that shows that the control problem of finding the minimum driver node set can be mapped into a graph-theoretic problem: maximum matching [@liu_controllability_2011; @liu_control_2016].
+We are often able to estimate *A* in ecological networks, as this matrix represents the interactions between species. 
+Part of the control problem resides in estimating a supportable estimation of *B*, which represents the links between external inputs and species. 
+Naively, any ecological community (and any system for that matter) could be controlled if we control the state of every species independently, but such an approach is typically impractical. 
+Here, we are interested in finding a minimum driver node-set (effectively finding *B*) with which to make the system controllable. 
+The brute-force search for this minimum driver node set is computationally prohibitive for most networks as it involves the evaluation of $2^N$ different controllability matrices. 
+We therefore instead employ a recently-developed approach that shows that the control problem of finding the minimum driver node set can be mapped into a graph-theoretic problem: maximum matching [@liu_controllability_2011; @liu_control_2016].
 
-Maximum-matching is a widely studied topic in graph theory and is commonly used in multiple applications, ranging from dating apps and wireless communications to organ transplant allocation and peer to peer file sharing.
-A matching in an unweighted directed graph is defined as a set of links that do not share a common start or end nodes; the largest possible matching is called maximum matching. 
-For example, in a network composed by jobs and job applicants, a matching is any pairing between applicants and positions that satisfies one basic constraint: an applicant can be assigned to at most one position and vice-versa.
+Maximum matching is a widely studied topic in graph theory and is commonly used in multiple applications, ranging from dating apps and wireless communications to organ transplant allocation and peer-to-peer file sharing.
+A matching in an unweighted directed graph is defined as a set of links that do not share a common start or end nodes; the largest possible matching is called a maximum matching. 
+For example, in a network composed by jobs and job applicants, a matching is any pairing between applicants and positions that satisfies one basic constraint: an applicant can be assigned to at most one position and vice versa.
 Consequently, a maximum matching is an optimal pairing, one that maximises the number of applicants with jobs and the number of positions filled. 
-At first glance, however, is hard to identify how exactly matchings are related to structural controllability. 
-The key is to note that the conditions of structural controllability imply that, just like the one to one relationship between jobs and applicants, there needs to be a one to one relationship between *superior* and *subordinate* nodes (Figure \@ref(fig:fig-example-networks)b, bottom left).
-We use the maximum matching algorithm to find an optimal pairing of superior and subordinate nodes in a way consistent with the controllability conditions (supplementary information section \@ref(S-one-maximum-matching)).
-The result is that a matching can actually be decomposed into a set of paths that reveal how a control signal can flow across the links in a network to reach every node that composes it. 
-And so, as recently shown [@liu_controllability_2011], the minimum driver node set, those to which an external control input should be applied to make the system controllable, corresponds exactly to the *unmatched* nodes in the network (Figure \@ref(fig:fig-control-configuration)).
+Admittedly, the link between matchings and structural controllability may appear far from straightforward. 
+The key is to note that the fundamental conditions of structural controllability imply that there is a one-to-one relationship between *superior* and *subordinate* nodes just like the one-to-one relationship between jobs and applicants (Figure \@ref(fig:fig-example-networks)b, bottom left).
+We thus use the maximum-matching algorithm to find an optimal pairing of superior and subordinate nodes in a manner consistent with the controllability conditions (supplementary information section \@ref(S-one-maximum-matching)).
+Given the result, we can further decompose the matching into a set of paths that reveal how a control signal can flow across the links in a network to reach every node that composes it. 
+As recently shown [@liu_controllability_2011], the minimum driver node set---those to which an external control input should be applied to make the system controllable---corresponds exactly to the *unmatched* nodes in the network (Figure \@ref(fig:fig-control-configuration)).
 
@@
 
-Our first main objective is to investigate whether the controllability of a community is associated with invasion status or not. 
-Finding out exactly, how difficult is to control a network depends strongly on the particularities of the desired control trajectory as well as the dynamical relationship between nodes. 
+Our first ecological objective is to investigate whether the controllability of a community is associated with invasion status or not. 
+Finding out exactly how difficult it is to control a network depends strongly on the particularities of the desired control trajectory as well as the dynamical relationship between nodes. 
 However, we are interested in understanding the controllability of a network in a more general sense, such that it can be applied even when the precise control scenario is known only incompletely. 
-We instead employ an indicator that follows from our approach: the size of the minimum driver node set. 
+To this end, we chose an indicator that follows directly from our approach: the size of the minimum driver node set. 
 This simple metric provides a general indication of how difficult controlling a network might be, as systems that require a large number of external inputs to be fully controlled are intuitively more difficult or costly to manage.
-Specifically, following the structural controllability literature, we use the size of the minimum driver node set relative to the total number of nodes $n_D = \frac{D}{N}$ as a measure of the extent to which the network structure can be harnessed to control the community.
+Specifically, drawing from the structural-controllability literature, we use the size of the minimum driver node set relative to the total number of nodes $n_D = \frac{D}{N}$ as a measure of the extent to which the network structure can be harnessed to control the community.
 In an ecological context, external inputs can be thought of as management interventions that modify the abundance of a particular species. 
+<!-- Would the two sentences below work better after the "Finding out exactly how difficult..." sentence? -->
 For instance, achieving full control in a "network" in which species do not interact at all is relatively difficult as we would require an intervention for every single species. 
@@
 
-After finding the minimum driver node set in each of our networks we want to test whether invasion status or other predictors are correlated to this metric of controllability. 
+After finding the minimum driver node set in each of our networks, we want to test whether invasion status or other predictors are correlated to this metric of controllability. 
 We, therefore, use a set of generalised linear models (with binomial error structure) to investigate the effect of invasion status while also including covariates related to species richness, since one might naively expect to see a negative relationship between richness and controllability [@menge_indirect_1995].
 These covariates included the total number of species, plant richness, pollinators richness, the ratio of plant to pollinator richness, the link density (connectance), and the study site (as a two-level factor).
-In addition, we also explored whether real networks differ in their architecture from random ones in a concerted way (supplementary information section \@ref(S-randomisations)).
+In addition, we also explored whether real networks differ in their architecture from random ones in a concerted way that could impact these results (supplementary information section \@ref(S-randomisations)).
 
@@
 
-While calculating the size of the minimum drive node set can measure the controllability of an ecological community, it does not provide information about the role that particular species play. 
 Our second key question is related to how species differ in their ability to drive the population dynamics of the community.
 Ecologically, these differences are relevant because resources and data are limited, and therefore full control is unfeasible. 
-To answer this question, we make two kinds of distinctions between species from a control perspective.
+While calculating the size of the minimum drive node set can measure the controllability of an ecological community, it does not provide information about the roles that particular species play. 
+To answer our question, we make two kinds of distinctions between species from a control perspective.
 
-First, we harness the fact that maximum matchings in a network are often not unique, and each maximum matching indicates unique paths that can potentially be used to control the network. 
-Specifically, we use the frequency with which a species is part of the multiple minimum driver node sets, its control capacity $\phi$, as an estimation of its relative importance in driving the state of the community as a whole [@jia_control_2013].
+First, we harness the fact there may be multiple maximum matchings for a given network, and each of these maximum matchings indicates unique paths that could potentially be used to control the network.
+Specifically, we use the frequency with which a species is part of the multiple minimum driver node sets---its control capacity $\phi$---as an estimation of its relative importance in driving the state of the community as a whole [@jia_control_2013].
 For example, a species with a control capacity $\phi_i= 1$ is a one that requires external input in every single control configuration. 
-This is, if we were to drive the community to an arbitrary alternate state, we would need to apply a management intervention to this species under any optimal control strategy.
+This is, if we were to drive the community to an arbitrary alternate state, we would need to apply a management intervention to this species under *any* optimal control strategy.
 
-Intuitively, to calculate a species control capacity $\phi$ we need to enumerate all possible maximum matchings (we detail the algorithm to find all maximum matchings in the Supplementary Information section \@ref(S-all-maximum-matching)).
-However, enumerating all maximum matchings extremely expensive from a computational perspective—a network with a couple dozen nodes could be controlled with several hundred million unique matchings. 
-To solve this problem we instead employ a recently developed algorithm that reveals the control correlations between the nodes in the graph [@zhang_input_2016, Supplementary Information section \@ref(S-input-graph)].
-Using this algorithm we are able to obtain every minimum driver node set with information obtained from a single maximum matching. 
+To calculate a species control capacity $\phi$, we need to enumerate all possible maximum matchings (we detail the algorithm to find all maximum matchings in the Supplementary Information section \@ref(S-all-maximum-matching)).
+However, enumerating all maximum matchings is extremely expensive from a computational perspective—a network with a couple dozen nodes could be controlled with several hundred million unique matchings.
+To solve this problem, we employ a recently-developed algorithm that reveals the control correlations between the nodes in the graph [@zhang_input_2016, Supplementary Information section \@ref(S-input-graph)].
+Using this algorithm, we are able to obtain every minimum driver node set with information obtained from a single maximum matching. <!-- I don't think I follow the end of this sentence. -->
 The end result is that we are now able to calculate the control capacity $\phi_i$ of every node in linear time—rather than polynomial as the algorithm for matching enumeration requires.
+
+<!-- The paragraph above reminded me of something in the back of my mind.
+Sometimes it's probably better to talk about species instead of nodes, even when we refer to aspects of graph theory.
+Could you go through and look carefully at every appearance of node to see if it would be easier for people that aren't us to understand if we said species instead?
+-->
 
@@
 Consequently, we make a second distinction between nodes based on whether they form part of possible control paths in the network and therefore are likely to influence the abundance of another species.
-We identify those species by checking whether they are classified as a superior node, this is they are at the beginning of a matched link. 
+We identify these species by checking whether they are classified as a superior node, this is they are at the beginning of a matched link. 
 While unmatched nodes correspond to those that should be influenced with an external control input, superior nodes correspond to those that influence other species internally. 
-Conveniently, with the exception of some pathological cases, superior nodes are such across every control configuration and therefore knowing one maximum matching provides enough information on whether a species is likely to play an important role at influencing the abundance of other species or not.
+Conveniently, with the exception of some pathological cases<!--expand or remove?-->, superior nodes always play this role across every control configuration, and therefore knowing one maximum matching provides enough information on whether a species is likely to play an important role at influencing the abundance of other species or not.
+<!--The end of this paragraph seems to just restate the end of the previous paragraph.
+What new info should I feel like I've gained but aren't?-->
 
-We then examined whether any species-level structural properties could predict a species control capacity $\phi$ and the likelihood of being a superior node.
+<!-- You never formally define sigma. -->
+
+To examine whether any species-level structural properties could predict a species control capacity $\phi$ and the likelihood of being a superior node $\sigma$, we calculated these properties for each of our networks.
+In the networks that contained reciprocal links (because there was not assymetry in the dependences of a species pair), we averaged a species' $\phi$ and $\sigma$ across every possible "non-reciprocal" realisation of the network (more details can be found in the Supplementary Information section \@ref(S-reciprocal-links)).
 *TODO: Still need to decide how to do this and how to compare traditional centrality metrics to the new control based ones.
-Will probably base the comparison on stability/feasibility metrics or/and on coextinction of species groups.*Maximum matchings and control configurations.
-In directed networks, a maximum matching is the largest possible set of links that do not share start or end nodes (dark purple).
-Maximum matchings are not necessarily unique, instead, each of them is related to a possible minimum driver node set in the network (the nodes to which an external control input, in orange, should be applied in order to ensure controllability).
-The size of the minimum driver node set *D* corresponds exactly to the number of unmatched nodes (the number of nodes in the network *N* minus the matching size).
-To account for network size, we use the size of the minimum driver node set relative to the total number of nodes *n~D~ = D/N* as a measure of the extent to which the network structure can be harnessed to control the system.
+Will probably base the comparison on stability/feasibility metrics or/and on coextinction of species groups.*
+<!-- Do you really think there is enough time left to test these things in anything but a correlational fashion? -->
 

### 2018-06-07 paper/manuscript.Rmd
Add comparison of controllability methods
Close #23

@@
 However, enumerating all maximum matchings is extremely expensive from a computational perspective—a network with a couple dozen nodes could be controlled with several hundred million unique matchings.
-To solve this problem, we employ a recently-developed algorithm that reveals the control correlations between the nodes in the graph [@zhang_input_2016, Supplementary Information section \@ref(S-input-graph)].
-Using this algorithm, we are able to obtain every minimum driver node set with information obtained from a single maximum matching. <!-- I don't think I follow the end of this sentence. -->
-The end result is that we are now able to calculate the control capacity $\phi_i$ of every node in linear time—rather than polynomial as the algorithm for matching enumeration requires.
+To solve this problem, we employ a recently-developed algorithm that reveals the control correlations between the nodes in the graph using considerably less computational resources [@zhang_input_2016, Supplementary Information section \@ref(S-input-graph)].
+Using this algorithm, we are able to identify species that are possible control inputs—those that belong to the minimum driver node set in at least one of the possible control configurations. 
+One of the original contributions of our work is to extend this algorithm such that it is possible to calculate a highly accurate approximation of the control capacity $\phi_i$ of every species in the network.
 

### 2018-06-07 paper/supp-info.Rmd
Add comparison of controllability methods
Close #23

@@
 
+In order to calculate a node's control capacity $\phi$, we harness the fact that nodes can be classified in three groups according to their role in the input graph. 
+First,  if $x_i$ belongs to the minimum driver node set and has no adjacent nodes, then it cannot be replaced and will be part of every possible control configuration. 
+Second, if $x_i$ does not belong to the minimum driver node set and is not adjacent to any possible input node, then it does not part of the minimum driver node set under any control configuration. 
+Finally, if a node $x_i$ belongs to the minimum driver node set and is adjacent to another node $x_j$ in the input graph, then $x_j$ must belong to another minimum driver node to which $x_i$ doesn not belong, in other words $x_i$ and $x_j$ are substitutable.
+
+The frist and the second group have a control capacity of $\phi = 1$ and $\phi = 0$ respectively. 
+Meanwhile, the third group has intermediate values of control capacity which can be calculated by computing the number of possible susbstitutions of a node by its control adjacent nodes. 
+As a rule of thumb the largest the number of possible substitutions an input node has, the smaller its control capacity.
+
+```{r control-capacity-correlations}
+drake::loadd(control_capacity_correlations, this_method)
+
+cc_corr <- control_capacity_correlations %>%
+  dplyr::inner_join(metadata, by = "net_name") %>%
+  dplyr::filter(study %in% c("bartomeus", "lopezaraiza")) %>%
+  dplyr::filter(!is.na(corr), method == this_method) %$%
+  corr
+```
+
+For larger networks, calculating the control capacities using the input graph is several orders of magnitude faster than computing all possible maximum matchings. 
+While the the computation time of the input graph grows linearly with network size, the compuation of all maximum matchings grows polynomially. 
+However, the control capacities obtained using the input graph are not identical to those obtained by computing all possible maximum matchings. 
+The reason of this discrepancy is that two maximum matchings might result in the same minimum driver node set. 
+Nevertheless, the results obtained using both approaches are extremely similar. 
+We compared the control capacity obtained by calculating all maximum matchings and that obtained using the input graph in `r length(cc_corr)` of our networks (those for which we were able to calculate all maximum matchings within reasonable time).
+The spearman correlation was very high in all cases, ranging between `r round(min(cc_corr),2)` and `r round(max(cc_corr), 2)` (median `r round(mean(cc_corr), 2)`).
+
 ## Networks with reciprocal links {#reciprocal-links}

### 2018-06-07 main.R

@@ -40,7 +40,6 @@ basic_analysis_plan <- drake::drake_plan(
     "ISA", 
     "weighted NODF")), 
   directed_networks = purrr::map(networks, as_directed_network, direction = "asymmetry", ties = "both", higher_level = "pol"),
-  matched_networks = purrr::map(directed_networks, control_capacity_empirical_nets, l = aggregation_option_list),
   strings_in_dots = "literals"
 )
 
@@ -58,6 +57,21 @@ example_plots_plan <- drake::drake_plan(
   fig_bidirectional = make_fig_bidirectional(en_chain)
 )
 
+control_capacity_testing_plan <- drake::drake_plan(
+  control_input_pub_method = test_control_metrics(directed_networks, "input_graph", method = "published"),
+  control_input_min_method = test_control_metrics(directed_networks, "input_graph", method = "mine"),
+  control_lineg_method = test_control_metrics(directed_networks, "complementer", timeout = 60*60, exclude = "CD_ctl"),
+  control_capacity_correlations = cc_correlations(control_input_pub_method, control_input_min_method, control_lineg_method),
+  this_method = compare_cc_options(control_capacity_correlations, metadata),
+  strings_in_dots = "literals"
+)
+
+controllability_plan <- drake::drake_plan(
+  matched_networks = purrr::map(directed_networks, control_capacity_empirical_nets, l = aggregation_option_list, .method = this_method),
+  controllability = controllability_emp(matched_networks),
+  strings_in_dots = "literals"
+)
+
 reporting_plan <- drake::drake_plan(
   render_pdf(drake::knitr_in('paper/supp-info.Rmd'), 
              drake::file_out('paper/supp-info.pdf'), clean_md = FALSE),
@@ -69,7 +83,9 @@ reporting_plan <- drake::drake_plan(
               drake::file_out('paper/cover-letter.pdf'))
 )
 
-project_plan <- rbind(read_data_plan, basic_analysis_plan, example_plots_plan, reporting_plan)
+project_plan <- drake::bind_plans(
+  read_data_plan, basic_analysis_plan, example_plots_plan, 
+  control_capacity_testing_plan, controllability_plan, reporting_plan)
 project_config <- drake::drake_config(project_plan)
 drake::make(project_plan, config = project_config)
 

### 2018-06-08 paper/supp-info.Rmd
Filter out ballantyne networks on its own function

@@
 ```{r}
-drake::loadd(directed_networks)
+drake::loadd(directed_networks, metadata)
 recipr <- directed_networks %>%
@@
   } %>%
-  dplyr::inner_join(metadata, by = "net_name") %>%
-  dplyr::filter(study %in% c("bartomeus", "lopezaraiza"))
+  filter_networks_df(metadata)
 ```

### 2018-06-08 code/calc_ntw_properties.R

@@ -52,3 +52,12 @@ keep_largest_component <- function(net){
 	largest_co <- which(co$csize == max(co$csize))
 	igraph::delete_vertices(net, co$membership != largest_co)
 }
+
+# filter out some networks from a data frame with a net_name data
+filter_networks_df <- function(x, metadata, desired_ntw = c("bartomeus", "lopezaraiza")){
+  m <- dplyr::select(metadata, net_name, study)
+  x %>% 
+    dplyr::inner_join(m, by = "net_name") %>%
+    dplyr::filter(study %in% desired_ntw) %>%
+    dplyr::select(-study)
+}

### 2018-06-08 code/ggplot_theme.R
Create ggplot theme for the ms

@@ -1,0 +1,13 @@
+base_ggplot_theme <- function(){
+  theme_bw() +
+    theme(text = element_text(family = "Helvetica"),
+          title = element_text(size = 7, hjust = 0),
+          legend.title = element_text(size = 8),
+          legend.text = element_text(size = 7),
+          axis.text = element_text(size = 7),
+          axis.title = element_text(size = 8, hjust = 0.5), 
+          strip.text = element_text(size = 8, hjust = 0), 
+          strip.background = element_blank(),
+          plot.margin = grid::unit(c(5, 0.5, 2, 0), "mm"),
+          panel.grid = element_blank())
+}

### 2018-06-08 paper/manuscript.Rmd
Initial commit of results
Addresses #19

@@
 
+# Results
+
+```{r controllability}
+drake::loadd(controllability, metadata)
+c_m <- controllability %>% 
+  filter_networks_df(metadata)
+```
+
+The size of the minimum driver node set relative to the number of species in each network $n_D$ ranged between `r round(min(c_m$n_D), 2)` and `r round(max(c_m$n_D), 2)` (mean `r round(mean(c_m$n_D), 2)`, Figure \@ref(fig:fig-emp-controllability)).
+
+```{r fig-emp-controllability, fig.width=fig_sizes()[[1]], fig.height=fig_sizes()[[1]]/sqrt(2), fig.cap="Density plot ofsize of the minimum driver node set.
+The vertical dashed line indicates the meann value."}
+drake::loadd(fig_emp_controllability)
+fig_emp_controllability
+```
+
 # References

### 2018-06-08 paper/supp-info.Rmd
Small edits in Supp materials

@@
 If a node $x_i$ is part of a minimum driver node set then every node in the same component of $x_i$ in the input graph is a possible driver node.
-Every node within the same component in the input graph has the same control capacity $\phi$ and the control capacity $\phi_i$ of node $x_i$ is inversely proportional to the number of nodes in the same component of $x_i$.
 
@@
 We compared the control capacity obtained by calculating all maximum matchings and that obtained using the input graph in `r length(cc_corr)` of our networks (those for which we were able to calculate all maximum matchings within reasonable time).
-The spearman correlation was very high in all cases, ranging between `r round(min(cc_corr),2)` and `r round(max(cc_corr), 2)` (median `r round(mean(cc_corr), 2)`).
+The spearman correlation was very high in all cases, ranging between `r round(min(cc_corr),2)` and `r round(max(cc_corr), 2)` (median `r round(median(cc_corr), 2)`).
 
@@
 
-Our procedures to find minimum driver node sets is only adequate when there are no reciprocal (bidirectional) links in the network. 
+Our procedures to find minimum driver node sets are only adequate when there are no reciprocal (bidirectional) links in the network. 
 The proportion of reciprocal links in relatively low. 
@@
 However, reciprocal links are not a rare occurrence as `r sum(recipr$prop_bid != 0)` out of `r nrow(recipr)` empirical networks had at least one. 
-To calculate our controllability metrics at both the network (the relative size of the minimum driver node set, $n_D$) and species level (control capacity, $\phi$, and the likelihood of being a superior node, $\sigma$) we first need to generate all possible versions of the of the network that include only non-reciprocal links.
+To calculate our controllability metrics at both the network (the relative size of the minimum driver node set, $n_D$) and species level (control capacity, $\phi$, and the likelihood of being a superior node, $\sigma$) we first need to generate all possible versions of the of the network that include only non-reciprocal links (Figure \@ref(fig:fig-bidirectional)).
 
-Based on the available information, all of these network is as likely to be one that best represent the superior/matched relationships in the network. 
+All of these non-reciprocal networks are as likely to be one that best represent the superior/matched relationships in the network. 
 As such, we average the three metrics ($n_D$, $\phi$, and $\sigma$) across all the networks without reciprocal links without weighting by the number of possible control configurations.

### 2018-06-08 paper/manuscript.Rmd
Add results of controllability models
Close #13

@@
 The size of the minimum driver node set relative to the number of species in each network $n_D$ ranged between `r round(min(c_m$n_D), 2)` and `r round(max(c_m$n_D), 2)` (mean `r round(mean(c_m$n_D), 2)`, Figure \@ref(fig:fig-emp-controllability)).
+We found this not to be related to any of the evaluated metrics. 
+The most parsimonious model, as determined by the AICc was the null model, which included not predictors (Supplementary Information \@ref(S-controllability-models)).
 
-```{r fig-emp-controllability, fig.width=fig_sizes()[[1]], fig.height=fig_sizes()[[1]]/sqrt(2), fig.cap="Density plot ofsize of the minimum driver node set.
+```{r fig-emp-controllability, fig.width=fig_sizes()[[1]], fig.height=fig_sizes()[[1]]/2, fig.cap="Density plot ofsize of the minimum driver node set.
 The vertical dashed line indicates the meann value."}

### 2018-06-08 paper/supp-info.Rmd
Add results of controllability models
Close #13

@@
 
+# Controllability models {#controllability-models}
+
+The models were
+
+```{r}
+drake::loadd(controllability_models)
+
+replace_terms <- function(x){
+  x %>% 
+    stringr::str_replace("inv", "inv") %>%
+    stringr::str_replace("connectance", "C") %>%
+    stringr::str_replace("weighted_NODF", "NODF") %>%
+    stringr::str_replace("n_sp", "n_s") %>%
+    stringr::str_replace("web_asymmetry", "AS_n") %>%
+    stringr::str_replace("interaction_strength_asymmetry", "AS_s") %>%
+    stringr::str_replace(stringr::fixed("~"), "\\sim ")
+}
+
+AICcmodavg::aictab(controllability_models) %>% 
+  dplyr::mutate(Modnames = replace_terms(Modnames)) %>% 
+  dplyr::select(Modnames, AICc, Delta_AICc, Cum.Wt) %>%
+  dplyr::filter(Delta_AICc <= 8) %>%
+  dplyr::rename(model = Modnames, `$\\Delta AICc$` = Delta_AICc, `$AICc$` = AICc, `Cum. Weight` = Cum.Wt) %>%
+  dplyr::mutate(model = paste0("$", model, "$")) %>% 
+  knitr::kable(escape = FALSE, 
+               booktabs = TRUE, 
+               digits = 2, 
+               linesep = c(""),
+               caption = "Model selection table based on the Akaike Information Criterion for small samples for candidate models of size of the minimum driver node set ($n_D$) in the empirical networks.
+There was no evidence for any of the evaluated predictors: the invasion status (inv), the network connectance (C), the network nestedness (NODF) the number of species ($n_S$) the network asymmetry ($AS_s$) or the interaction strength asymmetry ($AS_s$).
+Only candidate models with $\\Delta AIC < 8$ are shown.")
+```
+
 # References

### 2018-06-08 code/controllability_models.R

@@ -1,0 +1,47 @@
+assemble_controllabillity_df <- function(controllability, network_properties, metadata){
+  controllability %>%
+    filter_networks_df(metadata) %>%
+    dplyr::inner_join(metadata, by = "net_name") %>%
+    dplyr::inner_join(network_properties, by = "net_name") %>%
+    dplyr::rename(n_pla = n_pla.x, 
+                  n_pol = n_pol.x, 
+                  web_asymmetry = web.asymmetry, 
+                  interaction_strength_asymmetry = interaction.strength.asymmetry, 
+                  weighted_NODF = weighted.NODF)
+}
+# drake::loadd(controllability, network_properties, metadata)
+
+fit_controllability_models <- function(controllability_model_data){
+  vars = c("n_sp", "connectance", "web_asymmetry", "interaction_strength_asymmetry", "weighted_NODF", "inv", "study")
+  # extra = " + (1 | study)"
+  suppressWarnings({
+    models <- get_model_formulas("n_D", vars) %>% 
+      `names<-`(., .) %>%
+      purrr::map(~glm(as.formula(.), data = controllability_model_data, family = "binomial"))
+  })
+  models
+}
+# drake::loadd(controllability_model_data)
+
+get_model_formulas <- function(prefix, vars, suffix = "", add_1 = T){
+  # all combinations
+  length(vars):0 %>%
+    purrr::map(function(x){
+      f <- combn(vars, x) %>%
+        purrr::array_branch(2) %>%
+        purrr::map(paste, collapse = " + ")
+      if(add_1) {f <- f %>% purrr::modify_if(. == "", function(x) "1")}
+      f
+    }) %>%
+    purrr::flatten() %>%
+    purrr::map(~ paste(prefix, "~", ., suffix)) 
+}
+
+get_var_importance <- function(model_list){
+  params <- summary(model_list[[1]])$aliased %>% names() %>% extract(-1)
+  params %>% `names<-`(., .) %>%
+    as.list() %>%
+    purrr::map(~ AICcmodavg::importance(model_list, .)) %>%
+    purrr::map_dfr(as.data.frame)
+}
+# drake::loadd(controllability_model)

### 2018-06-08 main.R

@@ -73,6 +73,9 @@ control_capacity_testing_plan <- drake::drake_plan(
 controllability_plan <- drake::drake_plan(
   matched_networks = purrr::map(directed_networks, control_capacity_empirical_nets, l = aggregation_option_list, .method = this_method),
   controllability = controllability_emp(matched_networks),
+  controllability_model_data = assemble_controllabillity_df(controllability, network_properties, metadata),
+  controllability_models = fit_controllability_models(controllability_model_data),
+  controllability_variable_importance = get_var_importance(controllability_models),
   strings_in_dots = "literals"
 )
 

### 2018-06-09 paper/manuscript.Rmd
Complete controllability model wording
Towards #19

--- 2018-06-07 paper/manuscript.Rmd
@@
 
+# Results
+
+```{r controllability}
+drake::loadd(controllability, metadata)
+c_m <- controllability %>% 
+  filter_networks_df(metadata)
+```
+
+The size of the minimum driver node set relative to the number of species in each network $n_D$ ranged between $n_D = `r round(min(c_m$n_D), 2)`$ and $n_D = `r round(max(c_m$n_D), 2)`$ (mean `r round(mean(c_m$n_D), 2)`, Figure \@ref(fig:fig-emp-controllability)).
+We found that the relative size of the minimum driver node set was not related to any of our independent variables. 
+Indeed, as determined by the AICc, the null model was the most parsimonious candidate and all variables were relatively unimportant (Supplementary Information \@ref(S-controllability-models)).
+
+```{r fig-emp-controllability, fig.width=fig_sizes()[[1]], fig.height=fig_sizes()[[1]]/2, fig.cap="Density plot ofsize of the minimum driver node set.
+The vertical dashed line indicates the meann value."}
+drake::loadd(fig_emp_controllability)
+fig_emp_controllability
+```
+
 # References

### 2018-06-09 paper/supp-info.Rmd
Complete controllability model wording
Towards #19

@@
 
-# Empirical vs. random expectation of controllability {#randomisations}
-
 # Controllability models {#controllability-models}
 
-The models were
+We constructed a set of generalised linear models with binomial error structure. 
+The response variable was the size of the minimum driver node set of the twenty empirical networks (ten invaded and ten uninvaded). 
+The independent variables evaluated were the invasion status, the network connectance, the network nestedness (NODF) the number of species, the network asymmetry (an indication of the balance between plants and pollinators) or the interaction strength asymmetry [the asymmetry on the dependences between trophic levels; @bluthgen_specialization_2007].
 
-```{r}
+```{r controllability-variable-importance}
+drake::loadd(controllability_variable_importance)
+```
+
+We fitted the full set of possible candidate models and used the Akaike Information Criterion for small sample sizes (AICc) to compare the models. 
+We found little support for any of the evaluated variables (Table \@ref(tab:table-controllabillity-model-results)). 
+We measured the relative importance of an independent variable by adding the Akaike weights (the model probabilities) of the models in which the variable was present. 
+All variables were roughly equally un-important with the Akaike weights for each of them ranging between `r round(min(controllability_variable_importance$w.plus), 3)` and `r round(max(controllability_variable_importance$w.plus), 3)` (in a scale from 0 to 1).
+
+```{r table-controllabillity-model-results, results = "asis", sanitize = FALSE}
 drake::loadd(controllability_models)
@@
                caption = "Model selection table based on the Akaike Information Criterion for small samples for candidate models of size of the minimum driver node set ($n_D$) in the empirical networks.
-There was no evidence for any of the evaluated predictors: the invasion status (inv), the network connectance (C), the network nestedness (NODF) the number of species ($n_S$) the network asymmetry ($AS_s$) or the interaction strength asymmetry ($AS_s$).
+There was no evidence for any of the evaluated predictors: the invasion status (inv), the network connectance (c), the network nestedness (NODF) the number of species ($n_S$) the network asymmetry ($AS_s$) or the interaction strength asymmetry ($AS_s$).
 Only candidate models with $\\Delta AIC < 8$ are shown.")
@@
 
+# Empirical vs. random expectation of controllability {#randomisations}
+
 # References

### 2018-06-09 paper/manuscript.Rmd
Complete figure empirical controllability with the randomisations
Close #14

@@
 
-```{r fig-emp-controllability, fig.width=fig_sizes()[[1]], fig.height=fig_sizes()[[1]]/2, fig.cap="Density plot ofsize of the minimum driver node set.
-The vertical dashed line indicates the meann value."}
+```{r fig-emp-controllability, fig.width=fig_sizes()[[1]], fig.height=fig_sizes()[[1]], fig.cap="Density plot of (a) the relative size of the minimum driver node set $n_D$ in the empirical networks.
+(b) The density distribution of the difference between the relative size of the minimum driver node set of random networks and that of empirical networks.
+We randomised either the species visitation patterns (light line), or randomised the direction of control between a species pair (dark line).
+The vertical dashed lines indicate the median values of each distribution."}
 drake::loadd(fig_emp_controllability)
-fig_emp_controllability
+
+g <- fig_emp_controllability %>%
+  purrr::map(ggplot2::ggplotGrob)
+gb <- rbind(g[[1]], g[[2]], size = "first")
+gb$widths <- grid::unit.pmax(g[[1]]$widths, g[[2]]$widths)
+grid::grid.newpage()
+grid::grid.draw(gb)
 ```

### 2018-06-09 code/fig_emp_controllability.R

@@ -1,14 +1,39 @@
-make_fig_emp_contollability <- function(controllability, metadata){
+make_fig_emp_contollability <- function(controllability, randomisations_df, metadata){
   require(ggplot2)
   d <- controllability %>% 
     filter_networks_df(metadata) 
   
-  d %>%
+  r <- randomisations_df %>%
+    filter_networks_df(metadata) %>%
+    dplyr::mutate(delta_n_D = n_D.x - n_D.y) 
+  
+  p1 <- d %>%
     ggplot(aes(x = n_D)) +
     stat_density(geom= "line", size = 0.5) +
-    geom_vline(xintercept = mean(d$n_D), linetype = 2, size = 0.25) +
-    xlab(expression(paste("", n[D], "", " - relative size of the minimum driver node set"))) +
-    base_ggplot_theme()
+    geom_vline(xintercept = median(d$n_D), linetype = 2, size = 0.25) +
+    xlab(expression(paste(n[D]))) +
+    base_ggplot_theme() +
+    labs(title = expression(paste("(a) Relative size of the minimum driver node set (", n[D], ")")))
+
+  
+  means <- r %>%
+    dplyr::group_by(randomisation) %>%
+    dplyr::summarise(delta_n_D = median(delta_n_D, na.rm = T))
+  
+  p2 <- r %>% 
+    ggplot(aes(x = delta_n_D, color = randomisation)) +
+    stat_density(geom = "line", position = position_identity(), size = 0.5) +
+    geom_vline(data = means, aes(xintercept = delta_n_D, color = randomisation), size = 0.25, linetype = 2, show.legend = F) +
+    scale_color_manual(values = c(get_color("matched"), get_color("unmatched")), 
+                       name = "", 
+                       guide = guide_legend(reverse = T), labels = c("random directions", "random interactions")) +
+    base_ggplot_theme() +
+    theme(legend.position = c(0.82,0.88), legend.background = element_rect(fill = "NA"), legend.key.size = unit(0.15, "in")) +
+    labs(title = expression(paste("(b) Difference between random and empirical ", n[D])), 
+         x = expression(paste(Delta, n[D])))
+         
+ list(p1, p2)
 }
 
-# drake::loadd(controllability, metadata)
+ # drake::loadd(controllability, metadata, randomisations_df)
+

### 2018-06-09 main.R

@@ -58,7 +58,7 @@ example_plots_plan <- drake::drake_plan(
   fig_small_network = make_small_network(networks),
   fig_input_graph = make_fig_input_graph(en_direction, en_star, en_chain), 
   fig_bidirectional = make_fig_bidirectional(en_chain), 
-  fig_emp_controllability = make_fig_emp_contollability(controllability, metadata)
+  fig_emp_controllability = make_fig_emp_contollability(controllability, randomisations_df, metadata)
 )
 
 control_capacity_testing_plan <- drake::drake_plan(

### 2018-06-09 paper/manuscript.Rmd
Minor changes in results wording

@@
 In addition, we also explored whether real networks differ in their architecture from random ones in a concerted way that could impact these results (supplementary information section \@ref(S-randomisations)).
+<!-- Expand -->
 
@@
 
-The size of the minimum driver node set relative to the number of species in each network $n_D$ ranged between $n_D = `r round(min(c_m$n_D), 2)`$ and $n_D = `r round(max(c_m$n_D), 2)`$ (mean `r round(mean(c_m$n_D), 2)`, Figure \@ref(fig:fig-emp-controllability)).
+The size of the minimum driver node set relative to the number of species in each network $n_D$ ranged between $n_D = `r round(min(c_m$n_D), 2)`$ and $n_D = `r round(max(c_m$n_D), 2)`$ (median `r round(median(c_m$n_D), 2)`, Figure \@ref(fig:fig-emp-controllability)).
 We found that the relative size of the minimum driver node set was not related to any of our independent variables. 
-Indeed, as determined by the AICc, the null model was the most parsimonious candidate and all variables were relatively unimportant (Supplementary Information \@ref(S-controllability-models)).
+Indeed the null model ($n_D \sim 1$) was the most parsimonious candidate model and all variables were relatively unimportant (based on the AICc; Supplementary Information \@ref(S-controllability-models)).
 

### 2018-06-11 paper/manuscript.Rmd
Add figure species level to manuscript
Ref #32

@@
 
-```{r fig-emp-controllability, fig.width=fig_sizes()[[1]], fig.height=fig_sizes()[[1]], fig.cap="Density plot of (a) the relative size of the minimum driver node set $n_D$ in the empirical networks.
+```{r fig-emp-controllability, fig.width=fig_sizes()[[1]], fig.height=fig_sizes()[[1]], fig.cap="Density plot of (a) the relative size of the minimum driver node set $n_D$ in the invaded (light) and uninvaded (dark) empirical networks.
 (b) The density distribution of the difference between the relative size of the minimum driver node set of random networks and that of empirical networks.
@@
 
+```{r, fig.width=fig_sizes()[[1]], fig.height=fig_sizes()[[1]], fig.cap="unfinished figure"}
+drake::loadd(fig_species_level)
+
+fig_species_level[[1]]
+```
+
+I'm thinlking just adding a graph with the control capacity and superiorness of the invasive/non invasive species as well as the glm to predict these variables and leave it there.
+
+That means that it would be necessary to modify the introduction to remove the parts that claim that centrality is not good enough to predict coextinction. 
+The justification is just that centrality might just be telling a different thing to control. 
+We then just use the "empirically known" role of invasive species to show it works?
+
 # References

### 2018-06-11 main.R

@@ -58,7 +58,8 @@ example_plots_plan <- drake::drake_plan(
   fig_small_network = make_small_network(networks),
   fig_input_graph = make_fig_input_graph(en_direction, en_star, en_chain), 
   fig_bidirectional = make_fig_bidirectional(en_chain), 
-  fig_emp_controllability = make_fig_emp_contollability(controllability, randomisations_df, metadata)
+  fig_emp_controllability = make_fig_emp_contollability(controllability, randomisations_df, metadata), 
+  fig_species_level = make_fig_species_level(sl_char_corr)
 )
 
 control_capacity_testing_plan <- drake::drake_plan(

### 2018-06-11 paper/manuscript.Rmd
Make figure control capacity
REf #32

@@
 ```{r, fig.width=fig_sizes()[[1]], fig.height=fig_sizes()[[1]], fig.cap="unfinished figure"}
-drake::loadd(fig_species_level)
+drake::loadd(fig_correlation)
+fig_correlation[[1]]
+```
 
-fig_species_level[[1]]
+```{r, fig.width=fig_sizes()[[1]], fig.height=fig_sizes()[[1]]*0.5, fig.cap="unfinished figure"}
+drake::loadd(fig_control_capacity)
+fig_control_capacity[[1]] 
 ```

### 2018-06-11 code/fig_keystonness.R

@@ -1,4 +1,4 @@
-make_fig_species_level <- function(sl_char_corr){
+make_fig_correlation <- function(sl_char_corr){
   require(ggplot2)
   order <- sl_char_corr[[1]] %>% 
     as.dist() %>%
@@ -21,7 +21,7 @@ make_fig_species_level <- function(sl_char_corr){
   p1 <- plot_df %>%
     ggplot(aes(x = Var1, y = Var2, fill = value)) +
     geom_tile(width = 0.9, height = 0.9, size = 0.25) +
-    geom_text(aes(label = round(value, 2), fontface = interesting), size = 3) +
+    geom_text(aes(label = round(value, 2), fontface = interesting), size = 2) +
     coord_equal() +
     scale_fill_gradient2(low = my_pallete()$light_orange, 
                          high = my_pallete()$light_purple, 
@@ -33,10 +33,35 @@ make_fig_species_level <- function(sl_char_corr){
     labs(title= 'Correlation between control and commonly used "keystoness" metrics', x = "", y = "")
   
   list(p1)
- 
+  
 }
 
-# drake::loadd(sl_char_corr, secondary_ext_std)
+make_fig_control_capacity <- function(sigma_phi_df, species_empirical_coov, metadata){
+  require(ggplot2)
+  p2df <- sigma_phi_df %>%
+    dplyr::inner_join(species_empirical_coov) %>%
+    filter_networks_df(metadata) %>%
+    tidyr::gather(key = "metric", value = "value", control_capacity, superior) 
+  
+  invasive <- p2df %>%
+    dplyr::filter(invasive)
+  
+  p2 <- p2df %>%
+    ggplot(aes(x = value, fill = interaction(invasive, guild))) +
+    geom_histogram(aes(y = ..count..), geom = "line", position = position_stack(), binwidth =  1/25) +
+    facet_wrap(~metric, scales = "free") +
+    # scale_y_sqrt() +
+    scale_fill_manual(values = c(my_pallete()$light_orange, my_pallete()$dark_orange, my_pallete()$light_purple),
+                      name = "", labels = c("native plants", "invasive plants", "pollinators")) +
+    base_ggplot_theme() +
+    theme(legend.position = c(1, 1),
+          legend.justification = c(1,1),
+          legend.background = element_rect(fill = "NA"), legend.key.size = unit(0.15, "in"))
+  p2
+  list(p2)
+}
+
[…]

### 2018-06-11 code/species_coovariates.R

@@ -34,3 +34,10 @@ centrality_as_df <- function(x, label){
 # delta <- 0
 # rho <- 0.01
 # interaction_matrix <- interaction_matrix_mutualism
+
+plants_or_pols <- function(x){
+  dplyr::data_frame(sp_name = igraph::V(x)$name, 
+                    guild = igraph::V(x)$type) %>%
+    dplyr::mutate(invasive = dplyr::if_else(sp_name %in% c("p_4", "p_25", "Impatiens glandulifera"), TRUE, FALSE))
+}
+

### 2018-06-11 main.R

@@ -59,7 +59,8 @@ example_plots_plan <- drake::drake_plan(
   fig_input_graph = make_fig_input_graph(en_direction, en_star, en_chain), 
   fig_bidirectional = make_fig_bidirectional(en_chain), 
   fig_emp_controllability = make_fig_emp_contollability(controllability, randomisations_df, metadata), 
-  fig_species_level = make_fig_species_level(sl_char_corr)
+  fig_correlation = make_fig_correlation(sl_char_corr), 
+  fig_control_capacity = make_fig_control_capacity(sigma_phi_df, species_empirical_coov, metadata)
 )
 
 control_capacity_testing_plan <- drake::drake_plan(
@@ -84,6 +85,7 @@ controllability_plan <- drake::drake_plan(
 )
 
 species_level_plan <- drake::drake_plan(
+  species_empirical_coov = purrr::map_df(networks, plants_or_pols, .id = "net_name"),
   species_coovariates_df = purrr::map_df(directed_networks, get_species_coov, indices = c("degree", "species strength", "betweenness", "closeness"), .id = "net_name"), 
   sigma_phi_df = purrr::map_dfr(matched_networks, get_controllability_superiorness, .id = "net_name"),
   sl_characteristics = join_sl_characteristics(sigma_phi_df, species_coovariates_df),

### 2018-06-13 paper/manuscript.Rmd
Figure keystoness uses now model predictions

@@
 
-```{r, fig.width=fig_sizes()[[1]], fig.height=fig_sizes()[[1]]*0.5, fig.cap="unfinished figure"}
+```{r fig-species-level, fig.width=fig_sizes()[[2]], fig.height=fig_sizes()[[1]], fig.cap="Control capacity and "}
 drake::loadd(fig_control_capacity)
-fig_control_capacity[[1]] 
+fig_control_capacity %>%
+    cowplot::plot_grid(plotlist = .)
 ```

### 2018-06-13 code/fig_keystonness.R

@@ -1,4 +1,4 @@
-make_fig_correlation <- function(sl_char_corr){
+make_fig_correlation <- function(sl_char_corr, sl_characteristics, metadata){
   require(ggplot2)
   order <- sl_char_corr[[1]] %>% 
     as.dist() %>%
@@ -9,58 +9,264 @@ make_fig_correlation <- function(sl_char_corr){
   
   plot_df <- sl_char_corr[[1]][order, order] %>% {
     l <- .
-    l[upper.tri(l, diag = T)] <- NA
+    # l[upper.tri(l, diag = T)] <- NA
     l
   } %>%
     reshape2::melt() %>%
     dplyr::filter(!is.na(value)) %>%
     dplyr::mutate(Var1 = factor(Var1, levels = rev(order)), 
                   Var2 = factor(Var2, levels = order), 
-                  interesting = (Var2 %in% c("superior", "control_capacity")) | (Var1 %in% c("superior", "control_capacity")), 
+                  interesting = (Var1 %in% c("superior", "control_capacity")), 
                   interesting = dplyr::if_else(interesting, "bold", "plain"))
-  p1 <- plot_df %>%
-    ggplot(aes(x = Var1, y = Var2, fill = value)) +
+  
+  labels_long <- c("closeness" = "closeness  (l)",
+                   "page_rank.nondirected" = "page rank (g)",
+                   "eigen.nondirected" = "eigen centrality (e)",
+                   "superior" = expression(bold(paste("superior node (", sigma, ")"))),
+                   "betweenness" = "betweenness (w)",
+                   "control_capacity" = expression(bold(paste("control capacity (", phi, ")"))),
+                   "degree"= "degree (k)")
+  labels_short <- c("closeness" = "l",
+                    "page_rank.nondirected" = "g",
+                    "eigen.nondirected" = "e",
+                    "superior" = expression(sigma),
+                    "betweenness" = "w",
+                    "control_capacity" = expression(phi),
+                    "degree" = "k")
+  
+p1 <- plot_df %>%
+    ggplot(aes(x = as.numeric(Var1), y = as.numeric(Var2), fill = value)) +
     geom_tile(width = 0.9, height = 0.9, size = 0.25) +
-    geom_text(aes(label = round(value, 2), fontface = interesting), size = 2) +
+    geom_text(aes(label = round(value, 2), fontface = "plain", size = interesting)) +
     coord_equal() +
     scale_fill_gradient2(low = my_pallete()$light_orange, 
[…]

### 2018-06-13 main.R

@@ -60,7 +60,7 @@ example_plots_plan <- drake::drake_plan(
   fig_bidirectional = make_fig_bidirectional(en_chain), 
   fig_emp_controllability = make_fig_emp_contollability(controllability, randomisations_df, metadata), 
   fig_correlation = make_fig_correlation(sl_char_corr), 
-  fig_control_capacity = make_fig_control_capacity(sl_characteristics, metadata)
+  fig_control_capacity = make_fig_control_capacity(species_model_cc, species_model_superior)
 )
 
 control_capacity_testing_plan <- drake::drake_plan(

### 2018-06-13 paper/manuscript.Rmd
Caption for correlation figure

@@
 
-```{r, fig.width=fig_sizes()[[1]], fig.height=fig_sizes()[[1]], fig.cap="unfinished figure"}
+```{r fig-correlogram, fig.width=fig_sizes()[[1]], fig.height=fig_sizes()[[1]], fig.cap="Mean Spearman correlation coefficients between control metrics (control capcity $\\phi$ and the likelyhood of being a superior node $\\sigma$) and centrality metrics commonly used to estimate a species' 'keystoness' (closeness centrality $l$ , betwenness $w$, eigen centrality $e$, page rank $g$ and degre $k$) in each of the networks.
+Purple and orange tiles indicate a positive correlation or negative correlation respectively."}
 drake::loadd(fig_correlation)

### 2018-06-13 main.R
Use spearman correlation

@@ -89,7 +89,7 @@ species_level_plan <- drake::drake_plan(
   species_coovariates_df = purrr::map_df(directed_networks, get_species_coov, metrics = c("degree", "species strength", "betweenness", "closeness", "eigen", "page_rank", "nested_contribution", "interaction push pull"), .id = "net_name"), 
   sigma_phi_df = purrr::map_dfr(matched_networks, get_controllability_superiorness, .id = "net_name"),
   sl_characteristics = join_sl_characteristics(sigma_phi_df, species_coovariates_df, species_empirical_coov),
-  sl_char_corr = species_level_characteristics_correlation(sl_characteristics, metadata, vars = c("control_capacity", "superior", "page_rank.nondirected", "eigen.nondirected", "degree", "betweenness", "closeness"), method = "pearson"),
+  sl_char_corr = species_level_characteristics_correlation(sl_characteristics, metadata, vars = c("control_capacity", "superior", "page_rank.nondirected", "eigen.nondirected", "degree", "betweenness", "closeness"), method = "spearman"),
   secondary_ext = all_secondary_extinctions(networks, sl_characteristics),
   secondary_ext_std = standardize_secondary_extinctions(secondary_ext, controllability, metadata),
   species_model_superior = fit_species_models(sl_characteristics, metadata, response = "superior"), 

### 2018-06-13 paper/manuscript.Rmd
Table with model results

@@
 - \externaldocument[S-]{supp-info}
+- \usepackage{multirow}
+- \usepackage[table]{xcolor}
+- \usepackage{wrapfig}
+- \usepackage{colortbl}
+- \usepackage{pdflscape}
+- \usepackage{tabu}
+- \usepackage{threeparttable}
+- \usepackage{threeparttablex}
+- \usepackage[normalem]{ulem}
+- \usepackage{makecell}
 documentclass: artikel1
@@
                       warning = FALSE)
+options(knitr.kable.NA = '')
 ```
@@
 
+```{r tab-model-selection-table}
+drake::loadd(species_model_cc, species_model_superior)
+
+cc_table <- MuMIn::model.sel(species_model_cc$fixed) %>%
+  dplyr::filter(weight > 0.01)
+su_table <- MuMIn::model.sel(species_model_superior$fixed)%>%
+  dplyr::filter(weight > 0.01)
+
+dplyr::bind_rows(cc_table, su_table) %>%
+  dplyr::select(-logLik, - AICc) %>%
+  knitr::kable("latex", 
+               col.names = c("int.", "degree", "push/pull", "nested c.", "sp. strength", "d.f.",  "$\\Delta$AICc","weight"),
+               booktabs = T, 
+               caption = "asd", 
+               row.names = F, 
+               digits = 2, 
+               escape = F) %>%
+  kableExtra::add_header_above(c("model terms" = 5, " " = 3), escape = F) %>%
+  kableExtra::kable_styling(font_size = 8) %>%
+  kableExtra::group_rows("control capacity models", 1, nrow(cc_table), escape = F) %>%
+  kableExtra::group_rows("superior/subordinate models", nrow(cc_table) + 1, nrow(cc_table) + nrow(su_table))
+```
+
 I'm thinlking just adding a graph with the control capacity and superiorness of the invasive/non invasive species as well as the glm to predict these variables and leave it there.

### 2018-06-13 paper/manuscript.Rmd
Advances in text for results section

@@
 
+```{r correlation-calculations}
+drake::loadd(sl_char_corr)
+correlations <- sl_char_corr %>% 
+  extract2("mean") %>%
+  as.data.frame() %>%
+  tibble::rownames_to_column() %>%
+  dplyr::filter(!rowname %in% c("control_capacity", "superior"))
+```
+
+The control capacity $\phi$ and the likelihood of being a superior node $\sigma$ are weakly correlated with commonly used centrality metrics. 
+Specifically, the correlation coefficient between the control capacity $\phi$ and other metrics ranged between `r round(min(correlations$control_capacity), 2)` and `r round(max(correlations$control_capacity), 2)` while the correlation coefficient between the likelyhood of being a superior node $\sigma$ and the centrality metrics ranged between `r round(min(correlations$superior), 2)` and `r round(max(correlations$superior), 2)` (Figure \@ref(fig:fig-correlogram)).
+
 ```{r fig-correlogram, fig.width=fig_sizes()[[1]], fig.height=fig_sizes()[[1]], fig.cap="Mean Spearman correlation coefficients between control metrics (control capcity $\\phi$ and the likelyhood of being a superior node $\\sigma$) and centrality metrics commonly used to estimate a species' 'keystoness' (closeness centrality $l$ , betwenness $w$, eigen centrality $e$, page rank $g$ and degre $k$) in each of the networks.
@@
 
+Both plants and pollinators were distributed across a gradient of control capacity and wether they were superior nodes or not (Figure \@ref(fig:fig-species-level)). 
+This distribution, in particular for control capacity, was independent of the degree of species. 
+Remarkably, every single invasive plant species in our dataset had both the maximum control capacity and was classified as a superior node.
+
 ```{r fig-species-level, fig.width=fig_sizes()[[2]], fig.height=fig_sizes()[[1]], fig.cap="Control capacity and "}
@@
 ```
+
+The model that best explained Although a species control capacity was not correlated to any of the centrality metrics, we found that it was a strong correlation w  Control capacity was strongly related to the nested
 

### 2018-06-14 code/fig_structural_stability.R
Structural stability figure

@@ -1,0 +1,34 @@
+make_fig_structural_stability <- function(sl_characteristics, metadata){
+  require(ggplot2)
+  p1 <- sl_characteristics %>%
+    filter_networks_df(metadata) %>%
+    dplyr::inner_join(metadata, by = "net_name") %>%
+    dplyr::group_by(net_name) %>%
+    dplyr::filter(is.finite(feasibility), 
+                  guild == "pla") %>%
+    dplyr::mutate(feasibility1 = dplyr::percent_rank(feasibility),
+                  feasibility2 = scale(feasibility), 
+                  control_capacity = control_capacity) %>%
+    ggplot(aes(x = feasibility2 , y = control_capacity)) +
+    # scale_y_log10() +
+    # geom_point() +
+    geom_smooth(aes(group = net_name), 
+                method = "glm", 
+                se = F, 
+                size =0.25, 
+                method.args = list(family = "binomial"), 
+                colour = "grey", 
+                alpha = 0.25) +
+    geom_smooth(method = "glm", 
+                se = F, 
+                size =0.5, 
+                method.args = list(family = "binomial"), 
+                colour = "black") +
+    base_ggplot_theme() +
+    labs(title = "structural stability of species removal", 
+         x = latex2exp::TeX("scaled feasibility ($\\Omega$)"), 
+         y = latex2exp::TeX("control capacity ($\\phi$)"))
+  
+  list(p1)
+
+}

### 2018-06-14 main.R

@@ -60,7 +60,8 @@ example_plots_plan <- drake::drake_plan(
   fig_bidirectional = make_fig_bidirectional(en_chain), 
   fig_emp_controllability = make_fig_emp_contollability(controllability, randomisations_df, metadata), 
   fig_correlation = make_fig_correlation(sl_char_corr), 
-  fig_control_capacity = make_fig_control_capacity(species_model_cc, species_model_superior)
+  fig_control_capacity = make_fig_control_capacity(species_model_cc, species_model_superior),
+  fig_structural_stability = make_fig_structural_stability(sl_characteristics, metadata)
 )
 
 control_capacity_testing_plan <- drake::drake_plan(

### 2018-06-14 paper/manuscript.Rmd
Structural stability figure
Move correlogram to supplementary materials

@@
 
-```{r fig-correlogram, fig.width=fig_sizes()[[1]], fig.height=fig_sizes()[[1]], fig.cap="Mean Spearman correlation coefficients between control metrics (control capcity $\\phi$ and the likelyhood of being a superior node $\\sigma$) and centrality metrics commonly used to estimate a species' 'keystoness' (closeness centrality $l$ , betwenness $w$, eigen centrality $e$, page rank $g$ and degre $k$) in each of the networks.
-Purple and orange tiles indicate a positive correlation or negative correlation respectively."}
-drake::loadd(fig_correlation)
-fig_correlation[[1]]
-```
-
 Both plants and pollinators were distributed across a gradient of control capacity and wether they were superior nodes or not (Figure \@ref(fig:fig-species-level)). 
@@
 The model that best explained Although a species control capacity was not correlated to any of the centrality metrics, we found that it was a strong correlation w  Control capacity was strongly related to the nested
+
+```{r fig-structural-stability, fig.width=fig_sizes()[[1]], fig.height=fig_sizes()[[1]]/2, fig.cap="Control capacity and "}
+drake::loadd(fig_structural_stability)
+
+fig_structural_stability[[1]]
+```
 

### 2018-06-14 paper/supp-info.Rmd
Move correlogram to supplementary materials

@@
 
+```{r fig-correlogram, fig.width=fig_sizes()[[1]], fig.height=fig_sizes()[[1]], fig.cap="Mean Spearman correlation coefficients between control metrics (control capcity $\\phi$ and the likelyhood of being a superior node $\\sigma$) and centrality metrics commonly used to estimate a species' 'keystoness' (closeness centrality $l$ , betwenness $w$, eigen centrality $e$, page rank $g$ and degre $k$) in each of the networks.
+Purple and orange tiles indicate a positive correlation or negative correlation respectively."}
+drake::loadd(fig_correlation)
+fig_correlation[[1]]
+```
+
 # References

### 2018-06-14 paper/manuscript.Rmd
Aesthetical improvements to control capacity/ superior plot

@@
 
-```{r fig-species-level, fig.width=fig_sizes()[[2]], fig.height=fig_sizes()[[1]], fig.cap="Control capacity and "}
+```{r fig-species-level, fig.width=fig_sizes()[[2]]*2/3, fig.height=fig_sizes()[[1]], fig.cap="Control capacity and "}
 drake::loadd(fig_control_capacity)
+library(ggplot2)
+fig_control_capacity[[2]] <- fig_control_capacity[[2]] +
+  theme(axis.title.y = element_blank(),
+        axis.text.y = element_blank())
+fig_control_capacity[[4]] <- fig_control_capacity[[4]] +
+  theme(axis.title.y = element_blank(),
+        axis.text.y = element_blank())
+
+# pdf("test.pdf", width =fig_sizes()[[2]]*2/3, height = fig_sizes()[[1]])
 fig_control_capacity %>%
-    cowplot::plot_grid(plotlist = .)
+    cowplot::plot_grid(plotlist = ., rel_widths = c(1.21,1), align = "h")
+# dev.off()
+
 ```

### 2018-06-14 code/fig_keystonness.R

@@ -144,11 +144,18 @@ make_fig_control_capacity <- function(species_model_cc, species_model_superior){
                   nestedcontribution_o = unscale(nestedcontribution))
   
   invasive_cc <- df_cc %>%
-    dplyr::filter(invasive) 
+    dplyr::filter(invasive)
+  
+  # df_cc1 <- expand.grid(degree = 0, 
+  #                       guild = c("pla", "pol"), 
+  #                       species.strength = 0, 
+  #                       nestedcontribution = seq(-2.5, 5, length.out = 20), 
+  #                       interaction.push.pull = 0) %>%
+  #   modelr::add_predictions(cc_model)
   
   p1 <- df_cc %>%
     ggplot(aes(x = nestedcontribution_o, y = plogis(pred))) +
-    geom_point(aes(colour = guild), shape = 21, size = 1) +
+    geom_point(aes(colour = guild), shape = 21, size = 1, alpha = 0.25) +
     # scale_x_log10() + 
     geom_smooth(aes(color = guild, fill = guild), 
                 method = "glm", 
@@ -158,8 +165,9 @@ make_fig_control_capacity <- function(species_model_cc, species_model_superior){
                 alpha = 0.2) +
     geom_point(data = invasive_cc, aes(y = plogis(pred)), 
                fill = my_pallete()$dark_orange,
-               colour = my_pallete()$light_orange, 
-               shape = 21) +
+               colour = "black", 
+               shape = 21,
+               size = 1) +
     scale_color_manual(values = c(my_pallete()$light_orange, 
                                   my_pallete()$light_purple), 
                        name = "", 
@@ -171,14 +179,16 @@ make_fig_control_capacity <- function(species_model_cc, species_model_superior){
     base_ggplot_theme() +
     labs(title = "(a)", 
          x = "contribution to nestedness", 
-         y = latex2exp::TeX("control capacity ($\\alpha$)")) +
+         y = latex2exp::TeX("control capacity ($\\phi$)")) +
     theme(legend.position = c(1, 0),
           legend.justification = c(1,0),
-          legend.background = element_rect(fill = "NA"), legend.key.size = unit(0.15, "in"))
+          legend.background = element_rect(fill = "NA"), 
+          legend.key.size = unit(0.15, "in"), 
+          plot.margin = unit(c(0.5, 0.5, 0.5, 0.5), "mm")) 
   
   p2 <- df_cc %>%
[…]

### 2018-06-14 paper/manuscript.Rmd
Remove unused latex packages

@@
 - \usepackage{multirow}
-- \usepackage[table]{xcolor}
-- \usepackage{wrapfig}
-- \usepackage{colortbl}
-- \usepackage{pdflscape}
 - \usepackage{tabu}
-- \usepackage{threeparttable}
-- \usepackage{threeparttablex}
-- \usepackage[normalem]{ulem}
 - \usepackage{makecell}

### 2018-06-15 paper/manuscript.Rmd
Amend Introduction
Close #35

@@
 A major goal in ecology is to understand the roles played by different species in the biotic environment.
-Within community ecology, a complex-systems approach has led to the development of a variety analytical and simulation tools with which to compare and contrast the roles of species embedded in a network of interactions [@bascompte_assembly_2009; @stouffer_evolutionary_2012].
-<!-- Add some older references as this is a long-standing research line; see the 2012 paper for some if you'd like. -->
+Within community ecology, a complex-systems approach has led to the development of a variety analytical and simulation tools with which to compare and contrast the roles of species embedded in a network of interactions [@guimera_cartography_2005; @bascompte_assembly_2009; @stouffer_evolutionary_2012; @coux_linking_2016].
 A particularly relevant dimension of any species' role is its ability to alter the abundance of other species in the community—since changes of this nature impact ecosystem function and biodiversity, and might have knock-on effects on other processes and services.
-This ability is often referred to as a species' "keystoneness" [refmissing].
+This ability is often referred to as a species' "keystoneness" [@mills_keystone-species_1993].
 
-A significant proportion of the network tools used to estimate species roles in this context rely on the assumption that there is a link between a given species' centrality—a relative ranking of its importance that stems from social network research—and its ability to alter the abundances of other species.
-Taken at face value, the basis of this assumption is reasonably clear: a major justification for representing ecological communities as networks is the idea that the abundance of a species depends on the abundance of its neighbours (those species with which it interacts) and, by extension, the abundance of its neighbours' neighbours, and so on.
+A significant proportion of the network tools used to estimate species roles in this context rely on the calculation of a species' centrality—a relative ranking of its importance that stems from social network research [@noah_e._friedkin_theoretical_1991].
+Generally speaking, central species tend to be present in more food chains, are better connected, and have broader niches.
+Centrality metrics have been shown to be useful tools to rank species in regards to their risk of extinction or the potential secondary extinctions after the species is lost [@dunne_network_2002; @kaiser-bunbury_robustness_2010].
+Although there are some differences among centrality metrics—as each of them emphasizes a different aspect of a species' interaction patterns—they all tend to be correlated with the way species participate in the network's food chains [@jordan_quantifying_2007].
+Because of this property, centrality metrics have been often used to identify keystone species.
+
+This relationship between centrality and keystoneness relies on an important assumption. 
+That that there is a link between a given species' centrality and its ability to alter the abundances of other species. 
+The basis of this assumption is reasonably clear: a major justification for representing ecological communities as networks is the idea that the abundance of a species depends on the abundance of its neighbours (those species with which it interacts) and, by extension, the abundance of its neighbours' neighbours, and so on.
 By definition, more central species are better connected and hence should be more likely to affect the abundance of other species in the network.
 
-<!-- Beware that the paragraph above could rub some readers/reviewers (those that believe in the usefulness of centrality) the wrong way. -->
+Despite being conceptually intuitive, the relationship between centrality and keystoneness is largely phenomenological. 
+<!-- Daniel: I'm struggling to find an example of this idea. Does anything come to your mind? -->
+Often, dramatic changes in ecosystem functioning can also occur without complete removal of a species. 
+Hence, we expect the usefulness of centrality to diminish as we move beyond species removal towards understanding how species relate to the state and stability of the ecosystem. 
+Particularly so, when the state of an ecosystem is underpinned by more than a single species. 
+As a result, community ecology could arguably benefit from an alternative more mechanistically-grounded approach to understand how species affect each other's abundance.
 
-<!-- I believe it should be 'keystoneness' and not 'keystoness'. I've tried to correct all, but please check this. -->
-
-<!-- I didn't do it, but I would think about joining the text below (up to "more mechanistically-grounded") with the above to make a single paragraph. It'd be long, but the thoughts flow well. -->
-
-Though conceptually intuitive, the relationship between centrality and keystoneness is largely phenomenological. 
-On one hand, there is more than a dozen indices of centrality used in ecology. 
-Choosing a particular metric can be a difficult task, especially because to date there are no clear methods to determine the suitability of an index to a particular application.
-<!-- I feel like the question of there being so many centralities distracts from the main line of thinking.
-You could arguably emphasize the phenomenological piece better (with an example?) and jump straight to the sentence below this comment.
--->
-Furthermore, recent studies have shown that definitions of keystoneness based on centrality might not adequately predict the cascading extinctions keystone species are usually associated to. 
-As a result, community ecology could arguably benefit from an alternative, more mechanistically-grounded, approach to understand how species affect each other's abundance.
-
-Species abundances are also influenced by the specific dynamic relationships between nodes and the mechanisms of self-regulation; however, community and population dynamics can be modelled in innumerable ways, and empirical support for one versus another is often still ambiguous.
-The alternative approach should therefore acknowledge ecosystem dynamics, but without being overly dependent on the particular choices of how they are characterised.
+Species abundances (and consequently the state of the community) are influenced by both the species interactions and the specific dynamic relationships between nodes and the mechanisms of self-regulation.
+However, community and population dynamics can be modelled in innumerable ways, and empirical support for one versus another is often still ambiguous. 
+The alternative approach should, therefore, acknowledge ecosystem dynamics, but without being overly dependent on the particular choices of how they are characterised.
 Among the various possibilities, *control theory* appears to be a strong candidate [@isbell_human_2013]. 
@@
 Unlike centrality indices, however, this link is not based on a priori assumptions between network metrics and keystoneness but is instead based on well-established advances in both dynamical and complex-systems theory.
-<!--STOUFFER: Are we shooting ourselves in the foot since this isn't entirely true?
-That is, see comments from ELE about linearity and otherwise.
-CAGUA: How about this modified phrasing?
-DBS: I approve.
-;)-->.
 
-Despite the apparent overlap, the concepts and approaches of control theory are not yet commonly applied in an ecological context. 
-Possibly, this is in part because research on the control of complex networks is generally more concerned with the state of the system as a whole. 
-This is, in contrast with the interest in ecological roles, where the focus is on the nodes that compose the network.
 At its fundamental level, control theory first determines whether a system is controllable or not; that is, it asks if a system can be driven to a desired state within a finite amount of time. 
 Although the controllability of a network is a whole-system property, it has been recently shown that asking for the controllability of a complex-system is equivalent to finding a particular set of nodes: the set with which is possible to control the state of the whole network.
-Notably, this set of nodes is not always unique for a given network.
+Notably, control theory is consistent with the observation that to change the state of a network, more than a ranking, we need a set of nodes.
+Importantly, this set of nodes is not always unique for a given network.
 This implies that an examination of the distinct sets provides a means to connect nodes with its *general* ability to modify the system to which they belong.
-
-<!-- I feel like the paragraph above is trying to tell me two things and does neither very clearly.
-My gut tells me that it could probably be improved by removing the first sentence and worrying less about why it hasn't but ways in which the application to ecology could be improved.
-Does that make sense?
--->
 
@@
 This choice thus offers us an opportunity to explicitly contrast our theoretical observations with empirical evidence.
-With these network, we first ask whether there are differences between the controllability of invaded and uninvaded networks.
-This question is motivated by in the difficulties commonly encountered with invasive-species eradication and ecosystem restoration [@woodford_confronting_2016].
+With these networks, we first ask whether there are differences between the controllability of invaded and uninvaded networks. 
+This question is motivated by the difficulties commonly encountered with invasive-species eradication and ecosystem restoration [@woodford_confronting_2016].
 <!--STOUFFER: I'd remove the grounded in.... stuff, but that's just me.  CAGUA: I don't like it either. I tried removing but then it feels like this question is coming out of the blue.-->
@@
 We ask—from a control-theoretic perspective—whether there are key differences between species in the role they play at driving the population of other members of the community and identify the ecological factors related to these differences.
+This allows us to identify species that are critical to changes in the ecosystem state and show that they have a larger than expected impact on the structural stability of the community. 
 Finally, we compare the proposed approach to current methods based on species centrality and show how these methods are indeed valuable but ultimately paint a limited picture in regards to the dynamic "keystoneness" of a species.

### 2018-06-17 paper/manuscript.Rmd
Update and review methods
Close #27

@@
 The structure of all these communities was defined by the pollinator visitation frequency, which has been shown to be an appropriate surrogate for interspecific effects in pollination networks [@vazquez_interaction_2005; @bascompte_asymmetric_2006].
-Full details about the empirical networks, the implications of using visitation frequency to quantify the strength of the associations, and the sensitivity of the control-theoretic approach to undersampling of the interactions can be found in the supplementary information section \@ref(S-empirical-networks), XX, and XX.
+Full details about the empirical networks can be found in the Supporting Information Section \@ref(S-empirical-networks).
 
@@
 Previous research has shown that mutualistic interactions are often highly asymmetric in natural communities; in other words, if a plant species is largely dependent on a pollinator species, that pollinator tends to depend rather weakly on the plant (and vice versa).
-We, therefore, create a directed link between species *i* and *j* when $d_{ij}-d_{ji} \geq 0$ to establish the most likely direction of control between a species pair (Figure \@ref(fig:fig-example-networks)a).
-<!-- The sentence above is slightly ambiguous. Shouldn't it say "create a directed link from species *i* to species *j*"? -->
+We, therefore, create a directed link from species *i* to species *j* when $d_{ij}-d_{ji} \geq 0$ to establish the most likely direction of control between a species pair (Figure \@ref(fig:fig-example-networks)a).
 Sometimes there is no observed asymmetry between species pairs ($d_{ij}=d_{ji}$), and we cannot infer a dominant  direction of control. 
-When this occurs, we deem both species to be equally likely to affect each other and create two directed links between them, one from *i* to *j* and another from *j* to *i*. 
+When this occurs, we deem both species to be equally likely to affect each other and form a reciprocal interaction between them, this is a link from *i* to *j* and another from *j* to *i*. 
 By basing the direction of the links on the asymmetry of their dependence, we are able to generate a network that is consistent with the dynamics of the community while satisfying the requirements of structural controllability.
+That allow us to calculate the controllability of the networks and investigate whether there are differences between invaded and uninvaded communities.
 
@@
 
-After constructing the directed network, we can now calculate the controllability of the different networks and investigate whether there are differences between invaded and uninvaded communities.
-
-<!-- The sentence above needs a paragraph to belong to. It's too lonely. Seriously. -->
-
 ## Controllability
@@
 -->
-A simple dynamic system can be described by $\frac{dx}{dt} = Ax + Bu(t)$, where the change of its state over time ($\frac{dx}{dt}$) depends on its current state *x* (for example, the species' abundances), an external time-varying input *u(t)* (the control signal), and two matrices *A* and *B*, which encode information about the network structure and how species respond to external inputs, respectively.
+<!-- FDO: What about now Daniel? -->
+A simple version of such a system can be described by $\frac{dx}{dt} = Ax + Bu(t)$, where the change of its state over time ($\frac{dx}{dt}$) depends on its current state *x* (for example, the species' abundances), an external time-varying input *u(t)* (the control signal), and two matrices *A* and *B*, which encode information about the network structure and how species respond to external inputs, respectively.
 In classic control theory, determining wether this system is controllable can be achieved by checking that its controllability matrix $R= [ \begin{matrix}B & AB & A^{2}B & ...& A^{n-1}B\end{matrix} ]$ has full rank.
@@
 Here we use an approach based on the structural controllability theorem [@lin_structural_1974], which assumes that we are confident about which elements of *A* and *B* have either non-zero or zero values (there is an interaction or not), but that we less sure about the precise magnitude of the non-zero values.
-Using this structural approach we can find out the controllability of a system under almost all non-zero parameter realisations.
-Structural controllability also has a graphical interpretation that allows us to translate the control problem into a topological one: a network is controllable if there are no inaccessible nodes—nodes without incoming links—or dilations—*expansions* of the network (Figure \@ref(fig:fig-example-networks)b; Supplementary Information section \@ref(S-structural-controllability)).
+Using this structural approach we can find out the controllability of a system for every non-zero realisations of the parameters.
+An intuitive way to understand structural controllability is by looking at its graphical interpretation: from a topological perspective a network is structurally controllable if there are no inaccessible nodes—nodes without incoming links—or dilations—*expansions* of the network (Figure \@ref(fig:fig-example-networks)b; Supporting Information Section \@ref(S-structural-controllability)).
 <!-- The last sentence of the paragraph above sticks out a bit. -->
+<!-- I rephrased it the last couple of sentences, hopefully it flows better now -->
 
@@
 The key is to note that the fundamental conditions of structural controllability imply that there is a one-to-one relationship between *superior* and *subordinate* nodes just like the one-to-one relationship between jobs and applicants (Figure \@ref(fig:fig-example-networks)b, bottom left).
-We thus use the maximum-matching algorithm to find an optimal pairing of superior and subordinate nodes in a manner consistent with the controllability conditions (supplementary information section \@ref(S-one-maximum-matching)).
+We thus use the maximum-matching algorithm to find an optimal pairing of superior and subordinate nodes in a manner consistent with the controllability conditions (Supporting Information Section \@ref(S-one-maximum-matching)).
 Given the result, we can further decompose the matching into a set of paths that reveal how a control signal can flow across the links in a network to reach every node that composes it. 
@@
 This simple metric provides a general indication of how difficult controlling a network might be, as systems that require a large number of external inputs to be fully controlled are intuitively more difficult or costly to manage.
+For instance, achieving full control in a "network" in which species do not interact at all is relatively difficult as we would require an intervention for every single species. 
+Conversely, the structure of a linear trophic chain can be harnessed to achieve full control using just one intervention targeted the top species; the control signal would then cascade through the trophic levels and reach other species in the community.
 Specifically, drawing from the structural-controllability literature, we use the size of the minimum driver node set relative to the total number of nodes $n_D = \frac{D}{N}$ as a measure of the extent to which the network structure can be harnessed to control the community.
@@
 <!-- Would the two sentences below work better after the "Finding out exactly how difficult..." sentence? -->
-For instance, achieving full control in a "network" in which species do not interact at all is relatively difficult as we would require an intervention for every single species. 
-Conversely, the structure of a linear trophic chain can be harnessed to achieve full control using just one intervention targeted the top species; the control signal would then cascade through the trophic levels and reach other species in the community.
+<!-- I moved it to a different place where I think flows better -->
 
-After finding the minimum driver node set in each of our networks, we want to test whether invasion status or other predictors are correlated to this metric of controllability. 
-We, therefore, use a set of generalised linear models (with binomial error structure) to investigate the effect of invasion status while also including covariates related to species richness, since one might naively expect to see a negative relationship between richness and controllability [@menge_indirect_1995].
-These covariates included the total number of species, plant richness, pollinators richness, the ratio of plant to pollinator richness, the link density (connectance), and the study site (as a two-level factor).
-In addition, we also explored whether real networks differ in their architecture from random ones in a concerted way that could impact these results (supplementary information section \@ref(S-randomisations)).
-<!-- Expand -->
+After finding the minimum driver node set in each of our networks, we wanted to test whether invasion status or other predictors are correlated to this metric of controllability. 
+We, therefore, use a set of generalised linear models (with binomial error structure). 
+The response variable was the size of the minimum driver node set $n_D$ of the twenty empirical networks (ten invaded and ten uninvaded). 
+The independent variables evaluated were the invasion status, the network connectance, the network nestedness (NODF) the number of species [since one might naively expect to see a negative relationship between richness and controllability; @menge_indirect_1995], the network asymmetry (an indication of the balance between plant and pollinator diversity), and the interaction strength asymmetry [the asymmetry on the dependences between trophic levels; @bluthgen_specialization_2007].
+Models were compared using the Akaike Information Criterion for small sample sizes (AICc).
+
+In addition, we also explored whether real networks differ in their architecture from random ones in a concerted way that could impact these results. 
+Specifically we used two null models each with 99 randomisations per network. 
+In the first, we followed @vazquez_species_2007 and maintained the connectance of the network but randomised the visits across species such that the species-specific relative probabilities of interactions were maintained; we then calculated the direction of control and the corresponding size of the minimum driver node set.
+For the second null model, we used the empirical directed network and randomly shuffled the direction of control between a species pair.
 
@@
 
-To calculate a species control capacity $\phi$, we need to enumerate all possible maximum matchings (we detail the algorithm to find all maximum matchings in the Supplementary Information section \@ref(S-all-maximum-matching)).
+To calculate a species control capacity $\phi$, we need to enumerate all possible maximum matchings (we detail the algorithm to find all maximum matchings in the Supporting Information Section \@ref(S-all-maximum-matching)).
 However, enumerating all maximum matchings is extremely expensive from a computational perspective—a network with a couple dozen nodes could be controlled with several hundred million unique matchings.
-To solve this problem, we employ a recently-developed algorithm that reveals the control correlations between the nodes in the graph using considerably less computational resources [@zhang_input_2016, Supplementary Information section \@ref(S-input-graph)].
+To solve this problem, we employ a recently-developed algorithm that reveals the control correlations between the nodes in the graph using considerably less computational resources [@zhang_input_2016, Supporting Information Section \@ref(S-input-graph)].
 Using this algorithm, we are able to identify species that are possible control inputs—those that belong to the minimum driver node set in at least one of the possible control configurations. 
@@
 While unmatched nodes correspond to those that should be influenced with an external control input, superior nodes correspond to those that influence other species internally. 
-Conveniently, with the exception of some pathological cases<!--expand or remove?-->, superior nodes always play this role across every control configuration, and therefore knowing one maximum matching provides enough information on whether a species is likely to play an important role at influencing the abundance of other species or not.
+Conveniently, unlike the minimum driver node set, superior nodes are the same for all control configurations and so in a network without reciprocal links (see below) the probability that a node is superior $\sigma$ is either 1 or 0.
 <!--The end of this paragraph seems to just restate the end of the previous paragraph.
 What new info should I feel like I've gained but aren't?-->
+<!-- You never formally define sigma. -->
+<!-- CHanged wording to make it simpler and define sigma at the same time -->
 
-<!-- You never formally define sigma. -->
+We calculated the species control capacity $\phi$ and the probability of being a superior node $\sigma$ for each species in our networks.
+In the networks that contained reciprocal links (because there was not assymetry in the dependences of a species pair), we averaged a species' $\phi$ and $\sigma$ across every possible "non-reciprocal" realisation of the network (more details can be found in the Supporting Information Section \@ref(S-reciprocal-links)).
+We then examined how species-level structural properties were related to these two variables using two sets of generalised mixed-effects models with binomial error structure. 
+As explanatory variables in the fixed component we included four variables. 
+First, the species contribution to nestendess, which has been proposed as a key feature that promotes stability and robustness in mutualistic networks [@saavedra_strong_2011]. 
+Second, the visitation strength (the sum of a species' interactions), which quantifies the strength of a species associations and is indirectly related to its abbundance [@poisot_comparative_2012]. 
+Third, the direction of assymetry which quantifies the net balance in dependencies, this is it indicates if a species affects other species more than what they affect it or not [@vazquez_species_2007].
+Fourth, to account for the centrality of a species we included degree as the fourth fixed effect. 
+To facilitate comparison between variables, all four variables were scaled to have a mean of zero and a standard deviation of one. 
+To identify the models that were best supported by the data we first determined the most parsimonious random structure using the AICc. 
+Specifically we evaluated a random intercept for observations grouped by the study site, and a intercept and slope for the contribution to nestedness, visitation strength and assymetry grouped by the trophic guild (plant or pollinator).
+After identifying the most likely random structure we ranked models from all possible fixed effects combinations using the AICc weight.
+The relative importance of variables was then assessed by looking at both their effect sizes in the top ranked models and the cummulative weight of the models in which they are present.
 
-To examine whether any species-level structural properties could predict a species control capacity $\phi$ and the likelihood of being a superior node $\sigma$, we calculated these properties for each of our networks.
-In the networks that contained reciprocal links (because there was not assymetry in the dependences of a species pair), we averaged a species' $\phi$ and $\sigma$ across every possible "non-reciprocal" realisation of the network (more details can be found in the Supplementary Information section \@ref(S-reciprocal-links)).
-*TODO: Still need to decide how to do this and how to compare traditional centrality metrics to the new control based ones.
-Will probably base the comparison on stability/feasibility metrics or/and on coextinction of species groups.*
-<!-- Do you really think there is enough time left to test these things in anything but a correlational fashion? -->
+Some species have a control capacity $\phi = 1$. 
+These species are critical to control community because they are part of the minimum driver node set in every control scenario. 
+In other words, it is not possible to change the state of the community to a desired state without managing the abundance of these species. 
+We anticipate that these species have a disproportionally large impact on the community dynamics. 
+Therefore, we determined the critical species in each of the networks and investigated wether they have a larger than average impact on the stable coexistence of species in the community. 
+This property of promoting stable coexistence is called structural stability [@rohr_structural_2014]. 
+Mathematically it is denoted by the letter $\Omega$ and represents the size of the parameter space (growth rates, carrying capacities) under which all speces can sustain positive abundances [@saavedra_nested_2016].
+The contribution of species *i* to stable coexistence, can be estimated by calculating the structural stability of the community when the focal species *i* is removed. 
+We then used a t-test to compare the contribution to stable coexistence of critical and non-critical species. 
+More details about the calculation of structural stability can be found in the Supporting Information Section \@ref(S-structural-stability).
+
+Finally, we wanted to understand how the control capacity $\phi$ and the probability of being a superior node $\sigma$ is related to merics of keystoness based on centrality. 
+To do that, for each network, we calculated the Spearman correlation matrix between these two variables and some centrality metrics commonly used to identify keystone species. 
+Namely degree, betweenness, eigen centrality, page rank, and closeness centrality.
+
+## Testing assumptions
+
+Just like the centrality metrics, the information obtained by applying structural controllability depends on the ability of the network to accurately represent the ecological community. 
+We tested the sensitivity of our approach to two fundamental assumptions. 
+First we tested that visitation is an appropiate proxy to infer interspecific effects. 
+To do that we compared the results obtained using visitation, pollinator efficiency, and pollinator importance as alternative measures in a dataset that lacked invasive species [@neeman_framework_2009; @ballantyne_constructing_2015; more details in the Supporting Information Section \@ref(S-visitation-as-proxy)].
+Second, because interspecific dependencies depend on the network topology and consequently on the accurate sampling of interactions, we tested the robustness of structural controllability to the undersampling of interactions.
+To do that we compared the results obtained when using the full network and when randomly removing interactions preferentialy from the weakest links in the network. 
+This effectively removed the rare interactions from the networks (more details in the Supporting Information Section \@ref(S-undersampling)).
 

### 2018-06-17 paper/supp-info.Rmd
Add structural stability section in supp info

@@
 
+# Structural stability {#structural-stability}
+
+We follow @rohr_structural_2014 and @saavedra_nested_2016 to calculate the structural stability of the empirical networks. 
+We first calculate the stability condition $\hat{\gamma}$ using all species in the network. 
+To simplify the calculations we assummed that there is no mutualistic trade off, and a mean field interspecific competition of $\rho = 0.01$ [@saavedra_nested_2016]. 
+To calculate the contribution to stable coexistence of a given species, we removed the focal species from the network and then calculated the corresponding structural feasibility $\Omega$ for a level of mutualism equal to the stability condition found previously.
+The choice of the parameters, specifically the interspecific competition $\rho$ had only a small impact on the relative contribution of species to stable coexistence (Figure \@ref(fig:fig-rho-sensitivity)a).
+
+In addition, the interspecific competition had a minor impact on our result that indicates that critical species (those with $\phi = 1$) have a larger than average contribution to stable coexistence (Figure \@ref(fig:fig-rho-sensitivity)b).
+
+```{r fig-rho-sensitivity, fig.width=fig_sizes()[[2]], fig.height=fig_sizes()[[1]]/2, fig.cap="Spearman correlation coefficient of the contribution to stable coexistence of species.
+Grey lines indicate the correlation coeficient for each of the twenty empirical networks.
+The solid black line indicates the median value."}
+drake::loadd(fig_rho_sensitivity)
+fig_rho_sensitivity %<>% add_internal_margins()
+cowplot::plot_grid(plotlist = fig_rho_sensitivity, ncol = 2, align = "h")
+```
+
 # Controllability models {#controllability-models}

### 2018-06-17 paper/manuscript.Rmd
Controllability section in results

@@
 ```{r controllability}
-drake::loadd(controllability, metadata)
+drake::loadd(controllability, metadata, randomisations_test)
 c_m <- controllability %>% 
@@
 
-The size of the minimum driver node set relative to the number of species in each network $n_D$ ranged between $n_D = `r round(min(c_m$n_D), 2)`$ and $n_D = `r round(max(c_m$n_D), 2)`$ (median `r round(median(c_m$n_D), 2)`, Figure \@ref(fig:fig-emp-controllability)).
-We found that the relative size of the minimum driver node set was not related to any of our independent variables. 
-Indeed the null model ($n_D \sim 1$) was the most parsimonious candidate model and all variables were relatively unimportant (based on the AICc; Supplementary Information \@ref(S-controllability-models)).
+The size of the minimum driver node set relative to the number of species in each network $n_D$ ranged between $n_D = `r round(min(c_m$n_D), 2)`$ and $n_D = `r round(max(c_m$n_D), 2)`$ (median `r round(median(c_m$n_D), 2)`, Figure \@ref(fig:fig-emp-controllability)a).
+We found that the relative size of the minimum driver node set was not related to any of the independent variables we evaluated. 
+Indeed the null model ($n_D \sim 1$) was the most parsimonious candidate model and all variables were relatively unimportant (based on the AICc; Supporting Information Section \@ref(S-controllability-models)).
+The $n_D$ of empirical networks did not differ to that of a null model that roughly preserved the degree distribution and fully preserved the network connectance ($p = `r sprintf('\\num{%s}', format(randomisations_test$interactions$p.value, digits = 2))`$; Figure \@ref(fig:fig-emp-controllability)b).
+However empirical networks had a larger $n_D$ than null models that preserved the interactions but shuffled the direction of control of the empirical network ($p = `r sprintf('\\num{%s}', format(randomisations_test$directions$p.value, digits = 2))`$).
 

### 2018-06-17 paper/manuscript.Rmd
Models of control capacity / superior
Close #32

@@
 - \externaldocument[S-]{supp-info}
+- \usepackage{siunitx}
 - \usepackage{multirow}
-- \usepackage{tabu}
 - \usepackage{makecell}
+- \usepackage{threeparttablex}
 documentclass: artikel1
@@
                       warning = FALSE)
-options(knitr.kable.NA = '')
+options(knitr.kable.NA = '---')
 ```
@@
 
-```{r correlation-calculations}
-drake::loadd(sl_char_corr)
-correlations <- sl_char_corr %>% 
-  extract2("mean") %>%
-  as.data.frame() %>%
-  tibble::rownames_to_column() %>%
-  dplyr::filter(!rowname %in% c("control_capacity", "superior"))
+The models that best explained a species control capacity $\phi$, had a random intercept and slope for the species asymmetry grouped by guild (plants or pollinators; Table \@ref(S-tab:tab-model-output-control-capacity)).
+Contribution to nestedness was the most important variable followed by visitation strength (Table \@ref(tab:tab-model-selection-table), \@ref(S-tab:tab-var-importance)). 
+Species with large contribution to nestedness and large visitation strength were more likely to have a large control capacity (Figure \@ref(fig:fig-species-level)a and b). 
+For the probability of being a superior node $\sigma$, the most parsimonuous models did not include any random effect (Table \@ref(S-tab:tab-model-output-superior)). 
+The most important variables were the species asymmetry and the visitation strength (Table \@ref(tab:tab-model-selection-table), \@ref(S-tab:tab-var-importance)). 
+Specifically, species with a positive asymmetry (this is they affect their partners more than what their parners affect them), and with a large visitatin strength were more likely to be superior nodes (Figure \@ref(fig:fig-species-level)c and d).
+Furthermore, degree was positively, but only weakly asociated to both control capacity and the probability of being a superior node. 
+Remarkably, many species with a low degree, especially pollinators attained a large control capacity in their communities \@ref(S-fig:fig-species-models-degree).
+
+```{r tab-model-selection-table}
+drake::loadd(species_model_cc, species_model_superior)
+
+cc_table <- MuMIn::model.sel(species_model_cc$fixed) %>%
+  dplyr::filter(weight > 0.01)
+su_table <- MuMIn::model.sel(species_model_superior$fixed)%>%
+  dplyr::filter(weight > 0.01)
+
+dplyr::bind_rows(cc_table, su_table) %>%
+  dplyr::select(-logLik, - AICc) %>%
+  knitr::kable("latex", 
+               col.names = c("int.", "deg.", "asy.", "nes.", "str.", "d.f.",  "$\\Delta$AICc","weight"),
+               booktabs = T, 
+               caption = "Selection table of the generalised mixed effect models of control capacity $\\phi$ and the probability of being a superior node $\\sigma$.
+Only models with a weight larger than 0.01 are shown.
+All variables were scaled and so the effect sizes are comparable.",
+               row.names = F, 
+               digits = 2, 
+               escape = F) %>%
+  kableExtra::add_header_above(c("effect sizes" = 5, " " = 3), escape = F) %>%
+  kableExtra::kable_styling(font_size = 8) %>%
+  kableExtra::group_rows("control capacity models", 1, nrow(cc_table)) %>%
+  kableExtra::group_rows("superior probability models", nrow(cc_table) + 1, nrow(cc_table) + nrow(su_table)) %>%
+  kableExtra::footnote(general = "intercept (int), degree (deg), asymmetry (asy), visitation strength (str).", 
+                       general_title = "Terms: ", 
+                       footnote_as_chunk = TRUE, 
+                       threeparttable = TRUE)
 ```
 
-The control capacity $\phi$ and the likelihood of being a superior node $\sigma$ are weakly correlated with commonly used centrality metrics. 
-Specifically, the correlation coefficient between the control capacity $\phi$ and other metrics ranged between `r round(min(correlations$control_capacity), 2)` and `r round(max(correlations$control_capacity), 2)` while the correlation coefficient between the likelyhood of being a superior node $\sigma$ and the centrality metrics ranged between `r round(min(correlations$superior), 2)` and `r round(max(correlations$superior), 2)` (Figure \@ref(fig:fig-correlogram)).
-
-Both plants and pollinators were distributed across a gradient of control capacity and wether they were superior nodes or not (Figure \@ref(fig:fig-species-level)). 
-This distribution, in particular for control capacity, was independent of the degree of species. 
-Remarkably, every single invasive plant species in our dataset had both the maximum control capacity and was classified as a superior node.
-
-```{r fig-species-level, fig.width=fig_sizes()[[2]]*2/3, fig.height=fig_sizes()[[1]], fig.cap="Control capacity and "}
+```{r fig-species-level, fig.width=fig_sizes()[[2]]*2/3, fig.height=fig_sizes()[[1]], fig.cap="Relationship between the most important variables in the models of control capacity (a, b) and the probability of being a superior node (c, d).
+The plots show the values predicted by most parsimonious model for each response variable.
+The model for control capacity include a random effect for the trophic guild , while the model of superior probability does not include any random effect that distinguish between plants and pollinators.
+The invasive species are depicted with solid orange circles."}
 drake::loadd(fig_control_capacity)

### 2018-06-17 paper/supp-info.Rmd
Plot mean line on top

@@
 
+# Impact of visitation {#visitation-as-proxy}
+
+Visitation frequency has been shown to be an appropriate surrogate for inter-specific effects in pollination networks [@vazquez_interaction_2005; @bascompte_asymmetric_2006]. 
+Nevertheless visitation is not equivalent to pollen deposition and might be insufficient to reflect the dependences of plants on animals and vice versa [@alarcon_congruence_2010; @king_why_2013]. 
+We therefore investigated the effect of calculating the dependences using visitation or pollination effectiveness and importance---two metrics more proximate to plant reproductive success.
+We did this by comparing *(i)* the size of the minimum driver node set $n_D$ of the community, *(ii)* the species' control capacity and, *(iii)* the species' probability of being a superior node. 
+To do this, we used data collected by @ballantyne_constructing_2015 from a low diversity pollination community at a dry lowland heathland in Dorset, UK  (50° 43.7'N 2° 07.2'W). 
+First, deposition networks were quantified using the mean single visit deposition---the number of conspecific pollen grains effectively deposited on a virgin stigma during a single visit by a particular animal [@neeman_framework_2009; @king_why_2013; @ballantyne_constructing_2015].
+Second, visitation networks were constructed by counting the visits to flowers during Single Visit Depositions. 
+Finally, pollinator importance networks were constructed as the product of pollinator efficiency and visit frequency.
+
+```{r}
+drake::loadd(controllability, metadata)
+bal_nd <- controllability %>%
+  filter_networks_df(metadata, desired_ntw = "ballantyne") %>% {
+    list(vis = dplyr::filter(., net_name == "bal_vis")$n_D,
+         imp = dplyr::filter(., net_name == "bal_imp")$n_D,
+         eff = dplyr::filter(., net_name == "bal_eff")$n_D)
+  }
+```
+
+At a network scale the driver-node density $n_D$ was consistent among the three weighting schemes (`r round(bal_nd$eff, 2)` for deposition, `r round(bal_nd$vis, 2)` for the visitation, and `r round(bal_nd$imp, 2)` for the pollinator-importance network, respectively).
+The choice of weighting can also have an impact on at the species level.
+Therefore we calculated $\phi$ and $\sigma$ and calculated it's correlation among all three weighting schemes.
+Although visitation and efficiency (pollen deposition) produce moderately different results, we found a very strong agreement between the order produced by visitation and importance which is arguably a more accurate metric of interspecific effects (Table \@ref(tab:tab-asumption-visitation)).
+
+```{r tab-asumption-visitation}
+drake::loadd(visitation_importance_agreement)
+
+visitation_importance_agreement %>%
+  purrr::map(as.data.frame) %>%
+  purrr::map(tibble::rownames_to_column, var = "net") %>%
+  do.call(dplyr::bind_rows, .) %>%
+  dplyr::mutate(net = pretty_net_names(net)) %>%
+  knitr::kable("latex", 
+               digits = 2, 
+               row.names = F, 
+               col.name = c("", pretty_net_names(names(visitation_importance_agreement[[1]]))), 
+               booktabs = T,
+               linesep = "", 
+               caption = "Spearman correlation coefficient matrix between the control capacity and the probability obtained by weighting links by the visitation, pollinator efficiency and pollinator importance.") %>%
+  kableExtra::kable_styling(font_size = 8) %>%
+  kableExtra::group_rows("control capacity", 1, nrow(visitation_importance_agreement[[1]])) %>%
+  kableExtra::group_rows("superior probability", nrow(visitation_importance_agreement[[1]]) + 1, nrow(visitation_importance_agreement[[1]]) + nrow(visitation_importance_agreement[[2]]))
+
+```
+
+Altogether, the evidence supports the idea that visitation is a suitable metric to estimate the mutual dependence of species pairs.
+First, it is directly related to pollinator foraging.
+Second, it produces results within our controllability framework that are consistent with plant reproductive success (as estimated by the importance metric).
+
+\clearpage
 # Controllability models {#controllability-models}

### 2018-06-17 code/assumption_visitation.R

@@ -1,0 +1,15 @@
+get_visitation_importance_agreement <- function(sl_characteristics){
+  
+  c("control_capacity", "superior") %>%
+    set_names(., .) %>%
+    purrr::map(function(var){
+      sl_characteristics %>%
+        filter_networks_df(metadata, desired_ntw = "ballantyne") %>%
+        dplyr::filter(net_name != "bal_bin") %>%
+        dplyr::select_("net_name", "sp_name", var) %>%
+        tidyr::spread(net_name, var) %>%
+        dplyr::select_if(is.numeric) %>%
+        cor(method = "spearman") %>%
+        as.data.frame()
+    })
+}

### 2018-06-17 code/beautify_output.R

@@ -13,3 +13,13 @@ pretty_term_names <- function(x){
     stringr::str_replace(stringr::fixed("interaction.push.pull"), 
                          "asymmetry")
 }
+
+pretty_net_names <- function(x){
+  x %>% 
+    stringr::str_replace(stringr::fixed("bal_eff"), 
+                         "efficiency") %>%
+    stringr::str_replace(stringr::fixed("bal_imp"), 
+                         "importance") %>%
+    stringr::str_replace(stringr::fixed("bal_vis"), 
+                         "visitation")
+}

### 2018-06-17 code/fig_rho_sensitivity.R

@@ -11,11 +11,11 @@ make_fig_rho_sensitivity <- function(structural_rho_correlation, rho_feasibility
   
   p1 <- medians %>%
     ggplot(aes(x = rho, y = cor)) +
-    geom_line(aes(group = 1), colour = my_pallete()$dark_purple) + 
     geom_line(data = structural_rho_correlation, 
               aes(x = rho, y = cor, group = net_name),
               alpha = 0.25, 
               colour = my_pallete()$light_purple) +
+    geom_line(aes(group = 1), colour = my_pallete()$dark_purple) + 
     base_ggplot_theme() + 
     coord_cartesian(ylim = c(-1, 1)) +
     labs(title = "(a) Species contribution to coexistence", 

### 2018-06-17 main.R

@@ -104,6 +104,7 @@ species_level_plan <- drake::drake_plan(
   secondary_ext_std = standardize_secondary_extinctions(secondary_ext, controllability, metadata),
   species_model_superior = fit_species_models(sl_characteristics, metadata, response = "superior"), 
   species_model_cc = fit_species_models(sl_characteristics, metadata, response = "control_capacity"),
+  visitation_importance_agreement = get_visitation_importance_agreement(sl_characteristics),
   strings_in_dots = "literals"
 )
 

### 2018-06-17 paper/supp-info.Rmd
Improve captions

@@
 (2007), Spanish were networks assembled by Bartomeus et al.
-(2008).")
+(2008).") %>%
+  kableExtra::kable_styling(font_size = 8)
 ```
@@
 We first calculate the stability condition $\hat{\gamma}$ using all species in the network. 
-To simplify the calculations we assummed that there is no mutualistic trade off, and a mean field interspecific competition of $\rho = 0.01$ [@saavedra_nested_2016]. 
+To simplify the calculations we assummed that there is no mutualistic trade off, and a mean field interspecific competition of $\rho = 0.005$ [@saavedra_nested_2016]. 
 To calculate the contribution to stable coexistence of a given species, we removed the focal species from the network and then calculated the corresponding structural feasibility $\Omega$ for a level of mutualism equal to the stability condition found previously.
@@
 
-```{r fig-rho-sensitivity, fig.width=fig_sizes()[[2]], fig.height=fig_sizes()[[1]]/2, fig.cap="Spearman correlation coefficient of the contribution to stable coexistence of species.
-Grey lines indicate the correlation coeficient for each of the twenty empirical networks.
-The solid black line indicates the median value."}
+```{r fig-rho-sensitivity, fig.width=fig_sizes()[[2]], fig.height=fig_sizes()[[1]]/2, fig.cap="Sensitivity analysis on the impact of interspecific competition parameter $\\rho$ on structural stability.
+(a) Spearman correlation coefficient of the contribution to stable coexistence of species.
+Lighter lines indicate the correlation coeficient for each of the twenty empirical networks.
+The dark line indicates the median value.
+(b) Difference between the conribution to stable coexistence of critical and redundant species for different values of the iterspecific competition parameters $\\rho$."}
 drake::loadd(fig_rho_sensitivity)

### 2018-06-17 paper/manuscript.Rmd
Use references in submodule

@@
 documentclass: artikel1
-bibliography: references.bib
+bibliography: phd-bibliography/network-control.bib
 ---

### 2018-06-17 paper/supp-info.Rmd
Use references in submodule

@@
   - \externaldocument[M-]{manuscript}
-bibliography: references.bib
+  - \usepackage{multirow}
+bibliography: phd-bibliography/network-control.bib
 ---

### 2018-06-18 paper/supp-info.Rmd
Analysis of subsampling
Close #36 Close #37

@@
 \clearpage
-# Controllability models {#controllability-models}
 
-We constructed a set of generalised linear models with binomial error structure. 
-The response variable was the size of the minimum driver node set of the twenty empirical networks (ten invaded and ten uninvaded). 
-The independent variables evaluated were the invasion status, the network connectance, the network nestedness (NODF) the number of species, the network asymmetry (an indication of the balance between plants and pollinators) or the interaction strength asymmetry [the asymmetry on the dependences between trophic levels; @bluthgen_specialization_2007].
+# Sensitivity to sampling {#undersampling}
 
-```{r controllability-variable-importance}
-drake::loadd(controllability_variable_importance)
+Our approach is fundamentaly based on the network structure. 
+Often, the majority of the interactions that make up this structure are weak; in our networks this means that most interactions are formed by a small number of observed pollination visits, and therefore those weak intercations are less conspicuous in the field than strong ones.
+To strengthen the case of our approach, we therefore evaluated the robustness of our results to simulated sampling limitations.
+
+To do so we removed a portion of the visits, for each network, and calculated how three control metrics of the subsampled network compare to those of the full network. 
+Specifically, we calculated the difference between the relative size of the minimum driver node set $n_D$ of the subsampled and the full network, the Spearman correlation between the control capacities $\phi$ and the probability of being a superior node $\sigma$ that were obtained for the empirical network and subsamples of it.
+Finally, we also compared the control capacity of critical species ($\phi=1$) across the different subsamples. 
+We removed up to 20% of the interactions in 1% increments. 
+We repeated the procedure for each network to obtain a total sample size of $n=400$.
+
+Overall, the results of the sensitivity analysis indicate that our approach is likely to  still be useful in the absence of complete sampling. 
+Specifically, as the proportion of sampled interaction decreased, the variability of $n_D$ increased, but was overall similar to that obtained when using all available interactions (Figure \@ref(fig:fig-assumption-sampling-nd)).
+Similarly, the correlation between $\phi$ and $\sigma$ of empirical and subsampled networks was high even for extreme levels of undersampling (Figure \@ref(fig:fig-assumption-sampling-cor)). 
+Importantly, critical species in the empirical networks were also critical species in the subsampled networks in a large majority of cases (Figure \@ref(fig:fig-assumption-sampling-crit)).
+
+```{r fig-assumption-sampling-nd, fig.height=fig_sizes()[[1]]/2, fig.width=fig_sizes()[[1]], fig.cap="Difference between the size of the minimum driver node set of the empirical network and the subsampled network.
+Lighter lines indicate the changes for each networks and the darker line indicates the overall trend."}
+drake::loadd(fig_assumption_sampling)
+fig_assumption_sampling[[1]]
+```
+
+```{r fig-assumption-sampling-cor, fig.height=fig_sizes()[[1]]/2, fig.width=fig_sizes()[[2]], fig.cap="Spearman correlation between the control capacity and the probability of being a superior nodes of the empirical networks and subsampled networks.
+Lighter lines indicate the changes for each networks and the darker line indicates the overall trend."}
+fig_assumption_sampling[[2]]
+```
+
+```{r fig-assumption-sampling-crit, fig.height=fig_sizes()[[1]]/2, fig.width=fig_sizes()[[1]], fig.cap="Control capacity of critical species (those with $\\phi = 1$ in the empirical network) in subsampled networks.
+Lighter lines indicate the changes for each networks and the darker line indicates the overall trend."}
+fig_assumption_sampling[[3]]
 ```

### 2018-06-18 code/fig_assumption_sampling.R

@@ -1,0 +1,106 @@
+# drake::loadd(metrics_subsampled, metadata)
+make_fig_assumption_subsampling <- function(metrics_subsampled, metadata){
+  require(ggplot2)
+ 
+  p1 <- metrics_subsampled %>%
+    extract2("controllability") %>%
+    filter_networks_df(metadata) %>%
+    dplyr::arrange(net_name, prop) %>%
+    dplyr::group_by(net_name) %>%
+    dplyr::mutate(prop_int = n_int / orig_int, 
+                  n_D_diff = n_D - dplyr::first(n_D)) %>% 
+    ggplot(aes(x = prop_int, y = n_D_diff)) +
+    geom_point(shape = 21, colour = my_pallete()$light_purple, size = 1) +
+    geom_smooth(aes( group =net_name), 
+                method = "lm",
+                formula = y ~ 0 + I(-x -1), 
+                colour = my_pallete()$light_purple, 
+                fill = my_pallete()$light_purple, 
+                size = 0.25,
+                alpha  = 0.1,
+                se = T) +
+    geom_smooth(method = "lm",
+                formula = y ~ 0 + I(-x -1), 
+                colour = my_pallete()$dark_purple, 
+                size = 0.5,
+                alpha  = 0.1,
+                se = F) +
+    geom_hline(yintercept = 0, linetype = 2, size = 0.25) +
+    base_ggplot_theme() +
+    scale_x_reverse(labels = scales::percent) +
+    labs(x = "proportion of interactions", 
+         y = latex2exp::TeX("$\\Delta n_D$"))
+  
+  p2 <- c("superior", "control_capacity") %>%
+    set_names(., .) %>%
+    purrr::map_dfr(~ extract_correlations_subsamples(metrics_subsampled$species_metrics, .), .id = "metric") %>%
+    filter_networks_df(metadata) %>% 
+    dplyr::mutate(metric = dplyr::case_when(
+      metric == "control_capacity" ~ "control capacity", 
+      TRUE ~ "superior probability"
+    )) %>%
+    ggplot(aes(x = prop_int, y = cor - 1)) +
+    geom_point(shape = 21, colour = my_pallete()$light_purple, size = 1) +
+    geom_smooth(aes( group =net_name), 
+                method = "lm",
+                formula = I(y) ~ 0 + I(-x -1), 
+                colour = my_pallete()$light_purple, 
+                fill = my_pallete()$light_purple, 
+                size = 0.25,
+                alpha  = 0.1,
[…]

### 2018-06-18 main.R

@@ -63,7 +63,8 @@ example_plots_plan <- drake::drake_plan(
   fig_control_capacity = make_fig_control_capacity(species_model_cc, species_model_superior),
   fig_structural_stability = make_fig_structural_stability(sl_characteristics, metadata), 
   fig_models_degree = make_fig_models_degree(species_model_cc, species_model_superior),
-  fig_rho_sensitivity = make_fig_rho_sensitivity(structural_rho_correlation, rho_feasibility)
+  fig_rho_sensitivity = make_fig_rho_sensitivity(structural_rho_correlation, rho_feasibility),
+  fig_assumption_sampling = make_fig_assumption_subsampling(metrics_subsampled, metadata)
 )
 
 control_capacity_testing_plan <- drake::drake_plan(
@@ -118,7 +119,7 @@ reporting_plan <- drake::drake_plan(
              drake::file_out('paper/supp-info.pdf'), clean_md = FALSE),
   render_pdf(drake::knitr_in('paper/manuscript.Rmd'), 
              drake::file_out('paper/manuscript.pdf'), clean_md = FALSE),
-  render_pdf(drake::file_in('paper/reviewers-response.Rmd'), 
+  render_pdf(drake::file_in('paper/reviewers-response.Rmd'),
              drake::file_out('paper/reviewers-response.pdf'), clean_md = FALSE, clean_tex = FALSE), 
   compile_pdf(drake::file_in('paper/cover-letter.tex'), 
               drake::file_out('paper/cover-letter.pdf'))

### 2018-06-18 paper/manuscript.Rmd
Results mansucript!!
Close #19

@@
 We found that the relative size of the minimum driver node set was not related to any of the independent variables we evaluated. 
-Indeed the null model ($n_D \sim 1$) was the most parsimonious candidate model and all variables were relatively unimportant (based on the AICc; Supporting Information Section \@ref(S-controllability-models)).
+Indeed the null model ($n_D \sim 1$) was the most parsimonious candidate model and all variables were relatively unimportant (based on the AICc; Table  \@ref(S-tab:tab-controllabillity-model-results)).
 The $n_D$ of empirical networks did not differ to that of a null model that roughly preserved the degree distribution and fully preserved the network connectance ($p = `r sprintf('\\num{%s}', format(randomisations_test$interactions$p.value, digits = 2))`$; Figure \@ref(fig:fig-emp-controllability)b).
@@
 
-The models that best explained a species control capacity $\phi$, had a random intercept and slope for the species asymmetry grouped by guild (plants or pollinators; Table \@ref(S-tab:tab-model-output-control-capacity)).
-Contribution to nestedness was the most important variable followed by visitation strength (Table \@ref(tab:tab-model-selection-table), \@ref(S-tab:tab-var-importance)). 
-Species with large contribution to nestedness and large visitation strength were more likely to have a large control capacity (Figure \@ref(fig:fig-species-level)a and b). 
-For the probability of being a superior node $\sigma$, the most parsimonuous models did not include any random effect (Table \@ref(S-tab:tab-model-output-superior)). 
-The most important variables were the species asymmetry and the visitation strength (Table \@ref(tab:tab-model-selection-table), \@ref(S-tab:tab-var-importance)). 
+The models that best explained a species control capacity $\phi$, had a random intercept and slope for the species asymmetry grouped by guild (plants or pollinators; Table \@ref(S-tab:tab-species-model-random), Table \@ref(S-tab:tab-model-output-species-level)).
+Contribution to nestedness was the most important variable followed by visitation strength (Table \@ref(tab:tab-model-selection-table), Table \@ref(S-tab:tab-var-importance)) with species with large contribution to nestedness and large visitation strength being more likely to have a large control capacity (Figure \@ref(fig:fig-species-level)a and b).
+For the probability of being a superior node $\sigma$, the most parsimonuous models did not include any random effect Table \@ref(S-tab:tab-species-model-random), Table \@ref(S-tab:tab-model-output-species-level)).
+The most important variables were the species asymmetry and the visitation strength (Table \@ref(tab:tab-model-selection-table), Table \@ref(S-tab:tab-var-importance)). 
 Specifically, species with a positive asymmetry (this is they affect their partners more than what their parners affect them), and with a large visitatin strength were more likely to be superior nodes (Figure \@ref(fig:fig-species-level)c and d).
 Furthermore, degree was positively, but only weakly asociated to both control capacity and the probability of being a superior node. 
-Remarkably, many species with a low degree, especially pollinators attained a large control capacity in their communities \@ref(S-fig:fig-species-models-degree).
+Remarkably, many species with a low degree, especially pollinators attained a large control capacity in their communities (Figure \@ref(S-fig:fig-species-models-degree)). 
+In addition all invasive plants were both critical ($\phi = 1$) and were superior ($\sigma = 1$) species in their communities.
 
@@
 # dev.off()
-
 ```
 
-The model that best explained Although a species control capacity was not correlated to any of the centrality metrics, we found that it was a strong correlation w  Control capacity was strongly related to the nested
+```{r}
+drake::loadd(critical_sp_df)
+crit_test <- critical_sp_df  %$%
+    t.test(feasibility ~ critical, 
+           alternative = "less", 
+           conf.int = T)
+```
 
-```{r fig-structural-stability, fig.width=fig_sizes()[[1]], fig.height=fig_sizes()[[1]]/2, fig.cap="Control capacity and "}
+We also found that critical species (those with a control capacity $\phi = 1$) have a larger impact on species coexistence as the structural stability of the network was considerably reduced when these species were removed from their communities ($p = `r sprintf('\\num{%s}', format(crit_test$p.value, digits = 2))`$; Figure \@ref(fig:fig-structural-stability); Figure \@ref(S-fig:fig-rho-sensitivity)).
+Although some pollinators had large values of control capacity, the group of critical species in every community was composed exclusivelly by plants.
+
+```{r fig-structural-stability, fig.width=fig_sizes()[[1]], fig.height=fig_sizes()[[1]]/2, fig.cap="Density plot of the structural stability of the communities after a focal species is removed.
+The structural stability after critical species have been removed (darker line) is considerable smaller than the average.
+To allow comparison across communities, the structural stability values were scaled within each network to have a mean of 0 and a standard deviation of one."}
 drake::loadd(fig_structural_stability)
-
 fig_structural_stability[[1]]
@@
 
-```{r tab-model-selection-table}
-drake::loadd(species_model_cc, species_model_superior)
-
-cc_table <- MuMIn::model.sel(species_model_cc$fixed) %>%
-  dplyr::filter(weight > 0.01)
-su_table <- MuMIn::model.sel(species_model_superior$fixed)%>%
-  dplyr::filter(weight > 0.01)
-
-dplyr::bind_rows(cc_table, su_table) %>%
-  dplyr::select(-logLik, - AICc) %>%
-  knitr::kable("latex", 
-               col.names = c("int.", "degree", "push/pull", "nested c.", "sp. strength", "d.f.",  "$\\Delta$AICc","weight"),
-               booktabs = T, 
-               caption = "asd", 
-               row.names = F, 
-               digits = 2, 
-               escape = F) %>%
-  kableExtra::add_header_above(c("model terms" = 5, " " = 3), escape = F) %>%
-  kableExtra::kable_styling(font_size = 8) %>%
-  kableExtra::group_rows("control capacity models", 1, nrow(cc_table), escape = F) %>%
-  kableExtra::group_rows("superior/subordinate models", nrow(cc_table) + 1, nrow(cc_table) + nrow(su_table))
+```{r correlation-calculations}
+drake::loadd(sl_char_corr)
+correlations <- sl_char_corr %>% 
+  extract2("mean") %>%
+  as.data.frame() %>%
+  tibble::rownames_to_column() %>%
+  dplyr::filter(!rowname %in% c("control_capacity", "superior"))
 ```
 
-I'm thinlking just adding a graph with the control capacity and superiorness of the invasive/non invasive species as well as the glm to predict these variables and leave it there.
+The control capacity of a species $\phi$ was only weakly correlated with commonly used centrality metrics. 
+The Spearman correlation ranged between `r round(min(correlations$control_capacity), 2)` (with betweeness-centrality) and `r round(max(correlations$control_capacity), 2)` (with eigen-centrality). 
+On the other hand, the probability of being a superior node $\sigma$ was slightly more similar to established centrality metrics. 
+The Spearman correlation coefficient ranged between `r round(min(correlations$superior), 2)` (with eigen-centrality) and `r round(max(correlations$superior), 2)` (with degree; Figure \@ref(S-fig:fig-correlogram)).
 
-That means that it would be necessary to modify the introduction to remove the parts that claim that centrality is not good enough to predict coextinction. 
-The justification is just that centrality might just be telling a different thing to control. 
-We then just use the "empirically known" role of invasive species to show it works?
+We found that using visitation as a proxy for the strenghth of species interactions leads to similar results than those obtained using pollinator importance [regarded as an accurate measure of the pollination service to plants; Supporting Information Section \@ref(S-visitation-as-proxy); @neeman_framework_2009].
+Importantly, we also found that structural stability is robust to incomplete sampling of interactions. 
+We found a very strong agreement between results obtained using the complete empirical networks and those obtained by randomly removing interactions (Supporting Information Section \@ref(S-undersampling)).
+Despite removing rare interactions and species, the relative size of the minimum driver node set, the superior species, and the relative rankings of control capacity were generally maintained.
+Remarkably critical species in the full network, were also critical in the vast majority of rarefied networks.
+
+# Discussion
 

### 2018-06-18 paper/supp-info.Rmd
Force latex tables in kable

@@
 					"$AS$" = "web.asymmetry") %>% 
-  knitr::kable(escape = FALSE, 
+  knitr::kable("latex", 
+               escape = FALSE, 
                booktabs = TRUE, 

### 2018-06-18 paper/supp-info.Rmd
Make empty spaces in tables have a dash
Cosmetic changes to figure captions

@@
 ```{r setup, include=FALSE}
-knitr::opts_chunk$set(echo = FALSE, message = FALSE, 
+knitr::opts_chunk$set(echo = FALSE, 
+                      message = FALSE, 
                       warning = FALSE)
+options(knitr.kable.NA = '---')
 ```
@@
 (center) Alternative bipartite representations of the directed networks.
-(right) The matchings in the bipartite representation mapped back to the original network."}
+(right) The matchings in the bipartite representation mapped back to the original network.", fig.pos = "p", fig.align = "center"}
 replayPlot(fig_supp_matching$plot)
@@
 
-```{r fig-small-network, fig.height=fig_small_network$height, fig.width=fig_small_network$width,fig.cap = "Illustration of the procedure with an empirical community.
+```{r fig-small-network, fig.height=fig_small_network$height, fig.width=fig_small_network$width, fig.cap = "Illustration of the procedure with an empirical community.
 The visitation network (top), the number of visits between species pairs is shown on each link.
@@
 ```{r fig-all-maximum-matching, fig.height=fig_all_matching$height, fig.width=fig_all_matching$width,fig.cap = "Finding all possible maximum matchings.
-From left to right: alternative bipartite representation of the directed network in Figure \\@ref(fig:fig-maximum-matching-procedure)a.
+From left to right: alternative bipartite representation of the directed network.
 Line graph of the network.
@@
 ```
+
+\clearpage
 

### 2018-06-18 paper/supp-info.Rmd
Clear page between sections
Figure of assumption testing

@@
 
+\clearpage
+
 # Structural controllability {#structural-controllability}
@@
 Nevertheless, the lessons gained when assuming linearity---at both the network and the species level---are a prerequisite for eventually understanding nonlinear control [@liu_controllability_2011; @liu_control_2016].
+
+\newpage
 
@@
 
+\clearpage
+
 ## Networks with reciprocal links {#reciprocal-links}
@@
 
+\clearpage
+
 # Structural stability {#structural-stability}
@@
 
-```{r fig-rho-sensitivity, fig.width=fig_sizes()[[2]], fig.height=fig_sizes()[[1]]/2, fig.cap="Sensitivity analysis on the impact of interspecific competition parameter $\\rho$ on structural stability.
+```{r fig-rho-sensitivity, fig.width=fig_sizes()[[2]], fig.height=fig_sizes()[[1]]/2, fig.cap="A sensitivity analysis of the impact of interspecific competition parameter $\\rho$ on structural stability reveals that the choice of parameters has a negligible impact on the results.
 (a) Spearman correlation coefficient of the contribution to stable coexistence of species.
@@
 The dark line indicates the median value.
-(b) Difference between the conribution to stable coexistence of critical and redundant species for different values of the iterspecific competition parameters $\\rho$."}
+(b) Difference between the conribution to stable coexistence of critical and redundant species for different values of the iterspecific competition parameters $\\rho$.", fig.pos="p", fig.align='center'}
 drake::loadd(fig_rho_sensitivity)
@@
 
-# Impact of visitation {#visitation-as-proxy}
+\clearpage
+
+# Visitation as a proxy for species dependence {#visitation-as-proxy}
 
@@
 
+\clearpage
+
 We fitted the full set of possible candidate models and used the Akaike Information Criterion for small sample sizes (AICc) to compare the models. 
@@
 
+\clearpage
+
 # References

### 2018-06-18 paper/supp-info.Rmd
Table shows up above title. Fixing that

@@
                caption = "Spearman correlation coefficient matrix between the control capacity and the probability obtained by weighting links by the visitation, pollinator efficiency and pollinator importance.") %>%
-  kableExtra::kable_styling(font_size = 8) %>%
+  kableExtra::kable_styling(font_size = 8, latex_options = c("hold_position")) %>%
   kableExtra::group_rows("control capacity", 1, nrow(visitation_importance_agreement[[1]])) %>%

### 2018-06-18 paper/supp-info.Rmd
All table labels must start with tab

@@
 
-We fitted the full set of possible candidate models and used the Akaike Information Criterion for small sample sizes (AICc) to compare the models. 
-We found little support for any of the evaluated variables (Table \@ref(tab:table-controllabillity-model-results)). 
-We measured the relative importance of an independent variable by adding the Akaike weights (the model probabilities) of the models in which the variable was present. 
-All variables were roughly equally un-important with the Akaike weights for each of them ranging between `r round(min(controllability_variable_importance$w.plus), 3)` and `r round(max(controllability_variable_importance$w.plus), 3)` (in a scale from 0 to 1).
-
-```{r table-controllabillity-model-results, results = "asis", sanitize = FALSE}
+```{r tab-controllabillity-model-results, results = "asis", sanitize = FALSE}
 drake::loadd(controllability_models)

### 2018-06-18 paper/supp-info.Rmd
Figure was appearing before section title. Fixed that

@@
 ```{r fig-assumption-sampling-nd, fig.height=fig_sizes()[[1]]/2, fig.width=fig_sizes()[[1]], fig.cap="Difference between the size of the minimum driver node set of the empirical network and the subsampled network.
-Lighter lines indicate the changes for each networks and the darker line indicates the overall trend."}
+Lighter lines indicate the changes for each networks and the darker line indicates the overall trend.", fig.pos="p", fig.align='center'}
 drake::loadd(fig_assumption_sampling)

### 2018-06-18 paper/supp-info.Rmd
Kable tables must explicitly produce latex code

@@
   dplyr::mutate(model = paste0("$", model, "$")) %>% 
-  knitr::kable(escape = FALSE, 
+  knitr::kable("latex", 
+               escape = FALSE, 
                booktabs = TRUE, 
@@
 There was no evidence for any of the evaluated predictors: the invasion status (inv), the network connectance (c), the network nestedness (NODF) the number of species ($n_S$) the network asymmetry ($AS_s$) or the interaction strength asymmetry ($AS_s$).
-Only candidate models with $\\Delta AIC < 8$ are shown.")
+Only candidate models with $\\Delta AIC < 8$ are shown.") %>%
+  kableExtra::kable_styling(font_size = 8)
+```
 ```

### 2018-06-18 paper/supp-info.Rmd
Random effects model selection table for species level models

@@
 ```
+
+```{r tab-species-model-random, warning=FALSE}
+drake::loadd(species_model_cc, species_model_superior)
+
+get_term_table <- function(x) {
+  x %>%
+    attr("random.terms") %>%
+    purrr::map(paste, collapse = " + ") %>%
+    unlist() %>%
+    dplyr::data_frame(random = .) %>%
+    dplyr::bind_cols(x) %>%
+    dplyr::select(random, AICc, delta, weight) %>%
+    dplyr::filter(weight > 0.01)
+}
+
+tab_cc <- MuMIn::model.sel(species_model_cc$random) %>%
+  get_term_table()
+tab_su <- MuMIn::model.sel(species_model_superior$random) %>%
+  get_term_table()
+
+tab_cc %>%
+  dplyr::bind_rows(tab_su) %>%
+  dplyr::mutate(random = pretty_term_names(random)) %>%
+  dplyr::rename(`random effects` = random) %>%
+  knitr::kable("latex", 
+               booktabs = T, 
+               caption = "Selection table of the random effects in the generalised mixed effect models of control capacity $\\phi$ and the probability of being a superior node $\\sigma$.
+Only models with a weight larger than 0.01 are shown.
+We modelled the probability of being a superior node without random effects as the random intercept over site had zero variance.",
+               row.names = F, 
+               digits = 2, 
+               escape = F) %>%
+  kableExtra::kable_styling(font_size = 8) %>%
+  kableExtra::group_rows("control capacity models", 1, nrow(tab_cc)) %>%
+  kableExtra::group_rows("superior probability models", nrow(tab_cc) + 1, nrow(tab_cc) + nrow(tab_su)) 
+```
 ```

### 2018-06-18 paper/supp-info.Rmd
Fixed effects model selection table for species level

@@
 ```
+
+```{r tab-model-output-species-level}
+best_model_cc <- species_model_cc %$%
+  fixed %>%
+  get_best_model() 
+best_model_su <- species_model_superior %$%
+  fixed %>%
+  get_best_model()
+
+num_effects <- get_num_effects(best_model_cc)
+
+table_df <- best_model_cc %>%
+  broom::tidy() %>%
+  dplyr::bind_rows(broom::tidy(best_model_su))
+
+table_df %>%
+  dplyr::mutate(group = dplyr::if_else(is.na(group), "fixed", group)) %>%
+  dplyr::select(group, term, estimate, std.error, statistic, p.value) %>%
+  dplyr::mutate(term = pretty_term_names(term)) %>%
+  knitr::kable("latex", 
+               col.names = c("effect type", "term", "estimate", "std. error", "z value", "p value"),
+               booktabs = T, 
+               caption = "Summary table of the control capacity model with the smallest AICc.", 
+               row.names = F, 
+               digits = 2, 
+               escape = F) %>%
+  kableExtra::kable_styling(font_size = 8) %>%
+  kableExtra::group_rows("control capacity models", 1, purrr::reduce(num_effects, sum)) %>%
+  kableExtra::group_rows("superior probability models", purrr::reduce(num_effects, sum) + 1, nrow(table_df))
+
+```
 ```

### 2018-06-18 paper/supp-info.Rmd
Variable importance table for species level model

@@
 ```
+
+```{r tab-var-importance}
+cc_imp <- get_var_importance(species_model_cc$fixed) 
+su_imp <- get_var_importance(species_model_superior$fixed)
+
+dplyr::bind_rows(cc_imp, su_imp) %>%
+  dplyr::mutate(term = pretty_term_names(term)) %>%
+  knitr::kable("latex", 
+               booktabs = T, 
+               row.names = F, 
+               digits = 2, 
+               escape = F, 
+               caption = "Variable importance for each set of models. The importance is the sum of the weights of all models in which the variable was included.",
+               linesep = '') %>%
+  kableExtra::kable_styling(font_size = 8)%>%
+  kableExtra::group_rows("control capacity models", 1, nrow(cc_imp)) %>%
+  kableExtra::group_rows("superior probability models", nrow(cc_imp) + 1, nrow(cc_imp) + nrow(su_imp))
 ```

### 2018-06-18 paper/supp-info.Rmd
Degree and response plot for species level models

@@
 
-# Empirical vs. random expectation of controllability {#randomisations}
+```{r fig-species-models-degree, fig.width=fig_sizes()[[2]], fig.height=fig_sizes()[[1]]/2, fig.cap = "Relationship between degree and (a) the control capacity and (b) the probability of being a superior node.
+The plots show the values predicted by most parsimonious model for each response variable.
+The invasive species are depicted with solid orange circles."}
+drake::loadd(fig_models_degree)
+library(ggplot2)
+fig_models_degree %<>% add_internal_margins()
+cowplot::plot_grid(plotlist = fig_models_degree, ncol = 2)
+```
 

### 2018-06-18 paper/supp-info.Rmd
Plot Standard deviations for correlogram

@@
 
-```{r fig-correlogram, fig.width=fig_sizes()[[1]], fig.height=fig_sizes()[[1]], fig.cap="Mean Spearman correlation coefficients between control metrics (control capcity $\\phi$ and the likelyhood of being a superior node $\\sigma$) and centrality metrics commonly used to estimate a species' 'keystoness' (closeness centrality $l$ , betwenness $w$, eigen centrality $e$, page rank $g$ and degre $k$) in each of the networks.
+```{r fig-correlogram, fig.width=fig_sizes()[[2]], fig.height=fig_sizes()[[1]], fig.cap="Mean Spearman correlation coefficients between control metrics (control capcity $\\phi$ and the likelyhood of being a superior node $\\sigma$) and centrality metrics commonly used to estimate a species' 'keystoness' (closeness centrality $l$ , betwenness $w$, eigen centrality $e$, page rank $g$ and degre $k$) in each of the networks.
 Purple and orange tiles indicate a positive correlation or negative correlation respectively."}
 drake::loadd(fig_correlation)
-fig_correlation[[1]]
+cowplot::plot_grid(plotlist = fig_correlation, ncol = 2)
 ```

### 2018-06-18 main.R

@@ -61,7 +61,7 @@ example_plots_plan <- drake::drake_plan(
   fig_emp_controllability = make_fig_emp_contollability(controllability, randomisations_df, metadata), 
   fig_correlation = make_fig_correlation(sl_char_corr), 
   fig_control_capacity = make_fig_control_capacity(species_model_cc, species_model_superior),
-  fig_structural_stability = make_fig_structural_stability(sl_characteristics, metadata), 
+  fig_structural_stability = make_fig_structural_stability(critical_sp_df), 
   fig_models_degree = make_fig_models_degree(species_model_cc, species_model_superior),
   fig_rho_sensitivity = make_fig_rho_sensitivity(structural_rho_correlation, rho_feasibility),
   fig_assumption_sampling = make_fig_assumption_subsampling(metrics_subsampled, metadata)
@@ -102,6 +102,7 @@ species_level_plan <- drake::drake_plan(
   secondary_ext_std = standardize_secondary_extinctions(secondary_ext, controllability, metadata),
   species_model_superior = fit_species_models(sl_characteristics, metadata, response = "superior"), 
   species_model_cc = fit_species_models(sl_characteristics, metadata, response = "control_capacity"),
+  critical_sp_df = extract_critical_sp_df(sl_characteristics, metadata),
   strings_in_dots = "literals"
 )
 

### 2018-06-18 paper/manuscript.Rmd
Pollinator efficiency and importance needed some explanation

@@
 First we tested that visitation is an appropiate proxy to infer interspecific effects. 
-To do that we compared the results obtained using visitation, pollinator efficiency, and pollinator importance as alternative measures in a dataset that lacked invasive species [@neeman_framework_2009; @ballantyne_constructing_2015; more details in the Supporting Information Section \@ref(S-visitation-as-proxy)].
+To do that we compared the results obtained using visitation to two alternative metric in a dataset that lacked invasive species [@ballantyne_constructing_2015]. 
+Specifically we also applied the structural controllability approach to networks constructed using pollinator efficiency (which measures the pollen deposition of an interaction) and pollinator importance (which accounts for both pollen deposition and visitation and hence is regarded as a more accurate estimation of the pollination service received by plants) [@neeman_framework_2009].
+More details in the Supporting Information Section \@ref(S-visitation-as-proxy).
 Second, because interspecific dependencies depend on the network topology and consequently on the accurate sampling of interactions, we tested the robustness of structural controllability to the undersampling of interactions.

### 2018-06-18 paper/manuscript.Rmd
Check spelling

--- 2018-06-18 paper/manuscript.Rmd
@@
 By basing the direction of the links on the asymmetry of their dependence, we are able to generate a network that is consistent with the dynamics of the community while satisfying the requirements of structural controllability.
-That allow us to calculate the controllability of the networks and investigate whether there are differences between invaded and uninvaded communities.
+That allows us to calculate the controllability of the networks and investigate whether there are differences between invaded and uninvaded communities.
 
@@
 (a) To establish the direction of control we start with a weighted visitation network (on the left).
-In this network, the width of the links corresponds to the frequency of visitation between animals $a_i$ and plants $p_i$, with wider link indicating more visits.
+In this network, the width of the links corresponds to the frequency of visitation between animals $a_i$ and plants $p_i$, with wider links indicating more visits.
 Plant $p_1$ is visited exclusively by $a_1$ but $p_1$ represents only a small fraction of the floral resources of $a_1$.
-Therefore the population of $p_1$ is more likely to be affected by $a_1$ than visceversa.
+Therefore the population of $p_1$ is more likely to be affected by $a_1$ than vice-versa.
 We represent this with a directed link from $a_1$ to $p_1$ (right).
 The direction of control between all other species pairs can be similarly determined by inspecting the difference between their relative dependences.
-(b) Once we have established the directions of control we can determine wether the network is controllable or not.
+(b) Once we have established the directions of control we can determine whether the network is controllable or not.
 A system defined by a directed network (with state nodes $x_i$; species populations in an ecological context) and external control inputs (nodes $u_i$, orange links) is structurally controllable if it satisfies two conditions: it has no dilations (expansions in the network) and no inaccessible nodes.
-The system on the top left is not controllable because there is a dilation in which node $x_2$ is being used to control two nodes simultaneously, in other workds there are less superiors ($x_2$) than subordinates ($x_1$ and $x_3$).
+The system on the top left is not controllable because there is a dilation in which node $x_2$ is being used to control two nodes simultaneously, in other words, there are fewer superiors ($x_2$) than subordinates ($x_1$ and $x_3$).
 The network in the top right is not controllable because node $x_3$ is inaccessible for the only input node $u_1$ in the system.
@@
 <!-- The last sentence of the paragraph above sticks out a bit. -->
-<!-- I rephrased it the last couple of sentences, hopefully it flows better now -->
+<!-- I rephrased it the last couple of sentences, hopefully, it flows better now -->
 
@@
 
-Maximum matching is a widely studied topic in graph theory and is commonly used in multiple applications, ranging from dating apps and wireless communications to organ transplant allocation and peer-to-peer file sharing.
+Maximum-matching is a widely studied topic in graph theory and is commonly used in multiple applications, ranging from dating apps and wireless communications to organ transplant allocation and peer-to-peer file sharing.
 A matching in an unweighted directed graph is defined as a set of links that do not share a common start or end nodes; the largest possible matching is called a maximum matching. 
@@
 In addition, we also explored whether real networks differ in their architecture from random ones in a concerted way that could impact these results. 
-Specifically we used two null models each with 99 randomisations per network. 
+Specifically, we used two null models each with 99 randomisations per network. 
 In the first, we followed @vazquez_species_2007 and maintained the connectance of the network but randomised the visits across species such that the species-specific relative probabilities of interactions were maintained; we then calculated the direction of control and the corresponding size of the minimum driver node set.
@@
 We calculated the species control capacity $\phi$ and the probability of being a superior node $\sigma$ for each species in our networks.
-In the networks that contained reciprocal links (because there was not assymetry in the dependences of a species pair), we averaged a species' $\phi$ and $\sigma$ across every possible "non-reciprocal" realisation of the network (more details can be found in the Supporting Information Section \@ref(S-reciprocal-links)).
+In the networks that contained reciprocal links (because there was no asymmetry in the dependences of a species pair), we averaged a species' $\phi$ and $\sigma$ across every possible "non-reciprocal" realisation of the network (more details can be found in the Supporting Information Section \@ref(S-reciprocal-links)).
 We then examined how species-level structural properties were related to these two variables using two sets of generalised mixed-effects models with binomial error structure. 
-As explanatory variables in the fixed component we included four variables. 
-First, the species contribution to nestendess, which has been proposed as a key feature that promotes stability and robustness in mutualistic networks [@saavedra_strong_2011]. 
-Second, the visitation strength (the sum of a species' interactions), which quantifies the strength of a species associations and is indirectly related to its abbundance [@poisot_comparative_2012]. 
-Third, the direction of assymetry which quantifies the net balance in dependencies, this is it indicates if a species affects other species more than what they affect it or not [@vazquez_species_2007].
-Fourth, to account for the centrality of a species we included degree as the fourth fixed effect. 
+As explanatory variables in the fixed component, we included four variables. 
+First, the species contribution to nestedness, which has been proposed as a key feature that promotes stability and robustness in mutualistic networks [@saavedra_strong_2011]. 
+Second, the visitation strength (the sum of a species' interactions), which quantifies the strength of a species associations and is indirectly related to its abundance [@poisot_comparative_2012]. 
+Third, the direction of asymmetry which quantifies the net balance in dependencies, this is it indicates if a species affects other species more than what they affect it or not [@vazquez_species_2007].
+Fourth, to account for the centrality of a species we included the degree as the fourth fixed effect. 
 To facilitate comparison between variables, all four variables were scaled to have a mean of zero and a standard deviation of one. 
 To identify the models that were best supported by the data we first determined the most parsimonious random structure using the AICc. 
-Specifically we evaluated a random intercept for observations grouped by the study site, and a intercept and slope for the contribution to nestedness, visitation strength and assymetry grouped by the trophic guild (plant or pollinator).
+Specifically, we evaluated a random intercept for observations grouped by the study site, and an intercept and slope for the contribution to nestedness, visitation strength and asymmetry grouped by the trophic guild (plant or pollinator).
 After identifying the most likely random structure we ranked models from all possible fixed effects combinations using the AICc weight.
-The relative importance of variables was then assessed by looking at both their effect sizes in the top ranked models and the cummulative weight of the models in which they are present.
+The relative importance of variables was then assessed by looking at both their effect sizes in the top-ranked models and the cumulative weight of the models in which they are present.
 
 Some species have a control capacity $\phi = 1$. 
-These species are critical to control community because they are part of the minimum driver node set in every control scenario. 
+These species are critical to controlling community because they are part of the minimum driver node set in every control scenario. 
 In other words, it is not possible to change the state of the community to a desired state without managing the abundance of these species. 
 We anticipate that these species have a disproportionally large impact on the community dynamics. 
-Therefore, we determined the critical species in each of the networks and investigated wether they have a larger than average impact on the stable coexistence of species in the community. 
+Therefore, we determined the critical species in each of the networks and investigated whether they have a larger than average impact on the stable coexistence of species in the community. 
 This property of promoting stable coexistence is called structural stability [@rohr_structural_2014]. 
-Mathematically it is denoted by the letter $\Omega$ and represents the size of the parameter space (growth rates, carrying capacities) under which all speces can sustain positive abundances [@saavedra_nested_2016].
+Mathematically it is denoted by the letter $\Omega$ and represents the size of the parameter space (growth rates, carrying capacities) under which all species can sustain positive abundances [@saavedra_nested_2016].
 The contribution of species *i* to stable coexistence, can be estimated by calculating the structural stability of the community when the focal species *i* is removed. 
@@
 
-Finally, we wanted to understand how the control capacity $\phi$ and the probability of being a superior node $\sigma$ is related to merics of keystoness based on centrality. 
+Finally, we wanted to understand how the control capacity $\phi$ and the probability of being a superior node $\sigma$ is related to metrics of keystoness based on centrality. 
 To do that, for each network, we calculated the Spearman correlation matrix between these two variables and some centrality metrics commonly used to identify keystone species. 
@@
 We tested the sensitivity of our approach to two fundamental assumptions. 
-First we tested that visitation is an appropiate proxy to infer interspecific effects. 
-To do that we compared the results obtained using visitation, pollinator efficiency, and pollinator importance as alternative measures in a dataset that lacked invasive species [@neeman_framework_2009; @ballantyne_constructing_2015; more details in the Supporting Information Section \@ref(S-visitation-as-proxy)].
+First, we tested that visitation is an appropriate proxy to infer interspecific effects. 
+To do that we compared the results obtained using visitation to two alternative metrics in a dataset that lacked invasive species [@ballantyne_constructing_2015]. 
+Specifically, we also applied the structural controllability approach to networks constructed using pollinator efficiency (which measures the pollen deposition of an interaction) and pollinator importance (which accounts for both pollen deposition and visitation and hence is regarded as a more accurate estimation of the pollination service received by plants) [@neeman_framework_2009].
+More details in the Supporting Information Section \@ref(S-visitation-as-proxy).
 Second, because interspecific dependencies depend on the network topology and consequently on the accurate sampling of interactions, we tested the robustness of structural controllability to the undersampling of interactions.
-To do that we compared the results obtained when using the full network and when randomly removing interactions preferentialy from the weakest links in the network. 
+To do that we compared the results obtained when using the full network and when randomly removing interactions preferentially from the weakest links in the network. 
 This effectively removed the rare interactions from the networks (more details in the Supporting Information Section \@ref(S-undersampling)).
@@
 We found that the relative size of the minimum driver node set was not related to any of the independent variables we evaluated. 
-Indeed the null model ($n_D \sim 1$) was the most parsimonious candidate model and all variables were relatively unimportant (based on the AICc; Table  \@ref(S-tab:tab-controllabillity-model-results)).
+Indeed the null model ($n_D \sim 1$) was the most parsimonious candidate model and all variables were relatively unimportant (based on the AICc; Table  \@ref(S-tab:tab-controllability-model-results)).
 The $n_D$ of empirical networks did not differ to that of a null model that roughly preserved the degree distribution and fully preserved the network connectance ($p = `r sprintf('\\num{%s}', format(randomisations_test$interactions$p.value, digits = 2))`$; Figure \@ref(fig:fig-emp-controllability)b).
@@
 (b) The density distribution of the difference between the relative size of the minimum driver node set of random networks and that of empirical networks.
-We randomised either the species visitation patterns (light line), or randomised the direction of control between a species pair (dark line).
+We randomised either the species visitation patterns (light line) or randomised the direction of control between a species pair (dark line).
 The vertical dashed lines indicate the median values of each distribution."}
@@
 
-The models that best explained a species control capacity $\phi$, had a random intercept and slope for the species asymmetry grouped by guild (plants or pollinators; Table \@ref(S-tab:tab-species-model-random), Table \@ref(S-tab:tab-model-output-species-level)).
+The models that best explained a species control capacity $\phi$, had a random intercept and slope for the species asymmetry grouped by the species' guild (plants or pollinators; Table \@ref(S-tab:tab-species-model-random), Table \@ref(S-tab:tab-model-output-species-level)).
 Contribution to nestedness was the most important variable followed by visitation strength (Table \@ref(tab:tab-model-selection-table), Table \@ref(S-tab:tab-var-importance)) with species with large contribution to nestedness and large visitation strength being more likely to have a large control capacity (Figure \@ref(fig:fig-species-level)a and b).
@@
 The most important variables were the species asymmetry and the visitation strength (Table \@ref(tab:tab-model-selection-table), Table \@ref(S-tab:tab-var-importance)). 
-Specifically, species with a positive asymmetry (this is they affect their partners more than what their parners affect them), and with a large visitatin strength were more likely to be superior nodes (Figure \@ref(fig:fig-species-level)c and d).
-Furthermore, degree was positively, but only weakly asociated to both control capacity and the probability of being a superior node. 
+Specifically, species with a positive asymmetry (this is they affect their partners more than what their partners affect them), and with a large visitation strength were more likely to be superior nodes (Figure \@ref(fig:fig-species-level)c and d).
+Furthermore, species degree was positively, but only weakly associated with both control capacity and the probability of being a superior node. 
 Remarkably, many species with a low degree, especially pollinators attained a large control capacity in their communities (Figure \@ref(S-fig:fig-species-models-degree)). 
@@
 We also found that critical species (those with a control capacity $\phi = 1$) have a larger impact on species coexistence as the structural stability of the network was considerably reduced when these species were removed from their communities ($p = `r sprintf('\\num{%s}', format(crit_test$p.value, digits = 2))`$; Figure \@ref(fig:fig-structural-stability); Figure \@ref(S-fig:fig-rho-sensitivity)).
-Although some pollinators had large values of control capacity, the group of critical species in every community was composed exclusivelly by plants.
+Although some pollinators had large values of control capacity, the group of critical species in every community was composed exclusively of plants.
 
@@
 
-We found that using visitation as a proxy for the strenghth of species interactions leads to similar results than those obtained using pollinator importance [regarded as an accurate measure of the pollination service to plants; Supporting Information Section \@ref(S-visitation-as-proxy); @neeman_framework_2009].
+We found that using visitation as a proxy for the strength of species interactions leads to similar results than those obtained using pollinator importance [regarded as an accurate measure of the pollination service to plants; Supporting Information Section \@ref(S-visitation-as-proxy); @neeman_framework_2009].
 Importantly, we also found that structural stability is robust to incomplete sampling of interactions. 
@@
 Despite removing rare interactions and species, the relative size of the minimum driver node set, the superior species, and the relative rankings of control capacity were generally maintained.
-Remarkably critical species in the full network, were also critical in the vast majority of rarefied networks.
+Remarkably critical species in the full network were also critical in the vast majority of rarefied networks.
 

### 2018-06-18 paper/supp-info.Rmd
Check spelling

@@
 ```{r fig-small-network, fig.height=fig_small_network$height, fig.width=fig_small_network$width, fig.cap = "Illustration of the procedure with an empirical community.
-The visitation network (top), the number of visits between species pairs is shown on each link.
+The visitation network (top), the number of visits between species pairs are shown on each link.
 The directed network in which the direction of control is determined based on the mutual dependences (middle).
@@
 
-In order to calculate a node's control capacity $\phi$, we harness the fact that nodes can be classified in three groups according to their role in the input graph. 
+In order to calculate a node's control capacity $\phi$, we harness the fact that nodes can be classified into three groups according to their role in the input graph. 
 First,  if $x_i$ belongs to the minimum driver node set and has no adjacent nodes, then it cannot be replaced and will be part of every possible control configuration. 
 Second, if $x_i$ does not belong to the minimum driver node set and is not adjacent to any possible input node, then it does not part of the minimum driver node set under any control configuration. 
-Finally, if a node $x_i$ belongs to the minimum driver node set and is adjacent to another node $x_j$ in the input graph, then $x_j$ must belong to another minimum driver node to which $x_i$ doesn not belong, in other words $x_i$ and $x_j$ are substitutable.
+Finally, if a node $x_i$ belongs to the minimum driver node set and is adjacent to another node $x_j$ in the input graph, then $x_j$ must belong to another minimum driver node to which $x_i$ does not belong, in other words, $x_i$ and $x_j$ are substitutable.
 
 The frist and the second group have a control capacity of $\phi = 1$ and $\phi = 0$ respectively. 
-Meanwhile, the third group has intermediate values of control capacity which can be calculated by computing the number of possible susbstitutions of a node by its control adjacent nodes. 
-As a rule of thumb the largest the number of possible substitutions an input node has, the smaller its control capacity.
+Meanwhile, the third group has intermediate values of control capacity which can be calculated by computing the number of possible substitutions of a node by its control adjacent nodes. 
+As a rule of thumb, the largest the number of possible substitutions an input node has, the smaller its control capacity.
 
@@
 For larger networks, calculating the control capacities using the input graph is several orders of magnitude faster than computing all possible maximum matchings. 
-While the the computation time of the input graph grows linearly with network size, the compuation of all maximum matchings grows polynomially. 
+While the computation time of the input graph grows linearly with network size, the computation of all maximum matchings grows polynomially. 
 However, the control capacities obtained using the input graph are not identical to those obtained by computing all possible maximum matchings. 
-The reason of this discrepancy is that two maximum matchings might result in the same minimum driver node set. 
+The reason for this discrepancy is that two maximum matchings might result in the same minimum driver node set. 
 Nevertheless, the results obtained using both approaches are extremely similar. 
-We compared the control capacity obtained by calculating all maximum matchings and that obtained using the input graph in `r length(cc_corr)` of our networks (those for which we were able to calculate all maximum matchings within reasonable time).
+We compared the control capacity obtained by calculating all maximum matchings and that obtained using the input graph in `r length(cc_corr)` of our networks (those for which we were able to calculate all maximum matchings within a reasonable time).
 The spearman correlation was very high in all cases, ranging between `r round(min(cc_corr),2)` and `r round(max(cc_corr), 2)` (median `r round(median(cc_corr), 2)`).
@@
 The proportion of reciprocal links in relatively low. 
-In fact the proportion of species pairs that are reciprocally connected in our empirical networks is just `r round(mean(recipr$prop_bid)*100, 2)`%. 
+In fact, the proportion of species pairs that are reciprocally connected in our empirical networks is just `r round(mean(recipr$prop_bid)*100, 2)`%. 
 However, reciprocal links are not a rare occurrence as `r sum(recipr$prop_bid != 0)` out of `r nrow(recipr)` empirical networks had at least one. 
@@
 
-All of these non-reciprocal networks are as likely to be one that best represent the superior/matched relationships in the network. 
+All of these non-reciprocal networks are as likely to be one that best represents the superior/matched relationships in the network. 
 As such, we average the three metrics ($n_D$, $\phi$, and $\sigma$) across all the networks without reciprocal links without weighting by the number of possible control configurations.
@@
 ```{r fig-bidirectional, fig.height=fig_bidirectional$height, fig.width=fig_bidirectional$width,fig.cap = "In order to calculate the controllability metrics for a network with reciprocal links (left), we first decompose the network into several versions that contain no reciprocal links (right).
-As each of these networks represent a different equiprobable scenario, the controllability metrics for the network with reciprocal links are the unweighted mean of these metrics across the non-reciprocal networks."}
+As each of these networks represents a different equiprobable scenario, the controllability metrics for the network with reciprocal links are the unweighted mean of these metrics across the non-reciprocal networks."}
 replayPlot(fig_bidirectional$plot)
@@
 We first calculate the stability condition $\hat{\gamma}$ using all species in the network. 
-To simplify the calculations we assummed that there is no mutualistic trade off, and a mean field interspecific competition of $\rho = 0.005$ [@saavedra_nested_2016]. 
+To simplify the calculations we assumed that there is no mutualistic trade-off, and a mean field interspecific competition of $\rho = 0.005$ [@saavedra_nested_2016]. 
 To calculate the contribution to stable coexistence of a given species, we removed the focal species from the network and then calculated the corresponding structural feasibility $\Omega$ for a level of mutualism equal to the stability condition found previously.
@@
 Visitation frequency has been shown to be an appropriate surrogate for inter-specific effects in pollination networks [@vazquez_interaction_2005; @bascompte_asymmetric_2006]. 
-Nevertheless visitation is not equivalent to pollen deposition and might be insufficient to reflect the dependences of plants on animals and vice versa [@alarcon_congruence_2010; @king_why_2013]. 
-We therefore investigated the effect of calculating the dependences using visitation or pollination effectiveness and importance---two metrics more proximate to plant reproductive success.
+Nevertheless, visitation is not equivalent to pollen deposition and might be insufficient to reflect the dependences of plants on animals and vice versa [@alarcon_congruence_2010; @king_why_2013]. 
+We, therefore, investigated the effect of calculating the dependences using visitation or pollination effectiveness and importance---two metrics more proximate to plant reproductive success.
 We did this by comparing *(i)* the size of the minimum driver node set $n_D$ of the community, *(ii)* the species' control capacity and, *(iii)* the species' probability of being a superior node. 
@@
 Therefore we calculated $\phi$ and $\sigma$ and calculated it's correlation among all three weighting schemes.
-Although visitation and efficiency (pollen deposition) produce moderately different results, we found a very strong agreement between the order produced by visitation and importance which is arguably a more accurate metric of interspecific effects (Table \@ref(tab:tab-asumption-visitation)).
+Although visitation and efficiency (pollen deposition) produce moderately different results, we found a very strong agreement between the order produced by visitation and importance which is arguably a more accurate metric of interspecific effects (Table \@ref(tab:tab-assumption-visitation)).
 
@@
 
-Our approach is fundamentaly based on the network structure. 
-Often, the majority of the interactions that make up this structure are weak; in our networks this means that most interactions are formed by a small number of observed pollination visits, and therefore those weak intercations are less conspicuous in the field than strong ones.
-To strengthen the case of our approach, we therefore evaluated the robustness of our results to simulated sampling limitations.
+Our approach is fundamentally based on the network structure. 
+Often, the majority of the interactions that make up this structure are weak; in our networks, this means that most interactions are formed by a small number of observed pollination visits, and therefore those weak interactions are less conspicuous in the field than strong ones.
+To strengthen the case of our approach, we, therefore, evaluated the robustness of our results to simulated sampling limitations.
 
@@
 Overall, the results of the sensitivity analysis indicate that our approach is likely to still be useful in the absence of complete sampling. 
-Specifically, as the proportion of sampled interaction decreased, the variability of $n_D$ increased, but was overall similar to that obtained when using all available interactions (Figure \@ref(fig:fig-assumption-sampling-nd)).
+Specifically, as the proportion of sampled interaction decreased, the variability of $n_D$ increased but was overall similar to that obtained when using all available interactions (Figure \@ref(fig:fig-assumption-sampling-nd)).
 Similarly, the correlation between $\phi$ and $\sigma$ of empirical and subsampled networks was high even for extreme levels of undersampling (Figure \@ref(fig:fig-assumption-sampling-cor)). 

### 2018-06-19 paper/manuscript.Rmd
Alternative title

@@
 ---
-title: "Working title: Ecological network control"
+title: "Structural controllability of ecological networks"
 classoption: a4paper
@@
 ```
+
+*Alternative titles:*
+
+* Keystoneness, centrality, and the structural controllability of ecological networks
 

### 2018-06-19 paper/manuscript.Rmd
Using species instead of node might be easier to grasp for ecologists
Replacing node by species where appropriate

@@
 
-Species abundances (and consequently the state of the community) are influenced by both the species interactions and the specific dynamic relationships between nodes and the mechanisms of self-regulation.
+Species abundances (and consequently the state of the community) are influenced by both their interactions, the specific dynamics of these interactions and the mechanisms of self-regulation. 
 However, community and population dynamics can be modelled in innumerable ways, and empirical support for one versus another is often still ambiguous. 
@@
 Here, we are interested in finding a minimum driver node-set (effectively finding *B*) with which to make the system controllable. 
-The brute-force search for this minimum driver node set is computationally prohibitive for most networks as it involves the evaluation of $2^N$ different controllability matrices. 
-We therefore instead employ a recently-developed approach that shows that the control problem of finding the minimum driver node set can be mapped into a graph-theoretic problem: maximum matching [@liu_controllability_2011; @liu_control_2016].
+The brute-force search for this minimum driver node-set is computationally prohibitive for most networks as it involves the evaluation of $2^N$ different controllability matrices. 
+We therefore instead employ a recently-developed approach that shows that the control problem of finding the minimum driver node-set can be mapped into a graph-theoretic problem: maximum matching [@liu_controllability_2011; @liu_control_2016].
 
@@
 Given the result, we can further decompose the matching into a set of paths that reveal how a control signal can flow across the links in a network to reach every node that composes it. 
-As recently shown [@liu_controllability_2011], the minimum driver node set---those to which an external control input should be applied to make the system controllable---corresponds exactly to the *unmatched* nodes in the network (Figure \@ref(fig:fig-control-configuration)).
+As recently shown [@liu_controllability_2011], the minimum driver node-set---those to which an external control input should be applied to make the system controllable---corresponds exactly to the *unmatched* nodes in the network (Figure \@ref(fig:fig-control-configuration)).
 
@@
 In directed networks, a maximum matching is the largest possible set of links that do not share start or end nodes (dark purple).
-Maximum matchings are not necessarily unique, instead, each of them is related to a possible minimum driver node set in the network (the nodes to which an external control input, in orange, should be applied in order to ensure controllability).
-The size of the minimum driver node set *D* corresponds exactly to the number of unmatched nodes (the number of nodes in the network *N* minus the matching size).
-To account for network size, we use the size of the minimum driver node set relative to the total number of nodes *n~D~ = D/N* as a measure of the extent to which the network structure can be harnessed to control the system."}
+Maximum matchings are not necessarily unique, instead, each of them is related to a possible minimum driver node-set in the network (the nodes to which an external control input, in orange, should be applied in order to ensure controllability).
+The size of the minimum driver node-set *D* corresponds exactly to the number of unmatched nodes (the number of nodes in the network *N* minus the matching size).
+To account for network size, we use the size of the minimum driver node-set relative to the total number of nodes *n~D~ = D/N* as a measure of the extent to which the network structure can be harnessed to control the system."}
 replayPlot(fig_control_config$plot)
@@
 However, we are interested in understanding the controllability of a network in a more general sense, such that it can be applied even when the precise control scenario is known only incompletely. 
-To this end, we chose an indicator that follows directly from our approach: the size of the minimum driver node set. 
+To this end, we chose an indicator that follows directly from our approach: the size of the minimum driver node-set. 
 This simple metric provides a general indication of how difficult controlling a network might be, as systems that require a large number of external inputs to be fully controlled are intuitively more difficult or costly to manage.
@@
 Conversely, the structure of a linear trophic chain can be harnessed to achieve full control using just one intervention targeted the top species; the control signal would then cascade through the trophic levels and reach other species in the community.
-Specifically, drawing from the structural-controllability literature, we use the size of the minimum driver node set relative to the total number of nodes $n_D = \frac{D}{N}$ as a measure of the extent to which the network structure can be harnessed to control the community.
+Specifically, drawing from the structural-controllability literature, we use the size of the minimum driver node-set relative to the total number of species $n_D = \frac{D}{N}$ as a measure of the extent to which the network structure can be harnessed to control the community.
 In an ecological context, external inputs can be thought of as management interventions that modify the abundance of a particular species. 
@@
 
-After finding the minimum driver node set in each of our networks, we wanted to test whether invasion status or other predictors are correlated to this metric of controllability. 
+After finding the minimum driver node-set in each of our networks, we wanted to test whether invasion status or other predictors are correlated to this metric of controllability. 
 We, therefore, use a set of generalised linear models (with binomial error structure). 
-The response variable was the size of the minimum driver node set $n_D$ of the twenty empirical networks (ten invaded and ten uninvaded). 
+The response variable was the size of the minimum driver node-set $n_D$ of the twenty empirical networks (ten invaded and ten uninvaded). 
 The independent variables evaluated were the invasion status, the network connectance, the network nestedness (NODF) the number of species [since one might naively expect to see a negative relationship between richness and controllability; @menge_indirect_1995], the network asymmetry (an indication of the balance between plant and pollinator diversity), and the interaction strength asymmetry [the asymmetry on the dependences between trophic levels; @bluthgen_specialization_2007].
@@
 Specifically, we used two null models each with 99 randomisations per network. 
-In the first, we followed @vazquez_species_2007 and maintained the connectance of the network but randomised the visits across species such that the species-specific relative probabilities of interactions were maintained; we then calculated the direction of control and the corresponding size of the minimum driver node set.
+In the first, we followed @vazquez_species_2007 and maintained the connectance of the network but randomised the visits across species such that the species-specific relative probabilities of interactions were maintained; we then calculated the direction of control and the corresponding size of the minimum driver node-set.
 For the second null model, we used the empirical directed network and randomly shuffled the direction of control between a species pair.
@@
 Ecologically, these differences are relevant because resources and data are limited, and therefore full control is unfeasible. 
-While calculating the size of the minimum drive node set can measure the controllability of an ecological community, it does not provide information about the roles that particular species play. 
+While calculating the size of the minimum drive node-set can measure the controllability of an ecological community, it does not provide information about the roles that particular species play. 
 To answer our question, we make two kinds of distinctions between species from a control perspective.
@@
 First, we harness the fact there may be multiple maximum matchings for a given network, and each of these maximum matchings indicates unique paths that could potentially be used to control the network.
-Specifically, we use the frequency with which a species is part of the multiple minimum driver node sets---its control capacity $\phi$---as an estimation of its relative importance in driving the state of the community as a whole [@jia_control_2013].
+Specifically, we use the frequency with which a species is part of the multiple minimum driver node-sets---its control capacity $\phi$---as an estimation of its relative importance in driving the state of the community as a whole [@jia_control_2013].
 For example, a species with a control capacity $\phi_i= 1$ is a one that requires external input in every single control configuration. 
@@
 To calculate a species control capacity $\phi$, we need to enumerate all possible maximum matchings (we detail the algorithm to find all maximum matchings in the Supporting Information Section \@ref(S-all-maximum-matching)).
-However, enumerating all maximum matchings is extremely expensive from a computational perspective—a network with a couple dozen nodes could be controlled with several hundred million unique matchings.
+However, enumerating all maximum matchings is extremely expensive from a computational perspective—a network with a couple dozen species could be controlled with several hundred million unique matchings.
 To solve this problem, we employ a recently-developed algorithm that reveals the control correlations between the nodes in the graph using considerably less computational resources [@zhang_input_2016, Supporting Information Section \@ref(S-input-graph)].
-Using this algorithm, we are able to identify species that are possible control inputs—those that belong to the minimum driver node set in at least one of the possible control configurations. 
+Using this algorithm, we are able to identify species that are possible control inputs—those that belong to the minimum driver node-set in at least one of the possible control configurations. 
 One of the original contributions of our work is to extend this algorithm such that it is possible to calculate a highly accurate approximation of the control capacity $\phi_i$ of every species in the network.
@@
 However, in ecological settings, changing the state of the community as a whole is often not required or undesired. 
-Consequently, we make a second distinction between nodes based on whether they form part of possible control paths in the network and therefore are likely to influence the abundance of another species.
-We identify these species by checking whether they are classified as a superior node, this is they are at the beginning of a matched link. 
-While unmatched nodes correspond to those that should be influenced with an external control input, superior nodes correspond to those that influence other species internally. 
-Conveniently, unlike the minimum driver node set, superior nodes are the same for all control configurations and so in a network without reciprocal links (see below) the probability that a node is superior $\sigma$ is either 1 or 0.
+Consequently, we make a second distinction between species based on whether they form part of possible control paths in the network and therefore are likely to influence the abundance of another species.
+We identify these species by checking whether they are classified as *superiors*, this is they are at the beginning of a matched link. 
+While unmatched species correspond to those that should be influenced with an external control input, superior species correspond to those that influence other species internally. 
+Conveniently, unlike the minimum driver node-set, superior species are the same for all control configurations and so in a network without reciprocal links (see below) the probability that a species is superior $\sigma$ is either 1 or 0.
 <!--The end of this paragraph seems to just restate the end of the previous paragraph.
@@
 
-We calculated the species control capacity $\phi$ and the probability of being a superior node $\sigma$ for each species in our networks.
+We calculated the species control capacity $\phi$ and the probability of being superior $\sigma$ for each species in our networks.
 In the networks that contained reciprocal links (because there was no asymmetry in the dependences of a species pair), we averaged a species' $\phi$ and $\sigma$ across every possible "non-reciprocal" realisation of the network (more details can be found in the Supporting Information Section \@ref(S-reciprocal-links)).
@@
 Some species have a control capacity $\phi = 1$. 
-These species are critical to controlling community because they are part of the minimum driver node set in every control scenario. 
+These species are critical to controlling community because they are part of the minimum driver node-set in every control scenario. 
 In other words, it is not possible to change the state of the community to a desired state without managing the abundance of these species. 
@@
 
-Finally, we wanted to understand how the control capacity $\phi$ and the probability of being a superior node $\sigma$ is related to metrics of keystoness based on centrality. 
+Finally, we wanted to understand how the control capacity $\phi$ and the probability of being superior $\sigma$ is related to metrics of keystoness based on centrality. 
 To do that, for each network, we calculated the Spearman correlation matrix between these two variables and some centrality metrics commonly used to identify keystone species. 
@@
 
-The size of the minimum driver node set relative to the number of species in each network $n_D$ ranged between $n_D = `r round(min(c_m$n_D), 2)`$ and $n_D = `r round(max(c_m$n_D), 2)`$ (median `r round(median(c_m$n_D), 2)`, Figure \@ref(fig:fig-emp-controllability)a).
-We found that the relative size of the minimum driver node set was not related to any of the independent variables we evaluated. 
+The size of the minimum driver node-set relative to the number of species in each network $n_D$ ranged between $n_D = `r round(min(c_m$n_D), 2)`$ and $n_D = `r round(max(c_m$n_D), 2)`$ (median `r round(median(c_m$n_D), 2)`, Figure \@ref(fig:fig-emp-controllability)a).
+We found that the relative size of the minimum driver node-set was not related to any of the independent variables we evaluated. 
 Indeed the null model ($n_D \sim 1$) was the most parsimonious candidate model and all variables were relatively unimportant (based on the AICc; Table  \@ref(S-tab:tab-controllability-model-results)).
@@
 
-```{r fig-emp-controllability, fig.width=fig_sizes()[[1]], fig.height=fig_sizes()[[1]], fig.cap="Density plot of (a) the relative size of the minimum driver node set $n_D$ in the invaded (light) and uninvaded (dark) empirical networks.
-(b) The density distribution of the difference between the relative size of the minimum driver node set of random networks and that of empirical networks.
+```{r fig-emp-controllability, fig.width=fig_sizes()[[1]], fig.height=fig_sizes()[[1]], fig.cap="Density plot of (a) the relative size of the minimum driver node-set $n_D$ in the invaded (light) and uninvaded (dark) empirical networks.
+(b) The density distribution of the difference between the relative size of the minimum driver node-set of random networks and that of empirical networks.
 We randomised either the species visitation patterns (light line) or randomised the direction of control between a species pair (dark line).
@@
 Contribution to nestedness was the most important variable followed by visitation strength (Table \@ref(tab:tab-model-selection-table), Table \@ref(S-tab:tab-var-importance)) with species with large contribution to nestedness and large visitation strength being more likely to have a large control capacity (Figure \@ref(fig:fig-species-level)a and b).
-For the probability of being a superior node $\sigma$, the most parsimonuous models did not include any random effect Table \@ref(S-tab:tab-species-model-random), Table \@ref(S-tab:tab-model-output-species-level)).
+For the probability of being a superior species $\sigma$, the most parsimonuous models did not include any random effect Table \@ref(S-tab:tab-species-model-random), Table \@ref(S-tab:tab-model-output-species-level)).
 The most important variables were the species asymmetry and the visitation strength (Table \@ref(tab:tab-model-selection-table), Table \@ref(S-tab:tab-var-importance)). 
-Specifically, species with a positive asymmetry (this is they affect their partners more than what their partners affect them), and with a large visitation strength were more likely to be superior nodes (Figure \@ref(fig:fig-species-level)c and d).
-Furthermore, species degree was positively, but only weakly associated with both control capacity and the probability of being a superior node. 
+Specifically, species with a positive asymmetry (this is they affect their partners more than what their partners affect them), and with a large visitation strength were more likely to be superior (Figure \@ref(fig:fig-species-level)c and d).
+Furthermore, species degree was positively, but only weakly associated with both control capacity and the probability of being a superior species. 
 Remarkably, many species with a low degree, especially pollinators attained a large control capacity in their communities (Figure \@ref(S-fig:fig-species-models-degree)). 
@@
                booktabs = T, 
-               caption = "Selection table of the generalised mixed effect models of control capacity $\\phi$ and the probability of being a superior node $\\sigma$.
+               caption = "Selection table of the generalised mixed effect models of control capacity $\\phi$ and the probability of being a superior species $\\sigma$.
 Only models with a weight larger than 0.01 are shown.
@@
 
-```{r fig-species-level, fig.width=fig_sizes()[[2]]*2/3, fig.height=fig_sizes()[[1]], fig.cap="Relationship between the most important variables in the models of control capacity (a, b) and the probability of being a superior node (c, d).
+```{r fig-species-level, fig.width=fig_sizes()[[2]]*2/3, fig.height=fig_sizes()[[1]], fig.cap="Relationship between the most important variables in the models of control capacity (a, b) and the probability of being a superior species (c, d).
 The plots show the values predicted by most parsimonious model for each response variable.
@@
 The Spearman correlation ranged between `r round(min(correlations$control_capacity), 2)` (with betweeness-centrality) and `r round(max(correlations$control_capacity), 2)` (with eigen-centrality). 
-On the other hand, the probability of being a superior node $\sigma$ was slightly more similar to established centrality metrics. 
+On the other hand, the probability of being a superior species $\sigma$ was slightly more similar to established centrality metrics. 
 The Spearman correlation coefficient ranged between `r round(min(correlations$superior), 2)` (with eigen-centrality) and `r round(max(correlations$superior), 2)` (with degree; Figure \@ref(S-fig:fig-correlogram)).
@@
 We found a very strong agreement between results obtained using the complete empirical networks and those obtained by randomly removing interactions (Supporting Information Section \@ref(S-undersampling)).
-Despite removing rare interactions and species, the relative size of the minimum driver node set, the superior species, and the relative rankings of control capacity were generally maintained.
+Despite removing rare interactions and species, the relative size of the minimum driver node-set, the superior species, and the relative rankings of control capacity were generally maintained.
 Remarkably critical species in the full network were also critical in the vast majority of rarefied networks.

### 2018-06-19 paper/supp-info.Rmd
Alternative title
Figures were on top of titles

@@
 ---
-title: "Ecological network control"
+title: "Structural controllability of ecological networks"
 subtitle: "Supplementary Information"
@@
 The network in the middle panel has three minimum driver node sets $[x_1, x_2]$, $[x_1, x_3]$, and $[x_1, x_4]$.
-Finally the network in the bottom pannel has only one $[x_1]$."}
+Finally the network in the bottom pannel has only one $[x_1]$.", fig.pos="p"}
 replayPlot(fig_input_graph$plot)
@@
 ```{r fig-bidirectional, fig.height=fig_bidirectional$height, fig.width=fig_bidirectional$width,fig.cap = "In order to calculate the controllability metrics for a network with reciprocal links (left), we first decompose the network into several versions that contain no reciprocal links (right).
-As each of these networks represents a different equiprobable scenario, the controllability metrics for the network with reciprocal links are the unweighted mean of these metrics across the non-reciprocal networks."}
+As each of these networks represents a different equiprobable scenario, the controllability metrics for the network with reciprocal links are the unweighted mean of these metrics across the non-reciprocal networks.", fig.pos="p"}
 replayPlot(fig_bidirectional$plot)

### 2018-06-19 paper/reviewers-response.Rmd
Add capability to reference lines

@@
   - \usepackage{xr}
+  - \usepackage{lineno}
+  - \newcommand{\R}[1]{\label{#1}\linelabel{#1}}
+  - \newcommand{\lr}[1]{page~\pageref{#1}, line~\lineref{#1}}
   - \externaldocument[M-]{manuscript}

### 2018-06-19 paper/manuscript.Rmd
Add capability to reference lines

@@
 - \usepackage{lineno}
+- \newcommand{\R}[1]{\label{#1}\linelabel{#1}}
+- \newcommand{\lr}[1]{page~\pageref{#1}, line~\lineref{#1}}
 - \usepackage{xr}
@@
 
-Just like the centrality metrics, the information obtained by applying structural controllability depends on the ability of the network to accurately represent the ecological community. 
+\R{testing-assumptions-line}Just like the centrality metrics, the information obtained by applying structural controllability depends on the ability of the network to accurately represent the ecological community.
 We tested the sensitivity of our approach to two fundamental assumptions. 
@@
 
-We found that using visitation as a proxy for the strength of species interactions leads to similar results than those obtained using pollinator importance [regarded as an accurate measure of the pollination service to plants; Supporting Information Section \@ref(S-visitation-as-proxy); @neeman_framework_2009].
+\R{testing-asumptions-results-line} We found that using visitation as a proxy for the strength of species interactions leads to similar results than those obtained using pollinator importance [regarded as an accurate measure of the pollination service to plants; Supporting Information Section \@ref(S-visitation-as-proxy); @neeman_framework_2009].
 Importantly, we also found that structural stability is robust to incomplete sampling of interactions. 

### 2018-06-19 paper/supp-info.Rmd
Typo in chunk name
JOE uses Supporting Information

@@
 title: "Structural controllability of ecological networks"
-subtitle: "Supplementary Information"
+subtitle: "Supporting Information"
 author: "Fernando Cagua, Kate L. Wootton, Daniel B. Stouffer"
@@
 
-```{r tab-controllabillity-model-results, results = "asis", sanitize = FALSE}
+```{r tab-controllability-model-results, results = "asis", sanitize = FALSE}
 drake::loadd(controllability_models)

### 2018-06-19 paper/reviewers-response.Rmd
Use uncertainty to defend the assumption tests

@@
 
-> And finally I think mentioning the extreme uncertainty mostly seen in networks in the real world is key, how can approaches deal with this needs to be discussed.
-What do we need to think about in terms of key information to use this approach?
+> "And finally I think mentioning the extreme uncertainty mostly seen in networks in the real world is key, how can approaches deal with this needs to be discussed.
+What do we need to think about in terms of key information to use this approach?"
 
-XXX answer missing XXX
+In the previous manuscript, we discussed this uncertainty but it was buried in the Supporting Information. 
+We have now added a subsection in the Methods describing how we evaluate the impact of the uncertainty induced by using visitation as a proxy of species interdependence and that induced by incomplete sampling of rare interactions (\lr{M-testing-assumptions-line}).
+We found that the structural controllability approach is robust to these two sources of uncertainty (\lr{M-testing-assumptions-results-line}). 
+Further details can be found in the Supporting Information Section \@ref(S-visitation-as-proxy) and \@ref(S-undersampling). 
+In addition, we also included a reference to the key information needed to apply the method in the Discussion (XXX).
 

### 2018-06-19 paper/manuscript.Rmd
Use uncertainty to defend the assumption tests

@@
 To do that we compared the results obtained using visitation to two alternative metrics in a dataset that lacked invasive species [@ballantyne_constructing_2015]. 
-Specifically, we also applied the structural controllability approach to networks constructed using pollinator efficiency (which measures the pollen deposition of an interaction) and pollinator importance (which accounts for both pollen deposition and visitation and hence is regarded as a more accurate estimation of the pollination service received by plants) [@neeman_framework_2009].
+Specifically, we also applied the structural controllability approach to networks constructed using pollinator efficiency (which measures the pollen deposition of an interaction) and pollinator importance [which accounts for both pollen deposition and visitation and hence is regarded as a more accurate estimation of the pollination service received by plants; @neeman_framework_2009].
 More details in the Supporting Information Section \@ref(S-visitation-as-proxy).
-Second, because interspecific dependencies depend on the network topology and consequently on the accurate sampling of interactions, we tested the robustness of structural controllability to the undersampling of interactions.
-To do that we compared the results obtained when using the full network and when randomly removing interactions preferentially from the weakest links in the network. 
+Second, because interspecific dependencies depend on the network topology and consequently on the accurate sampling of interactions, we tested the robustness of structural controllability to the uncertainity involved with the sampling of interactions.
+To do that we compared the results obtained when using the full network and when randomly removing interactions from the weakest links in the network. 
 This effectively removed the rare interactions from the networks (more details in the Supporting Information Section \@ref(S-undersampling)).

### 2018-06-19 paper/reviewers-response.Rmd
Complete reviewers response
Close #31

@@
 ---
-title: "Ecological network control"
+title: "Structural controllability of ecological networks"
 subtitle: "JEcol-2017-0720 - Detailed response to comments"
@@
 Thanks to the Senior Editor, David Gibson, for his comments and his willingness to allow resubmission. 
-After lengthy consideration of the the two recommended alternatives, we have chosen to focus on the conceptual importance of our work in line with the editor's stated preference. 
+After lengthy consideration of the two recommended alternatives, we have chosen to focus on the conceptual importance of our work in line with the editor's stated preference. 
 To do this effectively, we ultimately ended up rewriting both the manuscript and the supplementary materials almost completely.
@@
 Second, we think that highlighting the conceptual approach offered a greater opportunity to draw attention to the strongest/most interesting aspects of the paper. 
-Namely, the contrasts between invaded and uninvaded communities and the role of invasive species, as the reviewer points out.
-
-XXX At end of last sentence above, which reviewer?
+Namely, the contrasts between invaded and uninvaded communities and the role of invasive species, as one of the reviewers points out.
 
@@
 Nevertheless, we have also rewritten the introduction and took care to be clear at explaining how this study relates to and differs from previous work. 
+In particular, we set up the stage for our work by briefly explaining how keystoneness metrics are mainly based on centrality metrics and how the proposed work differs from it.
 
-> Finally I think it is important to provide context about what kind of decisions are being made and could be informed by this approach.
+> "Finally I think it is important to provide context about what kind of decisions are being made and could be informed by this approach.
 Who is managing plant-pollinator networks and what choices would they actually be making.
 Some examples should be expanded on.
-And also how would the outputs of this work actual inform choices and guide prioritization
+And also how would the outputs of this work actual inform choices and guide prioritization"
 
-XXX answer missing XXX
+As it was explained in the previous response, in this paper we chose not to emphasize the empirical application of structural controllability. 
+We acknowledge however that the approach has potential to be applied in management and have hence added a couple of examples in the Discussion (line XXX).
 
@@
 We are thankful to the reviewer for indicating the aspects which they believe were strengths of our work.
-We maintain the methodological approach in the latest version, and have used these details to determine which elements were essential to maintain in the current revision.
+We maintain the methodological approach in the latest version and have used these details to determine which elements were essential to maintain in the current revision.
 
@@
 
-> In short, I feel that the manuscript is currently a hybrid between ecological theory and applied conservation without being fully beneficial for either of the two disciplines.
-With a few changes to the manuscript, the interpretation and presentation of the results, and a re-write of the discussion with more tangible points and concrete examples from practical experience, the manuscript has the potential to be a solid contribution to the field of applied ecology.
+We are very thankful for the insightful identification of the manuscript weaknesses and especially for clearly identifying possible pathways to fix them. 
+Following this suggestion and that of the editors, we chose to focus on how structural controllability offers a new perspective to understand the role of species in their community in the context of species "keystoneness".
+Despite this decision, we still discuss previous metrics as we found that being explicit about how the approach differs from classic centrality metrics to estimate species importance made the paper much clearer.
+These differences are discussed more in the light of network structure than in the design of efficient management interventions.
 
-> One last minor remark, the authors have overlooked some key references in the field of restoration/conservation and ecological interactions/networks, which would strengthen the manuscript further, e.g.
+> "In short, I feel that the manuscript is currently a hybrid between ecological theory and applied conservation without being fully beneficial for either of the two disciplines.
+With a few changes to the manuscript, the interpretation and presentation of the results, and a re-write of the discussion with more tangible points and concrete examples from practical experience, the manuscript has the potential to be a solid contribution to the field of applied ecology."
+
+As mentioned earlier in a response to the editor, we found that in order to address effectively all concerns, a rewrite of the whole paper was needed. 
+Although we have not gone in the applied ecology direction, we hope the current version addresses the fundamental reviewers concerns satisfactorily.
+
+> "One last minor remark, the authors have overlooked some key references in the field of restoration/conservation and ecological interactions/networks, which would strengthen the manuscript further, e.g.
 
 > * Harvey, E., Gounand, I., Ward, C.L. & Altermatt, F. (2017) Bridging ecology and conservation: from ecological networks to ecosystem function. Journal of Applied Ecology, 54, 371-379; 
-> * Devoto, M., Bailey, S., Craze, P. & Memmott, J. (2012) Understanding and planning ecological restoration of plant–pollinator networks. Ecology Letters, 15, 319-32; 
+> * Devoto, M., Bailey, S., Craze, P. & Memmott, J. (2012) Understanding and planning ecological restoration of plant-pollinator networks. Ecology Letters, 15, 319-32; 
 > * Kaiser-Bunbury, C.N., Mougal, J., Whittington, A.E., Valentin, T., Gabriel, R., Olesen, J.M.
@@
 Biological Conservation, 209, 245-252.
+
+Thanks for these references. We have used them to strengthen the Discussion (lines XXX).

### 2018-06-19 paper/manuscript.Rmd
typo

@@
 
-\R{testing-asumptions-results-line} We found that using visitation as a proxy for the strength of species interactions leads to similar results than those obtained using pollinator importance [regarded as an accurate measure of the pollination service to plants; Supporting Information Section \@ref(S-visitation-as-proxy); @neeman_framework_2009].
+\R{testing-assumptions-results-line} We found that using visitation as a proxy for the strength of species interactions leads to similar results than those obtained using pollinator importance [regarded as an accurate measure of the pollination service to plants; Supporting Information Section \@ref(S-visitation-as-proxy); @neeman_framework_2009].
 Importantly, we also found that structural stability is robust to incomplete sampling of interactions. 

### 2018-06-20 paper/manuscript.Rmd
Controllability model was not sensitive enough
And was spitting that no variable was correlated despite there being a clear correlation. It was because the range of probabilities was very small. So I ended up using a lm with logit link instead of a glm. The species level figure, the text in the results and the table in the Suppporting Information have been updated

@@
 
-The size of the minimum driver node-set relative to the number of species in each network $n_D$ ranged between $n_D = `r round(min(c_m$n_D), 2)`$ and $n_D = `r round(max(c_m$n_D), 2)`$ (median `r round(median(c_m$n_D), 2)`, Figure \@ref(fig:fig-emp-controllability)a).
-We found that the relative size of the minimum driver node-set was not related to any of the independent variables we evaluated. 
-Indeed the null model ($n_D \sim 1$) was the most parsimonious candidate model and all variables were relatively unimportant (based on the AICc; Table  \@ref(S-tab:tab-controllability-model-results)).
+The size of the minimum driver node-set relative to the number of species in each network $n_D$ ranged between $n_D = `r round(min(c_m$n_D), 2)`$ and $n_D = `r round(max(c_m$n_D), 2)`$ (median `r round(median(c_m$n_D), 2)`).
+We found that the relative size of the minimum driver node-set of invaded communities was not significantly different to that of communities that have not been invaded (Figure \@ref(fig:fig-emp-controllability)a).
+However there was an important negative relationship between $n_D$ and the network asymetry (Figure \@ref(fig:fig-emp-controllability)b). 
+Furthermore, there were also negative, albeit weaker, correlations between $n_D$ and connectance, nestedness and species richness (Table  \@ref(S-tab:tab-controllability-model-results)). 
 The $n_D$ of empirical networks did not differ to that of a null model that roughly preserved the degree distribution and fully preserved the network connectance ($p = `r sprintf('\\num{%s}', format(randomisations_test$interactions$p.value, digits = 2))`$; Figure \@ref(fig:fig-emp-controllability)b).
@@
 
-```{r fig-emp-controllability, fig.width=fig_sizes()[[1]], fig.height=fig_sizes()[[1]], fig.cap="Density plot of (a) the relative size of the minimum driver node-set $n_D$ in the invaded (light) and uninvaded (dark) empirical networks.
+```{r fig-emp-controllability, fig.width=fig_sizes()[[1]], fig.height=fig_sizes()[[1]]*1.5, fig.cap="Density plot of (a) the relative size of the minimum driver node-set $n_D$ in the invaded (light) and uninvaded (dark) empirical networks.
 (b) The density distribution of the difference between the relative size of the minimum driver node-set of random networks and that of empirical networks.
@@
 
-g <- fig_emp_controllability %>%
-  purrr::map(ggplot2::ggplotGrob)
-gb <- rbind(g[[1]], g[[2]], size = "first")
-gb$widths <- grid::unit.pmax(g[[1]]$widths, g[[2]]$widths)
-grid::grid.newpage()
-grid::grid.draw(gb)
+cowplot::plot_grid(plotlist = fig_emp_controllability, 
+                   ncol = 1, 
+                   align = "v")
 ```

### 2018-06-20 paper/supp-info.Rmd
Controllability model was not sensitive enough
And was spitting that no variable was correlated despite there being a clear correlation. It was because the range of probabilities was very small. So I ended up using a lm with logit link instead of a glm. The species level figure, the text in the results and the table in the Suppporting Information have been updated

@@
     stringr::str_replace("weighted_NODF", "NODF") %>%
-    stringr::str_replace("n_sp", "n_s") %>%
-    stringr::str_replace("web_asymmetry", "AS_n") %>%
-    stringr::str_replace("interaction_strength_asymmetry", "AS_s") %>%
+    stringr::str_replace("n_sp", "$n_s$") %>%
+    stringr::str_replace("web_asymmetry", "$AS_n$") %>%
+    stringr::str_replace("interaction_strength_asymmetry", "$AS_s$") %>%
     stringr::str_replace(stringr::fixed("~"), "\\sim ")
@@
 
-AICcmodavg::aictab(controllability_models) %>% 
-  dplyr::mutate(Modnames = replace_terms(Modnames)) %>% 
-  dplyr::select(Modnames, AICc, Delta_AICc, Cum.Wt) %>%
-  dplyr::filter(Delta_AICc <= 8) %>%
-  dplyr::rename(model = Modnames, `$\\Delta AICc$` = Delta_AICc, `$AICc$` = AICc, `Cum. Weight` = Cum.Wt) %>%
-  dplyr::mutate(model = paste0("$", model, "$")) %>% 
+c_mod_table <- MuMIn::model.sel(controllability_models) %>%
+  dplyr::filter(weight > 0.01) %>%
+  dplyr::select(-logLik, - AICc)
+
+names(c_mod_table) <- replace_terms(names(c_mod_table))
+
+c_mod_table %>% 
+  dplyr::mutate(weight = round(weight, 2)) %>%
   knitr::kable("latex", 

### 2018-06-20 code/calc_ntw_properties.R

@@ -26,7 +26,7 @@ calc_ntws_properties <- function(x, properties = c("connectance",
 #'
 calc_ntw_properties <- function(x, properties){
   types <- igraph::V(x)$type %>% unique()
-	keep_largest_component(x)
+	# keep_largest_component(x)
 	n_pla <- sum(igraph::V(x)$type == types[1])
 	n_pol <- sum(igraph::V(x)$type == types[2])
 	bipartite::networklevel(igraph::as_incidence_matrix(x, 

### 2018-06-20 code/controllability_models.R

@@ -1,5 +1,8 @@
 assemble_controllabillity_df <- function(controllability, network_properties, metadata){
-  controllability %>%
+  network_properties %<>% 
+    dplyr::mutate_if(is.numeric, scale)
+  
+    controllability %>%
     filter_networks_df(metadata) %>%
     dplyr::inner_join(metadata, by = "net_name") %>%
     dplyr::inner_join(network_properties, by = "net_name") %>%
@@ -11,13 +14,18 @@ assemble_controllabillity_df <- function(controllability, network_properties, me
 }
 # drake::loadd(controllability, network_properties, metadata)
 
+# controllability_model_data %>%
+#   ggplot(aes(x = web_asymmetry, y = qlogis(n_D))) + 
+#   geom_point() +
+#   geom_smooth(method = "lm")
+
 fit_controllability_models <- function(controllability_model_data){
   vars = c("n_sp", "connectance", "web_asymmetry", "interaction_strength_asymmetry", "weighted_NODF", "inv", "study")
   # extra = " + (1 | study)"
   suppressWarnings({
-    models <- get_model_formulas("n_D ~ ", vars) %>% 
+    models <- get_model_formulas("I(qlogis(n_D)) ~ ", vars) %>% 
       `names<-`(., .) %>%
-      purrr::map(~glm(as.formula(.), data = controllability_model_data, family = "binomial"))
+      purrr::map(~lm(as.formula(.), data = controllability_model_data))
   })
   models
 }

### 2018-06-20 code/fig_emp_controllability.R

@@ -1,4 +1,4 @@
-make_fig_emp_contollability <- function(controllability, randomisations_df, metadata){
+make_fig_emp_contollability <- function(controllability, randomisations_df, metadata, controllability_models, controllability_model_data, network_properties){
   require(ggplot2)
   d <- controllability %>% 
     filter_networks_df(metadata) %>%
@@ -30,6 +30,30 @@ make_fig_emp_contollability <- function(controllability, randomisations_df, meta
     dplyr::group_by(randomisation) %>%
     dplyr::summarise(delta_n_D = median(delta_n_D, na.rm = T))
   
+  cont_model <- controllability_models[[which.min(controllability_models %>% purrr::map(AICcmodavg::AICc))]]
+  
+  original_web_asymmetry <- network_properties %>%
+    dplyr::select(net_name, web.asymmetry) 
+  
+  df_cc <- controllability_model_data %>%
+    modelr::add_predictions(cont_model) %>% 
+    dplyr::inner_join(original_web_asymmetry, by = "net_name") %>%
+    dplyr::mutate(web.asymmetry = scale(web.asymmetry)) %>%
+    dplyr::mutate(web_asymmetry_o = unscale(web.asymmetry))
+  
+  p3 <- df_cc %>%
+    ggplot(aes(x = web_asymmetry_o, y = pred)) +
+    geom_point(shape = 21, size = 1, colour = "grey50", alpha = 0.75) +
+    geom_smooth(method = "lm", 
+                se = T, 
+                colour = "black", 
+                size = 0.5) +
+    scale_y_continuous(labels = function(x) round(plogis(x), 2)) +
+    labs(title = latex2exp::TeX("(b) Effect of network asymmetry on $n_D$"), 
+         x = "network asymmetry", 
+         y = latex2exp::TeX("$n_D$")) +
+    base_ggplot_theme()
+
   p2 <- r %>% 
     ggplot(aes(x = delta_n_D, color = randomisation)) +
     stat_density(geom = "line", position = position_identity(), size = 0.5) +
@@ -41,10 +65,10 @@ make_fig_emp_contollability <- function(controllability, randomisations_df, meta
     theme(legend.position = c(1,1.15), 
           legend.justification = c(1,1),
           legend.background = element_rect(fill = "NA"), legend.key.size = unit(0.15, "in")) +
-    labs(title = expression(paste("(b) Difference between random and empirical ", n[D])), 
[…]

### 2018-06-20 main.R

@@ -58,7 +58,7 @@ example_plots_plan <- drake::drake_plan(
   fig_small_network = make_small_network(networks),
   fig_input_graph = make_fig_input_graph(en_direction, en_star, en_chain), 
   fig_bidirectional = make_fig_bidirectional(en_chain), 
-  fig_emp_controllability = make_fig_emp_contollability(controllability, randomisations_df, metadata), 
+  fig_emp_controllability = make_fig_emp_contollability(controllability, randomisations_df, metadata, controllability_models, controllability_model_data, network_properties), 
   fig_correlation = make_fig_correlation(sl_char_corr), 
   fig_control_capacity = make_fig_control_capacity(species_model_cc, species_model_superior),
   fig_structural_stability = make_fig_structural_stability(critical_sp_df), 

### 2018-06-22 paper/manuscript.Rmd
Add histogram of control capacity and move superior model plots to supp

@@
 ```{r fig-emp-controllability, fig.width=fig_sizes()[[1]], fig.height=fig_sizes()[[1]]*1.5, fig.cap="Density plot of (a) the relative size of the minimum driver node-set $n_D$ in the invaded (light) and uninvaded (dark) empirical networks.
-(b) The density distribution of the difference between the relative size of the minimum driver node-set of random networks and that of empirical networks.
+(b) Relationship between the asymmetry plant/pollinator richness and $n_D$.
+The plot shows the values predicted by the most parsimoniouls model.
+(c) The density distribution of the difference between the relative size of the minimum driver node-set of random networks and that of empirical networks.
 We randomised either the species visitation patterns (light line) or randomised the direction of control between a species pair (dark line).
@@
 drake::loadd(fig_emp_controllability)
-
 cowplot::plot_grid(plotlist = fig_emp_controllability, 
@@
                    align = "v")
+```
+
+```{r}
+drake::loadd(sl_characteristics)
+crit <- sl_characteristics %>% 
+  filter_networks_df(metadata) %>%
+  dplyr::group_by(net_name) %>%
+  dplyr::summarise(n_crit = sum(control_capacity == 1), 
+                   n_sp = n()) %>%
+  dplyr::mutate(p_crit = n_crit/n_sp)
+
+pcrit_ran <- range(crit$p_crit)
+ncrit_ran <- range(crit$n_crit)
+pcrit_med <- median(crit$p_crit)
 ```
@@
 
-```{r fig-species-level, fig.width=fig_sizes()[[2]]*2/3, fig.height=fig_sizes()[[1]], fig.cap="Relationship between the most important variables in the models of control capacity (a, b) and the probability of being a superior species (c, d).
+```{r fig-species-level, fig.width=fig_sizes()[[2]]*2/3, fig.height=fig_sizes()[[1]], fig.cap="Density plot of the control capacity $\\phi$ of (a) plants and (b) pollinators.
+(c, d) Relationship between the most important variables in the models of control capacity.
 The plots show the values predicted by most parsimonious model for each response variable.
-The model for control capacity include a random effect for the trophic guild , while the model of superior probability does not include any random effect that distinguish between plants and pollinators.
+The model included a random effect for the trophic guild and hence trends of plants and pollinators are shown separately.
 The invasive species are depicted with solid orange circles."}

### 2018-06-22 paper/supp-info.Rmd
Add histogram of control capacity and move superior model plots to supp

@@
 
+```{r fig-superior, fig.width=fig_sizes()[[2]], fig.height=fig_sizes()[[1]]/2, fig.cap = "Relationship between the most important variables in the models of superior probability.
+The plots show the values predicted by most parsimonious model.
+Invasive species are depicted with solid orange circles."}
+drake::loadd(fig_superior)
+cowplot::plot_grid(plotlist = fig_superior, ncol = 2)
+```
+
 ```{r fig-species-models-degree, fig.width=fig_sizes()[[2]], fig.height=fig_sizes()[[1]]/2, fig.cap = "Relationship between degree and (a) the control capacity and (b) the probability of being a superior node.

### 2018-06-22 code/fig_keystonness.R

@@ -143,7 +143,7 @@ p2 <- plot_df_sd %>%
 }
 # drake::loadd(sl_char_corr, sl_characteristics, metadata)
 # drake::loadd(species_model_cc, species_model_superior)
-make_fig_control_capacity <- function(species_model_cc, species_model_superior){
+make_fig_control_capacity <- function(species_model_cc, sl_characteristics){
   require(ggplot2)
  
   cc_model <- species_model_cc$fixed[[which.min(species_model_cc$fixed %>% purrr::map(AICcmodavg::AICc))]]
@@ -188,7 +188,7 @@ make_fig_control_capacity <- function(species_model_cc, species_model_superior){
                       name = "", 
                       labels = c("plants", "pollinators")) +
     base_ggplot_theme() +
-    labs(title = "(a)", 
+    labs(title = "(c)", 
          x = "contribution to nestedness", 
          y = latex2exp::TeX("control capacity ($\\phi$)")) +
     theme(legend.position = c(1, 0),
@@ -222,7 +222,7 @@ make_fig_control_capacity <- function(species_model_cc, species_model_superior){
                       labels = c("plants", "pollinators")) +
     scale_x_log10() + 
     base_ggplot_theme() +
-    labs(title = "(b)", 
+    labs(title = "(d)", 
          x = "visitation strength", 
          y = latex2exp::TeX("control capacity ($\\phi$)")) +
     theme(legend.position = c(1, 0),
@@ -231,7 +231,58 @@ make_fig_control_capacity <- function(species_model_cc, species_model_superior){
           legend.key.size = unit(0.15, "in"),
           plot.margin = unit(c(0.5, 0.5, 0.5, 0.5), "mm"))
   
+ 
+  
+  p5 <- sl_characteristics %>%
+    filter_networks_df(metadata) %>%
+    dplyr::filter(guild == "pla") %>%
+    ggplot(aes(x = control_capacity, colour = guild)) +
+    stat_density(geom = "line", 
+                 bw = "SJ", 
+                 show.legend = FALSE) +
+    geom_point(aes(x = 1, y = 0), 
+               fill = my_pallete()$dark_orange,
+               colour = "black", 
+               shape = 21,
+               size = 1) +
+    scale_color_manual(values = my_pallete()$dark_orange) +
+    base_ggplot_theme() +
+    labs(title = "(a) Control capacity of plants", 
[…]

### 2018-06-22 main.R

@@ -60,7 +60,8 @@ example_plots_plan <- drake::drake_plan(
   fig_bidirectional = make_fig_bidirectional(en_chain), 
   fig_emp_controllability = make_fig_emp_contollability(controllability, randomisations_df, metadata, controllability_models, controllability_model_data, network_properties), 
   fig_correlation = make_fig_correlation(sl_char_corr), 
-  fig_control_capacity = make_fig_control_capacity(species_model_cc, species_model_superior),
+  fig_control_capacity = make_fig_control_capacity(species_model_cc, sl_characteristics),
+  fig_superior = make_fig_superior(species_model_superior),
   fig_structural_stability = make_fig_structural_stability(critical_sp_df), 
   fig_models_degree = make_fig_models_degree(species_model_cc, species_model_superior),
   fig_rho_sensitivity = make_fig_rho_sensitivity(structural_rho_correlation, rho_feasibility),

### 2018-06-22 paper/manuscript.Rmd
First draft of discussion

@@
 
+# Abstract
+
+\clearpage
+
 # Introduction
@@
 With these networks, we first ask whether there are differences between the controllability of invaded and uninvaded networks. 
-This question is motivated by the difficulties commonly encountered with invasive-species eradication and ecosystem restoration [@woodford_confronting_2016].
 <!--STOUFFER: I'd remove the grounded in.... stuff, but that's just me.  CAGUA: I don't like it either. I tried removing but then it feels like this question is coming out of the blue.-->
@@
 
+Our main goal was to understand the role that species play at both modifying the abbundance of the species they interact with and the state of the community as a whole. 
+To achieve that goal we applied *structural controllability*, a field at the intersection between control and complex theory that allow us to obtain two key pieces of information: the *controllability* of a network and a species *control capacity*.
+
+Empirical observations indicate that steering the state of some communities—for example during ecosystem restoration or invasive species removal—can be a very difficult task [@woodford_confronting_2016].
+Despite the large number of empirical examples, to date there is no thoretical basis that explains this difficutlies. 
+Here, we show that the *controllability* of a network provides a way to quantify this intrinsic difficulty of controlling an ecological community and the differences among them. 
+The controllability of a network is given by the relative size of the minimum driver node-set, $n_D$. 
+In other words, controllability is related to the smallest proportion of species whose abundances need to be directly managed in order to achieve full control of the community (to be able to steer the community to an arbitrary ecological state).
+We found that in the pollination networks from our dataset the median $n_D$ equals `r round(median(c_m$n_D),2)`. 
+This value is fairly high when compared to several other complex systems in which structural controllability has been applied. 
+For instance, in most social, power transmission, internet, neuronal, and even metabolic networks $0.1 < n_D < 0.35$ and, at least withing the biological realm, only gene regulation networks appear to achieve similar levels of controllability [@liu_controllability_2011].
+Although these results indicate that fully controlling ecological networks might currently be out of reach for all but the smallest communities [@motter_networkcontrology_2015], structural controllability might provide solid theoretical explanation to the many difficulties encountered in the management and restoration of natural communities.
+
+Structural controllability might also offer novel means to compare ecological networks, particularly when exploring the relationship between network structure and stability. 
+Even though all studied communities appear to be hard to control, we still found significant variation between them—the relative size of the minimum driver node set ranged between $n_D = `r round(min(c_m$n_D), 2)`$ and `r round(max(c_m$n_D), 2)`.
+Interestingly, we found that the controllability of a network is not related to their invasion status. 
+Instead, we found that, despite our relatively small sample size, these differences in controllability may stem from differences in structure. 
+Specifically, networks with a larger asymmetry between plant and pollinator species richness and with larger connectances were more likely to have higher values of $n_D$. 
+In addition, we found that the $n_D$ of empirical networks was indistinguishable from that of network randomisations that roughly maintained the degree distribution, but was significantly different to those in which the patterns of dependence were broken.
+All together, these results suggest that network controllability is almost completely constrained by the patterns of species richness at each trophic guild and their degree distributions [@melian_complex_2002; @bluthgen_specialization_2007].
+These two factors, in turn govern the asymmetric nature of mutual dependences-which constitute the foundations of structure and stability in mutualistic networks [@bascompte_asymmetric_2006; @memmott_tolerance_2004; @astegiano_robustness_2015].
+
+Structural controllability not only can offer valuable insight at the community level, but, by measuring a species *control capacity*, here we show that it can also be used to better understand the role of individual species.
+The group of species that compose the minimum driver node-set $n_D$ is often not unique. 
+This means that there are many species combinations with which it is possible to fully control a network
+Each of these combinations represents a control configuration. 
+Some species belong to these combinations more often that others. 
+We call this property a species control capacity $\phi$. 
+The higher a species control capacity, the higher the likelyhood that they would need to be directly managed to change (or maintain) the ecological state of their communities. 
+A small fraction of species in each network (between `r round(pcrit_ran[1]*100)` and `r round(pcrit_ran[2]*100)`%) had a control capacity of $\phi = 1$. 
+We call these *critical* species. 
+Because critical species are driver in every single control configuration it is unlikely that any attempt to steer the community to a different state will be successful without directly managing the abbundances of these species.
+Interestingly, although the average control capacity of pollinators was higher than that of plants, the group of critical species was exclusively composed by plants.
+
+Because of the presumed relationship between central and keystone species, we expected control capacity to be somewhat correlated with some metrics of centrality. 
+However, despite the influence that critical species might have into the state of the community, a large control capacity is not necessarly accompained by a large centrality. 
+Indeed,  the correlation coefficients between control capacity and five different centrality metrics was low and both specialist and generalist species could play an important role at changing the abbundances of other species.
+
+Althogh control capacity was poorly predicted by centrality, we found that it was strongly related to a species contribution to nestedness and, to a smaller extent, the species strength. 
+The species strength (the sum of visits that a species receivers or performs) quantifies how strongly a species interacts with its partners. 
+Indirectly, it is also a reflection of the species' abundance, and therefore its relationship with control capacity can be explained by the fact that species with large populations are anticipated to have a larger effect in the community than less common species.
+
+The strong relationship between control capacity and nestedness is more revealing in particular because we also found that critical species play a major role at enabling the coexistence of other species in their community.
+Previous studies suggest that nestedness is key to the persistence of pollination networks as it minimises species competition—and therefore promotes species coexistence—and confers robustness to species extinctions in the community.
+Using two completely different approaches, our results suggest that species that are more likely to determine the state of the community might also be more likely to contribute the most at "maintaining the organization and diversity of their ecological communities", one of the hallmarks of keystone species [@mills_keystone-species_1993].
+
+Invasive species have been previously found to exacerbate the asymmetries in their communities [@aizen_invasive_2008; bartomeus_contrasting_2008-1; @henriksson_strong_2016]. 
+Although this might be reflected on differences both at the community and the species level, we found that invasive plants are not inherently different to their native counterparts [@emer_species_2016; @stouffer_how_2014].
+Invasive plants, just like any other mutualist in our data set, tended to attain a high control capacity proportional to the degree to which they contribute to nestedness and interact strongly with other species.
+Nevertheless 
+Previous studies have found that supergeneralists, like invasive species, play a central role in their networks (Vilà et al. 2009; Palacio, Valderrama-Ardila & Kattan 2016). 
+XXXOur results take this one step further and indicate that dependence strength, rather than generalism or other metrics of centrality, is the factor that best explains the cascading effects a species could trigger on its community.
+
+The structural controllability approach, just like classic centrality metrics is sensitive to the uncertainity associated with the sampling of ecological interactions. 
+Our sensitivity analyses suggest that structural controllability is robust to at least two sources of uncertainity: when interactions are only sampled incompletly and when multiple metrics could be used used to quantify the strength of associations between species.
+
+Another common critique to structural controllability is that it is based on the premise that the system can be described using linear functional responses [@cowan_nodal_2012]. 
+This is indeed a current limitation, as we know that ecological systems are often best described using different nodal dynamics. 
+However, we are not discouraged by its application for three main reasons. 
+First, it has been shown that when the parameters that describe the mechanisms of self-regulation are not independent from each other, as is ofthen the case in ecological networks, the principles of structuctural controllability can still be applied [@zhao_intrinsic_2015].
+Second, although non-linear dynamics render structural controllability unsufficient to assure full control an ecological system, it is still a necessary step to achieve that goal. 
+Finally, by accounting for network dynamics (even if in a simple way) it incorporates more ecological realism than classical centrality metrics and hence is more likely to provide useful information even in the extreme scenario in which the state of a community depends almost exclusively on nodal dynamics rather than on the topology of their interactions.
+
+From an applied ecology perspective, @paine_note_1969 showed nearly 50 years ago that one species can dominate the state of its community. 
+Structural controllability suggests that this situation might be the exception rather than the rule, at least when were interested in *managing* the state of 
+community and not just on inducing a change. 
+Our results also provide support to the idea that management approaches focused on ecosystem processes and interactions might be more effective than traditional single-species approaches [@harvey_bridging_2017].
+A `r round(sum(crit$n_crit > 1)/nrow(crit)*100)`% of our communities contained more than one critical species. 
+Approaches identify keystone species and ultimately prioritise species for conservation are still useful at predicting the consequences of single species removals or reintroductions [@pires_friendship_2017; @devoto_understanding_2012], but effective management and restoration of ecological communities is likely to require more than a ranking of species based on their traits or centrality.
+
+<!-- Biggest lesson is that changing the state of the community in a requires concerted action by several species, not just changes in the abbundance of one species.  -->
+
+<!-- Control theory is flexible and awknoledges that there are multiple ways to achieve changes in the state of the community.  -->
+<!-- Managing the most central species might not be suficient or even required to achieve that goal.  -->
+
+<!-- Even if full control is not possible or not desired we learnt that there are critical species, those that no matter what the management strategy will need to be managed if one wants effective control of the populations in the ecological community.
+-->
+
+<!-- Centrality species concept is limited because we onl -->
+
+<!-- We propose structural controllbility as a metric that can be used to compare ecological systems both in a theoretical and applied context. -->
+
 # References

### 2018-06-22 paper/manuscript.Rmd
Improve Introduction so it fits better with the discussion

@@
 Within community ecology, a complex-systems approach has led to the development of a variety analytical and simulation tools with which to compare and contrast the roles of species embedded in a network of interactions [@guimera_cartography_2005; @bascompte_assembly_2009; @stouffer_evolutionary_2012; @coux_linking_2016].
-A particularly relevant dimension of any species' role is its ability to alter the abundance of other species in the community—since changes of this nature impact ecosystem function and biodiversity, and might have knock-on effects on other processes and services.
-This ability is often referred to as a species' "keystoneness" [@mills_keystone-species_1993].
+A particularly relevant dimension of any species' role is its ability to alter the abundance of other species in the community and in turn, modifying the state of the community—since changes of this nature impact ecosystem function and biodiversity, and might have knock-on effects on other processes and services.
+This ability is sometimes referred to as a species' "keystoneness" [@mills_keystone-species_1993].
 
-A significant proportion of the network tools used to estimate species roles in this context rely on the calculation of a species' centrality—a relative ranking of its importance that stems from social network research [@noah_e._friedkin_theoretical_1991].
-Generally speaking, central species tend to be present in more food chains, are better connected, and have broader niches.
-Centrality metrics have been shown to be useful tools to rank species in regards to their risk of extinction or the potential secondary extinctions after the species is lost [@dunne_network_2002; @kaiser-bunbury_robustness_2010].
-Although there are some differences among centrality metrics—as each of them emphasizes a different aspect of a species' interaction patterns—they all tend to be correlated with the way species participate in the network's food chains [@jordan_quantifying_2007].
-Because of this property, centrality metrics have been often used to identify keystone species.
+A significant proportion of the network tools used to estimate species roles in this context rely on the calculation of a species' centrality—a relative ranking of its positional importance that stems from social network research [@noah_e._friedkin_theoretical_1991].
+Generally speaking, central species tend to be better connected and consequently are more likely to participate in the network's food chains. 
+As species that participate in more food chains are assumed to be more likely to affect the abundance of other species, centrality metrics have often been used to identify keystone species in the community [@jordan_quantifying_2007].
+Centrality metrics have been shown to be useful tools to rank species in regards to the potential they have on altering the abundances of other species; especially in regards to possible secondary extinctions after the species is lost [@dunne_network_2002; @kaiser-bunbury_robustness_2010].
 
-This relationship between centrality and keystoneness relies on an important assumption. 
-That that there is a link between a given species' centrality and its ability to alter the abundances of other species. 
-The basis of this assumption is reasonably clear: a major justification for representing ecological communities as networks is the idea that the abundance of a species depends on the abundance of its neighbours (those species with which it interacts) and, by extension, the abundance of its neighbours' neighbours, and so on.
-By definition, more central species are better connected and hence should be more likely to affect the abundance of other species in the network.
-
-Despite being conceptually intuitive, the relationship between centrality and keystoneness is largely phenomenological. 
-<!-- Daniel: I'm struggling to find an example of this idea. Does anything come to your mind? -->
-Often, dramatic changes in ecosystem functioning can also occur without complete removal of a species. 
-Hence, we expect the usefulness of centrality to diminish as we move beyond species removal towards understanding how species relate to the state and stability of the ecosystem. 
-Particularly so, when the state of an ecosystem is underpinned by more than a single species. 
-As a result, community ecology could arguably benefit from an alternative more mechanistically-grounded approach to understand how species affect each other's abundance.
+Despite being conceptually intuitive, the relationship between centrality and the state of the community is largely phenomenological. 
+On one hand, dramatic changes in ecosystem functioning can also occur without complete removal of a species. 
+On the other, we are often more interested in a specific state of the community that might be desirable to attain (or preserve) because of its biodiversity, resilience, functioning, or the services it provides.
+In these cases, it might not enough to understand which species may cause a change in the community. 
+Rather we need to understand first, how the structure of the network can be harnessed to achieve the desired state and which species may play the largest role in this process. 
+When the state of a community is underpinned by more than a single species and we move beyond single-species removals, we expect the usefulness of centrality to diminish. 
+As a result, community ecology could arguably benefit from an alternative, perhaps more mechanistically-grounded, approach to understand how species affect each other's abundance.
 
@@
 However, community and population dynamics can be modelled in innumerable ways, and empirical support for one versus another is often still ambiguous. 
-The alternative approach should, therefore, acknowledge ecosystem dynamics, but without being overly dependent on the particular choices of how they are characterised.
+The alternative approach should, therefore, ideally acknowledge ecosystem dynamics, but without being overly dependent on the particular choices of how they are characterised.
 Among the various possibilities, *control theory* appears to be a strong candidate [@isbell_human_2013]. 
 Control theory is a widely-studied branch of engineering used to determine and supervise the behaviour of dynamical systems [@motter_networkcontrology_2015]. 
-It is inherently designed to deal with system feedbacks and its application has recently been expanded to complex networks [@liu_control_2016]. 
+It is inherently designed to deal with system feedbacks and its application has recently been expanded to complex networks [@lin_structural_1974;  @liu_control_2016]. 
 In concordance with long-standing ecological questions, advances in this field have established a clear link between the structure of the network and the way nodes affect each other. 
@@
 At its fundamental level, control theory first determines whether a system is controllable or not; that is, it asks if a system can be driven to a desired state within a finite amount of time. 
-Although the controllability of a network is a whole-system property, it has been recently shown that asking for the controllability of a complex-system is equivalent to finding a particular set of nodes: the set with which is possible to control the state of the whole network.
+Although the controllability of a network is a whole-system property, it has been recently shown that asking for the controllability of a complex-system is equivalent to finding a particular set of nodes: the set with which is possible to control the state of the whole network [@liu_control_2016].
 Notably, control theory is consistent with the observation that to change the state of a network, more than a ranking, we need a set of nodes.
@@
 With these networks, we first ask whether there are differences between the controllability of invaded and uninvaded networks. 
-<!--STOUFFER: I'd remove the grounded in.... stuff, but that's just me.  CAGUA: I don't like it either. I tried removing but then it feels like this question is coming out of the blue.-->
 We then expand existing methods from control theory to effectively link the *controllability* of a network with the role of particular species.
-We ask—from a control-theoretic perspective—whether there are key differences between species in the role they play at driving the population of other members of the community and identify the ecological factors related to these differences.
-This allows us to identify species that are critical to changes in the ecosystem state and show that they have a larger than expected impact on the structural stability of the community. 
-Finally, we compare the proposed approach to current methods based on species centrality and show how these methods are indeed valuable but ultimately paint a limited picture in regards to the dynamic "keystoneness" of a species.
+We ask—from a control-theoretic perspective—whether there are key differences between species in the role they play at driving the state of the community and explore the ecological factors related to these differences.
+This allows us to identify species that might be critical for network control and show that they have a larger than expected impact on the structural stability of the community. 
+Finally, we compare the proposed approach to current methods based on species centrality and show how these methods are indeed valuable but ultimately paint a limited picture in regards to the "keystoneness" of a species and its role at supporting the diversity of its community.
 

### 2018-06-22 paper/manuscript.Rmd
Minor edits to methiods

@@
 Sometimes there is no observed asymmetry between species pairs ($d_{ij}=d_{ji}$), and we cannot infer a dominant direction of control. 
-When this occurs, we deem both species to be equally likely to affect each other and form a reciprocal interaction between them, this is a link from *i* to *j* and another from *j* to *i*. 
+When this occurs, we deem both species to be equally likely to affect each other and form a reciprocal interaction between them (a link from *i* to *j* and another from *j* to *i*). 
 By basing the direction of the links on the asymmetry of their dependence, we are able to generate a network that is consistent with the dynamics of the community while satisfying the requirements of structural controllability.
@@
 This simple metric provides a general indication of how difficult controlling a network might be, as systems that require a large number of external inputs to be fully controlled are intuitively more difficult or costly to manage.
-For instance, achieving full control in a "network" in which species do not interact at all is relatively difficult as we would require an intervention for every single species. 
+For instance, achieving full control in a "network" in which species do not interact at all is relatively more difficult as we would require an intervention for every single species. 
 Conversely, the structure of a linear trophic chain can be harnessed to achieve full control using just one intervention targeted the top species; the control signal would then cascade through the trophic levels and reach other species in the community.
-Specifically, drawing from the structural-controllability literature, we use the size of the minimum driver node-set relative to the total number of species $n_D = \frac{D}{N}$ as a measure of the extent to which the network structure can be harnessed to control the community.
+Specifically, drawing from the structural-controllability literature, we use the size of the minimum driver node-set relative to the total number of species $n_D = \frac{D}{N}$ as a measure of the *controllability* of a network—the extent to which the network structure can be harnessed to control the community.
 In an ecological context, external inputs can be thought of as management interventions that modify the abundance of a particular species. 
@@
 
-After finding the minimum driver node-set in each of our networks, we wanted to test whether invasion status or other predictors are correlated to this metric of controllability. 
+After finding the minimum driver node-set in each of our networks, we wanted to test whether invasion status or other predictors are correlated to controllability. 
 We, therefore, use a set of generalised linear models (with binomial error structure). 
-The response variable was the size of the minimum driver node-set $n_D$ of the twenty empirical networks (ten invaded and ten uninvaded). 
-The independent variables evaluated were the invasion status, the network connectance, the network nestedness (NODF) the number of species [since one might naively expect to see a negative relationship between richness and controllability; @menge_indirect_1995], the network asymmetry (an indication of the balance between plant and pollinator diversity), and the interaction strength asymmetry [the asymmetry on the dependences between trophic levels; @bluthgen_specialization_2007].
+The response variable was the size of the minimum driver node-set $n_D$ of the twenty empirical networks (ten invaded and ten uninvaded) and we included invasion status as a predictor. 
+We also include the network connectance, the network nestedness (NODF) the number of species [since one might naively expect to see a negative relationship between richness and controllability; @menge_indirect_1995], the network asymmetry (an indication of the balance between plant and pollinator diversity), and the interaction strength asymmetry [the asymmetry on the dependences between trophic levels; @bluthgen_specialization_2007].
 Models were compared using the Akaike Information Criterion for small sample sizes (AICc).
@@
 Specifically, we used two null models each with 99 randomisations per network. 
-In the first, we followed @vazquez_species_2007 and maintained the connectance of the network but randomised the visits across species such that the species-specific relative probabilities of interactions were maintained; we then calculated the direction of control and the corresponding size of the minimum driver node-set.
+In the first, we followed @vazquez_species_2007 and maintained the connectance of the network but randomised the visits across species such that the relative probabilities of interactions were maintained.
+We then calculated the direction of control and the corresponding size of the minimum driver node-set, $n_D$. 
 For the second null model, we used the empirical directed network and randomly shuffled the direction of control between a species pair.
@@
 
+ND is a measure of the extent to which network structure can be harnessed to drive the state of the community.
+
 Empirical observations indicate that steering the state of some communities—for example during ecosystem restoration or invasive species removal—can be a very difficult task [@woodford_confronting_2016].

### 2018-06-26 paper/manuscript.Rmd
NAs in table are shown shown are empty spaces
Lines were ugly
Add abstract structure
Load metadata at the beginning of the document
Changes to intro

@@
                       warning = FALSE)
-options(knitr.kable.NA = '---')
+options(knitr.kable.NA = '')
+library(ggplot2)
+```
+
+```{r load-metadata}
+drake::loadd(metadata)
+lop <- dplyr::filter(metadata, study == "lopezaraiza") %>% 
+  dplyr::mutate(size = n_pla + n_pol) %$% size %>% summary() 
+bar <- dplyr::filter(metadata, study == "bartomeus") %>% 
+  dplyr::mutate(size = n_pla + n_pol) %$% size %>% summary() 
 ```
@@
 
-\newpage
+\clearpage
 
@@
 
-\clearpage
+1. Background
+
+2. Methods
+
+3. Results
+
+4. Synthesis
 
@@
 Within community ecology, a complex-systems approach has led to the development of a variety analytical and simulation tools with which to compare and contrast the roles of species embedded in a network of interactions [@guimera_cartography_2005; @bascompte_assembly_2009; @stouffer_evolutionary_2012; @coux_linking_2016].
-A particularly relevant dimension of any species' role is its ability to alter the abundance of other species in the community and in turn, modifying the state of the community—since changes of this nature impact ecosystem function and biodiversity, and might have knock-on effects on other processes and services.
+A particularly relevant dimension of any species' role is its ability to alter the abundance of other species and the state of the community—since changes of this nature can have knock-on effects on ecosystem function, diversity, processes, and services.
 This ability is sometimes referred to as a species' "keystoneness" [@mills_keystone-species_1993].
@@
 Generally speaking, central species tend to be better connected and consequently are more likely to participate in the network's food chains. 
-As species that participate in more food chains are assumed to be more likely to affect the abundance of other species, centrality metrics have often been used to identify keystone species in the community [@jordan_quantifying_2007].
-Centrality metrics have been shown to be useful tools to rank species in regards to the potential they have on altering the abundances of other species; especially in regards to possible secondary extinctions after the species is lost [@dunne_network_2002; @kaiser-bunbury_robustness_2010].
+Because species that participate in more chains are assumed to be more likely to affect the abundance of other species, centrality metrics have often been used to identify keystone species in the community [@jordan_quantifying_2007].
+Centrality metrics have been shown to be useful tools to rank species in regards to their potential to alter the abundances of other species; especially when estimating secondary extinctions that may follow the loss of a species [@dunne_network_2002; @kaiser-bunbury_robustness_2010].
 
@@
 On one hand, dramatic changes in ecosystem functioning can also occur without complete removal of a species. 
-On the other, we are often more interested in a specific state of the community that might be desirable to attain (or preserve) because of its biodiversity, resilience, functioning, or the services it provides.
-In these cases, it might not enough to understand which species may cause a change in the community. 
+On the other, we are often interested in a *specific* state of the community that might be desirable to attain (or preserve) because of its biodiversity, resilience, functioning, or the services it provides.
+In these cases, it might not enough to understand which species may cause *any* change in the community. 
 Rather we need to understand first, how the structure of the network can be harnessed to achieve the desired state and which species may play the largest role in this process. 
@@
 This choice thus offers us an opportunity to explicitly contrast our theoretical observations with empirical evidence.
-With these networks, we first ask whether there are differences between the controllability of invaded and uninvaded networks. 
+Empirical observations indicate that steering the state of some communities—for example during ecosystem restoration or invasive species removal—can be a very difficult task [@woodford_confronting_2016].
+Therefore, with these networks, we first ask whether there are differences between the controllability of invaded and uninvaded networks. 
 We then expand existing methods from control theory to effectively link the *controllability* of a network with the role of particular species.
@@
 # Methods
-
-```{r load-metadata}
-drake::loadd(metadata)
-lop <- dplyr::filter(metadata, study == "lopezaraiza") %>% 
-  dplyr::mutate(size = n_pla + n_pol) %$% size %>% summary() 
-bar <- dplyr::filter(metadata, study == "bartomeus") %>% 
-  dplyr::mutate(size = n_pla + n_pol) %$% size %>% summary() 
-```
 

### 2018-06-26 paper/manuscript.Rmd
Name all code chunks

@@
 
-```{r}
+```{r load-fig-example-networks}
 drake::loadd(fig_struct_control)
@@
 
-```{r}
+```{r load-fig-control-configuration}
 drake::loadd(fig_control_config)
@@
 
-```{r controllability}
+```{r controllability-calculations}
 drake::loadd(controllability, metadata, randomisations_test)
@@
 
-```{r}
+```{r cirtical-species-descriptive}
 drake::loadd(sl_characteristics)

### 2018-06-26 paper/manuscript.Rmd
Remove prob. superior from paper

@@
 
-```{r fig-example-networks, fig.width=fig_struct_control$width, fig.height=fig_struct_control$height, fig.cap="Direction of control and controllability conditions.
+```{r fig-example-networks, fig.width=fig_struct_control$width, fig.height=fig_struct_control$height, fig.cap="The direction of control and controllability conditions.
 (a) To establish the direction of control we start with a weighted visitation network (on the left).
@@
 The response variable was the size of the minimum driver node-set $n_D$ of the twenty empirical networks (ten invaded and ten uninvaded) and we included invasion status as a predictor. 
-We also include the network connectance, the network nestedness (NODF) the number of species [since one might naively expect to see a negative relationship between richness and controllability; @menge_indirect_1995], the network asymmetry (an indication of the balance between plant and pollinator diversity), and the interaction strength asymmetry [the asymmetry on the dependences between trophic levels; @bluthgen_specialization_2007].
+We also include the network connectance, the network nestedness (NODF), the number of species [since one might naively expect to see a negative relationship between richness and controllability; @menge_indirect_1995], the network asymmetry (an indication of the balance between plant and pollinator diversity), and the interaction strength asymmetry [the asymmetry on the dependences between trophic levels; @bluthgen_specialization_2007].
 Models were compared using the Akaike Information Criterion for small sample sizes (AICc).
@@
 While calculating the size of the minimum drive node-set can measure the controllability of an ecological community, it does not provide information about the roles that particular species play.
-To answer our question, we make two kinds of distinctions between species from a control perspective.
 
-First, we harness the fact there may be multiple maximum matchings for a given network, and each of these maximum matchings indicates unique paths that could potentially be used to control the network.
-Specifically, we use the frequency with which a species is part of the multiple minimum driver node-sets---its control capacity $\phi$---as an estimation of its relative importance in driving the state of the community as a whole [@jia_control_2013].
-For example, a species with a control capacity $\phi_i= 1$ is a one that requires external input in every single control configuration. 
-This is, if we were to drive the community to an arbitrary alternate state, we would need to apply a management intervention to this species under *any* optimal control strategy.
+To answer this question, we harness the fact there may be multiple maximum matchings for a given network, and each of these maximum matchings indicates a unique combination of species with which is possible to control the network.
+Some species belong to these combinations more often than others. 
+We call this property a species control capacity, $\phi$. 
+The higher a species control capacity, the higher the likelihood that they would need to be directly managed to change (or maintain) the ecological state of their communities. 
+Therefore a species' control capacity is an estimation of their relative importance at driving the state of the community [@jia_control_2013].
 
-To calculate a species control capacity $\phi$, we need to enumerate all possible maximum matchings (we detail the algorithm to find all maximum matchings in the Supporting Information Section \@ref(S-all-maximum-matching)).
-However, enumerating all maximum matchings is extremely expensive from a computational perspective—a network with a couple dozen species could be controlled with several hundred million unique matchings.
-To solve this problem, we employ a recently-developed algorithm that reveals the control correlations between the nodes in the graph using considerably less computational resources [@zhang_input_2016, Supporting Information Section \@ref(S-input-graph)].
+To calculate a species control capacity $\phi$, we need to enumerate all possible maximum matchings (Supporting Information Section \@ref(S-all-maximum-matching)). 
+However, enumerating all maximum matchings is extremely expensive from a computational perspective—a network with a couple dozen species has several hundred million unique maximum matchings. 
+To solve this problem, we employ a recently-developed algorithm that reveals the control correlations between the nodes in the graph using considerably less computational resources [@zhang_input_2016].
 Using this algorithm, we are able to identify species that are possible control inputs—those that belong to the minimum driver node-set in at least one of the possible control configurations. 
-One of the original contributions of our work is to extend this algorithm such that it is possible to calculate a highly accurate approximation of the control capacity $\phi_i$ of every species in the network.
+One of the original contributions of our work is to extend this algorithm such that it is possible to calculate a highly accurate approximation of the control capacity $\phi_i$ of every species in the network (Supporting Information Section \@ref(S-input-graph)).
+In the networks that contained reciprocal links (because there was no asymmetry in the dependences of a species pair), we averaged a species' control capacity $\phi$ across every possible "non-reciprocal" version of the network (Supporting Information Section \@ref(S-reciprocal-links)).
 
-<!-- The paragraph above reminded me of something in the back of my mind.
-Sometimes it's probably better to talk about species instead of nodes, even when we refer to aspects of graph theory.
-Could you go through and look carefully at every appearance of node to see if it would be easier for people that aren't us to understand if we said species instead?
--->
+We then examined how species-level properties were related to control capacity using a set of generalised linear models with binomial error structure. 
+As explanatory variables, we included five variables. 
+First, the species contribution to nestedness, which has been proposed as a key feature that promotes stability and robustness in mutualistic networks [@saavedra_strong_2011]. 
+Second, the species strength (the sum of a species' visits), which quantifies the strength of a species associations and is indirectly related to its abundance [@poisot_comparative_2012]. 
+Third, the direction of asymmetry which quantifies the net balance in dependencies, this is it indicates if a species affects other species more than what they affect it or not [@vazquez_species_2007].
+Fourth, the species degree in order to account for the centrality of a species. 
+Finally, we included a categorical variable for the species trophic level (plant or pollinator) and an interaction term between trophic level and the previous four variables. 
+To facilitate comparison between predictors, degree and visitation strength were log-transformed and all four continuous variables were scaled to have a mean of zero and a standard deviation of one.
 
-A species control capacity $\phi$ allow us to identify species that are critical to change or maintain the state of the community. 
-However, in ecological settings, changing the state of the community as a whole is often not required or undesired. 
-Consequently, we make a second distinction between species based on whether they form part of possible control paths in the network and therefore are likely to influence the abundance of another species.
-We identify these species by checking whether they are classified as *superiors*, this is they are at the beginning of a matched link. 
-While unmatched species correspond to those that should be influenced with an external control input, superior species correspond to those that influence other species internally. 
-Conveniently, unlike the minimum driver node-set, superior species are the same for all control configurations and so in a network without reciprocal links (see below) the probability that a species is superior $\sigma$ is either 1 or 0.
-<!--The end of this paragraph seems to just restate the end of the previous paragraph.
-What new info should I feel like I've gained but aren't?-->
-<!-- You never formally define sigma. -->
-<!-- CHanged wording to make it simpler and define sigma at the same time -->
-
-We calculated the species control capacity $\phi$ and the probability of being superior $\sigma$ for each species in our networks.
-In the networks that contained reciprocal links (because there was no asymmetry in the dependences of a species pair), we averaged a species' $\phi$ and $\sigma$ across every possible "non-reciprocal" realisation of the network (more details can be found in the Supporting Information Section \@ref(S-reciprocal-links)).
-We then examined how species-level structural properties were related to these two variables using two sets of generalised mixed-effects models with binomial error structure. 
-As explanatory variables in the fixed component, we included four variables. 
-First, the species contribution to nestedness, which has been proposed as a key feature that promotes stability and robustness in mutualistic networks [@saavedra_strong_2011]. 
-Second, the visitation strength (the sum of a species' interactions), which quantifies the strength of a species associations and is indirectly related to its abundance [@poisot_comparative_2012]. 
-Third, the direction of asymmetry which quantifies the net balance in dependencies, this is it indicates if a species affects other species more than what they affect it or not [@vazquez_species_2007].
-Fourth, to account for the centrality of a species we included the degree as the fourth fixed effect. 
-To facilitate comparison between variables, all four variables were scaled to have a mean of zero and a standard deviation of one. 
 To identify the models that were best supported by the data we first determined the most parsimonious random structure using the AICc. 
-Specifically, we evaluated a random intercept for observations grouped by the study site, and an intercept and slope for the contribution to nestedness, visitation strength and asymmetry grouped by the trophic guild (plant or pollinator).
-After identifying the most likely random structure we ranked models from all possible fixed effects combinations using the AICc weight.
 The relative importance of variables was then assessed by looking at both their effect sizes in the top-ranked models and the cumulative weight of the models in which they are present.
@@
 These species are critical to controlling community because they are part of the minimum driver node-set in every control scenario. 
-In other words, it is not possible to change the state of the community to a desired state without managing the abundance of these species. 
+In other words, it is not possible to drive the state of the community to a desired state without directly managing the abundance of these species. 
 We anticipate that these species have a disproportionally large impact on the community dynamics. 
@@
 
-Finally, we wanted to understand how the control capacity $\phi$ and the probability of being superior $\sigma$ is related to metrics of keystoness based on centrality. 
-To do that, for each network, we calculated the Spearman correlation matrix between these two variables and some centrality metrics commonly used to identify keystone species. 
-Namely degree, betweenness, eigen centrality, page rank, and closeness centrality.
+Finally, we wanted to understand how two species level control metrics are correlated with five metrics of keystoness based on centrality. 
+The first control metric we use is a species control capacity $\phi$. 
+The second metric is the probability that a focal species influences the abundance of another species internally, regardless of whether a management intervention is required in that species or not. 
+We call this the probability of being a superior node $\sigma$. 
+Because superior nodes are those at the beginning of a matched link, \(\sigma\) could be seen as a "softer" version of control capacity. 
+Conveniently, unlike the minimum driver node-set, superior species are the same for all control configurations and so in a network without reciprocal links the probability that a species is superior $\sigma$ is either 1 or 0.
+Specifically, we compare a species control capacity $\phi$ and the probability that a species is used to internally control another species in the network being superior $\sigma$. 
+As centrality metrics, we use a species' degree, betweenness, eigen centrality, page rank, and closeness centrality.
 
@@
 More details in the Supporting Information Section \@ref(S-visitation-as-proxy).
-Second, because interspecific dependencies depend on the network topology and consequently on the accurate sampling of interactions, we tested the robustness of structural controllability to the uncertainity involved with the sampling of interactions.
+Second, because interspecific dependencies depend on the network topology and consequently on the accurate sampling of interactions, we tested the robustness of structural controllability to the uncertainty involved with the sampling of interactions.
 To do that we compared the results obtained when using the full network and when randomly removing interactions from the weakest links in the network. 

### 2018-06-26 paper/manuscript.Rmd
Update methods
Remove prob. superior. Add partial plots and separate from structural controllability output. Make controllabillity figure fit a single line

@@
 The size of the minimum driver node-set relative to the number of species in each network $n_D$ ranged between $n_D = `r round(min(c_m$n_D), 2)`$ and $n_D = `r round(max(c_m$n_D), 2)`$ (median `r round(median(c_m$n_D), 2)`).
-We found that the relative size of the minimum driver node-set of invaded communities was not significantly different to that of communities that have not been invaded (Figure \@ref(fig:fig-emp-controllability)a).
-However there was an important negative relationship between $n_D$ and the network asymetry (Figure \@ref(fig:fig-emp-controllability)b). 
+We found that the relative size of the minimum driver node-set of invaded communities was not significantly different from that of communities that have not been invaded (Figure \@ref(fig:fig-emp-controllability)a).
+Contrastingly, there was an important negative relationship between $n_D$ and the network asymmetry (Figure \@ref(fig:fig-emp-controllability)b). 
 Furthermore, there were also negative, albeit weaker, correlations between $n_D$ and connectance, nestedness and species richness (Table  \@ref(S-tab:tab-controllability-model-results)). 
-The $n_D$ of empirical networks did not differ to that of a null model that roughly preserved the degree distribution and fully preserved the network connectance ($p = `r sprintf('\\num{%s}', format(randomisations_test$interactions$p.value, digits = 2))`$; Figure \@ref(fig:fig-emp-controllability)b).
+The relative size of the minimum driver-node set $n_D$ of empirical networks did not differ to that of a null model that roughly preserved the degree distribution and fully preserved the network connectance ($p = `r sprintf('\\num{%s}', format(randomisations_test$interactions$p.value, digits = 2))`$; Figure \@ref(fig:fig-emp-controllability)c).
 However empirical networks had a larger $n_D$ than null models that preserved the interactions but shuffled the direction of control of the empirical network ($p = `r sprintf('\\num{%s}', format(randomisations_test$directions$p.value, digits = 2))`$).
 
-```{r fig-emp-controllability, fig.width=fig_sizes()[[1]], fig.height=fig_sizes()[[1]]*1.5, fig.cap="Density plot of (a) the relative size of the minimum driver node-set $n_D$ in the invaded (light) and uninvaded (dark) empirical networks.
-(b) Relationship between the asymmetry plant/pollinator richness and $n_D$.
-The plot shows the values predicted by the most parsimoniouls model.
+```{r fig-emp-controllability, fig.width=fig_sizes()[[2]], fig.height=fig_sizes()[[1]]/2, fig.cap="(a) Density plot of the relative size of the minimum driver node-set $n_D$ in the invaded (light) and uninvaded (dark) empirical networks.
+(b) The relationship between the asymmetry plant/pollinator richness and $n_D$.
+The plot shows the values predicted by the most parsimonious model.
 (c) The density distribution of the difference between the relative size of the minimum driver node-set of random networks and that of empirical networks.
@@
 drake::loadd(fig_emp_controllability)
-cowplot::plot_grid(plotlist = fig_emp_controllability, 
-                   ncol = 1, 
-                   align = "v")
+fig_emp_controllability %>%
+  purrr::map(function(x) x + theme(plot.margin = grid::unit(c(0.5, 1.5, 0.5, 1.5), "mm"))) %>% {
+    cowplot::plot_grid(plotlist = ., 
+                     nrow = 1, 
+                     align = "h")
+  }
+
 ```
@@
 
-The models that best explained a species control capacity $\phi$, had a random intercept and slope for the species asymmetry grouped by the species' guild (plants or pollinators; Table \@ref(S-tab:tab-species-model-random), Table \@ref(S-tab:tab-model-output-species-level)).
-Contribution to nestedness was the most important variable followed by visitation strength (Table \@ref(tab:tab-model-selection-table), Table \@ref(S-tab:tab-var-importance)) with species with large contribution to nestedness and large visitation strength being more likely to have a large control capacity (Figure \@ref(fig:fig-species-level)a and b).
-For the probability of being a superior species $\sigma$, the most parsimonuous models did not include any random effect Table \@ref(S-tab:tab-species-model-random), Table \@ref(S-tab:tab-model-output-species-level)).
-The most important variables were the species asymmetry and the visitation strength (Table \@ref(tab:tab-model-selection-table), Table \@ref(S-tab:tab-var-importance)). 
-Specifically, species with a positive asymmetry (this is they affect their partners more than what their partners affect them), and with a large visitation strength were more likely to be superior (Figure \@ref(fig:fig-species-level)c and d).
-Furthermore, species degree was positively, but only weakly associated with both control capacity and the probability of being a superior species. 
-Remarkably, many species with a low degree, especially pollinators attained a large control capacity in their communities (Figure \@ref(S-fig:fig-species-models-degree)). 
-In addition all invasive plants were both critical ($\phi = 1$) and were superior ($\sigma = 1$) species in their communities.
+Species varied widely in their control capacity (Figure \@ref(fig:fig-species-level)). 
+Pollinators had, in average, larger control capacities than plants but almost no pollinator was critical for network control (a species is critical for control if it has control capacity of \(\phi = 1\)).
+Plants had a bimodal distribution with maxima in both extremes of the distribution (Figure \@ref(fig:fig-species-level)a). 
+Remarkably, every invasive species was critical for network control in each of their communities.
+The species level models indicate a positive relationship between control capacity \(\phi\) and a species' contribution to nestedness, visitation strength, and the asymmetry of the dependence (Table \@ref(tab:tab-model-selection-table); Figure \@ref(fig:fig-species-level); Table \@ref(S-tab:tab-model-output-species-level)).
+Comparatively, species' degree was only weakly associated with control capacity (Table \@ref(S-tab:tab-var-importance)). 
+In fact, many species with a low degree, especially pollinators, attained a large control capacity in their communities (Figure \@ref(S-fig:fig-species-models-degree)a).
 
 ```{r tab-model-selection-table}
-drake::loadd(species_model_cc, species_model_superior)
+drake::loadd(species_model_cc)
 
@@
   dplyr::filter(weight > 0.01)
-su_table <- MuMIn::model.sel(species_model_superior$fixed)%>%
-  dplyr::filter(weight > 0.01)
+# su_table <- MuMIn::model.sel(species_model_superior$fixed)%>%
+#   dplyr::filter(weight > 0.01)
 
-dplyr::bind_rows(cc_table, su_table) %>%
+dplyr::bind_rows(cc_table) %>%
   dplyr::select(-logLik, - AICc) %>%
+  set_names(., pretty_term_names(colnames(.), "short")) %>%
   knitr::kable("latex", 
-               col.names = c("int.", "deg.", "asy.", "nes.", "str.", "d.f.",  "$\\Delta$AICc","weight"),
+               # col.names = pretty_term_names(colnames(.), "short"),
                booktabs = T,
-               caption = "Selection table of the generalised mixed effect models of control capacity $\\phi$ and the probability of being a superior species $\\sigma$.
-Only models with a weight larger than 0.01 are shown.
-All variables were scaled and so the effect sizes are comparable.",
+               caption = "Selection table of the generalised linear models of control capacity, $\\phi$. Only models with a weight larger or equal to 0.01 are shown.", 
                row.names = F, 
@@
                escape = F) %>%
-  kableExtra::add_header_above(c("effect sizes" = 5, " " = 3), escape = F) %>%
+  kableExtra::add_header_above(c("model terms" = 10, " " = 3), escape = F) %>%
   kableExtra::kable_styling(font_size = 8) %>%
-  kableExtra::group_rows("control capacity models", 1, nrow(cc_table)) %>%
-  kableExtra::group_rows("superior probability models", nrow(cc_table) + 1, nrow(cc_table) + nrow(su_table)) %>%
-  kableExtra::footnote(general = "intercept (int), degree (deg), asymmetry (asy), visitation strength (str).", 
+  # kableExtra::group_rows("control capacity models", 1, nrow(cc_table)) %>%
+  # kableExtra::group_rows("superior probability models", nrow(cc_table) + 1, nrow(cc_table) + nrow(su_table)) %>%
+  kableExtra::footnote(general = "intercept (int), degree ($k$), trophic level ($l$), asymmetry ($a$), contribution to nestedness ($n$), visitation strength ($s$).", 
                        general_title = "Terms: ", 
                        footnote_as_chunk = TRUE, 
-                       threeparttable = TRUE)
+                       threeparttable = TRUE, 
+                       escape = F)
 ```
 
-```{r fig-species-level, fig.width=fig_sizes()[[2]]*2/3, fig.height=fig_sizes()[[1]], fig.cap="Density plot of the control capacity $\\phi$ of (a) plants and (b) pollinators.
-(c, d) Relationship between the most important variables in the models of control capacity.
-The plots show the values predicted by most parsimonious model for each response variable.
-The model included a random effect for the trophic guild and hence trends of plants and pollinators are shown separately.
-The invasive species are depicted with solid orange circles."}
+```{r fig-species-level, fig.width=fig_sizes()[[2]]*2/3, fig.height=fig_sizes()[[1]]/2, fig.cap="Density plot of the control capacity $\\phi$ of (a) plants and (b) pollinators.
+The control capacity of all invasive species is $\\phi = 1$ and is depicted with solid circles."}
 drake::loadd(fig_control_capacity)
-library(ggplot2)
 fig_control_capacity[[2]] <- fig_control_capacity[[2]] +
-  theme(axis.title.y = element_blank(),
-        axis.text.y = element_blank())
-fig_control_capacity[[4]] <- fig_control_capacity[[4]] +
   theme(axis.title.y = element_blank(),
@@
 
-```{r}
+```{r fig-species-partial, fig.width=fig_sizes()[[2]], fig.height=fig_sizes()[[1]]/2, fig.cap= "Model averaged partial residual plots for the relationship between control capacity and (a) contribution to nestedness, (b) visitation strength, (c) asymmetry of dependences, and (d) degree."}
+drake::loadd(fig_species_partial)
+fig_species_partial %>%
+  purrr::map_at(2:4, function(x) x  + theme(axis.title.y = element_blank(), axis.text.y = element_blank())) %>%
+    cowplot::plot_grid(plotlist = ., align = "h", nrow = 1, rel_widths = c(1.25, 1, 1,1))
+```
+
+```{r critical-species-test}
 drake::loadd(critical_sp_df)
@@
 
-We also found that critical species (those with a control capacity $\phi = 1$) have a larger impact on species coexistence as the structural stability of the network was considerably reduced when these species were removed from their communities ($p = `r sprintf('\\num{%s}', format(crit_test$p.value, digits = 2))`$; Figure \@ref(fig:fig-structural-stability); Figure \@ref(S-fig:fig-rho-sensitivity)).
-Although some pollinators had large values of control capacity, the group of critical species in every community was composed exclusively of plants.
+We also found that critical species have a large impact on species coexistence. 
+Indeed, the structural stability of the network was considerably reduced when these species were removed from their communities ($p = `r sprintf('\\num{%s}', format(crit_test$p.value, digits = 2))`$; Figure \@ref(fig:fig-structural-stability); Supporting Information \@ref(S-structural-stability)).
 
@@
 The Spearman correlation coefficient ranged between `r round(min(correlations$superior), 2)` (with eigen-centrality) and `r round(max(correlations$superior), 2)` (with degree; Figure \@ref(S-fig:fig-correlogram)).
+Despite the higher correlation with species' degree, with the exception of specialists that had only one interaction, we observed many species with a low degree and a  high probability of being superior nodes (Figure \@ref(S-fig:fig-species-models-degree)b).
 

### 2018-06-26 main.R
New figures

@@ -60,12 +60,13 @@ example_plots_plan <- drake::drake_plan(
   fig_bidirectional = make_fig_bidirectional(en_chain), 
   fig_emp_controllability = make_fig_emp_contollability(controllability, randomisations_df, metadata, controllability_models, controllability_model_data, network_properties), 
   fig_correlation = make_fig_correlation(sl_char_corr), 
-  fig_control_capacity = make_fig_control_capacity(species_model_cc, sl_characteristics),
+  fig_control_capacity = make_fig_control_capacity(sl_characteristics),
   fig_superior = make_fig_superior(species_model_superior),
   fig_structural_stability = make_fig_structural_stability(critical_sp_df), 
   fig_models_degree = make_fig_models_degree(species_model_cc, species_model_superior),
   fig_rho_sensitivity = make_fig_rho_sensitivity(structural_rho_correlation, rho_feasibility),
-  fig_assumption_sampling = make_fig_assumption_subsampling(metrics_subsampled, metadata)
+  fig_assumption_sampling = make_fig_assumption_subsampling(metrics_subsampled, metadata), 
+  fig_species_partial = make_fig_species_partial(species_model_cc)
 )
 
 control_capacity_testing_plan <- drake::drake_plan(

### 2018-06-26 paper/supp-info.Rmd
Caption table supp info was incorrect
Remove prob. superior from supp info
Close #24

@@
 There was no evidence for any of the evaluated predictors: the invasion status (inv), the network connectance (c), the network nestedness (NODF) the number of species ($n_S$) the network asymmetry ($AS_s$) or the interaction strength asymmetry ($AS_s$).
-Only candidate models with $\\Delta AIC < 8$ are shown.") %>%
+Only candidate models with a weight $>0.01$ are shown.") %>%
   kableExtra::kable_styling(font_size = 8)
@@
 
-```{r tab-species-model-random, warning=FALSE}
+```{r tab-species-model-random, warning=FALSE, eval = F}
 drake::loadd(species_model_cc, species_model_superior)
@@
                escape = F) %>%
-  kableExtra::kable_styling(font_size = 8) %>%
-  kableExtra::group_rows("control capacity models", 1, nrow(tab_cc)) %>%
-  kableExtra::group_rows("superior probability models", nrow(tab_cc) + 1, nrow(tab_cc) + nrow(tab_su)) 
+  kableExtra::kable_styling(font_size = 8) #%>%
+  # kableExtra::group_rows("control capacity models", 1, nrow(tab_cc)) %>%
+  # kableExtra::group_rows("superior probability models", nrow(tab_cc) + 1, nrow(tab_cc) + nrow(tab_su)) 
 ```
@@
 ```{r tab-model-output-species-level}
+drake::loadd(species_model_cc)
+
 best_model_cc <- species_model_cc %$%
@@
   get_best_model() 
-best_model_su <- species_model_superior %$%
-  fixed %>%
-  get_best_model()
+# best_model_su <- species_model_superior %$%
+  # fixed %>%
+  # get_best_model()
 
-num_effects <- get_num_effects(best_model_cc)
+# num_effects <- get_num_effects(best_model_cc)
 
 table_df <- best_model_cc %>%
-  broom::tidy() %>%
-  dplyr::bind_rows(broom::tidy(best_model_su))
+  broom::tidy()# %>%
+  # dplyr::bind_rows(broom::tidy(best_model_su))
 
 table_df %>%
-  dplyr::mutate(group = dplyr::if_else(is.na(group), "fixed", group)) %>%
-  dplyr::select(group, term, estimate, std.error, statistic, p.value) %>%
+  # dplyr::mutate(group = dplyr::if_else(is.na(group), "fixed", group)) %>%
+  dplyr::select(term, estimate, std.error, statistic, p.value) %>%
   dplyr::mutate(term = pretty_term_names(term)) %>% 
   knitr::kable("latex", 
-               col.names = c("effect type", "term", "estimate", "std. error", "z value", "p value"),
+               # col.names = c("effect type", "term", "estimate", "std. error", "z value", "p value"),
                booktabs = T, 
@@
                escape = F) %>%
-  kableExtra::kable_styling(font_size = 8) %>%
-  kableExtra::group_rows("control capacity models", 1, purrr::reduce(num_effects, sum)) %>%
-  kableExtra::group_rows("superior probability models", purrr::reduce(num_effects, sum) + 1, nrow(table_df))
+  kableExtra::kable_styling(font_size = 8)# %>%
+  # kableExtra::group_rows("control capacity# models", 1, purrr::reduce(num_effects, sum)) %>%
+  # kableExtra::group_rows("superior probability models", purrr::reduce(num_effects, sum) + 1, nrow(table_df))
 
@@
 cc_imp <- get_var_importance(species_model_cc$fixed) 
-su_imp <- get_var_importance(species_model_superior$fixed)
+# su_imp <- get_var_importance(species_model_superior$fixed)
 
-dplyr::bind_rows(cc_imp, su_imp) %>%
+# dplyr::bind_rows(cc_imp, su_imp) %>%
+  cc_imp %>%
   dplyr::mutate(term = pretty_term_names(term)) %>%
@@
                escape = F, 
-               caption = "Variable importance for each set of models. The importance is the sum of the weights of all models in which the variable was included.",
+               caption = "Variable importance for control capacity models. The importance is the sum of the weights of all models in which the variable was included.",
                linesep = '') %>%
-  kableExtra::kable_styling(font_size = 8)%>%
-  kableExtra::group_rows("control capacity models", 1, nrow(cc_imp)) %>%
-  kableExtra::group_rows("superior probability models", nrow(cc_imp) + 1, nrow(cc_imp) + nrow(su_imp))
+  kableExtra::kable_styling(font_size = 8) #%>%
+  # kableExtra::group_rows("control capacity models", 1, nrow(cc_imp)) %>%
+  # kableExtra::group_rows("superior probability models", nrow(cc_imp) + 1, nrow(cc_imp) + nrow(su_imp))
 ```
 
-```{r fig-superior, fig.width=fig_sizes()[[2]], fig.height=fig_sizes()[[1]]/2, fig.cap = "Relationship between the most important variables in the models of superior probability.
+```{r fig-superior, eval = FALSE, fig.width=fig_sizes()[[2]], fig.height=fig_sizes()[[1]]/2, fig.cap = "Relationship between the most important variables in the models of superior probability.
 The plots show the values predicted by most parsimonious model.
@@
 
-```{r fig-species-models-degree, fig.width=fig_sizes()[[2]], fig.height=fig_sizes()[[1]]/2, fig.cap = "Relationship between degree and (a) the control capacity and (b) the probability of being a superior node.
-The plots show the values predicted by most parsimonious model for each response variable.
-The invasive species are depicted with solid orange circles."}
+```{r fig-species-models-degree, fig.width=fig_sizes()[[1]], fig.height=fig_sizes()[[1]], fig.cap = "Relationship between degree and (a) control capacity and (b) the probability of being a superior node."}
 drake::loadd(fig_models_degree)
 library(ggplot2)
-fig_models_degree %<>% add_internal_margins()
-cowplot::plot_grid(plotlist = fig_models_degree, ncol = 2)
+# fig_models_degree %<>% add_internal_margins()
+fig_models_degree  %>%
+  purrr::map(function(x) x + theme(plot.margin = grid::unit(c(1.5, 0.5, 1.5, 0.5), "mm"))) %>%
+  cowplot::plot_grid(plotlist = ., ncol = 1)
+# fig_models_degree[[1]]
 ```

### 2018-06-26 paper/manuscript.Rmd

@@
 
-Our main goal was to understand the role that species play at both modifying the abbundance of the species they interact with and the state of the community as a whole. 
-To achieve that goal we applied *structural controllability*, a field at the intersection between control and complex theory that allow us to obtain two key pieces of information: the *controllability* of a network and a species *control capacity*.
+Our main goal was to understand the role that species play at both modifying the abundance of the species they interact with and the state of the community as a whole. 
+To achieve that goal we applied *structural controllability*, a field at the intersection between control and complex theory that allow us to obtain two key pieces of information: the *controllability* of a network and a species *control capacity* (Table \@ref(tab:tab-glossary)).
 
-ND is a measure of the extent to which network structure can be harnessed to drive the state of the community.
+```{r tab-glossary}
+defs <- list(
+  "network control" = "A network is said to be controllable if it is possible to steer it from an initial to an arbitrary final state within finite time.",
+  "controllability" = "The intrinsic difficulty of controlling an ecological community.
+It is measured by the relative size of the minimum driver node-set, $n_D$.
+It also indicates the extent to which network structure can be harnessed for network control.",
+  "minimum driver node-set" = "One of the often many smallest sets of species whose abundances need to be directly managed in order to achieve full control of the community.
+The minimum driver node-sets can be obtained by finding all maximum matchings in a network.",
+  "maximum matching" = "A matching is a set of links that do not share a common start or end nodes; the largest possible matching is called a maximum matching.",
+  "control configuration" = "One of the species combinations with which is possible to achieve network control. Optimal control configurations are given by the minimum driver node-sets.", 
+  "control capacity" = "The relative frequency \\(\\phi\\) which with a species is part of the optimal control configurations of a network.", 
+  "critical species" = "A species with the maximum control capacity \\(\\phi=1\\)",
+  "superior node" = "A species is a superior node if it that can internally affect the abundance of other species in the network.
+Superior nodes make up the chains that propagate the control signals through the network.")
 
-Empirical observations indicate that steering the state of some communities—for example during ecosystem restoration or invasive species removal—can be a very difficult task [@woodford_confronting_2016].
-Despite the large number of empirical examples, to date there is no thoretical basis that explains this difficutlies. 
-Here, we show that the *controllability* of a network provides a way to quantify this intrinsic difficulty of controlling an ecological community and the differences among them. 
-The controllability of a network is given by the relative size of the minimum driver node-set, $n_D$. 
-In other words, controllability is related to the smallest proportion of species whose abundances need to be directly managed in order to achieve full control of the community (to be able to steer the community to an arbitrary ecological state).
-We found that in the pollination networks from our dataset the median $n_D$ equals `r round(median(c_m$n_D),2)`. 
-This value is fairly high when compared to several other complex systems in which structural controllability has been applied. 
-For instance, in most social, power transmission, internet, neuronal, and even metabolic networks $0.1 < n_D < 0.35$ and, at least withing the biological realm, only gene regulation networks appear to achieve similar levels of controllability [@liu_controllability_2011].
-Although these results indicate that fully controlling ecological networks might currently be out of reach for all but the smallest communities [@motter_networkcontrology_2015], structural controllability might provide solid theoretical explanation to the many difficulties encountered in the management and restoration of natural communities.
+dplyr::data_frame(rows = c(rbind(names(defs), unlist(defs))), dummy2 = "") %>%
+  dplyr::mutate(rows = kableExtra::cell_spec(rows, "latex", bold = T:F, escape = F)) %>%
+  knitr::kable("latex", 
+               booktabs = T, 
+               col.names = NULL,
+               caption = "Glossary", 
+               escape = F, 
+               linesep = c('', '\\addlinespace')) %>% 
+  kableExtra::kable_styling(font_size = 8) %>%
+  kableExtra::add_indent(seq(2, length(defs)*2, by = 2)) %>%
+  kableExtra::column_spec(1, width = paste0(fig_sizes()[[1]], "in"))
+```
 
-Structural controllability might also offer novel means to compare ecological networks, particularly when exploring the relationship between network structure and stability. 
-Even though all studied communities appear to be hard to control, we still found significant variation between them—the relative size of the minimum driver node set ranged between $n_D = `r round(min(c_m$n_D), 2)`$ and `r round(max(c_m$n_D), 2)`.
-Interestingly, we found that the controllability of a network is not related to their invasion status. 
-Instead, we found that, despite our relatively small sample size, these differences in controllability may stem from differences in structure. 
-Specifically, networks with a larger asymmetry between plant and pollinator species richness and with larger connectances were more likely to have higher values of $n_D$. 
-In addition, we found that the $n_D$ of empirical networks was indistinguishable from that of network randomisations that roughly maintained the degree distribution, but was significantly different to those in which the patterns of dependence were broken.
-All together, these results suggest that network controllability is almost completely constrained by the patterns of species richness at each trophic guild and their degree distributions [@melian_complex_2002; @bluthgen_specialization_2007].
-These two factors, in turn govern the asymmetric nature of mutual dependences-which constitute the foundations of structure and stability in mutualistic networks [@bascompte_asymmetric_2006; @memmott_tolerance_2004; @astegiano_robustness_2015].
+The median size of the relative minimum driver node-set of in our dataset was $n_D = `r round(median(c_m$n_D),2)`$. 
+This value is high when compared to other complex systems in which controllability has been investigated.  
+For instance,  only gene regulation networks appear to achieve similar levels of controllability while most social, power transmission, internet, neuronal, and even metabolic networks seem to be easier to control ($0.1 < n_D < 0.35$) [@liu_controllability_2011].
+These results indicate that fully controlling ecological networks might currently be out of reach for all but the smallest communities [@motter_networkcontrology_2015]. 
+Nevertheless, structural controllability might be helpful at identifying communities in which changes in the ecological state are more likely to occur and provides solid theoretical explanation to the many difficulties encountered in the management and restoration of natural communities.
 
-Structural controllability not only can offer valuable insight at the community level, but, by measuring a species *control capacity*, here we show that it can also be used to better understand the role of individual species.
-The group of species that compose the minimum driver node-set $n_D$ is often not unique. 
-This means that there are many species combinations with which it is possible to fully control a network
-Each of these combinations represents a control configuration. 
-Some species belong to these combinations more often that others. 
-We call this property a species control capacity $\phi$. 
-The higher a species control capacity, the higher the likelyhood that they would need to be directly managed to change (or maintain) the ecological state of their communities. 
-A small fraction of species in each network (between `r round(pcrit_ran[1]*100)` and `r round(pcrit_ran[2]*100)`%) had a control capacity of $\phi = 1$. 
-We call these *critical* species. 
-Because critical species are driver in every single control configuration it is unlikely that any attempt to steer the community to a different state will be successful without directly managing the abbundances of these species.
-Interestingly, although the average control capacity of pollinators was higher than that of plants, the group of critical species was exclusively composed by plants.
+When controlling for network structure, we found no difference between the controllability of invaded and uninvaded networks. 
+Our results suggest that the differences between the controllability networks are instead likely to arise from differences in their structure. 
+Specifically, we found that network controllability is almost completely constrained by the patterns of species richness at each trophic guild and their degree distributions [@melian_complex_2002; @bluthgen_specialization_2007].
+These two factors are particularly relevant because they govern the asymmetric nature of mutual dependences-which constitute the foundations of structure and stability in mutualistic networks [@bascompte_asymmetric_2006; @memmott_tolerance_2004; @astegiano_robustness_2015].
 
-Because of the presumed relationship between central and keystone species, we expected control capacity to be somewhat correlated with some metrics of centrality. 
-However, despite the influence that critical species might have into the state of the community, a large control capacity is not necessarly accompained by a large centrality. 
-Indeed,  the correlation coefficients between control capacity and five different centrality metrics was low and both specialist and generalist species could play an important role at changing the abbundances of other species.
+Accordingly, our results suggest that structural controllability is closely related to the persistence of an ecological community. 
+First, we found a comparatively small but tantalising negative relationship between the controllability of a network and the nestedness of its interactions. 
+Previous studies indicate that nestedness promotes species coexistence and confers robustness to despeciation [@bastolla_architecture_2009; @memmott_tolerance_2004] at the expense of the dynamic stability of the mutualistic community [@saavedra_nested_2016].
+These observations are in agreement with our results, as we would expect the dynamic stability of a community to be correlated to the difficulty to control it. 
+Second, species' control capacity was strongly correlated to their contribution to nestedness and critical species had the largest impact to the stable coexistence of species in their communities. 
+Therefore, species that play a key role at determining the state of the community might also be more key to "maintain the organization and diversity of their ecological communities", one of the hallmarks of keystone species [@mills_keystone-species_1993].
 
-Althogh control capacity was poorly predicted by centrality, we found that it was strongly related to a species contribution to nestedness and, to a smaller extent, the species strength. 
-The species strength (the sum of visits that a species receivers or performs) quantifies how strongly a species interacts with its partners. 
-Indirectly, it is also a reflection of the species' abundance, and therefore its relationship with control capacity can be explained by the fact that species with large populations are anticipated to have a larger effect in the community than less common species.
+When controlling for a species' strength (which is indirectly a proxy of its abundance) and the net balance of its dependencies, we found that control capacity could not be easily predicted by species' degree or other metrics of centrality.
+For instance, some species with a low degree achieved the maximum control capacity and were critical for control in their communities. 
+At first glance, our findings challenge numerous studies that highlight the role that central species play in the dynamics of their communities and their utility at predicting species extinctions [@jordan_keystone_2009].
+However, further inspection shows that our results do not contradict these findings. 
+On the contrary, most species with a large degree also have a large control capacity and all of them were classified as superior nodes which corroborates the utility of classic centrality metrics. 
+What our results do, is to take previous findings one step further and suggest that centrality might paint only a limited picture of the relevance of species.
 
-The strong relationship between control capacity and nestedness is more revealing in particular because we also found that critical species play a major role at enabling the coexistence of other species in their community.
-Previous studies suggest that nestedness is key to the persistence of pollination networks as it minimises species competition—and therefore promotes species coexistence—and confers robustness to species extinctions in the community.
-Using two completely different approaches, our results suggest that species that are more likely to determine the state of the community might also be more likely to contribute the most at "maintaining the organization and diversity of their ecological communities", one of the hallmarks of keystone species [@mills_keystone-species_1993].
+Other conceptual differences between structural controllability and centrality metrics might provide further insight into the conservation of ecological networks. 
+First, structural controllability emphasizes that the effect a species has on the abundance of other species is not independent of the effects of other other species in their community. 
+Second, it demonstrates that to ensure the persistence of a community it is often necessary to consider the abundances of more than a single species, even when full control is unfeasible or undesired (for example `r round(sum(crit$n_crit > 1)/nrow(crit)*100)`% of our communities contained more than one critical species).
+Third, structural controllability explicitly acknowledges the existence of multiple management strategies and some will be better than others depending on the context.
+Approaches to prioritise species for conservation and reintroduction based on traits or centrality are still useful and are likely to overlap with a species' control capacity [@pires_friendship_2017; @devoto_understanding_2012].
+Altogether, our results also provide support to the idea that management decisions should not be based on a single technique, but indicates that focusing on ecosystem processes and interactions may be more effective than traditional ranking based approaches [@harvey_bridging_2017].
 
-Invasive species have been previously found to exacerbate the asymmetries in their communities [@aizen_invasive_2008; bartomeus_contrasting_2008-1; @henriksson_strong_2016]. 
-Although this might be reflected on differences both at the community and the species level, we found that invasive plants are not inherently different to their native counterparts [@emer_species_2016; @stouffer_how_2014].
-Invasive plants, just like any other mutualist in our data set, tended to attain a high control capacity proportional to the degree to which they contribute to nestedness and interact strongly with other species.
-Nevertheless 
-Previous studies have found that supergeneralists, like invasive species, play a central role in their networks (Vilà et al. 2009; Palacio, Valderrama-Ardila & Kattan 2016). 
-XXXOur results take this one step further and indicate that dependence strength, rather than generalism or other metrics of centrality, is the factor that best explains the cascading effects a species could trigger on its community.
+The choice of the invaded/uninvaded networks was based on our desire to contrast the extensive empirical evidence of the role of invasive plants with our theoretical results. 
+We found that without exception, invasive plants were critical for network control and as such our results were in line with our expectations. 
+Invasive plants have been previously found to exacerbate the asymmetries in their communities [@aizen_invasive_2008; bartomeus_contrasting_2008-1; @henriksson_strong_2016] and to be central in their communities [@vila_invasive_2009; @palacio_generalist_2016].
+We found that invasive plants are, however, unlikely to be inherently different from their native counterparts [@emer_species_2016; @stouffer_how_2014]. 
+Just like any other mutualist in our dataset, invasive plants tended to attain a high control capacity proportional to the degree to which they contribute to network persistence, are abundant, and depend little on other species.
+Furthermore, our observation that changes in the abundance of invasive plants (and presumably all critical species) are crucial to modify the state of the community agrees with recent evidence showing that ecosystem restoration focused on the eradication of invasive plants can have transformative desirable effects in plant-pollinator communities [@kaiser-bunbury_ecosystem_2017].
+However, our results also suggest that removals must be exercised with caution. 
+Not only it is hard to predict the direction in which the system will change, but we also show that critical species can underpin the coexistence of species and therefore some communities may be acutely vulnerable to their eradication [@traveset_invaders_2013; @albrecht_consequences_2014].
 
-The structural controllability approach, just like classic centrality metrics is sensitive to the uncertainity associated with the sampling of ecological interactions. 
-Our sensitivity analyses suggest that structural controllability is robust to at least two sources of uncertainity: when interactions are only sampled incompletly and when multiple metrics could be used used to quantify the strength of associations between species.
+Structural stability assumes that the networks can be approximated using linear functional responses. 
+The ramifications of this assumption imply that while structural controllability is useful to identify species that are relevant for network control, it cannot be used to design the precise interventions that should be applied to these species in order to achieve a desired state.
+While in an ideal scenario we would completely incorporate the species dynamics into the controllability analysis [@cornelius_realistic_2013], the reality is that such information is rarely available in most ecological scenarios.
+In contrast, structural controllability only requires a quantitative approximation of the network's interactions to gain valuable insight from the community.
+Furthermore, unlike centrality metrics, the assumptions of structural controllability are explicit and the estimation of a species importance arises from a mechanistic understanding of the population dynamics between species.
+By accounting for network dynamics (even if in a simple way) it incorporates more ecological realism even in the extreme scenario where the state of a community depends almost exclusively on nodal dynamics rather than on the topology of their interactions.
 
-Another common critique to structural controllability is that it is based on the premise that the system can be described using linear functional responses [@cowan_nodal_2012]. 
-This is indeed a current limitation, as we know that ecological systems are often best described using different nodal dynamics. 
-However, we are not discouraged by its application for three main reasons. 
-First, it has been shown that when the parameters that describe the mechanisms of self-regulation are not independent from each other, as is ofthen the case in ecological networks, the principles of structuctural controllability can still be applied [@zhao_intrinsic_2015].
-Second, although non-linear dynamics render structural controllability unsufficient to assure full control an ecological system, it is still a necessary step to achieve that goal. 
-Finally, by accounting for network dynamics (even if in a simple way) it incorporates more ecological realism than classical centrality metrics and hence is more likely to provide useful information even in the extreme scenario in which the state of a community depends almost exclusively on nodal dynamics rather than on the topology of their interactions.
-
-From an applied ecology perspective, @paine_note_1969 showed nearly 50 years ago that one species can dominate the state of its community. 
-Structural controllability suggests that this situation might be the exception rather than the rule, at least when were interested in *managing* the state of 
-community and not just on inducing a change. 
-Our results also provide support to the idea that management approaches focused on ecosystem processes and interactions might be more effective than traditional single-species approaches [@harvey_bridging_2017].
-A `r round(sum(crit$n_crit > 1)/nrow(crit)*100)`% of our communities contained more than one critical species. 
-Approaches identify keystone species and ultimately prioritise species for conservation are still useful at predicting the consequences of single species removals or reintroductions [@pires_friendship_2017; @devoto_understanding_2012], but effective management and restoration of ecological communities is likely to require more than a ranking of species based on their traits or centrality.
-
-<!-- Biggest lesson is that changing the state of the community in a requires concerted action by several species, not just changes in the abbundance of one species.  -->
-
-<!-- Control theory is flexible and awknoledges that there are multiple ways to achieve changes in the state of the community.  -->
-<!-- Managing the most central species might not be suficient or even required to achieve that goal.  -->
-
-<!-- Even if full control is not possible or not desired we learnt that there are critical species, those that no matter what the management strategy will need to be managed if one wants effective control of the populations in the ecological community.
--->
-
-<!-- Centrality species concept is limited because we onl -->
-
-<!-- We propose structural controllbility as a metric that can be used to compare ecological systems both in a theoretical and applied context. -->
+Here we show that structural controllability can be applied in an ecological setting to gain insight into the stability of a community and the role that species play at modifying the abundance of other species and ultimately the state of the community.
+These characteristics make structural stability an ideal framework to evaluate the effects of invasions and other types of perturbations. 
+Importantly, structural controllability can be used to identify critical species in the community. 
+Critical species promote biodiversity and underpin the stable coexistence of species in their community.
+Collectively critical species dominate the state of their community and therefore are likely to be highly relevant for ecosystem management and conservation. 
+Centrality metrics which have often been used as a proxy for keystoneness, although useful, fail to identify some of these species which highlights their limitations when we embrace that ecological communities are dynamical systems.
+@paine_note_1969 showed nearly 50 years ago that one single species can dominate the state of its community. 
+Structural controllability suggests that this situation might be the exception rather than the rule. 
+We see our study as a starting point to study the controllability of ecological and socio-ecological systems where many exciting questions lie ahead.
 

### 2018-06-26 paper/cover-letter.tex
Say that some emphasis on different analyses changed

@@
 \documentclass{letter}
-\usepackage[a4paper, total={5in, 9.1in}]{geometry}
+\usepackage[a4paper, total={5.2in, 9.4in}]{geometry}
 \usepackage{setspace}
@@
 We are also grateful for the opportunity to resubmit.
+
 In the attached document, you can find a detailed response to each of their comments. 
@@
 Therefore, we have rewritten almost entirely the manuscript and the supplementary materials. 
-We maintain the methodology and findings, but there has been a major change in the way we justify the study, introduce novel concepts to the ecological domain, and present our conclusions.
+We maintain the methodology and findings, but there has been a major change in the way we justify the study, introduce novel concepts to the ecological domain, emphasize resulys, and present our conclusions.
 

### 2018-06-26 paper/reviewers-response.Rmd
Finishing off questions and adding line numbers

@@
 As it was explained in the previous response, in this paper we chose not to emphasize the empirical application of structural controllability. 
-We acknowledge however that the approach has potential to be applied in management and have hence added a couple of examples in the Discussion (line XXX).
+We acknowledge however that the approach has potential to be applied in management and have hence described some insights that structural controllability could offer to the conservation of ecological networks (\lr{M-management-implications}).
 
@@
 Further details can be found in the Supporting Information Section \@ref(S-visitation-as-proxy) and \@ref(S-undersampling). 
-In addition, we also included a reference to the key information needed to apply the method in the Discussion (XXX).
+In addition, we also included a brief description of the key information needed to apply the method in the Discussion (\lr{M-data-requirements}).
 
@@
 
-Thanks for these references. We have used them to strengthen the Discussion (lines XXX).
+Thanks for these references. 
+They have been particularly useful to highlight the differences between structural controllability and other approaches (\lr{M-extra-references-1} and \lr{M-extra-references-2}) and to discuss the potential impact of invasive plants (\lr{M-extra-references-3}).

### 2018-06-26 paper/manuscript.Rmd
Add references for line numbers
Close #40

@@
 
-Other conceptual differences between structural controllability and centrality metrics might provide further insight into the conservation of ecological networks. 
+\R{management-implications}Other conceptual differences between structural controllability and centrality metrics might provide further insight into the conservation of ecological networks. 
 First, structural controllability emphasizes that the effect a species has on the abundance of other species is not independent of the effects of other other species in their community. 
@@
 Third, structural controllability explicitly acknowledges the existence of multiple management strategies and some will be better than others depending on the context.
-Approaches to prioritise species for conservation and reintroduction based on traits or centrality are still useful and are likely to overlap with a species' control capacity [@pires_friendship_2017; @devoto_understanding_2012].
-Altogether, our results also provide support to the idea that management decisions should not be based on a single technique, but indicates that focusing on ecosystem processes and interactions may be more effective than traditional ranking based approaches [@harvey_bridging_2017].
+Approaches to prioritise species for conservation and reintroduction based on traits or centrality are still useful and are likely to overlap with a species' control capacity\R{extra-references-1} [@pires_friendship_2017; @devoto_understanding_2012].
+Altogether, our results also provide support to the idea that management decisions should not be based on a single technique, but indicates that focusing on ecosystem processes and interactions may be more effective than traditional ranking based approaches\R{extra-references-2} [@harvey_bridging_2017].
 
@@
 Just like any other mutualist in our dataset, invasive plants tended to attain a high control capacity proportional to the degree to which they contribute to network persistence, are abundant, and depend little on other species.
-Furthermore, our observation that changes in the abundance of invasive plants (and presumably all critical species) are crucial to modify the state of the community agrees with recent evidence showing that ecosystem restoration focused on the eradication of invasive plants can have transformative desirable effects in plant-pollinator communities [@kaiser-bunbury_ecosystem_2017].
+Furthermore, our observation that changes in the abundance of invasive plants (and presumably all critical species) are crucial to modify the state of the community agrees with recent evidence showing that ecosystem restoration focused on the eradication of invasive plants can have transformative desirable effects in plant-pollinator communities\R{extra-references-3} [@kaiser-bunbury_ecosystem_2017].
 However, our results also suggest that removals must be exercised with caution. 
@@
 While in an ideal scenario we would completely incorporate the species dynamics into the controllability analysis [@cornelius_realistic_2013], the reality is that such information is rarely available in most ecological scenarios.
-In contrast, structural controllability only requires a quantitative approximation of the network's interactions to gain valuable insight from the community.
+\R{data-requirements}In contrast, structural controllability only requires a quantitative approximation of the network's interactions to gain valuable insight from the community.
 Furthermore, unlike centrality metrics, the assumptions of structural controllability are explicit and the estimation of a species importance arises from a mechanistic understanding of the population dynamics between species.

### 2018-06-26 paper/manuscript.Rmd
Dummy sections for submission
Addresses  #44

@@
 
+*Keywords:* ASD
+
 # Introduction
@@
 
-# Methods
+# Materials and methods
 
@@
 
+# Awknoledgements
+
+A brief statement acknowledging collaborators and research assistants who do not meet the criteria for authorship described above, or acknowledging funding sources, providing relevant permit numbers (including institutional animal use permits), or giving recognition to nature reserves or other organizations that made the work possible.
+
+# Author contributions
+
+All submissions with more than one author must include an Authors’ contributions statement. All persons listed as authors on a paper are expected to meet ALL of the following criteria for authorship:
+
+* substantial contributions to conception and design, or acquisition of data, or analysis and interpretation of data, or drafting the article or revising it critically for important intellectual content;
+* final approval of the version to be published;
+* agreement to be accountable for the aspects of the work that they conducted and ensuring that questions related to the accuracy or integrity of any part of their work are appropriately investigated and resolved.
+
+Acquisition of funding, provision of facilities, or supervising the research group of authors without additional contribution are not usually sufficient justifications for authorship.
+The statement should include an explanation of the contribution of each author.
+We suggest the following format for the Authors’ contributions statement:
+
+AB and CD conceived the ideas and designed methodology; CD and EF collected the data; EF and GH analysed the data; AB and CD led the writing of the manuscript.
+All authors contributed critically to the drafts and gave final approval for publication.
+
+# Data accessibility
+
+To enable readers to locate archived data from papers, we require that authors list the database and the respective accession numbers or DOIs for all data from the manuscript that has been made publicly available.
+Please see our editorial policies page for further information
+
 # References

### 2018-06-26 paper/cover-letter.tex
spell check is Fernando's least favorite part of writing, but Daniel loves it

@@
 Therefore, we have rewritten almost entirely the manuscript and the supplementary materials. 
-We maintain the methodology and findings, but there has been a major change in the way we justify the study, introduce novel concepts to the ecological domain, emphasize resulys, and present our conclusions.
+We maintain the methodology and findings, but there has been a major change in the way we justify the study, introduce novel concepts to the ecological domain, emphasize results, and present our conclusions.
 

### 2018-06-26 paper/reviewers-response.Rmd
very minor dbs changes to the response; looking good so far!

--- 2018-06-19 paper/reviewers-response.Rmd
@@
 As a consequence and despite the potential of the approach, we currently lack *direct* evidence of the utility of the approach for management decisions.
-Second, we think that highlighting the conceptual approach offered a greater opportunity to draw attention to the strongest/most interesting aspects of the paper. 
+Second, we concluded that highlighting the conceptual approach offered a greater opportunity to draw attention to the strongest/most interesting aspects of the paper. 
 Namely, the contrasts between invaded and uninvaded communities and the role of invasive species, as one of the reviewers points out.
@@
 
-Previously we used two sections to explain our approach: a section called "Theoretical framework" where we described the control methods, and another called "Methods" where we described their application on empirical data.
+Previously, we used two sections to explain our approach: a section called "Theoretical framework" where we described the control methods, and another called "Methods" where we described their application to empirical data.
 At that moment, we thought this was the best approach; in hindsight, we realise that separating these two aspects made it hard to understand the core control concepts and their relationship with ecology.
@@
 To improve clarity, we have now combined the two sections into a single "Methods" section in which we explain the theory alongside with the empirical application. 
-We also spend more time providing intuitive explanations of the concepts of control theory and have moved the most technical details to the supplementary information.
+We also spend more time working through intuitive explanations of the concepts of control theory and have moved the most technical details to the supplementary information. 
 This latter move (shifting the technical details to the supplementary information) allowed us to use far less jargon and simplify the notation. 
@@
 Nevertheless, we have also rewritten the introduction and took care to be clear at explaining how this study relates to and differs from previous work. 
-In particular, we set up the stage for our work by briefly explaining how keystoneness metrics are mainly based on centrality metrics and how the proposed work differs from it.
+In particular, we set the stage for our work by briefly explaining how keystoneness metrics are mainly based on centrality metrics and explicitly outline where and how the proposed work differs.
 
@@
 
-As it was explained in the previous response, in this paper we chose not to emphasize the empirical application of structural controllability. 
-We acknowledge however that the approach has potential to be applied in management and have hence added a couple of examples in the Discussion (line XXX).
+As it was explained in the previous response, we chose not to emphasize the empirical application of structural controllability in this paper. 
+However, we acknowledge that the approach has potential to be applied in management and have hence described some insights that structural controllability could offer to the conservation of ecological networks (\lr{M-management-implications}).
 
@@
 
-In the previous manuscript, we discussed this uncertainty but it was buried in the Supporting Information. 
-We have now added a subsection in the Methods describing how we evaluate the impact of the uncertainty induced by using visitation as a proxy of species interdependence and that induced by incomplete sampling of rare interactions (\lr{M-testing-assumptions-line}).
-We found that the structural controllability approach is robust to these two sources of uncertainty (\lr{M-testing-assumptions-results-line}). 
+In the previous version, we discussed this uncertainty but it was unfortunately buried in the Supporting Information. 
+We have now added a subsection in the Methods describing how we evaluate the impact of the uncertainty induced (i) by using visitation as a proxy of species interdependence and (ii) by incomplete sampling of rare interactions (\lr{M-testing-assumptions-line}).
+We found that the structural controllability approach is rather robust to these two sources of uncertainty (\lr{M-testing-assumptions-results-line}). 
 Further details can be found in the Supporting Information Section \@ref(S-visitation-as-proxy) and \@ref(S-undersampling). 
-In addition, we also included a reference to the key information needed to apply the method in the Discussion (XXX).
+In addition, we also included a brief description of the key information needed to apply the method in the Discussion (\lr{M-data-requirements}).
 
@@
 We are thankful to the reviewer for indicating the aspects which they believe were strengths of our work.
-We maintain the methodological approach in the latest version and have used these details to determine which elements were essential to maintain in the current revision.
+We maintain the methodological approach in the latest version and have used these comments to help determine which elements were essential to maintain in the current revision.
 
@@
 We are very thankful for the insightful identification of the manuscript weaknesses and especially for clearly identifying possible pathways to fix them. 
-Following this suggestion and that of the editors, we chose to focus on how structural controllability offers a new perspective to understand the role of species in their community in the context of species "keystoneness".
-Despite this decision, we still discuss previous metrics as we found that being explicit about how the approach differs from classic centrality metrics to estimate species importance made the paper much clearer.
-These differences are discussed more in the light of network structure than in the design of efficient management interventions.
+Following this suggestion and those of the editors, we chose to focus on how structural controllability offers a new perspective to understand the role of species in their community in the context of species "keystoneness".
+Despite this decision, we still discuss previous metrics since we found that the paper was much clearer after we being more explicit about how the approach differs from classic centrality metrics to estimate species importance.
+Note that these differences are discussed in the current version more in the light of network structure than in the design of efficient management interventions.
 
@@
 As mentioned earlier in a response to the editor, we found that in order to address effectively all concerns, a rewrite of the whole paper was needed. 
-Although we have not gone in the applied ecology direction, we hope the current version addresses the fundamental reviewers concerns satisfactorily.
+Although we have not gone in the applied ecology direction, we hope the current version addresses the fundamental reviewers concerns to their satisfaction.
 
@@
 
-Thanks for these references. We have used them to strengthen the Discussion (lines XXX).
+Thank you for pointing us toward these references.
+We have found them to be particularly useful to highlight the differences between structural controllability and other approaches (\lr{M-extra-references-1} and \lr{M-extra-references-2}) and to discuss the potential impact of invasive plants (\lr{M-extra-references-3}).

### 2018-06-26 paper/manuscript.Rmd
dbs edits and comments through to the results

@@
 
-**Author for correspondence:** Daniel Stouffer (daniel.stouffer@canterbury.ac.nz) - +64 3 364 2729 - Centre for Integrative Ecology, School of Biological Sciences, University of Canterbury, Private Bag 4800, Christchurch 8140, New Zealand
+**Author for correspondence:** Daniel B.
+Stouffer (daniel.stouffer@canterbury.ac.nz) - +64 3 364 2729 - Centre for Integrative Ecology, School of Biological Sciences, University of Canterbury, Private Bag 4800, Christchurch 8140, New Zealand
 
@@
 Within community ecology, a complex-systems approach has led to the development of a variety analytical and simulation tools with which to compare and contrast the roles of species embedded in a network of interactions [@guimera_cartography_2005; @bascompte_assembly_2009; @stouffer_evolutionary_2012; @coux_linking_2016].
-A particularly relevant dimension of any species' role is its ability to alter the abundance of other species and the state of the community—since changes of this nature can have knock-on effects on ecosystem function, diversity, processes, and services.
+A particularly relevant dimension of any species' role is its ability to alter the abundance of other species and the state of the community—since changes of this nature can have knock-on effects on ecosystem function, diversity, processes, and services [@ref_to_daniels_tree_paper_and_jasons_reviews].
 This ability is sometimes referred to as a species' "keystoneness" [@mills_keystone-species_1993].
 
-A significant proportion of the network tools used to estimate species roles in this context rely on the calculation of a species' centrality—a relative ranking of its positional importance that stems from social network research [@noah_e._friedkin_theoretical_1991].
-Generally speaking, central species tend to be better connected and consequently are more likely to participate in the network's food chains. 
+A significant proportion of the network tools used to estimate species roles in this context rely on the calculation of a species' centrality—a relative ranking of its positional importance that originally stems from social-network research [@noah_e._friedkin_theoretical_1991].
+Generally speaking, central species tend to be better connected and consequently are more likely to participate in the network's "food chains". 
 Because species that participate in more chains are assumed to be more likely to affect the abundance of other species, centrality metrics have often been used to identify keystone species in the community [@jordan_quantifying_2007].
-Centrality metrics have been shown to be useful tools to rank species in regards to their potential to alter the abundances of other species; especially when estimating secondary extinctions that may follow the loss of a species [@dunne_network_2002; @kaiser-bunbury_robustness_2010].
+Centrality metrics have been shown to be useful tools to rank species in regards to their potential to alter the abundances of other species, in particular when estimating secondary extinctions that may follow the loss of a species [@dunne_network_2002; @kaiser-bunbury_robustness_2010].
 
-Despite being conceptually intuitive, the relationship between centrality and the state of the community is largely phenomenological. 
-On one hand, dramatic changes in ecosystem functioning can also occur without complete removal of a species. 
-On the other, we are often interested in a *specific* state of the community that might be desirable to attain (or preserve) because of its biodiversity, resilience, functioning, or the services it provides.
-In these cases, it might not enough to understand which species may cause *any* change in the community. 
-Rather we need to understand first, how the structure of the network can be harnessed to achieve the desired state and which species may play the largest role in this process. 
+Despite being conceptually intuitive, the relationship between centrality and a species' presumed impact on the state of the community is largely phenomenological. 
+On one hand, substantive changes in ecosystem functioning can also occur without complete removal of a species [@needsrefs;@daniel_has_ideas]. 
+On the other, we are often interested in a *specific* state of the community that might be desirable to attain (or preserve) because of its biodiversity, resilience, functioning, or the ecosystem services it provides.
+In these cases, it might be less useful to understand which species may cause *any* change in the community. 
+Instead, we are better served by understanding how the structure of the network can be harnessed to achieve the desired state and which species may play the largest role in this targeted process. 
 When the state of a community is underpinned by more than a single species and we move beyond single-species removals, we expect the usefulness of centrality to diminish.
+<!-- DBS: We could potentially cut the sentence above; I see the merit, but I also feel like it could annoy readers/reviewers. -->
 As a result, community ecology could arguably benefit from an alternative, perhaps more mechanistically-grounded, approach to understand how species affect each other's abundance.
 
-Species abundances (and consequently the state of the community) are influenced by both their interactions, the specific dynamics of these interactions and the mechanisms of self-regulation. 
-However, community and population dynamics can be modelled in innumerable ways, and empirical support for one versus another is often still ambiguous. 
+Species abundances---and consequently the state of the community as a whole---are influenced by both their interactions, the specific dynamics of these interactions and the mechanisms of self-regulation [@addrefs].
+However, community and population dynamics can be modelled in innumerable ways, and empirical support for one versus another is often still ambiguous [@addrefs]. 
 The alternative approach should, therefore, ideally acknowledge ecosystem dynamics, but without being overly dependent on the particular choices of how they are characterised.
@@
 In concordance with long-standing ecological questions, advances in this field have established a clear link between the structure of the network and the way nodes affect each other. 
-Unlike centrality indices, however, this link is not based on a priori assumptions between network metrics and keystoneness but is instead based on well-established advances in both dynamical and complex-systems theory.
+Unlike centrality indices, however, this link is not based on a priori assumptions between network metrics and keystoneness but is instead based on well-established advances in both dynamical and complex-systems theory [@motter_networkcontrology_2015].
 
-At its fundamental level, control theory first determines whether a system is controllable or not; that is, it asks if a system can be driven to a desired state within a finite amount of time. 
-Although the controllability of a network is a whole-system property, it has been recently shown that asking for the controllability of a complex-system is equivalent to finding a particular set of nodes: the set with which is possible to control the state of the whole network [@liu_control_2016].
+At its fundamental level, control theory first determines whether a system is controllable or not; that is, it asks if a system could ever be driven to a desired state within a finite amount of time. 
+Although the controllability of a network is a whole-system property, it has recently been shown that asking for the controllability of a complex-system is equivalent to finding a particular set of relevant nodes: the set with which is possible to control the state of the whole network [@liu_control_2016].
 Notably, control theory is consistent with the observation that to change the state of a network, more than a ranking, we need a set of nodes.
+<!-- DBS: I don't get what "more than a ranking" means above. -->
 Importantly, this set of nodes is not always unique for a given network.
-This implies that an examination of the distinct sets provides a means to connect nodes with its *general* ability to modify the system to which they belong.
+This implies that an examination of the distinct sets provides a means to connect nodes with their *general* ability to modify the system to which they belong.
 
-Here, we apply methods from control theory to a particular ecological problem and show how it can be used to gain insight into the role of species in an ecological network. 
+Here, we apply methods from control theory to a particular ecological problem and show how it can be used to generate insight into the role of species in an ecological network. 
 Specifically, we outline the approach using a set of ten pairs of uninvaded and invaded plant-pollinator communities. 
@@
 This choice thus offers us an opportunity to explicitly contrast our theoretical observations with empirical evidence.
-Empirical observations indicate that steering the state of some communities—for example during ecosystem restoration or invasive species removal—can be a very difficult task [@woodford_confronting_2016].
-Therefore, with these networks, we first ask whether there are differences between the controllability of invaded and uninvaded networks. 
-We then expand existing methods from control theory to effectively link the *controllability* of a network with the role of particular species.
+Moreover, empirical observations indicate that steering the state of some communities—for example during ecosystem restoration or invasive species removal—can be a very difficult task [@woodford_confronting_2016].
+Therefore, we first ask whether there are differences between the controllability of invaded and uninvaded networks. 
+We then expand existing methods from control theory to effectively link the *controllability* of a network with the role of its constituent species.
 We ask—from a control-theoretic perspective—whether there are key differences between species in the role they play at driving the state of the community and explore the ecological factors related to these differences.
 This allows us to identify species that might be critical for network control and show that they have a larger than expected impact on the structural stability of the community.
+<!-- DBS: Do we need to introduce structural stability before mentioning it here? -->
 Finally, we compare the proposed approach to current methods based on species centrality and show how these methods are indeed valuable but ultimately paint a limited picture in regards to the "keystoneness" of a species and its role at supporting the diversity of its community.
+<!-- DBS: Is "supporting the diversity" the right function to call out at this point? -->
 
@@
 In pollination networks, however, this directionality is less obvious as both species can, in theory, benefit from the interaction. 
-We overcome that obstacle by noting that the extent to which species *i* affects species *j* relative to the extent to which *j* affects *i* can be summarised by the interaction asymmetry [@bascompte_asymmetric_2006].
+We overcome that obstacle by noting that the extent to which species *i* affects species *j* relative to the extent to which *j* affects *i* can be summarised by their interaction asymmetry [@bascompte_asymmetric_2006].
 This asymmetry is given by $$a(i,j) = a(j,i) = \frac{\left | d_{ij}-d_{ji} \right |}{max\left ( d_{ij}, d_{ji} \right )},$$ where the dependence of plant *i* on pollinator *j*, *d~ij~*, is the proportion of the visits from pollinator *j* compared to all pollinator visits to plant *i*.
 Previous research has shown that mutualistic interactions are often highly asymmetric in natural communities; in other words, if a plant species is largely dependent on a pollinator species, that pollinator tends to depend rather weakly on the plant (and vice versa).
-We, therefore, create a directed link from species *i* to species *j* when $d_{ij}-d_{ji} \geq 0$ to establish the most likely direction of control between a species pair (Figure \@ref(fig:fig-example-networks)a).
+We therefore create a directed link from species *i* to species *j* when $d_{ij}-d_{ji} \geq 0$ to establish the most likely direction of control between a species pair (Figure \@ref(fig:fig-example-networks)a).
 Sometimes there is no observed asymmetry between species pairs ($d_{ij}=d_{ji}$), and we cannot infer a dominant direction of control. 
-When this occurs, we deem both species to be equally likely to affect each other and form a reciprocal interaction between them (a link from *i* to *j* and another from *j* to *i*). 
+When this occurs, we deem both species to be equally likely to affect each other and leave a reciprocal interaction between them (a link from *i* to *j* and another from *j* to *i*). 
 By basing the direction of the links on the asymmetry of their dependence, we are able to generate a network that is consistent with the dynamics of the community while satisfying the requirements of structural controllability.
-That allows us to calculate the controllability of the networks and investigate whether there are differences between invaded and uninvaded communities.
+This allows us to calculate the controllability of the networks and investigate whether there are differences between invaded and uninvaded communities.
 
@@
 A simple version of such a system can be described by $\frac{dx}{dt} = Ax + Bu(t)$, where the change of its state over time ($\frac{dx}{dt}$) depends on its current state *x* (for example, the species' abundances), an external time-varying input *u(t)* (the control signal), and two matrices *A* and *B*, which encode information about the network structure and how species respond to external inputs, respectively.
-In classic control theory, determining wether this system is controllable can be achieved by checking that its controllability matrix $R= [ \begin{matrix}B & AB & A^{2}B & ...& A^{n-1}B\end{matrix} ]$ has full rank.
-In complex systems, however, employing this rank condition, or numerical approximations of it, is infeasible because it is hard to fully parameterize *A* and *B* (either because the weight of the links changes over time or because they are difficult to measure).
-Here we use an approach based on the structural controllability theorem [@lin_structural_1974], which assumes that we are confident about which elements of *A* and *B* have either non-zero or zero values (there is an interaction or not), but that we less sure about the precise magnitude of the non-zero values.
-Using this structural approach we can find out the controllability of a system for every non-zero realisations of the parameters.
-An intuitive way to understand structural controllability is by looking at its graphical interpretation: from a topological perspective a network is structurally controllable if there are no inaccessible nodes—nodes without incoming links—or dilations—*expansions* of the network (Figure \@ref(fig:fig-example-networks)b; Supporting Information Section \@ref(S-structural-controllability)).
+In classic control theory, determining whether this system is controllable can be achieved by checking that its controllability matrix $R= [ \begin{matrix}B & AB & A^{2}B & ...& A^{n-1}B\end{matrix} ]$ has full rank.
+In complex systems, however, employing this rank condition, or numerical approximations of it, is infeasible because it is hard to fully parameterise *A* and *B* (either because the weight of the links changes over time or because they are difficult to measure).
+Here, we use an approach based on the structural controllability theorem [@lin_structural_1974], which assumes that we are confident about which elements of *A* and *B* have either non-zero or zero values (there is an interaction or not), but that we less sure about the precise magnitude of the non-zero values.
+Using this structural approach, we can find out the controllability of a system for every non-zero realisation of the parameters.
+An intuitive way to understand structural controllability is by looking at its graphical interpretation: from a topological perspective a network is structurally controllable if there are no inaccessible nodes—that is, nodes without incoming links—or dilations—*expansions* of the network (Figure \@ref(fig:fig-example-networks)b; Supporting Information Section \@ref(S-structural-controllability)).
 <!-- The last sentence of the paragraph above sticks out a bit. -->
@@
 We are often able to estimate *A* in ecological networks, as this matrix represents the interactions between species. 
-Part of the control problem resides in estimating a supportable estimation of *B*, which represents the links between external inputs and species. 
+Part of the control problem thus resides in estimating a supportable estimation of *B*, which represents the links between external inputs and species. 
 Naively, any ecological community (and any system for that matter) could be controlled if we control the state of every species independently, but such an approach is typically impractical. 
 Here, we are interested in finding a minimum driver node-set (effectively finding *B*) with which to make the system controllable. 
-The brute-force search for this minimum driver node-set is computationally prohibitive for most networks as it involves the evaluation of $2^N$ different controllability matrices. 
+The brute-force search for this minimum driver node-set is computationally prohibitive for most networks as it involves the evaluation of $2^N$ different controllability matrices where $N$ is the number of species in the community.
 We therefore instead employ a recently-developed approach that shows that the control problem of finding the minimum driver node-set can be mapped into a graph-theoretic problem: maximum matching [@liu_controllability_2011; @liu_control_2016].
 
-Maximum-matching is a widely studied topic in graph theory and is commonly used in multiple applications, ranging from dating apps and wireless communications to organ transplant allocation and peer-to-peer file sharing.
-A matching in an unweighted directed graph is defined as a set of links that do not share a common start or end nodes; the largest possible matching is called a maximum matching. 
-For example, in a network composed by jobs and job applicants, a matching is any pairing between applicants and positions that satisfies one basic constraint: an applicant can be assigned to at most one position and vice versa.
+Maximum matching is a widely studied topic in graph theory and is commonly used in multiple applications, ranging from dating apps and wireless communications to organ transplant allocation and peer-to-peer file sharing.
+A matching in an unweighted directed graph is defined as a set of links that do not share common start or end nodes; the largest possible matching is called a maximum matching. 
+For example, in a network composed of jobs and job applicants, a matching is any pairing between applicants and positions that satisfies one basic constraint: an applicant can be assigned to at most one position and vice versa.
 Consequently, a maximum matching is an optimal pairing, one that maximises the number of applicants with jobs and the number of positions filled. 
@@
 The key is to note that the fundamental conditions of structural controllability imply that there is a one-to-one relationship between *superior* and *subordinate* nodes just like the one-to-one relationship between jobs and applicants (Figure \@ref(fig:fig-example-networks)b, bottom left).
+<!-- DBS: I think we should at least introduce what superior and subordinate means here even if they're also defined in the figure. -->
 We thus use the maximum-matching algorithm to find an optimal pairing of superior and subordinate nodes in a manner consistent with the controllability conditions (Supporting Information Section \@ref(S-one-maximum-matching)).
-Given the result, we can further decompose the matching into a set of paths that reveal how a control signal can flow across the links in a network to reach every node that composes it. 
+Given the result, we can further decompose the matching into a set of paths that reveal how a control signal can flow across the links in a network to reach every node within it. 
 As recently shown [@liu_controllability_2011], the minimum driver node-set---those to which an external control input should be applied to make the system controllable---corresponds exactly to the *unmatched* nodes in the network (Figure \@ref(fig:fig-control-configuration)).
@@
 However, we are interested in understanding the controllability of a network in a more general sense, such that it can be applied even when the precise control scenario is known only incompletely. 
-To this end, we chose an indicator that follows directly from our approach: the size of the minimum driver node-set. 
+To this end, we chose an indicator that follows directly from our approach: the size of the minimum driver-node set. 
 This simple metric provides a general indication of how difficult controlling a network might be, as systems that require a large number of external inputs to be fully controlled are intuitively more difficult or costly to manage.
 For instance, achieving full control in a "network" in which species do not interact at all is relatively more difficult as we would require an intervention for every single species. 
-Conversely, the structure of a linear trophic chain can be harnessed to achieve full control using just one intervention targeted the top species; the control signal would then cascade through the trophic levels and reach other species in the community.
-Specifically, drawing from the structural-controllability literature, we use the size of the minimum driver node-set relative to the total number of species $n_D = \frac{D}{N}$ as a measure of the *controllability* of a network—the extent to which the network structure can be harnessed to control the community.
+Conversely, the structure of a linear trophic chain can be harnessed to achieve full control using just one intervention targeted at the top species; a suitable control signal could then cascade through the trophic levels and reach other species in the community.
+Specifically, drawing from the structural-controllability literature, we use the size of the minimum driver-node set relative to the total number of species $n_D = \frac{D}{N}$ as a measure of the *controllability* of a network—the extent to which the network structure can be harnessed to control the community.
 In an ecological context, external inputs can be thought of as management interventions that modify the abundance of a particular species. 
@@
 After finding the minimum driver node-set in each of our networks, we wanted to test whether invasion status or other predictors are correlated to controllability. 
-We, therefore, use a set of generalised linear models (with binomial error structure). 
-The response variable was the size of the minimum driver node-set $n_D$ of the twenty empirical networks (ten invaded and ten uninvaded) and we included invasion status as a predictor. 
-We also include the network connectance, the network nestedness (NODF), the number of species [since one might naively expect to see a negative relationship between richness and controllability; @menge_indirect_1995], the network asymmetry (an indication of the balance between plant and pollinator diversity), and the interaction strength asymmetry [the asymmetry on the dependences between trophic levels; @bluthgen_specialization_2007].
-Models were compared using the Akaike Information Criterion for small sample sizes (AICc).
+We do this using a set of generalised linear models (with binomial error structure). 
+The response variable was the relative size of the minimum driver node-set $n_D$ of the twenty empirical networks (ten invaded and ten uninvaded), and we included invasion status as a predictor. 
+As predictors, we also include the network connectance, the network nestedness (NODF), the number of species [since one might naively expect to see a negative relationship between richness and controllability; @menge_indirect_1995], the network asymmetry (an indication of the balance between plant and pollinator diversity), and the interaction strength asymmetry [the asymmetry on the dependences between trophic levels; @bluthgen_specialization_2007].
+We compared models using the Akaike Information Criterion for small sample sizes (AICc).
 
@@
 In the first, we followed @vazquez_species_2007 and maintained the connectance of the network but randomised the visits across species such that the relative probabilities of interactions were maintained.
-We then calculated the direction of control and the corresponding size of the minimum driver node-set, $n_D$. 
-For the second null model, we used the empirical directed network and randomly shuffled the direction of control between a species pair.
+We then re-estimated the direction of control and the corresponding size of the minimum driver-node set, $n_D$. 
+For the second null model, we used the empirical directed network described above and randomly shuffled the direction of control between a species pair prior to re-estimating the size of the minimum driver-node set.
 
@@
 
-Our second key question is related to how species differ in their ability to drive the population dynamics of the community.
-Ecologically, these differences are relevant because resources and data are limited, and therefore full control is unfeasible. 
-While calculating the size of the minimum drive node-set can measure the controllability of an ecological community, it does not provide information about the roles that particular species play.
+Our second ecological objective is related to how species differ in their ability to drive the population dynamics of the community.
+Ecologically, these differences are relevant because resources and data are limited, and therefore full control is infeasible. 
+While calculating the size of the minimum drive-node set can measure the controllability of an ecological community, it does not provide information about the roles that particular species play.
 
 To answer this question, we harness the fact there may be multiple maximum matchings for a given network, and each of these maximum matchings indicates a unique combination of species with which is possible to control the network.
-Some species belong to these combinations more often than others. 
-We call this property a species control capacity, $\phi$. 
-The higher a species control capacity, the higher the likelihood that they would need to be directly managed to change (or maintain) the ecological state of their communities. 
-Therefore a species' control capacity is an estimation of their relative importance at driving the state of the community [@jia_control_2013].
+Moreover, some species belong to these combinations more often than do others. 
+We call this property a species "control capacity", $\phi$. 
+The higher a species control capacity, the greater the likelihood that they would need to be directly managed to change (or maintain) the ecological state of their community. 
+Therefore a species control capacity provides an estimation of their relative importance at driving the state of the community [@jia_control_2013].
 
-To calculate a species control capacity $\phi$, we need to enumerate all possible maximum matchings (Supporting Information Section \@ref(S-all-maximum-matching)). 
-However, enumerating all maximum matchings is extremely expensive from a computational perspective—a network with a couple dozen species has several hundred million unique maximum matchings. 
-To solve this problem, we employ a recently-developed algorithm that reveals the control correlations between the nodes in the graph using considerably less computational resources [@zhang_input_2016].
-Using this algorithm, we are able to identify species that are possible control inputs—those that belong to the minimum driver node-set in at least one of the possible control configurations. 
-One of the original contributions of our work is to extend this algorithm such that it is possible to calculate a highly accurate approximation of the control capacity $\phi_i$ of every species in the network (Supporting Information Section \@ref(S-input-graph)).
-In the networks that contained reciprocal links (because there was no asymmetry in the dependences of a species pair), we averaged a species' control capacity $\phi$ across every possible "non-reciprocal" version of the network (Supporting Information Section \@ref(S-reciprocal-links)).
+To calculate a species control capacity $\phi$, we must first enumerate all possible maximum matchings (Supporting Information Section \@ref(S-all-maximum-matching)). 
+Unfortunately, enumerating all maximum matchings is extremely expensive from a computational perspective—a network with a couple dozen species has several hundred million unique maximum matchings. 
+To solve this problem, we employ a recently-developed algorithm that reveals the control correlations between the nodes in the graph while requiring considerably less computational resources [@zhang_input_2016].
+Using this algorithm, we are able to identify species that are possible control inputs—those that belong to the minimum driver-node set in at least one of the possible control configurations. 
+Here, we extend this algorithm such that it is possible to calculate a highly accurate approximation of the control capacity $\phi_i$ of every species in the network (Supporting Information Section \@ref(S-input-graph)).
+In the networks that contained reciprocal links (because there was no asymmetry in the dependences of a species pair), we averaged a species control capacity $\phi$ across every possible "non-reciprocal" version of the network (Supporting Information Section \@ref(S-reciprocal-links)).
 
 We then examined how species-level properties were related to control capacity using a set of generalised linear models with binomial error structure.
-As explanatory variables, we included five variables. 
+These models included five predictor variables that mirror the network-level predictors. 
 First, the species contribution to nestedness, which has been proposed as a key feature that promotes stability and robustness in mutualistic networks [@saavedra_strong_2011]. 
 Second, the species strength (the sum of a species' visits), which quantifies the strength of a species associations and is indirectly related to its abundance [@poisot_comparative_2012]. 
-Third, the direction of asymmetry which quantifies the net balance in dependencies, this is it indicates if a species affects other species more than what they affect it or not [@vazquez_species_2007].
-Fourth, the species degree in order to account for the centrality of a species. 
+Third, the direction of asymmetry which quantifies the net balance in dependencies; that is it indicates if a species affects other species more than what they affect it or not [@vazquez_species_2007].
+Fourth, the species degree in order to account for the innate centrality of a species.
 Finally, we included a categorical variable for the species trophic level (plant or pollinator) and an interaction term between trophic level and the previous four variables. 
 To facilitate comparison between predictors, degree and visitation strength were log-transformed and all four continuous variables were scaled to have a mean of zero and a standard deviation of one.
+To identify the models that were best supported by the data, we first determined the most parsimonious random structure using the AICc. 
+The relative importance of variables was then assessed by looking at their effect sizes in the top-ranked models and the cumulative weight of the models in which they are present.
 
-To identify the models that were best supported by the data we first determined the most parsimonious random structure using the AICc. 
-The relative importance of variables was then assessed by looking at both their effect sizes in the top-ranked models and the cumulative weight of the models in which they are present.
-
-Some species have a control capacity $\phi = 1$. 
-These species are critical to controlling community because they are part of the minimum driver node-set in every control scenario. 
-In other words, it is not possible to drive the state of the community to a desired state without directly managing the abundance of these species. 
-We anticipate that these species have a disproportionally large impact on the community dynamics. 
-Therefore, we determined the critical species in each of the networks and investigated whether they have a larger than average impact on the stable coexistence of species in the community. 
-This property of promoting stable coexistence is called structural stability [@rohr_structural_2014]. 
-Mathematically it is denoted by the letter $\Omega$ and represents the size of the parameter space (growth rates, carrying capacities) under which all species can sustain positive abundances [@saavedra_nested_2016].
-The contribution of species *i* to stable coexistence, can be estimated by calculating the structural stability of the community when the focal species *i* is removed. 
-We then used a t-test to compare the contribution to stable coexistence of critical and non-critical species. 
+Our analysis revealed that some species have a control capacity $\phi_i = 1$. 
+These species are critical to controlling their community because they are part of the minimum driver-node set in *every* control scenario. 
+In other words, it is theoretically impossible to drive the state of the community to a desired state without directly managing the abundance of these species. 
+We thus anticipate that these species have a disproportionally large impact on the community dynamics. 
+To test this hypothesis, we identified these critical species in each of the networks and investigated whether they have a larger than average impact on the stable coexistence of species in the community.
+Within mutualistic networks, one useful measure of for how networks impact stable coexistence is called structural stability [@rohr_structural_2014]. 
+Mathematically, the structural stability $\Omega$ of a network represents the size of the parameter space (i.e., growth rates, carrying capacities, etc.) under which all species can sustain positive abundances [@saavedra_nested_2016].
+The contribution of any given species *i* to stable coexistence can be estimated by calculating the structural stability of the community when the focal species *i* is removed. 
+Given these species-specific estimates of structural stability, we then used a t-test to compare the contribution to stable coexistence of critical and non-critical species. 
 More details about the calculation of structural stability can be found in the Supporting Information Section \@ref(S-structural-stability).
 
-Finally, we wanted to understand how two species level control metrics are correlated with five metrics of keystoness based on centrality. 
-The first control metric we use is a species control capacity $\phi$. 
+<!-- DBS: I think we're far too sloppy about when things like phi have subscripts and when they don't. We really should be consistent throughout. -->
+Finally, we wanted to understand how two species-level control metrics are related to five metrics of keystoneness based on centrality. 
+For the centrality metrics, we use a species' degree, betweenness, eigen centrality, page rank, and closeness centrality. 
+<!-- DBS: You MUST cite where these centrality metrics come from. -->
+The first control metric we use is a species control capacity $\phi$ described above. 
 The second metric is the probability that a focal species influences the abundance of another species internally, regardless of whether a management intervention is required in that species or not. 
@@
 Because superior nodes are those at the beginning of a matched link, \(\sigma\) could be seen as a "softer" version of control capacity. 
-Conveniently, unlike the minimum driver node-set, superior species are the same for all control configurations and so in a network without reciprocal links the probability that a species is superior $\sigma$ is either 1 or 0.
-Specifically, we compare a species control capacity $\phi$ and the probability that a species is used to internally control another species in the network being superior $\sigma$. 
-As centrality metrics, we use a species' degree, betweenness, eigen centrality, page rank, and closeness centrality.
+Conveniently, unlike the minimum driver-node set, superior species are the same for all control configurations and so in a network without reciprocal links the probability that a species is superior $\sigma$ is either 1 or 0.
+<!-- DBS: I think that the statement above needs a reference as I don't think this is "new" here nor do I think everyone will necessarily understand why it's true without pointing them to a more formal explanation.
+-->
 
@@
 \R{testing-assumptions-line}Just like the centrality metrics, the information obtained by applying structural controllability depends on the ability of the network to accurately represent the ecological community.
-We tested the sensitivity of our approach to two fundamental assumptions. 
-First, we tested that visitation is an appropriate proxy to infer interspecific effects. 
-To do that we compared the results obtained using visitation to two alternative metrics in a dataset that lacked invasive species [@ballantyne_constructing_2015]. 
+We thus tested the sensitivity of our approach to two fundamental assumptions. 
+First, we tested that visitation is an appropriate proxy to infer interspecific effects by comparing the results obtained using visitation to two alternative metrics in a separate dataset that lacked invasive species [@ballantyne_constructing_2015].
 Specifically, we also applied the structural controllability approach to networks constructed using pollinator efficiency (which measures the pollen deposition of an interaction) and pollinator importance [which accounts for both pollen deposition and visitation and hence is regarded as a more accurate estimation of the pollination service received by plants; @neeman_framework_2009].
 More details in the Supporting Information Section \@ref(S-visitation-as-proxy).
-Second, because interspecific dependencies depend on the network topology and consequently on the accurate sampling of interactions, we tested the robustness of structural controllability to the uncertainty involved with the sampling of interactions.
-To do that we compared the results obtained when using the full network and when randomly removing interactions from the weakest links in the network. 
+Second, because interspecific dependencies themselves depend on the network topology and consequently on the accurate sampling of interactions, we tested the robustness of structural controllability to the uncertainty involved with the sampling of interactions.
+Here, we compared the results obtained when using the full network and when randomly removing interactions from the weakest links in the network. 
 This effectively removed the rare interactions from the networks (more details in the Supporting Information Section \@ref(S-undersampling)).

### 2018-06-26 paper/manuscript.Rmd
proper hyphenation of minimum driver-node set

@@
 Naively, any ecological community (and any system for that matter) could be controlled if we control the state of every species independently, but such an approach is typically impractical. 
-Here, we are interested in finding a minimum driver node-set (effectively finding *B*) with which to make the system controllable. 
-The brute-force search for this minimum driver node-set is computationally prohibitive for most networks as it involves the evaluation of $2^N$ different controllability matrices where $N$ is the number of species in the community.
-We therefore instead employ a recently-developed approach that shows that the control problem of finding the minimum driver node-set can be mapped into a graph-theoretic problem: maximum matching [@liu_controllability_2011; @liu_control_2016].
+Here, we are interested in finding a minimum driver-node set (effectively finding *B*) with which to make the system controllable. 
+The brute-force search for this minimum driver-node set is computationally prohibitive for most networks as it involves the evaluation of $2^N$ different controllability matrices where $N$ is the number of species in the community.
+We therefore instead employ a recently-developed approach that shows that the control problem of finding the minimum driver-node set can be mapped into a graph-theoretic problem: maximum matching [@liu_controllability_2011; @liu_control_2016].
 
@@
 Given the result, we can further decompose the matching into a set of paths that reveal how a control signal can flow across the links in a network to reach every node within it. 
-As recently shown [@liu_controllability_2011], the minimum driver node-set---those to which an external control input should be applied to make the system controllable---corresponds exactly to the *unmatched* nodes in the network (Figure \@ref(fig:fig-control-configuration)).
+As recently shown [@liu_controllability_2011], the minimum driver-node set---those to which an external control input should be applied to make the system controllable---corresponds exactly to the *unmatched* nodes in the network (Figure \@ref(fig:fig-control-configuration)).
 
@@
 In directed networks, a maximum matching is the largest possible set of links that do not share start or end nodes (dark purple).
-Maximum matchings are not necessarily unique, instead, each of them is related to a possible minimum driver node-set in the network (the nodes to which an external control input, in orange, should be applied in order to ensure controllability).
-The size of the minimum driver node-set *D* corresponds exactly to the number of unmatched nodes (the number of nodes in the network *N* minus the matching size).
-To account for network size, we use the size of the minimum driver node-set relative to the total number of nodes *n~D~ = D/N* as a measure of the extent to which the network structure can be harnessed to control the system."}
+Maximum matchings are not necessarily unique, instead, each of them is related to a possible minimum driver-node set in the network (the nodes to which an external control input, in orange, should be applied in order to ensure controllability).
+The size of the minimum driver-node set *D* corresponds exactly to the number of unmatched nodes (the number of nodes in the network *N* minus the matching size).
+To account for network size, we use the size of the minimum driver-node set relative to the total number of nodes *n~D~ = D/N* as a measure of the extent to which the network structure can be harnessed to control the system."}
 replayPlot(fig_control_config$plot)
@@
 
-After finding the minimum driver node-set in each of our networks, we wanted to test whether invasion status or other predictors are correlated to controllability. 
+After finding the minimum driver-node set in each of our networks, we wanted to test whether invasion status or other predictors are correlated to controllability. 
 We do this using a set of generalised linear models (with binomial error structure). 
-The response variable was the relative size of the minimum driver node-set $n_D$ of the twenty empirical networks (ten invaded and ten uninvaded), and we included invasion status as a predictor. 
+The response variable was the relative size of the minimum driver-node set $n_D$ of the twenty empirical networks (ten invaded and ten uninvaded), and we included invasion status as a predictor. 
 As predictors, we also include the network connectance, the network nestedness (NODF), the number of species [since one might naively expect to see a negative relationship between richness and controllability; @menge_indirect_1995], the network asymmetry (an indication of the balance between plant and pollinator diversity), and the interaction strength asymmetry [the asymmetry on the dependences between trophic levels; @bluthgen_specialization_2007].
@@
 
-The size of the minimum driver node-set relative to the number of species in each network $n_D$ ranged between $n_D = `r round(min(c_m$n_D), 2)`$ and $n_D = `r round(max(c_m$n_D), 2)`$ (median `r round(median(c_m$n_D), 2)`).
-We found that the relative size of the minimum driver node-set of invaded communities was not significantly different from that of communities that have not been invaded (Figure \@ref(fig:fig-emp-controllability)a).
+The size of the minimum driver-node set relative to the number of species in each network $n_D$ ranged between $n_D = `r round(min(c_m$n_D), 2)`$ and $n_D = `r round(max(c_m$n_D), 2)`$ (median `r round(median(c_m$n_D), 2)`).
+We found that the relative size of the minimum driver-node set of invaded communities was not significantly different from that of communities that have not been invaded (Figure \@ref(fig:fig-emp-controllability)a).
 Contrastingly, there was an important negative relationship between $n_D$ and the network asymmetry (Figure \@ref(fig:fig-emp-controllability)b). 
@@
 
-```{r fig-emp-controllability, fig.width=fig_sizes()[[2]], fig.height=fig_sizes()[[1]]/2, fig.cap="(a) Density plot of the relative size of the minimum driver node-set $n_D$ in the invaded (light) and uninvaded (dark) empirical networks.
+```{r fig-emp-controllability, fig.width=fig_sizes()[[2]], fig.height=fig_sizes()[[1]]/2, fig.cap="(a) Density plot of the relative size of the minimum driver-node set $n_D$ in the invaded (light) and uninvaded (dark) empirical networks.
 (b) The relationship between the asymmetry plant/pollinator richness and $n_D$.
 The plot shows the values predicted by the most parsimonious model.
-(c) The density distribution of the difference between the relative size of the minimum driver node-set of random networks and that of empirical networks.
+(c) The density distribution of the difference between the relative size of the minimum driver-node set of random networks and that of empirical networks.
 We randomised either the species visitation patterns (light line) or randomised the direction of control between a species pair (dark line).
@@
 We found a very strong agreement between results obtained using the complete empirical networks and those obtained by randomly removing interactions (Supporting Information Section \@ref(S-undersampling)).
-Despite removing rare interactions and species, the relative size of the minimum driver node-set, the superior species, and the relative rankings of control capacity were generally maintained.
+Despite removing rare interactions and species, the relative size of the minimum driver-node set, the superior species, and the relative rankings of control capacity were generally maintained.
 Remarkably critical species in the full network were also critical in the vast majority of rarefied networks.
@@
   "controllability" = "The intrinsic difficulty of controlling an ecological community.
-It is measured by the relative size of the minimum driver node-set, $n_D$.
+It is measured by the relative size of the minimum driver-node set, $n_D$.
 It also indicates the extent to which network structure can be harnessed for network control.",
-  "minimum driver node-set" = "One of the often many smallest sets of species whose abundances need to be directly managed in order to achieve full control of the community.
-The minimum driver node-sets can be obtained by finding all maximum matchings in a network.",
+  "minimum driver-node set" = "One of the often many smallest sets of species whose abundances need to be directly managed in order to achieve full control of the community.
+The minimum driver-node sets can be obtained by finding all maximum matchings in a network.",
   "maximum matching" = "A matching is a set of links that do not share a common start or end nodes; the largest possible matching is called a maximum matching.",
-  "control configuration" = "One of the species combinations with which is possible to achieve network control. Optimal control configurations are given by the minimum driver node-sets.", 
+  "control configuration" = "One of the species combinations with which is possible to achieve network control. Optimal control configurations are given by the minimum driver-node sets.", 
   "control capacity" = "The relative frequency \\(\\phi\\) which with a species is part of the optimal control configurations of a network.", 
@@
 
-The median size of the relative minimum driver node-set of in our dataset was $n_D = `r round(median(c_m$n_D),2)`$. 
+The median size of the relative minimum driver-node set of in our dataset was $n_D = `r round(median(c_m$n_D),2)`$. 
 This value is high when compared to other complex systems in which controllability has been investigated.  

### 2018-06-26 paper/manuscript.Rmd
dbs further edits to text; only captions are left to go through

@@
 We found that the relative size of the minimum driver-node set of invaded communities was not significantly different from that of communities that have not been invaded (Figure \@ref(fig:fig-emp-controllability)a).
-Contrastingly, there was an important negative relationship between $n_D$ and the network asymmetry (Figure \@ref(fig:fig-emp-controllability)b). 
-Furthermore, there were also negative, albeit weaker, correlations between $n_D$ and connectance, nestedness and species richness (Table  \@ref(S-tab:tab-controllability-model-results)). 
-The relative size of the minimum driver-node set $n_D$ of empirical networks did not differ to that of a null model that roughly preserved the degree distribution and fully preserved the network connectance ($p = `r sprintf('\\num{%s}', format(randomisations_test$interactions$p.value, digits = 2))`$; Figure \@ref(fig:fig-emp-controllability)c).
-However empirical networks had a larger $n_D$ than null models that preserved the interactions but shuffled the direction of control of the empirical network ($p = `r sprintf('\\num{%s}', format(randomisations_test$directions$p.value, digits = 2))`$).
+In contrast, there was an important negative relationship between $n_D$ and the network asymmetry (Figure \@ref(fig:fig-emp-controllability)b).
+<!-- DBS: "important" doesn't mean anything statistically. was it significant? -->
+Furthermore, there were also negative, albeit weaker, relationships between $n_D$ and connectance, nestedness and species richness (Table  \@ref(S-tab:tab-controllability-model-results)). 
+The relative size of the minimum driver-node set $n_D$ of empirical networks did not differ from that of a null model that roughly preserved the degree distribution and fully preserved the network connectance ($p = `r sprintf('\\num{%s}', format(randomisations_test$interactions$p.value, digits = 2))`$; Figure \@ref(fig:fig-emp-controllability)c).
+However, empirical networks had a larger $n_D$ than null models that preserved the interactions but shuffled the direction of control of the empirical network ($p = `r sprintf('\\num{%s}', format(randomisations_test$directions$p.value, digits = 2))`$).
 
@@
 Species varied widely in their control capacity (Figure \@ref(fig:fig-species-level)). 
-Pollinators had, in average, larger control capacities than plants but almost no pollinator was critical for network control (a species is critical for control if it has control capacity of \(\phi = 1\)).
-Plants had a bimodal distribution with maxima in both extremes of the distribution (Figure \@ref(fig:fig-species-level)a). 
-Remarkably, every invasive species was critical for network control in each of their communities.
-The species level models indicate a positive relationship between control capacity \(\phi\) and a species' contribution to nestedness, visitation strength, and the asymmetry of the dependence (Table \@ref(tab:tab-model-selection-table); Figure \@ref(fig:fig-species-level); Table \@ref(S-tab:tab-model-output-species-level)).
+Pollinators had, in average, larger control capacities than plants.
+That said, almost no pollinator was critical for network control, where a species is critical for control if it has control capacity \(\phi_i = 1\)).
+Plants had a multimodal distribution of control capacity with maxima at both extremes of the distribution (Figure \@ref(fig:fig-species-level)a). 
+Intriguingly, every invasive species was critical for network control in each of their communities.
+The species-level models identified a positive relationship between control capacity \(\phi\) and a species' contribution to nestedness, visitation strength, and the asymmetry of its dependences (Table \@ref(tab:tab-model-selection-table); Figure \@ref(fig:fig-species-level); Table \@ref(S-tab:tab-model-output-species-level)).
 Comparatively, species' degree was only weakly associated with control capacity (Table \@ref(S-tab:tab-var-importance)). 
-In fact, many species with a low degree, especially pollinators, attained a large control capacity in their communities (Figure \@ref(S-fig:fig-species-models-degree)a).
+In fact, many species with a low degree, especially pollinators, exhibited a large control capacity in their communities (Figure \@ref(S-fig:fig-species-models-degree)a).
 
@@
 
-We also found that critical species have a large impact on species coexistence. 
+We also found that critical species have a particularly large impact on species coexistence when compared to non-critical species.
 Indeed, the structural stability of the network was considerably reduced when these species were removed from their communities ($p = `r sprintf('\\num{%s}', format(crit_test$p.value, digits = 2))`$; Figure \@ref(fig:fig-structural-stability); Supporting Information \@ref(S-structural-stability)).
+<!-- DBS: I wonder if people will have a hard time understanding what these values mean.
+That is, the differences are clear visually but what do those values of Omega actually mean?
+I am almost certain a reviewer is going to nag about this.
+-->
 
@@
 
-The control capacity of a species $\phi$ was only weakly correlated with commonly used centrality metrics. 
-The Spearman correlation ranged between `r round(min(correlations$control_capacity), 2)` (with betweeness-centrality) and `r round(max(correlations$control_capacity), 2)` (with eigen-centrality). 
-On the other hand, the probability of being a superior species $\sigma$ was slightly more similar to established centrality metrics. 
-The Spearman correlation coefficient ranged between `r round(min(correlations$superior), 2)` (with eigen-centrality) and `r round(max(correlations$superior), 2)` (with degree; Figure \@ref(S-fig:fig-correlogram)).
+Species control capacity $\phi$ was only weakly correlated with commonly-used centrality metrics. 
+The Spearman correlation between these ranged between `r round(min(correlations$control_capacity), 2)` (with betweeness-centrality) and `r round(max(correlations$control_capacity), 2)` (with eigen-centrality).
+On the other hand, the probability of being a superior species $\sigma$ was slightly more correlated to established centrality metrics as its Spearman correlation ranged between `r round(min(correlations$superior), 2)` (with eigen-centrality) and `r round(max(correlations$superior), 2)` (with degree; Figure \@ref(S-fig:fig-correlogram)).
 Despite the higher correlation with species' degree, with the exception of specialists that had only one interaction, we observed many species with a low degree and a  high probability of being superior nodes (Figure \@ref(S-fig:fig-species-models-degree)b).
+<!-- DBS: Please rephrase this last sentence and/or chop it into two. It's unclear to me (at least) in particular the "with the exception" part. -->
 
@@
 Importantly, we also found that structural stability is robust to incomplete sampling of interactions. 
-We found a very strong agreement between results obtained using the complete empirical networks and those obtained by randomly removing interactions (Supporting Information Section \@ref(S-undersampling)).
+Indeed, we found strong agreement between results obtained using the complete empirical networks and those obtained by randomly removing the weakest interactions (Supporting Information Section \@ref(S-undersampling)).
 Despite removing rare interactions and species, the relative size of the minimum driver-node set, the superior species, and the relative rankings of control capacity were generally maintained.
-Remarkably critical species in the full network were also critical in the vast majority of rarefied networks.
+Of particular note, we found that critical species in the full network were also critical in the vast majority of rarefied networks.
 
@@
 To achieve that goal we applied *structural controllability*, a field at the intersection between control and complex theory that allow us to obtain two key pieces of information: the *controllability* of a network and a species *control capacity* (Table \@ref(tab:tab-glossary)).
+<!-- DBS: Two sentences does not make a paragraph.... Please add one more that summarizes what we found. -->
 
@@
 The median size of the relative minimum driver-node set of in our dataset was $n_D = `r round(median(c_m$n_D),2)`$. 
-This value is high when compared to other complex systems in which controllability has been investigated.  
-For instance,  only gene regulation networks appear to achieve similar levels of controllability while most social, power transmission, internet, neuronal, and even metabolic networks seem to be easier to control ($0.1 < n_D < 0.35$) [@liu_controllability_2011].
+This value is high when compared to other complex systems in which controllability has been investigated;  
+for instance, only gene regulation networks appear to achieve similar levels of controllability while most social, power transmission, internet, neuronal, and even metabolic networks seem to be "easier" to control ($0.1 < n_D < 0.35$) [@liu_controllability_2011].
 These results indicate that fully controlling ecological networks might currently be out of reach for all but the smallest communities [@motter_networkcontrology_2015]. 
-Nevertheless, structural controllability might be helpful at identifying communities in which changes in the ecological state are more likely to occur and provides solid theoretical explanation to the many difficulties encountered in the management and restoration of natural communities.
+Nevertheless, structural controllability might be helpful at identifying communities in which changes in the ecological state are more likely to occur and provides solid theoretical rationale for the many difficulties encountered in the management and restoration of natural communities [@addrefs].
 
 When controlling for network structure, we found no difference between the controllability of invaded and uninvaded networks. 
-Our results suggest that the differences between the controllability networks are instead likely to arise from differences in their structure. 
+These results suggest that the differences between the controllability across networks are instead likely to arise from differences in their structure. 
 Specifically, we found that network controllability is almost completely constrained by the patterns of species richness at each trophic guild and their degree distributions [@melian_complex_2002; @bluthgen_specialization_2007].
-These two factors are particularly relevant because they govern the asymmetric nature of mutual dependences-which constitute the foundations of structure and stability in mutualistic networks [@bascompte_asymmetric_2006; @memmott_tolerance_2004; @astegiano_robustness_2015].
+These two factors are particularly relevant because they govern the asymmetric nature of mutual dependences, which themselves provide the foundation of structure and stability in mutualistic networks [@bascompte_asymmetric_2006; @memmott_tolerance_2004; @astegiano_robustness_2015].
 
-Accordingly, our results suggest that structural controllability is closely related to the persistence of an ecological community. 
-First, we found a comparatively small but tantalising negative relationship between the controllability of a network and the nestedness of its interactions. 
-Previous studies indicate that nestedness promotes species coexistence and confers robustness to despeciation [@bastolla_architecture_2009; @memmott_tolerance_2004] at the expense of the dynamic stability of the mutualistic community [@saavedra_nested_2016].
+Accordingly, our results suggest that structural controllability is closely related to the dynamic persistence of an ecological community. 
+First, we found a comparatively small but thought-provoking negative relationship between the controllability of a network and the its nestedness. 
+Previous studies indicate that nestedness promotes species coexistence and confers robustness to extinction [@bastolla_architecture_2009; @memmott_tolerance_2004] even at the expense of the dynamic stability of the mutualistic community [@saavedra_nested_2016].
 These observations are in agreement with our results, as we would expect the dynamic stability of a community to be correlated to the difficulty to control it. 
@@
 
-When controlling for a species' strength (which is indirectly a proxy of its abundance) and the net balance of its dependencies, we found that control capacity could not be easily predicted by species' degree or other metrics of centrality.
+When controlling for a species' strength, which is indirectly a proxy of its abundance, and the net balance of its dependencies, we found that control capacity could not be easily predicted by species' degree or other metrics of centrality.
 For instance, some species with a low degree achieved the maximum control capacity and were critical for control in their communities. 
@@
 On the contrary, most species with a large degree also have a large control capacity and all of them were classified as superior nodes which corroborates the utility of classic centrality metrics. 
-What our results do, is to take previous findings one step further and suggest that centrality might paint only a limited picture of the relevance of species.
+Putting these observations together, our results therefore take previous findings one step further and suggest that centrality might paint an incomplete picture of the relevance of species.
 
@@
 First, structural controllability emphasizes that the effect a species has on the abundance of other species is not independent of the effects of other other species in their community. 
-Second, it demonstrates that to ensure the persistence of a community it is often necessary to consider the abundances of more than a single species, even when full control is unfeasible or undesired (for example `r round(sum(crit$n_crit > 1)/nrow(crit)*100)`% of our communities contained more than one critical species).
+Second, it demonstrates that to ensure the persistence of a community it is often necessary to consider the abundances of more than a single species, even when full control is infeasible or undesired (for example `r round(sum(crit$n_crit > 1)/nrow(crit)*100)`% of our communities contained more than one critical species).
 Third, structural controllability explicitly acknowledges the existence of multiple management strategies and some will be better than others depending on the context.
-Approaches to prioritise species for conservation and reintroduction based on traits or centrality are still useful and are likely to overlap with a species' control capacity\R{extra-references-1} [@pires_friendship_2017; @devoto_understanding_2012].
-Altogether, our results also provide support to the idea that management decisions should not be based on a single technique, but indicates that focusing on ecosystem processes and interactions may be more effective than traditional ranking based approaches\R{extra-references-2} [@harvey_bridging_2017].
+Approaches to prioritise species for conservation and reintroduction based on traits or centrality are still useful and are likely to overlap with species control capacity\R{extra-references-1} [@pires_friendship_2017; @devoto_understanding_2012].
+Stepping back, our results also provide support to the idea that management decisions should not be based on a single technique but indicate that focusing on ecosystem processes and interactions may be more effective than traditional ranking-based approaches \R{extra-references-2} [@harvey_bridging_2017].
 
-The choice of the invaded/uninvaded networks was based on our desire to contrast the extensive empirical evidence of the role of invasive plants with our theoretical results. 
-We found that without exception, invasive plants were critical for network control and as such our results were in line with our expectations. 
+Our choice of studying invaded/uninvaded networks was based on a desire to contrast the extensive empirical evidence of the role of invasive plants with our theoretical results. 
+Without exception, we found that invasive plants were critical for network control and as such our results were in line with our expectations. 
 Invasive plants have been previously found to exacerbate the asymmetries in their communities [@aizen_invasive_2008; bartomeus_contrasting_2008-1; @henriksson_strong_2016] and to be central in their communities [@vila_invasive_2009; @palacio_generalist_2016].
@@
 
-Structural stability assumes that the networks can be approximated using linear functional responses. 
-The ramifications of this assumption imply that while structural controllability is useful to identify species that are relevant for network control, it cannot be used to design the precise interventions that should be applied to these species in order to achieve a desired state.
-While in an ideal scenario we would completely incorporate the species dynamics into the controllability analysis [@cornelius_realistic_2013], the reality is that such information is rarely available in most ecological scenarios.
+Structural controllability assumes that the networks can be approximated using linear functional responses [@addrefs]. 
+The ramifications of this assumption imply that, while structural controllability is useful to identify species that are relevant for network control, it cannot be used to design the *exact* interventions that should be applied to these species in order to achieve a desired state.
+In an ideal scenario, we would completely incorporate the species dynamics into the controllability analysis [@cornelius_realistic_2013]; the reality is that such information is rarely available in most ecological scenarios.
 \R{data-requirements}In contrast, structural controllability only requires a quantitative approximation of the network's interactions to gain valuable insight from the community.
 Furthermore, unlike centrality metrics, the assumptions of structural controllability are explicit and the estimation of a species importance arises from a mechanistic understanding of the population dynamics between species.
-By accounting for network dynamics (even if in a simple way) it incorporates more ecological realism even in the extreme scenario where the state of a community depends almost exclusively on nodal dynamics rather than on the topology of their interactions.
+By accounting for network dynamics (even if in a simple way), it incorporates more ecological realism even in the extreme scenario where the state of a community depends almost exclusively on nodal dynamics rather than on the topology of their interactions.
+<!-- DBS: See what everyone else says about these last two sentences. I think they get harder and harder to follow as they evolve. -->
+
+# Conclusions
 
@@
 These characteristics make structural stability an ideal framework to evaluate the effects of invasions and other types of perturbations. 
-Importantly, structural controllability can be used to identify critical species in the community. 
-Critical species promote biodiversity and underpin the stable coexistence of species in their community.
-Collectively critical species dominate the state of their community and therefore are likely to be highly relevant for ecosystem management and conservation. 
-Centrality metrics which have often been used as a proxy for keystoneness, although useful, fail to identify some of these species which highlights their limitations when we embrace that ecological communities are dynamical systems.
+Importantly, structural controllability can be used to identify critical species in the community that promote biodiversity and underpin the stable coexistence of species in their community.
+Collectively, critical species dominate the state of their community and therefore are likely to be highly relevant for ecosystem management and conservation. 
+While useful, centrality metrics, which have often been used as a proxy for keystoneness, fail to identify some of these species which highlights their limitations when we fully embrace the notion that ecological communities are dynamical systems.
 @paine_note_1969 showed nearly 50 years ago that one single species can dominate the state of its community. 
 Structural controllability suggests that this situation might be the exception rather than the rule. 
-We see our study as a starting point to study the controllability of ecological and socio-ecological systems where many exciting questions lie ahead.
+<!-- We see our study as a starting point to study the controllability of ecological and socio-ecological systems where many exciting questions lie ahead.  -->
 
-# Awknoledgements
+# Acknowledgements
 
+<!-- DBS: Surely we had this before. Please copy it from a previous submission. And definitely DON'T submit without the right acknowledgement text! -->
 A brief statement acknowledging collaborators and research assistants who do not meet the criteria for authorship described above, or acknowledging funding sources, providing relevant permit numbers (including institutional animal use permits), or giving recognition to nature reserves or other organizations that made the work possible.
@@
 
+<!-- DBS: Surely we had this before. Please copy it from a previous submission. -->
 All submissions with more than one author must include an Authors’ contributions statement. All persons listed as authors on a paper are expected to meet ALL of the following criteria for authorship:

### 2018-06-26 paper/manuscript.Rmd
revised caption of figure 1

@@
 ```{r fig-example-networks, fig.width=fig_struct_control$width, fig.height=fig_struct_control$height, fig.cap="The direction of control and controllability conditions.
-(a) To establish the direction of control we start with a weighted visitation network (on the left).
+(a) To establish the direction of control, we start with a weighted visitation network (on the left).
 In this network, the width of the links corresponds to the frequency of visitation between animals $a_i$ and plants $p_i$, with wider links indicating more visits.
-Plant $p_1$ is visited exclusively by $a_1$ but $p_1$ represents only a small fraction of the floral resources of $a_1$.
-Therefore the population of $p_1$ is more likely to be affected by $a_1$ than vice-versa.
-We represent this with a directed link from $a_1$ to $p_1$ (right).
+Plant $p_1$ is visited exclusively by $a_1$ but $p_1$ represents only a small fraction of the floral resources exploited by $a_1$.
+Therefore, the population of $p_1$ is more likely to be affected by $a_1$ than vice versa.
+We represent this with a directed link from $a_1$ to $p_1$ in the control network (on the right).
 The direction of control between all other species pairs can be similarly determined by inspecting the difference between their relative dependences.
-(b) Once we have established the directions of control we can determine whether the network is controllable or not.
-A system defined by a directed network (with state nodes $x_i$; species populations in an ecological context) and external control inputs (nodes $u_i$, orange links) is structurally controllable if it satisfies two conditions: it has no dilations (expansions in the network) and no inaccessible nodes.
-The system on the top left is not controllable because there is a dilation in which node $x_2$ is being used to control two nodes simultaneously, in other words, there are fewer superiors ($x_2$) than subordinates ($x_1$ and $x_3$).
-The network in the top right is not controllable because node $x_3$ is inaccessible for the only input node $u_1$ in the system.
-Both systems can be made controllable by adding an extra input node (top)."}
+(b) Once we have established the directions of control, we can determine whether the network is controllable or not.
+Any system defined by a directed network (with state nodes $x_i$; species populations in an ecological context) and external control inputs (nodes $u_i$, orange links) is structurally controllable if it satisfies two conditions: it has no dilations (expansions in the network) and no inaccessible nodes.
+The system on the top left is not controllable because there is a dilation since node $x_2$ is being used to control two nodes simultaneously; in other words, there are fewer superiors ($x_2$) than subordinates ($x_1$ and $x_3$).
+The network on the top right is not controllable because node $x_3$ is inaccessible for the only input node $u_1$ in the system.
+Both systems can be made controllable by adding an extra input node ($u_2$ in both bottom networks)."}
 replayPlot(fig_struct_control$plot)

### 2018-06-26 paper/manuscript.Rmd
edits and comments about captions of figs 2 and 3

@@
 In directed networks, a maximum matching is the largest possible set of links that do not share start or end nodes (dark purple).
-Maximum matchings are not necessarily unique, instead, each of them is related to a possible minimum driver-node set in the network (the nodes to which an external control input, in orange, should be applied in order to ensure controllability).
+Maximum matchings are not necessarily unique; instead, each of them is related to a possible minimum driver-node set in the network (the nodes to which an external control input, in orange, should be applied in order to ensure controllability).
 The size of the minimum driver-node set *D* corresponds exactly to the number of unmatched nodes (the number of nodes in the network *N* minus the matching size).
@@
 
-```{r fig-emp-controllability, fig.width=fig_sizes()[[2]], fig.height=fig_sizes()[[1]]/2, fig.cap="(a) Density plot of the relative size of the minimum driver-node set $n_D$ in the invaded (light) and uninvaded (dark) empirical networks.
+<!-- DBS: I don't understand the description of (b) below about the values predicted by the most parsimonious model. I think it needs more info to be fully intelligible. -->
+```{r fig-emp-controllability, fig.width=fig_sizes()[[2]], fig.height=fig_sizes()[[1]]/2, fig.cap="Drivers of network controllability.
+(a) Probability density of the relative size of the minimum driver-node set $n_D$ in the invaded (light) and uninvaded (dark) empirical networks.
 (b) The relationship between the asymmetry plant/pollinator richness and $n_D$.
 The plot shows the values predicted by the most parsimonious model.
-(c) The density distribution of the difference between the relative size of the minimum driver-node set of random networks and that of empirical networks.
+(c) Probability density of the difference between the relative size of the minimum driver-node set of random networks and that of empirical networks.
 We randomised either the species visitation patterns (light line) or randomised the direction of control between a species pair (dark line).
-The vertical dashed lines indicate the median values of each distribution."}
+The vertical dashed lines in (a) and (c) indicate the median values of the distributions."}
 drake::loadd(fig_emp_controllability)

### 2018-06-26 paper/manuscript.Rmd
comments and edits to captions of figs 5 and 6

@@
 <!-- DBS: I don't understand the description of (b) below about the values predicted by the most parsimonious model. I think it needs more info to be fully intelligible. -->
+<!-- DBS: y-axes in (a) and (c) should be "probability density" -->
 ```{r fig-emp-controllability, fig.width=fig_sizes()[[2]], fig.height=fig_sizes()[[1]]/2, fig.cap="Drivers of network controllability.
@@
 
-```{r fig-species-level, fig.width=fig_sizes()[[2]]*2/3, fig.height=fig_sizes()[[1]]/2, fig.cap="Density plot of the control capacity $\\phi$ of (a) plants and (b) pollinators.
+<!-- DBS: y-axis in (a) should be "probability density" -->
+<!-- DBS: I also *love* this plot. -->
+```{r fig-species-level, fig.width=fig_sizes()[[2]]*2/3, fig.height=fig_sizes()[[1]]/2, fig.cap="Probability density of the control capacity $\\phi$ of (a) plants and (b) pollinators across all networks.
 The control capacity of all invasive species is $\\phi = 1$ and is depicted with solid circles."}
@@
 ```
-
-```{r fig-species-partial, fig.width=fig_sizes()[[2]], fig.height=fig_sizes()[[1]]/2, fig.cap= "Model averaged partial residual plots for the relationship between control capacity and (a) contribution to nestedness, (b) visitation strength, (c) asymmetry of dependences, and (d) degree."}
+<!-- DBS: You never state in the methods what you mean by model-average partial residuals.
+If you don't explain it there, you MUST explain it here as there is a good chance that no one will invest the time required to know what is actually going on.
+-->
+```{r fig-species-partial, fig.width=fig_sizes()[[2]], fig.height=fig_sizes()[[1]]/2, fig.cap= "Model-averaged partial-residual plots for the relationship between control capacity and (a) contribution to nestedness, (b) visitation strength, (c) asymmetry of dependences, and (d) degree."}
 drake::loadd(fig_species_partial)
@@
 
-```{r fig-structural-stability, fig.width=fig_sizes()[[1]], fig.height=fig_sizes()[[1]]/2, fig.cap="Density plot of the structural stability of the communities after a focal species is removed.
-The structural stability after critical species have been removed (darker line) is considerable smaller than the average.
-To allow comparison across communities, the structural stability values were scaled within each network to have a mean of 0 and a standard deviation of one."}
+<!-- DBS: y-axis should be "probability density" -->
+<!-- DBS: remove the title at the top of the figure -->
+<!-- DBS: the issue of scaling of Omega should likely appear in the methods too... -->
+```{r fig-structural-stability, fig.width=fig_sizes()[[1]], fig.height=fig_sizes()[[1]]/2, fig.cap="Probability density of the structural stability of the communities after a single focal species is removed.
+The structural stability after critical species have been removed (darker line) is considerable smaller than that after non-critical (redundant) species have been removed.
+To allow comparison across communities, the structural stability values were scaled within each network to have a mean of zero and a standard deviation of one."}
 drake::loadd(fig_structural_stability)

### 2018-06-26 paper/manuscript.Rmd
dbs edits to glossary

@@
 The minimum driver-node sets can be obtained by finding all maximum matchings in a network.",
-  "maximum matching" = "A matching is a set of links that do not share a common start or end nodes; the largest possible matching is called a maximum matching.",
+  "maximum matching" = "A matching is a set of links that do not share any common start or end nodes; the largest possible matching is called a maximum matching.",
   "control configuration" = "One of the species combinations with which is possible to achieve network control. Optimal control configurations are given by the minimum driver-node sets.", 
   "control capacity" = "The relative frequency \\(\\phi\\) which with a species is part of the optimal control configurations of a network.", 
-  "critical species" = "A species with the maximum control capacity \\(\\phi=1\\)",
-  "superior node" = "A species is a superior node if it that can internally affect the abundance of other species in the network.
+  "critical species" = "A species with a maximal control capacity \\(\\phi=1\\)",
+  "superior node" = "A species is a superior node if it can internally affect the abundance of other species in the network.
 Superior nodes make up the chains that propagate the control signals through the network.")

### 2018-06-26 paper/manuscript.Rmd
minor tweak to caption of Table 1

@@
                booktabs = T,
-               caption = "Selection table of the generalised linear models of control capacity, $\\phi$. Only models with a weight larger or equal to 0.01 are shown.", 
+               caption = "Selection table of the binomial generalised linear models of species control capacity, $\\phi$. Only models with a weight larger or equal to 0.01 are shown.", 
                row.names = F, 

### 2018-06-27 paper/manuscript.Rmd
Addressing Daniel's comments - Edits to introduction
#49

@@
 Within community ecology, a complex-systems approach has led to the development of a variety analytical and simulation tools with which to compare and contrast the roles of species embedded in a network of interactions [@guimera_cartography_2005; @bascompte_assembly_2009; @stouffer_evolutionary_2012; @coux_linking_2016].
-A particularly relevant dimension of any species' role is its ability to alter the abundance of other species and the state of the community—since changes of this nature can have knock-on effects on ecosystem function, diversity, processes, and services [@ref_to_daniels_tree_paper_and_jasons_reviews].
+A particularly relevant dimension of any species' role is its ability to alter the abundance of other species and the state of the community—since changes of this nature can have knock-on effects on ecosystem function, diversity, processes, and services [@thompson_food_2012; @tylianakis_global_2008; @tylianakis_conservation_2010].
 This ability is sometimes referred to as a species' "keystoneness" [@mills_keystone-species_1993].
@@
 Despite being conceptually intuitive, the relationship between centrality and a species' presumed impact on the state of the community is largely phenomenological. 
-On one hand, substantive changes in ecosystem functioning can also occur without complete removal of a species [@needsrefs;@daniel_has_ideas]. 
+On one hand, substantive changes in ecosystem functioning can also occur without complete removal of a species [@mouillot_functional_2013; @daniel_has_ideas]. 
 On the other, we are often interested in a *specific* state of the community that might be desirable to attain (or preserve) because of its biodiversity, resilience, functioning, or the ecosystem services it provides.
@@
 Instead, we are better served by understanding how the structure of the network can be harnessed to achieve the desired state and which species may play the largest role in this targeted process. 
-When the state of a community is underpinned by more than a single species and we move beyond single-species removals, we expect the usefulness of centrality to diminish.
+When the state of a community is underpinned by more than a single species and we move beyond single-species removals, we might expect the accuracy of centrality to diminish.
 <!-- DBS: We could potentially cut the sentence above; I see the merit, but I also feel like it could annoy readers/reviewers. -->
+<!-- FDO: I made the sentence softer, do you think it's good enough? I'm happy to remove it alltogether though -->
 As a result, community ecology could arguably benefit from an alternative, perhaps more mechanistically-grounded, approach to understand how species affect each other's abundance.
 
-Species abundances---and consequently the state of the community as a whole---are influenced by both their interactions, the specific dynamics of these interactions and the mechanisms of self-regulation [@addrefs].
-However, community and population dynamics can be modelled in innumerable ways, and empirical support for one versus another is often still ambiguous [@addrefs]. 
+Species abundances---and consequently the state of the community as a whole---are influenced by both their interactions, the specific dynamics of these interactions and the mechanisms of self-regulation [@lever_sudden_2014].
+However, community and population dynamics can be modelled in innumerable ways, and empirical support for one versus another is often still ambiguous [@holland_population_2002]. 
 The alternative approach should, therefore, ideally acknowledge ecosystem dynamics, but without being overly dependent on the particular choices of how they are characterised.
@@
 Although the controllability of a network is a whole-system property, it has recently been shown that asking for the controllability of a complex-system is equivalent to finding a particular set of relevant nodes: the set with which is possible to control the state of the whole network [@liu_control_2016].
-Notably, control theory is consistent with the observation that to change the state of a network, more than a ranking, we need a set of nodes.
-<!-- DBS: I don't get what "more than a ranking" means above. -->
 Importantly, this set of nodes is not always unique for a given network.
@@
 We ask—from a control-theoretic perspective—whether there are key differences between species in the role they play at driving the state of the community and explore the ecological factors related to these differences.
-This allows us to identify species that might be critical for network control and show that they have a larger than expected impact on the structural stability of the community.
+This allows us to identify species that might be critical for network control and show that they have a larger than expected impact on the stable coexistence of the community.
 <!-- DBS: Do we need to introduce structural stability before mentioning it here? -->
-Finally, we compare the proposed approach to current methods based on species centrality and show how these methods are indeed valuable but ultimately paint a limited picture in regards to the "keystoneness" of a species and its role at supporting the diversity of its community.
+<!-- FDO: Changed to stable coexistence, so maybe we can get by without further introduction -->
+Finally, we compare the proposed approach to current methods based on species centrality and show how these methods are indeed valuable but ultimately paint a limited picture in regards to the "keystoneness" of a species.
 <!-- DBS: Is "supporting the diversity" the right function to call out at this point? -->
+<!-- FDO: Removed that part of the sentence. I think it's fine without it -->
 

### 2018-06-28 paper/manuscript.Rmd
Daniel comments and extra minor edits
Close #49

@@
 
-A significant proportion of the network tools used to estimate species roles in this context rely on the calculation of a species' centrality—a relative ranking of its positional importance that originally stems from social-network research [@noah_e._friedkin_theoretical_1991].
+A significant proportion of the network tools used to estimate species roles in this context rely on the calculation of a species' centrality—a relative ranking of its positional importance that originally stems from social-network research [@noah_e._friedkin_theoretical_1991; @martin_gonzalez_centrality_2010].
 Generally speaking, central species tend to be better connected and consequently are more likely to participate in the network's "food chains". 
@@
 Despite being conceptually intuitive, the relationship between centrality and a species' presumed impact on the state of the community is largely phenomenological. 
-On one hand, substantive changes in ecosystem functioning can also occur without complete removal of a species [@mouillot_functional_2013; @daniel_has_ideas]. 
+On one hand, substantive changes in ecosystem functioning can also occur without complete removal of a species [@mouillot_functional_2013].
+<!-- Which ideas do you have (@daniel_has_ideas) -->
 On the other, we are often interested in a *specific* state of the community that might be desirable to attain (or preserve) because of its biodiversity, resilience, functioning, or the ecosystem services it provides.
@@
 A system is said to be controllable if it is possible to steer it from an initial to an arbitrary final state within finite time [@kalman_mathematical_1963]. 
-<!-- The sentence above and the sentence below both work well as leading sentences for a paragraph but neither works well as a second.
-Can you find somewhere to fold the one above into the paragraph (or elsewhere) or rewrite the beginning of the one below?
--->
-<!-- FDO: What about now Daniel? -->
 A simple version of such a system can be described by $\frac{dx}{dt} = Ax + Bu(t)$, where the change of its state over time ($\frac{dx}{dt}$) depends on its current state *x* (for example, the species' abundances), an external time-varying input *u(t)* (the control signal), and two matrices *A* and *B*, which encode information about the network structure and how species respond to external inputs, respectively.
@@
 An intuitive way to understand structural controllability is by looking at its graphical interpretation: from a topological perspective a network is structurally controllable if there are no inaccessible nodes—that is, nodes without incoming links—or dilations—*expansions* of the network (Figure \@ref(fig:fig-example-networks)b; Supporting Information Section \@ref(S-structural-controllability)).
-<!-- The last sentence of the paragraph above sticks out a bit. -->
-<!-- I rephrased it the last couple of sentences, hopefully, it flows better now -->
 
@@
 The key is to note that the fundamental conditions of structural controllability imply that there is a one-to-one relationship between *superior* and *subordinate* nodes just like the one-to-one relationship between jobs and applicants (Figure \@ref(fig:fig-example-networks)b, bottom left).
-<!-- DBS: I think we should at least introduce what superior and subordinate means here even if they're also defined in the figure. -->
-We thus use the maximum-matching algorithm to find an optimal pairing of superior and subordinate nodes in a manner consistent with the controllability conditions (Supporting Information Section \@ref(S-one-maximum-matching)).
+We thus use the maximum-matching algorithm to find an optimal pairing of superior (those that can control another node) and subordinate nodes (those that can be controlled by another node) in a manner consistent with the controllability conditions (Supporting Information Section \@ref(S-one-maximum-matching)).
 Given the result, we can further decompose the matching into a set of paths that reveal how a control signal can flow across the links in a network to reach every node within it. 
@@
 In an ecological context, external inputs can be thought of as management interventions that modify the abundance of a particular species.
-<!-- Would the two sentences below work better after the "Finding out exactly how difficult..." sentence? -->
-<!-- I moved it to a different place where I think flows better -->
 
 After finding the minimum driver-node set in each of our networks, we wanted to test whether invasion status or other predictors are correlated to controllability. 
-We do this using a set of generalised linear models (with binomial error structure). 
+We do this using a set of generalised linear models with binomial error structure. 
 The response variable was the relative size of the minimum driver-node set $n_D$ of the twenty empirical networks (ten invaded and ten uninvaded), and we included invasion status as a predictor. 
@@
 Using this algorithm, we are able to identify species that are possible control inputs—those that belong to the minimum driver-node set in at least one of the possible control configurations. 
-Here, we extend this algorithm such that it is possible to calculate a highly accurate approximation of the control capacity $\phi_i$ of every species in the network (Supporting Information Section \@ref(S-input-graph)).
+Here, we extend this algorithm such that it is possible to calculate a highly accurate approximation of the control capacity $\phi$ of every species in the network (Supporting Information Section \@ref(S-input-graph)).
 In the networks that contained reciprocal links (because there was no asymmetry in the dependences of a species pair), we averaged a species control capacity $\phi$ across every possible "non-reciprocal" version of the network (Supporting Information Section \@ref(S-reciprocal-links)).
@@
 Third, the direction of asymmetry which quantifies the net balance in dependencies; that is it indicates if a species affects other species more than what they affect it or not [@vazquez_species_2007].
-Fourth, the species degree in order to account for the innate centrality of a species.
+Fourth, the species degree in order to account for the inrinsic centrality of a species.
 Finally, we included a categorical variable for the species trophic level (plant or pollinator) and an interaction term between trophic level and the previous four variables. 
@@
 
-Our analysis revealed that some species have a control capacity $\phi_i = 1$. 
+Our analysis revealed that some species have a control capacity $\phi = 1$. 
 These species are critical to controlling their community because they are part of the minimum driver-node set in *every* control scenario. 
@@
 Within mutualistic networks, one useful measure of for how networks impact stable coexistence is called structural stability [@rohr_structural_2014]. 
-Mathematically, the structural stability $\Omega$ of a network represents the size of the parameter space (i.e., growth rates, carrying capacities, etc.) under which all species can sustain positive abundances [@saavedra_nested_2016].
+Mathematically, the structural stability of a network represents the size of the parameter space (i.e., growth rates, carrying capacities, etc.) under which all species can sustain positive abundances [@saavedra_nested_2016].
 The contribution of any given species *i* to stable coexistence can be estimated by calculating the structural stability of the community when the focal species *i* is removed. 
+To allow comparison across communities, the structural stability values were scaled within each network to have a mean of zero and a standard deviation of one.
 Given these species-specific estimates of structural stability, we then used a t-test to compare the contribution to stable coexistence of critical and non-critical species. 
@@
 <!-- DBS: I think we're far too sloppy about when things like phi have subscripts and when they don't. We really should be consistent throughout. -->
+<!-- I just removed the subscripts everywhere -->
 Finally, we wanted to understand how two species-level control metrics are related to five metrics of keystoneness based on centrality. 
-For the centrality metrics, we use a species' degree, betweenness, eigen centrality, page rank, and closeness centrality. 
+For the centrality metrics, we use a species' degree, betweenness, closeness centrality [@martin_gonzalez_centrality_2010], page rank [@mcdonald-madden_using_2016], and eigen centrality [@jordano_ecological_2006].
 <!-- DBS: You MUST cite where these centrality metrics come from. -->
+<!-- I just chose them cause they were easy to calculate... :( -->
 The first control metric we use is a species control capacity $\phi$ described above. 
@@
 -->
+<!-- I'm pretty sure that's the case cause that's what we get.
+I remember seeing it with slighlty different terminology in a paper a couple of months ago.
+I made a not and now I cannot find the note nor the paper...
+Will have another look and hopefully something will come out -->
 
@@
 We found that the relative size of the minimum driver-node set of invaded communities was not significantly different from that of communities that have not been invaded (Figure \@ref(fig:fig-emp-controllability)a).
-In contrast, there was an important negative relationship between $n_D$ and the network asymmetry (Figure \@ref(fig:fig-emp-controllability)b).
+In contrast, there was an large negative relationship between $n_D$ and the network asymmetry (Figure \@ref(fig:fig-emp-controllability)b).
 <!-- DBS: "important" doesn't mean anything statistically. was it significant? -->
+<!-- Yes it is but I'm using model evidence and effect size to assess the importance of variables as opposed to p-values -->
 Furthermore, there were also negative, albeit weaker, relationships between $n_D$ and connectance, nestedness and species richness (Table  \@ref(S-tab:tab-controllability-model-results)). 
@@
 <!-- DBS: I don't understand the description of (b) below about the values predicted by the most parsimonious model. I think it needs more info to be fully intelligible. -->
-<!-- DBS: y-axes in (a) and (c) should be "probability density" -->
+<!-- The points are actually raw values  -->
+
 ```{r fig-emp-controllability, fig.width=fig_sizes()[[2]], fig.height=fig_sizes()[[1]]/2, fig.cap="Drivers of network controllability.
 (a) Probability density of the relative size of the minimum driver-node set $n_D$ in the invaded (light) and uninvaded (dark) empirical networks.
-(b) The relationship between the asymmetry plant/pollinator richness and $n_D$.
-The plot shows the values predicted by the most parsimonious model.
+(b) Relationship between the asymmetry plant/pollinator richness and $n_D$.
 (c) Probability density of the difference between the relative size of the minimum driver-node set of random networks and that of empirical networks.
@@
   dplyr::filter(weight > 0.01)
-# su_table <- MuMIn::model.sel(species_model_superior$fixed)%>%
-#   dplyr::filter(weight > 0.01)
 
@@
   kableExtra::kable_styling(font_size = 8) %>%
-  # kableExtra::group_rows("control capacity models", 1, nrow(cc_table)) %>%
-  # kableExtra::group_rows("superior probability models", nrow(cc_table) + 1, nrow(cc_table) + nrow(su_table)) %>%
   kableExtra::footnote(general = "intercept (int), degree ($k$), trophic level ($l$), asymmetry ($a$), contribution to nestedness ($n$), visitation strength ($s$).", 
@@
 
-<!-- DBS: y-axis in (a) should be "probability density" -->
-<!-- DBS: I also *love* this plot. -->
 ```{r fig-species-level, fig.width=fig_sizes()[[2]]*2/3, fig.height=fig_sizes()[[1]]/2, fig.cap="Probability density of the control capacity $\\phi$ of (a) plants and (b) pollinators across all networks.
@@
 
-# pdf("test.pdf", width =fig_sizes()[[2]]*2/3, height = fig_sizes()[[1]])
 fig_control_capacity %>%
     cowplot::plot_grid(plotlist = ., rel_widths = c(1.21,1), align = "h")
-# dev.off()
 ```
-<!-- DBS: You never state in the methods what you mean by model-average partial residuals.
-If you don't explain it there, you MUST explain it here as there is a good chance that no one will invest the time required to know what is actually going on.
--->
-```{r fig-species-partial, fig.width=fig_sizes()[[2]], fig.height=fig_sizes()[[1]]/2, fig.cap= "Model-averaged partial-residual plots for the relationship between control capacity and (a) contribution to nestedness, (b) visitation strength, (c) asymmetry of dependences, and (d) degree."}
+
+```{r fig-species-partial, fig.width=fig_sizes()[[2]], fig.height=fig_sizes()[[1]]/2, fig.cap= "Partial-residual plots for the relationship between control capacity and the independent variables: (a) contribution to nestedness, (b) visitation strength, (c) asymmetry of dependences, and (d) degree.
+Partial residual plots show the relationship between the response and each of the independent variables given that all other independent variables have been accounted for.
+Ploted values correpond to the predictions of the weighted average of the models shown in Table \\@ref(tab:tab-model-selection-table)"}
 drake::loadd(fig_species_partial)
@@
 We also found that critical species have a particularly large impact on species coexistence when compared to non-critical species.
-Indeed, the structural stability of the network was considerably reduced when these species were removed from their communities ($p = `r sprintf('\\num{%s}', format(crit_test$p.value, digits = 2))`$; Figure \@ref(fig:fig-structural-stability); Supporting Information \@ref(S-structural-stability)).
+Indeed, the structural stability of the networks where critical species were removed was considerably to those in were non-critical speceis were removed ($p = `r sprintf('\\num{%s}', format(crit_test$p.value, digits = 2))`$; Figure \@ref(fig:fig-structural-stability); Supporting Information \@ref(S-structural-stability)).
 <!-- DBS: I wonder if people will have a hard time understanding what these values mean.
@@
 -->
+<!-- Tried to edit the results and the caption of the figure to help improve that -->
 
-<!-- DBS: y-axis should be "probability density" -->
-<!-- DBS: remove the title at the top of the figure -->
-<!-- DBS: the issue of scaling of Omega should likely appear in the methods too... -->
 ```{r fig-structural-stability, fig.width=fig_sizes()[[1]], fig.height=fig_sizes()[[1]]/2, fig.cap="Probability density of the structural stability of the communities after a single focal species is removed.
-The structural stability after critical species have been removed (darker line) is considerable smaller than that after non-critical (redundant) species have been removed.
+Mathematically, the structural stability of a network represents the size of the parameter space (i.e., growth rates, carrying capacities, etc.) under which all species can sustain positive abundances [@saavedra_nested_2016].
+The structural stability of communities in which critical species have been removed (darker line) is considerable smaller than that of communities in which non-critical species have been removes.
+This indicates that critical species contribute more to the stable coexistence of their communities.
 To allow comparison across communities, the structural stability values were scaled within each network to have a mean of zero and a standard deviation of one."}
@@
 On the other hand, the probability of being a superior species $\sigma$ was slightly more correlated to established centrality metrics as its Spearman correlation ranged between `r round(min(correlations$superior), 2)` (with eigen-centrality) and `r round(max(correlations$superior), 2)` (with degree; Figure \@ref(S-fig:fig-correlogram)).
-Despite the higher correlation with species' degree, with the exception of specialists that had only one interaction, we observed many species with a low degree and a  high probability of being superior nodes (Figure \@ref(S-fig:fig-species-models-degree)b).
-<!-- DBS: Please rephrase this last sentence and/or chop it into two. It's unclear to me (at least) in particular the "with the exception" part. -->
+Despite the higher correlation with species' degree we still observed many species with a low degree and a high probability of being superior nodes (Figure \@ref(S-fig:fig-species-models-degree)b).
 
@@
 First, structural controllability emphasizes that the effect a species has on the abundance of other species is not independent of the effects of other other species in their community. 
+The rankings provided by centrality metrics and other heuristics fail to account for the collective influence of several species at once. 
 Second, it demonstrates that to ensure the persistence of a community it is often necessary to consider the abundances of more than a single species, even when full control is infeasible or undesired (for example `r round(sum(crit$n_crit > 1)/nrow(crit)*100)`% of our communities contained more than one critical species).
@@
 \R{data-requirements}In contrast, structural controllability only requires a quantitative approximation of the network's interactions to gain valuable insight from the community.
-Furthermore, unlike centrality metrics, the assumptions of structural controllability are explicit and the estimation of a species importance arises from a mechanistic understanding of the population dynamics between species.
-By accounting for network dynamics (even if in a simple way), it incorporates more ecological realism even in the extreme scenario where the state of a community depends almost exclusively on nodal dynamics rather than on the topology of their interactions.
+Furthermore, while the relationship between centrality and keystoneness is based on an intuitive understanding of what a keystone species is, the assumptions of structural controllability are explicit and the estimation of a species importance arises from a mechanistic understanding of the population dynamics between species.
+By accounting for network dynamics (even if in a simple way), structural stability incorporates more ecological realism, especially in the extreme scenario in which the state of a community is only marginally affected by the topology of their interactions.
 <!-- DBS: See what everyone else says about these last two sentences. I think they get harder and harder to follow as they evolve. -->
+<!-- Made some edits, we'll se what people say -->
 

### 2018-06-28 paper/manuscript.Rmd
Improve caption of partial residuals plot

@@
 
-```{r fig-species-partial, fig.width=fig_sizes()[[2]], fig.height=fig_sizes()[[1]]/2, fig.cap= "Partial-residual plots for the relationship between control capacity and the independent variables: (a) contribution to nestedness, (b) visitation strength, (c) asymmetry of dependences, and (d) degree.
-Partial residual plots show the relationship between the response and each of the independent variables given that all other independent variables have been accounted for.
+```{r fig-species-partial, fig.width=fig_sizes()[[2]], fig.height=fig_sizes()[[1]]/2, fig.cap= "Partial-residual plots for the independent variables: (a) contribution to nestedness, (b) visitation strength, (c) asymmetry of dependences, and (d) degree.
+Partial-residual plots show the relationship between control capacity and each of the independent variables while acccounting for all other remaining variables.
 Ploted values correpond to the predictions of the weighted average of the models shown in Table \\@ref(tab:tab-model-selection-table)"}

### 2018-06-28 paper/manuscript.Rmd
remove annoying warnings from partial residual plot

@@
 drake::loadd(fig_species_partial)
+suppressWarnings({
   fig_species_partial %>%
-  purrr::map_at(2:4, function(x) x  + theme(axis.title.y = element_blank(), axis.text.y = element_blank())) %>%
-    cowplot::plot_grid(plotlist = ., align = "h", nrow = 1, rel_widths = c(1.25, 1, 1,1))
+  purrr::map_at(2:4, function(x) x  + theme(axis.title.y = element_blank(),
+                                            axis.text.y = element_blank())) %>%
+    cowplot::plot_grid(plotlist = ., 
+                       align = "h", nrow = 1, 
+                       rel_widths = c(1.25, 1, 1,1))
+})
+
 ```

### 2018-06-28 paper/manuscript.Rmd
Oops missed some references

@@
 These results indicate that fully controlling ecological networks might currently be out of reach for all but the smallest communities [@motter_networkcontrology_2015]. 
-Nevertheless, structural controllability might be helpful at identifying communities in which changes in the ecological state are more likely to occur and provides solid theoretical rationale for the many difficulties encountered in the management and restoration of natural communities [@addrefs].
+Nevertheless, structural controllability might be helpful at identifying communities in which changes in the ecological state are more likely to occur and provides solid theoretical rationale for the many difficulties encountered in the management and restoration of natural communities [@woodford_confronting_2016].
 
@@
 
-Structural controllability assumes that the networks can be approximated using linear functional responses [@addrefs]. 
+Structural controllability assumes that the networks can be approximated using linear functional responses [@liu_control_2016]. 
 The ramifications of this assumption imply that, while structural controllability is useful to identify species that are relevant for network control, it cannot be used to design the *exact* interventions that should be applied to these species in order to achieve a desired state.

### 2018-06-28 paper/manuscript.Rmd
Add awknoledgements
#44

@@
 
-<!-- DBS: Surely we had this before. Please copy it from a previous submission. And definitely DON'T submit without the right acknowledgement text! -->
-A brief statement acknowledging collaborators and research assistants who do not meet the criteria for authorship described above, or acknowledging funding sources, providing relevant permit numbers (including institutional animal use permits), or giving recognition to nature reserves or other organizations that made the work possible.
+The authors thank Jane Memmott and coauthors, and eveyone that has made their data available to us, Takeuki Uno for the insight provided to find the set of all maximum matching algorithms, and Jason Tylianakis, Bernat Bramon Mora, Guadalupe Peralta, Rogini Runghen, Michelle Marraffini, Warwick Allen, Matthew Hutchinson, and Marilia Gaiarsa for feedback and valuable discussions.
+EFC acknowledges the support from the University of Canterbury Doctoral Scholarship, the University of Canterbury Meadow Mushrooms Postgraduate Scholarship, a New Zealand International Doctoral Research Scholarship, and a travel grant from the European Space Agency.
+DBS acknowledges the support of a Marsden Fast-Start grant and a Rutherford Discovery Fellowship, administered by the Royal Society Te Aparangi.
 

### 2018-06-28 paper/manuscript.Rmd
Add author contributions
#44

@@
 
-<!-- DBS: Surely we had this before. Please copy it from a previous submission. -->
-All submissions with more than one author must include an Authors’ contributions statement. All persons listed as authors on a paper are expected to meet ALL of the following criteria for authorship:
-
-* substantial contributions to conception and design, or acquisition of data, or analysis and interpretation of data, or drafting the article or revising it critically for important intellectual content;
-* final approval of the version to be published;
-* agreement to be accountable for the aspects of the work that they conducted and ensuring that questions related to the accuracy or integrity of any part of their work are appropriately investigated and resolved.
-
-Acquisition of funding, provision of facilities, or supervising the research group of authors without additional contribution are not usually sufficient justifications for authorship.
-The statement should include an explanation of the contribution of each author.
-We suggest the following format for the Authors’ contributions statement:
-
-AB and CD conceived the ideas and designed methodology; CD and EF collected the data; EF and GH analysed the data; AB and CD led the writing of the manuscript.
-All authors contributed critically to the drafts and gave final approval for publication.
+DBS conceived the idea; all authors contributed to the development of the theoretical framework. EFC performed all analysis. EFC and DBS wrote the manuscript. All authors contributed to its revision.
 

### 2018-06-28 paper/manuscript.Rmd
Add data accessibility
#44

@@
 
-To enable readers to locate archived data from papers, we require that authors list the database and the respective accession numbers or DOIs for all data from the manuscript that has been made publicly available.
-Please see our editorial policies page for further information
+All data used in this manuscript have already been published by @lopezaraizamikel_impact_2007, @bartomeus_contrasting_2008-1, and @ballantyne_constructing_2015 The reader should refer to the original sources to access the data.
 

### 2018-06-28 paper/supp-info.Rmd
Typo in table label
Adapt figure in supp materials for having 3 deltas
#50

@@
 
-```{r fig-rho-sensitivity, fig.width=fig_sizes()[[2]], fig.height=fig_sizes()[[1]]/2, fig.cap="A sensitivity analysis of the impact of interspecific competition parameter $\\rho$ on structural stability reveals that the choice of parameters has a negligible impact on the results.
+```{r fig-rho-sensitivity, fig.width=fig_sizes()[[2]], fig.height=fig_sizes()[[1]], fig.cap="A sensitivity analysis of the impact of interspecific competition parameter $\\rho$ on structural stability reveals that the choice of parameters has a negligible impact on the results.
 (a) Spearman correlation coefficient of the contribution to stable coexistence of species.
@@
 fig_rho_sensitivity %<>% add_internal_margins()
-cowplot::plot_grid(plotlist = fig_rho_sensitivity, ncol = 2, align = "h")
+cowplot::plot_grid(plotlist = fig_rho_sensitivity, ncol = 1, align = "hv")
 ```
@@
 
-```{r tab-asumption-visitation}
+```{r tab-assumption-visitation}
 drake::loadd(visitation_importance_agreement)

### 2018-06-28 code/fig_rho_sensitivity.R

@@ -1,3 +1,4 @@
+# drake::loadd(structural_rho_correlation, rho_feasibility)
 make_fig_rho_sensitivity <- function(structural_rho_correlation, rho_feasibility){
   require(ggplot2)
   
@@ -18,6 +19,7 @@ make_fig_rho_sensitivity <- function(structural_rho_correlation, rho_feasibility
     geom_line(aes(group = 1), colour = my_pallete()$dark_purple) + 
     base_ggplot_theme() + 
     coord_cartesian(ylim = c(-1, 1)) +
+    facet_wrap(~delta, labeller = label_both) +
     labs(title = "(a) Species contribution to coexistence", 
          x = latex2exp::TeX("interspecific competition ($\\rho$)"), 
          y = "Spearman correlation")
@@ -28,6 +30,7 @@ make_fig_rho_sensitivity <- function(structural_rho_correlation, rho_feasibility
     geom_ribbon(aes(ymin = conf_low, ymax = conf_high), 
                 fill = my_pallete()$light_purple, 
                 alpha = 0.25) +
+    facet_wrap(~delta, labeller = label_both) +
     base_ggplot_theme() +
     labs(title = "(b) Diff. crirical - redundant species", 
          x = latex2exp::TeX("interspecific competition ($\\rho$)"), 

### 2018-06-28 code/rho_sensitivity.R

@@ -1,23 +1,30 @@
 # drake::loadd(structural_rho_sensitivity, metadata)
-get_structural_sensitivity_correlation <- function(sensitivity_rho, structural_rho_sensitivity, chosen_rho = 0.005, metadata){
-  purrr::map2_dfr(structural_rho_sensitivity, sensitivity_rho, 
-              ~dplyr::mutate(.x, rho = .y)) %>% 
-    dplyr::select(net_name, sp_name, feasibility, rho) %>%
+get_structural_sensitivity_correlation <- function(sensitivity_range, structural_rho_sensitivity, chosen_rho = 0.005, metadata){
+  separator <- "---"
+  purrr::cross(sensitivity_range) %>%
+    purrr::map2_df(structural_rho_sensitivity, 
+                   ~dplyr::mutate(.y, rho = .x[[1]], delta  = .x[[2]])) %>% 
+    dplyr::select(net_name, sp_name, feasibility, rho, delta) %>%
     filter_networks_df(metadata) %>%
-    split(.$net_name) %>%
+    split(list(.$net_name, .$delta), sep = separator) %>%
     purrr::map_dfr(function(x){
       x %>%
         tidyr::spread(rho, feasibility) %>%
         dplyr::select_if(is.numeric) %>%
-        cor(.$`0.005`, ., method = "spearman") %>%
+        dplyr::select(-delta) %>%
+        cor(.[, as.character(chosen_rho)], ., method = "spearman") %>%
         extract(1, ) %>%
         dplyr::data_frame(cor = ., rho = names(.))
-    }, .id = "net_name")
+    }, .id = "net_delta") %>%
+    tidyr::separate(col = "net_delta", into = c("net_name", "delta"), sep = separator) %>%
+    dplyr::mutate(delta = as.numeric(delta))
 }
 
-# drake::loadd(sigma_phi_df, species_coovariates_df, species_empirical_coov,structural_rho_sensitivity, sensitivity_rho)
+# drake::loadd(sigma_phi_df, species_coovariates_df, species_empirical_coov,structural_rho_sensitivity, sensitivity_rho, sensitivity_range, metadata)
 # calculate the difference between critical and redundant species for several values of rho
-get_rho_feasibility <- function(sigma_phi_df, species_coovariates_df, species_empirical_coov,structural_rho_sensitivity, sensitivity_rho){
[…]

### 2018-06-28 paper/supp-info.Rmd
Explain changes of delta in supp info
#50

@@
 We first calculate the stability condition $\hat{\gamma}$ using all species in the network. 
-To simplify the calculations we assumed that there is no mutualistic trade-off, and a mean field interspecific competition of $\rho = 0.005$ [@saavedra_nested_2016]. 
-To calculate the contribution to stable coexistence of a given species, we removed the focal species from the network and then calculated the corresponding structural feasibility $\Omega$ for a level of mutualism equal to the stability condition found previously.
-The choice of the parameters, specifically the interspecific competition $\rho$ had only a small impact on the relative contribution of species to stable coexistence (Figure \@ref(fig:fig-rho-sensitivity)a).
-
-In addition, the interspecific competition had a minor impact on our result that indicates that critical species (those with $\phi = 1$) have a larger than average contribution to stable coexistence (Figure \@ref(fig:fig-rho-sensitivity)b).
+To calculate the contribution to stable coexistence of a given species, we removed the focal species from the network and then calculated the corresponding structural stability $\Omega$ for a level of mutualism equal to the stability condition found previously.
+For simplicity, in the main text we show results for when there was no mutualistic trade-off $\delta = 0$ and an intermediate value of interspecific competition of $\rho = `r drake::readd(chosen_rho)`$ [@saavedra_nested_2016].
+The choice of the parameters had only a minor impact on the relative contribution of species to stable coexistence (Figure \@ref(fig:fig-rho-sensitivity)a) and overall there was no change on our result that indicates that critical species (those with $\phi = 1$) have a larger than average contribution to stable coexistence (Figure \@ref(fig:fig-rho-sensitivity)b).
 

### 2018-06-28 paper/manuscript.Rmd
Be explicit about delta and rho values in the main text figure
Close #50

@@
 ```{r fig-structural-stability, fig.width=fig_sizes()[[1]], fig.height=fig_sizes()[[1]]/2, fig.cap="Probability density of the structural stability of the communities after a single focal species is removed.
-Mathematically, the structural stability of a network represents the size of the parameter space (i.e., growth rates, carrying capacities, etc.) under which all species can sustain positive abundances [@saavedra_nested_2016].
+Mathematically, the structural stability of a network represents the size of the parameter space (i.e., growth rates, carrying capacities, etc.) under which all species can sustain positive abundances.
 The structural stability of communities in which critical species have been removed (darker line) is considerable smaller than that of communities in which non-critical species have been removes.
 This indicates that critical species contribute more to the stable coexistence of their communities.
-To allow comparison across communities, the structural stability values were scaled within each network to have a mean of zero and a standard deviation of one."}
+To allow comparison across communities, the structural stability values were scaled within each network to have a mean of zero and a standard deviation of one.
+We assume intermediate values of the mutualistic trade-off and mean interspecific competition : $\\delta = 0.25$, $\\rho = 0.005$ [@saavedra_nested_2016].
+However, the choice of parameters does not affect the results (Supporting Information \\@ref(S-structural-stability))"}
 drake::loadd(fig_structural_stability)

### 2018-06-29 paper/manuscript.Rmd
Add abstract
Close #43

@@
 
-1. Background
+1. An important dimension of a species role is its ability to alter the state and maintain the diversity of its community. 
+Centrality metrics have often been used to identify these species, which are sometimes referred as "keystone" species. 
+However, the relationship between centrality and keystoneness is phenomenological and largely based on an intuitive understanding of what may constitute an important species. 
+While centrality is good at predicting which species could cause the largest change in their community it says little about how these species could be used to attain (or preserve) a particular state of the community.
 
-2. Methods
+2. Here we introduce structural controllability an approach that allows us to quantify the extent to which network topology can be harnessed to achieve a desired state.  
+It also allows us to quantify a species control capacity—its relative importance—and identify the set of species that, collectively, are critical in this context.
+We illustrate the application of structural controllability with ten pairs of uninvaded and invaded plant-pollinator communities.
 
-3. Results
+3. We found that the controllability of a community is not dependent on its invasion status, but on the asymmetric nature of its mutual dependences. 
+While central species were also likely to have a large control capacity, centrality fails to identify species that despite being less connected were critical in their communities. 
+Interestingly, this set of critical species was mostly composed of plants and every invasive species in our dataset was part of it. 
+We also found that species with high control capacity and in particular critical species contribute the most to the to stable coexistence of their community even when controlling for its degree, abundance/interaction strength, and the relative dependence of their partners.
 
-4. Synthesis
+4. *Synthesis*: Structural controllability is strongly related to the stability of a network and measures the difficulty of managing an ecological community.
+It also identifies species that are critical to sustain biodiversity and to change or maintain the state of their community and are therefore likely to be very relevant for management and conservation.
 
-*Keywords:* ASD
+**Keywords:** Keystone species, ecological networks, management interventions, mutualism, network control theory, structural controllability, plant population and community dynamics, species importance
 

### 2018-06-29 paper/manuscript.Rmd
Typos and minor edits
Close #44

@@
 <!-- DBS: We could potentially cut the sentence above; I see the merit, but I also feel like it could annoy readers/reviewers. -->
-<!-- FDO: I made the sentence softer, do you think it's good enough? I'm happy to remove it alltogether though -->
+<!-- FDO: I made the sentence softer, do you think it's good enough? I'm happy to remove it altogether though -->
 As a result, community ecology could arguably benefit from an alternative, perhaps more mechanistically-grounded, approach to understand how species affect each other's abundance.
@@
 In classic control theory, determining whether this system is controllable can be achieved by checking that its controllability matrix $R= [ \begin{matrix}B & AB & A^{2}B & ...& A^{n-1}B\end{matrix} ]$ has full rank.
-In complex systems, however, employing this rank condition, or numerical approximations of it, is infeasible because it is hard to fully parameterise *A* and *B* (either because the weight of the links changes over time or because they are difficult to measure).
+In complex systems, however, employing this rank condition, or numerical approximations of it is infeasible because it is hard to fully parameterise *A* and *B* (either because the weight of the links changes over time or because they are difficult to measure).
 Here, we use an approach based on the structural controllability theorem [@lin_structural_1974], which assumes that we are confident about which elements of *A* and *B* have either non-zero or zero values (there is an interaction or not), but that we less sure about the precise magnitude of the non-zero values.
@@
 Third, the direction of asymmetry which quantifies the net balance in dependencies; that is it indicates if a species affects other species more than what they affect it or not [@vazquez_species_2007].
-Fourth, the species degree in order to account for the inrinsic centrality of a species.
+Fourth, the species degree in order to account for the intrinsic centrality of a species.
 Finally, we included a categorical variable for the species trophic level (plant or pollinator) and an interaction term between trophic level and the previous four variables. 
@@
 <!-- I'm pretty sure that's the case cause that's what we get.
-I remember seeing it with slighlty different terminology in a paper a couple of months ago.
+I remember seeing it with slightly different terminology in a paper a couple of months ago.
 I made a not and now I cannot find the note nor the paper...
-Will have another look and hopefully something will come out -->
+Will have another look and hopefully, something will come out -->
 
@@
 We found that the relative size of the minimum driver-node set of invaded communities was not significantly different from that of communities that have not been invaded (Figure \@ref(fig:fig-emp-controllability)a).
-In contrast, there was an large negative relationship between $n_D$ and the network asymmetry (Figure \@ref(fig:fig-emp-controllability)b).
+In contrast, there was a large negative relationship between $n_D$ and the network asymmetry (Figure \@ref(fig:fig-emp-controllability)b).
 <!-- DBS: "important" doesn't mean anything statistically. was it significant? -->
@@
 We also found that critical species have a particularly large impact on species coexistence when compared to non-critical species.
-Indeed, the structural stability of the networks where critical species were removed was considerably to those in were non-critical speceis were removed ($p = `r sprintf('\\num{%s}', format(crit_test$p.value, digits = 2))`$; Figure \@ref(fig:fig-structural-stability); Supporting Information \@ref(S-structural-stability)).
+Indeed, the structural stability of the networks where critical species were removed was considerably to those in were non-critical species were removed ($p = `r sprintf('\\num{%s}', format(crit_test$p.value, digits = 2))`$; Figure \@ref(fig:fig-structural-stability); Supporting Information \@ref(S-structural-stability)).
 <!-- DBS: I wonder if people will have a hard time understanding what these values mean.
@@
 Mathematically, the structural stability of a network represents the size of the parameter space (i.e., growth rates, carrying capacities, etc.) under which all species can sustain positive abundances.
-The structural stability of communities in which critical species have been removed (darker line) is considerable smaller than that of communities in which non-critical species have been removes.
+The structural stability of communities in which critical species have been removed (darker line) is considerably smaller than that of communities in which non-critical species have been removed.
 This indicates that critical species contribute more to the stable coexistence of their communities.
 To allow comparison across communities, the structural stability values were scaled within each network to have a mean of zero and a standard deviation of one.
-We assume intermediate values of the mutualistic trade-off and mean interspecific competition : $\\delta = 0.25$, $\\rho = 0.005$ [@saavedra_nested_2016].
-However, the choice of parameters does not affect the results (Supporting Information \\@ref(S-structural-stability))"}
+Here, we assume values of the mutualistic trade-off and mean interspecific competition of $\\delta = 0$ and $\\rho = 0.01$ respectively [@saavedra_nested_2016].
+However, the choice of these parameters does not affect the results (Supporting Information \\@ref(S-structural-stability))"}
 drake::loadd(fig_structural_stability)
@@
 To achieve that goal we applied *structural controllability*, a field at the intersection between control and complex theory that allow us to obtain two key pieces of information: the *controllability* of a network and a species *control capacity* (Table \@ref(tab:tab-glossary)).
-<!-- DBS: Two sentences does not make a paragraph.... Please add one more that summarizes what we found. -->
+We found that the controllability of a network does not depend on its invasion status and that the species that are critical to altering the state of the community are also the ones that sustain the most the stable coexistence of species in their communities.
 
@@
 Accordingly, our results suggest that structural controllability is closely related to the dynamic persistence of an ecological community. 
-First, we found a comparatively small but thought-provoking negative relationship between the controllability of a network and the its nestedness. 
+First, we found a comparatively small but thought-provoking negative relationship between the controllability of a network and its nestedness. 
 Previous studies indicate that nestedness promotes species coexistence and confers robustness to extinction [@bastolla_architecture_2009; @memmott_tolerance_2004] even at the expense of the dynamic stability of the mutualistic community [@saavedra_nested_2016].
@@
 At first glance, our findings challenge numerous studies that highlight the role that central species play in the dynamics of their communities and their utility at predicting species extinctions [@jordan_keystone_2009].
-However, further inspection shows that our results do not contradict these findings. 
+However, further, inspection shows that our results do not contradict these findings. 
 On the contrary, most species with a large degree also have a large control capacity and all of them were classified as superior nodes which corroborates the utility of classic centrality metrics. 
@@
 <!-- DBS: See what everyone else says about these last two sentences. I think they get harder and harder to follow as they evolve. -->
-<!-- Made some edits, we'll se what people say -->
+<!-- Made some edits, we'll see what people say -->
 
@@
 
-The authors thank Jane Memmott and coauthors, and eveyone that has made their data available to us, Takeuki Uno for the insight provided to find the set of all maximum matching algorithms, and Jason Tylianakis, Bernat Bramon Mora, Guadalupe Peralta, Rogini Runghen, Michelle Marraffini, Warwick Allen, Matthew Hutchinson, and Marilia Gaiarsa for feedback and valuable discussions.
+The authors thank Jane Memmott and coauthors, and everyone that has made their data available to us, Takeuki Uno for the insight provided to find the set of all maximum matching algorithms, and Jason Tylianakis, Bernat Bramon Mora, Guadalupe Peralta, Rogini Runghen, Michelle Marraffini, Warwick Allen, Matthew Hutchinson, and Marilia Gaiarsa for feedback and valuable discussions.
 EFC acknowledges the support from the University of Canterbury Doctoral Scholarship, the University of Canterbury Meadow Mushrooms Postgraduate Scholarship, a New Zealand International Doctoral Research Scholarship, and a travel grant from the European Space Agency.

### 2018-06-29 paper/supp-info.Rmd
Typos and minor edits
Close #44

@@
 Structural controllability avoids the limitation of not knowing the exact values of the matrices *A* and *B*. 
-Using structural controllability can be boiled down to two conditions: a system is controllable if there are no inaccessible nodes or dilations.
+Structural controllability boils down to two conditions: a system is controllable if there are no inaccessible nodes or dilations.
 A node is inaccessible if there are no directed paths between it and the input nodes.
@@
 Though one maximum matching is enough to calculate *n~D~* and hence to provide an indication of the manageability of a community, it is not sufficient to estimate the role of individual species. 
-To do that, we need to calculate all possible maximum matchings (or, equivalently, all maximal cardinality matchings in weighted networks like ours). 
+To do that, we need to calculate all possible maximum matchings. 
 To do this, we again start from the alternative bipartite representation in Figure \@ref(fig:fig-maximum-matching-procedure)b and assign an identity to each of the links in the network.
@@
 Lastly, a maximal clique is a clique such that there are no cliques composed of more nodes [@Gutin2013]. 
-In this example, there are two maximal cliques: the one formed by 1, 3 and 5, and the one formed by 2, 3 and 5. 
+In this example, there are two maximal cliques. 
 The final step is then to map these cliques onto the original network to obtain all possible maximal cardinality matchings as shown in Figure \@ref(M-fig:fig-control-configuration) in the main text.
@@
 To calculate the contribution to stable coexistence of a given species, we removed the focal species from the network and then calculated the corresponding structural stability $\Omega$ for a level of mutualism equal to the stability condition found previously.
-For simplicity, in the main text we show results for when there was no mutualistic trade-off $\delta = 0$ and an intermediate value of interspecific competition of $\rho = `r drake::readd(chosen_rho)`$ [@saavedra_nested_2016].
+For simplicity, in the main text we show results for when there is a  mutualistic trade-off of $\delta = `r drake::readd(chosen_delta)`$ and a mean interspecific competition of $\rho = `r drake::readd(chosen_rho)`$ [@saavedra_nested_2016].
 The choice of the parameters had only a minor impact on the relative contribution of species to stable coexistence (Figure \@ref(fig:fig-rho-sensitivity)a) and overall there was no change on our result that indicates that critical species (those with $\phi = 1$) have a larger than average contribution to stable coexistence (Figure \@ref(fig:fig-rho-sensitivity)b).

### 2018-06-29 main.R
Calculate structural stability without trade-off

@@ -94,8 +94,8 @@ controllability_plan <- drake::drake_plan(
 species_level_plan <- drake::drake_plan(
   species_empirical_coov = purrr::map_df(networks, plants_or_pols, .id = "net_name"),
   species_coovariates_df = purrr::map2_df(directed_networks, networks, get_species_coov, metrics = c("degree", "species strength", "betweenness", "closeness", "eigen", "page_rank", "nested_contribution", "interaction push pull"), .id = "net_name"), 
-  chosen_rho = sensitivity_range$rho[round(length(sensitivity_range$rho)/2)],
-  chosen_delta = sensitivity_range$delta[round(length(sensitivity_range$delta)/2)],
+  chosen_rho = sensitivity_range$rho[round(length(sensitivity_range$rho))],
+  chosen_delta = sensitivity_range$delta[1],
   structural_stability = get_all_struct(directed_networks, rho = chosen_rho, delta = chosen_delta), 
   sigma_phi_df = purrr::map_dfr(matched_networks, get_controllability_superiorness, .id = "net_name"),
   sl_characteristics = join_sl_characteristics(sigma_phi_df, species_coovariates_df, species_empirical_coov, structural_stability),

### 2018-06-29 paper/manuscript.Rmd
More spellchecking

@@
 <!-- FDO: I made the sentence softer, do you think it's good enough? I'm happy to remove it altogether though -->
-As a result, community ecology could arguably benefit from an alternative, perhaps more mechanistically-grounded, approach to understand how species affect each other's abundance.
+As a result, community ecology could arguably benefit from an alternative, perhaps more mechanistically-grounded, approach to understand how species affect each others abundance.
 
@@
 
-The first step in applying methods of control theory is to construct a directed network that is able to provide an indication of the extent to which species affect each other's abundance. 
+The first step in applying methods of control theory is to construct a directed network that is able to provide an indication of the extent to which species affect each others abundance. 
 In some ecological networks, establishing the directionality can be relatively straightforward, for example when links represent biomass transfer or energy flow [@isbell_human_2013]. 

### 2018-06-29 paper/supp-info.Rmd
More spellchecking

@@
 
-The frist and the second group have a control capacity of $\phi = 1$ and $\phi = 0$ respectively. 
+The first and the second group have a control capacity of $\phi = 1$ and $\phi = 0$ respectively. 
 Meanwhile, the third group has intermediate values of control capacity which can be calculated by computing the number of possible substitutions of a node by its control adjacent nodes. 
@@
 We compared the control capacity obtained by calculating all maximum matchings and that obtained using the input graph in `r length(cc_corr)` of our networks (those for which we were able to calculate all maximum matchings within a reasonable time).
-The spearman correlation was very high in all cases, ranging between `r round(min(cc_corr),2)` and `r round(max(cc_corr), 2)` (median `r round(median(cc_corr), 2)`).
+The Spearman correlation was very high in all cases, ranging between `r round(min(cc_corr),2)` and `r round(max(cc_corr), 2)` (median `r round(median(cc_corr), 2)`).
 

### 2018-06-30 paper/manuscript.Rmd
Minor mistakes corrected

@@
 Without exception, we found that invasive plants were critical for network control and as such our results were in line with our expectations. 
-Invasive plants have been previously found to exacerbate the asymmetries in their communities [@aizen_invasive_2008; bartomeus_contrasting_2008-1; @henriksson_strong_2016] and to be central in their communities [@vila_invasive_2009; @palacio_generalist_2016].
+Invasive plants have been previously found to exacerbate the asymmetries in their communities [@aizen_invasive_2008; @bartomeus_contrasting_2008-1; @henriksson_strong_2016] and to be central in their communities [@vila_invasive_2009; @palacio_generalist_2016].
 We found that invasive plants are, however, unlikely to be inherently different from their native counterparts [@emer_species_2016; @stouffer_how_2014]. 

### 2018-07-17 paper/manuscript.Rmd
Feedback Mark and Michelle, remove old comments

@@
 A major goal in ecology is to understand the roles played by different species in the biotic environment.
-Within community ecology, a complex-systems approach has led to the development of a variety analytical and simulation tools with which to compare and contrast the roles of species embedded in a network of interactions [@guimera_cartography_2005; @bascompte_assembly_2009; @stouffer_evolutionary_2012; @coux_linking_2016].
+Within community ecology, a complex-systems approach has led to the development of a variety of analytical and simulation tools with which to compare and contrast the roles of species embedded in a network of interactions [@guimera_cartography_2005; @bascompte_assembly_2009; @stouffer_evolutionary_2012; @coux_linking_2016].
 A particularly relevant dimension of any species' role is its ability to alter the abundance of other species and the state of the community—since changes of this nature can have knock-on effects on ecosystem function, diversity, processes, and services [@thompson_food_2012; @tylianakis_global_2008; @tylianakis_conservation_2010].
@@
 Generally speaking, central species tend to be better connected and consequently are more likely to participate in the network's "food chains". 
-Because species that participate in more chains are assumed to be more likely to affect the abundance of other species, centrality metrics have often been used to identify keystone species in the community [@jordan_quantifying_2007].
-Centrality metrics have been shown to be useful tools to rank species in regards to their potential to alter the abundances of other species, in particular when estimating secondary extinctions that may follow the loss of a species [@dunne_network_2002; @kaiser-bunbury_robustness_2010].
+Because species that participate in more chains are assumed to be more likely to affect the abundances of other species, centrality metrics have often been used to identify keystone species in the community [@jordan_quantifying_2007].
+Centrality metrics have been shown to be useful tools to rank species in regard to their potential to alter the abundances of other species, in particular when estimating the probability of secondary extinctions that may follow the loss of a species [@dunne_network_2002; @kaiser-bunbury_robustness_2010].
 
 Despite being conceptually intuitive, the relationship between centrality and a species' presumed impact on the state of the community is largely phenomenological. 
-On one hand, substantive changes in ecosystem functioning can also occur without complete removal of a species [@mouillot_functional_2013].
-<!-- Which ideas do you have (@daniel_has_ideas) -->
+On the one hand, substantive changes in ecosystem functioning can also occur without complete removal of a species [@mouillot_functional_2013].
 On the other, we are often interested in a *specific* state of the community that might be desirable to attain (or preserve) because of its biodiversity, resilience, functioning, or the ecosystem services it provides.
@@
 Instead, we are better served by understanding how the structure of the network can be harnessed to achieve the desired state and which species may play the largest role in this targeted process. 
-When the state of a community is underpinned by more than a single species and we move beyond single-species removals, we might expect the accuracy of centrality to diminish.
-<!-- DBS: We could potentially cut the sentence above; I see the merit, but I also feel like it could annoy readers/reviewers. -->
-<!-- FDO: I made the sentence softer, do you think it's good enough? I'm happy to remove it altogether though -->
-As a result, community ecology could arguably benefit from an alternative, perhaps more mechanistically-grounded, approach to understand how species affect each others abundance.
+When the state of a community is underpinned by more than a single species (often the case in real communities) and we move beyond single-species removals, we might expect the accuracy of centrality to diminish.
+As a result, community ecology could arguably benefit from an alternative, perhaps more mechanistically-grounded, approach to understand how species affect each other's abundance.
 
-Species abundances---and consequently the state of the community as a whole---are influenced by both their interactions, the specific dynamics of these interactions and the mechanisms of self-regulation [@lever_sudden_2014].
+Species abundances---and consequently the state of the community as a whole---are influenced by both the structure of their interactions and the dynamics of these interactions, including the mechanisms of self-regulation [@lever_sudden_2014].
 However, community and population dynamics can be modelled in innumerable ways, and empirical support for one versus another is often still ambiguous [@holland_population_2002]. 
 The alternative approach should, therefore, ideally acknowledge ecosystem dynamics, but without being overly dependent on the particular choices of how they are characterised.
-Among the various possibilities, *control theory* appears to be a strong candidate [@isbell_human_2013]. 
+Among the various possibilities *structural controllability*, a branch of control theory, appears to be a strong candidate [@isbell_human_2013]. 
 Control theory is a widely-studied branch of engineering used to determine and supervise the behaviour of dynamical systems [@motter_networkcontrology_2015]. 
 It is inherently designed to deal with system feedbacks and its application has recently been expanded to complex networks [@lin_structural_1974;  @liu_control_2016]. 
-In concordance with long-standing ecological questions, advances in this field have established a clear link between the structure of the network and the way nodes affect each other. 
+Consistent with long-standing ecological questions, advances in structural controllability have established a clear link between the structure of the network and the way nodes affect each other. 
 Unlike centrality indices, however, this link is not based on a priori assumptions between network metrics and keystoneness but is instead based on well-established advances in both dynamical and complex-systems theory [@motter_networkcontrology_2015].
 
-At its fundamental level, control theory first determines whether a system is controllable or not; that is, it asks if a system could ever be driven to a desired state within a finite amount of time. 
+At its fundamental level, structural controllability first determines whether a system is controllable or not; that is, it asks if a system could ever be driven to a desired state within a finite amount of time.
 Although the controllability of a network is a whole-system property, it has recently been shown that asking for the controllability of a complex-system is equivalent to finding a particular set of relevant nodes: the set with which is possible to control the state of the whole network [@liu_control_2016].
@@
 
-Here, we apply methods from control theory to a particular ecological problem and show how it can be used to generate insight into the role of species in an ecological network. 
+Here, we apply methods from structural controllability to a particular ecological problem and show how it can be used to generate insight into the role of species in an ecological network. 
 Specifically, we outline the approach using a set of ten pairs of uninvaded and invaded plant-pollinator communities. 
@@
 This allows us to identify species that might be critical for network control and show that they have a larger than expected impact on the stable coexistence of the community.
-<!-- DBS: Do we need to introduce structural stability before mentioning it here? -->
-<!-- FDO: Changed to stable coexistence, so maybe we can get by without further introduction -->
-Finally, we compare the proposed approach to current methods based on species centrality and show how these methods are indeed valuable but ultimately paint a limited picture in regards to the "keystoneness" of a species.
-<!-- DBS: Is "supporting the diversity" the right function to call out at this point? -->
-<!-- FDO: Removed that part of the sentence. I think it's fine without it -->
+Finally, we compare the proposed approach to current methods based on species centrality and show how these methods are indeed valuable but ultimately paint a limited picture in regard to the "keystoneness" of a species.
 
@@
 
-The first step in applying methods of control theory is to construct a directed network that is able to provide an indication of the extent to which species affect each others abundance. 
+The first step in applying methods of control theory is to construct a directed network that is able to provide an indication of the extent to which species affect each other's abundance. 
 In some ecological networks, establishing the directionality can be relatively straightforward, for example when links represent biomass transfer or energy flow [@isbell_human_2013]. 
@@
 Using this structural approach, we can find out the controllability of a system for every non-zero realisation of the parameters.
-An intuitive way to understand structural controllability is by looking at its graphical interpretation: from a topological perspective a network is structurally controllable if there are no inaccessible nodes—that is, nodes without incoming links—or dilations—*expansions* of the network (Figure \@ref(fig:fig-example-networks)b; Supporting Information Section \@ref(S-structural-controllability)).
 
@@
 Admittedly, the link between matchings and structural controllability may appear far from straightforward.
-The key is to note that the fundamental conditions of structural controllability imply that there is a one-to-one relationship between *superior* and *subordinate* nodes just like the one-to-one relationship between jobs and applicants (Figure \@ref(fig:fig-example-networks)b, bottom left).
+
+This link becomes apparent after examining the graphical interpretation of structural controllability: from a topological perspective a network is structurally controllable if there are no inaccessible nodes—that is, nodes without incoming links—or dilations—*expansions* of the network (Figure \@ref(fig:fig-example-networks)b; Supporting Information Section \@ref(S-structural-controllability)).
+The key is to note that these two fundamental conditions of structural controllability imply that there is a one-to-one relationship between *superior* and *subordinate* nodes just like the one-to-one relationship between jobs and applicants (Figure \@ref(fig:fig-example-networks)b, bottom left).
 We thus use the maximum-matching algorithm to find an optimal pairing of superior (those that can control another node) and subordinate nodes (those that can be controlled by another node) in a manner consistent with the controllability conditions (Supporting Information Section \@ref(S-one-maximum-matching)).
@@
 
-Our second ecological objective is related to how species differ in their ability to drive the population dynamics of the community.
+Our second objective is related to how species differ in their ability to drive the population dynamics of the community. 
+We in turn examine whether these differences are also reflected in the role species play at supporting the stable coexistence of other species in the community. 
 Ecologically, these differences are relevant because resources and data are limited, and therefore full control is infeasible. 
@@
 
-To answer this question, we harness the fact there may be multiple maximum matchings for a given network, and each of these maximum matchings indicates a unique combination of species with which is possible to control the network.
+To answer this question, we harness the fact there may be multiple maximum matchings for a given network, and each of these maximum matchings indicates a unique combination of species with which it is possible to control the network.
 Moreover, some species belong to these combinations more often than do others. 
@@
 
+In addition, we wanted to understand how two species-level control metrics are related to five metrics of keystoneness based on centrality. 
+For the centrality metrics, we use a species' degree, betweenness, closeness centrality [@martin_gonzalez_centrality_2010], page rank [@mcdonald-madden_using_2016], and eigen centrality [@jordano_ecological_2006].
+The first control metric we use is a species control capacity $\phi$ described above. 
+The second metric is the probability that a focal species influences the abundance of another species internally, regardless of whether a management intervention is required in that species or not. 
+We call this the probability of being a superior node $\sigma$. 
+Because superior nodes are those at the beginning of a matched link, \(\sigma\) could be seen as a "softer" version of control capacity. 
+Conveniently, unlike the minimum driver-node set, superior species are the same for all control configurations and so in a network without reciprocal links the probability that a species is superior $\sigma$ is either 1 or 0.
+
 Our analysis revealed that some species have a control capacity $\phi = 1$. 
@@
 
-<!-- DBS: I think we're far too sloppy about when things like phi have subscripts and when they don't. We really should be consistent throughout. -->
-<!-- I just removed the subscripts everywhere -->
-Finally, we wanted to understand how two species-level control metrics are related to five metrics of keystoneness based on centrality. 
-For the centrality metrics, we use a species' degree, betweenness, closeness centrality [@martin_gonzalez_centrality_2010], page rank [@mcdonald-madden_using_2016], and eigen centrality [@jordano_ecological_2006].
-<!-- DBS: You MUST cite where these centrality metrics come from. -->
-<!-- I just chose them cause they were easy to calculate... :( -->
-The first control metric we use is a species control capacity $\phi$ described above. 
-The second metric is the probability that a focal species influences the abundance of another species internally, regardless of whether a management intervention is required in that species or not. 
-We call this the probability of being a superior node $\sigma$. 
-Because superior nodes are those at the beginning of a matched link, \(\sigma\) could be seen as a "softer" version of control capacity. 
-Conveniently, unlike the minimum driver-node set, superior species are the same for all control configurations and so in a network without reciprocal links the probability that a species is superior $\sigma$ is either 1 or 0.
-<!-- DBS: I think that the statement above needs a reference as I don't think this is "new" here nor do I think everyone will necessarily understand why it's true without pointing them to a more formal explanation.
--->
-<!-- I'm pretty sure that's the case cause that's what we get.
-I remember seeing it with slightly different terminology in a paper a couple of months ago.
-I made a not and now I cannot find the note nor the paper...
-Will have another look and hopefully, something will come out -->
-
 ## Testing assumptions
@@
 First, we tested that visitation is an appropriate proxy to infer interspecific effects by comparing the results obtained using visitation to two alternative metrics in a separate dataset that lacked invasive species [@ballantyne_constructing_2015].
-Specifically, we also applied the structural controllability approach to networks constructed using pollinator efficiency (which measures the pollen deposition of an interaction) and pollinator importance [which accounts for both pollen deposition and visitation and hence is regarded as a more accurate estimation of the pollination service received by plants; @neeman_framework_2009].
+Specifically, we also calculated the controllability (the size of the minimum driver node-set) and the control capacity of networks constructed using pollinator efficiency (which measures the pollen deposition of an interaction) and pollinator importance [which accounts for both pollen deposition and visitation and hence is regarded as a more accurate estimation of the pollination service received by plants; @neeman_framework_2009].
 More details in the Supporting Information Section \@ref(S-visitation-as-proxy).
+
 Second, because interspecific dependencies themselves depend on the network topology and consequently on the accurate sampling of interactions, we tested the robustness of structural controllability to the uncertainty involved with the sampling of interactions.
@@
 # Results
+
+## Controllability
 
@@
 The size of the minimum driver-node set relative to the number of species in each network $n_D$ ranged between $n_D = `r round(min(c_m$n_D), 2)`$ and $n_D = `r round(max(c_m$n_D), 2)`$ (median `r round(median(c_m$n_D), 2)`).
+
+## Differences between invaded and uninvaded networks
+
 We found that the relative size of the minimum driver-node set of invaded communities was not significantly different from that of communities that have not been invaded (Figure \@ref(fig:fig-emp-controllability)a).
 In contrast, there was a large negative relationship between $n_D$ and the network asymmetry (Figure \@ref(fig:fig-emp-controllability)b).
-<!-- DBS: "important" doesn't mean anything statistically. was it significant? -->
-<!-- Yes it is but I'm using model evidence and effect size to assess the importance of variables as opposed to p-values -->
 Furthermore, there were also negative, albeit weaker, relationships between $n_D$ and connectance, nestedness and species richness (Table  \@ref(S-tab:tab-controllability-model-results)). 
@@
 However, empirical networks had a larger $n_D$ than null models that preserved the interactions but shuffled the direction of control of the empirical network ($p = `r sprintf('\\num{%s}', format(randomisations_test$directions$p.value, digits = 2))`$).
-
-<!-- DBS: I don't understand the description of (b) below about the values predicted by the most parsimonious model. I think it needs more info to be fully intelligible. -->
-<!-- The points are actually raw values  -->
 
@@
 
+## Species roles
+
 Species varied widely in their control capacity (Figure \@ref(fig:fig-species-level)). 
@@
 Intriguingly, every invasive species was critical for network control in each of their communities.
-The species-level models identified a positive relationship between control capacity \(\phi\) and a species' contribution to nestedness, visitation strength, and the asymmetry of its dependences (Table \@ref(tab:tab-model-selection-table); Figure \@ref(fig:fig-species-level); Table \@ref(S-tab:tab-model-output-species-level)).
+The species-level models identified a positive relationship between control capacity \(\phi\) and a species' contribution to nestedness, visitation strength, and the asymmetry of its dependences (Table \@ref(tab:tab-model-selection-table); Figure \@ref(fig:fig-species-partial); Table \@ref(S-tab:tab-model-output-species-level)).
 Comparatively, species' degree was only weakly associated with control capacity (Table \@ref(S-tab:tab-var-importance)). 
 In fact, many species with a low degree, especially pollinators, exhibited a large control capacity in their communities (Figure \@ref(S-fig:fig-species-models-degree)a).
+
+```{r correlation-calculations}
+drake::loadd(sl_char_corr)
+correlations <- sl_char_corr %>% 
+  extract2("mean") %>%
+  as.data.frame() %>%
+  tibble::rownames_to_column() %>%
+  dplyr::filter(!rowname %in% c("control_capacity", "superior"))
+```
+
+Species control capacity $\phi$ was only weakly correlated with commonly-used centrality metrics. 
+The Spearman correlation between these ranged between `r round(min(correlations$control_capacity), 2)` (with betweeness-centrality) and `r round(max(correlations$control_capacity), 2)` (with eigen-centrality).
+On the other hand, the probability of being a superior species $\sigma$ was slightly more correlated to established centrality metrics as its Spearman correlation ranged between `r round(min(correlations$superior), 2)` (with eigen-centrality) and `r round(max(correlations$superior), 2)` (with degree; Figure \@ref(S-fig:fig-correlogram)).
+Despite the higher correlation with species' degree we still observed many species with a low degree and a high probability of being superior nodes (Figure \@ref(S-fig:fig-species-models-degree)b).
 
@@
 Partial-residual plots show the relationship between control capacity and each of the independent variables while acccounting for all other remaining variables.
-Ploted values correpond to the predictions of the weighted average of the models shown in Table \\@ref(tab:tab-model-selection-table)"}
+Ploted values correpond to the predictions of the weighted average of the models shown in Table \\@ref(tab:tab-model-selection-table)."}
 drake::loadd(fig_species_partial)
@@
 
-We also found that critical species have a particularly large impact on species coexistence when compared to non-critical species.
-Indeed, the structural stability of the networks where critical species were removed was considerably to those in were non-critical species were removed ($p = `r sprintf('\\num{%s}', format(crit_test$p.value, digits = 2))`$; Figure \@ref(fig:fig-structural-stability); Supporting Information \@ref(S-structural-stability)).
-<!-- DBS: I wonder if people will have a hard time understanding what these values mean.
-That is, the differences are clear visually but what do those values of Omega actually mean?
-I am almost certain a reviewer is going to nag about this.
--->
-<!-- Tried to edit the results and the caption of the figure to help improve that -->
+Finally, we found that critical species have a particularly large impact on species coexistence when compared to non-critical species.
+Indeed, the structural stability of the networks where critical species were removed was considerably lower to those in were non-critical species were removed ($p = `r sprintf('\\num{%s}', format(crit_test$p.value, digits = 2))`$; Figure \@ref(fig:fig-structural-stability); Supporting Information \@ref(S-structural-stability)).
 
@@
 Here, we assume values of the mutualistic trade-off and mean interspecific competition of $\\delta = 0$ and $\\rho = 0.01$ respectively [@saavedra_nested_2016].
-However, the choice of these parameters does not affect the results (Supporting Information \\@ref(S-structural-stability))"}
+However, the choice of these parameters does not affect the results (Supporting Information \\@ref(S-structural-stability))."}
 drake::loadd(fig_structural_stability)
@@
 
-```{r correlation-calculations}
-drake::loadd(sl_char_corr)
-correlations <- sl_char_corr %>% 
-  extract2("mean") %>%
-  as.data.frame() %>%
-  tibble::rownames_to_column() %>%
-  dplyr::filter(!rowname %in% c("control_capacity", "superior"))
-```
-
-Species control capacity $\phi$ was only weakly correlated with commonly-used centrality metrics. 
-The Spearman correlation between these ranged between `r round(min(correlations$control_capacity), 2)` (with betweeness-centrality) and `r round(max(correlations$control_capacity), 2)` (with eigen-centrality).
-On the other hand, the probability of being a superior species $\sigma$ was slightly more correlated to established centrality metrics as its Spearman correlation ranged between `r round(min(correlations$superior), 2)` (with eigen-centrality) and `r round(max(correlations$superior), 2)` (with degree; Figure \@ref(S-fig:fig-correlogram)).
-Despite the higher correlation with species' degree we still observed many species with a low degree and a high probability of being superior nodes (Figure \@ref(S-fig:fig-species-models-degree)b).
+## Testing assumptions
 
@@
 To achieve that goal we applied *structural controllability*, a field at the intersection between control and complex theory that allow us to obtain two key pieces of information: the *controllability* of a network and a species *control capacity* (Table \@ref(tab:tab-glossary)).
-We found that the controllability of a network does not depend on its invasion status and that the species that are critical to altering the state of the community are also the ones that sustain the most the stable coexistence of species in their communities.
+We found that the controllability of a network does not depend on its invasion status and that the species that are critical to altering the state of the community are also the ones that most sustain the stable coexistence of species in their communities.
 
@@
 It also indicates the extent to which network structure can be harnessed for network control.",
-  "minimum driver-node set" = "One of the often many smallest sets of species whose abundances need to be directly managed in order to achieve full control of the community.
+  "minimum driver-node set" = "One of the sets of species whose abundances need to be directly managed in order to achieve full control of the community.
 The minimum driver-node sets can be obtained by finding all maximum matchings in a network.",
@@
 
-The median size of the relative minimum driver-node set of in our dataset was $n_D = `r round(median(c_m$n_D),2)`$. 
-This value is high when compared to other complex systems in which controllability has been investigated;  
-for instance, only gene regulation networks appear to achieve similar levels of controllability while most social, power transmission, internet, neuronal, and even metabolic networks seem to be "easier" to control ($0.1 < n_D < 0.35$) [@liu_controllability_2011].
-These results indicate that fully controlling ecological networks might currently be out of reach for all but the smallest communities [@motter_networkcontrology_2015]. 
-Nevertheless, structural controllability might be helpful at identifying communities in which changes in the ecological state are more likely to occur and provides solid theoretical rationale for the many difficulties encountered in the management and restoration of natural communities [@woodford_confronting_2016].
+Our results indicate that fully controlling ecological networks might currently be out of reach for all but the smallest communities [@motter_networkcontrology_2015]. 
+Indeed, the median size of the relative minimum driver-node set in our dataset was $n_D = `r round(median(c_m$n_D),2)`$, a high value when compared to other complex systems in which controllability has been investigated.
+For instance, only gene regulation networks appear to achieve similar levels of controllability while most social, power transmission, Internet, neuronal, and even metabolic networks seem to be "easier" to control ($0.1 < n_D < 0.35$) [@liu_controllability_2011].
+Structural controllability provides solid theoretical rationale for the many difficulties encountered in the management and restoration of natural communities [@woodford_confronting_2016]. 
+Nevertheless, structural controllability might be helpful at identifying communities in which changes in the ecological state are more likely to occur
 
-When controlling for network structure, we found no difference between the controllability of invaded and uninvaded networks. 
-These results suggest that the differences between the controllability across networks are instead likely to arise from differences in their structure. 
-Specifically, we found that network controllability is almost completely constrained by the patterns of species richness at each trophic guild and their degree distributions [@melian_complex_2002; @bluthgen_specialization_2007].
+The differences between the controllability across networks are likely to arise from differences in their structure rather than their invasion status. 
+Specifically, when controlling for network structure, we found no difference between the controllability of invaded and uninvaded networks. 
+instead controllability is almost completely constrained by the patterns of species richness at each trophic guild and their degree distributions [@melian_complex_2002; @bluthgen_specialization_2007].
 These two factors are particularly relevant because they govern the asymmetric nature of mutual dependences, which themselves provide the foundation of structure and stability in mutualistic networks [@bascompte_asymmetric_2006; @memmott_tolerance_2004; @astegiano_robustness_2015].
 
-Accordingly, our results suggest that structural controllability is closely related to the dynamic persistence of an ecological community. 
+Accordingly, our results suggest that structural controllability is closely related to the dynamic persistence of an ecological community based on two lines of evidence. 
 First, we found a comparatively small but thought-provoking negative relationship between the controllability of a network and its nestedness. 
@@
 At first glance, our findings challenge numerous studies that highlight the role that central species play in the dynamics of their communities and their utility at predicting species extinctions [@jordan_keystone_2009].
-However, further, inspection shows that our results do not contradict these findings. 
-On the contrary, most species with a large degree also have a large control capacity and all of them were classified as superior nodes which corroborates the utility of classic centrality metrics. 
+However, further, inspection shows that our results do not contradict these findings; most species with a large degree also have a large control capacity and all of them were classified as superior nodes which corroborates the utility of classic centrality metrics.
 Putting these observations together, our results therefore take previous findings one step further and suggest that centrality might paint an incomplete picture of the relevance of species.
 
-\R{management-implications}Other conceptual differences between structural controllability and centrality metrics might provide further insight into the conservation of ecological networks. 
+\R{management-implications}Other conceptual differences between structural controllability and centrality metrics provide three key insights into the conservation of ecological networks. 
 First, structural controllability emphasizes that the effect a species has on the abundance of other species is not independent of the effects of other other species in their community. 
@@
 By accounting for network dynamics (even if in a simple way), structural stability incorporates more ecological realism, especially in the extreme scenario in which the state of a community is only marginally affected by the topology of their interactions.
-<!-- DBS: See what everyone else says about these last two sentences. I think they get harder and harder to follow as they evolve. -->
-<!-- Made some edits, we'll see what people say -->
 
@@
 
-The authors thank Jane Memmott and coauthors, and everyone that has made their data available to us, Takeuki Uno for the insight provided to find the set of all maximum matching algorithms, and Jason Tylianakis, Bernat Bramon Mora, Guadalupe Peralta, Rogini Runghen, Michelle Marraffini, Warwick Allen, Matthew Hutchinson, and Marilia Gaiarsa for feedback and valuable discussions.
+The authors thank Jane Memmott and co-authors, and everyone that has made their data available to us, Takeuki Uno for the insight provided to find the set of all maximum matching algorithms, and Jason Tylianakis, Bernat Bramon Mora, Guadalupe Peralta, Rogini Runghen, Michelle Marraffini, Mark Herse, Warwick Allen, Matthew Hutchinson, and Marilia Gaiarsa for feedback and valuable discussions.
 EFC acknowledges the support from the University of Canterbury Doctoral Scholarship, the University of Canterbury Meadow Mushrooms Postgraduate Scholarship, a New Zealand International Doctoral Research Scholarship, and a travel grant from the European Space Agency.

### 2018-07-17 paper/manuscript.Rmd
Feedback Daniel

@@
 Centrality metrics have often been used to identify these species, which are sometimes referred as "keystone" species. 
-However, the relationship between centrality and keystoneness is phenomenological and largely based on an intuitive understanding of what may constitute an important species. 
-While centrality is good at predicting which species could cause the largest change in their community it says little about how these species could be used to attain (or preserve) a particular state of the community.
+However, the relationship between centrality and keystoneness is largely phenomenological and based mostly on our intuition regarding what constitutes an important species. 
+While centrality is useful when predicting which species extinctions could cause the largest change in a community, it says little about how these species could be used to attain or preserve a particular community state.
 
-2. Here we introduce structural controllability an approach that allows us to quantify the extent to which network topology can be harnessed to achieve a desired state. 
+2. Here we introduce structural controllability, an approach that allows us to quantify the extent to which network topology can be harnessed to achieve a desired state. 
 It also allows us to quantify a species control capacity—its relative importance—and identify the set of species that, collectively, are critical in this context.
@@
 Interestingly, this set of critical species was mostly composed of plants and every invasive species in our dataset was part of it. 
-We also found that species with high control capacity and in particular critical species contribute the most to the to stable coexistence of their community even when controlling for its degree, abundance/interaction strength, and the relative dependence of their partners.
+We also found that species with high control capacity and in particular critical species contribute the most to the stable coexistence of their community.
+This result was true, even when controlling for its degree, abundance/interaction strength, and the relative dependence of their partners.
 
@@
 
-**Keywords:** Keystone species, ecological networks, management interventions, mutualism, network control theory, structural controllability, plant population and community dynamics, species importance
+**Keywords:** Keystone species, management interventions, mutualism, network control theory, plant population and community dynamics, species importance, control capacity
 

### 2018-07-17 paper/manuscript.Rmd
Making explicit that lower Nd means higher controllability

@@
 Specifically, drawing from the structural-controllability literature, we use the size of the minimum driver-node set relative to the total number of species $n_D = \frac{D}{N}$ as a measure of the *controllability* of a network—the extent to which the network structure can be harnessed to control the community.
+The lower $n_D$ the more controllable the community. 
 In an ecological context, external inputs can be thought of as management interventions that modify the abundance of a particular species.
@@
 Our results indicate that fully controlling ecological networks might currently be out of reach for all but the smallest communities [@motter_networkcontrology_2015]. 
-Indeed, the median size of the relative minimum driver-node set in our dataset was $n_D = `r round(median(c_m$n_D),2)`$, a high value when compared to other complex systems in which controllability has been investigated.
+Indeed, the median size of the relative minimum driver-node set in our dataset was $n_D = `r round(median(c_m$n_D),2)`$, a high value when compared to other complex systems in which controllability has been investigated (the lower $n_D$ the more controllable the community).
 For instance, only gene regulation networks appear to achieve similar levels of controllability while most social, power transmission, Internet, neuronal, and even metabolic networks seem to be "easier" to control ($0.1 < n_D < 0.35$) [@liu_controllability_2011].

### 2018-07-17 paper/manuscript.Rmd
Alternative titles

@@
 * Keystoneness, centrality, and the structural controllability of ecological networks
+* Keystone and critical species, a structural controllability perspective of ecological networks
+* The controllability of ecological networks
+* Species with high control capacity support stable coexistence of pollination communities
+* Species with high control capacity support stable coexistence of pollination networks
+* A control theory perspective: species with high control capacity support stable coexistence of pollination communities
 
@@
 **Keywords:** Keystone species, management interventions, mutualism, network control theory, plant population and community dynamics, species importance, control capacity
+
+\clearpage
 

### 2018-07-17 paper/reviewers-response.Rmd
Also thank the assistant editor... better safe than sorry

@@
 
-We are thankful to the editors, David Gibson and Nicole Rafferty, and two anonymous reviewers for the insightful comments to improve the manuscript. 
+We are thankful to the assistant editor James Ross, the editors Nicole Rafferty and David Gibson, and two anonymous reviewers for the insightful comments to improve the manuscript. 
 In the following sections, you can find a detailed response to each comment raised during the previous round of review.

### 2018-07-17 paper/manuscript.Rmd
Narrow down titles

--- 2018-07-17 paper/manuscript.Rmd
@@
 ---
-title: "Structural controllability of ecological networks"
+title: "Species with high control capacity support stable coexistence of pollination networks"
 classoption: a4paper
@@
 
-* Keystoneness, centrality, and the structural controllability of ecological networks
+* Structural controllability of ecological networks
+* Structural controllability: species with high control capacity support stable coexistence of pollination networks
 

### 2018-07-18 paper/manuscript.Rmd
Commas and typos by Peter

@@
 3. We found that the controllability of a community is not dependent on its invasion status, but on the asymmetric nature of its mutual dependences. 
-While central species were also likely to have a large control capacity, centrality fails to identify species that despite being less connected were critical in their communities. 
+While central species were also likely to have a large control capacity, centrality fails to identify species that, despite being less connected, were critical in their communities. 
 Interestingly, this set of critical species was mostly composed of plants and every invasive species in our dataset was part of it. 
-We also found that species with high control capacity and in particular critical species contribute the most to the stable coexistence of their community.
+We also found that species with high control capacity, and in particular critical species, contribute the most to the stable coexistence of their community.
 This result was true, even when controlling for its degree, abundance/interaction strength, and the relative dependence of their partners.
@@
 Generally speaking, central species tend to be better connected and consequently are more likely to participate in the network's "food chains". 
-Because species that participate in more chains are assumed to be more likely to affect the abundances of other species, centrality metrics have often been used to identify keystone species in the community [@jordan_quantifying_2007].
+Because species that participate in more chains are more likely to affect the abundances of other species, centrality metrics have often been used to identify keystone species in the community [@jordan_quantifying_2007].
 Centrality metrics have been shown to be useful tools to rank species in regard to their potential to alter the abundances of other species, in particular when estimating the probability of secondary extinctions that may follow the loss of a species [@dunne_network_2002; @kaiser-bunbury_robustness_2010].
@@
 
-Species abundances---and consequently the state of the community as a whole---are influenced by both the structure of their interactions and the dynamics of these interactions, including the mechanisms of self-regulation [@lever_sudden_2014].
+Species abundances---and consequently the state of the community as a whole---are influenced both by the structure of their interactions and the dynamics of these interactions, including the mechanisms of self-regulation [@lever_sudden_2014].
 However, community and population dynamics can be modelled in innumerable ways, and empirical support for one versus another is often still ambiguous [@holland_population_2002]. 
@@
 A system is said to be controllable if it is possible to steer it from an initial to an arbitrary final state within finite time [@kalman_mathematical_1963]. 
-A simple version of such a system can be described by $\frac{dx}{dt} = Ax + Bu(t)$, where the change of its state over time ($\frac{dx}{dt}$) depends on its current state *x* (for example, the species' abundances), an external time-varying input *u(t)* (the control signal), and two matrices *A* and *B*, which encode information about the network structure and how species respond to external inputs, respectively.
+A simple version of such a system can be described by $\frac{dx}{dt} = Ax + Bu(t)$, where the change of its state over time ($\frac{dx}{dt}$) depends on its current state *x* (for example the species' abundances), an external time-varying input *u(t)* (the control signal), and two matrices *A* and *B*, which encode information about the network structure and how species respond to external inputs, respectively.
 In classic control theory, determining whether this system is controllable can be achieved by checking that its controllability matrix $R= [ \begin{matrix}B & AB & A^{2}B & ...& A^{n-1}B\end{matrix} ]$ has full rank.
 In complex systems, however, employing this rank condition, or numerical approximations of it is infeasible because it is hard to fully parameterise *A* and *B* (either because the weight of the links changes over time or because they are difficult to measure).
-Here, we use an approach based on the structural controllability theorem [@lin_structural_1974], which assumes that we are confident about which elements of *A* and *B* have either non-zero or zero values (there is an interaction or not), but that we less sure about the precise magnitude of the non-zero values.
+Here, we use an approach based on the structural controllability theorem [@lin_structural_1974], which assumes that we are confident about which elements of *A* and *B* have either non-zero or zero values (there is an interaction or not), but that we are less sure about the precise magnitude of the non-zero values.
 Using this structural approach, we can find out the controllability of a system for every non-zero realisation of the parameters.
@@
 
-This link becomes apparent after examining the graphical interpretation of structural controllability: from a topological perspective a network is structurally controllable if there are no inaccessible nodes—that is, nodes without incoming links—or dilations—*expansions* of the network (Figure \@ref(fig:fig-example-networks)b; Supporting Information Section \@ref(S-structural-controllability)).
+This link becomes apparent after examining the graphical interpretation of structural controllability: from a topological perspective, a network is structurally controllable if there are no inaccessible nodes—that is, nodes without incoming links—or dilations—*expansions* of the network (Figure \@ref(fig:fig-example-networks)b; Supporting Information Section \@ref(S-structural-controllability)).
 The key is to note that these two fundamental conditions of structural controllability imply that there is a one-to-one relationship between *superior* and *subordinate* nodes just like the one-to-one relationship between jobs and applicants (Figure \@ref(fig:fig-example-networks)b, bottom left).
@@
 The higher a species control capacity, the greater the likelihood that they would need to be directly managed to change (or maintain) the ecological state of their community. 
-Therefore a species control capacity provides an estimation of their relative importance at driving the state of the community [@jia_control_2013].
+Therefore, a species control capacity provides an estimation of their relative importance at driving the state of the community [@jia_control_2013].
 
@@
 Second, the species strength (the sum of a species' visits), which quantifies the strength of a species associations and is indirectly related to its abundance [@poisot_comparative_2012]. 
-Third, the direction of asymmetry which quantifies the net balance in dependencies; that is it indicates if a species affects other species more than what they affect it or not [@vazquez_species_2007].
+Third, the direction of asymmetry which quantifies the net balance in dependencies; that is, it indicates if a species affects other species more than what they affect it or not [@vazquez_species_2007].
 Fourth, the species degree in order to account for the intrinsic centrality of a species.
@@
 To test this hypothesis, we identified these critical species in each of the networks and investigated whether they have a larger than average impact on the stable coexistence of species in the community.
-Within mutualistic networks, one useful measure of for how networks impact stable coexistence is called structural stability [@rohr_structural_2014]. 
+Within mutualistic networks, one useful measure of stable coexistence is called structural stability [@rohr_structural_2014]. 
 Mathematically, the structural stability of a network represents the size of the parameter space (i.e., growth rates, carrying capacities, etc.) under which all species can sustain positive abundances [@saavedra_nested_2016].
@@
 Our choice of studying invaded/uninvaded networks was based on a desire to contrast the extensive empirical evidence of the role of invasive plants with our theoretical results. 
-Without exception, we found that invasive plants were critical for network control and as such our results were in line with our expectations. 
+We found that invasive plants were always critical for network control and as such our results were in line with our expectations. 
 Invasive plants have been previously found to exacerbate the asymmetries in their communities [@aizen_invasive_2008; @bartomeus_contrasting_2008-1; @henriksson_strong_2016] and to be central in their communities [@vila_invasive_2009; @palacio_generalist_2016].
@@
 Collectively, critical species dominate the state of their community and therefore are likely to be highly relevant for ecosystem management and conservation. 
-While useful, centrality metrics, which have often been used as a proxy for keystoneness, fail to identify some of these species which highlights their limitations when we fully embrace the notion that ecological communities are dynamical systems.
+While useful, centrality metrics, which have often been used as a proxy for keystoneness, fail to identify some of these species, highlighting their limitations when we fully embrace the notion that ecological communities are dynamical systems.
 @paine_note_1969 showed nearly 50 years ago that one single species can dominate the state of its community. 
 Structural controllability suggests that this situation might be the exception rather than the rule. 
-<!-- We see our study as a starting point to study the controllability of ecological and socio-ecological systems where many exciting questions lie ahead.  -->
+We see our study as a starting point to study the controllability of ecological and socio-ecological systems where many exciting questions lie ahead.
 

### 2018-07-18 paper/manuscript.Rmd
Settle on a title
Remove superior nodes stuff from the methods and the results

@@
 
-*Alternative titles:*
-
-* Structural controllability of ecological networks
-* Structural controllability: species with high control capacity support stable coexistence of pollination networks
+<!-- *Alternative titles:*  -->
+<!-- * Structural controllability of ecological networks -->
 
@@
 
-In addition, we wanted to understand how two species-level control metrics are related to five metrics of keystoneness based on centrality. 
-For the centrality metrics, we use a species' degree, betweenness, closeness centrality [@martin_gonzalez_centrality_2010], page rank [@mcdonald-madden_using_2016], and eigen centrality [@jordano_ecological_2006].
-The first control metric we use is a species control capacity $\phi$ described above. 
-The second metric is the probability that a focal species influences the abundance of another species internally, regardless of whether a management intervention is required in that species or not. 
-We call this the probability of being a superior node $\sigma$. 
-Because superior nodes are those at the beginning of a matched link, \(\sigma\) could be seen as a "softer" version of control capacity. 
-Conveniently, unlike the minimum driver-node set, superior species are the same for all control configurations and so in a network without reciprocal links the probability that a species is superior $\sigma$ is either 1 or 0.
+In addition, we wanted to understand how a species control capacity $\phi$ described above relates to metrics of keystoneness based on centrality. 
+Specifically, in each network, we calculated the species' degree, betweenness, closeness centrality [@martin_gonzalez_centrality_2010], page rank [@mcdonald-madden_using_2016], and eigen centrality [@jordano_ecological_2006].
+We then calculated the spearman correlation coefficient between control capacity and each of these centrality metrics.
 
@@
 Species control capacity $\phi$ was only weakly correlated with commonly-used centrality metrics. 
-The Spearman correlation between these ranged between `r round(min(correlations$control_capacity), 2)` (with betweeness-centrality) and `r round(max(correlations$control_capacity), 2)` (with eigen-centrality).
-On the other hand, the probability of being a superior species $\sigma$ was slightly more correlated to established centrality metrics as its Spearman correlation ranged between `r round(min(correlations$superior), 2)` (with eigen-centrality) and `r round(max(correlations$superior), 2)` (with degree; Figure \@ref(S-fig:fig-correlogram)).
-Despite the higher correlation with species' degree we still observed many species with a low degree and a high probability of being superior nodes (Figure \@ref(S-fig:fig-species-models-degree)b).
+The Spearman correlation between these ranged between `r round(min(correlations$control_capacity), 2)` (with betweeness-centrality) and `r round(max(correlations$control_capacity), 2)` (with eigen-centrality), see Figure \@ref(S-fig:fig-correlogram)a.
+The correlation coefficient with degree was `r round(correlations[correlations$rowname == "degree", ]$control_capacity, 2)`, however most species with high degree also tended to attain a high control capacity (Figure \@ref(S-fig:fig-species-models-degree)a).
 

### 2018-07-19 paper/cover-letter.tex
Also thank the assistant editor

@@
 
-We are thankful to the senior and associate editors, Prof.\ David Gibson and Prof.\ Nicole Rafferty, and two anonymous reviewers for the insightful comments to improve the manuscript. 
+We are thankful to the assistant editor James Ross, the editors Prof.\ Nicole Rafferty and Prof.\ David Gibson, and two anonymous reviewers for the insightful comments to improve the manuscript. 
 We are also grateful for the opportunity to resubmit.

### 2018-07-19 paper/reviewers-response.Rmd
Settle on a title

@@
 ---
-title: "Structural controllability of ecological networks"
+title: "Keystoneness, centrality, and the structural controllability of ecological networks"
 subtitle: "JEcol-2017-0720 - Detailed response to comments"

### 2018-07-19 paper/manuscript.Rmd
Settle on a title

@@
 ---
-title: "Species with high control capacity support stable coexistence of pollination networks"
+title: "Keystoneness, centrality, and the structural controllability of ecological networks"
 classoption: a4paper

### 2018-07-19 paper/manuscript.Rmd
Update keywords

@@
 
-**Keywords:** Keystone species, management interventions, mutualism, network control theory, plant population and community dynamics, species importance, control capacity
+**Keywords:** Keystone species, management interventions, mutualism, network control theory, plant population and community dynamics, species importance, control capacity, structural stability, controllability
 

### 2018-12-11 paper/reviewers-response.Rmd
First changes for review JEcol-2018-0545. Incomplete

--- 2018-06-26 paper/reviewers-response.Rmd
@@
 ---
-title: "Structural controllability of ecological networks"
-subtitle: "JEcol-2017-0720 - Detailed response to comments"
+title: "Keystoneness, centrality, and the structural controllability of ecological networks"
+subtitle: "JEcol-2018-0545 - Detailed response to comments"
 author: "Fernando Cagua, Kate L. Wootton, Daniel B. Stouffer"
@@
 
-We are thankful to the editors, David Gibson and Nicole Rafferty, and two anonymous reviewers for the insightful comments to improve the manuscript. 
+We are thankful to the assistant editor James Ross, the senior editor and David Gibson, and three anonymous reviewers for the insightful comments to improve the manuscript. 
 In the following sections, you can find a detailed response to each comment raised during the previous round of review.
@@
 # Editor comments
+
+# Associate Editor's comments:
+
+> "I think this ms now makes much clearer the potential insights to be gained by applying control theory to interaction networks.
+In particular, the authors have done a nice job of explaining how their findings reinforce existing ideas in the literature on the stability of ecological networks while also acknowledging limitations.
+The reviewers identify a few remaining issues that should be straightforward to address.
+I also noticed a few issues"
+
+Thank you for the positive feedback. We have addressed all of the specific issues raised and highlight these in red text in our resubmitted manuscript.
+
+# Reviewer comments #1
+
+> "I'd like to commend the authors to this revised version of the manuscript on "Keystoneness, centrality, and the structural controllability of ecological networks".
+I thoroughly enjoyed the re-written manuscript, which is now considerably more accessible and clearly targets the community of network ecologists, while not ignoring the importance of the applied relevance of the findings.
+Overall, I don't have any major comments.
+I guess the language is in parts on the casual side, yet without compromising the preciseness or clarity of the text.
+I noticed a few typos or style errors that the authors may want to address"
+
+We are pleased that the reviewer "thoroughly enjoyed the re-written manuscript", and appreciate the identified issues.
+We have addressed all issues in the text and identify these in red.
+We have rewritten the sentence on line 388 to improve clarity.
+It now reads as follows: "First, structural controllability emphasizes that the effect a species has on the abundance of other species is not independent of the effects of those other species in their community".
+
+> "L23-26: in these lines, you refer to critical species, but I think the distinction between having high control capacity versus being critical needs to be defined (briefly) earlier (it is stated in L18-19 that you will quantify both control capacity and identify critical species, but it is not explained how they are distinct)."
+
+We now identify the distinction between high control capacity and being critical on lines .............
+"It also allows us to quantify a species control capacity-its relative importance-and identify the set of species that, collectively, are critical-have maximum control capacity-in this context."
+
+# Reviewer comments #2
+
+-------------------------------------------------------
+
+# Previous response:
 

### 2018-12-11 paper/manuscript.Rmd
First changes for review JEcol-2018-0545. Incomplete

--- 2018-07-19 paper/manuscript.Rmd
@@
 
-1. An important dimension of a species role is its ability to alter the state and maintain the diversity of its community. 
+1. An important dimension of a species' role is its ability to alter the state and maintain the diversity of its community. 
 Centrality metrics have often been used to identify these species, which are sometimes referred as "keystone" species. 
 However, the relationship between centrality and keystoneness is largely phenomenological and based mostly on our intuition regarding what constitutes an important species. 
-While centrality is useful when predicting which species extinctions could cause the largest change in a community, it says little about how these species could be used to attain or preserve a particular community state.
+While centrality is useful when predicting which species' extinctions could cause the largest change in a community, it says little about how these species could be used to attain or preserve a particular community state.
 
 2. Here we introduce structural controllability, an approach that allows us to quantify the extent to which network topology can be harnessed to achieve a desired state. 
-It also allows us to quantify a species control capacity—its relative importance—and identify the set of species that, collectively, are critical in this context.
+It also allows us to quantify a species' control capacity—its relative importance—and identify the set of species that, collectively, are critical—have maximum control capacity—in this context. 
 We illustrate the application of structural controllability with ten pairs of uninvaded and invaded plant-pollinator communities.
@@
 While central species were also likely to have a large control capacity, centrality fails to identify species that, despite being less connected, were critical in their communities. 
-Interestingly, this set of critical species was mostly composed of plants and every invasive species in our dataset was part of it. 
+Interestingly, this set of critical species was mostly composed of plants and included every invasive species in our dataset. 
 We also found that species with high control capacity, and in particular critical species, contribute the most to the stable coexistence of their community.
@@
 
-**Keywords:** Keystone species, management interventions, mutualism, network control theory, plant population and community dynamics, species importance, control capacity
+**Keywords:** Keystone species, management interventions, mutualism, network control theory, plant population and community dynamics, species' importance, control capacity, structural stability, controllability
 
@@
 
-A significant proportion of the network tools used to estimate species roles in this context rely on the calculation of a species' centrality—a relative ranking of its positional importance that originally stems from social-network research [@noah_e._friedkin_theoretical_1991; @martin_gonzalez_centrality_2010].
+A significant proportion of the network tools used to estimate species' roles in this context rely on the calculation of a species' centrality—a relative ranking of its positional importance that originally stems from social-network research [@noah_e._friedkin_theoretical_1991; @martin_gonzalez_centrality_2010].
 Generally speaking, central species tend to be better connected and consequently are more likely to participate in the network's "food chains". 
@@
 
-Species abundances---and consequently the state of the community as a whole---are influenced both by the structure of their interactions and the dynamics of these interactions, including the mechanisms of self-regulation [@lever_sudden_2014].
+Species' abundances---and consequently the state of the community as a whole---are influenced both by the structure of their interactions and the dynamics of these interactions, including the mechanisms of self-regulation [@lever_sudden_2014].
 However, community and population dynamics can be modelled in innumerable ways, and empirical support for one versus another is often still ambiguous [@holland_population_2002]. 
@@
 Therefore, we first ask whether there are differences between the controllability of invaded and uninvaded networks. 
-We then expand existing methods from control theory to effectively link the *controllability* of a network with the role of its constituent species.
+We then expand existing methods from control theory to effectively link the *controllability* (Table \@ref(tab:tab-glossary)) of a network with the role of its constituent species.
 We ask—from a control-theoretic perspective—whether there are key differences between species in the role they play at driving the state of the community and explore the ecological factors related to these differences.
 This allows us to identify species that might be critical for network control and show that they have a larger than expected impact on the stable coexistence of the community.
-Finally, we compare the proposed approach to current methods based on species centrality and show how these methods are indeed valuable but ultimately paint a limited picture in regard to the "keystoneness" of a species.
+Finally, we compare the proposed approach to current methods based on species' centrality and show how these methods are indeed valuable but ultimately paint a limited picture in regard to the "keystoneness" of a species.
 
@@
 Four pairs correspond to natural or semi-natural vegetation communities in the city of Bristol, UK [@lopezaraizamikel_impact_2007]. 
-These communities are comprised of `r lop[1]`--`r lop[6]` species (mean `r round(lop[4])`), and non-invaded plots were obtained by experimentally removing all the flowers of the invasive species *Impatients grandulifera*.
+These communities comprised `r lop[1]`--`r lop[6]` species (mean `r round(lop[4])`), and non-invaded plots were obtained by experimentally removing all the flowers of the invasive species *Impatients grandulifera*.
 The other six pairs were obtained from lower diversity Mediterranean shrublands in Cap de Creus National Park, Spain [@bartomeus_contrasting_2008-1].
-These communities are comprised of `r bar[1]`--`r bar[6]` species (mean `r round(bar[4])`); in contrast to the above, uninvaded communities were obtained from plots that had not yet been colonised by either of the invasive species *Carpobrotus affine acinaciformis* or *Opuntia stricta*.
+These communities comprised `r bar[1]`--`r bar[6]` species (mean `r round(bar[4])`); in contrast to the above, uninvaded communities were obtained from plots that had not yet been colonised by either of the invasive species *Carpobrotus affine acinaciformis* or *Opuntia stricta*.
 The structure of all these communities was defined by the pollinator visitation frequency, which has been shown to be an appropriate surrogate for interspecific effects in pollination networks [@vazquez_interaction_2005; @bascompte_asymmetric_2006].
@@
 (b) Once we have established the directions of control, we can determine whether the network is controllable or not.
-Any system defined by a directed network (with state nodes $x_i$; species populations in an ecological context) and external control inputs (nodes $u_i$, orange links) is structurally controllable if it satisfies two conditions: it has no dilations (expansions in the network) and no inaccessible nodes.
+Any system defined by a directed network (with state nodes $x_i$; species' populations in an ecological context) and external control inputs (nodes $u_i$, orange links) is structurally controllable if it satisfies two conditions: it has no dilations (expansions in the network) and no inaccessible nodes.
 The system on the top left is not controllable because there is a dilation since node $x_2$ is being used to control two nodes simultaneously; in other words, there are fewer superiors ($x_2$) than subordinates ($x_1$ and $x_3$).
@@
 
-## Species roles
+## Species' roles
 
@@
 Moreover, some species belong to these combinations more often than do others. 
-We call this property a species "control capacity", $\phi$. 
-The higher a species control capacity, the greater the likelihood that they would need to be directly managed to change (or maintain) the ecological state of their community. 
-Therefore, a species control capacity provides an estimation of their relative importance at driving the state of the community [@jia_control_2013].
+We call this property a species' "control capacity", $\phi$. 
+The higher a species' control capacity, the greater the likelihood that it would need to be directly managed to change (or maintain) the ecological state of their community. 
+Therefore, a species' control capacity provides an estimation of its relative importance at driving the state of the community [@jia_control_2013].
 
-To calculate a species control capacity $\phi$, we must first enumerate all possible maximum matchings (Supporting Information Section \@ref(S-all-maximum-matching)). 
+To calculate a species' control capacity $\phi$, we must first enumerate all possible maximum matchings (Supporting Information Section \@ref(S-all-maximum-matching)). 
 Unfortunately, enumerating all maximum matchings is extremely expensive from a computational perspective—a network with a couple dozen species has several hundred million unique maximum matchings. 
@@
 Here, we extend this algorithm such that it is possible to calculate a highly accurate approximation of the control capacity $\phi$ of every species in the network (Supporting Information Section \@ref(S-input-graph)).
-In the networks that contained reciprocal links (because there was no asymmetry in the dependences of a species pair), we averaged a species control capacity $\phi$ across every possible "non-reciprocal" version of the network (Supporting Information Section \@ref(S-reciprocal-links)).
+In the networks that contained reciprocal links (because there was no asymmetry in the dependences of a species pair), we averaged a species' control capacity $\phi$ across every possible "non-reciprocal" version of the network (Supporting Information Section \@ref(S-reciprocal-links)).
 
@@
 These models included five predictor variables that mirror the network-level predictors. 
-First, the species contribution to nestedness, which has been proposed as a key feature that promotes stability and robustness in mutualistic networks [@saavedra_strong_2011]. 
-Second, the species strength (the sum of a species' visits), which quantifies the strength of a species associations and is indirectly related to its abundance [@poisot_comparative_2012]. 
+First, the species' contribution to nestedness, which has been proposed as a key feature that promotes stability and robustness in mutualistic networks [@saavedra_strong_2011]. 
+Second, the species' strength (the sum of a species' visits), which quantifies the strength of a species' associations and is indirectly related to its abundance [@poisot_comparative_2012]. 
 Third, the direction of asymmetry which quantifies the net balance in dependencies; that is, it indicates if a species affects other species more than what they affect it or not [@vazquez_species_2007].
-Fourth, the species degree in order to account for the intrinsic centrality of a species.
-Finally, we included a categorical variable for the species trophic level (plant or pollinator) and an interaction term between trophic level and the previous four variables. 
+Fourth, the species' degree in order to account for the intrinsic centrality of a species.
+Finally, we included a categorical variable for the species' trophic level (plant or pollinator) and an interaction term between trophic level and the previous four variables. 
 To facilitate comparison between predictors, degree and visitation strength were log-transformed and all four continuous variables were scaled to have a mean of zero and a standard deviation of one.
@@
 
-In addition, we wanted to understand how a species control capacity $\phi$ described above relates to metrics of keystoneness based on centrality. 
+In addition, we wanted to understand how a species' control capacity $\phi$ described above relates to metrics of keystoneness based on centrality. 
 Specifically, in each network, we calculated the species' degree, betweenness, closeness centrality [@martin_gonzalez_centrality_2010], page rank [@mcdonald-madden_using_2016], and eigen centrality [@jordano_ecological_2006].
@@
 Specifically, we also calculated the controllability (the size of the minimum driver node-set) and the control capacity of networks constructed using pollinator efficiency (which measures the pollen deposition of an interaction) and pollinator importance [which accounts for both pollen deposition and visitation and hence is regarded as a more accurate estimation of the pollination service received by plants; @neeman_framework_2009].
-More details in the Supporting Information Section \@ref(S-visitation-as-proxy).
+See Supporting Information Section \@ref(S-visitation-as-proxy) for more details.
 
@@
 Pollinators had, in average, larger control capacities than plants. 
-That said, almost no pollinator was critical for network control, where a species is critical for control if it has control capacity \(\phi_i = 1\)). 
+That said, almost no pollinator was critical for network control, (where a species is critical for control if it has control capacity \(\phi_i = 1\)). 
 Plants had a multimodal distribution of control capacity with maxima at both extremes of the distribution (Figure \@ref(fig:fig-species-level)a). 
@@
 
-Species control capacity $\phi$ was only weakly correlated with commonly-used centrality metrics. 
+Species' control capacity $\phi$ was only weakly correlated with commonly-used centrality metrics. 
 The Spearman correlation between these ranged between `r round(min(correlations$control_capacity), 2)` (with betweeness-centrality) and `r round(max(correlations$control_capacity), 2)` (with eigen-centrality), see Figure \@ref(S-fig:fig-correlogram)a.
@@
                booktabs = T,
-               caption = "Selection table of the binomial generalised linear models of species control capacity, $\\phi$. Only models with a weight larger or equal to 0.01 are shown.", 
+               caption = "Selection table of the binomial generalised linear models of species' control capacity, $\\phi$. Only models with a weight larger or equal to 0.01 are shown.", 
                row.names = F, 
@@
 
-\R{testing-assumptions-results-line} We found that using visitation as a proxy for the strength of species interactions leads to similar results than those obtained using pollinator importance [regarded as an accurate measure of the pollination service to plants; Supporting Information Section \@ref(S-visitation-as-proxy); @neeman_framework_2009].
+\R{testing-assumptions-results-line} We found that using visitation as a proxy for the strength of species' interactions leads to similar results than those obtained using pollinator importance [regarded as an accurate measure of the pollination service to plants; Supporting Information Section \@ref(S-visitation-as-proxy); @neeman_framework_2009].
 Importantly, we also found that structural stability is robust to incomplete sampling of interactions. 
@@
 
-Our main goal was to understand the role that species play at both modifying the abundance of the species they interact with and the state of the community as a whole. 
-To achieve that goal we applied *structural controllability*, a field at the intersection between control and complex theory that allow us to obtain two key pieces of information: the *controllability* of a network and a species *control capacity* (Table \@ref(tab:tab-glossary)).
+Our main goal was to understand the role that species play in both modifying the abundance of the species they interact with and the state of the community as a whole. 
+To achieve that goal we applied *structural controllability*, a field at the intersection between control and complex theory that allowed us to obtain two key pieces of information: the *controllability* of a network and a species' *control capacity* (Table \@ref(tab:tab-glossary)).
 We found that the controllability of a network does not depend on its invasion status and that the species that are critical to altering the state of the community are also the ones that most sustain the stable coexistence of species in their communities.
@@
 Structural controllability provides solid theoretical rationale for the many difficulties encountered in the management and restoration of natural communities [@woodford_confronting_2016]. 
-Nevertheless, structural controllability might be helpful at identifying communities in which changes in the ecological state are more likely to occur
+Nevertheless, structural controllability might be helpful at identifying communities in which changes in the ecological state are more likely to occur.
 
@@
 Specifically, when controlling for network structure, we found no difference between the controllability of invaded and uninvaded networks. 
-instead controllability is almost completely constrained by the patterns of species richness at each trophic guild and their degree distributions [@melian_complex_2002; @bluthgen_specialization_2007].
+Instead controllability is almost completely constrained by the patterns of species richness at each trophic guild and their degree distributions [@melian_complex_2002; @bluthgen_specialization_2007].
 These two factors are particularly relevant because they govern the asymmetric nature of mutual dependences, which themselves provide the foundation of structure and stability in mutualistic networks [@bascompte_asymmetric_2006; @memmott_tolerance_2004; @astegiano_robustness_2015].
@@
 At first glance, our findings challenge numerous studies that highlight the role that central species play in the dynamics of their communities and their utility at predicting species extinctions [@jordan_keystone_2009].
-However, further, inspection shows that our results do not contradict these findings; most species with a large degree also have a large control capacity and all of them were classified as superior nodes which corroborates the utility of classic centrality metrics.
+However, further inspection shows that our results do not contradict these findings; most species with a large degree also have a large control capacity and all of them were classified as superior nodes which corroborates the utility of classic centrality metrics.
 Putting these observations together, our results therefore take previous findings one step further and suggest that centrality might paint an incomplete picture of the relevance of species.
@@
 \R{management-implications}Other conceptual differences between structural controllability and centrality metrics provide three key insights into the conservation of ecological networks. 
-First, structural controllability emphasizes that the effect a species has on the abundance of other species is not independent of the effects of other other species in their community. 
+First, structural controllability emphasizes that the effect a species has on the abundance of other species is not independent of the effects of those other species in their community. 
 The rankings provided by centrality metrics and other heuristics fail to account for the collective influence of several species at once. 
@@
 Third, structural controllability explicitly acknowledges the existence of multiple management strategies and some will be better than others depending on the context.
-Approaches to prioritise species for conservation and reintroduction based on traits or centrality are still useful and are likely to overlap with species control capacity\R{extra-references-1} [@pires_friendship_2017; @devoto_understanding_2012].
+Approaches to prioritise species for conservation and reintroduction based on traits or centrality are still useful and are likely to overlap with species' control capacity\R{extra-references-1} [@pires_friendship_2017; @devoto_understanding_2012].
 Stepping back, our results also provide support to the idea that management decisions should not be based on a single technique but indicate that focusing on ecosystem processes and interactions may be more effective than traditional ranking-based approaches \R{extra-references-2} [@harvey_bridging_2017].
@@
 We found that invasive plants are, however, unlikely to be inherently different from their native counterparts [@emer_species_2016; @stouffer_how_2014]. 
-Just like any other mutualist in our dataset, invasive plants tended to attain a high control capacity proportional to the degree to which they contribute to network persistence, are abundant, and depend little on other species.
+Invasive plants tended to be important for network persistence, be abundant, and depend little on other species and, as a result, have high control capacity, just like any other mutualist in our data set with those properties.
 Furthermore, our observation that changes in the abundance of invasive plants (and presumably all critical species) are crucial to modify the state of the community agrees with recent evidence showing that ecosystem restoration focused on the eradication of invasive plants can have transformative desirable effects in plant-pollinator communities\R{extra-references-3} [@kaiser-bunbury_ecosystem_2017].
@@
 The ramifications of this assumption imply that, while structural controllability is useful to identify species that are relevant for network control, it cannot be used to design the *exact* interventions that should be applied to these species in order to achieve a desired state.
-In an ideal scenario, we would completely incorporate the species dynamics into the controllability analysis [@cornelius_realistic_2013]; the reality is that such information is rarely available in most ecological scenarios.
+In an ideal scenario, we would completely incorporate the species' dynamics into the controllability analysis [@cornelius_realistic_2013]; the reality is that such information is rarely available in most ecological scenarios.
 \R{data-requirements}In contrast, structural controllability only requires a quantitative approximation of the network's interactions to gain valuable insight from the community.
-Furthermore, while the relationship between centrality and keystoneness is based on an intuitive understanding of what a keystone species is, the assumptions of structural controllability are explicit and the estimation of a species importance arises from a mechanistic understanding of the population dynamics between species.
+Furthermore, while the relationship between centrality and keystoneness is based on an intuitive understanding of what a keystone species is, the assumptions of structural controllability are explicit and the estimation of a species' importance arises from a mechanistic understanding of the population dynamics between species.
 By accounting for network dynamics (even if in a simple way), structural stability incorporates more ecological realism, especially in the extreme scenario in which the state of a community is only marginally affected by the topology of their interactions.
@@
 
-Here we show that structural controllability can be applied in an ecological setting to gain insight into the stability of a community and the role that species play at modifying the abundance of other species and ultimately the state of the community.
+Here we show that structural controllability can be applied in an ecological setting to gain insight into the stability of a community and the role that species play in modifying the abundance of other species and ultimately the state of the community.
 These characteristics make structural stability an ideal framework to evaluate the effects of invasions and other types of perturbations. 

### 2018-12-12 paper/supp-info.Rmd
Settle on a title

@@
 ---
-title: "Structural controllability of ecological networks"
+title: "Keystoneness, centrality, and the structural controllability of ecological networks"
 subtitle: "Supporting Information"
@@
 
-```{r fig-correlogram, fig.width=fig_sizes()[[2]], fig.height=fig_sizes()[[1]], fig.cap="Mean Spearman correlation coefficients between control metrics (control capcity $\\phi$ and the likelyhood of being a superior node $\\sigma$) and centrality metrics commonly used to estimate a species' 'keystoness' (closeness centrality $l$ , betwenness $w$, eigen centrality $e$, page rank $g$ and degre $k$) in each of the networks.
+```{r fig-correlogram, fig.width=fig_sizes()[[2]], fig.height=fig_sizes()[[1]], fig.cap="Mean Spearman correlation coefficients between control metrics (control capcity $\\phi$ and the likelihood of being a superior node $\\sigma$) and centrality metrics commonly used to estimate a species' 'keystoness' (closeness centrality $l$ , betwenness $w$, eigen centrality $e$, page rank $g$ and degre $k$) in each of the networks.
 Purple and orange tiles indicate a positive correlation or negative correlation respectively."}

### 2018-12-24 paper/reviewers-response.Rmd
further updates to revision, and some minor corrections to the supplementary info

@@
 
+> L9: I think here and throughout much of the text, species should be possessive when followed by a noun ("species role" should be "species' role").
+The possessive is currently used in some instances but is inconsistently applied throughout the ms.
+
+We have checked through the manuscript and corrected this where relevant.
+
+> L25: ".
+every invasive species in our dataset was part of it ." Here it was unclear what "it" refers to (the set of critical species), and the reference to a singular dataset when you have 20 networks in total was a bit confusing to me.
+
+We have made this clearer as follows: "and included every invasive species in our dataset" (\lr{R2-our-dataset})
+
+> L23-26: in these lines, you refer to critical species, but I think the distinction between having high control capacity versus being critical needs to be defined (briefly) earlier (it is stated in L18-19 that you will quantify both control capacity and identify  critical species, but it is not explained how they are distinct).
+
+We now identify the distinction between high control capacity and being critical on lines \lr{R2-define-control-capacity} "It also allows us to quantify a species control capacity-its relative importance-and identify the set of species that, collectively, are critical-have maximum control capacity-in this context."
+
+> L27: unclear what "its" refers  to
+
+We now explicitly state "species' degree" \lr{R2-species-degree}
+
+> L111, 114: "are comprised of" should be "comprised "
+
+Thank you, we have corrected this.
+
+> L234, 235: awkward to refer to species as "they" and "their "
+
+We have changed this to "it" and "its"
+
+> L296: "More details in Supporting Information ."  is a sentence fragment.
+
+We have corrected this on line \lr{R2-sentence-fragment}
+
+> L339, 432: "at" should be "in"
+
+Thank you, this has been corrected.
+
+> L341: "allow" should be "allowed "
+
+Thank you, this has been corrected.
+
+> L343: I am not sure about citing Table 2 for the first time in the Discussion. Might it be more useful to cite this in the Introduction ?
+
+We now introduce table 2 on line \lr{R2-ref-glossary}.
+
+>L355: missing period
+
+Thank you for noticing this, we have inserted the missing period.
+
 # Reviewer comments #1
@@
 
-We are pleased that the reviewer "thoroughly enjoyed the re-written manuscript", and appreciate the identified issues.
-We have addressed all issues in the text and identify these in red.
-We have rewritten the sentence on line 388 to improve clarity.
+We are pleased that the reviewer "thoroughly enjoyed the re-written manuscript", and appreciate the identified issues. We have addressed all issues in the text and identify these in red.
+
+> A few references require editing to journal style (e.g. remove initials for many citations)
+
+>L314. open bracket missing .
+
+Thank you for pointing this out, we have inserted the missing bracket.
+
+> L358. change 'instead' to 'Instead'. L381. remove second comma
+
+We have made both of these changes.
+
+> L388. remove repeated 'other'. I suggest that the authors re-write this sentence to improve clarity .
+
+We have removed the second 'other'.
+We have rewritten the sentence on line \lr{R2-structural-controllability} to improve clarity.
 It now reads as follows: "First, structural controllability emphasizes that the effect a species has on the abundance of other species is not independent of the effects of those other species in their community".
 
-> "L23-26: in these lines, you refer to critical species, but I think the distinction between having high control capacity versus being critical needs to be defined (briefly) earlier (it is stated in L18-19 that you will quantify both control capacity and identify critical species, but it is not explained how they are distinct)."
+> Reference list needs updating, e.g. Ne'eman et al. is not 2009 but 2010.
 
-We now identify the distinction between high control capacity and being critical on lines .............
-"It also allows us to quantify a species control capacity-its relative importance-and identify the set of species that, collectively, are critical-have maximum control capacity-in this context."
+> Fig. S6 header of plot b). correct spelling of 'critical'
+
+> Congratulations on this thought-provoking methodological synthesis.
 
 # Reviewer comments #2
+
+> I think the concepts presented in this manuscript are a useful addition to the literature on management of ecological networks.
+I agree with the authors that it is important that the discussion surrounding what constitutes a "keystone" species should go beyond centrality metrics.
+
+> I found the results and concepts to be generally well presented, particularly graphically, and the authors present a thorough sensitivity analysis to various assumptions.
+The methods are mostly clear but there is no description of how the "likelihood of being a superior node " is calculated.
+
+> I would suggest including clarification on the limitations of using control capacity to summarise species' importance, and examples to help the reader build an intuition regarding the control capacity metric.
+As pointed out, networks that give rise to a species having a high control capacity can be quite distinct to networks that give rise to a species having a high value of particular centrality metrics.
+Providing an example in the Discussion of, for instance, those species that have a control capacity of 1 but a low degree would be very useful.
+
+> Jargon occasionally obfuscates the concepts being introduced and there are places where I thought the language used was vague (esp.
+if terms being used have particular meanings depending on the field you're coming from).
+I would suggest clarifying, or rewording, the following :
+
+> * "desired control trajectory " - does this mean "final state"?
+
+We have attempted to clarify this sentence as follows: Finding out exactly how difficult it is to control a network depends strongly on the particularities of the desired control trajectory (i.e.
+path to the desired final state)  as well as the dynamical relationship between nodes.
+\lr{R2-desired-control-trajectory}
+
+> * "dynamic persistence"  (p17,l364)
+
+> * "dynamic stability " (p17, l370)
+
+> * "ecological objective" (p9) - simply 'objective' ?
+
+We have changed this to simply 'objective', as suggested (\lr{R2-ecol-objective}).
+
+> * "central in their community " (p18, l 405)
+
+> * "inherently different " (p18, l 406). The sentence spanning lines 407-410 is quite confusing  - please clarify.
+
+We rephrased this line as follows: "We found that it is not that invasive plants have some different mechanism for influencing the community compared to their native counterparts" \lr{R2-inherrently-different}.
+
+> * "marginally affected by the topology of their interactions"  (p19, l 430)
+
+We have rephrased this line as: "By accounting for network dynamics (even if in a simple way), structural stability incorporates more ecological realism, especially in the extreme scenario in which the structure of interactions within the community only marginally affects the community's state.
+Both native species and invasive plants tended to attain a high control capacity if they were important to network persistence, were abundant, and depended little on other species." \lr{R2-marginally-affected}.
+
+> * "dominate the state [of their community ]" (p19, l436 & l441)
+
+>* "species' strength " (Discussion)
+
+>Minor typos:
+* Figure S11 caption: "likelyhood" -> likelihood 
+* References : several references use the term "plantPollinator", or "..."
+* Figure S1b is referred to (supp. p4 ) but doesn't exist in the figure.  
+* Page 18 Line 388: "other other" 
+* "driver node density" (supp p12) -> "size of the minimum driver node set"?
 

### 2018-12-24 paper/supp-info.Rmd
further updates to revision, and some minor corrections to the supplementary info

@@
 
-The networks studied had species richness ranging between `r min(net_prop$n_s_t)` and `r max(net_prop$n_s_t)` when considering only the largest component in each network). 
+The networks studied had species richness ranging between `r min(net_prop$n_s_t)` and `r max(net_prop$n_s_t)` (when considering only the largest component in each network). 
 As shown by the network asymmetry *AS* [@bluthgen_specialization_2007], the networks had a low ratio of plants to pollinators overall. 
@@
                caption = "Properties of the analysed plant-pollinator communities.
-Here show the number of species ($n_s$), the number of plants ($n_p$), the number of pollinators ($n_a$), the network connectance ($c$), the network asymmetry ($AS$), and the network nestedness (NODF index).
+Here show the number of species ($n_s$), the number of plants ($n_p$), the number of pollinators ($n_a$), the network connectance ($C$), the network asymmetry ($AS$), and the network nestedness (NODF index).
 All properties correspond to the network's largest component.
@@
 
-The algorithm proposed by @zhang_input_2016 enable us to find all minimum driver node sets without calculating all possible maximum matchings. 
+The algorithm proposed by @zhang_input_2016 enables us to find all minimum driver node sets without calculating all possible maximum matchings. 
 The algorithm is based on the construction of the input graph of the directed network. 
@@
 First,  if $x_i$ belongs to the minimum driver node set and has no adjacent nodes, then it cannot be replaced and will be part of every possible control configuration. 
-Second, if $x_i$ does not belong to the minimum driver node set and is not adjacent to any possible input node, then it does not part of the minimum driver node set under any control configuration. 
+Second, if $x_i$ does not belong to the minimum driver node set and is not adjacent to any possible input node, then it does not become part of the minimum driver node set under any control configuration.
 Finally, if a node $x_i$ belongs to the minimum driver node set and is adjacent to another node $x_j$ in the input graph, then $x_j$ must belong to another minimum driver node to which $x_i$ does not belong, in other words, $x_i$ and $x_j$ are substitutable.
@@
 Meanwhile, the third group has intermediate values of control capacity which can be calculated by computing the number of possible substitutions of a node by its control adjacent nodes. 
-As a rule of thumb, the largest the number of possible substitutions an input node has, the smaller its control capacity.
+As a rule of thumb, the larger the number of possible substitutions an input node has, the smaller its control capacity.
 
@@
 The choice of weighting can also have an impact on at the species level.
-Therefore we calculated $\phi$ and $\sigma$ and calculated it's correlation among all three weighting schemes.
+Therefore we calculated $\phi$ and $\sigma$ and calculated its correlation among all three weighting schemes.
 Although visitation and efficiency (pollen deposition) produce moderately different results, we found a very strong agreement between the order produced by visitation and importance which is arguably a more accurate metric of interspecific effects (Table \@ref(tab:tab-assumption-visitation)).
@@
 
-To do so we removed a portion of the visits, for each network, and calculated how three control metrics of the subsampled network compare to those of the full network. 
+To do so, we removed a portion of the visits, for each network, and calculated how three control metrics of the subsampled network compare to those of the full network. 
 Specifically, we calculated the difference between the relative size of the minimum driver node set $n_D$ of the subsampled and the full network, the Spearman correlation between the control capacities $\phi$ and the probability of being a superior node $\sigma$ that were obtained for the empirical network and subsamples of it.
@@
 Overall, the results of the sensitivity analysis indicate that our approach is likely to still be useful in the absence of complete sampling. 
-Specifically, as the proportion of sampled interaction decreased, the variability of $n_D$ increased but was overall similar to that obtained when using all available interactions (Figure \@ref(fig:fig-assumption-sampling-nd)).
+Specifically, as the proportion of sampled interactions decreased, the variability of $n_D$ increased but was overall similar to that obtained when using all available interactions (Figure \@ref(fig:fig-assumption-sampling-nd)).
 Similarly, the correlation between $\phi$ and $\sigma$ of empirical and subsampled networks was high even for extreme levels of undersampling (Figure \@ref(fig:fig-assumption-sampling-cor)). 
@@
                caption = "Model selection table based on the Akaike Information Criterion for small samples for candidate models of size of the minimum driver node set ($n_D$) in the empirical networks.
-There was no evidence for any of the evaluated predictors: the invasion status (inv), the network connectance (c), the network nestedness (NODF) the number of species ($n_S$) the network asymmetry ($AS_s$) or the interaction strength asymmetry ($AS_s$).
+There was no evidence for any of the evaluated predictors: the invasion status (inv), the network connectance ($C$), the network nestedness (NODF) the number of species ($n_S$) the network asymmetry ($AS_s$) or the interaction strength asymmetry ($AS_s$).
 Only candidate models with a weight $>0.01$ are shown.") %>%

### 2019-01-06 paper/manuscript.Rmd

@@
 2. Here we introduce structural controllability, an approach that allows us to quantify the extent to which network topology can be harnessed to achieve a desired state. 
-It also allows us to quantify a species' control capacity—its relative importance—and identify the set of species that, collectively, are critical—have maximum control capacity—in this context. 
+\R{R2-define-control-capacity} It also allows us to quantify a species' control capacity—its relative importance—and identify the set of species that, collectively, are critical—have maximum control capacity—in this context.
 We illustrate the application of structural controllability with ten pairs of uninvaded and invaded plant-pollinator communities.
@@
 While central species were also likely to have a large control capacity, centrality fails to identify species that, despite being less connected, were critical in their communities. 
-Interestingly, this set of critical species was mostly composed of plants and included every invasive species in our dataset. 
+\R{R2-our-dataset} Interestingly, this set of critical species was mostly composed of plants and included every invasive species in our dataset. 
 We also found that species with high control capacity, and in particular critical species, contribute the most to the stable coexistence of their community.
-This result was true, even when controlling for its degree, abundance/interaction strength, and the relative dependence of their partners.
+\R{R2-species-degree} This result was true, even when controlling for the species' degree, abundance/interaction strength, and the relative dependence of their partners.
 
@@
 Therefore, we first ask whether there are differences between the controllability of invaded and uninvaded networks. 
-We then expand existing methods from control theory to effectively link the *controllability* (Table \@ref(tab:tab-glossary)) of a network with the role of its constituent species.
+\R{R2-ref-glossary} We then expand existing methods from control theory to effectively link the *controllability* (Table \@ref(tab:tab-glossary)) of a network with the role of its constituent species.
 We ask—from a control-theoretic perspective—whether there are key differences between species in the role they play at driving the state of the community and explore the ecological factors related to these differences.
@@
 
-Our first ecological objective is to investigate whether the controllability of a community is associated with invasion status or not. 
-Finding out exactly how difficult it is to control a network depends strongly on the particularities of the desired control trajectory as well as the dynamical relationship between nodes. 
+\R{R2-ecol-objective} Our first objective is to investigate whether the controllability of a community is associated with invasion status or not. 
+\R{R2-desired-control-trajectory} Finding out exactly how difficult it is to control a network depends strongly on the particularities of the desired control trajectory (i.e.
+path to the desired final state)  as well as the dynamical relationship between nodes.
 However, we are interested in understanding the controllability of a network in a more general sense, such that it can be applied even when the precise control scenario is known only incompletely. 
@@
 Specifically, we also calculated the controllability (the size of the minimum driver node-set) and the control capacity of networks constructed using pollinator efficiency (which measures the pollen deposition of an interaction) and pollinator importance [which accounts for both pollen deposition and visitation and hence is regarded as a more accurate estimation of the pollination service received by plants; @neeman_framework_2009].
-See Supporting Information Section \@ref(S-visitation-as-proxy) for more details.
+\R{R2-sentence-fragment} See Supporting Information Section \@ref(S-visitation-as-proxy) for more details.
 
@@
 \R{management-implications}Other conceptual differences between structural controllability and centrality metrics provide three key insights into the conservation of ecological networks. 
-First, structural controllability emphasizes that the effect a species has on the abundance of other species is not independent of the effects of those other species in their community. 
+\R{R2-structural-controllability} First, structural controllability emphasizes that the effect a species has on the abundance of other species is not independent of the effects of those other species in their community.
 The rankings provided by centrality metrics and other heuristics fail to account for the collective influence of several species at once. 
@@
 Invasive plants have been previously found to exacerbate the asymmetries in their communities [@aizen_invasive_2008; @bartomeus_contrasting_2008-1; @henriksson_strong_2016] and to be central in their communities [@vila_invasive_2009; @palacio_generalist_2016].
-We found that invasive plants are, however, unlikely to be inherently different from their native counterparts [@emer_species_2016; @stouffer_how_2014]. 
-Invasive plants tended to be important for network persistence, be abundant, and depend little on other species and, as a result, have high control capacity, just like any other mutualist in our data set with those properties.
+\R{R2-inherrently-different} We found that it is not that invasive plants have some different mechanism for influencing the community compared to their native counterparts [@emer_species_2016; @stouffer_how_2014].
+Both native species and invasive plants tended to attain a high control capacity if they were important to network persistence, were abundant, and depended little on other species. 
 Furthermore, our observation that changes in the abundance of invasive plants (and presumably all critical species) are crucial to modify the state of the community agrees with recent evidence showing that ecosystem restoration focused on the eradication of invasive plants can have transformative desirable effects in plant-pollinator communities\R{extra-references-3} [@kaiser-bunbury_ecosystem_2017].
@@
 Furthermore, while the relationship between centrality and keystoneness is based on an intuitive understanding of what a keystone species is, the assumptions of structural controllability are explicit and the estimation of a species' importance arises from a mechanistic understanding of the population dynamics between species.
-By accounting for network dynamics (even if in a simple way), structural stability incorporates more ecological realism, especially in the extreme scenario in which the state of a community is only marginally affected by the topology of their interactions.
+\R{R2-marginally-affected} By accounting for network dynamics (even if in a simple way), structural stability incorporates more ecological realism, especially in the extreme scenario in which the structure of interactions within the community only marginally affects the community's state.
 

### 2019-01-11 paper/manuscript.Rmd
Fix citations
Close #55

@@
 Specifically, we outline the approach using a set of ten pairs of uninvaded and invaded plant-pollinator communities. 
-We use invaded communities because there is strong empirical evidence showing that invasive species play an important role shaping the abundances of other species, something which is particularly true in these ten networks [@lopezaraizamikel_impact_2007; @bartomeus_contrasting_2008-1].
+We use invaded communities because there is strong empirical evidence showing that invasive species play an important role shaping the abundances of other species, something which is particularly true in these ten networks [@lopezaraizamikel_impact_2007; @bartomeus_contrasting_2008].
 This choice thus offers us an opportunity to explicitly contrast our theoretical observations with empirical evidence.
@@
 These communities comprised `r lop[1]`--`r lop[6]` species (mean `r round(lop[4])`), and non-invaded plots were obtained by experimentally removing all the flowers of the invasive species *Impatients grandulifera*.
-The other six pairs were obtained from lower diversity Mediterranean shrublands in Cap de Creus National Park, Spain [@bartomeus_contrasting_2008-1].
+The other six pairs were obtained from lower diversity Mediterranean shrublands in Cap de Creus National Park, Spain [@bartomeus_contrasting_2008].
 These communities comprised `r bar[1]`--`r bar[6]` species (mean `r round(bar[4])`); in contrast to the above, uninvaded communities were obtained from plots that had not yet been colonised by either of the invasive species *Carpobrotus affine acinaciformis* or *Opuntia stricta*.
@@
 The response variable was the relative size of the minimum driver-node set $n_D$ of the twenty empirical networks (ten invaded and ten uninvaded), and we included invasion status as a predictor. 
-As predictors, we also include the network connectance, the network nestedness (NODF), the number of species [since one might naively expect to see a negative relationship between richness and controllability; @menge_indirect_1995], the network asymmetry (an indication of the balance between plant and pollinator diversity), and the interaction strength asymmetry [the asymmetry on the dependences between trophic levels; @bluthgen_specialization_2007].
+As predictors, we also include the network connectance, the network nestedness (NODF), the number of species [since one might naively expect to see a negative relationship between richness and controllability; @menge_indirect_1995], the network asymmetry (an indication of the balance between plant and pollinator diversity), and the interaction strength asymmetry [the asymmetry on the dependences between trophic levels; @bluthgen_specialization_2007]\R{R2-citation-with-name}.
 We compared models using the Akaike Information Criterion for small sample sizes (AICc).
@@
 We found that invasive plants were always critical for network control and as such our results were in line with our expectations. 
-Invasive plants have been previously found to exacerbate the asymmetries in their communities [@aizen_invasive_2008; @bartomeus_contrasting_2008-1; @henriksson_strong_2016] and to be central in their communities [@vila_invasive_2009; @palacio_generalist_2016].
+Invasive plants have been previously found to exacerbate the asymmetries in their communities [@aizen_invasive_2008; @bartomeus_contrasting_2008; @henriksson_strong_2016] and to be central in their communities [@vila_invasive_2009; @palacio_generalist_2016].
 \R{R2-inherrently-different} We found that it is not that invasive plants have some different mechanism for influencing the community compared to their native counterparts [@emer_species_2016; @stouffer_how_2014].
@@
 
-All data used in this manuscript have already been published by @lopezaraizamikel_impact_2007, @bartomeus_contrasting_2008-1, and @ballantyne_constructing_2015 The reader should refer to the original sources to access the data.
+All data used in this manuscript have already been published by @lopezaraizamikel_impact_2007, @bartomeus_contrasting_2008, and @ballantyne_constructing_2015 The reader should refer to the original sources to access the data.
 

### 2019-01-11 paper/reviewers-response.Rmd
Fix citations
Close #55
Moving glossary to the intro

@@
 
-Thank you, we have corrected this.
+> "*L343*: I am not sure about citing Table 2 for the first time in the Discussion. Might it be more useful to cite this in the Introduction?""
 
-> L234, 235: awkward to refer to species as "they" and "their "
+We now introduce the glossary at the end of the introdyction on \lr{M-R2-ref-glossary}.
 
@@
 Thank you, this has been corrected.
-
-> L343: I am not sure about citing Table 2 for the first time in the Discussion. Might it be more useful to cite this in the Introduction ?
-
-We now introduce table 2 on line \lr{R2-ref-glossary}.
 
@@
 > A few references require editing to journal style (e.g. remove initials for many citations)
+
+We have corrected all of them except on \lr{R2-citation-with-name} where the initial is used to distinguis between two authors with the same last name
 

### 2019-01-11 paper/reviewers-response.Rmd
Comments to associate editor done
Close #56

@@
 
-# Editor comments
-
 # Associate Editor's comments:
@@
 
-> L9: I think here and throughout much of the text, species should be possessive when followed by a noun ("species role" should be "species' role").
-The possessive is currently used in some instances but is inconsistently applied throughout the ms.
+> "*L9*: I think here and throughout much of the text, species should be possessive when followed by a noun ("species role" should be "species' role").
+The possessive is currently used in some instances but is inconsistently applied throughout the ms."
 
+*Accepted and changed*.
 We have checked through the manuscript and corrected this where relevant.
+Besides *specie's role*, we also changes instances of *species' contribution*, *species' degree*, *species' control capacity*, among others.
 
-> L25: ".
-every invasive species in our dataset was part of it ." Here it was unclear what "it" refers to (the set of critical species), and the reference to a singular dataset when you have 20 networks in total was a bit confusing to me.
+> "*L25*: 'every invasive species in our dataset was part of it' Here it was unclear what 'it' refers to (the set of critical species), and the reference to a singular dataset when you have 20 networks in total was a bit confusing to me.
 
-We have made this clearer as follows: "and included every invasive species in our dataset" (\lr{R2-our-dataset})
+*Accepted and changed*. We have made this clearer as follows: "and included every invasive species in our dataset" (\lr{M-R2-our-dataset})
 
-> L23-26: in these lines, you refer to critical species, but I think the distinction between having high control capacity versus being critical needs to be defined (briefly) earlier (it is stated in L18-19 that you will quantify both control capacity and identify  critical species, but it is not explained how they are distinct).
+> "*L23-26*: in these lines, you refer to critical species, but I think the distinction between having high control capacity versus being critical needs to be defined (briefly) earlier (it is stated in *L18-19* that you will quantify both control capacity and identify critical species, but it is not explained how they are distinct)."
 
-We now identify the distinction between high control capacity and being critical on lines \lr{R2-define-control-capacity} "It also allows us to quantify a species control capacity-its relative importance-and identify the set of species that, collectively, are critical-have maximum control capacity-in this context."
+*Accepted and changed*.
+We now identify the distinction between high control capacity and being critical on \lr{M-R2-define-control-capacity}.
+The text now reads "It also allows us to quantify a species control capacity-its relative importance-and identify the set of species that, collectively, are critical in this context because they have largest possible control capacity."
 
-> L27: unclear what "its" refers  to
+> "*L27*: unclear what 'its' refers  to."
 
-We now explicitly state "species' degree" \lr{R2-species-degree}
+*Accepted and changed*. We now explicitly state "species' degree" in  \lr{M-R2-species-degree}
 
-> L111, 114: "are comprised of" should be "comprised "
+> "*L234, 235*: awkward to refer to species as 'they' and 'their'"
+
+*Accepted and changed*. We have changed this to "it" and "its"
+
+> "*L296*: 'More details in Supporting Information.' is a sentence fragment."
+
+*Accepted and changed*. We have corrected this on \lr{M-R2-sentence-fragment}. The text now reads "See Supporting Information Section \@ref(S-visitation-as-proxy) for more details".
 
@@
 
-We have changed this to "it" and "its"
+> "*L111, 114*: 'are comprised of' should be 'comprised'. *L339, 432*: 'at' should be 'in'. *L341*: 'allow' should be 'allowed'. *L355*: missing period."
 
-> L296: "More details in Supporting Information ."  is a sentence fragment.
-
-We have corrected this on line \lr{R2-sentence-fragment}
-
-> L339, 432: "at" should be "in"
-
-Thank you, this has been corrected.
-
-> L341: "allow" should be "allowed "
-
-Thank you, this has been corrected.
-
->L355: missing period
-
-Thank you for noticing this, we have inserted the missing period.
+*Accepted and changed*. Thank you for pointing out these mistakes, we corrected all of them.
 

### 2019-01-11 paper/manuscript.Rmd
Moving glossary to the intro
Comments to associate editor done
Close #56

@@
 2. Here we introduce structural controllability, an approach that allows us to quantify the extent to which network topology can be harnessed to achieve a desired state. 
-\R{R2-define-control-capacity} It also allows us to quantify a species' control capacity—its relative importance—and identify the set of species that, collectively, are critical—have maximum control capacity—in this context.
+\R{R2-define-control-capacity} It also allows us to quantify a species' control capacity—its relative importance—and identify the set of species that, collectively, are critical in this context because they have largest possible control capacity.
 We illustrate the application of structural controllability with ten pairs of uninvaded and invaded plant-pollinator communities.
@@
 Finally, we compare the proposed approach to current methods based on species' centrality and show how these methods are indeed valuable but ultimately paint a limited picture in regard to the "keystoneness" of a species.
+
+```{r tab-glossary}
+defs <- list(
+  "network control" = "A network is said to be controllable if it is possible to steer it from an initial to an arbitrary final state within finite time.",
+  "controllability" = "The intrinsic difficulty of controlling an ecological community.
+It is measured by the relative size of the minimum driver-node set, $n_D$.
+It also indicates the extent to which network structure can be harnessed for network control.",
+  "minimum driver-node set" = "One of the sets of species whose abundances need to be directly managed in order to achieve full control of the community.
+The minimum driver-node sets can be obtained by finding all maximum matchings in a network.",
+  "maximum matching" = "A matching is a set of links that do not share any common start or end nodes; the largest possible matching is called a maximum matching.",
+  "control configuration" = "One of the species combinations with which is possible to achieve network control. Optimal control configurations are given by the minimum driver-node sets.", 
+  "control capacity" = "The relative frequency \\(\\phi\\) which with a species is part of the optimal control configurations of a network.", 
+  "critical species" = "A species with a maximal control capacity \\(\\phi=1\\)",
+  "superior node" = "A species is a superior node if it can internally affect the abundance of other species in the network.
+Superior nodes make up the chains that propagate the control signals through the network.")
+
+dplyr::data_frame(rows = c(rbind(names(defs), unlist(defs))), dummy2 = "") %>%
+  dplyr::mutate(rows = kableExtra::cell_spec(rows, "latex", bold = T:F, escape = F)) %>%
+  knitr::kable("latex", 
+               booktabs = T, 
+               col.names = NULL,
+               caption = "Glossary", 
+               escape = F, 
+               linesep = c('', '\\addlinespace')) %>% 
+  kableExtra::kable_styling(font_size = 8) %>%
+  kableExtra::add_indent(seq(2, length(defs)*2, by = 2)) %>%
+  kableExtra::column_spec(1, width = paste0(fig_sizes()[[1]], "in"))
+```
 
@@
 
-```{r tab-glossary}
-defs <- list(
-  "network control" = "A network is said to be controllable if it is possible to steer it from an initial to an arbitrary final state within finite time.",
-  "controllability" = "The intrinsic difficulty of controlling an ecological community.
-It is measured by the relative size of the minimum driver-node set, $n_D$.
-It also indicates the extent to which network structure can be harnessed for network control.",
-  "minimum driver-node set" = "One of the sets of species whose abundances need to be directly managed in order to achieve full control of the community.
-The minimum driver-node sets can be obtained by finding all maximum matchings in a network.",
-  "maximum matching" = "A matching is a set of links that do not share any common start or end nodes; the largest possible matching is called a maximum matching.",
-  "control configuration" = "One of the species combinations with which is possible to achieve network control. Optimal control configurations are given by the minimum driver-node sets.", 
-  "control capacity" = "The relative frequency \\(\\phi\\) which with a species is part of the optimal control configurations of a network.", 
-  "critical species" = "A species with a maximal control capacity \\(\\phi=1\\)",
-  "superior node" = "A species is a superior node if it can internally affect the abundance of other species in the network.
-Superior nodes make up the chains that propagate the control signals through the network.")
-
-dplyr::data_frame(rows = c(rbind(names(defs), unlist(defs))), dummy2 = "") %>%
-  dplyr::mutate(rows = kableExtra::cell_spec(rows, "latex", bold = T:F, escape = F)) %>%
-  knitr::kable("latex", 
-               booktabs = T, 
-               col.names = NULL,
-               caption = "Glossary", 
-               escape = F, 
-               linesep = c('', '\\addlinespace')) %>% 
-  kableExtra::kable_styling(font_size = 8) %>%
-  kableExtra::add_indent(seq(2, length(defs)*2, by = 2)) %>%
-  kableExtra::column_spec(1, width = paste0(fig_sizes()[[1]], "in"))
-```
-
 Our results indicate that fully controlling ecological networks might currently be out of reach for all but the smallest communities [@motter_networkcontrology_2015]. 

### 2019-01-12 paper/reviewers-response.Rmd
Comments reviewer #2
Close #57

@@
 
-> "I'd like to commend the authors to this revised version of the manuscript on "Keystoneness, centrality, and the structural controllability of ecological networks".
+> "I'd like to commend the authors to this revised version of the manuscript on 'Keystoneness, centrality, and the structural controllability of ecological networks'.
 I thoroughly enjoyed the re-written manuscript, which is now considerably more accessible and clearly targets the community of network ecologists, while not ignoring the importance of the applied relevance of the findings.
@@
 I guess the language is in parts on the casual side, yet without compromising the preciseness or clarity of the text.
-I noticed a few typos or style errors that the authors may want to address"
+I noticed a few typos or style errors that the authors may want to address.
+Congratulations on this thought-provoking methodological synthesis."
 
-We are pleased that the reviewer "thoroughly enjoyed the re-written manuscript", and appreciate the identified issues. We have addressed all issues in the text and identify these in red.
+We are pleased that the reviewer enjoyed the re-written manuscript. We did too!. We also grateful for the typos and style errors identifyed, we have striven to correct them all.
 
-> A few references require editing to journal style (e.g. remove initials for many citations)
+> "A few references require editing to journal style (e.g. remove initials for many citations)"
 
-We have corrected all of them except on \lr{R2-citation-with-name} where the initial is used to distinguis between two authors with the same last name
+*Accepted and changed*.
+We have corrected all citations.
+One of them, however, (\lr{R2-citation-with-name}) still shows an author's first name initial, as it is necessary to distinguish two authors with the same last name.
 
->L314. open bracket missing .
+> "*L388*: remove repeated 'other'. I suggest that the authors re-write this sentence to improve clarity."
 
-Thank you for pointing this out, we have inserted the missing bracket.
-
-> L358. change 'instead' to 'Instead'. L381. remove second comma
-
-We have made both of these changes.
-
-> L388. remove repeated 'other'. I suggest that the authors re-write this sentence to improve clarity .
-
+*Accepted and changed*.
 We have removed the second 'other'.
-We have rewritten the sentence on line \lr{R2-structural-controllability} to improve clarity.
+As suggested, we have rewritten the sentence to improve clarity (\lr{M-R2-structural-controllability}).
 It now reads as follows: "First, structural controllability emphasizes that the effect a species has on the abundance of other species is not independent of the effects of those other species in their community".
 
-> Reference list needs updating, e.g. Ne'eman et al. is not 2009 but 2010.
+> "Reference list needs updating, e.g. Ne'eman et al. is not 2009 but 2010."
 
-> Fig. S6 header of plot b). correct spelling of 'critical'
+*Accepted and changed*. Thanks for pointing this error out. We've corrected the reference.
 
-> Congratulations on this thought-provoking methodological synthesis.
+> "*L314*: open bracket missing. *L358*: change 'instead' to 'Instead'. *L381*: remove second comma. *Fig. S6* header of plot b). correct spelling of 'critical'."
+
+*Accepted and changed*. Thank you for pointing this out, made all these changes as indicated.
 

### 2019-01-13 paper/reviewers-response.Rmd
Clarify that we use one lumped model in the species level models

@@
 
->* "species' strength " (Discussion)
+*Accepted and changed*: We are sorry for the confusion.
+In the species level GLM, we lumped all species from different networks together.
+We have modified the text in \lr{M-R2-one-lumped-model-a} and \lr{M-R2-one-lumped-model-b} to make this clearer.
+We actually did test for random effects in the model.
+We tested random effects that allowed for a random intercept for the network (but also its site, and the study it comes from).
+In all cases, the variance among groups was zero.
+This means that likely there are no differences on the distribution of control capacity between networks (or site and study) and therefore it was not necessary to include random effects in the models presented in the paper.
+We have corrected this omission and describe the random effects in \lr{M-R2-random-effects}.
 

### 2019-01-13 paper/manuscript.Rmd
Clarify that we use one lumped model in the species level models

@@
 
-We then examined how species-level properties were related to control capacity using a set of generalised linear models with binomial error structure.
+\R{R2-one-lumped-model-a}We then examined how species-level properties were related to control capacity using a set of candidate generalised linear models with binomial error structure. 
 These models included five predictor variables that mirror the network-level predictors. 
@@
 To facilitate comparison between predictors, degree and visitation strength were log-transformed and all four continuous variables were scaled to have a mean of zero and a standard deviation of one.
+\R{R2-one-lumped-model-b}In these models, species from all networks were lumped together. 
 To identify the models that were best supported by the data, we first determined the most parsimonious random structure using the AICc. 

### 2019-01-13 paper/reviewers-response.Rmd
Clarify usage of species strength in the discussion

@@
 
-> Jargon occasionally obfuscates the concepts being introduced and there are places where I thought the language used was vague (esp.
-if terms being used have particular meanings depending on the field you're coming from).
-I would suggest clarifying, or rewording, the following :
+> "*Discussion*: 'species' strength'
+
+*Accepted and changed*: In the Methods section we deine species' strength as the sum of a species' visits (\lr{M-R2-species-strength-a}).
+For brevity, we did not define it again in the Disussion, but now we have improved the text and briefly describe it when we mention it there too.
+The text now reads "When controlling for a species' visitation strength (the sum of a species' visits), which is indirectly a proxy of its abundance..." (\lr{M-R2-species-strength-b}).
 

### 2019-01-13 paper/manuscript.Rmd
Clarify usage of species strength in the discussion

@@
 First, the species' contribution to nestedness, which has been proposed as a key feature that promotes stability and robustness in mutualistic networks [@saavedra_strong_2011]. 
-Second, the species' strength (the sum of a species' visits), which quantifies the strength of a species' associations and is indirectly related to its abundance [@poisot_comparative_2012]. 
+Second,\R{R2-species-strength-a} the species' strength (the sum of a species' visits), which quantifies the strength of a species' associations and is indirectly related to its abundance [@poisot_comparative_2012].
 Third, the direction of asymmetry which quantifies the net balance in dependencies; that is, it indicates if a species affects other species more than what they affect it or not [@vazquez_species_2007].
@@
 
-When controlling for a species' strength, which is indirectly a proxy of its abundance, and the net balance of its dependencies, we found that control capacity could not be easily predicted by species' degree or other metrics of centrality.
+When controlling for a \R{R2-species-strength-b}species' visitation strength (the sum of a species' visits), which is indirectly a proxy of its abundance, and the net balance of its dependencies, we found that control capacity could not be easily predicted by species' degree or other metrics of centrality.
 For instance, some species with a low degree achieved the maximum control capacity and were critical for control in their communities. 

### 2019-01-13 paper/reviewers-response.Rmd
Include explanation of random effects in the methods

@@
 
-> * "dominate the state [of their community ]" (p19, l436 & l441)
+> "In the species level glm, it was not entirely clear if models were fit to each network individually or if all species were lumped together (the former is what I think was done based on my reading of the text).
+Regardless I wonder if it would change the results if a mixed effects model was fit to lumped data, using network as a random effect."
 

### 2019-01-13 paper/reviewers-response.Rmd
Make it explicit that we generated all possible candidate models

@@
 
->Minor typos:
-* Figure S11 caption: "likelyhood" -> likelihood 
-* References : several references use the term "plantPollinator", or "..."
-* Figure S1b is referred to (supp. p4 ) but doesn't exist in the figure.  
-* Page 18 Line 388: "other other" 
-* "driver node density" (supp p12) -> "size of the minimum driver node set"?
+> "How were the model sets derived? Were all possible sub-models compared or was a step-wise approach used?"
+
+*Accepted and changed*: We actually compared all possible candidate models. We have edited the manuscript on \lr{M-R2-all-candidates} to include this information.
 

### 2019-01-13 paper/manuscript.Rmd
Include explanation of random effects in the methods
Make it explicit that we generated all possible candidate models

@@
 \R{R2-one-lumped-model-b}In these models, species from all networks were lumped together. 
+\R{R2-random-effects}We initially included random effects to account for possible variation across communities, but we found that the variance explained by these random effects was zero, and therefore random effects were not included in further analyses.
+\R{R2-all-candidates}We then generated all possible candidate models.
 To identify the models that were best supported by the data, we first determined the most parsimonious random structure using the AICc. 

### 2019-01-13 paper/manuscript.Rmd
Update neeman reference (it said it was 2009 but in reality it is 2010)

@@
 First, we tested that visitation is an appropriate proxy to infer interspecific effects by comparing the results obtained using visitation to two alternative metrics in a separate dataset that lacked invasive species [@ballantyne_constructing_2015].
-Specifically, we also calculated the controllability (the size of the minimum driver node-set) and the control capacity of networks constructed using pollinator efficiency (which measures the pollen deposition of an interaction) and pollinator importance [which accounts for both pollen deposition and visitation and hence is regarded as a more accurate estimation of the pollination service received by plants; @neeman_framework_2009].
+Specifically, we also calculated the controllability (the size of the minimum driver node-set) and the control capacity of networks constructed using pollinator efficiency (which measures the pollen deposition of an interaction) and pollinator importance [which accounts for both pollen deposition and visitation and hence is regarded as a more accurate estimation of the pollination service received by plants; @neeman_framework_2010].
 \R{R2-sentence-fragment} See Supporting Information Section \@ref(S-visitation-as-proxy) for more details.
@@
 
-\R{testing-assumptions-results-line} We found that using visitation as a proxy for the strength of species' interactions leads to similar results than those obtained using pollinator importance [regarded as an accurate measure of the pollination service to plants; Supporting Information Section \@ref(S-visitation-as-proxy); @neeman_framework_2009].
+\R{testing-assumptions-results-line} We found that using visitation as a proxy for the strength of species' interactions leads to similar results than those obtained using pollinator importance [regarded as an accurate measure of the pollination service to plants; Supporting Information Section \@ref(S-visitation-as-proxy); @neeman_framework_2010].
 Importantly, we also found that structural stability is robust to incomplete sampling of interactions. 

### 2019-01-13 paper/supp-info.Rmd
Update neeman reference (it said it was 2009 but in reality it is 2010)

@@
 To do this, we used data collected by @ballantyne_constructing_2015 from a low diversity pollination community at a dry lowland heathland in Dorset, UK  (50° 43.7'N 2° 07.2'W). 
-First, deposition networks were quantified using the mean single visit deposition---the number of conspecific pollen grains effectively deposited on a virgin stigma during a single visit by a particular animal [@neeman_framework_2009; @king_why_2013; @ballantyne_constructing_2015].
+First, deposition networks were quantified using the mean single visit deposition---the number of conspecific pollen grains effectively deposited on a virgin stigma during a single visit by a particular animal [@neeman_framework_2010; @king_why_2013; @ballantyne_constructing_2015].
 Second, visitation networks were constructed by counting the visits to flowers during Single Visit Depositions. 

### 2019-01-13 paper/reviewers-response.Rmd
Better saying what we mean by invasive species being central
"central in their communities"

@@
 
-> * "central in their community " (p18, l 405)
+*Accepted and changed*: We have corrected the refeerence that included 'plantPollinator' in the title.
+We have left the references that include an ellipsis in the author list as they are, as the Journal of Ecology Author Guidelines indicate that this is the preffered format when the reference has more than seven authors.
 

### 2019-01-13 paper/manuscript.Rmd
Better saying what we mean by invasive species being central
"central in their communities"

@@
 We found that invasive plants were always critical for network control and as such our results were in line with our expectations. 
-Invasive plants have been previously found to exacerbate the asymmetries in their communities [@aizen_invasive_2008; @bartomeus_contrasting_2008; @henriksson_strong_2016] and to be central in their communities [@vila_invasive_2009; @palacio_generalist_2016].
+Invasive plants have been previously found to exacerbate the asymmetries in their communities [@aizen_invasive_2008; @bartomeus_contrasting_2008; @henriksson_strong_2016] \R{R2-central-in-their-communities}and to attain high centrality in their communities [@vila_invasive_2009; @palacio_generalist_2016].
 \R{R2-inherrently-different} We found that it is not that invasive plants have some different mechanism for influencing the community compared to their native counterparts [@emer_species_2016; @stouffer_how_2014].

### 2019-01-13 paper/reviewers-response.Rmd
Fix reference with typo in the title
Specifiying what we mean by dynamic stability in the discussion

@@
 
+> "*L1370*: 'dynamic stability'"
+
+*Accepted and changed*: Contrastingly, in this case the word dynanamic distinguishes a particular facet of stability.
+We mean the ability of the system to return to an equilibrium state after a perturbation.
+We now include this definition on \lr{M-R2-dynamic-stability} to make the concept clearer.
+
 > I think the concepts presented in this manuscript are a useful addition to the literature on management of ecological networks.
@@
 
-We have changed this to simply 'objective', as suggested (\lr{R2-ecol-objective}).
+> "*References*: several references use the term 'plantPollinator', or '...'"
 

### 2019-01-13 paper/manuscript.Rmd
Specifiying what we mean by dynamic stability in the discussion

@@
 Previous studies indicate that nestedness promotes species coexistence and confers robustness to extinction [@bastolla_architecture_2009; @memmott_tolerance_2004] even at the expense of the dynamic stability of the mutualistic community [@saavedra_nested_2016].
-These observations are in agreement with our results, as we would expect the dynamic stability of a community to be correlated to the difficulty to control it. 
+These observations are in agreement with our results, as we would expect the dynamic stability \R{R2-dynamic-stability}(the ability to return to equilibrium after a perturbation in species abundances) of a community to be correlated to the difficulty to control it.
 Second, species' control capacity was strongly correlated to their contribution to nestedness and critical species had the largest impact to the stable coexistence of species in their communities. 

### 2019-01-13 paper/manuscript.Rmd
Replacing "dynamic persistence" to "persistence" in the manuscript

@@
 
-Accordingly, our results suggest that structural controllability is closely related to the dynamic persistence of an ecological community based on two lines of evidence. 
+\R{R2-dynamic-persistence}Accordingly, our results suggest that structural controllability is closely related to the persistence of an ecological community based on two lines of evidence. 
 First, we found a comparatively small but thought-provoking negative relationship between the controllability of a network and its nestedness. 

### 2019-01-13 paper/reviewers-response.Rmd
Replacing "dynamic persistence" to "persistence" in the manuscript
Removing reference to Figure S1b in supp info. It is Fig S1 (center)

@@
 
+> "*L1364*: 'dynamic persistence'"
+
+*Accepted and changed*: Thank you.
+To avoid confussion we have removed the word 'dynamic' and now the sentence reads "...our results suggest that structural controllability is closely related to the persistence..." (\lr{M-R2-dynamic-persistence}).
+It conserves its meaning without loosing much precision.
+
 > "*L1370*: 'dynamic stability'"
@@
 
-> * "dynamic stability " (p17, l370)
+> "*Figure S1b* is referred to (supp. p4 ) but doesn't exist in the figure"
 
-> * "ecological objective" (p9) - simply 'objective' ?
+*Accepted and changed*: Thanks for noticing this issue. We now refer to the figure as "Figure S1 (center panel)".
 

### 2019-01-13 paper/supp-info.Rmd
Removing reference to Figure S1b in supp info. It is Fig S1 (center)

@@
 To do that, we need to calculate all possible maximum matchings. 
-To do this, we again start from the alternative bipartite representation in Figure \@ref(fig:fig-maximum-matching-procedure)b and assign an identity to each of the links in the network.
+To do this, we again start from the alternative bipartite representation in Figure \@ref(fig:fig-maximum-matching-procedure) (center panel) and assign an identity to each of the links in the network.
 We will call this bipartite representation *P*. 

### 2019-01-13 paper/supp-info.Rmd
Indicating what we mean by probability of being a superior node
In the supplementary materials

@@
 However, reciprocal links are not a rare occurrence as `r sum(recipr$prop_bid != 0)` out of `r nrow(recipr)` empirical networks had at least one. 
-To calculate our controllability metrics at both the network (the relative size of the minimum driver node set, $n_D$) and species level (control capacity, $\phi$, and the likelihood of being a superior node, $\sigma$) we first need to generate all possible versions of the of the network that include only non-reciprocal links (Figure \@ref(fig:fig-bidirectional)).
+To calculate our controllability metrics at both the network (the relative size of the minimum driver node set, $n_D$) and species level (control capacity, $\phi$, and wether it is a superior node, $\sigma$) we first need to generate all possible versions of the of the network that include only non-reciprocal links (Figure \@ref(fig:fig-bidirectional)).
 
@@
 As such, we average the three metrics ($n_D$, $\phi$, and $\sigma$) across all the networks without reciprocal links without weighting by the number of possible control configurations. 
+It is important to note that a species that is found to be a superior node under a particular control configuration, will be so in all possible control configurations for the particular non-reciprocal network.
+We, therefore denote the average of $\sigma$ across all non-reciprocal versions as the probability of the species being a superior node in its community.
 

### 2019-01-13 paper/reviewers-response.Rmd
Indicating what we mean by probability of being a superior node
In the supplementary materials

@@
 # Reviewer comments #2
+
+> "The methods are mostly clear but there is no description of how the 'likelihood of being a superior node' is calculated."
+
+*Accepted and changed*.
+Thanks for pointing this out.
+We have modified the sentence mentioning 'the likelihood of being a superior node' in the first paragraph of the secition \@ref(S-reciprocal-links) to "...and wether it is a superior node..." to avoid confusion.
+Then we define the 'probability of being a superior node' at the end of the section: "It is important to note that a species that is found to be a superior node under a particular control configuration, will be so in all possible control configurations for the particular non-reciprocal network.
+We, therefore denote the average of $\sigma$ across all non-reciprocal versions as the probability of the species being a superior node in its community".
 

### 2019-01-13 paper/supp-info.Rmd
Indicating what we mean by probability of being a superior node
In the supplementary materials

@@
 As such, we average the three metrics ($n_D$, $\phi$, and $\sigma$) across all the networks without reciprocal links without weighting by the number of possible control configurations.
-It is important to note that a species that is found to be a superior node under a particular control configuration, will be so in all possible control configurations for the particular non-reciprocal network.
-We, therefore denote the average of $\sigma$ across all non-reciprocal versions as the probability of the species being a superior node in its community.
 

### 2019-01-13 paper/reviewers-response.Rmd
Removing reference to driver node density

@@
 
-We have attempted to clarify this sentence as follows: Finding out exactly how difficult it is to control a network depends strongly on the particularities of the desired control trajectory (i.e.
-path to the desired final state)  as well as the dynamical relationship between nodes.
-\lr{R2-desired-control-trajectory}
+> "'driver node density' (supp p12) -> 'size of the minimum driver node set'?"
 

### 2019-01-13 paper/supp-info.Rmd
Removing reference to driver node density

--- 2019-01-13 paper/supp-info.Rmd
@@
 
-At a network scale the driver-node density $n_D$ was consistent among the three weighting schemes (`r round(bal_nd$eff, 2)` for deposition, `r round(bal_nd$vis, 2)` for the visitation, and `r round(bal_nd$imp, 2)` for the pollinator-importance network, respectively).
+At a network scale the size of the minimum driver node set $n_D$ was consistent among the three weighting schemes (`r round(bal_nd$eff, 2)` for deposition, `r round(bal_nd$vis, 2)` for the visitation, and `r round(bal_nd$imp, 2)` for the pollinator-importance network, respectively).
 The choice of weighting can also have an impact on at the species level.

### 2019-01-13 paper/supp-info.Rmd
Supp info table heading said variables had no effect controllability

@@
                caption = "Model selection table based on the Akaike Information Criterion for small samples for candidate models of size of the minimum driver node set ($n_D$) in the empirical networks.
-There was no evidence for any of the evaluated predictors: the invasion status (inv), the network connectance ($C$), the network nestedness (NODF) the number of species ($n_S$) the network asymmetry ($AS_s$) or the interaction strength asymmetry ($AS_s$).
+The evaluated variables are: the invasion status (inv), the network connectance ($C$), the network nestedness (NODF) the number of species ($n_S$) the network asymmetry ($AS_s$) or the interaction strength asymmetry ($AS_s$).
 Only candidate models with a weight $>0.01$ are shown.") %>%

### 2019-01-13 paper/reviewers-response.Rmd
Remove reviewers response first round of reviews

@@
 
--------------------------------------------------------
-
-# Previous response:
-
-> "I agree with the AE and reviewers that this is an interesting and potentially important manuscript.
-I support the AE's decision to reject but invite resubmission for all the reasons mentioned.
-I encourage resubmission if you feel that you can better bring out the conceptual importance of their work for plant ecologists.
-If you wish to strengthen the applied focus with specific conservation recommendations then you may wish to submit to Journal of Applied Ecology.
-Reviewer 1 offers suggestions for both approaches.
-I hope that you choose the former."
-
-Thanks to the Senior Editor, David Gibson, for his comments and his willingness to allow resubmission. 
-After lengthy consideration of the two recommended alternatives, we have chosen to focus on the conceptual importance of our work in line with the editor's stated preference. 
-To do this effectively, we ultimately ended up rewriting both the manuscript and the supplementary materials almost completely.
-We think the extra effort was worth it as we feel the current version does a much better job at explaining the utility and insights generated by the proposed approach.
-
-#  Associate Editor comments
-
-> "Both reviewers see potential value in the application of control theory to species interaction networks and found the work to be of interest.
-I agree that the method and its application to plant-pollinator networks are interesting, particularly the findings that contrast invaded vs uninvaded networks and use novel metrics to describe the influence of invasive species in networks.
-Both reviewers also note, however, that the current ms falls short of clearly and convincingly demonstrating the utility of control theory in making management decisions.
-They call for more in-depth exploration and illustration of what novel and important contributions this method would make to conservation.
-For these reasons, this work may be better-suited to a more applied journal (e.g., Journal of Applied Ecology), assuming the ms is revised in the recommended direction."
-
-We thank the Associate Editor, Nicole Rafferty, for the constructive feedback and highlighting the strengths of the paper. 
-As we noted above in our response to the Senior Editor, we opted to use our revisions to strengthen the conceptual component rather than emphasising its application in specific management and conservation scenarios.
-We opted to take this decision for two main reasons. 
-First, the empirical data we use does not explicitly include any management or conservation scenarios. 
-As a consequence and despite the potential of the approach, we currently lack *direct* evidence of the utility of the approach for management decisions.
-Second, we concluded that highlighting the conceptual approach offered a greater opportunity to draw attention to the strongest/most interesting aspects of the paper. 
-Namely, the contrasts between invaded and uninvaded communities and the role of invasive species, as one of the reviewers points out.
-
-# Reviewer comments #1
-
-> "The management of complex ecological networks is of vast importance for the conservation of the natural world.
-While the field of ecological networks is vast few have tackled this question in a practical way.
-This paper would make a significant contribution to a field that needs to change direction if it is to help inform conservation as often purported in studies from this field."
-
-We are grateful to the reviewer for the positive feedback and encouraging words.
-
-> "The control theory approach is very interesting.
-I think however there needs to be more clarity in the paper.
-It is hard to read.
-A reworking of it including using descriptions of the variable throughout instead of variable names would improve this."
-
-Previously, we used two sections to explain our approach: a section called "Theoretical framework" where we described the control methods, and another called "Methods" where we described their application to empirical data.
-At that moment, we thought this was the best approach; in hindsight, we realise that separating these two aspects made it hard to understand the core control concepts and their relationship with ecology.
-As mentioned by the reviewer, this problem was compounded by abundant jargon and mathematical notation. 
-To improve clarity, we have now combined the two sections into a single "Methods" section in which we explain the theory alongside with the empirical application. 
-We also spend more time working through intuitive explanations of the concepts of control theory and have moved the most technical details to the supplementary information. 
-This latter move (shifting the technical details to the supplementary information) allowed us to use far less jargon and simplify the notation. 
-We hope that the reviewer agrees that the new version is easier to follow.
-
-> "Better context needs to be given for previous work to look at the management of networks in ecology.
-There are a few papers and knowing how this one differs from these (not just the ones that look at node importance for example) is important.
-Some of these papers are mentioned in the discussion but in the intro, it is important to know what they do and why this paper is novel."
-
-Thanks for this observation. 
-In line with feedback from both editors, we have chosen to emphasise on the conceptual aspects of the work and reduced the core question of management applications to appear only in the discussion. 
-Nevertheless, we have also rewritten the introduction and took care to be clear at explaining how this study relates to and differs from previous work. 
-In particular, we set the stage for our work by briefly explaining how keystoneness metrics are mainly based on centrality metrics and explicitly outline where and how the proposed work differs.
-
-> "Finally I think it is important to provide context about what kind of decisions are being made and could be informed by this approach.
-Who is managing plant-pollinator networks and what choices would they actually be making.
-Some examples should be expanded on.
-And also how would the outputs of this work actual inform choices and guide prioritization"
-
-As it was explained in the previous response, we chose not to emphasize the empirical application of structural controllability in this paper. 
-However, we acknowledge that the approach has potential to be applied in management and have hence described some insights that structural controllability could offer to the conservation of ecological networks (\lr{M-management-implications}).
-
-> "And finally I think mentioning the extreme uncertainty mostly seen in networks in the real world is key, how can approaches deal with this needs to be discussed.
-What do we need to think about in terms of key information to use this approach?"
-
-In the previous version, we discussed this uncertainty but it was unfortunately buried in the Supporting Information. 
-We have now added a subsection in the Methods describing how we evaluate the impact of the uncertainty induced (i) by using visitation as a proxy of species interdependence and (ii) by incomplete sampling of rare interactions (\lr{M-testing-assumptions-line}).
-We found that the structural controllability approach is rather robust to these two sources of uncertainty (\lr{M-testing-assumptions-results-line}). 
-Further details can be found in the Supporting Information Section \@ref(S-visitation-as-proxy) and \@ref(S-undersampling). 
-In addition, we also included a brief description of the key information needed to apply the method in the Discussion (\lr{M-data-requirements}).
-
-# Reviewer comments #2
-
-> "I read with great interest the manuscript by Cagua et al.
-on 'Quantifying the manageability of pollination networks in an invasion context'.
-The authors use control theory to develop an approach to assess how ecological networks – here pollination networks – can be managed, and test the approach on ten pairs of invaded and uninvaded plant-pollinator communities.
-Overall, the methodological approach appears to be sound (I’m not familiar with control theory, so I’ll have to leave in-depth assessment to an expert), the descriptions and rationale behind the assumptions used to develop the methods are logical and reasonable, and the illustration of the concept using published networks seems appropriate.
-Also, although the manuscript may require a few minor edits it is well and clearly written.
-I do, however, have some concerns about the applicability of the approach and the findings, which I’ll describe in more detail below."
-
-We are thankful to the reviewer for indicating the aspects which they believe were strengths of our work.
-We maintain the methodological approach in the latest version and have used these comments to help determine which elements were essential to maintain in the current revision.
-
-> "When I first read the title and the abstract of the manuscript I was excited about the prospect of reading about a way forward using ecological networks to improve ecosystem conservation.
-Now, having read the manuscript twice, I’m not persuaded that the proposed approach really advances our ability to conserve or restore ecological communities as the authors claim, or whether the approach provides primarily another, rather complex, way of analysing networks and describing the role of species in networks.
-As it is, the authors fail to convince me that the developed approach really advances our ability to prioritise species for ecosystem conservation, nor does the manuscript offer novel insights into the role and importance of certain species in a network and for ecosystem functioning.
-I’ve little doubt that there are ecological and theoretical justifications for combining control and network theory, but the authors don’t yet show that their proposed methods are overly useful in applied conservation."
-
-> "I can see two ways forward: the authors re-arrange and re-word the manuscript to focus on the ecological advances that such an approach would bring to explaining and predicting network structure; or the authors describe in more detail a few scenarios in which conservation practitioners and managers could apply the proposed method to ‘improve’ management strategies or measure the efficacy of interventions.
-The latter would require a stronger justification of the advantages of control-theory approach compared to the classic species-level network metrics."
-
-We are very thankful for the insightful identification of the manuscript weaknesses and especially for clearly identifying possible pathways to fix them. 
-Following this suggestion and those of the editors, we chose to focus on how structural controllability offers a new perspective to understand the role of species in their community in the context of species "keystoneness".
-Despite this decision, we still discuss previous metrics since we found that the paper was much clearer after we being more explicit about how the approach differs from classic centrality metrics to estimate species importance.
-Note that these differences are discussed in the current version more in the light of network structure than in the design of efficient management interventions.
-
-> "In short, I feel that the manuscript is currently a hybrid between ecological theory and applied conservation without being fully beneficial for either of the two disciplines.
-With a few changes to the manuscript, the interpretation and presentation of the results, and a re-write of the discussion with more tangible points and concrete examples from practical experience, the manuscript has the potential to be a solid contribution to the field of applied ecology."
-
-As mentioned earlier in a response to the editor, we found that in order to address effectively all concerns, a rewrite of the whole paper was needed. 
-Although we have not gone in the applied ecology direction, we hope the current version addresses the fundamental reviewers concerns to their satisfaction.
-
-> "One last minor remark, the authors have overlooked some key references in the field of restoration/conservation and ecological interactions/networks, which would strengthen the manuscript further, e.g.
-
-> * Harvey, E., Gounand, I., Ward, C.L. & Altermatt, F. (2017) Bridging ecology and conservation: from ecological networks to ecosystem function. Journal of Applied Ecology, 54, 371-379; 
-> * Devoto, M., Bailey, S., Craze, P. & Memmott, J. (2012) Understanding and planning ecological restoration of plant-pollinator networks. Ecology Letters, 15, 319-32; 
-> * Kaiser-Bunbury, C.N., Mougal, J., Whittington, A.E., Valentin, T., Gabriel, R., Olesen, J.M.
-& Blüthgen, N.
-(2017) Ecosystem restoration strengthens pollination network resilience and function.
-Nature, 542, 223-227;
-> * Pires, M.M., Marquitti, F.M.D.
-& Guimarães Jr, P.R.
-(2017) The friendship paradox in species-rich ecological networks: Implications for conservation and monitoring.
-Biological Conservation, 209, 245-252.
-
-Thank you for pointing us toward these references.
-We have found them to be particularly useful to highlight the differences between structural controllability and other approaches (\lr{M-extra-references-1} and \lr{M-extra-references-2}) and to discuss the potential impact of invasive plants (\lr{M-extra-references-3}).
+> "Reciprocal links were included in the directed graph when dij = dji. Would it have any effect if there was a little wiggle room there, e.g., when the two are close but not equal?"

### 2019-01-13 paper/manuscript.Rmd
Remove reviewers response first round of reviews

@@
 
-\R{testing-assumptions-line}Just like the centrality metrics, the information obtained by applying structural controllability depends on the ability of the network to accurately represent the ecological community.
+Just like the centrality metrics, the information obtained by applying structural controllability depends on the ability of the network to accurately represent the ecological community. 
 We thus tested the sensitivity of our approach to two fundamental assumptions. 
@@
 
-\R{testing-assumptions-results-line} We found that using visitation as a proxy for the strength of species' interactions leads to similar results than those obtained using pollinator importance [regarded as an accurate measure of the pollination service to plants; Supporting Information Section \@ref(S-visitation-as-proxy); @neeman_framework_2010].
+We found that using visitation as a proxy for the strength of species' interactions leads to similar results than those obtained using pollinator importance [regarded as an accurate measure of the pollination service to plants; Supporting Information Section \@ref(S-visitation-as-proxy); @neeman_framework_2010].
 Importantly, we also found that structural stability is robust to incomplete sampling of interactions. 
@@
 
-\R{management-implications}Other conceptual differences between structural controllability and centrality metrics provide three key insights into the conservation of ecological networks. 
+Other conceptual differences between structural controllability and centrality metrics provide three key insights into the conservation of ecological networks. 
 \R{R2-structural-controllability} First, structural controllability emphasizes that the effect a species has on the abundance of other species is not independent of the effects of those other species in their community.
@@
 Third, structural controllability explicitly acknowledges the existence of multiple management strategies and some will be better than others depending on the context.
-Approaches to prioritise species for conservation and reintroduction based on traits or centrality are still useful and are likely to overlap with species' control capacity\R{extra-references-1} [@pires_friendship_2017; @devoto_understanding_2012].
-Stepping back, our results also provide support to the idea that management decisions should not be based on a single technique but indicate that focusing on ecosystem processes and interactions may be more effective than traditional ranking-based approaches \R{extra-references-2} [@harvey_bridging_2017].
+Approaches to prioritise species for conservation and reintroduction based on traits or centrality are still useful and are likely to overlap with species' control capacity [@pires_friendship_2017; @devoto_understanding_2012].
+Stepping back, our results also provide support to the idea that management decisions should not be based on a single technique but indicate that focusing on ecosystem processes and interactions may be more effective than traditional ranking-based approaches [@harvey_bridging_2017].
 
@@
 Both native species and invasive plants tended to attain a high control capacity if they were important to network persistence, were abundant, and depended little on other species. 
-Furthermore, our observation that changes in the abundance of invasive plants (and presumably all critical species) are crucial to modify the state of the community agrees with recent evidence showing that ecosystem restoration focused on the eradication of invasive plants can have transformative desirable effects in plant-pollinator communities\R{extra-references-3} [@kaiser-bunbury_ecosystem_2017].
+Furthermore, our observation that changes in the abundance of invasive plants (and presumably all critical species) are crucial to modify the state of the community agrees with recent evidence showing that ecosystem restoration focused on the eradication of invasive plants can have transformative desirable effects in plant-pollinator communities [@kaiser-bunbury_ecosystem_2017].
 However, our results also suggest that removals must be exercised with caution. 
@@
 In an ideal scenario, we would completely incorporate the species' dynamics into the controllability analysis [@cornelius_realistic_2013]; the reality is that such information is rarely available in most ecological scenarios.
-\R{data-requirements}In contrast, structural controllability only requires a quantitative approximation of the network's interactions to gain valuable insight from the community.
+In contrast, structural controllability only requires a quantitative approximation of the network's interactions to gain valuable insight from the community.
 Furthermore, while the relationship between centrality and keystoneness is based on an intuitive understanding of what a keystone species is, the assumptions of structural controllability are explicit and the estimation of a species' importance arises from a mechanistic understanding of the population dynamics between species.

### 2019-01-13 paper/reviewers-response.Rmd
Editor's comments

@@
 
-# Associate Editor's comments:
+# Editor comments
+
+> "I agree that your manuscript is much improved and now only in need of relatively minor revisions.
+In addition to addressing the AE and reviewer's comments, please add terms related to invasive species to the keywords to aid in discoverability of your paper."
+
+Many thanks the encouraging words.
+We have included 'invasive species' as a keyword.
+To make space for this keyworkd we have removed 'controllability' which is already highlighted as part of the title.
+
+# Associate Editor's comments
 

### 2019-01-13 paper/manuscript.Rmd
Editor's comments

@@
 
-**Keywords:** Keystone species, management interventions, mutualism, network control theory, plant population and community dynamics, species' importance, control capacity, structural stability, controllability
+**Keywords:** Invasive species, keystone species, management interventions, mutualism, network control theory, plant population and community dynamics, species' importance, control capacity, structural stability
 

### 2019-01-13 paper/reviewers-response.Rmd
Minor improvements to associate editor comments

@@
 
-> "*L25*: 'every invasive species in our dataset was part of it' Here it was unclear what 'it' refers to (the set of critical species), and the reference to a singular dataset when you have 20 networks in total was a bit confusing to me.
+> "*L25*: 'every invasive species in our dataset was part of it' Here it was unclear what 'it' refers to (the set of critical species), and the reference to a singular dataset when you have 20 networks in total was a bit confusing to me."
 
-*Accepted and changed*. We have made this clearer as follows: "and included every invasive species in our dataset" (\lr{M-R2-our-dataset})
+*Accepted and changed*. We have made this clearer as follows: "and included every invasive species in our dataset" (\lr{M-R2-our-dataset}).
 
@@
 We now identify the distinction between high control capacity and being critical on \lr{M-R2-define-control-capacity}.
-The text now reads "It also allows us to quantify a species control capacity-its relative importance-and identify the set of species that, collectively, are critical in this context because they have largest possible control capacity."
+The text now reads "It also allows us to quantify a species control capacity-its relative importance-and identify the set of species that, collectively, are critical in this context because they have largest possible control capacity".
 
@@
 
-*Accepted and changed*. We now explicitly state "species' degree" in  \lr{M-R2-species-degree}
+*Accepted and changed*. We now explicitly state "species' degree" in  \lr{M-R2-species-degree}.
 
@@
 
-*Accepted and changed*. We have changed this to "it" and "its"
+*Accepted and changed*. We have changed this to "it" and "its".
 
@@
 
-> "*L343*: I am not sure about citing Table 2 for the first time in the Discussion. Might it be more useful to cite this in the Introduction?""
+> "*L343*: I am not sure about citing Table 2 for the first time in the Discussion. Might it be more useful to cite this in the Introduction?"
 
-We now introduce the glossary at the end of the introdyction on \lr{M-R2-ref-glossary}.
+*Accepted and changed*. We now introduce the glossary at the end of the introdyction on \lr{M-R2-ref-glossary}.
 

### 2019-01-13 paper/reviewers-response.Rmd
Minor improvements to Reviewer's #1 comments

@@
 We have corrected all citations.
-One of them, however, (\lr{R2-citation-with-name}) still shows an author's first name initial, as it is necessary to distinguish two authors with the same last name.
+One of them, however, still shows an author's first name initial, as it is necessary to distinguish two authors with the same last name (\lr{M-R2-citation-with-name}).
 

### 2019-01-13 paper/reviewers-response.Rmd
Finish reviewers comments except those that need input from Daniel

@@
 
-Many thanks the encouraging words.
+Many thanks for the encouraging words.
 We have included 'invasive species' as a keyword.
-To make space for this keyworkd we have removed 'controllability' which is already highlighted as part of the title.
+To make space for this keyword we have removed 'controllability' which is already highlighted as part of the title.
 
@@
 In particular, the authors have done a nice job of explaining how their findings reinforce existing ideas in the literature on the stability of ecological networks while also acknowledging limitations.
-The reviewers identify a few remaining issues that should be straightforward to address.
+The reviewers identified a few remaining issues that should be straightforward to address.
 I also noticed a few issues"
@@
 We have checked through the manuscript and corrected this where relevant.
-Besides *specie's role*, we also changes instances of *species' contribution*, *species' degree*, *species' control capacity*, among others.
+Besides *specie's role*, we also changed instances of *species' contribution*, *species' degree*, *species' control capacity*, among others.
 
@@
 
-*Accepted and changed*. We now introduce the glossary at the end of the introdyction on \lr{M-R2-ref-glossary}.
+*Accepted and changed*. We now introduce the glossary at the end of the introduction on \lr{M-R2-ref-glossary}.
 
@@
 
-We are pleased that the reviewer enjoyed the re-written manuscript. We did too!. We also grateful for the typos and style errors identifyed, we have striven to correct them all.
+We are pleased that the reviewer enjoyed the re-written manuscript. We did too!. We also grateful for the typos and style errors identified, we have striven to correct them all.
 
@@
 
+> "I think the concepts presented in this manuscript are a useful addition to the literature on management of ecological networks.
+I agree with the authors that it is important that the discussion surrounding what constitutes a 'keystone' species should go beyond centrality metrics.
+I found the results and concepts to be generally well presented, particularly graphically, and the authors present a thorough sensitivity analysis to various assumptions.
+
+We are very thankful for the positive feedback but also for the issues highlighted. We have aimed to address them all.
+
 > "The methods are mostly clear but there is no description of how the 'likelihood of being a superior node' is calculated."
@@
 Thanks for pointing this out.
-We have modified the sentence mentioning 'the likelihood of being a superior node' in the first paragraph of the secition \@ref(S-reciprocal-links) to "...and wether it is a superior node..." to avoid confusion.
+We have modified the sentence mentioning 'the likelihood of being a superior node' in the first paragraph of the section \@ref(S-reciprocal-links) to "...and whether it is a superior node..." to avoid confusion.
 Then we define the 'probability of being a superior node' at the end of the section: "It is important to note that a species that is found to be a superior node under a particular control configuration, will be so in all possible control configurations for the particular non-reciprocal network.
 We, therefore denote the average of $\sigma$ across all non-reciprocal versions as the probability of the species being a superior node in its community".
+
+> "I would suggest including clarification on the limitations of using control capacity to summarise species' importance, and examples to help the reader build an intuition regarding the control capacity metric.
+As pointed out, networks that give rise to a species having a high control capacity can be quite distinct to networks that give rise to a species having a high value of particular centrality metrics.
+Providing an example in the Discussion of, for instance, those species that have a control capacity of 1 but a low degree would be very useful."
+
+*Need Daniel's input*
+
+> "Jargon occasionally obfuscates the concepts being introduced and there are places where I thought the language used was vague (esp.
+if terms being used have particular meanings depending on the field you're coming from).
+I would suggest clarifying, or rewording, the following: 'desired control trajectory' - does this mean 'final state'?""
+
+*Accepted and changed*: We have attempted to clarify this sentence as follows: Finding out exactly how difficult it is to control a network depends strongly on the particularities of the desired control trajectory (i.e.
+the path to the desired final state)  as well as the dynamical relationship between nodes.
+\lr{M-R2-desired-control-trajectory}.
 
@@
 *Accepted and changed*: Thank you.
-To avoid confussion we have removed the word 'dynamic' and now the sentence reads "...our results suggest that structural controllability is closely related to the persistence..." (\lr{M-R2-dynamic-persistence}).
-It conserves its meaning without loosing much precision.
+To avoid confusion we have removed the word 'dynamic' and now the sentence reads "...our results suggest that structural controllability is closely related to the persistence..." (\lr{M-R2-dynamic-persistence}).
+It conserves its meaning without losing much precision.
 
@@
 
-*Accepted and changed*: Contrastingly, in this case the word dynanamic distinguishes a particular facet of stability.
+*Accepted and changed*: Contrastingly, in this case the word dynamic distinguishes a particular facet of stability.
 We mean the ability of the system to return to an equilibrium state after a perturbation.
@@
 
-> I think the concepts presented in this manuscript are a useful addition to the literature on management of ecological networks.
-I agree with the authors that it is important that the discussion surrounding what constitutes a "keystone" species should go beyond centrality metrics.
+> "*P9*: 'ecological objective' - simply 'objective'?"
 
-> I found the results and concepts to be generally well presented, particularly graphically, and the authors present a thorough sensitivity analysis to various assumptions.
-The methods are mostly clear but there is no description of how the "likelihood of being a superior node " is calculated.
+*Accepted and changed*: We have changed this to simply 'objective', as suggested (\lr{M-R2-ecol-objective}).
 
-> I would suggest including clarification on the limitations of using control capacity to summarise species' importance, and examples to help the reader build an intuition regarding the control capacity metric.
-As pointed out, networks that give rise to a species having a high control capacity can be quite distinct to networks that give rise to a species having a high value of particular centrality metrics.
-Providing an example in the Discussion of, for instance, those species that have a control capacity of 1 but a low degree would be very useful.
+> "*L405*: 'central in their community'"
 
-> "*Discussion*: 'species' strength'
+*Accepted and changed*: We've changed the wording to avoid ambiguity. Now the text reads "...to attain high centrality in their communities..." (\lr{M-R2-central-in-their-communities}).
+
+> "*L406*: 'inherently different. The sentence spanning lines 407-410 is quite confusing  - please clarify.
+
+*Accepted and changed*: We rephrased this line as follows: "We found that it is not that invasive plants have some different mechanism for influencing the community compared to their native counterparts" \lr{M-R2-inherrently-different}.
+
+> "*L430*: 'marginally affected by the topology of their interactions'"
+
+*Accepted and changed*: We have rephrased this line as: "By accounting for network dynamics (even if in a simple way), structural stability incorporates more ecological realism, especially in the extreme scenario in which the structure of interactions within the community only marginally affects the community's state.
+Both native species and invasive plants tended to attain a high control capacity if they were important to network persistence, were abundant, and depended little on other species" (\lr{M-R2-marginally-affected}).
+
+> "*L436* and *L441*: 'dominate the state [of their community]'"
+
+*Need Daniel's input*
+
+> "*Discussion*: 'species' strength'"
 
 *Accepted and changed*: In the Methods section we deine species' strength as the sum of a species' visits (\lr{M-R2-species-strength-a}).
-For brevity, we did not define it again in the Disussion, but now we have improved the text and briefly describe it when we mention it there too.
+For brevity, we did not define it again in the Discussion, but now we have improved the text and briefly describe it when we mention it there too.
 The text now reads "When controlling for a species' visitation strength (the sum of a species' visits), which is indirectly a proxy of its abundance..." (\lr{M-R2-species-strength-b}).
 
-> * "desired control trajectory " - does this mean "final state"?
+> "Minor typos: *Figure S11* caption: 'likelyhood' -> likelihood. *L388*: 'other other'. 'Driver node density' (supp p12) -> 'size of the minimum driver node set'?"
 
-> "'driver node density' (supp p12) -> 'size of the minimum driver node set'?"
-
-> * "dynamic persistence"  (p17,l364)
+*Accepted and changed*: All typos have been corrected as indicated.
 
@@
 
-*Accepted and changed*: We have corrected the refeerence that included 'plantPollinator' in the title.
-We have left the references that include an ellipsis in the author list as they are, as the Journal of Ecology Author Guidelines indicate that this is the preffered format when the reference has more than seven authors.
+*Accepted and changed*: We have corrected the reference that included 'plantPollinator' in the title.
+We have left the references that include an ellipsis in the author list as they are, as the Journal of Ecology Author Guidelines indicate that this is the preferred format when the reference has more than seven authors.
 
-> * "inherently different " (p18, l 406). The sentence spanning lines 407-410 is quite confusing  - please clarify.
+# Reviewer comments #3
 
-We rephrased this line as follows: "We found that it is not that invasive plants have some different mechanism for influencing the community compared to their native counterparts" \lr{R2-inherrently-different}.
+> "In the literature on ecological networks, the term keystone species has often been tossed around without any clear definition.
+I was pleased to read that here the authors have developed a cleaner, more effective way to identify keystone species in ecological networks than methods that have been proposed before.
+I think the authors have made the correct choice in emphasizing the conceptual aspects of the approach, and do so quite well.
+The background on control theory was complex but manageable to read and understand in this context."
 
-> * "marginally affected by the topology of their interactions"  (p19, l 430)
+We are very thankful for the positive feedback.
 
-We have rephrased this line as: "By accounting for network dynamics (even if in a simple way), structural stability incorporates more ecological realism, especially in the extreme scenario in which the structure of interactions within the community only marginally affects the community's state.
-Both native species and invasive plants tended to attain a high control capacity if they were important to network persistence, were abundant, and depended little on other species." \lr{R2-marginally-affected}.
+> "Overall I found the paper well-written and sound, but there were a few questions I had that could improve clarity in the methods used.
+In the glm that used nD as the response variable, is there any concern that including N (number of species) as a predictor may cause a problem when the response is D/N?
+I can understand why this was included, but I can also imagine this resulting in models that show an effect of N when there is none (I could be wrong on this)."
+
+*Need Daniel's input*
 

### 2019-01-13 paper/reviewers-response.Rmd
Add figure of interaction asymmetry in the response to the reviewers

@@
 ---
+
+\renewcommand\thefigure{R\arabic{figure}}    
+\setcounter{figure}{0}
 
@@
 > "Reciprocal links were included in the directed graph when dij = dji. Would it have any effect if there was a little wiggle room there, e.g., when the two are close but not equal?"
+
+We did not actually evaluate this When we evaluate the impact of this on our results.
+However, given that the interaction only a very small fraction of interactions had a small asymmetry (see Figure R1) we don't expect results to change considerably even when we include reciprocal links when the asymmetry is small but not zero.
+
+```{r fig-asymmetry, fig.width=6.3, fig.height=2, fig.cap = "Histogram of the interaction asymmetries between species.
+Previous research has shown that mutualistic interactions are often highly asymmetric in natural communities.
+Only 16.5% of interactions have asymetries smaller or equal than 0.5; 1% are smaller than 0.1."}
+drake::readd(fig_asymmetry_distribution)
+```

### 2019-01-13 code/fig_asymmetry_dist.R

@@ -1,0 +1,22 @@
+make_fig_asymmetry_dist <- function(directed_networks){
+  require(ggplot2)
+  directed_networks %>%
+    purrr::map(igraph::edge_attr, "weight") %>%
+    purrr::map_dfr(~tibble::data_frame(weight = .), .id = "net_name") %>%
+    dplyr::mutate(color = dplyr::case_when(
+      weight < 0.1 ~ "smaller", 
+      weight <= 0.5 ~ "small", 
+      TRUE ~ "large"
+    )) %>%
+    dplyr::group_by(color) %>%
+    dplyr::mutate(n = n()) %>%
+    ggplot(aes(weight)) +
+    # stat_ecdf() 
+    base_ggplot_theme() +
+    geom_histogram(aes(fill = color), breaks = seq(0,1, by = 0.05), fill = my_pallete()$light_grey) +
+    scale_fill_manual(values = c(my_pallete()$light_purple, my_pallete()$light_purple, my_pallete()$dark_purple)) +
+    theme(legend.position = "none", 
+          plot.subtitle = element_text(size = 8), 
+          plot.title = element_text(size = 9)) +
+    labs(x = "interaction asymmetry")
+}

### 2019-01-13 main.R

@@ -66,7 +66,8 @@ example_plots_plan <- drake::drake_plan(
   fig_models_degree = make_fig_models_degree(species_model_cc, species_model_superior),
   fig_rho_sensitivity = make_fig_rho_sensitivity(structural_rho_correlation, rho_feasibility),
   fig_assumption_sampling = make_fig_assumption_subsampling(metrics_subsampled, metadata), 
-  fig_species_partial = make_fig_species_partial(species_model_cc)
+  fig_species_partial = make_fig_species_partial(species_model_cc), 
+  fig_asymmetry_distribution = make_fig_asymmetry_dist(directed_networks)
 )
 
 control_capacity_testing_plan <- drake::drake_plan(
@@ -123,7 +124,7 @@ reporting_plan <- drake::drake_plan(
              drake::file_out('paper/supp-info.pdf'), clean_md = FALSE),
   render_pdf(drake::knitr_in('paper/manuscript.Rmd'), 
              drake::file_out('paper/manuscript.pdf'), clean_md = FALSE),
-  render_pdf(drake::file_in('paper/reviewers-response.Rmd'),
+  render_pdf(drake::knitr_in('paper/reviewers-response.Rmd'),
              drake::file_out('paper/reviewers-response.pdf'), clean_md = FALSE, clean_tex = FALSE), 
   compile_pdf(drake::file_in('paper/cover-letter.tex'), 
               drake::file_out('paper/cover-letter.pdf'))

### 2019-01-13 paper/drafts_and_revisions/2016-06-07/covering_letter_DBS_2016-06-30.tex
Add a bunch of tex files from the drafts and revisions

\documentclass[12pt, a4paper]{letter}

\usepackage[britdate]{canterbury-letter}
\usepackage{times}

\position{Associate Professor}
\department{School of Biological Sciences}
\location{Private Bag 4800}
\telephone{+64 3 364 2729}
\fax{+64 3 364 2590}
\email{daniel.stouffer@canterbury.ac.nz}
\url{http://stoufferlab.org}
\name{Daniel B. Stouffer}

\begin{document}

\begin{letter}{
       %\vspace*{20pt}
       Prof. Tim Coulson\\
       Editor in Chief\\
       Ecology Letters}

\opening{Dear Professor Coulson,}

We are submitting the manuscript entitled ``Biotic invasions reduce the
manageability of mutualistic networks'' {\bf update at end to match text} to
be considered for publication at \emph{Ecology Letters}.

Central to our manuscript is the introduction, development, and application of
the theoretical concept of \emph{ecological manageability}. Based on the
patterns of interactions between species, this idea can provide two main
pieces of information. First, it allows us to quantify \textit{community
manageability}---an indication of how difficult it is to control or manipulate
the abundances of all species in an ecological community. Second, it allows us
to identify the \textit{driver species}---those with a disproportionate
ability to alter other species' abundances.

Here, we use this concept as a framework to study the changes caused by biotic
invasions in pollination networks. Multiple empirical observations have
suggested that the structural changes caused by invasions may lead to
increased ecosystem resilience. However, our study is the first to use empirical data
to provide robust theoretical support for this idea. Furthermore, our
approach to quantify the relative importance of species is unique relative to the prevailing literature in that is
based on how structure underpins community dynamics while at the same
time having a direct link with management. Our results highlight the
extent to which some species---invaders in particular---can drive the
dynamics of other species across their community. It also identifies
``asymmetric dependence'' as the key factor driving these interspecific
differences.

Within the present manuscript, we develop the core ideas of community
manageability and driver species around the objective of using them to study
the consequences of biotic invasions in mutualistic systems like pollination
networks. Nevertheless, our framework and its potential application for
understanding how global-change drivers affect ecosystem dynamics are clearly
not exclusive to mutualistic communities. Indeed, we envisage the application
of the concepts we introduce to answer a wide range of ecological questions in
communities structured by different types of interactions. As such, we have
sought to highlight the methodology necessary for its implementation---an
extension of recently developed tools at the interface of complex systems and
control theory---throughout the manuscript.

% DBS: I'd cut the following paragraph entirely. Yes it's pertinent, but it's
% already in the abstract and conclusion and doesn't strike me as essential
% for the letter. Thoughts?

% In addition, although our study lies fundamentally within ecological theory,
% it has ramifications pertinent to ecological application. We think that
% concepts like theoretical manageability have the potential to stimulate much
% needed research that shorten the gap between ecological theory and
% management. Hopefully setting us on the track to informed, rather than
% hopeful, ecosystem interventions.

Lastly, please note that this manuscript represents a novel contribution for all co-authors involved and no related work published, in press, or submitted during this or last year has been cited.

\closing{Regards,}

\end{letter}

\end{document}

### 2019-01-13 paper/drafts_and_revisions/2016-07-11/covering_letter.tex
Add a bunch of tex files from the drafts and revisions

--- 2016-07-18 paper/covering_letter.tex
@@
 First, it allows to quantify the \textit{community manageability}---an indication of the difficulty of controlling the abundances of all species in the community. 
-Second it allows to identify \textit{driver species}--- those species with a disproportionate ability to alter other species' abundances.  
-Here, we use this concept as a framework to study the changes induced by biotic invasions to pollination networks.
+Second it allows to identify \textit{driver species}--- those with a disproportionate ability to alter other species' abundances.  
+Here, we use this concept as a framework to study the changes caused by biotic invasions to pollination networks.
 
@@
 Our study is the first to use empirical data to provide theoretical support for this idea. 
-Furthermore, our approach to identify driver species and quantify their relative importance, is unique in that it is based directly on the aspects of network structure that determine the behavior of the community as a holistic dynamical system.
-Our results also highlight the extent to which some species---invaders in particular---can drive the dynamics of other species across their community, and also identify ``asymmetric dependence'' as the potential mechanism driving the interspecific differences.
+Furthermore, our approach to identify driver species and quantify their relative importance, is unique in that it is based on the aspects of network structure that determine the behavior of the community as a dynamic system.
+Our results highlight the extent to which some species---invaders in particular---can drive the dynamics of other species across their community, and also identify ``asymmetric dependence'' as the potential mechanism driving the interspecific differences.
 
@@
 Our study fundamentally lies within ecological theory, yet it has ramifications pertinent to ecological application. 
-Indeed, we show in the paper that concepts like ``manageability'' have the potential to stimulate much needed research that reduce the gap between theory and management.
-Hopefully our study and more like it will set us on the track to informed, rather than hopeful, ecosystem interventions.
+We think that concepts like theoretical manageability have the potential to stimulate much needed research that shorten the gap between ecological theory and ecosystem management.
+Hopefully setting us on the track to informed, rather than hopeful, ecosystem interventions.
 

### 2019-01-13 paper/drafts_and_revisions/submission_2017Oct16/cover-letter.tex
Add a bunch of tex files from the drafts and revisions

\documentclass[12pt]{letter}

\usepackage[britdate]{canterbury-letter}
\usepackage{times}
%\usepackage{letterbib}
\usepackage{geometry}
% \usepackage[round]{natbib}
\usepackage{graphicx}
%\graphicspath{ {../figures/ecology_figs/} }
\geometry{a4paper}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{authblk}
\usepackage[running]{lineno}
\usepackage{amsmath,amsfonts,amssymb}
\usepackage[margin=10pt,font=small,labelfont=bf]{caption}

\newenvironment{refquote}{\smallskip \begin{it}}{\end{it}\smallskip}

\name{Dr.\ Daniel B.\ Stouffer}
\position{Associate Professor}
\department{School of Biological Sciences}
\location{Private Bag 4800}
\telephone{+64 3 364 2729}
\email{daniel.stouffer@canterbury.ac.nz}
\url{http://stoufferlab.org}

% \date{14 junio 2017}

\begin{document}

\begin{letter}{
       %\vspace*{20pt}
       Prof. David Gibson\\
       Executive Editor\\
       Journal of Ecology}

\opening{Dear Professor Gibson,}

We are submitting the manuscript entitled ``Quantifying the manageability of pollination networks in an invasion context'' to be considered for publication at \emph{Journal of Ecology}.

Central to this manuscript is the introduction, development, and application of the theoretical concept of \textbf{ecological manageability}.
Based on the patterns of interactions between species, this idea can provide two main pieces of information. 
First, it allows us to quantify the \textit{community manageability}---an indication of the inherent difficulty of controlling the abundances of all species in the community. 
Second it allows us to identify \textit{driver species}---those species whose manipulation exhibits a disproportionate ability to alter other species' abundances. 
Furthermore, our approach to identify driver species, and quantify their relative importance, is unique in that it is based directly on the aspects of network structure that determine the behavior of the community as a holistic dynamical system.

Here, we use the concept of ecological manageability and the information it provides as a framework to study the changes induced by biotic invasions to pollination networks. 
Multiple empirical observations have suggested that the structural changes caused by invasions may lead to changes to ecosystem resilience. 
Our study is the first to use empirical data to provide direct theoretical support for this idea. 
Our results also highlight the extent to which some species---invaders in particular---can drive the dynamics of other species across their community, and also identify ``asymmetric dependence'' as the potential mechanism driving the interspecific differences.

Despite our focus, understanding how drivers of ecosystem change affect ecosystem dynamics is not exclusive to mutualistic communities. 
Indeed, we envisage the application of the concepts we introduce to answer a wide range of ecological questions in communities structured by different types of interactions.
As such, we have sought to highlight the methodology necessary for its implementation---an extension of recently developed tools at the interface of complex systems and control theory---throughout the manuscript.

Our study fundamentally lies within ecological theory, yet it also has ramifications pertinent to ecological application. 
Indeed, we show in the paper that concepts like ``manageability'' have the potential to stimulate much needed research that can reduce the gap between theory and management.
Hopefully our study and more like it will set us on the track to informed, rather than hopeful, ecosystem interventions.

Thank you in advance for your consideration of our manuscript at your journal.

\closing{Regards,}

\end{letter}

\end{document}

### 2019-01-13 paper/drafts_and_revisions/2018-07-19/manuscript.tex
Add a bunch of tex files from the drafts and revisions

\documentclass[a4paper]{artikel1}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\usepackage[margin=1in]{geometry}
\usepackage{hyperref}
\hypersetup{unicode=true,
            pdftitle={Keystoneness, centrality, and the structural controllability of ecological networks},
            pdfborder={0 0 0},
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls
\usepackage{longtable,booktabs}
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
\IfFileExists{parskip.sty}{%
\usepackage{parskip}
}{% else
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{0}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

%%% Use protect on footnotes to avoid problems with footnotes in titles
\let\rmarkdownfootnote\footnote%
\def\footnote{\protect\rmarkdownfootnote}

%%% Change title format to be more compact
\usepackage{titling}

% Create subtitle command for use in maketitle
\newcommand{\subtitle}[1]{
  \posttitle{
    \begin{center}\large#1\end{center}
    }
}

\setlength{\droptitle}{-2em}
  \title{Keystoneness, centrality, and the structural controllability of
ecological networks}
  \pretitle{\vspace{\droptitle}\centering\huge}
  \posttitle{\par}
  \author{}
  \preauthor{}\postauthor{}
  \date{}
  \predate{}\postdate{}

\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage[table]{xcolor}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}

\usepackage{geometry}
\usepackage{setspace}
\usepackage{float}
\usepackage{booktabs}
\usepackage{caption}
\usepackage{lineno}
\newcommand{\R}[1]{\label{#1}\linelabel{#1}}
\newcommand{\lr}[1]{page~\pageref{#1}, line~\lineref{#1}}
\usepackage{xr}
\externaldocument[S-]{supp-info}
\usepackage{siunitx}
\usepackage{multirow}
\usepackage{makecell}
\usepackage{threeparttablex}

\usepackage{amsthm}
\newtheorem{theorem}{Theorem}
\newtheorem{lemma}{Lemma}
\theoremstyle{definition}
\newtheorem{definition}{Definition}
\newtheorem{corollary}{Corollary}
\newtheorem{proposition}{Proposition}
\theoremstyle{definition}
\newtheorem{example}{Example}
\theoremstyle{definition}
\newtheorem{exercise}{Exercise}
\theoremstyle{remark}
\newtheorem*{remark}{Remark}
\newtheorem*{solution}{Solution}
\begin{document}
\maketitle

\doublespacing
\linenumbers

\textbf{E. Fernando Cagua\textsuperscript{1}, Kate L.
Wootton\textsuperscript{1,2}, Daniel B. Stouffer\textsuperscript{1}}

\textsuperscript{1} Centre for Integrative Ecology, School of Biological
Sciences, University of Canterbury, Private Bag 4800, Christchurch 8041,
New Zealand

\textsuperscript{2} Current address: Department of Ecology, Swedish
University of Agricultural Sciences, Box 7044, SE-750 07 Uppsala, Sweden

\textbf{Author for correspondence:} Daniel B. Stouffer
(\href{mailto:daniel.stouffer@canterbury.ac.nz}{\nolinkurl{daniel.stouffer@canterbury.ac.nz}})
- +64 3 364 2729 - Centre for Integrative Ecology, School of Biological
Sciences, University of Canterbury, Private Bag 4800, Christchurch 8140,
New Zealand

\clearpage

\section{Abstract}\label{abstract}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\item
  An important dimension of a species role is its ability to alter the
  state and maintain the diversity of its community. Centrality metrics
  have often been used to identify these species, which are sometimes
  referred as ``keystone'' species. However, the relationship between
  centrality and keystoneness is largely phenomenological and based
  mostly on our intuition regarding what constitutes an important
  species. While centrality is useful when predicting which species
  extinctions could cause the largest change in a community, it says
  little about how these species could be used to attain or preserve a
  particular community state.
\item
  Here we introduce structural controllability, an approach that allows
  us to quantify the extent to which network topology can be harnessed
  to achieve a desired state. It also allows us to quantify a species
  control capacity---its relative importance---and identify the set of
  species that, collectively, are critical in this context. We
  illustrate the application of structural controllability with ten
  pairs of uninvaded and invaded plant-pollinator communities.
\item
  We found that the controllability of a community is not dependent on
  its invasion status, but on the asymmetric nature of its mutual
  dependences. While central species were also likely to have a large
  control capacity, centrality fails to identify species that, despite
  being less connected, were critical in their communities.
  Interestingly, this set of critical species was mostly composed of
  plants and every invasive species in our dataset was part of it. We
  also found that species with high control capacity, and in particular
  critical species, contribute the most to the stable coexistence of
  their community. This result was true, even when controlling for its
  degree, abundance/interaction strength, and the relative dependence of
  their partners.
\item
  \emph{Synthesis}: Structural controllability is strongly related to
  the stability of a network and measures the difficulty of managing an
  ecological community. It also identifies species that are critical to
  sustain biodiversity and to change or maintain the state of their
  community and are therefore likely to be very relevant for management
  and conservation.
\end{enumerate}

\textbf{Keywords:} Keystone species, management interventions,
mutualism, network control theory, plant population and community
dynamics, species importance, control capacity, structural stability,
controllability

\clearpage

\section{Introduction}\label{introduction}

A major goal in ecology is to understand the roles played by different
species in the biotic environment. Within community ecology, a
complex-systems approach has led to the development of a variety of
analytical and simulation tools with which to compare and contrast the
roles of species embedded in a network of interactions (J. Bascompte \&
Stouffer, 2009; Coux, Rader, Bartomeus, \& Tylianakis, 2016; Guimerà \&
Amaral, 2005; Stouffer, Sales-Pardo, Sirer, \& Bascompte, 2012). A
particularly relevant dimension of any species' role is its ability to
alter the abundance of other species and the state of the
community---since changes of this nature can have knock-on effects on
ecosystem function, diversity, processes, and services (Thompson et al.,
2012; Tylianakis, Didham, Bascompte, \& Wardle, 2008; Tylianakis,
Laliberté, Nielsen, \& Bascompte, 2010). This ability is sometimes
referred to as a species' ``keystoneness'' (Mills \& Doak, 1993).

A significant proportion of the network tools used to estimate species
roles in this context rely on the calculation of a species'
centrality---a relative ranking of its positional importance that
originally stems from social-network research (Friedkin, 1991; Martín
González, Dalsgaard, \& Olesen, 2010). Generally speaking, central
species tend to be better connected and consequently are more likely to
participate in the network's ``food chains''. Because species that
participate in more chains are more likely to affect the abundances of
other species, centrality metrics have often been used to identify
keystone species in the community (Jordán, Benedek, \& Podani, 2007).
Centrality metrics have been shown to be useful tools to rank species in
regard to their potential to alter the abundances of other species, in
particular when estimating the probability of secondary extinctions that
may follow the loss of a species (Dunne, Williams, \& Martinez, 2002;
Kaiser-Bunbury, Muff, Memmott, Müller, \& Caflisch, 2010).

Despite being conceptually intuitive, the relationship between
centrality and a species' presumed impact on the state of the community
is largely phenomenological. On the one hand, substantive changes in
ecosystem functioning can also occur without complete removal of a
species (Mouillot, Graham, Villéger, Mason, \& Bellwood, 2013). On the
other, we are often interested in a \emph{specific} state of the
community that might be desirable to attain (or preserve) because of its
biodiversity, resilience, functioning, or the ecosystem services it
provides. In these cases, it might be less useful to understand which
species may cause \emph{any} change in the community. Instead, we are
better served by understanding how the structure of the network can be
harnessed to achieve the desired state and which species may play the
largest role in this targeted process. When the state of a community is
underpinned by more than a single species (often the case in real
communities) and we move beyond single-species removals, we might expect
the accuracy of centrality to diminish. As a result, community ecology
could arguably benefit from an alternative, perhaps more
mechanistically-grounded, approach to understand how species affect each
other's abundance.

Species abundances---and consequently the state of the community as a
whole---are influenced both by the structure of their interactions and
the dynamics of these interactions, including the mechanisms of
self-regulation (Lever, van Nes, Scheffer, \& Bascompte, 2014). However,
community and population dynamics can be modelled in innumerable ways,
and empirical support for one versus another is often still ambiguous
(Holland, DeAngelis, \& Bronstein, 2002). The alternative approach
should, therefore, ideally acknowledge ecosystem dynamics, but without
being overly dependent on the particular choices of how they are
characterised. Among the various possibilities \emph{structural
controllability}, a branch of control theory, appears to be a strong
candidate (Isbell \& Loreau, 2013). Control theory is a widely-studied
branch of engineering used to determine and supervise the behaviour of
dynamical systems (A. E. Motter, 2015). It is inherently designed to
deal with system feedbacks and its application has recently been
expanded to complex networks (Lin, 1974; Liu \& Barabási, 2016).
Consistent with long-standing ecological questions, advances in
structural controllability have established a clear link between the
structure of the network and the way nodes affect each other. Unlike
centrality indices, however, this link is not based on a priori
assumptions between network metrics and keystoneness but is instead
based on well-established advances in both dynamical and complex-systems
theory (A. E. Motter, 2015).

At its fundamental level, structural controllability first determines
whether a system is controllable or not; that is, it asks if a system
could ever be driven to a desired state within a finite amount of time.
Although the controllability of a network is a whole-system property, it
has recently been shown that asking for the controllability of a
complex-system is equivalent to finding a particular set of relevant
nodes: the set with which is possible to control the state of the whole
network (Liu \& Barabási, 2016). Importantly, this set of nodes is not
always unique for a given network. This implies that an examination of
the distinct sets provides a means to connect nodes with their
\emph{general} ability to modify the system to which they belong.

Here, we apply methods from structural controllability to a particular
ecological problem and show how it can be used to generate insight into
the role of species in an ecological network. Specifically, we outline
the approach using a set of ten pairs of uninvaded and invaded
plant-pollinator communities. We use invaded communities because there
is strong empirical evidence showing that invasive species play an
important role shaping the abundances of other species, something which
is particularly true in these ten networks (Bartomeus, Vilà, \&
Santamaría, 2008; Lopezaraiza\textendash{}Mikel, Hayes, Whalley, \&
Memmott, 2007). This choice thus offers us an opportunity to explicitly
contrast our theoretical observations with empirical evidence. Moreover,
empirical observations indicate that steering the state of some
communities---for example during ecosystem restoration or invasive
species removal---can be a very difficult task (Woodford et al., 2016).
Therefore, we first ask whether there are differences between the
controllability of invaded and uninvaded networks. We then expand
existing methods from control theory to effectively link the
\emph{controllability} of a network with the role of its constituent
species. We ask---from a control-theoretic perspective---whether there
are key differences between species in the role they play at driving the
state of the community and explore the ecological factors related to
these differences. This allows us to identify species that might be
critical for network control and show that they have a larger than
expected impact on the stable coexistence of the community. Finally, we
compare the proposed approach to current methods based on species
centrality and show how these methods are indeed valuable but ultimately
paint a limited picture in regard to the ``keystoneness'' of a species.

\section{Materials and methods}\label{materials-and-methods}

We used ten paired pollination communities to apply the
control-theoretic approach. Each community pair was composed of a
community invaded by a plant and a community free of the invasive
species. Four pairs correspond to natural or semi-natural vegetation
communities in the city of Bristol, UK (Lopezaraiza\textendash{}Mikel et
al., 2007). These communities are comprised of 19--87 species (mean 55),
and non-invaded plots were obtained by experimentally removing all the
flowers of the invasive species \emph{Impatients grandulifera}. The
other six pairs were obtained from lower diversity Mediterranean
shrublands in Cap de Creus National Park, Spain (Bartomeus et al.,
2008). These communities are comprised of 30--57 species (mean 38); in
contrast to the above, uninvaded communities were obtained from plots
that had not yet been colonised by either of the invasive species
\emph{Carpobrotus affine acinaciformis} or \emph{Opuntia stricta}. The
structure of all these communities was defined by the pollinator
visitation frequency, which has been shown to be an appropriate
surrogate for interspecific effects in pollination networks (J.
Bascompte, Jordano, \& Olesen, 2006; Diego P. Vázquez, Morris, \&
Jordano, 2005). Full details about the empirical networks can be found
in the Supporting Information Section \ref{S-empirical-networks}.

The first step in applying methods of control theory is to construct a
directed network that is able to provide an indication of the extent to
which species affect each other's abundance. In some ecological
networks, establishing the directionality can be relatively
straightforward, for example when links represent biomass transfer or
energy flow (Isbell \& Loreau, 2013). In pollination networks, however,
this directionality is less obvious as both species can, in theory,
benefit from the interaction. We overcome that obstacle by noting that
the extent to which species \emph{i} affects species \emph{j} relative
to the extent to which \emph{j} affects \emph{i} can be summarised by
their interaction asymmetry (J. Bascompte et al., 2006). This asymmetry
is given by
\[a(i,j) = a(j,i) = \frac{\left | d_{ij}-d_{ji} \right |}{max\left ( d_{ij}, d_{ji} \right )},\]
where the dependence of plant \emph{i} on pollinator \emph{j},
\emph{d\textsubscript{ij}}, is the proportion of the visits from
pollinator \emph{j} compared to all pollinator visits to plant \emph{i}.
Previous research has shown that mutualistic interactions are often
highly asymmetric in natural communities; in other words, if a plant
species is largely dependent on a pollinator species, that pollinator
tends to depend rather weakly on the plant (and vice versa). We
therefore create a directed link from species \emph{i} to species
\emph{j} when \(d_{ij}-d_{ji} \geq 0\) to establish the most likely
direction of control between a species pair (Figure
\ref{fig:fig-example-networks}a). Sometimes there is no observed
asymmetry between species pairs (\(d_{ij}=d_{ji}\)), and we cannot infer
a dominant direction of control. When this occurs, we deem both species
to be equally likely to affect each other and leave a reciprocal
interaction between them (a link from \emph{i} to \emph{j} and another
from \emph{j} to \emph{i}). By basing the direction of the links on the
asymmetry of their dependence, we are able to generate a network that is
consistent with the dynamics of the community while satisfying the
requirements of structural controllability. This allows us to calculate
the controllability of the networks and investigate whether there are
differences between invaded and uninvaded communities.

\begin{figure}
\centering
\includegraphics{/Users/efc29/github/driver-species/paper/manuscript_files/figure-latex/fig-example-networks-1.pdf}
\caption{\label{fig:fig-example-networks}The direction of control and
controllability conditions. (a) To establish the direction of control,
we start with a weighted visitation network (on the left). In this
network, the width of the links corresponds to the frequency of
visitation between animals \(a_i\) and plants \(p_i\), with wider links
indicating more visits. Plant \(p_1\) is visited exclusively by \(a_1\)
but \(p_1\) represents only a small fraction of the floral resources
exploited by \(a_1\). Therefore, the population of \(p_1\) is more
likely to be affected by \(a_1\) than vice versa. We represent this with
a directed link from \(a_1\) to \(p_1\) in the control network (on the
right). The direction of control between all other species pairs can be
similarly determined by inspecting the difference between their relative
dependences. (b) Once we have established the directions of control, we
can determine whether the network is controllable or not. Any system
defined by a directed network (with state nodes \(x_i\); species
populations in an ecological context) and external control inputs (nodes
\(u_i\), orange links) is structurally controllable if it satisfies two
conditions: it has no dilations (expansions in the network) and no
inaccessible nodes. The system on the top left is not controllable
because there is a dilation since node \(x_2\) is being used to control
two nodes simultaneously; in other words, there are fewer superiors
(\(x_2\)) than subordinates (\(x_1\) and \(x_3\)). The network on the
top right is not controllable because node \(x_3\) is inaccessible for
the only input node \(u_1\) in the system. Both systems can be made
controllable by adding an extra input node (\(u_2\) in both bottom
networks).}
\end{figure}

\subsection{Controllability}\label{controllability}

A system is said to be controllable if it is possible to steer it from
an initial to an arbitrary final state within finite time (Kalman,
1963). A simple version of such a system can be described by
\(\frac{dx}{dt} = Ax + Bu(t)\), where the change of its state over time
(\(\frac{dx}{dt}\)) depends on its current state \emph{x} (for example
the species' abundances), an external time-varying input \emph{u(t)}
(the control signal), and two matrices \emph{A} and \emph{B}, which
encode information about the network structure and how species respond
to external inputs, respectively. In classic control theory, determining
whether this system is controllable can be achieved by checking that its
controllability matrix
\(R= [ \begin{matrix}B & AB & A^{2}B & ...& A^{n-1}B\end{matrix} ]\) has
full rank. In complex systems, however, employing this rank condition,
or numerical approximations of it is infeasible because it is hard to
fully parameterise \emph{A} and \emph{B} (either because the weight of
the links changes over time or because they are difficult to measure).
Here, we use an approach based on the structural controllability theorem
(Lin, 1974), which assumes that we are confident about which elements of
\emph{A} and \emph{B} have either non-zero or zero values (there is an
interaction or not), but that we are less sure about the precise
magnitude of the non-zero values. Using this structural approach, we can
find out the controllability of a system for every non-zero realisation
of the parameters.

We are often able to estimate \emph{A} in ecological networks, as this
matrix represents the interactions between species. Part of the control
problem thus resides in estimating a supportable estimation of \emph{B},
which represents the links between external inputs and species. Naively,
any ecological community (and any system for that matter) could be
controlled if we control the state of every species independently, but
such an approach is typically impractical. Here, we are interested in
finding a minimum driver-node set (effectively finding \emph{B}) with
which to make the system controllable. The brute-force search for this
minimum driver-node set is computationally prohibitive for most networks
as it involves the evaluation of \(2^N\) different controllability
matrices where \(N\) is the number of species in the community. We
therefore instead employ a recently-developed approach that shows that
the control problem of finding the minimum driver-node set can be mapped
into a graph-theoretic problem: maximum matching (Liu \& Barabási, 2016;
Liu, Slotine, \& Barabási, 2011).

Maximum matching is a widely studied topic in graph theory and is
commonly used in multiple applications, ranging from dating apps and
wireless communications to organ transplant allocation and peer-to-peer
file sharing. A matching in an unweighted directed graph is defined as a
set of links that do not share common start or end nodes; the largest
possible matching is called a maximum matching. For example, in a
network composed of jobs and job applicants, a matching is any pairing
between applicants and positions that satisfies one basic constraint: an
applicant can be assigned to at most one position and vice versa.
Consequently, a maximum matching is an optimal pairing, one that
maximises the number of applicants with jobs and the number of positions
filled. Admittedly, the link between matchings and structural
controllability may appear far from straightforward.

This link becomes apparent after examining the graphical interpretation
of structural controllability: from a topological perspective, a network
is structurally controllable if there are no inaccessible nodes---that
is, nodes without incoming links---or dilations---\emph{expansions} of
the network (Figure \ref{fig:fig-example-networks}b; Supporting
Information Section \ref{S-structural-controllability}). The key is to
note that these two fundamental conditions of structural controllability
imply that there is a one-to-one relationship between \emph{superior}
and \emph{subordinate} nodes just like the one-to-one relationship
between jobs and applicants (Figure \ref{fig:fig-example-networks}b,
bottom left). We thus use the maximum-matching algorithm to find an
optimal pairing of superior (those that can control another node) and
subordinate nodes (those that can be controlled by another node) in a
manner consistent with the controllability conditions (Supporting
Information Section \ref{S-one-maximum-matching}). Given the result, we
can further decompose the matching into a set of paths that reveal how a
control signal can flow across the links in a network to reach every
node within it. As recently shown (Liu et al., 2011), the minimum
driver-node set---those to which an external control input should be
applied to make the system controllable---corresponds exactly to the
\emph{unmatched} nodes in the network (Figure
\ref{fig:fig-control-configuration}).

\begin{figure}
\centering
\includegraphics{/Users/efc29/github/driver-species/paper/manuscript_files/figure-latex/fig-control-configuration-1.pdf}
\caption{\label{fig:fig-control-configuration}Maximum matchings and control
configurations. In directed networks, a maximum matching is the largest
possible set of links that do not share start or end nodes (dark
purple). Maximum matchings are not necessarily unique; instead, each of
them is related to a possible minimum driver-node set in the network
(the nodes to which an external control input, in orange, should be
applied in order to ensure controllability). The size of the minimum
driver-node set \emph{D} corresponds exactly to the number of unmatched
nodes (the number of nodes in the network \emph{N} minus the matching
size). To account for network size, we use the size of the minimum
driver-node set relative to the total number of nodes
\emph{n\textsubscript{D} = D/N} as a measure of the extent to which the
network structure can be harnessed to control the system.}
\end{figure}

\subsection{Differences between invaded and uninvaded
networks}\label{differences-between-invaded-and-uninvaded-networks}

Our first ecological objective is to investigate whether the
controllability of a community is associated with invasion status or
not. Finding out exactly how difficult it is to control a network
depends strongly on the particularities of the desired control
trajectory as well as the dynamical relationship between nodes. However,
we are interested in understanding the controllability of a network in a
more general sense, such that it can be applied even when the precise
control scenario is known only incompletely. To this end, we chose an
indicator that follows directly from our approach: the size of the
minimum driver-node set. This simple metric provides a general
indication of how difficult controlling a network might be, as systems
that require a large number of external inputs to be fully controlled
are intuitively more difficult or costly to manage. For instance,
achieving full control in a ``network'' in which species do not interact
at all is relatively more difficult as we would require an intervention
for every single species. Conversely, the structure of a linear trophic
chain can be harnessed to achieve full control using just one
intervention targeted at the top species; a suitable control signal
could then cascade through the trophic levels and reach other species in
the community. Specifically, drawing from the structural-controllability
literature, we use the size of the minimum driver-node set relative to
the total number of species \(n_D = \frac{D}{N}\) as a measure of the
\emph{controllability} of a network---the extent to which the network
structure can be harnessed to control the community. The lower \(n_D\)
the more controllable the community. In an ecological context, external
inputs can be thought of as management interventions that modify the
abundance of a particular species.

After finding the minimum driver-node set in each of our networks, we
wanted to test whether invasion status or other predictors are
correlated to controllability. We do this using a set of generalised
linear models with binomial error structure. The response variable was
the relative size of the minimum driver-node set \(n_D\) of the twenty
empirical networks (ten invaded and ten uninvaded), and we included
invasion status as a predictor. As predictors, we also include the
network connectance, the network nestedness (NODF), the number of
species (since one might naively expect to see a negative relationship
between richness and controllability; Menge, 1995), the network
asymmetry (an indication of the balance between plant and pollinator
diversity), and the interaction strength asymmetry (the asymmetry on the
dependences between trophic levels; N. Blüthgen, Menzel, Hovestadt,
Fiala, \& Blüthgen, 2007). We compared models using the Akaike
Information Criterion for small sample sizes (AICc).

In addition, we also explored whether real networks differ in their
architecture from random ones in a concerted way that could impact these
results. Specifically, we used two null models each with 99
randomisations per network. In the first, we followed Diego P Vázquez et
al. (2007) and maintained the connectance of the network but randomised
the visits across species such that the relative probabilities of
interactions were maintained. We then re-estimated the direction of
control and the corresponding size of the minimum driver-node set,
\(n_D\). For the second null model, we used the empirical directed
network described above and randomly shuffled the direction of control
between a species pair prior to re-estimating the size of the minimum
driver-node set.

\subsection{Species roles}\label{species-roles}

Our second objective is related to how species differ in their ability
to drive the population dynamics of the community. We in turn examine
whether these differences are also reflected in the role species play at
supporting the stable coexistence of other species in the community.
Ecologically, these differences are relevant because resources and data
are limited, and therefore full control is infeasible. While calculating
the size of the minimum drive-node set can measure the controllability
of an ecological community, it does not provide information about the
roles that particular species play.

To answer this question, we harness the fact there may be multiple
maximum matchings for a given network, and each of these maximum
matchings indicates a unique combination of species with which it is
possible to control the network. Moreover, some species belong to these
combinations more often than do others. We call this property a species
``control capacity'', \(\phi\). The higher a species control capacity,
the greater the likelihood that they would need to be directly managed
to change (or maintain) the ecological state of their community.
Therefore, a species control capacity provides an estimation of their
relative importance at driving the state of the community (Jia \&
Barabási, 2013).

To calculate a species control capacity \(\phi\), we must first
enumerate all possible maximum matchings (Supporting Information Section
\ref{S-all-maximum-matching}). Unfortunately, enumerating all maximum
matchings is extremely expensive from a computational perspective---a
network with a couple dozen species has several hundred million unique
maximum matchings. To solve this problem, we employ a recently-developed
algorithm that reveals the control correlations between the nodes in the
graph while requiring considerably less computational resources (Zhang,
Lv, \& Pu, 2016). Using this algorithm, we are able to identify species
that are possible control inputs---those that belong to the minimum
driver-node set in at least one of the possible control configurations.
Here, we extend this algorithm such that it is possible to calculate a
highly accurate approximation of the control capacity \(\phi\) of every
species in the network (Supporting Information Section
\ref{S-input-graph}). In the networks that contained reciprocal links
(because there was no asymmetry in the dependences of a species pair),
we averaged a species control capacity \(\phi\) across every possible
``non-reciprocal'' version of the network (Supporting Information
Section \ref{S-reciprocal-links}).

We then examined how species-level properties were related to control
capacity using a set of generalised linear models with binomial error
structure. These models included five predictor variables that mirror
the network-level predictors. First, the species contribution to
nestedness, which has been proposed as a key feature that promotes
stability and robustness in mutualistic networks (S. Saavedra, Stouffer,
Uzzi, \& Bascompte, 2011). Second, the species strength (the sum of a
species' visits), which quantifies the strength of a species
associations and is indirectly related to its abundance (Poisot, Canard,
Mouquet, \& Hochberg, 2012). Third, the direction of asymmetry which
quantifies the net balance in dependencies; that is, it indicates if a
species affects other species more than what they affect it or not
(Diego P Vázquez et al., 2007). Fourth, the species degree in order to
account for the intrinsic centrality of a species. Finally, we included
a categorical variable for the species trophic level (plant or
pollinator) and an interaction term between trophic level and the
previous four variables. To facilitate comparison between predictors,
degree and visitation strength were log-transformed and all four
continuous variables were scaled to have a mean of zero and a standard
deviation of one. To identify the models that were best supported by the
data, we first determined the most parsimonious random structure using
the AICc. The relative importance of variables was then assessed by
looking at their effect sizes in the top-ranked models and the
cumulative weight of the models in which they are present.

In addition, we wanted to understand how a species control capacity
\(\phi\) described above relates to metrics of keystoneness based on
centrality. Specifically, in each network, we calculated the species'
degree, betweenness, closeness centrality (Martín González et al.,
2010), page rank (McDonald-Madden et al., 2016), and eigen centrality
(Jordano, Bascompte, \& Olesen, 2006). We then calculated the spearman
correlation coefficient between control capacity and each of these
centrality metrics.

Our analysis revealed that some species have a control capacity
\(\phi = 1\). These species are critical to controlling their community
because they are part of the minimum driver-node set in \emph{every}
control scenario. In other words, it is theoretically impossible to
drive the state of the community to a desired state without directly
managing the abundance of these species. We thus anticipate that these
species have a disproportionally large impact on the community dynamics.
To test this hypothesis, we identified these critical species in each of
the networks and investigated whether they have a larger than average
impact on the stable coexistence of species in the community. Within
mutualistic networks, one useful measure of stable coexistence is called
structural stability (R. P. Rohr, Saavedra, \& Bascompte, 2014).
Mathematically, the structural stability of a network represents the
size of the parameter space (i.e., growth rates, carrying capacities,
etc.) under which all species can sustain positive abundances (S.
Saavedra, Rohr, Olesen, \& Bascompte, 2016). The contribution of any
given species \emph{i} to stable coexistence can be estimated by
calculating the structural stability of the community when the focal
species \emph{i} is removed. To allow comparison across communities, the
structural stability values were scaled within each network to have a
mean of zero and a standard deviation of one. Given these
species-specific estimates of structural stability, we then used a
t-test to compare the contribution to stable coexistence of critical and
non-critical species. More details about the calculation of structural
stability can be found in the Supporting Information Section
\ref{S-structural-stability}.

\subsection{Testing assumptions}\label{testing-assumptions}

\R{testing-assumptions-line}Just like the centrality metrics, the
information obtained by applying structural controllability depends on
the ability of the network to accurately represent the ecological
community. We thus tested the sensitivity of our approach to two
fundamental assumptions. First, we tested that visitation is an
appropriate proxy to infer interspecific effects by comparing the
results obtained using visitation to two alternative metrics in a
separate dataset that lacked invasive species (Ballantyne, Baldock, \&
Willmer, 2015). Specifically, we also calculated the controllability
(the size of the minimum driver node-set) and the control capacity of
networks constructed using pollinator efficiency (which measures the
pollen deposition of an interaction) and pollinator importance (which
accounts for both pollen deposition and visitation and hence is regarded
as a more accurate estimation of the pollination service received by
plants; Ne'eman, Jürgens, Newstrom-Lloyd, Potts, \& Dafni, 2009). More
details in the Supporting Information Section
\ref{S-visitation-as-proxy}.

Second, because interspecific dependencies themselves depend on the
network topology and consequently on the accurate sampling of
interactions, we tested the robustness of structural controllability to
the uncertainty involved with the sampling of interactions. Here, we
compared the results obtained when using the full network and when
randomly removing interactions from the weakest links in the network.
This effectively removed the rare interactions from the networks (more
details in the Supporting Information Section \ref{S-undersampling}).

\section{Results}\label{results}

\subsection{Controllability}\label{controllability-1}

The size of the minimum driver-node set relative to the number of
species in each network \(n_D\) ranged between \(n_D = 0.58\) and
\(n_D = 0.88\) (median 0.74).

\subsection{Differences between invaded and uninvaded
networks}\label{differences-between-invaded-and-uninvaded-networks-1}

We found that the relative size of the minimum driver-node set of
invaded communities was not significantly different from that of
communities that have not been invaded (Figure
\ref{fig:fig-emp-controllability}a). In contrast, there was a large
negative relationship between \(n_D\) and the network asymmetry (Figure
\ref{fig:fig-emp-controllability}b). Furthermore, there were also
negative, albeit weaker, relationships between \(n_D\) and connectance,
nestedness and species richness (Table
\ref{S-tab:tab-controllability-model-results}). The relative size of the
minimum driver-node set \(n_D\) of empirical networks did not differ
from that of a null model that roughly preserved the degree distribution
and fully preserved the network connectance (\(p = \num{0.66}\); Figure
\ref{fig:fig-emp-controllability}c). However, empirical networks had a
larger \(n_D\) than null models that preserved the interactions but
shuffled the direction of control of the empirical network
(\(p = \num{2.4e-07}\)).

\begin{figure}
\centering
\includegraphics{/Users/efc29/github/driver-species/paper/manuscript_files/figure-latex/fig-emp-controllability-1.pdf}
\caption{\label{fig:fig-emp-controllability}Drivers of network
controllability. (a) Probability density of the relative size of the
minimum driver-node set \(n_D\) in the invaded (light) and uninvaded
(dark) empirical networks. (b) Relationship between the asymmetry
plant/pollinator richness and \(n_D\). (c) Probability density of the
difference between the relative size of the minimum driver-node set of
random networks and that of empirical networks. We randomised either the
species visitation patterns (light line) or randomised the direction of
control between a species pair (dark line). The vertical dashed lines in
(a) and (c) indicate the median values of the distributions.}
\end{figure}

\subsection{Species roles}\label{species-roles-1}

Species varied widely in their control capacity (Figure
\ref{fig:fig-species-level}). Pollinators had, in average, larger
control capacities than plants. That said, almost no pollinator was
critical for network control, where a species is critical for control if
it has control capacity \(\phi_i = 1\)). Plants had a multimodal
distribution of control capacity with maxima at both extremes of the
distribution (Figure \ref{fig:fig-species-level}a). Intriguingly, every
invasive species was critical for network control in each of their
communities. The species-level models identified a positive relationship
between control capacity \(\phi\) and a species' contribution to
nestedness, visitation strength, and the asymmetry of its dependences
(Table \ref{tab:tab-model-selection-table}; Figure
\ref{fig:fig-species-partial}; Table
\ref{S-tab:tab-model-output-species-level}). Comparatively, species'
degree was only weakly associated with control capacity (Table
\ref{S-tab:tab-var-importance}). In fact, many species with a low
degree, especially pollinators, exhibited a large control capacity in
their communities (Figure \ref{S-fig:fig-species-models-degree}a).

Species control capacity \(\phi\) was only weakly correlated with
commonly-used centrality metrics. The Spearman correlation between these
ranged between -0.14 (with betweeness-centrality) and 0.42 (with
eigen-centrality), see Figure \ref{S-fig:fig-correlogram}a. The
correlation coefficient with degree was -0.13, however most species with
high degree also tended to attain a high control capacity (Figure
\ref{S-fig:fig-species-models-degree}a).

\begin{table}

\caption{\label{tab:tab-model-selection-table}Selection table of the binomial generalised linear models of species control capacity, $\phi$. Only models with a weight larger or equal to 0.01 are shown.}
\centering
\fontsize{8}{10}\selectfont
\begin{threeparttable}
\begin{tabular}[t]{rrlrrrllllrrr}
\toprule
\multicolumn{10}{c}{model terms} & \multicolumn{ 3}{c}{ } \\
\cmidrule(l{2pt}r{2pt}){1-10}
int. & $k$ & $l$ & $a$ & $n$ & $s$ & $k$:$l$ & $l$:$a$ & $l$:$n$ & $l$:$s$ & d.f. & $\Delta$AICc & weight\\
\midrule
-1.20 &  & + & 0.80 & 0.15 & 0.29 &  & + & + &  & 7 & 0.00 & 0.48\\
-1.19 &  & + & 0.76 & 0.13 & 0.35 &  & + & + & + & 8 & 1.52 & 0.22\\
-1.26 & -1.24 & + & 1.44 & 0.39 & 1.07 & + & + &  & + & 9 & 4.09 & 0.06\\
-1.37 & -0.66 & + & 1.03 &  & 1.06 & + & + &  & + & 8 & 4.39 & 0.05\\
-1.27 & -1.15 & + & 1.37 & 0.33 & 1.07 & + & + & + & + & 10 & 4.92 & 0.04\\
\addlinespace
-1.37 & -0.10 & + & 0.90 &  & 0.43 & + & + &  &  & 7 & 6.36 & 0.02\\
-1.25 & -0.28 & + & 1.24 & 0.40 &  & + & + &  &  & 7 & 6.47 & 0.02\\
-1.24 & -0.62 & + & 1.29 & 0.38 & 0.40 & + & + &  &  & 8 & 6.50 & 0.02\\
-1.39 & 0.30 & + & 0.83 &  &  & + & + &  &  & 6 & 6.72 & 0.02\\
-1.28 & -0.17 & + & 1.16 & 0.32 &  & + & + & + &  & 8 & 7.03 & 0.01\\
\addlinespace
-1.26 & -0.53 & + & 1.23 & 0.32 & 0.39 & + & + & + &  & 9 & 7.42 & 0.01\\
-1.02 &  & + & 0.69 & 0.30 & 0.31 &  & + &  &  & 6 & 7.48 & 0.01\\
\bottomrule
\end{tabular}
\begin{tablenotes}[para]
\item \textit{Terms: } 
\item intercept (int), degree ($k$), trophic level ($l$), asymmetry ($a$), contribution to nestedness ($n$), visitation strength ($s$).
\end{tablenotes}
\end{threeparttable}
\end{table}

\begin{figure}
\centering
\includegraphics{/Users/efc29/github/driver-species/paper/manuscript_files/figure-latex/fig-species-level-1.pdf}
\caption{\label{fig:fig-species-level}Probability density of the control
capacity \(\phi\) of (a) plants and (b) pollinators across all networks.
The control capacity of all invasive species is \(\phi = 1\) and is
depicted with solid circles.}
\end{figure}

\begin{figure}
\centering
\includegraphics{/Users/efc29/github/driver-species/paper/manuscript_files/figure-latex/fig-species-partial-1.pdf}
\caption{\label{fig:fig-species-partial}Partial-residual plots for the
independent variables: (a) contribution to nestedness, (b) visitation
strength, (c) asymmetry of dependences, and (d) degree. Partial-residual
plots show the relationship between control capacity and each of the
independent variables while acccounting for all other remaining
variables. Ploted values correpond to the predictions of the weighted
average of the models shown in Table
\ref{tab:tab-model-selection-table}.}
\end{figure}

Finally, we found that critical species have a particularly large impact
on species coexistence when compared to non-critical species. Indeed,
the structural stability of the networks where critical species were
removed was considerably lower to those in were non-critical species
were removed (\(p = \num{2e-15}\); Figure
\ref{fig:fig-structural-stability}; Supporting Information
\ref{S-structural-stability}).

\begin{figure}
\centering
\includegraphics{/Users/efc29/github/driver-species/paper/manuscript_files/figure-latex/fig-structural-stability-1.pdf}
\caption{\label{fig:fig-structural-stability}Probability density of the
structural stability of the communities after a single focal species is
removed. Mathematically, the structural stability of a network
represents the size of the parameter space (i.e., growth rates, carrying
capacities, etc.) under which all species can sustain positive
abundances. The structural stability of communities in which critical
species have been removed (darker line) is considerably smaller than
that of communities in which non-critical species have been removed.
This indicates that critical species contribute more to the stable
coexistence of their communities. To allow comparison across
communities, the structural stability values were scaled within each
network to have a mean of zero and a standard deviation of one. Here, we
assume values of the mutualistic trade-off and mean interspecific
competition of \(\delta = 0\) and \(\rho = 0.01\) respectively (S.
Saavedra et al., 2016). However, the choice of these parameters does not
affect the results (Supporting Information
\ref{S-structural-stability}).}
\end{figure}

\subsection{Testing assumptions}\label{testing-assumptions-1}

\R{testing-assumptions-results-line} We found that using visitation as a
proxy for the strength of species interactions leads to similar results
than those obtained using pollinator importance (regarded as an accurate
measure of the pollination service to plants; Supporting Information
Section \ref{S-visitation-as-proxy}; Ne'eman et al., 2009). Importantly,
we also found that structural stability is robust to incomplete sampling
of interactions. Indeed, we found strong agreement between results
obtained using the complete empirical networks and those obtained by
randomly removing the weakest interactions (Supporting Information
Section \ref{S-undersampling}). Despite removing rare interactions and
species, the relative size of the minimum driver-node set, the superior
species, and the relative rankings of control capacity were generally
maintained. Of particular note, we found that critical species in the
full network were also critical in the vast majority of rarefied
networks.

\section{Discussion}\label{discussion}

Our main goal was to understand the role that species play at both
modifying the abundance of the species they interact with and the state
of the community as a whole. To achieve that goal we applied
\emph{structural controllability}, a field at the intersection between
control and complex theory that allow us to obtain two key pieces of
information: the \emph{controllability} of a network and a species
\emph{control capacity} (Table \ref{tab:tab-glossary}). We found that
the controllability of a network does not depend on its invasion status
and that the species that are critical to altering the state of the
community are also the ones that most sustain the stable coexistence of
species in their communities.

\begin{table}

\caption{\label{tab:tab-glossary}Glossary}
\centering
\fontsize{8}{10}\selectfont
\begin{tabular}[t]{>{\raggedright\arraybackslash}p{3.4in}l}
\toprule
\textbf{network control} & \\
\hspace{1em}A network is said to be controllable if it is possible to steer it from an initial to an arbitrary final state within finite time. & \\
\addlinespace
\textbf{controllability} & \\
\hspace{1em}The intrinsic difficulty of controlling an ecological community. It is measured by the relative size of the minimum driver-node set, $n_D$. It also indicates the extent to which network structure can be harnessed for network control. & \\
\addlinespace
\textbf{minimum driver-node set} & \\
\hspace{1em}One of the sets of species whose abundances need to be directly managed in order to achieve full control of the community. The minimum driver-node sets can be obtained by finding all maximum matchings in a network. & \\
\addlinespace
\textbf{maximum matching} & \\
\hspace{1em}A matching is a set of links that do not share any common start or end nodes; the largest possible matching is called a maximum matching. & \\
\addlinespace
\textbf{control configuration} & \\
\hspace{1em}One of the species combinations with which is possible to achieve network control. Optimal control configurations are given by the minimum driver-node sets. & \\
\addlinespace
\textbf{control capacity} & \\
\hspace{1em}The relative frequency \(\phi\) which with a species is part of the optimal control configurations of a network. & \\
\addlinespace
\textbf{critical species} & \\
\hspace{1em}A species with a maximal control capacity \(\phi=1\) & \\
\addlinespace
\textbf{superior node} & \\
\hspace{1em}A species is a superior node if it can internally affect the abundance of other species in the network. Superior nodes make up the chains that propagate the control signals through the network. & \\
\bottomrule
\end{tabular}
\end{table}

Our results indicate that fully controlling ecological networks might
currently be out of reach for all but the smallest communities (A. E.
Motter, 2015). Indeed, the median size of the relative minimum
driver-node set in our dataset was \(n_D = 0.74\), a high value when
compared to other complex systems in which controllability has been
investigated (the lower \(n_D\) the more controllable the community).
For instance, only gene regulation networks appear to achieve similar
levels of controllability while most social, power transmission,
Internet, neuronal, and even metabolic networks seem to be ``easier'' to
control (\(0.1 < n_D < 0.35\)) (Liu et al., 2011). Structural
controllability provides solid theoretical rationale for the many
difficulties encountered in the management and restoration of natural
communities (Woodford et al., 2016). Nevertheless, structural
controllability might be helpful at identifying communities in which
changes in the ecological state are more likely to occur

The differences between the controllability across networks are likely
to arise from differences in their structure rather than their invasion
status. Specifically, when controlling for network structure, we found
no difference between the controllability of invaded and uninvaded
networks. instead controllability is almost completely constrained by
the patterns of species richness at each trophic guild and their degree
distributions (N. Blüthgen et al., 2007; C. J. Melián \& Bascompte,
2002). These two factors are particularly relevant because they govern
the asymmetric nature of mutual dependences, which themselves provide
the foundation of structure and stability in mutualistic networks
(Astegiano, Massol, Vidal, Cheptou, \& Guimarães, 2015; J. Bascompte et
al., 2006; J. Memmott, Waser, \& Price, 2004).

Accordingly, our results suggest that structural controllability is
closely related to the dynamic persistence of an ecological community
based on two lines of evidence. First, we found a comparatively small
but thought-provoking negative relationship between the controllability
of a network and its nestedness. Previous studies indicate that
nestedness promotes species coexistence and confers robustness to
extinction (Bastolla et al., 2009; J. Memmott et al., 2004) even at the
expense of the dynamic stability of the mutualistic community (S.
Saavedra et al., 2016). These observations are in agreement with our
results, as we would expect the dynamic stability of a community to be
correlated to the difficulty to control it. Second, species' control
capacity was strongly correlated to their contribution to nestedness and
critical species had the largest impact to the stable coexistence of
species in their communities. Therefore, species that play a key role at
determining the state of the community might also be more key to
``maintain the organization and diversity of their ecological
communities'', one of the hallmarks of keystone species (Mills \& Doak,
1993).

When controlling for a species' strength, which is indirectly a proxy of
its abundance, and the net balance of its dependencies, we found that
control capacity could not be easily predicted by species' degree or
other metrics of centrality. For instance, some species with a low
degree achieved the maximum control capacity and were critical for
control in their communities. At first glance, our findings challenge
numerous studies that highlight the role that central species play in
the dynamics of their communities and their utility at predicting
species extinctions (Jordan, 2009). However, further, inspection shows
that our results do not contradict these findings; most species with a
large degree also have a large control capacity and all of them were
classified as superior nodes which corroborates the utility of classic
centrality metrics. Putting these observations together, our results
therefore take previous findings one step further and suggest that
centrality might paint an incomplete picture of the relevance of
species.

\R{management-implications}Other conceptual differences between
structural controllability and centrality metrics provide three key
insights into the conservation of ecological networks. First, structural
controllability emphasizes that the effect a species has on the
abundance of other species is not independent of the effects of other
other species in their community. The rankings provided by centrality
metrics and other heuristics fail to account for the collective
influence of several species at once. Second, it demonstrates that to
ensure the persistence of a community it is often necessary to consider
the abundances of more than a single species, even when full control is
infeasible or undesired (for example 90\% of our communities contained
more than one critical species). Third, structural controllability
explicitly acknowledges the existence of multiple management strategies
and some will be better than others depending on the context. Approaches
to prioritise species for conservation and reintroduction based on
traits or centrality are still useful and are likely to overlap with
species control capacity\R{extra-references-1} (Devoto, Bailey, Craze,
\& Memmott, 2012; Pires, Marquitti, \& Guimarães, 2017). Stepping back,
our results also provide support to the idea that management decisions
should not be based on a single technique but indicate that focusing on
ecosystem processes and interactions may be more effective than
traditional ranking-based approaches \R{extra-references-2} (Harvey,
Gounand, Ward, \& Altermatt, 2017).

Our choice of studying invaded/uninvaded networks was based on a desire
to contrast the extensive empirical evidence of the role of invasive
plants with our theoretical results. We found that invasive plants were
always critical for network control and as such our results were in line
with our expectations. Invasive plants have been previously found to
exacerbate the asymmetries in their communities (Aizen, Morales, \&
Morales, 2008; Bartomeus et al., 2008; Henriksson, Wardle, Trygg, Diehl,
\& Englund, 2016) and to be central in their communities (Palacio,
Valderrama-Ardila, \& Kattan, 2016; Vila et al., 2009). We found that
invasive plants are, however, unlikely to be inherently different from
their native counterparts (Emer, Memmott, Vaughan, Montoya, \&
Tylianakis, 2016; Stouffer, Cirtwill, \& Bascompte, 2014). Just like any
other mutualist in our dataset, invasive plants tended to attain a high
control capacity proportional to the degree to which they contribute to
network persistence, are abundant, and depend little on other species.
Furthermore, our observation that changes in the abundance of invasive
plants (and presumably all critical species) are crucial to modify the
state of the community agrees with recent evidence showing that
ecosystem restoration focused on the eradication of invasive plants can
have transformative desirable effects in plant-pollinator
communities\R{extra-references-3} (Kaiser-Bunbury et al., 2017).
However, our results also suggest that removals must be exercised with
caution. Not only it is hard to predict the direction in which the
system will change, but we also show that critical species can underpin
the coexistence of species and therefore some communities may be acutely
vulnerable to their eradication (Albrecht, Padron, Bartomeus, \&
Traveset, 2014; Traveset et al., 2013).

Structural controllability assumes that the networks can be approximated
using linear functional responses (Liu \& Barabási, 2016). The
ramifications of this assumption imply that, while structural
controllability is useful to identify species that are relevant for
network control, it cannot be used to design the \emph{exact}
interventions that should be applied to these species in order to
achieve a desired state. In an ideal scenario, we would completely
incorporate the species dynamics into the controllability analysis
(Cornelius, Kath, \& Motter, 2013); the reality is that such information
is rarely available in most ecological scenarios.
\R{data-requirements}In contrast, structural controllability only
requires a quantitative approximation of the network's interactions to
gain valuable insight from the community. Furthermore, while the
relationship between centrality and keystoneness is based on an
intuitive understanding of what a keystone species is, the assumptions
of structural controllability are explicit and the estimation of a
species importance arises from a mechanistic understanding of the
population dynamics between species. By accounting for network dynamics
(even if in a simple way), structural stability incorporates more
ecological realism, especially in the extreme scenario in which the
state of a community is only marginally affected by the topology of
their interactions.

\section{Conclusions}\label{conclusions}

Here we show that structural controllability can be applied in an
ecological setting to gain insight into the stability of a community and
the role that species play at modifying the abundance of other species
and ultimately the state of the community. These characteristics make
structural stability an ideal framework to evaluate the effects of
invasions and other types of perturbations. Importantly, structural
controllability can be used to identify critical species in the
community that promote biodiversity and underpin the stable coexistence
of species in their community. Collectively, critical species dominate
the state of their community and therefore are likely to be highly
relevant for ecosystem management and conservation. While useful,
centrality metrics, which have often been used as a proxy for
keystoneness, fail to identify some of these species, highlighting their
limitations when we fully embrace the notion that ecological communities
are dynamical systems. Paine (1969) showed nearly 50 years ago that one
single species can dominate the state of its community. Structural
controllability suggests that this situation might be the exception
rather than the rule. We see our study as a starting point to study the
controllability of ecological and socio-ecological systems where many
exciting questions lie ahead.

\section{Acknowledgements}\label{acknowledgements}

The authors thank Jane Memmott and co-authors, and everyone that has
made their data available to us, Takeuki Uno for the insight provided to
find the set of all maximum matching algorithms, and Jason Tylianakis,
Bernat Bramon Mora, Guadalupe Peralta, Rogini Runghen, Michelle
Marraffini, Mark Herse, Warwick Allen, Matthew Hutchinson, and Marilia
Gaiarsa for feedback and valuable discussions. EFC acknowledges the
support from the University of Canterbury Doctoral Scholarship, the
University of Canterbury Meadow Mushrooms Postgraduate Scholarship, a
New Zealand International Doctoral Research Scholarship, and a travel
grant from the European Space Agency. DBS acknowledges the support of a
Marsden Fast-Start grant and a Rutherford Discovery Fellowship,
administered by the Royal Society Te Aparangi.

\section{Author contributions}\label{author-contributions}

DBS conceived the idea; all authors contributed to the development of
the theoretical framework. EFC performed all analysis. EFC and DBS wrote
the manuscript. All authors contributed to its revision.

\section{Data accessibility}\label{data-accessibility}

All data used in this manuscript have already been published by
Lopezaraiza\textendash{}Mikel et al. (2007), Bartomeus et al. (2008),
and Ballantyne et al. (2015) The reader should refer to the original
sources to access the data.

\section*{References}\label{references}
\addcontentsline{toc}{section}{References}

\hypertarget{refs}{}
\hypertarget{ref-aizen_invasive_2008}{}
Aizen, M. A., Morales, C. L., \& Morales, J. M. (2008). Invasive
Mutualists Erode Native Pollination Webs. \emph{PLoS Biology},
\emph{6}(2), e31.
doi:\href{https://doi.org/10.1371/journal.pbio.0060031}{10.1371/journal.pbio.0060031}

\hypertarget{ref-albrecht_consequences_2014}{}
Albrecht, M., Padron, B., Bartomeus, I., \& Traveset, A. (2014).
Consequences of plant invasions on compartmentalization and species'
roles in plant-pollinator networks. \emph{Proceedings of the Royal
Society B: Biological Sciences}, \emph{281}(1788), 20140773--20140773.
doi:\href{https://doi.org/10.1098/rspb.2014.0773}{10.1098/rspb.2014.0773}

\hypertarget{ref-astegiano_robustness_2015}{}
Astegiano, J., Massol, F., Vidal, M. M., Cheptou, P.-O., \& Guimarães,
P. R. (2015). The Robustness of Plant-Pollinator Assemblages: Linking
Plant Interaction Patterns and Sensitivity to Pollinator Loss.
\emph{PLOS ONE}, \emph{10}(2), e0117243.
doi:\href{https://doi.org/10.1371/journal.pone.0117243}{10.1371/journal.pone.0117243}

\hypertarget{ref-ballantyne_constructing_2015}{}
Ballantyne, G., Baldock, K. C. R., \& Willmer, P. G. (2015).
Constructing more informative plantPollinator networks: Visitation and
pollen deposition networks in a heathland plant community.
\emph{Proceedings of the Royal Society B: Biological Sciences},
\emph{282}(1814), 20151130.
doi:\href{https://doi.org/10.1098/rspb.2015.1130}{10.1098/rspb.2015.1130}

\hypertarget{ref-bartomeus_contrasting_2008-1}{}
Bartomeus, I., Vilà, M., \& Santamaría, L. (2008). Contrasting effects
of invasive plants in plantPollinator networks. \emph{Oecologia},
\emph{155}(4), 761--770.
doi:\href{https://doi.org/10.1007/s00442-007-0946-1}{10.1007/s00442-007-0946-1}

\hypertarget{ref-bascompte_assembly_2009}{}
Bascompte, J., \& Stouffer, D. B. (2009). The assembly and disassembly
of ecological networks. \emph{Philosophical Transactions of the Royal
Society B: Biological Sciences}, \emph{364}(1524), 1781--1787.
doi:\href{https://doi.org/10.1098/rstb.2008.0226}{10.1098/rstb.2008.0226}

\hypertarget{ref-bascompte_asymmetric_2006}{}
Bascompte, J., Jordano, P., \& Olesen, J. M. (2006). Asymmetric
Coevolutionary Networks Facilitate Biodiversity Maintenance.
\emph{Science}, \emph{312}(5772), 431--433.
doi:\href{https://doi.org/10.1126/science.1123412}{10.1126/science.1123412}

\hypertarget{ref-bastolla_architecture_2009}{}
Bastolla, U., Fortuna, M. A., Pascual-García, A., Ferrera, A., Luque,
B., \& Bascompte, J. (2009). The architecture of mutualistic networks
minimizes competition and increases biodiversity. \emph{Nature},
\emph{458}(7241), 1018--1020.
doi:\href{https://doi.org/10.1038/nature07950}{10.1038/nature07950}

\hypertarget{ref-bluthgen_specialization_2007}{}
Blüthgen, N., Menzel, F., Hovestadt, T., Fiala, B., \& Blüthgen, N.
(2007). Specialization, Constraints, and Conflicting Interests in
Mutualistic Networks. \emph{Current Biology}, \emph{17}(4), 341--346.
doi:\href{https://doi.org/10.1016/j.cub.2006.12.039}{10.1016/j.cub.2006.12.039}

\hypertarget{ref-cornelius_realistic_2013}{}
Cornelius, S. P., Kath, W. L., \& Motter, A. E. (2013). Realistic
control of network dynamics. \emph{Nature Communications}, \emph{4},
1942. doi:\href{https://doi.org/10.1038/ncomms2939}{10.1038/ncomms2939}

\hypertarget{ref-coux_linking_2016}{}
Coux, C., Rader, R., Bartomeus, I., \& Tylianakis, J. M. (2016). Linking
species functional roles to their network roles. \emph{Ecology Letters},
\emph{19}(7), 762--770.
doi:\href{https://doi.org/10.1111/ele.12612}{10.1111/ele.12612}

\hypertarget{ref-devoto_understanding_2012}{}
Devoto, M., Bailey, S., Craze, P., \& Memmott, J. (2012). Understanding
and planning ecological restoration of plant-pollinator networks:
Understanding network restoration. \emph{Ecology Letters}, \emph{15}(4),
319--328.
doi:\href{https://doi.org/10.1111/j.1461-0248.2012.01740.x}{10.1111/j.1461-0248.2012.01740.x}

\hypertarget{ref-dunne_network_2002}{}
Dunne, J. A., Williams, R. J., \& Martinez, N. D. (2002). Network
structure and biodiversity loss in food webs: Robustness increases with
connectance. \emph{Ecology Letters}, \emph{5}(4), 558--567.
doi:\href{https://doi.org/10.1046/j.1461-0248.2002.00354.x}{10.1046/j.1461-0248.2002.00354.x}

\hypertarget{ref-emer_species_2016}{}
Emer, C., Memmott, J., Vaughan, I. P., Montoya, D., \& Tylianakis, J. M.
(2016). Species roles in plant-pollinator communities are conserved
across native and alien ranges. \emph{Diversity and Distributions},
\emph{22}(8), 841--852.
doi:\href{https://doi.org/10.1111/ddi.12458}{10.1111/ddi.12458}

\hypertarget{ref-noah_e._friedkin_theoretical_1991}{}
Friedkin, N. E. (1991). Theoretical Foundations for Centrality Measures.
\emph{American Journal of Sociology}, \emph{96}(6), 1478--1504.

\hypertarget{ref-guimera_cartography_2005}{}
Guimerà, R., \& Amaral, L. A. N. (2005). Cartography of complex
networks: Modules and universal roles. \emph{Journal of Statistical
Mechanics: Theory and Experiment}, \emph{2005}(02), P02001.
doi:\href{https://doi.org/10.1088/1742-5468/2005/02/P02001}{10.1088/1742-5468/2005/02/P02001}

\hypertarget{ref-harvey_bridging_2017}{}
Harvey, E., Gounand, I., Ward, C. L., \& Altermatt, F. (2017). Bridging
ecology and conservation: From ecological networks to ecosystem
function. \emph{Journal of Applied Ecology}, \emph{54}(2), 371--379.
doi:\href{https://doi.org/10.1111/1365-2664.12769}{10.1111/1365-2664.12769}

\hypertarget{ref-henriksson_strong_2016}{}
Henriksson, A., Wardle, D. A., Trygg, J., Diehl, S., \& Englund, G.
(2016). Strong invaders are strong defenders - implications for the
resistance of invaded communities. \emph{Ecology Letters}, \emph{19}(4),
487--494.
doi:\href{https://doi.org/10.1111/ele.12586}{10.1111/ele.12586}

\hypertarget{ref-holland_population_2002}{}
Holland, J. N., DeAngelis, D. L., \& Bronstein, J. L. (2002). Population
Dynamics and Mutualism: Functional Responses of Benefits and Costs.
\emph{The American Naturalist}, \emph{159}(3), 231--244.
doi:\href{https://doi.org/10.1086/338510}{10.1086/338510}

\hypertarget{ref-isbell_human_2013}{}
Isbell, F., \& Loreau, M. (2013). Human impacts on minimum subsets of
species critical for maintaining ecosystem structure. \emph{Basic and
Applied Ecology}, \emph{14}(8), 623--629.
doi:\href{https://doi.org/10.1016/j.baae.2013.09.001}{10.1016/j.baae.2013.09.001}

\hypertarget{ref-jia_control_2013}{}
Jia, T., \& Barabási, A.-L. (2013). Control Capacity and A Random
Sampling Method in Exploring Controllability of Complex Networks.
\emph{Scientific Reports}, \emph{3}(1).
doi:\href{https://doi.org/10.1038/srep02354}{10.1038/srep02354}

\hypertarget{ref-jordan_keystone_2009}{}
Jordan, F. (2009). Keystone species and food webs. \emph{Philosophical
Transactions of the Royal Society B: Biological Sciences},
\emph{364}(1524), 1733--1741.
doi:\href{https://doi.org/10.1098/rstb.2008.0335}{10.1098/rstb.2008.0335}

\hypertarget{ref-jordano_ecological_2006}{}
Jordano, P., Bascompte, J., \& Olesen, J. M. (2006). The ecological
consequences of complex topology and nested structure in pollination
webs. In N. M. Waser \& J. Ollerton (Eds.), \emph{Plant-Pollinator
Interactions: From Specialization to Generalization} (pp. 173--199).
University of Chicago Press.

\hypertarget{ref-jordan_quantifying_2007}{}
Jordán, F., Benedek, Z., \& Podani, J. (2007). Quantifying positional
importance in food webs: A comparison of centrality indices.
\emph{Ecological Modelling}, \emph{205}(1-2), 270--275.
doi:\href{https://doi.org/10.1016/j.ecolmodel.2007.02.032}{10.1016/j.ecolmodel.2007.02.032}

\hypertarget{ref-kaiser-bunbury_ecosystem_2017}{}
Kaiser-Bunbury, C. N., Mougal, J., Whittington, A. E., Valentin, T.,
Gabriel, R., Olesen, J. M., \& Blüthgen, N. (2017). Ecosystem
restoration strengthens pollination network resilience and function.
\emph{Nature}, \emph{542}(7640), 223--227.
doi:\href{https://doi.org/10.1038/nature21071}{10.1038/nature21071}

\hypertarget{ref-kaiser-bunbury_robustness_2010}{}
Kaiser-Bunbury, C. N., Muff, S., Memmott, J., Müller, C. B., \&
Caflisch, A. (2010). The robustness of pollination networks to the loss
of species and interactions: A quantitative approach incorporating
pollinator behaviour. \emph{Ecology Letters}, \emph{13}(4), 442--452.
doi:\href{https://doi.org/10.1111/j.1461-0248.2009.01437.x}{10.1111/j.1461-0248.2009.01437.x}

\hypertarget{ref-kalman_mathematical_1963}{}
Kalman, R. E. (1963). Mathematical Description of Linear Dynamical
Systems. \emph{Journal of the Society for Industrial and Applied
Mathematics Series A Control}, \emph{1}(2), 152--192.
doi:\href{https://doi.org/10.1137/0301010}{10.1137/0301010}

\hypertarget{ref-lever_sudden_2014}{}
Lever, J. J., van Nes, E. H., Scheffer, M., \& Bascompte, J. (2014). The
sudden collapse of pollinator communities. \emph{Ecology Letters},
\emph{17}(3), 350--359.
doi:\href{https://doi.org/10.1111/ele.12236}{10.1111/ele.12236}

\hypertarget{ref-lin_structural_1974}{}
Lin, C. T. (1974). Structural Controllability. \emph{IEEE Transactions
on Automatic Control}, \emph{19}(3), 201--208.
doi:\href{https://doi.org/10.1109/TAC.1974.1100557}{10.1109/TAC.1974.1100557}

\hypertarget{ref-liu_control_2016}{}
Liu, Y.-Y., \& Barabási, A.-L. (2016). Control principles of complex
systems. \emph{Reviews of Modern Physics}, \emph{88}(3).
doi:\href{https://doi.org/10.1103/RevModPhys.88.035006}{10.1103/RevModPhys.88.035006}

\hypertarget{ref-liu_controllability_2011}{}
Liu, Y.-Y., Slotine, J.-J., \& Barabási, A.-L. (2011). Controllability
of complex networks. \emph{Nature}, \emph{473}(7346), 167--173.
doi:\href{https://doi.org/10.1038/nature10011}{10.1038/nature10011}

\hypertarget{ref-lopezaraizamikel_impact_2007}{}
Lopezaraiza\textendash{}Mikel, M. E., Hayes, R. B., Whalley, M. R., \&
Memmott, J. (2007). The impact of an alien plant on a native
plantPollinator network: An experimental approach. \emph{Ecology
Letters}, \emph{10}(7), 539--550.
doi:\href{https://doi.org/10.1111/j.1461-0248.2007.01055.x}{10.1111/j.1461-0248.2007.01055.x}

\hypertarget{ref-martin_gonzalez_centrality_2010}{}
Martín González, A. M., Dalsgaard, B., \& Olesen, J. M. (2010).
Centrality measures and the importance of generalist species in
pollination networks. \emph{Ecological Complexity}, \emph{7}(1), 36--43.
doi:\href{https://doi.org/10.1016/j.ecocom.2009.03.008}{10.1016/j.ecocom.2009.03.008}

\hypertarget{ref-mcdonald-madden_using_2016}{}
McDonald-Madden, E., Sabbadin, R., Game, E. T., Baxter, P. W. J.,
Chadès, I., \& Possingham, H. P. (2016). Using food-web theory to
conserve ecosystems. \emph{Nature Communications}, \emph{7}, 10245.
doi:\href{https://doi.org/10.1038/ncomms10245}{10.1038/ncomms10245}

\hypertarget{ref-melian_complex_2002}{}
Melián, C. J., \& Bascompte, J. (2002). Complex networks: Two ways to be
robust?: Complex networks: Two ways to be robust? \emph{Ecology
Letters}, \emph{5}(6), 705--708.
doi:\href{https://doi.org/10.1046/j.1461-0248.2002.00386.x}{10.1046/j.1461-0248.2002.00386.x}

\hypertarget{ref-memmott_tolerance_2004}{}
Memmott, J., Waser, N. M., \& Price, M. V. (2004). Tolerance of
pollination networks to species extinctions. \emph{Proceedings of the
Royal Society B: Biological Sciences}, \emph{271}(1557), 2605--2611.
doi:\href{https://doi.org/10.1098/rspb.2004.2909}{10.1098/rspb.2004.2909}

\hypertarget{ref-menge_indirect_1995}{}
Menge, B. A. (1995). Indirect Effects in Marine Rocky Intertidal
Interaction Webs: Patterns and Importance. \emph{Ecological Monographs},
\emph{65}(1), 21--74.
doi:\href{https://doi.org/10.2307/2937158}{10.2307/2937158}

\hypertarget{ref-mills_keystone-species_1993}{}
Mills, L. S., \& Doak, D. F. (1993). The Keystone-Species Concept in
Ecology and Conservation. \emph{BioScience}, \emph{43}(4), 219--224.
doi:\href{https://doi.org/10.2307/1312122}{10.2307/1312122}

\hypertarget{ref-motter_networkcontrology_2015}{}
Motter, A. E. (2015). Networkcontrology. \emph{Chaos}, \emph{25},
097621. doi:\href{https://doi.org/10.1063/1.4931570}{10.1063/1.4931570}

\hypertarget{ref-mouillot_functional_2013}{}
Mouillot, D., Graham, N. A., Villéger, S., Mason, N. W., \& Bellwood, D.
R. (2013). A functional approach reveals community responses to
disturbances. \emph{Trends in Ecology \& Evolution}, \emph{28}(3),
167--177.
doi:\href{https://doi.org/10.1016/j.tree.2012.10.004}{10.1016/j.tree.2012.10.004}

\hypertarget{ref-neeman_framework_2009}{}
Ne'eman, G., Jürgens, A., Newstrom-Lloyd, L., Potts, S. G., \& Dafni, A.
(2009). A framework for comparing pollinator performance: Effectiveness
and efficiency. \emph{Biological Reviews}, no--no.
doi:\href{https://doi.org/10.1111/j.1469-185X.2009.00108.x}{10.1111/j.1469-185X.2009.00108.x}

\hypertarget{ref-paine_note_1969}{}
Paine, R. T. (1969). A Note on Trophic Complexity and Community
Stability. \emph{The American Naturalist}, \emph{103}(929), 91--93.

\hypertarget{ref-palacio_generalist_2016}{}
Palacio, R. D., Valderrama-Ardila, C., \& Kattan, G. H. (2016).
Generalist Species Have a Central Role In a Highly Diverse
Plant-Frugivore Network. \emph{Biotropica}, \emph{48}(3), 349--355.
doi:\href{https://doi.org/10.1111/btp.12290}{10.1111/btp.12290}

\hypertarget{ref-pires_friendship_2017}{}
Pires, M. M., Marquitti, F. M., \& Guimarães, P. R. (2017). The
friendship paradox in species-rich ecological networks: Implications for
conservation and monitoring. \emph{Biological Conservation}, \emph{209},
245--252.
doi:\href{https://doi.org/10.1016/j.biocon.2017.02.026}{10.1016/j.biocon.2017.02.026}

\hypertarget{ref-poisot_comparative_2012}{}
Poisot, T., Canard, E., Mouquet, N., \& Hochberg, M. E. (2012). A
comparative study of ecological specialization estimators:
\emph{Species}\emph{-Level Specialization}. \emph{Methods in Ecology and
Evolution}, \emph{3}(3), 537--544.
doi:\href{https://doi.org/10.1111/j.2041-210X.2011.00174.x}{10.1111/j.2041-210X.2011.00174.x}

\hypertarget{ref-rohr_structural_2014}{}
Rohr, R. P., Saavedra, S., \& Bascompte, J. (2014). On the structural
stability of mutualistic systems. \emph{Science}, \emph{345}(6195),
1253497--1253497.
doi:\href{https://doi.org/10.1126/science.1253497}{10.1126/science.1253497}

\hypertarget{ref-saavedra_nested_2016}{}
Saavedra, S., Rohr, R. P., Olesen, J. M., \& Bascompte, J. (2016).
Nested species interactions promote feasibility over stability during
the assembly of a pollinator community. \emph{Ecology and Evolution},
\emph{6}(4), 997--1007.
doi:\href{https://doi.org/10.1002/ece3.1930}{10.1002/ece3.1930}

\hypertarget{ref-saavedra_strong_2011}{}
Saavedra, S., Stouffer, D. B., Uzzi, B., \& Bascompte, J. (2011). Strong
contributors to network persistence are the most vulnerable to
extinction. \emph{Nature}, \emph{478}(7368), 233--235.
doi:\href{https://doi.org/10.1038/nature10433}{10.1038/nature10433}

\hypertarget{ref-stouffer_how_2014}{}
Stouffer, D. B., Cirtwill, A. R., \& Bascompte, J. (2014). How exotic
plants integrate into pollination networks. \emph{Journal of Ecology},
\emph{102}(6), 1442--1450.
doi:\href{https://doi.org/10.1111/1365-2745.12310}{10.1111/1365-2745.12310}

\hypertarget{ref-stouffer_evolutionary_2012}{}
Stouffer, D. B., Sales-Pardo, M., Sirer, M. I., \& Bascompte, J. (2012).
Evolutionary Conservation of Species' Roles in Food Webs.
\emph{Science}, \emph{335}(6075), 1489--1492.
doi:\href{https://doi.org/10.1126/science.1216556}{10.1126/science.1216556}

\hypertarget{ref-thompson_food_2012}{}
Thompson, R. M., Brose, U., Dunne, J. A., Hall, R. O., Hladyz, S.,
Kitching, R. L., \ldots{} Tylianakis, J. M. (2012). Food webs:
Reconciling the structure and function of biodiversity. \emph{Trends in
Ecology \& Evolution}, \emph{27}(12), 689--697.
doi:\href{https://doi.org/10.1016/j.tree.2012.08.005}{10.1016/j.tree.2012.08.005}

\hypertarget{ref-traveset_invaders_2013}{}
Traveset, A., Heleno, R., Chamorro, S., Vargas, P., McMullen, C. K.,
Castro-Urgal, R., \ldots{} Olesen, J. M. (2013). Invaders of pollination
networks in the Galapagos Islands: Emergence of novel communities.
\emph{Proceedings of the Royal Society B: Biological Sciences},
\emph{280}(1758), 20123040--20123040.
doi:\href{https://doi.org/10.1098/rspb.2012.3040}{10.1098/rspb.2012.3040}

\hypertarget{ref-tylianakis_global_2008}{}
Tylianakis, J. M., Didham, R. K., Bascompte, J., \& Wardle, D. A.
(2008). Global change and species interactions in terrestrial
ecosystems. \emph{Ecology Letters}, \emph{11}(12), 1351--1363.
doi:\href{https://doi.org/10.1111/j.1461-0248.2008.01250.x}{10.1111/j.1461-0248.2008.01250.x}

\hypertarget{ref-tylianakis_conservation_2010}{}
Tylianakis, J. M., Laliberté, E., Nielsen, A., \& Bascompte, J. (2010).
Conservation of species interaction networks. \emph{Biological
Conservation}, \emph{143}(10), 2270--2279.
doi:\href{https://doi.org/10.1016/j.biocon.2009.12.004}{10.1016/j.biocon.2009.12.004}

\hypertarget{ref-vazquez_species_2007}{}
Vázquez, D. P., Melián, C. J., Williams, N. M., Blüthgen, N., Krasnov,
B. R., \& Poulin, R. (2007). Species Abundance and Asymmetric
Interaction Strength in Ecological Networks Author(s): Diego P. Vázquez,
Carlos J. Melián, Neal M. Williams, Nico Blüthgen, Boris R. Krasnov and
Robert Poulin. \emph{Oikos}, \emph{116}(7), 1120--1127.
doi:\href{https://doi.org/10.1111/j.2007.0030-1299.15828.x}{10.1111/j.2007.0030-1299.15828.x}

\hypertarget{ref-vazquez_interaction_2005}{}
Vázquez, D. P., Morris, W. F., \& Jordano, P. (2005). Interaction
frequency as a surrogate for the total effect of animal mutualists on
plants: Total effect of animal mutualists on plants. \emph{Ecology
Letters}, \emph{8}(10), 1088--1094.
doi:\href{https://doi.org/10.1111/j.1461-0248.2005.00810.x}{10.1111/j.1461-0248.2005.00810.x}

\hypertarget{ref-vila_invasive_2009}{}
Vila, M., Bartomeus, I., Dietzsch, A. C., Petanidou, T.,
Steffan-Dewenter, I., Stout, J. C., \& Tscheulin, T. (2009). Invasive
plant integration into native plant-pollinator networks across Europe.
\emph{Proceedings of the Royal Society B: Biological Sciences},
\emph{276}(1674), 3887--3893.
doi:\href{https://doi.org/10.1098/rspb.2009.1076}{10.1098/rspb.2009.1076}

\hypertarget{ref-woodford_confronting_2016}{}
Woodford, D. J., Richardson, D. M., MacIsaac, H. J., Mandrak, N. E., van
Wilgen, B. W., Wilson, J. R. U., \& Weyl, O. L. F. (2016). Confronting
the wicked problem of managing biological invasions. \emph{NeoBiota},
\emph{31}, 63--86.
doi:\href{https://doi.org/10.3897/neobiota.31.10038}{10.3897/neobiota.31.10038}

\hypertarget{ref-zhang_input_2016}{}
Zhang, X., Lv, T., \& Pu, Y. (2016). Input graph: The hidden geometry in
controlling complex networks. \emph{Scientific Reports}, \emph{6}(1).
doi:\href{https://doi.org/10.1038/srep38209}{10.1038/srep38209}

\end{document}

### 2019-01-13 paper/drafts_and_revisions/2018-07-19/supp-info.tex
Add a bunch of tex files from the drafts and revisions

\documentclass[a4paper]{artikel1}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\usepackage[margin=1in]{geometry}
\usepackage{hyperref}
\hypersetup{unicode=true,
            pdftitle={Keystoneness, centrality, and the structural controllability of ecological networks},
            pdfauthor={Fernando Cagua, Kate L. Wootton, Daniel B. Stouffer},
            pdfborder={0 0 0},
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls
\usepackage{longtable,booktabs}
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
\IfFileExists{parskip.sty}{%
\usepackage{parskip}
}{% else
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{5}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

%%% Use protect on footnotes to avoid problems with footnotes in titles
\let\rmarkdownfootnote\footnote%
\def\footnote{\protect\rmarkdownfootnote}

%%% Change title format to be more compact
\usepackage{titling}

% Create subtitle command for use in maketitle
\newcommand{\subtitle}[1]{
  \posttitle{
    \begin{center}\large#1\end{center}
    }
}

\setlength{\droptitle}{-2em}
  \title{Keystoneness, centrality, and the structural controllability of
ecological networks}
  \pretitle{\vspace{\droptitle}\centering\huge}
  \posttitle{\par}
\subtitle{Supporting Information}
  \author{Fernando Cagua, Kate L. Wootton, Daniel B. Stouffer}
  \preauthor{\centering\large\emph}
  \postauthor{\par}
  \date{}
  \predate{}\postdate{}

\usepackage{booktabs}
\usepackage{setspace}
\usepackage{xr}
\externaldocument[M-]{manuscript}
\usepackage{multirow}

\usepackage{amsthm}
\newtheorem{theorem}{Theorem}[section]
\newtheorem{lemma}{Lemma}[section]
\theoremstyle{definition}
\newtheorem{definition}{Definition}[section]
\newtheorem{corollary}{Corollary}[section]
\newtheorem{proposition}{Proposition}[section]
\theoremstyle{definition}
\newtheorem{example}{Example}[section]
\theoremstyle{definition}
\newtheorem{exercise}{Exercise}[section]
\theoremstyle{remark}
\newtheorem*{remark}{Remark}
\newtheorem*{solution}{Solution}
\begin{document}
\maketitle

\renewcommand\thefigure{S\arabic{figure}}

\setcounter{figure}{0}

\renewcommand\thetable{S\arabic{table}}

\setcounter{table}{0}

\renewcommand{\thesection}{S\arabic{section}}

\setcounter{section}{0}

\doublespacing

\section{Characteristics of the empirical
networks}\label{empirical-networks}

The networks studied had species richness ranging between 19 and 87 when
considering only the largest component in each network). As shown by the
network asymmetry \emph{AS} (N. Blüthgen, Menzel, Hovestadt, Fiala, \&
Blüthgen, 2007), the networks had a low ratio of plants to pollinators
overall. Furthermore, the networks had relatively low levels of
nestedness (when measured using the quantitative version of the NODF
index; Almeida-Neto \& Ulrich, 2011). Details for each network can be
found in the Table \ref{tab:table-network-properties}.

\begin{table}

\caption{\label{tab:table-network-properties}Properties of the analysed plant-pollinator communities. Here show the number of species ($n_s$), the number of plants ($n_p$), the number of pollinators ($n_a$), the network connectance ($c$), the network asymmetry ($AS$), and the network nestedness (NODF index). All properties correspond to the network's largest component. British networks were assembled by Lopezaraiza-Mikel et al. (2007), Spanish were networks assembled by Bartomeus et al. (2008).}
\centering
\fontsize{8}{10}\selectfont
\begin{tabular}[t]{rlrrrrrrl}
\toprule
site & invader & $n_s$ & $n_p$ & $n_a$ & $c$ & $AS$ & NODF & location\\
\midrule
1 & — & 35 & 9 & 26 & 0.17 & -0.49 & 8.68 & Cap de Creus, Spain\\
1 & \textit{Carpobrotus affine} & 57 & 10 & 47 & 0.17 & -0.65 & 13.27 & Cap de Creus, Spain\\
\addlinespace
2 & — & 40 & 10 & 30 & 0.16 & -0.50 & 11.66 & Cap de Creus, Spain\\
2 & \textit{Carpobrotus affine} & 38 & 11 & 27 & 0.21 & -0.42 & 15.04 & Cap de Creus, Spain\\
\addlinespace
3 & — & 31 & 7 & 24 & 0.19 & -0.55 & 12.91 & Cap de Creus, Spain\\
3 & \textit{Opuntia stricta} & 33 & 8 & 25 & 0.18 & -0.52 & 9.96 & Cap de Creus, Spain\\
\addlinespace
4 & — & 35 & 10 & 25 & 0.17 & -0.43 & 12.43 & Cap de Creus, Spain\\
4 & \textit{Carpobrotus affine} & 57 & 14 & 43 & 0.14 & -0.51 & 13.70 & Cap de Creus, Spain\\
\addlinespace
5 & — & 35 & 8 & 27 & 0.19 & -0.54 & 11.91 & Cap de Creus, Spain\\
5 & \textit{Opuntia stricta} & 32 & 8 & 24 & 0.19 & -0.50 & 10.96 & Cap de Creus, Spain\\
\addlinespace
6 & — & 30 & 9 & 21 & 0.17 & -0.40 & 6.91 & Cap de Creus, Spain\\
6 & \textit{Opuntia stricta} & 37 & 9 & 28 & 0.17 & -0.51 & 12.45 & Cap de Creus, Spain\\
\addlinespace
7 & — & 37 & 6 & 31 & 0.19 & -0.68 & 18.33 & Bristol, United Kingdom\\
7 & \textit{Impatients grandulifera} & 57 & 8 & 49 & 0.20 & -0.72 & 14.36 & Bristol, United Kingdom\\
\addlinespace
8 & — & 48 & 5 & 43 & 0.21 & -0.79 & 5.87 & Bristol, United Kingdom\\
8 & \textit{Impatients grandulifera} & 87 & 15 & 72 & 0.11 & -0.66 & 8.12 & Bristol, United Kingdom\\
\addlinespace
9 & — & 55 & 12 & 43 & 0.13 & -0.56 & 13.01 & Bristol, United Kingdom\\
9 & \textit{Impatients grandulifera} & 86 & 11 & 75 & 0.13 & -0.74 & 13.40 & Bristol, United Kingdom\\
\addlinespace
10 & — & 19 & 3 & 16 & 0.38 & -0.68 & 9.99 & Bristol, United Kingdom\\
10 & \textit{Impatients grandulifera} & 54 & 6 & 48 & 0.21 & -0.78 & 7.56 & Bristol, United Kingdom\\
\bottomrule
\end{tabular}
\end{table}

\clearpage

\section{Structural controllability}\label{structural-controllability}

Structural controllability avoids the limitation of not knowing the
exact values of the matrices \emph{A} and \emph{B}. Structural
controllability boils down to two conditions: a system is controllable
if there are no inaccessible nodes or dilations. A node is inaccessible
if there are no directed paths between it and the input nodes.
``Dilations are subgraphs in which a small subset of nodes attempts to
rule a larger subset of nodes. In other words, there are more
`subordinates' than `superiors'\,'' (Liu \& Barabási, 2016).

The goal of structural controllability is to use the information
contained in \textbf{A} to generate a supportable estimate of
\textbf{B}. This focus allows us to gain insight of the inherent
controllability of a network, and the roles of the species that compose
it, without being overly dependent on the particular choices of how the
system dynamics are modelled or characterised. The trade-off of this
approach is that, because of the assumption of linearity, structural
controllability alone does not allow us to fully design the time-varying
control signal \emph{u(t)} that can drive the system from one particular
equilibrium to another. Nevertheless, the lessons gained when assuming
linearity---at both the network and the species level---are a
prerequisite for eventually understanding nonlinear control (Liu \&
Barabási, 2016; Liu, Slotine, \& Barabási, 2011).

\newpage

\section{Maximum matching}\label{maximum-matching}

\subsection{Finding a single maximum
matching}\label{one-maximum-matching}

Our approach to finding the minimum number of driver nodes relies on
finding maximum matchings. We start with a directed network in which the
direction of the link represents the direction of control (Figure
\ref{fig:fig-maximum-matching-procedure} left panel). We then construct
an alternative representation of the directed network in which each node
of the directed network is represented by two nodes that indicate their
outgoing and incoming links respectively (Figure
\ref{fig:fig-maximum-matching-procedure} centre panel). Finding a
maximum matching in this alternative representation is equivalent to
finding the largest possible set of edges in which one node on the
left-hand side is connected to at most one node on the right-hand side.
To find the maximum matching we use the push-relabel algorithm
implemented in \texttt{max\_bipartite\_matching} in the R package igraph
1.0.1 (Csardi \& Nepusz, 2006). Once we have the matching (shown in the
Figure \ref{fig:fig-maximum-matching-procedure} center panel) it is then
easy to identify the roles of each node in this representation: nodes on
the top-level that are connected to a matched link (dark purple) are
superior while those connected to a matched link on the bottom-level are
matched. This information can then be mapped back to the original
representation to identify the control paths and the driver nodes in the
network (Figure \ref{fig:fig-maximum-matching-procedure} right panel).

\begin{figure}[p]

{\centering \includegraphics{/Users/efc29/github/driver-species/paper/supp-info_files/figure-latex/fig-maximum-matching-procedure-1}

}

\caption{Finding a maximum matching in a complex network. (left) Directed network that indicate the direction of control between species. (center) Alternative bipartite representations of the directed networks. (right) The matchings in the bipartite representation mapped back to the original network.}\label{fig:fig-maximum-matching-procedure}
\end{figure}

To further illustrate our methodology here, we also show the approach
for the smallest of our empirical networks, the uninvaded network at
site 10 (Table \ref{tab:table-network-properties}; Figure
\ref{fig:fig-small-network}). This network is composed of 19 species of
which three are non-invasive plants and the other 16 are pollinators.
The one-to-one relationship between matched and superior nodes implies
that in order to achieve full network controllability, most pollinators
would be unmatched, and hence are classified as driver nodes that
require external intervention. At the same time, both plants in the
community, \emph{Heracleum sphondylum} and \emph{Rubus fructicosus}, and
one of the pollinators, \emph{Orthotylus/Lygocorus}, tend to be
classified as superior nodes.

\begin{figure}
\centering
\includegraphics{/Users/efc29/github/driver-species/paper/supp-info_files/figure-latex/fig-small-network-1.pdf}
\caption{\label{fig:fig-small-network}Illustration of the procedure with an
empirical community. The visitation network (top), the number of visits
between species pairs are shown on each link. The directed network in
which the direction of control is determined based on the mutual
dependences (middle). One of the possible maximum matchings of this
network (bottom).}
\end{figure}

\subsection{Finding all possible maximum
matchings}\label{all-maximum-matching}

The algorithm implemented in \texttt{max\_bipartite\_matching}, however,
is only able to find \textbf{one} of possibly many maximum matchings in
a network. Though one maximum matching is enough to calculate
\emph{n\textsubscript{D}} and hence to provide an indication of the
manageability of a community, it is not sufficient to estimate the role
of individual species. To do that, we need to calculate all possible
maximum matchings. To do this, we again start from the alternative
bipartite representation in Figure
\ref{fig:fig-maximum-matching-procedure}b and assign an identity to each
of the links in the network. We will call this bipartite representation
\emph{P}. We then construct the line graph of the alternative bipartite
representation \emph{L(P)} (Figure \ref{fig:fig-all-maximum-matching}).
Each node in \emph{L(P)} represents a link in \emph{P} and these are
connected to each other if and only if they share a common node in
\emph{P}. We then calculate \emph{H}, the complement graph of
\emph{L(P)} and identify all of its maximal cliques (Figure
\ref{fig:fig-all-maximum-matching}). Here some extra definitions are
necessary. First, \emph{H} is a graph with the same nodes as \emph{L(P)}
but that has a link between two nodes if and only if there is not a link
in \emph{L(P)}. Second, a clique is a subset of nodes such that all
pairs of them are linked. Lastly, a maximal clique is a clique such that
there are no cliques composed of more nodes (Gutin, 2013). In this
example, there are two maximal cliques. The final step is then to map
these cliques onto the original network to obtain all possible maximal
cardinality matchings as shown in Figure
\ref{M-fig:fig-control-configuration} in the main text.

\begin{figure}
\centering
\includegraphics{/Users/efc29/github/driver-species/paper/supp-info_files/figure-latex/fig-all-maximum-matching-1.pdf}
\caption{\label{fig:fig-all-maximum-matching}Finding all possible maximum
matchings. From left to right: alternative bipartite representation of
the directed network. Line graph of the network. The complement of the
network. The two maximal cliques are shown in dark purple.}
\end{figure}

\clearpage

\subsection{Control adjacency and the input graph}\label{input-graph}

The algorithm proposed by Zhang, Lv, \& Pu (2016) enable us to find all
minimum driver node sets without calculating all possible maximum
matchings. The algorithm is based on the construction of the input graph
of the directed network. Components in the input graph reveal the
correlations between nodes from a structural control perspective (Figure
\ref{fig:fig-input-graph}). The input graph is constructed based on the
\emph{control adjacency} of nodes in a maximum matching. Two nodes
\(x_i\) and \(x_j\) are said to be control adjacent if there is a node
\(x_k\) connecting \(x_i\) and \(x_j\) with an unmatched link
\(x_k-x_i\) and a matched link \(x_k-x_j\). For example \(a_1\) is
control adjacent to \(a_2\) in the top panel of Figure
\ref{fig:fig-input-graph}. If a node \(x_i\) is part of a minimum driver
node set then every node in the same component of \(x_i\) in the input
graph is a possible driver node.

\begin{figure}
\centering
\includegraphics{/Users/efc29/github/driver-species/paper/supp-info_files/figure-latex/fig-input-graph-1.pdf}
\caption{\label{fig:fig-input-graph}Input graph. Two nodes \(x_i\) and
\(x_j\) are said to be control adjacent if there is a node \(x_k\)
connecting \(x_i\) and \(x_j\) with an unmatched link \(x_k-x_i\) and a
matched link \(x_k-x_j\). For example, in the top panel, \(a_1\) is
control adjacent to \(a_2\) (via \(p_2\)), \(p_1\) is control adjacent
to \(p_3\) (via \(a_1\)) and \(p_2\) has no control adjacent nodes. As
\(a_1\) and \(p_2\) belong to the minimum driver node set under the
control configuration found with the maximum matching shown, then every
node in the same component as these two nodes is also a possible driver
node. By combining the nodes from the components with minimum driver
node sets is possible to enumerate the different control configurations.
For example the network in the top panel has two possible minimum driver
node sets \([p_2, a_1]\) and \([p_2, a_2]\) (Figure
\ref{M-fig:fig-control-configuration}). The network in the middle panel
has three minimum driver node sets \([x_1, x_2]\), \([x_1, x_3]\), and
\([x_1, x_4]\). Finally the network in the bottom pannel has only one
\([x_1]\).}
\end{figure}

In order to calculate a node's control capacity \(\phi\), we harness the
fact that nodes can be classified into three groups according to their
role in the input graph. First, if \(x_i\) belongs to the minimum driver
node set and has no adjacent nodes, then it cannot be replaced and will
be part of every possible control configuration. Second, if \(x_i\) does
not belong to the minimum driver node set and is not adjacent to any
possible input node, then it does not part of the minimum driver node
set under any control configuration. Finally, if a node \(x_i\) belongs
to the minimum driver node set and is adjacent to another node \(x_j\)
in the input graph, then \(x_j\) must belong to another minimum driver
node to which \(x_i\) does not belong, in other words, \(x_i\) and
\(x_j\) are substitutable.

The first and the second group have a control capacity of \(\phi = 1\)
and \(\phi = 0\) respectively. Meanwhile, the third group has
intermediate values of control capacity which can be calculated by
computing the number of possible substitutions of a node by its control
adjacent nodes. As a rule of thumb, the largest the number of possible
substitutions an input node has, the smaller its control capacity.

For larger networks, calculating the control capacities using the input
graph is several orders of magnitude faster than computing all possible
maximum matchings. While the computation time of the input graph grows
linearly with network size, the computation of all maximum matchings
grows polynomially. However, the control capacities obtained using the
input graph are not identical to those obtained by computing all
possible maximum matchings. The reason for this discrepancy is that two
maximum matchings might result in the same minimum driver node set.
Nevertheless, the results obtained using both approaches are extremely
similar. We compared the control capacity obtained by calculating all
maximum matchings and that obtained using the input graph in 13 of our
networks (those for which we were able to calculate all maximum
matchings within a reasonable time). The Spearman correlation was very
high in all cases, ranging between 0.89 and 1 (median 0.98).

\clearpage

\subsection{Networks with reciprocal links}\label{reciprocal-links}

Our procedures to find minimum driver node sets are only adequate when
there are no reciprocal (bidirectional) links in the network. The
proportion of reciprocal links in relatively low. In fact, the
proportion of species pairs that are reciprocally connected in our
empirical networks is just 2.97\%. However, reciprocal links are not a
rare occurrence as 16 out of 20 empirical networks had at least one. To
calculate our controllability metrics at both the network (the relative
size of the minimum driver node set, \(n_D\)) and species level (control
capacity, \(\phi\), and the likelihood of being a superior node,
\(\sigma\)) we first need to generate all possible versions of the of
the network that include only non-reciprocal links (Figure
\ref{fig:fig-bidirectional}).

All of these non-reciprocal networks are as likely to be one that best
represents the superior/matched relationships in the network. As such,
we average the three metrics (\(n_D\), \(\phi\), and \(\sigma\)) across
all the networks without reciprocal links without weighting by the
number of possible control configurations.

\begin{figure}
\centering
\includegraphics{/Users/efc29/github/driver-species/paper/supp-info_files/figure-latex/fig-bidirectional-1.pdf}
\caption{\label{fig:fig-bidirectional}In order to calculate the
controllability metrics for a network with reciprocal links (left), we
first decompose the network into several versions that contain no
reciprocal links (right). As each of these networks represents a
different equiprobable scenario, the controllability metrics for the
network with reciprocal links are the unweighted mean of these metrics
across the non-reciprocal networks.}
\end{figure}

\clearpage

\section{Structural stability}\label{structural-stability}

We follow R. P. Rohr, Saavedra, \& Bascompte (2014) and S. Saavedra,
Rohr, Olesen, \& Bascompte (2016) to calculate the structural stability
of the empirical networks. We first calculate the stability condition
\(\hat{\gamma}\) using all species in the network. To calculate the
contribution to stable coexistence of a given species, we removed the
focal species from the network and then calculated the corresponding
structural stability \(\Omega\) for a level of mutualism equal to the
stability condition found previously. For simplicity, in the main text
we show results for when there is a mutualistic trade-off of
\(\delta = 0\) and a mean interspecific competition of \(\rho = 0.01\)
(S. Saavedra et al., 2016). The choice of the parameters had only a
minor impact on the relative contribution of species to stable
coexistence (Figure \ref{fig:fig-rho-sensitivity}a) and overall there
was no change on our result that indicates that critical species (those
with \(\phi = 1\)) have a larger than average contribution to stable
coexistence (Figure \ref{fig:fig-rho-sensitivity}b).

\begin{figure}[p]

{\centering \includegraphics{/Users/efc29/github/driver-species/paper/supp-info_files/figure-latex/fig-rho-sensitivity-1}

}

\caption{A sensitivity analysis of the impact of interspecific competition parameter $\rho$ on structural stability reveals that the choice of parameters has a negligible impact on the results. (a) Spearman correlation coefficient of the contribution to stable coexistence of species. Lighter lines indicate the correlation coeficient for each of the twenty empirical networks. The dark line indicates the median value. (b) Difference between the conribution to stable coexistence of critical and redundant species for different values of the iterspecific competition parameters $\rho$.}\label{fig:fig-rho-sensitivity}
\end{figure}

\clearpage

\section{Visitation as a proxy for species
dependence}\label{visitation-as-proxy}

Visitation frequency has been shown to be an appropriate surrogate for
inter-specific effects in pollination networks (Bascompte, Jordano, \&
Olesen, 2006; Vázquez, Morris, \& Jordano, 2005). Nevertheless,
visitation is not equivalent to pollen deposition and might be
insufficient to reflect the dependences of plants on animals and vice
versa (Alarcón, 2010; King, Ballantyne, \& Willmer, 2013). We,
therefore, investigated the effect of calculating the dependences using
visitation or pollination effectiveness and importance---two metrics
more proximate to plant reproductive success. We did this by comparing
\emph{(i)} the size of the minimum driver node set \(n_D\) of the
community, \emph{(ii)} the species' control capacity and, \emph{(iii)}
the species' probability of being a superior node. To do this, we used
data collected by G. Ballantyne, Baldock, \& Willmer (2015) from a low
diversity pollination community at a dry lowland heathland in Dorset, UK
(50° 43.7'N 2° 07.2'W). First, deposition networks were quantified using
the mean single visit deposition---the number of conspecific pollen
grains effectively deposited on a virgin stigma during a single visit by
a particular animal (G. Ballantyne et al., 2015; King et al., 2013;
Ne'eman, Jürgens, Newstrom-Lloyd, Potts, \& Dafni, 2009). Second,
visitation networks were constructed by counting the visits to flowers
during Single Visit Depositions. Finally, pollinator importance networks
were constructed as the product of pollinator efficiency and visit
frequency.

At a network scale the driver-node density \(n_D\) was consistent among
the three weighting schemes (0.67 for deposition, 0.67 for the
visitation, and 0.62 for the pollinator-importance network,
respectively). The choice of weighting can also have an impact on at the
species level. Therefore we calculated \(\phi\) and \(\sigma\) and
calculated it's correlation among all three weighting schemes. Although
visitation and efficiency (pollen deposition) produce moderately
different results, we found a very strong agreement between the order
produced by visitation and importance which is arguably a more accurate
metric of interspecific effects (Table
\ref{tab:tab-assumption-visitation}).

\begin{table}[!h]

\caption{\label{tab:tab-assumption-visitation}Spearman correlation coefficient matrix between the control capacity and the probability obtained by weighting links by the visitation, pollinator efficiency and pollinator importance.}
\centering
\fontsize{8}{10}\selectfont
\begin{tabular}[t]{lrrr}
\toprule
 & efficiency & importance & visitation\\
\midrule
\addlinespace[0.3em]
\multicolumn{4}{l}{\textbf{control capacity}}\\
\hspace{1em}efficiency & 1.00 & 0.37 & 0.38\\
\hspace{1em}importance & 0.37 & 1.00 & 0.86\\
\hspace{1em}visitation & 0.38 & 0.86 & 1.00\\
\addlinespace[0.3em]
\multicolumn{4}{l}{\textbf{superior probability}}\\
\hspace{1em}efficiency & 1.00 & 0.69 & 0.57\\
\hspace{1em}importance & 0.69 & 1.00 & 0.90\\
\hspace{1em}visitation & 0.57 & 0.90 & 1.00\\
\bottomrule
\end{tabular}
\end{table}

Altogether, the evidence supports the idea that visitation is a suitable
metric to estimate the mutual dependence of species pairs. First, it is
directly related to pollinator foraging. Second, it produces results
within our controllability framework that are consistent with plant
reproductive success (as estimated by the importance metric).

\clearpage

\section{Sensitivity to sampling}\label{undersampling}

Our approach is fundamentally based on the network structure. Often, the
majority of the interactions that make up this structure are weak; in
our networks, this means that most interactions are formed by a small
number of observed pollination visits, and therefore those weak
interactions are less conspicuous in the field than strong ones. To
strengthen the case of our approach, we, therefore, evaluated the
robustness of our results to simulated sampling limitations.

To do so we removed a portion of the visits, for each network, and
calculated how three control metrics of the subsampled network compare
to those of the full network. Specifically, we calculated the difference
between the relative size of the minimum driver node set \(n_D\) of the
subsampled and the full network, the Spearman correlation between the
control capacities \(\phi\) and the probability of being a superior node
\(\sigma\) that were obtained for the empirical network and subsamples
of it. Finally, we also compared the control capacity of critical
species (\(\phi=1\)) across the different subsamples. We removed up to
20\% of the interactions in 1\% increments. We repeated the procedure
for each network to obtain a total sample size of \(n=400\).

Overall, the results of the sensitivity analysis indicate that our
approach is likely to still be useful in the absence of complete
sampling. Specifically, as the proportion of sampled interaction
decreased, the variability of \(n_D\) increased but was overall similar
to that obtained when using all available interactions (Figure
\ref{fig:fig-assumption-sampling-nd}). Similarly, the correlation
between \(\phi\) and \(\sigma\) of empirical and subsampled networks was
high even for extreme levels of undersampling (Figure
\ref{fig:fig-assumption-sampling-cor}). Importantly, critical species in
the empirical networks were also critical species in the subsampled
networks in a large majority of cases (Figure
\ref{fig:fig-assumption-sampling-crit}).

\begin{figure}[p]

{\centering \includegraphics{/Users/efc29/github/driver-species/paper/supp-info_files/figure-latex/fig-assumption-sampling-nd-1}

}

\caption{Difference between the size of the minimum driver node set of the empirical network and the subsampled network. Lighter lines indicate the changes for each networks and the darker line indicates the overall trend.}\label{fig:fig-assumption-sampling-nd}
\end{figure}

\begin{figure}
\centering
\includegraphics{/Users/efc29/github/driver-species/paper/supp-info_files/figure-latex/fig-assumption-sampling-cor-1.pdf}
\caption{\label{fig:fig-assumption-sampling-cor}Spearman correlation between
the control capacity and the probability of being a superior nodes of
the empirical networks and subsampled networks. Lighter lines indicate
the changes for each networks and the darker line indicates the overall
trend.}
\end{figure}

\begin{figure}
\centering
\includegraphics{/Users/efc29/github/driver-species/paper/supp-info_files/figure-latex/fig-assumption-sampling-crit-1.pdf}
\caption{\label{fig:fig-assumption-sampling-crit}Control capacity of
critical species (those with \(\phi = 1\) in the empirical network) in
subsampled networks. Lighter lines indicate the changes for each
networks and the darker line indicates the overall trend.}
\end{figure}

\clearpage

\begin{table}

\caption{\label{tab:tab-controllability-model-results}Model selection table based on the Akaike Information Criterion for small samples for candidate models of size of the minimum driver node set ($n_D$) in the empirical networks. There was no evidence for any of the evaluated predictors: the invasion status (inv), the network connectance (c), the network nestedness (NODF) the number of species ($n_S$) the network asymmetry ($AS_s$) or the interaction strength asymmetry ($AS_s$). Only candidate models with a weight $>0.01$ are shown.}
\centering
\fontsize{8}{10}\selectfont
\begin{tabular}[t]{rrrlrlrrrrr}
\toprule
(Intercept) & C & $AS_s$ & inv & $n_s$ & study & $AS_n$ & NODF & df & delta & weight\\
\midrule
0.89 & -0.40 & --- & --- & -0.20 & --- & -0.50 & -0.19 & 6 & 0.00 & 0.21\\
1.07 & --- & -0.11 & --- & --- & --- & -0.31 & --- & 4 & 1.33 & 0.11\\
0.95 & -0.38 & --- & --- & -0.20 & --- & -0.50 & --- & 5 & 1.46 & 0.10\\
1.03 & --- & -0.10 & --- & --- & --- & -0.31 & -0.15 & 5 & 2.23 & 0.07\\
0.84 & -0.42 & --- & --- & -0.22 & + & -0.46 & -0.20 & 7 & 2.91 & 0.05\\
1.02 & -0.11 & -0.13 & --- & --- & --- & -0.31 & --- & 5 & 2.91 & 0.05\\
0.98 & -0.11 & -0.12 & --- & --- & --- & -0.31 & -0.16 & 6 & 3.66 & 0.03\\
1.07 & --- & --- & --- & --- & --- & -0.38 & --- & 3 & 3.79 & 0.03\\
1.02 & --- & --- & --- & --- & --- & -0.38 & -0.18 & 4 & 3.90 & 0.03\\
0.91 & -0.34 & -0.04 & --- & -0.16 & --- & -0.45 & -0.18 & 7 & 4.09 & 0.03\\
0.97 & -0.30 & -0.06 & --- & -0.14 & --- & -0.43 & --- & 6 & 4.32 & 0.02\\
0.90 & -0.40 & --- & --- & -0.21 & + & -0.47 & --- & 6 & 4.43 & 0.02\\
0.88 & -0.41 & --- & + & -0.21 & --- & -0.51 & -0.20 & 7 & 4.65 & 0.02\\
1.06 & --- & -0.12 & --- & 0.02 & --- & -0.29 & --- & 5 & 4.75 & 0.02\\
1.07 & --- & -0.11 & + & --- & --- & -0.31 & --- & 5 & 4.93 & 0.02\\
1.07 & --- & -0.11 & --- & --- & + & -0.31 & --- & 5 & 4.95 & 0.02\\
0.95 & -0.38 & --- & + & -0.20 & --- & -0.51 & --- & 6 & 5.62 & 0.01\\
1.08 & --- & --- & --- & -0.04 & --- & -0.40 & --- & 4 & 5.97 & 0.01\\
\bottomrule
\end{tabular}
\end{table}

\begin{table}

\caption{\label{tab:tab-model-output-species-level}Summary table of the control capacity model with the smallest AICc.}
\centering
\fontsize{8}{10}\selectfont
\begin{tabular}[t]{lrrrr}
\toprule
term & estimate & std.error & statistic & p.value\\
\midrule
(Intercept) & -1.20 & 0.37 & -3.21 & 0.00\\
visitation strength & 0.29 & 0.16 & 1.86 & 0.06\\
contribution to nestedness & 0.15 & 0.14 & 1.05 & 0.29\\
asymmetry & 0.80 & 0.25 & 3.14 & 0.00\\
level (pol.) & 2.70 & 0.39 & 6.96 & 0.00\\
\addlinespace
contribution to nestedness:level (pol.) & 0.32 & 0.19 & 1.70 & 0.09\\
asymmetry:level (pol.) & -1.98 & 0.28 & -7.17 & 0.00\\
\bottomrule
\end{tabular}
\end{table}

\begin{table}

\caption{\label{tab:tab-var-importance}Variable importance for control capacity models. The importance is the sum of the weights of all models in which the variable was included.}
\centering
\fontsize{8}{10}\selectfont
\begin{tabular}[t]{lr}
\toprule
term & importance\\
\midrule
level (pol.) & 1.00\\
asymmetry & 1.00\\
asymmetry:level (pol.) & 1.00\\
visitation strength & 0.93\\
contribution to nestedness & 0.91\\
contribution to nestedness:level (pol.) & 0.79\\
visitation strength:level (pol.) & 0.39\\
degree & 0.28\\
degree:level (pol.) & 0.25\\
\bottomrule
\end{tabular}
\end{table}

\begin{figure}
\centering
\includegraphics{/Users/efc29/github/driver-species/paper/supp-info_files/figure-latex/fig-species-models-degree-1.pdf}
\caption{\label{fig:fig-species-models-degree}Relationship between degree
and (a) control capacity and (b) the probability of being a superior
node.}
\end{figure}

\begin{figure}
\centering
\includegraphics{/Users/efc29/github/driver-species/paper/supp-info_files/figure-latex/fig-correlogram-1.pdf}
\caption{\label{fig:fig-correlogram}Mean Spearman correlation coefficients
between control metrics (control capcity \(\phi\) and the likelyhood of
being a superior node \(\sigma\)) and centrality metrics commonly used
to estimate a species' `keystoness' (closeness centrality \(l\) ,
betwenness \(w\), eigen centrality \(e\), page rank \(g\) and degre
\(k\)) in each of the networks. Purple and orange tiles indicate a
positive correlation or negative correlation respectively.}
\end{figure}

\clearpage

\section*{References}\label{references}
\addcontentsline{toc}{section}{References}

\hypertarget{refs}{}
\hypertarget{ref-alarcon_congruence_2010}{}
Alarcón, R. (2010). Congruence between visitation and pollen-transport
networks in a California plantPollinator community. \emph{Oikos},
\emph{119}(1), 35--44.
doi:\href{https://doi.org/10.1111/j.1600-0706.2009.17694.x}{10.1111/j.1600-0706.2009.17694.x}

\hypertarget{ref-almeida-neto_straightforward_2011}{}
Almeida-Neto, M., \& Ulrich, W. (2011). A straightforward computational
approach for measuring nestedness using quantitative matrices.
\emph{Environmental Modelling \& Software}, \emph{26}(2), 173--178.
doi:\href{https://doi.org/10.1016/j.envsoft.2010.08.003}{10.1016/j.envsoft.2010.08.003}

\hypertarget{ref-ballantyne_constructing_2015}{}
Ballantyne, G., Baldock, K. C. R., \& Willmer, P. G. (2015).
Constructing more informative plantPollinator networks: Visitation and
pollen deposition networks in a heathland plant community.
\emph{Proceedings of the Royal Society B: Biological Sciences},
\emph{282}(1814), 20151130.
doi:\href{https://doi.org/10.1098/rspb.2015.1130}{10.1098/rspb.2015.1130}

\hypertarget{ref-bascompte_asymmetric_2006}{}
Bascompte, J., Jordano, P., \& Olesen, J. M. (2006). Asymmetric
Coevolutionary Networks Facilitate Biodiversity Maintenance.
\emph{Science}, \emph{312}(5772), 431--433.
doi:\href{https://doi.org/10.1126/science.1123412}{10.1126/science.1123412}

\hypertarget{ref-bluthgen_specialization_2007}{}
Blüthgen, N., Menzel, F., Hovestadt, T., Fiala, B., \& Blüthgen, N.
(2007). Specialization, Constraints, and Conflicting Interests in
Mutualistic Networks. \emph{Current Biology}, \emph{17}(4), 341--346.
doi:\href{https://doi.org/10.1016/j.cub.2006.12.039}{10.1016/j.cub.2006.12.039}

\hypertarget{ref-Csardi2006a}{}
Csardi, G., \& Nepusz, T. (2006). The igraph software package for
complex network research. \emph{InterJournal, Complex Systems},
\emph{1695}(5), 1--9.

\hypertarget{ref-Gutin2013}{}
Gutin, G. (2013). Independence and Cliques. In P. Zhang (Ed.),
\emph{Handbook of Graph Theory} (Second Edi, pp. 475--489). Chapman and
Hall/CRC.
doi:\href{https://doi.org/10.1201/b16132-31}{10.1201/b16132-31}

\hypertarget{ref-king_why_2013}{}
King, C., Ballantyne, G., \& Willmer, P. G. (2013). Why flower
visitation is a poor proxy for pollination: Measuring single-visit
pollen deposition, with implications for pollination networks and
conservation. \emph{Methods in Ecology and Evolution}, \emph{4}(9),
811--818.
doi:\href{https://doi.org/10.1111/2041-210X.12074}{10.1111/2041-210X.12074}

\hypertarget{ref-liu_control_2016}{}
Liu, Y.-Y., \& Barabási, A.-L. (2016). Control principles of complex
systems. \emph{Reviews of Modern Physics}, \emph{88}(3).
doi:\href{https://doi.org/10.1103/RevModPhys.88.035006}{10.1103/RevModPhys.88.035006}

\hypertarget{ref-liu_controllability_2011}{}
Liu, Y.-Y., Slotine, J.-J., \& Barabási, A.-L. (2011). Controllability
of complex networks. \emph{Nature}, \emph{473}(7346), 167--173.
doi:\href{https://doi.org/10.1038/nature10011}{10.1038/nature10011}

\hypertarget{ref-neeman_framework_2009}{}
Ne'eman, G., Jürgens, A., Newstrom-Lloyd, L., Potts, S. G., \& Dafni, A.
(2009). A framework for comparing pollinator performance: Effectiveness
and efficiency. \emph{Biological Reviews}, no--no.
doi:\href{https://doi.org/10.1111/j.1469-185X.2009.00108.x}{10.1111/j.1469-185X.2009.00108.x}

\hypertarget{ref-rohr_structural_2014}{}
Rohr, R. P., Saavedra, S., \& Bascompte, J. (2014). On the structural
stability of mutualistic systems. \emph{Science}, \emph{345}(6195),
1253497--1253497.
doi:\href{https://doi.org/10.1126/science.1253497}{10.1126/science.1253497}

\hypertarget{ref-saavedra_nested_2016}{}
Saavedra, S., Rohr, R. P., Olesen, J. M., \& Bascompte, J. (2016).
Nested species interactions promote feasibility over stability during
the assembly of a pollinator community. \emph{Ecology and Evolution},
\emph{6}(4), 997--1007.
doi:\href{https://doi.org/10.1002/ece3.1930}{10.1002/ece3.1930}

\hypertarget{ref-vazquez_interaction_2005}{}
Vázquez, D. P., Morris, W. F., \& Jordano, P. (2005). Interaction
frequency as a surrogate for the total effect of animal mutualists on
plants: Total effect of animal mutualists on plants. \emph{Ecology
Letters}, \emph{8}(10), 1088--1094.
doi:\href{https://doi.org/10.1111/j.1461-0248.2005.00810.x}{10.1111/j.1461-0248.2005.00810.x}

\hypertarget{ref-zhang_input_2016}{}
Zhang, X., Lv, T., \& Pu, Y. (2016). Input graph: The hidden geometry in
controlling complex networks. \emph{Scientific Reports}, \emph{6}(1).
doi:\href{https://doi.org/10.1038/srep38209}{10.1038/srep38209}

\end{document}

### 2019-01-13 paper/drafts_and_revisions/2019-01-14/reviewers-response.tex
Add revision with most responses to reviewers

\documentclass[a4paper]{artikel1}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\usepackage[margin=1in]{geometry}
\usepackage{hyperref}
\hypersetup{unicode=true,
            pdftitle={Keystoneness, centrality, and the structural controllability of ecological networks},
            pdfauthor={Fernando Cagua, Kate L. Wootton, Daniel B. Stouffer},
            pdfborder={0 0 0},
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls
\usepackage{longtable,booktabs}
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
\IfFileExists{parskip.sty}{%
\usepackage{parskip}
}{% else
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{0}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

%%% Use protect on footnotes to avoid problems with footnotes in titles
\let\rmarkdownfootnote\footnote%
\def\footnote{\protect\rmarkdownfootnote}

%%% Change title format to be more compact
\usepackage{titling}

% Create subtitle command for use in maketitle
\newcommand{\subtitle}[1]{
  \posttitle{
    \begin{center}\large#1\end{center}
    }
}

\setlength{\droptitle}{-2em}
  \title{Keystoneness, centrality, and the structural controllability of
ecological networks}
  \pretitle{\vspace{\droptitle}\centering\huge}
  \posttitle{\par}
\subtitle{JEcol-2018-0545 - Detailed response to comments}
  \author{Fernando Cagua, Kate L. Wootton, Daniel B. Stouffer}
  \preauthor{\centering\large\emph}
  \postauthor{\par}
  \date{}
  \predate{}\postdate{}

\usepackage{setspace}
\usepackage{xr}
\usepackage{lineno}
\newcommand{\R}[1]{\label{#1}\linelabel{#1}}
\newcommand{\lr}[1]{page~\pageref{#1}, line~\lineref{#1}}
\externaldocument[M-]{manuscript}
\externaldocument[S-]{supp-info}
\usepackage[most]{tcolorbox}
\definecolor{block-gray}{gray}{0.9}
\newtcolorbox{myquote}{colback=block-gray,grow to right by=-10mm,grow to left by=-10mm, boxrule=0pt,boxsep=0pt,breakable}

\usepackage{amsthm}
\newtheorem{theorem}{Theorem}
\newtheorem{lemma}{Lemma}
\theoremstyle{definition}
\newtheorem{definition}{Definition}
\newtheorem{corollary}{Corollary}
\newtheorem{proposition}{Proposition}
\theoremstyle{definition}
\newtheorem{example}{Example}
\theoremstyle{definition}
\newtheorem{exercise}{Exercise}
\theoremstyle{remark}
\newtheorem*{remark}{Remark}
\newtheorem*{solution}{Solution}
\begin{document}
\maketitle

\renewcommand\thefigure{R\arabic{figure}}

\setcounter{figure}{0}

\doublespacing

We are thankful to the assistant editor James Ross, the senior editor
and David Gibson, and three anonymous reviewers for the insightful
comments to improve the manuscript. In the following sections, you can
find a detailed response to each comment raised during the previous
round of review.

\section{Editor comments}\label{editor-comments}

\begin{quote}
``I agree that your manuscript is much improved and now only in need of
relatively minor revisions. In addition to addressing the AE and
reviewer's comments, please add terms related to invasive species to the
keywords to aid in discoverability of your paper.''
\end{quote}

Many thanks for the encouraging words. We have included `invasive
species' as a keyword. To make space for this keyword we have removed
`controllability' which is already highlighted as part of the title.

\section{Associate Editor's comments}\label{associate-editors-comments}

\begin{quote}
``I think this ms now makes much clearer the potential insights to be
gained by applying control theory to interaction networks. In
particular, the authors have done a nice job of explaining how their
findings reinforce existing ideas in the literature on the stability of
ecological networks while also acknowledging limitations. The reviewers
identified a few remaining issues that should be straightforward to
address. I also noticed a few issues''
\end{quote}

Thank you for the positive feedback. We have addressed all of the
specific issues raised and highlight these in red text in our
resubmitted manuscript.

\begin{quote}
``\emph{L9}: I think here and throughout much of the text, species
should be possessive when followed by a noun (''species role" should be
``species' role''). The possessive is currently used in some instances
but is inconsistently applied throughout the ms."
\end{quote}

\emph{Accepted and changed}. We have checked through the manuscript and
corrected this where relevant. Besides \emph{specie's role}, we also
changed instances of \emph{species' contribution}, \emph{species'
degree}, \emph{species' control capacity}, among others.

\begin{quote}
``\emph{L25}: `every invasive species in our dataset was part of it'
Here it was unclear what `it' refers to (the set of critical species),
and the reference to a singular dataset when you have 20 networks in
total was a bit confusing to me.''
\end{quote}

\emph{Accepted and changed}. We have made this clearer as follows: ``and
included every invasive species in our dataset''
(\lr{M-R2-our-dataset}).

\begin{quote}
``\emph{L23-26}: in these lines, you refer to critical species, but I
think the distinction between having high control capacity versus being
critical needs to be defined (briefly) earlier (it is stated in
\emph{L18-19} that you will quantify both control capacity and identify
critical species, but it is not explained how they are distinct).''
\end{quote}

\emph{Accepted and changed}. We now identify the distinction between
high control capacity and being critical on
\lr{M-R2-define-control-capacity}. The text now reads ``It also allows
us to quantify a species control capacity-its relative importance-and
identify the set of species that, collectively, are critical in this
context because they have largest possible control capacity''.

\begin{quote}
``\emph{L27}: unclear what `its' refers to.''
\end{quote}

\emph{Accepted and changed}. We now explicitly state ``species' degree''
in \lr{M-R2-species-degree}.

\begin{quote}
``\emph{L234, 235}: awkward to refer to species as `they' and
`their'\,''
\end{quote}

\emph{Accepted and changed}. We have changed this to ``it'' and ``its''.

\begin{quote}
``\emph{L296}: `More details in Supporting Information.' is a sentence
fragment.''
\end{quote}

\emph{Accepted and changed}. We have corrected this on
\lr{M-R2-sentence-fragment}. The text now reads ``See Supporting
Information Section \ref{S-visitation-as-proxy} for more details''.

\begin{quote}
``\emph{L343}: I am not sure about citing Table 2 for the first time in
the Discussion. Might it be more useful to cite this in the
Introduction?''
\end{quote}

\emph{Accepted and changed}. We now introduce the glossary at the end of
the introduction on \lr{M-R2-ref-glossary}.

\begin{quote}
``\emph{L111, 114}: `are comprised of' should be `comprised'.
\emph{L339, 432}: `at' should be `in'. \emph{L341}: `allow' should be
`allowed'. \emph{L355}: missing period.''
\end{quote}

\emph{Accepted and changed}. Thank you for pointing out these mistakes,
we corrected all of them.

\section{Reviewer comments \#1}\label{reviewer-comments-1}

\begin{quote}
``I'd like to commend the authors to this revised version of the
manuscript on `Keystoneness, centrality, and the structural
controllability of ecological networks'. I thoroughly enjoyed the
re-written manuscript, which is now considerably more accessible and
clearly targets the community of network ecologists, while not ignoring
the importance of the applied relevance of the findings. Overall, I
don't have any major comments. I guess the language is in parts on the
casual side, yet without compromising the preciseness or clarity of the
text. I noticed a few typos or style errors that the authors may want to
address. Congratulations on this thought-provoking methodological
synthesis.''
\end{quote}

We are pleased that the reviewer enjoyed the re-written manuscript. We
did too!. We also grateful for the typos and style errors identified, we
have striven to correct them all.

\begin{quote}
``A few references require editing to journal style (e.g.~remove
initials for many citations)''
\end{quote}

\emph{Accepted and changed}. We have corrected all citations. One of
them, however, still shows an author's first name initial, as it is
necessary to distinguish two authors with the same last name
(\lr{M-R2-citation-with-name}).

\begin{quote}
``\emph{L388}: remove repeated `other'. I suggest that the authors
re-write this sentence to improve clarity.''
\end{quote}

\emph{Accepted and changed}. We have removed the second `other'. As
suggested, we have rewritten the sentence to improve clarity
(\lr{M-R2-structural-controllability}). It now reads as follows:
``First, structural controllability emphasizes that the effect a species
has on the abundance of other species is not independent of the effects
of those other species in their community''.

\begin{quote}
``Reference list needs updating, e.g.~Ne'eman et al. is not 2009 but
2010.''
\end{quote}

\emph{Accepted and changed}. Thanks for pointing this error out. We've
corrected the reference.

\begin{quote}
``\emph{L314}: open bracket missing. \emph{L358}: change `instead' to
`Instead'. \emph{L381}: remove second comma. \emph{Fig. S6} header of
plot b). correct spelling of `critical'.''
\end{quote}

\emph{Accepted and changed}. Thank you for pointing this out, made all
these changes as indicated.

\section{Reviewer comments \#2}\label{reviewer-comments-2}

\begin{quote}
``I think the concepts presented in this manuscript are a useful
addition to the literature on management of ecological networks. I agree
with the authors that it is important that the discussion surrounding
what constitutes a `keystone' species should go beyond centrality
metrics. I found the results and concepts to be generally well
presented, particularly graphically, and the authors present a thorough
sensitivity analysis to various assumptions.
\end{quote}

We are very thankful for the positive feedback but also for the issues
highlighted. We have aimed to address them all.

\begin{quote}
``The methods are mostly clear but there is no description of how the
`likelihood of being a superior node' is calculated.''
\end{quote}

\emph{Accepted and changed}. Thanks for pointing this out. We have
modified the sentence mentioning `the likelihood of being a superior
node' in the first paragraph of the section \ref{S-reciprocal-links} to
``\ldots{}and whether it is a superior node\ldots{}'' to avoid
confusion. Then we define the `probability of being a superior node' at
the end of the section: ``It is important to note that a species that is
found to be a superior node under a particular control configuration,
will be so in all possible control configurations for the particular
non-reciprocal network. We, therefore denote the average of \(\sigma\)
across all non-reciprocal versions as the probability of the species
being a superior node in its community''.

\begin{quote}
``I would suggest including clarification on the limitations of using
control capacity to summarise species' importance, and examples to help
the reader build an intuition regarding the control capacity metric. As
pointed out, networks that give rise to a species having a high control
capacity can be quite distinct to networks that give rise to a species
having a high value of particular centrality metrics. Providing an
example in the Discussion of, for instance, those species that have a
control capacity of 1 but a low degree would be very useful.''
\end{quote}

\emph{Need Daniel's input}

\begin{quote}
``Jargon occasionally obfuscates the concepts being introduced and there
are places where I thought the language used was vague (esp. if terms
being used have particular meanings depending on the field you're coming
from). I would suggest clarifying, or rewording, the following: `desired
control trajectory' - does this mean `final state'?''"
\end{quote}

\emph{Accepted and changed}: We have attempted to clarify this sentence
as follows: Finding out exactly how difficult it is to control a network
depends strongly on the particularities of the desired control
trajectory (i.e.~the path to the desired final state) as well as the
dynamical relationship between nodes.
\lr{M-R2-desired-control-trajectory}.

\begin{quote}
``\emph{L1364}: `dynamic persistence'\,''
\end{quote}

\emph{Accepted and changed}: Thank you. To avoid confusion we have
removed the word `dynamic' and now the sentence reads ``\ldots{}our
results suggest that structural controllability is closely related to
the persistence\ldots{}'' (\lr{M-R2-dynamic-persistence}). It conserves
its meaning without losing much precision.

\begin{quote}
``\emph{L1370}: `dynamic stability'\,''
\end{quote}

\emph{Accepted and changed}: Contrastingly, in this case the word
dynamic distinguishes a particular facet of stability. We mean the
ability of the system to return to an equilibrium state after a
perturbation. We now include this definition on
\lr{M-R2-dynamic-stability} to make the concept clearer.

\begin{quote}
``\emph{P9}: `ecological objective' - simply `objective'?''
\end{quote}

\emph{Accepted and changed}: We have changed this to simply `objective',
as suggested (\lr{M-R2-ecol-objective}).

\begin{quote}
``\emph{L405}: `central in their community'\,''
\end{quote}

\emph{Accepted and changed}: We've changed the wording to avoid
ambiguity. Now the text reads ``\ldots{}to attain high centrality in
their communities\ldots{}'' (\lr{M-R2-central-in-their-communities}).

\begin{quote}
``\emph{L406}: 'inherently different. The sentence spanning lines
407-410 is quite confusing - please clarify.
\end{quote}

\emph{Accepted and changed}: We rephrased this line as follows: ``We
found that it is not that invasive plants have some different mechanism
for influencing the community compared to their native counterparts''
\lr{M-R2-inherrently-different}.

\begin{quote}
``\emph{L430}: `marginally affected by the topology of their
interactions'\,''
\end{quote}

\emph{Accepted and changed}: We have rephrased this line as: ``By
accounting for network dynamics (even if in a simple way), structural
stability incorporates more ecological realism, especially in the
extreme scenario in which the structure of interactions within the
community only marginally affects the community's state. Both native
species and invasive plants tended to attain a high control capacity if
they were important to network persistence, were abundant, and depended
little on other species'' (\lr{M-R2-marginally-affected}).

\begin{quote}
``\emph{L436} and \emph{L441}: `dominate the state {[}of their
community{]}'\,''
\end{quote}

\emph{Need Daniel's input}

\begin{quote}
``\emph{Discussion}: `species' strength'''
\end{quote}

\emph{Accepted and changed}: In the Methods section we deine species'
strength as the sum of a species' visits (\lr{M-R2-species-strength-a}).
For brevity, we did not define it again in the Discussion, but now we
have improved the text and briefly describe it when we mention it there
too. The text now reads ``When controlling for a species' visitation
strength (the sum of a species' visits), which is indirectly a proxy of
its abundance\ldots{}'' (\lr{M-R2-species-strength-b}).

\begin{quote}
``Minor typos: \emph{Figure S11} caption: `likelyhood' -\textgreater{}
likelihood. \emph{L388}: `other other'. `Driver node density' (supp p12)
-\textgreater{} `size of the minimum driver node set'?''
\end{quote}

\emph{Accepted and changed}: All typos have been corrected as indicated.

\begin{quote}
``\emph{Figure S1b} is referred to (supp. p4 ) but doesn't exist in the
figure''
\end{quote}

\emph{Accepted and changed}: Thanks for noticing this issue. We now
refer to the figure as ``Figure S1 (center panel)''.

\begin{quote}
``\emph{References}: several references use the term `plantPollinator',
or `\ldots{}'\,''
\end{quote}

\emph{Accepted and changed}: We have corrected the reference that
included `plantPollinator' in the title. We have left the references
that include an ellipsis in the author list as they are, as the Journal
of Ecology Author Guidelines indicate that this is the preferred format
when the reference has more than seven authors.

\section{Reviewer comments \#3}\label{reviewer-comments-3}

\begin{quote}
``In the literature on ecological networks, the term keystone species
has often been tossed around without any clear definition. I was pleased
to read that here the authors have developed a cleaner, more effective
way to identify keystone species in ecological networks than methods
that have been proposed before. I think the authors have made the
correct choice in emphasizing the conceptual aspects of the approach,
and do so quite well. The background on control theory was complex but
manageable to read and understand in this context.''
\end{quote}

We are very thankful for the positive feedback.

\begin{quote}
``Overall I found the paper well-written and sound, but there were a few
questions I had that could improve clarity in the methods used. In the
glm that used nD as the response variable, is there any concern that
including N (number of species) as a predictor may cause a problem when
the response is D/N? I can understand why this was included, but I can
also imagine this resulting in models that show an effect of N when
there is none (I could be wrong on this).''
\end{quote}

\emph{Need Daniel's input}

\begin{quote}
``In the species level glm, it was not entirely clear if models were fit
to each network individually or if all species were lumped together (the
former is what I think was done based on my reading of the text).
Regardless I wonder if it would change the results if a mixed effects
model was fit to lumped data, using network as a random effect.''
\end{quote}

\emph{Accepted and changed}: We are sorry for the confusion. In the
species level GLM, we lumped all species from different networks
together. We have modified the text in \lr{M-R2-one-lumped-model-a} and
\lr{M-R2-one-lumped-model-b} to make this clearer. We actually did test
for random effects in the model. We tested random effects that allowed
for a random intercept for the network (but also its site, and the study
it comes from). In all cases, the variance among groups was zero. This
means that likely there are no differences on the distribution of
control capacity between networks (or site and study) and therefore it
was not necessary to include random effects in the models presented in
the paper. We have corrected this omission and describe the random
effects in \lr{M-R2-random-effects}.

\begin{quote}
``How were the model sets derived? Were all possible sub-models compared
or was a step-wise approach used?''
\end{quote}

\emph{Accepted and changed}: We actually compared all possible candidate
models. We have edited the manuscript on \lr{M-R2-all-candidates} to
include this information.

\begin{quote}
``Reciprocal links were included in the directed graph when dij = dji.
Would it have any effect if there was a little wiggle room there, e.g.,
when the two are close but not equal?''
\end{quote}

We did not actually evaluate this When we evaluate the impact of this on
our results. However, given that the interaction only a very small
fraction of interactions had a small asymmetry (see Figure R1) we don't
expect results to change considerably even when we include reciprocal
links when the asymmetry is small but not zero.

\begin{figure}
\centering
\includegraphics{/Users/efc29/github/driver-species/paper/reviewers-response_files/figure-latex/fig-asymmetry-1.pdf}
\caption{\label{fig:fig-asymmetry}Histogram of the interaction asymmetries
between species. Previous research has shown that mutualistic
interactions are often highly asymmetric in natural communities. Only
16.5\% of interactions have asymetries smaller or equal than 0.5; 1\%
are smaller than 0.1.}
\end{figure}

\end{document}

### 2019-01-13 paper/drafts_and_revisions/2019-01-14/manuscript.tex
Add revision with most responses to reviewers

--- 2019-01-13 paper/drafts_and_revisions/2018-07-19/manuscript.tex
@@
 \item
-  An important dimension of a species role is its ability to alter the
+  An important dimension of a species' role is its ability to alter the
   state and maintain the diversity of its community. Centrality metrics
@@
   mostly on our intuition regarding what constitutes an important
-  species. While centrality is useful when predicting which species
+  species. While centrality is useful when predicting which species'
   extinctions could cause the largest change in a community, it says
@@
   us to quantify the extent to which network topology can be harnessed
-  to achieve a desired state. It also allows us to quantify a species
-  control capacity---its relative importance---and identify the set of
-  species that, collectively, are critical in this context. We
-  illustrate the application of structural controllability with ten
-  pairs of uninvaded and invaded plant-pollinator communities.
+  to achieve a desired state. \R{R2-define-control-capacity} It also
+  allows us to quantify a species' control capacity---its relative
+  importance---and identify the set of species that, collectively, are
+  critical in this context because they have largest possible control
+  capacity. We illustrate the application of structural controllability
+  with ten pairs of uninvaded and invaded plant-pollinator communities.
 \item
@@
   being less connected, were critical in their communities.
-  Interestingly, this set of critical species was mostly composed of
-  plants and every invasive species in our dataset was part of it. We
-  also found that species with high control capacity, and in particular
-  critical species, contribute the most to the stable coexistence of
-  their community. This result was true, even when controlling for its
-  degree, abundance/interaction strength, and the relative dependence of
-  their partners.
+  \R{R2-our-dataset} Interestingly, this set of critical species was
+  mostly composed of plants and included every invasive species in our
+  dataset. We also found that species with high control capacity, and in
+  particular critical species, contribute the most to the stable
+  coexistence of their community. \R{R2-species-degree} This result was
+  true, even when controlling for the species' degree,
+  abundance/interaction strength, and the relative dependence of their
+  partners.
 \item
@@
 
-\textbf{Keywords:} Keystone species, management interventions,
-mutualism, network control theory, plant population and community
-dynamics, species importance, control capacity, structural stability,
-controllability
+\textbf{Keywords:} Invasive species, keystone species, management
+interventions, mutualism, network control theory, plant population and
+community dynamics, species' importance, control capacity, structural
+stability
 
@@
 analytical and simulation tools with which to compare and contrast the
-roles of species embedded in a network of interactions (J. Bascompte \&
+roles of species embedded in a network of interactions (Bascompte \&
 Stouffer, 2009; Coux, Rader, Bartomeus, \& Tylianakis, 2016; Guimerà \&
@@
 
-A significant proportion of the network tools used to estimate species
+A significant proportion of the network tools used to estimate species'
 roles in this context rely on the calculation of a species'
@@
 
-Species abundances---and consequently the state of the community as a
+Species' abundances---and consequently the state of the community as a
 whole---are influenced both by the structure of their interactions and
@@
 branch of engineering used to determine and supervise the behaviour of
-dynamical systems (A. E. Motter, 2015). It is inherently designed to
-deal with system feedbacks and its application has recently been
-expanded to complex networks (Lin, 1974; Liu \& Barabási, 2016).
-Consistent with long-standing ecological questions, advances in
-structural controllability have established a clear link between the
-structure of the network and the way nodes affect each other. Unlike
-centrality indices, however, this link is not based on a priori
-assumptions between network metrics and keystoneness but is instead
-based on well-established advances in both dynamical and complex-systems
-theory (A. E. Motter, 2015).
+dynamical systems (Motter, 2015). It is inherently designed to deal with
+system feedbacks and its application has recently been expanded to
+complex networks (Lin, 1974; Liu \& Barabási, 2016). Consistent with
+long-standing ecological questions, advances in structural
+controllability have established a clear link between the structure of
+the network and the way nodes affect each other. Unlike centrality
+indices, however, this link is not based on a priori assumptions between
+network metrics and keystoneness but is instead based on
+well-established advances in both dynamical and complex-systems theory
+(Motter, 2015).
 
@@
 Therefore, we first ask whether there are differences between the
-controllability of invaded and uninvaded networks. We then expand
-existing methods from control theory to effectively link the
-\emph{controllability} of a network with the role of its constituent
-species. We ask---from a control-theoretic perspective---whether there
-are key differences between species in the role they play at driving the
-state of the community and explore the ecological factors related to
-these differences. This allows us to identify species that might be
-critical for network control and show that they have a larger than
-expected impact on the stable coexistence of the community. Finally, we
-compare the proposed approach to current methods based on species
-centrality and show how these methods are indeed valuable but ultimately
-paint a limited picture in regard to the ``keystoneness'' of a species.
-
-\section{Materials and methods}\label{materials-and-methods}
-
-We used ten paired pollination communities to apply the
-control-theoretic approach. Each community pair was composed of a
-community invaded by a plant and a community free of the invasive
-species. Four pairs correspond to natural or semi-natural vegetation
-communities in the city of Bristol, UK (Lopezaraiza\textendash{}Mikel et
-al., 2007). These communities are comprised of 19--87 species (mean 55),
-and non-invaded plots were obtained by experimentally removing all the
-flowers of the invasive species \emph{Impatients grandulifera}. The
-other six pairs were obtained from lower diversity Mediterranean
-shrublands in Cap de Creus National Park, Spain (Bartomeus et al.,
-2008). These communities are comprised of 30--57 species (mean 38); in
-contrast to the above, uninvaded communities were obtained from plots
-that had not yet been colonised by either of the invasive species
-\emph{Carpobrotus affine acinaciformis} or \emph{Opuntia stricta}. The
-structure of all these communities was defined by the pollinator
-visitation frequency, which has been shown to be an appropriate
-surrogate for interspecific effects in pollination networks (J.
-Bascompte, Jordano, \& Olesen, 2006; Diego P. Vázquez, Morris, \&
-Jordano, 2005). Full details about the empirical networks can be found
-in the Supporting Information Section \ref{S-empirical-networks}.
-
-The first step in applying methods of control theory is to construct a
-directed network that is able to provide an indication of the extent to
-which species affect each other's abundance. In some ecological
-networks, establishing the directionality can be relatively
-straightforward, for example when links represent biomass transfer or
-energy flow (Isbell \& Loreau, 2013). In pollination networks, however,
-this directionality is less obvious as both species can, in theory,
-benefit from the interaction. We overcome that obstacle by noting that
-the extent to which species \emph{i} affects species \emph{j} relative
-to the extent to which \emph{j} affects \emph{i} can be summarised by
-their interaction asymmetry (J. Bascompte et al., 2006). This asymmetry
-is given by
-\[a(i,j) = a(j,i) = \frac{\left | d_{ij}-d_{ji} \right |}{max\left ( d_{ij}, d_{ji} \right )},\]
-where the dependence of plant \emph{i} on pollinator \emph{j},
-\emph{d\textsubscript{ij}}, is the proportion of the visits from
-pollinator \emph{j} compared to all pollinator visits to plant \emph{i}.
-Previous research has shown that mutualistic interactions are often
-highly asymmetric in natural communities; in other words, if a plant
-species is largely dependent on a pollinator species, that pollinator
-tends to depend rather weakly on the plant (and vice versa). We
-therefore create a directed link from species \emph{i} to species
-\emph{j} when \(d_{ij}-d_{ji} \geq 0\) to establish the most likely
-direction of control between a species pair (Figure
-\ref{fig:fig-example-networks}a). Sometimes there is no observed
-asymmetry between species pairs (\(d_{ij}=d_{ji}\)), and we cannot infer
-a dominant direction of control. When this occurs, we deem both species
-to be equally likely to affect each other and leave a reciprocal
-interaction between them (a link from \emph{i} to \emph{j} and another
-from \emph{j} to \emph{i}). By basing the direction of the links on the
-asymmetry of their dependence, we are able to generate a network that is
-consistent with the dynamics of the community while satisfying the
-requirements of structural controllability. This allows us to calculate
-the controllability of the networks and investigate whether there are
-differences between invaded and uninvaded communities.
-
-\begin{figure}
-\centering
-\includegraphics{/Users/efc29/github/driver-species/paper/manuscript_files/figure-latex/fig-example-networks-1.pdf}
-\caption{\label{fig:fig-example-networks}The direction of control and
-controllability conditions. (a) To establish the direction of control,
-we start with a weighted visitation network (on the left). In this
-network, the width of the links corresponds to the frequency of
-visitation between animals \(a_i\) and plants \(p_i\), with wider links
-indicating more visits. Plant \(p_1\) is visited exclusively by \(a_1\)
-but \(p_1\) represents only a small fraction of the floral resources
-exploited by \(a_1\). Therefore, the population of \(p_1\) is more
-likely to be affected by \(a_1\) than vice versa. We represent this with
-a directed link from \(a_1\) to \(p_1\) in the control network (on the
-right). The direction of control between all other species pairs can be
-similarly determined by inspecting the difference between their relative
-dependences. (b) Once we have established the directions of control, we
-can determine whether the network is controllable or not. Any system
-defined by a directed network (with state nodes \(x_i\); species
-populations in an ecological context) and external control inputs (nodes
-\(u_i\), orange links) is structurally controllable if it satisfies two
-conditions: it has no dilations (expansions in the network) and no
-inaccessible nodes. The system on the top left is not controllable
-because there is a dilation since node \(x_2\) is being used to control
-two nodes simultaneously; in other words, there are fewer superiors
-(\(x_2\)) than subordinates (\(x_1\) and \(x_3\)). The network on the
-top right is not controllable because node \(x_3\) is inaccessible for
-the only input node \(u_1\) in the system. Both systems can be made
-controllable by adding an extra input node (\(u_2\) in both bottom
-networks).}
-\end{figure}
-
-\subsection{Controllability}\label{controllability}
-
-A system is said to be controllable if it is possible to steer it from
-an initial to an arbitrary final state within finite time (Kalman,
-1963). A simple version of such a system can be described by
-\(\frac{dx}{dt} = Ax + Bu(t)\), where the change of its state over time
-(\(\frac{dx}{dt}\)) depends on its current state \emph{x} (for example
-the species' abundances), an external time-varying input \emph{u(t)}
-(the control signal), and two matrices \emph{A} and \emph{B}, which
-encode information about the network structure and how species respond
-to external inputs, respectively. In classic control theory, determining
-whether this system is controllable can be achieved by checking that its
-controllability matrix
-\(R= [ \begin{matrix}B & AB & A^{2}B & ...& A^{n-1}B\end{matrix} ]\) has
-full rank. In complex systems, however, employing this rank condition,
-or numerical approximations of it is infeasible because it is hard to
-fully parameterise \emph{A} and \emph{B} (either because the weight of
-the links changes over time or because they are difficult to measure).
-Here, we use an approach based on the structural controllability theorem
-(Lin, 1974), which assumes that we are confident about which elements of
-\emph{A} and \emph{B} have either non-zero or zero values (there is an
-interaction or not), but that we are less sure about the precise
-magnitude of the non-zero values. Using this structural approach, we can
-find out the controllability of a system for every non-zero realisation
-of the parameters.
-
-We are often able to estimate \emph{A} in ecological networks, as this
-matrix represents the interactions between species. Part of the control
-problem thus resides in estimating a supportable estimation of \emph{B},
-which represents the links between external inputs and species. Naively,
-any ecological community (and any system for that matter) could be
-controlled if we control the state of every species independently, but
-such an approach is typically impractical. Here, we are interested in
-finding a minimum driver-node set (effectively finding \emph{B}) with
-which to make the system controllable. The brute-force search for this
-minimum driver-node set is computationally prohibitive for most networks
-as it involves the evaluation of \(2^N\) different controllability
-matrices where \(N\) is the number of species in the community. We
-therefore instead employ a recently-developed approach that shows that
-the control problem of finding the minimum driver-node set can be mapped
-into a graph-theoretic problem: maximum matching (Liu \& Barabási, 2016;
-Liu, Slotine, \& Barabási, 2011).
-
-Maximum matching is a widely studied topic in graph theory and is
-commonly used in multiple applications, ranging from dating apps and
-wireless communications to organ transplant allocation and peer-to-peer
-file sharing. A matching in an unweighted directed graph is defined as a
-set of links that do not share common start or end nodes; the largest
-possible matching is called a maximum matching. For example, in a
-network composed of jobs and job applicants, a matching is any pairing
-between applicants and positions that satisfies one basic constraint: an
-applicant can be assigned to at most one position and vice versa.
-Consequently, a maximum matching is an optimal pairing, one that
-maximises the number of applicants with jobs and the number of positions
-filled. Admittedly, the link between matchings and structural
-controllability may appear far from straightforward.
-
-This link becomes apparent after examining the graphical interpretation
-of structural controllability: from a topological perspective, a network
-is structurally controllable if there are no inaccessible nodes---that
-is, nodes without incoming links---or dilations---\emph{expansions} of
-the network (Figure \ref{fig:fig-example-networks}b; Supporting
-Information Section \ref{S-structural-controllability}). The key is to
-note that these two fundamental conditions of structural controllability
-imply that there is a one-to-one relationship between \emph{superior}
-and \emph{subordinate} nodes just like the one-to-one relationship
-between jobs and applicants (Figure \ref{fig:fig-example-networks}b,
-bottom left). We thus use the maximum-matching algorithm to find an
-optimal pairing of superior (those that can control another node) and
-subordinate nodes (those that can be controlled by another node) in a
-manner consistent with the controllability conditions (Supporting
-Information Section \ref{S-one-maximum-matching}). Given the result, we
-can further decompose the matching into a set of paths that reveal how a
-control signal can flow across the links in a network to reach every
-node within it. As recently shown (Liu et al., 2011), the minimum
-driver-node set---those to which an external control input should be
-applied to make the system controllable---corresponds exactly to the
-\emph{unmatched} nodes in the network (Figure
-\ref{fig:fig-control-configuration}).
-
-\begin{figure}
-\centering
-\includegraphics{/Users/efc29/github/driver-species/paper/manuscript_files/figure-latex/fig-control-configuration-1.pdf}
-\caption{\label{fig:fig-control-configuration}Maximum matchings and control
-configurations. In directed networks, a maximum matching is the largest
-possible set of links that do not share start or end nodes (dark
-purple). Maximum matchings are not necessarily unique; instead, each of
-them is related to a possible minimum driver-node set in the network
-(the nodes to which an external control input, in orange, should be
-applied in order to ensure controllability). The size of the minimum
-driver-node set \emph{D} corresponds exactly to the number of unmatched
-nodes (the number of nodes in the network \emph{N} minus the matching
-size). To account for network size, we use the size of the minimum
-driver-node set relative to the total number of nodes
-\emph{n\textsubscript{D} = D/N} as a measure of the extent to which the
-network structure can be harnessed to control the system.}
-\end{figure}
-
-\subsection{Differences between invaded and uninvaded
-networks}\label{differences-between-invaded-and-uninvaded-networks}
-
-Our first ecological objective is to investigate whether the
-controllability of a community is associated with invasion status or
-not. Finding out exactly how difficult it is to control a network
-depends strongly on the particularities of the desired control
-trajectory as well as the dynamical relationship between nodes. However,
-we are interested in understanding the controllability of a network in a
-more general sense, such that it can be applied even when the precise
-control scenario is known only incompletely. To this end, we chose an
-indicator that follows directly from our approach: the size of the
-minimum driver-node set. This simple metric provides a general
-indication of how difficult controlling a network might be, as systems
-that require a large number of external inputs to be fully controlled
-are intuitively more difficult or costly to manage. For instance,
-achieving full control in a ``network'' in which species do not interact
-at all is relatively more difficult as we would require an intervention
-for every single species. Conversely, the structure of a linear trophic
-chain can be harnessed to achieve full control using just one
-intervention targeted at the top species; a suitable control signal
-could then cascade through the trophic levels and reach other species in
-the community. Specifically, drawing from the structural-controllability
-literature, we use the size of the minimum driver-node set relative to
-the total number of species \(n_D = \frac{D}{N}\) as a measure of the
-\emph{controllability} of a network---the extent to which the network
-structure can be harnessed to control the community. The lower \(n_D\)
-the more controllable the community. In an ecological context, external
-inputs can be thought of as management interventions that modify the
-abundance of a particular species.
-
-After finding the minimum driver-node set in each of our networks, we
-wanted to test whether invasion status or other predictors are
-correlated to controllability. We do this using a set of generalised
-linear models with binomial error structure. The response variable was
-the relative size of the minimum driver-node set \(n_D\) of the twenty
-empirical networks (ten invaded and ten uninvaded), and we included
-invasion status as a predictor. As predictors, we also include the
-network connectance, the network nestedness (NODF), the number of
-species (since one might naively expect to see a negative relationship
-between richness and controllability; Menge, 1995), the network
-asymmetry (an indication of the balance between plant and pollinator
-diversity), and the interaction strength asymmetry (the asymmetry on the
-dependences between trophic levels; N. Blüthgen, Menzel, Hovestadt,
-Fiala, \& Blüthgen, 2007). We compared models using the Akaike
-Information Criterion for small sample sizes (AICc).
-
-In addition, we also explored whether real networks differ in their
-architecture from random ones in a concerted way that could impact these
-results. Specifically, we used two null models each with 99
-randomisations per network. In the first, we followed Diego P Vázquez et
-al. (2007) and maintained the connectance of the network but randomised
-the visits across species such that the relative probabilities of
-interactions were maintained. We then re-estimated the direction of
-control and the corresponding size of the minimum driver-node set,
-\(n_D\). For the second null model, we used the empirical directed
-network described above and randomly shuffled the direction of control
-between a species pair prior to re-estimating the size of the minimum
-driver-node set.
-
-\subsection{Species roles}\label{species-roles}
-
-Our second objective is related to how species differ in their ability
-to drive the population dynamics of the community. We in turn examine
-whether these differences are also reflected in the role species play at
-supporting the stable coexistence of other species in the community.
-Ecologically, these differences are relevant because resources and data
-are limited, and therefore full control is infeasible. While calculating
-the size of the minimum drive-node set can measure the controllability
-of an ecological community, it does not provide information about the
-roles that particular species play.
-
-To answer this question, we harness the fact there may be multiple
-maximum matchings for a given network, and each of these maximum
-matchings indicates a unique combination of species with which it is
-possible to control the network. Moreover, some species belong to these
-combinations more often than do others. We call this property a species
-``control capacity'', \(\phi\). The higher a species control capacity,
-the greater the likelihood that they would need to be directly managed
-to change (or maintain) the ecological state of their community.
-Therefore, a species control capacity provides an estimation of their
-relative importance at driving the state of the community (Jia \&
-Barabási, 2013).
-
-To calculate a species control capacity \(\phi\), we must first
-enumerate all possible maximum matchings (Supporting Information Section
-\ref{S-all-maximum-matching}). Unfortunately, enumerating all maximum
-matchings is extremely expensive from a computational perspective---a
-network with a couple dozen species has several hundred million unique
-maximum matchings. To solve this problem, we employ a recently-developed
-algorithm that reveals the control correlations between the nodes in the
-graph while requiring considerably less computational resources (Zhang,
-Lv, \& Pu, 2016). Using this algorithm, we are able to identify species
-that are possible control inputs---those that belong to the minimum
-driver-node set in at least one of the possible control configurations.
-Here, we extend this algorithm such that it is possible to calculate a
-highly accurate approximation of the control capacity \(\phi\) of every
-species in the network (Supporting Information Section
-\ref{S-input-graph}). In the networks that contained reciprocal links
-(because there was no asymmetry in the dependences of a species pair),
-we averaged a species control capacity \(\phi\) across every possible
-``non-reciprocal'' version of the network (Supporting Information
-Section \ref{S-reciprocal-links}).
-
-We then examined how species-level properties were related to control
-capacity using a set of generalised linear models with binomial error
-structure. These models included five predictor variables that mirror
-the network-level predictors. First, the species contribution to
-nestedness, which has been proposed as a key feature that promotes
-stability and robustness in mutualistic networks (S. Saavedra, Stouffer,
-Uzzi, \& Bascompte, 2011). Second, the species strength (the sum of a
-species' visits), which quantifies the strength of a species
-associations and is indirectly related to its abundance (Poisot, Canard,
-Mouquet, \& Hochberg, 2012). Third, the direction of asymmetry which
-quantifies the net balance in dependencies; that is, it indicates if a
-species affects other species more than what they affect it or not
-(Diego P Vázquez et al., 2007). Fourth, the species degree in order to
-account for the intrinsic centrality of a species. Finally, we included
-a categorical variable for the species trophic level (plant or
-pollinator) and an interaction term between trophic level and the
-previous four variables. To facilitate comparison between predictors,
-degree and visitation strength were log-transformed and all four
-continuous variables were scaled to have a mean of zero and a standard
-deviation of one. To identify the models that were best supported by the
-data, we first determined the most parsimonious random structure using
-the AICc. The relative importance of variables was then assessed by
-looking at their effect sizes in the top-ranked models and the
-cumulative weight of the models in which they are present.
-
-In addition, we wanted to understand how a species control capacity
-\(\phi\) described above relates to metrics of keystoneness based on
-centrality. Specifically, in each network, we calculated the species'
-degree, betweenness, closeness centrality (Martín González et al.,
-2010), page rank (McDonald-Madden et al., 2016), and eigen centrality
-(Jordano, Bascompte, \& Olesen, 2006). We then calculated the spearman
-correlation coefficient between control capacity and each of these
-centrality metrics.
-
-Our analysis revealed that some species have a control capacity
-\(\phi = 1\). These species are critical to controlling their community
-because they are part of the minimum driver-node set in \emph{every}
-control scenario. In other words, it is theoretically impossible to
-drive the state of the community to a desired state without directly
-managing the abundance of these species. We thus anticipate that these
-species have a disproportionally large impact on the community dynamics.
-To test this hypothesis, we identified these critical species in each of
-the networks and investigated whether they have a larger than average
-impact on the stable coexistence of species in the community. Within
-mutualistic networks, one useful measure of stable coexistence is called
-structural stability (R. P. Rohr, Saavedra, \& Bascompte, 2014).
-Mathematically, the structural stability of a network represents the
-size of the parameter space (i.e., growth rates, carrying capacities,
-etc.) under which all species can sustain positive abundances (S.
-Saavedra, Rohr, Olesen, \& Bascompte, 2016). The contribution of any
-given species \emph{i} to stable coexistence can be estimated by
-calculating the structural stability of the community when the focal
-species \emph{i} is removed. To allow comparison across communities, the
-structural stability values were scaled within each network to have a
-mean of zero and a standard deviation of one. Given these
-species-specific estimates of structural stability, we then used a
-t-test to compare the contribution to stable coexistence of critical and
-non-critical species. More details about the calculation of structural
-stability can be found in the Supporting Information Section
-\ref{S-structural-stability}.
-
-\subsection{Testing assumptions}\label{testing-assumptions}
-
-\R{testing-assumptions-line}Just like the centrality metrics, the
-information obtained by applying structural controllability depends on
-the ability of the network to accurately represent the ecological
-community. We thus tested the sensitivity of our approach to two
-fundamental assumptions. First, we tested that visitation is an
-appropriate proxy to infer interspecific effects by comparing the
-results obtained using visitation to two alternative metrics in a
-separate dataset that lacked invasive species (Ballantyne, Baldock, \&
-Willmer, 2015). Specifically, we also calculated the controllability
-(the size of the minimum driver node-set) and the control capacity of
-networks constructed using pollinator efficiency (which measures the
-pollen deposition of an interaction) and pollinator importance (which
-accounts for both pollen deposition and visitation and hence is regarded
-as a more accurate estimation of the pollination service received by
-plants; Ne'eman, Jürgens, Newstrom-Lloyd, Potts, \& Dafni, 2009). More
-details in the Supporting Information Section
-\ref{S-visitation-as-proxy}.
-
-Second, because interspecific dependencies themselves depend on the
-network topology and consequently on the accurate sampling of
-interactions, we tested the robustness of structural controllability to
-the uncertainty involved with the sampling of interactions. Here, we
-compared the results obtained when using the full network and when
-randomly removing interactions from the weakest links in the network.
-This effectively removed the rare interactions from the networks (more
-details in the Supporting Information Section \ref{S-undersampling}).
-
-\section{Results}\label{results}
-
-\subsection{Controllability}\label{controllability-1}
-
-The size of the minimum driver-node set relative to the number of
-species in each network \(n_D\) ranged between \(n_D = 0.58\) and
-\(n_D = 0.88\) (median 0.74).
-
-\subsection{Differences between invaded and uninvaded
-networks}\label{differences-between-invaded-and-uninvaded-networks-1}
-
-We found that the relative size of the minimum driver-node set of
-invaded communities was not significantly different from that of
-communities that have not been invaded (Figure
-\ref{fig:fig-emp-controllability}a). In contrast, there was a large
-negative relationship between \(n_D\) and the network asymmetry (Figure
-\ref{fig:fig-emp-controllability}b). Furthermore, there were also
-negative, albeit weaker, relationships between \(n_D\) and connectance,
-nestedness and species richness (Table
-\ref{S-tab:tab-controllability-model-results}). The relative size of the
-minimum driver-node set \(n_D\) of empirical networks did not differ
-from that of a null model that roughly preserved the degree distribution
-and fully preserved the network connectance (\(p = \num{0.66}\); Figure
-\ref{fig:fig-emp-controllability}c). However, empirical networks had a
-larger \(n_D\) than null models that preserved the interactions but
-shuffled the direction of control of the empirical network
-(\(p = \num{2.4e-07}\)).
-
-\begin{figure}
-\centering
-\includegraphics{/Users/efc29/github/driver-species/paper/manuscript_files/figure-latex/fig-emp-controllability-1.pdf}
-\caption{\label{fig:fig-emp-controllability}Drivers of network
-controllability. (a) Probability density of the relative size of the
-minimum driver-node set \(n_D\) in the invaded (light) and uninvaded
-(dark) empirical networks. (b) Relationship between the asymmetry
-plant/pollinator richness and \(n_D\). (c) Probability density of the
-difference between the relative size of the minimum driver-node set of
-random networks and that of empirical networks. We randomised either the
-species visitation patterns (light line) or randomised the direction of
-control between a species pair (dark line). The vertical dashed lines in
-(a) and (c) indicate the median values of the distributions.}
-\end{figure}
-
-\subsection{Species roles}\label{species-roles-1}
-
-Species varied widely in their control capacity (Figure
-\ref{fig:fig-species-level}). Pollinators had, in average, larger
-control capacities than plants. That said, almost no pollinator was
-critical for network control, where a species is critical for control if
-it has control capacity \(\phi_i = 1\)). Plants had a multimodal
-distribution of control capacity with maxima at both extremes of the
-distribution (Figure \ref{fig:fig-species-level}a). Intriguingly, every
-invasive species was critical for network control in each of their
-communities. The species-level models identified a positive relationship
-between control capacity \(\phi\) and a species' contribution to
-nestedness, visitation strength, and the asymmetry of its dependences
-(Table \ref{tab:tab-model-selection-table}; Figure
-\ref{fig:fig-species-partial}; Table
-\ref{S-tab:tab-model-output-species-level}). Comparatively, species'
-degree was only weakly associated with control capacity (Table
-\ref{S-tab:tab-var-importance}). In fact, many species with a low
-degree, especially pollinators, exhibited a large control capacity in
-their communities (Figure \ref{S-fig:fig-species-models-degree}a).
-
-Species control capacity \(\phi\) was only weakly correlated with
-commonly-used centrality metrics. The Spearman correlation between these
-ranged between -0.14 (with betweeness-centrality) and 0.42 (with
-eigen-centrality), see Figure \ref{S-fig:fig-correlogram}a. The
-correlation coefficient with degree was -0.13, however most species with
-high degree also tended to attain a high control capacity (Figure
-\ref{S-fig:fig-species-models-degree}a).
-
-\begin{table}
-
-\caption{\label{tab:tab-model-selection-table}Selection table of the binomial generalised linear models of species control capacity, $\phi$.
-Only models with a weight larger or equal to 0.01 are shown.}
-\centering
-\fontsize{8}{10}\selectfont
-\begin{threeparttable}
-\begin{tabular}[t]{rrlrrrllllrrr}
-\toprule
-\multicolumn{10}{c}{model terms} & \multicolumn{ 3}{c}{ } \\
-\cmidrule(l{2pt}r{2pt}){1-10}
-int. & $k$ & $l$ & $a$ & $n$ & $s$ & $k$:$l$ & $l$:$a$ & $l$:$n$ & $l$:$s$ & d.f. & $\Delta$AICc & weight\\
-\midrule
--1.20 &  & + & 0.80 & 0.15 & 0.29 &  & + & + &  & 7 & 0.00 & 0.48\\
--1.19 &  & + & 0.76 & 0.13 & 0.35 &  & + & + & + & 8 & 1.52 & 0.22\\
--1.26 & -1.24 & + & 1.44 & 0.39 & 1.07 & + & + &  & + & 9 & 4.09 & 0.06\\
--1.37 & -0.66 & + & 1.03 &  & 1.06 & + & + &  & + & 8 & 4.39 & 0.05\\
--1.27 & -1.15 & + & 1.37 & 0.33 & 1.07 & + & + & + & + & 10 & 4.92 & 0.04\\
-\addlinespace
--1.37 & -0.10 & + & 0.90 &  & 0.43 & + & + &  &  & 7 & 6.36 & 0.02\\
--1.25 & -0.28 & + & 1.24 & 0.40 &  & + & + &  &  & 7 & 6.47 & 0.02\\
--1.24 & -0.62 & + & 1.29 & 0.38 & 0.40 & + & + &  &  & 8 & 6.50 & 0.02\\
--1.39 & 0.30 & + & 0.83 &  &  & + & + &  &  & 6 & 6.72 & 0.02\\
--1.28 & -0.17 & + & 1.16 & 0.32 &  & + & + & + &  & 8 & 7.03 & 0.01\\
-\addlinespace
--1.26 & -0.53 & + & 1.23 & 0.32 & 0.39 & + & + & + &  & 9 & 7.42 & 0.01\\
--1.02 &  & + & 0.69 & 0.30 & 0.31 &  & + &  &  & 6 & 7.48 & 0.01\\
-\bottomrule
-\end{tabular}
-\begin{tablenotes}[para]
-\item \textit{Terms: } 
-\item intercept (int), degree ($k$), trophic level ($l$), asymmetry ($a$), contribution to nestedness ($n$), visitation strength ($s$).
-\end{tablenotes}
-\end{threeparttable}
-\end{table}
-
-\begin{figure}
-\centering
-\includegraphics{/Users/efc29/github/driver-species/paper/manuscript_files/figure-latex/fig-species-level-1.pdf}
-\caption{\label{fig:fig-species-level}Probability density of the control
-capacity \(\phi\) of (a) plants and (b) pollinators across all networks.
-The control capacity of all invasive species is \(\phi = 1\) and is
-depicted with solid circles.}
-\end{figure}
-
-\begin{figure}
-\centering
-\includegraphics{/Users/efc29/github/driver-species/paper/manuscript_files/figure-latex/fig-species-partial-1.pdf}
-\caption{\label{fig:fig-species-partial}Partial-residual plots for the
-independent variables: (a) contribution to nestedness, (b) visitation
-strength, (c) asymmetry of dependences, and (d) degree. Partial-residual
-plots show the relationship between control capacity and each of the
-independent variables while acccounting for all other remaining
-variables. Ploted values correpond to the predictions of the weighted
-average of the models shown in Table
-\ref{tab:tab-model-selection-table}.}
-\end{figure}
-
-Finally, we found that critical species have a particularly large impact
-on species coexistence when compared to non-critical species. Indeed,
-the structural stability of the networks where critical species were
-removed was considerably lower to those in were non-critical species
-were removed (\(p = \num{2e-15}\); Figure
-\ref{fig:fig-structural-stability}; Supporting Information
-\ref{S-structural-stability}).
-
-\begin{figure}
-\centering
-\includegraphics{/Users/efc29/github/driver-species/paper/manuscript_files/figure-latex/fig-structural-stability-1.pdf}
-\caption{\label{fig:fig-structural-stability}Probability density of the
-structural stability of the communities after a single focal species is
-removed. Mathematically, the structural stability of a network
-represents the size of the parameter space (i.e., growth rates, carrying
-capacities, etc.) under which all species can sustain positive
-abundances. The structural stability of communities in which critical
-species have been removed (darker line) is considerably smaller than
-that of communities in which non-critical species have been removed.
-This indicates that critical species contribute more to the stable
-coexistence of their communities. To allow comparison across
-communities, the structural stability values were scaled within each
-network to have a mean of zero and a standard deviation of one. Here, we
-assume values of the mutualistic trade-off and mean interspecific
-competition of \(\delta = 0\) and \(\rho = 0.01\) respectively (S.
-Saavedra et al., 2016). However, the choice of these parameters does not
-affect the results (Supporting Information
-\ref{S-structural-stability}).}
-\end{figure}
-
-\subsection{Testing assumptions}\label{testing-assumptions-1}
-
-\R{testing-assumptions-results-line} We found that using visitation as a
-proxy for the strength of species interactions leads to similar results
-than those obtained using pollinator importance (regarded as an accurate
-measure of the pollination service to plants; Supporting Information
-Section \ref{S-visitation-as-proxy}; Ne'eman et al., 2009). Importantly,
-we also found that structural stability is robust to incomplete sampling
-of interactions. Indeed, we found strong agreement between results
-obtained using the complete empirical networks and those obtained by
-randomly removing the weakest interactions (Supporting Information
-Section \ref{S-undersampling}). Despite removing rare interactions and
-species, the relative size of the minimum driver-node set, the superior
-species, and the relative rankings of control capacity were generally
-maintained. Of particular note, we found that critical species in the
-full network were also critical in the vast majority of rarefied
-networks.
-
-\section{Discussion}\label{discussion}
-
-Our main goal was to understand the role that species play at both
-modifying the abundance of the species they interact with and the state
-of the community as a whole. To achieve that goal we applied
-\emph{structural controllability}, a field at the intersection between
-control and complex theory that allow us to obtain two key pieces of
-information: the \emph{controllability} of a network and a species
-\emph{control capacity} (Table \ref{tab:tab-glossary}). We found that
-the controllability of a network does not depend on its invasion status
-and that the species that are critical to altering the state of the
-community are also the ones that most sustain the stable coexistence of
-species in their communities.
+controllability of invaded and uninvaded networks. \R{R2-ref-glossary}
+We then expand existing methods from control theory to effectively link
+the \emph{controllability} (Table \ref{tab:tab-glossary}) of a network
+with the role of its constituent species. We ask---from a
+control-theoretic perspective---whether there are key differences
+between species in the role they play at driving the state of the
+community and explore the ecological factors related to these
+differences. This allows us to identify species that might be critical
+for network control and show that they have a larger than expected
+impact on the stable coexistence of the community. Finally, we compare
+the proposed approach to current methods based on species' centrality
+and show how these methods are indeed valuable but ultimately paint a
+limited picture in regard to the ``keystoneness'' of a species.
 
@@
 
+\section{Materials and methods}\label{materials-and-methods}
+
+We used ten paired pollination communities to apply the
+control-theoretic approach. Each community pair was composed of a
+community invaded by a plant and a community free of the invasive
+species. Four pairs correspond to natural or semi-natural vegetation
+communities in the city of Bristol, UK (Lopezaraiza\textendash{}Mikel et
+al., 2007). These communities comprised 19--87 species (mean 55), and
+non-invaded plots were obtained by experimentally removing all the
+flowers of the invasive species \emph{Impatients grandulifera}. The
+other six pairs were obtained from lower diversity Mediterranean
+shrublands in Cap de Creus National Park, Spain (Bartomeus et al.,
+2008). These communities comprised 30--57 species (mean 38); in contrast
+to the above, uninvaded communities were obtained from plots that had
+not yet been colonised by either of the invasive species
+\emph{Carpobrotus affine acinaciformis} or \emph{Opuntia stricta}. The
+structure of all these communities was defined by the pollinator
+visitation frequency, which has been shown to be an appropriate
+surrogate for interspecific effects in pollination networks (Bascompte,
+Jordano, \& Olesen, 2006; Vázquez, Morris, \& Jordano, 2005). Full
+details about the empirical networks can be found in the Supporting
+Information Section \ref{S-empirical-networks}.
+
+The first step in applying methods of control theory is to construct a
+directed network that is able to provide an indication of the extent to
+which species affect each other's abundance. In some ecological
+networks, establishing the directionality can be relatively
+straightforward, for example when links represent biomass transfer or
+energy flow (Isbell \& Loreau, 2013). In pollination networks, however,
+this directionality is less obvious as both species can, in theory,
+benefit from the interaction. We overcome that obstacle by noting that
+the extent to which species \emph{i} affects species \emph{j} relative
+to the extent to which \emph{j} affects \emph{i} can be summarised by
+their interaction asymmetry (Bascompte et al., 2006). This asymmetry is
+given by
+\[a(i,j) = a(j,i) = \frac{\left | d_{ij}-d_{ji} \right |}{max\left ( d_{ij}, d_{ji} \right )},\]
+where the dependence of plant \emph{i} on pollinator \emph{j},
+\emph{d\textsubscript{ij}}, is the proportion of the visits from
+pollinator \emph{j} compared to all pollinator visits to plant \emph{i}.
+Previous research has shown that mutualistic interactions are often
+highly asymmetric in natural communities; in other words, if a plant
+species is largely dependent on a pollinator species, that pollinator
+tends to depend rather weakly on the plant (and vice versa). We
+therefore create a directed link from species \emph{i} to species
+\emph{j} when \(d_{ij}-d_{ji} \geq 0\) to establish the most likely
+direction of control between a species pair (Figure
+\ref{fig:fig-example-networks}a). Sometimes there is no observed
+asymmetry between species pairs (\(d_{ij}=d_{ji}\)), and we cannot infer
+a dominant direction of control. When this occurs, we deem both species
+to be equally likely to affect each other and leave a reciprocal
+interaction between them (a link from \emph{i} to \emph{j} and another
+from \emph{j} to \emph{i}). By basing the direction of the links on the
+asymmetry of their dependence, we are able to generate a network that is
+consistent with the dynamics of the community while satisfying the
+requirements of structural controllability. This allows us to calculate
+the controllability of the networks and investigate whether there are
+differences between invaded and uninvaded communities.
+
+\begin{figure}
+\centering
+\includegraphics{/Users/efc29/github/driver-species/paper/manuscript_files/figure-latex/fig-example-networks-1.pdf}
+\caption{\label{fig:fig-example-networks}The direction of control and
+controllability conditions. (a) To establish the direction of control,
+we start with a weighted visitation network (on the left). In this
+network, the width of the links corresponds to the frequency of
+visitation between animals \(a_i\) and plants \(p_i\), with wider links
+indicating more visits. Plant \(p_1\) is visited exclusively by \(a_1\)
+but \(p_1\) represents only a small fraction of the floral resources
+exploited by \(a_1\). Therefore, the population of \(p_1\) is more
+likely to be affected by \(a_1\) than vice versa. We represent this with
+a directed link from \(a_1\) to \(p_1\) in the control network (on the
+right). The direction of control between all other species pairs can be
+similarly determined by inspecting the difference between their relative
+dependences. (b) Once we have established the directions of control, we
+can determine whether the network is controllable or not. Any system
+defined by a directed network (with state nodes \(x_i\); species'
+populations in an ecological context) and external control inputs (nodes
+\(u_i\), orange links) is structurally controllable if it satisfies two
+conditions: it has no dilations (expansions in the network) and no
+inaccessible nodes. The system on the top left is not controllable
+because there is a dilation since node \(x_2\) is being used to control
+two nodes simultaneously; in other words, there are fewer superiors
+(\(x_2\)) than subordinates (\(x_1\) and \(x_3\)). The network on the
+top right is not controllable because node \(x_3\) is inaccessible for
+the only input node \(u_1\) in the system. Both systems can be made
+controllable by adding an extra input node (\(u_2\) in both bottom
+networks).}
+\end{figure}
+
+\subsection{Controllability}\label{controllability}
+
+A system is said to be controllable if it is possible to steer it from
+an initial to an arbitrary final state within finite time (Kalman,
+1963). A simple version of such a system can be described by
+\(\frac{dx}{dt} = Ax + Bu(t)\), where the change of its state over time
+(\(\frac{dx}{dt}\)) depends on its current state \emph{x} (for example
+the species' abundances), an external time-varying input \emph{u(t)}
+(the control signal), and two matrices \emph{A} and \emph{B}, which
+encode information about the network structure and how species respond
+to external inputs, respectively. In classic control theory, determining
+whether this system is controllable can be achieved by checking that its
+controllability matrix
+\(R= [ \begin{matrix}B & AB & A^{2}B & ...& A^{n-1}B\end{matrix} ]\) has
+full rank. In complex systems, however, employing this rank condition,
+or numerical approximations of it is infeasible because it is hard to
+fully parameterise \emph{A} and \emph{B} (either because the weight of
+the links changes over time or because they are difficult to measure).
+Here, we use an approach based on the structural controllability theorem
+(Lin, 1974), which assumes that we are confident about which elements of
+\emph{A} and \emph{B} have either non-zero or zero values (there is an
+interaction or not), but that we are less sure about the precise
+magnitude of the non-zero values. Using this structural approach, we can
+find out the controllability of a system for every non-zero realisation
+of the parameters.
+
+We are often able to estimate \emph{A} in ecological networks, as this
+matrix represents the interactions between species. Part of the control
+problem thus resides in estimating a supportable estimation of \emph{B},
+which represents the links between external inputs and species. Naively,
+any ecological community (and any system for that matter) could be
+controlled if we control the state of every species independently, but
+such an approach is typically impractical. Here, we are interested in
+finding a minimum driver-node set (effectively finding \emph{B}) with
+which to make the system controllable. The brute-force search for this
+minimum driver-node set is computationally prohibitive for most networks
+as it involves the evaluation of \(2^N\) different controllability
+matrices where \(N\) is the number of species in the community. We
+therefore instead employ a recently-developed approach that shows that
+the control problem of finding the minimum driver-node set can be mapped
+into a graph-theoretic problem: maximum matching (Liu \& Barabási, 2016;
+Liu, Slotine, \& Barabási, 2011).
+
+Maximum matching is a widely studied topic in graph theory and is
+commonly used in multiple applications, ranging from dating apps and
+wireless communications to organ transplant allocation and peer-to-peer
+file sharing. A matching in an unweighted directed graph is defined as a
+set of links that do not share common start or end nodes; the largest
+possible matching is called a maximum matching. For example, in a
+network composed of jobs and job applicants, a matching is any pairing
+between applicants and positions that satisfies one basic constraint: an
+applicant can be assigned to at most one position and vice versa.
+Consequently, a maximum matching is an optimal pairing, one that
+maximises the number of applicants with jobs and the number of positions
+filled. Admittedly, the link between matchings and structural
+controllability may appear far from straightforward.
+
+This link becomes apparent after examining the graphical interpretation
+of structural controllability: from a topological perspective, a network
+is structurally controllable if there are no inaccessible nodes---that
+is, nodes without incoming links---or dilations---\emph{expansions} of
+the network (Figure \ref{fig:fig-example-networks}b; Supporting
+Information Section \ref{S-structural-controllability}). The key is to
+note that these two fundamental conditions of structural controllability
+imply that there is a one-to-one relationship between \emph{superior}
+and \emph{subordinate} nodes just like the one-to-one relationship
+between jobs and applicants (Figure \ref{fig:fig-example-networks}b,
+bottom left). We thus use the maximum-matching algorithm to find an
+optimal pairing of superior (those that can control another node) and
+subordinate nodes (those that can be controlled by another node) in a
+manner consistent with the controllability conditions (Supporting
+Information Section \ref{S-one-maximum-matching}). Given the result, we
+can further decompose the matching into a set of paths that reveal how a
+control signal can flow across the links in a network to reach every
+node within it. As recently shown (Liu et al., 2011), the minimum
+driver-node set---those to which an external control input should be
+applied to make the system controllable---corresponds exactly to the
+\emph{unmatched} nodes in the network (Figure
+\ref{fig:fig-control-configuration}).
+
+\begin{figure}
+\centering
+\includegraphics{/Users/efc29/github/driver-species/paper/manuscript_files/figure-latex/fig-control-configuration-1.pdf}
+\caption{\label{fig:fig-control-configuration}Maximum matchings and control
+configurations. In directed networks, a maximum matching is the largest
+possible set of links that do not share start or end nodes (dark
+purple). Maximum matchings are not necessarily unique; instead, each of
+them is related to a possible minimum driver-node set in the network
+(the nodes to which an external control input, in orange, should be
+applied in order to ensure controllability). The size of the minimum
+driver-node set \emph{D} corresponds exactly to the number of unmatched
+nodes (the number of nodes in the network \emph{N} minus the matching
+size). To account for network size, we use the size of the minimum
+driver-node set relative to the total number of nodes
+\emph{n\textsubscript{D} = D/N} as a measure of the extent to which the
+network structure can be harnessed to control the system.}
+\end{figure}
+
+\subsection{Differences between invaded and uninvaded
+networks}\label{differences-between-invaded-and-uninvaded-networks}
+
+\R{R2-ecol-objective} Our first objective is to investigate whether the
+controllability of a community is associated with invasion status or
+not. \R{R2-desired-control-trajectory} Finding out exactly how difficult
+it is to control a network depends strongly on the particularities of
+the desired control trajectory (i.e.~the path to the desired final
+state) as well as the dynamical relationship between nodes. However, we
+are interested in understanding the controllability of a network in a
+more general sense, such that it can be applied even when the precise
+control scenario is known only incompletely. To this end, we chose an
+indicator that follows directly from our approach: the size of the
+minimum driver-node set. This simple metric provides a general
+indication of how difficult controlling a network might be, as systems
+that require a large number of external inputs to be fully controlled
+are intuitively more difficult or costly to manage. For instance,
+achieving full control in a ``network'' in which species do not interact
+at all is relatively more difficult as we would require an intervention
+for every single species. Conversely, the structure of a linear trophic
+chain can be harnessed to achieve full control using just one
+intervention targeted at the top species; a suitable control signal
+could then cascade through the trophic levels and reach other species in
+the community. Specifically, drawing from the structural-controllability
+literature, we use the size of the minimum driver-node set relative to
+the total number of species \(n_D = \frac{D}{N}\) as a measure of the
+\emph{controllability} of a network---the extent to which the network
+structure can be harnessed to control the community. The lower \(n_D\)
+the more controllable the community. In an ecological context, external
+inputs can be thought of as management interventions that modify the
+abundance of a particular species.
+
+After finding the minimum driver-node set in each of our networks, we
+wanted to test whether invasion status or other predictors are
+correlated to controllability. We do this using a set of generalised
+linear models with binomial error structure. The response variable was
+the relative size of the minimum driver-node set \(n_D\) of the twenty
+empirical networks (ten invaded and ten uninvaded), and we included
+invasion status as a predictor. As predictors, we also include the
+network connectance, the network nestedness (NODF), the number of
+species (since one might naively expect to see a negative relationship
+between richness and controllability; Menge, 1995), the network
+asymmetry (an indication of the balance between plant and pollinator
+diversity), and the interaction strength asymmetry (the asymmetry on the
+dependences between trophic levels; N. Blüthgen, Menzel, Hovestadt,
+Fiala, \& Blüthgen, 2007)\R{R2-citation-with-name}. We compared models
+using the Akaike Information Criterion for small sample sizes (AICc).
+
+In addition, we also explored whether real networks differ in their
+architecture from random ones in a concerted way that could impact these
+results. Specifically, we used two null models each with 99
+randomisations per network. In the first, we followed Vázquez et al.
+(2007) and maintained the connectance of the network but randomised the
+visits across species such that the relative probabilities of
+interactions were maintained. We then re-estimated the direction of
+control and the corresponding size of the minimum driver-node set,
+\(n_D\). For the second null model, we used the empirical directed
+network described above and randomly shuffled the direction of control
+between a species pair prior to re-estimating the size of the minimum
+driver-node set.
+
+\subsection{Species' roles}\label{species-roles}
+
+Our second objective is related to how species differ in their ability
+to drive the population dynamics of the community. We in turn examine
+whether these differences are also reflected in the role species play at
+supporting the stable coexistence of other species in the community.
+Ecologically, these differences are relevant because resources and data
+are limited, and therefore full control is infeasible. While calculating
+the size of the minimum drive-node set can measure the controllability
+of an ecological community, it does not provide information about the
+roles that particular species play.
+
+To answer this question, we harness the fact there may be multiple
+maximum matchings for a given network, and each of these maximum
+matchings indicates a unique combination of species with which it is
+possible to control the network. Moreover, some species belong to these
+combinations more often than do others. We call this property a species'
+``control capacity'', \(\phi\). The higher a species' control capacity,
+the greater the likelihood that it would need to be directly managed to
+change (or maintain) the ecological state of their community. Therefore,
+a species' control capacity provides an estimation of its relative
+importance at driving the state of the community (Jia \& Barabási,
+2013).
+
+To calculate a species' control capacity \(\phi\), we must first
+enumerate all possible maximum matchings (Supporting Information Section
+\ref{S-all-maximum-matching}). Unfortunately, enumerating all maximum
+matchings is extremely expensive from a computational perspective---a
+network with a couple dozen species has several hundred million unique
+maximum matchings. To solve this problem, we employ a recently-developed
+algorithm that reveals the control correlations between the nodes in the
+graph while requiring considerably less computational resources (Zhang,
+Lv, \& Pu, 2016). Using this algorithm, we are able to identify species
+that are possible control inputs---those that belong to the minimum
+driver-node set in at least one of the possible control configurations.
+Here, we extend this algorithm such that it is possible to calculate a
+highly accurate approximation of the control capacity \(\phi\) of every
+species in the network (Supporting Information Section
+\ref{S-input-graph}). In the networks that contained reciprocal links
+(because there was no asymmetry in the dependences of a species pair),
+we averaged a species' control capacity \(\phi\) across every possible
+``non-reciprocal'' version of the network (Supporting Information
+Section \ref{S-reciprocal-links}).
+
+\R{R2-one-lumped-model-a}We then examined how species-level properties
+were related to control capacity using a set of candidate generalised
+linear models with binomial error structure. These models included five
+predictor variables that mirror the network-level predictors. First, the
+species' contribution to nestedness, which has been proposed as a key
+feature that promotes stability and robustness in mutualistic networks
+(Saavedra, Stouffer, Uzzi, \& Bascompte, 2011).
+Second,\R{R2-species-strength-a} the species' strength (the sum of a
+species' visits), which quantifies the strength of a species'
+associations and is indirectly related to its abundance (Poisot, Canard,
+Mouquet, \& Hochberg, 2012). Third, the direction of asymmetry which
+quantifies the net balance in dependencies; that is, it indicates if a
+species affects other species more than what they affect it or not
+(Vázquez et al., 2007). Fourth, the species' degree in order to account
+for the intrinsic centrality of a species. Finally, we included a
+categorical variable for the species' trophic level (plant or
+pollinator) and an interaction term between trophic level and the
+previous four variables. To facilitate comparison between predictors,
+degree and visitation strength were log-transformed and all four
+continuous variables were scaled to have a mean of zero and a standard
+deviation of one. \R{R2-one-lumped-model-b}In these models, species from
+all networks were lumped together. \R{R2-random-effects}We initially
+included random effects to account for possible variation across
+communities, but we found that the variance explained by these random
+effects was zero, and therefore random effects were not included in
+further analyses. \R{R2-all-candidates}We then generated all possible
+candidate models. To identify the models that were best supported by the
+data, we first determined the most parsimonious random structure using
+the AICc. The relative importance of variables was then assessed by
+looking at their effect sizes in the top-ranked models and the
+cumulative weight of the models in which they are present.
+
+In addition, we wanted to understand how a species' control capacity
+\(\phi\) described above relates to metrics of keystoneness based on
+centrality. Specifically, in each network, we calculated the species'
+degree, betweenness, closeness centrality (Martín González et al.,
+2010), page rank (McDonald-Madden et al., 2016), and eigen centrality
+(Jordano, Bascompte, \& Olesen, 2006). We then calculated the spearman
+correlation coefficient between control capacity and each of these
+centrality metrics.
+
+Our analysis revealed that some species have a control capacity
+\(\phi = 1\). These species are critical to controlling their community
+because they are part of the minimum driver-node set in \emph{every}
+control scenario. In other words, it is theoretically impossible to
+drive the state of the community to a desired state without directly
+managing the abundance of these species. We thus anticipate that these
+species have a disproportionally large impact on the community dynamics.
+To test this hypothesis, we identified these critical species in each of
+the networks and investigated whether they have a larger than average
+impact on the stable coexistence of species in the community. Within
+mutualistic networks, one useful measure of stable coexistence is called
+structural stability (Rohr, Saavedra, \& Bascompte, 2014).
+Mathematically, the structural stability of a network represents the
+size of the parameter space (i.e., growth rates, carrying capacities,
+etc.) under which all species can sustain positive abundances (Saavedra,
+Rohr, Olesen, \& Bascompte, 2016). The contribution of any given species
+\emph{i} to stable coexistence can be estimated by calculating the
+structural stability of the community when the focal species \emph{i} is
+removed. To allow comparison across communities, the structural
+stability values were scaled within each network to have a mean of zero
+and a standard deviation of one. Given these species-specific estimates
+of structural stability, we then used a t-test to compare the
+contribution to stable coexistence of critical and non-critical species.
+More details about the calculation of structural stability can be found
+in the Supporting Information Section \ref{S-structural-stability}.
+
+\subsection{Testing assumptions}\label{testing-assumptions}
+
+Just like the centrality metrics, the information obtained by applying
+structural controllability depends on the ability of the network to
+accurately represent the ecological community. We thus tested the
+sensitivity of our approach to two fundamental assumptions. First, we
+tested that visitation is an appropriate proxy to infer interspecific
+effects by comparing the results obtained using visitation to two
+alternative metrics in a separate dataset that lacked invasive species
+(Ballantyne, Baldock, \& Willmer, 2015). Specifically, we also
+calculated the controllability (the size of the minimum driver node-set)
+and the control capacity of networks constructed using pollinator
+efficiency (which measures the pollen deposition of an interaction) and
+pollinator importance (which accounts for both pollen deposition and
+visitation and hence is regarded as a more accurate estimation of the
+pollination service received by plants; Ne'eman, Jürgens,
+Newstrom-Lloyd, Potts, \& Dafni, 2010). \R{R2-sentence-fragment} See
+Supporting Information Section \ref{S-visitation-as-proxy} for more
+details.
+
+Second, because interspecific dependencies themselves depend on the
+network topology and consequently on the accurate sampling of
+interactions, we tested the robustness of structural controllability to
+the uncertainty involved with the sampling of interactions. Here, we
+compared the results obtained when using the full network and when
+randomly removing interactions from the weakest links in the network.
+This effectively removed the rare interactions from the networks (more
+details in the Supporting Information Section \ref{S-undersampling}).
+
+\section{Results}\label{results}
+
+\subsection{Controllability}\label{controllability-1}
+
+The size of the minimum driver-node set relative to the number of
+species in each network \(n_D\) ranged between \(n_D = 0.58\) and
+\(n_D = 0.88\) (median 0.74).
+
+\subsection{Differences between invaded and uninvaded
+networks}\label{differences-between-invaded-and-uninvaded-networks-1}
+
+We found that the relative size of the minimum driver-node set of
+invaded communities was not significantly different from that of
+communities that have not been invaded (Figure
+\ref{fig:fig-emp-controllability}a). In contrast, there was a large
+negative relationship between \(n_D\) and the network asymmetry (Figure
+\ref{fig:fig-emp-controllability}b). Furthermore, there were also
+negative, albeit weaker, relationships between \(n_D\) and connectance,
+nestedness and species richness (Table
+\ref{S-tab:tab-controllability-model-results}). The relative size of the
+minimum driver-node set \(n_D\) of empirical networks did not differ
+from that of a null model that roughly preserved the degree distribution
+and fully preserved the network connectance (\(p = \num{0.66}\); Figure
+\ref{fig:fig-emp-controllability}c). However, empirical networks had a
+larger \(n_D\) than null models that preserved the interactions but
+shuffled the direction of control of the empirical network
+(\(p = \num{2.4e-07}\)).
+
+\begin{figure}
+\centering
+\includegraphics{/Users/efc29/github/driver-species/paper/manuscript_files/figure-latex/fig-emp-controllability-1.pdf}
+\caption{\label{fig:fig-emp-controllability}Drivers of network
+controllability. (a) Probability density of the relative size of the
+minimum driver-node set \(n_D\) in the invaded (light) and uninvaded
+(dark) empirical networks. (b) Relationship between the asymmetry
+plant/pollinator richness and \(n_D\). (c) Probability density of the
+difference between the relative size of the minimum driver-node set of
+random networks and that of empirical networks. We randomised either the
+species visitation patterns (light line) or randomised the direction of
+control between a species pair (dark line). The vertical dashed lines in
+(a) and (c) indicate the median values of the distributions.}
+\end{figure}
+
+\subsection{Species' roles}\label{species-roles-1}
+
+Species varied widely in their control capacity (Figure
+\ref{fig:fig-species-level}). Pollinators had, in average, larger
+control capacities than plants. That said, almost no pollinator was
+critical for network control, (where a species is critical for control
+if it has control capacity \(\phi_i = 1\)). Plants had a multimodal
+distribution of control capacity with maxima at both extremes of the
+distribution (Figure \ref{fig:fig-species-level}a). Intriguingly, every
+invasive species was critical for network control in each of their
+communities. The species-level models identified a positive relationship
+between control capacity \(\phi\) and a species' contribution to
+nestedness, visitation strength, and the asymmetry of its dependences
+(Table \ref{tab:tab-model-selection-table}; Figure
+\ref{fig:fig-species-partial}; Table
+\ref{S-tab:tab-model-output-species-level}). Comparatively, species'
+degree was only weakly associated with control capacity (Table
+\ref{S-tab:tab-var-importance}). In fact, many species with a low
+degree, especially pollinators, exhibited a large control capacity in
+their communities (Figure \ref{S-fig:fig-species-models-degree}a).
+
+Species' control capacity \(\phi\) was only weakly correlated with
+commonly-used centrality metrics. The Spearman correlation between these
+ranged between -0.14 (with betweeness-centrality) and 0.42 (with
+eigen-centrality), see Figure \ref{S-fig:fig-correlogram}a. The
+correlation coefficient with degree was -0.13, however most species with
+high degree also tended to attain a high control capacity (Figure
+\ref{S-fig:fig-species-models-degree}a).
+
+\begin{table}
+
+\caption{\label{tab:tab-model-selection-table}Selection table of the binomial generalised linear models of species' control capacity, $\phi$.
+Only models with a weight larger or equal to 0.01 are shown.}
+\centering
+\fontsize{8}{10}\selectfont
+\begin{threeparttable}
+\begin{tabular}[t]{rrlrrrllllrrr}
+\toprule
+\multicolumn{10}{c}{model terms} & \multicolumn{ 3}{c}{ } \\
+\cmidrule(l{2pt}r{2pt}){1-10}
+int. & $k$ & $l$ & $a$ & $n$ & $s$ & $k$:$l$ & $l$:$a$ & $l$:$n$ & $l$:$s$ & d.f. & $\Delta$AICc & weight\\
+\midrule
+-1.20 &  & + & 0.80 & 0.15 & 0.29 &  & + & + &  & 7 & 0.00 & 0.48\\
+-1.19 &  & + & 0.76 & 0.13 & 0.35 &  & + & + & + & 8 & 1.52 & 0.22\\
+-1.26 & -1.24 & + & 1.44 & 0.39 & 1.07 & + & + &  & + & 9 & 4.09 & 0.06\\
+-1.37 & -0.66 & + & 1.03 &  & 1.06 & + & + &  & + & 8 & 4.39 & 0.05\\
+-1.27 & -1.15 & + & 1.37 & 0.33 & 1.07 & + & + & + & + & 10 & 4.92 & 0.04\\
+\addlinespace
+-1.37 & -0.10 & + & 0.90 &  & 0.43 & + & + &  &  & 7 & 6.36 & 0.02\\
+-1.25 & -0.28 & + & 1.24 & 0.40 &  & + & + &  &  & 7 & 6.47 & 0.02\\
+-1.24 & -0.62 & + & 1.29 & 0.38 & 0.40 & + & + &  &  & 8 & 6.50 & 0.02\\
+-1.39 & 0.30 & + & 0.83 &  &  & + & + &  &  & 6 & 6.72 & 0.02\\
+-1.28 & -0.17 & + & 1.16 & 0.32 &  & + & + & + &  & 8 & 7.03 & 0.01\\
+\addlinespace
+-1.26 & -0.53 & + & 1.23 & 0.32 & 0.39 & + & + & + &  & 9 & 7.42 & 0.01\\
+-1.02 &  & + & 0.69 & 0.30 & 0.31 &  & + &  &  & 6 & 7.48 & 0.01\\
+\bottomrule
+\end{tabular}
+\begin{tablenotes}[para]
+\item \textit{Terms: } 
+\item intercept (int), degree ($k$), trophic level ($l$), asymmetry ($a$), contribution to nestedness ($n$), visitation strength ($s$).
+\end{tablenotes}
+\end{threeparttable}
+\end{table}
+
+\begin{figure}
+\centering
+\includegraphics{/Users/efc29/github/driver-species/paper/manuscript_files/figure-latex/fig-species-level-1.pdf}
+\caption{\label{fig:fig-species-level}Probability density of the control
+capacity \(\phi\) of (a) plants and (b) pollinators across all networks.
+The control capacity of all invasive species is \(\phi = 1\) and is
+depicted with solid circles.}
+\end{figure}
+
+\begin{figure}
+\centering
+\includegraphics{/Users/efc29/github/driver-species/paper/manuscript_files/figure-latex/fig-species-partial-1.pdf}
+\caption{\label{fig:fig-species-partial}Partial-residual plots for the
+independent variables: (a) contribution to nestedness, (b) visitation
+strength, (c) asymmetry of dependences, and (d) degree. Partial-residual
+plots show the relationship between control capacity and each of the
+independent variables while acccounting for all other remaining
+variables. Ploted values correpond to the predictions of the weighted
+average of the models shown in Table
+\ref{tab:tab-model-selection-table}.}
+\end{figure}
+
+Finally, we found that critical species have a particularly large impact
+on species coexistence when compared to non-critical species. Indeed,
+the structural stability of the networks where critical species were
+removed was considerably lower to those in were non-critical species
+were removed (\(p = \num{2e-15}\); Figure
+\ref{fig:fig-structural-stability}; Supporting Information
+\ref{S-structural-stability}).
+
+\begin{figure}
+\centering
+\includegraphics{/Users/efc29/github/driver-species/paper/manuscript_files/figure-latex/fig-structural-stability-1.pdf}
+\caption{\label{fig:fig-structural-stability}Probability density of the
+structural stability of the communities after a single focal species is
+removed. Mathematically, the structural stability of a network
+represents the size of the parameter space (i.e., growth rates, carrying
+capacities, etc.) under which all species can sustain positive
+abundances. The structural stability of communities in which critical
+species have been removed (darker line) is considerably smaller than
+that of communities in which non-critical species have been removed.
+This indicates that critical species contribute more to the stable
+coexistence of their communities. To allow comparison across
+communities, the structural stability values were scaled within each
+network to have a mean of zero and a standard deviation of one. Here, we
+assume values of the mutualistic trade-off and mean interspecific
+competition of \(\delta = 0\) and \(\rho = 0.01\) respectively (Saavedra
+et al., 2016). However, the choice of these parameters does not affect
+the results (Supporting Information \ref{S-structural-stability}).}
+\end{figure}
+
+\subsection{Testing assumptions}\label{testing-assumptions-1}
+
+We found that using visitation as a proxy for the strength of species'
+interactions leads to similar results than those obtained using
+pollinator importance (regarded as an accurate measure of the
+pollination service to plants; Supporting Information Section
+\ref{S-visitation-as-proxy}; Ne'eman et al., 2010). Importantly, we also
+found that structural stability is robust to incomplete sampling of
+interactions. Indeed, we found strong agreement between results obtained
+using the complete empirical networks and those obtained by randomly
+removing the weakest interactions (Supporting Information Section
+\ref{S-undersampling}). Despite removing rare interactions and species,
+the relative size of the minimum driver-node set, the superior species,
+and the relative rankings of control capacity were generally maintained.
+Of particular note, we found that critical species in the full network
+were also critical in the vast majority of rarefied networks.
+
+\section{Discussion}\label{discussion}
+
+Our main goal was to understand the role that species play in both
+modifying the abundance of the species they interact with and the state
+of the community as a whole. To achieve that goal we applied
+\emph{structural controllability}, a field at the intersection between
+control and complex theory that allowed us to obtain two key pieces of
+information: the \emph{controllability} of a network and a species'
+\emph{control capacity} (Table \ref{tab:tab-glossary}). We found that
+the controllability of a network does not depend on its invasion status
+and that the species that are critical to altering the state of the
+community are also the ones that most sustain the stable coexistence of
+species in their communities.
+
 Our results indicate that fully controlling ecological networks might
-currently be out of reach for all but the smallest communities (A. E.
-Motter, 2015). Indeed, the median size of the relative minimum
-driver-node set in our dataset was \(n_D = 0.74\), a high value when
-compared to other complex systems in which controllability has been
-investigated (the lower \(n_D\) the more controllable the community).
-For instance, only gene regulation networks appear to achieve similar
-levels of controllability while most social, power transmission,
-Internet, neuronal, and even metabolic networks seem to be ``easier'' to
-control (\(0.1 < n_D < 0.35\)) (Liu et al., 2011). Structural
-controllability provides solid theoretical rationale for the many
-difficulties encountered in the management and restoration of natural
-communities (Woodford et al., 2016). Nevertheless, structural
-controllability might be helpful at identifying communities in which
-changes in the ecological state are more likely to occur
+currently be out of reach for all but the smallest communities (Motter,
+2015). Indeed, the median size of the relative minimum driver-node set
+in our dataset was \(n_D = 0.74\), a high value when compared to other
+complex systems in which controllability has been investigated (the
+lower \(n_D\) the more controllable the community). For instance, only
+gene regulation networks appear to achieve similar levels of
+controllability while most social, power transmission, Internet,
+neuronal, and even metabolic networks seem to be ``easier'' to control
+(\(0.1 < n_D < 0.35\)) (Liu et al., 2011). Structural controllability
+provides solid theoretical rationale for the many difficulties
+encountered in the management and restoration of natural communities
+(Woodford et al., 2016). Nevertheless, structural controllability might
+be helpful at identifying communities in which changes in the ecological
+state are more likely to occur.
 
@@
 no difference between the controllability of invaded and uninvaded
-networks. instead controllability is almost completely constrained by
+networks. Instead controllability is almost completely constrained by
 the patterns of species richness at each trophic guild and their degree
-distributions (N. Blüthgen et al., 2007; C. J. Melián \& Bascompte,
-2002). These two factors are particularly relevant because they govern
-the asymmetric nature of mutual dependences, which themselves provide
-the foundation of structure and stability in mutualistic networks
-(Astegiano, Massol, Vidal, Cheptou, \& Guimarães, 2015; J. Bascompte et
-al., 2006; J. Memmott, Waser, \& Price, 2004).
-
-Accordingly, our results suggest that structural controllability is
-closely related to the dynamic persistence of an ecological community
-based on two lines of evidence. First, we found a comparatively small
-but thought-provoking negative relationship between the controllability
-of a network and its nestedness. Previous studies indicate that
-nestedness promotes species coexistence and confers robustness to
-extinction (Bastolla et al., 2009; J. Memmott et al., 2004) even at the
-expense of the dynamic stability of the mutualistic community (S.
-Saavedra et al., 2016). These observations are in agreement with our
-results, as we would expect the dynamic stability of a community to be
-correlated to the difficulty to control it. Second, species' control
-capacity was strongly correlated to their contribution to nestedness and
-critical species had the largest impact to the stable coexistence of
-species in their communities. Therefore, species that play a key role at
+distributions (N. Blüthgen et al., 2007; Melián \& Bascompte, 2002).
+These two factors are particularly relevant because they govern the
+asymmetric nature of mutual dependences, which themselves provide the
+foundation of structure and stability in mutualistic networks
+(Astegiano, Massol, Vidal, Cheptou, \& Guimarães, 2015; Bascompte et
+al., 2006; Memmott, Waser, \& Price, 2004).
+
+\R{R2-dynamic-persistence}Accordingly, our results suggest that
+structural controllability is closely related to the persistence of an
+ecological community based on two lines of evidence. First, we found a
+comparatively small but thought-provoking negative relationship between
+the controllability of a network and its nestedness. Previous studies
+indicate that nestedness promotes species coexistence and confers
+robustness to extinction (Bastolla et al., 2009; Memmott et al., 2004)
+even at the expense of the dynamic stability of the mutualistic
+community (Saavedra et al., 2016). These observations are in agreement
+with our results, as we would expect the dynamic stability
+\R{R2-dynamic-stability}(the ability to return to equilibrium after a
+perturbation in species abundances) of a community to be correlated to
+the difficulty to control it. Second, species' control capacity was
+strongly correlated to their contribution to nestedness and critical
+species had the largest impact to the stable coexistence of species in
+their communities. Therefore, species that play a key role at
 determining the state of the community might also be more key to
@@
 
-When controlling for a species' strength, which is indirectly a proxy of
+When controlling for a \R{R2-species-strength-b}species' visitation
+strength (the sum of a species' visits), which is indirectly a proxy of
 its abundance, and the net balance of its dependencies, we found that
@@
 the dynamics of their communities and their utility at predicting
-species extinctions (Jordan, 2009). However, further, inspection shows
+species extinctions (Jordan, 2009). However, further inspection shows
 that our results do not contradict these findings; most species with a
@@
 
-\R{management-implications}Other conceptual differences between
-structural controllability and centrality metrics provide three key
-insights into the conservation of ecological networks. First, structural
+Other conceptual differences between structural controllability and
+centrality metrics provide three key insights into the conservation of
+ecological networks. \R{R2-structural-controllability} First, structural
 controllability emphasizes that the effect a species has on the
-abundance of other species is not independent of the effects of other
+abundance of other species is not independent of the effects of those
 other species in their community. The rankings provided by centrality
@@
 traits or centrality are still useful and are likely to overlap with
-species control capacity\R{extra-references-1} (Devoto, Bailey, Craze,
-\& Memmott, 2012; Pires, Marquitti, \& Guimarães, 2017). Stepping back,
-our results also provide support to the idea that management decisions
-should not be based on a single technique but indicate that focusing on
-ecosystem processes and interactions may be more effective than
-traditional ranking-based approaches \R{extra-references-2} (Harvey,
-Gounand, Ward, \& Altermatt, 2017).
+species' control capacity (Devoto, Bailey, Craze, \& Memmott, 2012;
+Pires, Marquitti, \& Guimarães, 2017). Stepping back, our results also
+provide support to the idea that management decisions should not be
+based on a single technique but indicate that focusing on ecosystem
+processes and interactions may be more effective than traditional
+ranking-based approaches (Harvey, Gounand, Ward, \& Altermatt, 2017).
 
@@
 Morales, 2008; Bartomeus et al., 2008; Henriksson, Wardle, Trygg, Diehl,
-\& Englund, 2016) and to be central in their communities (Palacio,
-Valderrama-Ardila, \& Kattan, 2016; Vila et al., 2009). We found that
-invasive plants are, however, unlikely to be inherently different from
-their native counterparts (Emer, Memmott, Vaughan, Montoya, \&
-Tylianakis, 2016; Stouffer, Cirtwill, \& Bascompte, 2014). Just like any
-other mutualist in our dataset, invasive plants tended to attain a high
-control capacity proportional to the degree to which they contribute to
-network persistence, are abundant, and depend little on other species.
+\& Englund, 2016) \R{R2-central-in-their-communities}and to attain high
+centrality in their communities (Palacio, Valderrama-Ardila, \& Kattan,
+2016; Vila et al., 2009). \R{R2-inherrently-different} We found that it
+is not that invasive plants have some different mechanism for
+influencing the community compared to their native counterparts (Emer,
+Memmott, Vaughan, Montoya, \& Tylianakis, 2016; Stouffer, Cirtwill, \&
+Bascompte, 2014). Both native species and invasive plants tended to
+attain a high control capacity if they were important to network
+persistence, were abundant, and depended little on other species.
 Furthermore, our observation that changes in the abundance of invasive
@@
 ecosystem restoration focused on the eradication of invasive plants can
-have transformative desirable effects in plant-pollinator
-communities\R{extra-references-3} (Kaiser-Bunbury et al., 2017).
-However, our results also suggest that removals must be exercised with
-caution. Not only it is hard to predict the direction in which the
-system will change, but we also show that critical species can underpin
-the coexistence of species and therefore some communities may be acutely
-vulnerable to their eradication (Albrecht, Padron, Bartomeus, \&
-Traveset, 2014; Traveset et al., 2013).
+have transformative desirable effects in plant-pollinator communities
+(Kaiser-Bunbury et al., 2017). However, our results also suggest that
+removals must be exercised with caution. Not only it is hard to predict
+the direction in which the system will change, but we also show that
+critical species can underpin the coexistence of species and therefore
+some communities may be acutely vulnerable to their eradication
+(Albrecht, Padron, Bartomeus, \& Traveset, 2014; Traveset et al., 2013).
 
@@
 achieve a desired state. In an ideal scenario, we would completely
-incorporate the species dynamics into the controllability analysis
+incorporate the species' dynamics into the controllability analysis
 (Cornelius, Kath, \& Motter, 2013); the reality is that such information
-is rarely available in most ecological scenarios.
-\R{data-requirements}In contrast, structural controllability only
-requires a quantitative approximation of the network's interactions to
-gain valuable insight from the community. Furthermore, while the
-relationship between centrality and keystoneness is based on an
-intuitive understanding of what a keystone species is, the assumptions
-of structural controllability are explicit and the estimation of a
-species importance arises from a mechanistic understanding of the
-population dynamics between species. By accounting for network dynamics
-(even if in a simple way), structural stability incorporates more
-ecological realism, especially in the extreme scenario in which the
-state of a community is only marginally affected by the topology of
-their interactions.
+is rarely available in most ecological scenarios. In contrast,
+structural controllability only requires a quantitative approximation of
+the network's interactions to gain valuable insight from the community.
+Furthermore, while the relationship between centrality and keystoneness
+is based on an intuitive understanding of what a keystone species is,
+the assumptions of structural controllability are explicit and the
+estimation of a species' importance arises from a mechanistic
+understanding of the population dynamics between species.
+\R{R2-marginally-affected} By accounting for network dynamics (even if
+in a simple way), structural stability incorporates more ecological
+realism, especially in the extreme scenario in which the structure of
+interactions within the community only marginally affects the
+community's state.
 
@@
 ecological setting to gain insight into the stability of a community and
-the role that species play at modifying the abundance of other species
+the role that species play in modifying the abundance of other species
 and ultimately the state of the community. These characteristics make
@@
 Ballantyne, G., Baldock, K. C. R., \& Willmer, P. G. (2015).
-Constructing more informative plantPollinator networks: Visitation and
+Constructing more informative plant-pollinator networks: Visitation and
 pollen deposition networks in a heathland plant community.
@@
 
-\hypertarget{ref-bartomeus_contrasting_2008-1}{}
+\hypertarget{ref-bartomeus_contrasting_2008}{}
 Bartomeus, I., Vilà, M., \& Santamaría, L. (2008). Contrasting effects
-of invasive plants in plantPollinator networks. \emph{Oecologia},
+of invasive plants in plant-pollinator networks. \emph{Oecologia},
 \emph{155}(4), 761--770.
@@
 
-\hypertarget{ref-neeman_framework_2009}{}
+\hypertarget{ref-neeman_framework_2010}{}
 Ne'eman, G., Jürgens, A., Newstrom-Lloyd, L., Potts, S. G., \& Dafni, A.
-(2009). A framework for comparing pollinator performance: Effectiveness
+(2010). A framework for comparing pollinator performance: Effectiveness
 and efficiency. \emph{Biological Reviews}, no--no.

### 2019-01-13 paper/drafts_and_revisions/2019-01-14/supp-info.tex
Add revision with most responses to reviewers

--- 2019-01-13 paper/drafts_and_revisions/2018-07-19/supp-info.tex
@@
 
-The networks studied had species richness ranging between 19 and 87 when
-considering only the largest component in each network). As shown by the
-network asymmetry \emph{AS} (N. Blüthgen, Menzel, Hovestadt, Fiala, \&
-Blüthgen, 2007), the networks had a low ratio of plants to pollinators
-overall. Furthermore, the networks had relatively low levels of
-nestedness (when measured using the quantitative version of the NODF
+The networks studied had species richness ranging between 19 and 87
+(when considering only the largest component in each network). As shown
+by the network asymmetry \emph{AS} (N. Blüthgen, Menzel, Hovestadt,
+Fiala, \& Blüthgen, 2007), the networks had a low ratio of plants to
+pollinators overall. Furthermore, the networks had relatively low levels
+of nestedness (when measured using the quantitative version of the NODF
 index; Almeida-Neto \& Ulrich, 2011). Details for each network can be
@@
 \caption{\label{tab:table-network-properties}Properties of the analysed plant-pollinator communities.
-Here show the number of species ($n_s$), the number of plants ($n_p$), the number of pollinators ($n_a$), the network connectance ($c$), the network asymmetry ($AS$), and the network nestedness (NODF index).
+Here show the number of species ($n_s$), the number of plants ($n_p$), the number of pollinators ($n_a$), the network connectance ($C$), the network asymmetry ($AS$), and the network nestedness (NODF index).
 All properties correspond to the network's largest component.
@@
 bipartite representation in Figure
-\ref{fig:fig-maximum-matching-procedure}b and assign an identity to each
-of the links in the network. We will call this bipartite representation
-\emph{P}. We then construct the line graph of the alternative bipartite
-representation \emph{L(P)} (Figure \ref{fig:fig-all-maximum-matching}).
-Each node in \emph{L(P)} represents a link in \emph{P} and these are
-connected to each other if and only if they share a common node in
-\emph{P}. We then calculate \emph{H}, the complement graph of
-\emph{L(P)} and identify all of its maximal cliques (Figure
-\ref{fig:fig-all-maximum-matching}). Here some extra definitions are
-necessary. First, \emph{H} is a graph with the same nodes as \emph{L(P)}
-but that has a link between two nodes if and only if there is not a link
-in \emph{L(P)}. Second, a clique is a subset of nodes such that all
-pairs of them are linked. Lastly, a maximal clique is a clique such that
-there are no cliques composed of more nodes (Gutin, 2013). In this
-example, there are two maximal cliques. The final step is then to map
-these cliques onto the original network to obtain all possible maximal
-cardinality matchings as shown in Figure
+\ref{fig:fig-maximum-matching-procedure} (center panel) and assign an
+identity to each of the links in the network. We will call this
+bipartite representation \emph{P}. We then construct the line graph of
+the alternative bipartite representation \emph{L(P)} (Figure
+\ref{fig:fig-all-maximum-matching}). Each node in \emph{L(P)} represents
+a link in \emph{P} and these are connected to each other if and only if
+they share a common node in \emph{P}. We then calculate \emph{H}, the
+complement graph of \emph{L(P)} and identify all of its maximal cliques
+(Figure \ref{fig:fig-all-maximum-matching}). Here some extra definitions
+are necessary. First, \emph{H} is a graph with the same nodes as
+\emph{L(P)} but that has a link between two nodes if and only if there
+is not a link in \emph{L(P)}. Second, a clique is a subset of nodes such
+that all pairs of them are linked. Lastly, a maximal clique is a clique
+such that there are no cliques composed of more nodes (Gutin, 2013). In
+this example, there are two maximal cliques. The final step is then to
+map these cliques onto the original network to obtain all possible
+maximal cardinality matchings as shown in Figure
 \ref{M-fig:fig-control-configuration} in the main text.
@@
 
-The algorithm proposed by Zhang, Lv, \& Pu (2016) enable us to find all
+The algorithm proposed by Zhang, Lv, \& Pu (2016) enables us to find all
 minimum driver node sets without calculating all possible maximum
@@
 not belong to the minimum driver node set and is not adjacent to any
-possible input node, then it does not part of the minimum driver node
-set under any control configuration. Finally, if a node \(x_i\) belongs
-to the minimum driver node set and is adjacent to another node \(x_j\)
-in the input graph, then \(x_j\) must belong to another minimum driver
-node to which \(x_i\) does not belong, in other words, \(x_i\) and
-\(x_j\) are substitutable.
+possible input node, then it does not become part of the minimum driver
+node set under any control configuration. Finally, if a node \(x_i\)
+belongs to the minimum driver node set and is adjacent to another node
+\(x_j\) in the input graph, then \(x_j\) must belong to another minimum
+driver node to which \(x_i\) does not belong, in other words, \(x_i\)
+and \(x_j\) are substitutable.
 
@@
 computing the number of possible substitutions of a node by its control
-adjacent nodes. As a rule of thumb, the largest the number of possible
+adjacent nodes. As a rule of thumb, the larger the number of possible
 substitutions an input node has, the smaller its control capacity.
@@
 size of the minimum driver node set, \(n_D\)) and species level (control
-capacity, \(\phi\), and the likelihood of being a superior node,
-\(\sigma\)) we first need to generate all possible versions of the of
-the network that include only non-reciprocal links (Figure
-\ref{fig:fig-bidirectional}).
+capacity, \(\phi\), and wether it is a superior node, \(\sigma\)) we
+first need to generate all possible versions of the of the network that
+include only non-reciprocal links (Figure \ref{fig:fig-bidirectional}).
 
@@
 all the networks without reciprocal links without weighting by the
-number of possible control configurations.
+number of possible control configurations. It is important to note that
+a species that is found to be a superior node under a particular control
+configuration, will be so in all possible control configurations for the
+particular non-reciprocal network. We, therefore denote the average of
+\(\sigma\) across all non-reciprocal versions as the probability of the
+species being a superior node in its community.
 
@@
 
-We follow R. P. Rohr, Saavedra, \& Bascompte (2014) and S. Saavedra,
-Rohr, Olesen, \& Bascompte (2016) to calculate the structural stability
-of the empirical networks. We first calculate the stability condition
+We follow Rohr, Saavedra, \& Bascompte (2014) and Saavedra, Rohr,
+Olesen, \& Bascompte (2016) to calculate the structural stability of the
+empirical networks. We first calculate the stability condition
 \(\hat{\gamma}\) using all species in the network. To calculate the
@@
 \(\delta = 0\) and a mean interspecific competition of \(\rho = 0.01\)
-(S. Saavedra et al., 2016). The choice of the parameters had only a
-minor impact on the relative contribution of species to stable
-coexistence (Figure \ref{fig:fig-rho-sensitivity}a) and overall there
-was no change on our result that indicates that critical species (those
-with \(\phi = 1\)) have a larger than average contribution to stable
+(Saavedra et al., 2016). The choice of the parameters had only a minor
+impact on the relative contribution of species to stable coexistence
+(Figure \ref{fig:fig-rho-sensitivity}a) and overall there was no change
+on our result that indicates that critical species (those with
+\(\phi = 1\)) have a larger than average contribution to stable
 coexistence (Figure \ref{fig:fig-rho-sensitivity}b).
@@
 a particular animal (G. Ballantyne et al., 2015; King et al., 2013;
-Ne'eman, Jürgens, Newstrom-Lloyd, Potts, \& Dafni, 2009). Second,
+Ne'eman, Jürgens, Newstrom-Lloyd, Potts, \& Dafni, 2010). Second,
 visitation networks were constructed by counting the visits to flowers
@@
 
-At a network scale the driver-node density \(n_D\) was consistent among
-the three weighting schemes (0.67 for deposition, 0.67 for the
-visitation, and 0.62 for the pollinator-importance network,
+At a network scale the size of the minimum driver node set \(n_D\) was
+consistent among the three weighting schemes (0.67 for deposition, 0.67
+for the visitation, and 0.62 for the pollinator-importance network,
 respectively). The choice of weighting can also have an impact on at the
 species level. Therefore we calculated \(\phi\) and \(\sigma\) and
-calculated it's correlation among all three weighting schemes. Although
+calculated its correlation among all three weighting schemes. Although
 visitation and efficiency (pollen deposition) produce moderately
@@
 
-To do so we removed a portion of the visits, for each network, and
+To do so, we removed a portion of the visits, for each network, and
 calculated how three control metrics of the subsampled network compare
@@
 approach is likely to still be useful in the absence of complete
-sampling. Specifically, as the proportion of sampled interaction
+sampling. Specifically, as the proportion of sampled interactions
 decreased, the variability of \(n_D\) increased but was overall similar
@@
 \caption{\label{tab:tab-controllability-model-results}Model selection table based on the Akaike Information Criterion for small samples for candidate models of size of the minimum driver node set ($n_D$) in the empirical networks.
-There was no evidence for any of the evaluated predictors: the invasion status (inv), the network connectance (c), the network nestedness (NODF) the number of species ($n_S$) the network asymmetry ($AS_s$) or the interaction strength asymmetry ($AS_s$).
+The evaluated variables are: the invasion status (inv), the network connectance ($C$), the network nestedness (NODF) the number of species ($n_S$) the network asymmetry ($AS_s$) or the interaction strength asymmetry ($AS_s$).
 Only candidate models with a weight $>0.01$ are shown.}
@@
 \caption{\label{fig:fig-correlogram}Mean Spearman correlation coefficients
-between control metrics (control capcity \(\phi\) and the likelyhood of
+between control metrics (control capcity \(\phi\) and the likelihood of
 being a superior node \(\sigma\)) and centrality metrics commonly used

### 2019-01-13 paper/supp-info.Rmd
caught a few minor typos in the supps

@@
 As such, we average the three metrics ($n_D$, $\phi$, and $\sigma$) across all the networks without reciprocal links without weighting by the number of possible control configurations. 
-It is important to note that a species that is found to be a superior node under a particular control configuration, will be so in all possible control configurations for the particular non-reciprocal network.
-We, therefore denote the average of $\sigma$ across all non-reciprocal versions as the probability of the species being a superior node in its community.
+It is important to note that a species that is found to be a superior node under a particular control configuration will be so in all possible control configurations for the particular non-reciprocal network.
+We therefore denote the average of $\sigma$ across all non-reciprocal versions as the probability of the species being a superior node in its community.
 
@@
                caption = "Model selection table based on the Akaike Information Criterion for small samples for candidate models of size of the minimum driver node set ($n_D$) in the empirical networks.
-The evaluated variables are: the invasion status (inv), the network connectance ($C$), the network nestedness (NODF) the number of species ($n_S$) the network asymmetry ($AS_s$) or the interaction strength asymmetry ($AS_s$).
+The evaluated variables are: the invasion status (inv), the network connectance ($C$), the network nestedness (NODF) the number of species ($n_S$) the network asymmetry ($AS_n$) or the interaction strength asymmetry ($AS_s$).
 Only candidate models with a weight $>0.01$ are shown.") %>%

### 2019-01-13 paper/manuscript.Rmd
Spell check msc
at least one typo and a few minor suggestions that relate to responses to reviewers

@@
 2. Here we introduce structural controllability, an approach that allows us to quantify the extent to which network topology can be harnessed to achieve a desired state. 
-\R{R2-define-control-capacity} It also allows us to quantify a species' control capacity—its relative importance—and identify the set of species that, collectively, are critical in this context because they have largest possible control capacity.
+\R{R2-define-control-capacity} It also allows us to quantify a species' control capacity—its relative importance—and identify the set of species that are critical in this context because they have largest possible collective control capacity.
 We illustrate the application of structural controllability with ten pairs of uninvaded and invaded plant-pollinator communities.
@@
   "control capacity" = "The relative frequency \\(\\phi\\) which with a species is part of the optimal control configurations of a network.", 
-  "critical species" = "A species with a maximal control capacity \\(\\phi=1\\)",
+  "critical species" = "A species with a maximal control capacity \\(\\phi=1\\).",
   "superior node" = "A species is a superior node if it can internally affect the abundance of other species in the network.
@@
 \R{R2-desired-control-trajectory} Finding out exactly how difficult it is to control a network depends strongly on the particularities of the desired control trajectory (i.e.
-path to the desired final state)  as well as the dynamical relationship between nodes.
+the path to the desired final state)  as well as the dynamical relationship between nodes.
 However, we are interested in understanding the controllability of a network in a more general sense, such that it can be applied even when the precise control scenario is known only incompletely. 
@@
 To facilitate comparison between predictors, degree and visitation strength were log-transformed and all four continuous variables were scaled to have a mean of zero and a standard deviation of one. 
-\R{R2-one-lumped-model-b}In these models, species from all networks were lumped together. 
+\R{R2-one-lumped-model-b}In these models, species from all networks were analysed together. 
 \R{R2-random-effects}We initially included random effects to account for possible variation across communities, but we found that the variance explained by these random effects was zero, and therefore random effects were not included in further analyses.
@@
 Invasive plants have been previously found to exacerbate the asymmetries in their communities [@aizen_invasive_2008; @bartomeus_contrasting_2008; @henriksson_strong_2016] \R{R2-central-in-their-communities}and to attain high centrality in their communities [@vila_invasive_2009; @palacio_generalist_2016].
-\R{R2-inherrently-different} We found that it is not that invasive plants have some different mechanism for influencing the community compared to their native counterparts [@emer_species_2016; @stouffer_how_2014].
+\R{R2-inherrently-different} We found, however, that it is not that invasive plants have some different mechanism for influencing the community compared to their native counterparts [@emer_species_2016; @stouffer_how_2014].
 Both native species and invasive plants tended to attain a high control capacity if they were important to network persistence, were abundant, and depended little on other species. 
@@
 Importantly, structural controllability can be used to identify critical species in the community that promote biodiversity and underpin the stable coexistence of species in their community.
-Collectively, critical species dominate the state of their community and therefore are likely to be highly relevant for ecosystem management and conservation. 
-While useful, centrality metrics, which have often been used as a proxy for keystoneness, fail to identify some of these species, highlighting their limitations when we fully embrace the notion that ecological communities are dynamical systems.
-@paine_note_1969 showed nearly 50 years ago that one single species can dominate the state of its community. 
+Collectively, critical species have the ability to strongly influence the state of their community and therefore are likely to be highly relevant for ecosystem management and conservation. 
+While useful, centrality metrics---which have often been used as a proxy for keystoneness---fail to identify some of these species, highlighting their limitations when we fully embrace the notion that ecological communities are dynamical systems.
+@paine_note_1969 showed nearly 50 years ago that a single species can sometimes fill this role on its own. 
 Structural controllability suggests that this situation might be the exception rather than the rule. 

### 2019-01-13 paper/reviewers-response.Rmd
dbs tweaks to the responses; outstanding points can be found by searching for DBS within reviewers-response.Rmd

--- 2019-01-13 paper/reviewers-response.Rmd
@@
 
+\renewcommand\thefigure{R\arabic{figure}}    
+\setcounter{figure}{0}
+
 \doublespacing
@@
 The reviewers identified a few remaining issues that should be straightforward to address.
-I also noticed a few issues"
+I also noticed a few issues:"
 
@@
 We have checked through the manuscript and corrected this where relevant.
-Besides *specie's role*, we also changed instances of *species' contribution*, *species' degree*, *species' control capacity*, among others.
+Besides *species' role*, we also changed instances of *species' contribution*, *species' degree*, *species' control capacity*, among others.
 
@@
 We now identify the distinction between high control capacity and being critical on \lr{M-R2-define-control-capacity}.
-The text now reads "It also allows us to quantify a species control capacity-its relative importance-and identify the set of species that, collectively, are critical in this context because they have largest possible control capacity".
+The text now reads "It also allows us to quantify a species' control capacity-its relative importance-and identify the set of species thatare critical in this context because they have largest possible collective control capacity".
 
@@
 
-*Accepted and changed*. Thank you for pointing out these mistakes, we corrected all of them.
+*Accepted and changed*. Thank you for pointing these out; we have corrected all of them.
 
@@
 
-We are pleased that the reviewer enjoyed the re-written manuscript. We did too!. We also grateful for the typos and style errors identified, we have striven to correct them all.
+We are pleased that the reviewer enjoyed the re-written manuscript. We did too!. We are also grateful for the typos and style errors they have identified and have striven to correct them all.
 
@@
 
+<!-- DBS: The sentence quoted below was NOT actually rewritten! All we did was remove an extra "other". -->
 *Accepted and changed*.
@@
 
-*Accepted and changed*. Thank you for pointing this out, made all these changes as indicated.
+*Accepted and changed*. Thank you again. We have made all these changes as indicated.
 
@@
 
+<!-- DBS: Don't you think they're asking for this to appear in the main text and not the supps? -->
 *Accepted and changed*.
@@
 We have modified the sentence mentioning 'the likelihood of being a superior node' in the first paragraph of the section \@ref(S-reciprocal-links) to "...and whether it is a superior node..." to avoid confusion.
-Then we define the 'probability of being a superior node' at the end of the section: "It is important to note that a species that is found to be a superior node under a particular control configuration, will be so in all possible control configurations for the particular non-reciprocal network.
-We, therefore denote the average of $\sigma$ across all non-reciprocal versions as the probability of the species being a superior node in its community".
+Then we define the 'probability of being a superior node' at the end of the section: "It is important to note that a species that is found to be a superior node under a particular control configuration will be so in all possible control configurations for the particular non-reciprocal network.
+We therefore denote the average of $\sigma$ across all non-reciprocal versions as the probability of the species being a superior node in its community".
 
@@
 *Need Daniel's input*
+<!-- DBS: Response sent to Fernando via slack. -->
 
@@
 
-*Accepted and changed*: We have attempted to clarify this sentence as follows: Finding out exactly how difficult it is to control a network depends strongly on the particularities of the desired control trajectory (i.e.
-the path to the desired final state)  as well as the dynamical relationship between nodes.
-\lr{M-R2-desired-control-trajectory}.
+*Accepted and changed*: We have attempted to clarify this sentence as follows: "Finding out exactly how difficult it is to control a network depends strongly on the particularities of the desired control trajectory (i.e.
+the path to the desired final state) as well as the dynamical relationship between nodes." (\lr{M-R2-desired-control-trajectory}).
 
@@
 To avoid confusion we have removed the word 'dynamic' and now the sentence reads "...our results suggest that structural controllability is closely related to the persistence..." (\lr{M-R2-dynamic-persistence}).
-It conserves its meaning without losing much precision.
+This preserves meaning without sacrificing precision.
 
@@
 
+<!-- DBS: This is the wrong sentence. You are quoting the sentence prior. -->
 *Accepted and changed*: We rephrased this line as follows: "We found that it is not that invasive plants have some different mechanism for influencing the community compared to their native counterparts" \lr{M-R2-inherrently-different}.
@@
 
+<!-- DBS: You are quoting the wrong section here... -->
 *Accepted and changed*: We have rephrased this line as: "By accounting for network dynamics (even if in a simple way), structural stability incorporates more ecological realism, especially in the extreme scenario in which the structure of interactions within the community only marginally affects the community's state.
@@
 *Need Daniel's input*
+<!-- DBS: See edits to manuscript.Rmd. -->
 
@@
 
-*Accepted and changed*: In the Methods section we deine species' strength as the sum of a species' visits (\lr{M-R2-species-strength-a}).
+*Accepted and changed*: In the Methods section, we define species' strength as the sum of a species' visits (\lr{M-R2-species-strength-a}).
 For brevity, we did not define it again in the Discussion, but now we have improved the text and briefly describe it when we mention it there too.
@@
 We have modified the text in \lr{M-R2-one-lumped-model-a} and \lr{M-R2-one-lumped-model-b} to make this clearer.
-We actually did test for random effects in the model.
+Moreover, we actually did test for random effects in the model.
 We tested random effects that allowed for a random intercept for the network (but also its site, and the study it comes from).
 In all cases, the variance among groups was zero.
-This means that likely there are no differences on the distribution of control capacity between networks (or site and study) and therefore it was not necessary to include random effects in the models presented in the paper.
+This means that likely there are no differences on the distribution of control capacity between networks (or site and study) and therefore it was unnecessary to include random effects in the models presented in the paper.
 We have corrected this omission and describe the random effects in \lr{M-R2-random-effects}.
+<!-- DBS: I don't think that "possible variation across communities" (which is the text in the paper) is specific enough to say what the random effects actually would have been. -->
 
@@
 *Accepted and changed*: We actually compared all possible candidate models. We have edited the manuscript on \lr{M-R2-all-candidates} to include this information.
+<!-- DBS: I think this needs a bit more explanation for reader that has never done this. As in "across the space of models with all, some, and none of the predictor variables." -->
 
 > "Reciprocal links were included in the directed graph when dij = dji. Would it have any effect if there was a little wiggle room there, e.g., when the two are close but not equal?"
+
+Rather than add yet another layer of complexity to our manuscript and given the rapid turnaround of the revised manuscript, we did not conduct this added sensitivity check.
+However, we note that only a very small fraction of interactions had a small asymmetry (see Figure R1).
+We therefore don't expect our results to change considerably even when we include reciprocal links when the asymmetry is small but not zero.
+<!-- DBS: Why don't we say something to this effect in the main text to throw them a bit of a bone? -->
+
+```{r fig-asymmetry, fig.width=6.3, fig.height=2, fig.cap = "Histogram of the interaction asymmetries between species.
+Previous research has shown that mutualistic interactions are often highly asymmetric in natural communities.
+Indeed, only 16.5% of interactions have asymmetries smaller or equal than 0.5; 1% are smaller than 0.1."}
+drake::readd(fig_asymmetry_distribution)
+```

### 2019-01-14 paper/reviewers-response.Rmd
Remove collective from the abstract

@@
 We now identify the distinction between high control capacity and being critical on \lr{M-R2-define-control-capacity}.
-The text now reads "It also allows us to quantify a species' control capacity-its relative importance-and identify the set of species thatare critical in this context because they have largest possible collective control capacity".
+The text now reads "It also allows us to quantify a species' control capacity-its relative importance-and identify the set of species that are critical in this context because they have the largest possible control capacity".
 

### 2019-01-14 paper/manuscript.Rmd
Remove collective from the abstract

@@
 2. Here we introduce structural controllability, an approach that allows us to quantify the extent to which network topology can be harnessed to achieve a desired state. 
-\R{R2-define-control-capacity} It also allows us to quantify a species' control capacity—its relative importance—and identify the set of species that are critical in this context because they have largest possible collective control capacity.
+\R{R2-define-control-capacity} It also allows us to quantify a species' control capacity—its relative importance—and identify the set of species that are critical in this context because they have the largest possible control capacity.
 We illustrate the application of structural controllability with ten pairs of uninvaded and invaded plant-pollinator communities.

### 2019-01-14 paper/reviewers-response.Rmd
Respond to question about using N as a predictor of D/N

@@
 
-*Need Daniel's input*
+Thanks for the observation.
+As you mention, we believe it is ok to include the sample size as a predictor in this model for three reasons.
+First, there are several instances when the probability of something occurring increases or decreases with sampling effort, etc.
+It *does* imply a non-linear relationship though.
+Second, if there were a relationship between N on D, then using D/N (as opposed to of D) as the response variable and N as a predictor would actually reduce the size of the effect of N, rather than amplify it.
+If on the other hand, N and D are completely decoupled, then using D/N as the response variable should affect the intercept but not the coefficient of D.
+Third, in any case we only found a comparatively small effect of N on D.
+Although it might be relevant statistically it seems to be ecologically insignificant.
+<!-- FDO: Daniel, could you please double check this makes sense? -->
 

### 2019-01-14 paper/manuscript.Rmd
Respond to question about using N as a predictor of D/N
Improve explanation about random effects in controllability models

@@
 After finding the minimum driver-node set in each of our networks, we wanted to test whether invasion status or other predictors are correlated to controllability. 
-We do this using a set of generalised linear models with binomial error structure. 
+We do this using a set of generalised linear models with Gaussian errors and a logit link function. 
 The response variable was the relative size of the minimum driver-node set $n_D$ of the twenty empirical networks (ten invaded and ten uninvaded), and we included invasion status as a predictor. 
@@
 \R{R2-one-lumped-model-b}In these models, species from all networks were analysed together. 
-\R{R2-random-effects}We initially included random effects to account for possible variation across communities, but we found that the variance explained by these random effects was zero, and therefore random effects were not included in further analyses.
+\R{R2-random-effects}We initially included random effects to account for possible variation across communities, but we found that the among-group variance was effectively zero, and therefore random effects were not included in further analyses.
 \R{R2-all-candidates}We then generated all possible candidate models.

### 2019-01-14 paper/reviewers-response.Rmd
Improve explanation about random effects in controllability models
Improve explanation about candidates in species models

@@
 <!-- DBS: I don't think that "possible variation across communities" (which is the text in the paper) is specific enough to say what the random effects actually would have been. -->
+<!-- FDO: I have reworded to 'We initially included random effects to account for possible variation across communities, but we found that the among-group variance was effectively zero, and therefore random effects were not included in further analyses'.
+Is that what you mean?
+-->
 
@@
 *Accepted and changed*: We actually compared all possible candidate models. We have edited the manuscript on \lr{M-R2-all-candidates} to include this information.
-<!-- DBS: I think this needs a bit more explanation for reader that has never done this. As in "across the space of models with all, some, and none of the predictor variables." -->
 

### 2019-01-14 paper/reviewers-response.Rmd
Correcting quoting mistakes in the response to reviewers

@@
 
-<!-- DBS: This is the wrong sentence. You are quoting the sentence prior. -->
-*Accepted and changed*: We rephrased this line as follows: "We found that it is not that invasive plants have some different mechanism for influencing the community compared to their native counterparts" \lr{M-R2-inherrently-different}.
+*Accepted and changed*: We rephrased this sentences as follows: "We found that it is not that invasive plants have some different mechanism for influencing the community compared to their native counterparts.
+Both native species and invasive plants tended to attain a high control capacity if they were important to network persistence, were abundant, and depended little on other species" \lr{M-R2-inherrently-different}.
 
@@
 
-<!-- DBS: You are quoting the wrong section here... -->
-*Accepted and changed*: We have rephrased this line as: "By accounting for network dynamics (even if in a simple way), structural stability incorporates more ecological realism, especially in the extreme scenario in which the structure of interactions within the community only marginally affects the community's state.
-Both native species and invasive plants tended to attain a high control capacity if they were important to network persistence, were abundant, and depended little on other species" (\lr{M-R2-marginally-affected}).
+*Accepted and changed*: We have rephrased this line as: "By accounting for network dynamics (even if in a simple way), structural stability incorporates more ecological realism, especially in the extreme scenario in which the structure of interactions within the community only marginally affects the community's state" (\lr{M-R2-marginally-affected}).
 

### 2019-01-14 paper/manuscript.Rmd
Improve explanation about candidates in species models
Correcting quoting mistakes in the response to reviewers

@@
 \R{R2-random-effects}We initially included random effects to account for possible variation across communities, but we found that the among-group variance was effectively zero, and therefore random effects were not included in further analyses.
-\R{R2-all-candidates}We then generated all possible candidate models.
+\R{R2-all-candidates}We then generated all possible candidate models across the space of models with all, some, and none of the predictor variables.
 To identify the models that were best supported by the data, we first determined the most parsimonious random structure using the AICc. 
@@
 Invasive plants have been previously found to exacerbate the asymmetries in their communities [@aizen_invasive_2008; @bartomeus_contrasting_2008; @henriksson_strong_2016] \R{R2-central-in-their-communities}and to attain high centrality in their communities [@vila_invasive_2009; @palacio_generalist_2016].
-\R{R2-inherrently-different} We found, however, that it is not that invasive plants have some different mechanism for influencing the community compared to their native counterparts [@emer_species_2016; @stouffer_how_2014].
+We found, however, that it is not that invasive plants have some \R{R2-inherrently-different} different mechanism for influencing the community compared to their native counterparts [@emer_species_2016; @stouffer_how_2014].
 Both native species and invasive plants tended to attain a high control capacity if they were important to network persistence, were abundant, and depended little on other species. 

### 2019-01-14 paper/reviewers-response.Rmd
Improve clarity of sentence with two others about the effect of species
on each other

@@
 
-<!-- DBS: The sentence quoted below was NOT actually rewritten! All we did was remove an extra "other". -->
 *Accepted and changed*.
@@
 As suggested, we have rewritten the sentence to improve clarity (\lr{M-R2-structural-controllability}).
-It now reads as follows: "First, structural controllability emphasizes that the effect a species has on the abundance of other species is not independent of the effects of those other species in their community".
+It now reads as follows: "First, structural controllability emphasizes that the effect a species has on other species is not independent of the effects that the other species have in the community".
 

### 2019-01-14 paper/manuscript.Rmd
Improve clarity of sentence with two others about the effect of species
on each other

@@
 Other conceptual differences between structural controllability and centrality metrics provide three key insights into the conservation of ecological networks. 
-\R{R2-structural-controllability} First, structural controllability emphasizes that the effect a species has on the abundance of other species is not independent of the effects of those other species in their community.
+\R{R2-structural-controllability} First, structural controllability emphasizes that the effect a species has on other species is not independent of the effects that the other species have in the community.
 The rankings provided by centrality metrics and other heuristics fail to account for the collective influence of several species at once. 

### 2019-01-14 paper/reviewers-response.Rmd
Add sentence about limitations of controllability

@@
 
-*Need Daniel's input*
-<!-- DBS: Response sent to Fernando via slack. -->
+*Partially accepted and changed*: We think that more studies are needed before we can accurately build an intuition of what constitutes a species with a high control capacity, especially in regards to other kinds of networks.
+As such we have added a clarification in \lr{M-R2-clarification-limitations} that states "As much potential as any metric or metrics to summarise species' importance might appear to have, it's clear that we also need more empirical studies in different types of networks in order to build intuition and ground truth their usefulness".
+We also considered the suggestion about including a specific example, but we ultimately concluded that none would be particularly didactic for a reader unfamiliar with the exact empirical context.
 

### 2019-01-14 paper/reviewers-response.Rmd
Remove 'dominate' from conclusion as we dont have a nice definition

@@
 
-*Need Daniel's input*
-<!-- DBS: See edits to manuscript.Rmd. -->
+*Accepted and changed*: Because we don't have a proper definition, we have modified the conclusion paragraph and now the affected sentences read: "Collectively, critical species have the ability to strongly influence the state of their community and therefore are likely to be highly relevant for ecosystem management and conservation.
+While useful, centrality metrics---which have often been used as a proxy for keystoneness---fail to identify some of these species, highlighting their limitations when we fully embrace the notion that ecological communities are dynamical systems.
+Paine (1969) showed nearly 50 years ago that a single species can sometimes fill this role on its own" (\lr{M-R2-dominate}).
 

### 2019-01-14 paper/manuscript.Rmd
Add sentence about limitations of controllability
Remove 'dominate' from conclusion as we dont have a nice definition

@@
 Stepping back, our results also provide support to the idea that management decisions should not be based on a single technique but indicate that focusing on ecosystem processes and interactions may be more effective than traditional ranking-based approaches [@harvey_bridging_2017].
+\R{R2-clarification-limitations}As much potential as any metric or metrics to summarise species' importance might appear to have, it's clear that we also need more empirical studies in different types of networks in order to build intuition and ground truth their usefulness.
 
@@
 Importantly, structural controllability can be used to identify critical species in the community that promote biodiversity and underpin the stable coexistence of species in their community.
-Collectively, critical species have the ability to strongly influence the state of their community and therefore are likely to be highly relevant for ecosystem management and conservation. 
+\R{R2-dominate}Collectively, critical species have the ability to strongly influence the state of their community and therefore are likely to be highly relevant for ecosystem management and conservation.
 While useful, centrality metrics---which have often been used as a proxy for keystoneness---fail to identify some of these species, highlighting their limitations when we fully embrace the notion that ecological communities are dynamical systems.

### 2019-01-14 paper/reviewers-response.Rmd
Typos and commas in the response to reviewers

@@
 <!-- DBS: Don't you think they're asking for this to appear in the main text and not the supps? -->
+<!-- FDO: The 'probability/likelihood of being a superior node' is not mentioned in the main text, not even once.
+It only briefly gets mentioned in the Results and the Discussion and that is more in the conceptual way of what it means to be superior node.
+Not on how we devise this 'likelihood' when we have multiple non-reciprocal instances of a network.
+Plus in the paper, we don't really get much ecological insight from it.
+Because it's only mentioned in the supp.
+info I added this there and I think that'll be fine.
+We can always change it if they come back to it -->
 *Accepted and changed*.
@@
 Then we define the 'probability of being a superior node' at the end of the section: "It is important to note that a species that is found to be a superior node under a particular control configuration will be so in all possible control configurations for the particular non-reciprocal network.
-We therefore denote the average of $\sigma$ across all non-reciprocal versions as the probability of the species being a superior node in its community".
+We, therefore, denote the average of $\sigma$ across all non-reciprocal versions as the probability of the species being a superior node in its community".
 
@@
 
-*Accepted and changed*: Contrastingly, in this case the word dynamic distinguishes a particular facet of stability.
+*Accepted and changed*: Contrastingly, in this case, the word dynamic distinguishes a particular facet of stability.
 We mean the ability of the system to return to an equilibrium state after a perturbation.
@@
 However, we note that only a very small fraction of interactions had a small asymmetry (see Figure R1).
-We therefore don't expect our results to change considerably even when we include reciprocal links when the asymmetry is small but not zero.
+We, therefore, don't expect our results to change considerably even when we include reciprocal links when the asymmetry is small but not zero.
 <!-- DBS: Why don't we say something to this effect in the main text to throw them a bit of a bone? -->
+<!-- FDO: Humm. I cannot find a good place to put this in the main text without having to write a half/full paragraph about it... -->
 

### 2019-01-14 paper/supp-info.Rmd
Typos and commas in the response to reviewers

@@
 It is important to note that a species that is found to be a superior node under a particular control configuration will be so in all possible control configurations for the particular non-reciprocal network.
-We therefore denote the average of $\sigma$ across all non-reciprocal versions as the probability of the species being a superior node in its community.
+We, therefore, denote the average of $\sigma$ across all non-reciprocal versions as the probability of the species being a superior node in its community.
 

### 2019-01-14 paper/reviewers-response.Rmd
answers to FDO comments and questions

@@
 We can always change it if they come back to it -->
+<!-- DBS: Agreed. -->
 *Accepted and changed*.
@@
 As you mention, we believe it is ok to include the sample size as a predictor in this model for three reasons.
-First, there are several instances when the probability of something occurring increases or decreases with sampling effort, etc.
-It *does* imply a non-linear relationship though.
-Second, if there were a relationship between N on D, then using D/N (as opposed to of D) as the response variable and N as a predictor would actually reduce the size of the effect of N, rather than amplify it.
-If on the other hand, N and D are completely decoupled, then using D/N as the response variable should affect the intercept but not the coefficient of D.
-Third, in any case we only found a comparatively small effect of N on D.
-Although it might be relevant statistically it seems to be ecologically insignificant.
+First, there are several instances when the probability of something occurring increases or decreases with sampling size, sampling effort, etc.
+A common ecological example would be a saturating predator functional response.
+Though this implies an underlying *non-linear* relationship, it does not invalidate the approach.
+Second, if there were a relationship between N and D, using D/N as the response variable (as opposed to D) and N as a predictor should actually reduce the size of the inferred effect of N, rather than amplify it.
+On the other hand, if N and D are completely decoupled, then using D/N as the response variable should affect the intercept but not the coefficient of D.
+Third, in our manuscript we found a comparatively small effect of N on D.
+Although it might be relevant statistically, it seems to be ecologically insignificant.
 <!-- FDO: Daniel, could you please double check this makes sense? -->
+<!-- DBS: The only thing that I don't understand is that part "but not the coefficient of D". In your scenario, D is the response so it shouldn't have any coefficient. Should this say N? -->
 
@@
 -->
+<!-- DBS: What I mean is what you said here in the response but not the text: what is meant by groups in the random effect model.
+So when you say possible variation across communities you should make explicit that this was done in some number of different ways, one with a random effect for network, one with a random effect for site, etc.
+We never specify the EXACT random effect structure (and I can only partially decipher it from the paragraph here), so "variation across communities" can be interpreted in a large number of ways.-->
 
@@
 <!-- FDO: Humm. I cannot find a good place to put this in the main text without having to write a half/full paragraph about it... -->
+<!-- DBS: Why not somewhere in line 172 (in the Rmd file)? You could replace "Sometimes" with "For X% of the observed species pairs, there is no asymmetry..." -->
 

### 2019-01-16 paper/reviewers-response.Rmd
Write proportion of bidirectional links in main text

@@
 We, therefore, don't expect our results to change considerably even when we include reciprocal links when the asymmetry is small but not zero.
-<!-- DBS: Why don't we say something to this effect in the main text to throw them a bit of a bone? -->
-<!-- FDO: Humm. I cannot find a good place to put this in the main text without having to write a half/full paragraph about it... -->
-<!-- DBS: Why not somewhere in line 172 (in the Rmd file)? You could replace "Sometimes" with "For X% of the observed species pairs, there is no asymmetry..." -->
+We have also included the actual proportion of interactions with no asymmetry in the main text to improve clarity (\lr{M-R2-reciprocal}).
 

### 2019-01-16 paper/manuscript.Rmd
Write proportion of bidirectional links in main text

@@
 We therefore create a directed link from species *i* to species *j* when $d_{ij}-d_{ji} \geq 0$ to establish the most likely direction of control between a species pair (Figure \@ref(fig:fig-example-networks)a).
-Sometimes there is no observed asymmetry between species pairs ($d_{ij}=d_{ji}$), and we cannot infer a dominant direction of control. 
+\R{R2-reciprocal}Sometimes (`r round(drake::readd(proportion_bilinks), digits = 1)`% of the observed interactions in our datasets) there is no observed asymmetry between species pairs ($d_{ij}=d_{ji}$), and we cannot infer a dominant direction of control.
 When this occurs, we deem both species to be equally likely to affect each other and leave a reciprocal interaction between them (a link from *i* to *j* and another from *j* to *i*). 
@@
   dplyr::select(-logLik, - AICc) %>%
-  set_names(., pretty_term_names(colnames(.), "short")) %>%
+  {set_names(., pretty_term_names(colnames(.), "short"))} %>%
   knitr::kable("latex", 

### 2019-01-16 code/bipartite_to_directed.R

@@ -89,3 +89,16 @@ replace_zeros <- function(x,y = 0){
   x
 }
 
+# get proportion of interactions with no asymmetry
+get_prop_bilinks <- function(networks, directed_networks){
+  n_bilinks <- directed_networks %>%
+    purrr::map(split_bilinks) %>%
+    purrr::map(length) %>%
+    purrr::map_dbl(log, base = 2) 
+  
+  n_links <- networks %>%
+    purrr::map(igraph::E) %>%
+    purrr::map_dbl(length)
+  
+  (sum(n_bilinks) / sum(n_links)) * 100
+}

### 2019-01-16 main.R

@@ -43,6 +43,7 @@ basic_analysis_plan <- drake::drake_plan(
     "ISA", 
     "weighted NODF")), 
   directed_networks = purrr::map(networks, as_directed_network, direction = "asymmetry", ties = "both", higher_level = "pol"),
+  proportion_bilinks = get_prop_bilinks(networks, directed_networks),
   strings_in_dots = "literals"
 )
 

### 2019-01-16 paper/reviewers-response.Rmd
Improve clarification of random effects in main text

@@
 We have corrected this omission and describe the random effects in \lr{M-R2-random-effects}.
-<!-- DBS: I don't think that "possible variation across communities" (which is the text in the paper) is specific enough to say what the random effects actually would have been. -->
-<!-- FDO: I have reworded to 'We initially included random effects to account for possible variation across communities, but we found that the among-group variance was effectively zero, and therefore random effects were not included in further analyses'.
-Is that what you mean?
--->
-<!-- DBS: What I mean is what you said here in the response but not the text: what is meant by groups in the random effect model.
-So when you say possible variation across communities you should make explicit that this was done in some number of different ways, one with a random effect for network, one with a random effect for site, etc.
-We never specify the EXACT random effect structure (and I can only partially decipher it from the paragraph here), so "variation across communities" can be interpreted in a large number of ways.-->
 

### 2019-01-16 paper/manuscript.Rmd
Improve clarification of random effects in main text

@@
 \R{R2-one-lumped-model-b}In these models, species from all networks were analysed together. 
-\R{R2-random-effects}We initially included random effects to account for possible variation across communities, but we found that the among-group variance was effectively zero, and therefore random effects were not included in further analyses.
+\R{R2-random-effects}We initially included random effects to account for possible variation across communities. 
+Specifically, we tested structures that allowed for a random intercept for the network, site, and the study it comes from.
+However, we found that in all cases the among-group variance was effectively zero, and therefore we did not include any random effect in further analyses. 
 \R{R2-all-candidates}We then generated all possible candidate models across the space of models with all, some, and none of the predictor variables.

### 2019-01-16 paper/reviewers-response.Rmd
Typo in response to reviewers

@@
 
-<!-- DBS: Don't you think they're asking for this to appear in the main text and not the supps? -->
-<!-- FDO: The 'probability/likelihood of being a superior node' is not mentioned in the main text, not even once.
-It only briefly gets mentioned in the Results and the Discussion and that is more in the conceptual way of what it means to be superior node.
-Not on how we devise this 'likelihood' when we have multiple non-reciprocal instances of a network.
-Plus in the paper, we don't really get much ecological insight from it.
-Because it's only mentioned in the supp.
-info I added this there and I think that'll be fine.
-We can always change it if they come back to it -->
-<!-- DBS: Agreed. -->
 *Accepted and changed*.
@@
 Second, if there were a relationship between N and D, using D/N as the response variable (as opposed to D) and N as a predictor should actually reduce the size of the inferred effect of N, rather than amplify it.
-On the other hand, if N and D are completely decoupled, then using D/N as the response variable should affect the intercept but not the coefficient of D.
+On the other hand, if N and D are completely decoupled, then using D/N as the response variable should affect the intercept but not the coefficient of N.
 Third, in our manuscript we found a comparatively small effect of N on D.
 Although it might be relevant statistically, it seems to be ecologically insignificant.
-<!-- FDO: Daniel, could you please double check this makes sense? -->
-<!-- DBS: The only thing that I don't understand is that part "but not the coefficient of D". In your scenario, D is the response so it shouldn't have any coefficient. Should this say N? -->
 

### 2019-01-17 paper/reviewers-response.Rmd
Minor change to sentence referring to last round of review
In reviewers response
Update manuscript number

@@
 title: "Keystoneness, centrality, and the structural controllability of ecological networks"
-subtitle: "JEcol-2018-0545 - Detailed response to comments"
+subtitle: "JEcol-2018-0545.R1 - Detailed response to comments"
 author: "Fernando Cagua, Kate L. Wootton, Daniel B. Stouffer"
@@
 We are thankful to the assistant editor James Ross, the senior editor and David Gibson, and three anonymous reviewers for the insightful comments to improve the manuscript. 
-In the following sections, you can find a detailed response to each comment raised during the previous round of review.
+In the following sections, you can find a detailed response to each comment raised in this round of review.
 

### 2019-02-18 paper/manuscript.Rmd
Remove "keystone species" from keywords
Only 8 keywords are allowed. Removed because it already appears a couple of times in the abstract

@@
 
-**Keywords:** Invasive species, keystone species, management interventions, mutualism, network control theory, plant population and community dynamics, species' importance, control capacity, structural stability
+**Keywords:** Invasive species, management interventions, mutualism, network control theory, plant population and community dynamics, species' importance, control capacity, structural stability
 

### 2019-02-18 paper/manuscript.Rmd
*Impatiens grandulifera* was misspelled as *Impatients grandulifera*

@@
 Four pairs correspond to natural or semi-natural vegetation communities in the city of Bristol, UK [@lopezaraizamikel_impact_2007]. 
-These communities comprised `r lop[1]`--`r lop[6]` species (mean `r round(lop[4])`), and non-invaded plots were obtained by experimentally removing all the flowers of the invasive species *Impatients grandulifera*.
+These communities comprised `r lop[1]`--`r lop[6]` species (mean `r round(lop[4])`), and non-invaded plots were obtained by experimentally removing all the flowers of the invasive species *Impatiens grandulifera*.
 The other six pairs were obtained from lower diversity Mediterranean shrublands in Cap de Creus National Park, Spain [@bartomeus_contrasting_2008].

### 2019-02-18 paper/manuscript.Rmd
Improve readability of sentence as highlighted by proofreader

@@
 Finally, we found that critical species have a particularly large impact on species coexistence when compared to non-critical species.
-Indeed, the structural stability of the networks where critical species were removed was considerably lower to those in were non-critical species were removed ($p = `r sprintf('\\num{%s}', format(crit_test$p.value, digits = 2))`$; Figure \@ref(fig:fig-structural-stability); Supporting Information \@ref(S-structural-stability)).
+Indeed, the structural stability of the networks where critical species were removed was considerably lower than those where non-critical species were removed ($p = `r sprintf('\\num{%s}', format(crit_test$p.value, digits = 2))`$; Figure \@ref(fig:fig-structural-stability); Supporting Information \@ref(S-structural-stability)).
 

### 2019-02-18 paper/manuscript.Rmd
Add New Zealand to full name of Royal Society Te Apārangi

@@
 EFC acknowledges the support from the University of Canterbury Doctoral Scholarship, the University of Canterbury Meadow Mushrooms Postgraduate Scholarship, a New Zealand International Doctoral Research Scholarship, and a travel grant from the European Space Agency.
-DBS acknowledges the support of a Marsden Fast-Start grant and a Rutherford Discovery Fellowship, administered by the Royal Society Te Aparangi.
+DBS acknowledges the support of a Marsden Fast-Start grant and a Rutherford Discovery Fellowship, administered by the Royal Society of New Zealand Te Aparangi.
 

### 2019-02-18 paper/manuscript.Rmd
Fix corresponding author in manuscript

@@
 
-**Author for correspondence:** Daniel B.
-Stouffer (daniel.stouffer@canterbury.ac.nz) - +64 3 364 2729 - Centre for Integrative Ecology, School of Biological Sciences, University of Canterbury, Private Bag 4800, Christchurch 8140, New Zealand
+**Author for correspondence:** E.
+Fernando Cagua (efc29@uclive.av.nz) - +64 3 364 2729 - Centre for Integrative Ecology, School of Biological Sciences, University of Canterbury, Private Bag 4800, Christchurch 8140, New Zealand
 

### 2019-02-19 paper/manuscript.Rmd
Capitalising Headings in Figures, Glossary and Table columns in MSC

@@
 defs <- list(
-  "network control" = "A network is said to be controllable if it is possible to steer it from an initial to an arbitrary final state within finite time.",
-  "controllability" = "The intrinsic difficulty of controlling an ecological community.
+  "Network control" = "A network is said to be controllable if it is possible to steer it from an initial to an arbitrary final state within finite time.",
+  "Controllability" = "The intrinsic difficulty of controlling an ecological community.
 It is measured by the relative size of the minimum driver-node set, $n_D$.
 It also indicates the extent to which network structure can be harnessed for network control.",
-  "minimum driver-node set" = "One of the sets of species whose abundances need to be directly managed in order to achieve full control of the community.
+  "Minimum driver-node set" = "One of the sets of species whose abundances need to be directly managed in order to achieve full control of the community.
 The minimum driver-node sets can be obtained by finding all maximum matchings in a network.",
-  "maximum matching" = "A matching is a set of links that do not share any common start or end nodes; the largest possible matching is called a maximum matching.",
-  "control configuration" = "One of the species combinations with which is possible to achieve network control. Optimal control configurations are given by the minimum driver-node sets.", 
-  "control capacity" = "The relative frequency \\(\\phi\\) which with a species is part of the optimal control configurations of a network.", 
-  "critical species" = "A species with a maximal control capacity \\(\\phi=1\\).",
-  "superior node" = "A species is a superior node if it can internally affect the abundance of other species in the network.
+  "Maximum matching" = "A matching is a set of links that do not share any common start or end nodes; the largest possible matching is called a maximum matching.",
+  "Control configuration" = "One of the species combinations with which is possible to achieve network control. Optimal control configurations are given by the minimum driver-node sets.", 
+  "Control capacity" = "The relative frequency \\(\\phi\\) which with a species is part of the optimal control configurations of a network.", 
+  "Critical species" = "A species with a maximal control capacity \\(\\phi=1\\).",
+  "Superior node" = "A species is a superior node if it can internally affect the abundance of other species in the network.
 Superior nodes make up the chains that propagate the control signals through the network.")
@@
   dplyr::select(-logLik, - AICc) %>%
+  dplyr::rename(Weight = weight) %>%
   {set_names(., pretty_term_names(colnames(.), "short"))} %>%
@@
                escape = F) %>%
-  kableExtra::add_header_above(c("model terms" = 10, " " = 3), escape = F) %>%
+  kableExtra::add_header_above(c("Model terms" = 10, " " = 3), escape = F) %>%
   kableExtra::kable_styling(font_size = 8) %>%
-  kableExtra::footnote(general = "intercept (int), degree ($k$), trophic level ($l$), asymmetry ($a$), contribution to nestedness ($n$), visitation strength ($s$).", 
-                       general_title = "Terms: ", 
+  kableExtra::footnote(general = "Terms: intercept (int), degree ($k$), trophic level ($l$), asymmetry ($a$), contribution to nestedness ($n$), visitation strength ($s$).", 
+                       general_title = "Note. ", 
                        footnote_as_chunk = TRUE, 

### 2019-02-19 code/fig_emp_controllability.R

@@ -15,14 +15,14 @@ make_fig_emp_contollability <- function(controllability, randomisations_df, meta
     geom_vline(data = medians_d, aes(xintercept = n_D, colour = inv),  linetype = 2, size = 0.25, show.legend = FALSE) +
     scale_color_manual(values = c(my_pallete()$light_grey, my_pallete()$dark_grey), 
                        name = "", 
-                       guide = guide_legend(reverse = F), labels = c("invaded", "uninvaded")) +
+                       guide = guide_legend(reverse = F), labels = c("Invaded", "Uninvaded")) +
     xlab(expression(paste(n[D]))) +
     base_ggplot_theme() +
     theme(legend.position = c(1, 1.15),
           legend.justification = c(1,1),
           legend.background = element_rect(fill = "NA"), legend.key.size = unit(0.15, "in")) +
     labs(title = "(a)", 
-         y = "probability density")
+         y = "Probability density")
   
   r <- randomisations_df %>%
     filter_networks_df(metadata) %>%
@@ -54,7 +54,7 @@ make_fig_emp_contollability <- function(controllability, randomisations_df, meta
                 size = 0.5) +
     scale_y_continuous(labels = function(x) round(plogis(x), 2)) +
     labs(title = latex2exp::TeX("(b)"), 
-         x = "network asymmetry", 
+         x = "Network asymmetry", 
          y = latex2exp::TeX("$n_D$")) +
     base_ggplot_theme()
 
@@ -64,14 +64,14 @@ make_fig_emp_contollability <- function(controllability, randomisations_df, meta
     geom_vline(data = means, aes(xintercept = delta_n_D, color = randomisation), size = 0.25, linetype = 2, show.legend = F) +
     scale_color_manual(values = c(my_pallete()$dark_grey,  my_pallete()$light_grey), 
                        name = "", 
-                       guide = guide_legend(reverse = T), labels = c("directions", "interactions")) +
+                       guide = guide_legend(reverse = T), labels = c("Directions", "Interactions")) +
     base_ggplot_theme() +
     theme(legend.position = c(1,1.15), 
           legend.justification = c(1,1),
           legend.background = element_rect(fill = "NA"), legend.key.size = unit(0.15, "in")) +
     labs(title = "(c)", 
          x = expression(paste(Delta, n[D])), 
-         y = "probability density")
+         y = "Probability density")
          
  list(p1, p3, p2)
 }

### 2019-02-19 code/fig_example_direction.R

@@ -82,7 +82,7 @@ make_fig_control_configurations <- function(en_chain, en_star, en_direction, pdf
   par(mar = rep(0,4), bg = "white", xpd = NA)
   
   # 31
-  standalone_text("directed network", y = 0.5, adj = c(0.5,0), font = 2)  
+  standalone_text("Directed network", y = 0.5, adj = c(0.5,0), font = 2)  
   rect(grconvertX(0, "inches", "user"),
        grconvertY(sum(heights) - heading_height - plot_1_height - desc_height, "inches", "user"),
        grconvertX(3.5, "inches", "user"),
@@ -130,7 +130,7 @@ make_fig_control_configurations <- function(en_chain, en_star, en_direction, pdf
        border = NA)
 
   # 32
-  standalone_text("maximum matchings / control configurations", y = 0.5, adj = c(0.5,0), font = 2)
+  standalone_text("Maximum matchings / Control configurations", y = 0.5, adj = c(0.5,0), font = 2)
   # 33
   # standalone_vline(lty = 2)
   # plot.new()
@@ -176,15 +176,15 @@ make_fig_control_configurations <- function(en_chain, en_star, en_direction, pdf
   y_desc <- 0.7
   standalone_text("N = 4", y = y_desc)
   
-  standalone_text(latex2exp::TeX("$matching\\,size = 3 \\;\\;\\; D = 1 \\;\\;\\; n_D = 0.25$"), y = y_desc)
+  standalone_text(latex2exp::TeX("$Matching\\,size = 3 \\;\\;\\; D = 1 \\;\\;\\; n_D = 0.25$"), y = y_desc)
   
   standalone_text("N = 4", y = y_desc)
   
-  standalone_text(latex2exp::TeX("$matching\\,size = 1 \\;\\;\\; D = 3 \\;\\;\\; n_D = 0.75$"), y = y_desc)
+  standalone_text(latex2exp::TeX("$Matching\\,size = 1 \\;\\;\\; D = 3 \\;\\;\\; n_D = 0.75$"), y = y_desc)
   
   standalone_text("N = 5", y = y_desc)
   
-  standalone_text(latex2exp::TeX("$matching\\,size = 3 \\;\\;\\; D = 2 \\;\\;\\; n_D = 0.40$"), y = y_desc)
+  standalone_text(latex2exp::TeX("$Matching\\,size = 3 \\;\\;\\; D = 2 \\;\\;\\; n_D = 0.40$"), y = y_desc)
   
   # plot.new()
   plot.new()
[…]

### 2019-02-19 code/fig_example_structural_control.R

@@ -95,11 +95,11 @@ make_fig_structural_control <- function(en_direction, en_structural, pdf_out = N
   # plot.new()
   ## FIGURE A
   # 10
-  standalone_text("visitation network", y = 0.25, adj = c(0.5,0), font = 2)
+  standalone_text("Visitation network", y = 0.25, adj = c(0.5,0), font = 2)
   text(0, 1, "(a)", adj = c(0.15,1.5), font = 1)
   
   # 11
-  standalone_text("direction of control", y = 0.25, adj = c(0.5,0), font = 2)
+  standalone_text("Direction of control", y = 0.25, adj = c(0.5,0), font = 2)
   
   # 12
   # standalone_vline(lty = 2)
@@ -111,14 +111,14 @@ make_fig_structural_control <- function(en_direction, en_structural, pdf_out = N
   }
   ## FIGURE B
   # 20
-  standalone_text("dilation", y = 0.5, adj = c(0.5,1), font = 1)
+  standalone_text("Dilation", y = 0.5, adj = c(0.5,1), font = 1)
   text(0, 1, "(b)", adj = c(0.15,1.5), font = 1)
   # 21
-  standalone_text("inaccessible node", y = 0.5, adj = c(0.5,1), font = 1)
+  standalone_text("Inaccessible node", y = 0.5, adj = c(0.5,1), font = 1)
   # 22
-  standalone_text("not\ncontrollable", srt = 90, font = 2)
+  standalone_text("Not\ncontrollable", srt = 90, font = 2)
   # 23
-  standalone_text("controllable", srt = 90, font = 2)
+  standalone_text("Controllable", srt = 90, font = 2)
   # 24-27
   for (i in c(4,2,5,3)){
     # if(i == 3)   text(-2.26, 1, "(b)", adj = c(0,1.3), font = 1)
@@ -141,7 +141,7 @@ make_fig_structural_control <- function(en_direction, en_structural, pdf_out = N
   # 83
   # standalone_hline(lty = 2)
   plot.new()
-  legend(0.5, 0.5,legend = c("control input"), horiz = TRUE,
+  legend(0.5, 0.5,legend = c("Control input"), horiz = TRUE,
          lty = 1, 
          col = get_color("control"),
          lwd = 1.5, cex = 0.9, xjust=0.5, yjust=0.5, bty = "n")

### 2019-02-19 code/fig_keystonness.R

@@ -162,8 +162,8 @@ make_fig_control_capacity <- function(sl_characteristics){
     scale_color_manual(values = my_pallete()$dark_orange) +
     base_ggplot_theme() +
     labs(title = "(a) Control capacity of plants", 
-         x = latex2exp::TeX("control capacity ($\\phi$)"), 
-         y = "probability density") +
+         x = latex2exp::TeX("Control capacity ($\\phi$)"), 
+         y = "Probability density") +
     scale_y_continuous(limits = c(0,9)) +
     theme(legend.position = c(1, 0),
           legend.justification = c(1,0),
@@ -181,8 +181,8 @@ make_fig_control_capacity <- function(sl_characteristics){
     scale_color_manual(values = my_pallete()$dark_purple) +
     base_ggplot_theme() +
     labs(title = "(b) Control capacity of pollinators", 
-         x = latex2exp::TeX("control capacity ($\\phi$)"), 
-         y = "probability density") +
+         x = latex2exp::TeX("Control capacity ($\\phi$)"), 
+         y = "Probability density") +
     scale_y_continuous(limits = c(0,9)) +
     theme(legend.position = c(1, 0),
           legend.justification = c(1,0),
@@ -240,28 +240,28 @@ make_fig_species_partial <- function(species_model_cc){
   ylims <- c(-11, 20)
   p1 <- partial_plot(df_cc, "pushpull_o", "I(pushpull_comp + res)", "lm") + 
     labs(title = "(c)", 
-         x = "dependence asymmetry", 
-         y = latex2exp::TeX("partial residuals")) +
+         x = "Dependence asymmetry", 
+         y = latex2exp::TeX("Partial residuals")) +
     coord_cartesian(ylim = ylims)
   
   p2 <- partial_plot(df_cc, "strength_o", "I(strength_comp + res)", "lm") +
     labs(title = "(b)", 
-         x = "visitation strength", 
-         y = latex2exp::TeX("partial residuals")) +
+         x = "Visitation strength", 
+         y = latex2exp::TeX("Partial residuals")) +
     scale_x_continuous(breaks = log(c(1,10,100)), labels = exp) +
     coord_cartesian(ylim = ylims)
   
   
   p3 <- partial_plot(df_cc, "nested_o", "I(nested_comp + res)", "lm") +
     labs(title = "(a)", 
-         x = "contribution to nestedness", 
-         y = latex2exp::TeX("partial residuals")) +
[…]

### 2019-02-19 code/fig_structural_stability.R

@@ -8,8 +8,8 @@ make_fig_structural_stability <- function(critical_sp_df){
     dplyr::summarise_if(is.numeric, mean, na.rm = T)
   
   value <- 1
-  my.labs <- list(bquote(paste("critical species (", phi==.(value), ")")), 
-                  bquote(paste("redundant (", phi<.(value), ")")))
+  my.labs <- list(bquote(paste("Critical species (", phi ==.(value), ")")), 
+                  bquote(paste("Redundant (", phi<.(value), ")")))
   
   p1 <- st_df %>%
     ggplot(aes(x = value, colour = critical)) +
@@ -29,8 +29,8 @@ make_fig_structural_stability <- function(critical_sp_df){
           legend.justification = c(0,1),
           legend.background = element_rect(fill = "NA"), 
           legend.key.size = unit(0.15, "in")) +
-    labs(y = "probability density",
-         x = "scaled structural stability")
+    labs(y = "Probability density",
+         x = "Scaled structural stability")
   
   list(p1)
 
